### 2017-05-14 Pure Exploration/Pure_Exploration.Rmd
initial commit

---
title: "Pure Exploration"
author: "Tim Radtke"
date: "5/3/2017"
header-includes:
   #- \documentclass[a4paper,twoside,english]{article}
   - \usepackage[retainorgcmds]{IEEEtrantools}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \newtheorem{theorem}{Theorem}
   #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
   #- \usepackage{fontspec}
   #-   \setmainfont{Arial}
keep_tex: TRUE
output:
  pdf_document:
    number_sections: true
    keep_tex: true
    #latex_engine: xelatex
fontsize: 12pt
urlcolor: blue
---

In some previous chapter, we must have introduced the Canonical Exponential Family (see Garivier and Kaufmann, page 3) and the Kullback Leibler distance; especially also the KL for exponential family, for Bernoulli and Gaussian in particular, and so that $kl()$ is defined.

Before this chapter, a general introduction to A/B tests, with general sampling bounds for two variants case and uniform sampling. Get people hooked by general application in website optimization?

## Multi Armed Bandit and Pure Exploration 
\label{ch:MABandPureExploration}

We now move beyond the previously described problem of A/B testing by opening restrictions which we held so far. There are several ways in which to do that, but the main way will be two no longer require uniform sampling strategies. Further, we most often are interested in finding the best among $K$ arms. Other parts of the literature try to find the best $m$ among $K$ arms.

(What should come first? Paper by Kaufmann et al. about A/B tests but unifying FC and FB, or first make a differentiation between FB and FC?)

For a start, consider again the idea of sampling $K$ variants of for example websites which return a real-valued (as simple as Bernoulli) feedback coming from distributions $\nu_k$, $k \in \{1, \dots, K\}$. We still want to find the distribution $k$ for which the mean is equal to the highest mean among the distributions $\mu=\mu^*$. To do so, we are no longer restricted to sampling the distributions in a round-robin fashion as previously, but we are allowed to set up new sampling strategies with the general purpose of finding the best arm as quick as possible with as much confidence as possible.

To be a little more precise, we consider $K$ probability distributions $\nu_1, \dots, \nu_k$ with respective means $\mu_1, \dots, \mu_k$. At each round $t = 1, 2, \dots$, we can decide from which distribution to sample, that is, we pick an arm $A_t \in \mathcal{A} = \{1, \dots, k\}$, and we observe the feedback $X_t$ from distribution $\mu_{A_t}$. What distinguishes this from the A/B testing setting is the fact that by picking an arm we actively choose at each time the distribution from which we would like to receive the next sample. We are no longer restricted to the uniform sampling strategy. In fact, our goal is define the a sampling strategy $(A_t)_t$ with characteristics that are to be analyzed and ideally optimal in a sense to be specified.

In any case, the literature considered in this chapter is concerned with strategies whose objective it is to identify the best arm defined by $\mu^* = \max_{1\leq a \leq K} \mu_a$. In contrast to multi-armed bandit problems concerned with optimizing regret (Auer et al, Agrawal et al), such algorithm could in an extreme case sample the best arm only once but the inferior arms multiple times, if this helps identifying it as the clearly best arm for some reason. In general, it is only important to make a single correct decision *after* the final sample has been drawn.

As described in Garivier and Kaufmann (2016), a general strategy to find $\mu^*$ can be defined by three attributes:

(Add sigma field definition???)

- a *sampling rule* $(A_t)_t$
- a *stopping rule* $\tau$
- a *decision rule* $\hat{a}_t \quad (=\hat{a}_t(\delta))$

This allows to describe the goal then as finding $\hat{a}_t \in \arg \max_a \mu_a$ with the largest confidence $\delta$ possible while constrained to minimizing the rounds $\tau$ needed to find the estimate and confidence.

Recent literature has dealt with this problem by specifying one of $\{\tau, \delta\}$ upfront and then optimizing the other. These two settings are called *fixed budget* (FB) and *fixed confidence* (FC).

Fixed confidence can seem like a more natural approach to the problems at first. Especially when considering the notion of statistical significance and the famous $\alpha = 0.05$ confidence level that comes with the attitude of "We do not accept any difference as significant unless a difference as large or larger as the one observed has a probability of less than 5% assuming there is no effect". In the problem of identifying a superior arm, assuming there exists a superior arm, this notion might lead to very large sample sizes depending on the effect size. In particular, in the application of web optimization, where websites are optimized by conversion rate, which might be at a level of $0.06$, for example, it would take $41575$ samples to detect a 10% (or larger) difference in conversion rate at a 5% significance (and 95% power) [source](http://www.evanmiller.org/ab-testing/sample-size.html#!6;95;5;10;1).

But in the situation described above, we're not really fixing the confidence level. We are fixing the number of samples to make sure that a given effect size could be detected as significant difference at some confidence level (here, 5%). But even if the actual difference between the two versions is less than the minimum detectable effect size, the test could give us some detected difference at some confidence. Looking at it this way, the fixed budget setting may actually be more alike to standard A/B testing procedures, in which a sample size is fixed *before* the test is run and determined by the minimum detectable effect, and confidence level and power of the test.

Consequently, the fixed confidence setting is concerned with fixing a maximal level of risk $\delta$ that one is willing to accept. While minimizing the expected sample size called *sample complexity*, a corresponding strategy needs to fulfill $\mathbb{P}(\hat{a}_\tau \notin \arg \max \mu_a)\leq \delta$ (and then is called $\delta$-PAC). Compare Garivier and Kaufmann (2016).

On the other hand, the fixed budget setting describes strategies which fix the number of samples $\tau$ upfront and then try to minimize the probability of error $\mathbb{P}(\hat{a}_\tau \notin \arg \max \mu_a)$ of the decision that's made after the last sample has been drawn.

Alternative formulations which are more rare in the literature are so called *anytime* strategies aiming to optimize the probability of error and the sample complexity in a way such that the procedure can be stopped at anytime (after every round) and return a decision with a certain guaranteed level of risk. See [Jun and Nowak (2016)](http://proceedings.mlr.press/v48/jun16-supp.pdf) for one discussion of the topic. The advantage over the fixed budget case is that users do not have to specify a budget in advance. This is especially helpful, if it is not foreseeable how many samples will be available. Since some fixed budget strategies explore arms in stages, they might not be able to guarantee a confidence when stopped before their budgeted rounds.

Other literature tries to analyze the two settings of fixed budget and fixed confidence seperately, but to make them comparable by using complexity measures for problems that are on the same scale (see Kaufmann et al. 2016, Kaufmann et al. 2017). We will come back to this topic in chapter ...

### Fixed Confidence

The setting of fixed confidence can be framed as a sequential testing problem. After each round, we might ask ourselves whether we have sufficient evidence to make a $\delta$-PAC decision. If we cannot make such decision, we continue to draw the next sample. And because we are not restricted to uniform sampling strategies, we pull the next sample so as to gain as much information with the purpose of minimizing the expected overall number of samples until we can make the $\delta$-PAC decision.

Descriptions like this lead back to Chernoff (1959) describing settings in which experiments (arms) are performed sequentially. After each round, it has to be decided whether a next experiment is performed or whether the final decision is made based on a hypothesis test where the decision selects between one of two actions. In contrast to the modern literature, Chernoff takes into account the cost that samples have and acknowledges that his derivations hold when the cost of sampling goes to zero. In particular, he compares two Bernoulli distributions based on their means $\mu_1, \mu_2$. The problem is formulated as hypotheses, with $H_0: \mu_1 > \mu_2$ and $H_1: \mu_1 \leq \mu_2$. After $n$ samples, one observes for the paramater vector $\mu = (\mu_1, \mu_2)$ the maximum likelihood estimate $\hat{\mu} = (\hat{\mu}_1, \hat{\mu}_2)=(m_1/n_1, m_2/n_2)$, where $m_1$ are the successes from distribution 1 after $n_1$ pulls. Assuming $\hat{\mu}_1 > \hat{\mu}_2$, and assuming that we believe this is the actual state of the world, $\mu =\hat{\mu}$, we assume $H_0$ and want to test it against the alternative $H_1$ represented by $\stackrel{\sim}{\mu}$, which is an undefined vector with some $\stackrel{\sim}{\mu}_1 \leq \stackrel{\sim}{\mu}_2$ so that $H_1$ holds.

Coming from sequential likelihood-ratio tests, Chernoff motivates the use of the Kullback-Leibler divergence to determine from which distribution to sample next. He computes the divergence for the first distribution comparing $\hat{\mu}_1$ and $\stackrel{\sim}{\mu}_1$, as well as the divergence for the second distribution comparing $\hat{\mu}_2$ with $\stackrel{\sim}{\mu}_2$. Chernoff shows to pick the distribution next which maximizes the Kullback-Leibler divergence. The intuition for this comes from how Chernoff computes the alternative $\stackrel{\sim}{\mu}$. It holds that $\stackrel{\sim}{\mu}_1$ = $\stackrel{\sim}{\mu}_2$ = $\stackrel{\sim}{\mu}_i$, where $\stackrel{\sim}{\mu}_i$ is a weighted average of $\hat{\mu}_1$ and $\hat{\mu}_2$. As noted by Chernoff (page 759), the weights $(1-\lambda, \lambda)$ are proportional to how often each distribution has been sampled.

Now, what happens is that long term, we expect the maximum likelihood estimates $\hat{\mu}$ to be close to $\mu$. At the same time, given that $\hat{\mu}$ does not fluctuate much anymore, there will be weights $(1-\lambda, \lambda)$ such that the two distributions are sampled in fixed proportions (a share of $\lambda$ for the second distribution), and the Kullback-Leibler divergence for each distribution will be equal: $D_{KL}(\mu_1, \stackrel{\sim}{\mu}_i^*, \nu_1) = D_{KL}(\mu_2, \stackrel{\sim}{\mu}_i^*, \nu_2)$, where $\stackrel{\sim}{\mu}_i^* = (1-\lambda) \mu_1 + \lambda \mu_2$.

(Is this not just the Chernoff Information as described in Garivier & Kaufmann page 6?)

This observation can be interpreted similar to how under standard composite hypothesis testing, one compares the $H_1$ against the value under $H_0$ that is the closest to $H_1$. For example, if we observe samples from a normal distribution and estimate the mean with the sample mean which is observed to be positive, $\hat{\mu}>0$, we might want to test $H_0: \mu \leq 0$ against $H_1: \mu > 0$. To do so, we compare $\hat{\mu}$ against the value $\mu_{H_0} \in (\infty, 0]$ closest to $H_1$; thus $\mu_{H_0} = 0$.

In our case, as argued by Chernoff, the mean vector closest to $\mu$ under the alternative hypothesis is given by $\stackrel{\sim}{\mu}^*$. Under this value, it is the most difficult to properly distinguish between the different hypotheses. It is the point at which we stand the worst chances to gain new information from sampling any of the two arms (as represented by the fact that both Kullback-Leibler divergences are equal). Consequently (ELABORATE!?), $\stackrel{\sim}{\mu}^* = \arg \min_{\stackrel{\sim}{\mu}} \max_{\nu_i} D_{KL}(\mu, \stackrel{\sim}{\mu}, \nu_i)$.

This result can be described as the solution to a zero-sum two-player minimax game, in which

- the experimenter picks from which distribution to sample from with the goal of maximizing $D_{KL}$
- then the opponent picks the alternative specification true under the alternative hypothesis to minimize $D_{KL}$

and the value of the game is given by $\max_{\nu} \min_{\omega} D_{KL}(\mu, \omega, \nu)$. Then, with the opponent picking $\omega = \stackrel{\sim}{\mu}^*$, the experimenter will choose the randomized maxmin strategy of picking $\nu_1$ and $\nu_2$ in proportions $(1-\lambda)$ and $\lambda$.

Very similar games have been described by by Russo (2016) and Garivier and Kaufmann (2016). Both analyze settings of pure exploration bandits with fixed confidence. While Garivier and Kaufmann find the game as part of their lower bound on the sample complexity $\mathbb{E}_{\mu}[\tau_{\delta}]$ in their theorem 1, Russo finds his version when deriving the posterior probability on selecting the wrong arm and determines that the solution to the game describes the asymptotically optimal allocation of draws for each arm (page 17).

However, as pointed out by Russo (2016), this game is based on the knowledge of the true parameter $\mu$ ($\bm{\theta}^*$ in his notation) and thus the optimal allocation is not readily available when designing an algorithm to solve the exploration problem. Instead, he shows that his algorithms reach the optimal allocation asymptotically eventhough they do not actively try to solve maxmin game.

(Put in more exact description of the problem solved by Russo so that one can exactly compare the different games and the exponents given by Russo and Garivier & Kaufmann)

In contrast, Garivier and Kaufmann (2016) do devise a sampling rule that is based on estimating the optimal sampling proportions $w^*(\bm{\mu})$ based on the current estimates $\hat{\mu}(t)$ leading to the plug-in estimates $w^*(\hat{\mu}(t))$. However, the authors acknowledge the fact that using these plug-in estimates in order to estimate the optimal sampling proportions may well lead to problems if the initial estimates $\hat{\mu}(t)$ are off for small $t$. A bad estimate can lead the bandit algorithm to abandon an arm in the further sampling. Then, an arm that should be explored more -- which would lead to a fix of the initial estimate -- might not be explored and distort the overall proportions and in the worst case the final decision. In the description of Garivier and Kaufmann, such sampling rule based on plug-in estimates would simply fail from time to time. Thus, they adjust the solution of the optimization problem solving for $w^*$ in order to enforce sufficient exploration of arms, see their lemma 7. More straightforward however is the adjustment in their *D-Tracking* rule in lemma 8, which checks every round whether there exists any arm with pulls $N_a(t) < \sqrt{t} - K/2$ lacking behind the other arms. If this is fulfilled, the arm with the least amount of pulls is pulled. Else, the pull is determined by the plug-in estimates. These rules then also satisfy what was described by Russo: Their empirical sampling proportions converge to the optimal proportions, compare proposition 9 in Garivier and Kaufmann (2016) and proposition 7 in Russo (2016).

#### Game, and Lower Bound on the Sample Complexity

We will now derive the lower bound on the sample complexity in the fixed confidence bandit setting demonstrated in Garivier and Kaufmann (2016).

Consider again the setting as defined in section \ref{ch:MABandPureExploration}. For their lower bound, Garivier and Kaufmann (2016) consider bandit models where the distributions come from one-parameter exponential families. Consequently, the distributions can be parameterized by their means. Therefore, if we let $\mathcal{S}$ to be a set of bandit models with $K$ distributions each, then each model is fully defined by a vector $\bm{\mu} = (\mu_1, \dots, \mu_K)$. Assume that every $\bm{\mu} \in \mathcal{S}$ has a unique maximum given by $a^*(\bm{\mu})$ such that $\mu_{a^*} > \max_{a \neq a^*(\bm{\mu})} \mu_a$. In order to fix the confidence, we specify the risk $\delta$. The strategies corresponding to this risk are called $\delta$-PAC if for every $\bm{\mu} \in \mathcal{S}$, $\mathbb{P}_{\bm{\mu}}(\tau_{\delta} < \infty) = 1$ (the strategy ends surely with after finite samples) and $\mathbb{P}_{\bm{\mu}}(\hat{a}_{\tau_{\delta}} \neq a^*) \leq \delta$ (the probability of picking not the optimal arm is smaller than the fixed risk). As in Garivier and Kaufmann, we introduce the set of problems for which the optimal arm is different from the one in $\bm{\mu}$:

\begin{equation*}
\text{Alt}(\bm{\mu}) := \{\bm{\lambda} \in \mathcal{S}: a^*(\bm{\lambda}) \neq a^*(\bm{\mu})\}
\end{equation*}

where $\bm{\lambda}$ is the vector of means defining the distributions of the alternative problem to $\bm{\mu}$. Lastly, we have the set of probability distributions on the arms $\mathcal{A}$: $\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}$. \marginpar{Give more intuition for what these probability distributions are} We are now ready to state the theorem.

\begin{theorem}[Garivier and Kaufmann, 2016] \label{theorem:GarivierKaufmannTheorem1}
Let $\delta \in (0,1)$. For any $\delta$-PAC strategy and any bandit model $\bm{\mu} \in \mathcal{S}$,

\begin{equation*}
\mathbb{E}_{\bm{\mu}} [\tau_{\delta}] \geq T^*(\bm{\mu}) \text{\em{kl}}(\delta,1-\delta),
\end{equation*}

where

\begin{equation} \label{eq:GarivierKaufmann_Theorem1_Game}
T^*(\bm{\mu})^{-1} := \sup_{w \in \Sigma_K} \inf_{\bm{\lambda} \in \text{\em{Alt}}(\bm{\mu})} \left( \sum_{a=1}^K w_a d(\mu_a, \lambda_a)\right) .
\end{equation}
\end{theorem}

In equation \eqref{eq:GarivierKaufmann_Theorem1_Game}, we again see the game occur that we describe above. In this case, the game is about the minimal number of rounds $T = T(w,\lambda)$ needed for any bandit strategy to ensure that the strategy fulfills the $\delta$-PAC constraint. Consider that we have the inverse of $T$ in equation \eqref{eq:GarivierKaufmann_Theorem1_Game}. Then we see that

- the statistician tries to minimize the number of rounds by choosing the optimal proportions of draws $w^*$ for each arm
- the opponent picks the alternative model $\bm{\lambda}$ so as to maximize the number of necessary rounds

When choosing $\bm{\lambda}$, the opponent will choose an alternative as close to the original model as possible so as to minimize the Kullback-Leibler divergence $d(\mu_a, \lambda_a)$. As already noted in Chernoff (1959), this will minimize the information available to the statistician and make it difficult to distinguish between the cases with confidence.

```{r, echo = FALSE, fig.cap = "Statistician chooses the curve by picking the weights w, then the opponent picks lambda. In the case of a two-armed bandit, we have w1+w2 = 1. The plot suggests that uniform allocation is optimal for Bernoulli bandits. The thick line shows the result for w1=w2=0.5."}
dkl <- function(x,y) {x*log(x/y) + (1-x)*log((1-x)/(1-y))}
mu <- c(0.7, 0.2)
#lambda <- c(0.4, 0.2)
w1 <- 1
w2 <- 0
lambda_2 <- seq(0,1,by = 0.01)

plot(lambda_2,
     w1*dkl(mu[1],lambda_2) + w2 * dkl(mu[2],lambda_2), type = "l",
     xlim = c(0,1), ylim = c(0,3),
     xlab = expression(paste(lambda)),
     ylab = expression(paste("w_1 * kl(", mu, ",", lambda, ") + w_2 * kl(", mu, ",", lambda, ")")))
for(i in seq(0,1, by = 0.1)) {
  lines(lambda_2,
        i * dkl(mu[1],lambda_2) + (1-i)* dkl(mu[2],lambda_2))
}
abline(v = mean(mu))
lines(lambda_2,
        0.5 * dkl(mu[1],lambda_2) + 0.5* dkl(mu[2],lambda_2), col = "red", lwd = 2)
```

```{r, echo = FALSE, include = FALSE, fig.cap = "Statistician chooses the curve by picking the weights w, then the opponent picks lambda. In the case of a three-armed bandit, we have w1+w2+w3 = 1. Holding w3 fixed at 0.4, the plot again suggests uniform allocation for the remaining two arms at w1=w2=0.3."}
dkl <- function(x,y) {x*log(x/y) + (1-x)*log((1-x)/(1-y))}
mu <- c(0.7, 0.2)
#lambda <- c(0.4, 0.2)
w1 <- 0.6
w2 <- 0
w3 <- 0.4
lambda_2 <- seq(0,1,by = 0.01)

plot(lambda_2,
     w1*dkl(mu[1],lambda_2) + w2 * dkl(mu[2],lambda_2), type = "l",
     xlim = c(0,1), ylim = c(0,3),
     xlab = expression(paste(lambda)),
     ylab = expression(paste("w_1 * kl(", mu, ",", lambda, ") + w_2 * kl(", mu, ",", lambda, ")")))
for(i in seq(0,1-w3, by = 0.1)) {
  lines(lambda_2,
        i * dkl(mu[1],lambda_2) + (1-i-w3)* dkl(mu[2],lambda_2))
}
abline(v = mean(mu))
lines(lambda_2,
        0.3 * dkl(mu[1],lambda_2) + 0.3* dkl(mu[2],lambda_2), col = "red")
```

The plot above specifies again the game and the reasoning of the opponent. Given a model $\bm{\mu} = (\mu_1, \dots, \mu_K)$ with $\mu_1 > \mu_2 \geq \dots \geq \mu_K$, the experimenter chooses the proportions of arm draws $w = (w_a)_a$. Then the opponent chooses an arm $a \in \{2, \dots, K\}$ and chooses the alternative distribution for arm $a$, $\lambda_a = \arg \min_{\lambda} w_1 d(\mu_1, \lambda) + w_a d(\mu_a, \lambda)$. The payoff of the game is then the minimal number of rounds $T$ so that the restriction $Tw_1 d(\mu_1, \lambda_a - \epsilon) + Tw_a d(\mu_a, \lambda + \epsilon) \geq \text{kl}(\delta, 1-\delta)$ holds when $a^*(\bm{\mu}) \neq a^*(\bm{\lambda})$ due to $\epsilon$. Consequently, the value is given by

\begin{equation}
T(w, a, \delta) = \frac{\text{kl}(\delta, 1-\delta)}{w_1 d(\mu_1, \lambda_a - \epsilon) + w_a d(\mu_a, \lambda + \epsilon)}
\end{equation}

which is comparable to the result in Theorem (Garivier and Kaufmann, 2016) \ref{theorem:GarivierKaufmannTheorem1}.

### Fixed Budget

Given the success of UCB, why not try it for this problem as well?

-> What would be the equivalent algorithm?
-> Audibert et al. (2009)
-> Adjustment proposed by Audibert et al. (2015)
    -> Choose a linear in t to explore more!
    -> Show upper bound
    -> Give at least the standard steps of lower bound proof

### 2017-05-14 Pure Exploration/Pure_Exploration.tex
initial commit

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={Pure Exploration},
            pdfauthor={Tim Radtke},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{Pure Exploration}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Tim Radtke}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{5/3/2017}

\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage{bm}
\usepackage{amsmath}
\newtheorem{theorem}{Theorem}

\begin{document}
\maketitle

In some previous chapter, we must have introduced the Canonical
Exponential Family (see Garivier and Kaufmann, page 3) and the Kullback
Leibler distance; especially also the KL for exponential family, for
Bernoulli and Gaussian in particular, and so that \(kl()\) is defined.

Before this chapter, a general introduction to A/B tests, with general
sampling bounds for two variants case and uniform sampling. Get people
hooked by general application in website optimization?

\subsection{Multi Armed Bandit and Pure
Exploration}\label{multi-armed-bandit-and-pure-exploration}

\label{ch:MABandPureExploration}

We now move beyond the previously described problem of A/B testing by
opening restrictions which we held so far. There are several ways in
which to do that, but the main way will be two no longer require uniform
sampling strategies. Further, we most often are interested in finding
the best among \(K\) arms. Other parts of the literature try to find the
best \(m\) among \(K\) arms.

(What should come first? Paper by Kaufmann et al. about A/B tests but
unifying FC and FB, or first make a differentiation between FB and FC?)

For a start, consider again the idea of sampling \(K\) variants of for
example websites which return a real-valued (as simple as Bernoulli)
feedback coming from distributions \(\nu_k\), \(k \in \{1, \dots, K\}\).
We still want to find the distribution \(k\) for which the mean is equal
to the highest mean among the distributions \(\mu=\mu^*\). To do so, we
are no longer restricted to sampling the distributions in a round-robin
fashion as previously, but we are allowed to set up new sampling
strategies with the general purpose of finding the best arm as quick as
possible with as much confidence as possible.

To be a little more precise, we consider \(K\) probability distributions
\(\nu_1, \dots, \nu_k\) with respective means \(\mu_1, \dots, \mu_k\).
At each round \(t = 1, 2, \dots\), we can decide from which distribution
to sample, that is, we pick an arm
\(A_t \in \mathcal{A} = \{1, \dots, k\}\), and we observe the feedback
\(X_t\) from distribution \(\mu_{A_t}\). What distinguishes this from
the A/B testing setting is the fact that by picking an arm we actively
choose at each time the distribution from which we would like to receive
the next sample. We are no longer restricted to the uniform sampling
strategy. In fact, our goal is define the a sampling strategy
\((A_t)_t\) with characteristics that are to be analyzed and ideally
optimal in a sense to be specified.

In any case, the literature considered in this chapter is concerned with
strategies whose objective it is to identify the best arm defined by
\(\mu^* = \max_{1\leq a \leq K} \mu_a\). In contrast to multi-armed
bandit problems concerned with optimizing regret (Auer et al, Agrawal et
al), such algorithm could in an extreme case sample the best arm only
once but the inferior arms multiple times, if this helps identifying it
as the clearly best arm for some reason. In general, it is only
important to make a single correct decision \emph{after} the final
sample has been drawn.

As described in Garivier and Kaufmann (2016), a general strategy to find
\(\mu^*\) can be defined by three attributes:

(Add sigma field definition???)

\begin{itemize}
\tightlist
\item
  a \emph{sampling rule} \((A_t)_t\)
\item
  a \emph{stopping rule} \(\tau\)
\item
  a \emph{decision rule} \(\hat{a}_t \quad (=\hat{a}_t(\delta))\)
\end{itemize}

This allows to describe the goal then as finding
\(\hat{a}_t \in \arg \max_a \mu_a\) with the largest confidence
\(\delta\) possible while constrained to minimizing the rounds \(\tau\)
needed to find the estimate and confidence.

Recent literature has dealt with this problem by specifying one of
\(\{\tau, \delta\}\) upfront and then optimizing the other. These two
settings are called \emph{fixed budget} (FB) and \emph{fixed confidence}
(FC).

Fixed confidence can seem like a more natural approach to the problems
at first. Especially when considering the notion of statistical
significance and the famous \(\alpha = 0.05\) confidence level that
comes with the attitude of ``We do not accept any difference as
significant unless a difference as large or larger as the one observed
has a probability of less than 5\% assuming there is no effect''. In the
problem of identifying a superior arm, assuming there exists a superior
arm, this notion might lead to very large sample sizes depending on the
effect size. In particular, in the application of web optimization,
where websites are optimized by conversion rate, which might be at a
level of \(0.06\), for example, it would take \(41575\) samples to
detect a 10\% (or larger) difference in conversion rate at a 5\%
significance (and 95\% power)
\href{http://www.evanmiller.org/ab-testing/sample-size.html\#!6;95;5;10;1}{source}.

But in the situation described above, we're not really fixing the
confidence level. We are fixing the number of samples to make sure that
a given effect size could be detected as significant difference at some
confidence level (here, 5\%). But even if the actual difference between
the two versions is less than the minimum detectable effect size, the
test could give us some detected difference at some confidence. Looking
at it this way, the fixed budget setting may actually be more alike to
standard A/B testing procedures, in which a sample size is fixed
\emph{before} the test is run and determined by the minimum detectable
effect, and confidence level and power of the test.

Consequently, the fixed confidence setting is concerned with fixing a
maximal level of risk \(\delta\) that one is willing to accept. While
minimizing the expected sample size called \emph{sample complexity}, a
corresponding strategy needs to fulfill
\(\mathbb{P}(\hat{a}_\tau \notin \arg \max \mu_a)\leq \delta\) (and then
is called \(\delta\)-PAC). Compare Garivier and Kaufmann (2016).

On the other hand, the fixed budget setting describes strategies which
fix the number of samples \(\tau\) upfront and then try to minimize the
probability of error \(\mathbb{P}(\hat{a}_\tau \notin \arg \max \mu_a)\)
of the decision that's made after the last sample has been drawn.

Alternative formulations which are more rare in the literature are so
called \emph{anytime} strategies aiming to optimize the probability of
error and the sample complexity in a way such that the procedure can be
stopped at anytime (after every round) and return a decision with a
certain guaranteed level of risk. See
\href{http://proceedings.mlr.press/v48/jun16-supp.pdf}{Jun and Nowak
(2016)} for one discussion of the topic. The advantage over the fixed
budget case is that users do not have to specify a budget in advance.
This is especially helpful, if it is not foreseeable how many samples
will be available. Since some fixed budget strategies explore arms in
stages, they might not be able to guarantee a confidence when stopped
before their budgeted rounds.

Other literature tries to analyze the two settings of fixed budget and
fixed confidence seperately, but to make them comparable by using
complexity measures for problems that are on the same scale (see
Kaufmann et al. 2016, Kaufmann et al. 2017). We will come back to this
topic in chapter \ldots{}

\subsubsection{Fixed Confidence}\label{fixed-confidence}

The setting of fixed confidence can be framed as a sequential testing
problem. After each round, we might ask ourselves whether we have
sufficient evidence to make a \(\delta\)-PAC decision. If we cannot make
such decision, we continue to draw the next sample. And because we are
not restricted to uniform sampling strategies, we pull the next sample
so as to gain as much information with the purpose of minimizing the
expected overall number of samples until we can make the \(\delta\)-PAC
decision.

Descriptions like this lead back to Chernoff (1959) describing settings
in which experiments (arms) are performed sequentially. After each
round, it has to be decided whether a next experiment is performed or
whether the final decision is made based on a hypothesis test where the
decision selects between one of two actions. In contrast to the modern
literature, Chernoff takes into account the cost that samples have and
acknowledges that his derivations hold when the cost of sampling goes to
zero. In particular, he compares two Bernoulli distributions based on
their means \(\mu_1, \mu_2\). The problem is formulated as hypotheses,
with \(H_0: \mu_1 > \mu_2\) and \(H_1: \mu_1 \leq \mu_2\). After \(n\)
samples, one observes for the paramater vector \(\mu = (\mu_1, \mu_2)\)
the maximum likelihood estimate
\(\hat{\mu} = (\hat{\mu}_1, \hat{\mu}_2)=(m_1/n_1, m_2/n_2)\), where
\(m_1\) are the successes from distribution 1 after \(n_1\) pulls.
Assuming \(\hat{\mu}_1 > \hat{\mu}_2\), and assuming that we believe
this is the actual state of the world, \(\mu =\hat{\mu}\), we assume
\(H_0\) and want to test it against the alternative \(H_1\) represented
by \(\stackrel{\sim}{\mu}\), which is an undefined vector with some
\(\stackrel{\sim}{\mu}_1 \leq \stackrel{\sim}{\mu}_2\) so that \(H_1\)
holds.

Coming from sequential likelihood-ratio tests, Chernoff motivates the
use of the Kullback-Leibler divergence to determine from which
distribution to sample next. He computes the divergence for the first
distribution comparing \(\hat{\mu}_1\) and \(\stackrel{\sim}{\mu}_1\),
as well as the divergence for the second distribution comparing
\(\hat{\mu}_2\) with \(\stackrel{\sim}{\mu}_2\). Chernoff shows to pick
the distribution next which maximizes the Kullback-Leibler divergence.
The intuition for this comes from how Chernoff computes the alternative
\(\stackrel{\sim}{\mu}\). It holds that \(\stackrel{\sim}{\mu}_1\) =
\(\stackrel{\sim}{\mu}_2\) = \(\stackrel{\sim}{\mu}_i\), where
\(\stackrel{\sim}{\mu}_i\) is a weighted average of \(\hat{\mu}_1\) and
\(\hat{\mu}_2\). As noted by Chernoff (page 759), the weights
\((1-\lambda, \lambda)\) are proportional to how often each distribution
has been sampled.

Now, what happens is that long term, we expect the maximum likelihood
estimates \(\hat{\mu}\) to be close to \(\mu\). At the same time, given
that \(\hat{\mu}\) does not fluctuate much anymore, there will be
weights \((1-\lambda, \lambda)\) such that the two distributions are
sampled in fixed proportions (a share of \(\lambda\) for the second
distribution), and the Kullback-Leibler divergence for each distribution
will be equal:
\(D_{KL}(\mu_1, \stackrel{\sim}{\mu}_i^*, \nu_1) = D_{KL}(\mu_2, \stackrel{\sim}{\mu}_i^*, \nu_2)\),
where \(\stackrel{\sim}{\mu}_i^* = (1-\lambda) \mu_1 + \lambda \mu_2\).

(Is this not just the Chernoff Information as described in Garivier \&
Kaufmann page 6?)

This observation can be interpreted similar to how under standard
composite hypothesis testing, one compares the \(H_1\) against the value
under \(H_0\) that is the closest to \(H_1\). For example, if we observe
samples from a normal distribution and estimate the mean with the sample
mean which is observed to be positive, \(\hat{\mu}>0\), we might want to
test \(H_0: \mu \leq 0\) against \(H_1: \mu > 0\). To do so, we compare
\(\hat{\mu}\) against the value \(\mu_{H_0} \in (\infty, 0]\) closest to
\(H_1\); thus \(\mu_{H_0} = 0\).

In our case, as argued by Chernoff, the mean vector closest to \(\mu\)
under the alternative hypothesis is given by \(\stackrel{\sim}{\mu}^*\).
Under this value, it is the most difficult to properly distinguish
between the different hypotheses. It is the point at which we stand the
worst chances to gain new information from sampling any of the two arms
(as represented by the fact that both Kullback-Leibler divergences are
equal). Consequently (ELABORATE!?),
\(\stackrel{\sim}{\mu}^* = \arg \min_{\stackrel{\sim}{\mu}} \max_{\nu_i} D_{KL}(\mu, \stackrel{\sim}{\mu}, \nu_i)\).

This result can be described as the solution to a zero-sum two-player
minimax game, in which

\begin{itemize}
\tightlist
\item
  the experimenter picks from which distribution to sample from with the
  goal of maximizing \(D_{KL}\)
\item
  then the opponent picks the alternative specification true under the
  alternative hypothesis to minimize \(D_{KL}\)
\end{itemize}

and the value of the game is given by
\(\max_{\nu} \min_{\omega} D_{KL}(\mu, \omega, \nu)\). Then, with the
opponent picking \(\omega = \stackrel{\sim}{\mu}^*\), the experimenter
will choose the randomized maxmin strategy of picking \(\nu_1\) and
\(\nu_2\) in proportions \((1-\lambda)\) and \(\lambda\).

Very similar games have been described by by Russo (2016) and Garivier
and Kaufmann (2016). Both analyze settings of pure exploration bandits
with fixed confidence. While Garivier and Kaufmann find the game as part
of their lower bound on the sample complexity
\(\mathbb{E}_{\mu}[\tau_{\delta}]\) in their theorem 1, Russo finds his
version when deriving the posterior probability on selecting the wrong
arm and determines that the solution to the game describes the
asymptotically optimal allocation of draws for each arm (page 17).

However, as pointed out by Russo (2016), this game is based on the
knowledge of the true parameter \(\mu\) (\(\bm{\theta}^*\) in his
notation) and thus the optimal allocation is not readily available when
designing an algorithm to solve the exploration problem. Instead, he
shows that his algorithms reach the optimal allocation asymptotically
eventhough they do not actively try to solve maxmin game.

(Put in more exact description of the problem solved by Russo so that
one can exactly compare the different games and the exponents given by
Russo and Garivier \& Kaufmann)

In contrast, Garivier and Kaufmann (2016) do devise a sampling rule that
is based on estimating the optimal sampling proportions
\(w^*(\bm{\mu})\) based on the current estimates \(\hat{\mu}(t)\)
leading to the plug-in estimates \(w^*(\hat{\mu}(t))\). However, the
authors acknowledge the fact that using these plug-in estimates in order
to estimate the optimal sampling proportions may well lead to problems
if the initial estimates \(\hat{\mu}(t)\) are off for small \(t\). A bad
estimate can lead the bandit algorithm to abandon an arm in the further
sampling. Then, an arm that should be explored more -- which would lead
to a fix of the initial estimate -- might not be explored and distort
the overall proportions and in the worst case the final decision. In the
description of Garivier and Kaufmann, such sampling rule based on
plug-in estimates would simply fail from time to time. Thus, they adjust
the solution of the optimization problem solving for \(w^*\) in order to
enforce sufficient exploration of arms, see their lemma 7. More
straightforward however is the adjustment in their \emph{D-Tracking}
rule in lemma 8, which checks every round whether there exists any arm
with pulls \(N_a(t) < \sqrt{t} - K/2\) lacking behind the other arms. If
this is fulfilled, the arm with the least amount of pulls is pulled.
Else, the pull is determined by the plug-in estimates. These rules then
also satisfy what was described by Russo: Their empirical sampling
proportions converge to the optimal proportions, compare proposition 9
in Garivier and Kaufmann (2016) and proposition 7 in Russo (2016).

\paragraph{Game, and Lower Bound on the Sample
Complexity}\label{game-and-lower-bound-on-the-sample-complexity}

We will now derive the lower bound on the sample complexity in the fixed
confidence bandit setting demonstrated in Garivier and Kaufmann (2016).

Consider again the setting as defined in section
\ref{ch:MABandPureExploration}. For their lower bound, Garivier and
Kaufmann (2016) consider bandit models where the distributions come from
one-parameter exponential families. Consequently, the distributions can
be parameterized by their means. Therefore, if we let \(\mathcal{S}\) to
be a set of bandit models with \(K\) distributions each, then each model
is fully defined by a vector \(\bm{\mu} = (\mu_1, \dots, \mu_K)\).
Assume that every \(\bm{\mu} \in \mathcal{S}\) has a unique maximum
given by \(a^*(\bm{\mu})\) such that
\(\mu_{a^*} > \max_{a \neq a^*(\bm{\mu})} \mu_a\). In order to fix the
confidence, we specify the risk \(\delta\). The strategies corresponding
to this risk are called \(\delta\)-PAC if for every
\(\bm{\mu} \in \mathcal{S}\),
\(\mathbb{P}_{\bm{\mu}}(\tau_{\delta} < \infty) = 1\) (the strategy ends
surely with after finite samples) and
\(\mathbb{P}_{\bm{\mu}}(\hat{a}_{\tau_{\delta}} \neq a^*) \leq \delta\)
(the probability of picking not the optimal arm is smaller than the
fixed risk). As in Garivier and Kaufmann, we introduce the set of
problems for which the optimal arm is different from the one in
\(\bm{\mu}\):

\begin{equation*}
\text{Alt}(\bm{\mu}) := \{\bm{\lambda} \in \mathcal{S}: a^*(\bm{\lambda}) \neq a^*(\bm{\mu})\}
\end{equation*}

where \(\bm{\lambda}\) is the vector of means defining the distributions
of the alternative problem to \(\bm{\mu}\). Lastly, we have the set of
probability distributions on the arms \(\mathcal{A}\):
\(\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}\).
\marginpar{Give more intuition for what these probability distributions are}
We are now ready to state the theorem.

\begin{theorem}[Garivier and Kaufmann, 2016] \label{theorem:GarivierKaufmannTheorem1}
Let $\delta \in (0,1)$. For any $\delta$-PAC strategy and any bandit model $\bm{\mu} \in \mathcal{S}$,

\begin{equation*}
\mathbb{E}_{\bm{\mu}} [\tau_{\delta}] \geq T^*(\bm{\mu}) \text{\em{kl}}(\delta,1-\delta),
\end{equation*}

where

\begin{equation} \label{eq:GarivierKaufmann_Theorem1_Game}
T^*(\bm{\mu})^{-1} := \sup_{w \in \Sigma_K} \inf_{\bm{\lambda} \in \text{\em{Alt}}(\bm{\mu})} \left( \sum_{a=1}^K w_a d(\mu_a, \lambda_a)\right) .
\end{equation}
\end{theorem}

In equation \eqref{eq:GarivierKaufmann_Theorem1_Game}, we again see the
game occur that we describe above. In this case, the game is about the
minimal number of rounds \(T = T(w,\lambda)\) needed for any bandit
strategy to ensure that the strategy fulfills the \(\delta\)-PAC
constraint. Consider that we have the inverse of \(T\) in equation
\eqref{eq:GarivierKaufmann_Theorem1_Game}. Then we see that

\begin{itemize}
\tightlist
\item
  the statistician tries to minimize the number of rounds by choosing
  the optimal proportions of draws \(w^*\) for each arm
\item
  the opponent picks the alternative model \(\bm{\lambda}\) so as to
  maximize the number of necessary rounds
\end{itemize}

When choosing \(\bm{\lambda}\), the opponent will choose an alternative
as close to the original model as possible so as to minimize the
Kullback-Leibler divergence \(d(\mu_a, \lambda_a)\). As already noted in
Chernoff (1959), this will minimize the information available to the
statistician and make it difficult to distinguish between the cases with
confidence.

\begin{figure}[htbp]
\centering
\includegraphics{Pure_Exploration_files/figure-latex/unnamed-chunk-1-1.pdf}
\caption{Statistician chooses the curve by picking the weights w, then
the opponent picks lambda. In the case of a two-armed bandit, we have
w1+w2 = 1. The plot suggests that uniform allocation is optimal for
Bernoulli bandits. The thick line shows the result for w1=w2=0.5.}
\end{figure}

The plot above specifies again the game and the reasoning of the
opponent. Given a model \(\bm{\mu} = (\mu_1, \dots, \mu_K)\) with
\(\mu_1 > \mu_2 \geq \dots \geq \mu_K\), the experimenter chooses the
proportions of arm draws \(w = (w_a)_a\). Then the opponent chooses an
arm \(a \in \{2, \dots, K\}\) and chooses the alternative distribution
for arm \(a\),
\(\lambda_a = \arg \min_{\lambda} w_1 d(\mu_1, \lambda) + w_a d(\mu_a, \lambda)\).
The payoff of the game is then the minimal number of rounds \(T\) so
that the restriction
\(Tw_1 d(\mu_1, \lambda_a - \epsilon) + Tw_a d(\mu_a, \lambda + \epsilon) \geq \text{kl}(\delta, 1-\delta)\)
holds when \(a^*(\bm{\mu}) \neq a^*(\bm{\lambda})\) due to \(\epsilon\).
Consequently, the value is given by

\begin{equation}
T(w, a, \delta) = \frac{\text{kl}(\delta, 1-\delta)}{w_1 d(\mu_1, \lambda_a - \epsilon) + w_a d(\mu_a, \lambda + \epsilon)}
\end{equation}

which is comparable to the result in Theorem (Garivier and Kaufmann,
2016) \ref{theorem:GarivierKaufmannTheorem1}.

\subsubsection{Fixed Budget}\label{fixed-budget}

\end{document}

### 2017-05-14 Thresholding Bandit/Theorem1.Rmd
initial commit

--- 
title: "Theorems and Proofs"
author: "Tim Radtke" 
date: "4/23/2017"
header-includes:
   #- \documentclass[a4paper,twoside,english]{article}
   - \usepackage[retainorgcmds]{IEEEtrantools}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{bbm}
   - \newtheorem{theorem}{Theorem}
   - \newcommand{\KL}{\,\text{KL}}
   - \newcommand{\der}{\,\text{d}}
   #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
   #- \usepackage{fontspec}
   #-   \setmainfont{Arial}
keep_tex: TRUE
output:
  pdf_document:
    number_sections: true
    keep_tex: true
    #latex_engine: xelatex
fontsize: 12pt
urlcolor: blue
---

## Theorem 1

In Theorem 1 of Locatelli et al. (2016), a lower bound for the thresholding bandit problem is shown. The basic idea is as follows. The problem formulation considered in the paper describes bandit problems for Sub-Gaussian distributions. To show a lower bound, we show that every algorithm is expected to make a certain error even if we restrict ourselves to a heavily specified scenario. Even then, any algorithm will have a certain level of risk with which it cannot distinguish between the actual setting and a slightly changed setting (under which the former answer leads to regret).

To be more specific, consider a case in which we set $\tau = 0$ and $\epsilon = 0$ w.l.o.g. If we then choose all arms to have normally distributed feedback with means $\mu_i$, we see that for each arm $i$ the distance from the threshold is given by $\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i$. Thus, assuming a variance of 1 for every arm, we have for every arm the distribution $\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)$. Furthermore, define $\nu_i' = \mathcal{N}(-\Delta_i,1)$.

The idea now is that every arm $i \in \{1,\dots,K\}$ generates a sample for every time point $t\in \{1, \dots, T\}$ from its distribution $\nu_i$ before the algorithm starts to choose arms. Thus, we have a $T \times K$ table of realized observations from the product distribution given by $\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K$. This is a product distribution where the $K$ different means all lie above the threshold. We would hope that an algorithm classifies the means accordingly. However, we will show in what follows that any algorithm makes a certain error by not being able to distinguish $\mathcal{B}^0$ from a product distribution $\mathcal{B}^i$ which differs only slightly and has the same overall complexity (as defined by $H = \sum_{i=1}^K (\Delta_i)^{-2}$).

Before the start of the algorithm, we introduce a slight variation in the setup. Similar to how one can switch arms in the pure exploration setup for multi-armed bandits (compare Audibert et al., Garivier & Kaufmann) to "confuse" the algorithm without introducing additional complexity to the specified problem. However, since we do not compare arms with each other directly in the thresholding bandit problem (switching arms would still keep all means above the threshold), we instead need to flip an arm with respect to the threshold. Since the threshold is $\tau = 0$, we have for the flipped arm the new distribution $\nu_i'$ as defined above. Indeed, we can define the new product distribution $B^i = \nu_1^i \otimes \dots \otimes \nu_K^i$ where for $k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}$. This flipping of the arm corresponds to multiplying all random variables $X_{i,t}$ of arm $i$ by $-1$.

As in Locatelli et al. (2016), we let for $i \leq K$, $\mathbb{P}_{\mathcal{B}^i}$ define the probability distribution describing all samples that a bandit strategy can potentially collect up to horizon $T$, i.e. according to the samples $(X_{k,s})_{k\leq K, s \leq T} \sim (\mathcal{B}^i)^{\otimes T}$. $(T_k)_{k\leq K}$ denotes the number of samples collected on arm $k$ until time $T$.

#### Reminder about the goal of the proof

At this point, we have defined a finite set of problems of Gaussian distributions with fixed variance 1 for a given set of set of gaps between the means of the distributions and the threshold, $(d_k)_k$. We will now proof a lower bound on the worst case regret of any algorithm; that is, the maximum error probability that even the best algorithm makes on this problem.

#### Statistical Decision

Given our formulation of the regret, the expected regret $\mathbb{E}[\mathcal{L}(T)]$ corresponds directly to the probability of making a wrong classification of any of the $K$ means. In general, let $T$ be a binary decision function, and define $\Omega = \{T = 0\}$ and $\Omega^C = \{T = 1\}$. Assume that the decision $T$ distinguishes between two states of the world, $H_0$ and $H_1$. Then our overall error probability is given by $P_{H_0}(T=1) + P_{H_1}(T = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)$.

In our case, $H_0$ may correspond to the state in which we have $\mathcal{B}^0$, and $H_1$ corresponds to the case where any arm has been flipped, $\mathcal{B}^i$. Furthermore, we consider the events in which the algorithm, making the decision, classifies arm $i$ as being above the threshold: $\mathcal{A}_i = \{i \in \hat{S}_\tau$. The event on which all arms are being classified as above the threshold is consequently given by $\mathcal{A} = \bigcap \mathcal{A}_i$. However, Theorem 1 does not bound the overall regret, but the maximum error probability. We can write this now as

\begin{equation}
\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big)
= \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
\end{equation}

In order to give a bound on above equation, we start by considering $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$. This probability can be measured as the expected change in the likelihood of observed data times the probability under the original state. The measure of event $\mathcal{A}_i$ under state $\mathcal{B}^i$ is given as the probability of $\mathcal{A}_i$ under the (original) state $\mathcal{B}^0$ multiplied by a factor. This factor is the change in the data likelihoods due to moving from $\mathcal{B}^0$ to $\mathcal{B}^i$, and is expressed as the expected likelihood ratio under $\mathcal{B}^0$. By definition though, this is equal to the empirical Kullback-Leibler divergence of the two measures.

First, let us define the change of measure in terms of the empirical log-likelihood for our case. Then, we will show how to replace the log-likelihood by the empirical Kullback-Leibler divergence.

Let every $\nu_i, \nu_i'$ be dominated by the Lebesgue measure $\lambda$. Then their density functions are given by $f_i = \frac{\der \nu_i}{\der \lambda}$ and $f_i' = \frac{\der \nu_i'}{\der \lambda}$ respectively. For $T \geq t \geq 0$, define the empirical Kullback-Leibler divergence as

\begin{align*}
\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log(\frac{\der \nu_k'}{\der \nu_k}(X_{k,s})) \\
& = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
& = \frac{1}{t} \log \big( \prod_{s=1}^{t} \frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
& \stackrel{\text{iid}}{=} \frac{1}{t} \log \big( \frac{f_k'(X_{k,1}, \dots,X_{k,t})}{f_k(X_{k,1}, \dots,X_{k,t})} \big) \\
& = \frac{1}{t} \log \big( \text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k) \big)
\end{align*}

Since we consider Gaussian distributions with variance 1, we have density functions $f_i(x) \propto \exp \big(-\frac{1}{2} (x-\Delta_i)^2\big)$ and $f_i'(x) \propto \exp \big(-\frac{1}{2} (x+\Delta_i)^2\big)$. Plugging this into the above definition of the empirical Kullback-Leibler divergence, we easily see

\begin{align*}
\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{\exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2\big)}{\exp \big(-\frac{1}{2} (X_{k,s}-\Delta_k)^2\big)} \big) \\
& = \frac{1}{t} \sum_{s=1}^{t} \log \big( \exp(-\frac{1}{2} (X_{k,s}+\Delta_k)^2 + \frac{1}{2} (X_{k,s}-\Delta_k)^2) \big) \\
& = - \frac{1}{t} \sum_{s=1}^{t} 2 X_{k,s} \Delta_k
\end{align*}

#### Change of Measure

We are now ready to state the change of measure. As alluded to above, we consider how the probability changes for the event $\mathcal{A}_i$ when we move from $\mathcal{B}^0$ to $\mathcal{B}^i$. When flipping arm $i$, we only changed the samples of this arm, that is, the first $T_i$ observations we got from arm $i$ the algorithm took. The change of measure is then defined as:

\begin{align*}
\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \text{LR}((X_{i,1}, \dots,X_{i,T_i}), \nu_i', \nu_i) ] \\
& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ]
\end{align*}

Obviously, $\hat{\KL}_{i,T_i}$ depends on the realized samples $X_{i,1}, \dots,X_{i,T_i}$. Consequently, we need to find a bound on $\hat{\KL}_{i,T_i}$ itself to incorporate the uncertainty involved in this metric.

#### Kullback-Leibler Divergence

For our problem, the Kullback-Leibler divergence of $/nu_k'$ from $\nu_k$ is given by $\KL_k := KL(\nu_k', \nu_k) = 2\Delta_k^2$.

#### Concentration of the Empirical Kullback-Leibler Divergence

It is easy to see that

\begin{equation*}
|\hat{\KL}_{k,t} - \KL_{k,t}| = |-\frac{2}{t} \Delta_k \sum_{s=1}^{t}(X_{k,s} - \Delta_k)|
\end{equation*}

itself is a normally distributed random variable with mean zero and a variance decreasing in $t$. Thus, one can show that $\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4$ for the event

\begin{equation}
\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}} \}. \label{LocatelliTheorem1EventXi}
\end{equation}

Thus, in order to bound the empirical Kullback-Leibler divergence in our change of measure, we can consider the intersection of $\mathcal{A}_i$ and $\xi$ as follows and plug in the bound on event $\xi$:

\begin{align*}
\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
\end{align*}

Two things are left to do: With $T_i$, we still have one random variable left which we cannot leave in our bound. Second, we are actually not interested in $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$ but in $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$.

#### Bounding $T_i$ for $\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$

Part of our bound is $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$, so let's continue with that. In general it holds that $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \bar{X}$. Thus we can write:

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
& \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
& \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
\end{align*}

where the second line is again the intersection of $\mathcal{A}_i$ and $\xi$ as before in order to apply the change of measure again in the third line.

What is left to show before we have our final bound is a bound on $T_i$. To show that any algorithm has a certain bound on its error, it only makes sense that every arm has to pulled at least a certain amount of times. Consequently, no arm should be pulled exclusively.

First, let $a = \Delta_i \sqrt{T_i}$ and $b = 4\sqrt{\log((4\log(T)+1)K)}$. Then use $ab \leq a^2 + b^2$ to write $ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)$. And so:

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) ]
\end{align*}

Furthermore, we know that the sum of the individual arm pulls has to be equal to the overall number of pulls (equal to the budget in the fixed budget sense), $\sum_i T_i = T$, and furthermore we know that $T_i>0$. The latter holds since any reasonable algorithm has to check each arm at least once in our setup. This is because we need to check each arm's performance in comparison to the threshold. Thus it is easy to show that $\exists i: T_i \leq \frac{T}{H \Delta_i^2} = \frac{T}{(\sum_{i=1}^{K} \Delta_i^{-2}) \Delta_i^2}$. To see this, assume the opposite: $\forall i: T_i > T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2}$. This implies however $\sum_{i=1}^K T_i > \sum_{i=1}^K T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2} = T \cdot 1 = T$ which is a contradiction.

So we can write $(\Delta_i \sqrt{T_i})^2 \leq \frac{T}{H}$. We use $\mathcal{A} = \cap_{i=1}^K \mathcal{A}_i$ to write:

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big] \\
& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}{K} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big]
\end{align*}

We write $\frac{1}{K} \sum_{i=1}^K \exp(-3T_i \Delta_i^2) \geq \frac{1}{K} \sum_{i=1}^K \exp(-3 T/H) = \exp(-3 T/H)$. Thus:

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i) \exp(-16 \log(4(\log(T)+1)K)) ] \\
& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
& = \mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
\end{align*}

#### Conclusion

Consider again the risk which we need to bound from equation \eqref{LocatelliTheorem1ExpRegret}. We bound the maximum expected loss over all $\mathcal{B}_i$. By again using the fact that in general $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \bar{X}$, we plug in our previous calculations:

\begin{align}
\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \label{LocatelliTheorem1DefinitionOfRisk}
\end{align}

From \eqref{LocatelliTheorem1EventXi} we know that for any $i \in \{0, \dots, K\}$, $\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4$. Following the argument in Locatelli et al. (2016), we now consider two cases: $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2$ and $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2$. In the former case, we can plug in the two probabilities into \eqref{LocatelliTheorem1DefinitionOfRisk}. If $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2$ and $\mathbb{P}_{\mathcal{B}^0}(\xi) \geq 3/4$, then $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \geq 1/4$. Thus:

\begin{align*}
\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \\
& \geq \frac{1}{8} \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
\end{align*}

where we drop the second summand of the second line so that the inequality holds.

On the other hand, when $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2$, then we know that $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \leq 1/2$ for any $\mathbb{P}_{\mathcal{B}^0}(\xi)$. At the same time $1-\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \geq 1/2$. Consequently, $1/4 \leq \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \leq 1/2$, while 
$\frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) \geq 0$. And so the stronger lower bound in that case is, as noticed by Locatelli et al. (2016), given simply by

\begin{align*}
\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
& \geq 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \\
& \geq \frac{1}{2}
\end{align*}

### 2017-05-14 Thresholding Bandit/Theorem1.tex
initial commit

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={Theorems and Proofs},
            pdfauthor={Tim Radtke},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{Theorems and Proofs}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Tim Radtke}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{4/23/2017}

\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{bbm}
\newtheorem{theorem}{Theorem}
\newcommand{\KL}{\,\text{KL}}
\newcommand{\der}{\,\text{d}}

\begin{document}
\maketitle

\subsection{Theorem 1}\label{theorem-1}

In Theorem 1 of Locatelli et al. (2016), a lower bound for the
thresholding bandit problem is shown. The basic idea is as follows. The
problem formulation considered in the paper describes bandit problems
for Sub-Gaussian distributions. To show a lower bound, we show that
every algorithm is expected to make a certain error even if we restrict
ourselves to a heavily specified scenario. Even then, any algorithm will
have a certain level of risk with which it cannot distinguish between
the actual setting and a slightly changed setting (under which the
former answer leads to regret).

To be more specific, consider a case in which we set \(\tau = 0\) and
\(\epsilon = 0\) w.l.o.g. If we then choose all arms to have normally
distributed feedback with means \(\mu_i\), we see that for each arm
\(i\) the distance from the threshold is given by
\(\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i\). Thus, assuming a
variance of 1 for every arm, we have for every arm the distribution
\(\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)\). Furthermore,
define \(\nu_i' = \mathcal{N}(-\Delta_i,1)\).

The idea now is that every arm \(i \in \{1,\dots,K\}\) generates a
sample for every time point \(t\in \{1, \dots, T\}\) from its
distribution \(\nu_i\) before the algorithm starts to choose arms. Thus,
we have a \(T \times K\) table of realized observations from the product
distribution given by
\(\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K\).
This is a product distribution where the \(K\) different means all lie
above the threshold. We would hope that an algorithm classifies the
means accordingly. However, we will show in what follows that any
algorithm makes a certain error by not being able to distinguish
\(\mathcal{B}^0\) from a product distribution \(\mathcal{B}^i\) which
differs only slightly and has the same overall complexity (as defined by
\(H = \sum_{i=1}^K (\Delta_i)^{-2}\)).

Before the start of the algorithm, we introduce a slight variation in
the setup. Similar to how one can switch arms in the pure exploration
setup for multi-armed bandits (compare Audibert et al., Garivier \&
Kaufmann) to ``confuse'' the algorithm without introducing additional
complexity to the specified problem. However, since we do not compare
arms with each other directly in the thresholding bandit problem
(switching arms would still keep all means above the threshold), we
instead need to flip an arm with respect to the threshold. Since the
threshold is \(\tau = 0\), we have for the flipped arm the new
distribution \(\nu_i'\) as defined above. Indeed, we can define the new
product distribution \(B^i = \nu_1^i \otimes \dots \otimes \nu_K^i\)
where for
\(k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}\).
This flipping of the arm corresponds to multiplying all random variables
\(X_{i,t}\) of arm \(i\) by \(-1\).

As in Locatelli et al. (2016), we let for \(i \leq K\),
\(\mathbb{P}_{\mathcal{B}^i}\) define the probability distribution
describing all samples that a bandit strategy can potentially collect up
to horizon \(T\), i.e.~according to the samples
\((X_{k,s})_{k\leq K, s \leq T} \sim (\mathcal{B}^i)^{\otimes T}\).
\((T_k)_{k\leq K}\) denotes the number of samples collected on arm \(k\)
until time \(T\).

\paragraph{Reminder about the goal of the
proof}\label{reminder-about-the-goal-of-the-proof}

At this point, we have defined a finite set of problems of Gaussian
distributions with fixed variance 1 for a given set of set of gaps
between the means of the distributions and the threshold, \((d_k)_k\).
We will now proof a lower bound on the worst case regret of any
algorithm; that is, the maximum error probability that even the best
algorithm makes on this problem.

\paragraph{Statistical Decision}\label{statistical-decision}

Given our formulation of the regret, the expected regret
\(\mathbb{E}[\mathcal{L}(T)]\) corresponds directly to the probability
of making a wrong classification of any of the \(K\) means. In general,
let \(T\) be a binary decision function, and define
\(\Omega = \{T = 0\}\) and \(\Omega^C = \{T = 1\}\). Assume that the
decision \(T\) distinguishes between two states of the world, \(H_0\)
and \(H_1\). Then our overall error probability is given by
\(P_{H_0}(T=1) + P_{H_1}(T = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)\).

In our case, \(H_0\) may correspond to the state in which we have
\(\mathcal{B}^0\), and \(H_1\) corresponds to the case where any arm has
been flipped, \(\mathcal{B}^i\). Furthermore, we consider the events in
which the algorithm, making the decision, classifies arm \(i\) as being
above the threshold: \(\mathcal{A}_i = \{i \in \hat{S}_\tau\). The event
on which all arms are being classified as above the threshold is
consequently given by \(\mathcal{A} = \bigcap \mathcal{A}_i\). However,
Theorem 1 does not bound the overall regret, but the maximum error
probability. We can write this now as

\begin{equation}
\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big)
= \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
\end{equation}

In order to give a bound on above equation, we start by considering
\(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\). This probability can be
measured as the expected change in the likelihood of observed data times
the probability under the original state. The measure of event
\(\mathcal{A}_i\) under state \(\mathcal{B}^i\) is given as the
probability of \(\mathcal{A}_i\) under the (original) state
\(\mathcal{B}^0\) multiplied by a factor. This factor is the change in
the data likelihoods due to moving from \(\mathcal{B}^0\) to
\(\mathcal{B}^i\), and is expressed as the expected likelihood ratio
under \(\mathcal{B}^0\). By definition though, this is equal to the
empirical Kullback-Leibler divergence of the two measures.

First, let us define the change of measure in terms of the empirical
log-likelihood for our case. Then, we will show how to replace the
log-likelihood by the empirical Kullback-Leibler divergence.

Let every \(\nu_i, \nu_i'\) be dominated by the Lebesgue measure
\(\lambda\). Then their density functions are given by
\(f_i = \frac{\der \nu_i}{\der \lambda}\) and
\(f_i' = \frac{\der \nu_i'}{\der \lambda}\) respectively. For
\(T \geq t \geq 0\), define the empirical Kullback-Leibler divergence as

\begin{align*}
\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log(\frac{\der \nu_k'}{\der \nu_k}(X_{k,s})) \\
& = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
& = \frac{1}{t} \log \big( \prod_{s=1}^{t} \frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
& \stackrel{\text{iid}}{=} \frac{1}{t} \log \big( \frac{f_k'(X_{k,1}, \dots,X_{k,t})}{f_k(X_{k,1}, \dots,X_{k,t})} \big) \\
& = \frac{1}{t} \log \big( \text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k) \big)
\end{align*}

Since we consider Gaussian distributions with variance 1, we have
density functions
\(f_i(x) \propto \exp \big(-\frac{1}{2} (x-\Delta_i)^2\big)\) and
\(f_i'(x) \propto \exp \big(-\frac{1}{2} (x+\Delta_i)^2\big)\). Plugging
this into the above definition of the empirical Kullback-Leibler
divergence, we easily see

\begin{align*}
\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{\exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2\big)}{\exp \big(-\frac{1}{2} (X_{k,s}-\Delta_k)^2\big)} \big) \\
& = \frac{1}{t} \sum_{s=1}^{t} \log \big( \exp(-\frac{1}{2} (X_{k,s}+\Delta_k)^2 + \frac{1}{2} (X_{k,s}-\Delta_k)^2) \big) \\
& = - \frac{1}{t} \sum_{s=1}^{t} 2 X_{k,s} \Delta_k
\end{align*}

\paragraph{Change of Measure}\label{change-of-measure}

We are now ready to state the change of measure. As alluded to above, we
consider how the probability changes for the event \(\mathcal{A}_i\)
when we move from \(\mathcal{B}^0\) to \(\mathcal{B}^i\). When flipping
arm \(i\), we only changed the samples of this arm, that is, the first
\(T_i\) observations we got from arm \(i\) the algorithm took. The
change of measure is then defined as:

\begin{align*}
\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \text{LR}((X_{i,1}, \dots,X_{i,T_i}), \nu_i', \nu_i) ] \\
& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ]
\end{align*}

Obviously, \(\hat{\KL}_{i,T_i}\) depends on the realized samples
\(X_{i,1}, \dots,X_{i,T_i}\). Consequently, we need to find a bound on
\(\hat{\KL}_{i,T_i}\) itself to incorporate the uncertainty involved in
this metric.

\paragraph{Kullback-Leibler
Divergence}\label{kullback-leibler-divergence}

For our problem, the Kullback-Leibler divergence of \(/nu_k'\) from
\(\nu_k\) is given by \(\KL_k := KL(\nu_k', \nu_k) = 2\Delta_k^2\).

\paragraph{Concentration of the Empirical Kullback-Leibler
Divergence}\label{concentration-of-the-empirical-kullback-leibler-divergence}

It is easy to see that

\begin{equation*}
|\hat{\KL}_{k,t} - \KL_{k,t}| = |-\frac{2}{t} \Delta_k \sum_{s=1}^{t}(X_{k,s} - \Delta_k)|
\end{equation*}

itself is a normally distributed random variable with mean zero and a
variance decreasing in \(t\). Thus, one can show that
\(\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4\) for the event

\begin{equation}
\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}} \}. \label{LocatelliTheorem1EventXi}
\end{equation}

Thus, in order to bound the empirical Kullback-Leibler divergence in our
change of measure, we can consider the intersection of \(\mathcal{A}_i\)
and \(\xi\) as follows and plug in the bound on event \(\xi\):

\begin{align*}
\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
\end{align*}

Two things are left to do: With \(T_i\), we still have one random
variable left which we cannot leave in our bound. Second, we are
actually not interested in \(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)
but in
\(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\).

\paragraph{\texorpdfstring{Bounding \(T_i\) for
\(\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)}{Bounding T\_i for \textbackslash{}max\_\{i \textbackslash{}in \textbackslash{}\{1,\textbackslash{}dots,K\textbackslash{}\}\}\textbackslash{}mathbb\{P\}\_\{\textbackslash{}mathcal\{B\}\^{}i\}(\textbackslash{}mathcal\{A\}\_i)}}\label{bounding-t_i-for-max_i-in-1dotskmathbbp_mathcalbimathcala_i}

Part of our bound is
\(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\),
so let's continue with that. In general it holds that
\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \bar{X}\). Thus we can
write:

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
& \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
& \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
\end{align*}

where the second line is again the intersection of \(\mathcal{A}_i\) and
\(\xi\) as before in order to apply the change of measure again in the
third line.

What is left to show before we have our final bound is a bound on
\(T_i\). To show that any algorithm has a certain bound on its error, it
only makes sense that every arm has to pulled at least a certain amount
of times. Consequently, no arm should be pulled exclusively.

First, let \(a = \Delta_i \sqrt{T_i}\) and
\(b = 4\sqrt{\log((4\log(T)+1)K)}\). Then use \(ab \leq a^2 + b^2\) to
write \(ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)\). And so:

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) ]
\end{align*}

Furthermore, we know that the sum of the individual arm pulls has to be
equal to the overall number of pulls (equal to the budget in the fixed
budget sense), \(\sum_i T_i = T\), and furthermore we know that
\(T_i>0\). The latter holds since any reasonable algorithm has to check
each arm at least once in our setup. This is because we need to check
each arm's performance in comparison to the threshold. Thus it is easy
to show that
\(\exists i: T_i \leq \frac{T}{H \Delta_i^2} = \frac{T}{(\sum_{i=1}^{K} \Delta_i^{-2}) \Delta_i^2}\).
To see this, assume the opposite:
\(\forall i: T_i > T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2}\). This
implies however
\(\sum_{i=1}^K T_i > \sum_{i=1}^K T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2} = T \cdot 1 = T\)
which is a contradiction.

So we can write \((\Delta_i \sqrt{T_i})^2 \leq \frac{T}{H}\). We use
\(\mathcal{A} = \cap_{i=1}^K \mathcal{A}_i\) to write:

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big] \\
& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}{K} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big]
\end{align*}

We write
\(\frac{1}{K} \sum_{i=1}^K \exp(-3T_i \Delta_i^2) \geq \frac{1}{K} \sum_{i=1}^K \exp(-3 T/H) = \exp(-3 T/H)\).
Thus:

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i) \exp(-16 \log(4(\log(T)+1)K)) ] \\
& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
& = \mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
\end{align*}

\paragraph{Conclusion}\label{conclusion}

Consider again the risk which we need to bound from equation
\eqref{LocatelliTheorem1ExpRegret}. We bound the maximum expected loss
over all \(\mathcal{B}_i\). By again using the fact that in general
\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \bar{X}\), we plug in
our previous calculations:

\begin{align}
\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \label{LocatelliTheorem1DefinitionOfRisk}
\end{align}

From \eqref{LocatelliTheorem1EventXi} we know that for any
\(i \in \{0, \dots, K\}\), \(\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4\).
Following the argument in Locatelli et al. (2016), we now consider two
cases: \(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2\) and
\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2\). In the former
case, we can plug in the two probabilities into
\eqref{LocatelliTheorem1DefinitionOfRisk}. If
\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2\) and
\(\mathbb{P}_{\mathcal{B}^0}(\xi) \geq 3/4\), then
\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \geq 1/4\). Thus:

\begin{align*}
\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \\
& \geq \frac{1}{8} \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
\end{align*}

where we drop the second summand of the second line so that the
inequality holds.

On the other hand, when
\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2\), then we know that
\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \leq 1/2\) for any
\(\mathbb{P}_{\mathcal{B}^0}(\xi)\). At the same time
\(1-\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \geq 1/2\).
Consequently,
\(1/4 \leq \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \leq 1/2\),
while
\(\frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) \geq 0\).
And so the stronger lower bound in that case is, as noticed by Locatelli
et al. (2016), given simply by

\begin{align*}
\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
& \geq 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \\
& \geq \frac{1}{2}
\end{align*}

\end{document}

### 2017-05-14 Thresholding Bandit/Theorem2.Rmd
initial commit

--- 
title: "Theorems and Proofs"
author: "Tim Radtke" 
date: "4/23/2017"
header-includes:
   - \usepackage[retainorgcmds]{IEEEtrantools}
keep_tex: TRUE
output:
  pdf_document
---

## Theorem 2

Let $K \geq 0$, $T \geq 2K$, and consider a problem $\mathbb{B}$. Assume that
all arms $\nu_k$ of the problem are R-sub-Gaussian with means $\mu_k$. Let $\tau
\in \mathbb{R}, \epsilon \geq 0$.

Algorithm APT's expected loss is upper bounded on this problem as 
\begin{equation*} \mathbb{E}(\mathcal{L}(T)) \leq \exp
(-\frac{1}{64R^2}\frac{T}{H} + 2 \log (T) + 1)K)) \end{equation*}

where we remind that $H = \sum_i (|\mu_i - \tau | + \epsilon)^{-2}$ and where
$\mathbb{E}$ is the expectation according to the samples of the problem.

### Proof

To prove above theorem, we first define a favorable event $\xi$ on which we hope
to make a loss with only a small probability. Indeed, it is the event for which
we want to upper bound the expected loss. As we want to find an upper bound for
the expected loss of the APT algorithm, the event corresponds to the decision
made by it. The APT algorithm's heuristic leads to a decision with low expected
regret, if it finds empirical mean estimates $\frac{1}{s} \sum_{t=1}^s X_{i,t}$
of the arms that are close to the true mean $mu_i$ of the arms. Then, we would
expect arms which are over $\tau + \epsilon$ to be classified correctly, and
arms that are under $\tau - \epsilon$ to be rejected.

Indeed, we have $\mathbb{E}(\mathcal{L}(T)) = P(S_{\tau + \epsilon} \cap
\hat{S}_\tau^C \neq \emptyset \lor S_{\tau-\epsilon}^C \cap \hat{S}_{\tau} \neq
\emptyset)$. But this just corresponds to $P(\{\exists i: ((\mu_i <
\tau-\epsilon) \land(\hat{\mu}_i \geq \tau)) \lor ((\mu_i > \tau + \epsilon)
\land (\hat{\mu}_i < \tau)))$. Each of the two $(...)\lor(...)$ conditions
corresponds to $| \hat{\mu}_i - \mu_i | \geq \epsilon$. It follows that the
expected loss can be rewritten as: $\mathbb{E}(\mathcal{L}(T)) = P(\exists i,
\exists s: |\hat{\mu}_{i,s} - \mu_i | \geq \epsilon) = P(\xi^C)$. But this is
exactly the probability of classifying at least one arm incorrectly which
results in a loss of size 1.

Thus we define as the favorable event:

\begin{equation} 
\xi = \{\forall i, \forall s: | \hat{\mu}_{i,s} - \mu_i | \leq
\epsilon\} 
\end{equation}

Furthermore, if we write $\xi_{i,s} = \{ |\hat{\mu}_{i,s}-\mu_i | \leq \epsilon
\}$, then the following holds by union bound.

\begin{equation} 
P(\xi) = P(\cap_i \cap_s \xi_{i,s}) = 1 - P(\cup_i \cup_s
\xi_{i,s}^C) \geq 1 - \sum_i \sum_s P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon)
\label{theorem2_prob_fav_event} 
\end{equation}

Furthermore, for any $i \in \{1, \dots, K\}$, for any $s \in \{1, \dots,
T(i)\}$, with $X_{it}$ being the random sample from the R-sub-Gaussian
distribution $v_i$ at time $t$:

\begin{equation} 
P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon) = P(| (\frac{1}{s}
\sum_{t=1}^{s} X_{it} - \mu_i) | \geq \epsilon) = P(| \sum_{t=1}^{s} (X_{it} -
\mu_i) | \geq s \epsilon) 
\end{equation}

where the latter can be bounded by a Hoeffding inequality:

\begin{equation} 
P(| \sum_{t=1}^{s} (X_{it} - \mu_i) | \geq s \epsilon) \leq
2\exp (-\frac{\epsilon^2 s}{2 R^2}) \label{theorem2_hoeffding} 
\end{equation}

The Hoeffding inequality as used here is as follows:

...

Plugging \eqref{theorem2_hoeffding} back into \eqref{theorem2_prob_fav_event},
we get:
\begin{equation}
P(\xi) \geq 1 - \sum_i \sum_s P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon) \geq 1 - 2 \sum_i \sum_s \exp (-\frac{\epsilon^2 s}{2 R^2})
\end{equation}

Now, in order to match the performance of the lower bound on the expected loss derived in theorem 1, we will choose $\epsilon = \sqrt{\frac{T \delta^2}{Hs}}$. Thus:

\begin{equation}
P(\xi) \geq 1 - 2 \sum_i \sum_s \exp (-\frac{\epsilon^2 s}{2 R^2}) = 1 - 2 \sum_i \sum_s \exp (-\frac{T \delta^2}{2 R^2 H}) \geq 1 - TK \exp(-\frac{T\delta^2}{2R^2H})
\end{equation}

Thus, we don't exactly get the bound from Locatelli et al. (2016) because we used the Hoeffding inequality instead of the martingale bound; but the the method should be clear.

What is left now is to show that the favorable event still holds under the proposed $\epsilon$, that is, we need to show that under $P(\xi) \geq 1 - TK \exp(-\frac{T\delta^2}{2R^2H})$ we still reject arms that are under $\tau - \epsilon$ and accept those above $\tau + \epsilon$.

#### Step 2: Lower Bound on Number of Pulls of Difficult Arm

In order to see that arms are correctly classified with large probability, we need to show that they are are pulled sufficiently often, that is, we have a degree of exploration for each arm $i$ that allows us to identify its characteristics. To see this, rewrite the favorable event of a single arm as follows with $s = T(i)$:

\begin{equation}
\xi_{i,s} = \{ |\hat{\mu}_{i,s}-\mu_i | \leq \epsilon \} = \{ |\hat{\mu}_{i,s} - \mu_i | \leq \sqrt{\frac{T \delta^2}{H T(i)}}\}
\end{equation}

To make sure that this deviation is small enough, we need to show that at time $T$, all $T(i)$ have a sufficient lower bound and thus all arms $i$ have been explored sufficiently to classify correctly with probability larger $TK \exp(-\frac{T\delta^2}{2R^2H})$.

To start off, notice that due to the initialization of the APT algorithm, every $T_i(T) \geq 1$. Furthermore, we have assumed that $T>2K$. Now, at time $T$, consider an arm $k$ that has been pulled $T_k(T) -1 \geq \frac{(T-K)}{H \Delta^2_k}$ times. That is, it has been pulled at least proportionally to it's contribution to the overall hardness of the problem $H$. Recall $H = \sum_{i=1}^K(|\mu_i - \tau|+\epsilon)^-2$ and $\delta^2_i = (|\mu_i - \tau | + \epsilon)^2$. To see that such arm $k$ exists, assume it does not. Then

\begin{equation*}
T_i(T) - 1 < \frac{T-K}{H \Delta_i^2} \forall i
\end{equation*}
\begin{equation*}
T- K = \sum_{i=1}^{K} T_i(T) - 1 < \sum_{i=1}^{K} \frac{T-K}{H \Delta_i^2} = \frac{T-K}{H \Delta_i^2} \sum_{i=1}^{K} \frac{1}{\Delta_i^2} = T-K
\end{equation*}

which is a contradiction.

Consequently, using the assumption $T>2K$ from above, we have

\begin{equation*}
T_k(T) \geq T_k(T) - 1 \geq \frac{T-K}{H \Delta^2_k} = \frac{T}{2H\Delta_k^2}
\end{equation*}

This states a lower bound on the amount of pulls $T_k(t)$ for an arm $k$ that contributes more than average to the overall hardness of the problem.

#### Step 3: Lower Bound on Number of Pulls of Simple Arm

Next, we would like to derive bounds on the number of pulls of the remaining arms $i$ at the time $t$, the last pull of arm $k$. To do so, consider that we are on the favorable event $\xi$. For every arm $i$, it holds:

\begin{equation}
|\hat{\mu}_i(t) - \mu_i | \leq \sqrt{\frac{T \delta^2}{HT_i(t)}} \label{step3_favorable_event} 
\end{equation}

As described in Locatelli et al., using the reverse triangle inequality, we can write

\begin{IEEEeqnarray*}{rCl}
|\hat{\mu}_i(t) - \mu_i | & = & | (\hat{\mu}_i(t) - \tau) - (\mu_i-\tau) |
\\
& \geq & | |\hat{\mu}_i(t) - \tau| - |\mu_i-\tau| |
\\
& = & | (|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i-\tau| - \epsilon) |
\\
& = & | \hat{\Delta}_i(t) - \Delta_i |
\end{IEEEeqnarray*}

Consequently, we can again employ the hardness of the task to start deriving bounds on the number of pulls of the arms:

\begin{equation*}
| \hat{\Delta}_i(t) - \Delta_i | \leq |\hat{\mu}_i(t) - \mu_i | \sqrt{\frac{T \delta^2}{HT_i(t)}}
\end{equation*}

From this, we get

\begin{IEEEeqnarray*}{rlCrl}
\Delta_i - \sqrt{\frac{T \delta^2}{HT_i(t)}} & \leq & \hat{\Delta}_i(t) & \leq & \Delta_i + \sqrt{\frac{T \delta^2}{HT_i(t)}}
\end{IEEEeqnarray*}

and in particular for the arm $k$ discussed above

\begin{IEEEeqnarray}{rlCrl}
\Delta_k - \sqrt{\frac{T \delta^2}{HT_k(t)}} & \leq & \hat{\Delta}_k(t) & \leq & \Delta_k + \sqrt{\frac{T \delta^2}{HT_k(t)}} \label{delta_hat_k_bounds}
\end{IEEEeqnarray}

To bound $T_i(t)$, it is helpful to compare $\Delta_i$ and $\Delta_k$ at time $t$. From the definition of the APT algorithm, we know that since arm $k$ has been pulled at time $t$ ("Pull arm $I_{t+1} = \arg \min_i \mathcal{B}_i (t+1)$"):

\begin{IEEEeqnarray*}{rCl}
\mathcal{B}_k(t) & \leq & \mathcal{B}_i(t)
\\
\sqrt{T_k(t)} \hat{\Delta}_k(t) & \leq & \sqrt{T_i(t)} \hat{\Delta}_i(t)
\end{IEEEeqnarray*}

Thus, every arm $i$ has a lower bound on it's number of pulls given by the lower bound for arm $k$ proportional with it's inverse relative estimated hardness $\hat{\Delta}_k(t) / \hat{\Delta}_i(t)$. We can easily derive a lower bound for the left hand side by plugging in \eqref{delta_hat_k_bounds}:

\begin{IEEEeqnarray}{rCl}
\sqrt{T_k(t)} (\Delta_k - \sqrt{\frac{T \delta^2}{HT_k(t)}}) & \leq & \mathcal{B}_k(t) 
\\
\sqrt{\frac{T}{2H\Delta_k^2}} (\Delta_k - \sqrt{2}\Delta_k \delta) & = & \sqrt{\frac{T}{H}} (\frac{1}{\sqrt{2}} - \delta)
\\
& \leq & \mathcal{B}_k(t)
\end{IEEEeqnarray}

since $T_k(t) \geq T/(2H\Delta^2_k)$ and $\sqrt{T \delta^2 / (HT_k(t))} \geq \sqrt{T \delta^2 / (H\frac{T}{2H \Delta^2_k})} = \sqrt{2}\Delta_k \delta$.

Next, upper bound $\mathcal{B}_i(t)$. In contrast to $T_k(t)$, there is no lower bound for $T_i(t)$ available yet that we could plug in. Thus we derive:

\begin{IEEEeqnarray*}{rCl}
\mathcal{B}_i(t) & = & \sqrt{T_i(t)} \hat{\Delta}_i(t) 
\\
& \leq & \sqrt{T_i(t)} (\Delta_i + \sqrt{\frac{T \delta^2}{H T_i(t)}})
\\
& = & \sqrt{T_i(t)} \Delta_i + \delta \sqrt{\frac{T}{H}}
\end{IEEEeqnarray*}

Combining the two bounds, we get a lower bound on the pulls for every other arm $i$:

\begin{IEEEeqnarray*}{rCl}
\Delta_i \sqrt{T_i(t)} + \delta \sqrt{\frac{T}{H}} & \geq & (\frac{1}{\sqrt{2}} - \delta) \sqrt{\frac{T}{H}}
\\
\sqrt{T_i(t)} & \geq & (\frac{1}{\sqrt{2}} - 2\delta) \sqrt{\frac{T}{H}} \frac{1}{\Delta_i}
\\ 
& & \text{(choose $2\delta > 1 / \sqrt{2}$ such that RHS is greater 0)}
% \\
% T_i(t) & \geq & (\frac{1}{2} - 2\sqrt{2} \delta + 4\delta^2) \underbrace{\frac{T}{H} \frac{1}{\Delta_i^2}}_\text{$i$'s share of the budget}
% \\
% T_i(t) & \geq & (1 - 4 \sqrt{2} \delta + 8\delta^2) \frac{T}{2H} \frac{1}{\Delta_i^2}
\end{IEEEeqnarray*}

#### Conclusion

As stated before, we require the lower bound on $T_i(t)$ in order to show that $|\hat{\mu}_i(t) - \mu_i | \leq \sqrt{frac{T \delta^2}{H T_i(t)}}$ holds for all $i$. So if we now simply plug in the derived lower bound, we get:

\begin{equation*}
\mu_i - \Delta_i (\frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}) \leq \hat{\mu}_i(t) \leq \mu_i + \Delta_i (\frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta})
\end{equation*}

and with $\lambda := (\frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}) > 0$:

\begin{equation*}
\mu_i - \Delta_i \lambda \leq \hat{\mu}_i(t) \leq \mu_i + \Delta_i \lambda
\end{equation*}

Under this formulation on $\xi$, do we accept arms with $\mu_i \geq \tau + \epsilon$? For these arms holds that $\Delta_i = \mu_i - \tau + \epsilon$. Consequently:

\begin{IEEEeqnarray*}{rCl}
\mu_i - (\mu_i - \tau + \epsilon) \lambda & \leq & \hat{\mu}_i(t) 
\\ 
\hat{\mu}_i(t) & \geq & \tau \lambda + \mu (1-\lambda) - \epsilon \lambda
\end{IEEEeqnarray*}

The arms are accepted if

\begin{IEEEeqnarray*}{rCl}
\hat{\mu}_i(t) - \epsilon & \geq & 0
\end{IEEEeqnarray*}

Or equivalently as long as

\begin{IEEEeqnarray*}{rCl}
\tau \lambda + \mu(1-\lambda) - \epsilon \lambda - \tau & \geq & 0
\\
\lambda & \leq & \frac{1}{2}
\end{IEEEeqnarray*}

### 2017-05-14 Thresholding Bandit/ThresholdingBandit.Rmd
initial commit

--- 
title: "The Thresholding Bandit Problem"
author: "Tim Radtke" 
date: "4/23/2017"
header-includes:
   #- \documentclass[a4paper,twoside,english]{article}
   - \usepackage[retainorgcmds]{IEEEtrantools}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{bbm}
   - \newtheorem{theorem}{Theorem}
   - \newcommand{\KL}{\,\text{KL}}
   - \newcommand{\der}{\,\text{d}}
   #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
   #- \usepackage{fontspec}
   #-   \setmainfont{Arial}
keep_tex: TRUE
output:
  pdf_document:
    number_sections: true
    keep_tex: true
    #latex_engine: xelatex
fontsize: 12pt
urlcolor: blue
---

The *Thresholding Bandit Problem* described in Locatelli et al. (2016) can be considered a variant of a variant. It can be framed into the wider literature of *Pure Exploration* multi-armed bandit problems. In particular, it shares characteristics with the *Top-$m$* problem. This problem is concerned with finding the $m$ best arms as described by the means of their corresponding distributions. This in turn is similar to the *combinatorial bandit* problem, which also aims at finding the $m$ best arms. However, it is able to pull several arms at once: Think of an online shop that shows five recommended products on a product detail page. These five recommended products might each be represented by an arm, and we look for the products with the largest mean conversion rate. The thresholding bandit problem we discuss here, however, is concerned with pulling a single arm at a time. And so a more appropriate situation is that of a website presenting a banner. Again, think of an online shop trying to promote a certain category. The content team came up with a number of different designs for the banner, and it's not clear how many click-throughs they will gather.

The idea now is that we would like to classify the banners into two distinct groups: A group with a mean conversion rate $\mu_i$ below threshold $\tau$, and a group with mean conversion rate $\mu_i$ above threshold $\tau$. This might be the optimization problem when we are concerned with not falling below a certain minimum level click-through rate with the banners we're choosing.

If it turns out that in general we can find relatively quickly whether arms are above or below a threshold, then this kind of test can be used to safeguard against very bad versions in a test. Before we move to a Top-$m$ test, we might want to run a thresholding version and then continue only with the arms classified into the group above the threshold. This might be justified when adjusting parts of the checkout process of an online shop, where the conversion rate or the average order value should not drop below a threshold.

## Setup

In any case, the problem boils down to the following. As standard in multi-armed bandit problems, we have $K$ arms $\mathcal{A} = \{1, \dots K\}$. We can pull arm $k$ at time $t$ to collect feedback in form of the random variable $X_{k,t}$ which is distributed accoring to the arm's distribution $\nu_k$. In general, we are concerned with estimating for each arm $i$ the mean $\mu_i$ of its distribution $\nu_i$. In contrast to most bandit problems, however, we do not directly compare arms with each other by comparing their means. In the case of pure exploration bandits, it is for example necessary to compare the arms because one aims to find the best one. In the case of the thresholding bandit, however, we compare each arm's mean $\mu_i$ individually against the threshold $\tau \in \mathbb{R}$ which is known and fixed before the experiment. One might compare this to a pure exploration bandit in which the mean of the best arm is known upfront. We will see later that this fact leads to advantages in the design of algorithms which are not as readily available in other bandit settings.

### 2017-05-14 Thresholding Bandit/ThresholdingBandit.tex
initial commit

--- 2017-05-14 Thresholding Bandit/Theorem1.tex
@@
 \hypersetup{unicode=true,
-            pdftitle={Theorems and Proofs},
+            pdftitle={The Thresholding Bandit Problem},
             pdfauthor={Tim Radtke},
@@
 \setlength{\droptitle}{-2em}
-  \title{Theorems and Proofs}
+  \title{The Thresholding Bandit Problem}
   \pretitle{\vspace{\droptitle}\centering\huge}
@@
 
-\subsection{Theorem 1}\label{theorem-1}
+The \emph{Thresholding Bandit Problem} described in Locatelli et al.
+(2016) can be considered a variant of a variant. It can be framed into
+the wider literature of \emph{Pure Exploration} multi-armed bandit
+problems. In particular, it shares characteristics with the
+\emph{Top-\(m\)} problem. This problem is concerned with finding the
+\(m\) best arms as described by the means of their corresponding
+distributions. This in turn is similar to the \emph{combinatorial
+bandit} problem, which also aims at finding the \(m\) best arms.
+However, it is able to pull several arms at once: Think of an online
+shop that shows five recommended products on a product detail page.
+These five recommended products might each be represented by an arm, and
+we look for the products with the largest mean conversion rate. The
+thresholding bandit problem we discuss here, however, is concerned with
+pulling a single arm at a time. And so a more appropriate situation is
+that of a website presenting a banner. Again, think of an online shop
+trying to promote a certain category. The content team came up with a
+number of different designs for the banner, and it's not clear how many
+click-throughs they will gather.
 
-In Theorem 1 of Locatelli et al. (2016), a lower bound for the
-thresholding bandit problem is shown. The basic idea is as follows. The
-problem formulation considered in the paper describes bandit problems
-for Sub-Gaussian distributions. To show a lower bound, we show that
-every algorithm is expected to make a certain error even if we restrict
-ourselves to a heavily specified scenario. Even then, any algorithm will
-have a certain level of risk with which it cannot distinguish between
-the actual setting and a slightly changed setting (under which the
-former answer leads to regret).
+The idea now is that we would like to classify the banners into two
+distinct groups: A group with a mean conversion rate \(\mu_i\) below
+threshold \(\tau\), and a group with mean conversion rate \(\mu_i\)
+above threshold \(\tau\). This might be the optimization problem when we
+are concerned with not falling below a certain minimum level
+click-through rate with the banners we're choosing.
 
-To be more specific, consider a case in which we set \(\tau = 0\) and
-\(\epsilon = 0\) w.l.o.g. If we then choose all arms to have normally
-distributed feedback with means \(\mu_i\), we see that for each arm
-\(i\) the distance from the threshold is given by
-\(\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i\). Thus, assuming a
-variance of 1 for every arm, we have for every arm the distribution
-\(\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)\). Furthermore,
-define \(\nu_i' = \mathcal{N}(-\Delta_i,1)\).
+If it turns out that in general we can find relatively quickly whether
+arms are above or below a threshold, then this kind of test can be used
+to safeguard against very bad versions in a test. Before we move to a
+Top-\(m\) test, we might want to run a thresholding version and then
+continue only with the arms classified into the group above the
+threshold. This might be justified when adjusting parts of the checkout
+process of an online shop, where the conversion rate or the average
+order value should not drop below a threshold.
 
-The idea now is that every arm \(i \in \{1,\dots,K\}\) generates a
-sample for every time point \(t\in \{1, \dots, T\}\) from its
-distribution \(\nu_i\) before the algorithm starts to choose arms. Thus,
-we have a \(T \times K\) table of realized observations from the product
-distribution given by
-\(\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K\).
-This is a product distribution where the \(K\) different means all lie
-above the threshold. We would hope that an algorithm classifies the
-means accordingly. However, we will show in what follows that any
-algorithm makes a certain error by not being able to distinguish
-\(\mathcal{B}^0\) from a product distribution \(\mathcal{B}^i\) which
-differs only slightly and has the same overall complexity (as defined by
-\(H = \sum_{i=1}^K (\Delta_i)^{-2}\)).
+\subsection{Setup}\label{setup}
 
-Before the start of the algorithm, we introduce a slight variation in
-the setup. Similar to how one can switch arms in the pure exploration
-setup for multi-armed bandits (compare Audibert et al., Garivier \&
-Kaufmann) to ``confuse'' the algorithm without introducing additional
-complexity to the specified problem. However, since we do not compare
-arms with each other directly in the thresholding bandit problem
-(switching arms would still keep all means above the threshold), we
-instead need to flip an arm with respect to the threshold. Since the
-threshold is \(\tau = 0\), we have for the flipped arm the new
-distribution \(\nu_i'\) as defined above. Indeed, we can define the new
-product distribution \(B^i = \nu_1^i \otimes \dots \otimes \nu_K^i\)
-where for
-\(k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}\).
-This flipping of the arm corresponds to multiplying all random variables
-\(X_{i,t}\) of arm \(i\) by \(-1\).
-
-As in Locatelli et al. (2016), we let for \(i \leq K\),
-\(\mathbb{P}_{\mathcal{B}^i}\) define the probability distribution
-describing all samples that a bandit strategy can potentially collect up
-to horizon \(T\), i.e.~according to the samples
-\((X_{k,s})_{k\leq K, s \leq T} \sim (\mathcal{B}^i)^{\otimes T}\).
-\((T_k)_{k\leq K}\) denotes the number of samples collected on arm \(k\)
-until time \(T\).
-
-\paragraph{Reminder about the goal of the
-proof}\label{reminder-about-the-goal-of-the-proof}
-
-At this point, we have defined a finite set of problems of Gaussian
-distributions with fixed variance 1 for a given set of set of gaps
-between the means of the distributions and the threshold, \((d_k)_k\).
-We will now proof a lower bound on the worst case regret of any
-algorithm; that is, the maximum error probability that even the best
-algorithm makes on this problem.
-
-\paragraph{Statistical Decision}\label{statistical-decision}
-
-Given our formulation of the regret, the expected regret
-\(\mathbb{E}[\mathcal{L}(T)]\) corresponds directly to the probability
-of making a wrong classification of any of the \(K\) means. In general,
-let \(T\) be a binary decision function, and define
-\(\Omega = \{T = 0\}\) and \(\Omega^C = \{T = 1\}\). Assume that the
-decision \(T\) distinguishes between two states of the world, \(H_0\)
-and \(H_1\). Then our overall error probability is given by
-\(P_{H_0}(T=1) + P_{H_1}(T = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)\).
-
-In our case, \(H_0\) may correspond to the state in which we have
-\(\mathcal{B}^0\), and \(H_1\) corresponds to the case where any arm has
-been flipped, \(\mathcal{B}^i\). Furthermore, we consider the events in
-which the algorithm, making the decision, classifies arm \(i\) as being
-above the threshold: \(\mathcal{A}_i = \{i \in \hat{S}_\tau\). The event
-on which all arms are being classified as above the threshold is
-consequently given by \(\mathcal{A} = \bigcap \mathcal{A}_i\). However,
-Theorem 1 does not bound the overall regret, but the maximum error
-probability. We can write this now as
-
-\begin{equation}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big)
-= \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
-\end{equation}
-
-In order to give a bound on above equation, we start by considering
-\(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\). This probability can be
-measured as the expected change in the likelihood of observed data times
-the probability under the original state. The measure of event
-\(\mathcal{A}_i\) under state \(\mathcal{B}^i\) is given as the
-probability of \(\mathcal{A}_i\) under the (original) state
-\(\mathcal{B}^0\) multiplied by a factor. This factor is the change in
-the data likelihoods due to moving from \(\mathcal{B}^0\) to
-\(\mathcal{B}^i\), and is expressed as the expected likelihood ratio
-under \(\mathcal{B}^0\). By definition though, this is equal to the
-empirical Kullback-Leibler divergence of the two measures.
-
-First, let us define the change of measure in terms of the empirical
-log-likelihood for our case. Then, we will show how to replace the
-log-likelihood by the empirical Kullback-Leibler divergence.
-
-Let every \(\nu_i, \nu_i'\) be dominated by the Lebesgue measure
-\(\lambda\). Then their density functions are given by
-\(f_i = \frac{\der \nu_i}{\der \lambda}\) and
-\(f_i' = \frac{\der \nu_i'}{\der \lambda}\) respectively. For
-\(T \geq t \geq 0\), define the empirical Kullback-Leibler divergence as
-
-\begin{align*}
-\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log(\frac{\der \nu_k'}{\der \nu_k}(X_{k,s})) \\
-& = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
-& = \frac{1}{t} \log \big( \prod_{s=1}^{t} \frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
-& \stackrel{\text{iid}}{=} \frac{1}{t} \log \big( \frac{f_k'(X_{k,1}, \dots,X_{k,t})}{f_k(X_{k,1}, \dots,X_{k,t})} \big) \\
-& = \frac{1}{t} \log \big( \text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k) \big)
-\end{align*}
-
-Since we consider Gaussian distributions with variance 1, we have
-density functions
-\(f_i(x) \propto \exp \big(-\frac{1}{2} (x-\Delta_i)^2\big)\) and
-\(f_i'(x) \propto \exp \big(-\frac{1}{2} (x+\Delta_i)^2\big)\). Plugging
-this into the above definition of the empirical Kullback-Leibler
-divergence, we easily see
-
-\begin{align*}
-\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{\exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2\big)}{\exp \big(-\frac{1}{2} (X_{k,s}-\Delta_k)^2\big)} \big) \\
-& = \frac{1}{t} \sum_{s=1}^{t} \log \big( \exp(-\frac{1}{2} (X_{k,s}+\Delta_k)^2 + \frac{1}{2} (X_{k,s}-\Delta_k)^2) \big) \\
-& = - \frac{1}{t} \sum_{s=1}^{t} 2 X_{k,s} \Delta_k
-\end{align*}
-
-\paragraph{Change of Measure}\label{change-of-measure}
-
-We are now ready to state the change of measure. As alluded to above, we
-consider how the probability changes for the event \(\mathcal{A}_i\)
-when we move from \(\mathcal{B}^0\) to \(\mathcal{B}^i\). When flipping
-arm \(i\), we only changed the samples of this arm, that is, the first
-\(T_i\) observations we got from arm \(i\) the algorithm took. The
-change of measure is then defined as:
-
-\begin{align*}
-\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \text{LR}((X_{i,1}, \dots,X_{i,T_i}), \nu_i', \nu_i) ] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ]
-\end{align*}
-
-Obviously, \(\hat{\KL}_{i,T_i}\) depends on the realized samples
-\(X_{i,1}, \dots,X_{i,T_i}\). Consequently, we need to find a bound on
-\(\hat{\KL}_{i,T_i}\) itself to incorporate the uncertainty involved in
-this metric.
-
-\paragraph{Kullback-Leibler
-Divergence}\label{kullback-leibler-divergence}
-
-For our problem, the Kullback-Leibler divergence of \(/nu_k'\) from
-\(\nu_k\) is given by \(\KL_k := KL(\nu_k', \nu_k) = 2\Delta_k^2\).
-
-\paragraph{Concentration of the Empirical Kullback-Leibler
-Divergence}\label{concentration-of-the-empirical-kullback-leibler-divergence}
-
-It is easy to see that
-
-\begin{equation*}
-|\hat{\KL}_{k,t} - \KL_{k,t}| = |-\frac{2}{t} \Delta_k \sum_{s=1}^{t}(X_{k,s} - \Delta_k)|
-\end{equation*}
-
-itself is a normally distributed random variable with mean zero and a
-variance decreasing in \(t\). Thus, one can show that
-\(\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4\) for the event
-
-\begin{equation}
-\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}} \}. \label{LocatelliTheorem1EventXi}
-\end{equation}
-
-Thus, in order to bound the empirical Kullback-Leibler divergence in our
-change of measure, we can consider the intersection of \(\mathcal{A}_i\)
-and \(\xi\) as follows and plug in the bound on event \(\xi\):
-
-\begin{align*}
-\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
-\end{align*}
-
-Two things are left to do: With \(T_i\), we still have one random
-variable left which we cannot leave in our bound. Second, we are
-actually not interested in \(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)
-but in
-\(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\).
-
-\paragraph{\texorpdfstring{Bounding \(T_i\) for
-\(\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)}{Bounding T\_i for \textbackslash{}max\_\{i \textbackslash{}in \textbackslash{}\{1,\textbackslash{}dots,K\textbackslash{}\}\}\textbackslash{}mathbb\{P\}\_\{\textbackslash{}mathcal\{B\}\^{}i\}(\textbackslash{}mathcal\{A\}\_i)}}\label{bounding-t_i-for-max_i-in-1dotskmathbbp_mathcalbimathcala_i}
-
-Part of our bound is
-\(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\),
-so let's continue with that. In general it holds that
-\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \bar{X}\). Thus we can
-write:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
-& \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
-& \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
-\end{align*}
-
-where the second line is again the intersection of \(\mathcal{A}_i\) and
-\(\xi\) as before in order to apply the change of measure again in the
-third line.
-
-What is left to show before we have our final bound is a bound on
-\(T_i\). To show that any algorithm has a certain bound on its error, it
-only makes sense that every arm has to pulled at least a certain amount
-of times. Consequently, no arm should be pulled exclusively.
-
-First, let \(a = \Delta_i \sqrt{T_i}\) and
-\(b = 4\sqrt{\log((4\log(T)+1)K)}\). Then use \(ab \leq a^2 + b^2\) to
-write \(ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)\). And so:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) ]
-\end{align*}
-
-Furthermore, we know that the sum of the individual arm pulls has to be
-equal to the overall number of pulls (equal to the budget in the fixed
-budget sense), \(\sum_i T_i = T\), and furthermore we know that
-\(T_i>0\). The latter holds since any reasonable algorithm has to check
-each arm at least once in our setup. This is because we need to check
-each arm's performance in comparison to the threshold. Thus it is easy
-to show that
-\(\exists i: T_i \leq \frac{T}{H \Delta_i^2} = \frac{T}{(\sum_{i=1}^{K} \Delta_i^{-2}) \Delta_i^2}\).
-To see this, assume the opposite:
-\(\forall i: T_i > T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2}\). This
-implies however
-\(\sum_{i=1}^K T_i > \sum_{i=1}^K T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2} = T \cdot 1 = T\)
-which is a contradiction.
-
-So we can write \((\Delta_i \sqrt{T_i})^2 \leq \frac{T}{H}\). We use
-\(\mathcal{A} = \cap_{i=1}^K \mathcal{A}_i\) to write:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}{K} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big]
-\end{align*}
-
-We write
-\(\frac{1}{K} \sum_{i=1}^K \exp(-3T_i \Delta_i^2) \geq \frac{1}{K} \sum_{i=1}^K \exp(-3 T/H) = \exp(-3 T/H)\).
-Thus:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i) \exp(-16 \log(4(\log(T)+1)K)) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
-& = \mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
-\end{align*}
-
-\paragraph{Conclusion}\label{conclusion}
-
-Consider again the risk which we need to bound from equation
-\eqref{LocatelliTheorem1ExpRegret}. We bound the maximum expected loss
-over all \(\mathcal{B}_i\). By again using the fact that in general
-\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \bar{X}\), we plug in
-our previous calculations:
-
-\begin{align}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \label{LocatelliTheorem1DefinitionOfRisk}
-\end{align}
-
-From \eqref{LocatelliTheorem1EventXi} we know that for any
-\(i \in \{0, \dots, K\}\), \(\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4\).
-Following the argument in Locatelli et al. (2016), we now consider two
-cases: \(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2\) and
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2\). In the former
-case, we can plug in the two probabilities into
-\eqref{LocatelliTheorem1DefinitionOfRisk}. If
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2\) and
-\(\mathbb{P}_{\mathcal{B}^0}(\xi) \geq 3/4\), then
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \geq 1/4\). Thus:
-
-\begin{align*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \\
-& \geq \frac{1}{8} \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
-\end{align*}
-
-where we drop the second summand of the second line so that the
-inequality holds.
-
-On the other hand, when
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2\), then we know that
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \leq 1/2\) for any
-\(\mathbb{P}_{\mathcal{B}^0}(\xi)\). At the same time
-\(1-\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \geq 1/2\).
-Consequently,
-\(1/4 \leq \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \leq 1/2\),
-while
-\(\frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) \geq 0\).
-And so the stronger lower bound in that case is, as noticed by Locatelli
-et al. (2016), given simply by
-
-\begin{align*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \\
-& \geq \frac{1}{2}
-\end{align*}
+In any case, the problem boils down to the following. As standard in
+multi-armed bandit problems, we have \(K\) arms
+\(\mathcal{A} = \{1, \dots K\}\). We can pull arm \(k\) at time \(t\) to
+collect feedback in form of the random variable \(X_{k,t}\) which is
+distributed accoring to the arm's distribution \(\nu_k\). In general, we
+are concerned with estimating for each arm \(i\) the mean \(\mu_i\) of
+its distribution \(\nu_i\). In contrast to most bandit problems,
+however, we do not directly compare arms with each other by comparing
+their means. In the case of pure exploration bandits, it is for example
+necessary to compare the arms because one aims to find the best one. In
+the case of the thresholding bandit, however, we compare each arm's mean
+\(\mu_i\) individually against the threshold \(\tau \in \mathbb{R}\)
+which is known and fixed before the experiment. One might compare this
+to a pure exploration bandit in which the mean of the best arm is known
+upfront. We will see later that this fact leads to advantages in the
+design of algorithms which are not as readily available in other bandit
+settings.
 

### 2017-05-14 R/KL_visualization.R

@@ -1,0 +1,51 @@
+# Visualization of KL Divergence for different Bernoullis
+
+KL_ber <- function(p,q) p*log(p/q) + (1-p)*log((1-p)/(1-q))
+
+KL_ber_approx <- function(p,q) (p-q)^2
+
+plot(seq(0.01,0.99,by = 0.01), KL_ber(seq(0.01,0.99,by = 0.01),0.001), type = "l")
+lines(seq(0.01,0.99,by = 0.01), KL_ber_approx(seq(0.01,0.99,by = 0.01), 0.001))
+
+lines(seq(0.01,0.99,by = 0.01), KL_ber(seq(0.01,0.99,by = 0.01), 0.0075),
+      col = "blue")
+lines(seq(0.01,0.99,by = 0.01), KL_ber(seq(0.01,0.99,by = 0.01), 0.01),
+      col = "green")
+lines(seq(0.01,0.99,by = 0.01), KL_ber_approx(seq(0.01,0.99,by = 0.01), 0.01),
+      col = "red")
+lines(seq(0.01,0.99,by = 0.01), KL_ber_approx(seq(0.01,0.99,by = 0.01), 0.01),
+      col = "red")
+
+plot(seq(0.01,0.99,by = 0.01), KL_ber(seq(0.01,0.99,by = 0.01),0.001), type = "l")
+for (i in c(0.001,0.01,0.1,0.5)) {
+  lines(seq(0.01,0.99,by = 0.01), KL_ber(seq(0.01,0.99,by = 0.01), i),)
+  lines(seq(0.01,0.99,by = 0.01), KL_ber_approx(seq(0.01,0.99,by = 0.01), i),
+        col = "red")
+}
+
+lines(seq(0.01,0.99,by = 0.01), 8.5*seq(0.01,0.99,by = 0.01),
+      lty=2)
+
+#### Show asymmetry of KL when moving close to 0 or 1
+#### (the divergence is different on the two sides of the threshold even though
+#### the absolute difference between theta and tau is the same on both sides)
+KL_comp <- function(theta1, theta2, tau) round(KL_ber(theta1,tau) - KL_ber(theta2,tau),5)
+
+# compare theta=0.45 and 0.55 to tau=0.5 (should be similar)
+KL_comp(0.45,0.55,0.5)  # 0
+
[…]

### 2017-05-14 R/Simulations/BTTS2_parallelized.R

@@ -1,0 +1,322 @@
+# simulation_functions
+
+library(plyr); library(dplyr); library(doParallel); library(parallel)
+
+simulate_data_bernoulli <- function(variants = 3,
+                                    means = c(0.5, 0.55, 0.6), 
+                                    rounds = 10000,
+                                    equal_splits = TRUE,
+                                    splits = NULL,
+                                    seed = NULL) {
+  if(variants != length(means)) {
+    stop("Number of variants does not equal number of means.")
+  }
+  
+  if(!is.null(splits)) {
+    if(sum(splits != 1)) {
+      stop("Splits don't sum up to 1.")
+    }
+  }
+  
+  if(is.null(splits)) {
+    splits <- rep(1/variants, times = variants)
+  }
+  
+  if(variants != length(splits)) {
+    stop("Number of variants does not equal number of splits.")
+  }
+  
+  if(!is.null(seed)) {
+    set.seed(seed)
+  }
+  
+  variant_names <- toupper(letters[1:variants])
+  variant_seq <- sample(variant_names, size = rounds, 
+                        replace = TRUE, prob = splits)
+  
+  params <- data.frame(variant = variant_names, mean = means,
+                       stringsAsFactors = FALSE)
+  experiment <- data.frame(variant = variant_seq,
+                           stringsAsFactors = FALSE)
+  experiment <- dplyr::left_join(experiment, params)
+  
+  experiment <- experiment %>% group_by(variant) %>%
+    dplyr::mutate(success = rbinom(n(), 1, mean),
+                  trials = n(),
+                  successes = sum(success),
+                  success_rate = successes/trials) %>%
+    ungroup() %>% as.data.frame()
+  
+  experiment_summary <- experiment %>%
+    select(variant, mean, trials, successes, success_rate) %>%
+    distinct() %>%
+    dplyr::arrange(variant)
+  
+  return(list(
+    experiment = experiment,
+    experiment_summary = experiment_summary
+  ))
+}
+
+
+# assumes that the argument data is a data frame with first column containing
+# the variants that are checked for;
+get_next_row <- function(data, variant, current_row) {
+  n <- dim(data)[1]
+  # if there is an observation remaining
[…]

### 2017-05-14 R/Simulations/BTTS_parallelized.R

@@ -1,0 +1,263 @@
+# simulation_functions
+
+library(plyr); library(dplyr); library(doParallel); library(parallel)
+
+simulate_data_bernoulli <- function(variants = 3,
+                                    means = c(0.5, 0.55, 0.6), 
+                                    rounds = 10000,
+                                    equal_splits = TRUE,
+                                    splits = NULL,
+                                    seed = NULL) {
+  if(variants != length(means)) {
+    stop("Number of variants does not equal number of means.")
+  }
+  
+  if(!is.null(splits)) {
+    if(sum(splits != 1)) {
+      stop("Splits don't sum up to 1.")
+    }
+  }
+  
+  if(is.null(splits)) {
+    splits <- rep(1/variants, times = variants)
+  }
+  
+  if(variants != length(splits)) {
+    stop("Number of variants does not equal number of splits.")
+  }
+  
+  if(!is.null(seed)) {
+    set.seed(seed)
+  }
+  
+  variant_names <- toupper(letters[1:variants])
+  variant_seq <- sample(variant_names, size = rounds, 
+                        replace = TRUE, prob = splits)
+  
+  params <- data.frame(variant = variant_names, mean = means,
+                       stringsAsFactors = FALSE)
+  experiment <- data.frame(variant = variant_seq,
+                           stringsAsFactors = FALSE)
+  experiment <- dplyr::left_join(experiment, params)
+  
+  experiment <- experiment %>% group_by(variant) %>%
+    dplyr::mutate(success = rbinom(n(), 1, mean),
+                  trials = n(),
+                  successes = sum(success),
+                  success_rate = successes/trials) %>%
+    ungroup() %>% as.data.frame()
+  
+  experiment_summary <- experiment %>%
+    select(variant, mean, trials, successes, success_rate) %>%
+    distinct() %>%
+    dplyr::arrange(variant)
+  
+  return(list(
+    experiment = experiment,
+    experiment_summary = experiment_summary
+  ))
+}
+
+
+# assumes that the argument data is a data frame with first column containing
+# the variants that are checked for;
+get_next_row <- function(data, variant, current_row) {
[…]

### 2017-05-14 R/Simulations/functions.R

@@ -1,0 +1,363 @@
+# simulation_functions
+
+library(plyr); library(dplyr)
+
+simulate_data_bernoulli <- function(variants = 3,
+                                    means = c(0.5, 0.55, 0.6), 
+                                    rounds = 10000,
+                                    equal_splits = TRUE,
+                                    splits = NULL,
+                                    seed = NULL) {
+  if(variants != length(means)) {
+    stop("Number of variants does not equal number of means.")
+  }
+  
+  if(!is.null(splits)) {
+    if(sum(splits != 1)) {
+      stop("Splits don't sum up to 1.")
+    }
+  }
+  
+  if(is.null(splits)) {
+    splits <- rep(1/variants, times = variants)
+  }
+  
+  if(variants != length(splits)) {
+    stop("Number of variants does not equal number of splits.")
+  }
+  
+  if(!is.null(seed)) {
+    set.seed(seed)
+  }
+  
+  variant_names <- toupper(letters[1:variants])
+  variant_seq <- sample(variant_names, size = rounds, 
+                        replace = TRUE, prob = splits)
+  
+  params <- data.frame(variant = variant_names, mean = means,
+                       stringsAsFactors = FALSE)
+  experiment <- data.frame(variant = variant_seq,
+                           stringsAsFactors = FALSE)
+  experiment <- dplyr::left_join(experiment, params)
+  
+  experiment <- experiment %>% group_by(variant) %>%
+    dplyr::mutate(success = rbinom(n(), 1, mean),
+           trials = n(),
+           successes = sum(success),
+           success_rate = successes/trials) %>%
+    ungroup() %>% as.data.frame()
+  
+  experiment_summary <- experiment %>%
+    select(variant, mean, trials, successes, success_rate) %>%
+    distinct() %>%
+    dplyr::arrange(variant)
+  
+  return(list(
+    experiment = experiment,
+    experiment_summary = experiment_summary
+  ))
+}
+
+
+# assumes that the argument data is a data frame with first column containing
+# the variants that are checked for;
+get_next_row <- function(data, variant, current_row) {
+  n <- dim(data)[1]
+  # if there is an observation remaining
+  if(sum(data[(current_row+1):n,1] == variant) > 0) {
+    next_row <- current_row + min((1:n)[data[(current_row+1):n,1] == variant])
[…]

### 2017-05-15 Thresholding Bandit/ThresholdingBandit.Rmd
add gitignore, update Thresholding Bandit

@@
 We will see later that this fact leads to advantages in the design of algorithms which are not as readily available in other bandit settings.
+
+In Locatelli (2016), the arms' distributions are assumed to follow a $R$-sub-Gaussian distribution.
+Under this assumption, the authors are able to proof a general lower bound as well as an algorithm with a matching upper bound.
+Both hinge upon the *complexity* of a given problem.
+Since bandit problems can differ in the number of the arms $K$ and the means of each arm, some pose easier identification problems than others.
+Indeed, in the thresholding problem, the difficulty of the problem naturally depends on how close (the means of the) distributions are to the fixed threshold.
+Intuitively, the closer a mean $\mu_i$ is to the threshold $\tau$, the more difficult it will be to distinguish the two successfully based on samples from the distribution $\nu_i$.
+For the case of the sub-Gaussian distributions, a natural measure of this distance is given by simply $\Delta_i = |\tau - \mu_i| + \epsilon$, where $\epsilon$ defines a $2\epsilon$ interval around the threshold $\tau$ in which we allow ourselves to make a mistake at no cost.
+
+If we extend this idea to the set of arms $i \in \{1,...,K\}$ of a given bandit problem, a natural measure of the overall diffulty of the problem, or the problem's complexity, might be given by $H = \sum_{i=1}^{K} \Delta_i^{-2}$.
+In particular, it shows that just adding additional arms leads to an increase in complexity (since we need to sample more of them), just as smaller $\Delta_i$ will increase the complexity as arms become harder to classify.
+(WHERE DOES THIS COMPLEXITY ORIGINALLY COME FROM?
+WHAT IS ITs MOTIVATION?
+ITS NOT THAAAT NATURAL)
+
+We also see that this definition may lose relevancy as we move away from $R$-sub-Gaussian distributions.
+(ADD QUICK EXAMPLE OF WHAT CHANGES; REFER TO LATER PART AND DESCRIBE THIS AS THE MOTIVATION OF THE PAPER)
+
+Another characteristic uniquely identifying bandit problems is the regret measure that we aim to optimize.
+As explained during the introduction, multi-armed bandits traditionally optimize cumulative regret.
+The notion of regret considered in the thresholding bandit, however, is more akin to the regret in pure exploration bandits or the error probability in sequential hypothesis testing.
+Indeed, one can most easily describe the regret in the thresholding case as the probability of making a misclassification of any arm.
+Or, more rigorously, let us define the set of all arms with mean larger than the threshold, $\mathcal{S}_\tau = \{i \in \mathcal{A}: \mu_i \geq \tau\}$.
+Consequently, $\mathcal{S}_\tau^C = \{i \in \mathcal{A}: \mu_i < \tau\}$.
+At the end of the sampling rule/procedure (!!we have not mentioned yet the fact that we're in the fixed budget case!!), we demand that any algorithm returns the two corresponding *estimated* sets: $\hat{\mathcal{S}}_{\tau} = \{i \in \mathcal{A}: \hat{\mu}_i \geq \tau\}$, as well as $\hat{\mathcal{S}}_{\tau}^C = \{i \in \mathcal{A}: \hat{\mu}_i < \tau\}$.
+We simply demand an answer to the question which arms have means above the threshold $/tau$, and which arms lie below  $\tau$.
+Let $T$ be the overall number of samples the algorithm is allowed to pull.
+We define the loss as $\mathcal{L}(T) = \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset\}} \cdot \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset\}}$.
+That is, we compare the return set with the true set and collect a loss of 1 if any arm with a true mean outside the $2\epsilon$ interval around $\tau$ was misclassified.
+It is important to realize that arms with means inside the $2 \epsilon$ interval may be misclassified without it affecting the loss.
+These arms are considered close enough to the threshold that we do not care whether they lie above or below.
+
+ADD A GRAPHIC THAT VISUALIZES THE ESTIMATED AND THE REQUIRED RETURN SETS
+
+From there, it is natural to define the expected regret/loss as $\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \land (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset))$.
+This, of course, is the mentioned probability of making a mistake.
+
+ADD REMARK ON WHAT THIS IMPLIES WITH REGARD TO THE MEANS
+
+Lastly, it is to mention that we are considering the fixed-budget version of the thresholding bandit problem.
+We thus fix the number of samples that the algorithm will pull upfront at $T$.
+The task of the algorithm is then to find a sampling rule or strategy which distributes the budget $T$ among the $K$ arms in such a way that the expected regret, or the error probability, is minimized.
+In other terms, the algorithm aims to use the $T$ samples in a way that lets him return the two sets $\hat{\mathcal{S}}_{\tau}$ and $\hat{\mathcal{S}}_{\tau}^C$ with as much confidence as possible.
+This again shows the contrast to the fixed confidence setting in which one fixes the confidence level upfront and lets the algorithm draw as many samples as necessary to reach the required confidence.
+
+At this point, we have defined the fixed budget thresholding bandit setup for any algorithm in the case of sub-Gaussian distributions.
+We thus proceed to describe the algorithm proposed in Locatelli et al.
+(2016).
+
+## The APT Algorithm
+
+In the following we describe the *Anytime Parameter-free Thresholding* (APT) algorithm proposed in Locatelli et al.
+(2016), which is a simple yet effective algorithm and displays some very favorable characteristics when compared with alternative algorithms.
+
+From the general setup, we already know how the algorithm will end.
+After it has drawn $T$ samples, the algorithm makes its decision of which arms to include in the return sets solely on basis of the empirical means $\hat{\mu}_i(T)$ estimated until time $T$.
+Furthermore, the threshold and interval around the threshold were fixed upfront and serve as argument to the algorithm: $(\tau, \epsilon)$.
+For a given arm $i$ and a given time $t$, we let $T_i(t)$ represent the number of samples drawn from arm $i$ until time $t$ (including).
+Consequently, the empirical mean of arm $i$ at time $t$ is given by $\mu_i = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}$ where $X_{i,s}$ is the feedback sampled from distribution $\nu_i$ when the arm is pulled for the $s$-th time.
+
+To be specific, the APT algorithm initiates by pulling each arm once.
+Then, for each $t > K$, it calculates for every arm the values $T_i(t)$ and $\mu_i(t)$.
+Based on the empirical mean, the algorithm computes the estimated gap between the mean and the threshold as $\hat{\Delta}_i(t) = \hat{\Delta}_i^{\tau, \epsilon}(t) = |\mu_i(t) - \tau| + \epsilon$.
+The decision of which arm is sampled next is then based on the value $B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t)$: the algorithm pulls arm $I_{t+1} = \arg \min_{i\leq K} B_i(t+1)$ minimizing this decision quantity.
+After $T$ pulls overall, the arm returns the sets described in the general setup, $\hat{\mathcal{S}}_{\tau}$ and $\hat{\mathcal{S}}^C_{\tau}$.
+
+**Remark**: Obviously, the APT algorithm tends to pull arms more often with corresponding mean close to the threshold and interval (small $\hat{\Delta}_i(t))$.
+This makes sure that more evidence is gathered on arms which appear to be inherently difficult to classify based on the samples collected until time $T_i(t)$, as these arms stifle the confidence the most.
+That is, until we have collected enough evidence to make a confident classification even if the mean is truly close to the threshold.
+In that case, $\sqrt{T_i(t)}$ will raise $B_i(t+1)$.
+Consequently, other arms farther away from the threshold will be sampled again.
+In this way, the algorithm tries to distribute the budget $T$ over all arms so as to define a sampling rule optimizing the confidence of the final decision.
+Of course, that's just Glivenko-Cantelli and the CLT making sure $B_i(t+1)$ is not degenerate.
+
+## Discussion
+
+One of the APT algorithm's main features is its simplicity.
+The sampling rule is very straightforward, and, as highlighted in Locatelli et al.
+(2016), it does not require any knowledge about the type of sub-Gaussianity $R$, or the complexity $H$ upfront.
+This makes the algorithm immediately applicable in practice while it still enjoys its upper bound on the expected regret.
+This is in particular worth highlighting when comparing APT to algorithms used in the pure exploration bandit setting.
+There, many algorithms require knowledge about the corresponding complexity upfront.
+The problem however being, that to know the complexity, the experimenter has to know all means up to a permutation of the arms (for example, see Audibert et al., 2010).
+This, of course, is not given in practice and thus alternative algorithms try to estimate the complexity online which is not a desirable solution either as especially in the beginning plug-in estimates based on the estimated means may lead to wrong estimates of the complexity and consequently budget allocation based on mistaken beliefs (compare Garivier and Kaufmann, 2016).
+
+Furthermore, Locatelli et al. (2016) were able to present an upper bound for the APT algorithm matching the lower bound in their Theorem 1. Proofs of both bounds are repeated below.
+
+Where the APT algorithm shows room for improvement is when it comes to settings with distributions that are not sub-Gaussian. This is mentioned in Locetelli et al. (2016). They suggest ...

### 2017-05-19 Thresholding Bandit/ThresholdingBandit.Rmd
add need for KL example

@@
 
-Furthermore, Locatelli et al. (2016) were able to present an upper bound for the APT algorithm matching the lower bound in their Theorem 1. Proofs of both bounds are repeated below.
+Furthermore, Locatelli et al. (2016) were able to present an upper bound for the APT algorithm matching the lower bound in their Theorem 1. Proofs of both bounds are given below.
 
-Where the APT algorithm shows room for improvement is when it comes to settings with distributions that are not sub-Gaussian. This is mentioned in Locetelli et al. (2016). They suggest ...
+Where the APT algorithm shows room for improvement is when it comes to settings with distributions that are not sub-Gaussian.
+This is mentioned in Locatelli et al.
+(2016).
+In general, the problem becomes that the assumptions for the bounds no longer hold; furthermore, the statistic $B_i(t+1)$, and the term $\hat{\Delta_i}(t)$ are motivated by (sub-)Gaussian distributions.
+The more one moves away from Gaussian-like distributions, the less appropriate this term becomes, however.
+In particular, the empirical mean will be less concentrated around the true mean and more impacted by outliers which are more likely under non sub-Gaussian distributions.
+Locatelli et al.
+(2016) thus refers to Bubeck et al.
+(2013) which considers solutions for multi-armed bandits that are based on heavy-tail distributions.
+By using more robust estimators of the mean, one could equip the APT algorithm to deal with such distributions.
+
+Another step towards dealing with non sub-Gaussianity is made by Mukherjee et al.
+(2017) who use an estimate of the variance additionally to the empirical mean in their Augmented UCB solution.
+Utilizing this additional information, the algorithm seems to perform better than for example APT, going from simulation results displayed in the paper.
+We will continue to discuss the Augmented UCB solution further in chapter 3.
+
+Yet another idea, again mentioned in Locatelli et al.
+(2016) is to show bounds based on the Kullback-Leibler divergence of the specific distribution directly.
+While the approximation through the Gaussian Kullback-Leibler divergence in the lower bound proof is convenient and leads to the simple APT algorithm, it might not stay appropriate for distributions whose Kullback-Leibler divergence tends to differ from the Gaussian.
+This, for example, is the case for Bernoulli distributions at very small parameters $\mu$.
+It's quite obvious simply by looking at examples that the Kullback-Leibler divergence of Bernoullis starts to lose any similarity to the plain quadratic approximation.
+The second graph then shows, that the actual Kullback-Leibler divergence of Bernoullis also has lost any symmetry over this range of parameter values.
+Given that Bernoulli distributions with very small parameter values arise naturally in many applications in website optimization and advertising click-through modeling, there is a need to tackle this problem.
+
+And so a potential approach can be to use the Kullback-Leibler divergence as measure similar to the methods proposed in Kaufmann et al.
+(2015).
+They proposed Kullback-Leibler based approaches for the pure exploration bandit setting, which we will describe in chapter 2.
+Then, in chapter 3, we will come back to the problem of using the Kullback-Leibler divergence in the thresholding bandit setting.
+
+```{r, echo = FALSE}
+KL_ber <- function(p,q) p*log(p/q) + (1-p)*log((1-p)/(1-q))
+par(mfcol = c(1,2))
+
+plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1), type = "n", asp = 1,
+     xlab = "p_1", ylab = "KL(Ber(p_1),Ber(p_2))", main = "KL of Bernoullis")
+for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
+  lines(seq(0.00001,0.3, by = 0.000005),
+       KL_ber(seq(0.00001,0.3, by = 0.000005),i))
+}
+
+plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1.5), type = "n", asp = 1,
+     xlab = "p_1", ylab = "(p_1 - p_2)^2", main = "Gaussian approx.\n KL of Bernoullis")
+for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
+  lines(seq(0.00001,0.3, by = 0.000005),
+        (seq(0.00001,0.3, by = 0.000005)-i)^2)
+}
+par(mfcol = c(1,1))
+```
+
+```{r, echo = FALSE}
+KL_ber <- function(p,q) p*log(p/q) + (1-p)*log((1-p)/(1-q))
+par(mfcol = c(1,2))
+
+plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1), type = "n", asp = 1,
+     xlab = "p_1", ylab = "KL(Ber(p_2),Ber(p_1))", main = "KL of Bernoullis")
+for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
+  lines(seq(0.00001,0.3, by = 0.000005),
+        KL_ber(i,seq(0.00001,0.3, by = 0.000005)))
+}
+
+plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1.5), type = "n", asp = 1,
+     xlab = "p_1", ylab = "(p_2 - p_1)^2", main = "Gaussian approx.\n KL of Bernoullis")
+for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
+  lines(seq(0.00001,0.3, by = 0.000005),
+        (i-seq(0.00001,0.3, by = 0.000005))^2)
+}
+par(mfcol = c(1,1))
+```

### 2017-05-19 Thresholding Bandit/ThresholdingBandit.tex
add need for KL example

@@
 
+In Locatelli (2016), the arms' distributions are assumed to follow a
+\(R\)-sub-Gaussian distribution. Under this assumption, the authors are
+able to proof a general lower bound as well as an algorithm with a
+matching upper bound. Both hinge upon the \emph{complexity} of a given
+problem. Since bandit problems can differ in the number of the arms
+\(K\) and the means of each arm, some pose easier identification
+problems than others. Indeed, in the thresholding problem, the
+difficulty of the problem naturally depends on how close (the means of
+the) distributions are to the fixed threshold. Intuitively, the closer a
+mean \(\mu_i\) is to the threshold \(\tau\), the more difficult it will
+be to distinguish the two successfully based on samples from the
+distribution \(\nu_i\). For the case of the sub-Gaussian distributions,
+a natural measure of this distance is given by simply
+\(\Delta_i = |\tau - \mu_i| + \epsilon\), where \(\epsilon\) defines a
+\(2\epsilon\) interval around the threshold \(\tau\) in which we allow
+ourselves to make a mistake at no cost.
+
+If we extend this idea to the set of arms \(i \in \{1,...,K\}\) of a
+given bandit problem, a natural measure of the overall diffulty of the
+problem, or the problem's complexity, might be given by
+\(H = \sum_{i=1}^{K} \Delta_i^{-2}\). In particular, it shows that just
+adding additional arms leads to an increase in complexity (since we need
+to sample more of them), just as smaller \(\Delta_i\) will increase the
+complexity as arms become harder to classify. (WHERE DOES THIS
+COMPLEXITY ORIGINALLY COME FROM? WHAT IS ITs MOTIVATION? ITS NOT THAAAT
+NATURAL)
+
+We also see that this definition may lose relevancy as we move away from
+\(R\)-sub-Gaussian distributions. (ADD QUICK EXAMPLE OF WHAT CHANGES;
+REFER TO LATER PART AND DESCRIBE THIS AS THE MOTIVATION OF THE PAPER)
+
+Another characteristic uniquely identifying bandit problems is the
+regret measure that we aim to optimize. As explained during the
+introduction, multi-armed bandits traditionally optimize cumulative
+regret. The notion of regret considered in the thresholding bandit,
+however, is more akin to the regret in pure exploration bandits or the
+error probability in sequential hypothesis testing. Indeed, one can most
+easily describe the regret in the thresholding case as the probability
+of making a misclassification of any arm. Or, more rigorously, let us
+define the set of all arms with mean larger than the threshold,
+\(\mathcal{S}_\tau = \{i \in \mathcal{A}: \mu_i \geq \tau\}\).
+Consequently,
+\(\mathcal{S}_\tau^C = \{i \in \mathcal{A}: \mu_i < \tau\}\). At the end
+of the sampling rule/procedure (!!we have not mentioned yet the fact
+that we're in the fixed budget case!!), we demand that any algorithm
+returns the two corresponding \emph{estimated} sets:
+\(\hat{\mathcal{S}}_{\tau} = \{i \in \mathcal{A}: \hat{\mu}_i \geq \tau\}\),
+as well as
+\(\hat{\mathcal{S}}_{\tau}^C = \{i \in \mathcal{A}: \hat{\mu}_i < \tau\}\).
+We simply demand an answer to the question which arms have means above
+the threshold \(/tau\), and which arms lie below \(\tau\). Let \(T\) be
+the overall number of samples the algorithm is allowed to pull. We
+define the loss as
+\(\mathcal{L}(T) = \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset\}} \cdot \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset\}}\).
+That is, we compare the return set with the true set and collect a loss
+of 1 if any arm with a true mean outside the \(2\epsilon\) interval
+around \(\tau\) was misclassified. It is important to realize that arms
+with means inside the \(2 \epsilon\) interval may be misclassified
+without it affecting the loss. These arms are considered close enough to
+the threshold that we do not care whether they lie above or below.
+
+ADD A GRAPHIC THAT VISUALIZES THE ESTIMATED AND THE REQUIRED RETURN SETS
+
+From there, it is natural to define the expected regret/loss as
+\(\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \land (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset))\).
+This, of course, is the mentioned probability of making a mistake.
+
+ADD REMARK ON WHAT THIS IMPLIES WITH REGARD TO THE MEANS
+
+Lastly, it is to mention that we are considering the fixed-budget
+version of the thresholding bandit problem. We thus fix the number of
+samples that the algorithm will pull upfront at \(T\). The task of the
+algorithm is then to find a sampling rule or strategy which distributes
+the budget \(T\) among the \(K\) arms in such a way that the expected
+regret, or the error probability, is minimized. In other terms, the
+algorithm aims to use the \(T\) samples in a way that lets him return
+the two sets \(\hat{\mathcal{S}}_{\tau}\) and
+\(\hat{\mathcal{S}}_{\tau}^C\) with as much confidence as possible. This
+again shows the contrast to the fixed confidence setting in which one
+fixes the confidence level upfront and lets the algorithm draw as many
+samples as necessary to reach the required confidence.
+
+At this point, we have defined the fixed budget thresholding bandit
+setup for any algorithm in the case of sub-Gaussian distributions. We
+thus proceed to describe the algorithm proposed in Locatelli et al.
+(2016).
+
+\subsection{The APT Algorithm}\label{the-apt-algorithm}
+
+In the following we describe the \emph{Anytime Parameter-free
+Thresholding} (APT) algorithm proposed in Locatelli et al. (2016), which
+is a simple yet effective algorithm and displays some very favorable
+characteristics when compared with alternative algorithms.
+
+From the general setup, we already know how the algorithm will end.
+After it has drawn \(T\) samples, the algorithm makes its decision of
+which arms to include in the return sets solely on basis of the
+empirical means \(\hat{\mu}_i(T)\) estimated until time \(T\).
+Furthermore, the threshold and interval around the threshold were fixed
+upfront and serve as argument to the algorithm: \((\tau, \epsilon)\).
+For a given arm \(i\) and a given time \(t\), we let \(T_i(t)\)
+represent the number of samples drawn from arm \(i\) until time \(t\)
+(including). Consequently, the empirical mean of arm \(i\) at time \(t\)
+is given by \(\mu_i = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}\)
+where \(X_{i,s}\) is the feedback sampled from distribution \(\nu_i\)
+when the arm is pulled for the \(s\)-th time.
+
+To be specific, the APT algorithm initiates by pulling each arm once.
+Then, for each \(t > K\), it calculates for every arm the values
+\(T_i(t)\) and \(\mu_i(t)\). Based on the empirical mean, the algorithm
+computes the estimated gap between the mean and the threshold as
+\(\hat{\Delta}_i(t) = \hat{\Delta}_i^{\tau, \epsilon}(t) = |\mu_i(t) - \tau| + \epsilon\).
+The decision of which arm is sampled next is then based on the value
+\(B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t)\): the algorithm pulls arm
+\(I_{t+1} = \arg \min_{i\leq K} B_i(t+1)\) minimizing this decision
+quantity. After \(T\) pulls overall, the arm returns the sets described
+in the general setup, \(\hat{\mathcal{S}}_{\tau}\) and
+\(\hat{\mathcal{S}}^C_{\tau}\).
+
+\textbf{Remark}: Obviously, the APT algorithm tends to pull arms more
+often with corresponding mean close to the threshold and interval (small
+\(\hat{\Delta}_i(t))\). This makes sure that more evidence is gathered
+on arms which appear to be inherently difficult to classify based on the
+samples collected until time \(T_i(t)\), as these arms stifle the
+confidence the most. That is, until we have collected enough evidence to
+make a confident classification even if the mean is truly close to the
+threshold. In that case, \(\sqrt{T_i(t)}\) will raise \(B_i(t+1)\).
+Consequently, other arms farther away from the threshold will be sampled
+again. In this way, the algorithm tries to distribute the budget \(T\)
+over all arms so as to define a sampling rule optimizing the confidence
+of the final decision. Of course, that's just Glivenko-Cantelli and the
+CLT making sure \(B_i(t+1)\) is not degenerate.
+
+\subsection{Discussion}\label{discussion}
+
+One of the APT algorithm's main features is its simplicity. The sampling
+rule is very straightforward, and, as highlighted in Locatelli et al.
+(2016), it does not require any knowledge about the type of
+sub-Gaussianity \(R\), or the complexity \(H\) upfront. This makes the
+algorithm immediately applicable in practice while it still enjoys its
+upper bound on the expected regret. This is in particular worth
+highlighting when comparing APT to algorithms used in the pure
+exploration bandit setting. There, many algorithms require knowledge
+about the corresponding complexity upfront. The problem however being,
+that to know the complexity, the experimenter has to know all means up
+to a permutation of the arms (for example, see Audibert et al., 2010).
+This, of course, is not given in practice and thus alternative
+algorithms try to estimate the complexity online which is not a
+desirable solution either as especially in the beginning plug-in
+estimates based on the estimated means may lead to wrong estimates of
+the complexity and consequently budget allocation based on mistaken
+beliefs (compare Garivier and Kaufmann, 2016).
+
+Furthermore, Locatelli et al. (2016) were able to present an upper bound
+for the APT algorithm matching the lower bound in their Theorem 1.
+Proofs of both bounds are given below.
+
+Where the APT algorithm shows room for improvement is when it comes to
+settings with distributions that are not sub-Gaussian. This is mentioned
+in Locatelli et al. (2016). In general, the problem becomes that the
+assumptions for the bounds no longer hold; furthermore, the statistic
+\(B_i(t+1)\), and the term \(\hat{\Delta_i}(t)\) are motivated by
+(sub-)Gaussian distributions. The more one moves away from Gaussian-like
+distributions, the less appropriate this term becomes, however. In
+particular, the empirical mean will be less concentrated around the true
+mean and more impacted by outliers which are more likely under non
+sub-Gaussian distributions. Locatelli et al. (2016) thus refers to
+Bubeck et al. (2013) which considers solutions for multi-armed bandits
+that are based on heavy-tail distributions. By using more robust
+estimators of the mean, one could equip the APT algorithm to deal with
+such distributions.
+
+Another step towards dealing with non sub-Gaussianity is made by
+Mukherjee et al. (2017) who use an estimate of the variance additionally
+to the empirical mean in their Augmented UCB solution. Utilizing this
+additional information, the algorithm seems to perform better than for
+example APT, going from simulation results displayed in the paper. We
+will continue to discuss the Augmented UCB solution further in chapter
+3.
+
+Yet another idea, again mentioned in Locatelli et al. (2016) is to show
+bounds based on the Kullback-Leibler divergence of the specific
+distribution directly. While the approximation through the Gaussian
+Kullback-Leibler divergence in the lower bound proof is convenient and
+leads to the simple APT algorithm, it might not stay appropriate for
+distributions whose Kullback-Leibler divergence tends to differ from the
+Gaussian. This, for example, is the case for Bernoulli distributions at
+very small parameters \(\mu\). It's quite obvious simply by looking at
+examples that the Kullback-Leibler divergence of Bernoullis starts to
+lose any similarity to the plain quadratic approximation. The second
+graph then shows, that the actual Kullback-Leibler divergence of
+Bernoullis also has lost any symmetry over this range of parameter
+values. Given that Bernoulli distributions with very small parameter
+values arise naturally in many applications in website optimization and
+advertising click-through modeling, there is a need to tackle this
+problem.
+
+And so a potential approach can be to use the Kullback-Leibler
+divergence as measure similar to the methods proposed in Kaufmann et al.
+(2015). They proposed Kullback-Leibler based approaches for the pure
+exploration bandit setting, which we will describe in chapter 2. Then,
+in chapter 3, we will come back to the problem of using the
+Kullback-Leibler divergence in the thresholding bandit setting.
+
+\includegraphics{ThresholdingBandit_files/figure-latex/unnamed-chunk-1-1.pdf}
+
+\includegraphics{ThresholdingBandit_files/figure-latex/unnamed-chunk-2-1.pdf}
+
 \end{document}

### 2017-05-25 Complexity of Best Arm Identification/kl_complexity.Rmd
Add proof of lower bound on FB complexity

---
title: "On the Complexity of Best Arm Identification"
author: "Tim Radtke"
date: "5/20/2017"
header-includes:
   #- \documentclass[a4paper,twoside,english]{article}
   - \usepackage[retainorgcmds]{IEEEtrantools}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{bbm}
   - \newtheorem{theorem}{Theorem}
   - \newtheorem{lemma}{Lemma}
   - \newcommand{\KL}{\,\text{KL}}
   - \newcommand{\der}{\,\text{d}}
   #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
   #- \usepackage{fontspec}
   #-   \setmainfont{Arial}
keep_tex: TRUE
output:
  pdf_document:
    number_sections: true
    keep_tex: true
    #latex_engine: xelatex
fontsize: 12pt
urlcolor: blue
---

In the previous chapter, we have discussed the thresholding bandit problem as presented in Locatelli et al. (2016). Doing so, we came across the complexity term $H = \sum_{i=1}^{K} \Delta_i^{-2}$. Furthermore, we have noted the fact that an algorithm and bounds based on *only* the gap between the respective mean and the threshold are useful in the case of sub-Gaussian problems. Furthermore, even for the case of Bernoulli arms, which are sub-Gaussian since their feedback is bounded on $[0,1]$, the gap $\Delta$ becomes less and less appropriate for situations in which both $\mu$ of the Bernoulli, and $\tau$ are very close to 0 or 1.

Even though the complexity $H$ enjoys popularity in the literature of the best m arm identification problem, $m \geq 1$, Kaufmann et al. (2016) show explicitly that $H$ is mainly useful for problems of Gaussian distributions. Indeed, they go so far as to define new measures of complexity that are based on information theoretic metrics. Using those they then display $H$ as an approximation to their measures in the case of Gaussian distributions. In turn, this makes apparent that especially Bernoulli distributions with small means have to be treated differently.

For the current chapter, we will adopt the notation of Kaufmann et al. (2016) so that it will be easier to compare the arguments.

Instead of the thresholding bandit problem, we now consider the problem of identifying the best $m$ out of $K$ arms, that is, the Top-$m$ problem. While we previously looked at a fixed budget formulation, we now mainly focus on a fixed confidence problem. That is, we hold the confidence $1-\delta$ fixed at which a strategy returns the correct $m$ arms while trying to find them in a way that minimizes the sample complexity $\mathbb{E}_{\nu}[\tau]$, that is, the expected number of overall draws of the arms. $\tau$ is also called the stopping time of the algorithm. Algorithms are supposed to find $\mathcal{S}_m^*$, the set of the $m$ arms with the largest means. If we let $(\mu_1, \dots, \mu_K)$ be the vector of the means of the arms, then let $(\mu_{[1]}, \dots, \mu_{[K]})$ be the tuple in which the means are arranged in decreasing order. For the rest of this chapter, we consider only settings with arms for which $\mu_{[m]} > \mu_{[m+1]}$; that is, the set of the top $m$ arms, $\mathcal{S}_m^*$, is unique. After the sampling phase, we require any algorithm to return the set $\hat{S}_m \subset \{1,\dots,K\}$ of $m$ arms that the algorithm believes to have the largest means. In the case of fixed confidence, we fix $\delta$ at the beginning, such that the algorithm only stops sampling when $\mathbb{P}_{\nu}(\hat{S}_m = \mathcal{S}_m^*) \geq 1-\delta$. We try to find algorithms who fulfill this as quickly as possible; that is, they minimize the expected stopping time (or number of draws), $\mathbb{E}_{\nu}[\tau]$.

To arrive at the new measure of complexity proposed by Kaufmann et al. (2016), it will actually make sense to first follow their arguments to a general lower bound on the sample complexity $\mathbb{E}_{\nu}[\tau]$ in the case of fixed confidence problems. This bound is given in their Theorem 4 (for common confidence levels of $\delta \leq 0.15$).

\begin{theorem}[Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem4}
Let $\nu \in \mathcal{M}_m$, where $\mathcal{M}_m$ is the set of uniquely identifiable bandit models described above. Assume that $\mathcal{P}$ satisfies the continuity conditions in Assumption 3. Any $\delta$-PAC algorithm on $\mathcal{M}_m$ satisfies, for $\delta \leq 0.15$:

\begin{equation*}
\mathbb{E}_{\nu}[\tau] \geq \Big[ \sum_{a \in \mathcal{S}^*_m} \frac{1}{KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}^*_m} \frac{1}{KL(\nu_a, \nu_{[m]})} \Big] \der(1-\delta, \delta),
\end{equation*}

where $\der(x,y) := x \log(x/y) + (1-x) \log((1-x)/(1-y))$ is the binary relative entropy, with the convention that $\der(0,0) = \der(1,1) = 0$.
\end{theorem}

To proof this statement, we assume as before that the arms are ordered by their means decreasing in size. For a given $\delta$-PAC algorithm $\mathcal{A} = ((A_t), \tau, \hat{S}_m)$, and under the continuity conditions, there exists for every arm $a \in \{1, \dots, K\}$ an alternative model $\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)$. In this alternative model, only arm $a$ is modified in accordance with the continuity conditions. Modified in such a way that measured by the Kullback-Leibler divergence, the arm $\nu_{m+1}$ is now closer to $\nu_a$ than $\nu_a'$ is to $\nu_a$, if $\mu_a > \mu_{m+1}$ (consequently, $\mu_a' < \mu_{m+1}$). On the other hand, if $\mu_a < \mu_{m}$, then $\nu_a'$ will be moved away from $\nu_a$ just enough so that $\nu_a$ is closer to $\nu_m$ than to $\nu_a'$ (consequently, $\mu_a' > \mu_m$). These changes in distribution make the original set of optimal arms, $\{1,\dots,m\}$ no longer optimal under the alternative model $\nu'$. Given that the algorithm returns $\hat{S}_m$, we know that for the event $\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})$ (which is element of the by the stopping time $\tau$ induced $\sigma$-Algebra $\mathcal{F}_{\tau}$), that $\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta$ and $\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta$ (because fixed confidence $\delta$!).

To now give the lower bound on the expected number of samples, $\mathbb{E}_{\nu}[\tau]$, we employ the general lemma given by the authors for such changes in distribution in bandit models.

\begin{lemma}[Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma1}
Let $\nu$ and $\nu'$ be two bandit models with $K$ arms such that for all $a$, the distributions $\nu_a$ and $\nu_a'$ are mutually absolutely continuous. For any almost-surely finite stopping time $\sigma$ with respect to $(\mathcal{F}_t)$,

\begin{equation*}
\sum_{a=1}^{K} \mathbb{E}_{\nu} [N_a(\sigma)] \KL(\nu_a, \nu_a') \geq \sup_{\mathcal{E} \in \mathcal{F}_{\sigma}} \der (\mathbb{P}_{\nu}(\mathcal{E}), \mathbb{P}_{\nu'}(\mathcal{E})),
\end{equation*}

where $\der(x,y)$ is the binary relative entropy as defined above.
\end{lemma}

We can apply this lemma directly on the expected number of draws for each arm, $\mathbb{E}_{\nu}[N_a]$. For each arm $a$, we thus have $\KL(\nu_a, \nu_a') \mathbb{E}_{\nu}[N_a] \geq \der (1-\delta, \delta)$. Using the definition of the alternative model above, we get for every small but fixed $\alpha > 0$, for every arm $a \in \{1, \dots, K\}$ and each arm $b \in \{m+1, \dots, K\}$:

\begin{equation*}
\mathbb{E}_{\nu}[N_a] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_a, \nu_{m+1}) + \alpha}
\end{equation*}

and

\begin{equation*}
\mathbb{E}_{\nu}[N_b] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_b, \nu_{m}) + \alpha}.
\end{equation*}

We can then let $\alpha \to 0$, sum the bounds on the individual arms to get the bound on the overall number of draws:

\begin{equation*}
\mathbb{E}_{\nu}[\tau] = \sum_{a=1}^K \mathbb{E}_{\nu}[N_a] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \der(1-\delta, \delta)
\end{equation*}

Given that we will be naturally interested in either very high or very low confidence of our algorithm, that is, $P_\nu(\mathcal{E})$ is either close to 0 or 1, it is possible to use the following approximation to the binary relative entropy:

\begin{equation*}
\forall x \in [0,1], \quad \der(x,1-x) = \der(1-x,x) \geq \log \frac{1}{2.4x}
\end{equation*}

And so the final lower bound can be written as

\begin{equation*}
\mathbb{E}_{\nu}[\tau] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
\end{equation*}

```{r, echo = FALSE}
x <- seq(0,1,by = 0.001)
bre <- function(x) x * log(x/(1-x)) + (1-x) * log((1-x)/x)
plot(x,bre(x), type = "l")
lines(x, log(1/(2.4*x)), col = "red")
abline(v = 0.15, lty = 2)
```

Given this general lower bound for the sampling complexity, or expected number of draws, it makes sense to define the complexity of a Top-$m$ bandit problem using the Kullback-Leibler divergence. After all, besides the number of arms and the experimenter-chosen confidence, it is just how close arms are with respect to each other in terms of Kullback-Leibler divergence that influences the sampling complexity. And in general, a problem requiring more samples is of course considered to be more complex (at least with respect to the samples, which is what needs to be optimized).

Thus, following Kaufmann et al. (2016), define the complexity $\mathcal{K}_C(\nu)$ for the fixed confidence setting as

\begin{equation}
\mathcal{K}_C(\nu) = \inf_{A \, \text{PAC}} \lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\nu}[\tau_{\delta}]}{\log \frac{1}{\delta}}.
\end{equation}

So if we were to plug in the lower bound on the sampling complexity, we would arrive at a complexity measure that basically depends only on the Kullback-Leibler measuring for each arm how far it is away from the border between the two groups of arms. To see this, consider the lower bound on the complexity measure given in Kaufmann et al. (2016):

\begin{equation*}
\mathcal{K}_C(\nu) \geq \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})}
\end{equation*}

Given this description, we can already note that an intuitive extension of this complexity notion to the thresholding bandit problem might involve replacing $\mu_{[m]}$ and $\mu_{[m+1]}$ by the actual threshold $\tau$ (notation in Locatelli et al.) that divides the group above the threshold from the group below the threshold. In that case, the previously used $\alpha$ might be very similar to the $\epsilon$ used in Locatelli et al. (2016).

To get there, however, at least two important steps remain. First, we need to define a complexity for the fixed budget problem. Second, we need to create algorithms that can match the lower bound.

Kaufmann et al. are able to provide a bound on their complexity measure in the fixed budget case, however only in the case of **two-armed** bandit models. As demanded in their paper, a fixed-budget algorithm is called consistent if the failure probability $p_t(\nu) := \mathbb{P}_{\nu}(\hat{S}_m \neq S^*_m)$ tends to zero as the number of samples goes to infinity. Also, define the complexity in the fixed-budget setting as follows:

\begin{equation}
\mathcal{K}_B(\nu) = \inf_{A \, \text{consistent}} \big(\lim_{t \to \infty} \sup - \frac{1}{t} \log p_t(\nu)\big)^{-1}.
\end{equation}

Given this definition, one can interpret the bound given in Theorem 12 of Kaufmann et al. directly as a lower bound on the complexity $\mathcal{K}_B(\nu)$ (note the inverse).

\begin{theorem}[Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem12}
Let $\nu = (\nu_1, \nu_2)$ be a two-armed bandit model such that $\mu_1 > \mu_2$. In the fixed-budget setting, any consistent algorithm satisfies:

\begin{equation*}
\lim_{t \to \infty} \sup - \frac{1}{t} \log p_t(\nu) \leq \inf_{(\nu_1', \nu_2') \in \mathcal{M}: \mu_1' < \mu_2'} \frac{\KL(\nu_1', \nu_1) + \KL(\nu_2', \nu_2)}{2}
\end{equation*}
\end{theorem}

For a proof, consider first the two different bandit models, $\nu$ and $\nu'$, where we fix without loss of generality that $a^* = 1$ is the best arm in $\nu$, while $a^* = 2$ in $\nu'$. Note that in this case we don't necessarily try to fool the algorithm by a change of distribution. Indeed, we want the algorithm $\mathcal{A}$ to be consistent for both problems. Since we are in the fixed-budget setting, the stopping time is fixed at $\tau = t$. Even though the correct decision differs between the two problems, we focus on the event $A = (\hat{S}_1 = 1)$. Given the formulation in Kaufmann et al. (2016), we have $A \in \mathcal{F}_t = \mathcal{F}_{\tau}$. Now, we can apply Lemma 1 as before, as it in essense gives a measure of how different two bandit models are. Here, we want to know how different $\nu$ is from $\nu'$, and so, given we have only two arms,

\begin{equation*}
\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2', \nu_2) \geq \der(\mathbb{P}_{\nu'}(A),\mathbb{P}_{\nu}(A)))
\end{equation*}

The expectations were chosen with respect to $\nu'$ in order to allow the for the following: We have $p_t(\nu) = 1 - \mathbb{P}_{\nu}(A)$ and $p_t(\nu') = \mathbb{P}_{\nu'}(A)$ (since $A$ is wrong in $\nu'$). But since algorithm $\mathcal{A}$ is consistent for both $\nu$ and $\nu'$, we know that there should exist some number of samples such that the probability of event $A$ is bigger in setting $\nu$ (where it is the correct decision), than in setting $\nu'$ (where this would be a wrong decision and failure). Thus, for every $\epsilon > 0$, there exists $t_0(\epsilon)$ such that for all $t \geq t_0(\epsilon)$, $\mathbb{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)$. Consequently, if we plug in the bound of $\epsilon$ for $\mathbb{P}_{\nu'}(A)$, then

\begin{align*}
\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2', \nu_2) & \geq \der(\epsilon,1-p_t(\nu))) \\
& = \epsilon \log \frac{\epsilon}{1-p_t(\nu)} + (1-\epsilon) \log \frac{1-\epsilon}{p_t(\nu)} \\
& \geq (1-\epsilon) \log \frac{1-\epsilon}{p_t(\nu)} + \epsilon \log \epsilon.
\end{align*}

Let $\epsilon$ go to zero so that

\begin{align*}
\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2', \nu_2)
& \geq \log \frac{1}{p_t(\nu)} = -\log p_t(\nu).
\end{align*}

Dividing both sides by $t$ and taking the limsup, we arrive at

\begin{align*}
\lim_{t \to 0} \sup - \frac{1}{t} \log p_t(\nu)
& \leq \lim_{t \to 0} \sup \frac{1}{t} \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)] \KL(\nu_a', \nu_a) \\
& \leq \max_{a=1,2} \KL(\nu_a', \nu_a),
\end{align*}

where the last line follows from the fact that the $\frac{1}{t} \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)]$ part creates a weighted average of the two divergences $\KL(\nu_a', \nu_a)$. As noted in Kaufmann et al. (2016), one arrives at the final result by choosing $\mu_1'$, $\mu_2'$ so that $| \KL(\nu_1', \nu_1) - \KL(\nu_2', \nu_2) |$ is as small as possible.

### 2017-05-25 Complexity of Best Arm Identification/kl_complexity.tex
Add proof of lower bound on FB complexity

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={On the Complexity of Best Arm Identification},
            pdfauthor={Tim Radtke},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{On the Complexity of Best Arm Identification}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Tim Radtke}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{5/20/2017}

\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{bbm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newcommand{\KL}{\,\text{KL}}
\newcommand{\der}{\,\text{d}}

\begin{document}
\maketitle

In the previous chapter, we have discussed the thresholding bandit
problem as presented in Locatelli et al. (2016). Doing so, we came
across the complexity term \(H = \sum_{i=1}^{K} \Delta_i^{-2}\).
Furthermore, we have noted the fact that an algorithm and bounds based
on \emph{only} the gap between the respective mean and the threshold are
useful in the case of sub-Gaussian problems. Furthermore, even for the
case of Bernoulli arms, which are sub-Gaussian since their feedback is
bounded on \([0,1]\), the gap \(\Delta\) becomes less and less
appropriate for situations in which both \(\mu\) of the Bernoulli, and
\(\tau\) are very close to 0 or 1.

Even though the complexity \(H\) enjoys popularity in the literature of
the best m arm identification problem, \(m \geq 1\), Kaufmann et al.
(2016) show explicitly that \(H\) is mainly useful for problems of
Gaussian distributions. Indeed, they go so far as to define new measures
of complexity that are based on information theoretic metrics. Using
those they then display \(H\) as an approximation to their measures in
the case of Gaussian distributions. In turn, this makes apparent that
especially Bernoulli distributions with small means have to be treated
differently.

For the current chapter, we will adopt the notation of Kaufmann et al.
(2016) so that it will be easier to compare the arguments.

Instead of the thresholding bandit problem, we now consider the problem
of identifying the best \(m\) out of \(K\) arms, that is, the Top-\(m\)
problem. While we previously looked at a fixed budget formulation, we
now mainly focus on a fixed confidence problem. That is, we hold the
confidence \(1-\delta\) fixed at which a strategy returns the correct
\(m\) arms while trying to find them in a way that minimizes the sample
complexity \(\mathbb{E}_{\nu}[\tau]\), that is, the expected number of
overall draws of the arms. \(\tau\) is also called the stopping time of
the algorithm. Algorithms are supposed to find \(\mathcal{S}_m^*\), the
set of the \(m\) arms with the largest means. If we let
\((\mu_1, \dots, \mu_K)\) be the vector of the means of the arms, then
let \((\mu_{[1]}, \dots, \mu_{[K]})\) be the tuple in which the means
are arranged in decreasing order. For the rest of this chapter, we
consider only settings with arms for which \(\mu_{[m]} > \mu_{[m+1]}\);
that is, the set of the top \(m\) arms, \(\mathcal{S}_m^*\), is unique.
After the sampling phase, we require any algorithm to return the set
\(\hat{S}_m \subset \{1,\dots,K\}\) of \(m\) arms that the algorithm
believes to have the largest means. In the case of fixed confidence, we
fix \(\delta\) at the beginning, such that the algorithm only stops
sampling when
\(\mathbb{P}_{\nu}(\hat{S}_m = \mathcal{S}_m^*) \geq 1-\delta\). We try
to find algorithms who fulfill this as quickly as possible; that is,
they minimize the expected stopping time (or number of draws),
\(\mathbb{E}_{\nu}[\tau]\).

To arrive at the new measure of complexity proposed by Kaufmann et al.
(2016), it will actually make sense to first follow their arguments to a
general lower bound on the sample complexity \(\mathbb{E}_{\nu}[\tau]\)
in the case of fixed confidence problems. This bound is given in their
Theorem 4 (for common confidence levels of \(\delta \leq 0.15\)).

\begin{theorem}[Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem4}
Let $\nu \in \mathcal{M}_m$, where $\mathcal{M}_m$ is the set of uniquely identifiable bandit models described above. Assume that $\mathcal{P}$ satisfies the continuity conditions in Assumption 3. Any $\delta$-PAC algorithm on $\mathcal{M}_m$ satisfies, for $\delta \leq 0.15$:

\begin{equation*}
\mathbb{E}_{\nu}[\tau] \geq \Big[ \sum_{a \in \mathcal{S}^*_m} \frac{1}{KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}^*_m} \frac{1}{KL(\nu_a, \nu_{[m]})} \Big] \der(1-\delta, \delta),
\end{equation*}

where $\der(x,y) := x \log(x/y) + (1-x) \log((1-x)/(1-y))$ is the binary relative entropy, with the convention that $\der(0,0) = \der(1,1) = 0$.
\end{theorem}

To proof this statement, we assume as before that the arms are ordered
by their means decreasing in size. For a given \(\delta\)-PAC algorithm
\(\mathcal{A} = ((A_t), \tau, \hat{S}_m)\), and under the continuity
conditions, there exists for every arm \(a \in \{1, \dots, K\}\) an
alternative model
\(\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)\).
In this alternative model, only arm \(a\) is modified in accordance with
the continuity conditions. Modified in such a way that measured by the
Kullback-Leibler divergence, the arm \(\nu_{m+1}\) is now closer to
\(\nu_a\) than \(\nu_a'\) is to \(\nu_a\), if \(\mu_a > \mu_{m+1}\)
(consequently, \(\mu_a' < \mu_{m+1}\)). On the other hand, if
\(\mu_a < \mu_{m}\), then \(\nu_a'\) will be moved away from \(\nu_a\)
just enough so that \(\nu_a\) is closer to \(\nu_m\) than to \(\nu_a'\)
(consequently, \(\mu_a' > \mu_m\)). These changes in distribution make
the original set of optimal arms, \(\{1,\dots,m\}\) no longer optimal
under the alternative model \(\nu'\). Given that the algorithm returns
\(\hat{S}_m\), we know that for the event
\(\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})\) (which is element of the
by the stopping time \(\tau\) induced \(\sigma\)-Algebra
\(\mathcal{F}_{\tau}\)), that
\(\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta\) and
\(\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta\) (because fixed confidence
\(\delta\)!).

To now give the lower bound on the expected number of samples,
\(\mathbb{E}_{\nu}[\tau]\), we employ the general lemma given by the
authors for such changes in distribution in bandit models.

\begin{lemma}[Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma1}
Let $\nu$ and $\nu'$ be two bandit models with $K$ arms such that for all $a$, the distributions $\nu_a$ and $\nu_a'$ are mutually absolutely continuous. For any almost-surely finite stopping time $\sigma$ with respect to $(\mathcal{F}_t)$,

\begin{equation*}
\sum_{a=1}^{K} \mathbb{E}_{\nu} [N_a(\sigma)] \KL(\nu_a, \nu_a') \geq \sup_{\mathcal{E} \in \mathcal{F}_{\sigma}} \der (\mathbb{P}_{\nu}(\mathcal{E}), \mathbb{P}_{\nu'}(\mathcal{E})),
\end{equation*}

where $\der(x,y)$ is the binary relative entropy as defined above.
\end{lemma}

We can apply this lemma directly on the expected number of draws for
each arm, \(\mathbb{E}_{\nu}[N_a]\). For each arm \(a\), we thus have
\(\KL(\nu_a, \nu_a') \mathbb{E}_{\nu}[N_a] \geq \der (1-\delta, \delta)\).
Using the definition of the alternative model above, we get for every
small but fixed \(\alpha > 0\), for every arm \(a \in \{1, \dots, K\}\)
and each arm \(b \in \{m+1, \dots, K\}\):

\begin{equation*}
\mathbb{E}_{\nu}[N_a] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_a, \nu_{m+1}) + \alpha}
\end{equation*}

and

\begin{equation*}
\mathbb{E}_{\nu}[N_b] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_b, \nu_{m}) + \alpha}.
\end{equation*}

We can then let \(\alpha \to 0\), sum the bounds on the individual arms
to get the bound on the overall number of draws:

\begin{equation*}
\mathbb{E}_{\nu}[\tau] = \sum_{a=1}^K \mathbb{E}_{\nu}[N_a] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \der(1-\delta, \delta)
\end{equation*}

Given that we will be naturally interested in either very high or very
low confidence of our algorithm, that is, \(P_\nu(\mathcal{E})\) is
either close to 0 or 1, it is possible to use the following
approximation to the binary relative entropy:

\begin{equation*}
\forall x \in [0,1], \quad \der(x,1-x) = \der(1-x,x) \geq \log \frac{1}{2.4x}
\end{equation*}

And so the final lower bound can be written as

\begin{equation*}
\mathbb{E}_{\nu}[\tau] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
\end{equation*}

\includegraphics{kl_complexity_files/figure-latex/unnamed-chunk-1-1.pdf}

Given this general lower bound for the sampling complexity, or expected
number of draws, it makes sense to define the complexity of a Top-\(m\)
bandit problem using the Kullback-Leibler divergence. After all, besides
the number of arms and the experimenter-chosen confidence, it is just
how close arms are with respect to each other in terms of
Kullback-Leibler divergence that influences the sampling complexity. And
in general, a problem requiring more samples is of course considered to
be more complex (at least with respect to the samples, which is what
needs to be optimized).

Thus, following Kaufmann et al. (2016), define the complexity
\(\mathcal{K}_C(\nu)\) for the fixed confidence setting as

\begin{equation}
\mathcal{K}_C(\nu) = \inf_{A \, \text{PAC}} \lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\nu}[\tau_{\delta}]}{\log \frac{1}{\delta}}.
\end{equation}

So if we were to plug in the lower bound on the sampling complexity, we
would arrive at a complexity measure that basically depends only on the
Kullback-Leibler measuring for each arm how far it is away from the
border between the two groups of arms. To see this, consider the lower
bound on the complexity measure given in Kaufmann et al. (2016):

\begin{equation*}
\mathcal{K}_C(\nu) \geq \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})}
\end{equation*}

Given this description, we can already note that an intuitive extension
of this complexity notion to the thresholding bandit problem might
involve replacing \(\mu_{[m]}\) and \(\mu_{[m+1]}\) by the actual
threshold \(\tau\) (notation in Locatelli et al.) that divides the group
above the threshold from the group below the threshold. In that case,
the previously used \(\alpha\) might be very similar to the \(\epsilon\)
used in Locatelli et al. (2016).

To get there, however, at least two important steps remain. First, we
need to define a complexity for the fixed budget problem. Second, we
need to create algorithms that can match the lower bound.

Kaufmann et al. are able to provide a bound on their complexity measure
in the fixed budget case, however only in the case of \textbf{two-armed}
bandit models. As demanded in their paper, a fixed-budget algorithm is
called consistent if the failure probability
\(p_t(\nu) := \mathbb{P}_{\nu}(\hat{S}_m \neq S^*_m)\) tends to zero as
the number of samples goes to infinity. Also, define the complexity in
the fixed-budget setting as follows:

\begin{equation}
\mathcal{K}_B(\nu) = \inf_{A \, \text{consistent}} \big(\lim_{t \to \infty} \sup - \frac{1}{t} \log p_t(\nu)\big)^{-1}.
\end{equation}

Given this definition, one can interpret the bound given in Theorem 12
of Kaufmann et al. directly as a lower bound on the complexity
\(\mathcal{K}_B(\nu)\) (note the inverse).

\begin{theorem}[Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem12}
Let $\nu = (\nu_1, \nu_2)$ be a two-armed bandit model such that $\mu_1 > \mu_2$. In the fixed-budget setting, any consistent algorithm satisfies:

\begin{equation*}
\lim_{t \to \infty} \sup - \frac{1}{t} \log p_t(\nu) \leq \inf_{(\nu_1', \nu_2') \in \mathcal{M}: \mu_1' < \mu_2'} \frac{\KL(\nu_1', \nu_1) + \KL(\nu_2', \nu_2)}{2}
\end{equation*}
\end{theorem}

For a proof, consider first the two different bandit models, \(\nu\) and
\(\nu'\), where we fix without loss of generality that \(a^* = 1\) is
the best arm in \(\nu\), while \(a^* = 2\) in \(\nu'\). Note that in
this case we don't necessarily try to fool the algorithm by a change of
distribution. Indeed, we want the algorithm \(\mathcal{A}\) to be
consistent for both problems. Since we are in the fixed-budget setting,
the stopping time is fixed at \(\tau = t\). Even though the correct
decision differs between the two problems, we focus on the event
\(A = (\hat{S}_1 = 1)\). Given the formulation in Kaufmann et al.
(2016), we have \(A \in \mathcal{F}_t = \mathcal{F}_{\tau}\). Now, we
can apply Lemma 1 as before, as it in essense gives a measure of how
different two bandit models are. Here, we want to know how different
\(\nu\) is from \(\nu'\), and so, given we have only two arms,

\begin{equation*}
\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2', \nu_2) \geq \der(\mathbb{P}_{\nu'}(A),\mathbb{P}_{\nu}(A)))
\end{equation*}

The expectations were chosen with respect to \(\nu'\) in order to allow
the for the following: We have \(p_t(\nu) = 1 - \mathbb{P}_{\nu}(A)\)
and \(p_t(\nu') = \mathbb{P}_{\nu'}(A)\) (since \(A\) is wrong in
\(\nu'\)). But since algorithm \(\mathcal{A}\) is consistent for both
\(\nu\) and \(\nu'\), we know that there should exist some number of
samples such that the probability of event \(A\) is bigger in setting
\(\nu\) (where it is the correct decision), than in setting \(\nu'\)
(where this would be a wrong decision and failure). Thus, for every
\(\epsilon > 0\), there exists \(t_0(\epsilon)\) such that for all
\(t \geq t_0(\epsilon)\),
\(\mathbb{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)\). Consequently,
if we plug in the bound of \(\epsilon\) for \(\mathbb{P}_{\nu'}(A)\),
then

\begin{align*}
\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2', \nu_2) & \geq \der(\epsilon,1-p_t(\nu))) \\
& = \epsilon \log \frac{\epsilon}{1-p_t(\nu)} + (1-\epsilon) \log \frac{1-\epsilon}{p_t(\nu)} \\
& \geq (1-\epsilon) \log \frac{1-\epsilon}{p_t(\nu)} + \epsilon \log \epsilon.
\end{align*}

Let \(\epsilon\) go to zero so that

\begin{align*}
\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2', \nu_2)
& \geq \log \frac{1}{p_t(\nu)} = -\log p_t(\nu).
\end{align*}

Dividing both sides by \(t\) and taking the limsup, we arrive at

\begin{align*}
\lim_{t \to 0} \sup - \frac{1}{t} \log p_t(\nu)
& \leq \lim_{t \to 0} \sup \frac{1}{t} \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)] \KL(\nu_a', \nu_a) \\
& \leq \max_{a=1,2} \KL(\nu_a', \nu_a),
\end{align*}

where the last line follows from the fact that the
\(\frac{1}{t} \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)]\) part creates a
weighted average of the two divergences \(\KL(\nu_a', \nu_a)\). As noted
in Kaufmann et al. (2016), one arrives at the final result by choosing
\(\mu_1'\), \(\mu_2'\) so that
\(| \KL(\nu_1', \nu_1) - \KL(\nu_2', \nu_2) |\) is as small as possible.

\end{document}

### 2017-05-25 Pure Exploration/Pure_Exploration.tex
Add proof of lower bound on FB complexity

@@
 
+Given the success of UCB, why not try it for this problem as well?
+
+-\textgreater{} What would be the equivalent algorithm? -\textgreater{}
+Audibert et al. (2009) -\textgreater{} Adjustment proposed by Audibert
+et al. (2015) -\textgreater{} Choose a linear in t to explore more!
+-\textgreater{} Show upper bound -\textgreater{} Give at least the
+standard steps of lower bound proof
+
 \end{document}

### 2017-05-25 Complexity of Best Arm Identification/kl_complexity.Rmd
add matching algorithms to complexity of best-arm identification

@@
 (2016), one arrives at the final result by choosing $\mu_1'$, $\mu_2'$ so that $| \KL(\nu_1', \nu_1) - \KL(\nu_2', \nu_2) |$ is as small as possible.
+
+Note that while deriving the lower bound on the complexity measure, we have also derived the following lower bound on the failure probability for the two-armed fixed-budget bandit:
+
+\begin{equation*}
+p_t(\nu) \geq \exp \big(- \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)] \KL(\nu_a', \nu_a) \big)
+\end{equation*}
+
+or, to not rely on the share of samples attributed to each arm,
+
+\begin{equation*}
+p_t(\nu) \geq \exp \big(- \max_{a=1,2} \KL(\nu_a', \nu_a) \big).
+\end{equation*}
+
+**Mention something about the fact that we were not able to do this for more than 2 arms and top-m bandits. How could it be extended to that? How could it be extended to the threshold bandit?**
+
+As noted by Kaufmann et al.
+(2016), the advantage of this lower bound is that it makes the complexity in the fixed-confidence and the fixed-budget setting directly comparable.
+The disadvantage of course being that the result only holds for two-armed models.
+While the authors were not able to derive directly comparable lower bounds for the Top-$m$ case, they did derive a first lower bound in the Gaussian case with equal variances.
+While we would like to move beyond Gaussian distributions in the work at hand, the idea for the proof might show a way of how the ideas can be transferred to the thresholding bandit problem.
+We first state the result and then discuss the proof.
+
+\begin{lemma}[Lemma 15, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma15}
+Let $\nu$ and $\nu'$ be two bandit models such that $S^*_m(\nu) \neq S*_m(\nu')$. Then
+
+\begin{equation*}
+\max \big( \mathbb{P}_{\nu}(S \neq S^*_m(\nu)), \mathbb{P}_{\nu'}(S \neq S^*_m(\nu')) \big) \geq \frac{1}{4} \exp \Big(-\sum_{a=1}^{K} \mathbb{E}_{\nu}[N_a] \KL(\nu_a, \nu_a') \Big).
+\end{equation*}
+\end{lemma}
+
+The following theorem only holds in the case of Gaussian bandit models with equal known variance.
+
+\begin{theorem}[Theorem 17, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem17}
+
+Let $\mathcal{M}_m = \{\nu = (\nu_1, \dots, \nu_K): \nu_a = \mathcal{N}(\mu_a, \sigma^2), \mu_a \in \mathbb{R}, \mu_{[m]}\neq \mu_{[m+1]}\}.$ Furthermore, let $\nu$ be such that $\mu_1 > \dots > \mu_m > \mu_{m+1} > \dots > \mu_K$, and let
+
+\begin{equation*}
+H +(\nu) = \sum_{a=1}^m \frac{2\sigma^2}{(\mu_a - \mu_{m+1})^2}, \quad H^-(\nu) = \sum_{a=m+1}^K \frac{2\sigma^2}{(\mu_m - \mu_a)^2} \quad
+and \quad
+H(\nu) = H^+(\nu) + H^-(\nu).
+\end{equation*}
+
+There exists $a \in {1, \dots, m}$ and $b \in \{m+1, \dots, K\}$ such that the bandit model $\nu^{[a,b]}$ described in Figure 4 (Kaufmann et al., 2016) satisfies $H(\nu^{[a,b]}) < H(\nu)$ and is such that
+
+\begin{equation*}
+\max \big( p_t(\nu),p_t(\nu^{[a,b]})\big) \geq \frac{1}{4} \exp \big(-\frac{4t}{\bar{H}(\nu)}\big), \quad where \quad \bar{H}(\nu) = \frac{H(\nu) \min(H^+(\nu),H^-(\nu))}{H(\nu)+\min(H^+(\nu),H^-(\nu))}
+\end{equation*}
+\end{theorem}
+
+Given that we are again in the Top-$m$ setting, the proof idea is similar to the proof of Theorem \ref{theorem:KaufmannEtAlTheorem4} in that we again consider problems where we switch arms around the limit seperating the two groups of arms as given implicitly by $\mu_{[m]}$ and $\mu_{[m+1]}$.
+The hope here being that these methods could be applied to the thresholding bandit problem where the threshold of course gives the limit between the arms above and below the threshold.
+As we have seen in chapter 1, this flip around the threshold was of course used in the proof of the lower bound in Theorem 1 of Locatelli et al.
+(2016).
+However, there, again, the distributions were assumed to be Gaussian.
+This brings the big advantage that the Kullback-Leibler divergence becomes symmetric, and the feedback can take values on all $\mathbb{R}$.
+And by using the complexity measure $H(\nu)$, it is also clear that there exists an arm that is undersampled with respect to its contribution to the overall complexity of the problem (or sampled exactly according to its contribution), which leads to leads to a convenient upper bound on this arms number of draws which is again employed in both the proof of Theorem \ref{theorem:KaufmannEtAlTheorem17} and in Locatelli et al.
+(2016).
+It is not clear yet, whether the same can also be done with other complexity measures.
+
+We do not repeat the proof here for now.
+
+See p20!
+
+What remains is to present algorithms that are able to match the lower bounds derived so far.
+
+#### Matching algorithm strategies
+
+Given those lower bounds, all that is left is to find algorithms which are able to match the complexity. Sadly, not straightforward for Bernoullis.
+
+Kaufmann et al.
+(2016) do not present algorithms matching the lower bound of Theorem \ref{theorem:KaufmannEtAlTheorem17}.
+They do consider algorithms that connect to Theorem \ref{theorem:KaufmannEtAlTheorem4} and Theorem \ref{theorem:KaufmannEtAlTheorem12}.
+
+Given that Locatelli et al.
+(2016), and thus the problem we mostly consider in this thesis, is in the fixed-budget setting, we are most interested in the matching strategies for Theorem \ref{theorem:KaufmannEtAlTheorem12}.
+However, given that the lower bound applies only to two-armed bandits, the algorithms are of limited practical interest.
+Furthermore, the algorithms proposed require knowledge that is in general not available upfront.
+
+For the example of Gaussian distributions, the knowledge of the (potentially different) variance is assumed which enables a strategy that pulls each arm proportional to its variance.
+
+Even worse is the case of Bernoulli two-armed bandit models where the proposed algorithm requires knowledge about the true parameters of the distributions.
+That this limits the practical interest is also noted by the authors of Kaufmann et al.
+(2016).
+Thus, they suggest to use uniform sampling strategies in the case of two-armed Bernoulli bandits, and show that there is not much to be lost by doing so.
+
+Thus, Kaufmann et al.
+(2016) join a number of other papers like Audibert et al.
+(2010) and Kaufmann and Kalyanakrishnan (2013) which struggle to find matching strategies in the fixed-budget setting that do not rely on knowledge of parameters or the complexity of the problem.
+
+In contrast, Kaufmann et al.
+(2016) are able to show that their complexity measure derived for the fixed-confidence setting, $\mathcal{K}_C(\nu)$, can be upper-bounded using the upper bound of the sample complexity (number of pulls) given for the KL-LUCB algorithm in Kaufmann and Kalyanakrishnan (2013).
+Consequently, in the case of exponential family bandits, the complexity $\mathcal{K}_C(\nu)$ is bounded as given in equation (6) in Kaufmann et al.
+(2016):
+
+\begin{equation*}
+\sum_{a \in S^*_m} \frac{1}{K(\theta_a, \theta_{[m+1]})} + \sum_{a \notin S^*_m \frac{1}{K(\theta_a,\theta_{[m]})}} \leq \mathcal{K}_C(\nu) \leq 24 \min_{\theta \in [\theta_{[m+1]},\theta_{[m]}]} \sum_{a=1}^{K} \frac{1}{K^*(\theta_a, \theta)},
+\end{equation*}
+
+where $K(\theta, \theta') = \KL(\nu_{\theta}, \nu_{\theta'})$ for $(\theta, \theta') \in \Theta^2$ was defined as the shorthand for the Kullback-Leibler divergence for two distributions from the exponential family parameterized by $\theta$ and $\theta'$ respectively.
+$K^*(\theta,\theta') = K(\theta^*, \theta)$ is the Chernoff distribution between the two distributions, where $\theta^*$ is chosen so that $K(\theta^*,\theta) = K(\theta^*, \theta')$.

### 2017-05-25 Complexity of Best Arm Identification/kl_complexity.tex
add matching algorithms to complexity of best-arm identification

@@
 
+Note that while deriving the lower bound on the complexity measure, we
+have also derived the following lower bound on the failure probability
+for the two-armed fixed-budget bandit:
+
+\begin{equation*}
+p_t(\nu) \geq \exp \big(- \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)] \KL(\nu_a', \nu_a) \big)
+\end{equation*}
+
+or, to not rely on the share of samples attributed to each arm,
+
+\begin{equation*}
+p_t(\nu) \geq \exp \big(- \max_{a=1,2} \KL(\nu_a', \nu_a) \big).
+\end{equation*}
+
+\textbf{Mention something about the fact that we were not able to do
+this for more than 2 arms and top-m bandits. How could it be extended to
+that? How could it be extended to the threshold bandit?}
+
+As noted by Kaufmann et al. (2016), the advantage of this lower bound is
+that it makes the complexity in the fixed-confidence and the
+fixed-budget setting directly comparable. The disadvantage of course
+being that the result only holds for two-armed models. While the authors
+were not able to derive directly comparable lower bounds for the
+Top-\(m\) case, they did derive a first lower bound in the Gaussian case
+with equal variances. While we would like to move beyond Gaussian
+distributions in the work at hand, the idea for the proof might show a
+way of how the ideas can be transferred to the thresholding bandit
+problem. We first state the result and then discuss the proof.
+
+\begin{lemma}[Lemma 15, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma15}
+Let $\nu$ and $\nu'$ be two bandit models such that $S^*_m(\nu) \neq S*_m(\nu')$. Then
+
+\begin{equation*}
+\max \big( \mathbb{P}_{\nu}(S \neq S^*_m(\nu)), \mathbb{P}_{\nu'}(S \neq S^*_m(\nu')) \big) \geq \frac{1}{4} \exp \Big(-\sum_{a=1}^{K} \mathbb{E}_{\nu}[N_a] \KL(\nu_a, \nu_a') \Big).
+\end{equation*}
+\end{lemma}
+
+The following theorem only holds in the case of Gaussian bandit models
+with equal known variance.
+
+\begin{theorem}[Theorem 17, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem17}
+
+Let $\mathcal{M}_m = \{\nu = (\nu_1, \dots, \nu_K): \nu_a = \mathcal{N}(\mu_a, \sigma^2), \mu_a \in \mathbb{R}, \mu_{[m]}\neq \mu_{[m+1]}\}.$ Furthermore, let $\nu$ be such that $\mu_1 > \dots > \mu_m > \mu_{m+1} > \dots > \mu_K$, and let
+
+\begin{equation*}
+H +(\nu) = \sum_{a=1}^m \frac{2\sigma^2}{(\mu_a - \mu_{m+1})^2}, \quad H^-(\nu) = \sum_{a=m+1}^K \frac{2\sigma^2}{(\mu_m - \mu_a)^2} \quad
+and \quad
+H(\nu) = H^+(\nu) + H^-(\nu).
+\end{equation*}
+
+There exists $a \in {1, \dots, m}$ and $b \in \{m+1, \dots, K\}$ such that the bandit model $\nu^{[a,b]}$ described in Figure 4 (Kaufmann et al., 2016) satisfies $H(\nu^{[a,b]}) < H(\nu)$ and is such that
+
+\begin{equation*}
+\max \big( p_t(\nu),p_t(\nu^{[a,b]})\big) \geq \frac{1}{4} \exp \big(-\frac{4t}{\bar{H}(\nu)}\big), \quad where \quad \bar{H}(\nu) = \frac{H(\nu) \min(H^+(\nu),H^-(\nu))}{H(\nu)+\min(H^+(\nu),H^-(\nu))}
+\end{equation*}
+\end{theorem}
+
+Given that we are again in the Top-\(m\) setting, the proof idea is
+similar to the proof of Theorem \ref{theorem:KaufmannEtAlTheorem4} in
+that we again consider problems where we switch arms around the limit
+seperating the two groups of arms as given implicitly by \(\mu_{[m]}\)
+and \(\mu_{[m+1]}\). The hope here being that these methods could be
+applied to the thresholding bandit problem where the threshold of course
+gives the limit between the arms above and below the threshold. As we
+have seen in chapter 1, this flip around the threshold was of course
+used in the proof of the lower bound in Theorem 1 of Locatelli et al.
+(2016). However, there, again, the distributions were assumed to be
+Gaussian. This brings the big advantage that the Kullback-Leibler
+divergence becomes symmetric, and the feedback can take values on all
+\(\mathbb{R}\). And by using the complexity measure \(H(\nu)\), it is
+also clear that there exists an arm that is undersampled with respect to
+its contribution to the overall complexity of the problem (or sampled
+exactly according to its contribution), which leads to leads to a
+convenient upper bound on this arms number of draws which is again
+employed in both the proof of Theorem
+\ref{theorem:KaufmannEtAlTheorem17} and in Locatelli et al. (2016). It
+is not clear yet, whether the same can also be done with other
+complexity measures.
+
+We do not repeat the proof here for now.
+
+See p20!
+
+What remains is to present algorithms that are able to match the lower
+bounds derived so far.
+
+\paragraph{Matching algorithm
+strategies}\label{matching-algorithm-strategies}
+
+Given those lower bounds, all that is left is to find algorithms which
+are able to match the complexity. Sadly, not straightforward for
+Bernoullis.
+
+Kaufmann et al. (2016) do not present algorithms matching the lower
+bound of Theorem \ref{theorem:KaufmannEtAlTheorem17}. They do consider
+algorithms that connect to Theorem \ref{theorem:KaufmannEtAlTheorem4}
+and Theorem \ref{theorem:KaufmannEtAlTheorem12}.
+
+Given that Locatelli et al. (2016), and thus the problem we mostly
+consider in this thesis, is in the fixed-budget setting, we are most
+interested in the matching strategies for Theorem
+\ref{theorem:KaufmannEtAlTheorem12}. However, given that the lower bound
+applies only to two-armed bandits, the algorithms are of limited
+practical interest. Furthermore, the algorithms proposed require
+knowledge that is in general not available upfront.
+
+For the example of Gaussian distributions, the knowledge of the
+(potentially different) variance is assumed which enables a strategy
+that pulls each arm proportional to its variance.
+
+Even worse is the case of Bernoulli two-armed bandit models where the
+proposed algorithm requires knowledge about the true parameters of the
+distributions. That this limits the practical interest is also noted by
+the authors of Kaufmann et al. (2016). Thus, they suggest to use uniform
+sampling strategies in the case of two-armed Bernoulli bandits, and show
+that there is not much to be lost by doing so.
+
+Thus, Kaufmann et al. (2016) join a number of other papers like Audibert
+et al. (2010) and Kaufmann and Kalyanakrishnan (2013) which struggle to
+find matching strategies in the fixed-budget setting that do not rely on
+knowledge of parameters or the complexity of the problem.
+
+In contrast, Kaufmann et al. (2016) are able to show that their
+complexity measure derived for the fixed-confidence setting,
+\(\mathcal{K}_C(\nu)\), can be upper-bounded using the upper bound of
+the sample complexity (number of pulls) given for the KL-LUCB algorithm
+in Kaufmann and Kalyanakrishnan (2013). Consequently, in the case of
+exponential family bandits, the complexity \(\mathcal{K}_C(\nu)\) is
+bounded as given in equation (6) in Kaufmann et al. (2016):
+
+\begin{equation*}
+\sum_{a \in S^*_m} \frac{1}{K(\theta_a, \theta_{[m+1]})} + \sum_{a \notin S^*_m \frac{1}{K(\theta_a,\theta_{[m]})}} \leq \mathcal{K}_C(\nu) \leq 24 \min_{\theta \in [\theta_{[m+1]},\theta_{[m]}]} \sum_{a=1}^{K} \frac{1}{K^*(\theta_a, \theta)},
+\end{equation*}
+
+where \(K(\theta, \theta') = \KL(\nu_{\theta}, \nu_{\theta'})\) for
+\((\theta, \theta') \in \Theta^2\) was defined as the shorthand for the
+Kullback-Leibler divergence for two distributions from the exponential
+family parameterized by \(\theta\) and \(\theta'\) respectively.
+\(K^*(\theta,\theta') = K(\theta^*, \theta)\) is the Chernoff
+distribution between the two distributions, where \(\theta^*\) is chosen
+so that \(K(\theta^*,\theta) = K(\theta^*, \theta')\).
+
 \end{document}

### 2017-05-26 Complexity of Best Arm Identification/kl_complexity.Rmd
add theorem 1 of Garivier and Kaufmann

@@
 \begin{equation*}
-\sum_{a \in S^*_m} \frac{1}{K(\theta_a, \theta_{[m+1]})} + \sum_{a \notin S^*_m \frac{1}{K(\theta_a,\theta_{[m]})}} \leq \mathcal{K}_C(\nu) \leq 24 \min_{\theta \in [\theta_{[m+1]},\theta_{[m]}]} \sum_{a=1}^{K} \frac{1}{K^*(\theta_a, \theta)},
+\sum_{a \in S^*_m} \frac{1}{K(\theta_a, \theta_{[m+1]})} + \sum_{a \notin S^*_m} \frac{1}{K(\theta_a,\theta_{[m]})} \leq \mathcal{K}_C(\nu) \leq 24 \min_{\theta \in [\theta_{[m+1]},\theta_{[m]}]} \sum_{a=1}^{K} \frac{1}{K^*(\theta_a, \theta)},
 \end{equation*}
@@
 $K^*(\theta,\theta') = K(\theta^*, \theta)$ is the Chernoff distribution between the two distributions, where $\theta^*$ is chosen so that $K(\theta^*,\theta) = K(\theta^*, \theta')$.
+
+### Optimal Best Arm Identification
+
+A very similar application of the KL divergence has been given in Garivier and Kaufmann to derive a lower bound on the sample complexity in the case of best arm identification.
+In particular, the transportation Lemma 1 is used again.
+And a matching algorithm for $K \geq 2$ arms is proposed.
+
+Talk about:
+- Not a simple sum of squares
+- Idea of algorithm: Equalize the probability of all wrong decisions
+
+In Garivier and Kaufmann (2016), the authors are able to derive a somewhat similar lower bound on the sample complexity of a $K$-armed bandit in the single best arm identification problem with fixed confidence.
+Additionally, they provide a $\delta$-PAC algorithm achieving said bound asymptotically.
+
+In particular, the authors pick up Lemma 1 from Kaufmann et al.
+(2016) -- which we discussed above -- to derive the lower bound.
+While presenting these results, we try to stick as much as possible with the notation used so far.
+In particular, we let for distributions $\nu_{\theta}$ from a canonical exponential family, which can be parameterized by its mean $\stackrel{.}{b}(\theta) = \mu$ and thus be written as $\nu^{\mu}$; for these, we continue to write the Kullback-Leibler divergence as
+
+\begin{equation*}
+\KL(\mu, \mu') = \KL(\nu^{\mu},\nu^{\mu'}) = \KL(\nu_{\theta},\nu_{\theta'}) = \KL(\nu, \nu')
+\end{equation*}
+
+while $d(x,y)$ continues to represent the binary relative entropy.
+
+As we will consider only problems with exponential family distributions, the distributions can be parameterized by their means.
+Therefore, if we let $\mathcal{S}$ to be a set of bandit models with $K$ distributions each, then each model is fully defined by a vector $\bm{\mu} = (\mu_1, \dots, \mu_K)$.
+Assume that every $\bm{\mu} \in \mathcal{S}$ has a unique maximum given by $a^*(\bm{\mu})$ such that $\mu_{a^*} > \max_{a \neq a^*(\bm{\mu})} \mu_a$.
+In order to fix the confidence, we specify the risk $\delta$.
+The strategies corresponding to this risk are called $\delta$-PAC if for every $\bm{\mu} \in \mathcal{S}$, $\mathbb{P}_{\bm{\mu}}(\tau_{\delta} < \infty) = 1$ (the strategy ends surely after a finite number of samples) and $\mathbb{P}_{\bm{\mu}}(\hat{a}_{\tau_{\delta}} \neq a^*) \leq \delta$ (the probability of picking not the optimal arm is smaller than the fixed risk).
+As in Garivier and Kaufmann (2016), we introduce the set of problems for which the optimal arm is different from the one in $\bm{\mu}$:
+
+\begin{equation*}
+\text{Alt}(\bm{\mu}) := \{\bm{\lambda} \in \mathcal{S}: a^*(\bm{\lambda}) \neq a^*(\bm{\mu})\}
+\end{equation*}
+
+where $\bm{\lambda}$ is the vector of means defining the distributions of the alternative problem to $\bm{\mu}$.
+Lastly, we have the set of probability distributions on the arms $\mathcal{A}$: $\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}$.
+\marginpar{Give more intuition for what these probability distributions are} We are now ready to state the theorem.
+
+\begin{theorem}[Theorem 1, Garivier and Kaufmann, 2016] \label{theorem:GarivierKaufmannTheorem1}
+Let $\delta \in (0,1)$. For any $\delta$-PAC strategy and any bandit model $\bm{\mu} \in \mathcal{S}$,
+
+\begin{equation*}
+\mathbb{E}_{\bm{\mu}} [\tau_{\delta}] \geq T^*(\bm{\mu}) \text{\em{d}}(\delta,1-\delta),
+\end{equation*}
+
+where
+
+\begin{equation} \label{eq:GarivierKaufmann_Theorem1_Game}
+T^*(\bm{\mu})^{-1} := \sup_{w \in \Sigma_K} \inf_{\bm{\lambda} \in \text{\em{Alt}}(\bm{\mu})} \left( \sum_{a=1}^K w_a \text{\em{KL}}(\mu_a, \lambda_a)\right) .
+\end{equation}
+\end{theorem}
+
+And so we see that the two bounds on the sample complexity (one for Top-$m$, one for best arm identification) differ only in the way that they build the sum of Kullback-Leibler divergences over the $K$ arms.
+In contrast to Theorem \ref{theorem:KaufmannEtAl2016Theorem1}, here the contribution of each arm through its KL-divergence is weighted.
+The difference is that while we were able to very clearly describe the change of distribution in the Top-$m$ case for each arm -- for each arm, we specified an alternative model that yields a new set of $m$ optimal arms -- we now consider all alternative models that yield a different best arm than the model $\bm{\mu}$.
+In the previous theorem, we sum over the complexity of each individual arm, as the change in distribution only ever touches one arm, thus leading to a KL-divergence of 0 for the other arms while still changing the optimal set.
+Here, we consider all instances of alternative models $\bm{\lambda}$, and thus also those in which several arms are modified (and thus have a KL-divergence unequal 0 in the result of Lemma 1).
+
+*Proof of Theorem \ref{theorem:GarivierKaufmannTheorem1}*: As stated before, we let $\delta \in (0,1)$, $\bm{\mu} \in \mathcal{S}$, and only consider $\delta$-PAC strategies.
+As before, $N_a(t)$ describes the random number of pulls of arm $a$ until time $t$, for all $t\geq 1$.
+Again, Lemma \ref{theorem:KaufmannEtAlLemma1} states how the failure probability $\delta$ relates to the expected number of draws of each arm given two models which differ in their optimal arm, and where it is evaluated based on the Kullback-Leibler divergence for each pair of arms how much the two models differ:
+
+\begin{equation*}
+\forall \lambda \in \mathcal{S}: a^*(\lambda) \neq a^*(\mu), \sum_{a=1}^K \KL(\mu_a,\lambda_a)\mathbb{E}_{\bm{\mu}}[N_a(\tau_{\delta})] \geq \d(\delta, 1- \delta).
+\end{equation*}
+
+As mentioned, we now do not consider a specific alternative for each arm, but instead look at the infimum over all the possible alternatives, and use the fact that $\mathbb{E}_{\bm{\mu}}[\tau_{\delta}] = \sum_{a=1}^K \mathbb{E}_{\bm{\mu}}[N_a(\tau_{\delta})]$:
+
+\begin{align*}
+\der(\delta, 1-\delta) & \leq \inf_{\lambda \in \text{Alt}(\bm{\mu})} \mathbb{E}_{\bm{\mu}}[\tau_{\delta}] \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[\tau_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
+& = \mathbb{E}_{\bm{\mu}}[\tau_{\delta}] \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[\tau_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
+& \leq \mathbb{E}_{\bm{\mu}}[\tau_{\delta}] \sup_{w \in \Sigma_K} \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K w_a \KL(\mu_a, \lambda_a)\Big).
+\end{align*}
+
+As stated in Garivier and Kaufmann (2016), the term $\frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[\tau_{\delta}]}$ gives the fraction of draws each arm receives.
+This value, however, depends on the used algorithm.
+To make it hold for any $\delta$-PAC algorithm, it is replaced by the supremum over $\Sigma_K$, which is the distribution over these fractions for any $\mathcal{A}$, that is, for any $\delta$-PAC strategy.
+
+This lower bound can be interpreted as a Minimax game, where the experimenter has to choose the share of samples he attributes to each arm in a way that is optimal given that nature will respond and choose the most difficult alternative model given his weights.
+Thus, to make the lower bound practical, it is a matter of finding the optimal weights $w^*(\bm{\mu})$.

### 2017-05-26 Complexity of Best Arm Identification/kl_complexity.tex
add theorem 1 of Garivier and Kaufmann

@@
 
+\subsubsection{Optimal Best Arm
+Identification}\label{optimal-best-arm-identification}
+
+A very similar application of the KL divergence has been given in
+Garivier and Kaufmann to derive a lower bound on the sample complexity
+in the case of best arm identification. In particular, the
+transportation Lemma 1 is used again. And a matching algorithm for
+\(K \geq 2\) arms is proposed.
+
+Talk about: - Not a simple sum of squares - Idea of algorithm: Equalize
+the probability of all wrong decisions
+
+In Garivier and Kaufmann (2016), the authors are able to derive a
+somewhat similar lower bound on the sample complexity of a \(K\)-armed
+bandit in the single best arm identification problem with fixed
+confidence. Additionally, they provide a \(\delta\)-PAC algorithm
+achieving said bound asymptotically.
+
+In particular, the authors pick up Lemma 1 from Kaufmann et al. (2016)
+-- which we discussed above -- to derive the lower bound. While
+presenting these results, we try to stick as much as possible with the
+notation used so far. In particular, we let for distributions
+\(\nu_{\theta}\) from a canonical exponential family, which can be
+parameterized by its mean \(\stackrel{.}{b}(\theta) = \mu\) and thus be
+written as \(\nu^{\mu}\); for these, we continue to write the
+Kullback-Leibler divergence as
+
+\begin{equation*}
+\KL(\mu, \mu') = \KL(\nu^{\mu},\nu^{\mu'}) = \KL(\nu_{\theta},\nu_{\theta'}) = \KL(\nu, \nu')
+\end{equation*}
+
+while \(d(x,y)\) continues to represent the binary relative entropy.
+
+As we will consider only problems with exponential family distributions,
+the distributions can be parameterized by their means. Therefore, if we
+let \(\mathcal{S}\) to be a set of bandit models with \(K\)
+distributions each, then each model is fully defined by a vector
+\(\bm{\mu} = (\mu_1, \dots, \mu_K)\). Assume that every
+\(\bm{\mu} \in \mathcal{S}\) has a unique maximum given by
+\(a^*(\bm{\mu})\) such that
+\(\mu_{a^*} > \max_{a \neq a^*(\bm{\mu})} \mu_a\). In order to fix the
+confidence, we specify the risk \(\delta\). The strategies corresponding
+to this risk are called \(\delta\)-PAC if for every
+\(\bm{\mu} \in \mathcal{S}\),
+\(\mathbb{P}_{\bm{\mu}}(\tau_{\delta} < \infty) = 1\) (the strategy ends
+surely after a finite number of samples) and
+\(\mathbb{P}_{\bm{\mu}}(\hat{a}_{\tau_{\delta}} \neq a^*) \leq \delta\)
+(the probability of picking not the optimal arm is smaller than the
+fixed risk). As in Garivier and Kaufmann (2016), we introduce the set of
+problems for which the optimal arm is different from the one in
+\(\bm{\mu}\):
+
+\begin{equation*}
+\text{Alt}(\bm{\mu}) := \{\bm{\lambda} \in \mathcal{S}: a^*(\bm{\lambda}) \neq a^*(\bm{\mu})\}
+\end{equation*}
+
+where \(\bm{\lambda}\) is the vector of means defining the distributions
+of the alternative problem to \(\bm{\mu}\). Lastly, we have the set of
+probability distributions on the arms \(\mathcal{A}\):
+\(\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}\).
+\marginpar{Give more intuition for what these probability distributions are}
+We are now ready to state the theorem.
+
+\begin{theorem}[Theorem 1, Garivier and Kaufmann, 2016] \label{theorem:GarivierKaufmannTheorem1}
+Let $\delta \in (0,1)$. For any $\delta$-PAC strategy and any bandit model $\bm{\mu} \in \mathcal{S}$,
+
+\begin{equation*}
+\mathbb{E}_{\bm{\mu}} [\tau_{\delta}] \geq T^*(\bm{\mu}) \text{\em{d}}(\delta,1-\delta),
+\end{equation*}
+
+where
+
+\begin{equation} \label{eq:GarivierKaufmann_Theorem1_Game}
+T^*(\bm{\mu})^{-1} := \sup_{w \in \Sigma_K} \inf_{\bm{\lambda} \in \text{\em{Alt}}(\bm{\mu})} \left( \sum_{a=1}^K w_a \text{\em{KL}}(\mu_a, \lambda_a)\right) .
+\end{equation}
+\end{theorem}
+
+And so we see that the two bounds on the sample complexity (one for
+Top-\(m\), one for best arm identification) differ only in the way that
+they build the sum of Kullback-Leibler divergences over the \(K\) arms.
+In contrast to Theorem \ref{theorem:KaufmannEtAl2016Theorem1}, here the
+contribution of each arm through its KL-divergence is weighted. The
+difference is that while we were able to very clearly describe the
+change of distribution in the Top-\(m\) case for each arm -- for each
+arm, we specified an alternative model that yields a new set of \(m\)
+optimal arms -- we now consider all alternative models that yield a
+different best arm than the model \(\bm{\mu}\). In the previous theorem,
+we sum over the complexity of each individual arm, as the change in
+distribution only ever touches one arm, thus leading to a KL-divergence
+of 0 for the other arms while still changing the optimal set. Here, we
+consider all instances of alternative models \(\bm{\lambda}\), and thus
+also those in which several arms are modified (and thus have a
+KL-divergence unequal 0 in the result of Lemma 1).
+
+\emph{Proof of Theorem \ref{theorem:GarivierKaufmannTheorem1}}: As
+stated before, we let \(\delta \in (0,1)\),
+\(\bm{\mu} \in \mathcal{S}\), and only consider \(\delta\)-PAC
+strategies. As before, \(N_a(t)\) describes the random number of pulls
+of arm \(a\) until time \(t\), for all \(t\geq 1\). Again, Lemma
+\ref{theorem:KaufmannEtAlLemma1} states how the failure probability
+\(\delta\) relates to the expected number of draws of each arm given two
+models which differ in their optimal arm, and where it is evaluated
+based on the Kullback-Leibler divergence for each pair of arms how much
+the two models differ:
+
+\begin{equation*}
+\forall \lambda \in \mathcal{S}: a^*(\lambda) \neq a^*(\mu), \sum_{a=1}^K \KL(\mu_a,\lambda_a)\mathbb{E}_{\bm{\mu}}[N_a(\tau_{\delta})] \geq \d(\delta, 1- \delta).
+\end{equation*}
+
+As mentioned, we now do not consider a specific alternative for each
+arm, but instead look at the infimum over all the possible alternatives,
+and use the fact that
+\(\mathbb{E}_{\bm{\mu}}[\tau_{\delta}] = \sum_{a=1}^K \mathbb{E}_{\bm{\mu}}[N_a(\tau_{\delta})]\):
+
+\begin{align*}
+\der(\delta, 1-\delta) & \leq \inf_{\lambda \in \text{Alt}(\bm{\mu})} \mathbb{E}_{\bm{\mu}}[\tau_{\delta}] \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[\tau_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
+& = \mathbb{E}_{\bm{\mu}}[\tau_{\delta}] \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[\tau_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
+& \leq \mathbb{E}_{\bm{\mu}}[\tau_{\delta}] \sup_{w \in \Sigma_K} \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K w_a \KL(\mu_a, \lambda_a)\Big).
+\end{align*}
+
+As stated in Garivier and Kaufmann (2016), the term
+\(\frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[\tau_{\delta}]}\)
+gives the fraction of draws each arm receives. This value, however,
+depends on the used algorithm. To make it hold for any \(\delta\)-PAC
+algorithm, it is replaced by the supremum over \(\Sigma_K\), which is
+the distribution over these fractions for any \(\mathcal{A}\), that is,
+for any \(\delta\)-PAC strategy.
+
+This lower bound can be interpreted as a Minimax game, where the
+experimenter has to choose the share of samples he attributes to each
+arm in a way that is optimal given that nature will respond and choose
+the most difficult alternative model given his weights. Thus, to make
+the lower bound practical, it is a matter of finding the optimal weights
+\(w^*(\bm{\mu})\).
+
 \end{document}

### 2017-05-28 Complexity of Best Arm Identification/kl_complexity.Rmd
Add Track-and-Stop algorithm

@@
 Thus, to make the lower bound practical, it is a matter of finding the optimal weights $w^*(\bm{\mu})$.
+This step did not occur in the previous lower bound, as the alternative models were made specific by changing the distribution of one arm with respect to the "border" between the two groups of arms.
+
+In any case, the existence of the optimal weights suggests an algorithm that keeps track of the share of samples that is attributed to each arm and makes sure that it stays close to the optimum until some decision rule assures that the $\delta$-PAC condition is fulfilled.
+
+And so by assuring the reader that there are ways to compute $w_a^*$ and $T^*$ given $\bm{\mu}$ (see chapter 2.2 in Garivier and Kaufmann (2016)), we can now introduce the *Track-and-Stop* strategy given in Garivier and Kaufmann (2016) that is able to match the lower bound by the intuition given above.
+
+When going from theory to algorithm, the obvious problem is of course that we do no longer know $\bm{\mu}$ and thus cannot simply calculate the optimal weights.
+Instead, we are estimating the maximum likelihood estimates $\hat{\mu}(t) = (\hat{\mu}_1(t), \dots, \hat{\mu}_K(t))$ of the true mean at the current round $t$ and need to base our weights based on these.
+It is however problematic to rely on these sample means as we are inherently unsure about them.
+And so wrong estimates, which naturally occur most easily in the beginning when not many samples have been pulled, are prone to lead to wrong weights.
+Thus, if a wrong estimate $\hat{\mu}_a$ for arm $a$ leads to a small weight $w_a$, then neither the estimate nor the weight will be correct soon.
+Thus, Kaufmann and Garivier conclude that "a naive plug-in sampling rule sometimes fails".
+They propose to enforce a certain minimum level of exploration to make sure that arms that erroneously received a very small weight will be further explored regardless.
+
+A very intuitive fix to this problem is the solution proposed in Lemma 8 of Garivier and Kaufmann (2016), with their $D-Tracking$ rule.
+Basically, whenever an arm has received a very low number of pulls $N_a(t)$ given the number of iterations so far, $t$ and the number of arms $K$ that have to share the samples, pull the arm that has received the smallest amount of samples so far.
+Else, pull the arm which number of pulls so far $N_a(t)$ is the furthest away from what its optimal share $t\cdot w^*_a(\hat{\bm{\mu}}(t))$ would be.
+Given this sampling rule, the authors can show in their Proposition 9 that the empirical proportion of draws converges in probability to the optimal weights given the true means.
+
+When combining this sampling rule with an appropriate stopping rule, the authors are able to prove in Theorem 14 an upper bound on the expected sampling complexity $\mathbb{E}_{\mu}[\tau_{\delta}]$.
+The stopping rule ensures that the algorithm explores sufficiently to promise a risk smaller than $\delta$, while stopping as soon as possible.
+Given that the sampling rule is independent of this stopping rule, the rule boils down to a statistical test at every iteration and thus is a sequential test based on the current estimate of $\hat{\bm{\mu}}$.
+The Chernoff's Stopping Rule proposed in Garivier and Kaufmann (2016) calculates for each arm $a\in \mathcal{A}$ the Generalized Likelihood Ratio statistic with every arm $b \in \mathcal{A}^{\setminus a}$, which for $\hat{\mu}_a(t) \geq \hat{\mu}_b(t)$ can be written as
+
+\begin{equation*}
+Z_{a,b}(t) = - Z_{b,a} = N_a(t) \KL(\hat{\mu},\hat{\mu}_{a,b})) + N_b(t) \KL(\hat{\mu}_{b(t)}, \hat{\mu}_{a,b}),
+\end{equation*}
+
+where
+
+\begin{equation*}
+\hat{\mu}_{a,b}(t) := \frac{N_a(t)}{N_a(t) + N_b(t)}\hat{\mu}_a + \frac{N_b(t)}{N_a(t) + N_b(t)}\hat{\mu}_b.
+\end{equation*}
+
+Consequently, a sensible idea for a stopping rule would be that there has to be an arm $a \in \mathcal{A}$ for which $Z_{a,b} \geq 0 \forall b \in \mathcal{A}^{\setminus a}$ (which is always fulfilled if there is a uniquely best arm), and, additionally, we demand that for this arm the smallest of the $(K-1)$ test statistics has to be larger than an exploration threshold $\beta(t, \delta)$.
+Consequently, the final number of samples $\tau_{\delta}$ of an algorithm is given by:
+
+\begin{equation*}
+\tau_{\delta} = \inf \{t \in \mathbb{N}: \exists a \in \mathcal{A}, \forall b\in \mathcal{A}^{\setminus a}, Z_{a,b}(t) > \beta(t, \delta)\}
+\end{equation*}
+
+Demanding that the optimal exploration threshold increases in rounds $t$ (if we have more samples, require more certainty; also, punish for failing previous tests) and decreases in the risk $\delta$, and does so at a diminishing rate, the optimal threshold derived in Theorem 10 of Garivier and Kaufmann (2016) makes sense intuitively:
+
+\begin{equation*}
+\beta(t, \delta) = \log \Big(\frac{2t(K-1)}{\delta}\Big)
+\end{equation*}.

### 2017-05-28 Complexity of Best Arm Identification/kl_complexity.tex
Add Track-and-Stop algorithm

@@
 the lower bound practical, it is a matter of finding the optimal weights
-\(w^*(\bm{\mu})\).
+\(w^*(\bm{\mu})\). This step did not occur in the previous lower bound,
+as the alternative models were made specific by changing the
+distribution of one arm with respect to the ``border'' between the two
+groups of arms.
+
+In any case, the existence of the optimal weights suggests an algorithm
+that keeps track of the share of samples that is attributed to each arm
+and makes sure that it stays close to the optimum until some decision
+rule assures that the \(\delta\)-PAC condition is fulfilled.
+
+And so by assuring the reader that there are ways to compute \(w_a^*\)
+and \(T^*\) given \(\bm{\mu}\) (see chapter 2.2 in Garivier and Kaufmann
+(2016)), we can now introduce the \emph{Track-and-Stop} strategy given
+in Garivier and Kaufmann (2016) that is able to match the lower bound by
+the intuition given above.
+
+When going from theory to algorithm, the obvious problem is of course
+that we do no longer know \(\bm{\mu}\) and thus cannot simply calculate
+the optimal weights. Instead, we are estimating the maximum likelihood
+estimates \(\hat{\mu}(t) = (\hat{\mu}_1(t), \dots, \hat{\mu}_K(t))\) of
+the true mean at the current round \(t\) and need to base our weights
+based on these. It is however problematic to rely on these sample means
+as we are inherently unsure about them. And so wrong estimates, which
+naturally occur most easily in the beginning when not many samples have
+been pulled, are prone to lead to wrong weights. Thus, if a wrong
+estimate \(\hat{\mu}_a\) for arm \(a\) leads to a small weight \(w_a\),
+then neither the estimate nor the weight will be correct soon. Thus,
+Kaufmann and Garivier conclude that ``a naive plug-in sampling rule
+sometimes fails''. They propose to enforce a certain minimum level of
+exploration to make sure that arms that erroneously received a very
+small weight will be further explored regardless.
+
+A very intuitive fix to this problem is the solution proposed in Lemma 8
+of Garivier and Kaufmann (2016), with their \(D-Tracking\) rule.
+Basically, whenever an arm has received a very low number of pulls
+\(N_a(t)\) given the number of iterations so far, \(t\) and the number
+of arms \(K\) that have to share the samples, pull the arm that has
+received the smallest amount of samples so far. Else, pull the arm which
+number of pulls so far \(N_a(t)\) is the furthest away from what its
+optimal share \(t\cdot w^*_a(\hat{\bm{\mu}}(t))\) would be. Given this
+sampling rule, the authors can show in their Proposition 9 that the
+empirical proportion of draws converges in probability to the optimal
+weights given the true means.
+
+When combining this sampling rule with an appropriate stopping rule, the
+authors are able to prove in Theorem 14 an upper bound on the expected
+sampling complexity \(\mathbb{E}_{\mu}[\tau_{\delta}]\). The stopping
+rule ensures that the algorithm explores sufficiently to promise a risk
+smaller than \(\delta\), while stopping as soon as possible. Given that
+the sampling rule is independent of this stopping rule, the rule boils
+down to a statistical test at every iteration and thus is a sequential
+test based on the current estimate of \(\hat{\bm{\mu}}\). The Chernoff's
+Stopping Rule proposed in Garivier and Kaufmann (2016) calculates for
+each arm \(a\in \mathcal{A}\) the Generalized Likelihood Ratio statistic
+with every arm \(b \in \mathcal{A}^{\setminus a}\), which for
+\(\hat{\mu}_a(t) \geq \hat{\mu}_b(t)\) can be written as
+
+\begin{equation*}
+Z_{a,b}(t) = - Z_{b,a} = N_a(t) \KL(\hat{\mu},\hat{\mu}_{a,b})) + N_b(t) \KL(\hat{\mu}_{b(t)}, \hat{\mu}_{a,b}),
+\end{equation*}
+
+where
+
+\begin{equation*}
+\hat{\mu}_{a,b}(t) := \frac{N_a(t)}{N_a(t) + N_b(t)}\hat{\mu}_a + \frac{N_b(t)}{N_a(t) + N_b(t)}\hat{\mu}_b.
+\end{equation*}
+
+Consequently, a sensible idea for a stopping rule would be that there
+has to be an arm \(a \in \mathcal{A}\) for which
+\(Z_{a,b} \geq 0 \forall b \in \mathcal{A}^{\setminus a}\) (which is
+always fulfilled if there is a uniquely best arm), and, additionally, we
+demand that for this arm the smallest of the \((K-1)\) test statistics
+has to be larger than an exploration threshold \(\beta(t, \delta)\).
+Consequently, the final number of samples \(\tau_{\delta}\) of an
+algorithm is given by:
+
+\begin{equation*}
+\tau_{\delta} = \inf \{t \in \mathbb{N}: \exists a \in \mathcal{A}, \forall b\in \mathcal{A}^{\setminus a}, Z_{a,b}(t) > \beta(t, \delta)\}
+\end{equation*}
+
+Demanding that the optimal exploration threshold increases in rounds
+\(t\) (if we have more samples, require more certainty; also, punish for
+failing previous tests) and decreases in the risk \(\delta\), and does
+so at a diminishing rate, the optimal threshold derived in Theorem 10 of
+Garivier and Kaufmann (2016) makes sense intuitively:
+
+\begin{equation*}
+\beta(t, \delta) = \log \Big(\frac{2t(K-1)}{\delta}\Big)
+\end{equation*}
+
+.
 

### 2017-05-28 Complexity of Best Arm Identification/kl_complexity.Rmd
Add conclusion to KL Complexity chapter

@@
 
-\begin{equation*}
+\begin{equation}\label{bre_approx}
 \forall x \in [0,1], \quad \der(x,1-x) = \der(1-x,x) \geq \log \frac{1}{2.4x}
-\end{equation*}
+\end{equation}
 
@@
 bre <- function(x) x * log(x/(1-x)) + (1-x) * log((1-x)/x)
-plot(x,bre(x), type = "l")
+plot(x,bre(x), type = "l", ylab = "Binary Relative Entropy")
 lines(x, log(1/(2.4*x)), col = "red")
@@
 
-Thus, following Kaufmann et al. (2016), define the complexity $\mathcal{K}_C(\nu)$ for the fixed confidence setting as
+Thus, following Kaufmann et al. (2016), define the complexity $\kappa_C(\nu)$ for the fixed confidence setting as
 
 \begin{equation}
-\mathcal{K}_C(\nu) = \inf_{A \, \text{PAC}} \lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\nu}[\tau_{\delta}]}{\log \frac{1}{\delta}}.
+\kappa_C(\nu) = \inf_{A \, \text{PAC}} \lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\nu}[\tau_{\delta}]}{\log \frac{1}{\delta}}.
 \end{equation}
@@
 \begin{equation*}
-\mathcal{K}_C(\nu) \geq \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})}
+\kappa_C(\nu) \geq \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})}
 \end{equation*}
@@
 \begin{equation}
-\mathcal{K}_B(\nu) = \inf_{A \, \text{consistent}} \big(\lim_{t \to \infty} \sup - \frac{1}{t} \log p_t(\nu)\big)^{-1}.
+\kappa_B(\nu) = \inf_{A \, \text{consistent}} \big(\lim_{t \to \infty} \sup - \frac{1}{t} \log p_t(\nu)\big)^{-1}.
 \end{equation}
 
-Given this definition, one can interpret the bound given in Theorem 12 of Kaufmann et al. directly as a lower bound on the complexity $\mathcal{K}_B(\nu)$ (note the inverse).
+Given this definition, one can interpret the bound given in Theorem 12 of Kaufmann et al. directly as a lower bound on the complexity $\kappa_B(\nu)$ (note the inverse).
 
@@
 In contrast, Kaufmann et al.
-(2016) are able to show that their complexity measure derived for the fixed-confidence setting, $\mathcal{K}_C(\nu)$, can be upper-bounded using the upper bound of the sample complexity (number of pulls) given for the KL-LUCB algorithm in Kaufmann and Kalyanakrishnan (2013).
-Consequently, in the case of exponential family bandits, the complexity $\mathcal{K}_C(\nu)$ is bounded as given in equation (6) in Kaufmann et al.
+(2016) are able to show that their complexity measure derived for the fixed-confidence setting, $\kappa_C(\nu)$, can be upper-bounded using the upper bound of the sample complexity (number of pulls) given for the KL-LUCB algorithm in Kaufmann and Kalyanakrishnan (2013).
+Consequently, in the case of exponential family bandits, the complexity $\kappa_C(\nu)$ is bounded as given in equation (6) in Kaufmann et al.
 (2016):
@@
 \begin{equation*}
-\sum_{a \in S^*_m} \frac{1}{K(\theta_a, \theta_{[m+1]})} + \sum_{a \notin S^*_m} \frac{1}{K(\theta_a,\theta_{[m]})} \leq \mathcal{K}_C(\nu) \leq 24 \min_{\theta \in [\theta_{[m+1]},\theta_{[m]}]} \sum_{a=1}^{K} \frac{1}{K^*(\theta_a, \theta)},
+\sum_{a \in S^*_m} \frac{1}{K(\theta_a, \theta_{[m+1]})} + \sum_{a \notin S^*_m} \frac{1}{K(\theta_a,\theta_{[m]})} \leq \kappa_C(\nu) \leq 24 \min_{\theta \in [\theta_{[m+1]},\theta_{[m]}]} \sum_{a=1}^{K} \frac{1}{K^*(\theta_a, \theta)},
 \end{equation*}
@@
 \begin{equation} \label{eq:GarivierKaufmann_Theorem1_Game}
-T^*(\bm{\mu})^{-1} := \sup_{w \in \Sigma_K} \inf_{\bm{\lambda} \in \text{\em{Alt}}(\bm{\mu})} \left( \sum_{a=1}^K w_a \text{\em{KL}}(\mu_a, \lambda_a)\right) .
+T^*(\bm{\mu})^{-1} := \sup_{w \in \Sigma_K} \inf_{\bm{\lambda} \in \text{\em{Alt}}(\bm{\mu})} \left( \sum_{a=1}^K w_a \text{\em{KL}}(\mu_a, \lambda_a)\right).
 \end{equation}
@@
 And so we see that the two bounds on the sample complexity (one for Top-$m$, one for best arm identification) differ only in the way that they build the sum of Kullback-Leibler divergences over the $K$ arms.
-In contrast to Theorem \ref{theorem:KaufmannEtAl2016Theorem1}, here the contribution of each arm through its KL-divergence is weighted.
+In contrast to Theorem \ref{theorem:KaufmannEtAlTheorem4}, here the contribution of each arm through its KL-divergence is weighted.
 The difference is that while we were able to very clearly describe the change of distribution in the Top-$m$ case for each arm -- for each arm, we specified an alternative model that yields a new set of $m$ optimal arms -- we now consider all alternative models that yield a different best arm than the model $\bm{\mu}$.
@@
 \begin{equation*}
-Z_{a,b}(t) = - Z_{b,a} = N_a(t) \KL(\hat{\mu},\hat{\mu}_{a,b})) + N_b(t) \KL(\hat{\mu}_{b(t)}, \hat{\mu}_{a,b}),
+Z_{a,b}(t) = - Z_{b,a} = N_a(t) \KL(\hat{\mu}_a(t),\hat{\mu}_{a,b}(t)) + N_b(t) \KL(\hat{\mu}_{b}(t), \hat{\mu}_{a,b}(t)),
 \end{equation*}
@@
 \begin{equation*}
-\beta(t, \delta) = \log \Big(\frac{2t(K-1)}{\delta}\Big)
-\end{equation*}.
+\beta(t, \delta) = \log \Big(\frac{2t(K-1)}{\delta}\Big).
+\end{equation*}
+
+With this, we can state the final theorem of the chapter, which gives the upper bound matching the lower bound in Theorem \ref{theorem:GarivierKaufmannTheorem1} for small risk values $\delta$ using the D-Tracking rule and Chernoff's stopping rule with the exploration term given in the previous equation:
+
+\begin{theorem}[Theorem 14, Garivier and Kaufmann, 2016] \label{theorem:GarivierAndKaufmannTheorem14}
+Let $\bm{\mu}$ be an exponential family bandit model.
+Let $\alpha \in [1, e/2]$ and $r(t) = O(t^{\alpha})$.
+Using Chernoff's stopping rule with $\beta(t,\delta) = \log(r(t)/\delta)$ and the sampling rule C-Tracking or D-Tracking,
+
+\begin{equation*}
+\lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\bm{\mu}}[\tau_{\delta}]}{\log(1/\delta)} \leq \alpha T^*(\mu).
+\end{equation*}
+\end{theorem}
+
+### Conclusion of Complexity of Best Arm Identification
+
+Overall, the two papers presented in this chapter make significant contributions to identifying the top-$1$ or the top-$m$ arms in a multi-armed bandit setting.
+Their contribution is primarily based on including the Kullback-Leibler divergence in the derivation of bounds and the matching algorithms and thus going beyond a sum of squared gaps which is most practical only in the case of Gaussian distributions.
+While the contribution in the fixed-budget setting was limited to the two-armed bandit case, the authors derive general lower bounds in the fixed-confidence setting which are primarily based on Lemma \ref{theorem:KaufmannEtAlLemma1}.
+Lemma \ref{theorem:KaufmannEtAlLemma1} is able to measure the "transportation cost" (see Garivier and Kaufmann, 2016) of moving from one distribution to another one in terms of Kullback-Leibler divergence.
+Using the information from the lower bound of how well any $\delta$-PAC algorithm can potentially be, the authors design algorithms matching these lower bounds.
+In the case of Top-$m$ identification, a simple application of the existing KL-LUCB algorithm works.
+In the case of best arm identification, the lower bound provides a way of calculating the optimal proportions in which the arms need to be pulled.
+Consequently, a matching algorithm can be set up so that it draws arms in these proportions, and so that it is robust against estimation errors of the plug-in estimates.
+Combining this sampling rule with an appropriate stopping rule makes for a $\delta$-PAC algorithm that matches the lower bound, where the upper bound in Theorem \ref{theorem:GarivierAndKaufmannTheorem14} matches the lower bound from Theorem \ref{theorem:GarivierKaufmannTheorem1} using equation \eqref{bre_approx}.

### 2017-05-28 Complexity of Best Arm Identification/kl_complexity.tex
Add conclusion to KL Complexity chapter

@@
 Thus, following Kaufmann et al. (2016), define the complexity
-\(\mathcal{K}_C(\nu)\) for the fixed confidence setting as
+\(\kappa_C(\nu)\) for the fixed confidence setting as
 
 \begin{equation}
-\mathcal{K}_C(\nu) = \inf_{A \, \text{PAC}} \lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\nu}[\tau_{\delta}]}{\log \frac{1}{\delta}}.
+\kappa_C(\nu) = \inf_{A \, \text{PAC}} \lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\nu}[\tau_{\delta}]}{\log \frac{1}{\delta}}.
 \end{equation}
@@
 \begin{equation}
-\mathcal{K}_B(\nu) = \inf_{A \, \text{consistent}} \big(\lim_{t \to \infty} \sup - \frac{1}{t} \log p_t(\nu)\big)^{-1}.
+\kappa_B(\nu) = \inf_{A \, \text{consistent}} \big(\lim_{t \to \infty} \sup - \frac{1}{t} \log p_t(\nu)\big)^{-1}.
 \end{equation}
@@
 of Kaufmann et al. directly as a lower bound on the complexity
-\(\mathcal{K}_B(\nu)\) (note the inverse).
+\(\kappa_B(\nu)\) (note the inverse).
 
@@
 complexity measure derived for the fixed-confidence setting,
-\(\mathcal{K}_C(\nu)\), can be upper-bounded using the upper bound of
-the sample complexity (number of pulls) given for the KL-LUCB algorithm
-in Kaufmann and Kalyanakrishnan (2013). Consequently, in the case of
-exponential family bandits, the complexity \(\mathcal{K}_C(\nu)\) is
-bounded as given in equation (6) in Kaufmann et al. (2016):
+\(\kappa_C(\nu)\), can be upper-bounded using the upper bound of the
+sample complexity (number of pulls) given for the KL-LUCB algorithm in
+Kaufmann and Kalyanakrishnan (2013). Consequently, in the case of
+exponential family bandits, the complexity \(\kappa_C(\nu)\) is bounded
+as given in equation (6) in Kaufmann et al. (2016):
 
 \begin{equation*}
-\sum_{a \in S^*_m} \frac{1}{K(\theta_a, \theta_{[m+1]})} + \sum_{a \notin S^*_m} \frac{1}{K(\theta_a,\theta_{[m]})} \leq \mathcal{K}_C(\nu) \leq 24 \min_{\theta \in [\theta_{[m+1]},\theta_{[m]}]} \sum_{a=1}^{K} \frac{1}{K^*(\theta_a, \theta)},
+\sum_{a \in S^*_m} \frac{1}{K(\theta_a, \theta_{[m+1]})} + \sum_{a \notin S^*_m} \frac{1}{K(\theta_a,\theta_{[m]})} \leq \kappa_C(\nu) \leq 24 \min_{\theta \in [\theta_{[m+1]},\theta_{[m]}]} \sum_{a=1}^{K} \frac{1}{K^*(\theta_a, \theta)},
 \end{equation*}
@@
 they build the sum of Kullback-Leibler divergences over the \(K\) arms.
-In contrast to Theorem \ref{theorem:KaufmannEtAl2016Theorem1}, here the
+In contrast to Theorem \ref{theorem:KaufmannEtAlTheorem4}, here the
 contribution of each arm through its KL-divergence is weighted. The
@@
 \begin{equation*}
-\beta(t, \delta) = \log \Big(\frac{2t(K-1)}{\delta}\Big)
+\beta(t, \delta) = \log \Big(\frac{2t(K-1)}{\delta}\Big).
 \end{equation*}
 
-.
+With this, we can state the final theorem of the chapter, which gives
+the upper bound matching the lower bound in Theorem
+\ref{theorem:GarivierKaufmannTheorem1} for small risk values \(\delta\)
+using the D-Tracking rule and Chernoff's stopping rule with the
+exploration term given in the previous equation:
+
+\begin{theorem}[Theorem 14, Garivier and Kaufmann, 2016] \label{theorem:GarivierAndKaufmannTheorem14}
+Let $\bm{\mu}$ be an exponential family bandit model.
+Let $\alpha \in [1, e/2]$ and $r(t) = O(t^{\alpha})$.
+Using Chernoff's stopping rule with $\beta(t,\delta) = \log(r(t)/\delta)$ and the sampling rule C-Tracking or D-Tracking,
+
+\begin{equation*}
+\lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\bm{\mu}}[\tau_{\delta}]}{\log(1/\delta)} \leq \alpha T^*(\mu).
+\end{equation*}
+\end{theorem}
+
+\subsubsection{Conclusion of Complexity of Best Arm
+Identification}\label{conclusion-of-complexity-of-best-arm-identification}
+
+Overall, the two papers presented in this chapter make significant
+contributions to identifying the top-\(1\) or the top-\(m\) arms in a
+multi-armed bandit setting. Their contribution is primarily based on
+including the Kullback-Leibler divergence in the derivation of bounds
+and the matching algorithms and thus going beyond a sum of squared gaps
+which is most practical only in the case of Gaussian distributions.
+While the contribution in the fixed-budget setting was limited to the
+two-armed bandit case, the authors derive general lower bounds in the
+fixed-confidence setting which are primarily based on Lemma
+\ref{theorem:KaufmannEtAlLemma1}. Lemma \ref{theorem:KaufmannEtAlLemma1}
+is able to measure the ``transportation cost'' (see Garivier and
+Kaufmann, 2016) of moving from one distribution to another one in terms
+of Kullback-Leibler divergence. Using the information from the lower
+bound of how well any \(\delta\)-PAC algorithm can potentially be, the
+authors design algorithms matching these lower bounds. In the case of
+Top-\(m\) identification, a simple application of the existing KL-LUCB
+algorithm works. In the case of best arm identification, the lower bound
+provides a way of calculating the optimal proportions in which the arms
+need to be pulled. Consequently, a matching algorithm can be set up so
+that it draws arms in these proportions, and so that it is robust
+against estimation errors of the plug-in estimates. Combining this
+sampling rule with an appropriate stopping rule makes for a
+\(\delta\)-PAC algorithm that matches the lower bound, where the upper
+bound in Theorem \ref{theorem:GarivierAndKaufmannTheorem14} matches the
+lower bound from Theorem \ref{theorem:GarivierKaufmannTheorem1} using
+equation \eqref{bre_approx}.
 

### 2017-05-28 Complexity of Best Arm Identification/kl_complexity.Rmd
Improve TBP Theorem 1

@@
 
+Indeed, the optimal weights will lead to a sampling structure in which arms are drawn in such a way ensuring that their individual failure probabilities are at the same level.
+Take a situation where the currently best arm $\hat{\mu}_1$ is the best arm.
+Then, we calculate for each arm the risk that actually it is better than arm 1.
+Since the arms are assumed to be independent, the we only have to compare every arm individually to arm 1.
+Given that, it makes sense that we don't want to disregard an arm that has a high probability of being better than arm 1.
+Assuming arm 1 is actually the best arm, we would an algorithm that ensures a low failure probability on all arms, thus equalizing the failure probability for every arm compared to arm 1.
+
+This is exactly what happens when we look for the proportions $w \in \Sigma_K$ that minimize the cost from a change in distributions, that is, the term $F(\bm{\mu}, \bm{w}) = \inf_{\bm{\lambda} \in \text{Alt}(\bm{\mu})} \Big(\sum_{a= 1}^K w_a \KL(\mu_a, \lambda_a)\Big)$.
+In the proof of Lemma 3 of Garivier and Kaufmann, it is shown that nature, selecting the alternative model $bm{\lambda}$ will always pick an alternative model in which only a single arm $a$ is changed such that $\lambda_a > \lambda_1$ since
+
+\begin{align*}
+T^*(\bm{\mu})^{-1} & = \sup_{w \in \Sigma_K} \min_{a \neq 1} \inf_{\bm{\lambda} \in \mathcal{S}: \lambda_a > \lambda_1} \sum_{a=1}^K w_a \KL(\mu_a, \lambda_a)  \\
+& = \sup_{w \in \Sigma_K} \min_{a \neq 1} \inf_{\bm{\lambda}: \lambda_a \geq \lambda_1} [w_1 \KL(\mu_1, \lambda_1)+w_a \KL(\mu_a, \lambda_a)].
+\end{align*}
+
+Consequently, $w$ will be chosen so as to minimize $T^*(\bm{\mu})$ no matter which arm $a$ was picked.
+It is a minimax game, so the ideal solution is to keep for each arm $a \neq 1$ the term $w_1 \KL(\mu_1, \lambda_1) + w_a \KL(\mu_a, \lambda_a)$ at the same level.
+Garivier and Kaufmann show that this can be written in terms of the Jenson-Shannon divergence, defined for every $\alpha \in [0,1]$ as
+
+\begin{equation*}
+I_{\alpha}(\mu_1, \mu_2) := \alpha \KL(\mu_1, \alpha \mu_1 + (1-\alpha) \mu_2) + (1-\alpha) \KL(\mu_2, \alpha \mu_1 + (1-\alpha) \mu_2).
+\end{equation*}
+
+Using this notation, the optimal proportions can be written as 
+\begin{equation*}
+w^*(\bm{\mu}) = \arg \max_{w \in \Sigma_K} \min_{a \neq 1} (w_1 + w_a) I_{\frac{w_1}{w_1+w_a}}(\mu_1, \mu_a)
+\end{equation*}
+
+which let's us furthermore conclude that these quantities are equal for all $a,b \in \{2,\dots, K\}$ with
+\begin{equation*}
+(w_1^* + w_a^*) I_{\frac{w_1^*}{w_1^*+w_a^*}}(\mu_1, \mu_a) = (w_1^* + w_b^*) I_{\frac{w_1^*}{w_1^*+w_b^*}}(\mu_1, \mu_b),
+\end{equation*}
+
+which is simply the statement in Lemma 4 of Garivier and Kaufmann (2016).
+
 And so by assuring the reader that there are ways to compute $w_a^*$ and $T^*$ given $\bm{\mu}$ (see chapter 2.2 in Garivier and Kaufmann (2016)), we can now introduce the *Track-and-Stop* strategy given in Garivier and Kaufmann (2016) that is able to match the lower bound by the intuition given above.
@@
 Lemma \ref{theorem:KaufmannEtAlLemma1} is able to measure the "transportation cost" (see Garivier and Kaufmann, 2016) of moving from one distribution to another one in terms of Kullback-Leibler divergence.
+This transportation cost will increase the expected stopping time, and so the experimenter has to be careful when selecting which arm to sample.
+By picking proportions $w^*(\bm{\mu})$ that minimize the transportation cost, a solution is found with as few iterations as possible.
+
+With respect to the optimal proportions we have derived some characteristics that now allow for a few interpretations.
+First, we have demanded that the algorithm keeps arms proportions in a way that equalizes the failure probability of every arm with respect to the best arm.
+This is basically similar to keeping the weighted Jensen-Shannon divergence at the same level which was shown in Lemma 4 of Garivier and Kaufmann (2016) and which we have repeated above.
+The fact that the risk plays an important role at any round of the algorithm suggests the possibility of turning the algorithm into an anytime algorithm.
+That is, instead of relying on Chernoff's stopping rule to end the algorithm at one point, and not being able to stop the algorithm before that and receiving a meaningful result, one would be able to stop the algorithm at any iteration, and receive both the recommended best arm and a confidence level.
+Second, the idea of comparing each arm to the best arm and based on that keeping the failure probabilities at a flat level seems transferrable to the thresholding bandit problem.
+Indeed, it might even be easier as the best arm does not have to be estimated; thus, the risk with respect to this estimate goes away.
+Instead, every arm will be compared to the threshold.
+One idea might be to compute for each arm $a$ the probability that the mean $\mu_a$ is actually on the other side of the threshold as currently suggested by $\hat{\mu}_a(t)$.
+This is independent of the other arms.
+And so a strategy might be to draw arms such that their failure probabilities are at the same level (draw whatever arm has the highest failure probability).
+We will come back to this idea in chapter 3.
+
 Using the information from the lower bound of how well any $\delta$-PAC algorithm can potentially be, the authors design algorithms matching these lower bounds.

### 2017-05-28 Complexity of Best Arm Identification/kl_complexity.tex
Improve TBP Theorem 1

@@
 
+Indeed, the optimal weights will lead to a sampling structure in which
+arms are drawn in such a way ensuring that their individual failure
+probabilities are at the same level. Take a situation where the
+currently best arm \(\hat{\mu}_1\) is the best arm. Then, we calculate
+for each arm the risk that actually it is better than arm 1. Since the
+arms are assumed to be independent, the we only have to compare every
+arm individually to arm 1. Given that, it makes sense that we don't want
+to disregard an arm that has a high probability of being better than arm
+1. Assuming arm 1 is actually the best arm, we would an algorithm that
+ensures a low failure probability on all arms, thus equalizing the
+failure probability for every arm compared to arm 1.
+
+This is exactly what happens when we look for the proportions
+\(w \in \Sigma_K\) that minimize the cost from a change in
+distributions, that is, the term
+\(F(\bm{\mu}, \bm{w}) = \inf_{\bm{\lambda} \in \text{Alt}(\bm{\mu})} \Big(\sum_{a= 1}^K w_a \KL(\mu_a, \lambda_a)\Big)\).
+In the proof of Lemma 3 of Garivier and Kaufmann, it is shown that
+nature, selecting the alternative model \(bm{\lambda}\) will always pick
+an alternative model in which only a single arm \(a\) is changed such
+that \(\lambda_a > \lambda_1\) since
+
+\begin{align*}
+T^*(\bm{\mu})^{-1} & = \sup_{w \in \Sigma_K} \min_{a \neq 1} \inf_{\bm{\lambda} \in \mathcal{S}: \lambda_a > \lambda_1} \sum_{a=1}^K w_a \KL(\mu_a, \lambda_a)  \\
+& = \sup_{w \in \Sigma_K} \min_{a \neq 1} \inf_{\bm{\lambda}: \lambda_a \geq \lambda_1} [w_1 \KL(\mu_1, \lambda_1)+w_a \KL(\mu_a, \lambda_a)].
+\end{align*}
+
+Consequently, \(w\) will be chosen so as to minimize \(T^*(\bm{\mu})\)
+no matter which arm \(a\) was picked. It is a minimax game, so the ideal
+solution is to keep for each arm \(a \neq 1\) the term
+\(w_1 \KL(\mu_1, \lambda_1) + w_a \KL(\mu_a, \lambda_a)\) at the same
+level. Garivier and Kaufmann show that this can be written in terms of
+the Jenson-Shannon divergence, defined for every \(\alpha \in [0,1]\) as
+
+\begin{equation*}
+I_{\alpha}(\mu_1, \mu_2) := \alpha \KL(\mu_1, \alpha \mu_1 + (1-\alpha) \mu_2) + (1-\alpha) \KL(\mu_2, \alpha \mu_1 + (1-\alpha) \mu_2).
+\end{equation*}
+
+Using this notation, the optimal proportions can be written as
+
+\begin{equation*}
+w^*(\bm{\mu}) = \arg \max_{w \in \Sigma_K} \min_{a \neq 1} (w_1 + w_a) I_{\frac{w_1}{w_1+w_a}}(\mu_1, \mu_a)
+\end{equation*}
+
+which let's us furthermore conclude that these quantities are equal for
+all \(a,b \in \{2,\dots, K\}\) with
+
+\begin{equation*}
+(w_1^* + w_a^*) I_{\frac{w_1^*}{w_1^*+w_a^*}}(\mu_1, \mu_a) = (w_1^* + w_b^*) I_{\frac{w_1^*}{w_1^*+w_b^*}}(\mu_1, \mu_b),
+\end{equation*}
+
+which is simply the statement in Lemma 4 of Garivier and Kaufmann
+(2016).
+
 And so by assuring the reader that there are ways to compute \(w_a^*\)
@@
 Kaufmann, 2016) of moving from one distribution to another one in terms
-of Kullback-Leibler divergence. Using the information from the lower
-bound of how well any \(\delta\)-PAC algorithm can potentially be, the
-authors design algorithms matching these lower bounds. In the case of
-Top-\(m\) identification, a simple application of the existing KL-LUCB
-algorithm works. In the case of best arm identification, the lower bound
-provides a way of calculating the optimal proportions in which the arms
-need to be pulled. Consequently, a matching algorithm can be set up so
-that it draws arms in these proportions, and so that it is robust
-against estimation errors of the plug-in estimates. Combining this
-sampling rule with an appropriate stopping rule makes for a
-\(\delta\)-PAC algorithm that matches the lower bound, where the upper
-bound in Theorem \ref{theorem:GarivierAndKaufmannTheorem14} matches the
-lower bound from Theorem \ref{theorem:GarivierKaufmannTheorem1} using
-equation \eqref{bre_approx}.
+of Kullback-Leibler divergence. This transportation cost will increase
+the expected stopping time, and so the experimenter has to be careful
+when selecting which arm to sample. By picking proportions
+\(w^*(\bm{\mu})\) that minimize the transportation cost, a solution is
+found with as few iterations as possible.
+
+With respect to the optimal proportions we have derived some
+characteristics that now allow for a few interpretations. First, we have
+demanded that the algorithm keeps arms proportions in a way that
+equalizes the failure probability of every arm with respect to the best
+arm. This is basically similar to keeping the weighted Jensen-Shannon
+divergence at the same level which was shown in Lemma 4 of Garivier and
+Kaufmann (2016) and which we have repeated above. The fact that the risk
+plays an important role at any round of the algorithm suggests the
+possibility of turning the algorithm into an anytime algorithm. That is,
+instead of relying on Chernoff's stopping rule to end the algorithm at
+one point, and not being able to stop the algorithm before that and
+receiving a meaningful result, one would be able to stop the algorithm
+at any iteration, and receive both the recommended best arm and a
+confidence level. Second, the idea of comparing each arm to the best arm
+and based on that keeping the failure probabilities at a flat level
+seems transferrable to the thresholding bandit problem. Indeed, it might
+even be easier as the best arm does not have to be estimated; thus, the
+risk with respect to this estimate goes away. Instead, every arm will be
+compared to the threshold. One idea might be to compute for each arm
+\(a\) the probability that the mean \(\mu_a\) is actually on the other
+side of the threshold as currently suggested by \(\hat{\mu}_a(t)\). This
+is independent of the other arms. And so a strategy might be to draw
+arms such that their failure probabilities are at the same level (draw
+whatever arm has the highest failure probability). We will come back to
+this idea in chapter 3.
+
+Using the information from the lower bound of how well any
+\(\delta\)-PAC algorithm can potentially be, the authors design
+algorithms matching these lower bounds. In the case of Top-\(m\)
+identification, a simple application of the existing KL-LUCB algorithm
+works. In the case of best arm identification, the lower bound provides
+a way of calculating the optimal proportions in which the arms need to
+be pulled. Consequently, a matching algorithm can be set up so that it
+draws arms in these proportions, and so that it is robust against
+estimation errors of the plug-in estimates. Combining this sampling rule
+with an appropriate stopping rule makes for a \(\delta\)-PAC algorithm
+that matches the lower bound, where the upper bound in Theorem
+\ref{theorem:GarivierAndKaufmannTheorem14} matches the lower bound from
+Theorem \ref{theorem:GarivierKaufmannTheorem1} using equation
+\eqref{bre_approx}.
 

### 2017-05-28 Thresholding Bandit/Theorem1.Rmd
Improve TBP Theorem 1

@@
    - \newtheorem{theorem}{Theorem}
+   - \newtheorem{lemma}{Lemma}
    - \newcommand{\KL}{\,\text{KL}}
@@
 The basic idea is as follows.
-The problem formulation considered in the paper describes bandit problems for Sub-Gaussian distributions.
-To show a lower bound, we show that every algorithm is expected to make a certain error even if we restrict ourselves to a heavily specified scenario.
-Even then, any algorithm will have a certain level of risk with which it cannot distinguish between the actual setting and a slightly changed setting (under which the former answer leads to regret).
+The problem formulation considered in the paper describes bandit problems for sub-Gaussian distributions.
+To show a lower bound, we show that every algorithm is expected to make a certain error even if we restrict ourselves to a very restricted scenario.
+Even then, any algorithm will have a certain level of risk with which it cannot distinguish between the actual setting and slightly changed settings (under which the former answer leads to regret).
 
@@
 Thus, assuming a variance of 1 for every arm, we have for every arm the distribution $\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)$.
-Furthermore, define $\nu_i' = \mathcal{N}(-\Delta_i,1)$.
+Furthermore, define for each arm $i \in \{1, \dots, K\}$ the alternative distribution $\nu_i' = \mathcal{N}(-\Delta_i,1)$.
+It is easy to see that in this case, this is equivalent to a "flip around the threshold".
+Arms that originally have a mean larger than the threshold have a mean smaller than the threshold after the flip.
 
@@
 We would hope that an algorithm classifies the means accordingly.
-However, we will show in what follows that any algorithm makes a certain error by not being able to distinguish $\mathcal{B}^0$ from a product distribution $\mathcal{B}^i$ which differs only slightly and has the same overall complexity (as defined by $H = \sum_{i=1}^K (\Delta_i)^{-2}$).
+However, we will show in what follows that any algorithm makes a certain error by not being able to distinguish $\mathcal{B}^0$ from at least one of $K$ alternative product distributions $\mathcal{B}^i, i \in \{1, \dots, K\}$, of which each differs only slightly in one arm from the original distribution, and has the same overall complexity (as defined by $H = \sum_{i=1}^K (\Delta_i)^{-2}$).
+We require $K$ different distributions so that an arm sampling arm $i$ very often for some reason will not have a smaller lower bound by chance.
 
+For each of the $K$ arms, we introduce an alternative model of the following kind.
 Before the start of the algorithm, we introduce a slight variation in the setup.
-Similar to how one can switch arms in the pure exploration setup for multi-armed bandits (compare Audibert et al., Garivier & Kaufmann) to "confuse" the algorithm without introducing additional complexity to the specified problem.
-However, since we do not compare arms with each other directly in the thresholding bandit problem (switching arms would still keep all means above the threshold), we instead need to flip an arm with respect to the threshold.
+The idea is similar to how one can switch arms in the pure exploration setup for multi-armed bandits (compare Audibert et al., 2010; Garivier & Kaufmann, 2016) to "confuse" any algorithm without introducing additional complexity to the specified problem.
+However, since we do not compare arms directly with each other in the thresholding bandit problem (switching arms would still keep all means above the threshold), we instead need to flip an arm $i$ with respect to the threshold in order to get the alternative model $\mathcal{B}_i$.
 Since the threshold is $\tau = 0$, we have for the flipped arm the new distribution $\nu_i'$ as defined above.
@@
 Given our formulation of the regret, the expected regret $\mathbb{E}[\mathcal{L}(T)]$ corresponds directly to the probability of making a wrong classification of any of the $K$ means.
-In general, let $T$ be a binary decision function, and define $\Omega = \{T = 0\}$ and $\Omega^C = \{T = 1\}$.
+In general, let $g$ be a binary decision function, and define $\Omega = \{g = 0\}$ and $\Omega^C = \{g = 1\}$.
 Assume that the decision $T$ distinguishes between two states of the world, $H_0$ and $H_1$.
-Then our overall error probability is given by $P_{H_0}(T=1) + P_{H_1}(T = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)$.
+Then our overall error probability is given by $P_{H_0}(g=1) + P_{H_1}(g = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)$.
 
 In our case, $H_0$ may correspond to the state in which we have $\mathcal{B}^0$, and $H_1$ corresponds to the case where any arm has been flipped, $\mathcal{B}^i$.
-Furthermore, we consider the events in which the algorithm, making the decision, classifies arm $i$ as being above the threshold: $\mathcal{A}_i = \{i \in \hat{S}_\tau$.
+Furthermore, we consider the events in which the algorithm, making the decision, classifies arm $i$ as being above the threshold: $\mathcal{A}_i = \{i \in \hat{S}_\tau\}$.
 The event on which all arms are being classified as above the threshold is consequently given by $\mathcal{A} = \bigcap \mathcal{A}_i$.
-However, Theorem 1 does not bound the overall regret, but the maximum error probability.
+However, Theorem 1 does not bound the overall regret, but the maximum error probability on the $K+1$ different models.
 We can write this now as
 
-\begin{equation}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big)
-= \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
-\end{equation}
+\begin{align}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big) \\
+& = \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
+\end{align}
 
 In order to give a bound on above equation, we start by considering $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$.
-This probability can be measured as the expected change in the likelihood of observed data times the probability under the original state.
-The measure of event $\mathcal{A}_i$ under state $\mathcal{B}^i$ is given as the probability of $\mathcal{A}_i$ under the (original) state $\mathcal{B}^0$ multiplied by a factor.
-This factor is the change in the data likelihoods due to moving from $\mathcal{B}^0$ to $\mathcal{B}^i$, and is expressed as the expected likelihood ratio under $\mathcal{B}^0$.
-By definition though, this is equal to the empirical Kullback-Leibler divergence of the two measures.
+This probability can be written as the expected change in the likelihood of observed data when moving from distribution $P_{\mathcal{B}_0}$ to $P_{\mathcal{B}_i}$, times the probability under the original state.
+In other words, the probability of event $\mathcal{A}_i$ under state $\mathcal{B}^i$ is given as the probability of $\mathcal{A}_i$ under the (original) state $\mathcal{B}^0$ multiplied by a factor.
+This factor describes whether the new distribution increases or decreases the probability of the event, and is given by the change in the data likelihoods due to moving from $\mathcal{B}^0$ to $\mathcal{B}^i$, expressed as the expected likelihood ratio under $\mathcal{B}^0$.
+By definition, the latter is equal to the empirical Kullback-Leibler divergence of the two distributions.
 
-First, let us define the change of measure in terms of the empirical log-likelihood for our case. Then, we will show how to replace the log-likelihood by the empirical Kullback-Leibler divergence.
+We will define the change of distribution in terms of the empirical log-likelihood for our case.
+Then, we will show how to replace the log-likelihood by the empirical Kullback-Leibler divergence.
+So let us first introduce the empirical Kullback-Leibler divergence.
 
@@
 
-#### Change of Measure
+#### Change of Distribution
 
-We are now ready to state the change of measure.
+We are now ready to state the change of distribution.
 As alluded to above, we consider how the probability changes for the event $\mathcal{A}_i$ when we move from $\mathcal{B}^0$ to $\mathcal{B}^i$.
 When flipping arm $i$, we only changed the samples of this arm, that is, the first $T_i$ observations we got from arm $i$ the algorithm took.
-The change of measure is then defined as:
+The change of distribution is then defined as:
 
@@
 
-#### Kullback-Leibler Divergence
+#### Concentration of the Empirical Kullback-Leibler Divergence
 
-For our problem, the Kullback-Leibler divergence of $/nu_k'$ from $\nu_k$ is given by $\KL_k := KL(\nu_k', \nu_k) = 2\Delta_k^2$.
-
-#### Concentration of the Empirical Kullback-Leibler Divergence
+For our problem, the Kullback-Leibler divergence of $\nu_k'$ from $\nu_k$ is given by $\KL_k := KL(\nu_k', \nu_k) = 2\Delta_k^2$.
 
@@
 
-itself is a normally distributed random variable with mean zero and a variance decreasing in $t$. Thus, one can show that $\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4$ for the event
+itself is a normally distributed random variable with mean zero and a variance decreasing in $t$.
+Thus, one can show as in Locatelli et al.
+(2016) that $\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4$ for the event
 
 \begin{equation}
-\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}} \}. \label{LocatelliTheorem1EventXi}
+\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}}\}. \label{LocatelliTheorem1EventXi}
 \end{equation}
@@
 Part of our bound is $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$, so let's continue with that.
-In general it holds that $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \bar{X}$.
+In general it holds that $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K}\sum_{i=1}^K X_i$.
 Thus we can write:
@@
 \begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
-& \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
-& \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
+& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
+& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
 \end{align*}
 
-where the second line is again the intersection of $\mathcal{A}_i$ and $\xi$ as before in order to apply the change of measure again in the third line.
+where the second line is again the intersection of $\mathcal{A}_i$ and $\xi$ as before in order to apply the change of distribution in the third line.
 
@@
 
-#### Conclusion
+#### Bringing everything together
 
@@
 We bound the maximum expected loss over all $\mathcal{B}_i$.
-By again using the fact that in general $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \bar{X}$, we plug in our previous calculations:
+By again using the fact that in general $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K} \sum_{i = 1}^K X_i$, we plug in our previous calculations:
 

### 2017-05-28 Thresholding Bandit/Theorem1.tex
Improve TBP Theorem 1

@@
 \newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
 \newcommand{\KL}{\,\text{KL}}
@@
 problem formulation considered in the paper describes bandit problems
-for Sub-Gaussian distributions. To show a lower bound, we show that
+for sub-Gaussian distributions. To show a lower bound, we show that
 every algorithm is expected to make a certain error even if we restrict
-ourselves to a heavily specified scenario. Even then, any algorithm will
+ourselves to a very restricted scenario. Even then, any algorithm will
 have a certain level of risk with which it cannot distinguish between
-the actual setting and a slightly changed setting (under which the
-former answer leads to regret).
+the actual setting and slightly changed settings (under which the former
+answer leads to regret).
 
@@
 \(\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)\). Furthermore,
-define \(\nu_i' = \mathcal{N}(-\Delta_i,1)\).
+define for each arm \(i \in \{1, \dots, K\}\) the alternative
+distribution \(\nu_i' = \mathcal{N}(-\Delta_i,1)\). It is easy to see
+that in this case, this is equivalent to a ``flip around the
+threshold''. Arms that originally have a mean larger than the threshold
+have a mean smaller than the threshold after the flip.
 
@@
 algorithm makes a certain error by not being able to distinguish
-\(\mathcal{B}^0\) from a product distribution \(\mathcal{B}^i\) which
-differs only slightly and has the same overall complexity (as defined by
-\(H = \sum_{i=1}^K (\Delta_i)^{-2}\)).
+\(\mathcal{B}^0\) from at least one of \(K\) alternative product
+distributions \(\mathcal{B}^i, i \in \{1, \dots, K\}\), of which each
+differs only slightly in one arm from the original distribution, and has
+the same overall complexity (as defined by
+\(H = \sum_{i=1}^K (\Delta_i)^{-2}\)). We require \(K\) different
+distributions so that an arm sampling arm \(i\) very often for some
+reason will not have a smaller lower bound by chance.
 
-Before the start of the algorithm, we introduce a slight variation in
-the setup. Similar to how one can switch arms in the pure exploration
-setup for multi-armed bandits (compare Audibert et al., Garivier \&
-Kaufmann) to ``confuse'' the algorithm without introducing additional
-complexity to the specified problem. However, since we do not compare
-arms with each other directly in the thresholding bandit problem
-(switching arms would still keep all means above the threshold), we
-instead need to flip an arm with respect to the threshold. Since the
-threshold is \(\tau = 0\), we have for the flipped arm the new
-distribution \(\nu_i'\) as defined above. Indeed, we can define the new
-product distribution \(B^i = \nu_1^i \otimes \dots \otimes \nu_K^i\)
-where for
+For each of the \(K\) arms, we introduce an alternative model of the
+following kind. Before the start of the algorithm, we introduce a slight
+variation in the setup. The idea is similar to how one can switch arms
+in the pure exploration setup for multi-armed bandits (compare Audibert
+et al., 2010; Garivier \& Kaufmann, 2016) to ``confuse'' any algorithm
+without introducing additional complexity to the specified problem.
+However, since we do not compare arms directly with each other in the
+thresholding bandit problem (switching arms would still keep all means
+above the threshold), we instead need to flip an arm \(i\) with respect
+to the threshold in order to get the alternative model
+\(\mathcal{B}_i\). Since the threshold is \(\tau = 0\), we have for the
+flipped arm the new distribution \(\nu_i'\) as defined above. Indeed, we
+can define the new product distribution
+\(B^i = \nu_1^i \otimes \dots \otimes \nu_K^i\) where for
 \(k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}\).
@@
 of making a wrong classification of any of the \(K\) means. In general,
-let \(T\) be a binary decision function, and define
-\(\Omega = \{T = 0\}\) and \(\Omega^C = \{T = 1\}\). Assume that the
+let \(g\) be a binary decision function, and define
+\(\Omega = \{g = 0\}\) and \(\Omega^C = \{g = 1\}\). Assume that the
 decision \(T\) distinguishes between two states of the world, \(H_0\)
 and \(H_1\). Then our overall error probability is given by
-\(P_{H_0}(T=1) + P_{H_1}(T = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)\).
+\(P_{H_0}(g=1) + P_{H_1}(g = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)\).
 
@@
 which the algorithm, making the decision, classifies arm \(i\) as being
-above the threshold: \(\mathcal{A}_i = \{i \in \hat{S}_\tau\). The event
-on which all arms are being classified as above the threshold is
+above the threshold: \(\mathcal{A}_i = \{i \in \hat{S}_\tau\}\). The
+event on which all arms are being classified as above the threshold is
 consequently given by \(\mathcal{A} = \bigcap \mathcal{A}_i\). However,
 Theorem 1 does not bound the overall regret, but the maximum error
-probability. We can write this now as
+probability on the \(K+1\) different models. We can write this now as
 
-\begin{equation}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big)
-= \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
-\end{equation}
+\begin{align}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big) \\
+& = \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
+\end{align}
 
@@
 \(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\). This probability can be
-measured as the expected change in the likelihood of observed data times
-the probability under the original state. The measure of event
-\(\mathcal{A}_i\) under state \(\mathcal{B}^i\) is given as the
-probability of \(\mathcal{A}_i\) under the (original) state
-\(\mathcal{B}^0\) multiplied by a factor. This factor is the change in
-the data likelihoods due to moving from \(\mathcal{B}^0\) to
-\(\mathcal{B}^i\), and is expressed as the expected likelihood ratio
-under \(\mathcal{B}^0\). By definition though, this is equal to the
-empirical Kullback-Leibler divergence of the two measures.
+written as the expected change in the likelihood of observed data when
+moving from distribution \(P_{\mathcal{B}_0}\) to \(P_{\mathcal{B}_i}\),
+times the probability under the original state. In other words, the
+probability of event \(\mathcal{A}_i\) under state \(\mathcal{B}^i\) is
+given as the probability of \(\mathcal{A}_i\) under the (original) state
+\(\mathcal{B}^0\) multiplied by a factor. This factor describes whether
+the new distribution increases or decreases the probability of the
+event, and is given by the change in the data likelihoods due to moving
+from \(\mathcal{B}^0\) to \(\mathcal{B}^i\), expressed as the expected
+likelihood ratio under \(\mathcal{B}^0\). By definition, the latter is
+equal to the empirical Kullback-Leibler divergence of the two
+distributions.
 
-First, let us define the change of measure in terms of the empirical
+We will define the change of distribution in terms of the empirical
 log-likelihood for our case. Then, we will show how to replace the
-log-likelihood by the empirical Kullback-Leibler divergence.
+log-likelihood by the empirical Kullback-Leibler divergence. So let us
+first introduce the empirical Kullback-Leibler divergence.
 
@@
 
-\paragraph{Change of Measure}\label{change-of-measure}
+\paragraph{Change of Distribution}\label{change-of-distribution}
 
-We are now ready to state the change of measure. As alluded to above, we
-consider how the probability changes for the event \(\mathcal{A}_i\)
-when we move from \(\mathcal{B}^0\) to \(\mathcal{B}^i\). When flipping
-arm \(i\), we only changed the samples of this arm, that is, the first
-\(T_i\) observations we got from arm \(i\) the algorithm took. The
-change of measure is then defined as:
+We are now ready to state the change of distribution. As alluded to
+above, we consider how the probability changes for the event
+\(\mathcal{A}_i\) when we move from \(\mathcal{B}^0\) to
+\(\mathcal{B}^i\). When flipping arm \(i\), we only changed the samples
+of this arm, that is, the first \(T_i\) observations we got from arm
+\(i\) the algorithm took. The change of distribution is then defined as:
 
@@
 
-\paragraph{Kullback-Leibler
-Divergence}\label{kullback-leibler-divergence}
-
-For our problem, the Kullback-Leibler divergence of \(/nu_k'\) from
-\(\nu_k\) is given by \(\KL_k := KL(\nu_k', \nu_k) = 2\Delta_k^2\).
-
 \paragraph{Concentration of the Empirical Kullback-Leibler
 Divergence}\label{concentration-of-the-empirical-kullback-leibler-divergence}
+
+For our problem, the Kullback-Leibler divergence of \(\nu_k'\) from
+\(\nu_k\) is given by \(\KL_k := KL(\nu_k', \nu_k) = 2\Delta_k^2\).
 
@@
 itself is a normally distributed random variable with mean zero and a
-variance decreasing in \(t\). Thus, one can show that
-\(\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4\) for the event
+variance decreasing in \(t\). Thus, one can show as in Locatelli et al.
+(2016) that \(\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4\) for the event
 
 \begin{equation}
-\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}} \}. \label{LocatelliTheorem1EventXi}
+\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}}\}. \label{LocatelliTheorem1EventXi}
 \end{equation}
@@
 so let's continue with that. In general it holds that
-\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \bar{X}\). Thus we can
-write:
+\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K}\sum_{i=1}^K X_i\).
+Thus we can write:
 
 \begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
-& \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
-& \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
+& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
+& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
 \end{align*}
@@
 where the second line is again the intersection of \(\mathcal{A}_i\) and
-\(\xi\) as before in order to apply the change of measure again in the
+\(\xi\) as before in order to apply the change of distribution in the
 third line.
@@
 
-\paragraph{Conclusion}\label{conclusion}
+\paragraph{Bringing everything
+together}\label{bringing-everything-together}
 
@@
 over all \(\mathcal{B}_i\). By again using the fact that in general
-\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \bar{X}\), we plug in
-our previous calculations:
+\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K} \sum_{i = 1}^K X_i\),
+we plug in our previous calculations:
 

### 2017-05-31 Chapter Three/Chapter3.Rmd
Add start of chapter three

---
title: "Chapter Three"
author: "Tim Radtke"
date: "5/31/2017"
header-includes:
   #- \documentclass[a4paper,twoside,english]{article}
   - \usepackage[retainorgcmds]{IEEEtrantools}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{bbm}
   - \newtheorem{theorem}{Theorem}
   - \newtheorem{lemma}{Lemma}
   - \newcommand{\KL}{\,\text{KL}}
   - \newcommand{\der}{\,\text{d}}
   #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
   #- \usepackage{fontspec}
   #-   \setmainfont{Arial}
keep_tex: TRUE
output:
  pdf_document:
    number_sections: true
    keep_tex: true
    toc: true
    toc_depth: 3
    #latex_engine: xelatex
fontsize: 12pt
urlcolor: blue
---

# KL and Bayesian Thresholding Bandits

## Introduction

We have introduced the thresholding bandit problem in chapter 1. The APT algorith described in Locatelli et al. (2016) is able to match a lower bound (be more specific!) given in the same paper, and has several favorable characteristics such as its overall simplicity and it being an anytime algorithm. However, the bounds on the expected loss assume the arms' distributions to be $R$-sub-Gaussian. This is reflected in the algorithm's complexity measure $H = \sum_{i=1}^K (\Delta_i^{\tau, \epsilon})^{-2}$, where $\Delta_i^{\tau,\epsilon} = |\mu_i - \tau| + \epsilon$, which -- given the known threshold $\tau \pm \epsilon$ -- only depends on the distribution's mean. This is appropriate for Gaussian arms with equal variances, but potentially inefficient for other kinds of distributions.

In the case of Gaussian distributions with varying variances, for example, it makes sense to take the variance into account; after all, given two Gaussians with equal mean, intuitively we would prefer to get a sample from the distribution of larger variance.

In the case of Gaussians, the complexity $H$ is nice also because it reflects the Kullback-Leibler divergence between two Gaussians. And since Bernoulli distributions are bounded on the interval $[0,1]$, they are consequently sub-Gaussian, meaning that their Kullback-Leibler divergence can be approximated by the Gaussian one. However, while Bernoullis are sub-Gaussian, the approximation of their divergence by the Gaussian divergence becomes less and less optimal as the parameter (and thus mean) goes to $0$ or $1$, as shown in chapter 1. And while online advertisements might not be an obvious use case for thresholding bandits, they are just one real life scenario dominated by Bernoulli distributions with very small parameters. Thus it is worthwile to adapt current solutions of the thresholding bandit problem to cases in which the Gaussian Kullback-Leibler divergence is no longer an appropriate approximation.

Large motiviation for the idea of adjusting the complexity measure (and thus the algorithms) to distributions more generally based on the Kullback-Leibler divergence stems from the work discussed in chapter 2, complexity measures were defined for the pure exploration bandits in terms of the Kullback-Leibler divergence. Based on this, the authors were for example able to point our differences between Gaussian and Bernoulli bandits. We expect that results in a similar vain could be derived for thresholding bandits.

To this end, in the following, we first present an extension of mean based algorithms to an algorithm that incorporates empirical variances as described in Mukherjee et al. (2017). Afterwards, we propose and discuss potential further improvements based on Kullback-Leibler divergence and Bayesian posterior distributions. Finally, we compare the performance of different algorithms based on simulations and real world data sets.

## Variance Based Algorithms for Thresholding Bandits

Mukherjee et al. (2017) propose an algorithm based on variance estimates called Augmented-UCB (AugUCB). The setting in which the algorithm is proposed is very similar to the setting in Locatelli et al. (2016). The algorithm itself, however, differs heavily from the APT algorithm. So is AugUCB for example not an anytime algorithm. Furthermore, arms can be deleted in every round if there are "far enough" away from the mean. Both the decision of which arm is played in a given round, and whether an arm is removed from the active set of arm, is based not only on the empirical mean estimate $\mu_i(t)$, but also on a term $s_i$ that is increasing linearly in the estimated standard deviation. While the APT algorithm plays the arm minimizing the quantity $B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t) = \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau| + \epsilon)$, AugUCB plays the arm minimizing the quantity $(\hat{\Delta}_i(t) - 2s_i)$, where $s_i$ is based on the variance estimate $\hat{v}_i$, and an exploration $\psi_m$ term linear in $T$, and an elimination parameter $\rho$ (compare Algorithm 1 in Mukherjee et al., 2017):

\begin{equation*}
s_i = \sqrt{\frac{\rho \psi_m (\hat{v}_i + 1) \log(T \epsilon_m)}{4n_i}}
\end{equation*}

Consequently, the authors also introduce complexity measures which take the variance into account. From Gabillon et al. (2011) they use $H_{\sigma, 1}= \sum_{i=1}^K \frac{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}{\Delta_i^2}$. Furthermore, with $\stackrel{\sim}{\Delta}_i^2 = \frac{\Delta_i^2}{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}$, and with $\stackrel{\sim}{\Delta}_{(i)}$ being an increasing ordering of $\stackrel{\sim}{\Delta}_i$, the authors define a complexity corresponding to $H_{CSAR,2}$ in Chen et al. (2014):

\begin{equation*}
H_{\sigma,2} = \max_{i \ in \mathcal{A}} \frac{i}{\stackrel{\sim}{\Delta}_{(i)}^2}.
\end{equation*}

While the latter complexity appears in the provided upper bound on the AugUCB algorithm's expected loss, it could be replaced by $H_{\sigma, 1}$ since $H_{\sigma, 2} \leq H_{\sigma,1}$. $H_{\sigma,1}$ is of course more directly comparable to the complexity $H$ that we are used to.

While in the case of the APT algorithm the number of times a specific arm has been drawn $T_i$ measures how concentrated the estimated mean is around the true mean (and thus for large $T_i$ an arm is no longer drawn even if $\hat{\mu}$ is close to $\tau$); in the case of the AugUCB algorithm this is regulated by the combination of the variance estimate $\hat{v}_i$ and the exploration factor $\psi_m$, where they ensure that certain arms are no longer pulled when the algorithm is sufficiently confident in its knowledge about the true mean. Therefore, when using a very similar favorable event in the proof of their upper bound, Mukherjee et al. (2017) have to bound the probability that an an arm is not removed from the active set after the a certain number of rounds -- even though the arm is above (respectively below) the threshold. If this probability is low, then this means that the algorithm is able to be certain about an arm's true mean *quickly* by employing variance estimates. In comparison, Locatelli et al (2016) used bounds on on how often arms are drawn ($T_i$) to give a bound on the probability of the favorable event. In order to derive the bound, Mukherjee et al. (2017) use the Bernstein inequality.

It has to be noted that Mukherjee et al. (2017) have to assume that the distributions have rewards bounded in $[0,1]$ in order to derive the bound on the probability that an arm has not been eliminated correctly in round $T_i$. Thus, the distributions for which their upper bound holds are a subset of the sub-Gaussian distributions considered in Locatelli et al. (2016). However, it is not that the authors need to assume that the rewards are in $[0,1]$, but this was assumed so that the variance of the distribution is in $[0,1]$. Thus, the upper bound holds in particular for Gaussian distributions with variance $\sigma^2 \in [0,1]$.

Based on this assumption, the authors show that the probability that an arm has not been eliminated after $m_i$ rounds is given by (compare equation (2) in Mukherjee et al., 2017):

\begin{equation} \label{Mukherjee2017Equation2}
\mathbb{P}(\hat{\mu}_i > \mu_i + 2s_i) \leq \mathbb{P} (\hat{\mu}_i > \mu_i + 2\bar{s}_i) + \mathbb{P}(\hat{v}_i \geq \sigma^2_i + \sqrt{\rho \epsilon_{T_i}})
\end{equation}

Compare Mukherjee et al. (2017) for the notation. Then it becomes clear that the left part of the RHS gives the probability that the mean estimate is out of wack, while the right term gives the probability that the variance is overestimated. The first term is bounded by the Bernstein inequality. In the cumulative regret setting, there exists a similar decomposition that bounds the expected number of pulls of a suboptimal arm. Compare for example chapter 3.1 in "Thompson Sampling: An Asymptotically Optimal Finite Time Analysis" by Kaufmann, Korda and Munos (2012). There they decompose the expected number of draws of an suboptimal arm for an optimistic (UCB like) into the probability that the optimal arm's mean is underestimated, and the probability that the UCB of the suboptimal arm is still very large. To give bounds for UCB algorithms, it is then shown that these two terms show a certain convergence. Mukherjee et al. do similarly for their variance based algorithm in the thresholding setting.

(since the AugUCB eliminates arms, it is interesting to see how it behaves when the underlying CTR changes over time...)

## New Approaches

### 2017-05-31 Chapter Three/Chapter3.tex
Add start of chapter three

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={Chapter Three},
            pdfauthor={Tim Radtke},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{Chapter Three}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Tim Radtke}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{5/31/2017}

\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{bbm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newcommand{\KL}{\,\text{KL}}
\newcommand{\der}{\,\text{d}}

\begin{document}
\maketitle

{
\hypersetup{linkcolor=black}
\setcounter{tocdepth}{3}
\tableofcontents
}
\section{KL and Bayesian Thresholding
Bandits}\label{kl-and-bayesian-thresholding-bandits}

\subsection{Introduction}\label{introduction}

We have introduced the thresholding bandit problem in chapter 1. The APT
algorith described in Locatelli et al. (2016) is able to match a lower
bound (be more specific!) given in the same paper, and has several
favorable characteristics such as its overall simplicity and it being an
anytime algorithm. However, the bounds on the expected loss assume the
arms' distributions to be \(R\)-sub-Gaussian. This is reflected in the
algorithm's complexity measure
\(H = \sum_{i=1}^K (\Delta_i^{\tau, \epsilon})^{-2}\), where
\(\Delta_i^{\tau,\epsilon} = |\mu_i - \tau| + \epsilon\), which -- given
the known threshold \(\tau \pm \epsilon\) -- only depends on the
distribution's mean. This is appropriate for Gaussian arms with equal
variances, but potentially inefficient for other kinds of distributions.

In the case of Gaussian distributions with varying variances, for
example, it makes sense to take the variance into account; after all,
given two Gaussians with equal mean, intuitively we would prefer to get
a sample from the distribution of larger variance.

In the case of Gaussians, the complexity \(H\) is nice also because it
reflects the Kullback-Leibler divergence between two Gaussians. And
since Bernoulli distributions are bounded on the interval \([0,1]\),
they are consequently sub-Gaussian, meaning that their Kullback-Leibler
divergence can be approximated by the Gaussian one. However, while
Bernoullis are sub-Gaussian, the approximation of their divergence by
the Gaussian divergence becomes less and less optimal as the parameter
(and thus mean) goes to \(0\) or \(1\), as shown in chapter 1. And while
online advertisements might not be an obvious use case for thresholding
bandits, they are just one real life scenario dominated by Bernoulli
distributions with very small parameters. Thus it is worthwile to adapt
current solutions of the thresholding bandit problem to cases in which
the Gaussian Kullback-Leibler divergence is no longer an appropriate
approximation.

Large motiviation for the idea of adjusting the complexity measure (and
thus the algorithms) to distributions more generally based on the
Kullback-Leibler divergence stems from the work discussed in chapter 2,
complexity measures were defined for the pure exploration bandits in
terms of the Kullback-Leibler divergence. Based on this, the authors
were for example able to point our differences between Gaussian and
Bernoulli bandits. We expect that results in a similar vain could be
derived for thresholding bandits.

To this end, in the following, we first present an extension of mean
based algorithms to an algorithm that incorporates empirical variances
as described in Mukherjee et al. (2017). Afterwards, we propose and
discuss potential further improvements based on Kullback-Leibler
divergence and Bayesian posterior distributions. Finally, we compare the
performance of different algorithms based on simulations and real world
data sets.

\subsection{Variance Based Algorithms for Thresholding
Bandits}\label{variance-based-algorithms-for-thresholding-bandits}

Mukherjee et al. (2017) propose an algorithm based on variance estimates
called Augmented-UCB (AugUCB). The setting in which the algorithm is
proposed is very similar to the setting in Locatelli et al. (2016). The
algorithm itself, however, differs heavily from the APT algorithm. So is
AugUCB for example not an anytime algorithm. Furthermore, arms can be
deleted in every round if there are ``far enough'' away from the mean.
Both the decision of which arm is played in a given round, and whether
an arm is removed from the active set of arm, is based not only on the
empirical mean estimate \(\mu_i(t)\), but also on a term \(s_i\) that is
increasing linearly in the estimated standard deviation. While the APT
algorithm plays the arm minimizing the quantity
\(B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t) = \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau| + \epsilon)\),
AugUCB plays the arm minimizing the quantity
\((\hat{\Delta}_i(t) - 2s_i)\), where \(s_i\) is based on the variance
estimate \(\hat{v}_i\), and an exploration \(\psi_m\) term linear in
\(T\), and an elimination parameter \(\rho\) (compare Algorithm 1 in
Mukherjee et al., 2017):

\begin{equation*}
s_i = \sqrt{\frac{\rho \psi_m (\hat{v}_i + 1) \log(T \epsilon_m)}{4n_i}}
\end{equation*}

Consequently, the authors also introduce complexity measures which take
the variance into account. From Gabillon et al. (2011) they use
\(H_{\sigma, 1}= \sum_{i=1}^K \frac{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}{\Delta_i^2}\).
Furthermore, with
\(\stackrel{\sim}{\Delta}_i^2 = \frac{\Delta_i^2}{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}\),
and with \(\stackrel{\sim}{\Delta}_{(i)}\) being an increasing ordering
of \(\stackrel{\sim}{\Delta}_i\), the authors define a complexity
corresponding to \(H_{CSAR,2}\) in Chen et al. (2014):

\begin{equation*}
H_{\sigma,2} = \max_{i \ in \mathcal{A}} \frac{i}{\stackrel{\sim}{\Delta}_{(i)}^2}.
\end{equation*}

While the latter complexity appears in the provided upper bound on the
AugUCB algorithm's expected loss, it could be replaced by
\(H_{\sigma, 1}\) since \(H_{\sigma, 2} \leq H_{\sigma,1}\).
\(H_{\sigma,1}\) is of course more directly comparable to the complexity
\(H\) that we are used to.

While in the case of the APT algorithm the number of times a specific
arm has been drawn \(T_i\) measures how concentrated the estimated mean
is around the true mean (and thus for large \(T_i\) an arm is no longer
drawn even if \(\hat{\mu}\) is close to \(\tau\)); in the case of the
AugUCB algorithm this is regulated by the combination of the variance
estimate \(\hat{v}_i\) and the exploration factor \(\psi_m\), where they
ensure that certain arms are no longer pulled when the algorithm is
sufficiently confident in its knowledge about the true mean. Therefore,
when using a very similar favorable event in the proof of their upper
bound, Mukherjee et al. (2017) have to bound the probability that an an
arm is not removed from the active set after the a certain number of
rounds -- even though the arm is above (respectively below) the
threshold. If this probability is low, then this means that the
algorithm is able to be certain about an arm's true mean \emph{quickly}
by employing variance estimates. In comparison, Locatelli et al (2016)
used bounds on on how often arms are drawn (\(T_i\)) to give a bound on
the probability of the favorable event. In order to derive the bound,
Mukherjee et al. (2017) use the Bernstein inequality.

It has to be noted that Mukherjee et al. (2017) have to assume that the
distributions have rewards bounded in \([0,1]\) in order to derive the
bound on the probability that an arm has not been eliminated correctly
in round \(T_i\). Thus, the distributions for which their upper bound
holds are a subset of the sub-Gaussian distributions considered in
Locatelli et al. (2016). However, it is not that the authors need to
assume that the rewards are in \([0,1]\), but this was assumed so that
the variance of the distribution is in \([0,1]\). Thus, the upper bound
holds in particular for Gaussian distributions with variance
\(\sigma^2 \in [0,1]\).

Based on this assumption, the authors show that the probability that an
arm has not been eliminated after \(m_i\) rounds is given by (compare
equation (2) in Mukherjee et al., 2017):

\begin{equation} \label{Mukherjee2017Equation2}
\mathbb{P}(\hat{\mu}_i > \mu_i + 2s_i) \leq \mathbb{P} (\hat{\mu}_i > \mu_i + 2\bar{s}_i) + \mathbb{P}(\hat{v}_i \geq \sigma^2_i + \sqrt{\rho \epsilon_{T_i}})
\end{equation}

Compare Mukherjee et al. (2017) for the notation. Then it becomes clear
that the left part of the RHS gives the probability that the mean
estimate is out of wack, while the right term gives the probability that
the variance is overestimated. The first term is bounded by the
Bernstein inequality. In the cumulative regret setting, there exists a
similar decomposition that bounds the expected number of pulls of a
suboptimal arm. Compare for example chapter 3.1 in ``Thompson Sampling:
An Asymptotically Optimal Finite Time Analysis'' by Kaufmann, Korda and
Munos (2012). There they decompose the expected number of draws of an
suboptimal arm for an optimistic (UCB like) into the probability that
the optimal arm's mean is underestimated, and the probability that the
UCB of the suboptimal arm is still very large. To give bounds for UCB
algorithms, it is then shown that these two terms show a certain
convergence. Mukherjee et al. do similarly for their variance based
algorithm in the thresholding setting.

(since the AugUCB eliminates arms, it is interesting to see how it
behaves when the underlying CTR changes over time\ldots{})

\subsection{New Approaches}\label{new-approaches}

\end{document}

### 2017-05-31 Thesis/Draft.Rmd
Add start of chapter three

--- 2017-05-28 Complexity of Best Arm Identification/kl_complexity.Rmd
@@
 ---
-title: "On the Complexity of Best Arm Identification"
+title: "Draft"
 author: "Tim Radtke"
-date: "5/20/2017"
+date: "5/28/2017"
 header-includes:
@@
     keep_tex: true
+    toc: true
+    toc_depth: 3
     #latex_engine: xelatex
@@
 ---
+
+# Thresholding Bandit Problem
+
+The *Thresholding Bandit Problem* described in Locatelli et al.
+(2016) can be considered a variant of a variant.
+It can be framed into the wider literature of *Pure Exploration* multi-armed bandit problems.
+In particular, it shares characteristics with the *Top-$m$* problem.
+This problem is concerned with finding the $m$ best arms as described by the means of their corresponding distributions.
+This in turn is similar to the *combinatorial bandit* problem, which also aims at finding the $m$ best arms.
+However, it is able to pull several arms at once: Think of an online shop that shows five recommended products on a product detail page.
+These five recommended products might each be represented by an arm, and we look for the products with the largest mean conversion rate.
+The thresholding bandit problem we discuss here, however, is concerned with pulling a single arm at a time.
+And so a more appropriate situation is that of a website presenting a banner.
+Again, think of an online shop trying to promote a certain category.
+The content team came up with a number of different designs for the banner, and it's not clear how many click-throughs they will gather.
+
+The idea now is that we would like to classify the banners into two distinct groups: A group with a mean conversion rate $\mu_i$ below threshold $\tau$, and a group with mean conversion rate $\mu_i$ above threshold $\tau$.
+This might be the optimization problem when we are concerned with not falling below a certain minimum level click-through rate with the banners we're choosing.
+
+If it turns out that in general we can find relatively quickly whether arms are above or below a threshold, then this kind of test can be used to safeguard against very bad versions in a test.
+Before we move to a Top-$m$ test, we might want to run a thresholding version and then continue only with the arms classified into the group above the threshold.
+This might be justified when adjusting parts of the checkout process of an online shop, where the conversion rate or the average order value should not drop below a threshold.
+
+## Setup
+
+In any case, the problem boils down to the following.
+As standard in multi-armed bandit problems, we have $K$ arms $\mathcal{A} = \{1, \dots K\}$.
+We can pull arm $k$ at time $t$ to collect feedback in form of the random variable $X_{k,t}$ which is distributed accoring to the arm's distribution $\nu_k$.
+In general, we are concerned with estimating for each arm $i$ the mean $\mu_i$ of its distribution $\nu_i$.
+In contrast to most bandit problems, however, we do not directly compare arms with each other by comparing their means.
+In the case of pure exploration bandits, it is for example necessary to compare the arms because one aims to find the best one.
+In the case of the thresholding bandit, however, we compare each arm's mean $\mu_i$ individually against the threshold $\tau \in \mathbb{R}$ which is known and fixed before the experiment.
+One might compare this to a pure exploration bandit in which the mean of the best arm is known upfront.
+We will see later that this fact leads to advantages in the design of algorithms which are not as readily available in other bandit settings.
+
+In Locatelli (2016), the arms' distributions are assumed to follow a $R$-sub-Gaussian distribution.
+Under this assumption, the authors are able to proof a general lower bound as well as an algorithm with a matching upper bound.
+Both hinge upon the *complexity* of a given problem.
+Since bandit problems can differ in the number of the arms $K$ and the means of each arm, some pose easier identification problems than others.
+Indeed, in the thresholding problem, the difficulty of the problem naturally depends on how close (the means of the) distributions are to the fixed threshold.
+Intuitively, the closer a mean $\mu_i$ is to the threshold $\tau$, the more difficult it will be to distinguish the two successfully based on samples from the distribution $\nu_i$.
+For the case of the sub-Gaussian distributions, a natural measure of this distance is given by simply $\Delta_i = |\tau - \mu_i| + \epsilon$, where $\epsilon$ defines a $2\epsilon$ interval around the threshold $\tau$ in which we allow ourselves to make a mistake at no cost.
+
+If we extend this idea to the set of arms $i \in \{1,...,K\}$ of a given bandit problem, a natural measure of the overall diffulty of the problem, or the problem's complexity, might be given by $H = \sum_{i=1}^{K} \Delta_i^{-2}$.
+In particular, it shows that just adding additional arms leads to an increase in complexity (since we need to sample more of them), just as smaller $\Delta_i$ will increase the complexity as arms become harder to classify.
+(WHERE DOES THIS COMPLEXITY ORIGINALLY COME FROM?
+WHAT IS ITs MOTIVATION?
+ITS NOT THAAAT NATURAL)
+
+We also see that this definition may lose relevancy as we move away from $R$-sub-Gaussian distributions.
+(ADD QUICK EXAMPLE OF WHAT CHANGES; REFER TO LATER PART AND DESCRIBE THIS AS THE MOTIVATION OF THE PAPER)
+
+Another characteristic uniquely identifying bandit problems is the regret measure that we aim to optimize.
+As explained during the introduction, multi-armed bandits traditionally optimize cumulative regret.
+The notion of regret considered in the thresholding bandit, however, is more akin to the regret in pure exploration bandits or the error probability in sequential hypothesis testing.
+Indeed, one can most easily describe the regret in the thresholding case as the probability of making a misclassification of any arm.
+Or, more rigorously, let us define the set of all arms with mean larger than the threshold, $\mathcal{S}_\tau = \{i \in \mathcal{A}: \mu_i \geq \tau\}$.
+Consequently, $\mathcal{S}_\tau^C = \{i \in \mathcal{A}: \mu_i < \tau\}$.
+At the end of the sampling rule/procedure (!!we have not mentioned yet the fact that we're in the fixed budget case!!), we demand that any algorithm returns the two corresponding *estimated* sets: $\hat{\mathcal{S}}_{\tau} = \{i \in \mathcal{A}: \hat{\mu}_i \geq \tau\}$, as well as $\hat{\mathcal{S}}_{\tau}^C = \{i \in \mathcal{A}: \hat{\mu}_i < \tau\}$.
+We simply demand an answer to the question which arms have means above the threshold $/tau$, and which arms lie below  $\tau$.
+Let $T$ be the overall number of samples the algorithm is allowed to pull.
+We define the loss as $\mathcal{L}(T) = \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset\}} \cdot \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset\}}$.
+That is, we compare the return set with the true set and collect a loss of 1 if any arm with a true mean outside the $2\epsilon$ interval around $\tau$ was misclassified.
+It is important to realize that arms with means inside the $2 \epsilon$ interval may be misclassified without it affecting the loss.
+These arms are considered close enough to the threshold that we do not care whether they lie above or below.
+
+ADD A GRAPHIC THAT VISUALIZES THE ESTIMATED AND THE REQUIRED RETURN SETS
+
+From there, it is natural to define the expected regret/loss as $\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \land (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset))$.
+This, of course, is the mentioned probability of making a mistake.
+
+ADD REMARK ON WHAT THIS IMPLIES WITH REGARD TO THE MEANS
+
+Lastly, it is to mention that we are considering the fixed-budget version of the thresholding bandit problem.
+We thus fix the number of samples that the algorithm will pull upfront at $T$.
+The task of the algorithm is then to find a sampling rule or strategy which distributes the budget $T$ among the $K$ arms in such a way that the expected regret, or the error probability, is minimized.
+In other terms, the algorithm aims to use the $T$ samples in a way that lets him return the two sets $\hat{\mathcal{S}}_{\tau}$ and $\hat{\mathcal{S}}_{\tau}^C$ with as much confidence as possible.
+This again shows the contrast to the fixed confidence setting in which one fixes the confidence level upfront and lets the algorithm draw as many samples as necessary to reach the required confidence.
+
+At this point, we have defined the fixed budget thresholding bandit setup for any algorithm in the case of sub-Gaussian distributions.
+We thus proceed to describe the algorithm proposed in Locatelli et al.
+(2016).
+
+## The APT Algorithm
+
+In the following we describe the *Anytime Parameter-free Thresholding* (APT) algorithm proposed in Locatelli et al.
+(2016), which is a simple yet effective algorithm and displays some very favorable characteristics when compared with alternative algorithms.
+
+From the general setup, we already know how the algorithm will end.
+After it has drawn $T$ samples, the algorithm makes its decision of which arms to include in the return sets solely on basis of the empirical means $\hat{\mu}_i(T)$ estimated until time $T$.
+Furthermore, the threshold and interval around the threshold were fixed upfront and serve as argument to the algorithm: $(\tau, \epsilon)$.
+For a given arm $i$ and a given time $t$, we let $T_i(t)$ represent the number of samples drawn from arm $i$ until time $t$ (including).
+Consequently, the empirical mean of arm $i$ at time $t$ is given by $\mu_i = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}$ where $X_{i,s}$ is the feedback sampled from distribution $\nu_i$ when the arm is pulled for the $s$-th time.
+
+To be specific, the APT algorithm initiates by pulling each arm once.
+Then, for each $t > K$, it calculates for every arm the values $T_i(t)$ and $\mu_i(t)$.
+Based on the empirical mean, the algorithm computes the estimated gap between the mean and the threshold as $\hat{\Delta}_i(t) = \hat{\Delta}_i^{\tau, \epsilon}(t) = |\mu_i(t) - \tau| + \epsilon$.
+The decision of which arm is sampled next is then based on the value $B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t)$: the algorithm pulls arm $I_{t+1} = \arg \min_{i\leq K} B_i(t+1)$ minimizing this decision quantity.
+After $T$ pulls overall, the arm returns the sets described in the general setup, $\hat{\mathcal{S}}_{\tau}$ and $\hat{\mathcal{S}}^C_{\tau}$.
+
+**Remark**: Obviously, the APT algorithm tends to pull arms more often with corresponding mean close to the threshold and interval (small $\hat{\Delta}_i(t))$.
+This makes sure that more evidence is gathered on arms which appear to be inherently difficult to classify based on the samples collected until time $T_i(t)$, as these arms stifle the confidence the most.
+That is, until we have collected enough evidence to make a confident classification even if the mean is truly close to the threshold.
+In that case, $\sqrt{T_i(t)}$ will raise $B_i(t+1)$.
+Consequently, other arms farther away from the threshold will be sampled again.
+In this way, the algorithm tries to distribute the budget $T$ over all arms so as to define a sampling rule optimizing the confidence of the final decision.
+Of course, that's just Glivenko-Cantelli and the CLT making sure $B_i(t+1)$ is not degenerate.
+
+## Discussion
+
+One of the APT algorithm's main features is its simplicity.
+The sampling rule is very straightforward, and, as highlighted in Locatelli et al.
+(2016), it does not require any knowledge about the type of sub-Gaussianity $R$, or the complexity $H$ upfront.
+This makes the algorithm immediately applicable in practice while it still enjoys its upper bound on the expected regret.
+This is in particular worth highlighting when comparing APT to algorithms used in the pure exploration bandit setting.
+There, many algorithms require knowledge about the corresponding complexity upfront.
+The problem however being, that to know the complexity, the experimenter has to know all means up to a permutation of the arms (for example, see Audibert et al., 2010).
+This, of course, is not given in practice and thus alternative algorithms try to estimate the complexity online which is not a desirable solution either as especially in the beginning plug-in estimates based on the estimated means may lead to wrong estimates of the complexity and consequently budget allocation based on mistaken beliefs (compare Garivier and Kaufmann, 2016).
+
+Furthermore, Locatelli et al. (2016) were able to present an upper bound for the APT algorithm matching the lower bound in their Theorem 1. Proofs of both bounds are given below.
+
+Where the APT algorithm shows room for improvement is when it comes to settings with distributions that are not sub-Gaussian.
+This is mentioned in Locatelli et al.
+(2016).
+In general, the problem becomes that the assumptions for the bounds no longer hold; furthermore, the statistic $B_i(t+1)$, and the term $\hat{\Delta_i}(t)$ are motivated by (sub-)Gaussian distributions.
+The more one moves away from Gaussian-like distributions, the less appropriate this term becomes, however.
+In particular, the empirical mean will be less concentrated around the true mean and more impacted by outliers which are more likely under non sub-Gaussian distributions.
+Locatelli et al.
+(2016) thus refers to Bubeck et al.
+(2013) which considers solutions for multi-armed bandits that are based on heavy-tail distributions.
+By using more robust estimators of the mean, one could equip the APT algorithm to deal with such distributions.
+
+Another step towards dealing with non sub-Gaussianity is made by Mukherjee et al.
+(2017) who use an estimate of the variance additionally to the empirical mean in their Augmented UCB solution.
+Utilizing this additional information, the algorithm seems to perform better than for example APT, going from simulation results displayed in the paper.
+We will continue to discuss the Augmented UCB solution further in chapter 3.
+
+Yet another idea, again mentioned in Locatelli et al.
+(2016) is to show bounds based on the Kullback-Leibler divergence of the specific distribution directly.
+While the approximation through the Gaussian Kullback-Leibler divergence in the lower bound proof is convenient and leads to the simple APT algorithm, it might not stay appropriate for distributions whose Kullback-Leibler divergence tends to differ from the Gaussian.
+This, for example, is the case for Bernoulli distributions at very small parameters $\mu$.
+It's quite obvious simply by looking at examples that the Kullback-Leibler divergence of Bernoullis starts to lose any similarity to the plain quadratic approximation.
+The second graph then shows, that the actual Kullback-Leibler divergence of Bernoullis also has lost any symmetry over this range of parameter values.
+Given that Bernoulli distributions with very small parameter values arise naturally in many applications in website optimization and advertising click-through modeling, there is a need to tackle this problem.
+
+Refer also to page 6 in Kaufmann et al. (2016): "This information-theoretic lower bound permits to interpret the quantity $H(\nu)$ defined in (2) as a subgaussian approximation".
+
+And so a potential approach can be to use the Kullback-Leibler divergence as measure similar to the methods proposed in Kaufmann et al.
+(2015).
+They proposed Kullback-Leibler based approaches for the pure exploration bandit setting, which we will describe in chapter 2.
+Then, in chapter 3, we will come back to the problem of using the Kullback-Leibler divergence in the thresholding bandit setting.
+
+```{r, echo = FALSE}
+KL_ber <- function(p,q) p*log(p/q) + (1-p)*log((1-p)/(1-q))
+par(mfcol = c(1,2))
+
+plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1), type = "n", asp = 1,
+     xlab = "p_1", ylab = "KL(Ber(p_1),Ber(p_2))", main = "KL of Bernoullis")
+for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
+  lines(seq(0.00001,0.3, by = 0.000005),
+       KL_ber(seq(0.00001,0.3, by = 0.000005),i))
+}
+
+plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1.5), type = "n", asp = 1,
+     xlab = "p_1", ylab = "(p_1 - p_2)^2", main = "Gaussian approx.\n KL of Bernoullis")
+for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
+  lines(seq(0.00001,0.3, by = 0.000005),
+        (seq(0.00001,0.3, by = 0.000005)-i)^2)
+}
+par(mfcol = c(1,1))
+```
+
+```{r, echo = FALSE}
+KL_ber <- function(p,q) p*log(p/q) + (1-p)*log((1-p)/(1-q))
+par(mfcol = c(1,2))
+
+plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1), type = "n", asp = 1,
+     xlab = "p_1", ylab = "KL(Ber(p_2),Ber(p_1))", main = "KL of Bernoullis")
+for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
+  lines(seq(0.00001,0.3, by = 0.000005),
+        KL_ber(i,seq(0.00001,0.3, by = 0.000005)))
+}
+
+plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1.5), type = "n", asp = 1,
+     xlab = "p_1", ylab = "(p_2 - p_1)^2", main = "Gaussian approx.\n KL of Bernoullis")
+for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
+  lines(seq(0.00001,0.3, by = 0.000005),
+        (i-seq(0.00001,0.3, by = 0.000005))^2)
+}
+par(mfcol = c(1,1))
+```
+
+## Lower Bound: Theorem and Proof
+
+\begin{theorem}[Theorem 1, Locatelli et al., 2016] 
+\label{theorem:Locatelli2016Theorem1}
+For any sequence of gaps $(d_k)_k$, define a finite set of problems with Gaussian distributions with means corresponding to the gaps, and with variance 1.
+Lower bound the largest probability of error among these problems for the best possible algorithm as follows.
+Let $K,T \geq 0$.
+Let for any $i \leq K$, $d_i \geq 0$.
+Let $\tau \in \mathbb{R}, \epsilon > 0$.
+
+For $0 \leq i \leq K$, we write $\mathcal{B}^i$ for the problem where the distribution of arm $j \in \{1, \dots, K\}$ is $\mathcal{N}(\tau+d_i+\epsilon, 1)$ if $i \neq j$ and $\mathcal{N}(\tau-d_i-\epsilon, 1)$ otherwise.
+For all these problems, $H := H_{\tau, \epsilon} = \sum_i (d_i+2\epsilon)^{-2}$ is the same by definition.
+
+It holds that for any bandit algorithm,
+
+\begin{equation*}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) \geq \exp(-3T/H-4 \log(12(\log(T)+1)K)),
+\end{equation*}
+
+where $\mathbb{E}_{\mathcal{B}^i}$ is the expectation according to the samples of problem $\mathcal{B}^i$.
+\end{theorem}
+
+*Proof of Theorem \ref{theorem:Locatelli2016Theorem1}*: In Theorem 1 of Locatelli et al.
+(2016), a lower bound for the thresholding bandit problem is shown.
+The basic idea is as follows.
+The problem formulation considered in the paper describes bandit problems for sub-Gaussian distributions.
+To show a lower bound, we show that every algorithm is expected to make a certain error even if we restrict ourselves to a very restricted scenario.
+Even then, any algorithm will have a certain level of risk with which it cannot distinguish between the actual setting and slightly changed settings (under which the former answer leads to regret).
+
+To be more specific, consider a case in which we set $\tau = 0$ and $\epsilon = 0$ w.l.o.g.
+If we then choose all arms to have normally distributed feedback with means $\mu_i$, we see that for each arm $i$ the distance from the threshold is given by $\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i$.
+Thus, assuming a variance of 1 for every arm, we have for every arm the distribution $\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)$.
+Furthermore, define for each arm $i \in \{1, \dots, K\}$ the alternative distribution $\nu_i' = \mathcal{N}(-\Delta_i,1)$.
+It is easy to see that in this case, this is equivalent to a "flip around the threshold".
+Arms that originally have a mean larger than the threshold have a mean smaller than the threshold after the flip.
+
+The idea now is that every arm $i \in \{1,\dots,K\}$ generates a sample for every time point $t\in \{1, \dots, T\}$ from its distribution $\nu_i$ before the algorithm starts to choose arms.
+Thus, we have a $T \times K$ table of realized observations from the product distribution given by $\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K$.
+This is a product distribution where the $K$ different means all lie above the threshold.
+We would hope that an algorithm classifies the means accordingly.
+However, we will show in what follows that any algorithm makes a certain error by not being able to distinguish $\mathcal{B}^0$ from at least one of $K$ alternative product distributions $\mathcal{B}^i, i \in \{1, \dots, K\}$, of which each differs only slightly in one arm from the original distribution, and has the same overall complexity (as defined by $H = \sum_{i=1}^K (\Delta_i)^{-2}$).
+We require $K$ different distributions so that an arm sampling arm $i$ very often for some reason will not have a smaller lower bound by chance.
+
+For each of the $K$ arms, we introduce an alternative model of the following kind.
+Before the start of the algorithm, we introduce a slight variation in the setup.
+The idea is similar to how one can switch arms in the pure exploration setup for multi-armed bandits (compare Audibert et al., 2010; Garivier & Kaufmann, 2016) to "confuse" any algorithm without introducing additional complexity to the specified problem.
+However, since we do not compare arms directly with each other in the thresholding bandit problem (switching arms would still keep all means above the threshold), we instead need to flip an arm $i$ with respect to the threshold in order to get the alternative model $\mathcal{B}_i$.
+Since the threshold is $\tau = 0$, we have for the flipped arm the new distribution $\nu_i'$ as defined above.
+Indeed, we can define the new product distribution $B^i = \nu_1^i \otimes \dots \otimes \nu_K^i$ where for $k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}$.
+This flipping of the arm corresponds to multiplying all random variables $X_{i,t}$ of arm $i$ by $-1$.
+
+As in Locatelli et al.
+(2016), we let for $i \leq K$, $\mathbb{P}_{\mathcal{B}^i}$ define the probability distribution describing all samples that a bandit strategy can potentially collect up to horizon $T$, i.e.
+according to the samples $(X_{k,s})_{k\leq K, s \leq T} \sim (\mathcal{B}^i)^{\otimes T}$.
+$(T_k)_{k\leq K}$ denotes the number of samples collected on arm $k$ until time $T$.
+
+#### Reminder about the goal of the proof
+
+At this point, we have defined a finite set of problems of Gaussian distributions with fixed variance 1 for a given set of set of gaps between the means of the distributions and the threshold, $(d_k)_k$.
+We will now proof a lower bound on the worst case regret of any algorithm; that is, the maximum error probability that even the best algorithm makes on this problem.
+
+#### Statistical Decision
+
+Given our formulation of the regret, the expected regret $\mathbb{E}[\mathcal{L}(T)]$ corresponds directly to the probability of making a wrong classification of any of the $K$ means.
+In general, let $g$ be a binary decision function, and define $\Omega = \{g = 0\}$ and $\Omega^C = \{g = 1\}$.
+Assume that the decision $T$ distinguishes between two states of the world, $H_0$ and $H_1$.
+Then our overall error probability is given by $P_{H_0}(g=1) + P_{H_1}(g = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)$.
+
+In our case, $H_0$ may correspond to the state in which we have $\mathcal{B}^0$, and $H_1$ corresponds to the case where any arm has been flipped, $\mathcal{B}^i$.
+Furthermore, we consider the events in which the algorithm, making the decision, classifies arm $i$ as being above the threshold: $\mathcal{A}_i = \{i \in \hat{S}_\tau\}$.
+The event on which all arms are being classified as above the threshold is consequently given by $\mathcal{A} = \bigcap \mathcal{A}_i$.
+However, Theorem 1 does not bound the overall regret, but the maximum error probability on the $K+1$ different models.
+We can write this now as
+
+\begin{align}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big) \\
+& = \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
+\end{align}
+
+In order to give a bound on above equation, we start by considering $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$.
+This probability can be written as the expected change in the likelihood of observed data when moving from distribution $P_{\mathcal{B}_0}$ to $P_{\mathcal{B}_i}$, times the probability under the original state.
+In other words, the probability of event $\mathcal{A}_i$ under state $\mathcal{B}^i$ is given as the probability of $\mathcal{A}_i$ under the (original) state $\mathcal{B}^0$ multiplied by a factor.
+This factor describes whether the new distribution increases or decreases the probability of the event, and is given by the change in the data likelihoods due to moving from $\mathcal{B}^0$ to $\mathcal{B}^i$, expressed as the expected likelihood ratio under $\mathcal{B}^0$.
+By definition, the latter is equal to the empirical Kullback-Leibler divergence of the two distributions.
+
+We will define the change of distribution in terms of the empirical log-likelihood for our case.
+Then, we will show how to replace the log-likelihood by the empirical Kullback-Leibler divergence.
+So let us first introduce the empirical Kullback-Leibler divergence.
+
+Let every $\nu_i, \nu_i'$ be dominated by the Lebesgue measure $\lambda$.
+Then their density functions are given by $f_i = \frac{\der \nu_i}{\der \lambda}$ and $f_i' = \frac{\der \nu_i'}{\der \lambda}$ respectively.
+For $T \geq t \geq 0$, define the empirical Kullback-Leibler divergence as
+
+\begin{align*}
+\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log(\frac{\der \nu_k'}{\der \nu_k}(X_{k,s})) \\
+& = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
+& = \frac{1}{t} \log \big( \prod_{s=1}^{t} \frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
+& \stackrel{\text{iid}}{=} \frac{1}{t} \log \big( \frac{f_k'(X_{k,1}, \dots,X_{k,t})}{f_k(X_{k,1}, \dots,X_{k,t})} \big) \\
+& = \frac{1}{t} \log \big( \text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k) \big)
+\end{align*}
+
+Since we consider Gaussian distributions with variance 1, we have density functions $f_i(x) \propto \exp \big(-\frac{1}{2} (x-\Delta_i)^2\big)$ and $f_i'(x) \propto \exp \big(-\frac{1}{2} (x+\Delta_i)^2\big)$.
+Plugging this into the above definition of the empirical Kullback-Leibler divergence, we easily see
+
+\begin{align*}
+\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{\exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2\big)}{\exp \big(-\frac{1}{2} (X_{k,s}-\Delta_k)^2\big)} \big) \\
+& = \frac{1}{t} \sum_{s=1}^{t} \log \big( \exp(-\frac{1}{2} (X_{k,s}+\Delta_k)^2 + \frac{1}{2} (X_{k,s}-\Delta_k)^2) \big) \\
+& = - \frac{1}{t} \sum_{s=1}^{t} 2 X_{k,s} \Delta_k
+\end{align*}
+
+#### Change of Distribution
+
+We are now ready to state the change of distribution.
+As alluded to above, we consider how the probability changes for the event $\mathcal{A}_i$ when we move from $\mathcal{B}^0$ to $\mathcal{B}^i$.
+When flipping arm $i$, we only changed the samples of this arm, that is, the first $T_i$ observations we got from arm $i$ the algorithm took.
+The change of distribution is then defined as:
+
+\begin{align*}
+\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \text{LR}((X_{i,1}, \dots,X_{i,T_i}), \nu_i', \nu_i) ] \\
+& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ]
+\end{align*}
+
+Obviously, $\hat{\KL}_{i,T_i}$ depends on the realized samples $X_{i,1}, \dots,X_{i,T_i}$.
+Consequently, we need to find a bound on $\hat{\KL}_{i,T_i}$ itself to incorporate the uncertainty involved in this metric.
+
+#### Concentration of the Empirical Kullback-Leibler Divergence
+
+For our problem, the Kullback-Leibler divergence of $\nu_k'$ from $\nu_k$ is given by $\KL_k := KL(\nu_k', \nu_k) = 2\Delta_k^2$.
+
+It is easy to see that
+
+\begin{equation*}
+|\hat{\KL}_{k,t} - \KL_{k,t}| = |-\frac{2}{t} \Delta_k \sum_{s=1}^{t}(X_{k,s} - \Delta_k)|
+\end{equation*}
+
+itself is a normally distributed random variable with mean zero and a variance decreasing in $t$.
+Thus, one can show as in Locatelli et al.
+(2016) that $\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4$ for the event
+
+\begin{equation}
+\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}}\}. \label{LocatelliTheorem1EventXi}
+\end{equation}
+
+Thus, in order to bound the empirical Kullback-Leibler divergence in our change of measure, we can consider the intersection of $\mathcal{A}_i$ and $\xi$ as follows and plug in the bound on event $\xi$:
+
+\begin{align*}
+\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
+& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
+& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
+\end{align*}
+
+Two things are left to do: With $T_i$, we still have one random variable left which we cannot leave in our bound.
+Second, we are actually not interested in $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$ but in $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$.
+
+#### Bounding $T_i$ for $\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$
+
+Part of our bound is $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$, so let's continue with that.
+In general it holds that $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K}\sum_{i=1}^K X_i$.
+Thus we can write:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
+& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
+& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
+\end{align*}
+
+where the second line is again the intersection of $\mathcal{A}_i$ and $\xi$ as before in order to apply the change of distribution in the third line.
+
+What is left to show before we have our final bound is a bound on $T_i$.
+To show that any algorithm has a certain bound on its error, it only makes sense that every arm has to pulled at least a certain amount of times.
+Consequently, no arm should be pulled exclusively.
+
+First, let $a = \Delta_i \sqrt{T_i}$ and $b = 4\sqrt{\log((4\log(T)+1)K)}$. Then use $ab \leq a^2 + b^2$ to write $ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)$. And so:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) ]
+\end{align*}
+
+Furthermore, we know that the sum of the individual arm pulls has to be equal to the overall number of pulls (equal to the budget in the fixed budget sense), $\sum_i T_i = T$, and furthermore we know that $T_i>0$.
+The latter holds since any reasonable algorithm has to check each arm at least once in our setup.
+This is because we need to check each arm's performance in comparison to the threshold.
+Thus it is easy to show that $\exists i: T_i \leq \frac{T}{H \Delta_i^2} = \frac{T}{(\sum_{i=1}^{K} \Delta_i^{-2}) \Delta_i^2}$.
+To see this, assume the opposite: $\forall i: T_i > T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2}$.
+This implies however $\sum_{i=1}^K T_i > \sum_{i=1}^K T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2} = T \cdot 1 = T$ which is a contradiction.
+
+So we can write $(\Delta_i \sqrt{T_i})^2 \leq \frac{T}{H}$. We use $\mathcal{A} = \cap_{i=1}^K \mathcal{A}_i$ to write:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big] \\
+& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}{K} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big]
+\end{align*}
+
+We write $\frac{1}{K} \sum_{i=1}^K \exp(-3T_i \Delta_i^2) \geq \frac{1}{K} \sum_{i=1}^K \exp(-3 T/H) = \exp(-3 T/H)$. Thus:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i) \exp(-16 \log(4(\log(T)+1)K)) ] \\
+& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
+& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
+& = \mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
+\end{align*}
+
+#### Bringing everything together
+
+Consider again the risk which we need to bound from equation \eqref{LocatelliTheorem1ExpRegret}.
+We bound the maximum expected loss over all $\mathcal{B}_i$.
+By again using the fact that in general $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K} \sum_{i = 1}^K X_i$, we plug in our previous calculations:
+
+\begin{align}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
+& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \label{LocatelliTheorem1DefinitionOfRisk}
+\end{align}
+
+From \eqref{LocatelliTheorem1EventXi} we know that for any $i \in \{0, \dots, K\}$, $\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4$.
+Following the argument in Locatelli et al.
+(2016), we now consider two cases: $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2$ and $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2$.
+In the former case, we can plug in the two probabilities into \eqref{LocatelliTheorem1DefinitionOfRisk}.
+If $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2$ and $\mathbb{P}_{\mathcal{B}^0}(\xi) \geq 3/4$, then $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \geq 1/4$.
+Thus:
+
+\begin{align*}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
+& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \\
+& \geq \frac{1}{8} \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
+\end{align*}
+
+where we drop the second summand of the second line so that the inequality holds.
+
+On the other hand, when $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2$, then we know that $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \leq 1/2$ for any $\mathbb{P}_{\mathcal{B}^0}(\xi)$.
+At the same time $1-\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \geq 1/2$.
+Consequently, $1/4 \leq \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \leq 1/2$, while
+$\frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) \geq 0$.
+And so the stronger lower bound in that case is, as noticed by Locatelli et al.
+(2016), given simply by
+
+\begin{align*}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
+& \geq 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \\
+& \geq \frac{1}{2}
+\end{align*}
+
+## Upper Bound: Theorem and Proof
+
+\begin{theorem}[Locatelli et al., 2016] \label{theorem:LocatelliTheorem4}
+Let $K \geq 0$, $T \geq 2K$, and consider a problem $\mathbb{B}$. Assume that
+all arms $\nu_k$ of the problem are R-sub-Gaussian with means $\mu_k$. Let $\tau
+\in \mathbb{R}, \epsilon \geq 0$.
+
+Algorithm APT's expected loss is upper bounded on this problem as 
+\begin{equation*} \mathbb{E}(\mathcal{L}(T)) \leq \exp
+(-\frac{1}{64R^2}\frac{T}{H} + 2 \log (T) + 1)K)) \end{equation*}
+
+where we remind that $H = \sum_i (|\mu_i - \tau | + \epsilon)^{-2}$ and where
+$\mathbb{E}$ is the expectation according to the samples of the problem.
+\end{theorem}
+
+*Proof of Theorem \ref{theorem:LocatelliTheorem4}:* To prove above theorem, we first define a favorable event $\xi$ on which we hope
+to make a loss with only a small probability. Indeed, it is the event for which
+we want to upper bound the expected loss. As we want to find an upper bound for
+the expected loss of the APT algorithm, the event corresponds to the decision
+made by it.
+Given that the APT algorithm's sampling rule and final decision is based on the empirical mean of each arm, it will have low expected regret, if it finds empirical mean estimates $\hat{\mu}_i(t) = \frac{1}{s} \sum_{t=1}^s X_{i,t}$
+that are close to the true means $\mu_i$ of the arms. Then, we would
+expect arms with $\hat{\mu}_i(T) > \tau + \epsilon$ to be classified correctly, and
+arms with $\hat{\mu}_i(T) < \tau - \epsilon$ to be rejected.
+
+Indeed, we have $\mathbb{E}(\mathcal{L}(T)) = P(S_{\tau + \epsilon} \cap
+\hat{S}_\tau^C \neq \emptyset \lor S_{\tau-\epsilon}^C \cap \hat{S}_{\tau} \neq
+\emptyset)$. But this just corresponds to $P(\{\exists i: ((\mu_i <
+\tau-\epsilon) \land(\hat{\mu}_i \geq \tau)) \lor ((\mu_i > \tau + \epsilon)
+\land (\hat{\mu}_i < \tau)))$. Each of the two $(...)\lor(...)$ conditions
+corresponds to $| \hat{\mu}_i - \mu_i | \geq \epsilon$. It follows that the
+expected loss can be rewritten as: $\mathbb{E}(\mathcal{L}(T)) = P(\exists i,
+\exists s: |\hat{\mu}_{i,s} - \mu_i | \geq \epsilon) = P(\xi^C)$. This is
+exactly the probability of classifying at least one arm incorrectly which
+results in a loss of size 1.
+
+Thus we define as the favorable event as:
+
+\begin{equation} 
+\xi = \{\forall i, \forall s: | \hat{\mu}_{i,s} - \mu_i | \leq
+\epsilon\} 
+\end{equation}
+
+Furthermore, if we write $\xi_{i,s} = \{ |\hat{\mu}_{i,s}-\mu_i | \leq \epsilon
+\}$, then the following holds by a union bound.
+
+\begin{equation} 
+P(\xi) = P(\cap_i \cap_s \xi_{i,s}) = 1 - P(\cup_i \cup_s
+\xi_{i,s}^C) \geq 1 - \sum_i \sum_s P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon)
+\label{theorem2_prob_fav_event} 
+\end{equation}
+
+Furthermore, for any $i \in \{1, \dots, K\}$, for any $s \in \{1, \dots,
+T(i)\}$, with $X_{it}$ being the random sample from the R-sub-Gaussian
+distribution $v_i$ at time $t$:
+
+\begin{equation} 
+P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon) = P(| (\frac{1}{s}
+\sum_{t=1}^{s} X_{it} - \mu_i) | \geq \epsilon) = P(| \sum_{t=1}^{s} (X_{it} -
+\mu_i) | \geq s \epsilon) 
+\end{equation}
+
+where the latter can be bounded by a Hoeffding inequality:
+
+\begin{equation} 
+P(| \sum_{t=1}^{s} (X_{it} - \mu_i) | \geq s \epsilon) \leq
+2\exp (-\frac{\epsilon^2 s}{2 R^2}) \label{theorem2_hoeffding} 
+\end{equation}
+
+The Hoeffding inequality as used here is as follows:
+
+\begin{lemma}[Hoeffding's Inequality] \label{lemma:HoeffdingInequality}
+Consider $X_1, \dots, X_T$ independent random variables from R-sub-Gaussian distributions $\nu_i$ with mean $\mu_i$. Then, for any $\epsilon > 0$,
+
+\begin{equation*}
+\mathbb{P} \Big( | \sum_{i = 1}^T (X_i - \mu_i) | \geq \epsilon \Big) \leq 2\exp \Big(\frac{-\epsilon^2}{2T R^2}\Big).
+\end{equation*}
+\end{lemma}
+
+Plugging equation \eqref{theorem2_hoeffding} back into equation \eqref{theorem2_prob_fav_event},
+we get:
+\begin{equation}
+P(\xi) \geq 1 - \sum_i \sum_s P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon) \geq 1 - 2 \sum_i \sum_s \exp (-\frac{\epsilon^2 s}{2 R^2})
+\end{equation}
+
+Now, in order to match the performance of the lower bound on the expected loss derived in Theorem \ref{theorem:Locatelli2016Theorem1}, we will choose $\epsilon = \sqrt{\frac{T \delta^2}{Hs}}$. Thus:
+
+\begin{equation}
+P(\xi) \geq 1 - 2 \sum_i \sum_s \exp (-\frac{\epsilon^2 s}{2 R^2}) = 1 - 2 \sum_i \sum_s \exp (-\frac{T \delta^2}{2 R^2 H}) \geq 1 - TK \exp(-\frac{T\delta^2}{2R^2H})
+\end{equation}
+
+Thus, we do not exactly get the bound from Locatelli et al. (2016) because we used the Hoeffding inequality instead of the martingale bound; but the the method should be clear.
+
+What is left now is to show that the favorable event still holds under the proposed $\epsilon$, that is, we need to show that under $P(\xi) \geq 1 - TK \exp(-\frac{T\delta^2}{2R^2H})$ we still reject arms that are under $\tau - \epsilon$ and accept those above $\tau + \epsilon$.
+
+#### Step 2: Lower Bound on Number of Pulls of Difficult Arm
+
+In order to see that arms are correctly classified with large probability, we need to show that they are are pulled sufficiently often, that is, we have a degree of exploration for each arm $i$ that allows us to identify its characteristics.
+To see this, rewrite the favorable event of a single arm as follows with $s = T(i)$:
+
+\begin{equation}
+\xi_{i,s} = \{ |\hat{\mu}_{i,s}-\mu_i | \leq \epsilon \} = \{ |\hat{\mu}_{i,s} - \mu_i | \leq \sqrt{\frac{T \delta^2}{H T(i)}}\}
+\end{equation}
+
+To make sure that this deviation is small enough, we need to show that at time $T$, all $T(i)$ have a sufficient lower bound and thus all arms $i$ have been explored sufficiently to classify correctly with probability larger $TK \exp(-\frac{T\delta^2}{2R^2H})$.
+
+To start off, notice that due to the initialization of the APT algorithm, every $T_i(T) \geq 1$.
+Furthermore, we have assumed that $T>2K$.
+Now, at time $T$, consider an arm $k$ that has been pulled $T_k(T) -1 \geq \frac{(T-K)}{H \Delta^2_k}$ times.
+That is, it has been pulled at least proportionally to it's contribution to the overall hardness of the problem $H$.
+Recall $H = \sum_{i=1}^K(|\mu_i - \tau|+\epsilon)^-2$ and $\delta^2_i = (|\mu_i - \tau | + \epsilon)^2$.
+To see that such arm $k$ exists, assume it does not.
+Then
+
+\begin{equation*}
+T_i(T) - 1 < \frac{T-K}{H \Delta_i^2} \forall i
+\end{equation*}
+\begin{equation*}
+T- K = \sum_{i=1}^{K} T_i(T) - 1 < \sum_{i=1}^{K} \frac{T-K}{H \Delta_i^2} = \frac{T-K}{H \Delta_i^2} \sum_{i=1}^{K} \frac{1}{\Delta_i^2} = T-K
+\end{equation*}
+
+which is a contradiction.
+
+Consequently, using the assumption $T>2K$ from above, we have
+
+\begin{equation*}
+T_k(T) \geq T_k(T) - 1 \geq \frac{T-K}{H \Delta^2_k} = \frac{T}{2H\Delta_k^2}
+\end{equation*}
+
+This states a lower bound on the amount of pulls $T_k(t)$ for an arm $k$ that contributes more than average to the overall hardness of the problem.
+
+#### Step 3: Lower Bound on Number of Pulls of Simple Arm
+
+Next, we would like to derive bounds on the number of pulls of the remaining arms $i$ at the time $t$, the last pull of arm $k$.
+To do so, consider that we are on the favorable event $\xi$.
+For every arm $i$, it holds:
+
+\begin{equation}
+|\hat{\mu}_i(t) - \mu_i | \leq \sqrt{\frac{T \delta^2}{HT_i(t)}} \label{step3_favorable_event} 
+\end{equation}
+
+As described in Locatelli et al., using the reverse triangle inequality, we can write
+
+\begin{IEEEeqnarray*}{rCl}
+|\hat{\mu}_i(t) - \mu_i | & = & | (\hat{\mu}_i(t) - \tau) - (\mu_i-\tau) |
+\\
+& \geq & | |\hat{\mu}_i(t) - \tau| - |\mu_i-\tau| |
+\\
+& = & | (|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i-\tau| - \epsilon) |
+\\
+& = & | \hat{\Delta}_i(t) - \Delta_i |
+\end{IEEEeqnarray*}
+
+Consequently, we can again employ the hardness of the task to start deriving bounds on the number of pulls of the arms:
+
+\begin{equation*}
+| \hat{\Delta}_i(t) - \Delta_i | \leq |\hat{\mu}_i(t) - \mu_i | \sqrt{\frac{T \delta^2}{HT_i(t)}}
+\end{equation*}
+
+From this, we get
+
+\begin{IEEEeqnarray*}{rlCrl}
+\Delta_i - \sqrt{\frac{T \delta^2}{HT_i(t)}} & \leq & \hat{\Delta}_i(t) & \leq & \Delta_i + \sqrt{\frac{T \delta^2}{HT_i(t)}}
+\end{IEEEeqnarray*}
+
+and in particular for the arm $k$ discussed above
+
+\begin{IEEEeqnarray}{rlCrl}
+\Delta_k - \sqrt{\frac{T \delta^2}{HT_k(t)}} & \leq & \hat{\Delta}_k(t) & \leq & \Delta_k + \sqrt{\frac{T \delta^2}{HT_k(t)}} \label{delta_hat_k_bounds}
+\end{IEEEeqnarray}
+
+To bound $T_i(t)$, it is helpful to compare $\Delta_i$ and $\Delta_k$ at time $t$.
+From the definition of the APT algorithm, we know that since arm $k$ has been pulled at time $t$ ("Pull arm $I_{t+1} = \arg \min_i \mathcal{B}_i (t+1)$"):
+
+\begin{IEEEeqnarray*}{rCl}
+\mathcal{B}_k(t) & \leq & \mathcal{B}_i(t)
+\\
+\sqrt{T_k(t)} \hat{\Delta}_k(t) & \leq & \sqrt{T_i(t)} \hat{\Delta}_i(t)
+\end{IEEEeqnarray*}
+
+Thus, every arm $i$ has a lower bound on it's number of pulls given by the lower bound for arm $k$ proportional with it's inverse relative estimated hardness $\hat{\Delta}_k(t) / \hat{\Delta}_i(t)$.
+We can easily derive a lower bound for the left hand side by plugging in \eqref{delta_hat_k_bounds}:
+
+\begin{IEEEeqnarray}{rCl}
+\sqrt{T_k(t)} (\Delta_k - \sqrt{\frac{T \delta^2}{HT_k(t)}}) & \leq & \mathcal{B}_k(t) 
+\\
+\sqrt{\frac{T}{2H\Delta_k^2}} (\Delta_k - \sqrt{2}\Delta_k \delta) & = & \sqrt{\frac{T}{H}} (\frac{1}{\sqrt{2}} - \delta)
+\\
+& \leq & \mathcal{B}_k(t)
+\end{IEEEeqnarray}
+
+since $T_k(t) \geq T/(2H\Delta^2_k)$ and $\sqrt{T \delta^2 / (HT_k(t))} \geq \sqrt{T \delta^2 / (H\frac{T}{2H \Delta^2_k})} = \sqrt{2}\Delta_k \delta$.
+
+Next, upper bound $\mathcal{B}_i(t)$. In contrast to $T_k(t)$, there is no lower bound for $T_i(t)$ available yet that we could plug in. Thus we derive:
+
+\begin{IEEEeqnarray*}{rCl}
+\mathcal{B}_i(t) & = & \sqrt{T_i(t)} \hat{\Delta}_i(t) 
+\\
+& \leq & \sqrt{T_i(t)} (\Delta_i + \sqrt{\frac{T \delta^2}{H T_i(t)}})
+\\
+& = & \sqrt{T_i(t)} \Delta_i + \delta \sqrt{\frac{T}{H}}
+\end{IEEEeqnarray*}
+
+Combining the two bounds, we get a lower bound on the pulls for every other arm $i$:
+
+\begin{IEEEeqnarray*}{rCl}
+\Delta_i \sqrt{T_i(t)} + \delta \sqrt{\frac{T}{H}} & \geq & (\frac{1}{\sqrt{2}} - \delta) \sqrt{\frac{T}{H}}
+\\
+\sqrt{T_i(t)} & \geq & (\frac{1}{\sqrt{2}} - 2\delta) \sqrt{\frac{T}{H}} \frac{1}{\Delta_i}
+\\ 
+& & \text{(choose $2\delta > 1 / \sqrt{2}$ such that RHS is greater 0)}
+% \\
+% T_i(t) & \geq & (\frac{1}{2} - 2\sqrt{2} \delta + 4\delta^2) \underbrace{\frac{T}{H} \frac{1}{\Delta_i^2}}_\text{$i$'s share of the budget}
+% \\
+% T_i(t) & \geq & (1 - 4 \sqrt{2} \delta + 8\delta^2) \frac{T}{2H} \frac{1}{\Delta_i^2}
+\end{IEEEeqnarray*}
+
+#### Conclusion
+
+As stated before, we require the lower bound on $T_i(t)$ in order to show that $|\hat{\mu}_i(t) - \mu_i | \leq \sqrt{frac{T \delta^2}{H T_i(t)}}$ holds for all $i$.
+So if we now simply plug in the derived lower bound, we get:
+
+\begin{equation*}
+\mu_i - \Delta_i (\frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}) \leq \hat{\mu}_i(t) \leq \mu_i + \Delta_i (\frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta})
+\end{equation*}
+
+and with $\lambda := (\frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}) > 0$:
+
+\begin{equation*}
+\mu_i - \Delta_i \lambda \leq \hat{\mu}_i(t) \leq \mu_i + \Delta_i \lambda
+\end{equation*}
+
+Under this formulation on $\xi$, do we accept arms with $\mu_i \geq \tau + \epsilon$? For these arms holds that $\Delta_i = \mu_i - \tau + \epsilon$. Consequently:
+
+\begin{IEEEeqnarray*}{rCl}
+\mu_i - (\mu_i - \tau + \epsilon) \lambda & \leq & \hat{\mu}_i(t) 
+\\ 
+\hat{\mu}_i(t) & \geq & \tau \lambda + \mu (1-\lambda) - \epsilon \lambda
+\end{IEEEeqnarray*}
+
+The arms are accepted if
+
+\begin{IEEEeqnarray*}{rCl}
+\hat{\mu}_i(t) - \epsilon & \geq & 0
+\end{IEEEeqnarray*}
+
+Or equivalently as long as
+
+\begin{IEEEeqnarray*}{rCl}
+\tau \lambda + \mu(1-\lambda) - \epsilon \lambda - \tau & \geq & 0
+\\
+\lambda & \leq & \frac{1}{2}
+\end{IEEEeqnarray*}
+
+\newpage
+
+# Kullback-Leibler Complexity of Pure Exploration
 
@@
 For the current chapter, we will adopt the notation of Kaufmann et al. (2016) so that it will be easier to compare the arguments.
+
+## Complexity of Best-Arm and Top-*m* Identification
 
@@
 
-### Optimal Best Arm Identification
+## Optimal Best Arm Identification
 
@@
 
-### Conclusion of Complexity of Best Arm Identification
+## Conclusion of Complexity of Best Arm Identification
 

### 2017-05-31 Thesis/Draft.tex
Add start of chapter three

--- 2017-05-28 Complexity of Best Arm Identification/kl_complexity.tex
@@
 \hypersetup{unicode=true,
-            pdftitle={On the Complexity of Best Arm Identification},
+            pdftitle={Draft},
             pdfauthor={Tim Radtke},
@@
 \setlength{\droptitle}{-2em}
-  \title{On the Complexity of Best Arm Identification}
+  \title{Draft}
   \pretitle{\vspace{\droptitle}\centering\huge}
@@
   \postdate{\par}
-  \date{5/20/2017}
+  \date{5/28/2017}
 
@@
 \maketitle
+
+{
+\hypersetup{linkcolor=black}
+\setcounter{tocdepth}{3}
+\tableofcontents
+}
+\section{Thresholding Bandit Problem}\label{thresholding-bandit-problem}
+
+The \emph{Thresholding Bandit Problem} described in Locatelli et al.
+(2016) can be considered a variant of a variant. It can be framed into
+the wider literature of \emph{Pure Exploration} multi-armed bandit
+problems. In particular, it shares characteristics with the
+\emph{Top-\(m\)} problem. This problem is concerned with finding the
+\(m\) best arms as described by the means of their corresponding
+distributions. This in turn is similar to the \emph{combinatorial
+bandit} problem, which also aims at finding the \(m\) best arms.
+However, it is able to pull several arms at once: Think of an online
+shop that shows five recommended products on a product detail page.
+These five recommended products might each be represented by an arm, and
+we look for the products with the largest mean conversion rate. The
+thresholding bandit problem we discuss here, however, is concerned with
+pulling a single arm at a time. And so a more appropriate situation is
+that of a website presenting a banner. Again, think of an online shop
+trying to promote a certain category. The content team came up with a
+number of different designs for the banner, and it's not clear how many
+click-throughs they will gather.
+
+The idea now is that we would like to classify the banners into two
+distinct groups: A group with a mean conversion rate \(\mu_i\) below
+threshold \(\tau\), and a group with mean conversion rate \(\mu_i\)
+above threshold \(\tau\). This might be the optimization problem when we
+are concerned with not falling below a certain minimum level
+click-through rate with the banners we're choosing.
+
+If it turns out that in general we can find relatively quickly whether
+arms are above or below a threshold, then this kind of test can be used
+to safeguard against very bad versions in a test. Before we move to a
+Top-\(m\) test, we might want to run a thresholding version and then
+continue only with the arms classified into the group above the
+threshold. This might be justified when adjusting parts of the checkout
+process of an online shop, where the conversion rate or the average
+order value should not drop below a threshold.
+
+\subsection{Setup}\label{setup}
+
+In any case, the problem boils down to the following. As standard in
+multi-armed bandit problems, we have \(K\) arms
+\(\mathcal{A} = \{1, \dots K\}\). We can pull arm \(k\) at time \(t\) to
+collect feedback in form of the random variable \(X_{k,t}\) which is
+distributed accoring to the arm's distribution \(\nu_k\). In general, we
+are concerned with estimating for each arm \(i\) the mean \(\mu_i\) of
+its distribution \(\nu_i\). In contrast to most bandit problems,
+however, we do not directly compare arms with each other by comparing
+their means. In the case of pure exploration bandits, it is for example
+necessary to compare the arms because one aims to find the best one. In
+the case of the thresholding bandit, however, we compare each arm's mean
+\(\mu_i\) individually against the threshold \(\tau \in \mathbb{R}\)
+which is known and fixed before the experiment. One might compare this
+to a pure exploration bandit in which the mean of the best arm is known
+upfront. We will see later that this fact leads to advantages in the
+design of algorithms which are not as readily available in other bandit
+settings.
+
+In Locatelli (2016), the arms' distributions are assumed to follow a
+\(R\)-sub-Gaussian distribution. Under this assumption, the authors are
+able to proof a general lower bound as well as an algorithm with a
+matching upper bound. Both hinge upon the \emph{complexity} of a given
+problem. Since bandit problems can differ in the number of the arms
+\(K\) and the means of each arm, some pose easier identification
+problems than others. Indeed, in the thresholding problem, the
+difficulty of the problem naturally depends on how close (the means of
+the) distributions are to the fixed threshold. Intuitively, the closer a
+mean \(\mu_i\) is to the threshold \(\tau\), the more difficult it will
+be to distinguish the two successfully based on samples from the
+distribution \(\nu_i\). For the case of the sub-Gaussian distributions,
+a natural measure of this distance is given by simply
+\(\Delta_i = |\tau - \mu_i| + \epsilon\), where \(\epsilon\) defines a
+\(2\epsilon\) interval around the threshold \(\tau\) in which we allow
+ourselves to make a mistake at no cost.
+
+If we extend this idea to the set of arms \(i \in \{1,...,K\}\) of a
+given bandit problem, a natural measure of the overall diffulty of the
+problem, or the problem's complexity, might be given by
+\(H = \sum_{i=1}^{K} \Delta_i^{-2}\). In particular, it shows that just
+adding additional arms leads to an increase in complexity (since we need
+to sample more of them), just as smaller \(\Delta_i\) will increase the
+complexity as arms become harder to classify. (WHERE DOES THIS
+COMPLEXITY ORIGINALLY COME FROM? WHAT IS ITs MOTIVATION? ITS NOT THAAAT
+NATURAL)
+
+We also see that this definition may lose relevancy as we move away from
+\(R\)-sub-Gaussian distributions. (ADD QUICK EXAMPLE OF WHAT CHANGES;
+REFER TO LATER PART AND DESCRIBE THIS AS THE MOTIVATION OF THE PAPER)
+
+Another characteristic uniquely identifying bandit problems is the
+regret measure that we aim to optimize. As explained during the
+introduction, multi-armed bandits traditionally optimize cumulative
+regret. The notion of regret considered in the thresholding bandit,
+however, is more akin to the regret in pure exploration bandits or the
+error probability in sequential hypothesis testing. Indeed, one can most
+easily describe the regret in the thresholding case as the probability
+of making a misclassification of any arm. Or, more rigorously, let us
+define the set of all arms with mean larger than the threshold,
+\(\mathcal{S}_\tau = \{i \in \mathcal{A}: \mu_i \geq \tau\}\).
+Consequently,
+\(\mathcal{S}_\tau^C = \{i \in \mathcal{A}: \mu_i < \tau\}\). At the end
+of the sampling rule/procedure (!!we have not mentioned yet the fact
+that we're in the fixed budget case!!), we demand that any algorithm
+returns the two corresponding \emph{estimated} sets:
+\(\hat{\mathcal{S}}_{\tau} = \{i \in \mathcal{A}: \hat{\mu}_i \geq \tau\}\),
+as well as
+\(\hat{\mathcal{S}}_{\tau}^C = \{i \in \mathcal{A}: \hat{\mu}_i < \tau\}\).
+We simply demand an answer to the question which arms have means above
+the threshold \(/tau\), and which arms lie below \(\tau\). Let \(T\) be
+the overall number of samples the algorithm is allowed to pull. We
+define the loss as
+\(\mathcal{L}(T) = \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset\}} \cdot \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset\}}\).
+That is, we compare the return set with the true set and collect a loss
+of 1 if any arm with a true mean outside the \(2\epsilon\) interval
+around \(\tau\) was misclassified. It is important to realize that arms
+with means inside the \(2 \epsilon\) interval may be misclassified
+without it affecting the loss. These arms are considered close enough to
+the threshold that we do not care whether they lie above or below.
+
+ADD A GRAPHIC THAT VISUALIZES THE ESTIMATED AND THE REQUIRED RETURN SETS
+
+From there, it is natural to define the expected regret/loss as
+\(\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \land (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset))\).
+This, of course, is the mentioned probability of making a mistake.
+
+ADD REMARK ON WHAT THIS IMPLIES WITH REGARD TO THE MEANS
+
+Lastly, it is to mention that we are considering the fixed-budget
+version of the thresholding bandit problem. We thus fix the number of
+samples that the algorithm will pull upfront at \(T\). The task of the
+algorithm is then to find a sampling rule or strategy which distributes
+the budget \(T\) among the \(K\) arms in such a way that the expected
+regret, or the error probability, is minimized. In other terms, the
+algorithm aims to use the \(T\) samples in a way that lets him return
+the two sets \(\hat{\mathcal{S}}_{\tau}\) and
+\(\hat{\mathcal{S}}_{\tau}^C\) with as much confidence as possible. This
+again shows the contrast to the fixed confidence setting in which one
+fixes the confidence level upfront and lets the algorithm draw as many
+samples as necessary to reach the required confidence.
+
+At this point, we have defined the fixed budget thresholding bandit
+setup for any algorithm in the case of sub-Gaussian distributions. We
+thus proceed to describe the algorithm proposed in Locatelli et al.
+(2016).
+
+\subsection{The APT Algorithm}\label{the-apt-algorithm}
+
+In the following we describe the \emph{Anytime Parameter-free
+Thresholding} (APT) algorithm proposed in Locatelli et al. (2016), which
+is a simple yet effective algorithm and displays some very favorable
+characteristics when compared with alternative algorithms.
+
+From the general setup, we already know how the algorithm will end.
+After it has drawn \(T\) samples, the algorithm makes its decision of
+which arms to include in the return sets solely on basis of the
+empirical means \(\hat{\mu}_i(T)\) estimated until time \(T\).
+Furthermore, the threshold and interval around the threshold were fixed
+upfront and serve as argument to the algorithm: \((\tau, \epsilon)\).
+For a given arm \(i\) and a given time \(t\), we let \(T_i(t)\)
+represent the number of samples drawn from arm \(i\) until time \(t\)
+(including). Consequently, the empirical mean of arm \(i\) at time \(t\)
+is given by \(\mu_i = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}\)
+where \(X_{i,s}\) is the feedback sampled from distribution \(\nu_i\)
+when the arm is pulled for the \(s\)-th time.
+
+To be specific, the APT algorithm initiates by pulling each arm once.
+Then, for each \(t > K\), it calculates for every arm the values
+\(T_i(t)\) and \(\mu_i(t)\). Based on the empirical mean, the algorithm
+computes the estimated gap between the mean and the threshold as
+\(\hat{\Delta}_i(t) = \hat{\Delta}_i^{\tau, \epsilon}(t) = |\mu_i(t) - \tau| + \epsilon\).
+The decision of which arm is sampled next is then based on the value
+\(B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t)\): the algorithm pulls arm
+\(I_{t+1} = \arg \min_{i\leq K} B_i(t+1)\) minimizing this decision
+quantity. After \(T\) pulls overall, the arm returns the sets described
+in the general setup, \(\hat{\mathcal{S}}_{\tau}\) and
+\(\hat{\mathcal{S}}^C_{\tau}\).
+
+\textbf{Remark}: Obviously, the APT algorithm tends to pull arms more
+often with corresponding mean close to the threshold and interval (small
+\(\hat{\Delta}_i(t))\). This makes sure that more evidence is gathered
+on arms which appear to be inherently difficult to classify based on the
+samples collected until time \(T_i(t)\), as these arms stifle the
+confidence the most. That is, until we have collected enough evidence to
+make a confident classification even if the mean is truly close to the
+threshold. In that case, \(\sqrt{T_i(t)}\) will raise \(B_i(t+1)\).
+Consequently, other arms farther away from the threshold will be sampled
+again. In this way, the algorithm tries to distribute the budget \(T\)
+over all arms so as to define a sampling rule optimizing the confidence
+of the final decision. Of course, that's just Glivenko-Cantelli and the
+CLT making sure \(B_i(t+1)\) is not degenerate.
+
+\subsection{Discussion}\label{discussion}
+
+One of the APT algorithm's main features is its simplicity. The sampling
+rule is very straightforward, and, as highlighted in Locatelli et al.
+(2016), it does not require any knowledge about the type of
+sub-Gaussianity \(R\), or the complexity \(H\) upfront. This makes the
+algorithm immediately applicable in practice while it still enjoys its
+upper bound on the expected regret. This is in particular worth
+highlighting when comparing APT to algorithms used in the pure
+exploration bandit setting. There, many algorithms require knowledge
+about the corresponding complexity upfront. The problem however being,
+that to know the complexity, the experimenter has to know all means up
+to a permutation of the arms (for example, see Audibert et al., 2010).
+This, of course, is not given in practice and thus alternative
+algorithms try to estimate the complexity online which is not a
+desirable solution either as especially in the beginning plug-in
+estimates based on the estimated means may lead to wrong estimates of
+the complexity and consequently budget allocation based on mistaken
+beliefs (compare Garivier and Kaufmann, 2016).
+
+Furthermore, Locatelli et al. (2016) were able to present an upper bound
+for the APT algorithm matching the lower bound in their Theorem 1.
+Proofs of both bounds are given below.
+
+Where the APT algorithm shows room for improvement is when it comes to
+settings with distributions that are not sub-Gaussian. This is mentioned
+in Locatelli et al. (2016). In general, the problem becomes that the
+assumptions for the bounds no longer hold; furthermore, the statistic
+\(B_i(t+1)\), and the term \(\hat{\Delta_i}(t)\) are motivated by
+(sub-)Gaussian distributions. The more one moves away from Gaussian-like
+distributions, the less appropriate this term becomes, however. In
+particular, the empirical mean will be less concentrated around the true
+mean and more impacted by outliers which are more likely under non
+sub-Gaussian distributions. Locatelli et al. (2016) thus refers to
+Bubeck et al. (2013) which considers solutions for multi-armed bandits
+that are based on heavy-tail distributions. By using more robust
+estimators of the mean, one could equip the APT algorithm to deal with
+such distributions.
+
+Another step towards dealing with non sub-Gaussianity is made by
+Mukherjee et al. (2017) who use an estimate of the variance additionally
+to the empirical mean in their Augmented UCB solution. Utilizing this
+additional information, the algorithm seems to perform better than for
+example APT, going from simulation results displayed in the paper. We
+will continue to discuss the Augmented UCB solution further in chapter
+3.
+
+Yet another idea, again mentioned in Locatelli et al. (2016) is to show
+bounds based on the Kullback-Leibler divergence of the specific
+distribution directly. While the approximation through the Gaussian
+Kullback-Leibler divergence in the lower bound proof is convenient and
+leads to the simple APT algorithm, it might not stay appropriate for
+distributions whose Kullback-Leibler divergence tends to differ from the
+Gaussian. This, for example, is the case for Bernoulli distributions at
+very small parameters \(\mu\). It's quite obvious simply by looking at
+examples that the Kullback-Leibler divergence of Bernoullis starts to
+lose any similarity to the plain quadratic approximation. The second
+graph then shows, that the actual Kullback-Leibler divergence of
+Bernoullis also has lost any symmetry over this range of parameter
+values. Given that Bernoulli distributions with very small parameter
+values arise naturally in many applications in website optimization and
+advertising click-through modeling, there is a need to tackle this
+problem.
+
+Refer also to page 6 in Kaufmann et al. (2016): ``This
+information-theoretic lower bound permits to interpret the quantity
+\(H(\nu)\) defined in (2) as a subgaussian approximation''.
+
+And so a potential approach can be to use the Kullback-Leibler
+divergence as measure similar to the methods proposed in Kaufmann et al.
+(2015). They proposed Kullback-Leibler based approaches for the pure
+exploration bandit setting, which we will describe in chapter 2. Then,
+in chapter 3, we will come back to the problem of using the
+Kullback-Leibler divergence in the thresholding bandit setting.
+
+\includegraphics{Draft_files/figure-latex/unnamed-chunk-1-1.pdf}
+
+\includegraphics{Draft_files/figure-latex/unnamed-chunk-2-1.pdf}
+
+\subsection{Lower Bound: Theorem and
+Proof}\label{lower-bound-theorem-and-proof}
+
+\begin{theorem}[Theorem 1, Locatelli et al., 2016] 
+\label{theorem:Locatelli2016Theorem1}
+For any sequence of gaps $(d_k)_k$, define a finite set of problems with Gaussian distributions with means corresponding to the gaps, and with variance 1.
+Lower bound the largest probability of error among these problems for the best possible algorithm as follows.
+Let $K,T \geq 0$.
+Let for any $i \leq K$, $d_i \geq 0$.
+Let $\tau \in \mathbb{R}, \epsilon > 0$.
+
+For $0 \leq i \leq K$, we write $\mathcal{B}^i$ for the problem where the distribution of arm $j \in \{1, \dots, K\}$ is $\mathcal{N}(\tau+d_i+\epsilon, 1)$ if $i \neq j$ and $\mathcal{N}(\tau-d_i-\epsilon, 1)$ otherwise.
+For all these problems, $H := H_{\tau, \epsilon} = \sum_i (d_i+2\epsilon)^{-2}$ is the same by definition.
+
+It holds that for any bandit algorithm,
+
+\begin{equation*}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) \geq \exp(-3T/H-4 \log(12(\log(T)+1)K)),
+\end{equation*}
+
+where $\mathbb{E}_{\mathcal{B}^i}$ is the expectation according to the samples of problem $\mathcal{B}^i$.
+\end{theorem}
+
+\emph{Proof of Theorem \ref{theorem:Locatelli2016Theorem1}}: In Theorem
+1 of Locatelli et al. (2016), a lower bound for the thresholding bandit
+problem is shown. The basic idea is as follows. The problem formulation
+considered in the paper describes bandit problems for sub-Gaussian
+distributions. To show a lower bound, we show that every algorithm is
+expected to make a certain error even if we restrict ourselves to a very
+restricted scenario. Even then, any algorithm will have a certain level
+of risk with which it cannot distinguish between the actual setting and
+slightly changed settings (under which the former answer leads to
+regret).
+
+To be more specific, consider a case in which we set \(\tau = 0\) and
+\(\epsilon = 0\) w.l.o.g. If we then choose all arms to have normally
+distributed feedback with means \(\mu_i\), we see that for each arm
+\(i\) the distance from the threshold is given by
+\(\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i\). Thus, assuming a
+variance of 1 for every arm, we have for every arm the distribution
+\(\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)\). Furthermore,
+define for each arm \(i \in \{1, \dots, K\}\) the alternative
+distribution \(\nu_i' = \mathcal{N}(-\Delta_i,1)\). It is easy to see
+that in this case, this is equivalent to a ``flip around the
+threshold''. Arms that originally have a mean larger than the threshold
+have a mean smaller than the threshold after the flip.
+
+The idea now is that every arm \(i \in \{1,\dots,K\}\) generates a
+sample for every time point \(t\in \{1, \dots, T\}\) from its
+distribution \(\nu_i\) before the algorithm starts to choose arms. Thus,
+we have a \(T \times K\) table of realized observations from the product
+distribution given by
+\(\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K\).
+This is a product distribution where the \(K\) different means all lie
+above the threshold. We would hope that an algorithm classifies the
+means accordingly. However, we will show in what follows that any
+algorithm makes a certain error by not being able to distinguish
+\(\mathcal{B}^0\) from at least one of \(K\) alternative product
+distributions \(\mathcal{B}^i, i \in \{1, \dots, K\}\), of which each
+differs only slightly in one arm from the original distribution, and has
+the same overall complexity (as defined by
+\(H = \sum_{i=1}^K (\Delta_i)^{-2}\)). We require \(K\) different
+distributions so that an arm sampling arm \(i\) very often for some
+reason will not have a smaller lower bound by chance.
+
+For each of the \(K\) arms, we introduce an alternative model of the
+following kind. Before the start of the algorithm, we introduce a slight
+variation in the setup. The idea is similar to how one can switch arms
+in the pure exploration setup for multi-armed bandits (compare Audibert
+et al., 2010; Garivier \& Kaufmann, 2016) to ``confuse'' any algorithm
+without introducing additional complexity to the specified problem.
+However, since we do not compare arms directly with each other in the
+thresholding bandit problem (switching arms would still keep all means
+above the threshold), we instead need to flip an arm \(i\) with respect
+to the threshold in order to get the alternative model
+\(\mathcal{B}_i\). Since the threshold is \(\tau = 0\), we have for the
+flipped arm the new distribution \(\nu_i'\) as defined above. Indeed, we
+can define the new product distribution
+\(B^i = \nu_1^i \otimes \dots \otimes \nu_K^i\) where for
+\(k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}\).
+This flipping of the arm corresponds to multiplying all random variables
+\(X_{i,t}\) of arm \(i\) by \(-1\).
+
+As in Locatelli et al. (2016), we let for \(i \leq K\),
+\(\mathbb{P}_{\mathcal{B}^i}\) define the probability distribution
+describing all samples that a bandit strategy can potentially collect up
+to horizon \(T\), i.e.~according to the samples
+\((X_{k,s})_{k\leq K, s \leq T} \sim (\mathcal{B}^i)^{\otimes T}\).
+\((T_k)_{k\leq K}\) denotes the number of samples collected on arm \(k\)
+until time \(T\).
+
+\paragraph{Reminder about the goal of the
+proof}\label{reminder-about-the-goal-of-the-proof}
+
+At this point, we have defined a finite set of problems of Gaussian
+distributions with fixed variance 1 for a given set of set of gaps
+between the means of the distributions and the threshold, \((d_k)_k\).
+We will now proof a lower bound on the worst case regret of any
+algorithm; that is, the maximum error probability that even the best
+algorithm makes on this problem.
+
+\paragraph{Statistical Decision}\label{statistical-decision}
+
+Given our formulation of the regret, the expected regret
+\(\mathbb{E}[\mathcal{L}(T)]\) corresponds directly to the probability
+of making a wrong classification of any of the \(K\) means. In general,
+let \(g\) be a binary decision function, and define
+\(\Omega = \{g = 0\}\) and \(\Omega^C = \{g = 1\}\). Assume that the
+decision \(T\) distinguishes between two states of the world, \(H_0\)
+and \(H_1\). Then our overall error probability is given by
+\(P_{H_0}(g=1) + P_{H_1}(g = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)\).
+
+In our case, \(H_0\) may correspond to the state in which we have
+\(\mathcal{B}^0\), and \(H_1\) corresponds to the case where any arm has
+been flipped, \(\mathcal{B}^i\). Furthermore, we consider the events in
+which the algorithm, making the decision, classifies arm \(i\) as being
+above the threshold: \(\mathcal{A}_i = \{i \in \hat{S}_\tau\}\). The
+event on which all arms are being classified as above the threshold is
+consequently given by \(\mathcal{A} = \bigcap \mathcal{A}_i\). However,
+Theorem 1 does not bound the overall regret, but the maximum error
+probability on the \(K+1\) different models. We can write this now as
+
+\begin{align}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big) \\
+& = \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
+\end{align}
+
+In order to give a bound on above equation, we start by considering
+\(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\). This probability can be
+written as the expected change in the likelihood of observed data when
+moving from distribution \(P_{\mathcal{B}_0}\) to \(P_{\mathcal{B}_i}\),
+times the probability under the original state. In other words, the
+probability of event \(\mathcal{A}_i\) under state \(\mathcal{B}^i\) is
+given as the probability of \(\mathcal{A}_i\) under the (original) state
+\(\mathcal{B}^0\) multiplied by a factor. This factor describes whether
+the new distribution increases or decreases the probability of the
+event, and is given by the change in the data likelihoods due to moving
+from \(\mathcal{B}^0\) to \(\mathcal{B}^i\), expressed as the expected
+likelihood ratio under \(\mathcal{B}^0\). By definition, the latter is
+equal to the empirical Kullback-Leibler divergence of the two
+distributions.
+
+We will define the change of distribution in terms of the empirical
+log-likelihood for our case. Then, we will show how to replace the
+log-likelihood by the empirical Kullback-Leibler divergence. So let us
+first introduce the empirical Kullback-Leibler divergence.
+
+Let every \(\nu_i, \nu_i'\) be dominated by the Lebesgue measure
+\(\lambda\). Then their density functions are given by
+\(f_i = \frac{\der \nu_i}{\der \lambda}\) and
+\(f_i' = \frac{\der \nu_i'}{\der \lambda}\) respectively. For
+\(T \geq t \geq 0\), define the empirical Kullback-Leibler divergence as
+
+\begin{align*}
+\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log(\frac{\der \nu_k'}{\der \nu_k}(X_{k,s})) \\
+& = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
+& = \frac{1}{t} \log \big( \prod_{s=1}^{t} \frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
+& \stackrel{\text{iid}}{=} \frac{1}{t} \log \big( \frac{f_k'(X_{k,1}, \dots,X_{k,t})}{f_k(X_{k,1}, \dots,X_{k,t})} \big) \\
+& = \frac{1}{t} \log \big( \text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k) \big)
+\end{align*}
+
+Since we consider Gaussian distributions with variance 1, we have
+density functions
+\(f_i(x) \propto \exp \big(-\frac{1}{2} (x-\Delta_i)^2\big)\) and
+\(f_i'(x) \propto \exp \big(-\frac{1}{2} (x+\Delta_i)^2\big)\). Plugging
+this into the above definition of the empirical Kullback-Leibler
+divergence, we easily see
+
+\begin{align*}
+\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{\exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2\big)}{\exp \big(-\frac{1}{2} (X_{k,s}-\Delta_k)^2\big)} \big) \\
+& = \frac{1}{t} \sum_{s=1}^{t} \log \big( \exp(-\frac{1}{2} (X_{k,s}+\Delta_k)^2 + \frac{1}{2} (X_{k,s}-\Delta_k)^2) \big) \\
+& = - \frac{1}{t} \sum_{s=1}^{t} 2 X_{k,s} \Delta_k
+\end{align*}
+
+\paragraph{Change of Distribution}\label{change-of-distribution}
+
+We are now ready to state the change of distribution. As alluded to
+above, we consider how the probability changes for the event
+\(\mathcal{A}_i\) when we move from \(\mathcal{B}^0\) to
+\(\mathcal{B}^i\). When flipping arm \(i\), we only changed the samples
+of this arm, that is, the first \(T_i\) observations we got from arm
+\(i\) the algorithm took. The change of distribution is then defined as:
+
+\begin{align*}
+\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \text{LR}((X_{i,1}, \dots,X_{i,T_i}), \nu_i', \nu_i) ] \\
+& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ]
+\end{align*}
+
+Obviously, \(\hat{\KL}_{i,T_i}\) depends on the realized samples
+\(X_{i,1}, \dots,X_{i,T_i}\). Consequently, we need to find a bound on
+\(\hat{\KL}_{i,T_i}\) itself to incorporate the uncertainty involved in
+this metric.
+
+\paragraph{Concentration of the Empirical Kullback-Leibler
+Divergence}\label{concentration-of-the-empirical-kullback-leibler-divergence}
+
+For our problem, the Kullback-Leibler divergence of \(\nu_k'\) from
+\(\nu_k\) is given by \(\KL_k := KL(\nu_k', \nu_k) = 2\Delta_k^2\).
+
+It is easy to see that
+
+\begin{equation*}
+|\hat{\KL}_{k,t} - \KL_{k,t}| = |-\frac{2}{t} \Delta_k \sum_{s=1}^{t}(X_{k,s} - \Delta_k)|
+\end{equation*}
+
+itself is a normally distributed random variable with mean zero and a
+variance decreasing in \(t\). Thus, one can show as in Locatelli et al.
+(2016) that \(\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4\) for the event
+
+\begin{equation}
+\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}}\}. \label{LocatelliTheorem1EventXi}
+\end{equation}
+
+Thus, in order to bound the empirical Kullback-Leibler divergence in our
+change of measure, we can consider the intersection of \(\mathcal{A}_i\)
+and \(\xi\) as follows and plug in the bound on event \(\xi\):
+
+\begin{align*}
+\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
+& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
+& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
+\end{align*}
+
+Two things are left to do: With \(T_i\), we still have one random
+variable left which we cannot leave in our bound. Second, we are
+actually not interested in \(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)
+but in
+\(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\).
+
+\paragraph{\texorpdfstring{Bounding \(T_i\) for
+\(\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)}{Bounding T\_i for \textbackslash{}max\_\{i \textbackslash{}in \textbackslash{}\{1,\textbackslash{}dots,K\textbackslash{}\}\}\textbackslash{}mathbb\{P\}\_\{\textbackslash{}mathcal\{B\}\^{}i\}(\textbackslash{}mathcal\{A\}\_i)}}\label{bounding-t_i-for-max_i-in-1dotskmathbbp_mathcalbimathcala_i}
+
+Part of our bound is
+\(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\),
+so let's continue with that. In general it holds that
+\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K}\sum_{i=1}^K X_i\).
+Thus we can write:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
+& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
+& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
+\end{align*}
+
+where the second line is again the intersection of \(\mathcal{A}_i\) and
+\(\xi\) as before in order to apply the change of distribution in the
+third line.
+
+What is left to show before we have our final bound is a bound on
+\(T_i\). To show that any algorithm has a certain bound on its error, it
+only makes sense that every arm has to pulled at least a certain amount
+of times. Consequently, no arm should be pulled exclusively.
+
+First, let \(a = \Delta_i \sqrt{T_i}\) and
+\(b = 4\sqrt{\log((4\log(T)+1)K)}\). Then use \(ab \leq a^2 + b^2\) to
+write \(ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)\). And so:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) ]
+\end{align*}
+
+Furthermore, we know that the sum of the individual arm pulls has to be
+equal to the overall number of pulls (equal to the budget in the fixed
+budget sense), \(\sum_i T_i = T\), and furthermore we know that
+\(T_i>0\). The latter holds since any reasonable algorithm has to check
+each arm at least once in our setup. This is because we need to check
+each arm's performance in comparison to the threshold. Thus it is easy
+to show that
+\(\exists i: T_i \leq \frac{T}{H \Delta_i^2} = \frac{T}{(\sum_{i=1}^{K} \Delta_i^{-2}) \Delta_i^2}\).
+To see this, assume the opposite:
+\(\forall i: T_i > T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2}\). This
+implies however
+\(\sum_{i=1}^K T_i > \sum_{i=1}^K T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2} = T \cdot 1 = T\)
+which is a contradiction.
+
+So we can write \((\Delta_i \sqrt{T_i})^2 \leq \frac{T}{H}\). We use
+\(\mathcal{A} = \cap_{i=1}^K \mathcal{A}_i\) to write:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big] \\
+& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}{K} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big]
+\end{align*}
+
+We write
+\(\frac{1}{K} \sum_{i=1}^K \exp(-3T_i \Delta_i^2) \geq \frac{1}{K} \sum_{i=1}^K \exp(-3 T/H) = \exp(-3 T/H)\).
+Thus:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i) \exp(-16 \log(4(\log(T)+1)K)) ] \\
+& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
+& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
+& = \mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
+\end{align*}
+
+\paragraph{Bringing everything
+together}\label{bringing-everything-together}
+
+Consider again the risk which we need to bound from equation
+\eqref{LocatelliTheorem1ExpRegret}. We bound the maximum expected loss
+over all \(\mathcal{B}_i\). By again using the fact that in general
+\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K} \sum_{i = 1}^K X_i\),
+we plug in our previous calculations:
+
+\begin{align}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
+& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \label{LocatelliTheorem1DefinitionOfRisk}
+\end{align}
+
+From \eqref{LocatelliTheorem1EventXi} we know that for any
+\(i \in \{0, \dots, K\}\), \(\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4\).
+Following the argument in Locatelli et al. (2016), we now consider two
+cases: \(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2\) and
+\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2\). In the former
+case, we can plug in the two probabilities into
+\eqref{LocatelliTheorem1DefinitionOfRisk}. If
+\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2\) and
+\(\mathbb{P}_{\mathcal{B}^0}(\xi) \geq 3/4\), then
+\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \geq 1/4\). Thus:
+
+\begin{align*}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
+& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \\
+& \geq \frac{1}{8} \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
+\end{align*}
+
+where we drop the second summand of the second line so that the
+inequality holds.
+
+On the other hand, when
+\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2\), then we know that
+\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \leq 1/2\) for any
+\(\mathbb{P}_{\mathcal{B}^0}(\xi)\). At the same time
+\(1-\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \geq 1/2\).
+Consequently,
+\(1/4 \leq \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \leq 1/2\),
+while
+\(\frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) \geq 0\).
+And so the stronger lower bound in that case is, as noticed by Locatelli
+et al. (2016), given simply by
+
+\begin{align*}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
+& \geq 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \\
+& \geq \frac{1}{2}
+\end{align*}
+
+\subsection{Upper Bound: Theorem and
+Proof}\label{upper-bound-theorem-and-proof}
+
+\begin{theorem}[Locatelli et al., 2016] \label{theorem:LocatelliTheorem4}
+Let $K \geq 0$, $T \geq 2K$, and consider a problem $\mathbb{B}$. Assume that
+all arms $\nu_k$ of the problem are R-sub-Gaussian with means $\mu_k$. Let $\tau
+\in \mathbb{R}, \epsilon \geq 0$.
+
+Algorithm APT's expected loss is upper bounded on this problem as 
+\begin{equation*} \mathbb{E}(\mathcal{L}(T)) \leq \exp
+(-\frac{1}{64R^2}\frac{T}{H} + 2 \log (T) + 1)K)) \end{equation*}
+
+where we remind that $H = \sum_i (|\mu_i - \tau | + \epsilon)^{-2}$ and where
+$\mathbb{E}$ is the expectation according to the samples of the problem.
+\end{theorem}
+
+\emph{Proof of Theorem \ref{theorem:LocatelliTheorem4}:} To prove above
+theorem, we first define a favorable event \(\xi\) on which we hope to
+make a loss with only a small probability. Indeed, it is the event for
+which we want to upper bound the expected loss. As we want to find an
+upper bound for the expected loss of the APT algorithm, the event
+corresponds to the decision made by it. Given that the APT algorithm's
+sampling rule and final decision is based on the empirical mean of each
+arm, it will have low expected regret, if it finds empirical mean
+estimates \(\hat{\mu}_i(t) = \frac{1}{s} \sum_{t=1}^s X_{i,t}\) that are
+close to the true means \(\mu_i\) of the arms. Then, we would expect
+arms with \(\hat{\mu}_i(T) > \tau + \epsilon\) to be classified
+correctly, and arms with \(\hat{\mu}_i(T) < \tau - \epsilon\) to be
+rejected.
+
+Indeed, we have
+\(\mathbb{E}(\mathcal{L}(T)) = P(S_{\tau + \epsilon} \cap \hat{S}_\tau^C \neq \emptyset \lor S_{\tau-\epsilon}^C \cap \hat{S}_{\tau} \neq \emptyset)\).
+But this just corresponds to
+\(P(\{\exists i: ((\mu_i < \tau-\epsilon) \land(\hat{\mu}_i \geq \tau)) \lor ((\mu_i > \tau + \epsilon) \land (\hat{\mu}_i < \tau)))\).
+Each of the two \((...)\lor(...)\) conditions corresponds to
+\(| \hat{\mu}_i - \mu_i | \geq \epsilon\). It follows that the expected
+loss can be rewritten as:
+\(\mathbb{E}(\mathcal{L}(T)) = P(\exists i, \exists s: |\hat{\mu}_{i,s} - \mu_i | \geq \epsilon) = P(\xi^C)\).
+This is exactly the probability of classifying at least one arm
+incorrectly which results in a loss of size 1.
+
+Thus we define as the favorable event as:
+
+\begin{equation} 
+\xi = \{\forall i, \forall s: | \hat{\mu}_{i,s} - \mu_i | \leq
+\epsilon\} 
+\end{equation}
+
+Furthermore, if we write
+\(\xi_{i,s} = \{ |\hat{\mu}_{i,s}-\mu_i | \leq \epsilon \}\), then the
+following holds by a union bound.
+
+\begin{equation} 
+P(\xi) = P(\cap_i \cap_s \xi_{i,s}) = 1 - P(\cup_i \cup_s
+\xi_{i,s}^C) \geq 1 - \sum_i \sum_s P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon)
+\label{theorem2_prob_fav_event} 
+\end{equation}
+
+Furthermore, for any \(i \in \{1, \dots, K\}\), for any
+\(s \in \{1, \dots, T(i)\}\), with \(X_{it}\) being the random sample
+from the R-sub-Gaussian distribution \(v_i\) at time \(t\):
+
+\begin{equation} 
+P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon) = P(| (\frac{1}{s}
+\sum_{t=1}^{s} X_{it} - \mu_i) | \geq \epsilon) = P(| \sum_{t=1}^{s} (X_{it} -
+\mu_i) | \geq s \epsilon) 
+\end{equation}
+
+where the latter can be bounded by a Hoeffding inequality:
+
+\begin{equation} 
+P(| \sum_{t=1}^{s} (X_{it} - \mu_i) | \geq s \epsilon) \leq
+2\exp (-\frac{\epsilon^2 s}{2 R^2}) \label{theorem2_hoeffding} 
+\end{equation}
+
+The Hoeffding inequality as used here is as follows:
+
+\begin{lemma}[Hoeffding's Inequality] \label{lemma:HoeffdingInequality}
+Consider $X_1, \dots, X_T$ independent random variables from R-sub-Gaussian distributions $\nu_i$ with mean $\mu_i$. Then, for any $\epsilon > 0$,
+
+\begin{equation*}
+\mathbb{P} \Big( | \sum_{i = 1}^T (X_i - \mu_i) | \geq \epsilon \Big) \leq 2\exp \Big(\frac{-\epsilon^2}{2T R^2}\Big).
+\end{equation*}
+\end{lemma}
+
+Plugging equation \eqref{theorem2_hoeffding} back into equation
+\eqref{theorem2_prob_fav_event}, we get:
+
+\begin{equation}
+P(\xi) \geq 1 - \sum_i \sum_s P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon) \geq 1 - 2 \sum_i \sum_s \exp (-\frac{\epsilon^2 s}{2 R^2})
+\end{equation}
+
+Now, in order to match the performance of the lower bound on the
+expected loss derived in Theorem \ref{theorem:Locatelli2016Theorem1}, we
+will choose \(\epsilon = \sqrt{\frac{T \delta^2}{Hs}}\). Thus:
+
+\begin{equation}
+P(\xi) \geq 1 - 2 \sum_i \sum_s \exp (-\frac{\epsilon^2 s}{2 R^2}) = 1 - 2 \sum_i \sum_s \exp (-\frac{T \delta^2}{2 R^2 H}) \geq 1 - TK \exp(-\frac{T\delta^2}{2R^2H})
+\end{equation}
+
+Thus, we do not exactly get the bound from Locatelli et al. (2016)
+because we used the Hoeffding inequality instead of the martingale
+bound; but the the method should be clear.
+
+What is left now is to show that the favorable event still holds under
+the proposed \(\epsilon\), that is, we need to show that under
+\(P(\xi) \geq 1 - TK \exp(-\frac{T\delta^2}{2R^2H})\) we still reject
+arms that are under \(\tau - \epsilon\) and accept those above
+\(\tau + \epsilon\).
+
+\paragraph{Step 2: Lower Bound on Number of Pulls of Difficult
+Arm}\label{step-2-lower-bound-on-number-of-pulls-of-difficult-arm}
+
+In order to see that arms are correctly classified with large
+probability, we need to show that they are are pulled sufficiently
+often, that is, we have a degree of exploration for each arm \(i\) that
+allows us to identify its characteristics. To see this, rewrite the
+favorable event of a single arm as follows with \(s = T(i)\):
+
+\begin{equation}
+\xi_{i,s} = \{ |\hat{\mu}_{i,s}-\mu_i | \leq \epsilon \} = \{ |\hat{\mu}_{i,s} - \mu_i | \leq \sqrt{\frac{T \delta^2}{H T(i)}}\}
+\end{equation}
+
+To make sure that this deviation is small enough, we need to show that
+at time \(T\), all \(T(i)\) have a sufficient lower bound and thus all
+arms \(i\) have been explored sufficiently to classify correctly with
+probability larger \(TK \exp(-\frac{T\delta^2}{2R^2H})\).
+
+To start off, notice that due to the initialization of the APT
+algorithm, every \(T_i(T) \geq 1\). Furthermore, we have assumed that
+\(T>2K\). Now, at time \(T\), consider an arm \(k\) that has been pulled
+\(T_k(T) -1 \geq \frac{(T-K)}{H \Delta^2_k}\) times. That is, it has
+been pulled at least proportionally to it's contribution to the overall
+hardness of the problem \(H\). Recall
+\(H = \sum_{i=1}^K(|\mu_i - \tau|+\epsilon)^-2\) and
+\(\delta^2_i = (|\mu_i - \tau | + \epsilon)^2\). To see that such arm
+\(k\) exists, assume it does not. Then
+
+\begin{equation*}
+T_i(T) - 1 < \frac{T-K}{H \Delta_i^2} \forall i
+\end{equation*}\begin{equation*}
+T- K = \sum_{i=1}^{K} T_i(T) - 1 < \sum_{i=1}^{K} \frac{T-K}{H \Delta_i^2} = \frac{T-K}{H \Delta_i^2} \sum_{i=1}^{K} \frac{1}{\Delta_i^2} = T-K
+\end{equation*}
+
+which is a contradiction.
+
+Consequently, using the assumption \(T>2K\) from above, we have
+
+\begin{equation*}
+T_k(T) \geq T_k(T) - 1 \geq \frac{T-K}{H \Delta^2_k} = \frac{T}{2H\Delta_k^2}
+\end{equation*}
+
+This states a lower bound on the amount of pulls \(T_k(t)\) for an arm
+\(k\) that contributes more than average to the overall hardness of the
+problem.
+
+\paragraph{Step 3: Lower Bound on Number of Pulls of Simple
+Arm}\label{step-3-lower-bound-on-number-of-pulls-of-simple-arm}
+
+Next, we would like to derive bounds on the number of pulls of the
+remaining arms \(i\) at the time \(t\), the last pull of arm \(k\). To
+do so, consider that we are on the favorable event \(\xi\). For every
+arm \(i\), it holds:
+
+\begin{equation}
+|\hat{\mu}_i(t) - \mu_i | \leq \sqrt{\frac{T \delta^2}{HT_i(t)}} \label{step3_favorable_event} 
+\end{equation}
+
+As described in Locatelli et al., using the reverse triangle inequality,
+we can write
+
+\begin{IEEEeqnarray*}{rCl}
+|\hat{\mu}_i(t) - \mu_i | & = & | (\hat{\mu}_i(t) - \tau) - (\mu_i-\tau) |
+\\
+& \geq & | |\hat{\mu}_i(t) - \tau| - |\mu_i-\tau| |
+\\
+& = & | (|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i-\tau| - \epsilon) |
+\\
+& = & | \hat{\Delta}_i(t) - \Delta_i |
+\end{IEEEeqnarray*}
+
+Consequently, we can again employ the hardness of the task to start
+deriving bounds on the number of pulls of the arms:
+
+\begin{equation*}
+| \hat{\Delta}_i(t) - \Delta_i | \leq |\hat{\mu}_i(t) - \mu_i | \sqrt{\frac{T \delta^2}{HT_i(t)}}
+\end{equation*}
+
+From this, we get
+
+\begin{IEEEeqnarray*}{rlCrl}
+\Delta_i - \sqrt{\frac{T \delta^2}{HT_i(t)}} & \leq & \hat{\Delta}_i(t) & \leq & \Delta_i + \sqrt{\frac{T \delta^2}{HT_i(t)}}
+\end{IEEEeqnarray*}
+
+and in particular for the arm \(k\) discussed above
+
+\begin{IEEEeqnarray}{rlCrl}
+\Delta_k - \sqrt{\frac{T \delta^2}{HT_k(t)}} & \leq & \hat{\Delta}_k(t) & \leq & \Delta_k + \sqrt{\frac{T \delta^2}{HT_k(t)}} \label{delta_hat_k_bounds}
+\end{IEEEeqnarray}
+
+To bound \(T_i(t)\), it is helpful to compare \(\Delta_i\) and
+\(\Delta_k\) at time \(t\). From the definition of the APT algorithm, we
+know that since arm \(k\) has been pulled at time \(t\) (``Pull arm
+\(I_{t+1} = \arg \min_i \mathcal{B}_i (t+1)\)''):
+
+\begin{IEEEeqnarray*}{rCl}
+\mathcal{B}_k(t) & \leq & \mathcal{B}_i(t)
+\\
+\sqrt{T_k(t)} \hat{\Delta}_k(t) & \leq & \sqrt{T_i(t)} \hat{\Delta}_i(t)
+\end{IEEEeqnarray*}
+
+Thus, every arm \(i\) has a lower bound on it's number of pulls given by
+the lower bound for arm \(k\) proportional with it's inverse relative
+estimated hardness \(\hat{\Delta}_k(t) / \hat{\Delta}_i(t)\). We can
+easily derive a lower bound for the left hand side by plugging in
+\eqref{delta_hat_k_bounds}:
+
+\begin{IEEEeqnarray}{rCl}
+\sqrt{T_k(t)} (\Delta_k - \sqrt{\frac{T \delta^2}{HT_k(t)}}) & \leq & \mathcal{B}_k(t) 
+\\
+\sqrt{\frac{T}{2H\Delta_k^2}} (\Delta_k - \sqrt{2}\Delta_k \delta) & = & \sqrt{\frac{T}{H}} (\frac{1}{\sqrt{2}} - \delta)
+\\
+& \leq & \mathcal{B}_k(t)
+\end{IEEEeqnarray}
+
+since \(T_k(t) \geq T/(2H\Delta^2_k)\) and
+\(\sqrt{T \delta^2 / (HT_k(t))} \geq \sqrt{T \delta^2 / (H\frac{T}{2H \Delta^2_k})} = \sqrt{2}\Delta_k \delta\).
+
+Next, upper bound \(\mathcal{B}_i(t)\). In contrast to \(T_k(t)\), there
+is no lower bound for \(T_i(t)\) available yet that we could plug in.
+Thus we derive:
+
+\begin{IEEEeqnarray*}{rCl}
+\mathcal{B}_i(t) & = & \sqrt{T_i(t)} \hat{\Delta}_i(t) 
+\\
+& \leq & \sqrt{T_i(t)} (\Delta_i + \sqrt{\frac{T \delta^2}{H T_i(t)}})
+\\
+& = & \sqrt{T_i(t)} \Delta_i + \delta \sqrt{\frac{T}{H}}
+\end{IEEEeqnarray*}
+
+Combining the two bounds, we get a lower bound on the pulls for every
+other arm \(i\):
+
+\begin{IEEEeqnarray*}{rCl}
+\Delta_i \sqrt{T_i(t)} + \delta \sqrt{\frac{T}{H}} & \geq & (\frac{1}{\sqrt{2}} - \delta) \sqrt{\frac{T}{H}}
+\\
+\sqrt{T_i(t)} & \geq & (\frac{1}{\sqrt{2}} - 2\delta) \sqrt{\frac{T}{H}} \frac{1}{\Delta_i}
+\\ 
+& & \text{(choose $2\delta > 1 / \sqrt{2}$ such that RHS is greater 0)}
+% \\
+% T_i(t) & \geq & (\frac{1}{2} - 2\sqrt{2} \delta + 4\delta^2) \underbrace{\frac{T}{H} \frac{1}{\Delta_i^2}}_\text{$i$'s share of the budget}
+% \\
+% T_i(t) & \geq & (1 - 4 \sqrt{2} \delta + 8\delta^2) \frac{T}{2H} \frac{1}{\Delta_i^2}
+\end{IEEEeqnarray*}
+
+\paragraph{Conclusion}\label{conclusion}
+
+As stated before, we require the lower bound on \(T_i(t)\) in order to
+show that
+\(|\hat{\mu}_i(t) - \mu_i | \leq \sqrt{frac{T \delta^2}{H T_i(t)}}\)
+holds for all \(i\). So if we now simply plug in the derived lower
+bound, we get:
+
+\begin{equation*}
+\mu_i - \Delta_i (\frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}) \leq \hat{\mu}_i(t) \leq \mu_i + \Delta_i (\frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta})
+\end{equation*}
+
+and with \(\lambda := (\frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}) > 0\):
+
+\begin{equation*}
+\mu_i - \Delta_i \lambda \leq \hat{\mu}_i(t) \leq \mu_i + \Delta_i \lambda
+\end{equation*}
+
+Under this formulation on \(\xi\), do we accept arms with
+\(\mu_i \geq \tau + \epsilon\)? For these arms holds that
+\(\Delta_i = \mu_i - \tau + \epsilon\). Consequently:
+
+\begin{IEEEeqnarray*}{rCl}
+\mu_i - (\mu_i - \tau + \epsilon) \lambda & \leq & \hat{\mu}_i(t) 
+\\ 
+\hat{\mu}_i(t) & \geq & \tau \lambda + \mu (1-\lambda) - \epsilon \lambda
+\end{IEEEeqnarray*}
+
+The arms are accepted if
+
+\begin{IEEEeqnarray*}{rCl}
+\hat{\mu}_i(t) - \epsilon & \geq & 0
+\end{IEEEeqnarray*}
+
+Or equivalently as long as
+
+\begin{IEEEeqnarray*}{rCl}
+\tau \lambda + \mu(1-\lambda) - \epsilon \lambda - \tau & \geq & 0
+\\
+\lambda & \leq & \frac{1}{2}
+\end{IEEEeqnarray*}
+
+\newpage
+
+\section{Kullback-Leibler Complexity of Pure
+Exploration}\label{kullback-leibler-complexity-of-pure-exploration}
 
@@
 (2016) so that it will be easier to compare the arguments.
+
+\subsection{\texorpdfstring{Complexity of Best-Arm and Top-\emph{m}
+Identification}{Complexity of Best-Arm and Top-m Identification}}\label{complexity-of-best-arm-and-top-m-identification}
 
@@
 
-\includegraphics{kl_complexity_files/figure-latex/unnamed-chunk-1-1.pdf}
+\includegraphics{Draft_files/figure-latex/unnamed-chunk-3-1.pdf}
 
@@
 
-\subsubsection{Optimal Best Arm
+\subsection{Optimal Best Arm
 Identification}\label{optimal-best-arm-identification}
@@
 
-\subsubsection{Conclusion of Complexity of Best Arm
+\subsection{Conclusion of Complexity of Best Arm
 Identification}\label{conclusion-of-complexity-of-best-arm-identification}

### 2017-05-31 Thresholding Bandit/Theorem2.Rmd
Add start of chapter three

@@
 header-includes:
+   #- \documentclass[a4paper,twoside,english]{article}
    - \usepackage[retainorgcmds]{IEEEtrantools}
+   - \usepackage{bm}
+   - \usepackage{amsmath}
+   - \usepackage{bbm}
+   - \newtheorem{theorem}{Theorem}
+   - \newtheorem{lemma}{Lemma}
+   - \newcommand{\KL}{\,\text{KL}}
+   - \newcommand{\der}{\,\text{d}}
+   #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
+   #- \usepackage{fontspec}
+   #-   \setmainfont{Arial}
 keep_tex: TRUE
 output:
-  pdf_document
+  pdf_document:
+    number_sections: true
+    keep_tex: true
+    #latex_engine: xelatex
+fontsize: 12pt
+urlcolor: blue
 ---
@@
 
+\begin{theorem}[Locatelli et al., 2016] \label{theorem:LocatelliTheorem4}
 Let $K \geq 0$, $T \geq 2K$, and consider a problem $\mathbb{B}$. Assume that
@@
 $\mathbb{E}$ is the expectation according to the samples of the problem.
+\end{theorem}
 
-### Proof
-
-To prove above theorem, we first define a favorable event $\xi$ on which we hope
+*Proof of Theorem \ref{theorem:LocatelliTheorem4}:* To prove above theorem, we first define a favorable event $\xi$ on which we hope
 to make a loss with only a small probability. Indeed, it is the event for which
@@
 the expected loss of the APT algorithm, the event corresponds to the decision
-made by it. The APT algorithm's heuristic leads to a decision with low expected
-regret, if it finds empirical mean estimates $\frac{1}{s} \sum_{t=1}^s X_{i,t}$
-of the arms that are close to the true mean $mu_i$ of the arms. Then, we would
-expect arms which are over $\tau + \epsilon$ to be classified correctly, and
-arms that are under $\tau - \epsilon$ to be rejected.
+made by it.
+Given that the APT algorithm's sampling rule and final decision is based on the empirical mean of each arm, it will have low expected regret, if it finds empirical mean estimates $\hat{\mu}_i(t) = \frac{1}{s} \sum_{t=1}^s X_{i,t}$
+that are close to the true means $\mu_i$ of the arms. Then, we would
+expect arms with $\hat{\mu}_i(T) > \tau + \epsilon$ to be classified correctly, and
+arms with $\hat{\mu}_i(T) < \tau - \epsilon$ to be rejected.
 
@@
 expected loss can be rewritten as: $\mathbb{E}(\mathcal{L}(T)) = P(\exists i,
-\exists s: |\hat{\mu}_{i,s} - \mu_i | \geq \epsilon) = P(\xi^C)$. But this is
+\exists s: |\hat{\mu}_{i,s} - \mu_i | \geq \epsilon) = P(\xi^C)$. This is
 exactly the probability of classifying at least one arm incorrectly which
@@
 
-Thus we define as the favorable event:
+Thus we define as the favorable event as:
 
@@
 Furthermore, if we write $\xi_{i,s} = \{ |\hat{\mu}_{i,s}-\mu_i | \leq \epsilon
-\}$, then the following holds by union bound.
+\}$, then the following holds by a union bound.
 
@@
 
-...
+\begin{lemma}[Hoeffding's Inequality] \label{lemma:HoeffdingInequality}
+Consider $X_1, \dots, X_T$ independent random variables from R-sub-Gaussian distributions $\nu_i$ with mean $\mu_i$. Then, for any $\epsilon > 0$,
 
-Plugging \eqref{theorem2_hoeffding} back into \eqref{theorem2_prob_fav_event},
+\begin{equation*}
+\mathbb{P} \Big( | \sum_{i = 1}^T (X_i - \mu_i) | \geq \epsilon \Big) \leq 2\exp \Big(\frac{-\epsilon^2}{2T R^2}\Big).
+\end{equation*}
+\end{lemma}
+
+Plugging equation \eqref{theorem2_hoeffding} back into equation \eqref{theorem2_prob_fav_event},
 we get:
@@
 
-Now, in order to match the performance of the lower bound on the expected loss derived in theorem 1, we will choose $\epsilon = \sqrt{\frac{T \delta^2}{Hs}}$. Thus:
+Now, in order to match the performance of the lower bound on the expected loss derived in Theorem \ref{theorem:Locatelli2016Theorem1}, we will choose $\epsilon = \sqrt{\frac{T \delta^2}{Hs}}$. Thus:
 
@@
 
-Thus, we don't exactly get the bound from Locatelli et al. (2016) because we used the Hoeffding inequality instead of the martingale bound; but the the method should be clear.
+Thus, we do not exactly get the bound from Locatelli et al. (2016) because we used the Hoeffding inequality instead of the martingale bound; but the the method should be clear.
 

### 2017-05-31 Thresholding Bandit/Theorem2.tex
Add start of chapter three

--- 2017-05-28 Complexity of Best Arm Identification/kl_complexity.tex
@@
 \hypersetup{unicode=true,
-            pdftitle={On the Complexity of Best Arm Identification},
+            pdftitle={Theorems and Proofs},
             pdfauthor={Tim Radtke},
@@
 \setlength{\droptitle}{-2em}
-  \title{On the Complexity of Best Arm Identification}
+  \title{Theorems and Proofs}
   \pretitle{\vspace{\droptitle}\centering\huge}
@@
   \postdate{\par}
-  \date{5/20/2017}
+  \date{4/23/2017}
 
@@
 
-In the previous chapter, we have discussed the thresholding bandit
-problem as presented in Locatelli et al. (2016). Doing so, we came
-across the complexity term \(H = \sum_{i=1}^{K} \Delta_i^{-2}\).
-Furthermore, we have noted the fact that an algorithm and bounds based
-on \emph{only} the gap between the respective mean and the threshold are
-useful in the case of sub-Gaussian problems. Furthermore, even for the
-case of Bernoulli arms, which are sub-Gaussian since their feedback is
-bounded on \([0,1]\), the gap \(\Delta\) becomes less and less
-appropriate for situations in which both \(\mu\) of the Bernoulli, and
-\(\tau\) are very close to 0 or 1.
+\subsection{Theorem 2}\label{theorem-2}
 
-Even though the complexity \(H\) enjoys popularity in the literature of
-the best m arm identification problem, \(m \geq 1\), Kaufmann et al.
-(2016) show explicitly that \(H\) is mainly useful for problems of
-Gaussian distributions. Indeed, they go so far as to define new measures
-of complexity that are based on information theoretic metrics. Using
-those they then display \(H\) as an approximation to their measures in
-the case of Gaussian distributions. In turn, this makes apparent that
-especially Bernoulli distributions with small means have to be treated
-differently.
+\begin{theorem}[Locatelli et al., 2016] \label{theorem:LocatelliTheorem4}
+Let $K \geq 0$, $T \geq 2K$, and consider a problem $\mathbb{B}$. Assume that
+all arms $\nu_k$ of the problem are R-sub-Gaussian with means $\mu_k$. Let $\tau
+\in \mathbb{R}, \epsilon \geq 0$.
 
-For the current chapter, we will adopt the notation of Kaufmann et al.
-(2016) so that it will be easier to compare the arguments.
+Algorithm APT's expected loss is upper bounded on this problem as 
+\begin{equation*} \mathbb{E}(\mathcal{L}(T)) \leq \exp
+(-\frac{1}{64R^2}\frac{T}{H} + 2 \log (T) + 1)K)) \end{equation*}
 
-Instead of the thresholding bandit problem, we now consider the problem
-of identifying the best \(m\) out of \(K\) arms, that is, the Top-\(m\)
-problem. While we previously looked at a fixed budget formulation, we
-now mainly focus on a fixed confidence problem. That is, we hold the
-confidence \(1-\delta\) fixed at which a strategy returns the correct
-\(m\) arms while trying to find them in a way that minimizes the sample
-complexity \(\mathbb{E}_{\nu}[\tau]\), that is, the expected number of
-overall draws of the arms. \(\tau\) is also called the stopping time of
-the algorithm. Algorithms are supposed to find \(\mathcal{S}_m^*\), the
-set of the \(m\) arms with the largest means. If we let
-\((\mu_1, \dots, \mu_K)\) be the vector of the means of the arms, then
-let \((\mu_{[1]}, \dots, \mu_{[K]})\) be the tuple in which the means
-are arranged in decreasing order. For the rest of this chapter, we
-consider only settings with arms for which \(\mu_{[m]} > \mu_{[m+1]}\);
-that is, the set of the top \(m\) arms, \(\mathcal{S}_m^*\), is unique.
-After the sampling phase, we require any algorithm to return the set
-\(\hat{S}_m \subset \{1,\dots,K\}\) of \(m\) arms that the algorithm
-believes to have the largest means. In the case of fixed confidence, we
-fix \(\delta\) at the beginning, such that the algorithm only stops
-sampling when
-\(\mathbb{P}_{\nu}(\hat{S}_m = \mathcal{S}_m^*) \geq 1-\delta\). We try
-to find algorithms who fulfill this as quickly as possible; that is,
-they minimize the expected stopping time (or number of draws),
-\(\mathbb{E}_{\nu}[\tau]\).
+where we remind that $H = \sum_i (|\mu_i - \tau | + \epsilon)^{-2}$ and where
+$\mathbb{E}$ is the expectation according to the samples of the problem.
+\end{theorem}
 
-To arrive at the new measure of complexity proposed by Kaufmann et al.
-(2016), it will actually make sense to first follow their arguments to a
-general lower bound on the sample complexity \(\mathbb{E}_{\nu}[\tau]\)
-in the case of fixed confidence problems. This bound is given in their
-Theorem 4 (for common confidence levels of \(\delta \leq 0.15\)).
+\emph{Proof of Theorem \ref{theorem:LocatelliTheorem4}:} To prove above
+theorem, we first define a favorable event \(\xi\) on which we hope to
+make a loss with only a small probability. Indeed, it is the event for
+which we want to upper bound the expected loss. As we want to find an
+upper bound for the expected loss of the APT algorithm, the event
+corresponds to the decision made by it. Given that the APT algorithm's
+sampling rule and final decision is based on the empirical mean of each
+arm, it will have low expected regret, if it finds empirical mean
+estimates \(\hat{\mu}_i(t) = \frac{1}{s} \sum_{t=1}^s X_{i,t}\) that are
+close to the true means \(\mu_i\) of the arms. Then, we would expect
+arms with \(\hat{\mu}_i(T) > \tau + \epsilon\) to be classified
+correctly, and arms with \(\hat{\mu}_i(T) < \tau - \epsilon\) to be
+rejected.
 
-\begin{theorem}[Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem4}
-Let $\nu \in \mathcal{M}_m$, where $\mathcal{M}_m$ is the set of uniquely identifiable bandit models described above.
-Assume that $\mathcal{P}$ satisfies the continuity conditions in Assumption 3.
-Any $\delta$-PAC algorithm on $\mathcal{M}_m$ satisfies, for $\delta \leq 0.15$:
+Indeed, we have
+\(\mathbb{E}(\mathcal{L}(T)) = P(S_{\tau + \epsilon} \cap \hat{S}_\tau^C \neq \emptyset \lor S_{\tau-\epsilon}^C \cap \hat{S}_{\tau} \neq \emptyset)\).
+But this just corresponds to
+\(P(\{\exists i: ((\mu_i < \tau-\epsilon) \land(\hat{\mu}_i \geq \tau)) \lor ((\mu_i > \tau + \epsilon) \land (\hat{\mu}_i < \tau)))\).
+Each of the two \((...)\lor(...)\) conditions corresponds to
+\(| \hat{\mu}_i - \mu_i | \geq \epsilon\). It follows that the expected
+loss can be rewritten as:
+\(\mathbb{E}(\mathcal{L}(T)) = P(\exists i, \exists s: |\hat{\mu}_{i,s} - \mu_i | \geq \epsilon) = P(\xi^C)\).
+This is exactly the probability of classifying at least one arm
+incorrectly which results in a loss of size 1.
+
+Thus we define as the favorable event as:
+
+\begin{equation} 
+\xi = \{\forall i, \forall s: | \hat{\mu}_{i,s} - \mu_i | \leq
+\epsilon\} 
+\end{equation}
+
+Furthermore, if we write
+\(\xi_{i,s} = \{ |\hat{\mu}_{i,s}-\mu_i | \leq \epsilon \}\), then the
+following holds by a union bound.
+
+\begin{equation} 
+P(\xi) = P(\cap_i \cap_s \xi_{i,s}) = 1 - P(\cup_i \cup_s
+\xi_{i,s}^C) \geq 1 - \sum_i \sum_s P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon)
+\label{theorem2_prob_fav_event} 
+\end{equation}
+
+Furthermore, for any \(i \in \{1, \dots, K\}\), for any
+\(s \in \{1, \dots, T(i)\}\), with \(X_{it}\) being the random sample
+from the R-sub-Gaussian distribution \(v_i\) at time \(t\):
+
+\begin{equation} 
+P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon) = P(| (\frac{1}{s}
+\sum_{t=1}^{s} X_{it} - \mu_i) | \geq \epsilon) = P(| \sum_{t=1}^{s} (X_{it} -
+\mu_i) | \geq s \epsilon) 
+\end{equation}
+
+where the latter can be bounded by a Hoeffding inequality:
+
+\begin{equation} 
+P(| \sum_{t=1}^{s} (X_{it} - \mu_i) | \geq s \epsilon) \leq
+2\exp (-\frac{\epsilon^2 s}{2 R^2}) \label{theorem2_hoeffding} 
+\end{equation}
+
+The Hoeffding inequality as used here is as follows:
+
+\begin{lemma}[Hoeffding's Inequality] \label{lemma:HoeffdingInequality}
+Consider $X_1, \dots, X_T$ independent random variables from R-sub-Gaussian distributions $\nu_i$ with mean $\mu_i$. Then, for any $\epsilon > 0$,
 
 \begin{equation*}
-\mathbb{E}_{\nu}[\tau] \geq \Big[ \sum_{a \in \mathcal{S}^*_m} \frac{1}{KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}^*_m} \frac{1}{KL(\nu_a, \nu_{[m]})} \Big] \der(1-\delta, \delta),
-\end{equation*}
-
-where $\der(x,y) := x \log(x/y) + (1-x) \log((1-x)/(1-y))$ is the binary relative entropy, with the convention that $\der(0,0) = \der(1,1) = 0$.
-\end{theorem}
-
-To proof this statement, we assume as before that the arms are ordered
-by their means decreasing in size. For a given \(\delta\)-PAC algorithm
-\(\mathcal{A} = ((A_t), \tau, \hat{S}_m)\), and under the continuity
-conditions, there exists for every arm \(a \in \{1, \dots, K\}\) an
-alternative model
-\(\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)\).
-In this alternative model, only arm \(a\) is modified in accordance with
-the continuity conditions. Modified in such a way that measured by the
-Kullback-Leibler divergence, the arm \(\nu_{m+1}\) is now closer to
-\(\nu_a\) than \(\nu_a'\) is to \(\nu_a\), if \(\mu_a > \mu_{m+1}\)
-(consequently, \(\mu_a' < \mu_{m+1}\)). On the other hand, if
-\(\mu_a < \mu_{m}\), then \(\nu_a'\) will be moved away from \(\nu_a\)
-just enough so that \(\nu_a\) is closer to \(\nu_m\) than to \(\nu_a'\)
-(consequently, \(\mu_a' > \mu_m\)). These changes in distribution make
-the original set of optimal arms, \(\{1,\dots,m\}\) no longer optimal
-under the alternative model \(\nu'\). Given that the algorithm returns
-\(\hat{S}_m\), we know that for the event
-\(\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})\) (which is element of the
-by the stopping time \(\tau\) induced \(\sigma\)-Algebra
-\(\mathcal{F}_{\tau}\)), that
-\(\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta\) and
-\(\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta\) (because fixed confidence
-\(\delta\)!).
-
-To now give the lower bound on the expected number of samples,
-\(\mathbb{E}_{\nu}[\tau]\), we employ the general lemma given by the
-authors for such changes in distribution in bandit models.
-
-\begin{lemma}[Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma1}
-Let $\nu$ and $\nu'$ be two bandit models with $K$ arms such that for all $a$, the distributions $\nu_a$ and $\nu_a'$ are mutually absolutely continuous.
-For any almost-surely finite stopping time $\sigma$ with respect to $(\mathcal{F}_t)$,
-
-\begin{equation*}
-\sum_{a=1}^{K} \mathbb{E}_{\nu} [N_a(\sigma)] \KL(\nu_a, \nu_a') \geq \sup_{\mathcal{E} \in \mathcal{F}_{\sigma}} \der (\mathbb{P}_{\nu}(\mathcal{E}), \mathbb{P}_{\nu'}(\mathcal{E})),
-\end{equation*}
-
-where $\der(x,y)$ is the binary relative entropy as defined above.
-\end{lemma}
-
-We can apply this lemma directly on the expected number of draws for
-each arm, \(\mathbb{E}_{\nu}[N_a]\). For each arm \(a\), we thus have
-\(\KL(\nu_a, \nu_a') \mathbb{E}_{\nu}[N_a] \geq \der (1-\delta, \delta)\).
-Using the definition of the alternative model above, we get for every
-small but fixed \(\alpha > 0\), for every arm \(a \in \{1, \dots, K\}\)
-and each arm \(b \in \{m+1, \dots, K\}\):
-
-\begin{equation*}
-\mathbb{E}_{\nu}[N_a] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_a, \nu_{m+1}) + \alpha}
-\end{equation*}
-
-and
-
-\begin{equation*}
-\mathbb{E}_{\nu}[N_b] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_b, \nu_{m}) + \alpha}.
-\end{equation*}
-
-We can then let \(\alpha \to 0\), sum the bounds on the individual arms
-to get the bound on the overall number of draws:
-
-\begin{equation*}
-\mathbb{E}_{\nu}[\tau] = \sum_{a=1}^K \mathbb{E}_{\nu}[N_a] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \der(1-\delta, \delta)
-\end{equation*}
-
-Given that we will be naturally interested in either very high or very
-low confidence of our algorithm, that is, \(P_\nu(\mathcal{E})\) is
-either close to 0 or 1, it is possible to use the following
-approximation to the binary relative entropy:
-
-\begin{equation}\label{bre_approx}
-\forall x \in [0,1], \quad \der(x,1-x) = \der(1-x,x) \geq \log \frac{1}{2.4x}
-\end{equation}
-
-And so the final lower bound can be written as
-
-\begin{equation*}
-\mathbb{E}_{\nu}[\tau] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
-\end{equation*}
-
-\includegraphics{kl_complexity_files/figure-latex/unnamed-chunk-1-1.pdf}
-
-Given this general lower bound for the sampling complexity, or expected
-number of draws, it makes sense to define the complexity of a Top-\(m\)
-bandit problem using the Kullback-Leibler divergence. After all, besides
-the number of arms and the experimenter-chosen confidence, it is just
-how close arms are with respect to each other in terms of
-Kullback-Leibler divergence that influences the sampling complexity. And
-in general, a problem requiring more samples is of course considered to
-be more complex (at least with respect to the samples, which is what
-needs to be optimized).
-
-Thus, following Kaufmann et al. (2016), define the complexity
-\(\kappa_C(\nu)\) for the fixed confidence setting as
-
-\begin{equation}
-\kappa_C(\nu) = \inf_{A \, \text{PAC}} \lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\nu}[\tau_{\delta}]}{\log \frac{1}{\delta}}.
-\end{equation}
-
-So if we were to plug in the lower bound on the sampling complexity, we
-would arrive at a complexity measure that basically depends only on the
-Kullback-Leibler measuring for each arm how far it is away from the
-border between the two groups of arms. To see this, consider the lower
-bound on the complexity measure given in Kaufmann et al. (2016):
-
-\begin{equation*}
-\kappa_C(\nu) \geq \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})}
-\end{equation*}
-
-Given this description, we can already note that an intuitive extension
-of this complexity notion to the thresholding bandit problem might
-involve replacing \(\mu_{[m]}\) and \(\mu_{[m+1]}\) by the actual
-threshold \(\tau\) (notation in Locatelli et al.) that divides the group
-above the threshold from the group below the threshold. In that case,
-the previously used \(\alpha\) might be very similar to the \(\epsilon\)
-used in Locatelli et al. (2016).
-
-To get there, however, at least two important steps remain. First, we
-need to define a complexity for the fixed budget problem. Second, we
-need to create algorithms that can match the lower bound.
-
-Kaufmann et al. are able to provide a bound on their complexity measure
-in the fixed budget case, however only in the case of \textbf{two-armed}
-bandit models. As demanded in their paper, a fixed-budget algorithm is
-called consistent if the failure probability
-\(p_t(\nu) := \mathbb{P}_{\nu}(\hat{S}_m \neq S^*_m)\) tends to zero as
-the number of samples goes to infinity. Also, define the complexity in
-the fixed-budget setting as follows:
-
-\begin{equation}
-\kappa_B(\nu) = \inf_{A \, \text{consistent}} \big(\lim_{t \to \infty} \sup - \frac{1}{t} \log p_t(\nu)\big)^{-1}.
-\end{equation}
-
-Given this definition, one can interpret the bound given in Theorem 12
-of Kaufmann et al. directly as a lower bound on the complexity
-\(\kappa_B(\nu)\) (note the inverse).
-
-\begin{theorem}[Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem12}
-Let $\nu = (\nu_1, \nu_2)$ be a two-armed bandit model such that $\mu_1 > \mu_2$. In the fixed-budget setting, any consistent algorithm satisfies:
-
-\begin{equation*}
-\lim_{t \to \infty} \sup - \frac{1}{t} \log p_t(\nu) \leq \inf_{(\nu_1', \nu_2') \in \mathcal{M}: \mu_1' < \mu_2'} \frac{\KL(\nu_1', \nu_1) + \KL(\nu_2', \nu_2)}{2}
-\end{equation*}
-\end{theorem}
-
-For a proof, consider first the two different bandit models, \(\nu\) and
-\(\nu'\), where we fix without loss of generality that \(a^* = 1\) is
-the best arm in \(\nu\), while \(a^* = 2\) in \(\nu'\). Note that in
-this case we don't necessarily try to fool the algorithm by a change of
-distribution. Indeed, we want the algorithm \(\mathcal{A}\) to be
-consistent for both problems. Since we are in the fixed-budget setting,
-the stopping time is fixed at \(\tau = t\). Even though the correct
-decision differs between the two problems, we focus on the event
-\(A = (\hat{S}_1 = 1)\). Given the formulation in Kaufmann et al.
-(2016), we have \(A \in \mathcal{F}_t = \mathcal{F}_{\tau}\). Now, we
-can apply Lemma 1 as before, as it in essense gives a measure of how
-different two bandit models are. Here, we want to know how different
-\(\nu\) is from \(\nu'\), and so, given we have only two arms,
-
-\begin{equation*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2', \nu_2) \geq \der(\mathbb{P}_{\nu'}(A),\mathbb{P}_{\nu}(A)))
-\end{equation*}
-
-The expectations were chosen with respect to \(\nu'\) in order to allow
-the for the following: We have \(p_t(\nu) = 1 - \mathbb{P}_{\nu}(A)\)
-and \(p_t(\nu') = \mathbb{P}_{\nu'}(A)\) (since \(A\) is wrong in
-\(\nu'\)). But since algorithm \(\mathcal{A}\) is consistent for both
-\(\nu\) and \(\nu'\), we know that there should exist some number of
-samples such that the probability of event \(A\) is bigger in setting
-\(\nu\) (where it is the correct decision), than in setting \(\nu'\)
-(where this would be a wrong decision and failure). Thus, for every
-\(\epsilon > 0\), there exists \(t_0(\epsilon)\) such that for all
-\(t \geq t_0(\epsilon)\),
-\(\mathbb{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)\). Consequently,
-if we plug in the bound of \(\epsilon\) for \(\mathbb{P}_{\nu'}(A)\),
-then
-
-\begin{align*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2', \nu_2) & \geq \der(\epsilon,1-p_t(\nu))) \\
-& = \epsilon \log \frac{\epsilon}{1-p_t(\nu)} + (1-\epsilon) \log \frac{1-\epsilon}{p_t(\nu)} \\
-& \geq (1-\epsilon) \log \frac{1-\epsilon}{p_t(\nu)} + \epsilon \log \epsilon.
-\end{align*}
-
-Let \(\epsilon\) go to zero so that
-
-\begin{align*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2', \nu_2)
-& \geq \log \frac{1}{p_t(\nu)} = -\log p_t(\nu).
-\end{align*}
-
-Dividing both sides by \(t\) and taking the limsup, we arrive at
-
-\begin{align*}
-\lim_{t \to 0} \sup - \frac{1}{t} \log p_t(\nu)
-& \leq \lim_{t \to 0} \sup \frac{1}{t} \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)] \KL(\nu_a', \nu_a) \\
-& \leq \max_{a=1,2} \KL(\nu_a', \nu_a),
-\end{align*}
-
-where the last line follows from the fact that the
-\(\frac{1}{t} \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)]\) part creates a
-weighted average of the two divergences \(\KL(\nu_a', \nu_a)\). As noted
-in Kaufmann et al. (2016), one arrives at the final result by choosing
-\(\mu_1'\), \(\mu_2'\) so that
-\(| \KL(\nu_1', \nu_1) - \KL(\nu_2', \nu_2) |\) is as small as possible.
-
-Note that while deriving the lower bound on the complexity measure, we
-have also derived the following lower bound on the failure probability
-for the two-armed fixed-budget bandit:
-
-\begin{equation*}
-p_t(\nu) \geq \exp \big(- \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)] \KL(\nu_a', \nu_a) \big)
-\end{equation*}
-
-or, to not rely on the share of samples attributed to each arm,
-
-\begin{equation*}
-p_t(\nu) \geq \exp \big(- \max_{a=1,2} \KL(\nu_a', \nu_a) \big).
-\end{equation*}
-
-\textbf{Mention something about the fact that we were not able to do
-this for more than 2 arms and top-m bandits. How could it be extended to
-that? How could it be extended to the threshold bandit?}
-
-As noted by Kaufmann et al. (2016), the advantage of this lower bound is
-that it makes the complexity in the fixed-confidence and the
-fixed-budget setting directly comparable. The disadvantage of course
-being that the result only holds for two-armed models. While the authors
-were not able to derive directly comparable lower bounds for the
-Top-\(m\) case, they did derive a first lower bound in the Gaussian case
-with equal variances. While we would like to move beyond Gaussian
-distributions in the work at hand, the idea for the proof might show a
-way of how the ideas can be transferred to the thresholding bandit
-problem. We first state the result and then discuss the proof.
-
-\begin{lemma}[Lemma 15, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma15}
-Let $\nu$ and $\nu'$ be two bandit models such that $S^*_m(\nu) \neq S*_m(\nu')$. Then
-
-\begin{equation*}
-\max \big( \mathbb{P}_{\nu}(S \neq S^*_m(\nu)), \mathbb{P}_{\nu'}(S \neq S^*_m(\nu')) \big) \geq \frac{1}{4} \exp \Big(-\sum_{a=1}^{K} \mathbb{E}_{\nu}[N_a] \KL(\nu_a, \nu_a') \Big).
+\mathbb{P} \Big( | \sum_{i = 1}^T (X_i - \mu_i) | \geq \epsilon \Big) \leq 2\exp \Big(\frac{-\epsilon^2}{2T R^2}\Big).
 \end{equation*}
@@
 
-The following theorem only holds in the case of Gaussian bandit models
-with equal known variance.
+Plugging equation \eqref{theorem2_hoeffding} back into equation
+\eqref{theorem2_prob_fav_event}, we get:
 
-\begin{theorem}[Theorem 17, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem17}
+\begin{equation}
+P(\xi) \geq 1 - \sum_i \sum_s P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon) \geq 1 - 2 \sum_i \sum_s \exp (-\frac{\epsilon^2 s}{2 R^2})
+\end{equation}
 
-Let $\mathcal{M}_m = \{\nu = (\nu_1, \dots, \nu_K): \nu_a = \mathcal{N}(\mu_a, \sigma^2), \mu_a \in \mathbb{R}, \mu_{[m]}\neq \mu_{[m+1]}\}.$ Furthermore, let $\nu$ be such that $\mu_1 > \dots > \mu_m > \mu_{m+1} > \dots > \mu_K$, and let
+Now, in order to match the performance of the lower bound on the
+expected loss derived in Theorem \ref{theorem:Locatelli2016Theorem1}, we
+will choose \(\epsilon = \sqrt{\frac{T \delta^2}{Hs}}\). Thus:
+
+\begin{equation}
+P(\xi) \geq 1 - 2 \sum_i \sum_s \exp (-\frac{\epsilon^2 s}{2 R^2}) = 1 - 2 \sum_i \sum_s \exp (-\frac{T \delta^2}{2 R^2 H}) \geq 1 - TK \exp(-\frac{T\delta^2}{2R^2H})
+\end{equation}
+
+Thus, we do not exactly get the bound from Locatelli et al. (2016)
+because we used the Hoeffding inequality instead of the martingale
+bound; but the the method should be clear.
+
+What is left now is to show that the favorable event still holds under
+the proposed \(\epsilon\), that is, we need to show that under
+\(P(\xi) \geq 1 - TK \exp(-\frac{T\delta^2}{2R^2H})\) we still reject
+arms that are under \(\tau - \epsilon\) and accept those above
+\(\tau + \epsilon\).
+
+\paragraph{Step 2: Lower Bound on Number of Pulls of Difficult
+Arm}\label{step-2-lower-bound-on-number-of-pulls-of-difficult-arm}
+
+In order to see that arms are correctly classified with large
+probability, we need to show that they are are pulled sufficiently
+often, that is, we have a degree of exploration for each arm \(i\) that
+allows us to identify its characteristics. To see this, rewrite the
+favorable event of a single arm as follows with \(s = T(i)\):
+
+\begin{equation}
+\xi_{i,s} = \{ |\hat{\mu}_{i,s}-\mu_i | \leq \epsilon \} = \{ |\hat{\mu}_{i,s} - \mu_i | \leq \sqrt{\frac{T \delta^2}{H T(i)}}\}
+\end{equation}
+
+To make sure that this deviation is small enough, we need to show that
+at time \(T\), all \(T(i)\) have a sufficient lower bound and thus all
+arms \(i\) have been explored sufficiently to classify correctly with
+probability larger \(TK \exp(-\frac{T\delta^2}{2R^2H})\).
+
+To start off, notice that due to the initialization of the APT
+algorithm, every \(T_i(T) \geq 1\). Furthermore, we have assumed that
+\(T>2K\). Now, at time \(T\), consider an arm \(k\) that has been pulled
+\(T_k(T) -1 \geq \frac{(T-K)}{H \Delta^2_k}\) times. That is, it has
+been pulled at least proportionally to it's contribution to the overall
+hardness of the problem \(H\). Recall
+\(H = \sum_{i=1}^K(|\mu_i - \tau|+\epsilon)^-2\) and
+\(\delta^2_i = (|\mu_i - \tau | + \epsilon)^2\). To see that such arm
+\(k\) exists, assume it does not. Then
 
 \begin{equation*}
-H +(\nu) = \sum_{a=1}^m \frac{2\sigma^2}{(\mu_a - \mu_{m+1})^2}, \quad H^-(\nu) = \sum_{a=m+1}^K \frac{2\sigma^2}{(\mu_m - \mu_a)^2} \quad
-and \quad
-H(\nu) = H^+(\nu) + H^-(\nu).
+T_i(T) - 1 < \frac{T-K}{H \Delta_i^2} \forall i
+\end{equation*}\begin{equation*}
+T- K = \sum_{i=1}^{K} T_i(T) - 1 < \sum_{i=1}^{K} \frac{T-K}{H \Delta_i^2} = \frac{T-K}{H \Delta_i^2} \sum_{i=1}^{K} \frac{1}{\Delta_i^2} = T-K
 \end{equation*}
 
-There exists $a \in {1, \dots, m}$ and $b \in \{m+1, \dots, K\}$ such that the bandit model $\nu^{[a,b]}$ described in Figure 4 (Kaufmann et al., 2016) satisfies $H(\nu^{[a,b]}) < H(\nu)$ and is such that
+which is a contradiction.
+
+Consequently, using the assumption \(T>2K\) from above, we have
 
 \begin{equation*}
-\max \big( p_t(\nu),p_t(\nu^{[a,b]})\big) \geq \frac{1}{4} \exp \big(-\frac{4t}{\bar{H}(\nu)}\big), \quad where \quad \bar{H}(\nu) = \frac{H(\nu) \min(H^+(\nu),H^-(\nu))}{H(\nu)+\min(H^+(\nu),H^-(\nu))}
+T_k(T) \geq T_k(T) - 1 \geq \frac{T-K}{H \Delta^2_k} = \frac{T}{2H\Delta_k^2}
 \end{equation*}
-\end{theorem}
 
-Given that we are again in the Top-\(m\) setting, the proof idea is
-similar to the proof of Theorem \ref{theorem:KaufmannEtAlTheorem4} in
-that we again consider problems where we switch arms around the limit
-seperating the two groups of arms as given implicitly by \(\mu_{[m]}\)
-and \(\mu_{[m+1]}\). The hope here being that these methods could be
-applied to the thresholding bandit problem where the threshold of course
-gives the limit between the arms above and below the threshold. As we
-have seen in chapter 1, this flip around the threshold was of course
-used in the proof of the lower bound in Theorem 1 of Locatelli et al.
-(2016). However, there, again, the distributions were assumed to be
-Gaussian. This brings the big advantage that the Kullback-Leibler
-divergence becomes symmetric, and the feedback can take values on all
-\(\mathbb{R}\). And by using the complexity measure \(H(\nu)\), it is
-also clear that there exists an arm that is undersampled with respect to
-its contribution to the overall complexity of the problem (or sampled
-exactly according to its contribution), which leads to leads to a
-convenient upper bound on this arms number of draws which is again
-employed in both the proof of Theorem
-\ref{theorem:KaufmannEtAlTheorem17} and in Locatelli et al. (2016). It
-is not clear yet, whether the same can also be done with other
-complexity measures.
+This states a lower bound on the amount of pulls \(T_k(t)\) for an arm
+\(k\) that contributes more than average to the overall hardness of the
+problem.
 
-We do not repeat the proof here for now.
+\paragraph{Step 3: Lower Bound on Number of Pulls of Simple
+Arm}\label{step-3-lower-bound-on-number-of-pulls-of-simple-arm}
 
-See p20!
+Next, we would like to derive bounds on the number of pulls of the
+remaining arms \(i\) at the time \(t\), the last pull of arm \(k\). To
+do so, consider that we are on the favorable event \(\xi\). For every
+arm \(i\), it holds:
 
-What remains is to present algorithms that are able to match the lower
-bounds derived so far.
+\begin{equation}
+|\hat{\mu}_i(t) - \mu_i | \leq \sqrt{\frac{T \delta^2}{HT_i(t)}} \label{step3_favorable_event} 
+\end{equation}
 
-\paragraph{Matching algorithm
-strategies}\label{matching-algorithm-strategies}
+As described in Locatelli et al., using the reverse triangle inequality,
+we can write
 
-Given those lower bounds, all that is left is to find algorithms which
-are able to match the complexity. Sadly, not straightforward for
-Bernoullis.
+\begin{IEEEeqnarray*}{rCl}
+|\hat{\mu}_i(t) - \mu_i | & = & | (\hat{\mu}_i(t) - \tau) - (\mu_i-\tau) |
+\\
+& \geq & | |\hat{\mu}_i(t) - \tau| - |\mu_i-\tau| |
+\\
+& = & | (|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i-\tau| - \epsilon) |
+\\
+& = & | \hat{\Delta}_i(t) - \Delta_i |
+\end{IEEEeqnarray*}
 
-Kaufmann et al. (2016) do not present algorithms matching the lower
-bound of Theorem \ref{theorem:KaufmannEtAlTheorem17}. They do consider
-algorithms that connect to Theorem \ref{theorem:KaufmannEtAlTheorem4}
-and Theorem \ref{theorem:KaufmannEtAlTheorem12}.
-
-Given that Locatelli et al. (2016), and thus the problem we mostly
-consider in this thesis, is in the fixed-budget setting, we are most
-interested in the matching strategies for Theorem
-\ref{theorem:KaufmannEtAlTheorem12}. However, given that the lower bound
-applies only to two-armed bandits, the algorithms are of limited
-practical interest. Furthermore, the algorithms proposed require
-knowledge that is in general not available upfront.
-
-For the example of Gaussian distributions, the knowledge of the
-(potentially different) variance is assumed which enables a strategy
-that pulls each arm proportional to its variance.
-
-Even worse is the case of Bernoulli two-armed bandit models where the
-proposed algorithm requires knowledge about the true parameters of the
-distributions. That this limits the practical interest is also noted by
-the authors of Kaufmann et al. (2016). Thus, they suggest to use uniform
-sampling strategies in the case of two-armed Bernoulli bandits, and show
-that there is not much to be lost by doing so.
-
-Thus, Kaufmann et al. (2016) join a number of other papers like Audibert
-et al. (2010) and Kaufmann and Kalyanakrishnan (2013) which struggle to
-find matching strategies in the fixed-budget setting that do not rely on
-knowledge of parameters or the complexity of the problem.
-
-In contrast, Kaufmann et al. (2016) are able to show that their
-complexity measure derived for the fixed-confidence setting,
-\(\kappa_C(\nu)\), can be upper-bounded using the upper bound of the
-sample complexity (number of pulls) given for the KL-LUCB algorithm in
-Kaufmann and Kalyanakrishnan (2013). Consequently, in the case of
-exponential family bandits, the complexity \(\kappa_C(\nu)\) is bounded
-as given in equation (6) in Kaufmann et al. (2016):
+Consequently, we can again employ the hardness of the task to start
+deriving bounds on the number of pulls of the arms:
 
 \begin{equation*}
-\sum_{a \in S^*_m} \frac{1}{K(\theta_a, \theta_{[m+1]})} + \sum_{a \notin S^*_m} \frac{1}{K(\theta_a,\theta_{[m]})} \leq \kappa_C(\nu) \leq 24 \min_{\theta \in [\theta_{[m+1]},\theta_{[m]}]} \sum_{a=1}^{K} \frac{1}{K^*(\theta_a, \theta)},
+| \hat{\Delta}_i(t) - \Delta_i | \leq |\hat{\mu}_i(t) - \mu_i | \sqrt{\frac{T \delta^2}{HT_i(t)}}
 \end{equation*}
 
-where \(K(\theta, \theta') = \KL(\nu_{\theta}, \nu_{\theta'})\) for
-\((\theta, \theta') \in \Theta^2\) was defined as the shorthand for the
-Kullback-Leibler divergence for two distributions from the exponential
-family parameterized by \(\theta\) and \(\theta'\) respectively.
-\(K^*(\theta,\theta') = K(\theta^*, \theta)\) is the Chernoff
-distribution between the two distributions, where \(\theta^*\) is chosen
-so that \(K(\theta^*,\theta) = K(\theta^*, \theta')\).
+From this, we get
 
-\subsubsection{Optimal Best Arm
-Identification}\label{optimal-best-arm-identification}
+\begin{IEEEeqnarray*}{rlCrl}
+\Delta_i - \sqrt{\frac{T \delta^2}{HT_i(t)}} & \leq & \hat{\Delta}_i(t) & \leq & \Delta_i + \sqrt{\frac{T \delta^2}{HT_i(t)}}
+\end{IEEEeqnarray*}
 
-A very similar application of the KL divergence has been given in
-Garivier and Kaufmann to derive a lower bound on the sample complexity
-in the case of best arm identification. In particular, the
-transportation Lemma 1 is used again. And a matching algorithm for
-\(K \geq 2\) arms is proposed.
+and in particular for the arm \(k\) discussed above
 
-Talk about: - Not a simple sum of squares - Idea of algorithm: Equalize
-the probability of all wrong decisions
+\begin{IEEEeqnarray}{rlCrl}
+\Delta_k - \sqrt{\frac{T \delta^2}{HT_k(t)}} & \leq & \hat{\Delta}_k(t) & \leq & \Delta_k + \sqrt{\frac{T \delta^2}{HT_k(t)}} \label{delta_hat_k_bounds}
+\end{IEEEeqnarray}
 
-In Garivier and Kaufmann (2016), the authors are able to derive a
-somewhat similar lower bound on the sample complexity of a \(K\)-armed
-bandit in the single best arm identification problem with fixed
-confidence. Additionally, they provide a \(\delta\)-PAC algorithm
-achieving said bound asymptotically.
+To bound \(T_i(t)\), it is helpful to compare \(\Delta_i\) and
+\(\Delta_k\) at time \(t\). From the definition of the APT algorithm, we
+know that since arm \(k\) has been pulled at time \(t\) (``Pull arm
+\(I_{t+1} = \arg \min_i \mathcal{B}_i (t+1)\)''):
 
-In particular, the authors pick up Lemma 1 from Kaufmann et al. (2016)
--- which we discussed above -- to derive the lower bound. While
-presenting these results, we try to stick as much as possible with the
-notation used so far. In particular, we let for distributions
-\(\nu_{\theta}\) from a canonical exponential family, which can be
-parameterized by its mean \(\stackrel{.}{b}(\theta) = \mu\) and thus be
-written as \(\nu^{\mu}\); for these, we continue to write the
-Kullback-Leibler divergence as
+\begin{IEEEeqnarray*}{rCl}
+\mathcal{B}_k(t) & \leq & \mathcal{B}_i(t)
+\\
+\sqrt{T_k(t)} \hat{\Delta}_k(t) & \leq & \sqrt{T_i(t)} \hat{\Delta}_i(t)
+\end{IEEEeqnarray*}
+
+Thus, every arm \(i\) has a lower bound on it's number of pulls given by
+the lower bound for arm \(k\) proportional with it's inverse relative
+estimated hardness \(\hat{\Delta}_k(t) / \hat{\Delta}_i(t)\). We can
+easily derive a lower bound for the left hand side by plugging in
+\eqref{delta_hat_k_bounds}:
+
+\begin{IEEEeqnarray}{rCl}
+\sqrt{T_k(t)} (\Delta_k - \sqrt{\frac{T \delta^2}{HT_k(t)}}) & \leq & \mathcal{B}_k(t) 
+\\
+\sqrt{\frac{T}{2H\Delta_k^2}} (\Delta_k - \sqrt{2}\Delta_k \delta) & = & \sqrt{\frac{T}{H}} (\frac{1}{\sqrt{2}} - \delta)
+\\
+& \leq & \mathcal{B}_k(t)
+\end{IEEEeqnarray}
+
+since \(T_k(t) \geq T/(2H\Delta^2_k)\) and
+\(\sqrt{T \delta^2 / (HT_k(t))} \geq \sqrt{T \delta^2 / (H\frac{T}{2H \Delta^2_k})} = \sqrt{2}\Delta_k \delta\).
+
+Next, upper bound \(\mathcal{B}_i(t)\). In contrast to \(T_k(t)\), there
+is no lower bound for \(T_i(t)\) available yet that we could plug in.
+Thus we derive:
+
+\begin{IEEEeqnarray*}{rCl}
+\mathcal{B}_i(t) & = & \sqrt{T_i(t)} \hat{\Delta}_i(t) 
+\\
+& \leq & \sqrt{T_i(t)} (\Delta_i + \sqrt{\frac{T \delta^2}{H T_i(t)}})
+\\
+& = & \sqrt{T_i(t)} \Delta_i + \delta \sqrt{\frac{T}{H}}
+\end{IEEEeqnarray*}
+
+Combining the two bounds, we get a lower bound on the pulls for every
+other arm \(i\):
+
+\begin{IEEEeqnarray*}{rCl}
+\Delta_i \sqrt{T_i(t)} + \delta \sqrt{\frac{T}{H}} & \geq & (\frac{1}{\sqrt{2}} - \delta) \sqrt{\frac{T}{H}}
+\\
+\sqrt{T_i(t)} & \geq & (\frac{1}{\sqrt{2}} - 2\delta) \sqrt{\frac{T}{H}} \frac{1}{\Delta_i}
+\\ 
+& & \text{(choose $2\delta > 1 / \sqrt{2}$ such that RHS is greater 0)}
+% \\
+% T_i(t) & \geq & (\frac{1}{2} - 2\sqrt{2} \delta + 4\delta^2) \underbrace{\frac{T}{H} \frac{1}{\Delta_i^2}}_\text{$i$'s share of the budget}
+% \\
+% T_i(t) & \geq & (1 - 4 \sqrt{2} \delta + 8\delta^2) \frac{T}{2H} \frac{1}{\Delta_i^2}
+\end{IEEEeqnarray*}
+
+\paragraph{Conclusion}\label{conclusion}
+
+As stated before, we require the lower bound on \(T_i(t)\) in order to
+show that
+\(|\hat{\mu}_i(t) - \mu_i | \leq \sqrt{frac{T \delta^2}{H T_i(t)}}\)
+holds for all \(i\). So if we now simply plug in the derived lower
+bound, we get:
 
 \begin{equation*}
-\KL(\mu, \mu') = \KL(\nu^{\mu},\nu^{\mu'}) = \KL(\nu_{\theta},\nu_{\theta'}) = \KL(\nu, \nu')
+\mu_i - \Delta_i (\frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}) \leq \hat{\mu}_i(t) \leq \mu_i + \Delta_i (\frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta})
 \end{equation*}
 
-while \(d(x,y)\) continues to represent the binary relative entropy.
-
-As we will consider only problems with exponential family distributions,
-the distributions can be parameterized by their means. Therefore, if we
-let \(\mathcal{S}\) to be a set of bandit models with \(K\)
-distributions each, then each model is fully defined by a vector
-\(\bm{\mu} = (\mu_1, \dots, \mu_K)\). Assume that every
-\(\bm{\mu} \in \mathcal{S}\) has a unique maximum given by
-\(a^*(\bm{\mu})\) such that
-\(\mu_{a^*} > \max_{a \neq a^*(\bm{\mu})} \mu_a\). In order to fix the
-confidence, we specify the risk \(\delta\). The strategies corresponding
-to this risk are called \(\delta\)-PAC if for every
-\(\bm{\mu} \in \mathcal{S}\),
-\(\mathbb{P}_{\bm{\mu}}(\tau_{\delta} < \infty) = 1\) (the strategy ends
-surely after a finite number of samples) and
-\(\mathbb{P}_{\bm{\mu}}(\hat{a}_{\tau_{\delta}} \neq a^*) \leq \delta\)
-(the probability of picking not the optimal arm is smaller than the
-fixed risk). As in Garivier and Kaufmann (2016), we introduce the set of
-problems for which the optimal arm is different from the one in
-\(\bm{\mu}\):
+and with \(\lambda := (\frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}) > 0\):
 
 \begin{equation*}
-\text{Alt}(\bm{\mu}) := \{\bm{\lambda} \in \mathcal{S}: a^*(\bm{\lambda}) \neq a^*(\bm{\mu})\}
+\mu_i - \Delta_i \lambda \leq \hat{\mu}_i(t) \leq \mu_i + \Delta_i \lambda
 \end{equation*}
 
-where \(\bm{\lambda}\) is the vector of means defining the distributions
-of the alternative problem to \(\bm{\mu}\). Lastly, we have the set of
-probability distributions on the arms \(\mathcal{A}\):
-\(\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}\).
-\marginpar{Give more intuition for what these probability distributions are}
-We are now ready to state the theorem.
+Under this formulation on \(\xi\), do we accept arms with
+\(\mu_i \geq \tau + \epsilon\)? For these arms holds that
+\(\Delta_i = \mu_i - \tau + \epsilon\). Consequently:
 
-\begin{theorem}[Theorem 1, Garivier and Kaufmann, 2016] \label{theorem:GarivierKaufmannTheorem1}
-Let $\delta \in (0,1)$. For any $\delta$-PAC strategy and any bandit model $\bm{\mu} \in \mathcal{S}$,
+\begin{IEEEeqnarray*}{rCl}
+\mu_i - (\mu_i - \tau + \epsilon) \lambda & \leq & \hat{\mu}_i(t) 
+\\ 
+\hat{\mu}_i(t) & \geq & \tau \lambda + \mu (1-\lambda) - \epsilon \lambda
+\end{IEEEeqnarray*}
 
-\begin{equation*}
-\mathbb{E}_{\bm{\mu}} [\tau_{\delta}] \geq T^*(\bm{\mu}) \text{\em{d}}(\delta,1-\delta),
-\end{equation*}
+The arms are accepted if
 
-where
+\begin{IEEEeqnarray*}{rCl}
+\hat{\mu}_i(t) - \epsilon & \geq & 0
+\end{IEEEeqnarray*}
 
-\begin{equation} \label{eq:GarivierKaufmann_Theorem1_Game}
-T^*(\bm{\mu})^{-1} := \sup_{w \in \Sigma_K} \inf_{\bm{\lambda} \in \text{\em{Alt}}(\bm{\mu})} \left( \sum_{a=1}^K w_a \text{\em{KL}}(\mu_a, \lambda_a)\right).
-\end{equation}
-\end{theorem}
+Or equivalently as long as
 
-And so we see that the two bounds on the sample complexity (one for
-Top-\(m\), one for best arm identification) differ only in the way that
-they build the sum of Kullback-Leibler divergences over the \(K\) arms.
-In contrast to Theorem \ref{theorem:KaufmannEtAlTheorem4}, here the
-contribution of each arm through its KL-divergence is weighted. The
-difference is that while we were able to very clearly describe the
-change of distribution in the Top-\(m\) case for each arm -- for each
-arm, we specified an alternative model that yields a new set of \(m\)
-optimal arms -- we now consider all alternative models that yield a
-different best arm than the model \(\bm{\mu}\). In the previous theorem,
-we sum over the complexity of each individual arm, as the change in
-distribution only ever touches one arm, thus leading to a KL-divergence
-of 0 for the other arms while still changing the optimal set. Here, we
-consider all instances of alternative models \(\bm{\lambda}\), and thus
-also those in which several arms are modified (and thus have a
-KL-divergence unequal 0 in the result of Lemma 1).
-
-\emph{Proof of Theorem \ref{theorem:GarivierKaufmannTheorem1}}: As
-stated before, we let \(\delta \in (0,1)\),
-\(\bm{\mu} \in \mathcal{S}\), and only consider \(\delta\)-PAC
-strategies. As before, \(N_a(t)\) describes the random number of pulls
-of arm \(a\) until time \(t\), for all \(t\geq 1\). Again, Lemma
-\ref{theorem:KaufmannEtAlLemma1} states how the failure probability
-\(\delta\) relates to the expected number of draws of each arm given two
-models which differ in their optimal arm, and where it is evaluated
-based on the Kullback-Leibler divergence for each pair of arms how much
-the two models differ:
-
-\begin{equation*}
-\forall \lambda \in \mathcal{S}: a^*(\lambda) \neq a^*(\mu), \sum_{a=1}^K \KL(\mu_a,\lambda_a)\mathbb{E}_{\bm{\mu}}[N_a(\tau_{\delta})] \geq \d(\delta, 1- \delta).
-\end{equation*}
-
-As mentioned, we now do not consider a specific alternative for each
-arm, but instead look at the infimum over all the possible alternatives,
-and use the fact that
-\(\mathbb{E}_{\bm{\mu}}[\tau_{\delta}] = \sum_{a=1}^K \mathbb{E}_{\bm{\mu}}[N_a(\tau_{\delta})]\):
-
-\begin{align*}
-\der(\delta, 1-\delta) & \leq \inf_{\lambda \in \text{Alt}(\bm{\mu})} \mathbb{E}_{\bm{\mu}}[\tau_{\delta}] \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[\tau_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
-& = \mathbb{E}_{\bm{\mu}}[\tau_{\delta}] \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[\tau_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
-& \leq \mathbb{E}_{\bm{\mu}}[\tau_{\delta}] \sup_{w \in \Sigma_K} \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K w_a \KL(\mu_a, \lambda_a)\Big).
-\end{align*}
-
-As stated in Garivier and Kaufmann (2016), the term
-\(\frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[\tau_{\delta}]}\)
-gives the fraction of draws each arm receives. This value, however,
-depends on the used algorithm. To make it hold for any \(\delta\)-PAC
-algorithm, it is replaced by the supremum over \(\Sigma_K\), which is
-the distribution over these fractions for any \(\mathcal{A}\), that is,
-for any \(\delta\)-PAC strategy.
-
-This lower bound can be interpreted as a Minimax game, where the
-experimenter has to choose the share of samples he attributes to each
-arm in a way that is optimal given that nature will respond and choose
-the most difficult alternative model given his weights. Thus, to make
-the lower bound practical, it is a matter of finding the optimal weights
-\(w^*(\bm{\mu})\). This step did not occur in the previous lower bound,
-as the alternative models were made specific by changing the
-distribution of one arm with respect to the ``border'' between the two
-groups of arms.
-
-In any case, the existence of the optimal weights suggests an algorithm
-that keeps track of the share of samples that is attributed to each arm
-and makes sure that it stays close to the optimum until some decision
-rule assures that the \(\delta\)-PAC condition is fulfilled.
-
-And so by assuring the reader that there are ways to compute \(w_a^*\)
-and \(T^*\) given \(\bm{\mu}\) (see chapter 2.2 in Garivier and Kaufmann
-(2016)), we can now introduce the \emph{Track-and-Stop} strategy given
-in Garivier and Kaufmann (2016) that is able to match the lower bound by
-the intuition given above.
-
-When going from theory to algorithm, the obvious problem is of course
-that we do no longer know \(\bm{\mu}\) and thus cannot simply calculate
-the optimal weights. Instead, we are estimating the maximum likelihood
-estimates \(\hat{\mu}(t) = (\hat{\mu}_1(t), \dots, \hat{\mu}_K(t))\) of
-the true mean at the current round \(t\) and need to base our weights
-based on these. It is however problematic to rely on these sample means
-as we are inherently unsure about them. And so wrong estimates, which
-naturally occur most easily in the beginning when not many samples have
-been pulled, are prone to lead to wrong weights. Thus, if a wrong
-estimate \(\hat{\mu}_a\) for arm \(a\) leads to a small weight \(w_a\),
-then neither the estimate nor the weight will be correct soon. Thus,
-Kaufmann and Garivier conclude that ``a naive plug-in sampling rule
-sometimes fails''. They propose to enforce a certain minimum level of
-exploration to make sure that arms that erroneously received a very
-small weight will be further explored regardless.
-
-A very intuitive fix to this problem is the solution proposed in Lemma 8
-of Garivier and Kaufmann (2016), with their \(D-Tracking\) rule.
-Basically, whenever an arm has received a very low number of pulls
-\(N_a(t)\) given the number of iterations so far, \(t\) and the number
-of arms \(K\) that have to share the samples, pull the arm that has
-received the smallest amount of samples so far. Else, pull the arm which
-number of pulls so far \(N_a(t)\) is the furthest away from what its
-optimal share \(t\cdot w^*_a(\hat{\bm{\mu}}(t))\) would be. Given this
-sampling rule, the authors can show in their Proposition 9 that the
-empirical proportion of draws converges in probability to the optimal
-weights given the true means.
-
-When combining this sampling rule with an appropriate stopping rule, the
-authors are able to prove in Theorem 14 an upper bound on the expected
-sampling complexity \(\mathbb{E}_{\mu}[\tau_{\delta}]\). The stopping
-rule ensures that the algorithm explores sufficiently to promise a risk
-smaller than \(\delta\), while stopping as soon as possible. Given that
-the sampling rule is independent of this stopping rule, the rule boils
-down to a statistical test at every iteration and thus is a sequential
-test based on the current estimate of \(\hat{\bm{\mu}}\). The Chernoff's
-Stopping Rule proposed in Garivier and Kaufmann (2016) calculates for
-each arm \(a\in \mathcal{A}\) the Generalized Likelihood Ratio statistic
-with every arm \(b \in \mathcal{A}^{\setminus a}\), which for
-\(\hat{\mu}_a(t) \geq \hat{\mu}_b(t)\) can be written as
-
-\begin{equation*}
-Z_{a,b}(t) = - Z_{b,a} = N_a(t) \KL(\hat{\mu}_a(t),\hat{\mu}_{a,b}(t)) + N_b(t) \KL(\hat{\mu}_{b}(t), \hat{\mu}_{a,b}(t)),
-\end{equation*}
-
-where
-
-\begin{equation*}
-\hat{\mu}_{a,b}(t) := \frac{N_a(t)}{N_a(t) + N_b(t)}\hat{\mu}_a + \frac{N_b(t)}{N_a(t) + N_b(t)}\hat{\mu}_b.
-\end{equation*}
-
-Consequently, a sensible idea for a stopping rule would be that there
-has to be an arm \(a \in \mathcal{A}\) for which
-\(Z_{a,b} \geq 0 \forall b \in \mathcal{A}^{\setminus a}\) (which is
-always fulfilled if there is a uniquely best arm), and, additionally, we
-demand that for this arm the smallest of the \((K-1)\) test statistics
-has to be larger than an exploration threshold \(\beta(t, \delta)\).
-Consequently, the final number of samples \(\tau_{\delta}\) of an
-algorithm is given by:
-
-\begin{equation*}
-\tau_{\delta} = \inf \{t \in \mathbb{N}: \exists a \in \mathcal{A}, \forall b\in \mathcal{A}^{\setminus a}, Z_{a,b}(t) > \beta(t, \delta)\}
-\end{equation*}
-
-Demanding that the optimal exploration threshold increases in rounds
-\(t\) (if we have more samples, require more certainty; also, punish for
-failing previous tests) and decreases in the risk \(\delta\), and does
-so at a diminishing rate, the optimal threshold derived in Theorem 10 of
-Garivier and Kaufmann (2016) makes sense intuitively:
-
-\begin{equation*}
-\beta(t, \delta) = \log \Big(\frac{2t(K-1)}{\delta}\Big).
-\end{equation*}
-
-With this, we can state the final theorem of the chapter, which gives
-the upper bound matching the lower bound in Theorem
-\ref{theorem:GarivierKaufmannTheorem1} for small risk values \(\delta\)
-using the D-Tracking rule and Chernoff's stopping rule with the
-exploration term given in the previous equation:
-
-\begin{theorem}[Theorem 14, Garivier and Kaufmann, 2016] \label{theorem:GarivierAndKaufmannTheorem14}
-Let $\bm{\mu}$ be an exponential family bandit model.
-Let $\alpha \in [1, e/2]$ and $r(t) = O(t^{\alpha})$.
-Using Chernoff's stopping rule with $\beta(t,\delta) = \log(r(t)/\delta)$ and the sampling rule C-Tracking or D-Tracking,
-
-\begin{equation*}
-\lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\bm{\mu}}[\tau_{\delta}]}{\log(1/\delta)} \leq \alpha T^*(\mu).
-\end{equation*}
-\end{theorem}
-
-\subsubsection{Conclusion of Complexity of Best Arm
-Identification}\label{conclusion-of-complexity-of-best-arm-identification}
-
-Overall, the two papers presented in this chapter make significant
-contributions to identifying the top-\(1\) or the top-\(m\) arms in a
-multi-armed bandit setting. Their contribution is primarily based on
-including the Kullback-Leibler divergence in the derivation of bounds
-and the matching algorithms and thus going beyond a sum of squared gaps
-which is most practical only in the case of Gaussian distributions.
-While the contribution in the fixed-budget setting was limited to the
-two-armed bandit case, the authors derive general lower bounds in the
-fixed-confidence setting which are primarily based on Lemma
-\ref{theorem:KaufmannEtAlLemma1}. Lemma \ref{theorem:KaufmannEtAlLemma1}
-is able to measure the ``transportation cost'' (see Garivier and
-Kaufmann, 2016) of moving from one distribution to another one in terms
-of Kullback-Leibler divergence. Using the information from the lower
-bound of how well any \(\delta\)-PAC algorithm can potentially be, the
-authors design algorithms matching these lower bounds. In the case of
-Top-\(m\) identification, a simple application of the existing KL-LUCB
-algorithm works. In the case of best arm identification, the lower bound
-provides a way of calculating the optimal proportions in which the arms
-need to be pulled. Consequently, a matching algorithm can be set up so
-that it draws arms in these proportions, and so that it is robust
-against estimation errors of the plug-in estimates. Combining this
-sampling rule with an appropriate stopping rule makes for a
-\(\delta\)-PAC algorithm that matches the lower bound, where the upper
-bound in Theorem \ref{theorem:GarivierAndKaufmannTheorem14} matches the
-lower bound from Theorem \ref{theorem:GarivierKaufmannTheorem1} using
-equation \eqref{bre_approx}.
+\begin{IEEEeqnarray*}{rCl}
+\tau \lambda + \mu(1-\lambda) - \epsilon \lambda - \tau & \geq & 0
+\\
+\lambda & \leq & \frac{1}{2}
+\end{IEEEeqnarray*}
 

### 2017-06-29 AugUCB/Experiment_Documentation.Rmd
Scripts for calibrating algorithms

---
title: "Experiment Documentation"
author: "Tim Radtke"
date: "6/26/2017"
output: html_document
---

```{r, echo = FALSE}
current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
```

# First Experiment

Just as in Locatelli et al. (2016).

```{r, echo = FALSE}
mean_loc <- c(0.1, 0.1, 0.1, 
              0.35, 0.45, 0.55, 0.65,
              0.9, 0.9, 0.9)
tau_loc <- 0.5
epsilon_loc <- 0.1
```

While $\tau = 0.5$ and $\epsilon = 0.1$, we have 10 arms with the following means:

```{r, echo = FALSE}
mean_loc
```

Let's plot just the performance of APT and BUCB over 5000 simulations. We observe that APT (blue) and BUCB_squared (orange) perform extremely similar, while the simple BUCB (red) cannot keep up after about 200 observations.

```{r, echo = FALSE}
load(paste0(current_path, "loc_comp_APT.Rda"))
load(paste0(current_path, "loc_comp_BUCB.Rda"))
load(paste0(current_path, "loc_comp_BUCB_squared.Rda"))

plot(c(0,1000), c(0, -10), type = "n")
lines(log(loc_comp_APT), col = "blue")
#lines(log(loc_comp_UNIFORM), col = "black")
#lines(log(loc_comp_PI), col = "darkgreen")
#lines(log(loc_comp_TTS), col = "lightgreen")
lines(log(loc_comp_BUCB), col = "red")
lines(log(loc_comp_BUCB_squared), col = "orange")
#lines(log(loc_comp_KL), col = "lightblue")
#lines(log(loc_comp_KL_not_tau), col = "blue")
#lines(log(loc_comp_KL_horizon), col = "darkblue")
#lines(log(loc_comp_KL_horizon2), col = "darkred")
#lines(log(loc_comp_KL_horizon1), col = "red")
```

The next table shows how often each algorithm pulls each arm. As is to be expected, the arms above and below the threshold are pulled nearly perfectly symmetrically, as the threshold is at 0.5. Furthermore, it is obvious where APT and BUCB have their differences. BUCB clearly focuses on the two arms which are within the epsilon interval, and allocates respectively 40 observations less than APT to the two arms that are close to the epsilon interval but outside. Thus likely explaining the worse performance over time. This behavior is much less dramatic for BUCB_squared, where the two critical arms only receive 6 observations less respectively. However, there is no reason to believe at this point that BUCB_squared could be superior to APT.

```{r, echo = FALSE}
library(plyr)
load(paste0(current_path, "loc_APT.Rda"))
load(paste0(current_path, "loc_BUCB.Rda"))
load(paste0(current_path, "loc_BUCB_squared.Rda"))
#loc_UNIFORM_as <- colMeans(ldply(loc_UNIFORM, function(x) table(x$arm_sequence)))
loc_APT_as <- colMeans(ldply(loc_APT, function(x) table(x$arm_sequence)))
#loc_PI_as <- colMeans(ldply(loc_PI, function(x) table(x$arm_sequence)))
#loc_TTS_as <- colMeans(ldply(loc_TTS, function(x) table(x$arm_sequence)))
loc_BUCB_as <- colMeans(ldply(loc_BUCB, function(x) table(x$arm_sequence)))
loc_BUCB_squared_as <- colMeans(ldply(loc_BUCB_squared, function(x) table(x$arm_sequence)))
#loc_KL_as <- colMeans(ldply(loc_KL, function(x) table(x$arm_sequence)))
#loc_KL_not_tau_as <- colMeans(ldply(loc_KL_not_tau, function(x) table(x$arm_sequence)))
#loc_KL_horizon_as <- colMeans(ldply(loc_KL_horizon, function(x) table(x$arm_sequence)))

round(data.frame(loc_APT_as, loc_BUCB_as, loc_BUCB_squared_as))
```
```{r, echo = FALSE}
arm_seq_res_APT <- data.frame(t(laply(loc_APT, function(x) x$arm_sequence)))
library(tidyr)
library(dplyr)
#arm_seq_table <- arm_seq_res %>% tbl_df() %>% mutate(index = 1:1000) %>%
#  gather(key = iter, value = arm, -index) %>%
#  group_by(index, arm) %>% summarize(count = n())

library(ggplot2)
arm_seq_res_APT %>% tbl_df() %>% mutate(index = 1:1000) %>%
  gather(key = iter, value = arm, -index) %>%
  filter(index > 10) %>%
  ggplot(aes(index, arm)) + geom_count(aes(size = ..prop.., group = index)) +
  scale_size_area(max_size = 10)
#ggplot(arm_seq_table[11:9910,], aes(index, arm)) + geom_tile(aes(fill = count))

arm_seq_res_BUCB_squared <- data.frame(t(laply(loc_BUCB_squared, function(x) x$arm_sequence)))
arm_seq_res_BUCB_squared %>% tbl_df() %>% mutate(index = 1:1000) %>%
  gather(key = iter, value = arm, -index) %>%
  filter(index > 10) %>%
  ggplot(aes(index, arm)) + geom_count(aes(size = ..prop.., group = index)) +
  scale_size_area(max_size = 10)

```

# Experiment 2: Low threshold

Again 5000 simulations à 1000 iterations. We have $\tau = 0.05$, $\epsilon = 0.005$, and the following means:

```{r, echo = FALSE}
mean_loc3 <- c(0.001, 0.005, 0.01, 0.015,
               0.0475, 0.0525,
               0.085, 0.09, 0.095, 0.099)
tau_loc3 <- 0.05
epsilon_loc3 <- 0.005

mean_loc3
```

Interestingly, most algorithms we initially thought of as extensions start to fail hard in this case. (Darkblue is KL, lightblue is KL with epsilon. Darkgreen is PI, lightgreen is TTS)

```{r, echo = FALSE}
load(paste0(current_path, "loc3_comp_APT.Rda"))
load(paste0(current_path, "loc3_comp_UNIFORM.Rda"))
load(paste0(current_path, "loc3_comp_PI.Rda"))
load(paste0(current_path, "loc3_comp_TTS.Rda"))
load(paste0(current_path, "loc3_comp_KL.Rda"))
load(paste0(current_path, "loc3_comp_KL_horizon1.Rda"))

plot(c(0,1000), c(0, -4), type = "n")
lines(log(loc3_comp_UNIFORM), col = "black")
lines(log(loc3_comp_APT), col = "red")
lines(log(loc3_comp_PI), col = "darkgreen")
lines(log(loc3_comp_TTS), col = "lightgreen")
#lines(log(loc3_comp_BUCB), col = "orange")
#lines(log(loc3_comp_BUCB_squared), col = "darkorange")
#lines(log(loc3_comp_BUCB_cubic), col = "violet")
lines(log(loc3_comp_KL), col = "darkblue")
lines(log(loc3_comp_KL_horizon1), col = "lightblue")
```

When we look at how often the algorithms pull each arm, we get a hint on what the problem is. The following table shows that the biggest difference between APT and all other adaptive algorithms is that APT pulls arms below the threshold (thus very close to zero mean) more often than those above the threshold, while all other algorithms try to do the opposite. They focus on the arms for which it is more likely to get successes, and which don't accumalate on a short interval due to the 0 lower limit.

Why do PI and TTS focus on arm above the threshold? The other arms' posteriors are heavily jammed below the threshold and barely croach above tau. At first it seems to make sense that we want to focus on arms that give more than just zeroes. But as long as we have received zeroes exclusively from an arm, we can basically not say anything about it. So it makes sense to try to collect more information about it. A similar interpretation is reached when considering the Kullback-Leibler based methods.

When calculating the KL divergence, we want to pull the arm next that minimizes the distance to tau (+- epsilon). However, as long as the observations are all zero, the estimated mean is zero and thus the KL divergence is ill defined. And so the arms are not pulled. According to the KL divergence, the distance from any other density is infinite.

```{r, echo = FALSE}
load(paste0(current_path, "loc3_APT.Rda"))
load(paste0(current_path, "loc3_UNIFORM.Rda"))
load(paste0(current_path, "loc3_PI.Rda"))
load(paste0(current_path, "loc3_TTS.Rda"))
load(paste0(current_path, "loc3_KL.Rda"))
load(paste0(current_path, "loc3_KL_horizon1.Rda"))
load(paste0(current_path, "loc3_BUCB.Rda"))
load(paste0(current_path, "loc3_BUCB_squared.Rda"))
load(paste0(current_path, "loc3_BUCB_cubic.Rda"))
load(paste0(current_path, "loc3_comp_BUCB.Rda"))
load(paste0(current_path, "loc3_comp_BUCB_squared.Rda"))
load(paste0(current_path, "loc3_comp_BUCB_cubic.Rda"))

loc3_UNIFORM_as <- colMeans(ldply(loc3_UNIFORM, function(x) table(x$arm_sequence)))
loc3_APT_as <- colMeans(ldply(loc3_APT, function(x) table(x$arm_sequence)))
loc3_PI_as <- colMeans(ldply(loc3_PI, function(x) table(x$arm_sequence)))
loc3_TTS_as <- colMeans(ldply(loc3_TTS, function(x) table(x$arm_sequence)))
loc3_BUCB_as <- colMeans(ldply(loc3_BUCB, function(x) table(x$arm_sequence)))
loc3_BUCB_squared_as <- colMeans(ldply(loc3_BUCB_squared, function(x) table(x$arm_sequence)))
loc3_BUCB_cubic_as <- colMeans(ldply(loc3_BUCB_cubic, function(x) table(x$arm_sequence)))
loc3_KL_as <- colMeans(ldply(loc3_KL, function(x) table(x$arm_sequence)))
loc3_KL_horizon1_as <- colMeans(ldply(loc3_KL_horizon1, function(x) table(x$arm_sequence)))

round(data.frame(loc3_UNIFORM_as, loc3_APT_as,
                 loc3_PI_as, loc3_TTS_as,
                 loc3_KL_as, loc3_KL_horizon1_as))
```

The exact opposite happens when we dare to pull arms that maximize the distance between tau (+- epsilon) and their lower/upper bounds respectively. Because the distributions with mean below the threshold are very limited between 0 and tau, their upper bound is intuitively much further apart from tau than the lower bound of arms above tau can be (in fact, the distance of the lower bound is limited to 0.045 in this case). Thus, if we follow the BUCB_squared strategy, we quickly demand very high lower/upper bounds and thus very quickly start to focus on arms that are below the low threshold which is a good thing.

The following graph shows again APT (red) and Uniform (black) against BUCB (blue), BUCB_squared (darkblue), BUCB_cubic (lightblue). The effect of the squared term is dramatic.

```{r, echo = FALSE}
plot(c(0,1000), c(0, -4), type = "n")
lines(log(loc3_comp_UNIFORM), col = "black")
lines(log(loc3_comp_APT), col = "red")
lines(log(loc3_comp_BUCB), col = "blue")
lines(log(loc3_comp_BUCB_squared), col = "darkblue")
lines(log(loc3_comp_BUCB_cubic), col = "lightblue")
```

This becomes even more apparent in the following table. Additionally, due to the quickly increasing confidence bounds, the arms within the epsilon interval aren't pulled as often, which helps a lot and is very different from APT. Interestingly, the simple BUCB suffers from the same problem as the other algorithms too.

```{r,echo = FALSE} 
round(data.frame(loc3_UNIFORM_as, loc3_APT_as,
                 loc3_BUCB_as, loc3_BUCB_squared_as,
                 loc3_PI_as, loc3_KL_horizon1_as))
```

```{r, echo = FALSE}
arm_seq_res_APT <- data.frame(t(laply(loc3_APT, function(x) x$arm_sequence)))

arm_seq_res_APT %>% tbl_df() %>% mutate(index = 1:1000) %>%
  gather(key = iter, value = arm, -index) %>%
  filter(index > 10) %>%
  ggplot(aes(index, arm)) + geom_count(aes(size = ..prop.., group = index)) +
  scale_size_area(max_size = 10)

arm_seq_res_BUCB_squared <- data.frame(t(laply(loc3_BUCB_squared, function(x) x$arm_sequence)))
arm_seq_res_BUCB_squared %>% tbl_df() %>% mutate(index = 1:1000) %>%
  gather(key = iter, value = arm, -index) %>%
  filter(index > 10) %>%
  ggplot(aes(index, arm)) + geom_count(aes(size = ..prop.., group = index)) +
  scale_size_area(max_size = 10)
```

### 2017-06-29 AugUCB/algorithm_comparison.Rmd
Scripts for calibrating algorithms

---
title: "Algorithm Comparison"
author: "Tim Radtke"
date: "6/5/2017"
output: html_document
---

specify the problem that we want to look at

20 arms, low threshold of 0.04, epsilon of 0.01
5 arms very low, 5 arms very high
3 arms below 0.04, 3 arms above 0.04
2 arms below within epsilon, 2 arms above within epsilon

```{r, echo = FALSE}
mean_twenty <- c(0.0005, 0.0005, 0.001, 0.001, 0.005,
                 0.3, 0.4, 0.5, 0.6, 0.7,
                 0.01, 0.02, 0.02,
                 0.06, 0.06, 0.07,
                 0.035, 0.035, 0.045, 0.045)
```

```{r, echo = FALSE}
script_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"

load(file = paste0(script_path, "ber20_TTS_comp.Rda"))
load(file = paste0(script_path, "ber20_PI_informative_nosamples_comp.Rda"))
load(file = paste0(script_path, "ber20_PI_informative_comp.Rda"))
load(file = paste0(script_path, "ber20_PI_uniform_prior_comp.Rda"))
load(file = paste0(script_path, "ber20_AugUCB_comp.Rda"))
load(file = paste0(script_path, "ber20_APT_comp.Rda"))
load(file = paste0(script_path, "ber20_uniform_comp.Rda"))
load(file = paste0(script_path, "ber20_KL_comp.Rda"))
load(file = paste0(script_path, "ber20_TTS_informative_comp.Rda"))
load(file = paste0(script_path, "ber20_JC_informative_comp.Rda"))
load(file = paste0(script_path, "ber20_BUCB_informative_comp.Rda"))
load(file = paste0(script_path, "ber20_BUCB_comp.Rda"))
load(file = paste0(script_path, "ber20_BLUCB_comp.Rda"))
load(file = paste0(script_path, "ber20_BUCB_inverse_horizon_comp.Rda"))

xmax <- 1000
plot(log(ber20_uniform_comp$mean), type = "l", xlim = c(0,xmax))
lines(log(ber20_APT_comp$mean), col = "red", xlim = c(0,xmax))
lines(log(ber20_AugUCB_comp$mean), col = "green", xlim = c(0,xmax))
#lines(log(ber20_PI_uniform_prior_comp$mean), col = "blue", xlim = c(0,xmax))
#lines(log(ber20_PI_informative_comp$mean), col = "blue", xlim = c(0,xmax))
#lines(log(ber20_PI_informative_nosamples_comp$mean), col = "pink", xlim = c(0,xmax))
lines(log(ber20_TTS_comp$mean), col = "orange", xlim = c(0,xmax))
#lines(log(ber20_KL_comp$mean), col = "violet", xlim = c(0,xmax))
lines(log(ber20_TTS_informative_comp$mean), col = "darkgrey", xlim = c(0,xmax))
#lines(log(ber20_JC_informative_comp$mean), col = "darkgreen", xlim = c(0,xmax))
lines(log(ber20_BUCB_informative_comp$mean), col = "darkgreen", xlim = c(0,xmax))
lines(log(ber20_BUCB_inverse_horizon_comp$mean), col = "darkred", xlim = c(0,xmax))
#lines(log(ber20_BUCB_comp$mean), col = "darkred", xlim = c(0,xmax))
lines(seq(1,1961,by=2), log(ber20_BLUCB_comp$mean), col = "pink", xlim = c(0,xmax))
```

### 2017-06-29 Thesis/Draft.Rmd
Scripts for calibrating algorithms

@@
 
-The idea now is that we would like to classify the banners into two distinct groups: A group with a mean conversion rate $\mu_i$ below threshold $\tau$, and a group with mean conversion rate $\mu_i$ above threshold $\tau$.
+The idea now is that we would like to classify the banners into two distinct groups: A group with mean conversion rates $\mu_i$ below threshold $\tau$, and a group with mean conversion rates $\mu_i$ above threshold $\tau$.
 This might be the optimization problem when we are concerned with not falling below a certain minimum level click-through rate with the banners we're choosing.
@@
 As standard in multi-armed bandit problems, we have $K$ arms $\mathcal{A} = \{1, \dots K\}$.
-We can pull arm $k$ at time $t$ to collect feedback in form of the random variable $X_{k,t}$ which is distributed accoring to the arm's distribution $\nu_k$.
+We can pull arm $k$ at time $t$ to collect feedback in form of the random variable $X_{k,t}$ which is distributed according to the arm's distribution $\nu_k$.
 In general, we are concerned with estimating for each arm $i$ the mean $\mu_i$ of its distribution $\nu_i$.
 In contrast to most bandit problems, however, we do not directly compare arms with each other by comparing their means.
-In the case of pure exploration bandits, it is for example necessary to compare the arms because one aims to find the best one.
+That would for example be the case for pure exploration bandits, where it is necessary to compare the arms because one aims to find the best one relative to the others.
 In the case of the thresholding bandit, however, we compare each arm's mean $\mu_i$ individually against the threshold $\tau \in \mathbb{R}$ which is known and fixed before the experiment.
@@
 
-In Locatelli (2016), the arms' distributions are assumed to follow a $R$-sub-Gaussian distribution.
+In Locatelli (2016), the arms' distributions are assumed to follow an $R$-sub-Gaussian distribution.
 Under this assumption, the authors are able to proof a general lower bound as well as an algorithm with a matching upper bound.
@@
 In particular, it shows that just adding additional arms leads to an increase in complexity (since we need to sample more of them), just as smaller $\Delta_i$ will increase the complexity as arms become harder to classify.
-(WHERE DOES THIS COMPLEXITY ORIGINALLY COME FROM?
-WHAT IS ITs MOTIVATION?
-ITS NOT THAAAT NATURAL)
+(WHERE DOES THIS COMPLEXITY ORIGINALLY COME FROM?)
 
@@
 As explained during the introduction, multi-armed bandits traditionally optimize cumulative regret.
-The notion of regret considered in the thresholding bandit, however, is more akin to the regret in pure exploration bandits or the error probability in sequential hypothesis testing.
+The notion of regret considered in the thresholding bandit, however, is more akin to the simple regret in pure exploration bandits or the error probability in sequential hypothesis testing.
 Indeed, one can most easily describe the regret in the thresholding case as the probability of making a misclassification of any arm.
@@
 From the general setup, we already know how the algorithm will end.
-After it has drawn $T$ samples, the algorithm makes its decision of which arms to include in the return sets solely on basis of the empirical means $\hat{\mu}_i(T)$ estimated until time $T$.
+After it has drawn $T$ samples, the algorithm makes its decision of which arms to include in the return sets solely on basis of the empirical means $\hat{\mu}_i(T)$ estimated based on the samples drawn until time $T$.
 Furthermore, the threshold and interval around the threshold were fixed upfront and serve as argument to the algorithm: $(\tau, \epsilon)$.
@@
 In this way, the algorithm tries to distribute the budget $T$ over all arms so as to define a sampling rule optimizing the confidence of the final decision.
-Of course, that's just Glivenko-Cantelli and the CLT making sure $B_i(t+1)$ is not degenerate.
+This is Glivenko-Cantelli and the CLT making sure $B_i(t+1)$ is not degenerate.
+(?)
 
@@
 (2016).
-In general, the problem becomes that the assumptions for the bounds no longer hold; furthermore, the statistic $B_i(t+1)$, and the term $\hat{\Delta_i}(t)$ are motivated by (sub-)Gaussian distributions.
+In general, the problem becomes that the assumptions for the bounds no longer hold; furthermore, the statistic $B_i(t+1)$, and the term $\hat{\Delta}_i(t)$ are motivated by (sub-)Gaussian distributions.
 The more one moves away from Gaussian-like distributions, the less appropriate this term becomes, however.
@@
 Utilizing this additional information, the algorithm seems to perform better than for example APT, going from simulation results displayed in the paper.
-We will continue to discuss the Augmented UCB solution further in chapter 3.
+However, the simulations deal exclusively with normal distributions, as the variance has to be bounded for the upper bound of the Augmented UCB to hold.
+We will continue to discuss the Augmented UCB solution in chapter 3.
 
@@
 This, for example, is the case for Bernoulli distributions at very small parameters $\mu$.
-It's quite obvious simply by looking at examples that the Kullback-Leibler divergence of Bernoullis starts to lose any similarity to the plain quadratic approximation.
-The second graph then shows, that the actual Kullback-Leibler divergence of Bernoullis also has lost any symmetry over this range of parameter values.
+By looking at the graphical examples below it becomes obvious that the Kullback-Leibler divergence of Bernoullis starts to lose any similarity to the plain quadratic approximation.
+The second graph then shows that the actual Kullback-Leibler divergence of Bernoullis also has lost any symmetry over this range of parameter values.
 Given that Bernoulli distributions with very small parameter values arise naturally in many applications in website optimization and advertising click-through modeling, there is a need to tackle this problem.
@@
 
-plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1.5), type = "n", asp = 1,
+plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1), type = "n", asp = 1,
      xlab = "p_1", ylab = "(p_1 - p_2)^2", main = "Gaussian approx.\n KL of Bernoullis")
@@
 
-plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1.5), type = "n", asp = 1,
+plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1), type = "n", asp = 1,
      xlab = "p_1", ylab = "(p_2 - p_1)^2", main = "Gaussian approx.\n KL of Bernoullis")
@@
 
-*Proof of Theorem \ref{theorem:Locatelli2016Theorem1}*: In Theorem 1 of Locatelli et al.
+*Proof of Theorem \ref{theorem:Locatelli2016Theorem1}*: In Theorem \ref{theorem:Locatelli2016Theorem1} of Locatelli et al.
 (2016), a lower bound for the thresholding bandit problem is shown.
@@
 
-#### Reminder about the goal of the proof
+### Reminder about the goal of the proof
 
@@
 
-#### Statistical Decision
+### Statistical Decision
 
@@
 
-#### Change of Distribution
+### Change of Distribution
 
@@
 
-#### Concentration of the Empirical Kullback-Leibler Divergence
+### Concentration of the Empirical Kullback-Leibler Divergence
 
@@
 
-#### Bounding $T_i$ for $\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$
+### Bounding $T_i$ for $\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$
 
@@
 
-#### Bringing everything together
+### Bringing everything together
 
@@
 
-The Hoeffding inequality as used here is as follows:
+The Hoeffding inequality as used here is as follows (compare chapter 2.4 in [David Pollard (2015)](http://www.stat.yale.edu/~pollard/Books/Mini/Basic.pdf)):
 
@@
 
-#### Step 2: Lower Bound on Number of Pulls of Difficult Arm
+### Step 2: Lower Bound on Number of Pulls of Difficult Arm
 
@@
 
-#### Step 3: Lower Bound on Number of Pulls of Simple Arm
+### Step 3: Lower Bound on Number of Pulls of Simple Arm
 
@@
 
-#### Conclusion
+### Conclusion
 
@@
 
-Even though the complexity $H$ enjoys popularity in the literature of the best m arm identification problem, $m \geq 1$, Kaufmann et al.
+Even though the complexity $H$ enjoys popularity in the literature of the best $m$ arm identification problem, $m \geq 1$, Kaufmann et al.
 (2016) show explicitly that $H$ is mainly useful for problems of Gaussian distributions.
-Indeed, they go so far as to define new measures of complexity that are based on information theoretic metrics.
-Using those they then display $H$ as an approximation to their measures in the case of Gaussian distributions.
+Indeed, they go so far as to define new measures of complexity that are based on information theoretic measures Using those they then display $H$ as an approximation to their measures in the case of Gaussian distributions.
 In turn, this makes apparent that especially Bernoulli distributions with small means have to be treated differently.
@@
 
-\begin{theorem}[Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem4}
+\begin{theorem}[Theorem 4, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem4}
 Let $\nu \in \mathcal{M}_m$, where $\mathcal{M}_m$ is the set of uniquely identifiable bandit models described above.
@@
 To proof this statement, we assume as before that the arms are ordered by their means decreasing in size.
-For a given $\delta$-PAC algorithm $\mathcal{A} = ((A_t), \tau, \hat{S}_m)$, and under the continuity conditions, there exists for every arm $a \in \{1, \dots, K\}$ an alternative model $\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)$.
+For a given $\delta$-PAC algorithm $\mathcal{A} = ((A_t), \tau, \hat{S}_m)$, and under the continuity conditions (compare Kaufmann et al.
+(2016)), there exists for every arm $a \in \{1, \dots, K\}$ an alternative model $\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)$.
 In this alternative model, only arm $a$ is modified in accordance with the continuity conditions.
@@
 
-\begin{theorem}[Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem12}
+\begin{theorem}[Theorem 12, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem12}
 Let $\nu = (\nu_1, \nu_2)$ be a two-armed bandit model such that $\mu_1 > \mu_2$. In the fixed-budget setting, any consistent algorithm satisfies:
@@
 
-#### Matching algorithm strategies
-
-Given those lower bounds, all that is left is to find algorithms which are able to match the complexity. Sadly, not straightforward for Bernoullis.
+### Matching algorithm strategies
+
+Given these lower bounds, all that is left is to find algorithms which are able to match the complexity. Sadly, not straightforward for Bernoullis.
 
@@
 
-A very similar application of the KL divergence has been given in Garivier and Kaufmann to derive a lower bound on the sample complexity in the case of best arm identification.
+A very similar application of the KL divergence has been given in Garivier and Kaufmann (2016) to derive a lower bound on the sample complexity in the case of best arm identification.
 In particular, the transportation Lemma 1 is used again.
@@
 Combining this sampling rule with an appropriate stopping rule makes for a $\delta$-PAC algorithm that matches the lower bound, where the upper bound in Theorem \ref{theorem:GarivierAndKaufmannTheorem14} matches the lower bound from Theorem \ref{theorem:GarivierKaufmannTheorem1} using equation \eqref{bre_approx}.
+
+\newpage
+
+# KL and Bayesian Thresholding Bandits
+
+## Introduction
+
+We have introduced the thresholding bandit problem in chapter 1.
+The APT algorith described in Locatelli et al.
+(2016) is able to match a lower bound (be more specific!) given in the same paper, and has several favorable characteristics such as its overall simplicity and it being an anytime algorithm.
+However, the bounds on the expected loss assume the arms' distributions to be $R$-sub-Gaussian.
+This is reflected in the algorithm's complexity measure $H = \sum_{i=1}^K (\Delta_i^{\tau, \epsilon})^{-2}$, where $\Delta_i^{\tau,\epsilon} = |\mu_i - \tau| + \epsilon$, which -- given the known threshold $\tau \pm \epsilon$ -- only depends on the distribution's mean.
+This is appropriate for Gaussian arms with equal variances, but potentially inefficient for other kinds of distributions.
+
+In the case of Gaussian distributions with varying variances, for example, it makes sense to take the variance into account; after all, given two Gaussians with equal mean, intuitively we would prefer to get a sample from the distribution of larger variance.
+
+In the case of Gaussians, the complexity $H$ is nice also because it reflects the Kullback-Leibler divergence between two Gaussians.
+And since Bernoulli distributions are bounded on the interval $[0,1]$, they are consequently sub-Gaussian, meaning that their Kullback-Leibler divergence can be approximated by the Gaussian one.
+However, while Bernoullis are sub-Gaussian, the approximation of their divergence by the Gaussian divergence becomes less and less optimal as the parameter (and thus mean) goes to $0$ or $1$, as shown in chapter 1.
+And while online advertisements might not be an obvious use case for thresholding bandits, they are just one real life scenario dominated by Bernoulli distributions with very small parameters.
+Thus it is worthwile to adapt current solutions of the thresholding bandit problem to cases in which the Gaussian Kullback-Leibler divergence is no longer an appropriate approximation.
+
+Large motiviation for the idea of adjusting the complexity measure (and thus the algorithms) to distributions more generally based on the Kullback-Leibler divergence stems from the work discussed in chapter 2, complexity measures were defined for the pure exploration bandits in terms of the Kullback-Leibler divergence.
+Based on this, the authors were for example able to point our differences between Gaussian and Bernoulli bandits.
+We expect that results in a similar vain could be derived for thresholding bandits.
+
+To this end, in the following, we first present an extension of mean based algorithms to an algorithm that incorporates empirical variances as described in Mukherjee et al.
+(2017).
+Afterwards, we propose and discuss potential further improvements based on Kullback-Leibler divergence and Bayesian posterior distributions.
+Finally, we compare the performance of different algorithms based on simulations and real world data sets.
+
+## Variance Based Algorithms for Thresholding Bandits
+
+Mukherjee et al.
+(2017) propose an algorithm based on variance estimates called Augmented-UCB (AugUCB).
+The setting in which the algorithm is proposed is very similar to the setting in Locatelli et al.
+(2016).
+The algorithm itself, however, differs heavily from the APT algorithm.
+So is AugUCB for example not an anytime algorithm.
+Furthermore, arms can be deleted in every round if there are "far enough" away from the mean.
+Both the decision of which arm is played in a given round, and whether an arm is removed from the active set of arm, is based not only on the empirical mean estimate $\mu_i(t)$, but also on a term $s_i$ that is increasing linearly in the estimated standard deviation.
+While the APT algorithm plays the arm minimizing the quantity $B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t) = \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau| + \epsilon)$, AugUCB plays the arm minimizing the quantity $(\hat{\Delta}_i(t) - 2s_i)$, where $s_i$ is based on the variance estimate $\hat{v}_i$, and an exploration $\psi_m$ term linear in $T$, and an elimination parameter $\rho$ (compare Algorithm 1 in Mukherjee et al., 2017):
+
+\begin{equation*}
+s_i = \sqrt{\frac{\rho \psi_m (\hat{v}_i + 1) \log(T \epsilon_m)}{4n_i}}
+\end{equation*}
+
+Consequently, the authors also introduce complexity measures which take the variance into account.
+From Gabillon et al.
+(2011) they use $H_{\sigma, 1}= \sum_{i=1}^K \frac{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}{\Delta_i^2}$.
+Furthermore, with $\stackrel{\sim}{\Delta}_i^2 = \frac{\Delta_i^2}{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}$, and with $\stackrel{\sim}{\Delta}_{(i)}$ being an increasing ordering of $\stackrel{\sim}{\Delta}_i$, the authors define a complexity corresponding to $H_{CSAR,2}$ in Chen et al.
+(2014):
+
+\begin{equation*}
+H_{\sigma,2} = \max_{i \ in \mathcal{A}} \frac{i}{\stackrel{\sim}{\Delta}_{(i)}^2}.
+\end{equation*}
+
+While the latter complexity appears in the provided upper bound on the AugUCB algorithm's expected loss, it could be replaced by $H_{\sigma, 1}$ since $H_{\sigma, 2} \leq H_{\sigma,1}$.
+$H_{\sigma,1}$ is of course more directly comparable to the complexity $H$ that we are used to.
+
+While in the case of the APT algorithm the number of times a specific arm has been drawn $T_i$ measures how concentrated the estimated mean is around the true mean (and thus for large $T_i$ an arm is no longer drawn even if $\hat{\mu}$ is close to $\tau$); in the case of the AugUCB algorithm this is regulated by the combination of the variance estimate $\hat{v}_i$ and the exploration factor $\psi_m$, where they ensure that certain arms are no longer pulled when the algorithm is sufficiently confident in its knowledge about the true mean.
+Therefore, when using a very similar favorable event in the proof of their upper bound, Mukherjee et al.
+(2017) have to bound the probability that an an arm is not removed from the active set after the a certain number of rounds -- even though the arm is above (respectively below) the threshold.
+If this probability is low, then this means that the algorithm is able to be certain about an arm's true mean *quickly* by employing variance estimates.
+In comparison, Locatelli et al (2016) used bounds on on how often arms are drawn ($T_i$) to give a bound on the probability of the favorable event.
+In order to derive the bound, Mukherjee et al.
+(2017) use the Bernstein inequality.
+
+It has to be noted that Mukherjee et al.
+(2017) have to assume that the distributions have rewards bounded in $[0,1]$ in order to derive the bound on the probability that an arm has not been eliminated correctly in round $T_i$.
+Thus, the distributions for which their upper bound holds are a subset of the sub-Gaussian distributions considered in Locatelli et al.
+(2016).
+However, it is not that the authors need to assume that the rewards are in $[0,1]$, but this was assumed so that the variance of the distribution is in $[0,1]$.
+Thus, the upper bound holds in particular for Gaussian distributions with variance $\sigma^2 \in [0,1]$.
+
+Based on this assumption, the authors show that the probability that an arm has not been eliminated after $m_i$ rounds is given by (compare equation (2) in Mukherjee et al., 2017):
+
+\begin{equation} \label{Mukherjee2017Equation2}
+\mathbb{P}(\hat{\mu}_i > \mu_i + 2s_i) \leq \mathbb{P} (\hat{\mu}_i > \mu_i + 2\bar{s}_i) + \mathbb{P}(\hat{v}_i \geq \sigma^2_i + \sqrt{\rho \epsilon_{T_i}})
+\end{equation}
+
+Compare Mukherjee et al.
+(2017) for the notation.
+Then it becomes clear that the left part of the RHS gives the probability that the mean estimate is out of wack, while the right term gives the probability that the variance is overestimated.
+The first term is bounded by the Bernstein inequality.
+In the cumulative regret setting, there exists a similar decomposition that bounds the expected number of pulls of a suboptimal arm.
+Compare for example chapter 3.1 in "Thompson Sampling: An Asymptotically Optimal Finite Time Analysis" by Kaufmann, Korda and Munos (2012).
+There they decompose the expected number of draws of an suboptimal arm for an optimistic (UCB like) into the probability that the optimal arm's mean is underestimated, and the probability that the UCB of the suboptimal arm is still very large.
+To give bounds for UCB algorithms, it is then shown that these two terms show a certain convergence.
+Mukherjee et al.
+do similarly for their variance based algorithm in the thresholding setting.
+
+(since the AugUCB eliminates arms, it is interesting to see how it behaves when the underlying CTR changes over time...)
+
+## New Approaches

### 2017-06-29 Thesis/Draft.tex
Scripts for calibrating algorithms

@@
 The idea now is that we would like to classify the banners into two
-distinct groups: A group with a mean conversion rate \(\mu_i\) below
-threshold \(\tau\), and a group with mean conversion rate \(\mu_i\)
+distinct groups: A group with mean conversion rates \(\mu_i\) below
+threshold \(\tau\), and a group with mean conversion rates \(\mu_i\)
 above threshold \(\tau\). This might be the optimization problem when we
@@
 collect feedback in form of the random variable \(X_{k,t}\) which is
-distributed accoring to the arm's distribution \(\nu_k\). In general, we
-are concerned with estimating for each arm \(i\) the mean \(\mu_i\) of
-its distribution \(\nu_i\). In contrast to most bandit problems,
+distributed according to the arm's distribution \(\nu_k\). In general,
+we are concerned with estimating for each arm \(i\) the mean \(\mu_i\)
+of its distribution \(\nu_i\). In contrast to most bandit problems,
 however, we do not directly compare arms with each other by comparing
-their means. In the case of pure exploration bandits, it is for example
-necessary to compare the arms because one aims to find the best one. In
-the case of the thresholding bandit, however, we compare each arm's mean
-\(\mu_i\) individually against the threshold \(\tau \in \mathbb{R}\)
-which is known and fixed before the experiment. One might compare this
-to a pure exploration bandit in which the mean of the best arm is known
-upfront. We will see later that this fact leads to advantages in the
-design of algorithms which are not as readily available in other bandit
-settings.
-
-In Locatelli (2016), the arms' distributions are assumed to follow a
+their means. That would for example be the case for pure exploration
+bandits, where it is necessary to compare the arms because one aims to
+find the best one relative to the others. In the case of the
+thresholding bandit, however, we compare each arm's mean \(\mu_i\)
+individually against the threshold \(\tau \in \mathbb{R}\) which is
+known and fixed before the experiment. One might compare this to a pure
+exploration bandit in which the mean of the best arm is known upfront.
+We will see later that this fact leads to advantages in the design of
+algorithms which are not as readily available in other bandit settings.
+
+In Locatelli (2016), the arms' distributions are assumed to follow an
 \(R\)-sub-Gaussian distribution. Under this assumption, the authors are
@@
 complexity as arms become harder to classify. (WHERE DOES THIS
-COMPLEXITY ORIGINALLY COME FROM? WHAT IS ITs MOTIVATION? ITS NOT THAAAT
-NATURAL)
+COMPLEXITY ORIGINALLY COME FROM?)
 
@@
 regret. The notion of regret considered in the thresholding bandit,
-however, is more akin to the regret in pure exploration bandits or the
-error probability in sequential hypothesis testing. Indeed, one can most
-easily describe the regret in the thresholding case as the probability
-of making a misclassification of any arm. Or, more rigorously, let us
-define the set of all arms with mean larger than the threshold,
+however, is more akin to the simple regret in pure exploration bandits
+or the error probability in sequential hypothesis testing. Indeed, one
+can most easily describe the regret in the thresholding case as the
+probability of making a misclassification of any arm. Or, more
+rigorously, let us define the set of all arms with mean larger than the
+threshold,
 \(\mathcal{S}_\tau = \{i \in \mathcal{A}: \mu_i \geq \tau\}\).
@@
 which arms to include in the return sets solely on basis of the
-empirical means \(\hat{\mu}_i(T)\) estimated until time \(T\).
-Furthermore, the threshold and interval around the threshold were fixed
-upfront and serve as argument to the algorithm: \((\tau, \epsilon)\).
-For a given arm \(i\) and a given time \(t\), we let \(T_i(t)\)
-represent the number of samples drawn from arm \(i\) until time \(t\)
-(including). Consequently, the empirical mean of arm \(i\) at time \(t\)
-is given by \(\mu_i = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}\)
-where \(X_{i,s}\) is the feedback sampled from distribution \(\nu_i\)
-when the arm is pulled for the \(s\)-th time.
+empirical means \(\hat{\mu}_i(T)\) estimated based on the samples drawn
+until time \(T\). Furthermore, the threshold and interval around the
+threshold were fixed upfront and serve as argument to the algorithm:
+\((\tau, \epsilon)\). For a given arm \(i\) and a given time \(t\), we
+let \(T_i(t)\) represent the number of samples drawn from arm \(i\)
+until time \(t\) (including). Consequently, the empirical mean of arm
+\(i\) at time \(t\) is given by
+\(\mu_i = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}\) where
+\(X_{i,s}\) is the feedback sampled from distribution \(\nu_i\) when the
+arm is pulled for the \(s\)-th time.
 
@@
 over all arms so as to define a sampling rule optimizing the confidence
-of the final decision. Of course, that's just Glivenko-Cantelli and the
-CLT making sure \(B_i(t+1)\) is not degenerate.
+of the final decision. This is Glivenko-Cantelli and the CLT making sure
+\(B_i(t+1)\) is not degenerate. (?)
 
@@
 assumptions for the bounds no longer hold; furthermore, the statistic
-\(B_i(t+1)\), and the term \(\hat{\Delta_i}(t)\) are motivated by
+\(B_i(t+1)\), and the term \(\hat{\Delta}_i(t)\) are motivated by
 (sub-)Gaussian distributions. The more one moves away from Gaussian-like
@@
 additional information, the algorithm seems to perform better than for
-example APT, going from simulation results displayed in the paper. We
-will continue to discuss the Augmented UCB solution further in chapter
-3.
+example APT, going from simulation results displayed in the paper.
+However, the simulations deal exclusively with normal distributions, as
+the variance has to be bounded for the upper bound of the Augmented UCB
+to hold. We will continue to discuss the Augmented UCB solution in
+chapter 3.
 
@@
 Gaussian. This, for example, is the case for Bernoulli distributions at
-very small parameters \(\mu\). It's quite obvious simply by looking at
-examples that the Kullback-Leibler divergence of Bernoullis starts to
-lose any similarity to the plain quadratic approximation. The second
-graph then shows, that the actual Kullback-Leibler divergence of
-Bernoullis also has lost any symmetry over this range of parameter
-values. Given that Bernoulli distributions with very small parameter
-values arise naturally in many applications in website optimization and
-advertising click-through modeling, there is a need to tackle this
-problem.
+very small parameters \(\mu\). By looking at the graphical examples
+below it becomes obvious that the Kullback-Leibler divergence of
+Bernoullis starts to lose any similarity to the plain quadratic
+approximation. The second graph then shows that the actual
+Kullback-Leibler divergence of Bernoullis also has lost any symmetry
+over this range of parameter values. Given that Bernoulli distributions
+with very small parameter values arise naturally in many applications in
+website optimization and advertising click-through modeling, there is a
+need to tackle this problem.
 
@@
 \emph{Proof of Theorem \ref{theorem:Locatelli2016Theorem1}}: In Theorem
-1 of Locatelli et al. (2016), a lower bound for the thresholding bandit
-problem is shown. The basic idea is as follows. The problem formulation
-considered in the paper describes bandit problems for sub-Gaussian
-distributions. To show a lower bound, we show that every algorithm is
-expected to make a certain error even if we restrict ourselves to a very
-restricted scenario. Even then, any algorithm will have a certain level
-of risk with which it cannot distinguish between the actual setting and
-slightly changed settings (under which the former answer leads to
-regret).
+\ref{theorem:Locatelli2016Theorem1} of Locatelli et al. (2016), a lower
+bound for the thresholding bandit problem is shown. The basic idea is as
+follows. The problem formulation considered in the paper describes
+bandit problems for sub-Gaussian distributions. To show a lower bound,
+we show that every algorithm is expected to make a certain error even if
+we restrict ourselves to a very restricted scenario. Even then, any
+algorithm will have a certain level of risk with which it cannot
+distinguish between the actual setting and slightly changed settings
+(under which the former answer leads to regret).
 
@@
 
-\paragraph{Reminder about the goal of the
+\subsubsection{Reminder about the goal of the
 proof}\label{reminder-about-the-goal-of-the-proof}
@@
 
-\paragraph{Statistical Decision}\label{statistical-decision}
+\subsubsection{Statistical Decision}\label{statistical-decision}
 
@@
 
-\paragraph{Change of Distribution}\label{change-of-distribution}
+\subsubsection{Change of Distribution}\label{change-of-distribution}
 
@@
 
-\paragraph{Concentration of the Empirical Kullback-Leibler
+\subsubsection{Concentration of the Empirical Kullback-Leibler
 Divergence}\label{concentration-of-the-empirical-kullback-leibler-divergence}
@@
 
-\paragraph{\texorpdfstring{Bounding \(T_i\) for
+\subsubsection{\texorpdfstring{Bounding \(T_i\) for
 \(\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)}{Bounding T\_i for \textbackslash{}max\_\{i \textbackslash{}in \textbackslash{}\{1,\textbackslash{}dots,K\textbackslash{}\}\}\textbackslash{}mathbb\{P\}\_\{\textbackslash{}mathcal\{B\}\^{}i\}(\textbackslash{}mathcal\{A\}\_i)}}\label{bounding-t_i-for-max_i-in-1dotskmathbbp_mathcalbimathcala_i}
@@
 
-\paragraph{Bringing everything
+\subsubsection{Bringing everything
 together}\label{bringing-everything-together}
@@
 
-The Hoeffding inequality as used here is as follows:
+The Hoeffding inequality as used here is as follows (compare chapter 2.4
+in \href{http://www.stat.yale.edu/~pollard/Books/Mini/Basic.pdf}{David
+Pollard (2015)}):
 
@@
 
-\paragraph{Step 2: Lower Bound on Number of Pulls of Difficult
+\subsubsection{Step 2: Lower Bound on Number of Pulls of Difficult
 Arm}\label{step-2-lower-bound-on-number-of-pulls-of-difficult-arm}
@@
 
-\paragraph{Step 3: Lower Bound on Number of Pulls of Simple
+\subsubsection{Step 3: Lower Bound on Number of Pulls of Simple
 Arm}\label{step-3-lower-bound-on-number-of-pulls-of-simple-arm}
@@
 
-\paragraph{Conclusion}\label{conclusion}
+\subsubsection{Conclusion}\label{conclusion}
 
@@
 Even though the complexity \(H\) enjoys popularity in the literature of
-the best m arm identification problem, \(m \geq 1\), Kaufmann et al.
+the best \(m\) arm identification problem, \(m \geq 1\), Kaufmann et al.
 (2016) show explicitly that \(H\) is mainly useful for problems of
 Gaussian distributions. Indeed, they go so far as to define new measures
-of complexity that are based on information theoretic metrics. Using
+of complexity that are based on information theoretic measures Using
 those they then display \(H\) as an approximation to their measures in
@@
 \(\mathcal{A} = ((A_t), \tau, \hat{S}_m)\), and under the continuity
-conditions, there exists for every arm \(a \in \{1, \dots, K\}\) an
-alternative model
+conditions (compare Kaufmann et al. (2016)), there exists for every arm
+\(a \in \{1, \dots, K\}\) an alternative model
 \(\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)\).
@@
 
-\paragraph{Matching algorithm
+\subsubsection{Matching algorithm
 strategies}\label{matching-algorithm-strategies}
 
-Given those lower bounds, all that is left is to find algorithms which
+Given these lower bounds, all that is left is to find algorithms which
 are able to match the complexity. Sadly, not straightforward for
@@
 A very similar application of the KL divergence has been given in
-Garivier and Kaufmann to derive a lower bound on the sample complexity
-in the case of best arm identification. In particular, the
+Garivier and Kaufmann (2016) to derive a lower bound on the sample
+complexity in the case of best arm identification. In particular, the
 transportation Lemma 1 is used again. And a matching algorithm for
@@
 
+\newpage
+
+\section{KL and Bayesian Thresholding
+Bandits}\label{kl-and-bayesian-thresholding-bandits}
+
+\subsection{Introduction}\label{introduction}
+
+We have introduced the thresholding bandit problem in chapter 1. The APT
+algorith described in Locatelli et al. (2016) is able to match a lower
+bound (be more specific!) given in the same paper, and has several
+favorable characteristics such as its overall simplicity and it being an
+anytime algorithm. However, the bounds on the expected loss assume the
+arms' distributions to be \(R\)-sub-Gaussian. This is reflected in the
+algorithm's complexity measure
+\(H = \sum_{i=1}^K (\Delta_i^{\tau, \epsilon})^{-2}\), where
+\(\Delta_i^{\tau,\epsilon} = |\mu_i - \tau| + \epsilon\), which -- given
+the known threshold \(\tau \pm \epsilon\) -- only depends on the
+distribution's mean. This is appropriate for Gaussian arms with equal
+variances, but potentially inefficient for other kinds of distributions.
+
+In the case of Gaussian distributions with varying variances, for
+example, it makes sense to take the variance into account; after all,
+given two Gaussians with equal mean, intuitively we would prefer to get
+a sample from the distribution of larger variance.
+
+In the case of Gaussians, the complexity \(H\) is nice also because it
+reflects the Kullback-Leibler divergence between two Gaussians. And
+since Bernoulli distributions are bounded on the interval \([0,1]\),
+they are consequently sub-Gaussian, meaning that their Kullback-Leibler
+divergence can be approximated by the Gaussian one. However, while
+Bernoullis are sub-Gaussian, the approximation of their divergence by
+the Gaussian divergence becomes less and less optimal as the parameter
+(and thus mean) goes to \(0\) or \(1\), as shown in chapter 1. And while
+online advertisements might not be an obvious use case for thresholding
+bandits, they are just one real life scenario dominated by Bernoulli
+distributions with very small parameters. Thus it is worthwile to adapt
+current solutions of the thresholding bandit problem to cases in which
+the Gaussian Kullback-Leibler divergence is no longer an appropriate
+approximation.
+
+Large motiviation for the idea of adjusting the complexity measure (and
+thus the algorithms) to distributions more generally based on the
+Kullback-Leibler divergence stems from the work discussed in chapter 2,
+complexity measures were defined for the pure exploration bandits in
+terms of the Kullback-Leibler divergence. Based on this, the authors
+were for example able to point our differences between Gaussian and
+Bernoulli bandits. We expect that results in a similar vain could be
+derived for thresholding bandits.
+
+To this end, in the following, we first present an extension of mean
+based algorithms to an algorithm that incorporates empirical variances
+as described in Mukherjee et al. (2017). Afterwards, we propose and
+discuss potential further improvements based on Kullback-Leibler
+divergence and Bayesian posterior distributions. Finally, we compare the
+performance of different algorithms based on simulations and real world
+data sets.
+
+\subsection{Variance Based Algorithms for Thresholding
+Bandits}\label{variance-based-algorithms-for-thresholding-bandits}
+
+Mukherjee et al. (2017) propose an algorithm based on variance estimates
+called Augmented-UCB (AugUCB). The setting in which the algorithm is
+proposed is very similar to the setting in Locatelli et al. (2016). The
+algorithm itself, however, differs heavily from the APT algorithm. So is
+AugUCB for example not an anytime algorithm. Furthermore, arms can be
+deleted in every round if there are ``far enough'' away from the mean.
+Both the decision of which arm is played in a given round, and whether
+an arm is removed from the active set of arm, is based not only on the
+empirical mean estimate \(\mu_i(t)\), but also on a term \(s_i\) that is
+increasing linearly in the estimated standard deviation. While the APT
+algorithm plays the arm minimizing the quantity
+\(B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t) = \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau| + \epsilon)\),
+AugUCB plays the arm minimizing the quantity
+\((\hat{\Delta}_i(t) - 2s_i)\), where \(s_i\) is based on the variance
+estimate \(\hat{v}_i\), and an exploration \(\psi_m\) term linear in
+\(T\), and an elimination parameter \(\rho\) (compare Algorithm 1 in
+Mukherjee et al., 2017):
+
+\begin{equation*}
+s_i = \sqrt{\frac{\rho \psi_m (\hat{v}_i + 1) \log(T \epsilon_m)}{4n_i}}
+\end{equation*}
+
+Consequently, the authors also introduce complexity measures which take
+the variance into account. From Gabillon et al. (2011) they use
+\(H_{\sigma, 1}= \sum_{i=1}^K \frac{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}{\Delta_i^2}\).
+Furthermore, with
+\(\stackrel{\sim}{\Delta}_i^2 = \frac{\Delta_i^2}{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}\),
+and with \(\stackrel{\sim}{\Delta}_{(i)}\) being an increasing ordering
+of \(\stackrel{\sim}{\Delta}_i\), the authors define a complexity
+corresponding to \(H_{CSAR,2}\) in Chen et al. (2014):
+
+\begin{equation*}
+H_{\sigma,2} = \max_{i \ in \mathcal{A}} \frac{i}{\stackrel{\sim}{\Delta}_{(i)}^2}.
+\end{equation*}
+
+While the latter complexity appears in the provided upper bound on the
+AugUCB algorithm's expected loss, it could be replaced by
+\(H_{\sigma, 1}\) since \(H_{\sigma, 2} \leq H_{\sigma,1}\).
+\(H_{\sigma,1}\) is of course more directly comparable to the complexity
+\(H\) that we are used to.
+
+While in the case of the APT algorithm the number of times a specific
+arm has been drawn \(T_i\) measures how concentrated the estimated mean
+is around the true mean (and thus for large \(T_i\) an arm is no longer
+drawn even if \(\hat{\mu}\) is close to \(\tau\)); in the case of the
+AugUCB algorithm this is regulated by the combination of the variance
+estimate \(\hat{v}_i\) and the exploration factor \(\psi_m\), where they
+ensure that certain arms are no longer pulled when the algorithm is
+sufficiently confident in its knowledge about the true mean. Therefore,
+when using a very similar favorable event in the proof of their upper
+bound, Mukherjee et al. (2017) have to bound the probability that an an
+arm is not removed from the active set after the a certain number of
+rounds -- even though the arm is above (respectively below) the
+threshold. If this probability is low, then this means that the
+algorithm is able to be certain about an arm's true mean \emph{quickly}
+by employing variance estimates. In comparison, Locatelli et al (2016)
+used bounds on on how often arms are drawn (\(T_i\)) to give a bound on
+the probability of the favorable event. In order to derive the bound,
+Mukherjee et al. (2017) use the Bernstein inequality.
+
+It has to be noted that Mukherjee et al. (2017) have to assume that the
+distributions have rewards bounded in \([0,1]\) in order to derive the
+bound on the probability that an arm has not been eliminated correctly
+in round \(T_i\). Thus, the distributions for which their upper bound
+holds are a subset of the sub-Gaussian distributions considered in
+Locatelli et al. (2016). However, it is not that the authors need to
+assume that the rewards are in \([0,1]\), but this was assumed so that
+the variance of the distribution is in \([0,1]\). Thus, the upper bound
+holds in particular for Gaussian distributions with variance
+\(\sigma^2 \in [0,1]\).
+
+Based on this assumption, the authors show that the probability that an
+arm has not been eliminated after \(m_i\) rounds is given by (compare
+equation (2) in Mukherjee et al., 2017):
+
+\begin{equation} \label{Mukherjee2017Equation2}
+\mathbb{P}(\hat{\mu}_i > \mu_i + 2s_i) \leq \mathbb{P} (\hat{\mu}_i > \mu_i + 2\bar{s}_i) + \mathbb{P}(\hat{v}_i \geq \sigma^2_i + \sqrt{\rho \epsilon_{T_i}})
+\end{equation}
+
+Compare Mukherjee et al. (2017) for the notation. Then it becomes clear
+that the left part of the RHS gives the probability that the mean
+estimate is out of wack, while the right term gives the probability that
+the variance is overestimated. The first term is bounded by the
+Bernstein inequality. In the cumulative regret setting, there exists a
+similar decomposition that bounds the expected number of pulls of a
+suboptimal arm. Compare for example chapter 3.1 in ``Thompson Sampling:
+An Asymptotically Optimal Finite Time Analysis'' by Kaufmann, Korda and
+Munos (2012). There they decompose the expected number of draws of an
+suboptimal arm for an optimistic (UCB like) into the probability that
+the optimal arm's mean is underestimated, and the probability that the
+UCB of the suboptimal arm is still very large. To give bounds for UCB
+algorithms, it is then shown that these two terms show a certain
+convergence. Mukherjee et al. do similarly for their variance based
+algorithm in the thresholding setting.
+
+(since the AugUCB eliminates arms, it is interesting to see how it
+behaves when the underlying CTR changes over time\ldots{})
+
+\subsection{New Approaches}\label{new-approaches}
+
 \end{document}

### 2017-06-29 AugUCB/APT.R

@@ -3,19 +3,19 @@
 # Locatelli et al. (2016)
 # Proceedings of the 33rd International Conference on Machine Learning
 
-means <- c(0.55, 0.38, 0.95)
-variances <- c(0.5, 0.9, 1.7)
-system.time(res_apt <- APT(means = means, K = 3, rounds = 5000, 
-                        variances = variances, seed = 54))
-lapply(res_apt$arm_list, length)
-res_apt$means
-means
-plot(x = c(0,5000), y = c(0,2), type = "n")
-lines(res_apt$mean_storage[,1])
-lines(res_apt$mean_storage[,2], col = "blue")
-lines(res_apt$mean_storage[,3], col = "red")
+#means <- c(0.55, 0.38, 0.95)
+#variances <- c(0.5, 0.9, 1.7)
+#system.time(res_apt <- APT(means = means, K = 3, rounds = 5000, 
+#                        variances = variances, seed = 54))
+#lapply(res_apt$arm_list, length)
+#res_apt$means
+#means
+#plot(x = c(0,5000), y = c(0,2), type = "n")
+#lines(res_apt$mean_storage[,1])
+#lines(res_apt$mean_storage[,2], col = "blue")
+#lines(res_apt$mean_storage[,3], col = "red")
 
-APT <- function(means, K = 4, rounds = 5000, tau = 0.5, epsilon = 0.1,
+APT <- function(means, K = 4, rounds = 5000, tau, epsilon,
                 variances = NA, verbose = FALSE, seed = NA
 ) {
   

### 2017-06-29 AugUCB/BayesLUCB.R

@@ -1,0 +1,169 @@
+# Using Bayes Quantiles, similar to
+# On Bayesian Upper Confidence Bounds for Bandit Problems
+# Kaufmann, Cappe, Garivier
+
+#means <- c(0.55, 0.38, 0.95)
+#variances <- c(0.5, 0.9, 1.7)
+#system.time(res_tts <- TTS(means = means, alpha = 1, beta = 1,
+#                           K = 3, rounds = 5000, 
+#                           variances = NA, seed = 54))
+# user  system elapsed 
+#0.390   0.057   0.446 
+#lapply(res_tts$arm_list, length)
+#res_tts$means
+#means
+#plot(x = c(0,5000), y = c(0,2), type = "n")
+#lines(res_tts$mean_storage[,1])
+#lines(res_tts$mean_storage[,2], col = "blue")
+#lines(res_tts$mean_storage[,3], col = "red")
+
+#system.time(res_blucb <- BayesLUCB(means = mean_twenty,
+#                                   tau = 0.04, epsilon = 0.01,
+#                                   alpha = 0.04, beta = 0.96,
+#                                   K = 20, rounds = 2000,
+#                                   variances = NA, seed = 60))
+##lapply(res_bucb$arm_list, length)
+#lapply(res_bucb2$arm_list, length)
+#res_bucb$means#
+
+#res_bucb <- as.data.frame(res_bucb$mean_storage)
+#res_bucb$round <- 1:dim(res_bucb)[1]
+#res_bucb_long <- gather(res_bucb[1:700,], key = "Arm", value = "Mean", 
+#                        -round)
+#ggplot(res_bucb_long, aes(x = round, y = Mean, color = Arm)) +
+#  geom_line()
+
+###############################################################################
+
+BayesLUCB <- function(means, K = 4, rounds = 5000, tau = 0.5, epsilon = 0.1,
+                      alpha = 1, beta = 1, mean_prior = NA, n_prior = NA,
+                      variances = NA, verbose = FALSE, seed = NA) {
+  
+  if(!is.na(seed)) set.seed(seed)
+  
+  # initialize by pulling each arm once
+  arm_list <- NA
+  for(i in 1:K) {
+    # Ideally it should also take an argument specifying how
+    # the sample is generated (e.g., from existing data, bernoulli or other distr.)
+    arm_list[[i]] <- pull_arm(k = i, means = means, variances = variances)
+  }
+  arm_list <- as.list(arm_list)
[…]

### 2017-06-29 AugUCB/BayesUCB.R

@@ -1,0 +1,176 @@
+# Using Bayes Quantiles, similar to
+# On Bayesian Upper Confidence Bounds for Bandit Problems
+# Kaufmann, Cappe, Garivier
+
+#system.time(res_bucb1 <- BayesUCB(means = mean_twenty,
+#                                   tau = 0.04, epsilon = 0.01,
+#                                   alpha = 0.04, beta = 0.96,
+#                                   K = 20, rounds = 2000,
+#                                   variances = NA, seed = 60,
+#                                   rate = "inverse"))
+#system.time(res_bucb2 <- BayesUCB(means = mean_twenty,
+#                                    tau = 0.04, epsilon = 0.01,
+#                                    alpha = 0.04, beta = 0.96,
+#                                    K = 20, rounds = 2000,
+#                                    variances = NA, seed = 60,
+#                                    rate = "inverse_horizon"))
+#system.time(res_bucb3 <- BayesUCB(means = mean_twenty,
+#                                    tau = 0.04, epsilon = 0.01,
+#                                    alpha = 0.04, beta = 0.96,
+#                                    K = 20, rounds = 2000,
+#                                    variances = NA, seed = 60,
+#                                    rate = "inverse_squared"))
+#system.time(res_bucb4 <- BayesUCB(means = mean_twenty,
+#                                    tau = 0.04, epsilon = 0.01,
+#                                    alpha = 0.04, beta = 0.96,
+#                                    K = 20, rounds = 2000,
+#                                    variances = NA, seed = 60,
+#                                    rate = "inverse_log"))
+#lapply(res_bucb1$arm_list, length)
+#data.frame(means = mean_twenty,
+#           a = unlist(lapply(res_bucb1$arm_list, length)),
+#           b = unlist(lapply(res_bucb2$arm_list, length)),
+#           c = unlist(lapply(res_bucb3$arm_list, length)),
+#           d = unlist(lapply(res_bucb4$arm_list, length)))
+#lapply(res_bucb2$arm_list, length)
+#res_bucb$means#
+
+#res_bucb <- as.data.frame(res_bucb$mean_storage)
+#res_bucb$round <- 1:dim(res_bucb)[1]
+#res_bucb_long <- gather(res_bucb[1:700,], key = "Arm", value = "Mean", 
+#                        -round)
+#ggplot(res_bucb_long, aes(x = round, y = Mean, color = Arm)) +
+#  geom_line()
+
[…]

### 2017-06-29 AugUCB/JustCount.R

@@ -1,0 +1,106 @@
+# Just count
+
+#mean_twenty <- c(0.0005, 0.0005, 0.001, 0.001, 0.005,
+#                 0.3, 0.4, 0.5, 0.6, 0.7,
+#                 0.01, 0.02, 0.02,
+#                 0.06, 0.06, 0.07,
+#                 0.035, 0.035, 0.045, 0.045)
+#system.time(res_jc <- JC_bandit(means = mean_twenty,
+#                                tau = 0.04, epsilon = 0.01,
+#                                alpha = 0.04, beta = 0.96,
+#                                K = 20, rounds = 5000, seed = 58))
+#lapply(res_jc$arm_list, length)
+#res_jc$means
+#jc_means <- as.data.frame(res_jc$mean_storage)
+#jc_means$round <- 1:dim(jc_means)[1]
+#jc_means_long <- gather(jc_means, key = "Arm", value = "Mean", -round)
+#ggplot(jc_means_long, aes(x = round, y = Mean, color = Arm)) +
+#  geom_line()
+
+
+
+JC_bandit <- function(means, K, rounds, tau, epsilon,
+                      alpha, beta, verbose = FALSE, seed = NA) {
+  
+  if(!is.na(seed)) set.seed(seed)
+  
+  # initialize by pulling each arm once
+  arm_list <- NA
+  for(i in 1:K) {
+    # Ideally it should also take an argument specifying how
+    # the sample is generated (e.g., from existing data, bernoulli or other distr.)
+    arm_list[[i]] <- pull_arm_JC(k = i, means = means)
+  }
+  arm_list <- as.list(arm_list)
+  # initialize mean storage and the counter
+  mean_storage <- matrix(unlist(lapply(arm_list, mean)), nrow = 1)
+  counter <- K
+  
+  for(i in (K+1):rounds) {
+    if(verbose) message(paste("this is round", i))
+    next_arm <- get_min(unlist(get_next_arm_JC(arm_list, tau = tau,
+                                               epsilon = epsilon,
+                                               alpha = alpha,
+                                               beta = beta)))
+    
+    if(verbose) message("arm selecting done")
+    arm_list[[next_arm]] <- c(arm_list[[next_arm]], pull_arm_JC(k = next_arm, 
+                                                                means = means))
+    mean_storage <- rbind(mean_storage, unlist(lapply(arm_list,
+                                                      get_posterior_mean_JC,
[…]

### 2017-06-29 AugUCB/PI.R

@@ -1,0 +1,192 @@
+# Probability of Improvement-like (actually, probability of error)
+
+#means <- c(0.55, 0.38, 0.95)
+#variances <- c(0.5, 0.9, 1.7)
+#system.time(res_pi <- PI_bandit(means = means, variances = variances,
+#                                alpha = 10, beta = 5000,
+#                                mean_prior = 0.5, n_prior = 10,
+#                                K = 3, rounds = 5000,
+#                                seed = 54))
+# Bernoulli version
+#means <- c(0.02, 0.06, 0.065, 0.07, 0.01, 0.03)
+#system.time(res_pi <- PI_bandit(means = means, alpha = 0.04*28, beta = 0.96*28,
+#                                K = 6, rounds = 5000,
+#                                tau = 0.04, epsilon = 0.011,
+#                                variances = NA, seed = 54))
+
+#means <- c(0.55, 0.38, 0.95)
+#system.time(res_pi <- PI_bandit(means = means, alpha = 1, beta = 1,
+#                                K = 3, rounds = 5000,
+#                                variances = NA, seed = 54))
+# user  system elapsed 
+#0.401   0.079   0.481
+#lapply(res_pi$arm_list, length)
+#res_pi$means
+#means
+#plot(x = c(0,5000), y = c(0,0.1), type = "n")
+#lines(res_pi$mean_storage[,1])
+#lines(res_pi$mean_storage[,2], col = "blue")
+#lines(res_pi$mean_storage[,3], col = "red")
+#lines(res_pi$mean_storage[,4], col = "red")
+#lines(res_pi$mean_storage[,5], col = "red")
+#lines(res_pi$mean_storage[,6], col = "red")
+
+#mean_twenty <- c(0.0005, 0.0005, 0.001, 0.001, 0.005,
+#                 0.3, 0.4, 0.5, 0.6, 0.7,
+#                 0.01, 0.02, 0.02,
+#                 0.06, 0.06, 0.07,
+#                 0.035, 0.035, 0.045, 0.045)
+#system.time(res_pi <- PI_bandit(means = mean_twenty,
+#                                tau = 0.04, epsilon = 0.01,
+#                                alpha = 0.04, beta = 0.96,
+#                                K = 20, rounds = 2000,
+#                                variances = NA, seed = 58))
+#lapply(res_pi$arm_list, length)
+#res_pi$means
+#pi_means <- as.data.frame(res_pi$mean_storage)
[…]

### 2017-06-29 AugUCB/TTS.R

@@ -1,0 +1,184 @@
+# Use probability of error but do proportional sampling
+# Threshold Thompson Sampling-like
+
+#means <- c(0.55, 0.38, 0.95)
+#variances <- c(0.5, 0.9, 1.7)
+#system.time(res_tts <- TTS(means = means, alpha = 1, beta = 1,
+#                           K = 3, rounds = 5000, 
+#                           variances = NA, seed = 54))
+# user  system elapsed 
+#0.390   0.057   0.446 
+#lapply(res_tts$arm_list, length)
+#res_tts$means
+#means
+#plot(x = c(0,5000), y = c(0,2), type = "n")
+#lines(res_tts$mean_storage[,1])
+#lines(res_tts$mean_storage[,2], col = "blue")
+#lines(res_tts$mean_storage[,3], col = "red")
+
+#system.time(res_tts <- TTS(means = mean_twenty,
+#                          tau = 0.04, epsilon = 0.01,
+#                          alpha = 0.04, beta = 0.96,
+#                          K = 20, rounds = 2000,
+#                          variances = NA, seed = 60))
+#system.time(res_tts2 <- TTS(means = mean_twenty,
+#                           tau = 0.04, epsilon = 0.01,
+#                           alpha = 0.04, beta = 0.96,
+#                           K = 20, rounds = 2000,
+#                           variances = NA, seed = 60,
+#                           interval_adj = TRUE))
+#lapply(res_tts$arm_list, length)
+#res_tts$means
+
+#tts_means <- as.data.frame(res_tts$mean_storage)
+#tts_means$round <- 1:dim(tts_means)[1]
+#tts_means_long <- gather(tts_means[1:700,], key = "Arm", value = "Mean", -round)
+#ggplot(tts_means_long, aes(x = round, y = Mean, color = Arm)) +
+#  geom_line()
+
+###############################################################################
+
+TTS <- function(means, K = 4, rounds = 5000, tau = 0.5, epsilon = 0.1,
+                alpha = 1, beta = 1, mean_prior = NA, n_prior = NA,
+                variances = NA, verbose = FALSE, seed = NA,
+                interval_adj = FALSE) {
+  
+  if(!is.na(seed)) set.seed(seed)
+  
+  # initialize by pulling each arm once
+  arm_list <- NA
+  for(i in 1:K) {
+    # Ideally it should also take an argument specifying how
[…]

### 2017-06-29 AugUCB/Uniform.R

@@ -2,19 +2,19 @@
 # Common knowledge
 # Our ancestors
 
-means <- c(0.55, 0.38, 0.95)
-variances <- c(0.5, 0.9, 1.7)
-system.time(res_uniform <- uniform_bandit(means = means, K = 3, rounds = 5000, 
-                                          variances = variances, seed = 54))
+#means <- c(0.55, 0.38, 0.95)
+#variances <- c(0.5, 0.9, 1.7)
+#system.time(res_uniform <- uniform_bandit(means = means, K = 3, rounds = 5000, 
+#                                          variances = variances, seed = 54))
 # user  system elapsed 
 #0.533   0.065   0.603 
-lapply(res_uniform$arm_list, length)
-res_uniform$means
-means
-plot(x = c(0,5000), y = c(0,2), type = "n")
-lines(res_uniform$mean_storage[,1])
-lines(res_uniform$mean_storage[,2], col = "blue")
-lines(res_uniform$mean_storage[,3], col = "red")
+#lapply(res_uniform$arm_list, length)
+#res_uniform$means
+#means
+#plot(x = c(0,5000), y = c(0,2), type = "n")
+#lines(res_uniform$mean_storage[,1])
+#lines(res_uniform$mean_storage[,2], col = "blue")
+#lines(res_uniform$mean_storage[,3], col = "red")
 
 uniform_bandit <- function(means, K = 4, rounds = 5000,
                            variances = NA, verbose = FALSE, seed = NA) {

### 2017-06-29 AugUCB/calibrate_algorithms_from_data.R

@@ -1,0 +1,210 @@
+# run a simulation based on a simple example that can hopefully serve to
+# calibrate the algorithms
+########################################################################
+# load functions
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+
+########################################################################
+# Create the data
+
+mean_loc <- c(0.1, 0.1, 0.1, 
+              0.35, 0.45, 0.55, 0.65,
+              0.9, 0.9, 0.9)
+tau_loc <- 0.5
+epsilon_loc <- 0.1
+
+data_list <- list()
+set.seed(1024)
+for(j in 1:5000) {
+  curr_data <- data.frame(rep(NA, times = 1000))
+  for(i in 1:length(mean_loc)) {
+    curr_data[[i]] <- as.numeric(purrr::rbernoulli(1000, p  = mean_loc[i]))
+  }
+  names(curr_data) <- paste0("V", rep(1:length(mean_loc)))
+  data_list[[j]] <- curr_data
+}
+
+########################################################################
+# Standard APT Algorithm
+# a seed is built in
+system.time(loc_APT <- para_bandit_sim_APT(data = data_list, rounds = 1000, 
+                                           tau = tau_loc, epsilon = epsilon_loc))
+# user  system elapsed 
+#6.508   3.544 300.383
+save(loc_APT, file = paste0(current_path, "loc_APT.Rda"))
+loc_comp_APT <- compare_to_ground_truth(mean_loc, loc_APT, tau_loc, 
+                                        epsilon_loc)$mean
+save(loc_comp_APT, file = paste0(current_path, "loc_comp_APT.Rda"))
+########################################################################
+# Standard Uniform
+
+system.time(loc_UNIFORM <- para_bandit_sim_uniform(data = data_list, 
+                                                   rounds = 1000))
+# user  system elapsed 
+# 6.268   3.400 211.002 
+save(loc_UNIFORM, file = paste0(current_path, "loc_UNIFORM.Rda"))
+loc_comp_UNIFORM <- compare_to_ground_truth(mean_loc, loc_UNIFORM, tau_loc, 
+                                            epsilon_loc)$mean
+save(loc_comp_UNIFORM, file = paste0(current_path, "loc_comp_UNIFORM.Rda"))
+
+########################################################################
[…]

### 2017-06-29 AugUCB/calibrate_algorithms_from_data2.R

@@ -1,0 +1,187 @@
+# run a simulation based on a simple example that can hopefully serve to
+# calibrate the algorithms
+########################################################################
+# load functions
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+
+########################################################################
+# Create the data
+
+mean_loc2 <- c(0.2+(0:3)*0.05,
+              0.45, 0.55,
+              0.65+(0:3)*0.05)
+tau_loc2 <- 0.5
+epsilon_loc2 <- 0.1
+
+data_list2 <- list()
+for(j in 1:5000) {
+  set.seed(1024+j)
+  curr_data <- data.frame(rep(NA, times = 1000))
+  for(i in 1:length(mean_loc2)) {
+    curr_data[[i]] <- as.numeric(purrr::rbernoulli(1000, p  = mean_loc2[i]))
+  }
+  names(curr_data) <- paste0("V", rep(1:length(mean_loc2)))
+  data_list2[[j]] <- curr_data
+}
+
+########################################################################
+# Standard APT Algorithm
+# a seed is built in
+system.time(loc2_APT <- para_bandit_sim_APT(data = data_list2, rounds = 1000, 
+                                           tau = tau_loc2, epsilon = epsilon_loc2))
+# user  system elapsed 
+#6.508   3.544 300.383
+save(loc2_APT, file = paste0(current_path, "loc2_APT.Rda"))
+loc2_APT[[1]]
+loc2_APT[[5000]]
+
+loc2_comp_APT <- compare_to_ground_truth(mean_loc2, loc2_APT, tau_loc2, 
+                                        epsilon_loc2)$mean
+save(loc2_comp_APT, file = paste0(current_path, "loc2_comp_APT.Rda"))
+########################################################################
+# Standard Uniform
+
+system.time(loc2_UNIFORM <- para_bandit_sim_uniform(data = data_list2, 
+                                                    rounds = 1000))
+# user  system elapsed 
+# 6.268   3.400 211.002 
+save(loc2_UNIFORM, file = paste0(current_path, "loc2_UNIFORM.Rda"))
+loc2_comp_UNIFORM <- compare_to_ground_truth(mean_loc2, loc2_UNIFORM, tau_loc2, 
+                                            epsilon_loc2)$mean
[…]

### 2017-06-29 AugUCB/calibrate_algorithms_from_data3.R

@@ -1,0 +1,362 @@
+# run a simulation based on a simple example that can hopefully serve to
+# calibrate the algorithms
+########################################################################
+# load functions
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+
+########################################################################
+# Create the data
+
+mean_loc3 <- c(0.001, 0.005, 0.01, 0.015,
+               0.0475, 0.0525,
+               0.085, 0.09, 0.095, 0.099)
+tau_loc3 <- 0.05
+epsilon_loc3 <- 0.005
+
+data_list3 <- list()
+set.seed(1024)
+for(j in 1:5000) {
+  curr_data <- data.frame(rep(NA, times = 1000))
+  for(i in 1:length(mean_loc3)) {
+    curr_data[[i]] <- as.numeric(purrr::rbernoulli(1000, p  = mean_loc3[i]))
+  }
+  names(curr_data) <- paste0("V", rep(1:length(mean_loc3)))
+  data_list3[[j]] <- curr_data
+}
+
+########################################################################
+# Standard APT Algorithm
+# a seed is built in
+system.time(loc3_APT <- para_bandit_sim_APT(data = data_list3, rounds = 1000, 
+                                            tau = tau_loc3, epsilon = epsilon_loc3))
+# user  system elapsed 
+#6.508   3.544 300.383
+save(loc3_APT, file = paste0(current_path, "loc3_APT.Rda"))
+loc3_comp_APT <- compare_to_ground_truth(mean_loc3, loc3_APT, tau_loc3, 
+                                         epsilon_loc3)$mean
+save(loc3_comp_APT, file = paste0(current_path, "loc3_comp_APT.Rda"))
+########################################################################
+# Standard Uniform
+
+system.time(loc3_UNIFORM <- para_bandit_sim_uniform(data = data_list3, 
+                                                    rounds = 1000))
+# user  system elapsed 
+# 6.268   3.400 211.002 
+save(loc3_UNIFORM, file = paste0(current_path, "loc3_UNIFORM.Rda"))
+loc3_comp_UNIFORM <- compare_to_ground_truth(mean_loc3, loc3_UNIFORM, tau_loc3, 
+                                             epsilon_loc3)$mean
+save(loc3_comp_UNIFORM, file = paste0(current_path, "loc3_comp_UNIFORM.Rda"))
+
[…]

### 2017-06-29 AugUCB/calibrate_algorithms_from_data4.R

@@ -1,0 +1,369 @@
+# run a simulation based on a simple example that can hopefully serve to
+# calibrate the algorithms
+########################################################################
+# load functions
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+
+########################################################################
+# Create the data
+
+# do 2000 rounds
+mean_loc4 <- c(0.0005, 0.001, 0.001, 0.005, 0.009,
+               0.02, 0.0275, 0.0325, 0.04,
+               0.08, 0.09)
+tau_loc4 <- 0.03
+epsilon_loc4 <- 0.005
+
+data_list4 <- list()
+set.seed(1024)
+for(j in 1:5000) {
+  curr_data <- data.frame(rep(NA, times = 2000))
+  for(i in 1:length(mean_loc4)) {
+    curr_data[[i]] <- as.numeric(purrr::rbernoulli(2000, p  = mean_loc4[i]))
+  }
+  names(curr_data) <- paste0("V", rep(1:length(mean_loc4)))
+  data_list4[[j]] <- curr_data
+}
+
+########################################################################
+# Standard APT Algorithm
+# a seed is built in
+system.time(loc4_APT <- para_bandit_sim_APT(data = data_list4, rounds = 2000, 
+                                            tau = tau_loc4, epsilon = epsilon_loc4))
+# user  system elapsed 
+#6.508   3.544 300.383
+save(loc4_APT, file = paste0(current_path, "loc4_APT.Rda"))
+loc4_comp_APT <- compare_to_ground_truth(mean_loc4, loc4_APT, tau_loc4, 
+                                         epsilon_loc4)$mean
+save(loc4_comp_APT, file = paste0(current_path, "loc4_comp_APT.Rda"))
+########################################################################
+# Standard Uniform
+
+system.time(loc4_UNIFORM <- para_bandit_sim_uniform(data = data_list4, 
+                                                    rounds = 2000))
+# user  system elapsed 
+# 6.268   3.400 211.002 
+save(loc4_UNIFORM, file = paste0(current_path, "loc4_UNIFORM.Rda"))
+loc4_comp_UNIFORM <- compare_to_ground_truth(mean_loc4, loc4_UNIFORM, tau_loc4, 
[…]

### 2017-06-29 AugUCB/calibrate_algorithms_from_data5.R

@@ -1,0 +1,376 @@
+# run a simulation based on a simple example that can hopefully serve to
+# calibrate the algorithms
+########################################################################
+# load functions
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+
+########################################################################
+# Create the data
+
+# do 2000 rounds
+mean_loc5 <- c(0.0005, 0.001,
+               0.05, 0.055,
+               0.065, 0.075,
+               0.085, 0.09,
+               0.1, 0.1)
+tau_loc5 <- 0.07
+epsilon_loc5 <- 0.01
+
+plot(mean_loc5, rep(1,10))
+abline(v=tau_loc5)
+abline(v=tau_loc5+epsilon_loc5, lty=2)
+abline(v=tau_loc5-epsilon_loc5, lty=2)
+
+data_list5 <- list()
+set.seed(256)
+for(j in 1:5000) {
+  curr_data <- data.frame(rep(NA, times = 1000))
+  for(i in 1:length(mean_loc5)) {
+    curr_data[[i]] <- as.numeric(purrr::rbernoulli(1000, p  = mean_loc5[i]))
+  }
+  names(curr_data) <- paste0("V", rep(1:length(mean_loc5)))
+  data_list5[[j]] <- curr_data
+}
+
+########################################################################
+# Standard APT Algorithm
+# a seed is built in
+system.time(loc5_APT <- para_bandit_sim_APT(data = data_list5, rounds = 1000, 
+                                            tau = tau_loc5, epsilon = epsilon_loc5))
+# user  system elapsed 
+#6.508   3.544 300.383
+save(loc5_APT, file = paste0(current_path, "loc5_APT.Rda"))
+loc5_comp_APT <- compare_to_ground_truth(mean_loc5, loc5_APT, tau_loc5, 
+                                         epsilon_loc5)$mean
+save(loc5_comp_APT, file = paste0(current_path, "loc5_comp_APT.Rda"))
+########################################################################
+# Standard Uniform
+
+system.time(loc5_UNIFORM <- para_bandit_sim_uniform(data = data_list5, 
+                                                    rounds = 1000))
+# user  system elapsed 
+# 6.268   3.400 211.002 
[…]

### 2017-06-29 AugUCB/parallelized_simulations.R

@@ -22,14 +22,22 @@ para_bandit_sim_AugUCB <- function(reps = 6, seed = NA, do_verbose = FALSE, ...)
     AugUCB(...)$mean_storage
 }
 
-means <- c(0.55, 0.38, 0.95)
-variances <- c(0.5, 0.9, 1.7)
-system.time(
-para_res <- para_bandit_sim_AugUCB(reps = 100, means = means, variances = variances, 
-                                   K = 3, rounds = 5000)
-)
+#means <- c(0.55, 0.38, 0.95)
+#variances <- c(0.5, 0.9, 1.7)
+#system.time(
+#para_res <- para_bandit_sim_AugUCB(reps = 100, means = means, variances = variances, 
+#                                   K = 3, rounds = 5000)
+#)
 #  user  system elapsed 
 # 0.331   0.256  98.026
+#system.time(
+#para_res_ber <- para_bandit_sim_AugUCB(reps = 100, means = means, variances = NA, 
+#                                       K = 3, rounds = 5000)
+#)
+#   user  system elapsed 
+#  0.373   0.253  91.681 
+
+#################################################################################
 
 para_bandit_sim_APT <- function(reps = 6, seed = NA, do_verbose = FALSE, ...) {
   require(foreach)
@@ -44,12 +52,36 @@ para_bandit_sim_APT <- function(reps = 6, seed = NA, do_verbose = FALSE, ...) {
     APT(...)$mean_storage
 }
 
-system.time(
-  para_apt <- para_bandit_sim_APT(reps = 100, means = means, variances = variances, 
-                                  K = 3, rounds = 5000)
-)
+#system.time(
+#  para_apt <- para_bandit_sim_APT(reps = 100, means = means, variances = variances, 
+#                                  K = 3, rounds = 5000)
+#)
 #  user  system elapsed 
 # 0.255   0.126  33.540
+#system.time(
+#  para_apt_ber <- para_bandit_sim_APT(reps = 100, means = means, variances = NA, 
+#                                      K = 3, rounds = 5000)
+#)
+# user  system elapsed 
+#0.237   0.086  23.364
+
+#################################################################################
+
+para_bandit_sim_KL <- function(reps = 6, seed = NA, do_verbose = FALSE, ...) {
+  require(foreach)
+  require(doParallel)
+  
+  gc()
+  cl <- makeCluster(max(1,detectCores()-1))
+  registerDoParallel(cl)
+  foreach(j = 1:reps, .errorhandling = 'remove',
[…]

### 2017-06-29 AugUCB/run_from_data.R

@@ -1,0 +1,510 @@
+# pull_arm_from_tsdata
+
+pull_arm_from_tsdata <- function(k, data, iter) {
+  data[iter, k]
+}
+
+##############################################################
+
+# General functions
+
+get_min <- function(x) {
+  mini <- min(x)
+  ifelse(sum(x==mini) == 1, which.min(x),
+         sample(which(x==mini)))
+}
+
+##############################################################
+
+# APT Algorithm
+
+get_next_arm_apt <- function(armls, tau, rounds, epsilon) {
+  get_metric <- function(x) {
+    xhat <- mean(x)
+    ni <- length(x)
+    return(sqrt(ni) * (abs(xhat-tau)+epsilon))
+  }
+  lapply(armls, get_metric)
+}
+
+APT_from_tsdata <- function(data, rounds = 5000, tau, epsilon,
+                            verbose = FALSE, seed = NA) {
+  
+  if(!is.na(seed)) set.seed(seed)
+  K <- dim(data)[2]
+  
+  # initialize by pulling each arm once
+  arm_list <- diag(as.matrix(data[1:K,]))
+  arm_list <- as.list(arm_list)
+  
+  # initialize mean storage, arm sequence, and the counter
+  mean_storage <- matrix(unlist(lapply(arm_list, mean)), nrow = 1)
+  arm_sequence <- 1:K
+  
+  for(i in (K+1):rounds) {
+    if(verbose) message(paste("this is round", i))
+    next_arm <- get_min(unlist(get_next_arm_apt(arm_list, tau = tau, 
+                                                rounds = rounds, 
+                                                epsilon = epsilon)))
+    arm_sequence <- c(arm_sequence, next_arm)
+    
+    if(verbose) message("arm selecting done")
+    arm_list[[next_arm]] <- c(arm_list[[next_arm]], data[i, next_arm])
+    mean_storage <- rbind(mean_storage, unlist(lapply(arm_list, mean)))
+    
+    if(verbose) message("arm pulling done")
+    
+  }
+  return(list(means = unlist(lapply(arm_list, mean)),
+              arm_list = arm_list,
+              input = data,
+              arm_sequence = arm_sequence,
+              mean_storage = mean_storage))
+}
+
+##############################################################
+
+# KL-based Algorithm
+
+KL_bandit_from_tsdata <- function(data, rounds = 5000, tau, epsilon,
+                                  verbose = FALSE, seed = NA,
+                                  at_tau = FALSE, horizon = NA) {
+  
[…]

### 2017-06-29 AugUCB/run_parallelized_from_data.R

@@ -1,0 +1,242 @@
+# parallelize bandit simulation
+
+#set.seed(512)
+#testt <- data.frame(rep(NA, times = 6000))
+#for(i in 1:length(mean_002)) {
+#  testt[[i]] <- as.numeric(purrr::rbernoulli(6000, p  = mean_002[i]))
+#}
+
+#set.seed(513)
+#testt2 <- data.frame(rep(NA, times = 6000))
+#for(i in 1:length(mean_002)) {
+#  testt2[[i]] <- as.numeric(purrr::rbernoulli(6000, p  = mean_002[i]))
+#}
+
+#test_list <- list(testt, testt2)
+
+#para_test_res <- para_bandit_sim_APT(data = test_list, rounds = 5000, 
+#                                     tau = tau_002, epsilon = epsilon_002)
+#para_test_resKL <- para_bandit_sim_KL(data = test_list, rounds = 5000, 
+#                                      tau = tau_002, epsilon = epsilon_002, 
+#                                      at_tau = FALSE)
+#para_test_resuni <- para_bandit_sim_uniform(data = test_list, rounds = 5000)
+#para_test_resPI <- para_bandit_sim_PI(data = test_list, rounds = 5000,
+#                                      tau = tau_002, epsilon = epsilon_002,
+#                                      alpha = tau_002, beta = 1 - tau_002)
+#para_test_resbucb <- para_bandit_sim_bucb(data = test_list, rounds = 5000, 
+#                                          rate = "inverse",
+#                                          tau = tau_002, epsilon = epsilon_002, 
+#                                          alpha = tau_002, beta = 1-tau_002)
+
+#############################################################################
+
+# Get the average performance over all simulations
+
+# expect a list of matrices of size rounds x K as input from the simulations,
+# as well as a vector with the true means of length K to compare agains
+compare_to_ground_truth <- function(true_means, sim_res, tau, epsilon) {
+  message(paste0("Comparing ", length(sim_res), " simulations."))
+  true_classification_up <- which(true_means > tau+epsilon)
+  true_classification_down <- which(true_means < tau-epsilon)
+  
+  get_iter_error <- function(x, true_class_up, true_class_down) {
+    ifelse(true_class_up %in% which(x > tau) && 
+             true_class_down %in% which(x < tau),
+           0,1)
+  }
+  
+  get_error <- function(res_df, ...) {
+    apply(res_df$mean_storage, 1, get_iter_error, ...)
+  }
[…]

### 2017-06-29 AugUCB/simulations2.R

@@ -1,0 +1,147 @@
+script_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+
+# load all required functions and bandit models
+tau_001 <- 0.035
+epsilon_001 <- 0.005
+
+mean_001 <- c(0.0005, 0.0005, 0.001, 0.001, 
+                  0.005, 0.005, 0.01, 0.01,
+                  0.05, 0.05, 0.1, 0.1,
+                  0.11, 0.12, 0.13, 0.14,
+                  0.06, 0.07, 0.08, 0.08)
+                  
+length(mean_001)
+
+####################################################################
+# for each model, run 1000 repititions with a budget of 600 samples
+source(paste0(script_path, "parallelized_simulations.R"))
+####################################################################
+source(paste0(script_path, "Uniform.R"))
+# Standard uniform sampling (which doesn't need info about tau and epsilon!)
+system.time(
+  ber001_uniform <- para_bandit_sim_uniform(reps = 1000, means = mean_001,
+                                            variances = NA, K = 20, rounds = 1000)
+)
+#  user  system elapsed 
+# 0.889   0.275  36.618
+save(ber001_uniform, file = paste0(script_path, "ber001_uniform.Rda"))
+ber001_uniform_comp <- compare_to_ground_truth(mean_001, ber001_uniform, 
+                                               tau = tau_001, epsilon = epsilon_001)
+save(ber001_uniform_comp, file = paste0(script_path, "ber001_uniform_comp.Rda"))
+lines(log(ber001_uniform_comp$mean), col = "black", xlim = c(0,1000))
+####################################################################
+
+source(paste0(script_path, "APT.R"))
+# Standard APT
+system.time(
+  ber001_APT <- para_bandit_sim_APT(reps = 1000, means = mean_001, 
+                                    variances = NA, K = 20, rounds = 1000,
+                                    tau = tau_001, epsilon = epsilon_001)
+)
+# user  system elapsed 
+#1.140   0.587 109.989 
+save(ber001_APT, file = paste0(script_path, "ber001_APT.Rda"))
+ber001_APT_comp <- compare_to_ground_truth(mean_001, ber001_APT, 
+                                           tau = tau_001, epsilon = epsilon_001)
+save(ber001_APT_comp, file = paste0(script_path, "ber001_APT_comp.Rda"))
+lines(log(ber001_APT_comp$mean), col = "red", xlim = c(0,1000))
+
[…]

### 2017-06-29 AugUCB/simulations3.R

@@ -1,0 +1,192 @@
+script_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+
+# load all required functions and bandit models
+tau_002 <- 0.035
+epsilon_002 <- 0.005
+
+# symmetric distances
+mean_002 <- c(0.033, 0.033, 0.037, 0.037,
+              0.031, 0.031, 0.039, 0.039,
+              0.027, 0.027, 0.043, 0.043,
+              0.02, 0.02, 0.05, 0.05,
+              0.005, 0.005, 0.065, 0.065)
+
+length(mean_002)
+
+####################################################################
+# for each model, run 1000 repititions with a budget of 600 samples
+source(paste0(script_path, "parallelized_simulations.R"))
+####################################################################
+source(paste0(script_path, "Uniform.R"))
+# Standard uniform sampling (which doesn't need info about tau and epsilon!)
+system.time(
+  ber002_uniform <- para_bandit_sim_uniform(reps = 1000, means = mean_002,
+                                            variances = NA, K = 20, rounds = 1000)
+)
+save(ber002_uniform, file = paste0(script_path, "ber002_uniform.Rda"))
+ber002_uniform_comp <- compare_to_ground_truth(mean_002, ber002_uniform, 
+                                               tau = tau_002, epsilon = epsilon_002)
+save(ber002_uniform_comp, file = paste0(script_path, "ber002_uniform_comp.Rda"))
+plot(log(ber002_uniform_comp$mean), type = "l", col = "black", xlim = c(0,1000), ylim = c(-1,0))
+####################################################################
+
+source(paste0(script_path, "APT.R"))
+# Standard APT
+system.time(
+  ber002_APT <- para_bandit_sim_APT(reps = 1000, means = mean_002, 
+                                    variances = NA, K = 20, rounds = 1000,
+                                    tau = tau_002, epsilon = epsilon_002)
+)
+save(ber002_APT, file = paste0(script_path, "ber002_APT.Rda"))
+ber002_APT_comp <- compare_to_ground_truth(mean_002, ber002_APT, 
+                                           tau = tau_002, epsilon = epsilon_002)
+save(ber002_APT_comp, file = paste0(script_path, "ber002_APT_comp.Rda"))
+lines(log(ber002_APT_comp$mean), col = "red", xlim = c(0,1000))
+
+####################################################################
+
+source(paste0(script_path, "KL.R"))
[…]

### 2017-07-19 synthetic_experiments/experiments_summary.Rmd
add experiment scripts

---
output: pdf_document
urlcolor: blue
fontsize: 12pt
---

## Comparison of Suggested Algorithms Based on Synthetic Data

In the following, we present results regarding the performance of difference algorithms. All experiments are based on the average error of algorithms over 5000 simulations. All experiments are with Bernoulli distributions as arms as in Locatelli et al. (2016).

In general, we compare the following algorithms:

- Uniform Sampling (UNIFORM)
- Anytime Parameter-free Thresholding algorithm (APT), [Locatelli et al., 2016](http://proceedings.mlr.press/v48/locatelli16.html)
- Augmented UCB (AugUCB), [Mukherjee et al., 2017](https://arxiv.org/pdf/1704.02281)
- Kullback-Leibler Divergence-based Algorithm (KL)
- Posterior Probability of Error-based Algorithm (PI)
- Thompson Sampling-like Algorithm (TTS)
- Bayes UCB Algorithm adapted for Thresholding Bandits (BUCB), compare *[On Bayesian Upper Confidence Bounds for Bandit Problems](http://proceedings.mlr.press/v22/kaufmann12.html)* by Kaufmann et al., 2012

## Experiment 1

The same as experiment 1 in Locatelli et al. (2016). We have the following means and thresholds:

```{r, echo = FALSE, fig.height = 3}
mean_loc <- c(0.1, 0.1, 0.1, 
              0.35, 0.45, 0.55, 0.65,
              0.9, 0.9, 0.9)
tau_loc <- 0.5
epsilon_loc <- 0.1

plot(mean_loc, c(0.9,1,1.1,1,1,1,1,1.1,1,0.9), pch = 19, ylim = c(0.8,1.2), ylab = "", main = "Setup Experiment 1", xlab = "Mean Locations")
abline(v=tau_loc)
abline(v=tau_loc+epsilon_loc, lty=2)
abline(v=tau_loc-epsilon_loc, lty=2)

# Complexity:
print("Complexity as defined in Locatelli et al. (2016):")
round(sum((abs(mean_loc-tau_loc)+epsilon_loc)^(-2)))
```

The experiment results are as follows:

```{r, echo = FALSE}
current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
library(ggplot2)

load(paste0(current_path, "loc_comp_APT.Rda"))
load(paste0(current_path, "loc_comp_AugUCB.Rda"))
load(paste0(current_path, "loc_comp_UNIFORM.Rda"))
load(paste0(current_path, "loc_comp_PI.Rda"))
load(paste0(current_path, "loc_comp_TTS.Rda"))
load(paste0(current_path, "loc_comp_BUCB.Rda"))
load(paste0(current_path, "loc_comp_BUCB_horizon.Rda"))
load(paste0(current_path, "loc_comp_BUCB_squared.Rda"))
load(paste0(current_path, "loc_comp_BUCB_power5.Rda"))
load(paste0(current_path, "loc_comp_KL.Rda"))
load(paste0(current_path, "loc_comp_KL_tau_horizon.Rda"))
load(paste0(current_path, "loc_comp_KL_horizon1.Rda"))
load(paste0(current_path, "loc_comp_KL_not_tau_horizon1000.Rda"))

alg_names <- rep(c("APT", "AugUCB", "UNIFORM", "PI", "TTS", "BUCB", "BUCB_horizon", "BUCB_squared", "KL_at_tau", "KL_not_at_tau"), each = 991)
index <- rep(10:1000, times = 10)
alg_res <- log(c(loc_comp_APT, loc_comp_AugUCB, loc_comp_UNIFORM,
             loc_comp_PI, loc_comp_TTS, loc_comp_BUCB, loc_comp_BUCB_horizon,
             loc_comp_BUCB_squared, loc_comp_KL_tau_horizon,
             loc_comp_KL_not_tau_horizon1000))
loc1_comp_res <- data.frame(index = index, names = alg_names, 
                            results = alg_res)
ggplot(loc1_comp_res, aes(x = index, y = alg_res)) + geom_line(aes(group = alg_names, color = alg_names)) +
  labs(title = "Experiment 1 Results", y = "log(Error)")
```

We clearly observe that most algorithms are able to solve this problem at more or less the same performance. Also, most algorithms are clearly superior to uniform sampling. The proposed new algorithms cannot perform better than APT. The BayesUCB algorithm without a $\log (T)$ horizon term in the denominator performs worse. Same for the KL-based algorithm that does not take the $\epsilon$ interval into account.

\newpage

## Experiment 2

The same as experiment 3 in Locatelli et al. (2016). We have the following means, threshold (solid line), and epsilon interval (dashed line):

```{r, echo = FALSE, fig.height = 3}
mean_loc <- c(0.4-0.2^(1:4),
              0.45, 0.55,
              0.6+0.2^(5-(1:4)))
tau_loc <- 0.5
epsilon_loc <- 0.1

plot(mean_loc, c(1,1,0.98,1.02,1,1,1.02,0.98,1,1), pch = 19, ylim = c(0.8,1.2), ylab = "", main = "Setup Experiment 2", xlab = "Mean Locations")
abline(v=tau_loc)
abline(v=tau_loc+epsilon_loc, lty=2)
abline(v=tau_loc-epsilon_loc, lty=2)

# Complexity:
print("Complexity as defined in Locatelli et al. (2016):")
round(sum((abs(mean_loc-tau_loc)+epsilon_loc)^(-2)))
```

The experiment results are as follows:

```{r, echo = FALSE}
current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
library(ggplot2)

load(paste0(current_path, "loc2_comp_APT.Rda"))
load(paste0(current_path, "loc2_comp_AugUCB.Rda"))
load(paste0(current_path, "loc2_comp_UNIFORM.Rda"))
load(paste0(current_path, "loc2_comp_PI.Rda"))
load(paste0(current_path, "loc2_comp_TTS.Rda"))
load(paste0(current_path, "loc2_comp_BUCB.Rda"))
load(paste0(current_path, "loc2_comp_BUCB_horizon.Rda"))
load(paste0(current_path, "loc2_comp_BUCB_squared.Rda"))
#load(paste0(current_path, "loc2_comp_BUCB_power5.Rda"))
load(paste0(current_path, "loc2_comp_KL.Rda"))
load(paste0(current_path, "loc2_comp_KL_tau_horizon.Rda"))
#load(paste0(current_path, "loc2_comp_KL_horizon1.Rda"))
load(paste0(current_path, "loc2_comp_KL_not_tau_horizon1000.Rda"))

alg_names <- rep(c("APT", "AugUCB", "UNIFORM", "PI", "TTS", "BUCB", "BUCB_horizon", "BUCB_squared", "KL_at_tau", "KL_not_at_tau"), each = 991)
index <- rep(10:1000, times = 10)
alg_res <- log(c(loc2_comp_APT, loc2_comp_AugUCB, loc2_comp_UNIFORM,
             loc2_comp_PI, loc2_comp_TTS, loc2_comp_BUCB, loc2_comp_BUCB_horizon,
             loc2_comp_BUCB_squared, loc2_comp_KL_tau_horizon,
             loc2_comp_KL_not_tau_horizon1000))
loc2_comp_res <- data.frame(index = index, names = alg_names, 
                            results = alg_res)
ggplot(loc2_comp_res, aes(x = index, y = alg_res)) + geom_line(aes(group = alg_names, color = alg_names)) +
  labs(title = "Experiment 2 Results", y = "log(Error)")
```

In terms of relative performance across algorithms, the results are very similar to experiment 1, in that most algorithms have a very similar performance. Also, again uniform sampling, the BUCB without the $\log(T)$ horizon denominator, and the KL without $\epsilon$ interval perform clearly worse. This is the only experiment where the algorithm PI (posterior probability of error based) comes in at first place at the end.

\newpage

## Experiment 3

This is the first of three experiments at a very small threshold and with accordingly small means for again 10 arms. As before, the arms are distributed symmetrically around the threshold. We let the algorithms run for more iterations than previously. The means, threshold, intervals are as follows:

```{r, echo = FALSE, fig.height = 3}
mean_loc <- c(0.001, 0.005, 0.01, 0.015,
               0.0475, 0.0525,
               0.085, 0.09, 0.095, 0.099)
tau_loc <- 0.05
epsilon_loc <- 0.005

plot(mean_loc, c(1,1,1,1,1,1,1,1,1,1), pch = 19, ylim = c(0.8,1.2), ylab = "", main = "Setup Experiment 3", xlab = "Mean Locations")
abline(v=tau_loc)
abline(v=tau_loc+epsilon_loc, lty=2)
abline(v=tau_loc-epsilon_loc, lty=2)

# Complexity:
print("Complexity as defined in Locatelli et al. (2016):")
round(sum((abs(mean_loc-tau_loc)+epsilon_loc)^(-2)))
```

The results are as follows:

```{r, echo = FALSE}

load(paste0(current_path, "loc3_comp_APT.Rda"))
load(paste0(current_path, "loc3_comp_UNIFORM.Rda"))
load(paste0(current_path, "loc3_comp_BUCB.Rda"))
load(paste0(current_path, "loc3_comp_BUCB_horizon.Rda"))
load(paste0(current_path, "loc3_comp_TTS.Rda"))
load(paste0(current_path, "loc3_comp_PI.Rda"))
load(paste0(current_path, "loc3_comp_AugUCB.Rda"))
load(paste0(current_path, "loc3_comp_KL_tau_horizon.Rda"))
load(paste0(current_path, "loc3_comp_KL_horizon.Rda"))

alg_names <- rep(c("APT", "AugUCB", "UNIFORM", "PI", "TTS", "BUCB", "BUCB_horizon", "KL_at_tau", "KL_not_at_tau"), each = 2491)
index <- rep(10:2500, times = 9)
alg_res <- log(c(loc3_comp_APT, loc3_comp_AugUCB, loc3_comp_UNIFORM,
             loc3_comp_PI, loc3_comp_TTS, loc3_comp_BUCB,
             loc3_comp_BUCB_horizon, loc3_comp_KL_tau_horizon,
             loc3_comp_KL_horizon))
loc3_comp_res <- data.frame(index = index, names = alg_names, 
                            results = alg_res)
ggplot(loc3_comp_res, aes(x = index, y = alg_res)) + geom_line(aes(group = alg_names, color = alg_names)) +
  labs(title = "Experiment 3 Results", y = "log(Error)")
```

The performance of the algorithms is now clearly different than in the first two experiments at the perfectly symmetric threshold at 0.5. Now, the uniform sampling strategy performs better or similarly to many of the algorithms. The algorithm based on the posterior probability of error (PI) performs worst, followed by the KL-based algorithm *without* epsilon interval. At 2500 iterations, the KL-based algorithm *with* epsilon interval is improving faster than the APT algorithm. Both of their rates are still worse than uniform sampling. Only the AugUCB algorithm eventually catches up on uniform sampling and is better after 2000 iterations. Only the BayesUCB algorithm *with* $log(T)$ horizon term in the denominator performs clearly better than everything else.

\newpage

## Experiment 4

We now consider an experiment with even smaller threshold, in which the majority of arms is below the threshold, and the arms are clearly asymmetric around the threshold. We have run the experiment for 2000 observations. Three of the arms are expected to have only one or two observations of value 1 in the entire sample.

```{r, echo = FALSE, fig.height = 3}
mean_loc <- c(0.0005, 0.001, 0.001, 0.005, 0.009,
               0.02, 0.0275, 0.0325, 0.04,
               0.08, 0.09)
tau_loc <- 0.03
epsilon_loc <- 0.005

plot(mean_loc, c(1,0.98,1.02,1,1,1,1,1,1,1,1), pch = 19, ylim = c(0.8,1.2), ylab = "", main = "Setup Experiment 4", xlab = "Mean Locations")
abline(v=tau_loc)
abline(v=tau_loc+epsilon_loc, lty=2)
abline(v=tau_loc-epsilon_loc, lty=2)

# Complexity:
print("Complexity as defined in Locatelli et al. (2016):")
round(sum((abs(mean_loc-tau_loc)+epsilon_loc)^(-2)))
```

The results are as follows:

```{r, echo = FALSE}
load(file = paste0(current_path, "loc4_comp_UNIFORM.Rda"))
load(file = paste0(current_path, "loc4_comp_APT.Rda"))
load(file = paste0(current_path, "loc4_comp_AugUCB.Rda"))
load(file = paste0(current_path, "loc4_comp_KL_tau_horizon.Rda"))
load(file = paste0(current_path, "loc4_comp_TTS.Rda"))
load(file = paste0(current_path, "loc4_comp_BUCB_sqrt.Rda"))
load(file = paste0(current_path, "loc4_comp_BUCB.Rda"))
load(file = paste0(current_path, "loc4_comp_BUCB_horizon.Rda"))
#load(file = paste0(current_path, "loc4_comp_BUCB_horizon5.Rda"))
load(file = paste0(current_path, "loc4_comp_BUCB_squared.Rda"))

alg_names <- rep(c("APT", "AugUCB", "UNIFORM", "TTS","BUCB_sqrt", "BUCB", "BUCB_horizon", "BUCB_squared", "KL_at_tau"), each = 1990)
index <- rep(11:2000, times = 9)
alg_res <- log(c(loc4_comp_APT, loc4_comp_AugUCB, loc4_comp_UNIFORM,
                 loc4_comp_TTS, loc4_comp_BUCB_sqrt, loc4_comp_BUCB,
                 loc4_comp_BUCB_horizon, loc4_comp_BUCB_squared,
                 loc4_comp_KL_tau_horizon))
loc4_comp_res <- data.frame(index = index, names = alg_names, 
                            results = alg_res)
ggplot(loc4_comp_res, aes(x = index, y = alg_res)) + geom_line(aes(group = alg_names, color = alg_names)) +
  labs(title = "Experiment 4 Results", y = "log(Error)")
```

Again, the KL-based algorithm cannot improve over uniform sampling. Both APT and AugUCB improve upon uniform sampling and perform equally well until iteration 2000. This time, the Thompson Sampling-like algorithm (TTS) performs clearly better than APT after half of the budget. Both previously considered Bayes-UCB algorithms perform clearly better than the competition. However even they still have a mean error of about 0.22 after 2000 samples. which is large compared to the other experiments. The new Bayes-UCB algorithm with a squared term $T_i^2$ in the denominator first performs very bad, but then improves very rapidly until iteration 2000. In contrast, the Bayes-UCB algorithm with a $\sqrt(T_i)$ term performs bad.

\newpage

## Experiment 5

In contrast to experiment 4, we now consider again an asymmetric problem, but shifted away from 0. We have the same amount of arms on both sides of the threshold, with 2 arms on each side that are symmetrically positioned around the threshold, but then two arms with very small means. The epsilon interval is now of size 0.02 in contrast to the previous 0.01. The setup is as follows:

```{r, echo = FALSE, fig.height = 3}
mean_loc <- c(0.0005, 0.001,
               0.05, 0.055,
               0.065, 0.075,
               0.085, 0.09,
               0.1, 0.1)
tau_loc <- 0.07
epsilon_loc <- 0.01

plot(mean_loc, c(0.98,1.02,1,1,1,1,1,1,1.02,0.98), pch = 19, ylim = c(0.8,1.2), ylab = "", main = "Setup Experiment 5", xlab = "Mean Locations")
abline(v=tau_loc)
abline(v=tau_loc+epsilon_loc, lty=2)
abline(v=tau_loc-epsilon_loc, lty=2)

# Complexity:
print("Complexity as defined in Locatelli et al. (2016):")
round(sum((abs(mean_loc-tau_loc)+epsilon_loc)^(-2)))
```

The results are as follows:

```{r, echo = FALSE}
load(paste0(current_path, "loc5_comp_APT.Rda"))
load(paste0(current_path, "loc5_comp_AugUCB.Rda"))
load(paste0(current_path, "loc5_comp_TTS.Rda"))
load(paste0(current_path, "loc5_comp_BUCB.Rda"))
load(paste0(current_path, "loc5_comp_BUCB_horizon.Rda"))
load(paste0(current_path, "loc5_comp_BUCB_squared.Rda"))
load(paste0(current_path, "loc5_comp_UNIFORM.Rda"))

alg_names <- c(rep(c("APT", "AugUCB", "UNIFORM", "TTS"), each = 2491), rep("BUCB", times = 1991), rep(c("BUCB_horizon", "BUCB_squared"), each = 2491))
index <- c(rep(10:2500, times = 4), 10:2000, rep(10:2500, times = 2))
alg_res <- log(c(loc5_comp_APT, loc5_comp_AugUCB, loc5_comp_UNIFORM,
                 loc5_comp_TTS, loc5_comp_BUCB,
                 loc5_comp_BUCB_horizon, loc5_comp_BUCB_squared))
loc5_comp_res <- data.frame(index = index, names = alg_names, 
                            results = alg_res)
ggplot(loc5_comp_res, aes(x = index, y = alg_res)) + geom_line(aes(group = alg_names, color = alg_names)) +
  labs(title = "Experiment 5 Results", y = "log(Error)")
```

This problem seems to be the hardest for the tested algorithms in terms of the error after 2000 and 2500 iterations respectively. This is very much in contrast to the complexity measure $H$ as defined in Locatelli et al. (2016). According to which experiments 3 and 4 are harder. However, the complexity measure does not take into consideration where in the means are located, only their position in relation to the threshold.

Again, BUCB_horizon comes in first. This time, BUCB_squared is performing very well as well, at least when compared to APT and AugUCB. AugUCB actually performs worse than APT until this point. And TTS manages to cross APT in performance after close to 2500 iterations. Due to the high error metric, it might be useful to run the algorithms for more iterations on this problem to observe long-term behavior. Especially with regard to their current rate of improvement.

### 2017-07-19 AugUCB/calibrate_algorithms_from_data2.R

@@ -41,6 +41,16 @@ loc2_APT[[5000]]
 loc2_comp_APT <- compare_to_ground_truth(mean_loc2, loc2_APT, tau_loc2, 
                                         epsilon_loc2)$mean
 save(loc2_comp_APT, file = paste0(current_path, "loc2_comp_APT.Rda"))
+
+########################################################################
+# Standard AugUCB
+system.time(loc2_AugUCB <- para_bandit_sim_AugUCB(data = data_list2, rounds = 1000, 
+                                                  tau = tau_loc2))
+save(loc2_AugUCB, file = paste0(current_path, "loc2_AugUCB.Rda"))
+loc2_comp_AugUCB <- compare_to_ground_truth(mean_loc2, loc2_AugUCB, tau_loc2, 
+                                            epsilon_loc2)$mean
+save(loc2_comp_AugUCB, file = paste0(current_path, "loc2_comp_AugUCB.Rda"))
+
 ########################################################################
 # Standard Uniform
 

### 2017-07-19 AugUCB/run_from_data.R

@@ -16,6 +16,119 @@ get_min <- function(x) {
 
 ##############################################################
 
+#mean_002 <- c(0.033, 0.033, 0.037, 0.037,
+#              0.031, 0.031, 0.039, 0.039,
+#              0.027, 0.027, 0.043, 0.043,
+#              0.02, 0.02, 0.05, 0.05,
+#              0.005, 0.005, 0.065, 0.065)
+#tau_002 <- 0.035
+#epsilon_002 <- 0.005#
+
+#set.seed(512)
+#testt <- data.frame(rep(NA, times = 500))
+#for(i in 1:length(mean_002)) {
+#  testt[[i]] <- as.numeric(purrr::rbernoulli(500, p  = mean_002[i]))
+#}
+#names(testt) <- paste0("V", 1:20)
+
+#aug_test <- AugUCB_from_tsdata(testt, rounds = 500, tau = tau_002, 
+#                               verbose = TRUE, seed = 46)
+
+# AugUCB Algorithm
+
+AugUCB_from_tsdata <- function(data, rounds = 5000, rho = 1/3, tau = NA,
+                               verbose = FALSE, seed = NA) {
+  if(!is.na(seed)) set.seed(seed)
+  K <- dim(data)[2]
+  
+  # initialize by pulling each arm once
+  arm_list <- diag(as.matrix(data[1:K,]))
+  arm_list <- as.list(arm_list)
+  
+  # initialize mean storage, arm sequence, and the counter
+  mean_storage <- matrix(unlist(lapply(arm_list, mean)), nrow = 1)
+  arm_sequence <- 1:K
+  
+  # Initialize the remaining parameters as in the paper
+  B <- 1:K # the active set of arms
+  m <- 0
+  epsilon <- 1
+  e <- exp(1) # ????????
+  M <- floor(0.5*log2(rounds/e))
+  psi <- rounds*epsilon/(128 * (log(3/16 * K * log(K)))^2)
+  l <- ceiling(2*psi*log(rounds * epsilon)/epsilon)
+  N <- K * l
+  
+  if(verbose) counter <- K
+  
+  for(i in (K+1):rounds) {
+    if(verbose) message(paste("this is round", i))
+    next_arm <- get_min(unlist(get_next_arm_augucb(arm_list, tau = tau, rho = rho,
+                                                   psi = psi, rounds = rounds, 
+                                                   epsilon = epsilon,
+                                                   active_set = B)))
[…]

### 2017-07-19 AugUCB/run_parallelized_from_data.R

@@ -40,9 +40,9 @@ compare_to_ground_truth <- function(true_means, sim_res, tau, epsilon) {
   true_classification_down <- which(true_means < tau-epsilon)
   
   get_iter_error <- function(x, true_class_up, true_class_down) {
-    ifelse(true_class_up %in% which(x > tau) && 
-             true_class_down %in% which(x < tau),
-           0,1)
+    ifelse(sum(true_class_up %in% which(x >= tau)) == length(true_class_up) &
+             sum(true_class_down %in% which(x < tau)) == length(true_class_down),
+           0, 1)
   }
   
   get_error <- function(res_df, ...) {
@@ -57,6 +57,39 @@ compare_to_ground_truth <- function(true_means, sim_res, tau, epsilon) {
   
   return(list(mean = comp_mean, full = comp_list))
 }
+
+#############################################################################
+
+# Get the average performance over all simulations
+
+# expect a list of matrices of size rounds x K as input from the simulations,
+# as well as a vector with the true means of length K to compare agains
+compare_to_cv_data <- function(mean_list, sim_res, thresh, eps) {
+  
+  get_iter_error <- function(x, true_class_up, true_class_down) {
+    ifelse(sum(true_class_up %in% which(x >= thresh)) == length(true_class_up) &&
+             sum(true_class_down %in% which(x < thresh)) == length(true_class_down),
+           0,1)
+  }
+  
+  iter_error_vectors <- list()
+  
+  for(i in 1:length(sim_res)) {
+    true_classification_up <- which(mean_list[[i]] > thresh+eps)
+    true_classification_down <- which(mean_list[[i]] < thresh-eps)
+    
+    iter_error_vectors[[i]] <- apply(sim_res[[i]]$mean_storage, 1, get_iter_error,
+                                     true_class_up = true_classification_up,
+                                     true_class_down = true_classification_down)
+  }
+  
+  comp_mean <- rowMeans(as.data.frame(iter_error_vectors, 
+                                      col.names = 1:length(iter_error_vectors)))
+  
+  return(list(mean = comp_mean, full = iter_error_vectors))
+}
+
+#################################################################################
 
 #################################################################################
 # input has to be a list of different data frames
[…]

### 2017-07-19 run_from_amo_data/experiments1.R

@@ -1,0 +1,59 @@
+sessions_threshold <- 0
+set.seed(512)
+selected_products <- sample(1:196, 15)
+niter <- 5000
+nrounds <- 1440 # Analyzing a data set of a day length
+nahead <- 10080 # Computing CR a week ahead
+source("/Users/timradtke/Desktop/thesis_data/get_dataset.R")
+
+dim(pv_list[[1]])
+pv_list[[1]]
+
+pv_list[[1]]
+pv_list[[5000]]
+round(pv_next_means[[5000]],4)
+round(pv_next_means[[1]],4)
+
+#res <- matrix(ncol = 10, nrow = 5000)
+#for(i in 1:5000) {
+#  res[i,] <- round(pv_next_means[[i]] - pv_own_means[[i]], 4)
+#}
+#res
+
+####################################################################
+
+source("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/run_from_data.R")
+source("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/run_parallelized_from_data.R")
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/run_from_amo_data"
+
+####################################################################
+
+tau_amo1 <- 0.05
+epsilon_amo1 <- 0.01
+data_amo1 <- pv_list
+rm(pv_list)
+gc()
+
+########################################################################
+# Standard APT Algorithm
+system.time(amo1_APT <- para_bandit_sim_APT(data = data_amo1, rounds = 1440, 
+                                            tau = tau_amo1, epsilon = epsilon_amo1))
+save(amo1_APT, file = paste0(current_path, "amo1_APT.Rda"))
+amo1_comp_APT <- compare_to_cv_data(pv_next_means, amo1_APT, tau_amo1, epsilon_amo1)$mean
+save(amo1_comp_APT, file = paste0(current_path, "amo1_comp_APT.Rda"))
+rm(amo1_APT)
+gc()
+
+########################################################################
+
+plot(c(0,1440), c(0, -4), type = "n")
+lines(log(amo1_comp_APT), col = "red")
+lines(log(loc2_comp_UNIFORM), col = "black")
+lines(log(loc2_comp_PI), col = "darkgreen")
+lines(log(loc2_comp_TTS), col = "lightgreen")
[…]

### 2017-07-19 synthetic_experiments/cal_algs_long2.R

@@ -1,0 +1,274 @@
+# run a simulation based on a simple example that can hopefully serve to
+# calibrate the algorithms
+########################################################################
+# load functions
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
+
+########################################################################
+# Create the data
+
+mean_loc2 <- c(0.4-0.2^(1:4),
+              0.45, 0.55,
+              0.6+0.2^(5-(1:4)))
+tau_loc2 <- 0.5
+epsilon_loc2 <- 0.1
+H_loc2 <- get_complexity(mean_loc2, tau_loc2, epsilon_loc2)
+
+plot(mean_loc2, rep(1,10), main = paste0("Complexity of ", round(H_loc2,2)))
+abline(v=tau_loc2)
+abline(v=tau_loc2+epsilon_loc2, lty=2)
+abline(v=tau_loc2-epsilon_loc2, lty=2)
+
+data_list2 <- list()
+set.seed(1024)
+for(j in 1:5000) {
+  curr_data <- data.frame(rep(NA, times = 1000))
+  for(i in 1:length(mean_loc2)) {
+    curr_data[[i]] <- as.numeric(purrr::rbernoulli(1000, p  = mean_loc2[i]))
+  }
+  names(curr_data) <- paste0("V", rep(1:length(mean_loc2)))
+  data_list2[[j]] <- curr_data
+}
+
+########################################################################
+# KL-UCB Algorithm
+system.time(loc2_KLUCB60 <- para_bandit_sim_KLUCB(data = data_list2[1:100], 
+                                                  rounds = 1000, 
+                                                  tau = tau_loc2, 
+                                                  epsilon = epsilon_loc2,
+                                                  horizon = 6000,
+                                                  H = H_loc2))
+# user  system elapsed 
+#1.019   1.369 553.760
+save(loc2_KLUCB60, file = paste0(current_path, "loc2_KLUCB60.Rda"))
+#load(file = paste0(current_path, "loc4_KLUCB40.Rda"))
+loc2_comp_KLUCB60 <- compare_to_ground_truth(mean_loc2, loc2_KLUCB60, tau_loc2, 
+                                             epsilon_loc2)$mean
[…]

### 2017-07-19 synthetic_experiments/cal_algs_long_3.R

@@ -6,6 +6,7 @@
 current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
 source(paste0(current_path, "run_from_data.R"))
 source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
 
 ########################################################################
 # Create the data
@@ -24,9 +25,9 @@ abline(v=tau_loc3-epsilon_loc3, lty=2)
 data_list3 <- list()
 set.seed(1024)
 for(j in 1:5000) {
-  curr_data <- data.frame(rep(NA, times = 1000))
+  curr_data <- data.frame(rep(NA, times = 2500))
   for(i in 1:length(mean_loc3)) {
-    curr_data[[i]] <- as.numeric(purrr::rbernoulli(1000, p  = mean_loc3[i]))
+    curr_data[[i]] <- as.numeric(purrr::rbernoulli(2500, p  = mean_loc3[i]))
   }
   names(curr_data) <- paste0("V", rep(1:length(mean_loc3)))
   data_list3[[j]] <- curr_data
@@ -35,20 +36,105 @@ for(j in 1:5000) {
 ########################################################################
 # Standard APT Algorithm
 # a seed is built in
-system.time(loc3_APT <- para_bandit_sim_APT(data = data_list3, rounds = 1000, 
-                                            tau = tau_loc3, epsilon = epsilon_loc3))
+system.time(loc3_APT <- para_bandit_sim_APT(data = data_list3, rounds = 2500, 
+                                            tau = tau_loc3, 
+                                            epsilon = epsilon_loc3))
 # user  system elapsed 
-#6.508   3.544 300.383
+#12.497    9.065 1227.363
 save(loc3_APT, file = paste0(current_path, "loc3_APT.Rda"))
-load(file = paste0(current_path, "loc3_APT.Rda"))
+#load(file = paste0(current_path, "loc3_APT.Rda"))
 loc3_comp_APT <- compare_to_ground_truth(mean_loc3, loc3_APT, tau_loc3, 
                                          epsilon_loc3)$mean
 save(loc3_comp_APT, file = paste0(current_path, "loc3_comp_APT.Rda"))
 rm(loc3_APT)
 gc()
+
+########################################################################
+
+loc3_BUCB <- para_bandit_sim_bucb(data = data_list3, rounds = 2500, 
[…]

### 2017-07-19 synthetic_experiments/cal_algs_long_4.R

@@ -6,6 +6,7 @@
 current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
 source(paste0(current_path, "run_from_data.R"))
 source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
 
 ########################################################################
 # Create the data
@@ -16,6 +17,7 @@ mean_loc4 <- c(0.0005, 0.001, 0.001, 0.005, 0.009,
                0.08, 0.09)
 tau_loc4 <- 0.03
 epsilon_loc4 <- 0.005
+
 plot(mean_loc4, rep(1,11))
 abline(v=tau_loc4)
 abline(v=tau_loc4+epsilon_loc4, lty=2)
@@ -33,6 +35,19 @@ for(j in 1:5000) {
 }
 
 ########################################################################
+# Standard Uniform
+system.time(loc4_UNIFORM <- para_bandit_sim_uniform(data = data_list4, 
+                                                    rounds = 2000))
+# user  system elapsed 
+# 6.268   3.400 211.002 
+save(loc4_UNIFORM, file = paste0(current_path, "loc4_UNIFORM.Rda"))
+load(file = paste0(current_path, "loc4_UNIFORM.Rda"))
+loc4_comp_UNIFORM <- compare_to_ground_truth(mean_loc4, loc4_UNIFORM, tau_loc4, 
+                                             epsilon_loc4)$mean
+save(loc4_comp_UNIFORM, file = paste0(current_path, "loc4_comp_UNIFORM.Rda"))
+rm(loc4_UNIFORM)
+gc()
+########################################################################
 # Standard APT Algorithm
 # a seed is built in
 system.time(loc4_APT <- para_bandit_sim_APT(data = data_list4, rounds = 2000, 
@@ -44,28 +59,138 @@ load(file = paste0(current_path, "loc4_APT.Rda"))
 loc4_comp_APT <- compare_to_ground_truth(mean_loc4, loc4_APT, tau_loc4, 
                                          epsilon_loc4)$mean
 save(loc4_comp_APT, file = paste0(current_path, "loc4_comp_APT.Rda"))
+load(file = paste0(current_path, "loc4_comp_APT.Rda"))
 rm(loc4_APT)
 gc()
+
+########################################################################
+
[…]

### 2017-07-19 synthetic_experiments/cal_algs_long_5.R

@@ -6,11 +6,11 @@
 current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
 source(paste0(current_path, "run_from_data.R"))
 source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
 
 ########################################################################
 # Create the data
 
-# do 2000 rounds
 mean_loc5 <- c(0.0005, 0.001,
                0.05, 0.055,
                0.065, 0.075,
@@ -27,29 +27,18 @@ abline(v=tau_loc5-epsilon_loc5, lty=2)
 data_list5 <- list()
 set.seed(256)
 for(j in 1:5000) {
-  curr_data <- data.frame(rep(NA, times = 1000))
+  curr_data <- data.frame(rep(NA, times = 2500))
   for(i in 1:length(mean_loc5)) {
-    curr_data[[i]] <- as.numeric(purrr::rbernoulli(1000, p  = mean_loc5[i]))
+    curr_data[[i]] <- as.numeric(purrr::rbernoulli(2500, p  = mean_loc5[i]))
   }
   names(curr_data) <- paste0("V", rep(1:length(mean_loc5)))
   data_list5[[j]] <- curr_data
 }
 
-data_list5_long <- list()
-set.seed(256)
-for(j in 1:5000) {
-  curr_data <- data.frame(rep(NA, times = 2000))
-  for(i in 1:length(mean_loc5)) {
-    curr_data[[i]] <- as.numeric(purrr::rbernoulli(2000, p  = mean_loc5[i]))
-  }
-  names(curr_data) <- paste0("V", rep(1:length(mean_loc5)))
-  data_list5_long[[j]] <- curr_data
-}
-
 ########################################################################
 # Standard APT Algorithm
 # a seed is built in
-system.time(loc5_APT <- para_bandit_sim_APT(data = data_list5, rounds = 2000, 
+system.time(loc5_APT <- para_bandit_sim_APT(data = data_list5, rounds = 2500, 
                                             tau = tau_loc5, epsilon = epsilon_loc5))
 # user  system elapsed 
 #6.508   3.544 300.383
@@ -58,26 +47,69 @@ load(file = paste0(current_path, "loc5_APT.Rda"))
[…]

### 2017-07-19 synthetic_experiments/cal_algs_verylong_2.R

@@ -1,0 +1,191 @@
+# run a simulation based on a simple example that can hopefully serve to
+# calibrate the algorithms
+########################################################################
+# load functions
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
+
+########################################################################
+# Create the data
+
+mean_loc2 <- c(0.4-0.2^(1:4),
+               0.45, 0.55,
+               0.6+0.2^(5-(1:4)))
+tau_loc2 <- 0.5
+epsilon_loc2 <- 0.1
+H_loc2 <- get_complexity(mean_loc2, tau_loc2, epsilon_loc2)
+
+plot(mean_loc2, rep(1,10), main = paste0("Complexity of ", round(H_loc2,2)))
+abline(v=tau_loc2)
+abline(v=tau_loc2+epsilon_loc2, lty=2)
+abline(v=tau_loc2-epsilon_loc2, lty=2)
+
+data_list2 <- list()
+set.seed(1024)
+for(j in 1:5000) {
+  curr_data <- data.frame(rep(NA, times = 4000))
+  for(i in 1:length(mean_loc2)) {
+    curr_data[[i]] <- as.numeric(purrr::rbernoulli(4000, p  = mean_loc2[i]))
+  }
+  names(curr_data) <- paste0("V", rep(1:length(mean_loc2)))
+  data_list2[[j]] <- curr_data
+}
+
+########################################################################
+# Plot the results
+
+load(paste0(current_path, "/loc2_comp_BUCB_horizon_4000.Rda"))
+load(paste0(current_path, "/loc2_comp_APT_2000.Rda"))
+load(paste0(current_path, "/loc2_comp_AugUCB_2000.Rda"))
+
+plot(c(0,2000), c(0, -9), type = "n")
+lines(log(loc2_comp_BUCB_horizon_4000), col = "blue")
+lines(log(loc2_comp_APT_2000), col = "red")
+lines(log(loc2_comp_AugUCB_2000), col = "grey")
+#lines(log(loc2_comp_KLUCB100), col = "green")
+#lines(log(loc2_comp_KLUCB80), col = "green")
[…]

### 2017-07-19 synthetic_experiments/cal_algs_verylong_3.R

@@ -1,0 +1,157 @@
+# run a simulation based on a simple example that can hopefully serve to
+# calibrate the algorithms
+########################################################################
+# load functions
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
+
+########################################################################
+# Create the data
+
+mean_loc3 <- c(0.001, 0.005, 0.01, 0.015,
+               0.0475, 0.0525,
+               0.085, 0.09, 0.095, 0.099)
+tau_loc3 <- 0.05
+epsilon_loc3 <- 0.005
+H_loc3 <- get_complexity(mean_loc3, tau_loc3, epsilon_loc3)
+
+plot(mean_loc3, rep(1,10), main = paste0("Complexity of ", round(H_loc3,2)))
+abline(v=tau_loc3)
+abline(v=tau_loc3+epsilon_loc3, lty=2)
+abline(v=tau_loc3-epsilon_loc3, lty=2)
+
+data_list3 <- list()
+set.seed(1024)
+for(j in 1:5000) {
+  curr_data <- data.frame(rep(NA, times = 7000))
+  for(i in 1:length(mean_loc3)) {
+    curr_data[[i]] <- as.numeric(purrr::rbernoulli(7000, p  = mean_loc3[i]))
+  }
+  names(curr_data) <- paste0("V", rep(1:length(mean_loc3)))
+  data_list3[[j]] <- curr_data
+}
+
+########################################################################
+# Plot the results
+
+load(paste0(current_path, "/loc3_comp_BUCB_horizon_7000.Rda"))
+load(paste0(current_path, "/loc3_comp_BUCB_horizon.Rda"))
+load(paste0(current_path, "/loc3_comp_APT.Rda"))
+load(paste0(current_path, "/loc3_comp_APT_7000.Rda"))
+load(paste0(current_path, "/loc3_comp_AugUCB.Rda"))
+load(paste0(current_path, "/loc3_comp_AugUCB_7000.Rda"))
+
+plot(c(0,7000), c(0, -9), type = "n")
[…]

### 2017-07-19 synthetic_experiments/cal_algs_verylong_5.R

@@ -6,11 +6,11 @@
 current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
 source(paste0(current_path, "run_from_data.R"))
 source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
 
 ########################################################################
 # Create the data
 
-# do 2000 rounds
 mean_loc5 <- c(0.0005, 0.001,
                0.05, 0.055,
                0.065, 0.075,
@@ -18,8 +18,9 @@ mean_loc5 <- c(0.0005, 0.001,
                0.1, 0.1)
 tau_loc5 <- 0.07
 epsilon_loc5 <- 0.01
+H_loc5 <- get_complexity(mean_loc5, tau_loc5, epsilon_loc5)
 
-plot(mean_loc5, rep(1,10))
+plot(mean_loc5, rep(1,10), main = paste0("Complexity: ", round(H_loc5)))
 abline(v=tau_loc5)
 abline(v=tau_loc5+epsilon_loc5, lty=2)
 abline(v=tau_loc5-epsilon_loc5, lty=2)
@@ -27,77 +28,270 @@ abline(v=tau_loc5-epsilon_loc5, lty=2)
 data_list5 <- list()
 set.seed(256)
 for(j in 1:5000) {
-  curr_data <- data.frame(rep(NA, times = 1000))
+  curr_data <- data.frame(rep(NA, times = 6000))
   for(i in 1:length(mean_loc5)) {
-    curr_data[[i]] <- as.numeric(purrr::rbernoulli(1000, p  = mean_loc5[i]))
+    curr_data[[i]] <- as.numeric(purrr::rbernoulli(6000, p  = mean_loc5[i]))
   }
   names(curr_data) <- paste0("V", rep(1:length(mean_loc5)))
   data_list5[[j]] <- curr_data
 }
 
-data_list5_long <- list()
+data_list5_8000 <- list()
 set.seed(256)
 for(j in 1:5000) {
-  curr_data <- data.frame(rep(NA, times = 2000))
+  curr_data <- data.frame(rep(NA, times = 8000))
   for(i in 1:length(mean_loc5)) {
-    curr_data[[i]] <- as.numeric(purrr::rbernoulli(2000, p  = mean_loc5[i]))
[…]

### 2017-07-19 synthetic_experiments/quantile_visualization.R

@@ -1,0 +1,20 @@
+# After four rounds, only 0 observations, alpha = 0.04 and beta = 0.96
+
+alpha_prime <- 0.04
+beta_prime <- 0.96+4
+(mean_post <- alpha_prime/(alpha_prime+beta_prime))
+mean <- 0
+# tau = 0.05
+Ti <- 4
+N <- 2500
+log(N)
+
+plot(seq(0,1,by = 0.001),dbeta(seq(0,1,by = 0.001), alpha_prime, beta_prime), type = "l")
+plot(seq(0,1,by = 0.001),pbeta(seq(0,1,by = 0.001), alpha_prime, beta_prime), type = "l")
+round(qbeta(1 - 1/Ti, alpha_prime, beta_prime),5)
+round(qbeta(1 - 1/sqrt(Ti), alpha_prime, beta_prime),5)
+round(qbeta(1 - 1/(Ti)^2, alpha_prime, beta_prime),5)
+round(qbeta(1 - 1/(Ti)^5, alpha_prime, beta_prime),5)
+round(qbeta(1 - 1/((Ti)*log(N)), alpha_prime, beta_prime),5)
+round(qbeta(1 - 1/((Ti)*log(N)^5), alpha_prime, beta_prime),5)
+round(qbeta(1 - 1/((Ti)*N), alpha_prime, beta_prime),5)

### 2017-07-20 synthetic_experiments/long_experiments_summary.Rmd
write summary of long experiments

---
output: html_document
urlcolor: blue
fontsize: 12pt
---

## Comparison of Suggested Algorithms Based on Synthetic Data

In the following, we present results regarding the performance of difference algorithms. All experiments are based on the average error of algorithms over 5000 simulations. All experiments are with Bernoulli distributions as arms as in Locatelli et al. (2016).

In general, we compare the following algorithms:

- Uniform Sampling (UNIFORM)
- Anytime Parameter-free Thresholding algorithm (APT), [Locatelli et al., 2016](http://proceedings.mlr.press/v48/locatelli16.html)
- Augmented UCB (AugUCB), [Mukherjee et al., 2017](https://arxiv.org/pdf/1704.02281)
- Kullback-Leibler Divergence-based Algorithm (KL)
- Posterior Probability of Error-based Algorithm (PI)
- Thompson Sampling-like Algorithm (TTS)
- Bayes UCB Algorithm adapted for Thresholding Bandits (BUCB), compare *[On Bayesian Upper Confidence Bounds for Bandit Problems](http://proceedings.mlr.press/v22/kaufmann12.html)* by Kaufmann et al., 2012

```{r, echo = FALSE}
current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
source(paste0(current_path, "run_from_data.R"))
source(paste0(current_path, "run_parallelized_from_data.R"))
current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
library(ggplot2)
```

## Experiment 1

The same as experiment 1 in Locatelli et al. (2016). We have the following means and thresholds:

```{r, echo = FALSE, fig.height = 3}
mean_loc1 <- c(0.1, 0.1, 0.1, 
              0.35, 0.45, 0.55, 0.65,
              0.9, 0.9, 0.9)
tau_loc1 <- 0.5
epsilon_loc1 <- 0.1
H_loc1 <- get_complexity(mean_loc1, tau_loc1, epsilon_loc1)

plot(mean_loc1, c(0.9,1,1.1,1,1,1,1,1.1,1,0.9), pch = 19, ylim = c(0.8,1.2), ylab = "", main = paste0("Setup Experiment 1 - Complexity of ", round(H_loc1)), xlab = "Mean Locations")
abline(v=tau_loc1)
abline(v=tau_loc1+epsilon_loc1, lty=2)
abline(v=tau_loc1-epsilon_loc1, lty=2)
```

The experiment results are as follows:

```{r, echo = FALSE}
load(paste0(current_path, "loc_comp_APT.Rda"))
load(paste0(current_path, "loc_comp_AugUCB.Rda"))
load(paste0(current_path, "loc_comp_UNIFORM.Rda"))
load(paste0(current_path, "loc_comp_PI.Rda"))
load(paste0(current_path, "loc_comp_TTS.Rda"))
load(paste0(current_path, "loc_comp_BUCB.Rda"))
load(paste0(current_path, "loc_comp_BUCB_horizon.Rda"))
load(paste0(current_path, "loc_comp_BUCB_squared.Rda"))
load(paste0(current_path, "loc_comp_BUCB_power5.Rda"))
load(paste0(current_path, "loc_comp_KL.Rda"))
load(paste0(current_path, "loc_comp_KL_tau_horizon.Rda"))
load(paste0(current_path, "loc_comp_KL_horizon1.Rda"))
load(paste0(current_path, "loc_comp_KL_not_tau_horizon1000.Rda"))

alg_names <- rep(c("APT", "AugUCB", "UNIFORM", "PI", "TTS", "BUCB", "BUCB_horizon", "BUCB_squared", "KL_at_tau", "KL_not_at_tau"), each = 991)
index <- rep(10:1000, times = 10)
alg_res <- log(c(loc_comp_APT, loc_comp_AugUCB, loc_comp_UNIFORM,
             loc_comp_PI, loc_comp_TTS, loc_comp_BUCB, loc_comp_BUCB_horizon,
             loc_comp_BUCB_squared, loc_comp_KL_tau_horizon,
             loc_comp_KL_not_tau_horizon1000))
loc1_comp_res <- data.frame(index = index, names = alg_names, 
                            results = alg_res)
ggplot(loc1_comp_res, aes(x = index, y = alg_res)) + geom_line(aes(group = alg_names, color = alg_names)) +
  labs(title = "Experiment 1 Results", y = "log(Error)")
```

We clearly observe that most algorithms are able to solve this problem at more or less the same performance. Also, most algorithms are clearly superior to uniform sampling. The proposed new algorithms cannot perform better than APT. The BayesUCB algorithm without a $\log (T)$ horizon term in the denominator performs worse. Same for the KL-based algorithm that does not take the $\epsilon$ interval into account.

\newpage

## Experiment 2

The same as experiment 3 in Locatelli et al. (2016). We have the following means, threshold (solid line), and epsilon interval (dashed line):

```{r, echo = FALSE, fig.height = 3}
mean_loc2 <- c(0.4-0.2^(1:4),
               0.45, 0.55,
               0.6+0.2^(5-(1:4)))
tau_loc2 <- 0.5
epsilon_loc2 <- 0.1
H_loc2 <- get_complexity(mean_loc2, tau_loc2, epsilon_loc2)

plot(mean_loc2, c(1,1,0.98,1.02,1,1,1.02,0.98,1,1), pch = 19, ylim = c(0.8,1.2), ylab = "", xlab = "Mean Locations", main = paste0("Setup Experiment 2 - Complexity of ", round(H_loc2)))
abline(v=tau_loc2)
abline(v=tau_loc2+epsilon_loc2, lty=2)
abline(v=tau_loc2-epsilon_loc2, lty=2)
```

The experiment results are as follows:

```{r, echo = FALSE}
library(ggplot2)

load(paste0(current_path, "/loc2_comp_BUCB_horizon_4000.Rda"))
load(paste0(current_path, "/loc2_comp_APT_2000.Rda"))
load(paste0(current_path, "/loc2_comp_AugUCB_2000.Rda"))
load(paste0(current_path, "/loc2_comp_KLUCB80_long.Rda"))
load(paste0(current_path, "/loc2_comp_UNIFORM_2000.Rda"))

alg_names <- c(rep(c("Uniform", "APT", "AugUCB", "B-UCB"), each = 1991), rep("KL-UCB", 1491))
index <- c(rep(10:2000, times = 4), 10:1500)
alg_res <- log(c(loc2_comp_UNIFORM_2000, loc2_comp_APT_2000, loc2_comp_AugUCB_2000, loc2_comp_BUCB_horizon_4000[1:1991], loc2_comp_KLUCB80_long))
loc2_comp_res <- data.frame(Round = index, Algorithm = alg_names, 
                            results = alg_res)
ggplot(loc2_comp_res, aes(x = Round, y = alg_res)) + geom_line(aes(group = Algorithm, color = Algorithm)) + geom_hline(aes(yintercept = log(0.01)), linetype = 2) +
  labs(title = "Experiment 2 Results", y = "log(Error)", subtitle = "Horizontal Bar at 0.05 Average Error")
```

\newpage

## Experiment 3

This is the first of three experiments at a very small threshold and with accordingly small means for again 10 arms. As before, the arms are distributed symmetrically around the threshold. We let the algorithms run for more iterations than previously. The means, threshold, intervals are as follows:

```{r, echo = FALSE, fig.height = 3}
mean_loc3 <- c(0.001, 0.005, 0.01, 0.015,
               0.0475, 0.0525,
               0.085, 0.09, 0.095, 0.099)
tau_loc3 <- 0.05
epsilon_loc3 <- 0.005
H_loc3 <- get_complexity(mean_loc3, tau_loc3, epsilon_loc3)

plot(mean_loc3, c(1,1,1,1,1,1,1,1,1,1), pch = 19, ylim = c(0.8,1.2), ylab = "", xlab = "Mean Locations", main = paste0("Setup Experiment 3 - Complexity of ", round(H_loc3)))
abline(v=tau_loc3)
abline(v=tau_loc3+epsilon_loc3, lty=2)
abline(v=tau_loc3-epsilon_loc3, lty=2)
```

The results are as follows:

```{r, echo = FALSE}
load(paste0(current_path, "/loc3_comp_BUCB_horizon_7000.Rda"))
load(paste0(current_path, "/loc3_comp_AugUCB_7000.Rda"))
load(paste0(current_path, "/loc3_comp_KLUCB370_5000.Rda"))
load(paste0(current_path, "/loc3_comp_UNIFORM_7000.Rda"))
load(paste0(current_path, "/loc3_comp_APT_7000.Rda"))

alg_names <- c(rep(c("Uniform", "APT", "AugUCB", "B-UCB"), each = 6991), rep("KL-UCB", 4991))
index <- c(rep(10:7000, times = 4), 10:5000)
alg_res <- log(c(loc3_comp_UNIFORM_7000, loc3_comp_APT_7000, loc3_comp_AugUCB_7000, loc3_comp_BUCB_horizon_7000, loc3_comp_KLUCB370_5000))
loc3_comp_res <- data.frame(index = index, names = alg_names, 
                            results = alg_res)
ggplot(loc3_comp_res, aes(x = index, y = alg_res)) + geom_line(aes(group = alg_names, color = alg_names)) + geom_hline(aes(yintercept = log(0.01)), linetype = 2) +
  labs(title = "Experiment 3 Results", subtitle = paste0("Complexity of ", round(H_loc3)), y = "log(Error)")
```

\newpage

## Experiment 4

We now consider an experiment with even smaller threshold, in which the majority of arms is below the threshold, and the arms are clearly asymmetric around the threshold. We have run the experiment for 2000 observations. Three of the arms are expected to have only one or two observations of value 1 in the entire sample.

```{r, echo = FALSE, fig.height = 3}
mean_loc4 <- c(0.0005, 0.001, 0.001, 0.005, 0.009,
               0.02, 0.0275, 0.0325, 0.04,
               0.08, 0.09)
tau_loc4 <- 0.03
epsilon_loc4 <- 0.005
H_loc4 <- get_complexity(mean_loc4, tau_loc4, epsilon_loc4)

plot(mean_loc4, c(1,0.98,1.02,1,1,1,1,1,1,1,1), pch = 19, ylim = c(0.8,1.2), ylab = "", xlab = "Mean Locations", main = paste0("Setup Experiment 4 - Complexity of ", round(H_loc4)))
abline(v=tau_loc4)
abline(v=tau_loc4+epsilon_loc4, lty=2)
abline(v=tau_loc4-epsilon_loc4, lty=2)
```

The results are as follows:

```{r, echo = FALSE}
load(paste0(current_path, "loc4_comp_BUCB_horizon_8000.Rda"))
load(paste0(current_path, "loc4_comp_AugUCB_8000.Rda"))
load(paste0(current_path, "loc4_comp_APT_8000.Rda"))
load(paste0(current_path, "loc4_comp_KLUCB90_long.Rda"))
load(paste0(current_path, "loc4_comp_UNIFORM_8000.Rda"))

alg_names <- rep(c("Uniform", "APT", "AugUCB", "B-UCB", "KL-UCB"), each = 7990)
index <- rep(11:8000, times = 5)
alg_res <- log(c(loc4_comp_UNIFORM_8000, loc4_comp_APT_8000, loc4_comp_AugUCB_8000, loc4_comp_BUCB_horizon_8000, loc4_comp_KLUCB90_long))
loc4_comp_res <- data.frame(Round = index, Algorithm = alg_names, 
                            results = alg_res)
ggplot(loc4_comp_res, aes(x = Round, y = alg_res)) + geom_line(aes(group = Algorithm, color = Algorithm)) + geom_hline(aes(yintercept = log(0.01)), linetype = 2) +
  labs(title = "Experiment 4 Results", subtitle = paste0("Complexity of ", round(H_loc4)), y = "log(Error)")
```

\newpage

## Experiment 5

In contrast to experiment 4, we now consider again an asymmetric problem, but shifted away from 0. We have the same amount of arms on both sides of the threshold, with 2 arms on each side that are symmetrically positioned around the threshold, but then two arms with very small means. The epsilon interval is now of size 0.02 in contrast to the previous 0.01. The setup is as follows:

```{r, echo = FALSE, fig.height = 3}
mean_loc5 <- c(0.0005, 0.001,
               0.05, 0.055,
               0.065, 0.075,
               0.085, 0.09,
               0.1, 0.1)
tau_loc5 <- 0.07
epsilon_loc5 <- 0.01
H_loc5 <- get_complexity(mean_loc5, tau_loc5, epsilon_loc5)

plot(mean_loc5, c(0.98,1.02,1,1,1,1,1,1,1.02,0.98), pch = 19, ylim = c(0.8,1.2), ylab = "", xlab = "Mean Locations", main = paste0("Setup Experiment 5 - Complexity of ", round(H_loc5)))
abline(v=tau_loc5)
abline(v=tau_loc5+epsilon_loc5, lty=2)
abline(v=tau_loc5-epsilon_loc5, lty=2)
```

The results are as follows:

```{r, echo = FALSE}
load(paste0(current_path, "loc5_comp_KLUCB72_long.Rda"))
load(paste0(current_path, "loc5_comp_BUCB_horizon_long_8000.Rda"))
load(paste0(current_path, "loc5_comp_AugUCB_8000.Rda"))
load(paste0(current_path, "loc5_comp_APT_8000.Rda"))
load(paste0(current_path, "loc5_comp_UNIFORM_8000.Rda"))

alg_names <- c(rep(c("Uniform", "APT", "AugUCB", "B-UCB", "KL-UCB"), each = 7991))
index <- c(rep(10:8000, times = 5))
alg_res <- log(c(loc5_comp_UNIFORM_8000, loc5_comp_APT_8000, loc5_comp_AugUCB_8000, loc5_comp_BUCB_horizon_long_8000, loc5_comp_KLUCB72_long))
loc5_comp_res <- data.frame(Index = index, Algorithm = alg_names, 
                            results = alg_res)
ggplot(loc5_comp_res, aes(x = Index, y = alg_res)) + geom_line(aes(group = Algorithm, color = Algorithm)) + geom_hline(aes(yintercept = log(0.01)), linetype = 2) +
  labs(title = "Experiment 5 Results", subtitle = paste0("Complexity of ", round(H_loc5)), y = "log(Error)")
```

### 2017-07-20 synthetic_experiments/cal_algs_verylong_2.R

@@ -40,6 +40,8 @@ for(j in 1:5000) {
 load(paste0(current_path, "/loc2_comp_BUCB_horizon_4000.Rda"))
 load(paste0(current_path, "/loc2_comp_APT_2000.Rda"))
 load(paste0(current_path, "/loc2_comp_AugUCB_2000.Rda"))
+load(paste0(current_path, "/loc2_comp_KLUCB80_long.Rda"))
+load(paste0(current_path, "/loc2_comp_KLUCB15_long.Rda"))
 
 plot(c(0,2000), c(0, -9), type = "n")
 lines(log(loc2_comp_BUCB_horizon_4000), col = "blue")
@@ -82,6 +84,18 @@ loc2_comp_APT_2000 <- compare_to_ground_truth(mean_loc2, loc2_APT_2000, tau_loc2
 save(loc2_comp_APT_2000, file = paste0(current_path, "loc2_comp_APT_2000.Rda"))
 rm(loc2_APT)
 gc()
+
+########################################################################
+
+system.time(loc2_UNIFORM_2000 <- para_bandit_sim_uniform(data = data_list2, 
+                                                         rounds = 2000))
+save(loc2_UNIFORM_2000, file = paste0(current_path, "loc2_UNIFORM_2000.Rda"))
+loc2_comp_UNIFORM_2000 <- compare_to_ground_truth(mean_loc2, 
+                                                  loc2_UNIFORM_2000, 
+                                                  tau_loc2, 
+                                                  epsilon_loc2)$mean
+save(loc2_comp_UNIFORM_2000, file = paste0(current_path, 
+                                           "loc2_comp_UNIFORM_2000.Rda"))
 
 ########################################################################
 # Standard AugUCB

### 2017-07-20 synthetic_experiments/cal_algs_verylong_3.R

@@ -38,22 +38,22 @@ for(j in 1:5000) {
 # Plot the results
 
 load(paste0(current_path, "/loc3_comp_BUCB_horizon_7000.Rda"))
-load(paste0(current_path, "/loc3_comp_BUCB_horizon.Rda"))
-load(paste0(current_path, "/loc3_comp_APT.Rda"))
-load(paste0(current_path, "/loc3_comp_APT_7000.Rda"))
-load(paste0(current_path, "/loc3_comp_AugUCB.Rda"))
 load(paste0(current_path, "/loc3_comp_AugUCB_7000.Rda"))
+load(paste0(current_path, "/loc3_comp_KLUCB370_5000.Rda"))
+load(paste0(current_path, "/loc3_comp_UNIFORM_7000.Rda"))
+load(paste0(current_path, "/loc3_comp_APT_7000.Rda"))
 
 plot(c(0,7000), c(0, -9), type = "n")
 lines(log(loc3_comp_BUCB_horizon_7000), col = "blue")
-lines(log(loc3_comp_BUCB_horizon), col = "lightblue")
-lines(log(loc3_comp_APT), col = "pink")
+#lines(log(loc3_comp_BUCB_horizon), col = "lightblue")
+#lines(log(loc3_comp_APT), col = "pink")
 lines(log(loc3_comp_APT_7000), col = "red")
-lines(log(loc3_comp_AugUCB), col = "grey")
-lines(log(loc3_comp_AugUCB_7000), col = "black")
-lines(log(loc3_comp_KLUCB7), col = "green")
-lines(log(loc3_comp_KLUCB30), col = "green")
-lines(log(loc3_comp_KLUCB370), col = "darkgreen")
+lines(log(loc3_comp_UNIFORM_7000), col = "black")
+#lines(log(loc3_comp_AugUCB), col = "grey")
+lines(log(loc3_comp_AugUCB_7000), col = "grey")
+#lines(log(loc3_comp_KLUCB7), col = "green")
+#lines(log(loc3_comp_KLUCB30), col = "green")
+#lines(log(loc3_comp_KLUCB370), col = "darkgreen")
 lines(log(loc3_comp_KLUCB370_5000), col = "darkgreen")
 
 ########################################################################
@@ -86,6 +86,32 @@ loc3_comp_AugUCB_7000 <- compare_to_ground_truth(mean_loc3, loc3_AugUCB_7000,
[…]

### 2017-07-20 synthetic_experiments/cal_algs_verylong_4.R

@@ -152,6 +152,18 @@ loc4_comp_UNIFORM <- compare_to_ground_truth(mean_loc4, loc4_UNIFORM, tau_loc4,
 save(loc4_comp_UNIFORM, file = paste0(current_path, "loc4_comp_UNIFORM.Rda"))
 rm(loc4_UNIFORM)
 gc()
+
+########################################################################
+# Standard Uniform
+system.time(loc4_UNIFORM_8000 <- para_bandit_sim_uniform(data = data_list4_8000, 
+                                                         rounds = 8000))
+save(loc4_UNIFORM_8000, file = paste0(current_path, "loc4_UNIFORM_8000.Rda"))
+loc4_comp_UNIFORM_8000 <- compare_to_ground_truth(mean_loc4, loc4_UNIFORM_8000, 
+                                                  tau_loc4, 
+                                                  epsilon_loc4)$mean
+save(loc4_comp_UNIFORM_8000, file = paste0(current_path,
+                                           "loc4_comp_UNIFORM_8000.Rda"))
+
 ########################################################################
 # Standard APT Algorithm
 # a seed is built in
@@ -167,6 +179,20 @@ save(loc4_comp_APT, file = paste0(current_path, "loc4_comp_APT.Rda"))
 load(file = paste0(current_path, "loc4_comp_APT.Rda"))
 rm(loc4_APT)
 gc()
+
+########################################################################
+# Standard APT Algorithm
+# a seed is built in
+system.time(loc4_APT_8000 <- para_bandit_sim_APT(data = data_list4_8000, 
+                                                 rounds = 8000, 
+                                                 tau = tau_loc4, 
+                                                 epsilon = epsilon_loc4))
+save(loc4_APT_8000, file = paste0(current_path, "loc4_APT_8000.Rda"))
+loc4_comp_APT_8000 <- compare_to_ground_truth(mean_loc4, loc4_APT_8000, 
+                                              tau_loc4, 
+                                              epsilon_loc4)$mean
+save(loc4_comp_APT_8000, file = paste0(current_path, 
+                                       "loc4_comp_APT_8000.Rda"))
 
[…]

### 2017-07-20 synthetic_experiments/cal_algs_verylong_5.R

@@ -168,6 +168,38 @@ save(loc5_comp_KLUCB60, file = paste0(current_path,
 ########################################################################
 # Standard APT Algorithm
 # a seed is built in
+system.time(loc5_APT_8000 <- para_bandit_sim_APT(data = data_list5_8000, 
+                                                 rounds = 8000, 
+                                                 tau = tau_loc5, 
+                                                 epsilon = epsilon_loc5))
+# user   system  elapsed 
+#25.142   19.384 3997.529 
+save(loc5_APT_8000, file = paste0(current_path, "loc5_APT_8000.Rda"))
+#load(file = paste0(current_path, "loc5_APT_long.Rda"))
+loc5_comp_APT_8000 <- compare_to_ground_truth(mean_loc5, loc5_APT_8000, 
+                                              tau_loc5, 
+                                              epsilon_loc5)$mean
+save(loc5_comp_APT_8000, file = paste0(current_path, "loc5_comp_APT_8000.Rda"))
+#load(file = paste0(current_path, "loc5_comp_APT_long.Rda"))
+rm(loc5_APT_8000)
+gc()
+
+system.time(loc5_UNIFORM_8000 <- para_bandit_sim_uniform(data = data_list5_8000, 
+                                                         rounds = 8000))
+save(loc5_UNIFORM_8000, file = paste0(current_path, "loc5_UNIFORM_8000.Rda"))
+#load(file = paste0(current_path, "loc5_UNIFORM.Rda"))
+loc5_comp_UNIFORM_8000 <- compare_to_ground_truth(mean_loc5, 
+                                                  loc5_UNIFORM_8000, 
+                                                  tau_loc5, 
+                                                  epsilon_loc5)$mean
+save(loc5_comp_UNIFORM_8000, file = paste0(current_path, 
+                                           "loc5_comp_UNIFORM_8000.Rda"))
+rm(loc5_UNIFORM_8000)
+gc()
+
+########################################################################
+# Standard APT Algorithm
+# a seed is built in
 system.time(loc5_APT_long <- para_bandit_sim_APT(data = data_list5, rounds = 6000, 
[…]

### 2017-07-26 synthetic_experiments/long_experiments_summary.Rmd
add experiments on real data

@@
 ```{r, echo = FALSE}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE)
+
 current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
@@
 library(ggplot2)
+library(ggjoy)
+library(dplyr)
+library(tidyr)
 ```
@@
 ```
+
+## Joy Plots of Algorithm Sampling Choices
+
+### Experiment 3
+
+```{r, echo = FALSE}
+load(file = paste0(current_path, "arm_seq_loc2.Rda"))
+
+arm_seq_APT_loc2 %>% tbl_df() %>% 
+  mutate(index = 1:2000) %>%
+  gather(key = iter, value = arm, -index) %>%
+  dplyr::filter(index > 10, index <= 1500) %>%
+  dplyr::group_by(arm, index) %>%
+  dplyr::summarize(n = n()) %>%
+  ungroup() %>%
+  mutate(arm = as.factor(arm)) %>%
+  ggplot(aes(x = index, y = arm, height = n)) +
+  geom_joy(stat = "identity", scale = 1.2, size = 0.2) + theme_joy() +
+  labs(title = "APT")
+
+arm_seq_BUCB_loc2 %>% tbl_df() %>% 
+  mutate(index = 1:4000) %>%
+  gather(key = iter, value = arm, -index) %>%
+  dplyr::filter(index > 10, index <= 1500) %>%
+  dplyr::group_by(arm, index) %>%
+  dplyr::summarize(n = n()) %>%
+  ungroup() %>%
+  mutate(arm = as.factor(arm)) %>%
+  ggplot(aes(x = index, y = arm, height = n)) +
+  geom_joy(stat = "identity", scale = 1.2, size = 0.2) + theme_joy() +
+  labs(title = "Bayes-UCB")
+
+arm_seq_KLUCB_loc2 %>% tbl_df() %>% 
+  mutate(index = 1:1500) %>%
+  gather(key = iter, value = arm, -index) %>%
+  dplyr::filter(index > 10) %>%
+  dplyr::group_by(arm, index) %>%
+  dplyr::summarize(n = n()) %>%
+  ungroup() %>%
+  mutate(arm = as.factor(arm)) %>%
+  ggplot(aes(x = index, y = arm, height = n)) +
+  geom_joy(stat = "identity", scale = 1.2, size = 0.2) + theme_joy() +
+  labs(title = "KL-UCB")
+
+arm_seq_AugUCB_loc2 %>% tbl_df() %>% 
+  mutate(index = 1:2000) %>%
+  gather(key = iter, value = arm, -index) %>%
+  dplyr::filter(index > 10, index <= 1500) %>%
+  dplyr::group_by(arm, index) %>%
+  dplyr::summarize(n = n()) %>%
+  ungroup() %>%
+  mutate(arm = as.factor(arm)) %>%
+  ggplot(aes(x = index, y = arm, height = n)) +
+  geom_joy(stat = "identity", scale = 1.2, size = 0.2) + theme_joy() +
+  labs(title = "Augmented UCB")
+```
+
+### Experiment 3
+
+```{r, echo = FALSE}
+load(file = paste0(current_path, "arm_seq_loc3.Rda"))
+
+arm_seq_APT_loc3 %>% tbl_df() %>% 
+  mutate(index = 1:7000) %>%
+  gather(key = iter, value = arm, -index) %>%
+  dplyr::filter(index > 10, index <= 5000) %>%
+  dplyr::group_by(arm, index) %>%
+  dplyr::summarize(n = n()) %>%
+  ungroup() %>%
+  mutate(arm = as.factor(arm)) %>%
+  ggplot(aes(x = index, y = arm, height = n)) +
+  geom_joy(stat = "identity", scale = 1.5, size = 0.2) + theme_joy() +
+  labs(title = "APT")
+
+arm_seq_BUCB_loc3 %>% tbl_df() %>% 
+  mutate(index = 1:7000) %>%
+  gather(key = iter, value = arm, -index) %>%
+  dplyr::filter(index > 10, index <= 5000) %>%
+  dplyr::group_by(arm, index) %>%
+  dplyr::summarize(n = n()) %>%
+  ungroup() %>%
+  mutate(arm = as.factor(arm)) %>%
+  ggplot(aes(x = index, y = arm, height = n)) +
+  geom_joy(stat = "identity", scale = 1.5, size = 0.2) + theme_joy() +
+  labs(title = "Bayes-UCB")
+
+arm_seq_KLUCB_loc3 %>% tbl_df() %>% 
+  mutate(index = 1:5000) %>%
+  gather(key = iter, value = arm, -index) %>%
+  dplyr::filter(index > 10) %>%
+  dplyr::group_by(arm, index) %>%
+  dplyr::summarize(n = n()) %>%
+  ungroup() %>%
+  mutate(arm = as.factor(arm)) %>%
+  ggplot(aes(x = index, y = arm, height = n)) +
+  geom_joy(stat = "identity", scale = 1.5, size = 0.2) + theme_joy() +
+  labs(title = "KL-UCB")
+
+arm_seq_AugUCB_loc3 %>% tbl_df() %>% 
+  mutate(index = 1:7000) %>%
+  gather(key = iter, value = arm, -index) %>%
+  dplyr::filter(index > 10, index <= 5000) %>%
+  dplyr::group_by(arm, index) %>%
+  dplyr::summarize(n = n()) %>%
+  ungroup() %>%
+  mutate(arm = as.factor(arm)) %>%
+  ggplot(aes(x = index, y = arm, height = n)) +
+  geom_joy(stat = "identity", scale = 1.5, size = 0.2) + theme_joy() +
+  labs(title = "Augmented UCB")
+```
+
+### Experiment 4
+
+```{r, echo = FALSE}
+load(file = paste0(current_path, "arm_seq_loc4.Rda"))
+
+arm_seq_APT_loc4 %>% tbl_df() %>% 
+  mutate(index = 1:8000) %>%
+  gather(key = iter, value = arm, -index) %>%
+  dplyr::filter(index > 11) %>%
+  dplyr::group_by(arm, index) %>%
+  dplyr::summarize(n = n()) %>%
+  ungroup() %>%
+  mutate(arm = as.factor(arm)) %>%
+  ggplot(aes(x = index, y = arm, height = n)) +
+  geom_joy(stat = "identity", scale = 1.2, size = 0.2) + theme_joy() +
+  labs(title = "APT")
+
+arm_seq_BUCB_loc4 %>% tbl_df() %>% 
+  mutate(index = 1:8000) %>%
+  gather(key = iter, value = arm, -index) %>%
+  dplyr::filter(index > 11) %>%
+  dplyr::group_by(arm, index) %>%
+  dplyr::summarize(n = n()) %>%
+  ungroup() %>%
+  mutate(arm = as.factor(arm)) %>%
+  ggplot(aes(x = index, y = arm, height = n)) +
+  geom_joy(stat = "identity", scale = 1.2, size = 0.2) + theme_joy() +
+  labs(title = "Bayes-UCB")
+
+arm_seq_KLUCB_loc4 %>% tbl_df() %>% 
+  mutate(index = 1:8000) %>%
+  gather(key = iter, value = arm, -index) %>%
+  dplyr::filter(index > 11) %>%
+  dplyr::group_by(arm, index) %>%
+  dplyr::summarize(n = n()) %>%
+  ungroup() %>%
+  mutate(arm = as.factor(arm)) %>%
+  ggplot(aes(x = index, y = arm, height = n)) +
+  geom_joy(stat = "identity", scale = 1.2, size = 0.2) + theme_joy() +
+  labs(title = "KL-UCB")
+
+arm_seq_AugUCB_loc4 %>% tbl_df() %>% 
+  mutate(index = 1:8000) %>%
+  gather(key = iter, value = arm, -index) %>%
+  dplyr::filter(index > 11) %>%
+  dplyr::group_by(arm, index) %>%
+  dplyr::summarize(n = n()) %>%
+  ungroup() %>%
+  mutate(arm = as.factor(arm)) %>%
+  ggplot(aes(x = index, y = arm, height = n)) +
+  geom_joy(stat = "identity", scale = 1.2, size = 0.2) + theme_joy() +
+  labs(title = "Augmented UCB")
+```
+
+### Experiment 5
+
+```{r, echo = FALSE}
+load(file = paste0(current_path, "arm_seq_loc5.Rda"))
+
+arm_seq_APT_loc5 %>% tbl_df() %>% 
+  mutate(index = 1:8000) %>%
+  gather(key = iter, value = arm, -index) %>%
+  dplyr::filter(index > 10) %>%
+  dplyr::group_by(arm, index) %>%
+  dplyr::summarize(n = n()) %>%
+  ungroup() %>%
+  mutate(arm = as.factor(arm)) %>%
+  ggplot(aes(x = index, y = arm, height = n)) +
+  geom_joy(stat = "identity", scale = 1.5, size = 0.2) + theme_joy() +
+  labs(title = "APT")
+
+arm_seq_BUCB_loc5 %>% tbl_df() %>% 
+  mutate(index = 1:8000) %>%
+  gather(key = iter, value = arm, -index) %>%
+  dplyr::filter(index > 10) %>%
+  dplyr::group_by(arm, index) %>%
+  dplyr::summarize(n = n()) %>%
+  ungroup() %>%
+  mutate(arm = as.factor(arm)) %>%
+  ggplot(aes(x = index, y = arm, height = n)) +
+  geom_joy(stat = "identity", scale = 1.5, size = 0.2) + theme_joy() +
+  labs(title = "Bayes-UCB")
+
+arm_seq_KLUCB_loc5 %>% tbl_df() %>% 
+  mutate(index = 1:8000) %>%
+  gather(key = iter, value = arm, -index) %>%
+  dplyr::filter(index > 10) %>%
+  dplyr::group_by(arm, index) %>%
+  dplyr::summarize(n = n()) %>%
+  ungroup() %>%
+  mutate(arm = as.factor(arm)) %>%
+  ggplot(aes(x = index, y = arm, height = n)) +
+  geom_joy(stat = "identity", scale = 1.5, size = 0.2) + theme_joy() +
+  labs(title = "KL-UCB")
+
+arm_seq_AugUCB_loc5 %>% tbl_df() %>% 
+  mutate(index = 1:8000) %>%
+  gather(key = iter, value = arm, -index) %>%
+  dplyr::filter(index > 10) %>%
+  dplyr::group_by(arm, index) %>%
+  dplyr::summarize(n = n()) %>%
+  ungroup() %>%
+  mutate(arm = as.factor(arm)) %>%
+  ggplot(aes(x = index, y = arm, height = n)) +
+  geom_joy(stat = "identity", scale = 1.5, size = 0.2) + theme_joy() +
+  labs(title = "Augmented UCB")
+```
+
+```{r, echo = FALSE, include = FALSE}
+arm_seq_APT_loc5 %>% tbl_df() %>% 
+  mutate(index = 1:8000) %>%
+  gather(key = iter, value = arm, -index) %>%
+  mutate(arm = as.factor(arm)) %>%
+  ggplot(aes(x = index, y = arm)) +
+  geom_joy(scale = 2) + theme_joy() +
+  scale_y_discrete(expand = c(0.01, 0)) +
+  scale_x_continuous(expand = c(0, 0)) +
+  labs(title = "APT")
+
+arm_seq_APT_loc5 %>% tbl_df() %>% 
+  mutate(index = 1:8000) %>%
+  filter(index <= 2000) %>%
+  gather(key = iter, value = arm, -index) %>%
+  filter(index %in% seq(11,4000, by = 100)) %>%
+  mutate(index = as.factor(index)) %>%
+  ggplot(aes(x = arm, y = index)) +
+  geom_joy(stat = "binline", binwidth = 1, scale = 0.9) + theme_joy() +
+  scale_y_discrete(expand = c(0.01, 0)) +
+  scale_x_continuous(expand = c(0, 0)) +
+  labs(title = "APT")
+```
+
+```{r, echo = FALSE}
+load(file = paste0(current_path, "wrong_arms_BUCB_loc2.Rda"))
+head(wrong_arms_BUCB_loc2,100)
+wrong_arms_BUCB_loc2 %>%
+  filter(!is.na(arm), round > 10) %>%
+  group_by(round, arm) %>%
+  summarize(n = n()) %>%
+  ungroup() %>%
+  mutate(arm = as.factor(arm)) %>%
+  ggplot(aes(x = round, y = arm, height = n)) +
+  geom_joy(stat = "identity", scale = 1.8, size = 0.2) + theme_joy() +
+  labs(title = "Bayes-UCB - Experiment 2")
+```

### 2017-07-26 AugUCB/run_parallelized_from_data.R

@@ -91,6 +91,47 @@ compare_to_cv_data <- function(mean_list, sim_res, thresh, eps) {
 
 #################################################################################
 
+# The result is a very long data frame where each row is a (round, arm)
+# combination and specifies which arm was wrong in that round; since the
+# data frame carries information on all iterations of the simulation,
+# some combinations will (and should!) be repeated; this way it's perfect
+# for further piping into ggplot to discover which arms are classified
+# wrong by the algorithm at what stage of the sampling process
+
+# REQUIRES plyr AND IS SLOW!
+
+get_wrong_arms_per_round <- function(true_means, sim_res, tau, epsilon) {
+  n <- length(true_means)
+  message(paste0("Comparing ", length(sim_res), " simulations."))
+  true_classification_up <- which(true_means > tau+epsilon)
+  true_classification_down <- which(true_means < tau-epsilon)
+  
+  get_wrong_arms_in_iter <- function(x, true_class_up, true_class_down) {
+    arms <- sort(c(true_class_up[!(true_class_up %in% which(x >= tau))],
+                   true_class_down[!(true_class_down %in% which(x < tau))]))
+    ifelse(length(arms) == 0, NA, arms)
+  }
+  
+  get_wrong_arms <- function(res_df, ...) {
+    larms <- alply(res_df$mean_storage, .margins = 1, get_wrong_arms_in_iter, ...,
+                   .expand = TRUE)
+    dfarms <- data.frame(round = rep(0, n), arm = 1:n)
+    for(i in 1:length(larms)) {
+      dfarms <- rbind(dfarms,
+                      data.frame(round = rep(i, length(larms[[i]])),
+                                 arm = larms[[i]]))
+    }
+    return(dfarms)
+  }
+  
+  comp_list <- ldply(sim_res, get_wrong_arms, 
+                     true_class_up = true_classification_up,
+                     true_class_down = true_classification_down,
+                     .progress = "text")
+  
+  return(comp_list)
+}
+
 #################################################################################
 # input has to be a list of different data frames
 # each data frame is a run of the algorithm

### 2017-07-26 real_experiments/maximal_length.R

@@ -1,0 +1,226 @@
+sessions_threshold <- 0
+set.seed(512)
+selected_products <- sample(1:196, 10)
+niter <- 5000
+nrounds <- 7580 # These two values give the maximum size data 
+nahead <- 7580  # possible given the data set size we have
+source("/Users/timradtke/Desktop/thesis_data/get_dataset.R")
+
+dim(pv_list[[1]])
+pv_list[[1]]
+
+pv_list[[1]]
+pv_list[[5000]]
+tail(pv_list[[5000]])
+round(pv_next_means[[5000]],4)
+round(pv_next_means[[1]],4)
+
+####################################################################
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/"
+
+####################################################################
+
+data_amo1 <- pv_list
+data_amo1_wide <- pv_products_wide
+data_amo1_own_means <- pv_own_means
+data_amo1_next_means <- pv_next_means
+data_amo1_mean_secondhalf <- colMeans(data_amo1_wide[12581:20160,])
+data_amo1_mean_middlehalf <- colMeans(data_amo1_wide[7581:15161,])
+data_amo1_mean_firsthalf <- colMeans(data_amo1_wide[1:12580,])
+save(data_amo1, file = paste0(current_path, "data_amo1.Rda"))
+save(data_amo1_wide, file = paste0(current_path, "data_amo1_wide.Rda"))
+save(data_amo1_own_means, file = paste0(current_path, "data_amo1_own_means.Rda"))
+save(data_amo1_next_means, file = paste0(current_path, "data_amo1_next_means.Rda"))
+save(data_amo1_mean_firsthalf, file = paste0(current_path, "data_amo1_mean_firsthalf.Rda"))
+save(data_amo1_mean_secondhalf, file = paste0(current_path, "data_amo1_mean_secondhalf.Rda"))
+save(data_amo1_mean_middlehalf, file = paste0(current_path, "data_amo1_mean_middlehalf.Rda"))
+rm(pv_list, pv_own_means, pv_next_means, pv_products_wide)
+gc()
+
+load(paste0(current_path, "data_amo1_mean_firsthalf"))
[…]

### 2017-07-26 real_experiments/maximal_length2.R

@@ -1,0 +1,200 @@
+sessions_threshold <- 0
+set.seed(1068)
+selected_products <- sample(1:196, 10)
+niter <- 5000
+nrounds <- 7580 # These two values give the maximum size data 
+nahead <- 7580  # possible given the data set size we have
+source("/Users/timradtke/Desktop/thesis_data/get_dataset.R")
+
+dim(pv_list[[1]])
+pv_list[[1]]
+
+pv_list[[1]]
+pv_list[[5000]]
+tail(pv_list[[5000]])
+round(pv_next_means[[5000]],4)
+round(pv_next_means[[1]],4)
+
+####################################################################
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/"
+
+####################################################################
+
+data_amo2 <- pv_list
+data_amo2_wide <- pv_products_wide
+data_amo2_own_means <- pv_own_means
+data_amo2_next_means <- pv_next_means
+data_amo2_mean_secondhalf <- colMeans(data_amo2_wide[12581:20160,])
+data_amo2_mean_middlehalf <- colMeans(data_amo2_wide[7581:15161,])
+data_amo2_mean_firsthalf <- colMeans(data_amo2_wide[1:12580,])
+save(data_amo2, file = paste0(current_path, "data_amo2.Rda"))
+save(data_amo2_wide, file = paste0(current_path, "data_amo2_wide.Rda"))
+save(data_amo2_own_means, file = paste0(current_path, "data_amo2_own_means.Rda"))
+save(data_amo2_next_means, file = paste0(current_path, "data_amo2_next_means.Rda"))
+save(data_amo2_mean_firsthalf, file = paste0(current_path, "data_amo2_mean_firsthalf.Rda"))
+save(data_amo2_mean_secondhalf, file = paste0(current_path, "data_amo2_mean_secondhalf.Rda"))
+rm(pv_list, pv_own_means, pv_next_means, pv_products_wide)
+gc()
+
+load(paste0(current_path, "data_amo2_mean_firsthalf.Rda"))
+load(paste0(current_path, "data_amo2_mean_secondhalf.Rda"))
+load(paste0(current_path, "data_amo2.Rda"))
[…]

### 2017-07-26 real_experiments/post_processing_for_ggplot.R

@@ -1,0 +1,445 @@
+# a script that takes experiment results and transforms them into
+# data frames for piping into ggplot
+
+library(plyr)
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/"
+
+######################################################################
+
+#amo1
+
+load(paste0(current_path, "amo1_APT.Rda"))
+arm_seq_APT_amo1 <- data.frame(t(laply(amo1_APT, 
+                                       function(x) x$arm_sequence)))
+save(arm_seq_APT_amo1,
+     file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/arm_seq_APT_amo1.Rda")
+rm(amo1_APT)
+gc()
+
+load(paste0(current_path, "amo1_BUCB.Rda"))
+arm_seq_BUCB_amo1 <- data.frame(t(laply(amo1_BUCB, 
+                                        function(x) x$arm_sequence)))
+save(arm_seq_BUCB_amo1,
+     file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/arm_seq_BUCB_amo1.Rda")
+rm(amo1_BUCB)
+gc()
+
+load(paste0(current_path, "amo1_KLUCB.Rda"))
+arm_seq_KLUCB_amo1 <- data.frame(t(laply(amo1_KLUCB, 
+                                        function(x) x$arm_sequence)))
+save(arm_seq_KLUCB_amo1,
+     file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/arm_seq_KLUCB_amo1.Rda")
+rm(amo1_KLUCB)
+gc()
+
+load(paste0(current_path, "amo1_AugUCB.Rda"))
+arm_seq_AugUCB_amo1 <- data.frame(t(laply(amo1_AugUCB, 
+                                        function(x) x$arm_sequence)))
[…]

### 2017-07-26 real_experiments/real_vs_syn_comparison.R

@@ -1,0 +1,101 @@
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/"
+
+load(paste0(current_path, "data_amo1_mean_firsthalf"))
+load(paste0(current_path, "data_amo1_mean_secondhalf"))
+load(paste0(current_path, "data_amo1.Rda"))
+tau_amo1 <- 3/60
+epsilon_amo1 <- 1/60
+
+data <- data_amo1[[1]]
+rm(data_amo1)
+gc()
+
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+
+data.frame(index = 1:7521,
+           lapply(data, FUN = zoo::rollapply, width = 60, mean)) %>%
+  gather(arm, mean, -index) %>% 
+  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
+  geom_line() + geom_hline(aes(yintercept = tau_amo1))
+
+data.frame(index = 1:6141,
+           lapply(data, FUN = zoo::rollapply, width = 24*60, mean)) %>%
+  gather(arm, mean, -index) %>% 
+  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
+  geom_line() + geom_hline(aes(yintercept = tau_amo1))
+
+data.frame(index = 1:4701,
+           lapply(data, FUN = zoo::rollapply, width = 2*24*60, mean)) %>%
+  gather(arm, mean, -index) %>% 
+  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
+  geom_line() + geom_hline(aes(yintercept = tau_amo1))
+
+
+real_mean <- unlist(lapply(data, mean))
+H_real <- get_complexity(real_mean, tau_amo1, epsilon_amo1)
+
+
+syn_data <- data.frame(rep(NA, times = 7580))
+set.seed(124632728)
+for(i in 1:length(real_mean)) {
+  syn_data[[i]] <- as.numeric(purrr::rbernoulli(7580, p  = real_mean[i]))
+}
+names(syn_data) <- names(real_mean)
+
+data.frame(index = 1:7521,
+           lapply(syn_data, FUN = zoo::rollapply, width = 60, mean)) %>%
+  gather(arm, mean, -index) %>% 
[…]

### 2017-07-26 synthetic_experiments/post_processing_for_ggplot.R

@@ -1,0 +1,285 @@
+# a script that takes experiment results and transforms them into
+# data frames for piping into ggplot
+
+library(plyr)
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
+
+######################################################################
+
+#amo1
+
+load(paste0("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/amo1_APT.Rda"))
+load(paste0("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/amo1_BUCB.Rda"))
+
+arm_seq_APT_amo1 <- data.frame(t(laply(amo1_APT, 
+                                       function(x) x$arm_sequence)))
+arm_seq_BUCB_amo1 <- data.frame(t(laply(amo1_BUCB, 
+                                       function(x) x$arm_sequence)))
+
+save(arm_seq_APT_amo1,
+     file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/arm_seq_APT_amo1.Rda")
+save(arm_seq_BUCB_amo1,
+     file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/arm_seq_BUCB_amo1.Rda")
+
+library(ggplot)
+library(ggjoy)
+library(dplyr)
+library(tidyr)
+
+arm_seq_APT_amo1 %>% tbl_df() %>% 
+  mutate(index = 1:7580) %>%
+  gather(key = iter, value = arm, -index) %>%
+  dplyr::filter(index > 10) %>%
+  dplyr::group_by(arm, index) %>%
+  dplyr::summarize(n = n()) %>%
+  ungroup() %>%
+  mutate(arm = as.factor(arm)) %>%
+  ggplot(aes(x = index, y = arm, height = n)) +
+  geom_joy(stat = "identity", scale = 1.2, size = 0.2) + theme_joy() +
+  labs(title = "APT", y = "Arm", x = "Round",
[…]

### 2017-07-30 real_experiments/long_experiments_summary_LR.Rmd
add LR algorithm to experiments

---
title: "Experiments with LR-based Strategy"
output: pdf_document
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)

current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
source(paste0(current_path, "run_from_data.R"))
source(paste0(current_path, "run_parallelized_from_data.R"))
current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
library(ggplot2)
library(ggjoy)
library(dplyr)
library(tidyr)
```

In the following experiments which are all based on 5000 iterations, we consider the following algorithms:

- APT (Locatelli et al. (2016))
- UNIFORM
- LR Likelihood Ratio based strategy
- AugUCB Augmented-UCB (Mukherjee et al., 2017)
- B-UCB Bayes-UCB (adapted from "On Bayesian Upper Confidence Bounds for Bandit Problems" by Kaufmann, Cappé, Garivier, 2012)
- KL-UCB (adapted version of fixed budget KL-LUCB-E in "Information Complexity in Bandit Subset Selection" by Kaufmann, Kalyanakrishnan, 2013)
- TTS Thompson-Sampling based strategy adapted for thresholding problem (only in the problem on real data).

## Experiment 2

The same as experiment 3 in Locatelli et al. (2016). We have the following means, threshold (solid line), and epsilon interval (dashed line):

```{r, echo = FALSE, fig.height = 3}
mean_loc2 <- c(0.4-0.2^(1:4),
               0.45, 0.55,
               0.6+0.2^(5-(1:4)))
tau_loc2 <- 0.5
epsilon_loc2 <- 0.1
H_loc2 <- get_complexity(mean_loc2, tau_loc2, epsilon_loc2)

plot(mean_loc2, c(1,1,0.98,1.02,1,1,1.02,0.98,1,1), pch = 19, ylim = c(0.8,1.2), ylab = "", xlab = "Mean Locations", main = paste0("Setup Experiment 2 - Complexity of ", round(H_loc2)))
abline(v=tau_loc2)
abline(v=tau_loc2+epsilon_loc2, lty=2)
abline(v=tau_loc2-epsilon_loc2, lty=2)
```

The experiment results are as follows:

```{r, echo = FALSE}
library(ggplot2)

load(paste0(current_path, "/loc2_comp_BUCB_horizon_4000.Rda"))
load(paste0(current_path, "/loc2_comp_APT_2000.Rda"))
load(paste0(current_path, "/loc2_comp_AugUCB_2000.Rda"))
load(paste0(current_path, "/loc2_comp_KLUCB80_long.Rda"))
load(paste0(current_path, "/loc2_comp_UNIFORM_2000.Rda"))
load(paste0(current_path, "/loc2_comp_LR_2000.Rda"))

alg_names <- c(rep(c("Uniform", "APT", "AugUCB", "B-UCB", "LR"), each = 1991), rep("KL-UCB", 1491))
index <- c(rep(10:2000, times = 5), 10:1500)
alg_res <- log(c(loc2_comp_UNIFORM_2000, loc2_comp_APT_2000, loc2_comp_AugUCB_2000, loc2_comp_BUCB_horizon_4000[1:1991], loc2_comp_LR_2000, loc2_comp_KLUCB80_long))
loc2_comp_res <- data.frame(Round = index, Algorithm = alg_names, 
                            results = alg_res)
ggplot(loc2_comp_res, aes(x = Round, y = alg_res)) + geom_line(aes(group = Algorithm, color = Algorithm)) + geom_hline(aes(yintercept = log(0.01)), linetype = 2) +
  labs(title = "Experiment 2 Results", y = "log(Error)", subtitle = "Horizontal Bar at 0.05 Average Error")
```

\newpage

## Experiment 3

This is the first of three experiments at a very small threshold and with accordingly small means for again 10 arms. As before, the arms are distributed symmetrically around the threshold. We let the algorithms run for more iterations than previously. The means, threshold, intervals are as follows:

```{r, echo = FALSE, fig.height = 3}
mean_loc3 <- c(0.001, 0.005, 0.01, 0.015,
               0.0475, 0.0525,
               0.085, 0.09, 0.095, 0.099)
tau_loc3 <- 0.05
epsilon_loc3 <- 0.005
H_loc3 <- get_complexity(mean_loc3, tau_loc3, epsilon_loc3)

plot(mean_loc3, c(1,1,1,1,1,1,1,1,1,1), pch = 19, ylim = c(0.8,1.2), ylab = "", xlab = "Mean Locations", main = paste0("Setup Experiment 3 - Complexity of ", round(H_loc3)))
abline(v=tau_loc3)
abline(v=tau_loc3+epsilon_loc3, lty=2)
abline(v=tau_loc3-epsilon_loc3, lty=2)
```

The results are as follows:

```{r, echo = FALSE}
load(paste0(current_path, "/loc3_comp_BUCB_horizon_7000.Rda"))
load(paste0(current_path, "/loc3_comp_AugUCB_7000.Rda"))
load(paste0(current_path, "/loc3_comp_KLUCB370_5000.Rda"))
load(paste0(current_path, "/loc3_comp_UNIFORM_7000.Rda"))
load(paste0(current_path, "/loc3_comp_APT_7000.Rda"))
load(paste0(current_path, "/loc3_comp_LR_7000.Rda"))

alg_names <- c(rep(c("Uniform", "APT", "AugUCB", "B-UCB", "LR"), each = 6991), rep("KL-UCB", 4991))
index <- c(rep(10:7000, times = 5), 10:5000)
alg_res <- log(c(loc3_comp_UNIFORM_7000, loc3_comp_APT_7000, loc3_comp_AugUCB_7000, loc3_comp_BUCB_horizon_7000, loc3_comp_LR_7000, loc3_comp_KLUCB370_5000))
loc3_comp_res <- data.frame(index = index, names = alg_names, 
                            results = alg_res)
ggplot(loc3_comp_res, aes(x = index, y = alg_res)) + geom_line(aes(group = alg_names, color = alg_names)) + geom_hline(aes(yintercept = log(0.01)), linetype = 2) +
  labs(title = "Experiment 3 Results", subtitle = paste0("Complexity of ", round(H_loc3)), y = "log(Error)")
```

\newpage

## Experiment on Real Data

This experiment is based on data from Amorelie where each observation is based on whether or not a page had viewers during the minute. Thus, one round has observations for 7580 minutes, or a little more than 5 days. We observe that the mean of the data fluctuates over time. If we consider a moving average the observations with a window of 60*24 minutes, and compare it against a data set that was drawn randomly from Bernoulli distributions based on the sample means from the real data, we clearly see time dependency:

```{r, echo = FALSE, fig.height = 4}
current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/"

load(paste0(current_path, "data_amo1_mean_firsthalf"))
load(paste0(current_path, "data_amo1_mean_secondhalf"))
load(paste0(current_path, "data_amo1.Rda"))
tau_amo1 <- 3/60
epsilon_amo1 <- 1/60

data <- data_amo1[[1]]
rm(data_amo1)
#gc()

library(dplyr)
library(tidyr)
library(ggplot2)

real_mean <- unlist(lapply(data, mean))
H_real <- get_complexity(real_mean, tau_amo1, epsilon_amo1)

syn_data <- data.frame(rep(NA, times = 7580))
set.seed(124632728)
for(i in 1:length(real_mean)) {
  syn_data[[i]] <- as.numeric(purrr::rbernoulli(7580, p  = real_mean[i]))
}
names(syn_data) <- names(real_mean)

real_daily <- data.frame(source = rep("Real", 6141),
                         index = 1:6141,
                        lapply(data, FUN = zoo::rollapply, width = 24*60, mean)) %>%
  gather(arm, mean, -index, -source)
syn_daily <- data.frame(source = rep("Synthetic", 6141),
                        index = 1:6141,
                        lapply(syn_data, FUN = zoo::rollapply, width = 24*60, mean)) %>%
  gather(arm, mean, -index, -source)

rbind(real_daily, syn_daily) %>%
  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
  geom_line() + geom_hline(aes(yintercept = tau_amo1)) + geom_hline(aes(yintercept = tau_amo1+epsilon_amo1), linetype = 2) + geom_hline(aes(yintercept = tau_amo1-epsilon_amo1), linetype = 2) +
  facet_grid(.~source) + labs(title = "Moving average over 24*60 observations (1 day)", subtitle = "Horizontal Bar indicates the threshold")

```

The results on the **real** data are as follows:

```{r, echo = FALSE}
load(paste0(current_path, "amo1_comp_BUCB.Rda"))
load(paste0(current_path, "amo1_comp_APT.Rda"))
load(paste0(current_path, "amo1_comp_UNIFORM.Rda"))
load(paste0(current_path, "amo1_comp_KLUCB.Rda"))
load(paste0(current_path, "amo1_comp_AugUCB.Rda"))
load(paste0(current_path, "amo1_comp_TTS.Rda"))
load(paste0(current_path, "amo1_comp_LR.Rda"))

alg_names <- c(rep(c("Uniform", "APT", "AugUCB", "B-UCB", "KL-UCB", "TTS", "LR"), each = 7571))
index <- c(rep(10:7580, times = 7))
alg_res <- log(c(amo1_comp_UNIFORM, amo1_comp_APT, amo1_comp_AugUCB, amo1_comp_BUCB, amo1_comp_KLUCB, amo1_comp_TTS, amo1_comp_LR))
loc3_comp_res <- data.frame(index = index, names = alg_names, 
                            results = alg_res)
ggplot(loc3_comp_res, aes(x = index, y = alg_res)) + geom_line(aes(group = alg_names, color = alg_names)) +
  labs(title = "Experiment on Real Data Results", subtitle = paste0("Sample Mean Complexity of ", round(H_real)), y = "log(Error)")
```

### 2017-07-30 AugUCB/run_from_data.R

@@ -686,6 +686,63 @@ get_next_arm_uniform <- function(armls) {
 
 ##############################################################
 
+# Likelihood Ratio based Algorithm
+
+LR_bandit_from_tsdata <- function(data, rounds = 5000, tau, epsilon,
+                                  verbose = FALSE, seed = NA) {
+  
+  if(!is.na(seed)) set.seed(seed)
+  K <- dim(data)[2]
+  
+  # initialize by pulling each arm once
+  arm_list <- diag(as.matrix(data[1:K,]))
+  arm_list <- as.list(arm_list)
+  
+  # initialize mean storage and the counter
+  mean_storage <- matrix(unlist(lapply(arm_list, mean)), nrow = 1)
+  arm_sequence <- 1:K
+  
+  for(i in (K+1):rounds) {
+    if(verbose) message(paste("this is round", i))
+    next_arm <- get_min(-unlist(get_next_arm_lr(arm_list, tau = tau,
+                                                epsilon = epsilon)))
+    arm_sequence <- c(arm_sequence, next_arm)
+    
+    if(verbose) message("arm selecting done")
+    if(verbose) message(next_arm)
+    arm_list[[next_arm]] <- c(arm_list[[next_arm]], data[i, next_arm])
+    
+    mean_storage <- rbind(mean_storage, unlist(lapply(arm_list, mean)))
+    
+    if(verbose) message("arm pulling done")
+    
+  }
+  return(list(means = unlist(lapply(arm_list, mean)),
+              arm_list = arm_list,
+              arm_sequence = arm_sequence,
+              mean_storage = mean_storage))
+}
+
+lr_ber <- function(x,S,N) {
+  # here, S/N is the empirical mean (successes over trials)
+  # while x represents some H0 mean we test against
+  (x/(S/N))^(S) * ((1-x)/(1-S/N))^(N-S)
+}
+
+get_next_arm_lr <- function(armls, tau, epsilon) {
+  get_metric <- function(x) {
+    successes <- sum(x)
+    trials <- length(x)
+    LRhat <- ifelse(successes/trials >= tau,
+                    lr_ber(tau-epsilon, successes, trials),
+                    lr_ber(tau+epsilon, successes, trials))
+    return(LRhat)
+  }
+  lapply(armls, get_metric)
+}
+
+##############################################################
+
 
 #mean_002 <- c(0.033, 0.033, 0.037, 0.037,
 #              0.031, 0.031, 0.039, 0.039,

### 2017-07-30 AugUCB/run_parallelized_from_data.R

@@ -164,6 +164,37 @@ para_bandit_sim_APT <- function(data, seed = NA, do_verbose = FALSE, ...) {
 }
 
 #################################################################################
+# input has to be a list of different data frames
+# each data frame is a run of the algorithm
+# in the end, return a list of lists
+# each object of the first list should be a list that contains 
+# the mean_storage data frame and the arm_sequence vector
+
+para_bandit_sim_LR <- function(data, seed = NA, do_verbose = FALSE, ...) {
+  require(foreach)
+  require(doParallel)
+  
+  # assume that data is a list of data frames
+  reps <- length(data)
+  
+  gc()
+  cl <- makeCluster(max(1,detectCores()-1))
+  registerDoParallel(cl)
+  res <- foreach(j = 1:reps, #.errorhandling = 'remove',
+                 .export = c("LR_bandit_from_tsdata", "get_next_arm_lr",
+                             "get_min", "lr_ber"), 
+                 .verbose = do_verbose, .inorder = TRUE) %dopar% {
+                   alg_res <- LR_bandit_from_tsdata(data = data[[j]], 
+                                              seed = 512+j, ...)
+                   list(mean_storage = alg_res$mean_storage,
+                        arm_sequence = alg_res$arm_sequence,
+                        input_data = data[[j]])
+                 }
+  stopCluster(cl)
+  return(res)
+}
+
+#################################################################################
 
 para_bandit_sim_AugUCB <- function(data, seed = NA, do_verbose = FALSE, ...) {
   require(foreach)

### 2017-07-30 for_theory/bound_comparison.R

@@ -1,0 +1,116 @@
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+
+
+get_chernoff_info <- function(x,y) {
+  if(x < y) {
+    S <- seq(x,y,by=0.00001)
+  } else {
+    S <- seq(y,x,by=0.00001)
+  }
+  klx <- kl_ber(S,x)
+  kly <- kl_ber(S,y)
+  kl_ber(S[which.min(abs(klx-kly))],y)
+}
+
+get_chernoff_info(0.2,0.4)
+
+test_grid <- expand.grid(p = seq(0.001,0.999,0.001),
+                         tau = seq(0.001,0.999,0.001))
+test_grid <- test_grid[test_grid$p != test_grid$tau,]
+test_grid$chernoff <- NA
+test_grid$DeltaSquared <- (test_grid$p - test_grid$tau)^2
+dim(test_grid)
+#for(i in 1:10) {
+#  test_grid[i,3] <- get_chernoff_info(test_grid[i,1], test_grid[i,2])
+#}
+
+library(dplyr)
+test_grid %>% filter(p > 0.48, p<0.52)
+test_grid %>% filter(chernoff < DeltaSquared)
+dim(test_grid[is.na(test_grid$chernoff),])
+
+
+#############################################
+
+get_complexity
+get_chernoff_complexity <- function(means, tau, epsilon) {
+  res <- vector(length = length(means))
+  for(i in 1:length(means)) {
+    res[i] <- max(get_chernoff_info(means[i], tau), epsilon^2/2)
+  }
+  sum(1/res)
+}
+get_APT_complexity <- function(means, tau, epsilon) {
+  res <- vector(length = length(means))
+  for(i in 1:length(means)) {
+    res[i] <- (abs(means[i] - tau) + epsilon)^2
+  }
+  sum(1/res)
+}
+
+mean_loc7nt <- c(10^-4, 10^-3.5, 10^-3.25, 10^-3, 
+                 10^-2.75, 10^-2.5, 10^-2.25, 10^-1.85, 10^-1.75,
[…]

### 2017-07-30 real_experiments/maximal_length.R

@@ -115,6 +115,22 @@ gc()
 
 
 ########################################################################
+# LR Algorithm
+system.time(amo1_LR <- para_bandit_sim_LR(data = data_amo1, rounds = 7580, 
+                                            tau = tau_amo1, epsilon = epsilon_amo1))
+save(amo1_LR, file = paste0(current_path, "amo1_LR.Rda"))
+#load(paste0(current_path, "amo1_LR.Rda"))
+amo1_comp_LR <- compare_to_ground_truth(data_amo1_mean_firsthalf, amo1_LR, 
+                                         tau_amo1, epsilon_amo1)$mean
+amo1_compholdout_LR <- compare_to_ground_truth(data_amo1_mean_secondhalf, amo1_LR, 
+                                                tau_amo1, epsilon_amo1)$mean
+
+save(amo1_comp_LR, file = paste0(current_path, "amo1_comp_LR.Rda"))
+save(amo1_compholdout_LR, file = paste0(current_path, "amo1_compholdout_LR.Rda"))
+rm(amo1_LR)
+gc()
+
+########################################################################
 # Standard Uniform
 system.time(amo1_UNIFORM <- para_bandit_sim_uniform(data = data_amo1, 
                                                     rounds = 7580))
@@ -203,6 +219,11 @@ data_amo1_mean_firsthalf > 3/60
 data_amo1_mean_firsthalf < 1/60
 load(paste0(current_path, "amo1_comp_APT.Rda"))
 load(paste0(current_path, "amo1_comp_BUCB.Rda"))
+load(paste0(current_path, "amo1_comp_KLUCB.Rda"))
+load(paste0(current_path, "amo1_comp_AugUCB.Rda"))
+load(paste0(current_path, "amo1_comp_UNIFORM.Rda"))
+load(paste0(current_path, "amo1_comp_TTS.Rda"))
+load(paste0(current_path, "amo1_comp_LR.Rda"))
 plot(c(0,8000), c(0, -8), type = "n")
 lines(log(amo1_comp_UNIFORM), col = "black")
 lines(log(amo1_comp_APT), col = "blue")
@@ -210,12 +231,18 @@ lines(log(amo1_comp_AugUCB), col = "red")
 lines(log(amo1_comp_BUCB), col = "green")
 lines(log(amo1_comp_KLUCB), col = "darkgreen")
[…]

### 2017-07-30 real_experiments/maximal_length2.R

@@ -177,6 +177,7 @@ data_amo2_mean_firsthalf > 3/60
 data_amo2_mean_firsthalf < 1/60
 load(paste0(current_path, "amo2_comp_APT.Rda"))
 load(paste0(current_path, "amo2_comp_BUCB.Rda"))
+load(paste0(current_path, "amo2_comp_UNIFORM.Rda"))
 plot(c(0,8000), c(0, -8), type = "n")
 lines(log(amo2_comp_UNIFORM), col = "black")
 lines(log(amo2_comp_APT), col = "blue")
@@ -190,6 +191,7 @@ data_amo2_mean_secondhalf > 3/60
 data_amo2_mean_secondhalf < 1/60
 load(paste0(current_path, "amo2_compholdout_BUCB.Rda"))
 load(paste0(current_path, "amo2_compholdout_APT.Rda"))
+load(paste0(current_path, "amo2_compholdout_UNIFORM.Rda"))
 plot(c(0,8000), c(0, -6), type = "n")
 lines(log(amo2_compholdout_UNIFORM), col = "black")
 lines(log(amo2_compholdout_APT), col = "blue")

### 2017-07-30 synthetic_experiments/cal_algs_very_long_no_tau.R

@@ -1,0 +1,198 @@
+# run a simulation based on a simple example that can hopefully serve to
+# calibrate the algorithms
+########################################################################
+# load functions
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
+
+########################################################################
+# Create the data
+
+mean_loc3nt <- c(0.001, 0.005, 0.01, 0.015,
+               0.0475, 0.0525,
+               0.085, 0.09, 0.095, 0.099)
+tau_loc3nt <- 0.05
+epsilon_loc3nt <- 0
+H_loc3nt <- get_complexity(mean_loc3nt, tau_loc3nt, epsilon_loc3nt)
+
+plot(mean_loc3nt, rep(1,10), main = paste0("Complexity of ", round(H_loc3nt,2)))
+abline(v=tau_loc3nt)
+abline(v=tau_loc3nt+epsilon_loc3nt, lty=2)
+abline(v=tau_loc3nt-epsilon_loc3nt, lty=2)
+
+data_list3 <- list()
+set.seed(1024)
+for(j in 1:5000) {
+  curr_data <- data.frame(rep(NA, times = 7000))
+  for(i in 1:length(mean_loc3nt)) {
+    curr_data[[i]] <- as.numeric(purrr::rbernoulli(7000, p  = mean_loc3nt[i]))
+  }
+  names(curr_data) <- paste0("V", rep(1:length(mean_loc3nt)))
+  data_list3[[j]] <- curr_data
+}
+
+########################################################################
+# Plot the results
+
+load(paste0(current_path, "/loc3nt_comp_BUCB_horizon_7000.Rda"))
+load(paste0(current_path, "/loc3nt_comp_AugUCB_7000.Rda"))
+load(paste0(current_path, "/loc3nt_comp_KLUCB370_5000.Rda"))
+load(paste0(current_path, "/loc3nt_comp_UNIFORM_7000.Rda"))
+load(paste0(current_path, "/loc3nt_comp_APT_7000.Rda"))
+load(paste0(current_path, "/loc3nt_comp_LR_7000.Rda"))
+
[…]

### 2017-07-30 synthetic_experiments/cal_algs_verylong_2.R

@@ -39,6 +39,7 @@ for(j in 1:5000) {
 
 load(paste0(current_path, "/loc2_comp_BUCB_horizon_4000.Rda"))
 load(paste0(current_path, "/loc2_comp_APT_2000.Rda"))
+load(paste0(current_path, "/loc2_comp_LR_2000.Rda"))
 load(paste0(current_path, "/loc2_comp_AugUCB_2000.Rda"))
 load(paste0(current_path, "/loc2_comp_KLUCB80_long.Rda"))
 load(paste0(current_path, "/loc2_comp_KLUCB15_long.Rda"))
@@ -46,6 +47,7 @@ load(paste0(current_path, "/loc2_comp_KLUCB15_long.Rda"))
 plot(c(0,2000), c(0, -9), type = "n")
 lines(log(loc2_comp_BUCB_horizon_4000), col = "blue")
 lines(log(loc2_comp_APT_2000), col = "red")
+lines(log(loc2_comp_LR_2000), col = "black")
 lines(log(loc2_comp_AugUCB_2000), col = "grey")
 #lines(log(loc2_comp_KLUCB100), col = "green")
 #lines(log(loc2_comp_KLUCB80), col = "green")
@@ -83,6 +85,21 @@ loc2_comp_APT_2000 <- compare_to_ground_truth(mean_loc2, loc2_APT_2000, tau_loc2
                                          epsilon_loc2)$mean
 save(loc2_comp_APT_2000, file = paste0(current_path, "loc2_comp_APT_2000.Rda"))
 rm(loc2_APT)
+gc()
+
+########################################################################
+# Standard LR Algorithm
+
+system.time(loc2_LR_2000 <- para_bandit_sim_LR(data = data_list2, 
+                                               rounds = 2000, 
+                                               tau = tau_loc2, 
+                                               epsilon = epsilon_loc2))
+save(loc2_LR_2000, file = paste0(current_path, "loc2_LR_2000.Rda"))
+#load(file = paste0(current_path, "loc2_APT.Rda"))
+loc2_comp_LR_2000 <- compare_to_ground_truth(mean_loc2, loc2_LR_2000, tau_loc2, 
+                                              epsilon_loc2)$mean
+save(loc2_comp_LR_2000, file = paste0(current_path, "loc2_comp_LR_2000.Rda"))
+rm(loc2_LR)
 gc()
 
 ########################################################################

### 2017-07-30 synthetic_experiments/cal_algs_verylong_3.R

@@ -42,11 +42,13 @@ load(paste0(current_path, "/loc3_comp_AugUCB_7000.Rda"))
 load(paste0(current_path, "/loc3_comp_KLUCB370_5000.Rda"))
 load(paste0(current_path, "/loc3_comp_UNIFORM_7000.Rda"))
 load(paste0(current_path, "/loc3_comp_APT_7000.Rda"))
+load(paste0(current_path, "/loc3_comp_LR_7000.Rda"))
 
 plot(c(0,7000), c(0, -9), type = "n")
 lines(log(loc3_comp_BUCB_horizon_7000), col = "blue")
 #lines(log(loc3_comp_BUCB_horizon), col = "lightblue")
 #lines(log(loc3_comp_APT), col = "pink")
+lines(log(loc3_comp_LR_7000), col = "green")
 lines(log(loc3_comp_APT_7000), col = "red")
 lines(log(loc3_comp_UNIFORM_7000), col = "black")
 #lines(log(loc3_comp_AugUCB), col = "grey")
@@ -88,18 +90,30 @@ save(loc3_comp_AugUCB_7000, file = paste0(current_path,
                                           "loc3_comp_AugUCB_7000.Rda"))
 
 ########################################################################
-# Standard AugUCB
+# Standard APT
 system.time(loc3_APT_7000 <- para_bandit_sim_APT(data = data_list3, 
                                                  rounds = 7000, 
                                                  tau = tau_loc3, 
                                                  epsilon = epsilon_loc3))
-#     user    system   elapsed 
-#46.915    50.807 18671.723
+
 save(loc3_APT_7000, file = paste0(current_path, "loc3_APT_7000.Rda"))
 loc3_comp_APT_7000 <- compare_to_ground_truth(mean_loc3, loc3_APT_7000, 
                                                  tau_loc3, epsilon_loc3)$mean
 save(loc3_comp_APT_7000, file = paste0(current_path, 
                                        "loc3_comp_APT_7000.Rda"))
+
+########################################################################
+# Standard Likelihood Ratio
+system.time(loc3_LR_7000 <- para_bandit_sim_LR(data = data_list3, 
+                                               rounds = 7000, 
+                                               tau = tau_loc3, 
+                                               epsilon = epsilon_loc3))
+
+save(loc3_LR_7000, file = paste0(current_path, "loc3_LR_7000.Rda"))
+loc3_comp_LR_7000 <- compare_to_ground_truth(mean_loc3, loc3_LR_7000, 
[…]

### 2017-07-30 synthetic_experiments/cal_algs_verylong_6_no_tau.R

@@ -1,0 +1,196 @@
+# run a simulation based on a simple example that can hopefully serve to
+# calibrate the algorithms
+########################################################################
+# load functions
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
+
+########################################################################
+# Create the data
+
+mean_loc6nt <- c(0.001, 0.005, 0.01, 0.015,
+                 0.04, 0.06,
+                 0.085, 0.09, 0.095, 0.099)
+tau_loc6nt <- 0.05
+epsilon_loc6nt <- 0
+H_loc6nt <- get_complexity(mean_loc6nt, tau_loc6nt, epsilon_loc6nt)
+
+plot(mean_loc6nt, rep(1,10), main = paste0("Complexity of ", round(H_loc6nt,2)))
+abline(v=tau_loc6nt)
+abline(v=tau_loc6nt+epsilon_loc6nt, lty=2)
+abline(v=tau_loc6nt-epsilon_loc6nt, lty=2)
+
+data_list6 <- list()
+set.seed(8247502)
+for(j in 1:5000) {
+  curr_data <- data.frame(rep(NA, times = 7000))
+  for(i in 1:length(mean_loc6nt)) {
+    curr_data[[i]] <- as.numeric(purrr::rbernoulli(7000, p  = mean_loc6nt[i]))
+  }
+  names(curr_data) <- paste0("V", rep(1:length(mean_loc6nt)))
+  data_list6[[j]] <- curr_data
+}
+
+########################################################################
+# Plot the results
+
+load(paste0(current_path, "/loc6nt_comp_BUCB_horizon_7000.Rda"))
+load(paste0(current_path, "/loc6nt_comp_AugUCB_7000.Rda"))
+load(paste0(current_path, "/loc6nt_comp_KLUCB370_5000.Rda"))
+load(paste0(current_path, "/loc6nt_comp_UNIFORM_7000.Rda"))
+load(paste0(current_path, "/loc6nt_comp_APT_7000.Rda"))
[…]

### 2017-07-30 LR_Theory/LR_theory.Rmd
Start proof of LR strategy

---
title: "LR Theory"
author: "Tim Radtke"
header-includes:
   #- \documentclass[a4paper,twoside,english]{article}
   - \usepackage[retainorgcmds]{IEEEtrantools}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{bbm}
   - \newtheorem{theorem}{Theorem}
   - \newtheorem{lemma}{Lemma}
   - \newcommand{\KL}{\,\text{KL}}
   - \newcommand{\der}{\,\text{d}}
   #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
   #- \usepackage{fontspec}
   #-   \setmainfont{TimesNewRoman}
keep_tex: TRUE
output:
  pdf_document:
    number_sections: true
    keep_tex: true
    #toc: true
    #toc_depth: 3
    #latex_engine: xelatex
fontsize: 12pt
urlcolor: blue
---

# Kullback-Leibler Divergence Strategy

We start with a definition of the Likelihood Ratio. See for example Example 6 in [http://math.arizona.edu/~jwatkins/s-lrt.pdf](http://math.arizona.edu/~jwatkins/s-lrt.pdf).

In our strategy, we will have at time $t$ a sample of observations for arm $i$ of size $T_i(t)$: $\mathbb{x} = x_1, ..., x_{T_i(t)}$. Since we are only considering Bernoulli distributions at this point, the Likelihood for a sample from distribution $Ber(\mu)$ is given by

$$ 
L(\mu|\mathbb{x}) = (1-\mu)^{T_i(t) - \sum_{s = 1}^{T_i(t)} x_s} \mu^{\sum_{s = 1}^{T_i(t)} x_s}
$$

We want to test whether the sample $\mathbb{x}$ with maximum likelihood estimate ($H_1: \mu = \hat{\mu}$) is actually different from the standard hypothesis that it is equal to the threshold $\tau$ ($H_0: \mu = \tau$). To test this, we can use the likelihood ratio:

$$
\Lambda = \frac{L(\tau|\mathbb{x})}{L(\hat{\mu}|\mathbb{x})} = \frac{\tau^{\hat{\mu}T_i(t)}(1-\tau)^{(1-\hat{\mu})T_i(t)} }{\hat{\mu}^{\hat{\mu}T_i(t)}(1-\hat{\mu})^{(1-\hat{\mu})T_i(t)}}
$$
If the likelihood ratio is large, then it's quite likely that the sample was generated by a Bernoulli distribution with parameter $\tau$. If the ratio is small, then the maximum likelihood estimate is very different from the threshold. The statistic should be smaller than 1 given that we compare to the maximum likelihood estimate.

In an adaptive sampling strategy that is based on this ratio, it is natural to pull the arm that currently maximizes the ratio (an arm with distribution close to $\tau$). Even if the true parameter $\mu$ is close to $\tau$, the ratio will increase over time as $T_i(t)$ increases. Thus given two distributions with the same maximum likelihood estimate, the strategy will pull the arm that has a smaller $T_i(t)$.

Thus our strategy could be to pull arm $i^*$ at time $t+1$ that maximizes $\tilde{B}_i(t) = \Lambda_i$. Of course, $\arg \max_i \Lambda_i(t) = \arg \min_i -\log(\Lambda_i(t))$. And so an equivalent strategy is to pull $i^*(t) = \arg \min_i -\log(\Lambda_i(t))$. We now show that this is equivalent to $i^*(t) = \arg \min_i T_i(t)\hat{\KL}(\hat{\mu}||\tau)$.

We have

\begin{align*}
-\log(\Lambda_i(t)) & = \hat{\mu}T_i(t) \log(\frac{\hat{\mu}_i(t)}{\tau}) + (1-\hat{\mu})T_i(t) \log(\frac{1-\hat{\mu}_i(t)}{1-\tau}) \\
& = T_i(t) [\hat{\mu}_i(t) \log(\frac{\hat{\mu}_i(t)}{\tau}) + (1-\hat{\mu}_i(t)) \log(\frac{1-\hat{\mu}_i(t)}{1-\tau})] \\
& = T_i(t) \der(\hat{\mu}_i(t), \tau) \\
& = B_i(t)
\end{align*}

This notation of the index will prove useful in theoretical derivations, while the likelihood ratio is advantageous in the implementation of the algorithm, as it can be computed even when $\hat{\mu}=0$ or $\hat{\mu}=1$, which will always occur in the beginning of the sampling.

## Comparison with Other Indices

If we consider $B_i^{APT}(t) = T_i(t) \der(\hat{\mu}_i(t), \tau)$, we see a similarity in the index that first showed up in Locatelli et al. with the APT strategy where $B^{APT}_i(t) = \sqrt{T_i(t)} \Delta_i(t) = \sqrt{T_i(t)} |\mu_i - \tau|$ (if we consider the case where $\epsilon = 0$). This format for the strategy's index was inherited by Zhong et al. (2017) for their EVT algorithm which adapts both the term estimating the difference between $\hat{\mu}$ and $\tau$, which I will now refer to as $D_k(t)$, and the confidence term of the current estimate. In Zhong et al., the index is given by $B_i^{EVT}(t) = D_i^{EVT}(t)S^{EVT}_i(t)$, where the difference term $D_i^{EVT}(t) = D_i^{APT}(t) = |\mu_i(t) - \tau|$, but where the confidence term $S_i^{EVT}(t)$ is no longer equal to $S_i^{APT}(t)=\sqrt{T_i(t)}$ but $S_i^{EVT}(t) = \Big(\frac{a}{T_i(t)} + \sqrt{\frac{a}{T_i(t)}}\hat{\sigma}_i(t)\Big)$, and thus depends on the current estimate of the variance, $\hat{\sigma}_i(t)$. Continuing this format of indices, the strategy proposed above has an index that can be written as

$$
B_i(t) = S^{KL}_i(t) D_i^{KL}(t) = T_i(t) \der(\hat{\mu}_i(t), \tau)
$$

If we write the Kullback-Leibler divergence as approximated by a Normal distribution, $\der(\hat{\mu}, \tau) \approx \frac{(\hat{\mu}-\tau)^2}{\tau(1-\tau)}$ or using Pinsker's inequality to bound it as $\der(\hat{\mu}, \tau) \geq 2|\hat{\mu}-\tau|^2$, we see that these approximations lead to the index that is used by the APT strategy. Thus, the motivation behind the likelihood ratio based strategy is to improve upon APT for cases where the approximation fails. We see that in the case of Bernoulli distributions, the two strategies are equivalent for $\tau = 0.5$.

## Upper Bound for KL Strategy

Given the general schema for the index in both the APT and the EVT strategy, the proofs for their respective upper bound on the expected loss share share certain steps. Both proofs build on favorable events which hold with large probability for certain levels of $T$, $T_i$, $H$. In both proofs, the authors bound the number of pulls that a helpful arm receives; that is, an arm that received at least a share of the budget $T$ that is proportional to his contribution to the overall complexity $H$, and which is played in the final round $T$. Both strategies need to show that on the favorable event, after $T$ rounds, every arm has been pulled a suffient amount of times for $\hat{\mu}_i(T)$ to be seperated sufficiently from $\tau$ to make a correct classification of arm $i$. In the design of the favorable event, both strategies can use the fact that the $|\hat{\mu} - \tau|$ term in the index get the following upper bound $|\hat{\Delta}_i(t) - \Delta_i| \leq |\hat{\mu}_i(t)-\mu_i|$ on the $D_i^{APT}(t) = D_i^{EVT}(t) = \hat{\Delta}_i(t)$ part of the index. Given this bound, both proofs use a favorable event on which $\hat{\mu}$ is very close to $\mu$ with large probability.

Given that the Kullback-Leibler divergence is not a metric, and more specifically, the triangle inequality does not hold, the favorable event from the other proofs will not suffice to bound $D_i^{KL}(t)$.

Given the lower bound on $T_k(t)$ for the helpful arm $k$, and the lower and upper bound on $\hat{\Delta}_k(t)$ and $\hat{\Delta}_i(t)$ through the favorable event (compare equation (10) in A.2 of Locatelli et al.), all that remains to show the sufficiently seperated $\hat{\mu}$ from $\tau$ is to lower bound the number of times the not helpful arms are pulled, $T_i(t)$. Locatelli et al. can derive this easily from the other bounds by comparing the two indices $B_k(t)$ and $B_i(t)$. Since at time $t$ the arm $k$ has been pulled, the APT strategy has $B_k^{APT}(t) \leq B_i^{APT}(t)$, since the algorithm pulls the $\arg \min$. Similar holds for the EVT algorithm. And using the Kullback-Leibler distance instead of the Likelihood-ratio, the KL based strategy also minimizes $B_i(t)$ (instead of maximizing $\tilde{B}_i(t)$.

Thus, for the KL-based strategy, consider again for the helpful arm $k$ pulled at time $t$, and some other arm $i$:

$$
B_k(t) \leq B_i(t) \Leftrightarrow T_k(t) \der(\hat{\mu}_k(t), \tau) \leq T_i(t) \der(\hat{\mu}_i(t), \tau)
$$

Starting from here, our goal will be to show that some kind of seperation of the arms holds on the favorable event, where the favorable event is set up such that the above quantities are bounded and the seperation condition can be checked. On the way, the favorable event will have an impact on how the complexity $H$ will be defined for this problem. In the end, we want to derive an upper bound of rate $\exp(-\frac{T}{H})$ on the error probability.

### 2017-07-30 LR_Theory/LR_theory.tex
Start proof of LR strategy

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={LR Theory},
            pdfauthor={Tim Radtke},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{LR Theory}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Tim Radtke}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \date{}
  \predate{}\postdate{}

\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{bbm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newcommand{\KL}{\,\text{KL}}
\newcommand{\der}{\,\text{d}}

\begin{document}
\maketitle

\section{Kullback-Leibler Divergence
Strategy}\label{kullback-leibler-divergence-strategy}

We start with a definition of the Likelihood Ratio. See for example
Example 6 in \url{http://math.arizona.edu/~jwatkins/s-lrt.pdf}.

In our strategy, we will have at time \(t\) a sample of observations for
arm \(i\) of size \(T_i(t)\): \(\mathbb{x} = x_1, ..., x_{T_i(t)}\).
Since we are only considering Bernoulli distributions at this point, the
Likelihood for a sample from distribution \(Ber(\mu)\) is given by

\[ 
L(\mu|\mathbb{x}) = (1-\mu)^{T_i(t) - \sum_{s = 1}^{T_i(t)} x_s} \mu^{\sum_{s = 1}^{T_i(t)} x_s}
\]

We want to test whether the sample \(\mathbb{x}\) with maximum
likelihood estimate (\(H_1: \mu = \hat{\mu}\)) is actually different
from the standard hypothesis that it is equal to the threshold \(\tau\)
(\(H_0: \mu = \tau\)). To test this, we can use the likelihood ratio:

\[
\Lambda = \frac{L(\tau|\mathbb{x})}{L(\hat{\mu}|\mathbb{x})} = \frac{\tau^{\hat{\mu}T_i(t)}(1-\tau)^{(1-\hat{\mu})T_i(t)} }{\hat{\mu}^{\hat{\mu}T_i(t)}(1-\hat{\mu})^{(1-\hat{\mu})T_i(t)}}
\] If the likelihood ratio is large, then it's quite likely that the
sample was generated by a Bernoulli distribution with parameter
\(\tau\). If the ratio is small, then the maximum likelihood estimate is
very different from the threshold. The statistic should be smaller than
1 given that we compare to the maximum likelihood estimate.

In an adaptive sampling strategy that is based on this ratio, it is
natural to pull the arm that currently maximizes the ratio (an arm with
distribution close to \(\tau\)). Even if the true parameter \(\mu\) is
close to \(\tau\), the ratio will increase over time as \(T_i(t)\)
increases. Thus given two distributions with the same maximum likelihood
estimate, the strategy will pull the arm that has a smaller \(T_i(t)\).

Thus our strategy could be to pull arm \(i^*\) at time \(t+1\) that
maximizes \(\tilde{B}_i(t) = \Lambda_i\). Of course,
\(\arg \max_i \Lambda_i(t) = \arg \min_i -\log(\Lambda_i(t))\). And so
an equivalent strategy is to pull
\(i^*(t) = \arg \min_i -\log(\Lambda_i(t))\). We now show that this is
equivalent to \(i^*(t) = \arg \min_i T_i(t)\hat{\KL}(\hat{\mu}||\tau)\).

We have

\begin{align*}
-\log(\Lambda_i(t)) & = \hat{\mu}T_i(t) \log(\frac{\hat{\mu}_i(t)}{\tau}) + (1-\hat{\mu})T_i(t) \log(\frac{1-\hat{\mu}_i(t)}{1-\tau}) \\
& = T_i(t) [\hat{\mu}_i(t) \log(\frac{\hat{\mu}_i(t)}{\tau}) + (1-\hat{\mu}_i(t)) \log(\frac{1-\hat{\mu}_i(t)}{1-\tau})] \\
& = T_i(t) \der(\hat{\mu}_i(t), \tau) \\
& = B_i(t)
\end{align*}

This notation of the index will prove useful in theoretical derivations,
while the likelihood ratio is advantageous in the implementation of the
algorithm, as it can be computed even when \(\hat{\mu}=0\) or
\(\hat{\mu}=1\), which will always occur in the beginning of the
sampling.

\subsection{Comparison with Other
Indices}\label{comparison-with-other-indices}

If we consider \(B_i^{APT}(t) = T_i(t) \der(\hat{\mu}_i(t), \tau)\), we
see a similarity in the index that first showed up in Locatelli et al.
with the APT strategy where
\(B^{APT}_i(t) = \sqrt{T_i(t)} \Delta_i(t) = \sqrt{T_i(t)} |\mu_i - \tau|\)
(if we consider the case where \(\epsilon = 0\)). This format for the
strategy's index was inherited by Zhong et al. (2017) for their EVT
algorithm which adapts both the term estimating the difference between
\(\hat{\mu}\) and \(\tau\), which I will now refer to as \(D_k(t)\), and
the confidence term of the current estimate. In Zhong et al., the index
is given by \(B_i^{EVT}(t) = D_i^{EVT}(t)S^{EVT}_i(t)\), where the
difference term \(D_i^{EVT}(t) = D_i^{APT}(t) = |\mu_i(t) - \tau|\), but
where the confidence term \(S_i^{EVT}(t)\) is no longer equal to
\(S_i^{APT}(t)=\sqrt{T_i(t)}\) but
\(S_i^{EVT}(t) = \Big(\frac{a}{T_i(t)} + \sqrt{\frac{a}{T_i(t)}}\hat{\sigma}_i(t)\Big)\),
and thus depends on the current estimate of the variance,
\(\hat{\sigma}_i(t)\). Continuing this format of indices, the strategy
proposed above has an index that can be written as

\[
B_i(t) = S^{KL}_i(t) D_i^{KL}(t) = T_i(t) \der(\hat{\mu}_i(t), \tau)
\]

If we write the Kullback-Leibler divergence as approximated by a Normal
distribution,
\(\der(\hat{\mu}, \tau) \approx \frac{(\hat{\mu}-\tau)^2}{\tau(1-\tau)}\)
or using Pinsker's inequality to bound it as
\(\der(\hat{\mu}, \tau) \geq 2|\hat{\mu}-\tau|^2\), we see that these
approximations lead to the index that is used by the APT strategy. Thus,
the motivation behind the likelihood ratio based strategy is to improve
upon APT for cases where the approximation fails. We see that in the
case of Bernoulli distributions, the two strategies are equivalent for
\(\tau = 0.5\).

\subsection{Upper Bound for KL
Strategy}\label{upper-bound-for-kl-strategy}

Given the general schema for the index in both the APT and the EVT
strategy, the proofs for their respective upper bound on the expected
loss share share certain steps. Both proofs build on favorable events
which hold with large probability for certain levels of \(T\), \(T_i\),
\(H\). In both proofs, the authors bound the number of pulls that a
helpful arm receives; that is, an arm that received at least a share of
the budget \(T\) that is proportional to his contribution to the overall
complexity \(H\), and which is played in the final round \(T\). Both
strategies need to show that on the favorable event, after \(T\) rounds,
every arm has been pulled a suffient amount of times for
\(\hat{\mu}_i(T)\) to be seperated sufficiently from \(\tau\) to make a
correct classification of arm \(i\). In the design of the favorable
event, both strategies can use the fact that the \(|\hat{\mu} - \tau|\)
term in the index get the following upper bound
\(|\hat{\Delta}_i(t) - \Delta_i| \leq |\hat{\mu}_i(t)-\mu_i|\) on the
\(D_i^{APT}(t) = D_i^{EVT}(t) = \hat{\Delta}_i(t)\) part of the index.
Given this bound, both proofs use a favorable event on which
\(\hat{\mu}\) is very close to \(\mu\) with large probability.

Given that the Kullback-Leibler divergence is not a metric, and more
specifically, the triangle inequality does not hold, the favorable event
from the other proofs will not suffice to bound \(D_i^{KL}(t)\).

Given the lower bound on \(T_k(t)\) for the helpful arm \(k\), and the
lower and upper bound on \(\hat{\Delta}_k(t)\) and \(\hat{\Delta}_i(t)\)
through the favorable event (compare equation (10) in A.2 of Locatelli
et al.), all that remains to show the sufficiently seperated
\(\hat{\mu}\) from \(\tau\) is to lower bound the number of times the
not helpful arms are pulled, \(T_i(t)\). Locatelli et al. can derive
this easily from the other bounds by comparing the two indices
\(B_k(t)\) and \(B_i(t)\). Since at time \(t\) the arm \(k\) has been
pulled, the APT strategy has \(B_k^{APT}(t) \leq B_i^{APT}(t)\), since
the algorithm pulls the \(\arg \min\). Similar holds for the EVT
algorithm. And using the Kullback-Leibler distance instead of the
Likelihood-ratio, the KL based strategy also minimizes \(B_i(t)\)
(instead of maximizing \(\tilde{B}_i(t)\).

Thus, for the KL-based strategy, consider again for the helpful arm
\(k\) pulled at time \(t\), and some other arm \(i\):

\[
B_k(t) \leq B_i(t) \Leftrightarrow T_k(t) \der(\hat{\mu}_k(t), \tau) \leq T_i(t) \der(\hat{\mu}_i(t), \tau)
\]

Starting from here, our goal will be to show that some kind of
seperation of the arms holds on the favorable event, where the favorable
event is set up such that the above quantities are bounded and the
seperation condition can be checked. On the way, the favorable event
will have an impact on how the complexity \(H\) will be defined for this
problem. In the end, we want to derive an upper bound of rate
\(\exp(-\frac{T}{H})\) on the error probability.

\end{document}

### 2017-07-30 synthetic_experiments/cal_algs_verylong_7_no_tau.R

@@ -95,12 +95,12 @@ save(loc7nt_comp_APT_10000, file = paste0(current_path,
 ########################################################################
 
 loc7nt_BUCB_horizon_10000 <- para_bandit_sim_bucb(data = data_list7_10000, 
-                                               rounds = 10000, 
-                                               rate = "inverse_horizon",
-                                               tau = tau_loc7nt, 
-                                               epsilon = epsilon_loc7nt, 
-                                               alpha = tau_loc7nt, 
-                                               beta = 1-tau_loc7nt)
+                                                  rounds = 10000, 
+                                                  rate = "inverse_horizon",
+                                                  tau = tau_loc7nt, 
+                                                  epsilon = epsilon_loc7nt, 
+                                                  alpha = tau_loc7nt, 
+                                                  beta = 1-tau_loc7nt)
 save(loc7nt_BUCB_horizon_10000, 
      file = paste0(current_path, "loc7nt_BUCB_horizon_10000.Rda"))
 loc7nt_comp_BUCB_horizon_10000 <- compare_to_ground_truth(mean_loc7nt, 
@@ -142,6 +142,7 @@ save(loc7nt_comp_AugUCB_10000, file = paste0(current_path,
 load(file = paste0(current_path, "loc7nt_comp_UNIFORM_10000.Rda"))
 load(file = paste0(current_path, "loc7nt_comp_APT_10000.Rda"))
 load(file = paste0(current_path, "loc7nt_comp_LR_10000.Rda"))
+load(file = paste0(current_path, "loc7nt_comp_BUCB_horizon_10000.Rda"))
 load(file = paste0(current_path, "loc7nt_comp_AugUCB_10000.Rda"))
 
 plot(c(0,10000), c(0, -5), type = "n")

### 2017-08-06 LR_Theory/LR_theory.Rmd
Add Likelihood Ratio based algorithms

@@
 
-In our strategy, we will have at time $t$ a sample of observations for arm $i$ of size $T_i(t)$: $\mathbb{x} = x_1, ..., x_{T_i(t)}$.
+In our strategy, we will have at time $t$ a sample of observations for arm $i$ of size $T_i(t)$: $X = x_1, ..., x_{T_i(t)}$.
 Since we are only considering Bernoulli distributions at this point, the Likelihood for a sample from distribution $Ber(\mu)$ is given by
@@
 $$ 
-L(\mu|\mathbb{x}) = (1-\mu)^{T_i(t) - \sum_{s = 1}^{T_i(t)} x_s} \mu^{\sum_{s = 1}^{T_i(t)} x_s}
+L(\mu|X) = (1-\mu)^{T_i(t) - \sum_{s = 1}^{T_i(t)} x_s} \mu^{\sum_{s = 1}^{T_i(t)} x_s}
 $$
 
-We want to test whether the sample $\mathbb{x}$ with maximum likelihood estimate ($H_1: \mu = \hat{\mu}$) is actually different from the standard hypothesis that it is equal to the threshold $\tau$ ($H_0: \mu = \tau$).
+We want to test whether the sample $X$ with maximum likelihood estimate ($H_1: \mu = \hat{\mu}$) is actually different from the standard hypothesis that it is equal to the threshold $\tau$ ($H_0: \mu = \tau$).
 To test this, we can use the likelihood ratio:
@@
 $$
-\Lambda = \frac{L(\tau|\mathbb{x})}{L(\hat{\mu}|\mathbb{x})} = \frac{\tau^{\hat{\mu}T_i(t)}(1-\tau)^{(1-\hat{\mu})T_i(t)} }{\hat{\mu}^{\hat{\mu}T_i(t)}(1-\hat{\mu})^{(1-\hat{\mu})T_i(t)}}
+\Lambda = \frac{L(\tau|X)}{L(\hat{\mu}|X)} = \frac{\tau^{\hat{\mu}T_i(t)}(1-\tau)^{(1-\hat{\mu})T_i(t)} }{\hat{\mu}^{\hat{\mu}T_i(t)}(1-\hat{\mu})^{(1-\hat{\mu})T_i(t)}}
 $$
+
 If the likelihood ratio is large, then it's quite likely that the sample was generated by a Bernoulli distribution with parameter $\tau$.
@@
 
-If we consider $B_i^{APT}(t) = T_i(t) \der(\hat{\mu}_i(t), \tau)$, we see a similarity in the index that first showed up in Locatelli et al.
-with the APT strategy where $B^{APT}_i(t) = \sqrt{T_i(t)} \Delta_i(t) = \sqrt{T_i(t)} |\mu_i - \tau|$ (if we consider the case where $\epsilon = 0$).
-This format for the strategy's index was inherited by Zhong et al.
-(2017) for their EVT algorithm which adapts both the term estimating the difference between $\hat{\mu}$ and $\tau$, which I will now refer to as $D_k(t)$, and the confidence term of the current estimate.
+If we consider $B_i^{KL}(t) = T_i(t) \der(\hat{\mu}_i(t), \tau)$, we see a similarity to the index that first showed up in Locatelli et al.
+(2016) with the APT strategy where $B^{APT}_i(t) = \sqrt{T_i(t)} \Delta_i(t) = \sqrt{T_i(t)} |\mu_i(t) - \tau|$ (if we consider the case where $\epsilon = 0$).
+This format for the strategy's index was inherited by [Zhong et al.
+(2017)](https://arxiv.org/pdf/1704.04567.pdf) for their EVT algorithm which adapts both the term estimating the difference between $\hat{\mu}$ and $\tau$, which I will now refer to as $D_k(t)$, and the confidence term of the current estimate, which they call $S_i^{EVT}(t)$.
 In Zhong et al., the index is given by $B_i^{EVT}(t) = D_i^{EVT}(t)S^{EVT}_i(t)$, where the difference term $D_i^{EVT}(t) = D_i^{APT}(t) = |\mu_i(t) - \tau|$, but where the confidence term $S_i^{EVT}(t)$ is no longer equal to $S_i^{APT}(t)=\sqrt{T_i(t)}$ but $S_i^{EVT}(t) = \Big(\frac{a}{T_i(t)} + \sqrt{\frac{a}{T_i(t)}}\hat{\sigma}_i(t)\Big)$, and thus depends on the current estimate of the variance, $\hat{\sigma}_i(t)$.
@@
 
-Given the general schema for the index in both the APT and the EVT strategy, the proofs for their respective upper bound on the expected loss share share certain steps.
+Given the general schema for the index in both the APT and the EVT strategy, the proofs for their respective upper bound on the expected loss share certain steps.
 Both proofs build on favorable events which hold with large probability for certain levels of $T$, $T_i$, $H$.
@@
 
-Given the lower bound on $T_k(t)$ for the helpful arm $k$, and the lower and upper bound on $\hat{\Delta}_k(t)$ and $\hat{\Delta}_i(t)$ through the favorable event (compare equation (10) in A.2 of Locatelli et al.), all that remains to show the sufficiently seperated $\hat{\mu}$ from $\tau$ is to lower bound the number of times the not helpful arms are pulled, $T_i(t)$.
+Given the lower bound on $T_k(t)$ for the helpful arm $k$, and the lower and upper bound on $\hat{\Delta}_k(t)$ and $\hat{\Delta}_i(t)$ through the favorable event (compare equation (10) in A.2 of Locatelli et al., 2016), all that remains to show the sufficiently seperated $\hat{\mu}$ from $\tau$ is to lower bound the number of times the not helpful arms are pulled, $T_i(t)$.
 Locatelli et al.
@@
 In the end, we want to derive an upper bound of rate $\exp(-\frac{T}{H})$ on the error probability.
+
+To achieve correct seperation at the end of the algorithm, [Zhong et al.
+(2017)](https://arxiv.org/pdf/1704.04567.pdf) require that after the last round $T$, the sample means $\hat{\mu}$ of the arms are closer to the true mean $\mu$ of the distribution than to the threshold $\tau$:
+
+$$
+|\hat{\mu}_i(T_i(T)) - \mu| \leq \frac{\Delta_i}{2}
+$$
+
+More explicitly, for an arm below the threshold, $\mu_i < \tau$, they demand $\hat{\mu}_i(T_i(T)) \geq \mu_i - \frac{\mu_i-\tau}{2}$.
+On the other hand, for an arm above the threshold, $\mu_i \geq \tau$, they demand $\hat{\mu}_i(T_i(T)) \leq \mu_i - \frac{\mu_i-\tau}{2}$.
+
+Based on a similar idea, the fixed-confidence KL-LUCB algorithm introduced in [Kaufmann and Kalyanakrishnan](http://proceedings.mlr.press/v30/Kaufmann13.pdf) (2013) for the Top-$m$ problem employs a stopping rule that checks whether the smallest lower bound among the currently best $m$ algorithms is larger than the largest upper bound of the other arms that currently are not among the $m$ best.
+If the lower bound is larger than the upper bound, the two sets of arms are considered to be sufficiently seperated; it is unlikely, that there are two arms that are classified into the wrong set (compare with Proposition 1, [Kaufmann and Kalyanakrishnan](http://proceedings.mlr.press/v30/Kaufmann13.pdf), 2013).
+
+Thus a simple demand that we can pose for our strategy is the one from Zhong et al. (2017), which directly translates into
+
+$$
+\der(\hat{\mu}_i(T_i(T)), \tau) \geq \der(\mu_i +\frac{\tau-\mu_i}{2}, \tau)
+$$
+
+for arms with mean below the threshold, $\mu_i < \tau$. On the other hand, for arms with mean above the threshold, $\mu_i > \tau$, we demand
+
+$$
+\der(\hat{\mu}_i(T_i(T)), \tau) \geq \der(\mu_i - \frac{\mu_i - \tau}{2}, \tau).
+$$
+
+These two conditions are equivalent to the conditions given in [Zhong et al.
+(2017)](https://arxiv.org/pdf/1704.04567.pdf) due to the monotonicity of the KL divergence.
+If we could check whether these conditions hold on whatever favorable event we use, that would be a very convenient check.
+
+UPDATE: This translation into the Kullback-Leibler distance does not work as easily, because the above conditions might hold even if $\mu < \tau < \hat{\mu}$, for example.
+
+### The Favorable Event
+
+Intuitively, it should be an event of large probability that $|\der(\mu,\tau) - \der(\hat{\mu},\tau)|<\epsilon$, given that $|\mu - \hat{\mu}|<\delta$ is likely.
+Also since we know that $\der(\hat{\mu}(t), \mu) \leq \epsilon$ is likely for large $t$ following for example Proposition 1 in [Cappé et al.
+(2013)](https://projecteuclid.org/download/pdfview_1/euclid.aos/1375362558).
+Additionally we know that $\der(\hat{\mu}, \tau) = \der(\mu, \tau)$ for $\hat{mu} = \mu$, however otherwise the inequality  $\der(\hat{\mu}, \tau) \geq \der(\hat{\mu}, \mu) + \der(\mu, \tau)$ only holds for $\mu \in [\hat{\mu}, \tau]$ (or $\mu \in [\tau, \hat{\mu}]$).
+
+Instead, we will try to base our favorable event on a variant of Lemma 1 in [Kaufmann and Kalyanakrishnan](http://proceedings.mlr.press/v30/Kaufmann13.pdf) (2013), which states the following.
+
+Let $T \geq 1$ be an integer. Let $\delta > 0$, $\gamma > 0$, and $c \in (0,1)$ be such that $mu_a \neq \tau$.
+
+$$
+\sum_{t=1}^T \mathbb{P} \Big(a = u_t \lor a = l_t, T_a(t) > \left \lceil{\frac{\gamma}{d^*(\mu_a,\tau)}}\right \rceil, T_a(t) d(\hat{\mu}_a, \tau) \leq \gamma \Big) \leq \frac{exp(-\gamma)}{d^*(\mu_a, \tau)}
+$$
+
+Given Lemma 2 in the same paper, as well as the proof of Lemma 1 in Appendix C of the paper (last inequality), the same bound should hold if we write the event without the lower and upper bounds $u_t$ and $l_t$ of arm $a$:
+
+$$
+\sum_{t=1}^T \mathbb{P} \Big(T_a(t) > \left \lceil{\frac{\gamma}{d^*(\mu_a,\tau)}}\right \rceil, T_a(t) d(\hat{\mu}_a, \tau) \leq \gamma \Big) \leq \frac{exp(-\gamma)}{d^*(\mu_a, \tau)}
+$$
+
+Thus on the favorable event for a single arm $a$, we have that
+
+$$
+T_a(t) -1 \geq \frac{\gamma}{d^*(\mu_a, \tau)} \qquad \text{and} \qquad d(\hat{\mu}_a, \tau) > \frac{\gamma}{T_a(t)}
+$$
+
+### Characterization of some helpful arm
+
+Locatelli et al.
+(2016) show for arm $k$ that $T_k(t) \geq T_k(T) - 1 \geq \frac{T}{2H_{APT}\Delta^2_{APT,k}}$.
+We expect (CHECK THIS) that a similar condition holds for our algorithm, however with a different $H_{KL}$ and $h_{KL,k}$, $H_{KL} = \sum_{i=1}^K h_{KL,i}$, $h_{APT,k} = 1/(|\hat{\mu}-\tau|+\epsilon)^2$; but where the helpful arm $k$ still has at least as many pulls as would be its share of the budget given its contribution to the overall complexity.
+
+Now, we can go ahead and plug the favorable event directly into $B_k(t)$ (on the favorable event, it is likely that $\gamma < T_a(t) d(\hat{\mu}_a, \tau)$):
+
+$$
+B_k(t) \leq B_i(t) \Leftrightarrow \gamma < T_k(t) \der(\hat{\mu}_k(t), \tau) \leq T_i(t) \der(\hat{\mu}_i(t), \tau) 
+$$
+
+To check whether this makes sense, we need to choose a value for $\gamma$, such that the second part of the favorable event is fulfilled.
+Given the lower bound for the helpful arm, we can define the complexity in terms of the Chernoff information used in [Kaufmann and Kalyanakrishnan](http://proceedings.mlr.press/v30/Kaufmann13.pdf) (2013).
+We write
+
+$$
+H_{KL} = \sum_{i=1}^K \frac{1}{d^*(\mu_i, \tau)}
+$$
+
+For two Bernoullis, the Chernoff information is defined as $d^*(\mu_i, \tau) = d(z^*,\mu_i) = d(z^*, \tau)$ (compare [Kaufmann and Kalyanakrishnan](http://proceedings.mlr.press/v30/Kaufmann13.pdf), 2013).
+For the helpful arm we thus get
+
+$$
+T_k(t) \geq T_k(T) -1 \geq \frac{T}{2 H_{KL} d^*(\mu_i, \tau)}
+$$
+such that by choosing $\gamma = \frac{T}{2H_{KL}}$ the favorable event $T_a(t) -1 > \frac{\gamma}{d^*(\mu_a, \tau)}$ works for the helpful arm:
+
+$$
+\gamma = \frac{T}{2H_{KL}} \leq T_k(t) \der(\hat{\mu}_k(t), \tau) \leq T_i(t) \der(\hat{\mu}_i(t), \tau) 
+$$
+
+Given that we can conclude the proof successfully, this choice of the exploration exponent $\gamma$ already implies that the budget should be rather large if $H_{KL}$ is large.
+But it also implies that the favorable event occurs at the rate that we demanded upfront, since then $exp(-\gamma) = exp(-T/(2H))$.
+
+### Problem
+
+At this point, however, I am stuck since the favorable event does not give an upper bound on the RHS of the equation.
+Thus I don't have a way of bounding $T_i(t)$.
+I tried to approximate the KL-divergence $d(\hat{\mu}_k(t), \tau) \leq \frac{(\hat{\mu}-\tau)^2}{\tau(1-\tau)}$ to get a bound similarly as in Locatelli et al.
+(2016) using the favorable event mentioned there; this gave me indeed a lower bound on $T_i(t)$ similar to the one in that paper.
+However, given that the favorable event bounds the KL divergence from below as $\frac{\gamma}{T_a(t)} < d(\hat{\mu}_a, \tau)$, the lower bound for $T_i(t)$ did not prove useful.
+Instead, it might have showed me another problem.
+At first I believed it would suffice to show that $d(\hat{\mu}_a, \tau)$ is larger than e.g.
+$d^*(\mu_a, \tau)$ on the favorable event.
+But in theory, this could also hold if $\mu_a < \tau$ and $\tau < \hat{\mu}_a$.
+So a check against that probably needs to be included in the favorable event as well.
+This might be possible with some proposition from the [KL-UCB paper by Cappé et al.
+(2013)](https://projecteuclid.org/download/pdfview_1/euclid.aos/1375362558), or a self-normalized inequality by [Garivier and Cappé (2011, Theorem 10)](https://arxiv.org/pdf/1102.2490.pdf).
+
+In general, I'm simply wondering which inequality might suffice to bound $B_k(t) < B_i(t)$.
+I believed that the one from [Kaufmann and Kalyanakrishnan](http://proceedings.mlr.press/v30/Kaufmann13.pdf) sufficed, but in their paper it is combined with a nice separation condition stemming from the lower and upper bounds, which is integrated into the stopping rule of the fixed-*confidence* algorithm (where the separation thus has to hold).
+
+## Experiments
+
+First, we again show the result of experiment 3.
+This time around, however, we set $\epsilon = 0$ as recommended by Andrea.
+Also, we move the two arms that previously have been inside the $\epsilon$-interval a little away from the threshold $\tau = 0.5$ to remove the need for a very large sample size.
+The likelihood-ratio based algorithm is now able to show it's advantage.
+
+The setup is as follows:
+
+```{r, message = FALSE, echo = FALSE}
+get_APT_complexity <- function(means, tau, epsilon) {
+  res <- vector(length = length(means))
+  for(i in 1:length(means)) {
+    res[i] <- (abs(means[i] - tau) + epsilon)^2
+  }
+  sum(1/res)
+}
+
+mean_loc6nt <- c(0.001, 0.005, 0.01, 0.015,
+                 0.04, 0.06,
+                 0.085, 0.09, 0.095, 0.099)
+tau_loc6nt <- 0.05
+epsilon_loc6nt <- 0
+H_loc6nt <- get_APT_complexity(mean_loc6nt, tau_loc6nt, epsilon_loc6nt)
+
+print(mean_loc6nt)
+
+plot(mean_loc6nt, rep(1,10), main = paste0("APT Complexity of ", round(H_loc6nt,2)))
+abline(v=tau_loc6nt)
+```
+
+```{r, echo = FALSE, message = FALSE}
+library(dplyr)
+library(ggplot2)
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
+
+load(paste0(current_path, "/loc6nt_comp_BUCB_horizon_7000.Rda"))
+load(paste0(current_path, "/loc6nt_comp_UNIFORM_7000.Rda"))
+load(paste0(current_path, "/loc6nt_comp_APT_7000.Rda"))
+load(paste0(current_path, "/loc6nt_comp_LR_7000.Rda"))
+
+alg_names <- c(rep(c("Uniform", "APT", "B-UCB", "LR"), each = 6991))
+index <- c(rep(10:7000, times = 4))
+alg_res <- log(c(loc6nt_comp_UNIFORM_7000, loc6nt_comp_APT_7000, loc6nt_comp_BUCB_horizon_7000, loc6nt_comp_LR_7000))
+loc3_comp_res <- data.frame(index = index, names = alg_names, 
+                            results = alg_res)
+ggplot(loc3_comp_res, aes(x = index, y = alg_res)) + geom_line(aes(group = alg_names, color = alg_names)) + geom_hline(aes(yintercept = log(0.1)), linetype = 2) + geom_hline(aes(yintercept = log(0.01)), linetype = 2) +
+  labs(title = "Experiment 3 Results", subtitle = paste0("APT Complexity of ", round(H_loc6nt),  ". Horizontal lines at 0.1 and 0.01."), y = "log(Error)")
+```
+
+### Experiment 2
+
+This is a new setup in which the observations are set in more or less the same distance from each other on a log10 scale.
+Again, $\epsilon = 0$.
+We choose a very small threshold with $\tau = 0.01$.
+Also note that we have increased the budget to $T=10000$, while the previous experiment had $T=7000$.
+
+```{r, message = FALSE, echo = FALSE}
+get_APT_complexity <- function(means, tau, epsilon) {
+  res <- vector(length = length(means))
+  for(i in 1:length(means)) {
+    res[i] <- (abs(means[i] - tau) + epsilon)^2
+  }
+  sum(1/res)
+}
+
+mean_loc7nt <- c(10^-4, 10^-3.5, 10^-3.25, 10^-3, 
+                 10^-2.75, 10^-2.5, 10^-2.25, 10^-1.85, 10^-1.75,
+                 10^-1.5, 10^-1)
+tau_loc7nt <- 10^-2
+epsilon_loc7nt <- 0
+H_loc7nt <- get_APT_complexity(mean_loc7nt, tau_loc7nt, epsilon_loc7nt)
+
+print(round(mean_loc7nt,5))
+
+plot(log10(mean_loc7nt), rep(1,11), main = paste0("Complexity of ", round(H_loc7nt,2)), ylab = "", xlab = "log10(mean)")
+abline(v=log10(tau_loc7nt))
+```
+
+```{r, echo = FALSE, message = FALSE}
+library(dplyr)
+library(ggplot2)
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
+
+load(paste0(current_path, "/loc7nt_comp_BUCB_horizon_10000.Rda"))
+load(paste0(current_path, "/loc7nt_comp_UNIFORM_10000.Rda"))
+load(paste0(current_path, "/loc7nt_comp_APT_10000.Rda"))
+load(paste0(current_path, "/loc7nt_comp_LR_10000.Rda"))
+load(paste0(current_path, "/loc7nt_comp_AugUCB_10000.Rda"))
+
+alg_names <- c(rep(c("Uniform", "APT", "B-UCB", "LR", "AugUCB"), each = 9990))
+index <- c(rep(11:10000, times = 5))
+alg_res <- log(c(loc7nt_comp_UNIFORM_10000, loc7nt_comp_APT_10000, loc7nt_comp_BUCB_horizon_10000, loc7nt_comp_LR_10000, loc7nt_comp_AugUCB_10000))
+loc3_comp_res <- data.frame(index = index, names = alg_names, 
+                            results = alg_res)
+ggplot(loc3_comp_res, aes(x = index, y = alg_res)) + geom_line(aes(group = alg_names, color = alg_names)) + geom_hline(aes(yintercept = log(0.1)), linetype = 2) + geom_hline(aes(yintercept = log(0.01)), linetype = 2) +
+  labs(title = "Experiment Results", subtitle = paste0("APT Complexity of ", round(H_loc7nt),  ". Horizontal lines at 0.1 and 0.01."), y = "log(Error)")
+```

### 2017-08-06 LR_Theory/LR_theory.tex
Add Likelihood Ratio based algorithms

@@
 In our strategy, we will have at time \(t\) a sample of observations for
-arm \(i\) of size \(T_i(t)\): \(\mathbb{x} = x_1, ..., x_{T_i(t)}\).
-Since we are only considering Bernoulli distributions at this point, the
-Likelihood for a sample from distribution \(Ber(\mu)\) is given by
+arm \(i\) of size \(T_i(t)\): \(X = x_1, ..., x_{T_i(t)}\). Since we are
+only considering Bernoulli distributions at this point, the Likelihood
+for a sample from distribution \(Ber(\mu)\) is given by
 
 \[ 
-L(\mu|\mathbb{x}) = (1-\mu)^{T_i(t) - \sum_{s = 1}^{T_i(t)} x_s} \mu^{\sum_{s = 1}^{T_i(t)} x_s}
+L(\mu|X) = (1-\mu)^{T_i(t) - \sum_{s = 1}^{T_i(t)} x_s} \mu^{\sum_{s = 1}^{T_i(t)} x_s}
 \]
 
-We want to test whether the sample \(\mathbb{x}\) with maximum
-likelihood estimate (\(H_1: \mu = \hat{\mu}\)) is actually different
-from the standard hypothesis that it is equal to the threshold \(\tau\)
+We want to test whether the sample \(X\) with maximum likelihood
+estimate (\(H_1: \mu = \hat{\mu}\)) is actually different from the
+standard hypothesis that it is equal to the threshold \(\tau\)
 (\(H_0: \mu = \tau\)). To test this, we can use the likelihood ratio:
@@
 \[
-\Lambda = \frac{L(\tau|\mathbb{x})}{L(\hat{\mu}|\mathbb{x})} = \frac{\tau^{\hat{\mu}T_i(t)}(1-\tau)^{(1-\hat{\mu})T_i(t)} }{\hat{\mu}^{\hat{\mu}T_i(t)}(1-\hat{\mu})^{(1-\hat{\mu})T_i(t)}}
-\] If the likelihood ratio is large, then it's quite likely that the
-sample was generated by a Bernoulli distribution with parameter
-\(\tau\). If the ratio is small, then the maximum likelihood estimate is
-very different from the threshold. The statistic should be smaller than
-1 given that we compare to the maximum likelihood estimate.
+\Lambda = \frac{L(\tau|X)}{L(\hat{\mu}|X)} = \frac{\tau^{\hat{\mu}T_i(t)}(1-\tau)^{(1-\hat{\mu})T_i(t)} }{\hat{\mu}^{\hat{\mu}T_i(t)}(1-\hat{\mu})^{(1-\hat{\mu})T_i(t)}}
+\]
+
+If the likelihood ratio is large, then it's quite likely that the sample
+was generated by a Bernoulli distribution with parameter \(\tau\). If
+the ratio is small, then the maximum likelihood estimate is very
+different from the threshold. The statistic should be smaller than 1
+given that we compare to the maximum likelihood estimate.
 
@@
 
-If we consider \(B_i^{APT}(t) = T_i(t) \der(\hat{\mu}_i(t), \tau)\), we
-see a similarity in the index that first showed up in Locatelli et al.
-with the APT strategy where
-\(B^{APT}_i(t) = \sqrt{T_i(t)} \Delta_i(t) = \sqrt{T_i(t)} |\mu_i - \tau|\)
+If we consider \(B_i^{KL}(t) = T_i(t) \der(\hat{\mu}_i(t), \tau)\), we
+see a similarity to the index that first showed up in Locatelli et al.
+(2016) with the APT strategy where
+\(B^{APT}_i(t) = \sqrt{T_i(t)} \Delta_i(t) = \sqrt{T_i(t)} |\mu_i(t) - \tau|\)
 (if we consider the case where \(\epsilon = 0\)). This format for the
-strategy's index was inherited by Zhong et al. (2017) for their EVT
-algorithm which adapts both the term estimating the difference between
-\(\hat{\mu}\) and \(\tau\), which I will now refer to as \(D_k(t)\), and
-the confidence term of the current estimate. In Zhong et al., the index
-is given by \(B_i^{EVT}(t) = D_i^{EVT}(t)S^{EVT}_i(t)\), where the
-difference term \(D_i^{EVT}(t) = D_i^{APT}(t) = |\mu_i(t) - \tau|\), but
-where the confidence term \(S_i^{EVT}(t)\) is no longer equal to
+strategy's index was inherited by
+\href{https://arxiv.org/pdf/1704.04567.pdf}{Zhong et al. (2017)} for
+their EVT algorithm which adapts both the term estimating the difference
+between \(\hat{\mu}\) and \(\tau\), which I will now refer to as
+\(D_k(t)\), and the confidence term of the current estimate, which they
+call \(S_i^{EVT}(t)\). In Zhong et al., the index is given by
+\(B_i^{EVT}(t) = D_i^{EVT}(t)S^{EVT}_i(t)\), where the difference term
+\(D_i^{EVT}(t) = D_i^{APT}(t) = |\mu_i(t) - \tau|\), but where the
+confidence term \(S_i^{EVT}(t)\) is no longer equal to
 \(S_i^{APT}(t)=\sqrt{T_i(t)}\) but
@@
 strategy, the proofs for their respective upper bound on the expected
-loss share share certain steps. Both proofs build on favorable events
-which hold with large probability for certain levels of \(T\), \(T_i\),
-\(H\). In both proofs, the authors bound the number of pulls that a
-helpful arm receives; that is, an arm that received at least a share of
-the budget \(T\) that is proportional to his contribution to the overall
-complexity \(H\), and which is played in the final round \(T\). Both
-strategies need to show that on the favorable event, after \(T\) rounds,
-every arm has been pulled a suffient amount of times for
-\(\hat{\mu}_i(T)\) to be seperated sufficiently from \(\tau\) to make a
-correct classification of arm \(i\). In the design of the favorable
-event, both strategies can use the fact that the \(|\hat{\mu} - \tau|\)
-term in the index get the following upper bound
+loss share certain steps. Both proofs build on favorable events which
+hold with large probability for certain levels of \(T\), \(T_i\), \(H\).
+In both proofs, the authors bound the number of pulls that a helpful arm
+receives; that is, an arm that received at least a share of the budget
+\(T\) that is proportional to his contribution to the overall complexity
+\(H\), and which is played in the final round \(T\). Both strategies
+need to show that on the favorable event, after \(T\) rounds, every arm
+has been pulled a suffient amount of times for \(\hat{\mu}_i(T)\) to be
+seperated sufficiently from \(\tau\) to make a correct classification of
+arm \(i\). In the design of the favorable event, both strategies can use
+the fact that the \(|\hat{\mu} - \tau|\) term in the index get the
+following upper bound
 \(|\hat{\Delta}_i(t) - \Delta_i| \leq |\hat{\mu}_i(t)-\mu_i|\) on the
@@
 through the favorable event (compare equation (10) in A.2 of Locatelli
-et al.), all that remains to show the sufficiently seperated
+et al., 2016), all that remains to show the sufficiently seperated
 \(\hat{\mu}\) from \(\tau\) is to lower bound the number of times the
@@
 
+To achieve correct seperation at the end of the algorithm,
+\href{https://arxiv.org/pdf/1704.04567.pdf}{Zhong et al. (2017)} require
+that after the last round \(T\), the sample means \(\hat{\mu}\) of the
+arms are closer to the true mean \(\mu\) of the distribution than to the
+threshold \(\tau\):
+
+\[
+|\hat{\mu}_i(T_i(T)) - \mu| \leq \frac{\Delta_i}{2}
+\]
+
+More explicitly, for an arm below the threshold, \(\mu_i < \tau\), they
+demand \(\hat{\mu}_i(T_i(T)) \geq \mu_i - \frac{\mu_i-\tau}{2}\). On the
+other hand, for an arm above the threshold, \(\mu_i \geq \tau\), they
+demand \(\hat{\mu}_i(T_i(T)) \leq \mu_i - \frac{\mu_i-\tau}{2}\).
+
+Based on a similar idea, the fixed-confidence KL-LUCB algorithm
+introduced in
+\href{http://proceedings.mlr.press/v30/Kaufmann13.pdf}{Kaufmann and
+Kalyanakrishnan} (2013) for the Top-\(m\) problem employs a stopping
+rule that checks whether the smallest lower bound among the currently
+best \(m\) algorithms is larger than the largest upper bound of the
+other arms that currently are not among the \(m\) best. If the lower
+bound is larger than the upper bound, the two sets of arms are
+considered to be sufficiently seperated; it is unlikely, that there are
+two arms that are classified into the wrong set (compare with
+Proposition 1,
+\href{http://proceedings.mlr.press/v30/Kaufmann13.pdf}{Kaufmann and
+Kalyanakrishnan}, 2013).
+
+Thus a simple demand that we can pose for our strategy is the one from
+Zhong et al. (2017), which directly translates into
+
+\[
+\der(\hat{\mu}_i(T_i(T)), \tau) \geq \der(\mu_i +\frac{\tau-\mu_i}{2}, \tau)
+\]
+
+for arms with mean below the threshold, \(\mu_i < \tau\). On the other
+hand, for arms with mean above the threshold, \(\mu_i > \tau\), we
+demand
+
+\[
+\der(\hat{\mu}_i(T_i(T)), \tau) \geq \der(\mu_i - \frac{\mu_i - \tau}{2}, \tau).
+\]
+
+These two conditions are equivalent to the conditions given in
+\href{https://arxiv.org/pdf/1704.04567.pdf}{Zhong et al. (2017)} due to
+the monotonicity of the KL divergence. If we could check whether these
+conditions hold on whatever favorable event we use, that would be a very
+convenient check.
+
+UPDATE: This translation into the Kullback-Leibler distance does not
+work as easily, because the above conditions might hold even if
+\(\mu < \tau < \hat{\mu}\), for example.
+
+\subsubsection{The Favorable Event}\label{the-favorable-event}
+
+Intuitively, it should be an event of large probability that
+\(|\der(\mu,\tau) - \der(\hat{\mu},\tau)|<\epsilon\), given that
+\(|\mu - \hat{\mu}|<\delta\) is likely. Also since we know that
+\(\der(\hat{\mu}(t), \mu) \leq \epsilon\) is likely for large \(t\)
+following for example Proposition 1 in
+\href{https://projecteuclid.org/download/pdfview_1/euclid.aos/1375362558}{Cappé
+et al. (2013)}. Additionally we know that
+\(\der(\hat{\mu}, \tau) = \der(\mu, \tau)\) for \(\hat{mu} = \mu\),
+however otherwise the inequality
+\(\der(\hat{\mu}, \tau) \geq \der(\hat{\mu}, \mu) + \der(\mu, \tau)\)
+only holds for \(\mu \in [\hat{\mu}, \tau]\) (or
+\(\mu \in [\tau, \hat{\mu}]\)).
+
+Instead, we will try to base our favorable event on a variant of Lemma 1
+in \href{http://proceedings.mlr.press/v30/Kaufmann13.pdf}{Kaufmann and
+Kalyanakrishnan} (2013), which states the following.
+
+Let \(T \geq 1\) be an integer. Let \(\delta > 0\), \(\gamma > 0\), and
+\(c \in (0,1)\) be such that \(mu_a \neq \tau\).
+
+\[
+\sum_{t=1}^T \mathbb{P} \Big(a = u_t \lor a = l_t, T_a(t) > \left \lceil{\frac{\gamma}{d^*(\mu_a,\tau)}}\right \rceil, T_a(t) d(\hat{\mu}_a, \tau) \leq \gamma \Big) \leq \frac{exp(-\gamma)}{d^*(\mu_a, \tau)}
+\]
+
+Given Lemma 2 in the same paper, as well as the proof of Lemma 1 in
+Appendix C of the paper (last inequality), the same bound should hold if
+we write the event without the lower and upper bounds \(u_t\) and
+\(l_t\) of arm \(a\):
+
+\[
+\sum_{t=1}^T \mathbb{P} \Big(T_a(t) > \left \lceil{\frac{\gamma}{d^*(\mu_a,\tau)}}\right \rceil, T_a(t) d(\hat{\mu}_a, \tau) \leq \gamma \Big) \leq \frac{exp(-\gamma)}{d^*(\mu_a, \tau)}
+\]
+
+Thus on the favorable event for a single arm \(a\), we have that
+
+\[
+T_a(t) -1 \geq \frac{\gamma}{d^*(\mu_a, \tau)} \qquad \text{and} \qquad d(\hat{\mu}_a, \tau) > \frac{\gamma}{T_a(t)}
+\]
+
+\subsubsection{Characterization of some helpful
+arm}\label{characterization-of-some-helpful-arm}
+
+Locatelli et al. (2016) show for arm \(k\) that
+\(T_k(t) \geq T_k(T) - 1 \geq \frac{T}{2H_{APT}\Delta^2_{APT,k}}\). We
+expect (CHECK THIS) that a similar condition holds for our algorithm,
+however with a different \(H_{KL}\) and \(h_{KL,k}\),
+\(H_{KL} = \sum_{i=1}^K h_{KL,i}\),
+\(h_{APT,k} = 1/(|\hat{\mu}-\tau|+\epsilon)^2\); but where the helpful
+arm \(k\) still has at least as many pulls as would be its share of the
+budget given its contribution to the overall complexity.
+
+Now, we can go ahead and plug the favorable event directly into
+\(B_k(t)\) (on the favorable event, it is likely that
+\(\gamma < T_a(t) d(\hat{\mu}_a, \tau)\)):
+
+\[
+B_k(t) \leq B_i(t) \Leftrightarrow \gamma < T_k(t) \der(\hat{\mu}_k(t), \tau) \leq T_i(t) \der(\hat{\mu}_i(t), \tau) 
+\]
+
+To check whether this makes sense, we need to choose a value for
+\(\gamma\), such that the second part of the favorable event is
+fulfilled. Given the lower bound for the helpful arm, we can define the
+complexity in terms of the Chernoff information used in
+\href{http://proceedings.mlr.press/v30/Kaufmann13.pdf}{Kaufmann and
+Kalyanakrishnan} (2013). We write
+
+\[
+H_{KL} = \sum_{i=1}^K \frac{1}{d^*(\mu_i, \tau)}
+\]
+
+For two Bernoullis, the Chernoff information is defined as
+\(d^*(\mu_i, \tau) = d(z^*,\mu_i) = d(z^*, \tau)\) (compare
+\href{http://proceedings.mlr.press/v30/Kaufmann13.pdf}{Kaufmann and
+Kalyanakrishnan}, 2013). For the helpful arm we thus get
+
+\[
+T_k(t) \geq T_k(T) -1 \geq \frac{T}{2 H_{KL} d^*(\mu_i, \tau)}
+\] such that by choosing \(\gamma = \frac{T}{2H_{KL}}\) the favorable
+event \(T_a(t) -1 > \frac{\gamma}{d^*(\mu_a, \tau)}\) works for the
+helpful arm:
+
+\[
+\gamma = \frac{T}{2H_{KL}} \leq T_k(t) \der(\hat{\mu}_k(t), \tau) \leq T_i(t) \der(\hat{\mu}_i(t), \tau) 
+\]
+
+Given that we can conclude the proof successfully, this choice of the
+exploration exponent \(\gamma\) already implies that the budget should
+be rather large if \(H_{KL}\) is large. But it also implies that the
+favorable event occurs at the rate that we demanded upfront, since then
+\(exp(-\gamma) = exp(-T/(2H))\).
+
+\subsubsection{Problem}\label{problem}
+
+At this point, however, I am stuck since the favorable event does not
+give an upper bound on the RHS of the equation. Thus I don't have a way
+of bounding \(T_i(t)\). I tried to approximate the KL-divergence
+\(d(\hat{\mu}_k(t), \tau) \leq \frac{(\hat{\mu}-\tau)^2}{\tau(1-\tau)}\)
+to get a bound similarly as in Locatelli et al. (2016) using the
+favorable event mentioned there; this gave me indeed a lower bound on
+\(T_i(t)\) similar to the one in that paper. However, given that the
+favorable event bounds the KL divergence from below as
+\(\frac{\gamma}{T_a(t)} < d(\hat{\mu}_a, \tau)\), the lower bound for
+\(T_i(t)\) did not prove useful. Instead, it might have showed me
+another problem. At first I believed it would suffice to show that
+\(d(\hat{\mu}_a, \tau)\) is larger than e.g. \(d^*(\mu_a, \tau)\) on the
+favorable event. But in theory, this could also hold if \(\mu_a < \tau\)
+and \(\tau < \hat{\mu}_a\). So a check against that probably needs to be
+included in the favorable event as well. This might be possible with
+some proposition from the
+\href{https://projecteuclid.org/download/pdfview_1/euclid.aos/1375362558}{KL-UCB
+paper by Cappé et al. (2013)}, or a self-normalized inequality by
+\href{https://arxiv.org/pdf/1102.2490.pdf}{Garivier and Cappé (2011,
+Theorem 10)}.
+
+In general, I'm simply wondering which inequality might suffice to bound
+\(B_k(t) < B_i(t)\). I believed that the one from
+\href{http://proceedings.mlr.press/v30/Kaufmann13.pdf}{Kaufmann and
+Kalyanakrishnan} sufficed, but in their paper it is combined with a nice
+separation condition stemming from the lower and upper bounds, which is
+integrated into the stopping rule of the fixed-\emph{confidence}
+algorithm (where the separation thus has to hold).
+
+\subsection{Experiments}\label{experiments}
+
+First, we again show the result of experiment 3. This time around,
+however, we set \(\epsilon = 0\) as recommended by Andrea. Also, we move
+the two arms that previously have been inside the \(\epsilon\)-interval
+a little away from the threshold \(\tau = 0.5\) to remove the need for a
+very large sample size. The likelihood-ratio based algorithm is now able
+to show it's advantage.
+
+The setup is as follows:
+
+\begin{verbatim}
+##  [1] 0.001 0.005 0.010 0.015 0.040 0.060 0.085 0.090 0.095 0.099
+\end{verbatim}
+
+\includegraphics{LR_theory_files/figure-latex/unnamed-chunk-1-1.pdf}
+
+\includegraphics{LR_theory_files/figure-latex/unnamed-chunk-2-1.pdf}
+
+\subsubsection{Experiment 2}\label{experiment-2}
+
+This is a new setup in which the observations are set in more or less
+the same distance from each other on a log10 scale. Again,
+\(\epsilon = 0\). We choose a very small threshold with \(\tau = 0.01\).
+Also note that we have increased the budget to \(T=10000\), while the
+previous experiment had \(T=7000\).
+
+\begin{verbatim}
+##  [1] 0.00010 0.00032 0.00056 0.00100 0.00178 0.00316 0.00562 0.01413
+##  [9] 0.01778 0.03162 0.10000
+\end{verbatim}
+
+\includegraphics{LR_theory_files/figure-latex/unnamed-chunk-3-1.pdf}
+
+\includegraphics{LR_theory_files/figure-latex/unnamed-chunk-4-1.pdf}
+
 \end{document}

### 2017-08-06 AugUCB/run_from_data.R

@@ -421,70 +421,6 @@ get_posterior_mean <- function(x, alpha, beta) {
 
 ##############################################################
 
-# Probability of Improvement
-
-BETA_from_tsdata <- function(data, rounds, tau, epsilon,
-                             alpha, beta, verbose = FALSE, 
-                             seed = NA) {
-  
-  if(!is.na(seed)) set.seed(seed)
-  K <- dim(data)[2]
-  
-  # initialize by pulling each arm once
-  arm_list <- diag(as.matrix(data[1:K,]))
-  arm_list <- as.list(arm_list)
-  
-  # initialize mean storage and the counter
-  mean_storage <- matrix(unlist(lapply(arm_list, mean)), nrow = 1)
-  arm_sequence <- 1:K
-  
-  for(i in (K+1):rounds) {
-    if(verbose) message(paste("this is round", i))
-    # NOTE THE MINUS SIGN; find the arm that MAXIMIZES the error probability
-    next_arm <- get_min(-unlist(get_next_arm_BETA(arm_list, tau = tau,
-                                                  epsilon = epsilon,
-                                                  alpha = alpha,
-                                                  beta = beta)))
-    arm_sequence <- c(arm_sequence, next_arm)
-    
-    if(verbose) message("arm selecting done")
-    arm_list[[next_arm]] <- c(arm_list[[next_arm]], data[i, next_arm])
-    mean_storage <- rbind(mean_storage, unlist(lapply(arm_list,
-                                                      get_posterior_mean,
-                                                      alpha = alpha,
-                                                      beta = beta)))
-    
-    if(verbose) message("arm pulling done")
-    
-  }
-  return(list(means = unlist(lapply(arm_list, mean)),
-              arm_list = arm_list,
-              arm_sequence = arm_sequence,
-              mean_storage = mean_storage))
-}
-
-get_next_arm_BETA <- function(armls, tau, epsilon,
-                              alpha, beta) {
-  get_metric <- function(x) {
-    alpha_prime <- sum(x)+alpha
-    beta_prime <- length(x)+beta-sum(x)
-    posterior_mean <- alpha_prime/(alpha_prime+beta_prime)
[…]

### 2017-08-06 AugUCB/run_parallelized_from_data.R

@@ -164,6 +164,33 @@ para_bandit_sim_APT <- function(data, seed = NA, do_verbose = FALSE, ...) {
 }
 
 #################################################################################
+# EVT Algorithm
+
+para_bandit_sim_EVT <- function(data, seed = NA, do_verbose = FALSE, ...) {
+  require(foreach)
+  require(doParallel)
+  
+  # assume that data is a list of data frames
+  reps <- length(data)
+  
+  gc()
+  cl <- makeCluster(max(1,detectCores()-1))
+  registerDoParallel(cl)
+  res <- foreach(j = 1:reps, #.errorhandling = 'remove',
+                 .export = c("EVT_from_tsdata", "get_next_arm_evt",
+                             "get_min"), 
+                 .verbose = do_verbose, .inorder = TRUE) %dopar% {
+                   alg_res <- EVT_from_tsdata(data = data[[j]], 
+                                              seed = 512+j, ...)
+                   list(mean_storage = alg_res$mean_storage,
+                        arm_sequence = alg_res$arm_sequence,
+                        input_data = data[[j]])
+                 }
+  stopCluster(cl)
+  return(res)
+}
+
+#################################################################################
 # input has to be a list of different data frames
 # each data frame is a run of the algorithm
 # in the end, return a list of lists
@@ -182,10 +209,83 @@ para_bandit_sim_LR <- function(data, seed = NA, do_verbose = FALSE, ...) {
   registerDoParallel(cl)
   res <- foreach(j = 1:reps, #.errorhandling = 'remove',
                  .export = c("LR_bandit_from_tsdata", "get_next_arm_lr",
-                             "get_min", "lr_ber"), 
+                             "get_min", "lr_ber", "lr_gaussian", "lr_exponential",
+                             "get_next_arm_lr_gaussian", "get_next_arm_lr_exponential"), 
                  .verbose = do_verbose, .inorder = TRUE) %dopar% {
                    alg_res <- LR_bandit_from_tsdata(data = data[[j]], 
                                               seed = 512+j, ...)
+                   list(mean_storage = alg_res$mean_storage,
+                        arm_sequence = alg_res$arm_sequence,
+                        input_data = data[[j]])
+                 }
+  stopCluster(cl)
+  return(res)
+}
+
+para_bandit_sim_LR_gaussian <- function(data, seed = NA, do_verbose = FALSE, ...) {
+  require(foreach)
[…]

### 2017-08-06 synthetic_experiments/cal_algs_verylong_7_no_tau.R

@@ -113,21 +113,10 @@ rm(loc7nt_BUCB_horizon_10000)
 gc()
 
 ########################################################################
-# Standard AugUCB
-system.time(loc7nt_AugUCB <- para_bandit_sim_AugUCB(data = data_list7, 
-                                                  rounds = 2000, 
-                                                  tau = tau_loc7nt))
-save(loc7nt_AugUCB, file = paste0(current_path, "loc7nt_AugUCB.Rda"))
-load(file = paste0(current_path, "loc7nt_AugUCB.Rda"))
-loc7nt_comp_AugUCB <- compare_to_ground_truth(mean_loc7nt, loc7nt_AugUCB, tau_loc7nt, 
-                                            epsilon_loc7nt)$mean
-save(loc7nt_comp_AugUCB, file = paste0(current_path, "loc7nt_comp_AugUCB.Rda"))
-
-# now with 10000
 
 system.time(loc7nt_AugUCB_10000 <- para_bandit_sim_AugUCB(data = data_list7_10000, 
-                                                       rounds = 10000, 
-                                                       tau = tau_loc7nt))
+                                                          rounds = 10000, 
+                                                          tau = tau_loc7nt))
 #user    system   elapsed 
 #60.824    67.047 24179.679 
 save(loc7nt_AugUCB_10000, file = paste0(current_path, "loc7nt_AugUCB_10000.Rda"))
@@ -146,7 +135,8 @@ load(file = paste0(current_path, "loc7nt_comp_BUCB_horizon_10000.Rda"))
 load(file = paste0(current_path, "loc7nt_comp_AugUCB_10000.Rda"))
 
 plot(c(0,10000), c(0, -5), type = "n")
-lines(log(loc7nt_comp_BUCB_horizon_10000), col = "red")
+lines(log(loc7nt_comp_BUCB_horizon_10000), col = "green")
 lines(log(loc7nt_comp_UNIFORM_10000), col = "darkblue")
-lines(log(loc7nt_comp_APT_10000), col = "green")
+lines(log(loc7nt_comp_APT_10000), col = "red")
 lines(log(loc7nt_comp_LR_10000), col = "darkred")
+lines(log(loc7nt_comp_AugUCB_10000), col = "darkgreen")

### 2017-08-06 synthetic_experiments/exponential/exp_exp_1.R

@@ -1,0 +1,80 @@
+########################################################################
+# load functions
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/exponential/"
+
+########################################################################
+# Create the data from exponential distributions
+
+set.seed(58459230)
+tau_expEasy <- 1
+epsilon_expEasy <- 0
+mu_expEasy <- c(0.01, 0.3, 0.6, 0.8, 0.8, 
+                1.2, 1.2, 1.4, 2, 5)
+
+plot(c(0,8), c(0,2), type = "n")
+for(i in 1:length(mu_expEasy)) {
+  lines(seq(0,8,0.001), dexp(seq(0,8,0.001), mu_expEasy[i]), col = rainbow(length(mu_expEasy))[i])
+}
+
+data_list_expEasy <- list()
+for(j in 1:5000) {
+  curr_data <- data.frame(rep(NA, times = 2000))
+  for(i in 1:length(mu_expEasy)) {
+    curr_data[[i]] <- as.numeric(rexp(2000, 1/mu_expEasy[i]))
+  }
+  names(curr_data) <- paste0("V", rep(1:length(mu_expEasy)))
+  data_list_expEasy[[j]] <- curr_data
+}
+gc()
+
+########################################################################
+
+plot(c(0,2000), c(0, -8), type = "n")
+abline(h=log(0.01), lty = 2)
+lines(log(expEasy_comp_APT), col = "black")
+lines(log(expEasy_comp_LR), col = "blue")
+lines(log(expEasy_comp_EVT), col = "red")
+
+########################################################################
+# Gaussian Likelihood Ratio
+system.time(expEasy_LR <- para_bandit_sim_LR_exponential(data = data_list_expEasy, 
+                                                         rounds = 2000, 
+                                                         tau = tau_expEasy, 
+                                                         epsilon = epsilon_expEasy))
+
+
+
+save(expEasy_LR, file = paste0(current_path, "expEasy_LR.Rda"))
+expEasy_comp_LR <- compare_to_ground_truth(mu_expEasy, expEasy_LR, 
[…]

### 2017-08-06 synthetic_experiments/gaussian/exp_gaussian_1.R

@@ -1,0 +1,84 @@
+########################################################################
+# load functions
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/gaussian/"
+
+########################################################################
+# Create the data
+
+tau_gax1 <- 10
+epsilon_gax1 <- 0
+mu_gax1 <- c(-5, -5,
+             0, 0,
+             5, 5,
+             13, 15,
+             18, 20)
+sd_gax1 <- c(5, 10,
+             5, 10,
+             5, 10,
+             5, 10,
+             5, 10)
+
+data_list_gax1 <- list()
+set.seed(268549023)
+for(j in 1:1000) {
+  curr_data <- data.frame(rep(NA, times = 2000))
+  for(i in 1:length(mu_gax1)) {
+    curr_data[[i]] <- as.numeric(rnorm(2000, mu_gax1[i], sd_gax1[i]))
+  }
+  names(curr_data) <- paste0("V", rep(1:length(mu_gax1)))
+  data_list_gax1[[j]] <- curr_data
+}
+gc()
+########################################################################
+
+plot(c(0,2000), c(0, -8), type = "n")
+lines(log(gax1_comp_APT), col = "black")
+lines(log(gax1_comp_LR), col = "red")
+
+########################################################################
+# Gaussian Likelihood Ratio
+single_gax1_LR <- LR_bandit_from_tsdata_gaussian(data_list_gax1[[1]], 
+                                        rounds = 2000, tau_gax1, epsilon_gax1,
+                                        verbose = TRUE, seed = NA)
+
+gax1_LR <- list()
+for(j in 1:length(data_list_gax1)) {
+  message(j)
+  alg_res <- LR_bandit_from_tsdata_gaussian(data_list_gax1[[j]], 
+                                 rounds = 2000, tau_gax1, epsilon_gax1,
+                                 verbose = TRUE, seed = 512+j)
+  gax1_LR[[j]] <- list(mean_storage = alg_res$mean_storage,
+                       arm_sequence = alg_res$arm_sequence,
+                       input_data = data_list_gax1[[j]])
+}
+
[…]

### 2017-08-06 synthetic_experiments/gaussian/exp_gaussian_3.R

@@ -1,0 +1,71 @@
+########################################################################
+# load functions
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/gaussian/"
+
+########################################################################
+# Create the data
+# Setup as in Experiment 5 of Mukherjee et al.
+
+set.seed(58459230)
+tau_gax3 <- 0.5
+epsilon_gax3 <- 0
+mu_gax3 <- c(rep(0.4, 3),
+             rep(0.6, 3),
+             rep(0.3, 4))
+sd_gax3 <- c(rep(sqrt(0.4), 3),
+             rep(sqrt(1), 3),
+             sqrt(runif(4,0.2,0.4)))
+
+plot(seq(-2,3,by=0.0001), dnorm(seq(-2,3,by=0.0001), 0.4, sqrt(0.4)), type = "l",
+     ylim = c(0,2))
+lines(seq(-2,3,by=0.0001), dnorm(seq(-2,3,by=0.0001), 0.6, sqrt(1)), col = "red")
+abline(v = 0.5)
+
+data_list_gax3 <- list()
+for(j in 1:1000) {
+  curr_data <- data.frame(rep(NA, times = 10000))
+  for(i in 1:length(mu_gax3)) {
+    curr_data[[i]] <- as.numeric(rnorm(10000, mu_gax3[i], sd_gax3[i]))
+  }
+  names(curr_data) <- paste0("V", rep(1:length(mu_gax3)))
+  data_list_gax3[[j]] <- curr_data
+}
+gc()
+
+########################################################################
+
+plot(c(0,10000), c(0, -8), type = "n")
+lines(log(gax3_comp_APT), col = "black")
+lines(log(gax3_comp_LR), col = "red")
+
+########################################################################
+# Gaussian Likelihood Ratio
+system.time(gax3_LR <- para_bandit_sim_LR_gaussian(data = data_list_gax3, 
+                                                   rounds = 10000, 
+                                                   tau = tau_gax3, 
+                                                   epsilon = epsilon_gax3))
+
+save(gax3_LR, file = paste0(current_path, "gax3_LR.Rda"))
+gax3_comp_LR <- compare_to_ground_truth(mu_gax3, gax3_LR, 
[…]

### 2017-08-06 synthetic_experiments/gaussian/exp_gaussian_easy.R

@@ -1,0 +1,73 @@
+########################################################################
+# load functions
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/gaussian/"
+
+########################################################################
+# Create the data
+# Setup as in Experiment 5 of Mukherjee et al.
+
+set.seed(58459230)
+tau_gaxEasy <- 0.5
+epsilon_gaxEasy <- 0
+mu_gaxEasy <- c(0.45, 0.55,
+                0.45, 0.55,
+                0.45, 0.55,
+                0.45, 0.55)
+sd_gaxEasy <- c(0.05, 0.1,
+                0.1, 0.15,
+                0.15, 0.2,
+                0.05, 0.025)
+
+plot(seq(-2,3,by=0.0001), dnorm(seq(-2,3,by=0.0001), mu_gaxEasy[1], sd_gaxEasy[1]), type = "l",
+     ylim = c(0,5))
+lines(seq(-2,3,by=0.0001), dnorm(seq(-2,3,by=0.0001), mu_gaxEasy[2], sd_gaxEasy[2]), col = "red")
+abline(v = 0.5)
+
+data_list_gaxEasy <- list()
+for(j in 1:5000) {
+  curr_data <- data.frame(rep(NA, times = 2000))
+  for(i in 1:length(mu_gaxEasy)) {
+    curr_data[[i]] <- as.numeric(rnorm(2000, mu_gaxEasy[i], sd_gaxEasy[i]))
+  }
+  names(curr_data) <- paste0("V", rep(1:length(mu_gaxEasy)))
+  data_list_gaxEasy[[j]] <- curr_data
+}
+gc()
+
+########################################################################
+
+plot(c(0,2000), c(0, -8), type = "n")
+lines(log(gaxEasy_comp_APT), col = "black")
+lines(log(gaxEasy_comp_LR), col = "blue")
+
+########################################################################
+# Gaussian Likelihood Ratio
+system.time(gaxEasy_LR <- para_bandit_sim_LR_gaussian(data = data_list_gaxEasy, 
+                                                   rounds = 2000, 
+                                                   tau = tau_gaxEasy, 
[…]

### 2017-08-06 synthetic_experiments/poisson/exp_pois_1.R

@@ -1,0 +1,102 @@
+########################################################################
+# load functions
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/exponential/"
+
+########################################################################
+# Create the data from exponential distributions
+
+set.seed(834795)
+tau_pois1 <- 1
+epsilon_pois1 <- 0
+mu_pois1 <- rexp(20, 1/5)
+
+plot(c(0,8), c(0,2), type = "n")
+for(i in order(mu_pois1)) {
+  lines(seq(0,8,0.001), dpois(seq(0,8,0.001), mu_pois1[i]), col = rainbow(length(mu_pois1))[i])
+}
+
+data_list_pois1 <- list()
+for(j in 1:5000) {
+  curr_data <- data.frame(rep(NA, times = 10000))
+  for(i in 1:length(mu_pois1)) {
+    curr_data[[i]] <- as.numeric(rpois(10000, 1/mu_pois1[i]))
+  }
+  names(curr_data) <- paste0("V", rep(1:length(mu_pois1)))
+  data_list_pois1[[j]] <- curr_data
+}
+gc()
+
+########################################################################
+
+plot(c(0,10000), c(0, -8), type = "n")
+abline(h=log(0.01), lty = 2)
+lines(log(pois1_comp_APT), col = "black")
+lines(log(pois1_comp_LR), col = "blue")
+lines(log(pois1_comp_EVT), col = "red")
+
+########################################################################
+# Gaussian Likelihood Ratio
+system.time(pois1_LR <- para_bandit_sim_LR_poisson(data = data_list_pois1, 
+                                                   rounds = 10000, 
+                                                   tau = tau_pois1, 
+                                                   epsilon = epsilon_pois1))
+
+save(pois1_LR, file = paste0(current_path, "pois1_LR.Rda"))
+pois1_comp_LR <- compare_to_ground_truth(mu_pois1, pois1_LR, 
+                                        tau_pois1, epsilon_pois1)$mean
+save(pois1_comp_LR, file = paste0(current_path, "pois1_comp_LR.Rda"))
+gc()
+
+########################################################################
+
[…]

### 2017-08-06 Thesis/APT_UB_revised/Untitled.Rmd
Add new version of APT UB proof

---
title: "APT Upper Bound"
header-includes:
   #- \documentclass[a4paper,twoside,english]{article}
   - \usepackage[retainorgcmds]{IEEEtrantools}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{bbm}
   - \newtheorem{theorem}{Theorem}
   - \newtheorem{lemma}{Lemma}
   - \newcommand{\KL}{\,\text{KL}}
   - \newcommand{\der}{\,\text{d}}
   #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
   #- \usepackage{fontspec}
   #-   \setmainfont{Arial}
keep_tex: TRUE
output:
  pdf_document:
    number_sections: true
    keep_tex: true
    toc: true
    toc_depth: 3
    #latex_engine: xelatex
fontsize: 12pt
urlcolor: blue
---

```{r setup, include=TRUE, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

## Upper Bound on Loss of APT

\begin{theorem}[Locatelli et al., 2016] \label{theorem:LocatelliTheorem4}
Let $K \geq 0$, $T \geq 2K$, and consider a problem $\mathbb{B}$. Assume that
all arms $\nu_k$ of the problem are R-sub-Gaussian with means $\mu_k$. Let $\tau
\in \mathbb{R}, \epsilon \geq 0$.

Algorithm APT's expected loss is upper bounded on this problem as 
\begin{equation*} \mathbb{E}(\mathcal{L}(T)) \leq \exp
(-\frac{1}{64R^2}\frac{T}{H} + 2 \log (T) + 1)K)) \end{equation*}

where we remind that $H = \sum_i (|\mu_i - \tau | + \epsilon)^{-2}$ and where
$\mathbb{E}$ is the expectation according to the samples of the problem.
\end{theorem}

*Proof of Theorem \ref{theorem:LocatelliTheorem4}:*

In order to bound the expected loss of the APT algorithm, we want to find an event on which the algorithm would correctly seperate arms from the threshold, that is, on the event a seperation condition holds. We then want to show that with large probability, this *favorable* event does indeed hold. Consequently, the expected loss (probability of an error) will correspond to the probability that the favorable event does not hold after all as this leads the seperation condition to fail, and the algorithm to classify at least one arm incorrectly.

While this is the general idea, we have to jump between seperation condition, favorable event, and large probability.

### Separation Condition

As noted in Zhong et al. (2017), a simple requirement to correctly classify arms at the final round is the following. For every arm $i \in \{1, ..., K\}$ at round $T$,

$$
\hat{\mu}_{i,T_i(n)} \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
$$
or

$$
\hat{\mu}_{i,T_i(n)} \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
$$
Or simply in terms of the gap between the arm and the threshold as used as index by the algorithm,

$$
| \hat{\mu}_{i, T_i(n)} - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
$$

Intuitively, the conditions make sense as they ensure that the current mean estimate is closer to the true mean than to the threshold. Consequently, there is no possible arrangement left in which the condition would hold, but the arm be classified incorrectly. Assuming $\mu_i < \tau$ and $\epsilon = 0$, an incorrect classification would require $\mu_i < \tau \leq \hat{\mu_i}$. But then  $| \hat{\mu}_{i, T_i(n)} - \mu_i | \geq |\mu_i - \tau|$, violating the separation condition.

Thus, we need to show that in the very final round, this condition holds for every arm $i \in \{1,...,K\}$ with large probability. Or more precisely, we need to derive a bound on the probability with which this does not hold.

### The Favorable Event

The separation condition gives a good idea of what event we need to hold in order to make a correct classification. The smaller the deviation of the empirical mean from the population mean, the more difficult it is for the classification to be wrong. Moreover, if the mean and empirical mean are identical, then the classification is correct independent of the threshold. And furthermore, the closer the mean and the threshold are, the better the estimate must be for a correct classification.

Having to bound the absolute deviation of the sample mean from the population mean is a very thankful operation. Define the favorable event $\xi$ as

$$
\xi = \Big\{\forall i \in \mathbb{A}, \forall s \in \{1,...,T\} : |\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}} \Big\}.
$$

We want the probability that this favorable event occurs to be large, that is, the probability that the deviation is small, such that the separation condition holds with large probability. Indeed, we bound the deviation for *all* arms $i \leq K$ and for *every* round $s \leq T$. Using some Chernoff Hoeffding bounds, we are able to write

$$
\mathbb{P}(\xi) \geq 1 - 2(\log(T) +1)K \exp(-\frac{T\delta^2}{2R^2H})
$$

## Need to Bound $T_i$

We now have that with large probability, the favorable event holds. On the favorable event, we have for every arm $i$:

$$
| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}
$$

The deviation of arm $i$ at time $t$ depends on how large $H$, $T$, and $T_i(t)$ are. While $t$, $H$, $T$ are deterministic, the number of times arm $i$ has been pulled at round $t$, $T_i(t)$, is a random variable. In order to know how large the probability of the favorable event is (and thus the error probability), we need to know what realistic values for $T_i(t)$ will be. Put differently: To ensure a deviation smaller than $\sqrt{\frac{T\delta^2}{HT_i(t)}}$ for arm $i$, we need to ensure that arm $i$ has been pulled at least $T_i(t)$ times. As usual in multi-armed bandits, and different from uniform sampling, the number of pulls is a random variable that also depends on how often other arms are pulled. In general, we do not want each arm to be pulled an equal amount, but each arm should be pulled some times, and not too many times. This especially holds for our exploration setting.

Thus, in order to check that the deviation of arm $i$ really is small enough for the separation condition to hold on the favorable event, we need to bound the number of pulls of every arm from below.

## Characteristics of a Frequently Pulled Arm (Lower Bound on $T_k(T)$)

Given that we do not follow a uniform sampling strategy, we know that at time $T$, some arms will have been pulled more frequently than others. In particular, some arms will have been pulled more than $T/K$ times. How often an arm is pulled can be related to the individual arm's contribution to the overall complexity measure. Let $h_i$ be a measure of arm $i$'s individual problem complexity and write for the overall problem complexity

$$
H = \sum_{i = 1}^{K} h_i.
$$

Then arm $i$ contributes a share of $h_i/H$ to the overall problem complexity. We can now show that there exists an arm that has been pulled at least as often as the share of his complexity contribution.

Given the initialization of the APT algorithm, every arm is pulled once initially. Consequently, there is a budget of $T-K$ rounds left after the initialization. As shown in Locatelli et al. (2016), there exists an arm $k$ that has been pulled after the initialization ($\geq 2$ pulls) and for which at the final round $T$ holds: $T_k(T) - 1 \geq \frac{(T-K)h_k}{H}$. This can be shown by a quick contradiction proof. Assume the opposite, that is

$$
\forall i \in \{1,...,K\}: T_i(T) - 1 < \frac{(T-K)h_i}{H}
$$

Consequently, at time $T$, we would have pulled across all arms $\sum_{i=1}^KT_i(T)-1$ times. If the previous assumption holds, we would not have used the entire budget:

$$
\sum_{i=1}^K T_i(T)-1 < \sum_{i=1}^K \frac{(T-K)h_i}{H} = (T-K)\sum_{i=1}^K \frac{h_i}{H} = T-K
$$

This is a contradiction, since as an requirement to the algorithm we have that $\sum_{i=1}^K T_i(T)-1 = (T-K)$, that is, we use the entire budget of samples.

Another such requirement has been that $T>2K$. Plugging this in gives 
$$
T_k(T) - 1 \geq \frac{(T-K)h_k}{H} \leq \frac{(T-1/2T)h_k}{H} = \frac{Th_i}{2H}
$$

Now we know how often the arm has been pulled at the very end. That does not mean that $k$ has been pulled at time $T$. Thus we consider the time $t \leq T$ at which arm $k$ is pulled for the last time. We get (!!!!!SHOOOOWWW THIIIISSSS!!!!!!!!!)

$$
T_k(t) \geq T_k(T) - 1 \geq \frac{Th_i}{2H}.
$$

This gives us a lower bound on how often arms are pulled that are pulled frequently relative to their contribution to the problem complexity. Now we need a lower bound on $T_i(T)$ for every other arm $i$.

## Lower Bound on $T_i(T)$

Consider again as before the round $t$ in which arm $k$ is pulled for the very last time. Since the APT algorithm minimizes at every round $s$ the index $B_j(s)$, and pulls the arm with the smallest index, we know that arm $k$ must have had the smallest index at round $t$. We have:

$$
B_k(t) \leq B_i(t) \Leftrightarrow \sqrt{T_k(t)}\hat{\Delta}_k(t) \leq \sqrt{T_i(t)} \hat{\Delta}_i(t)
$$

One can already expect that this can be used to derive a lower bound on $T_i(t)$ on the RHS, and this is exactly what we do.

On the LHS, we will plug in the lower bound for $T_k(t)$ derived before. Additionally bounding $\Delta_k(t)$ from below, and $\hat{\Delta}_i(t)$ from above using the favorable event will give the desired lower bound.

Thus assume we are on the favorable event $\xi$ with large probability. we consequently have

$$
| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}.
$$

As shown in Locatelli et al. (2016), one can use the reverse triangle inequality to get:

$$
|\hat{\mu}_i(t) - \mu_i| = |(\hat{\mu}_i(t) - \tau) - (\mu_i - \tau)| \geq || \hat{\mu}_i(t) - \tau | - |\mu_i - \tau|| \geq |(|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i - \tau| + \epsilon)| \geq |\hat{\Delta}_i(t) - \Delta_i|
$$

If we combine this with the favorable event, we get

$$
\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}} \leq \hat{\Delta}_k(t) \leq \Delta_k + \sqrt{\frac{T\delta^2}{HT_k(t)}}
$$

and similar for $\hat{\Delta}_i$.

We can now lower bound the LHS of the indices as

$$
\Big(\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}}\Big) \sqrt{T_k(t)} \leq B_k(t)
$$

$$
\Big(\Delta_k - \sqrt{\frac{2}{h_k}}\delta \Big) \sqrt{\frac{Th_k}{2H}} \leq B_k(t)
$$

At this point, it is useful to have a well chosen complexity measure. If we set $h_i = \frac{1}{\Delta_i^2}$ as in Locatelli et al. (2016), we get

$$
\Big(\Delta_k - \sqrt{2}\delta \Delta \Big) \sqrt{\frac{T}{2H\Delta_k^2}} \leq B_k(t)
$$

which can be now be reduced to a form that is not specific to $k$:

$$
\Big( \frac{1}{\sqrt{2}} - \delta \Big) \sqrt{\frac{T}{H}} \leq B_k(t).
$$

Now we need to get rid of $\hat{\Delta}_i$ in order to bound $T_i(t)$. Thus, we bound the RHS again using the favorable event much as we did for the LHS:

$$
B_i(t) = \hat{\Delta}_i \sqrt{T_i(t)} \leq \Big(\Delta_i + \sqrt{\frac{T\delta^2}{HT_i(t)}}\Big) \sqrt{T_i(t)} \leq \Delta_i \sqrt{T_i(t)} + \delta \sqrt{\frac{T}{H}}
$$

As in Locatelli et al. (2016) we use the fact that by definition $\Delta$ and $\hat{\Delta}$ are positive in order to square both sides and write

$$
(1 - 2\sqrt{2}\delta)^2 \frac{T}{2H\Delta^2_i} \leq T_i(t)
$$

We thus have derived a lower bound on the amount of pulls for any arm. That means that we can show that no arm is pulled an insufficient amount of times with large probability, and that consequently the favorable event hold and the estimated mean is sufficienctly separated from the threshold.

## Check Separation Condition

### 2017-08-06 Thesis/APT_UB_revised/Untitled.tex
Add new version of APT UB proof

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={APT Upper Bound},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{APT Upper Bound}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{bbm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newcommand{\KL}{\,\text{KL}}
\newcommand{\der}{\,\text{d}}

\begin{document}
\maketitle

{
\hypersetup{linkcolor=black}
\setcounter{tocdepth}{3}
\tableofcontents
}
\subsection{Upper Bound on Loss of
APT}\label{upper-bound-on-loss-of-apt}

\begin{theorem}[Locatelli et al., 2016] \label{theorem:LocatelliTheorem4}
Let $K \geq 0$, $T \geq 2K$, and consider a problem $\mathbb{B}$. Assume that
all arms $\nu_k$ of the problem are R-sub-Gaussian with means $\mu_k$. Let $\tau
\in \mathbb{R}, \epsilon \geq 0$.

Algorithm APT's expected loss is upper bounded on this problem as 
\begin{equation*} \mathbb{E}(\mathcal{L}(T)) \leq \exp
(-\frac{1}{64R^2}\frac{T}{H} + 2 \log (T) + 1)K)) \end{equation*}

where we remind that $H = \sum_i (|\mu_i - \tau | + \epsilon)^{-2}$ and where
$\mathbb{E}$ is the expectation according to the samples of the problem.
\end{theorem}

\emph{Proof of Theorem \ref{theorem:LocatelliTheorem4}:}

In order to bound the expected loss of the APT algorithm, we want to
find an event on which the algorithm would correctly seperate arms from
the threshold, that is, on the event a seperation condition holds. We
then want to show that with large probability, this \emph{favorable}
event does indeed hold. Consequently, the expected loss (probability of
an error) will correspond to the probability that the favorable event
does not hold after all as this leads the seperation condition to fail,
and the algorithm to classify at least one arm incorrectly.

While this is the general idea, we have to jump between seperation
condition, favorable event, and large probability.

\subsubsection{Separation Condition}\label{separation-condition}

As noted in Zhong et al. (2017), a simple requirement to correctly
classify arms at the final round is the following. For every arm
\(i \in \{1, ..., K\}\) at round \(T\),

\[
\hat{\mu}_{i,T_i(n)} \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
\] or

\[
\hat{\mu}_{i,T_i(n)} \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
\] Or simply in terms of the gap between the arm and the threshold as
used as index by the algorithm,

\[
| \hat{\mu}_{i, T_i(n)} - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
\]

Intuitively, the conditions make sense as they ensure that the current
mean estimate is closer to the true mean than to the threshold.
Consequently, there is no possible arrangement left in which the
condition would hold, but the arm be classified incorrectly. Assuming
\(\mu_i < \tau\) and \(\epsilon = 0\), an incorrect classification would
require \(\mu_i < \tau \leq \hat{\mu_i}\). But then
\(| \hat{\mu}_{i, T_i(n)} - \mu_i | \geq |\mu_i - \tau|\), violating the
separation condition.

Thus, we need to show that in the very final round, this condition holds
for every arm \(i \in \{1,...,K\}\) with large probability. Or more
precisely, we need to derive a bound on the probability with which this
does not hold.

\subsubsection{The Favorable Event}\label{the-favorable-event}

The separation condition gives a good idea of what event we need to hold
in order to make a correct classification. The smaller the deviation of
the empirical mean from the population mean, the more difficult it is
for the classification to be wrong. Moreover, if the mean and empirical
mean are identical, then the classification is correct independent of
the threshold. And furthermore, the closer the mean and the threshold
are, the better the estimate must be for a correct classification.

Having to bound the absolute deviation of the sample mean from the
population mean is a very thankful operation. Define the favorable event
\(\xi\) as

\[
\xi = \Big\{\forall i \in \mathbb{A}, \forall s \in \{1,...,T\} : |\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}} \Big\}.
\]

We want the probability that this favorable event occurs to be large,
that is, the probability that the deviation is small, such that the
separation condition holds with large probability. Indeed, we bound the
deviation for \emph{all} arms \(i \leq K\) and for \emph{every} round
\(s \leq T\). Using some Chernoff Hoeffding bounds, we are able to write

\[
\mathbb{P}(\xi) \geq 1 - 2(\log(T) +1)K \exp(-\frac{T\delta^2}{2R^2H})
\]

\subsection{\texorpdfstring{Need to Bound
\(T_i\)}{Need to Bound T\_i}}\label{need-to-bound-t_i}

We now have that with large probability, the favorable event holds. On
the favorable event, we have for every arm \(i\):

\[
| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}
\]

The deviation of arm \(i\) at time \(t\) depends on how large \(H\),
\(T\), and \(T_i(t)\) are. While \(t\), \(H\), \(T\) are deterministic,
the number of times arm \(i\) has been pulled at round \(t\),
\(T_i(t)\), is a random variable. In order to know how large the
probability of the favorable event is (and thus the error probability),
we need to know what realistic values for \(T_i(t)\) will be. Put
differently: To ensure a deviation smaller than
\(\sqrt{\frac{T\delta^2}{HT_i(t)}}\) for arm \(i\), we need to ensure
that arm \(i\) has been pulled at least \(T_i(t)\) times. As usual in
multi-armed bandits, and different from uniform sampling, the number of
pulls is a random variable that also depends on how often other arms are
pulled. In general, we do not want each arm to be pulled an equal
amount, but each arm should be pulled some times, and not too many
times. This especially holds for our exploration setting.

Thus, in order to check that the deviation of arm \(i\) really is small
enough for the separation condition to hold on the favorable event, we
need to bound the number of pulls of every arm from below.

\subsection{\texorpdfstring{Characteristics of a Frequently Pulled Arm
(Lower Bound on
\(T_k(T)\))}{Characteristics of a Frequently Pulled Arm (Lower Bound on T\_k(T))}}\label{characteristics-of-a-frequently-pulled-arm-lower-bound-on-t_kt}

Given that we do not follow a uniform sampling strategy, we know that at
time \(T\), some arms will have been pulled more frequently than others.
In particular, some arms will have been pulled more than \(T/K\) times.
How often an arm is pulled can be related to the individual arm's
contribution to the overall complexity measure. Let \(h_i\) be a measure
of arm \(i\)'s individual problem complexity and write for the overall
problem complexity

\[
H = \sum_{i = 1}^{K} h_i.
\]

Then arm \(i\) contributes a share of \(h_i/H\) to the overall problem
complexity. We can now show that there exists an arm that has been
pulled at least as often as the share of his complexity contribution.

Given the initialization of the APT algorithm, every arm is pulled once
initially. Consequently, there is a budget of \(T-K\) rounds left after
the initialization. As shown in Locatelli et al. (2016), there exists an
arm \(k\) that has been pulled after the initialization (\(\geq 2\)
pulls) and for which at the final round \(T\) holds:
\(T_k(T) - 1 \geq \frac{(T-K)h_k}{H}\). This can be shown by a quick
contradiction proof. Assume the opposite, that is

\[
\forall i \in \{1,...,K\}: T_i(T) - 1 < \frac{(T-K)h_i}{H}
\]

Consequently, at time \(T\), we would have pulled across all arms
\(\sum_{i=1}^KT_i(T)-1\) times. If the previous assumption holds, we
would not have used the entire budget:

\[
\sum_{i=1}^K T_i(T)-1 < \sum_{i=1}^K \frac{(T-K)h_i}{H} = (T-K)\sum_{i=1}^K \frac{h_i}{H} = T-K
\]

This is a contradiction, since as an requirement to the algorithm we
have that \(\sum_{i=1}^K T_i(T)-1 = (T-K)\), that is, we use the entire
budget of samples.

Another such requirement has been that \(T>2K\). Plugging this in gives
\[
T_k(T) - 1 \geq \frac{(T-K)h_k}{H} \leq \frac{(T-1/2T)h_k}{H} = \frac{Th_i}{2H}
\]

Now we know how often the arm has been pulled at the very end. That does
not mean that \(k\) has been pulled at time \(T\). Thus we consider the
time \(t \leq T\) at which arm \(k\) is pulled for the last time. We get
(!!!!!SHOOOOWWW THIIIISSSS!!!!!!!!!)

\[
T_k(t) \geq T_k(T) - 1 \geq \frac{Th_i}{2H}.
\]

This gives us a lower bound on how often arms are pulled that are pulled
frequently relative to their contribution to the problem complexity. Now
we need a lower bound on \(T_i(T)\) for every other arm \(i\).

\subsection{\texorpdfstring{Lower Bound on
\(T_i(T)\)}{Lower Bound on T\_i(T)}}\label{lower-bound-on-t_it}

Consider again as before the round \(t\) in which arm \(k\) is pulled
for the very last time. Since the APT algorithm minimizes at every round
\(s\) the index \(B_j(s)\), and pulls the arm with the smallest index,
we know that arm \(k\) must have had the smallest index at round \(t\).
We have:

\[
B_k(t) \leq B_i(t) \Leftrightarrow \sqrt{T_k(t)}\hat{\Delta}_k(t) \leq \sqrt{T_i(t)} \hat{\Delta}_i(t)
\]

One can already expect that this can be used to derive a lower bound on
\(T_i(t)\) on the RHS, and this is exactly what we do.

On the LHS, we will plug in the lower bound for \(T_k(t)\) derived
before. Additionally bounding \(\Delta_k(t)\) from below, and
\(\hat{\Delta}_i(t)\) from above using the favorable event will give the
desired lower bound.

Thus assume we are on the favorable event \(\xi\) with large
probability. we consequently have

\[
| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}.
\]

As shown in Locatelli et al. (2016), one can use the reverse triangle
inequality to get:

\[
|\hat{\mu}_i(t) - \mu_i| = |(\hat{\mu}_i(t) - \tau) - (\mu_i - \tau)| \geq || \hat{\mu}_i(t) - \tau | - |\mu_i - \tau|| \geq |(|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i - \tau| + \epsilon)| \geq |\hat{\Delta}_i(t) - \Delta_i|
\]

If we combine this with the favorable event, we get

\[
\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}} \leq \hat{\Delta}_k(t) \leq \Delta_k + \sqrt{\frac{T\delta^2}{HT_k(t)}}
\]

and similar for \(\hat{\Delta}_i\).

We can now lower bound the LHS of the indices as

\[
\Big(\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}}\Big) \sqrt{T_k(t)} \leq B_k(t)
\]

\[
\Big(\Delta_k - \sqrt{\frac{2}{h_k}}\delta \Big) \sqrt{\frac{Th_k}{2H}} \leq B_k(t)
\]

At this point, it is useful to have a well chosen complexity measure. If
we set \(h_i = \frac{1}{\Delta_i^2}\) as in Locatelli et al. (2016), we
get

\[
\Big(\Delta_k - \sqrt{2}\delta \Delta \Big) \sqrt{\frac{T}{2H\Delta_k^2}} \leq B_k(t)
\]

which can be now be reduced to a form that is not specific to \(k\):

\[
\Big( \frac{1}{\sqrt{2}} - \delta \Big) \sqrt{\frac{T}{H}} \leq B_k(t).
\]

Now we need to get rid of \(\hat{\Delta}_i\) in order to bound
\(T_i(t)\). Thus, we bound the RHS again using the favorable event much
as we did for the LHS:

\[
B_i(t) = \hat{\Delta}_i \sqrt{T_i(t)} \leq \Big(\Delta_i + \sqrt{\frac{T\delta^2}{HT_i(t)}}\Big) \sqrt{T_i(t)} \leq \Delta_i \sqrt{T_i(t)} + \delta \sqrt{\frac{T}{H}}
\]

As in Locatelli et al. (2016) we use the fact that by definition
\(\Delta\) and \(\hat{\Delta}\) are positive in order to square both
sides and write

\[
(1 - 2\sqrt{2}\delta)^2 \frac{T}{2H\Delta^2_i} \leq T_i(t)
\]

We thus have derived a lower bound on the amount of pulls for any arm.
That means that we can show that no arm is pulled an insufficient amount
of times with large probability, and that consequently the favorable
event hold and the estimated mean is sufficienctly separated from the
threshold.

\subsection{Check Separation
Condition}\label{check-separation-condition}

\end{document}

### 2017-08-06 real_experiments/real_pois_exp_1.R

@@ -1,0 +1,12 @@
+#sessions_threshold <- 0
+set.seed(35968399)
+selected_products <- sample(1:196, 20)
+niter <- 5000
+nrounds <- 7580 # These two values give the maximum size data 
+nahead <- 7580  # possible given the data set size we have
+source("/Users/timradtke/Desktop/thesis_data/get_count_dataset.R")
+
+head(pv_list[[1]])
+colMeans(pv_list[[1]])
+hist(pv_list[[1]][,8])
+colMeans(pv_products_wide)

### 2017-08-06 synthetic_experiments/exponential/exp_exp_2.R

@@ -21,9 +21,9 @@ for(i in order(mu_exp2)) {
 
 data_list_exp2 <- list()
 for(j in 1:5000) {
-  curr_data <- data.frame(rep(NA, times = 10000))
+  curr_data <- data.frame(rep(NA, times = 4000))
   for(i in 1:length(mu_exp2)) {
-    curr_data[[i]] <- as.numeric(rexp(10000, 1/mu_exp2[i]))
+    curr_data[[i]] <- as.numeric(rexp(4000, 1/mu_exp2[i]))
   }
   names(curr_data) <- paste0("V", rep(1:length(mu_exp2)))
   data_list_exp2[[j]] <- curr_data
@@ -31,8 +31,11 @@ for(j in 1:5000) {
 gc()
 
 ########################################################################
+load(paste0(current_path, "exp2_comp_LR.Rda"))
+load(paste0(current_path, "exp2_comp_APT.Rda"))
+load(paste0(current_path, "exp2_comp_EVT.Rda"))
 
-plot(c(0,10000), c(0, -8), type = "n")
+plot(c(0,4000), c(0, -8), type = "n")
 abline(h=log(0.01), lty = 2)
 lines(log(exp2_comp_UNIFORM), col = "black")
 lines(log(exp2_comp_LR), col = rainbow(4)[1])
@@ -42,8 +45,8 @@ lines(log(exp2_comp_AugUCB), col = rainbow(4)[4])
 
 ########################################################################
 # Exponential-Distribution Likelihood Ratio
-system.time(exp2_LR <- para_bandit_sim_LR_exponential(data = data_list_exp2[1:500], 
-                                                      rounds = 5000, 
+system.time(exp2_LR <- para_bandit_sim_LR_exponential(data = data_list_exp2, 
+                                                      rounds = 4000, 
                                                       tau = tau_exp2, 
                                                       epsilon = epsilon_exp2))
 
@@ -57,33 +60,35 @@ gc()
 # Anytime Parameter Free (Locatelli et al., 2016)
 
 system.time(exp2_APT <- para_bandit_sim_APT(data = data_list_exp2, 
-                                               rounds = 10000, 
+                                               rounds = 4000, 
                                                tau = tau_exp2, 
                                                epsilon = epsilon_exp2))
 save(exp2_APT, file = paste0(current_path, "exp2_APT.Rda"))
 exp2_comp_APT <- compare_to_ground_truth(mu_exp2, exp2_APT, 
                                             tau_exp2, epsilon_exp2)$mean
[…]

### 2017-08-11 Thesis/APT_UB_revised/APT_UB_Proof.Rmd
add long real experiments

--- 2017-08-06 Thesis/APT_UB_revised/Untitled.Rmd
@@
 
-## Upper Bound on Loss of APT
+## Upper Bound on Expected Loss of APT
 
@@
 $$
-(1 - 2\sqrt{2}\delta)^2 \frac{T}{2H\Delta^2_i} \leq T_i(t)
+(1 - 2\sqrt{2}\delta)^2 \frac{T}{2H\Delta^2_i} \leq T_i(t) \leq T_i(T)
 $$
@@
 ## Check Separation Condition
+
+As last step, we need to check whether the lower bound on the pulls of any arm suffices to ensure that the separation condition holds on the favorable event.
+That means, given $T_i(T) \geq (1-2\sqrt{2}\delta)^2 \frac{T}{2H\Delta_i^2}$, do we have $|\hat{\mu}_i(T) - \mu | \leq \frac{\Delta}{2}$ on the favorable event $\xi = \Big\{|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}}\Big\}$?
+
+To check, we plug the lower bound into the favorable event and get
+
+$$
+|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}} \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}
+$$
+Using $\delta = (4\sqrt{2})^-1$ as in Locatelli et al. (2016), we get
+
+$$
+|\hat{\mu}_i - \mu | \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta} \leq \frac{1}{2}\Delta_i.
+$$
+
+Thus the separation condition still holds for this value of $\delta$.
+
+## Upper Bound on Error Probability
+
+We have seen that on the favorable event $\xi$, which holds with large probability $\mathbb{P}(\xi)$, the separation condition holds as all arms have been pulled a sufficient number of times, such that their estimated mean is close to the true mean.
+All arms are classified correctly, and the algorithm does not suffer a loss.
+On the other hand, we make an error whenever the favorable event does not hold after all; that is, the deviation bound for the mean does not hold.
+At least one arm is misclassified and the arm suffers a loss.
+This occurs with probability $1-\mathbb{P}(\xi)$.
+Consequently, the expected loss is upper bounded by
+
+$$
+\mathbb{E}[L] = 1 - \mathbb{P}(\xi) \leq 2(\log(T)+1)K \exp(-\frac{1}{64R^2}\frac{T}{H})
+$$

### 2017-08-11 Thesis/Draft.Rmd
add long real experiments

@@
 
-# KL and Bayesian Thresholding Bandits
+# Extensions to the Thresholding Bandit Problem
 
@@
 ## Variance Based Algorithms for Thresholding Bandits
+
+### Augmented-UCB Algorithm
 
@@
 
-## New Approaches
+-> Happens for exponential distribution
+
+### Anytime Parameter-free Empirical Variance Guided Algorithm
+
+Another algorithm for the thresholding bandit problem is introduced in Zhong et al.
+(2017).
+Indeed, they discuss several variations of their algorithm which extend their central idea to applications in which several samples need to be pulled in a parallel and asynchronous fashion.
+An easy example known from the multi-armed bandit literature (SOURCE????!!??!?!?!) is a website where different versions are served to customers and each version is an arm in the bandit setting.
+If the feedback that is observed by the algorithm is whether or not a user makes a purchase, then it is likely that a new user arrives before the feedback for the previous user has been observed.
+The algorithm has to pull the next arm before the feedback of the previous arm has been observed.
+With their variants the authors approach this problem of having to take asynchronous and parallel actions.
+But their algorithm can also be reduced to a simpler version that can be compared directly with the problem described in Locatelli et al.
+(2016) where we assume the problem of the feedback lag away.
+
+This simpler version is the anytime parameter-free version of their Empirical Variance Guided Algorithm (EVT$_{pf}$).
+The EVT$_{pf}$ algorithm is a smart extension of the APT algorithm to an approach that takes the empirical variance of the arms into account and deduces an upper bound through Bernstein bounds.
+
+In order to describe their algorithm, we adapt a formulation used in Zhong et al.
+(2017) to describe the index used by the algorithms in a more general fashion.
+Write the index $B_i(t)$ of arm $i$ at round $t$ as previously as
+
+$$
+B_i(t) = S_i(t) D_i(t),
+$$
+
+where $D_i(t)$ is some measure of the distance between the mean $\mu_i$ or the distribution $\nu_i$ of the arm $i$ from the threshold $\tau$, while $S_i(t)$ is some confidence value.
+Thus, for the APT algorithm, if we let $\epsilon = 0$ as in Zhong et al.
+(2016), we have
+
+$$
+D_i^{APT}(t) = \hat{\Delta}_i(t) = |\hat{\mu}_i(t) - \tau| \quad \land \quad S_i^{APT}(t) = \sqrt{T_i(t)}
+$$
+
+We see that $D_i(t)$ is the probably most straightforward distance between the sample mean and the threshold, while $S_i(t)$ increases over time, as we become more confident in our sample mean, and thus ensures that we do not continue pulling the same arm forever.
+
+Based on this, we can now easily compare APT to EVT$_{pf}$ for which the index can be written as:
+
+$$
+D_i^{EVT}(t) = \hat{\Delta}_i(t) = |\hat{\mu}_i(t) - \tau| \quad \land \quad S_i^{EVT}(t) = \Big(\frac{1}{T_i(t) + \sqrt{\frac{1}{T_i(t)}}\hat{\sigma}_{i}(t)}\Big)^{-1}
+$$
+
+or equivalently as
+
+$$
+D_i^{EVT}(t) = \sqrt{\hat{\sigma}^2_{i}(t) + \hat{\Delta}_i(t)} - \hat{\sigma}_i(t) \quad \land \quad S_i^{EVT} = \sqrt{T_i(t)}
+$$
+
+We see that in both formulations either the distance term $D_i$ or the confidence term $S_i$ between the two algorithms is equivalent.
+While the empirical variance is a natural confidence measure -- and thus makes sense in the $S_i^{EVT}$ part in the first equation -- it also describes the shape of the distribution and thus is also a measure of how far the distribution (in contrast to just the mean) is away from the threshold, and thus can belong to $D_i^{EVT}$.
+We will focus on the latter formulation for the remaining paper.
+
+In comparison with the APT algorithm, the EVT$_{pf}$ algorithm adds the empirical variance into the index to measure how well we can expect the distribution (and the mean) to be seperated from the threshold; it serves as a crude measure of distance between threshold and distribution.
+We note that for a Bernoulli distributed random variable, $D_i^{EVT}$ is decreasing as the mean approaches the threshold.
+Similar should hold in general for bounded variables as the variance and the mean are linked by the distance of the mean to the bound of the support (in contrast to, for example, a normal distributed random variable where a change in the mean does not correspond to a change in the variance).
+This is important as the bounds of the EVT$_{pf}$ algorithm only hold for random variables bounded in $[0,1]$.
+
+```{r EVT_Index_Bernoulli, echo = FALSE}
+bfun <- function(mu, tau) sqrt((mu*(1-mu))^2 + abs(tau-mu)) - mu*(1-mu)
+plot(seq(0,1,0.0001), bfun(0,seq(0,1,0.0001)), type = "l",
+     xlab = "Sample Mean", ylab = "Distance $D_i(t)$", main = "Variation over tau")
+for(i in 1:length(seq(0,1,by=0.1))) {
+  lines(seq(0,1,0.0001), bfun(seq(0,1,by=0.1)[i], seq(0,1,0.0001)), 
+        col = rainbow(length(seq(0,1,by=0.1)))[i])
+}
+```
+
+By defining a new complexity measure $H^{\text{EVT}_{pf}}$ for the EVT$_{pf}$ algorithm, Zhong et al.
+(2017) are able to derive an upper bound on the expected loss of the algorithm.
+Let the complexity increase in the variance and decrease in the distance of the mean from the threshold such that
+
+$$
+H^{\text{EVT}_{pf}} = \sum_{i=1}^K h_i^{\text{EVT}_{pf}} = \sum_{i=1}^K (\sigma_i^2\Delta_i^{-2} + \Delta_i^{-1}).
+$$
+
+Then one can state the following theorem.
+
+\begin{theorem}[Theorem 5, Zhong et al., 2017] 
+\label{theorem:ZhongEtAl2017Theorem5}
+Let $K > 0$, $T > 2K$, and consider a thresholding bandit problem. Assume that all arms of the problem are bounded in $[0,1]$. Then the probability of an error is bounded as
+
+\begin{equation*}
+\mathbb{E}[L] \leq TK \exp\Big(-C\frac{T}{H^{\text{EVT}_{pf}}}\Big),
+\end{equation*}
+
+where $C$ is some positive constant.
+\end{theorem}
+
+The authors approach the proof very similarly as Locatelli et al.
+(2016) in the proof of their lower bound.
+They define favorable events that hold with large probability, make sure the same separation condition holds for them given that each arm is pulled often enough.
+Additionally to a favorable event that bounds the deviation between sample mean and population mean, they define a second event on which the sample standard deviation is close to the population standard deviation.
+This is bounded in large probability by a Bernstein inequality.
+The union of the two events then serves as the favorable event in the remainder of their proof.
+
+Given a lower bound that is also adapted to the new complexity $H^{\text{EVT}_{pf}}$, the authors show that the EVT$_pf$ algorithm is optimal.
+Furthermore, they compare their algorithms in experiments against the APT algorithm.
+The experiments use data generated from uniform distributions.
+Each experiment compares 100 arms with variances picked at random from a range of possible variances.
+Over three experiments, the range of variances is varied from small to large, where the authors expect their algorithm to show the largest advantage compared to APT on the problem with small variances.
+Interestingly, they report the largest advantage of their variance based algorithms in comparison to APT when the variances are very small; given they only consider problems bounded on a support of $[0,1]$, $\sigma_i \ll 1$.
+In this case the problem complexity $H^{\text{EVT}_{pf}}$ can be much smaller than $H^{APT}$ -- the EVT algorithm profits more from distributions that are simple to estimate in terms of their variance than the APT algorithm does.
+
+When comparing the two complexities for example for Bernoulli random variables against some fixed threshold, we see that the smaller complexity of the EVT$_{pf}$ algorithm implies in particular that EVT$_{pf}$ could be able to cope with distributions of parameter $\mu$ close to $\tau$ much better than APT.
+
+```{r Hevt_Hapt_Comparison, echo = FALSE, message = FALSE}
+hevt <- function(mu, tau) {
+  (mu*(1-mu))^2 * (abs(mu-tau))^{-2} + abs(mu-tau)^{-1}
+}
+
+hapt <- function(mu, tau) {
+  abs(mu-tau)^{-2}
+}
+
+plot(seq(0.1,0.9,0.0001), 
+     hapt(seq(0.1,0.9,0.0001), 0.5), type = "l",
+     ylim = c(0,400), ylab = "Complexity", xlab = "Bernoulli Mean",
+     main = "APT vs EVT Complexity for tau = 0.5")
+lines(c(seq(0.1,0.9,0.0001)), 
+      hevt(c(seq(0.1,0.9,0.0001)), 0.5),
+      col = "blue")
+abline(v = 0.5, lty = 2)
+```
+
+## Likelihood Ratio for Exponential Family Distributions
+
+We now present an approach that builds on the idea of the likelihood ratio statistic for hypothesis tests.
+We first present the general idea of likelihood ratio based tests, and then introduce our new algorithm for the thresholding bandit problem.
+
+### Likelihood Ratio-based Hypothesis Tests
+
+In a standard parametric testing problem, we have drawn an iid sample $x = (x_1, ..., x_T)$, where each $x_i$ is a realization from the random variable $X_i$.
+We assume that $X_i$ follows some probability distribution $Q(\theta)$ paramaterized by a vector $\theta$.
+Let $q(x;\theta)$ be the density function corresponding to the distribution.
+In a standard hypothesis test, we test whether an alternative parameterization is more likely than the parameterization given by the null hypothesis.
+That is, we test
+
+$$
+H_0: \quad \theta = \theta_{H_0} \qquad \text{vs.} \qquad H_1: \quad \theta = \theta_{H_1}
+$$
+
+In order to assess whether the $H_0$ hypothesis can be rejected, one computes the likelihood $L(x|\theta)$ of the observed sample under both parameterizations: $L_{H_0} = L(x|\theta = \theta_{H_0}) = \prod_{i=1}^T q(x_i|\theta_{H_0})$ and $L_{H_1} = L(x|\theta = \theta_{H_1}) = \prod_{i=1}^T q(x_i|\theta_{H_1})$.
+The likelihood ratio test statistic is then given as
+
+$$
+LR(\theta_{H_0}|| \theta_{H_1}) = \frac{L_{H_0}}{L_{H_1}} = \prod_{i=1}^T\frac{q(x_i|\theta_{H_0})}{ q(x_i|\theta_{H_1})}.
+$$
+The intuition behind the test of course being that, if the true parameterization is $H_1$ and not $H_0$, then the likelihood $L_{H_1}$ should be larger than $L_{H_0}$.
+A small enough likelihood ratio would thus lead us to a rejection of the null hypothesis, while a large likelihood ratio is evidence in favor of the null hypothesis.
+
+Consider an example in which we assume that the sample stems from a normal distribution with unknown mean but known variance $\sigma^2 = 1$ such that $X_i \sim N(\mu, 1)$.
+We test $H_0: \mu = \mu_0$ against $H_1: \mu = \mu_1$.
+
+### Likelihood Ratio-based Thresholding Bandit
+
+# Experiments
+
+## Real Data
+
+We show two experiments that were performed on real data.
+While most papers in the multi-armed bandit literature resort to synthetic data to assess the performance of algorithms -- just as we have done in the previous chapter -- we have tried to acquire real world data.
+This data is what bandit algorithms are used for in practice, and does not fulfill the standard independence and identical distribution assumptions as nicely.
+The real data thus can be considered a first robustness test for the algorithms.
+
+### The Data Set
+
+The data have been collected by the German ecommerce company [Amorelie](https://amorelie.de) as part of standard website performance tracking.
+For 197 selected products, we have the number of users visiting each product's detail page at a given minute.
+The data set we use here has been collected during the entire month of November 2016.
+It can be considered time series data collected at minutely frequency.
+Thus the data contain 43200 observations per product, and overall 8510400 observations.
+
+Given that we want to run an offline comparison of bandit algorithms, it is important to have at each time point an observation for each arm.
+Given that, it is easy to evaluate the perfomance of algorithms that make different decisions at different point in times and thus do not observe the same samples.
+By having an observation for each arm at any given time point, each algorithm had at least the opportunity to observe a certain sample.
+Other papers (CITE YAHOO!) have solved this problem by using a sample drawn uniformly during for example an A/B test.
+Then, if the next observation in the sample is not from the same arm that the algorithm would like to draw from, observations are discarded until the next observation from the selected arm.
+
+The choice of having basically multiple time series data as the sample leads to a simple way of running the algorithms just as often on the data as for simulated data.
+In particular, the goal is to perform 5000 runs over the sample to confidently assess the performance.
+Since we wanted to preserve the potential time dependency of the data, a simple resampling of the data was not an option to create the needed 5000 variations of the sample.
+Thus what we did instead was a form of time series cross validation.
+To preserve the autocorrelation, one can create different samples of $X$ observations by sliding a window of size $X$ over the time series.
+Moving the window one period (in our case minute) at a time, one ensures that no sample shares start and end observation with another sample.
+In particular, this means for a given bandit strategy and two samples that the observations that the algorithm collects as feedback during the two initialization phases differ from sample to sample and are never the same.
+This is because during initialization every strategy pulls arms $1, ..., K$ once in this order.

### 2017-08-11 Thesis/Draft.tex
add long real experiments

@@
 
-\section{KL and Bayesian Thresholding
-Bandits}\label{kl-and-bayesian-thresholding-bandits}
+\section{Extensions to the Thresholding Bandit
+Problem}\label{extensions-to-the-thresholding-bandit-problem}
 
@@
 Bandits}\label{variance-based-algorithms-for-thresholding-bandits}
+
+\subsubsection{Augmented-UCB Algorithm}\label{augmented-ucb-algorithm}
 
@@
 
-\subsection{New Approaches}\label{new-approaches}
+-\textgreater{} Happens for exponential distribution
+
+\subsubsection{Anytime Parameter-free Empirical Variance Guided
+Algorithm}\label{anytime-parameter-free-empirical-variance-guided-algorithm}
+
+Another algorithm for the thresholding bandit problem is introduced in
+Zhong et al. (2017). Indeed, they discuss several variations of their
+algorithm which extend their central idea to applications in which
+several samples need to be pulled in a parallel and asynchronous
+fashion. An easy example known from the multi-armed bandit literature
+(SOURCE????!!??!?!?!) is a website where different versions are served
+to customers and each version is an arm in the bandit setting. If the
+feedback that is observed by the algorithm is whether or not a user
+makes a purchase, then it is likely that a new user arrives before the
+feedback for the previous user has been observed. The algorithm has to
+pull the next arm before the feedback of the previous arm has been
+observed. With their variants the authors approach this problem of
+having to take asynchronous and parallel actions. But their algorithm
+can also be reduced to a simpler version that can be compared directly
+with the problem described in Locatelli et al. (2016) where we assume
+the problem of the feedback lag away.
+
+This simpler version is the anytime parameter-free version of their
+Empirical Variance Guided Algorithm (EVT\(_{pf}\)). The EVT\(_{pf}\)
+algorithm is a smart extension of the APT algorithm to an approach that
+takes the empirical variance of the arms into account and deduces an
+upper bound through Bernstein bounds.
+
+In order to describe their algorithm, we adapt a formulation used in
+Zhong et al. (2017) to describe the index used by the algorithms in a
+more general fashion. Write the index \(B_i(t)\) of arm \(i\) at round
+\(t\) as previously as
+
+\[
+B_i(t) = S_i(t) D_i(t),
+\]
+
+where \(D_i(t)\) is some measure of the distance between the mean
+\(\mu_i\) or the distribution \(\nu_i\) of the arm \(i\) from the
+threshold \(\tau\), while \(S_i(t)\) is some confidence value. Thus, for
+the APT algorithm, if we let \(\epsilon = 0\) as in Zhong et al. (2016),
+we have
+
+\[
+D_i^{APT}(t) = \hat{\Delta}_i(t) = |\hat{\mu}_i(t) - \tau| \quad \land \quad S_i^{APT}(t) = \sqrt{T_i(t)}
+\]
+
+We see that \(D_i(t)\) is the probably most straightforward distance
+between the sample mean and the threshold, while \(S_i(t)\) increases
+over time, as we become more confident in our sample mean, and thus
+ensures that we do not continue pulling the same arm forever.
+
+Based on this, we can now easily compare APT to EVT\(_{pf}\) for which
+the index can be written as:
+
+\[
+D_i^{EVT}(t) = \hat{\Delta}_i(t) = |\hat{\mu}_i(t) - \tau| \quad \land \quad S_i^{EVT}(t) = \Big(\frac{1}{T_i(t) + \sqrt{\frac{1}{T_i(t)}}\hat{\sigma}_{i}(t)}\Big)^{-1}
+\]
+
+or equivalently as
+
+\[
+D_i^{EVT}(t) = \sqrt{\hat{\sigma}^2_{i}(t) + \hat{\Delta}_i(t)} - \hat{\sigma}_i(t) \quad \land \quad S_i^{EVT} = \sqrt{T_i(t)}
+\]
+
+We see that in both formulations either the distance term \(D_i\) or the
+confidence term \(S_i\) between the two algorithms is equivalent. While
+the empirical variance is a natural confidence measure -- and thus makes
+sense in the \(S_i^{EVT}\) part in the first equation -- it also
+describes the shape of the distribution and thus is also a measure of
+how far the distribution (in contrast to just the mean) is away from the
+threshold, and thus can belong to \(D_i^{EVT}\). We will focus on the
+latter formulation for the remaining paper.
+
+In comparison with the APT algorithm, the EVT\(_{pf}\) algorithm adds
+the empirical variance into the index to measure how well we can expect
+the distribution (and the mean) to be seperated from the threshold; it
+serves as a crude measure of distance between threshold and
+distribution. We note that for a Bernoulli distributed random variable,
+\(D_i^{EVT}\) is decreasing as the mean approaches the threshold.
+Similar should hold in general for bounded variables as the variance and
+the mean are linked by the distance of the mean to the bound of the
+support (in contrast to, for example, a normal distributed random
+variable where a change in the mean does not correspond to a change in
+the variance). This is important as the bounds of the EVT\(_{pf}\)
+algorithm only hold for random variables bounded in \([0,1]\).
+
+\includegraphics{Draft_files/figure-latex/EVT_Index_Bernoulli-1.pdf}
+
+By defining a new complexity measure \(H^{\text{EVT}_{pf}}\) for the
+EVT\(_{pf}\) algorithm, Zhong et al. (2017) are able to derive an upper
+bound on the expected loss of the algorithm. Let the complexity increase
+in the variance and decrease in the distance of the mean from the
+threshold such that
+
+\[
+H^{\text{EVT}_{pf}} = \sum_{i=1}^K h_i^{\text{EVT}_{pf}} = \sum_{i=1}^K (\sigma_i^2\Delta_i^{-2} + \Delta_i^{-1}).
+\]
+
+Then one can state the following theorem.
+
+\begin{theorem}[Theorem 5, Zhong et al., 2017] 
+\label{theorem:ZhongEtAl2017Theorem5}
+Let $K > 0$, $T > 2K$, and consider a thresholding bandit problem. Assume that all arms of the problem are bounded in $[0,1]$. Then the probability of an error is bounded as
+
+\begin{equation*}
+\mathbb{E}[L] \leq TK \exp\Big(-C\frac{T}{H^{\text{EVT}_{pf}}}\Big),
+\end{equation*}
+
+where $C$ is some positive constant.
+\end{theorem}
+
+The authors approach the proof very similarly as Locatelli et al. (2016)
+in the proof of their lower bound. They define favorable events that
+hold with large probability, make sure the same separation condition
+holds for them given that each arm is pulled often enough. Additionally
+to a favorable event that bounds the deviation between sample mean and
+population mean, they define a second event on which the sample standard
+deviation is close to the population standard deviation. This is bounded
+in large probability by a Bernstein inequality. The union of the two
+events then serves as the favorable event in the remainder of their
+proof.
+
+Given a lower bound that is also adapted to the new complexity
+\(H^{\text{EVT}_{pf}}\), the authors show that the EVT\(_pf\) algorithm
+is optimal. Furthermore, they compare their algorithms in experiments
+against the APT algorithm. The experiments use data generated from
+uniform distributions. Each experiment compares 100 arms with variances
+picked at random from a range of possible variances. Over three
+experiments, the range of variances is varied from small to large, where
+the authors expect their algorithm to show the largest advantage
+compared to APT on the problem with small variances. Interestingly, they
+report the largest advantage of their variance based algorithms in
+comparison to APT when the variances are very small; given they only
+consider problems bounded on a support of \([0,1]\), \(\sigma_i \ll 1\).
+In this case the problem complexity \(H^{\text{EVT}_{pf}}\) can be much
+smaller than \(H^{APT}\) -- the EVT algorithm profits more from
+distributions that are simple to estimate in terms of their variance
+than the APT algorithm does.
+
+When comparing the two complexities for example for Bernoulli random
+variables against some fixed threshold, we see that the smaller
+complexity of the EVT\(_{pf}\) algorithm implies in particular that
+EVT\(_{pf}\) could be able to cope with distributions of parameter
+\(\mu\) close to \(\tau\) much better than APT.
+
+\includegraphics{Draft_files/figure-latex/Hevt_Hapt_Comparison-1.pdf}
+
+\subsection{Likelihood Ratio for Exponential Family
+Distributions}\label{likelihood-ratio-for-exponential-family-distributions}
+
+We now present an approach that builds on the idea of the likelihood
+ratio statistic for hypothesis tests. We first present the general idea
+of likelihood ratio based tests, and then introduce our new algorithm
+for the thresholding bandit problem.
+
+\subsubsection{Likelihood Ratio-based Hypothesis
+Tests}\label{likelihood-ratio-based-hypothesis-tests}
+
+In a standard parametric testing problem, we have drawn an iid sample
+\(x = (x_1, ..., x_T)\), where each \(x_i\) is a realization from the
+random variable \(X_i\). We assume that \(X_i\) follows some
+distribution \(Q(\theta)\) paramaterized by a vector \(\theta\). In a
+standard hypothesis test, we would then want to test whether an
+alternative parameterization is more likely than the parameterization
+given by the null hypothesis. That is, we test
+
+\[
+H_0: \quad \theta = \theta_{H_0} \qquad \text{vs.} \qquad H_1: \quad \theta = \theta_{H_1}
+\]
+
+In order to assess whether the \(H_0\) hypothesis can be rejected, one
+computes the likelihood \(L(x|\theta)\) of the observed sample under
+both parameterizations: \(L_{H_0} = L(x|\theta = \theta_{H_0})\) and
+\(L_{H_1} = L(x|\theta = \theta_{H_1})\). The likelihood ratio test
+statistic is then given as
+
+\[
+LR(\theta_{H_0}|| \theta_{H_1}) = \frac{L_{H_0}}{L_{H_1}}.
+\] The intuition behind the test of course being that, if the true
+parameterization is \(H_1\) and not \(H_0\), then the likelihood
+\(L_{H_1}\) should be larger than \(L_{H_0}\). A small enough likelihood
+ratio would thus lead us to a rejection of the null hypothesis, while a
+large likelihood ratio is evidence in favor of the null hypothesis.
+
+\subsubsection{Likelihood Ratio-based Thresholding
+Bandit}\label{likelihood-ratio-based-thresholding-bandit}
 

### 2017-08-11 AugUCB/run_from_data.R

@@ -63,14 +63,18 @@ AugUCB_from_tsdata <- function(data, rounds = 5000, rho = 1/3, tau = NA,
   
   for(i in (K+1):rounds) {
     if(verbose) message(paste("this is round", i))
-    next_arm <- get_min(unlist(get_next_arm_augucb(arm_list, tau = tau, rho = rho,
-                                                   psi = psi, rounds = rounds, 
-                                                   epsilon = epsilon,
-                                                   active_set = B)))
-    arm_sequence <- c(arm_sequence, next_arm)
-    if(verbose) message("arm selecting done")
+    if(length(B) > 0) {
+      next_arm <- get_min(unlist(get_next_arm_augucb(arm_list, tau = tau, rho = rho,
+                                                     psi = psi, rounds = rounds, 
+                                                     epsilon = epsilon,
+                                                     active_set = B)))
+      arm_sequence <- c(arm_sequence, next_arm)
+      if(verbose) message("arm selecting done")
+      
+      arm_list[[next_arm]] <- c(arm_list[[next_arm]], data[i, next_arm])
+    }
     
-    arm_list[[next_arm]] <- c(arm_list[[next_arm]], data[i, next_arm])
+    # Continue adding the same mean if the active set is empty
     mean_storage <- rbind(mean_storage, unlist(lapply(arm_list, mean)))
     if(verbose) message("arm pulling done")
     
@@ -78,14 +82,16 @@ AugUCB_from_tsdata <- function(data, rounds = 5000, rho = 1/3, tau = NA,
     if(verbose) message("Counter: ", counter)
     
     # delete arms should return a logical index for each arm in active set
-    B <- B[!unlist(delete_arms(arm_list, tau = tau, rho = rho,
-                               psi = psi, rounds = rounds, epsilon = epsilon,
-                               active_set = B))]
+    if(length(B) > 0) { # stop updating the active set if already empty
+      B <- B[!unlist(delete_arms(arm_list, tau = tau, rho = rho,
+                                 psi = psi, rounds = rounds, epsilon = epsilon,
+                                 active_set = B))]
+    }
     
     if(verbose) message("B done")
     if(verbose) message(B)
     
-    if((i >= N) && (m <= M)) {
+    if((i >= N) & (m <= M) & (length(B)>0)) {
[…]

### 2017-08-11 AugUCB/run_parallelized_from_data.R

@@ -209,8 +209,7 @@ para_bandit_sim_LR <- function(data, seed = NA, do_verbose = FALSE, ...) {
   registerDoParallel(cl)
   res <- foreach(j = 1:reps, #.errorhandling = 'remove',
                  .export = c("LR_bandit_from_tsdata", "get_next_arm_lr",
-                             "get_min", "lr_ber", "lr_gaussian", "lr_exponential",
-                             "get_next_arm_lr_gaussian", "get_next_arm_lr_exponential"), 
+                             "get_min", "lr_ber"), 
                  .verbose = do_verbose, .inorder = TRUE) %dopar% {
                    alg_res <- LR_bandit_from_tsdata(data = data[[j]], 
                                               seed = 512+j, ...)
@@ -306,7 +305,7 @@ para_bandit_sim_AugUCB <- function(data, seed = NA, do_verbose = FALSE, ...) {
   gc()
   cl <- makeCluster(max(1,detectCores()-1))
   registerDoParallel(cl)
-  res <- foreach(j = 1:reps, .errorhandling = 'remove',
+  res <- foreach(j = 1:reps, #.errorhandling = 'remove',
                  .export = c("AugUCB_from_tsdata", "get_next_arm_augucb",
                              "get_min", "delete_arms"), 
                  .verbose = do_verbose, .inorder = TRUE) %dopar% {

### 2017-08-11 real_experiments/real_exp_1week_1.R

@@ -1,0 +1,254 @@
+####################################################################
+
+# This script loads real data for 10 products out of 197 products.
+# We look at 10080 rounds per iteration so as to cover a whole week.
+# This is useful to account for seasonality effects in the data (if
+# looking at uniformly sampled data).
+
+####################################################################
+
+sessions_threshold <- 0
+set.seed(1068)
+selected_products <- sample(1:197, 10)
+niter <- 5000
+nrounds <- 10080 # These two values give the maximum size data 
+nahead <- 10080  # possible given the data set size we have
+source("/Users/timradtke/Desktop/thesis_data/get_dataset.R")
+
+dim(pv_list[[1]])
+pv_list[[1]]
+
+pv_list[[1]]
+pv_list[[5000]]
+tail(pv_list[[5000]])
+round(pv_next_means[[5000]],4)
+round(pv_next_means[[1]],4)
+
+####################################################################
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/"
+
+####################################################################
+
+data_amo3 <- pv_list
+data_amo3_wide <- pv_products_wide
+data_amo3_own_means <- pv_own_means
+data_amo3_next_means <- pv_next_means
+data_amo3_mean_secondhalf <- colMeans(data_amo3_wide[15081:25160,])
+data_amo3_mean_middlehalf <- colMeans(data_amo3_wide[10081:20160,])
+data_amo3_mean_firsthalf <- colMeans(data_amo3_wide[1:15080,])
+save(data_amo3, file = paste0(current_path, "data_amo3.Rda"))
+save(data_amo3_wide, file = paste0(current_path, "data_amo3_wide.Rda"))
+save(data_amo3_own_means, file = paste0(current_path, "data_amo3_own_means.Rda"))
+save(data_amo3_next_means, file = paste0(current_path, "data_amo3_next_means.Rda"))
+save(data_amo3_mean_firsthalf, file = paste0(current_path, "data_amo3_mean_firsthalf.Rda"))
+save(data_amo3_mean_secondhalf, file = paste0(current_path, "data_amo3_mean_secondhalf.Rda"))
+rm(pv_list, pv_own_means, pv_next_means, pv_products_wide)
+gc()
+
[…]

### 2017-08-11 real_experiments/real_exp_1week_2.R

@@ -1,0 +1,254 @@
+####################################################################
+
+# This script loads real data for 10 products out of 197 products.
+# We look at 10080 rounds per iteration so as to cover a whole week.
+# This is useful to account for seasonality effects in the data (if
+# looking at uniformly sampled data).
+
+####################################################################
+
+sessions_threshold <- 0
+set.seed(357458)
+selected_products <- sample(1:197, 10)
+niter <- 5000
+nrounds <- 10080 # These two values give the maximum size data 
+nahead <- 10080  # possible given the data set size we have
+source("/Users/timradtke/Desktop/thesis_data/get_dataset.R")
+
+dim(pv_list[[1]])
+pv_list[[1]]
+
+pv_list[[1]]
+pv_list[[5000]]
+tail(pv_list[[5000]])
+round(pv_next_means[[5000]],4)
+round(pv_next_means[[1]],4)
+
+####################################################################
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/"
+
+####################################################################
+
+data_amo4 <- pv_list
+data_amo4_wide <- pv_products_wide
+data_amo4_own_means <- pv_own_means
+data_amo4_next_means <- pv_next_means
+data_amo4_mean_secondhalf <- colMeans(data_amo4_wide[15081:25160,])
+data_amo4_mean_middlehalf <- colMeans(data_amo4_wide[10081:20160,])
+data_amo4_mean_firsthalf <- colMeans(data_amo4_wide[1:15080,])
+save(data_amo4, file = paste0(current_path, "data_amo4.Rda"))
+save(data_amo4_wide, file = paste0(current_path, "data_amo4_wide.Rda"))
+save(data_amo4_own_means, file = paste0(current_path, "data_amo4_own_means.Rda"))
+save(data_amo4_next_means, file = paste0(current_path, "data_amo4_next_means.Rda"))
+save(data_amo4_mean_firsthalf, file = paste0(current_path, "data_amo4_mean_firsthalf.Rda"))
+save(data_amo4_mean_secondhalf, file = paste0(current_path, "data_amo4_mean_secondhalf.Rda"))
+rm(pv_list, pv_own_means, pv_next_means, pv_products_wide)
[…]

### 2017-08-11 synthetic_experiments/exponential/exp_exp_2.R

@@ -34,6 +34,7 @@ gc()
 load(paste0(current_path, "exp2_comp_LR.Rda"))
 load(paste0(current_path, "exp2_comp_APT.Rda"))
 load(paste0(current_path, "exp2_comp_EVT.Rda"))
+load(paste0(current_path, "exp2_comp_UNIFORM.Rda"))
 
 plot(c(0,4000), c(0, -8), type = "n")
 abline(h=log(0.01), lty = 2)
@@ -90,19 +91,26 @@ gc()
 system.time(exp2_UNIFORM <- para_bandit_sim_uniform(data = data_list_exp2, 
                                                     rounds = 4000))
 save(exp2_UNIFORM, file = paste0(current_path, "exp2_UNIFORM.Rda"))
-exp2_comp_UNIFORM <- compare_to_ground_truth(mean_exp2, 
+exp2_comp_UNIFORM <- compare_to_ground_truth(mu_exp2, 
                                                exp2_UNIFORM, 
                                                tau_exp2, 
                                                epsilon_exp2)$mean
 save(exp2_comp_UNIFORM, file = paste0(current_path, "exp2_comp_UNIFORM.Rda"))
+rm(exp2_UNIFORM)
+gc()
 
 ########################################################################
 # Augmented-UCB (Mukherjee et al., 2017)
+
+#augtest <- AugUCB_from_tsdata(data = data_list_exp2[[1]], rounds = 2000, tau = tau_exp2,
+#                   verbose = TRUE)
 
 exp2_AugUCB <- para_bandit_sim_AugUCB(data = data_list_exp2, 
                                       rounds = 4000, 
                                       tau = tau_exp2)
 save(exp2_AugUCB, file = paste0(current_path, "exp2_AugUCB.Rda"))
-exp2_comp_AugUCB <- compare_to_ground_truth(mean_exp2, exp2_AugUCB, 
+exp2_comp_AugUCB <- compare_to_ground_truth(mu_exp2, exp2_AugUCB, 
                                             tau_exp2, epsilon_exp2)$mean
 save(exp2_comp_AugUCB, file = paste0(current_path, "exp2_comp_AugUCB.Rda"))
+rm(exp2_AugUCB)
+gc()

### 2017-08-11 synthetic_experiments/poisson/exp_pois_1.R

@@ -4,7 +4,7 @@
 current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
 source(paste0(current_path, "run_from_data.R"))
 source(paste0(current_path, "run_parallelized_from_data.R"))
-current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/exponential/"
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/poisson/"
 
 ########################################################################
 # Create the data from exponential distributions
@@ -14,16 +14,16 @@ tau_pois1 <- 1
 epsilon_pois1 <- 0
 mu_pois1 <- rexp(20, 1/5)
 
-plot(c(0,8), c(0,2), type = "n")
-for(i in order(mu_pois1)) {
-  lines(seq(0,8,0.001), dpois(seq(0,8,0.001), mu_pois1[i]), col = rainbow(length(mu_pois1))[i])
-}
+#plot(c(0,8), c(0,2), type = "n")
+#for(i in order(mu_pois1)) {
+#  lines(seq(0,8,0.001), dpois(seq(0,8,0.001), mu_pois1[i]), col = rainbow(length(mu_pois1))[i])
+#}
 
 data_list_pois1 <- list()
 for(j in 1:5000) {
-  curr_data <- data.frame(rep(NA, times = 10000))
+  curr_data <- data.frame(rep(NA, times = 5000))
   for(i in 1:length(mu_pois1)) {
-    curr_data[[i]] <- as.numeric(rpois(10000, 1/mu_pois1[i]))
+    curr_data[[i]] <- as.numeric(rpois(5000, mu_pois1[i]))
   }
   names(curr_data) <- paste0("V", rep(1:length(mu_pois1)))
   data_list_pois1[[j]] <- curr_data
@@ -39,9 +39,10 @@ lines(log(pois1_comp_LR), col = "blue")
 lines(log(pois1_comp_EVT), col = "red")
 
 ########################################################################
-# Gaussian Likelihood Ratio
+# Poisson Likelihood Ratio
+
 system.time(pois1_LR <- para_bandit_sim_LR_poisson(data = data_list_pois1, 
-                                                   rounds = 10000, 
+                                                   rounds = 5000, 
                                                    tau = tau_pois1, 
                                                    epsilon = epsilon_pois1))
 
[…]

### 2017-08-11 synthetic_experiments/poisson/exp_pois_2.R

@@ -1,0 +1,107 @@
+########################################################################
+# load functions
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/poisson/"
+
+########################################################################
+# Create the data from exponential distributions
+
+set.seed(3795969)
+tau_pois2 <- 0.4
+epsilon_pois2 <- 0
+mu_pois2 <- rexp(20, 1/0.7)
+
+#plot(c(0,8), c(0,2), type = "n")
+#for(i in order(mu_pois2)) {
+#  lines(seq(0,8,0.001), dpois(seq(0,8,0.001), mu_pois2[i]), col = rainbow(length(mu_pois2))[i])
+#}
+
+data_list_pois2 <- list()
+for(j in 1:5000) {
+  curr_data <- data.frame(rep(NA, times = 10000))
+  for(i in 1:length(mu_pois2)) {
+    curr_data[[i]] <- as.numeric(rpois(10000, mu_pois2[i]))
+  }
+  names(curr_data) <- paste0("V", rep(1:length(mu_pois2)))
+  data_list_pois2[[j]] <- curr_data
+}
+gc()
+
+########################################################################
+
+plot(c(0,10000), c(0, -8), type = "n")
+abline(h=log(0.01), lty = 2)
+lines(log(pois2_comp_APT), col = "black")
+lines(log(pois2_comp_LR), col = "blue")
+lines(log(pois2_comp_EVT), col = "red")
+
+########################################################################
+# Poisson Likelihood Ratio
+
+system.time(pois2_LR <- para_bandit_sim_LR_poisson(data = data_list_pois2, 
+                                                   rounds = 10000, 
+                                                   tau = tau_pois2, 
+                                                   epsilon = epsilon_pois2))
+
+save(pois2_LR, file = paste0(current_path, "pois2_LR.Rda"))
+pois2_comp_LR <- compare_to_ground_truth(mu_pois2, pois2_LR, 
+                                         tau_pois2, epsilon_pois2)$mean
+save(pois2_comp_LR, file = paste0(current_path, "pois2_comp_LR.Rda"))
+rm(pois2_LR)
+gc()
+
[…]

### 2017-08-12 Thesis/Draft.Rmd
Add exponential family to draft

@@
 
-Consider an example in which we assume that the sample stems from a normal distribution with unknown mean but known variance $\sigma^2 = 1$ such that $X_i \sim N(\mu, 1)$.
-We test $H_0: \mu = \mu_0$ against $H_1: \mu = \mu_1$.
+By considering $lr = -2\log(LR(\theta_{H_0}|| \theta_{H_1}))$, one has a statistic that is $\chi^2$ distributed with degrees of freedom that depend on the null and alternative hypothesis.
+Assessing whether the null hypothesis can be rejected with large confidence thus becomes straightforward.
 
 ### Likelihood Ratio-based Thresholding Bandit
+
+The simple concept of the likelihood-ratio test serves as foundation for a new sampling strategy that can be applied to the thresholding bandit problem.
+In contrast to the cumulative regret problem, or even the best arm identification problem, we have some sort of null hypothesis for the distributions in the thresholding bandit problem.
+In case of no information and no observed samples, the null hypothesis might simply be that all distributions have a mean that equals the threshold.
+By observing samples, we then want to test whether the mean of the distributions is different from the threshold $\tau$ in either direction.
+Once we are sure that there is a difference, we do not want to continue to test.
+Instead, we would like to focus our sampling effort on a different arm where we are not as sure.
+The likelihood ratio quantifies how "significant"" of a difference there is between the threshold $\tau$ and the current sample mean $\hat{\mu}_i(t)$ of an arm.
+Given that we plug in the sample mean, that is, the maximum likelihood estimator for the true mean for many distributions, the likelihood ratio will be smaller than 1 and decrease in sample size even if the threshold and sample mean are constant.
+
+Due to these characteristics, the likelihood ratio can serve as a natural index for sampling strategies. Thus write as index
+
+$$
+B_i(t) = LR(\tau|| \hat{\mu}_i(t)) = \prod_{i=1}^T\frac{q(x_i|\tau)}{ q(x_i|\hat{\mu}_i(t))}
+$$
+
+and pull at round $t$ the arm $i^* = \arg \max_i B_i(t)$.
+As we described in the previous paragraph, we have $B_i(t) \leq 1$, $t \uparrow \rightarrow B_i(t) \downarrow$, and $|\hat{\mu}_i(t) - \tau| \uparrow \rightarrow B_i(t) \downarrow$.
+Consequently, by choosing the arm that maximizes $B_i(t)$, we choose an arm for which we either have not collected many samples, or where the sample mean is close to the threshold $\tau$.
+In this sense, a strategy based on the likelihood ratio is of course very reminiscient of the index employed by the APT algorithm.
+Indeed, assuming the samples are normally distributed with the same variance for the distribution $\nu_i$ under both $H_0$ and $H_1$, then $-\log(LR(\tau||\hat{\mu}_i(t)))$ equals the index in APT.
+Why then would one use the likelihood based strategy?
+
+Given that the APT index and the likelihood-ratio based index are only equivalent for normally distributed random variables with fixed standard deviation, the new strategy promises efficiency improvements whenever the true distribution is known and different from the normal distribution.
+The most important example are Bernoulli arms with small means as discussed before.
+Here, it is also easy to assume that the true distribution is known upfront.
+Similarly, the likelihood ratio statistic can be used for other univariate distributions of the exponential family.
+But we also propose a version for the Normal distribution with unknown mean.
+
+We now focus on the case where the distributions $\nu_{\theta_1}, ..., \nu_{\theta_K}$ are all the same canonical exponential family of distributions with scalar parameter $\theta_i \in \Theta$.
+The probability density function of the absolutely continuous distribution $\nu_{\theta_i}$ with regard to a dominating measure $\rho$ on $\mathbb{R}$ is given by $q(x|\theta) = h(x) \exp(T(x)\theta - b(\theta))$.
+As described in Cappé et al.
+(2013), citing Lehmann and Casella (1998), the derivative $b'(\theta)$ of $b(\theta)$ is an increasing continuous function such that the expected value $\mathbb{E}(\nu_{\theta}) = b'(\theta)$ for all $\theta \in \Theta$.
+Given that $b'(x)$ is strictly convex, we have a one-to-one relation between $b'(\theta)$ and $\mathbb{E}(\nu_{\theta})$ through the continuous inverse $b'^{-1}(\theta)$.
+Consequently, one can just as well parameterize the distribution its mean $\mu = \mathbb{\nu_{\theta}}$ and write $\nu_{b'^{-1}(\mu)}$ with the probability density function
+
+$$
+q(x|b'^{-1}(\mu)) = h(x) \exp(T(x) b'^{-1}(\mu) - b(b'^{-1}(\mu))).
+$$
+
+This lets us write the likelihood ratio for the exponential family distributions as
+
+$$
+LR(b'^{-1}(\mu_0)||b'^{-1}(\mu_1)) = \prod_{i=1}^n \frac{\exp(T(x_i) b'^{-1}(\mu_0) - b(b'^{-1}(\mu_0)))}{\exp(T(x_i) b'^{-1}(\mu_1) - b(b'^{-1}(\mu_1)))}
+$$
+
+or if we write it as negative log-likelihood ratio:
+
+$$
+-\log(LR) = n\Big(b\big(b'^{-1}(\mu_0)) - b(b'^{-1}(\mu_1)\big)\Big) - \Big(b'^{-1}(\mu_0)-b'^{-1}(\mu_1)\Big)\sum_{i=1}^nT(x_i)
+$$
+
+As we will see now, this statistic is easily derived for many specific distributions.
+
+#### Example 1: Bernoulli Distribution
+
+We have $T(x_i) = x_i$, $\theta = \log(\mu/(1-\mu))$, $\Theta = (0,1)$, $b(\theta) = \log(1+\exp(\theta))$, and $\mu \in (0,1)$. Then $b'(\theta) = \mu$, and we can write
+
+$$
+-\log(LR(\mu_0||\mu_1)) = n(\log\Big(\frac{1-\mu_0}{1-\mu_1}\Big)) - \Big(\log(\frac{\mu_0}{1-\mu_0}) - \log(\frac{\mu_1}{1-\mu_1})\Big)\sum_{i=1}^{n}x_i = (1-\hat{\mu})\log\Big(\frac{1-\mu_1}{1-\mu_0}\Big) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0})
+$$
+
+We observe that, if we let $\mu_0 = \tau$ and $\mu_1 = \hat{\mu}$, then
+
+$$
+-\log(LR(\tau||\hat{\mu})) = KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = d(\hat{\mu},\tau)
+$$
+
+#### Example 2: Poisson Distribution
+
+We have $T(x_i) = x_i$, $\theta = \log(\mu)$, $\Theta = \mathbb{R}$, $b(\theta) = \exp(\theta)$, and $\mu \in (0, +\infty)$. Then $b'(\theta) = \mu$, and we can write:
+
+$$
+-\log(LR(\mu_0||\mu_1)) = n(\mu_0 - \mu_1) - (\log(\mu_0) - \log(\mu_1))\sum_{i=1}^n x_i = (\mu_0 - \mu_1) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}\Big)
+$$
+
+We observe that, if we let $\mu_0 = \tau$ and $\mu_1 = \hat{\mu}$, then
+
+$$
+-\log(LR(\tau||\hat{\mu})) = KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = d(\hat{\mu},\tau) = (\tau - \hat{\mu}) + \hat{\mu}\log\Big(\frac{\hat{\mu}}{\tau}\Big)
+$$
+
+#### Example 3: Normal distributions with known variance $\sigma^2$
+
+We have $T(x_i) = x_i$, $\theta = \mu/\sigma^2$, $\Theta = \mathbb{R}$, $b(\theta) = \sigma^2\theta^2/2$, $\mu \in \mathbb{R}$. Then $b'(\theta) = \mu$, and we can write
+
+$$
+-\log(LR(\mu_0||\mu_1)) = n (\frac{\mu_0^2}{2\sigma^2} - \frac{\mu_1^2}{2\sigma^2}) - (\frac{\mu_0}{\sigma^2} - \frac{\mu_1}{\sigma^2})\sum_{i=1}^nx_i = \frac{1}{2\sigma^2}\Big(\mu_0^2-\mu_1^2 - 2\mu_0\hat{\mu} + 2\mu_1\hat{\mu}\Big)
+$$
+
+And again, if we let $\mu_1 = \hat{\mu}$ and $\mu_0 = \tau$, then
+
+$$
+-\log(LR(\tau||\hat{\mu})) = KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = d(\hat{\mu},\tau) = \frac{(\hat{\mu} - \tau)^2}{2\sigma^2}.
+$$
 
@@
 The data have been collected by the German ecommerce company [Amorelie](https://amorelie.de) as part of standard website performance tracking.
-For 197 selected products, we have the number of users visiting each product's detail page at a given minute.
+For 197 selected products, we have the number of users visiting each product's detail page (PDP) at a given minute.
 The data set we use here has been collected during the entire month of November 2016.
@@
 This is because during initialization every strategy pulls arms $1, ..., K$ once in this order.
+
+While the data is count data (the number of visits to a PDP during a given minute), we binarize the data by applying a certain threshold.
+If the counts is above this threshold, the observation becomes a $1$, else $0$.
+Thus we have a binary time series of length 43200 for each of the 197 products.
+Given that the number of visitors that come to a given PDP is likely to vary by time of day and by day, and in general over time, we expect that the mean of the time series to not be stable over time.
+For example, less visitors will come during night than during evening, thus leading to a decreasein the average.
+On the other hand, more users may visit the site during a weekend, thus leading to a spike on Saturdays and Sundays.
+Because of the latter time dependency, it is best practice to run online A/B tests for at least a week, or an integer multiple of weeks, so as to take into account the weekly seasonality in the time series.
+For this reason, the experiments we present below were run on $60 \cdot 24 \cdot 7 = 10080$ observations for each arm, so as to have a sample for one full week.
+
+We can look at summary statistics for the sample means of the 197 products over the month of November to get a first idea of the data we are dealing with.
+We see that most products have a low mean, which is very common also for actual conversion rate data that would be tested with A/B tests or multi-armed bandits.
+Yet the sample of products contains a few outliers with very large view rates, with a maximum rate of 78%.
+If we used a threshold $\gamma$ to binarize the count data, then this means that on average every fourth minute the count of visitors was below $\gamma$ for this product.
+On the other hand, we conclude that using thresholding bandit strategies to test the products against a threshold of for example $\tau = \frac{2}{60} = 0.333$ or $\tau = \frac{5}{60} = 0.083$ is likely to create more complex problems than a threshold of, say, $\tau = \frac{15}{60} = 0.25$ would.
+
+```{r amo_data_summary, echo = FALSE, message = FALSE}
+load(file = "/Users/timradtke/Desktop/thesis_data/pv_summary.Rda")
+
+knitr::kable(pv_summary, digits = 3, col.names = c("Mean", "Minimum", "25% Quantile", "Median", "75% Quantile", "Maximum"), caption = "Summary Statistics for View Rates of 197 Products")
+```
+
+### Experiment 1: $\tau = \frac{2}{60}$
+
+In this first experiment, we pick ten arms randomly from the set of 197 arms.
+The experiment is run on these 10 arms with a budget of $T=10080$ samples during each of the $5000$ iterations for which we repeat the experiment.
+Given the time series cross-validation idea described above, this means that in total, $15080$ observations of the available $43200$ available observations per arm are used in training.
+In the thresholding bandit problem, we classify arms as below or above a threshold.
+Thus we can evaluate the strategies also based on whether their classifications are correct in a holdout sample.
+As this holdout sample, we can use the 10080 observations in our data set that follow the first 15080 observations used in training.
+In the table below, we present the count rates of the ten products for both training and test samples.
+
+```{r experiment1_arm_means, echo = FALSE, message = FALSE}
+
+load("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/data_amo3_mean_firsthalf.Rda")
+load("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/data_amo3_mean_secondhalf.Rda")
+
+Training <- data_amo3_mean_firsthalf
+Test <- data_amo3_mean_secondhalf
+tau <- 2/60
+TrainingMinusTau <- Training - tau
+
+knitr::kable(rbind(Training, Test, TrainingMinusTau), digits = 3, col.names = names(data_amo3_mean_firsthalf),
+             caption = "Count rates for ten products for both training and test sample.")
+
+```
+
+We see that while the rates do vary across samples, they are relatively stable which is likely due to the fact that the samples come from an entire week's worth of observations.
+In particular, since we test against a threshold of $\tau = \frac{2}{60} = 0.333$ in this experiment, the classifications of arms do not differ across training and test data.
+A correct classification after training will be correct in the test set.
+For the rest of the analysis, we thus evaluate the performance using the training rates.
+
+When comparing the rates against the threshold, we see that three products are below the already small threshold.
+Product $V64$ seems to be especially difficult to classify correctly, even without time dependency.
+On the other hand, arms $V119$ and $V118$ should be much easier than the rest.
+
+In order to visualize the time dependency that we expect for our samples, we plot a moving average of the mean of the time series for the first week of data.
+To remove the daily seasonality, we select a moving average window of $60\cdot24 = 1440$ observations.
+To make the time dependency even more obvious, we contrast the actual data against synthetic data generated using the sample means of the actual data.
+
+The graph again underlines that arm $V64$ is likely to be very difficult to classify given that it's moving average even crosses the threshold twice.
+The same is true for arm $V139$, which is not visible when considering the overall mean alone.
+Furthermore, arms $V159$ and $V189$ come very close to the threshold at times.
+
+```{r, echo = FALSE, message = FALSE}
+library(zoo)
+library(tidyr)
+library(dplyr)
+library(ggplot2)
+load("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/data_amo3_wide.Rda")
+
+real_daily <- data.frame(index = 1:8641,
+                                lapply(data_amo3_wide[1:10080,], FUN = rollapply, 
+                                       width = 24*60, mean)) %>%
+  gather(arm, mean, -index) %>%
+  mutate(source = rep("Real", 86410))
+
+real_means <- colMeans(data_amo3_wide[1:10080,])
+tau_amo3 <- 2/60
+
+syn_data <- data.frame(rep(NA, times = 10080))
+set.seed(124632728)
+for(i in 1:length(real_means)) {
+  syn_data[[i]] <- as.numeric(purrr::rbernoulli(10080, p  = real_means[i]))
+}
+names(syn_data) <- names(data_amo3_wide)
+
+syn_daily <- data.frame(source = rep("Synthetic", 8641),
+                        index = 1:8641,
+                        lapply(syn_data, FUN = zoo::rollapply, width = 24*60, mean)) %>%
+  gather(arm, mean, -index, -source)
+
+rbind(real_daily, syn_daily) %>%
+  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
+  geom_line(size = 0.4) +
+  geom_hline(aes(yintercept = tau_amo3), linetype = 2) +
+  facet_grid(.~source) + 
+  labs(title = "Moving average over 24*60 observations (1 day)", 
+       subtitle = "Horizontal bar indicates the threshold.", 
+       x = "Index", y = "One day moving average")
+```
+
+### Experiment 2: $\tau = \frac{5}{60}$

### 2017-08-12 Thesis/Draft.tex
Add exponential family to draft

@@
 \urlstyle{same}  % don't use monospace font for urls
+\usepackage{longtable,booktabs}
 \usepackage{graphicx,grffile}
@@
 \(x = (x_1, ..., x_T)\), where each \(x_i\) is a realization from the
-random variable \(X_i\). We assume that \(X_i\) follows some
-distribution \(Q(\theta)\) paramaterized by a vector \(\theta\). In a
-standard hypothesis test, we would then want to test whether an
+random variable \(X_i\). We assume that \(X_i\) follows some probability
+distribution \(Q(\theta)\) paramaterized by a vector \(\theta\). Let
+\(q(x;\theta)\) be the density function corresponding to the
+distribution. In a standard hypothesis test, we test whether an
 alternative parameterization is more likely than the parameterization
@@
 computes the likelihood \(L(x|\theta)\) of the observed sample under
-both parameterizations: \(L_{H_0} = L(x|\theta = \theta_{H_0})\) and
-\(L_{H_1} = L(x|\theta = \theta_{H_1})\). The likelihood ratio test
-statistic is then given as
+both parameterizations:
+\(L_{H_0} = L(x|\theta = \theta_{H_0}) = \prod_{i=1}^T q(x_i|\theta_{H_0})\)
+and
+\(L_{H_1} = L(x|\theta = \theta_{H_1}) = \prod_{i=1}^T q(x_i|\theta_{H_1})\).
+The likelihood ratio test statistic is then given as
 
 \[
-LR(\theta_{H_0}|| \theta_{H_1}) = \frac{L_{H_0}}{L_{H_1}}.
+LR(\theta_{H_0}|| \theta_{H_1}) = \frac{L_{H_0}}{L_{H_1}} = \prod_{i=1}^T\frac{q(x_i|\theta_{H_0})}{ q(x_i|\theta_{H_1})}.
 \] The intuition behind the test of course being that, if the true
@@
 
+By considering \(lr = -2\log(LR(\theta_{H_0}|| \theta_{H_1}))\), one has
+a statistic that is \(\chi^2\) distributed with degrees of freedom that
+depend on the null and alternative hypothesis. Assessing whether the
+null hypothesis can be rejected with large confidence thus becomes
+straightforward.
+
 \subsubsection{Likelihood Ratio-based Thresholding
@@
 
+The simple concept of the likelihood-ratio test serves as foundation for
+a new sampling strategy that can be applied to the thresholding bandit
+problem. In contrast to the cumulative regret problem, or even the best
+arm identification problem, we have some sort of null hypothesis for the
+distributions in the thresholding bandit problem. In case of no
+information and no observed samples, the null hypothesis might simply be
+that all distributions have a mean that equals the threshold. By
+observing samples, we then want to test whether the mean of the
+distributions is different from the threshold \(\tau\) in either
+direction. Once we are sure that there is a difference, we do not want
+to continue to test. Instead, we would like to focus our sampling effort
+on a different arm where we are not as sure. The likelihood ratio
+quantifies how ``significant''" of a difference there is between the
+threshold \(\tau\) and the current sample mean \(\hat{\mu}_i(t)\) of an
+arm. Given that we plug in the sample mean, that is, the maximum
+likelihood estimator for the true mean for many distributions, the
+likelihood ratio will be smaller than 1 and decrease in sample size even
+if the threshold and sample mean are constant.
+
+Due to these characteristics, the likelihood ratio can serve as a
+natural index for sampling strategies. Thus write as index
+
+\[
+B_i(t) = LR(\tau|| \hat{\mu}_i(t)) = \prod_{i=1}^T\frac{q(x_i|\tau)}{ q(x_i|\hat{\mu}_i(t))}
+\]
+
+and pull at round \(t\) the arm \(i^* = \arg \max_i B_i(t)\). As we
+described in the previous paragraph, we have \(B_i(t) \leq 1\),
+\(t \uparrow \rightarrow B_i(t) \downarrow\), and
+\(|\hat{\mu}_i(t) - \tau| \uparrow \rightarrow B_i(t) \downarrow\).
+Consequently, by choosing the arm that maximizes \(B_i(t)\), we choose
+an arm for which we either have not collected many samples, or where the
+sample mean is close to the threshold \(\tau\). In this sense, a
+strategy based on the likelihood ratio is of course very reminiscient of
+the index employed by the APT algorithm. Indeed, assuming the samples
+are normally distributed with the same variance for the distribution
+\(\nu_i\) under both \(H_0\) and \(H_1\), then
+\(-\log(LR(\tau||\hat{\mu}_i(t)))\) equals the index in APT. Why then
+would one use the likelihood based strategy?
+
+Given that the APT index and the likelihood-ratio based index are only
+equivalent for normally distributed random variables with fixed standard
+deviation, the new strategy promises efficiency improvements whenever
+the true distribution is known and different from the normal
+distribution. The most important example are Bernoulli arms with small
+means as discussed before. Here, it is also easy to assume that the true
+distribution is known upfront. Similarly, the likelihood ratio statistic
+can be used for other univariate distributions of the exponential
+family. But we also propose a version for the Normal distribution with
+unknown mean.
+
+We now focus on the case where the distributions
+\(\nu_{\theta_1}, ..., \nu_{\theta_K}\) are all the same canonical
+exponential family of distributions with scalar parameter
+\(\theta_i \in \Theta\). The probability density function of the
+absolutely continuous distribution \(\nu_{\theta_i}\) with regard to a
+dominating measure \(\rho\) on \(\mathbb{R}\) is given by
+\(q(x|\theta) = h(x) \exp(T(x)\theta - b(\theta))\). As described in
+Cappé et al. (2013), citing Lehmann and Casella (1998), the derivative
+\(b'(\theta)\) of \(b(\theta)\) is an increasing continuous function
+such that the expected value \(\mathbb{E}(\nu_{\theta}) = b'(\theta)\)
+for all \(\theta \in \Theta\). Given that \(b'(x)\) is strictly convex,
+we have a one-to-one relation between \(b'(\theta)\) and
+\(\mathbb{E}(\nu_{\theta})\) through the continuous inverse
+\(b'^{-1}(\theta)\). Consequently, one can just as well parameterize the
+distribution its mean \(\mu = \mathbb{\nu_{\theta}}\) and write
+\(\nu_{b'^{-1}(\mu)}\) with the probability density function
+
+\[
+q(x|b'^{-1}(\mu)) = h(x) \exp(T(x) b'^{-1}(\mu) - b(b'^{-1}(\mu))).
+\]
+
+This lets us write the likelihood ratio for the exponential family
+distributions as
+
+\[
+LR(b'^{-1}(\mu_0)||b'^{-1}(\mu_1)) = \prod_{i=1}^n \frac{\exp(T(x_i) b'^{-1}(\mu_0) - b(b'^{-1}(\mu_0)))}{\exp(T(x_i) b'^{-1}(\mu_1) - b(b'^{-1}(\mu_1)))}
+\]
+
+or if we write it as negative log-likelihood ratio:
+
+\[
+-\log(LR) = n\Big(b\big(b'^{-1}(\mu_0)) - b(b'^{-1}(\mu_1)\big)\Big) - \Big(b'^{-1}(\mu_0)-b'^{-1}(\mu_1)\Big)\sum_{i=1}^nT(x_i)
+\]
+
+As we will see now, this statistic is easily derived for many specific
+distributions.
+
+\paragraph{Example 1: Bernoulli
+Distribution}\label{example-1-bernoulli-distribution}
+
+We have \(T(x_i) = x_i\), \(\theta = \log(\mu/(1-\mu))\),
+\(\Theta = (0,1)\), \(b(\theta) = \log(1+\exp(\theta))\), and
+\(\mu \in (0,1)\). Then \(b'(\theta) = \mu\), and we can write
+
+\[
+-\log(LR(\mu_0||\mu_1)) = n(\log\Big(\frac{1-\mu_0}{1-\mu_1}\Big)) - \Big(\log(\frac{\mu_0}{1-\mu_0}) - \log(\frac{\mu_1}{1-\mu_1})\Big)\sum_{i=1}^{n}x_i = (1-\hat{\mu})\log\Big(\frac{1-\mu_1}{1-\mu_0}\Big) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0})
+\]
+
+We observe that, if we let \(\mu_0 = \tau\) and \(\mu_1 = \hat{\mu}\),
+then
+
+\[
+-\log(LR(\tau||\hat{\mu})) = KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = d(\hat{\mu},\tau)
+\]
+
+\paragraph{Example 2: Poisson
+Distribution}\label{example-2-poisson-distribution}
+
+We have \(T(x_i) = x_i\), \(\theta = \log(\mu)\),
+\(\Theta = \mathbb{R}\), \(b(\theta) = \exp(\theta)\), and
+\(\mu \in (0, +\infty)\). Then \(b'(\theta) = \mu\), and we can write:
+
+\[
+-\log(LR(\mu_0||\mu_1)) = n(\mu_0 - \mu_1) - (\log(\mu_0) - \log(\mu_1))\sum_{i=1}^n x_i = (\mu_0 - \mu_1) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}\Big)
+\]
+
+We observe that, if we let \(\mu_0 = \tau\) and \(\mu_1 = \hat{\mu}\),
+then
+
+\[
+-\log(LR(\tau||\hat{\mu})) = KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = d(\hat{\mu},\tau) = (\tau - \hat{\mu}) + \hat{\mu}\log\Big(\frac{\hat{\mu}}{\tau}\Big)
+\]
+
+\paragraph{\texorpdfstring{Example 3: Normal distributions with known
+variance
+\(\sigma^2\)}{Example 3: Normal distributions with known variance \textbackslash{}sigma\^{}2}}\label{example-3-normal-distributions-with-known-variance-sigma2}
+
+We have \(T(x_i) = x_i\), \(\theta = \mu/\sigma^2\),
+\(\Theta = \mathbb{R}\), \(b(\theta) = \sigma^2\theta^2/2\),
+\(\mu \in \mathbb{R}\). Then \(b'(\theta) = \mu\), and we can write
+
+\[
+-\log(LR(\mu_0||\mu_1)) = n (\frac{\mu_0^2}{2\sigma^2} - \frac{\mu_1^2}{2\sigma^2}) - (\frac{\mu_0}{\sigma^2} - \frac{\mu_1}{\sigma^2})\sum_{i=1}^nx_i = \frac{1}{2\sigma^2}\Big(\mu_0^2-\mu_1^2 - 2\mu_0\hat{\mu} + 2\mu_1\hat{\mu}\Big)
+\]
+
+And again, if we let \(\mu_1 = \hat{\mu}\) and \(\mu_0 = \tau\), then
+
+\[
+-\log(LR(\tau||\hat{\mu})) = KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = d(\hat{\mu},\tau) = \frac{(\hat{\mu} - \tau)^2}{2\sigma^2}.
+\]
+
+\section{Experiments}\label{experiments}
+
+\subsection{Real Data}\label{real-data}
+
+We show two experiments that were performed on real data. While most
+papers in the multi-armed bandit literature resort to synthetic data to
+assess the performance of algorithms -- just as we have done in the
+previous chapter -- we have tried to acquire real world data. This data
+is what bandit algorithms are used for in practice, and does not fulfill
+the standard independence and identical distribution assumptions as
+nicely. The real data thus can be considered a first robustness test for
+the algorithms.
+
+\subsubsection{The Data Set}\label{the-data-set}
+
+The data have been collected by the German ecommerce company
+\href{https://amorelie.de}{Amorelie} as part of standard website
+performance tracking. For 197 selected products, we have the number of
+users visiting each product's detail page (PDP) at a given minute. The
+data set we use here has been collected during the entire month of
+November 2016. It can be considered time series data collected at
+minutely frequency. Thus the data contain 43200 observations per
+product, and overall 8510400 observations.
+
+Given that we want to run an offline comparison of bandit algorithms, it
+is important to have at each time point an observation for each arm.
+Given that, it is easy to evaluate the perfomance of algorithms that
+make different decisions at different point in times and thus do not
+observe the same samples. By having an observation for each arm at any
+given time point, each algorithm had at least the opportunity to observe
+a certain sample. Other papers (CITE YAHOO!) have solved this problem by
+using a sample drawn uniformly during for example an A/B test. Then, if
+the next observation in the sample is not from the same arm that the
+algorithm would like to draw from, observations are discarded until the
+next observation from the selected arm.
+
+The choice of having basically multiple time series data as the sample
+leads to a simple way of running the algorithms just as often on the
+data as for simulated data. In particular, the goal is to perform 5000
+runs over the sample to confidently assess the performance. Since we
+wanted to preserve the potential time dependency of the data, a simple
+resampling of the data was not an option to create the needed 5000
+variations of the sample. Thus what we did instead was a form of time
+series cross validation. To preserve the autocorrelation, one can create
+different samples of \(X\) observations by sliding a window of size
+\(X\) over the time series. Moving the window one period (in our case
+minute) at a time, one ensures that no sample shares start and end
+observation with another sample. In particular, this means for a given
+bandit strategy and two samples that the observations that the algorithm
+collects as feedback during the two initialization phases differ from
+sample to sample and are never the same. This is because during
+initialization every strategy pulls arms \(1, ..., K\) once in this
+order.
+
+While the data is count data (the number of visits to a PDP during a
+given minute), we binarize the data by applying a certain threshold. If
+the counts is above this threshold, the observation becomes a \(1\),
+else \(0\). Thus we have a binary time series of length 43200 for each
+of the 197 products. Given that the number of visitors that come to a
+given PDP is likely to vary by time of day and by day, and in general
+over time, we expect that the mean of the time series to not be stable
+over time. For example, less visitors will come during night than during
+evening, thus leading to a decreasein the average. On the other hand,
+more users may visit the site during a weekend, thus leading to a spike
+on Saturdays and Sundays. Because of the latter time dependency, it is
+best practice to run online A/B tests for at least a week, or an integer
+multiple of weeks, so as to take into account the weekly seasonality in
+the time series. For this reason, the experiments we present below were
+run on \(60 \cdot 24 \cdot 7 = 10080\) observations for each arm, so as
+to have a sample for one full week.
+
+We can look at summary statistics for the sample means of the 197
+products over the month of November to get a first idea of the data we
+are dealing with. We see that most products have a low mean, which is
+very common also for actual conversion rate data that would be tested
+with A/B tests or multi-armed bandits. Yet the sample of products
+contains a few outliers with very large view rates, with a maximum rate
+of 78\%. If we used a threshold \(\gamma\) to binarize the count data,
+then this means that on average every fourth minute the count of
+visitors was below \(\gamma\) for this product. On the other hand, we
+conclude that using thresholding bandit strategies to test the products
+against a threshold of for example \(\tau = \frac{2}{60} = 0.333\) or
+\(\tau = \frac{5}{60} = 0.083\) is likely to create more complex
+problems than a threshold of, say, \(\tau = \frac{15}{60} = 0.25\)
+would.
+
+\begin{longtable}[]{@{}rrrrrr@{}}
+\caption{Summary Statistics for View Rates of 197
+Products}\tabularnewline
+\toprule
+Mean & Minimum & 25\% Quantile & Median & 75\% Quantile &
+Maximum\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+Mean & Minimum & 25\% Quantile & Median & 75\% Quantile &
+Maximum\tabularnewline
+\midrule
+\endhead
+0.12 & 0 & 0.036 & 0.074 & 0.136 & 0.778\tabularnewline
+\bottomrule
+\end{longtable}
+
+\subsubsection{\texorpdfstring{Experiment 1:
+\(\tau = \frac{2}{60}\)}{Experiment 1: \textbackslash{}tau = \textbackslash{}frac\{2\}\{60\}}}\label{experiment-1-tau-frac260}
+
+In this first experiment, we pick ten arms randomly from the set of 197
+arms. The experiment is run on these 10 arms with a budget of
+\(T=10080\) samples during each of the \(5000\) iterations for which we
+repeat the experiment. Given the time series cross-validation idea
+described above, this means that in total, \(15080\) observations of the
+available \(43200\) available observations per arm are used in training.
+In the thresholding bandit problem, we classify arms as below or above a
+threshold. Thus we can evaluate the strategies also based on whether
+their classifications are correct in a holdout sample. As this holdout
+sample, we can use the 10080 observations in our data set that follow
+the first 15080 observations used in training. In the table below, we
+present the count rates of the ten products for both training and test
+samples.
+
+\begin{longtable}[]{@{}lrrrrrrrrrr@{}}
+\caption{Count rates for ten products for both training and test
+sample.}\tabularnewline
+\toprule
+& V64 & V1 & V159 & V119 & V70 & V114 & V189 & V139 & V118 &
+V148\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+& V64 & V1 & V159 & V119 & V70 & V114 & V189 & V139 & V118 &
+V148\tabularnewline
+\midrule
+\endhead
+Training & 0.027 & 0.001 & 0.013 & 0.158 & 0.071 & 0.071 & 0.059 & 0.053
+& 0.156 & 0.102\tabularnewline
+Test & 0.022 & 0.000 & 0.011 & 0.130 & 0.064 & 0.060 & 0.058 & 0.055 &
+0.150 & 0.115\tabularnewline
+TrainingMinusTau & -0.006 & -0.033 & -0.021 & 0.125 & 0.038 & 0.038 &
+0.026 & 0.019 & 0.123 & 0.068\tabularnewline
+\bottomrule
+\end{longtable}
+
+We see that while the rates do vary across samples, they are relatively
+stable which is likely due to the fact that the samples come from an
+entire week's worth of observations. In particular, since we test
+against a threshold of \(\tau = \frac{2}{60} = 0.333\) in this
+experiment, the classifications of arms do not differ across training
+and test data. A correct classification after training will be correct
+in the test set. For the rest of the analysis, we thus evaluate the
+performance using the training rates.
+
+When comparing the rates against the threshold, we see that three
+products are below the already small threshold. Product \(V64\) seems to
+be especially difficult to classify correctly, even without time
+dependency. On the other hand, arms \(V119\) and \(V118\) should be much
+easier than the rest.
+
+In order to visualize the time dependency that we expect for our
+samples, we plot a moving average of the mean of the time series for the
+first week of data. To remove the daily seasonality, we select a moving
+average window of \(60\cdot24 = 1440\) observations. To make the time
+dependency even more obvious, we contrast the actual data against
+synthetic data generated using the sample means of the actual data.
+
+The graph again underlines that arm \(V64\) is likely to be very
+difficult to classify given that it's moving average even crosses the
+threshold twice. The same is true for arm \(V139\), which is not visible
+when considering the overall mean alone. Furthermore, arms \(V159\) and
+\(V189\) come very close to the threshold at times.
+
+\includegraphics{Draft_files/figure-latex/unnamed-chunk-4-1.pdf}
+
+\subsubsection{\texorpdfstring{Experiment 2:
+\(\tau = \frac{5}{60}\)}{Experiment 2: \textbackslash{}tau = \textbackslash{}frac\{5\}\{60\}}}\label{experiment-2-tau-frac560}
+
 \end{document}

### 2017-08-12 real_experiments/real_exp_1week_2.R

@@ -56,31 +56,6 @@ tau_amo4 <- 5/60
 epsilon_amo4 <- 0
 
 ########################################################################
-# Bayes-UCB
-
-amo4_BUCB <- para_bandit_sim_bucb(data = data_amo4, rounds = 7580, 
-                                  rate = "inverse_horizon",
-                                  tau = tau_amo4, epsilon = epsilon_amo4, 
-                                  alpha = tau_amo4, beta = 1-tau_amo4)
-save(amo4_BUCB, 
-     file = paste0(current_path, "amo4_BUCB.Rda"))
-amo4_compnext_BUCB <- compare_to_cv_data(data_amo4_next_means, amo4_BUCB, 
-                                         tau_amo4, epsilon_amo4)$mean
-amo4_compown_BUCB <- compare_to_cv_data(data_amo4_own_means, amo4_BUCB, 
-                                        tau_amo4, epsilon_amo4)$mean
-amo4_comp_BUCB <- compare_to_ground_truth(data_amo4_mean_firsthalf, amo4_BUCB, 
-                                          tau_amo4, epsilon_amo4)$mean
-amo4_compholdout_BUCB <- compare_to_ground_truth(data_amo4_mean_secondhalf, 
-                                                 amo4_BUCB, 
-                                                 tau_amo4, epsilon_amo4)$mean
-save(amo4_compnext_BUCB, file = paste0(current_path, "amo4_compnext_BUCB.Rda"))
-save(amo4_compown_BUCB, file = paste0(current_path, "amo4_compown_BUCB.Rda"))
-save(amo4_comp_BUCB, file = paste0(current_path, "amo4_comp_BUCB.Rda"))
-save(amo4_compholdout_BUCB, file = paste0(current_path, "amo4_compholdout_BUCB.Rda"))
-rm(amo4_BUCB)
-gc()
-
-########################################################################
 # Standard Likelihood Ratio
 system.time(amo4_LR <- para_bandit_sim_LR(data = data_amo4, 
                                           rounds = 10080, 
@@ -139,6 +114,25 @@ save(amo4_comp_AugUCB, file = paste0(current_path, "amo4_comp_AugUCB.Rda"))
 save(amo4_compholdout_AugUCB, file = paste0(current_path, 
                                             "amo4_compholdout_AugUCB.Rda"))
[…]

### 2017-08-12 real_experiments/real_exp_1week_2_sim.R

@@ -1,0 +1,134 @@
+# What happens if we use synthetic data with the same mean as in the real data?
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/"
+
+load(paste0(current_path, "data_amo4_mean_firsthalf.Rda"))
+tau_amo4sim <- 5/60
+epsilon_amo4sim <- 0
+
+data_amo4sim <- list()
+set.seed(458693)
+for(j in 1:5000) {
+  curr_data <- data.frame(rep(NA, times = 10080))
+  for(i in 1:length(data_amo4_mean_firsthalf)) {
+    curr_data[[i]] <- as.numeric(purrr::rbernoulli(10080, p  = data_amo4_mean_firsthalf[i]))
+  }
+  names(curr_data) <- paste0("V", rep(1:length(data_amo4_mean_firsthalf)))
+  data_amo4sim[[j]] <- curr_data
+}
+gc()
+
+
+
+
+########################################################################
+# Standard Likelihood Ratio
+system.time(amo4sim_LR <- para_bandit_sim_LR(data = data_amo4sim, 
+                                          rounds = 10080, 
+                                          tau = tau_amo4sim, 
+                                          epsilon = epsilon_amo4sim))
+
+save(amo4sim_LR, file = paste0(current_path, "amo4sim_LR.Rda"))
+#load(file = paste0(current_path, "amo4sim_LR.Rda"))
+amo4sim_comp_LR <- compare_to_ground_truth(data_amo4_mean_firsthalf, 
+                                           amo4sim_LR, 
+                                           tau_amo4sim, epsilon_amo4sim)$mean
+save(amo4sim_comp_LR, file = paste0(current_path, "amo4sim_comp_LR.Rda"))
+rm(amo4sim_LR, amo4sim_comp_LR)
+gc()
+
+########################################################################
+# Standard Uniform
+system.time(amo4sim_UNIFORM <- para_bandit_sim_uniform(data = data_amo4sim, 
+                                                       rounds = 10080))
+save(amo4sim_UNIFORM, file = paste0(current_path, "amo4sim_UNIFORM.Rda"))
[…]

### 2017-08-13 Thesis/Draft.Rmd
Add experiment results discussion to thesis draft

@@
 $$
--\log(LR(\mu_0||\mu_1)) = n(\log\Big(\frac{1-\mu_0}{1-\mu_1}\Big)) - \Big(\log(\frac{\mu_0}{1-\mu_0}) - \log(\frac{\mu_1}{1-\mu_1})\Big)\sum_{i=1}^{n}x_i = (1-\hat{\mu})\log\Big(\frac{1-\mu_1}{1-\mu_0}\Big) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0})
+-\log(LR(\mu_0||\mu_1)) = n(\log\Big(\frac{1-\mu_0}{1-\mu_1}\Big)) - \Big(\log(\frac{\mu_0}{1-\mu_0}) - \log(\frac{\mu_1}{1-\mu_1})\Big)\sum_{i=1}^{n}x_i = n \Big( (1-\hat{\mu})\log\Big(\frac{1-\mu_1}{1-\mu_0}\Big) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}) \Big)
 $$
@@
 $$
--\log(LR(\tau||\hat{\mu})) = KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = d(\hat{\mu},\tau)
+-\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n \Big(\hat{\mu}\log\big(\frac{\hat{\mu}}{\tau}\big) + (1-\hat{\mu})\log\big(\frac{1-\hat{\mu}}{1-\tau}\big)\Big)
 $$
@@
 $$
--\log(LR(\mu_0||\mu_1)) = n(\mu_0 - \mu_1) - (\log(\mu_0) - \log(\mu_1))\sum_{i=1}^n x_i = (\mu_0 - \mu_1) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}\Big)
+-\log(LR(\mu_0||\mu_1)) = n(\mu_0 - \mu_1) - (\log(\mu_0) - \log(\mu_1))\sum_{i=1}^n x_i = n\Big((\mu_0 - \mu_1) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}\Big)\Big)
 $$
@@
 $$
--\log(LR(\tau||\hat{\mu})) = KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = d(\hat{\mu},\tau) = (\tau - \hat{\mu}) + \hat{\mu}\log\Big(\frac{\hat{\mu}}{\tau}\Big)
+-\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n\Big((\tau - \hat{\mu}) + \hat{\mu}\log\Big(\frac{\hat{\mu}}{\tau}\Big)\Big)
 $$
@@
 $$
--\log(LR(\mu_0||\mu_1)) = n (\frac{\mu_0^2}{2\sigma^2} - \frac{\mu_1^2}{2\sigma^2}) - (\frac{\mu_0}{\sigma^2} - \frac{\mu_1}{\sigma^2})\sum_{i=1}^nx_i = \frac{1}{2\sigma^2}\Big(\mu_0^2-\mu_1^2 - 2\mu_0\hat{\mu} + 2\mu_1\hat{\mu}\Big)
+-\log(LR(\mu_0||\mu_1)) = n (\frac{\mu_0^2}{2\sigma^2} - \frac{\mu_1^2}{2\sigma^2}) - (\frac{\mu_0}{\sigma^2} - \frac{\mu_1}{\sigma^2})\sum_{i=1}^nx_i = n\frac{1}{2\sigma^2}\Big(\mu_0^2-\mu_1^2 - 2\mu_0\hat{\mu} + 2\mu_1\hat{\mu}\Big)
 $$
@@
 $$
--\log(LR(\tau||\hat{\mu})) = KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = d(\hat{\mu},\tau) = \frac{(\hat{\mu} - \tau)^2}{2\sigma^2}.
-$$
+-\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n\frac{(\hat{\mu} - \tau)^2}{2\sigma^2}.
+$$
+
+#### Example 4: Gamma distributions with known shape parameter $\alpha$
+
+We have $T(x_i) = x_i$, $\theta = -\alpha/\mu$, $\Theta = (-\infty, 0)$, $b(\theta) = -\alpha \log(-\theta)$, $\mu \in (0,+\infty)$. Then $b'(\theta) = -\mu$, and we can write
+
+$$
+-\log(LR(\mu_0||\mu_1)) = n\alpha(-\log(\frac{\alpha}{\mu_0}) - \log(\frac{\mu_1}{\alpha})) - (-\frac{\alpha}{\mu_0} + \frac{\alpha}{\mu_1})\sum_{i=1}^{n}x_i = n\alpha \Big(\log\big(\frac{\mu_0}{\mu_1}\big) - \frac{\hat{\mu}}{\mu_1} + \frac{\hat{\mu}}{\mu_0}\Big).
+$$
+And again, if we let $\mu_1 = \hat{\mu}$ and $\mu_0 = \tau$, then
+
+$$
+-\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n\alpha \Big(\frac{\hat{\mu}}{\tau} - 1 - \log\big(\frac{\hat{\mu}}{\tau}\big)\Big).
+$$
+
+For $\alpha = 1$, the Gamma distribution is equal to the Exponential distribution.
+
+Given these results for the exponential family of distributions, we can now define the SLR (Simple Likelihood Ratio) algorithm.
+
+### 1D-SLR Algorithm for One-Dimensional Exponential Family of Distributions
+
+Very similar to the APT algorithm, the SLR algorithm receives as input the definition of the problem $(\tau, \epsilon)$ (compare Locatelli et al., 2016).
+Additionally, the algorithm receives as input the name of the distribution that the arms follow, as well as potential additional parameters ($\sigma_1, ..., \sigma_K$ for Normal distributions, $\alpha_1, ..., \alpha_K$ for Gamma distributions).
+We assume that each arm follows the same kind of distribution, with potentially different parameters $\theta_1, ..., \theta_K$.
+The algorithm pulls each arm once.
+At time $t>K$, the algorithm updates the number of pulls for arm $i$ at time $t$, $T_i(t)$, for each arm, as well as the empirical mean $\hat{\mu}_i(t)$ of arm $i$ after $T_i(t)$ pulls.
+The empirical mean is calculated for each arm $k\in \{1,...,K\}$ as $\hat{\mu}_i(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)} x_{i,s}$, with $T_i(t) = \sum_{s=1}^{t}\mathbb{I}(I_s = i)$.
+As in Locatelli et al.
+(2016), the $X_{i,s}$ is the sample received when pulling arm $i$ for the $s$-th time.
+Depending on the distribution, the algorithm then computes the index
+
+$$
+B_i^{SLR}(t+1) = \mathbb{I}(\hat{\mu}\geq \tau)(-\log\big(LR(\tau-\epsilon||\hat{\mu}_i(t))\big) + \mathbb{I}(\hat{\mu}< \tau)(-\log\big(LR(\tau+\epsilon||\hat{\mu}_i(t))\big) = T_i(t) \Big( \mathbb{I}(\hat{\mu}\geq \tau)\cdot KL(\nu_{b'^{-1}(\hat{\mu}(t))}||\nu_{b'^{-1}(\tau-\epsilon)}) + \mathbb{I}(\hat{\mu} < \tau)\cdot KL(\nu_{b'^{-1}(\hat{\mu}(t))}||\nu_{b'^{-1}(\tau+\epsilon)}) \Big).
+$$
+
+The next arm to be pulled is the minimizer of the index $B_i^{SLR}(t+1)$, $I_{t+1} = \arg \min_{i\leq K} B_i(t+1)$.
+At the end of the horizon $T$, the algorithm outputs the set of arms $\hat{S}_\tau = \{k: \hat{\mu}_k(T) \geq \tau\}$.
+
+### 2D-SLR Algorithm for Normal Distributions with Unknown Mean and Unknown Variance
+
+As soon as we move away from univariate distributions parameterized by their mean, it becomes less clear how the likelihood ratio for $H_0: \mu = \tau$ and $H_1: \mu = \hat{\mu}$ should be calculated.
+In the case of Normal distributions with unknown mean and unknown variance, given that the variance and mean estimate are linked, we can use $H_0: \mu = \tau \land \sigma^2 = \sigma^2_{\tau} = \frac{1}{n}\sum_{i=1}^{n}(x_i-\tau)^2$ and the alternative hypothesis based on the maximum likelihood estimates $H_1: \mu = \hat{\mu} \land \sigma^2 = \hat{\sigma}^2 = \frac{1}{n}\sum_{i=1}^{n}(x_i-\hat{\mu})^2$.
+
+In the following, we assume $\epsilon = 0$.
+
+Now, at each round $t$, the algorithm computes $T_i(t)$ and $\hat{\mu}_i(t)$ as before, but additionally the empirical variances $\sigma_{\tau,i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\tau)^2$ and $\hat{\sigma}_{i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\hat{\mu})^2$.
+The index is then given by
+
+$$
+B_i^{2DSLR}(t+1) = -\log(LR(\tau, \sigma_{\tau,i}^2(t)||\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t))) = T_i(t) \log\Big(\frac{\sigma_{\tau,i}^2(t)}{\hat{\sigma}_i^2(t)}\Big) = T_i(t) KL(\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t)||\tau, \sigma_{\tau,i}^2(t))
+$$
+
+(SHOW THAT THE NOTATION CAN BE ABUSED AND THE KL WRITTEN THIS WAY BECAUSE UNIQUELY DEFINED BY MEAN AND VARIANCE)
+
+Then, as for the univariate case, the next arm to be pulled is the minimizer of the index $B_i^{2DSLR}(t+1)$, $I_{t+1} = \arg \min_{i\leq K} B_i(t+1)$.
+At the end of the horizon $T$, the algorithm outputs the set of arms $\hat{S}_\tau = \{k: \hat{\mu}_k(T) \geq \tau\}$.
 
@@
 
-knitr::kable(rbind(Training, Test, TrainingMinusTau), digits = 3, col.names = names(data_amo3_mean_firsthalf),
+knitr::kable(rbind(Training, Test, TrainingMinusTau)[,order(Training)], digits = 3, col.names = names(data_amo3_mean_firsthalf),
              caption = "Count rates for ten products for both training and test sample.")
@@
 
+These difficulties seem to have a large impact on the performance of all algorithms.
+Given that the data are $\{0,1\}$ observations, we can compare all algorithms in a setting in which one expects all assumptions to hold before having observed the data.
+The distribution is sub-Gaussian for the APT algorithm, bounded between $0$ and $1$ for the variance-based algorithms, and assumed to be Bernoulli for the SLR algorithm.
+Additionally, we use the B-UCB algorithm as it performed often best on the synthetic data.
+
+We set $\epsilon = 0$, and $\tau = 2/60$.
+For the AugUCB algorithm we use the parameters as in Mukherjee et al.
+(2017), that is, $\rho = 1/3$.
+For B-UCB we set the prior to $\alpha = \tau$ and $\beta = 1-\tau$.
+All other algorithms are parameter free.
+
+The corresponding results are shown in the next figure.
+
+```{r, echo = FALSE}
+library(ggplot2)
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/"
+
+#load(paste0(current_path, "amo3_comp_BUCB.Rda"))
+load(paste0(current_path, "amo3_comp_APT.Rda"))
+load(paste0(current_path, "amo3_comp_UNIFORM.Rda"))
+load(paste0(current_path, "amo3_comp_AugUCB.Rda"))
+load(paste0(current_path, "amo3_comp_LR.Rda"))
+load(paste0(current_path, "amo3_comp_EVT.Rda"))
+
+alg_names <- c(rep(c("Uniform", "APT", "AugUCB","LR"), 
+                   each = 10071), rep("EVT", 10061))
+index <- c(rep(10:10080, times = 4), 20:10080)
+alg_res <- log(c(amo3_comp_UNIFORM, amo3_comp_APT, amo3_comp_AugUCB, amo3_comp_LR, amo3_comp_EVT))
+loc3_comp_res <- data.frame(index = index, names = alg_names, 
+                            results = alg_res)
+ggplot(loc3_comp_res, aes(x = index, y = results)) + 
+  geom_line(aes(group = names, color = names)) +
+  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
+  labs(title = "Results of Real Data Experiment 1", 
+       subtitle = paste0("Sample Mean Complexity of "), 
+       y = "log(Error)", x = "Round Index")
+```
+
+Compared to the previous simulations with synthetic data, the results are dramatic.
+First of all, we see that all strategies perform not well.
+All of them end above the 10% error mark after 1 week of data.
+Second, the uniform sampling strategy fares best when evaluated against the sample mean of all observations used during training.
+This of course is the opposite of what we would like to see, and the opposite of what we saw on the synthetic data, where we were able to improve upon the naive strategy.
+Third, again in contrast to the results on synthetic data, we observe non-monotonicity in the error curves.
+Given that the highs and lows run very much parallel for the different models, it stands to reason that this effect is caused by the variation in means of the arms over time.
+Indeed, roughly comparing the error curves to the moving averages in the previous figure, the increase in errors after round $5000$ and the decreasing error after round $7500$ seems to line up more or less with the fluctuations observed in the data.
+Given that we evaluate the models against a sample mean of all observations, it is not surprising that the uniform sampling strategy has a certain advantage when it comes to "factoring out" the seasonalities.
+In contrast, the adaptive sampling schemes try to adapt more or less quickly to the changes in the means; a feature that would be valuable in a cumulative regret multi-armed bandit setting.
+Here, however, it leads to wrong estimates of the sample mean.
+
+If we focus on a comparison of adaptive sampling strategies and less on their globally bad performance, we see that the variance based strategies perform worse than APT and SLR.
+Very dramatic is the behavior of the Augmented-UCB algorithm, which first seems to perform well; that, however, is a result of it mostly pulling arms uniformly, until it starts to adapt its sampling and discarding arms after nearly 5000 rounds.
+The result is a dramatic increase in error which leads to the worst performs at the end of the budget.
+The difference between APT, SLR, and EVT is not very large, and their performance fluctuates in sync.
+None of them is really able to converge due to the changes in the underlying means.
+Advantageous only seems to be the fact that their behavior is less erratic than that of the Augmented-UCB strategy given that they do not discard arms.
+
 ### Experiment 2: $\tau = \frac{5}{60}$
+
+In order to underline the results of the previous experiment, we perform a second experiment using the data collected by Amorelie.
+We increase the threshold to $\tau = \frac{5}{60} = 0.833$ to make the problem in general slightly easier, and again pick 10 arms at random from the data set of 197 arms.
+We again use a rolling window of $10080$ observations to create $5000$ iterations and look at the training and test sample means as in Experiment 1.
+
+Some arms, in particular $V110$ and $V150$, but also $V103$, $V149$, $V104$, and $V112$ are quite close to the threshold.
+Two arms, $V129$ and $V32$ appear to have basically no positive observation in the training set.
+On the other hand, arm $V154$ is larger than the threshold by a fair amount and should be easier to classify.
+
+```{r experiment2_arm_means, echo = FALSE, message = FALSE}
+
+load("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/data_amo4_mean_firsthalf.Rda")
+load("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/data_amo4_mean_secondhalf.Rda")
+
+Training <- data_amo4_mean_firsthalf
+Test <- data_amo4_mean_secondhalf
+tau <- 5/60
+TrainingMinusTau <- Training - tau
+
+knitr::kable(rbind(Training, Test, TrainingMinusTau)[,order(Training)], digits = 3, col.names = names(data_amo4_mean_firsthalf),
+             caption = "Count rates for ten products for both training and test sample.")
+
+```
+
+As in the previous experiment, we can also take a look at the one day moving averages of the arms to quickly assess the time dependency of the means.
+Given that the data here are collected at the same time points as the data used in the previous experiment, it is not surprising to see a similar spike in means during the second half of the observations with the maximum moving average around index 7500.
+We also observe that these fluctuations are heavier for products with in general larger means (that is, more visitors on the website).
+But these fluctuations are clearly much larger and systematic than those observed for synthetic data with the same sample means.
+While the moving average of product $V159$ in the synthetic data has a valley after index 5000, this can be explained by the natural variance (which increases as the mean is closer to $0.5$).
+
+Given the moving averages and the previous experiment, the performance results of Experiment 2 shown in the next figure are not surprising.
+We recognize the same structure as previously.
+The uniform sampling strategy performs the best.
+The adaptive sampling strategies perform bad, do not converge, and end above the 10% error mark.
+This time, Augmented-UCB is not (yet) the worst performing strategy, but equally erratic after it actually adapts its sampling.
+This time around, it even has two spikes in its adaptive phase.
+Again, APT, SLR, and EVT perform in sync and more or less equally bad, with EVT slightly better than APT and SLR this time around.
+Interestingly, Bayes-UCB performs clearly worst of all strategies.
+Its performance changes at the same time as Augmented-UCB starts to adapt its sampling strategy, near round 7000.
+
+This last fact is of particular interest, as Bayes-UCB is dramatically better than the other strategies in experiments on synthetic data.
+On the right hand side of the same figure, the performance of the algorithms on synthetic data from Bernoulli distributions with the same sample mean is depicted.
+On this data, Bayes-UCB performs very well, ending at an average error of about 0.1% of the simulations.
+This mirrors its performance observed in the previous simulations with synthetic data.
+Also all other strategies perform clearly better now, and their error rates are strictly decreasing.
+Interestingly, the uniform sampling scheme is now much worse than in the experiment on real data; it does no longer have the advantage of sampling the different mean phases at a representative rate.
+Instead, it is no in its original position of serving as upper bound on the error rate.
+Excluding Bayes-UCB, we see that the SLR algorithm performs better the best, followed by the variance-based algorithms.
+APT comes in at the same error rate as uniform sampling.
+While the difference between SLR and EVT are less than 2% (1.2% vs 3%), the difference to uniform sampling (10%) is relevant.
+The performance of 10% error rate is achieved by SLR about 1000 observations earlier than by EVT.
+
+```{r, echo = FALSE, message = FALSE}
+library(zoo)
+library(tidyr)
+library(dplyr)
+library(ggplot2)
+load("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/data_amo4_wide.Rda")
+
+real_daily <- data.frame(index = 1:8641,
+                                lapply(data_amo4_wide[1:10080,], FUN = rollapply, 
+                                       width = 24*60, mean)) %>%
+  gather(arm, mean, -index) %>%
+  mutate(source = rep("Real", 86410))
+
+real_means <- colMeans(data_amo4_wide[1:10080,])
+tau_amo4 <- 5/60
+
+syn_data <- data.frame(rep(NA, times = 10080))
+set.seed(124632728)
+for(i in 1:length(real_means)) {
+  syn_data[[i]] <- as.numeric(purrr::rbernoulli(10080, p  = real_means[i]))
+}
+names(syn_data) <- names(data_amo4_wide)
+
+syn_daily <- data.frame(source = rep("Synthetic", 8641),
+                        index = 1:8641,
+                        lapply(syn_data, FUN = zoo::rollapply, width = 24*60, mean)) %>%
+  gather(arm, mean, -index, -source)
+
+rbind(real_daily, syn_daily) %>%
+  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
+  geom_line(size = 0.4) +
+  geom_hline(aes(yintercept = tau_amo4), linetype = 2) +
+  facet_grid(.~source) + 
+  labs(title = "Moving average over 24*60 observations (1 day)", 
+       subtitle = "Horizontal bar indicates the threshold.", 
+       x = "Index", y = "One day moving average")
+```
+
+```{r, echo = FALSE}
+library(ggplot2)
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/"
+
+load(paste0(current_path, "amo4_comp_BUCB.Rda"))
+load(paste0(current_path, "amo4_comp_APT.Rda"))
+load(paste0(current_path, "amo4_comp_UNIFORM.Rda"))
+load(paste0(current_path, "amo4_comp_AugUCB.Rda"))
+load(paste0(current_path, "amo4_comp_LR.Rda"))
+load(paste0(current_path, "amo4_comp_EVT.Rda"))
+
+load(paste0(current_path, "amo4sim_comp_BUCB.Rda"))
+load(paste0(current_path, "amo4sim_comp_APT.Rda"))
+load(paste0(current_path, "amo4sim_comp_UNIFORM.Rda"))
+load(paste0(current_path, "amo4sim_comp_AugUCB.Rda"))
+load(paste0(current_path, "amo4sim_comp_LR.Rda"))
+load(paste0(current_path, "amo4sim_comp_EVT.Rda"))
+
+alg_names <- c(rep(c("Uniform", "APT", "AugUCB","LR", "B-UCB"), 
+                   each = 10071), rep("EVT", 10061))
+index <- c(rep(10:10080, times = 5), 20:10080)
+alg_res <- log(c(amo4_comp_UNIFORM, amo4_comp_APT, amo4_comp_AugUCB, amo4_comp_LR, amo4_comp_BUCB, amo4_comp_EVT))
+source_name <- rep("Real", 60416)
+loc4_comp_res <- data.frame(source = source_name, 
+                            index = index, names = alg_names, 
+                            results = alg_res)
+
+alg_names <- c(rep(c("Uniform", "APT", "AugUCB", "LR", "B-UCB"), 
+                   each = 10071), rep("EVT", 10061))
+index <- c(rep(10:10080, times = 5), 20:10080)
+alg_res <- log(c(amo4sim_comp_UNIFORM, amo4sim_comp_APT, amo4sim_comp_AugUCB,
+                 amo4sim_comp_LR, amo4sim_comp_BUCB, amo4sim_comp_EVT))
+source_name <- rep("Synthetic", 60416)
+loc4sim_comp_res <- data.frame(source = source_name, index = index, 
+                               names = alg_names, results = alg_res)
+loc4total <- rbind(loc4_comp_res, loc4sim_comp_res)
+
+ggplot(loc4total, aes(x = index, y = results, 
+                      group = names, color = names)) + 
+  geom_line() +
+  facet_grid(.~source) +
+  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
+  labs(title = "Results of Real Data Experiment 2", 
+       subtitle = paste0("Sample Mean Complexity of "), 
+       y = "log(Error)", x = "Round Index")
+```

### 2017-08-13 Thesis/Draft.tex
Add experiment results discussion to thesis draft

@@
 \[
--\log(LR(\mu_0||\mu_1)) = n(\log\Big(\frac{1-\mu_0}{1-\mu_1}\Big)) - \Big(\log(\frac{\mu_0}{1-\mu_0}) - \log(\frac{\mu_1}{1-\mu_1})\Big)\sum_{i=1}^{n}x_i = (1-\hat{\mu})\log\Big(\frac{1-\mu_1}{1-\mu_0}\Big) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0})
+-\log(LR(\mu_0||\mu_1)) = n(\log\Big(\frac{1-\mu_0}{1-\mu_1}\Big)) - \Big(\log(\frac{\mu_0}{1-\mu_0}) - \log(\frac{\mu_1}{1-\mu_1})\Big)\sum_{i=1}^{n}x_i = n \Big( (1-\hat{\mu})\log\Big(\frac{1-\mu_1}{1-\mu_0}\Big) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}) \Big)
 \]
@@
 \[
--\log(LR(\tau||\hat{\mu})) = KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = d(\hat{\mu},\tau)
+-\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n \Big(\hat{\mu}\log\big(\frac{\hat{\mu}}{\tau}\big) + (1-\hat{\mu})\log\big(\frac{1-\hat{\mu}}{1-\tau}\big)\Big)
 \]
@@
 \[
--\log(LR(\mu_0||\mu_1)) = n(\mu_0 - \mu_1) - (\log(\mu_0) - \log(\mu_1))\sum_{i=1}^n x_i = (\mu_0 - \mu_1) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}\Big)
+-\log(LR(\mu_0||\mu_1)) = n(\mu_0 - \mu_1) - (\log(\mu_0) - \log(\mu_1))\sum_{i=1}^n x_i = n\Big((\mu_0 - \mu_1) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}\Big)\Big)
 \]
@@
 \[
--\log(LR(\tau||\hat{\mu})) = KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = d(\hat{\mu},\tau) = (\tau - \hat{\mu}) + \hat{\mu}\log\Big(\frac{\hat{\mu}}{\tau}\Big)
+-\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n\Big((\tau - \hat{\mu}) + \hat{\mu}\log\Big(\frac{\hat{\mu}}{\tau}\Big)\Big)
 \]
@@
 \[
--\log(LR(\mu_0||\mu_1)) = n (\frac{\mu_0^2}{2\sigma^2} - \frac{\mu_1^2}{2\sigma^2}) - (\frac{\mu_0}{\sigma^2} - \frac{\mu_1}{\sigma^2})\sum_{i=1}^nx_i = \frac{1}{2\sigma^2}\Big(\mu_0^2-\mu_1^2 - 2\mu_0\hat{\mu} + 2\mu_1\hat{\mu}\Big)
+-\log(LR(\mu_0||\mu_1)) = n (\frac{\mu_0^2}{2\sigma^2} - \frac{\mu_1^2}{2\sigma^2}) - (\frac{\mu_0}{\sigma^2} - \frac{\mu_1}{\sigma^2})\sum_{i=1}^nx_i = n\frac{1}{2\sigma^2}\Big(\mu_0^2-\mu_1^2 - 2\mu_0\hat{\mu} + 2\mu_1\hat{\mu}\Big)
 \]
@@
 \[
--\log(LR(\tau||\hat{\mu})) = KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = d(\hat{\mu},\tau) = \frac{(\hat{\mu} - \tau)^2}{2\sigma^2}.
+-\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n\frac{(\hat{\mu} - \tau)^2}{2\sigma^2}.
 \]
+
+\paragraph{\texorpdfstring{Example 4: Gamma distributions with known
+shape parameter
+\(\alpha\)}{Example 4: Gamma distributions with known shape parameter \textbackslash{}alpha}}\label{example-4-gamma-distributions-with-known-shape-parameter-alpha}
+
+We have \(T(x_i) = x_i\), \(\theta = -\alpha/\mu\),
+\(\Theta = (-\infty, 0)\), \(b(\theta) = -\alpha \log(-\theta)\),
+\(\mu \in (0,+\infty)\). Then \(b'(\theta) = -\mu\), and we can write
+
+\[
+-\log(LR(\mu_0||\mu_1)) = n\alpha(-\log(\frac{\alpha}{\mu_0}) - \log(\frac{\mu_1}{\alpha})) - (-\frac{\alpha}{\mu_0} + \frac{\alpha}{\mu_1})\sum_{i=1}^{n}x_i = n\alpha \Big(\log\big(\frac{\mu_0}{\mu_1}\big) - \frac{\hat{\mu}}{\mu_1} + \frac{\hat{\mu}}{\mu_0}\Big).
+\] And again, if we let \(\mu_1 = \hat{\mu}\) and \(\mu_0 = \tau\), then
+
+\[
+-\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n\alpha \Big(\frac{\hat{\mu}}{\tau} - 1 - \log\big(\frac{\hat{\mu}}{\tau}\big)\Big).
+\]
+
+For \(\alpha = 1\), the Gamma distribution is equal to the Exponential
+distribution.
+
+Given these results for the exponential family of distributions, we can
+now define the SLR (Simple Likelihood Ratio) algorithm.
+
+\subsubsection{1D-SLR Algorithm for One-Dimensional Exponential Family
+of
+Distributions}\label{d-slr-algorithm-for-one-dimensional-exponential-family-of-distributions}
+
+Very similar to the APT algorithm, the SLR algorithm receives as input
+the definition of the problem \((\tau, \epsilon)\) (compare Locatelli et
+al., 2016). Additionally, the algorithm receives as input the name of
+the distribution that the arms follow, as well as potential additional
+parameters (\(\sigma_1, ..., \sigma_K\) for Normal distributions,
+\(\alpha_1, ..., \alpha_K\) for Gamma distributions). We assume that
+each arm follows the same kind of distribution, with potentially
+different parameters \(\theta_1, ..., \theta_K\). The algorithm pulls
+each arm once. At time \(t>K\), the algorithm updates the number of
+pulls for arm \(i\) at time \(t\), \(T_i(t)\), for each arm, as well as
+the empirical mean \(\hat{\mu}_i(t)\) of arm \(i\) after \(T_i(t)\)
+pulls. The empirical mean is calculated for each arm
+\(k\in \{1,...,K\}\) as
+\(\hat{\mu}_i(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)} x_{i,s}\), with
+\(T_i(t) = \sum_{s=1}^{t}\mathbb{I}(I_s = i)\). As in Locatelli et al.
+(2016), the \(X_{i,s}\) is the sample received when pulling arm \(i\)
+for the \(s\)-th time. Depending on the distribution, the algorithm then
+computes the index
+
+\[
+B_i^{SLR}(t+1) = \mathbb{I}(\hat{\mu}\geq \tau)(-\log\big(LR(\tau-\epsilon||\hat{\mu}_i(t))\big) + \mathbb{I}(\hat{\mu}< \tau)(-\log\big(LR(\tau+\epsilon||\hat{\mu}_i(t))\big) = T_i(t) \Big( \mathbb{I}(\hat{\mu}\geq \tau)\cdot KL(\nu_{b'^{-1}(\hat{\mu}(t))}||\nu_{b'^{-1}(\tau-\epsilon)}) + \mathbb{I}(\hat{\mu} < \tau)\cdot KL(\nu_{b'^{-1}(\hat{\mu}(t))}||\nu_{b'^{-1}(\tau+\epsilon)}) \Big).
+\]
+
+The next arm to be pulled is the minimizer of the index
+\(B_i^{SLR}(t+1)\), \(I_{t+1} = \arg \min_{i\leq K} B_i(t+1)\). At the
+end of the horizon \(T\), the algorithm outputs the set of arms
+\(\hat{S}_\tau = \{k: \hat{\mu}_k(T) \geq \tau\}\).
+
+\subsubsection{2D-SLR Algorithm for Normal Distributions with Unknown
+Mean and Unknown
+Variance}\label{d-slr-algorithm-for-normal-distributions-with-unknown-mean-and-unknown-variance}
+
+As soon as we move away from univariate distributions parameterized by
+their mean, it becomes less clear how the likelihood ratio for
+\(H_0: \mu = \tau\) and \(H_1: \mu = \hat{\mu}\) should be calculated.
+In the case of Normal distributions with unknown mean and unknown
+variance, given that the variance and mean estimate are linked, we can
+use
+\(H_0: \mu = \tau \land \sigma^2 = \sigma^2_{\tau} = \frac{1}{n}\sum_{i=1}^{n}(x_i-\tau)^2\)
+and the alternative hypothesis based on the maximum likelihood estimates
+\(H_1: \mu = \hat{\mu} \land \sigma^2 = \hat{\sigma}^2 = \frac{1}{n}\sum_{i=1}^{n}(x_i-\hat{\mu})^2\).
+
+In the following, we assume \(\epsilon = 0\).
+
+Now, at each round \(t\), the algorithm computes \(T_i(t)\) and
+\(\hat{\mu}_i(t)\) as before, but additionally the empirical variances
+\(\sigma_{\tau,i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\tau)^2\)
+and
+\(\hat{\sigma}_{i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\hat{\mu})^2\).
+The index is then given by
+
+\[
+B_i^{2DSLR}(t+1) = -\log(LR(\tau, \sigma_{\tau,i}^2(t)||\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t))) = T_i(t) \log\Big(\frac{\sigma_{\tau,i}^2(t)}{\hat{\sigma}_i^2(t)}\Big) = T_i(t) KL(\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t)||\tau, \sigma_{\tau,i}^2(t))
+\]
+
+(SHOW THAT THE NOTATION CAN BE ABUSED AND THE KL WRITTEN THIS WAY
+BECAUSE UNIQUELY DEFINED BY MEAN AND VARIANCE)
+
+Then, as for the univariate case, the next arm to be pulled is the
+minimizer of the index \(B_i^{2DSLR}(t+1)\),
+\(I_{t+1} = \arg \min_{i\leq K} B_i(t+1)\). At the end of the horizon
+\(T\), the algorithm outputs the set of arms
+\(\hat{S}_\tau = \{k: \hat{\mu}_k(T) \geq \tau\}\).
 
@@
 \endhead
-Training & 0.027 & 0.001 & 0.013 & 0.158 & 0.071 & 0.071 & 0.059 & 0.053
-& 0.156 & 0.102\tabularnewline
-Test & 0.022 & 0.000 & 0.011 & 0.130 & 0.064 & 0.060 & 0.058 & 0.055 &
-0.150 & 0.115\tabularnewline
-TrainingMinusTau & -0.006 & -0.033 & -0.021 & 0.125 & 0.038 & 0.038 &
-0.026 & 0.019 & 0.123 & 0.068\tabularnewline
+Training & 0.001 & 0.013 & 0.027 & 0.053 & 0.059 & 0.071 & 0.071 & 0.102
+& 0.156 & 0.158\tabularnewline
+Test & 0.000 & 0.011 & 0.022 & 0.055 & 0.058 & 0.064 & 0.060 & 0.115 &
+0.150 & 0.130\tabularnewline
+TrainingMinusTau & -0.033 & -0.021 & -0.006 & 0.019 & 0.026 & 0.038 &
+0.038 & 0.068 & 0.123 & 0.125\tabularnewline
 \bottomrule
@@
 
+These difficulties seem to have a large impact on the performance of all
+algorithms. Given that the data are \(\{0,1\}\) observations, we can
+compare all algorithms in a setting in which one expects all assumptions
+to hold before having observed the data. The distribution is
+sub-Gaussian for the APT algorithm, bounded between \(0\) and \(1\) for
+the variance-based algorithms, and assumed to be Bernoulli for the SLR
+algorithm. Additionally, we use the B-UCB algorithm as it performed
+often best on the synthetic data.
+
+We set \(\epsilon = 0\), and \(\tau = 2/60\). For the AugUCB algorithm
+we use the parameters as in Mukherjee et al. (2017), that is,
+\(\rho = 1/3\). For B-UCB we set the prior to \(\alpha = \tau\) and
+\(\beta = 1-\tau\). All other algorithms are parameter free.
+
+The corresponding results are shown in the next figure.
+
+\includegraphics{Draft_files/figure-latex/unnamed-chunk-5-1.pdf}
+
+Compared to the previous simulations with synthetic data, the results
+are dramatic. First of all, we see that all strategies perform not well.
+All of them end above the 10\% error mark after 1 week of data. Second,
+the uniform sampling strategy fares best when evaluated against the
+sample mean of all observations used during training. This of course is
+the opposite of what we would like to see, and the opposite of what we
+saw on the synthetic data, where we were able to improve upon the naive
+strategy. Third, again in contrast to the results on synthetic data, we
+observe non-monotonicity in the error curves. Given that the highs and
+lows run very much parallel for the different models, it stands to
+reason that this effect is caused by the variation in means of the arms
+over time. Indeed, roughly comparing the error curves to the moving
+averages in the previous figure, the increase in errors after round
+\(5000\) and the decreasing error after round \(7500\) seems to line up
+more or less with the fluctuations observed in the data. Given that we
+evaluate the models against a sample mean of all observations, it is not
+surprising that the uniform sampling strategy has a certain advantage
+when it comes to ``factoring out'' the seasonalities. In contrast, the
+adaptive sampling schemes try to adapt more or less quickly to the
+changes in the means; a feature that would be valuable in a cumulative
+regret multi-armed bandit setting. Here, however, it leads to wrong
+estimates of the sample mean.
+
+If we focus on a comparison of adaptive sampling strategies and less on
+their globally bad performance, we see that the variance based
+strategies perform worse than APT and SLR. Very dramatic is the behavior
+of the Augmented-UCB algorithm, which first seems to perform well; that,
+however, is a result of it mostly pulling arms uniformly, until it
+starts to adapt its sampling and discarding arms after nearly 5000
+rounds. The result is a dramatic increase in error which leads to the
+worst performs at the end of the budget. The difference between APT,
+SLR, and EVT is not very large, and their performance fluctuates in
+sync. None of them is really able to converge due to the changes in the
+underlying means. Advantageous only seems to be the fact that their
+behavior is less erratic than that of the Augmented-UCB strategy given
+that they do not discard arms.
+
 \subsubsection{\texorpdfstring{Experiment 2:
@@
 
+In order to underline the results of the previous experiment, we perform
+a second experiment using the data collected by Amorelie. We increase
+the threshold to \(\tau = \frac{5}{60} = 0.833\) to make the problem in
+general slightly easier, and again pick 10 arms at random from the data
+set of 197 arms. We again use a rolling window of \(10080\) observations
+to create \(5000\) iterations and look at the training and test sample
+means as in Experiment 1.
+
+Some arms, in particular \(V110\) and \(V150\), but also \(V103\),
+\(V149\), \(V104\), and \(V112\) are quite close to the threshold. Two
+arms, \(V129\) and \(V32\) appear to have basically no positive
+observation in the training set. On the other hand, arm \(V154\) is
+larger than the threshold by a fair amount and should be easier to
+classify.
+
+\begin{longtable}[]{@{}lrrrrrrrrrr@{}}
+\caption{Count rates for ten products for both training and test
+sample.}\tabularnewline
+\toprule
+& V129 & V32 & V76 & V103 & V149 & V104 & V110 & V150 & V112 &
+V154\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+& V129 & V32 & V76 & V103 & V149 & V104 & V110 & V150 & V112 &
+V154\tabularnewline
+\midrule
+\endhead
+Training & 0.000 & 0.000 & 0.012 & 0.044 & 0.049 & 0.053 & 0.055 & 0.095
+& 0.123 & 0.199\tabularnewline
+Test & 0.013 & 0.000 & 0.011 & 0.040 & 0.049 & 0.063 & 0.060 & 0.114 &
+0.137 & 0.202\tabularnewline
+TrainingMinusTau & -0.083 & -0.083 & -0.071 & -0.039 & -0.035 & -0.030 &
+-0.028 & 0.011 & 0.039 & 0.116\tabularnewline
+\bottomrule
+\end{longtable}
+
+As in the previous experiment, we can also take a look at the one day
+moving averages of the arms to quickly assess the time dependency of the
+means. Given that the data here are collected at the same time points as
+the data used in the previous experiment, it is not surprising to see a
+similar spike in means during the second half of the observations with
+the maximum moving average around index 7500. We also observe that these
+fluctuations are heavier for products with in general larger means (that
+is, more visitors on the website). But these fluctuations are clearly
+much larger and systematic than those observed for synthetic data with
+the same sample means. While the moving average of product \(V159\) in
+the synthetic data has a valley after index 5000, this can be explained
+by the natural variance (which increases as the mean is closer to
+\(0.5\)).
+
+Given the moving averages and the previous experiment, the performance
+results of Experiment 2 shown in the next figure are not surprising. We
+recognize the same structure as previously. The uniform sampling
+strategy performs the best. The adaptive sampling strategies perform
+bad, do not converge, and end above the 10\% error mark. This time,
+Augmented-UCB is not (yet) the worst performing strategy, but equally
+erratic after it actually adapts its sampling. This time around, it even
+has two spikes in its adaptive phase. Again, APT, SLR, and EVT perform
+in sync and more or less equally bad, with EVT slightly better than APT
+and SLR this time around. Interestingly, Bayes-UCB performs clearly
+worst of all strategies. Its performance changes at the same time as
+Augmented-UCB starts to adapt its sampling strategy, near round 7000.
+
+This last fact is of particular interest, as Bayes-UCB is dramatically
+better than the other strategies in experiments on synthetic data. On
+the right hand side of the same figure, the performance of the
+algorithms on synthetic data from Bernoulli distributions with the same
+sample mean is depicted. On this data, Bayes-UCB performs very well,
+ending at an average error of about 0.1\% of the simulations. This
+mirrors its performance observed in the previous simulations with
+synthetic data. Also all other strategies perform clearly better now,
+and their error rates are strictly decreasing. Interestingly, the
+uniform sampling scheme is now much worse than in the experiment on real
+data; it does no longer have the advantage of sampling the different
+mean phases at a representative rate. Instead, it is no in its original
+position of serving as upper bound on the error rate. Excluding
+Bayes-UCB, we see that the SLR algorithm performs better the best,
+followed by the variance-based algorithms. APT comes in at the same
+error rate as uniform sampling. While the difference between SLR and EVT
+are less than 2\% (1.2\% vs 3\%), the difference to uniform sampling
+(10\%) is relevant. The performance of 10\% error rate is achieved by
+SLR about 1000 observations earlier than by EVT.
+
+\includegraphics{Draft_files/figure-latex/unnamed-chunk-6-1.pdf}
+
+\includegraphics{Draft_files/figure-latex/unnamed-chunk-7-1.pdf}
+
 \end{document}

### 2017-08-13 Thesis/experiment_postprocessing/real_exp_1week_2_postprocessing.R

@@ -1,0 +1,14 @@
+# Post processing of data for arm sequence visualization.
+# This is for Experiment 2 on real data as used in thesis.
+
+##########################################################
+
+# load the algorithm results from Experiment 2
+
+library(plyr)
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/"
+
+

### 2017-08-13 real_experiments/real_exp_1week_2_sim.R

@@ -117,18 +117,18 @@ gc()
 
 round(data_amo4_mean_firsthalf - tau_amo4,2)
 
-load(paste0(current_path, "amo4_comp_UNIFORM.Rda"))
-load(paste0(current_path, "amo4_comp_APT.Rda"))
+load(paste0(current_path, "amo4sim_comp_UNIFORM.Rda"))
+load(paste0(current_path, "amo4sim_comp_APT.Rda"))
 load(paste0(current_path, "amo4sim_comp_LR.Rda"))
-load(paste0(current_path, "amo4_comp_AugUCB.Rda"))
-load(paste0(current_path, "amo4_comp_EVT.Rda"))
-load(paste0(current_path, "amo4_comp_BUCB.Rda"))
+load(paste0(current_path, "amo4sim_comp_AugUCB.Rda"))
+load(paste0(current_path, "amo4sim_comp_EVT.Rda"))
+load(paste0(current_path, "amo4sim_comp_BUCB.Rda"))
 
 plot(c(0,10080), c(0, -5), type = "n")
 lines(log(amo4sim_comp_UNIFORM), col = "black")
-lines(log(amo4_comp_APT), col = "blue")
-lines(log(amo4_comp_AugUCB), col = "green")
-lines(log(amo4_comp_EVT), col = "darkgreen")
+lines(log(amo4sim_comp_APT), col = "blue")
+lines(log(amo4sim_comp_AugUCB), col = "green")
+lines(log(amo4sim_comp_EVT), col = "darkgreen")
 lines(log(amo4sim_comp_LR), col = "red")
-lines(log(amo4_comp_BUCB), col = "violet")
+lines(log(amo4sim_comp_BUCB), col = "violet")
 abline(h = log(0.1), lty = 2)

### 2017-08-17 Thesis/Draft.Rmd
add description of experiments

@@
 
+### Discussion
+
+At the beginning of this thesis, we set out to find an algorithm that improves upon the Anytime Parameter Free algorithm introduced in Locatelli et al.
+(2016) for the thresholding bandit problem in two directions.
+First, we wanted to make the algorithm perform better in problems that are not well approximated as sub-Gaussian; that is, in particular a problem with Bernoulli arms with small means and low threshold.
+Unsurprisingly, this meant that we need to find a solution that takes more into account than just the sample mean.
+With the Simple Likelihood Ratio strategy, we propose an algorithm that fulfills that goal at the cost of being distribution specific.
+
+The Simple Likelihood Ratio strategy requires the knowledge of the class of distribution upfront, just as other algorithms require parameters.
+While this is likely to be a negligiable problem in the case of $\{0,1\}$ observations which can be modeled reasonably by Bernoulli distributions if we are only interested in estimating the mean, it can be more difficult to know the true class of distribution upfront when the random variables can take values in $\mathbb{R}$.
+We have shown however, that the SLR strategy can be adapted to all univariate distributions in the exponential family of distributions.
+The algorithm even offers a natural adaptation to the problem of normal distributions with unknown mean and unknown variance.
+
+Furthermore, the Simple Likelihood Ratio strategy reduces to the Anytime Parameter Free strategy in the case where arms are normally distributed with equal variance that is known upfront.
+In that case we have as index (compare example 3 above):
+
+$$
+B_i^{SLR}(t) = T_i(t)\frac{(\hat{\mu}_i(t) - \tau)^2}{2\sigma^2}.
+$$
+In order to decide at time $t$ which arm to draw next, we necessarily compare the indices of arm $i$ and arm $j$. Assume w.l.o.g. that $B_i^{SLR}(t) < B_j^{SLR}(t)$. Then:
+
+$$
+B_i^{SLR}(t) < B_j^{SLR}(t) \Leftrightarrow 
+T_i(t)\frac{(\hat{\mu}_i(t) - \tau)^2}{2\sigma^2} < T_j(t)\frac{(\hat{\mu}_j(t) - \tau)^2}{2\sigma^2} 
+\Leftrightarrow 
+\sqrt{T_i(t)}\sqrt{(\hat{\mu}_i(t) - \tau)^2} < \sqrt{T_j(t)}\sqrt{(\hat{\mu}_j(t) - \tau)^2}
+\Leftrightarrow 
+B_i^{APT}(t) < B_j^{APT}(t)
+$$
+
+Given that in all other cases the Simple Likelihood Strategy is able to take more information about the distributions into account through the Kullback-Leibler divergence (in the case of the exponential family of distributions), the algorithm is expected to improve upon the Anytime Parameter Free strategy.
+
+As mentioned before, this improvement comes only at the cost of knowing the correct distribution upfront.
+In particular, as for the Anytime Parameter Free algorithm, there are no parameters which would need to be tuned upfront as is usually the case for upper-confidence bound based algorithms.
+
+As we see in the experiments that follow, the Simple Likelihood Strategy is able to improve significantly upon the Anytime Parameter Free strategy in many cases.
+
 # Experiments
+
+## Synthetic Data
+
+In order to evaluate the empirical performance of the proposed algorithms, we run the algorithm on synthetic data as is usual.
+We compare its performance on this data not only against the APT algorithm, but also against the variance-based algorithms.
+Thus we also compare the variance-based algorithms for the first time directly against each other instead of just relative to the APT algorithm.
+
+Each of the experiments is repeated for 5000 iterations.
+Depending on the experiment, the observations are generated randomly by some distribution of the exponential family of distributions.
+As we were originally concerned with improving upon APT with respect to non-sub-Gaussian distributions, the first experiments focus on Bernoulli distributions, and especially those with small means.
+We then go on to show with experiments on Gaussian, Exponential, and Poisson data that the SLR algorithm is able to improve upon APT given that we know the true kind of distribution.
+
+### Experiment 1: Bernoulli with $\tau = 0.5$
+
+The first experiment is equal to experiment 3 in Locatelli et al.
+(2016).
+We compare ten Bernoulli arms that move away from the threshold at $\tau = 0.5$ geometrically with $\mu_{1:4} = 0.4-0.2^{1:4}$, $\mu_5 = 0.45$, $\mu_6 = 0.55$, and $\mu_{7:10} = 0.6 + 0.2^{5-1:4}$.
+We run the standard APT algorithm with $\epsilon = 0.1$, as well as SLR with $\epsilon = 0.1$.
+We compare those additionally to Augmented-UCB with the standard parameter choice of $\rho = 1/3$ as used by its authors in Mukherjee et al.
+(2017).
+We run the parameter-free version of the Empirical Variance Guided algorithm without any feedback delay, thus making it directly comparable to the other algorithms.
+The Bayes-UCB algorithm takes as prior a Beta distribution with parameters $\alpha_0 = \tau$ and $\beta_0 = 1 - \tau$, thus leading to a mean of the prior distribution at $\tau$ while keeping the prior as weak as possible.
+Lastly, we run the uniform sampling strategy as the naive benchmark.
+
+```{r loc2_data_summary, echo = FALSE, message = FALSE}
+mean_loc2 <- c(0.4-0.2^(1:4),
+               0.45, 0.55,
+               0.6+0.2^(5-(1:4)))
+
+knitr::kable(t(mean_loc2), digits = 3, col.names = paste0("V", 1:10), caption = "Mean of arms in simulation 1.")
+```
+
+This first experiment gives an experiment where all algorithms should perform well.
+The problem is not very difficult, and due to the threshold at $\tau = 0.5$, the Bernoulli distribution can be perfectly approximated by a Gaussian.
+This thus is the perfect environment for the APT algorithm.
+
+As the next figure shows, essentially all methods converge rapidly to an error rate of zero.
+Except for the uniform method that clearly lacks behind.
+We also observe that the variance based algorithms (Augmented UCB and EVT) lag behind at first.
+Augmented UCB is able to adjust its sampling scheme after 1000 iterations and rapdily improves to the level of APT.
+EVT takes about 250 samples more to start a quick descend to the performance of the other algorithms.
+All of this, however, happens below an error rate of 0.01.
+While the SLR algorithm improves upon APT, the improvement is a slight one, and not very large in terms of budget difference.
+This underlines that the scenario at hand is the ideal one for the APT algorithm.
+
+```{r simulation1_results, echo = FALSE}
+library(ggplot2)
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
+
+load(paste0(current_path, "loc2_comp_BUCB_horizon_4000.Rda"))
+load(paste0(current_path, "loc2_comp_APT_2000.Rda"))
+load(paste0(current_path, "loc2_comp_LR_2000.Rda"))
+load(paste0(current_path, "loc2_comp_AugUCB_2000.Rda"))
+load(paste0(current_path, "loc2_comp_UNIFORM_2000.Rda"))
+load(paste0(current_path, "loc2_comp_EVT.Rda"))
+
+alg_names <- c(rep(c("Uniform", "APT", "AugUCB","SLR"), 
+                   each = 1991), rep("B-UCB", 3991), rep("EVT", 1981))
+index <- c(rep(10:2000, times = 4), 10:4000, 20:2000)
+alg_res <- log(c(loc2_comp_UNIFORM_2000, loc2_comp_APT_2000, 
+                 loc2_comp_AugUCB_2000, loc2_comp_LR_2000,
+                 loc2_comp_BUCB_horizon_4000, loc2_comp_EVT))
+loc2_comp_res <- data.frame(index = index, names = alg_names, 
+                            results = alg_res)
+ggplot(loc2_comp_res, aes(x = index, y = results)) + 
+  geom_line(aes(group = names, color = names)) +
+  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
+  labs(title = "Results of Synthetic Experiment 1", 
+       subtitle = expression(paste("Ideal scenario for APT; ", 
+                                   tau,' = 0.5')), 
+       y = "log(Error)", x = "Round Index") + 
+  coord_cartesian(xlim = c(0,2000)) +
+  scale_color_discrete(name = "Algorithm")
+
+```
+
+### Experiment 2: Bernoulli with $\tau = 0.05$
+
+In the second experiment, we compare the same algorithms as in the first experiment.
+Again, we classify 10 arms, but this time against a threshold of $\tau = 0.05$ and without an epsilon interval, $\epsilon = 0$.
+Consequently, we choose the distributions for the arms to be much smaller too, and arrange them symmetrically around the threshold.
+While the distributions are bounded and thus still sub-Gaussian, the Normal approximation should be poor in comparison to the previous case.
+We expect an improvement for the SLR algorithm compared to APT as it takes the Bernoulli characteristics into account.
+For example, even though the arms are symmetrically distributed around the threshold in terms of absolute distance, they are not symmetrically around the threshold in terms of their Kullback-Leibler divergence given the threshold is unequal 0.5.
+Thus we expect the SLR algorithm to not pull them equally.
+Furthermore, we expect an improvement for the variance-based algorithms, as the variances are now smaller than in experiment 1, which should at least benefit the EVT algorithm given its theoretical analysis.
+
+The figure below shows the performance of all algorithms.
+We see that the problem appears to be significantly more difficult in general.
+The variance based algorithms perform maybe surprisingly bad; EVT even worse than uniform sampling nearly until the horizon, while Augmented UCB takes a long time to adjust away from uniform sampling.
+Both algorithms perform worse than APT after 7000 rounds.
+One potential reason for this might be the fact that the index used by the EVT algorithm reduces to $B_i^{EVT}(t) = \sqrt{T_i(t)} \cdot \sqrt{|\hat{\mu}_i(t) - \tau|}$ if $\hat{\sigma}_i^2(t) = 0$, which, given Bernoulli arms with small means, could be the case for long runs of the algorithm.
+In contrast, the index of the APT algorithm is  $B_i^{APT}(t) = \sqrt{T_i(t)} \cdot |\hat{\mu}_i(t) - \tau|$.
+
+One interesting observation, that we will observe in all experiments with synthetic Bernoulli arms, is the superior performance of the Bayes-UCB algorithm adapted from Kaufmann and Kalyanakrishnan (2013) which was originally designed for cumulative regret problems.
+Nonetheless, the algorithm will again and again proof to be the best performing.
+
+While the Bayes-UCB performance is impressive, we observe that also the Simple Likelihood Ratio strategy improves considerably upon the alternative strategies.
+SLR reaches the average empirical error of 0.1 within the budget, and the improvement is exponential within the entire budget; in contrast to APT which appears to improve linearly in the observations.
+At the end of the budget, the difference in the empirical error is nearly 10% between the two strategies.
+
+In order to assess how the SLR strategy improves upon the APT algorithm, we can use the fact that we have run the experiment for 5000 iterations.
+We thus can look at how often each arm was pulled by a strategy at any given round.
+Across the 5000 iterations, the algorithm should pull at any given iteration the arm most often that it thinks is the most difficult to classify.
+In the figure below, we plot the resulting curves where the value at an iteration is the 10-round moving average to remove some unimportant variation.
+
+We see that both APT and SLR correctly single out the two arms that are much closer to the threshold than the remaining arms and allocate most of the budget to them.
+However, while SLR keeps the two arms constant at two different levels (about 1900 for arm 5 and about 2500 for arm 6), APT at first pulls arm 5 much more than arm 6.
+Then, the budget allocated to the two arms appears to converge to about 2000.
+Given that the two arms are symmetric around the threshold, it makes sense that APT would allocate the same exploration effort to both of them.
+And given that the variation of arm 5 away from the threshold is limited from below by zero, it is much easier for arm 6 to have an empirical mean larger than it's true mean, and thus to have a larger index than arm 5.
+Consequently, APT would prefer to sample arm 5.
+This, however, is wrong in terms of Kullback-Leibler divergence.
+Measured by the divergence, arm 6 is closer to the threshold than arm 5, thus harder to classify, and consequently preferred by the SLR algorithm.
+Furthermore, the SLR algorithm appears to quickly find the correct share that it has to allocate to the two arms.
+In contrast to APT which continues to adjust the shares across the entire budget.
+
+Additionally, we can observe that the SLR strategy starts to drop arms much quicker than APT, and it drops arm 1 to 3 first, which again underlines the effect of the asymmetric Kullback-Leibler divergence.
+If we consider arm 3 and arm 8, we have $d(0.01||0.05) \approx 0.025$ while $d(0.09||0.05) = 0.014$.
+The divergence is much smaller for arm 8.
+The asymmetry is even more dramatic for arm 1 and arm 10 with $d(0.001||0.05) \approx 0.046$ and $d(0.099||0.05) \approx 0.020$; in terms of the divergence, the distance between arm 1 and the threshold is twice as far as between arm 10 and the threshold.
+APT considers them to be equally distant from the threshold.
+
+```{r loc6nt_data_summary, echo = FALSE, message = FALSE}
+mean_loc6nt <- c(0.001, 0.005, 0.01, 0.015,
+                 0.04, 0.06,
+                 0.085, 0.09, 0.095, 0.099)
+
+knitr::kable(t(mean_loc6nt), digits = 3, col.names = paste0("V", 1:10), caption = "Mean of arms in simulation 2 classified against threshold of 0.05.")
+```
+
+```{r simulation2_results, echo = FALSE}
+library(ggplot2)
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
+
+load(paste0(current_path, "loc6nt_comp_BUCB_horizon_7000.Rda"))
+load(paste0(current_path, "loc6nt_comp_AugUCB_7000.Rda"))
+load(paste0(current_path, "loc6nt_comp_UNIFORM_7000.Rda"))
+load(paste0(current_path, "loc6nt_comp_APT_7000.Rda"))
+load(paste0(current_path, "loc6nt_comp_LR_7000.Rda"))
+load(paste0(current_path, "loc6nt_comp_EVT.Rda"))
+
+alg_names <- c(rep(c("Uniform", "APT", "AugUCB","SLR", "B-UCB"), 
+                   each = 6991), rep("EVT", 6981))
+index <- c(rep(10:7000, times = 5), 20:7000)
+alg_res <- log(c(loc6nt_comp_UNIFORM_7000, loc6nt_comp_APT_7000,
+                 loc6nt_comp_AugUCB_7000, loc6nt_comp_LR_7000,
+                 loc6nt_comp_BUCB_horizon_7000, loc6nt_comp_EVT))
+loc6nt_comp_res <- data.frame(index = index, names = alg_names, 
+                            results = alg_res)
+ggplot(loc6nt_comp_res, aes(x = index, y = results)) + 
+  geom_line(aes(group = names, color = names)) +
+  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
+  labs(title = "Results of Synthetic Experiment 2", 
+       subtitle = expression(paste("Difficult scenario for APT; ", 
+                                   tau,' = 0.05 and 10 arms. Dashed line at Error = 0.1.')), 
+       y = "log(Error)", x = "Round Index") +
+  scale_color_discrete(name = "Algorithm")
+```
+
+```{r, echo = FALSE, message = FALSE}
+load(file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/loc6nt_ma.Rda")
+library(dplyr)
+
+rbind(loc6nt_APT_ma, loc6nt_LR_ma) %>%
+  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
+  geom_line(size = 0.3) +
+  facet_grid(.~algorithm) +
+  labs(x = "Index", y = "10 Rounds Moving Average",
+       title = "Average Number of Pulls Allocated to Each Arm per Round",
+       subtitle = "5000 iterations; a value of 1000 means that in 20% of 
+the iterations the arm was pulled in that round.")
+
+```
+
+### Experiment 3: Bernoulli with $\tau = 0.01$
+
+In the third experiment, we lower the threshold further to $\tau = 0.1$ and arrange the arms on a $\log_{10}$ scale around it.
+Again, there is no epsilon interval.
+We add one additional arm, thus now classifying eleven arms.
+We run the same arms as previously.
+Notice that the experiment horizon is now $10000$ rounds instead of $7000$ rounds as in the previous experiment.
+We test the same algorithms used in the previous two experiments.
+
+If we look at the performance after 7000 rounds, we see that the problem appears to be slightly more difficult compared to the previous one.
+We see that up until this point the variance-based strategies cannot improve upon APT.
+Also, SLR has not yet crossed the 10% empirical error.
+However, we observe that in the following rounds EVT decreases at an exponential rate and thus crosses the error of APT and continues to improve upon it.
+At the end of the budget, the improvement of SLR compared to the other algorithms is again very large, and likely to increase.
+However, Bayes-UCB is again the best performing algorithm and is improving at a faster rate than SLR.
+As in the previous experiment, Bayes-UCB and SLR show significant improvements on this Bernoulli problem with very small means and threshold compared to APT in particular.
+
+```{r loc7nt_data_summary, echo = FALSE, message = FALSE}
+mean_loc7nt <- c(10^-4, 10^-3.5, 10^-3.25, 10^-3, 
+                 10^-2.75, 10^-2.5, 10^-2.25, 10^-1.85, 10^-1.75,
+                 10^-1.5, 10^-1)
+
+knitr::kable(t(mean_loc7nt), digits = 4, col.names = paste0("V", 1:11), caption = "Mean of arms in simulation 2 compared to a threshold of 0.01.")
+```
+
+```{r simulation3_results, echo = FALSE}
+library(ggplot2)
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
+
+load(file = paste0(current_path, "loc7nt_comp_UNIFORM_10000.Rda"))
+load(file = paste0(current_path, "loc7nt_comp_APT_10000.Rda"))
+load(file = paste0(current_path, "loc7nt_comp_LR_10000.Rda"))
+load(file = paste0(current_path, "loc7nt_comp_BUCB_horizon_10000.Rda"))
+load(file = paste0(current_path, "loc7nt_comp_AugUCB_10000.Rda"))
+load(file = paste0(current_path, "loc7nt_comp_EVT.Rda"))
+
+alg_names <- c(rep(c("Uniform", "APT", "AugUCB", "SLR", "B-UCB"), 
+                   each = 9990), rep("EVT", times = 9979))
+index <- c(rep(11:10000, times = 5), 22:10000)
+alg_res <- log(c(loc7nt_comp_UNIFORM_10000, loc7nt_comp_APT_10000,
+                 loc7nt_comp_AugUCB_10000, loc7nt_comp_LR_10000,
+                 loc7nt_comp_BUCB_horizon_10000, loc7nt_comp_EVT))
+loc7nt_comp_res <- data.frame(index = index, names = alg_names, 
+                            results = alg_res)
+ggplot(loc7nt_comp_res, aes(x = index, y = results)) + 
+  geom_line(aes(group = names, color = names)) +
+  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
+  geom_vline(aes(xintercept = 7000), linetype = 2) +
+  labs(title = "Results of Synthetic Experiment 3", 
+       subtitle = expression(paste("Difficult scenario for APT; ", 
+                        tau,' = 0.01 and 11 arms. Dashed line at Error = 0.1.')), 
+       y = "log(Error)", x = "Round Index")
+```
+
+## Experiment 4: Exponential Distribution with $\tau = 1$
+
+```{r simulation4_results, echo = FALSE}
+library(ggplot2)
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/exponential/"
+
+load(paste0(current_path, "exp2_comp_LR.Rda"))
+load(paste0(current_path, "exp2_comp_APT.Rda"))
+load(paste0(current_path, "exp2_comp_EVT.Rda"))
+load(paste0(current_path, "exp2_comp_UNIFORM.Rda"))
+
+alg_names <- c(rep(c("Uniform", "APT","SLR"), 
+                   each = 3981), rep("EVT", 3961))
+index <- c(rep(20:4000, times = 3), 40:4000)
+alg_res <- log(c(exp2_comp_UNIFORM, exp2_comp_APT, exp2_comp_LR, exp2_comp_EVT))
+exp2_comp_res <- data.frame(index = index, names = alg_names, 
+                            results = alg_res)
+ggplot(exp2_comp_res, aes(x = index, y = results)) + 
+  geom_line(aes(group = names, color = names)) +
+  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
+  labs(title = "Results of Experiment 4", 
+       subtitle = expression(paste("Exponential distributed arms; ", 
+                        tau,' = 1 and 20 arms. Dashed line at Error = 0.1.')), 
+       y = "log(Error)", x = "Round Index")
+```
+
+## Experiment 5: Poisson Distribution with $\tau = 1$
+
+```{r simulation5_results, echo = FALSE}
+library(ggplot2)
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/poisson/"
+
+load(paste0(current_path, "pois2_comp_LR.Rda"))
+load(paste0(current_path, "pois2_comp_APT.Rda"))
+#load(paste0(current_path, "pois2_comp_EVT.Rda"))
+#load(paste0(current_path, "pois2_comp_UNIFORM.Rda"))
+
+alg_names <- c(rep("APT", 7981), rep("SLR", 9981))
+index <- c(20:8000, 20:10000)
+alg_res <- log(c(pois2_comp_APT, pois2_comp_LR))
+pois2_comp_res <- data.frame(index = index, names = alg_names, 
+                            results = alg_res)
+ggplot(pois2_comp_res, aes(x = index, y = results)) + 
+  geom_line(aes(group = names, color = names)) +
+  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
+  labs(title = "Results of Experiment 4", 
+       subtitle = expression(paste("Poisson distributed arms; ", 
+                        tau,' = 0.4 and 20 arms. Dashed line at Error = 0.1.')), 
+       y = "log(Error)", x = "Round Index")
+```
 
@@
 
-knitr::kable(rbind(Training, Test, TrainingMinusTau)[,order(Training)], digits = 3, col.names = names(data_amo3_mean_firsthalf),
+knitr::kable(rbind(Training, Test, TrainingMinusTau)[,order(Training)], digits = 3, col.names = names(data_amo3_mean_firsthalf)[order(Training)],
              caption = "Count rates for ten products for both training and test sample.")
@@
 
-#load(paste0(current_path, "amo3_comp_BUCB.Rda"))
+load(paste0(current_path, "amo3_comp_BUCB.Rda"))
 load(paste0(current_path, "amo3_comp_APT.Rda"))
@@
 
-alg_names <- c(rep(c("Uniform", "APT", "AugUCB","LR"), 
+alg_names <- c(rep(c("Uniform", "APT", "AugUCB","SLR","B-UCB"), 
                    each = 10071), rep("EVT", 10061))
-index <- c(rep(10:10080, times = 4), 20:10080)
-alg_res <- log(c(amo3_comp_UNIFORM, amo3_comp_APT, amo3_comp_AugUCB, amo3_comp_LR, amo3_comp_EVT))
+index <- c(rep(10:10080, times = 5), 20:10080)
+alg_res <- log(c(amo3_comp_UNIFORM, amo3_comp_APT, amo3_comp_AugUCB, amo3_comp_LR, amo3_comp_BUCB, amo3_comp_EVT))
 loc3_comp_res <- data.frame(index = index, names = alg_names, 
@@
 
-knitr::kable(rbind(Training, Test, TrainingMinusTau)[,order(Training)], digits = 3, col.names = names(data_amo4_mean_firsthalf),
+knitr::kable(rbind(Training, Test, TrainingMinusTau)[,order(Training)], digits = 3, col.names = names(data_amo4_mean_firsthalf)[order(Training)],
              caption = "Count rates for ten products for both training and test sample.")
@@
 
-alg_names <- c(rep(c("Uniform", "APT", "AugUCB","LR", "B-UCB"), 
+alg_names <- c(rep(c("Uniform", "APT", "AugUCB","SLR", "B-UCB"), 
                    each = 10071), rep("EVT", 10061))
@@
 
-alg_names <- c(rep(c("Uniform", "APT", "AugUCB", "LR", "B-UCB"), 
+alg_names <- c(rep(c("Uniform", "APT", "AugUCB", "SLR", "B-UCB"), 
                    each = 10071), rep("EVT", 10061))
@@
 ```
+
+We can try to understand why some strategies fail, while showing significant improvements on synthetic data.
+Given that we run 5000 iterations of the experiment, we can assess in how many of these iterations a given arm was pulled at a given round.
+Comparing these sampling shares across algorithms may give us hints to as to why algorithms perform a certain way.
+Given the setup with 5000 iterations and 10 arms in the current experiment, we would expect for the uniform strategy on average 500 pulls for each arm in every round.
+Given this benchmark, we can now look at how the other strategies split their budget.
+In the figures below, we have plotted not the absolute pulls per round, but have applied a 10-round moving average to remove some of the fluctuation in the plotted lines.
+
+We observe that the patterns across algorithms are quite similar, while the patterns are very different across data sets.
+Given that arm $V149$ is clearly the most difficult arm to classify due to its closeness to the threshold $\tau$, all algorithms focus a major share of their budget on this arm.
+The speed at which they start to do so, however, differs.
+Perhaps surprisingly, the best performing Bayes-UCB algorithm increases its focus on arm $V149$ the slowest, while in many iterations spending budget on exploring other arms.
+Surprisingly because Bayes-UCB is designed for the cumulative regret problem.
+Thus one would expect it to explore *less* than other algorithms.
+But its performance does not seem to be easily explained by the lessened focus on the most difficult arm; else we would expect the APT algorithm to perform second best.
+However, both SLR and EVT perform better than APT while converging more quickly to a higher share of samples allocated to the most difficult arm.
+
+One striking feature of the EVT algorithm seems to be the overall iterations and budget allocated to arm $V32$, which, as we have seen, has a sample mean of zero.
+Something that might be hidden by this aggregated view of all 5000 iterations are a share of iterations in which the EVT completely fails by exploring wrong arms for long periods.
+This effect might even be more drastic for the APT algorithm.
+Even though it seems as if its behavior is very similar to SLR and EVT, the overall performance is not better than the performance of uniform sampling.
+Taking this reasoning into account, one can hypothesize that the Bayes-UCB algorithm finds the most difficult arm uniformly across most iterations as the rounds increase, while other algorithms either find the most difficult arm right away or never and thus have many iterations that end with a misclassification.
+
+For the real data, the difference between Bayes-UCB and the other algorithms is just as apparent.
+As is the effect of the time varying means of the arms on the rate at which they are sampled.
+APT, SLR, and EVT all focus quickly in many iterations on the still most difficult arm $V149$.
+However, in the case of the real data this behavior is not rewarded in the end, as this leads to biased samples and thus wrong estimation of the overall sample mean against which the algorithms are evaluated.
+We see in the curves of arms $V32$ and arm $V154$ that the EVT algorithm is less impacted by daily seasonalities, while APT clearly is.
+
+```{r ShareOfPullsAtEachIteration, echo = FALSE, include = FALSE}
+load(file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/amo4_arm_seq_ma.Rda")
+
+rbind(amo4_LR_ma, amo4sim_LR_ma, amo4_AugUCB_ma, amo4sim_AugUCB_ma) %>%
+  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
+  geom_line(size = 0.3) +
+  facet_grid(source~algorithm) +
+  labs(x = "Index", y = "10 Rounds Moving Average",
+       title = "Average Number of Pulls Allocated to Each Arm per Round")
+```
+
+```{r, echo = FALSE}
+load(file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/amo4_arm_seq_ma.Rda")
+rbind(amo4sim_APT_ma, amo4_APT_ma, amo4_LR_ma, amo4sim_LR_ma, amo4_EVT_ma, amo4sim_EVT_ma, amo4_BUCB_ma, amo4sim_BUCB_ma) %>%
+  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
+  geom_line(size = 0.3) +
+  facet_grid(source~algorithm) +
+  labs(x = "Index", y = "10 Rounds Moving Average",
+       title = "Share of Iterations Pulling an Arm at a Given Round") +
+  theme(legend.position = "bottom") +
+  scale_color_discrete(name = "Arms")
+```

### 2017-08-17 Thesis/Draft.tex
add description of experiments

@@
 
+\subsubsection{Discussion}\label{discussion-1}
+
+At the beginning of this thesis, we set out to find an algorithm that
+improves upon the Anytime Parameter Free algorithm introduced in
+Locatelli et al. (2016) for the thresholding bandit problem in two
+directions. First, we wanted to make the algorithm perform better in
+problems that are not well approximated as sub-Gaussian; that is, in
+particular a problem with Bernoulli arms with small means and low
+threshold. Unsurprisingly, this meant that we need to find a solution
+that takes more into account than just the sample mean. With the Simple
+Likelihood Ratio strategy, we propose an algorithm that fulfills that
+goal at the cost of being distribution specific.
+
+The Simple Likelihood Ratio strategy requires the knowledge of the class
+of distribution upfront, just as other algorithms require parameters.
+While this is likely to be a negligiable problem in the case of
+\(\{0,1\}\) observations which can be modeled reasonably by Bernoulli
+distributions if we are only interested in estimating the mean, it can
+be more difficult to know the true class of distribution upfront when
+the random variables can take values in \(\mathbb{R}\). We have shown
+however, that the SLR strategy can be adapted to all univariate
+distributions in the exponential family of distributions. The algorithm
+even offers a natural adaptation to the problem of normal distributions
+with unknown mean and unknown variance.
+
+Furthermore, the Simple Likelihood Ratio strategy reduces to the Anytime
+Parameter Free strategy in the case where arms are normally distributed
+with equal variance that is known upfront. In that case we have as index
+(compare example 3 above):
+
+\[
+B_i^{SLR}(t) = T_i(t)\frac{(\hat{\mu}_i(t) - \tau)^2}{2\sigma^2}.
+\] In order to decide at time \(t\) which arm to draw next, we
+necessarily compare the indices of arm \(i\) and arm \(j\). Assume
+w.l.o.g. that \(B_i^{SLR}(t) < B_j^{SLR}(t)\). Then:
+
+\[
+B_i^{SLR}(t) < B_j^{SLR}(t) \Leftrightarrow 
+T_i(t)\frac{(\hat{\mu}_i(t) - \tau)^2}{2\sigma^2} < T_j(t)\frac{(\hat{\mu}_j(t) - \tau)^2}{2\sigma^2} 
+\Leftrightarrow 
+\sqrt{T_i(t)}\sqrt{(\hat{\mu}_i(t) - \tau)^2} < \sqrt{T_j(t)}\sqrt{(\hat{\mu}_j(t) - \tau)^2}
+\Leftrightarrow 
+B_i^{APT}(t) < B_j^{APT}(t)
+\]
+
 \section{Experiments}\label{experiments}
+
+\subsection{Synthetic Data}\label{synthetic-data}
+
+In order to evaluate the empirical performance of the proposed
+algorithms, we run the algorithm on synthetic data as is usual. We
+compare its performance on this data not only against the APT algorithm,
+but also against the variance-based algorithms. Thus we also compare the
+variance-based algorithms for the first time directly against each other
+instead of just relative to the APT algorithm.
+
+Each of the experiments is repeated for 5000 iterations. Depending on
+the experiment, the observations are generated randomly by some
+distribution of the exponential family of distributions. As we were
+originally concerned with improving upon APT with respect to
+non-sub-Gaussian distributions, the first experiments focus on Bernoulli
+distributions, and especially those with small means. We then go on to
+show with experiments on Gaussian, Exponential, and Poisson data that
+the SLR algorithm is able to improve upon APT given that we know the
+true kind of distribution.
+
+\subsubsection{\texorpdfstring{Experiment 1: Bernoulli with
+\(\tau = 0.5\)}{Experiment 1: Bernoulli with \textbackslash{}tau = 0.5}}\label{experiment-1-bernoulli-with-tau-0.5}
+
+The first experiment is equal to experiment 3 in Locatelli et al.
+(2016). We compare ten Bernoulli arms that move away from the threshold
+at \(\tau = 0.5\) geometrically with \(\mu_{1:4} = 0.4-0.2^{1:4}\),
+\(\mu_5 = 0.45\), \(\mu_6 = 0.55\), and
+\(\mu_{7:10} = 0.6 + 0.2^{5-1:4}\). We run the standard APT algorithm
+with \(\epsilon = 0.1\), as well as SLR with \(\epsilon = 0.1\). We
+compare those additionally to Augmented-UCB with the standard parameter
+choice of \(\rho = 1/3\) as used by its authors in Mukherjee et al.
+(2017). We run the parameter-free version of the Empirical Variance
+Guided algorithm without any feedback delay, thus making it directly
+comparable to the other algorithms. The Bayes-UCB algorithm takes as
+prior a Beta distribution with parameters \(\alpha_0 = \tau\) and
+\(\beta_0 = 1 - \tau\), thus leading to a mean of the prior distribution
+at \(\tau\) while keeping the prior as weak as possible. Lastly, we run
+the uniform sampling strategy as the naive benchmark.
+
+\begin{longtable}[]{@{}rrrrrrrrrr@{}}
+\caption{Mean of arms in simulation 1.}\tabularnewline
+\toprule
+V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
+\midrule
+\endhead
+0.2 & 0.36 & 0.392 & 0.398 & 0.45 & 0.55 & 0.602 & 0.608 & 0.64 &
+0.8\tabularnewline
+\bottomrule
+\end{longtable}
+
+This first experiment gives an experiment where all algorithms should
+perform well. The problem is not very difficult, and due to the
+threshold at \(\tau = 0.5\), the Bernoulli distribution can be perfectly
+approximated by a Gaussian. This thus is the perfect environment for the
+APT algorithm.
+
+As the next figure shows, essentially all methods converge rapidly to an
+error rate of zero. Except for the uniform method that clearly lacks
+behind. We also observe that the variance based algorithms (Augmented
+UCB and EVT) lag behind at first. Augmented UCB is able to adjust its
+sampling scheme after 1000 iterations and rapdily improves to the level
+of APT. EVT takes about 250 samples more to start a quick descend to the
+performance of the other algorithms. All of this, however, happens below
+an error rate of 0.01. While the SLR algorithm improves upon APT, the
+improvement is a slight one, and not very large in terms of budget
+difference. This underlines that the scenario at hand is the ideal one
+for the APT algorithm.
+
+\includegraphics{Draft_files/figure-latex/simulation1_results-1.pdf}
+
+\subsubsection{\texorpdfstring{Experiment 2: Bernoulli with
+\(\tau = 0.05\)}{Experiment 2: Bernoulli with \textbackslash{}tau = 0.05}}\label{experiment-2-bernoulli-with-tau-0.05}
+
+In the second experiment, we compare the same algorithms as in the first
+experiment. Again, we classify 10 arms, but this time against a
+threshold of \(\tau = 0.05\) and without an epsilon interval,
+\(\epsilon = 0\). Consequently, we choose the distributions for the arms
+to be much smaller too, and arrange them symmetrically around the
+threshold. While the distributions are bounded and thus still
+sub-Gaussian, the Normal approximation should be poor in comparison to
+the previous case. We expect an improvement for the SLR algorithm
+compared to APT as it takes the Bernoulli characteristics into account.
+For example, even though the arms are symmetrically distributed around
+the threshold in terms of absolute distance, they are not symmetrically
+around the threshold in terms of their Kullback-Leibler divergence given
+the threshold is unequal 0.5. Thus we expect the SLR algorithm to not
+pull them equally. Furthermore, we expect an improvement for the
+variance-based algorithms, as the variances are now smaller than in
+experiment 1, which should at least benefit the EVT algorithm given its
+theoretical analysis.
+
+The figure below shows the performance of all algorithms. We see that
+the problem appears to be significantly more difficult in general. The
+variance based algorithms perform maybe surprisingly bad; EVT even worse
+than uniform sampling nearly until the horizon, while Augmented UCB
+takes a long time to adjust away from uniform sampling. Both algorithms
+perform worse than APT after 7000 rounds. One potential reason for this
+might be the fact that the index used by the EVT algorithm reduces to
+\(B_i^{EVT}(t) = \sqrt{T_i(t)} \cdot \sqrt{|\hat{\mu}_i(t) - \tau|}\) if
+\(\hat{\sigma}_i^2(t) = 0\), which, given Bernoulli arms with small
+means, could be the case for long runs of the algorithm. In contrast,
+the index of the APT algorithm is
+\(B_i^{APT}(t) = \sqrt{T_i(t)} \cdot |\hat{\mu}_i(t) - \tau|\).
+
+One interesting observation, that we will observe in all experiments
+with synthetic Bernoulli arms, is the superior performance of the
+Bayes-UCB algorithm adapted from Kaufmann and Kalyanakrishnan (2013)
+which was originally designed for cumulative regret problems.
+Nonetheless, the algorithm will again and again proof to be the best
+performing.
+
+While the Bayes-UCB performance is impressive, we observe that also the
+Simple Likelihood Ratio strategy improves considerably upon the
+alternative strategies. SLR reaches the average empirical error of 0.1
+within the budget, and the improvement is exponential within the entire
+budget; in contrast to APT which appears to improve linearly in the
+observations. At the end of the budget, the difference in the empirical
+error is nearly 10\% between the two strategies.
+
+In order to assess how the SLR strategy improves upon the APT algorithm,
+we can use the fact that we have run the experiment for 5000 iterations.
+We thus can look at how often each arm was pulled by a strategy at any
+given round. Across the 5000 iterations, the algorithm should pull at
+any given iteration the arm most often that it thinks is the most
+difficult to classify. In the figure below, we plot the resulting curves
+where the value at an iteration is the 10-round moving average to remove
+some unimportant variation.
+
+We see that both APT and SLR correctly single out the two arms that are
+much closer to the threshold than the remaining arms and allocate most
+of the budget to them. However, while SLR keeps the two arms constant at
+two different levels (about 1900 for arm 5 and about 2500 for arm 6),
+APT at first pulls arm 5 much more than arm 6. Then, the budget
+allocated to the two arms appears to converge to about 2000. Given that
+the two arms are symmetric around the threshold, it makes sense that APT
+would allocate the same exploration effort to both of them. And given
+that the variation of arm 5 away from the threshold is limited from
+below by zero, it is much easier for arm 6 to have an empirical mean
+larger than it's true mean, and thus to have a larger index than arm 5.
+Consequently, APT would prefer to sample arm 5. This, however, is wrong
+in terms of Kullback-Leibler divergence. Measured by the divergence, arm
+6 is closer to the threshold than arm 5, thus harder to classify, and
+consequently preferred by the SLR algorithm. Furthermore, the SLR
+algorithm appears to quickly find the correct share that it has to
+allocate to the two arms. In contrast to APT which continues to adjust
+the shares across the entire budget.
+
+Additionally, we can observe that the SLR strategy starts to drop arms
+much quicker than APT, and it drops arm 1 to 3 first, which again
+underlines the effect of the asymmetric Kullback-Leibler divergence. If
+we consider arm 3 and arm 8, we have \(d(0.01||0.05) \approx 0.025\)
+while \(d(0.09||0.05) = 0.014\). The divergence is much smaller for arm
+8. The asymmetry is even more dramatic for arm 1 and arm 10 with
+\(d(0.001||0.05) \approx 0.046\) and \(d(0.099||0.05) \approx 0.020\);
+in terms of the divergence, the distance between arm 1 and the threshold
+is twice as far as between arm 10 and the threshold. APT considers them
+to be equally distant from the threshold.
+
+\begin{longtable}[]{@{}rrrrrrrrrr@{}}
+\caption{Mean of arms in simulation 2 classified against threshold of
+0.05.}\tabularnewline
+\toprule
+V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
+\midrule
+\endhead
+0.001 & 0.005 & 0.01 & 0.015 & 0.04 & 0.06 & 0.085 & 0.09 & 0.095 &
+0.099\tabularnewline
+\bottomrule
+\end{longtable}
+
+\includegraphics{Draft_files/figure-latex/simulation2_results-1.pdf}
+
+\includegraphics{Draft_files/figure-latex/unnamed-chunk-4-1.pdf}
+
+\subsubsection{\texorpdfstring{Experiment 3: Bernoulli with
+\(\tau = 0.01\)}{Experiment 3: Bernoulli with \textbackslash{}tau = 0.01}}\label{experiment-3-bernoulli-with-tau-0.01}
+
+In the third experiment, we lower the threshold further to
+\(\tau = 0.1\) and arrange the arms on a \(\log_{10}\) scale around it.
+Again, there is no epsilon interval. We add one additional arm, thus now
+classifying eleven arms. We run the same arms as previously. Notice that
+the experiment horizon is now \(10000\) rounds instead of \(7000\)
+rounds as in the previous experiment. We test the same algorithms used
+in the previous two experiments.
+
+If we look at the performance after 7000 rounds, we see that the problem
+appears to be slightly more difficult compared to the previous one. We
+see that up until this point the variance-based strategies cannot
+improve upon APT. Also, SLR has not yet crossed the 10\% empirical
+error. However, we observe that in the following rounds EVT decreases at
+an exponential rate and thus crosses the error of APT and continues to
+improve upon it. At the end of the budget, the improvement of SLR
+compared to the other algorithms is again very large, and likely to
+increase. However, Bayes-UCB is again the best performing algorithm and
+is improving at a faster rate than SLR. As in the previous experiment,
+Bayes-UCB and SLR show significant improvements on this Bernoulli
+problem with very small means and threshold compared to APT in
+particular.
+
+\begin{longtable}[]{@{}rrrrrrrrrrr@{}}
+\caption{Mean of arms in simulation 2 compared to a threshold of
+0.01.}\tabularnewline
+\toprule
+V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10 & V11\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10 & V11\tabularnewline
+\midrule
+\endhead
+1e-04 & 3e-04 & 6e-04 & 0.001 & 0.0018 & 0.0032 & 0.0056 & 0.0141 &
+0.0178 & 0.0316 & 0.1\tabularnewline
+\bottomrule
+\end{longtable}
+
+\includegraphics{Draft_files/figure-latex/simulation3_results-1.pdf}
+
+\subsection{\texorpdfstring{Experiment 4: Exponential Distribution with
+\(\tau = 1\)}{Experiment 4: Exponential Distribution with \textbackslash{}tau = 1}}\label{experiment-4-exponential-distribution-with-tau-1}
+
+\includegraphics{Draft_files/figure-latex/simulation4_results-1.pdf}
+
+\subsection{\texorpdfstring{Experiment 5: Poisson Distribution with
+\(\tau = 1\)}{Experiment 5: Poisson Distribution with \textbackslash{}tau = 1}}\label{experiment-5-poisson-distribution-with-tau-1}
+
+\includegraphics{Draft_files/figure-latex/simulation5_results-1.pdf}
 
@@
 \toprule
-& V64 & V1 & V159 & V119 & V70 & V114 & V189 & V139 & V118 &
-V148\tabularnewline
+& V1 & V159 & V64 & V139 & V189 & V70 & V114 & V148 & V118 &
+V119\tabularnewline
 \midrule
@@
 
-\includegraphics{Draft_files/figure-latex/unnamed-chunk-4-1.pdf}
+\includegraphics{Draft_files/figure-latex/unnamed-chunk-5-1.pdf}
 
@@
 
-\includegraphics{Draft_files/figure-latex/unnamed-chunk-5-1.pdf}
+\includegraphics{Draft_files/figure-latex/unnamed-chunk-6-1.pdf}
 
@@
 \toprule
-& V129 & V32 & V76 & V103 & V149 & V104 & V110 & V150 & V112 &
+& V112 & V129 & V104 & V76 & V103 & V110 & V150 & V149 & V32 &
 V154\tabularnewline
@@
 
-\includegraphics{Draft_files/figure-latex/unnamed-chunk-6-1.pdf}
-
 \includegraphics{Draft_files/figure-latex/unnamed-chunk-7-1.pdf}
 
+\includegraphics{Draft_files/figure-latex/unnamed-chunk-8-1.pdf}
+
+We can try to understand why some strategies fail, while showing
+significant improvements on synthetic data. Given that we run 5000
+iterations of the experiment, we can assess in how many of these
+iterations a given arm was pulled at a given round. Comparing these
+sampling shares across algorithms may give us hints to as to why
+algorithms perform a certain way. Given the setup with 5000 iterations
+and 10 arms in the current experiment, we would expect for the uniform
+strategy on average 500 pulls for each arm in every round. Given this
+benchmark, we can now look at how the other strategies split their
+budget. In the figures below, we have plotted not the absolute pulls per
+round, but have applied a 10-round moving average to remove some of the
+fluctuation in the plotted lines.
+
+We observe that the patterns across algorithms are quite similar, while
+the patterns are very different across data sets. Given that arm
+\(V149\) is clearly the most difficult arm to classify due to its
+closeness to the threshold \(\tau\), all algorithms focus a major share
+of their budget on this arm. The speed at which they start to do so,
+however, differs. Perhaps surprisingly, the best performing Bayes-UCB
+algorithm increases its focus on arm \(V149\) the slowest, while in many
+iterations spending budget on exploring other arms. Surprisingly because
+Bayes-UCB is designed for the cumulative regret problem. Thus one would
+expect it to explore \emph{less} than other algorithms. But its
+performance does not seem to be easily explained by the lessened focus
+on the most difficult arm; else we would expect the APT algorithm to
+perform second best. However, both SLR and EVT perform better than APT
+while converging more quickly to a higher share of samples allocated to
+the most difficult arm.
+
+One striking feature of the EVT algorithm seems to be the overall
+iterations and budget allocated to arm \(V32\), which, as we have seen,
+has a sample mean of zero. Something that might be hidden by this
+aggregated view of all 5000 iterations are a share of iterations in
+which the EVT completely fails by exploring wrong arms for long periods.
+This effect might even be more drastic for the APT algorithm. Even
+though it seems as if its behavior is very similar to SLR and EVT, the
+overall performance is not better than the performance of uniform
+sampling. Taking this reasoning into account, one can hypothesize that
+the Bayes-UCB algorithm finds the most difficult arm uniformly across
+most iterations as the rounds increase, while other algorithms either
+find the most difficult arm right away or never and thus have many
+iterations that end with a misclassification.
+
+For the real data, the difference between Bayes-UCB and the other
+algorithms is just as apparent. As is the effect of the time varying
+means of the arms on the rate at which they are sampled. APT, SLR, and
+EVT all focus quickly in many iterations on the still most difficult arm
+\(V149\). However, in the case of the real data this behavior is not
+rewarded in the end, as this leads to biased samples and thus wrong
+estimation of the overall sample mean against which the algorithms are
+evaluated. We see in the curves of arms \(V32\) and arm \(V154\) that
+the EVT algorithm is less impacted by daily seasonalities, while APT
+clearly is.
+
+\includegraphics{Draft_files/figure-latex/unnamed-chunk-9-1.pdf}
+
 \end{document}

### 2017-08-17 Thesis/experiment_postprocessing/loc6nt_postprocessing.R

@@ -1,0 +1,97 @@
+# Post processing of data for arm sequence visualization.
+# This is for Simulation 2 on synthetic data as used in thesis.
+
+##########################################################
+
+# load the algorithm results from Experiment 2
+
+library(plyr)
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
+
+load(paste0(current_path, "loc6nt_BUCB_horizon_7000.Rda"))
+loc6nt_BUCB_arm_seq <- data.frame(t(laply(loc6nt_BUCB_horizon_7000, 
+                                        function(x) x$arm_sequence)))
+save(loc6nt_BUCB_arm_seq, file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/loc6nt_BUCB_arm_seq.Rda")
+rm(loc6nt_BUCB_7000, loc6nt_BUCB_arm_seq)
+gc()
+
+load(paste0(current_path, "loc6nt_APT_7000.Rda"))
+loc6nt_APT_arm_seq <- data.frame(t(laply(loc6nt_APT_7000, 
+                                       function(x) x$arm_sequence)))
+save(loc6nt_APT_arm_seq, file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/loc6nt_APT_arm_seq.Rda")
+rm(loc6nt_APT_7000, loc6nt_APT_arm_seq)
+gc()
+
+load(paste0(current_path, "loc6nt_LR_7000.Rda"))
+loc6nt_LR_arm_seq <- data.frame(t(laply(loc6nt_LR_7000, 
+                                      function(x) x$arm_sequence)))
+save(loc6nt_LR_arm_seq, file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/loc6nt_LR_arm_seq.Rda")
+rm(loc6nt_LR_7000, loc6nt_LR_arm_seq)
+gc()
+
+
[…]

### 2017-08-17 Thesis/experiment_postprocessing/real_exp_1week_2_postprocessing.R

@@ -11,4 +11,392 @@ source(paste0(current_path, "run_from_data.R"))
 source(paste0(current_path, "run_parallelized_from_data.R"))
 current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/"
 
+load(paste0(current_path, "amo4_BUCB.Rda"))
+amo4_BUCB_arm_seq <- data.frame(t(laply(amo4_BUCB, 
+                                       function(x) x$arm_sequence)))
+save(amo4_BUCB_arm_seq, file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/amo4_BUCB_arm_seq.Rda")
+rm(amo4_BUCB, amo4_BUCB_arm_seq)
+gc()
 
+load(paste0(current_path, "amo4_APT.Rda"))
+amo4_APT_arm_seq <- data.frame(t(laply(amo4_APT, 
+                                       function(x) x$arm_sequence)))
+save(amo4_APT_arm_seq, file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/amo4_APT_arm_seq.Rda")
+rm(amo4_APT, amo4_APT_arm_seq)
+gc()
+
+load(paste0(current_path, "amo4_AugUCB.Rda"))
+amo4_AugUCB_arm_seq <- data.frame(t(laply(amo4_AugUCB, 
+                                       function(x) x$arm_sequence)))
+save(amo4_AugUCB_arm_seq, file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/amo4_AugUCB_arm_seq.Rda")
+rm(amo4_AugUCB, amo4_AugUCB_arm_seq)
+gc()
+
+load(paste0(current_path, "amo4_LR.Rda"))
+amo4_LR_arm_seq <- data.frame(t(laply(amo4_LR, 
+                                          function(x) x$arm_sequence)))
+save(amo4_LR_arm_seq, file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/amo4_LR_arm_seq.Rda")
+rm(amo4_LR, amo4_LR_arm_seq)
+gc()
+
+load(paste0(current_path, "amo4_EVT.Rda"))
+amo4_EVT_arm_seq <- data.frame(t(laply(amo4_EVT, 
[…]

### 2017-08-17 real_experiments/real_exp_1week_2.R

@@ -51,6 +51,7 @@ gc()
 
 load(paste0(current_path, "data_amo4_mean_firsthalf.Rda"))
 load(paste0(current_path, "data_amo4_mean_secondhalf.Rda"))
+load(paste0(current_path, "data_amo4_own_means.Rda"))
 load(paste0(current_path, "data_amo4.Rda"))
 tau_amo4 <- 5/60
 epsilon_amo4 <- 0
@@ -70,9 +71,13 @@ amo4_comp_LR <- compare_to_ground_truth(data_amo4_mean_firsthalf,
 amo4_compholdout_LR <- compare_to_ground_truth(data_amo4_mean_secondhalf, 
                                                amo4_LR, 
                                                tau_amo4, epsilon_amo4)$mean
+amo4_compown_LR <- compare_to_cv_data(data_amo4_own_means, amo4_LR, 
+                                        tau_amo4, epsilon_amo4)$mean
 save(amo4_comp_LR, file = paste0(current_path, "amo4_comp_LR.Rda"))
 save(amo4_compholdout_LR, file = paste0(current_path, 
                                         "amo4_compholdout_LR.Rda"))
+save(amo4_compown_LR, file = paste0(current_path, 
+                                        "amo4_compown_LR.Rda"))
 rm(amo4_LR, amo4_comp_LR)
 gc()
 
@@ -226,11 +231,12 @@ load(paste0(current_path, "amo4_comp_AugUCB.Rda"))
 load(paste0(current_path, "amo4_comp_EVT.Rda"))
 load(paste0(current_path, "amo4_comp_BUCB.Rda"))
 
-plot(c(0,10080), c(0, -5), type = "n")
+plot(c(0,10080), c(0, -1.5), type = "n")
 lines(log(amo4_comp_UNIFORM), col = "black")
 lines(log(amo4_comp_APT), col = "blue")
 lines(log(amo4_comp_AugUCB), col = "green")
 lines(log(amo4_comp_EVT), col = "darkgreen")
 lines(log(amo4_comp_LR), col = "red")
+lines(log(amo4_compown_LR), col = "blue")
 lines(log(amo4_comp_BUCB), col = "violet")
 abline(h = log(0.1), lty = 2)

### 2017-08-17 synthetic_experiments/cal_algs_verylong_2.R

@@ -40,6 +40,7 @@ for(j in 1:5000) {
 load(paste0(current_path, "/loc2_comp_BUCB_horizon_4000.Rda"))
 load(paste0(current_path, "/loc2_comp_APT_2000.Rda"))
 load(paste0(current_path, "/loc2_comp_LR_2000.Rda"))
+load(paste0(current_path, "/loc2_comp_EVT.Rda"))
 load(paste0(current_path, "/loc2_comp_AugUCB_2000.Rda"))
 load(paste0(current_path, "/loc2_comp_KLUCB80_long.Rda"))
 load(paste0(current_path, "/loc2_comp_KLUCB15_long.Rda"))
@@ -49,14 +50,26 @@ lines(log(loc2_comp_BUCB_horizon_4000), col = "blue")
 lines(log(loc2_comp_APT_2000), col = "red")
 lines(log(loc2_comp_LR_2000), col = "black")
 lines(log(loc2_comp_AugUCB_2000), col = "grey")
-#lines(log(loc2_comp_KLUCB100), col = "green")
+lines(log(loc2_comp_EVT), col = "green")
 #lines(log(loc2_comp_KLUCB80), col = "green")
 lines(log(loc2_comp_KLUCB80_long), col = "green")
 lines(log(loc2_comp_KLUCB15_long), col = "darkgreen")
 #lines(log(loc2_comp_KLUCB60), col = "darkgreen")
 #lines(log(loc2_comp_KLUCB20), col = "darkgreen")
 
-8000/H_loc2
+########################################################################
+# Empirical Variance Guided Algorithm (Zhong et al., 2017)
+
+loc2_EVT <- para_bandit_sim_EVT(data = data_list2, 
+                                rounds = 2000, 
+                                tau = tau_loc2, 
+                                epsilon = epsilon_loc2)
+save(loc2_EVT, file = paste0(current_path, "loc2_EVT.Rda"))
+loc2_comp_EVT <- compare_to_ground_truth(mean_loc2, loc2_EVT, 
+                                         tau_loc2, epsilon_loc2)$mean
+save(loc2_comp_EVT, file = paste0(current_path, "loc2_comp_EVT.Rda"))
+rm(loc2_EVT)
+gc()
 
 ########################################################################
 

### 2017-08-17 synthetic_experiments/cal_algs_verylong_6_no_tau.R

@@ -35,6 +35,20 @@ for(j in 1:5000) {
 }
 
 ########################################################################
+# Empirical Variance Guided Algorithm (Zhong et al., 2017)
+
+loc6nt_EVT <- para_bandit_sim_EVT(data = data_list6, 
+                                  rounds = 7000, 
+                                  tau = tau_loc6nt, 
+                                  epsilon = epsilon_loc6nt)
+save(loc6nt_EVT, file = paste0(current_path, "loc6nt_EVT.Rda"))
+loc6nt_comp_EVT <- compare_to_ground_truth(mean_loc6nt, loc6nt_EVT, 
+                                           tau_loc6nt, epsilon_loc6nt)$mean
+save(loc6nt_comp_EVT, file = paste0(current_path, "loc6nt_comp_EVT.Rda"))
+rm(loc6nt_EVT)
+gc()
+
+########################################################################
 # Plot the results
 
 load(paste0(current_path, "/loc6nt_comp_BUCB_horizon_7000.Rda"))
@@ -44,7 +58,7 @@ load(paste0(current_path, "/loc6nt_comp_UNIFORM_7000.Rda"))
 load(paste0(current_path, "/loc6nt_comp_APT_7000.Rda"))
 load(paste0(current_path, "/loc6nt_comp_LR_7000.Rda"))
 
-plot(c(0,7000), c(0, -4), type = "n")
+plot(c(0,7000), c(0, -5), type = "n")
 lines(log(loc6nt_comp_BUCB_horizon_7000), col = "blue")
 #lines(log(loc6nt_comp_BUCB_horizon), col = "lightblue")
 #lines(log(loc6nt_comp_APT), col = "pink")
@@ -57,7 +71,21 @@ lines(log(loc6nt_comp_AugUCB_7000), col = "grey")
 #lines(log(loc6nt_comp_KLUCB7), col = "green")
 #lines(log(loc6nt_comp_KLUCB30), col = "green")
 #lines(log(loc6nt_comp_KLUCB370), col = "darkgreen")
-lines(log(loc6nt_comp_KLUCB370_5000), col = "darkgreen")
+#lines(log(loc6nt_comp_KLUCB370_5000), col = "darkgreen")
+
+########################################################################
+# Empirical Variance Guided Algorithm (Zhong et al., 2017)
+
+loc6nt_EVT <- para_bandit_sim_EVT(data = data_list6, 
+                                rounds = 7000, 
+                                tau = tau_loc6nt, 
[…]

### 2017-08-17 synthetic_experiments/cal_algs_verylong_7_no_tau.R

@@ -36,6 +36,21 @@ for(j in 1:5000) {
   data_list7_10000[[j]] <- curr_data
 }
 gc()
+
+########################################################################
+# Empirical Variance Guided Algorithm (Zhong et al., 2017)
+
+loc7nt_EVT <- para_bandit_sim_EVT(data = data_list7_10000, 
+                                  rounds = 10000, 
+                                  tau = tau_loc7nt, 
+                                  epsilon = epsilon_loc7nt)
+save(loc7nt_EVT, file = paste0(current_path, "loc7nt_EVT.Rda"))
+loc7nt_comp_EVT <- compare_to_ground_truth(mean_loc7nt, loc7nt_EVT, 
+                                           tau_loc7nt, epsilon_loc7nt)$mean
+save(loc7nt_comp_EVT, file = paste0(current_path, "loc7nt_comp_EVT.Rda"))
+rm(loc7nt_EVT)
+gc()
+
 ########################################################################
 
 system.time(loc7nt_KLUCB90_long <- para_bandit_sim_KLUCB(data = data_list7_10000, 
@@ -133,6 +148,7 @@ load(file = paste0(current_path, "loc7nt_comp_APT_10000.Rda"))
 load(file = paste0(current_path, "loc7nt_comp_LR_10000.Rda"))
 load(file = paste0(current_path, "loc7nt_comp_BUCB_horizon_10000.Rda"))
 load(file = paste0(current_path, "loc7nt_comp_AugUCB_10000.Rda"))
+load(file = paste0(current_path, "loc7nt_comp_EVT.Rda"))
 
 plot(c(0,10000), c(0, -5), type = "n")
 lines(log(loc7nt_comp_BUCB_horizon_10000), col = "green")
@@ -140,3 +156,4 @@ lines(log(loc7nt_comp_UNIFORM_10000), col = "darkblue")
 lines(log(loc7nt_comp_APT_10000), col = "red")
 lines(log(loc7nt_comp_LR_10000), col = "darkred")
 lines(log(loc7nt_comp_AugUCB_10000), col = "darkgreen")
+lines(log(loc7nt_comp_EVT), col = "blue")

### 2017-08-17 synthetic_experiments/poisson/exp_pois_2.R

@@ -32,6 +32,10 @@ gc()
 
 ########################################################################
 
+load(paste0(current_path, "pois2_comp_LR.Rda"))
+load(paste0(current_path, "pois2_comp_APT.Rda"))
+load(paste0(current_path, "pois2_comp_EVT.Rda"))
+
 plot(c(0,10000), c(0, -8), type = "n")
 abline(h=log(0.01), lty = 2)
 lines(log(pois2_comp_APT), col = "black")

### 2017-08-25 Thesis/APT_UB_revised/APT_UB_Proof_Old.Rmd
Add Introduction

--- 2017-08-12 Thesis/Draft.Rmd
@@
----
-title: "Draft"
-author: "Tim Radtke"
-date: "5/28/2017"
-header-includes:
-   #- \documentclass[a4paper,twoside,english]{article}
-   - \usepackage[retainorgcmds]{IEEEtrantools}
-   - \usepackage{bm}
-   - \usepackage{amsmath}
-   - \usepackage{bbm}
-   - \newtheorem{theorem}{Theorem}
-   - \newtheorem{lemma}{Lemma}
-   - \newcommand{\KL}{\,\text{KL}}
-   - \newcommand{\der}{\,\text{d}}
-   #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
-   #- \usepackage{fontspec}
-   #-   \setmainfont{Arial}
-keep_tex: TRUE
-output:
-  pdf_document:
-    number_sections: true
-    keep_tex: true
-    toc: true
-    toc_depth: 3
-    #latex_engine: xelatex
-fontsize: 12pt
-urlcolor: blue
----
-
-# Thresholding Bandit Problem
-
-The *Thresholding Bandit Problem* described in Locatelli et al.
-(2016) can be considered a variant of a variant.
-It can be framed into the wider literature of *Pure Exploration* multi-armed bandit problems.
-In particular, it shares characteristics with the *Top-$m$* problem.
-This problem is concerned with finding the $m$ best arms as described by the means of their corresponding distributions.
-This in turn is similar to the *combinatorial bandit* problem, which also aims at finding the $m$ best arms.
-However, it is able to pull several arms at once: Think of an online shop that shows five recommended products on a product detail page.
-These five recommended products might each be represented by an arm, and we look for the products with the largest mean conversion rate.
-The thresholding bandit problem we discuss here, however, is concerned with pulling a single arm at a time.
-And so a more appropriate situation is that of a website presenting a banner.
-Again, think of an online shop trying to promote a certain category.
-The content team came up with a number of different designs for the banner, and it's not clear how many click-throughs they will gather.
-
-The idea now is that we would like to classify the banners into two distinct groups: A group with mean conversion rates $\mu_i$ below threshold $\tau$, and a group with mean conversion rates $\mu_i$ above threshold $\tau$.
-This might be the optimization problem when we are concerned with not falling below a certain minimum level click-through rate with the banners we're choosing.
-
-If it turns out that in general we can find relatively quickly whether arms are above or below a threshold, then this kind of test can be used to safeguard against very bad versions in a test.
-Before we move to a Top-$m$ test, we might want to run a thresholding version and then continue only with the arms classified into the group above the threshold.
-This might be justified when adjusting parts of the checkout process of an online shop, where the conversion rate or the average order value should not drop below a threshold.
-
-## Setup
-
-In any case, the problem boils down to the following.
-As standard in multi-armed bandit problems, we have $K$ arms $\mathcal{A} = \{1, \dots K\}$.
-We can pull arm $k$ at time $t$ to collect feedback in form of the random variable $X_{k,t}$ which is distributed according to the arm's distribution $\nu_k$.
-In general, we are concerned with estimating for each arm $i$ the mean $\mu_i$ of its distribution $\nu_i$.
-In contrast to most bandit problems, however, we do not directly compare arms with each other by comparing their means.
-That would for example be the case for pure exploration bandits, where it is necessary to compare the arms because one aims to find the best one relative to the others.
-In the case of the thresholding bandit, however, we compare each arm's mean $\mu_i$ individually against the threshold $\tau \in \mathbb{R}$ which is known and fixed before the experiment.
-One might compare this to a pure exploration bandit in which the mean of the best arm is known upfront.
-We will see later that this fact leads to advantages in the design of algorithms which are not as readily available in other bandit settings.
-
-In Locatelli (2016), the arms' distributions are assumed to follow an $R$-sub-Gaussian distribution.
-Under this assumption, the authors are able to proof a general lower bound as well as an algorithm with a matching upper bound.
-Both hinge upon the *complexity* of a given problem.
-Since bandit problems can differ in the number of the arms $K$ and the means of each arm, some pose easier identification problems than others.
-Indeed, in the thresholding problem, the difficulty of the problem naturally depends on how close (the means of the) distributions are to the fixed threshold.
-Intuitively, the closer a mean $\mu_i$ is to the threshold $\tau$, the more difficult it will be to distinguish the two successfully based on samples from the distribution $\nu_i$.
-For the case of the sub-Gaussian distributions, a natural measure of this distance is given by simply $\Delta_i = |\tau - \mu_i| + \epsilon$, where $\epsilon$ defines a $2\epsilon$ interval around the threshold $\tau$ in which we allow ourselves to make a mistake at no cost.
-
-If we extend this idea to the set of arms $i \in \{1,...,K\}$ of a given bandit problem, a natural measure of the overall diffulty of the problem, or the problem's complexity, might be given by $H = \sum_{i=1}^{K} \Delta_i^{-2}$.
-In particular, it shows that just adding additional arms leads to an increase in complexity (since we need to sample more of them), just as smaller $\Delta_i$ will increase the complexity as arms become harder to classify.
-(WHERE DOES THIS COMPLEXITY ORIGINALLY COME FROM?)
-
-We also see that this definition may lose relevancy as we move away from $R$-sub-Gaussian distributions.
-(ADD QUICK EXAMPLE OF WHAT CHANGES; REFER TO LATER PART AND DESCRIBE THIS AS THE MOTIVATION OF THE PAPER)
-
-Another characteristic uniquely identifying bandit problems is the regret measure that we aim to optimize.
-As explained during the introduction, multi-armed bandits traditionally optimize cumulative regret.
-The notion of regret considered in the thresholding bandit, however, is more akin to the simple regret in pure exploration bandits or the error probability in sequential hypothesis testing.
-Indeed, one can most easily describe the regret in the thresholding case as the probability of making a misclassification of any arm.
-Or, more rigorously, let us define the set of all arms with mean larger than the threshold, $\mathcal{S}_\tau = \{i \in \mathcal{A}: \mu_i \geq \tau\}$.
-Consequently, $\mathcal{S}_\tau^C = \{i \in \mathcal{A}: \mu_i < \tau\}$.
-At the end of the sampling rule/procedure (!!we have not mentioned yet the fact that we're in the fixed budget case!!), we demand that any algorithm returns the two corresponding *estimated* sets: $\hat{\mathcal{S}}_{\tau} = \{i \in \mathcal{A}: \hat{\mu}_i \geq \tau\}$, as well as $\hat{\mathcal{S}}_{\tau}^C = \{i \in \mathcal{A}: \hat{\mu}_i < \tau\}$.
-We simply demand an answer to the question which arms have means above the threshold $/tau$, and which arms lie below  $\tau$.
-Let $T$ be the overall number of samples the algorithm is allowed to pull.
-We define the loss as $\mathcal{L}(T) = \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset\}} \cdot \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset\}}$.
-That is, we compare the return set with the true set and collect a loss of 1 if any arm with a true mean outside the $2\epsilon$ interval around $\tau$ was misclassified.
-It is important to realize that arms with means inside the $2 \epsilon$ interval may be misclassified without it affecting the loss.
-These arms are considered close enough to the threshold that we do not care whether they lie above or below.
-
-ADD A GRAPHIC THAT VISUALIZES THE ESTIMATED AND THE REQUIRED RETURN SETS
-
-From there, it is natural to define the expected regret/loss as $\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \land (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset))$.
-This, of course, is the mentioned probability of making a mistake.
-
-ADD REMARK ON WHAT THIS IMPLIES WITH REGARD TO THE MEANS
-
-Lastly, it is to mention that we are considering the fixed-budget version of the thresholding bandit problem.
-We thus fix the number of samples that the algorithm will pull upfront at $T$.
-The task of the algorithm is then to find a sampling rule or strategy which distributes the budget $T$ among the $K$ arms in such a way that the expected regret, or the error probability, is minimized.
-In other terms, the algorithm aims to use the $T$ samples in a way that lets him return the two sets $\hat{\mathcal{S}}_{\tau}$ and $\hat{\mathcal{S}}_{\tau}^C$ with as much confidence as possible.
-This again shows the contrast to the fixed confidence setting in which one fixes the confidence level upfront and lets the algorithm draw as many samples as necessary to reach the required confidence.
-
-At this point, we have defined the fixed budget thresholding bandit setup for any algorithm in the case of sub-Gaussian distributions.
-We thus proceed to describe the algorithm proposed in Locatelli et al.
-(2016).
-
-## The APT Algorithm
-
-In the following we describe the *Anytime Parameter-free Thresholding* (APT) algorithm proposed in Locatelli et al.
-(2016), which is a simple yet effective algorithm and displays some very favorable characteristics when compared with alternative algorithms.
-
-From the general setup, we already know how the algorithm will end.
-After it has drawn $T$ samples, the algorithm makes its decision of which arms to include in the return sets solely on basis of the empirical means $\hat{\mu}_i(T)$ estimated based on the samples drawn until time $T$.
-Furthermore, the threshold and interval around the threshold were fixed upfront and serve as argument to the algorithm: $(\tau, \epsilon)$.
-For a given arm $i$ and a given time $t$, we let $T_i(t)$ represent the number of samples drawn from arm $i$ until time $t$ (including).
-Consequently, the empirical mean of arm $i$ at time $t$ is given by $\mu_i = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}$ where $X_{i,s}$ is the feedback sampled from distribution $\nu_i$ when the arm is pulled for the $s$-th time.
-
-To be specific, the APT algorithm initiates by pulling each arm once.
-Then, for each $t > K$, it calculates for every arm the values $T_i(t)$ and $\mu_i(t)$.
-Based on the empirical mean, the algorithm computes the estimated gap between the mean and the threshold as $\hat{\Delta}_i(t) = \hat{\Delta}_i^{\tau, \epsilon}(t) = |\mu_i(t) - \tau| + \epsilon$.
-The decision of which arm is sampled next is then based on the value $B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t)$: the algorithm pulls arm $I_{t+1} = \arg \min_{i\leq K} B_i(t+1)$ minimizing this decision quantity.
-After $T$ pulls overall, the arm returns the sets described in the general setup, $\hat{\mathcal{S}}_{\tau}$ and $\hat{\mathcal{S}}^C_{\tau}$.
-
-**Remark**: Obviously, the APT algorithm tends to pull arms more often with corresponding mean close to the threshold and interval (small $\hat{\Delta}_i(t))$.
-This makes sure that more evidence is gathered on arms which appear to be inherently difficult to classify based on the samples collected until time $T_i(t)$, as these arms stifle the confidence the most.
-That is, until we have collected enough evidence to make a confident classification even if the mean is truly close to the threshold.
-In that case, $\sqrt{T_i(t)}$ will raise $B_i(t+1)$.
-Consequently, other arms farther away from the threshold will be sampled again.
-In this way, the algorithm tries to distribute the budget $T$ over all arms so as to define a sampling rule optimizing the confidence of the final decision.
-This is Glivenko-Cantelli and the CLT making sure $B_i(t+1)$ is not degenerate.
-(?)
-
-## Discussion
-
-One of the APT algorithm's main features is its simplicity.
-The sampling rule is very straightforward, and, as highlighted in Locatelli et al.
-(2016), it does not require any knowledge about the type of sub-Gaussianity $R$, or the complexity $H$ upfront.
-This makes the algorithm immediately applicable in practice while it still enjoys its upper bound on the expected regret.
-This is in particular worth highlighting when comparing APT to algorithms used in the pure exploration bandit setting.
-There, many algorithms require knowledge about the corresponding complexity upfront.
-The problem however being, that to know the complexity, the experimenter has to know all means up to a permutation of the arms (for example, see Audibert et al., 2010).
-This, of course, is not given in practice and thus alternative algorithms try to estimate the complexity online which is not a desirable solution either as especially in the beginning plug-in estimates based on the estimated means may lead to wrong estimates of the complexity and consequently budget allocation based on mistaken beliefs (compare Garivier and Kaufmann, 2016).
-
-Furthermore, Locatelli et al. (2016) were able to present an upper bound for the APT algorithm matching the lower bound in their Theorem 1. Proofs of both bounds are given below.
-
-Where the APT algorithm shows room for improvement is when it comes to settings with distributions that are not sub-Gaussian.
-This is mentioned in Locatelli et al.
-(2016).
-In general, the problem becomes that the assumptions for the bounds no longer hold; furthermore, the statistic $B_i(t+1)$, and the term $\hat{\Delta}_i(t)$ are motivated by (sub-)Gaussian distributions.
-The more one moves away from Gaussian-like distributions, the less appropriate this term becomes, however.
-In particular, the empirical mean will be less concentrated around the true mean and more impacted by outliers which are more likely under non sub-Gaussian distributions.
-Locatelli et al.
-(2016) thus refers to Bubeck et al.
-(2013) which considers solutions for multi-armed bandits that are based on heavy-tail distributions.
-By using more robust estimators of the mean, one could equip the APT algorithm to deal with such distributions.
-
-Another step towards dealing with non sub-Gaussianity is made by Mukherjee et al.
-(2017) who use an estimate of the variance additionally to the empirical mean in their Augmented UCB solution.
-Utilizing this additional information, the algorithm seems to perform better than for example APT, going from simulation results displayed in the paper.
-However, the simulations deal exclusively with normal distributions, as the variance has to be bounded for the upper bound of the Augmented UCB to hold.
-We will continue to discuss the Augmented UCB solution in chapter 3.
-
-Yet another idea, again mentioned in Locatelli et al.
-(2016) is to show bounds based on the Kullback-Leibler divergence of the specific distribution directly.
-While the approximation through the Gaussian Kullback-Leibler divergence in the lower bound proof is convenient and leads to the simple APT algorithm, it might not stay appropriate for distributions whose Kullback-Leibler divergence tends to differ from the Gaussian.
-This, for example, is the case for Bernoulli distributions at very small parameters $\mu$.
-By looking at the graphical examples below it becomes obvious that the Kullback-Leibler divergence of Bernoullis starts to lose any similarity to the plain quadratic approximation.
-The second graph then shows that the actual Kullback-Leibler divergence of Bernoullis also has lost any symmetry over this range of parameter values.
-Given that Bernoulli distributions with very small parameter values arise naturally in many applications in website optimization and advertising click-through modeling, there is a need to tackle this problem.
-
-Refer also to page 6 in Kaufmann et al. (2016): "This information-theoretic lower bound permits to interpret the quantity $H(\nu)$ defined in (2) as a subgaussian approximation".
-
-And so a potential approach can be to use the Kullback-Leibler divergence as measure similar to the methods proposed in Kaufmann et al.
-(2015).
-They proposed Kullback-Leibler based approaches for the pure exploration bandit setting, which we will describe in chapter 2.
-Then, in chapter 3, we will come back to the problem of using the Kullback-Leibler divergence in the thresholding bandit setting.
-
-```{r, echo = FALSE}
-KL_ber <- function(p,q) p*log(p/q) + (1-p)*log((1-p)/(1-q))
-par(mfcol = c(1,2))
-
-plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1), type = "n", asp = 1,
-     xlab = "p_1", ylab = "KL(Ber(p_1),Ber(p_2))", main = "KL of Bernoullis")
-for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
-  lines(seq(0.00001,0.3, by = 0.000005),
-       KL_ber(seq(0.00001,0.3, by = 0.000005),i))
-}
-
-plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1), type = "n", asp = 1,
-     xlab = "p_1", ylab = "(p_1 - p_2)^2", main = "Gaussian approx.\n KL of Bernoullis")
-for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
-  lines(seq(0.00001,0.3, by = 0.000005),
-        (seq(0.00001,0.3, by = 0.000005)-i)^2)
-}
-par(mfcol = c(1,1))
-```
-
-```{r, echo = FALSE}
-KL_ber <- function(p,q) p*log(p/q) + (1-p)*log((1-p)/(1-q))
-par(mfcol = c(1,2))
-
-plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1), type = "n", asp = 1,
-     xlab = "p_1", ylab = "KL(Ber(p_2),Ber(p_1))", main = "KL of Bernoullis")
-for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
-  lines(seq(0.00001,0.3, by = 0.000005),
-        KL_ber(i,seq(0.00001,0.3, by = 0.000005)))
-}
-
-plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1), type = "n", asp = 1,
-     xlab = "p_1", ylab = "(p_2 - p_1)^2", main = "Gaussian approx.\n KL of Bernoullis")
-for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
-  lines(seq(0.00001,0.3, by = 0.000005),
-        (i-seq(0.00001,0.3, by = 0.000005))^2)
-}
-par(mfcol = c(1,1))
-```
-
-## Lower Bound: Theorem and Proof
-
-\begin{theorem}[Theorem 1, Locatelli et al., 2016] 
-\label{theorem:Locatelli2016Theorem1}
-For any sequence of gaps $(d_k)_k$, define a finite set of problems with Gaussian distributions with means corresponding to the gaps, and with variance 1.
-Lower bound the largest probability of error among these problems for the best possible algorithm as follows.
-Let $K,T \geq 0$.
-Let for any $i \leq K$, $d_i \geq 0$.
-Let $\tau \in \mathbb{R}, \epsilon > 0$.
-
-For $0 \leq i \leq K$, we write $\mathcal{B}^i$ for the problem where the distribution of arm $j \in \{1, \dots, K\}$ is $\mathcal{N}(\tau+d_i+\epsilon, 1)$ if $i \neq j$ and $\mathcal{N}(\tau-d_i-\epsilon, 1)$ otherwise.
-For all these problems, $H := H_{\tau, \epsilon} = \sum_i (d_i+2\epsilon)^{-2}$ is the same by definition.
-
-It holds that for any bandit algorithm,
-
-\begin{equation*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) \geq \exp(-3T/H-4 \log(12(\log(T)+1)K)),
-\end{equation*}
-
-where $\mathbb{E}_{\mathcal{B}^i}$ is the expectation according to the samples of problem $\mathcal{B}^i$.
-\end{theorem}
-
-*Proof of Theorem \ref{theorem:Locatelli2016Theorem1}*: In Theorem \ref{theorem:Locatelli2016Theorem1} of Locatelli et al.
-(2016), a lower bound for the thresholding bandit problem is shown.
-The basic idea is as follows.
-The problem formulation considered in the paper describes bandit problems for sub-Gaussian distributions.
-To show a lower bound, we show that every algorithm is expected to make a certain error even if we restrict ourselves to a very restricted scenario.
-Even then, any algorithm will have a certain level of risk with which it cannot distinguish between the actual setting and slightly changed settings (under which the former answer leads to regret).
-
-To be more specific, consider a case in which we set $\tau = 0$ and $\epsilon = 0$ w.l.o.g.
-If we then choose all arms to have normally distributed feedback with means $\mu_i$, we see that for each arm $i$ the distance from the threshold is given by $\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i$.
-Thus, assuming a variance of 1 for every arm, we have for every arm the distribution $\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)$.
-Furthermore, define for each arm $i \in \{1, \dots, K\}$ the alternative distribution $\nu_i' = \mathcal{N}(-\Delta_i,1)$.
-It is easy to see that in this case, this is equivalent to a "flip around the threshold".
-Arms that originally have a mean larger than the threshold have a mean smaller than the threshold after the flip.
-
-The idea now is that every arm $i \in \{1,\dots,K\}$ generates a sample for every time point $t\in \{1, \dots, T\}$ from its distribution $\nu_i$ before the algorithm starts to choose arms.
-Thus, we have a $T \times K$ table of realized observations from the product distribution given by $\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K$.
-This is a product distribution where the $K$ different means all lie above the threshold.
-We would hope that an algorithm classifies the means accordingly.
-However, we will show in what follows that any algorithm makes a certain error by not being able to distinguish $\mathcal{B}^0$ from at least one of $K$ alternative product distributions $\mathcal{B}^i, i \in \{1, \dots, K\}$, of which each differs only slightly in one arm from the original distribution, and has the same overall complexity (as defined by $H = \sum_{i=1}^K (\Delta_i)^{-2}$).
-We require $K$ different distributions so that an arm sampling arm $i$ very often for some reason will not have a smaller lower bound by chance.
-
-For each of the $K$ arms, we introduce an alternative model of the following kind.
-Before the start of the algorithm, we introduce a slight variation in the setup.
-The idea is similar to how one can switch arms in the pure exploration setup for multi-armed bandits (compare Audibert et al., 2010; Garivier & Kaufmann, 2016) to "confuse" any algorithm without introducing additional complexity to the specified problem.
-However, since we do not compare arms directly with each other in the thresholding bandit problem (switching arms would still keep all means above the threshold), we instead need to flip an arm $i$ with respect to the threshold in order to get the alternative model $\mathcal{B}_i$.
-Since the threshold is $\tau = 0$, we have for the flipped arm the new distribution $\nu_i'$ as defined above.
-Indeed, we can define the new product distribution $B^i = \nu_1^i \otimes \dots \otimes \nu_K^i$ where for $k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}$.
-This flipping of the arm corresponds to multiplying all random variables $X_{i,t}$ of arm $i$ by $-1$.
-
-As in Locatelli et al.
-(2016), we let for $i \leq K$, $\mathbb{P}_{\mathcal{B}^i}$ define the probability distribution describing all samples that a bandit strategy can potentially collect up to horizon $T$, i.e.
-according to the samples $(X_{k,s})_{k\leq K, s \leq T} \sim (\mathcal{B}^i)^{\otimes T}$.
-$(T_k)_{k\leq K}$ denotes the number of samples collected on arm $k$ until time $T$.
-
-### Reminder about the goal of the proof
-
-At this point, we have defined a finite set of problems of Gaussian distributions with fixed variance 1 for a given set of set of gaps between the means of the distributions and the threshold, $(d_k)_k$.
-We will now proof a lower bound on the worst case regret of any algorithm; that is, the maximum error probability that even the best algorithm makes on this problem.
-
-### Statistical Decision
-
-Given our formulation of the regret, the expected regret $\mathbb{E}[\mathcal{L}(T)]$ corresponds directly to the probability of making a wrong classification of any of the $K$ means.
-In general, let $g$ be a binary decision function, and define $\Omega = \{g = 0\}$ and $\Omega^C = \{g = 1\}$.
-Assume that the decision $T$ distinguishes between two states of the world, $H_0$ and $H_1$.
-Then our overall error probability is given by $P_{H_0}(g=1) + P_{H_1}(g = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)$.
-
-In our case, $H_0$ may correspond to the state in which we have $\mathcal{B}^0$, and $H_1$ corresponds to the case where any arm has been flipped, $\mathcal{B}^i$.
-Furthermore, we consider the events in which the algorithm, making the decision, classifies arm $i$ as being above the threshold: $\mathcal{A}_i = \{i \in \hat{S}_\tau\}$.
-The event on which all arms are being classified as above the threshold is consequently given by $\mathcal{A} = \bigcap \mathcal{A}_i$.
-However, Theorem 1 does not bound the overall regret, but the maximum error probability on the $K+1$ different models.
-We can write this now as
-
-\begin{align}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big) \\
-& = \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
-\end{align}
-
-In order to give a bound on above equation, we start by considering $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$.
-This probability can be written as the expected change in the likelihood of observed data when moving from distribution $P_{\mathcal{B}_0}$ to $P_{\mathcal{B}_i}$, times the probability under the original state.
-In other words, the probability of event $\mathcal{A}_i$ under state $\mathcal{B}^i$ is given as the probability of $\mathcal{A}_i$ under the (original) state $\mathcal{B}^0$ multiplied by a factor.
-This factor describes whether the new distribution increases or decreases the probability of the event, and is given by the change in the data likelihoods due to moving from $\mathcal{B}^0$ to $\mathcal{B}^i$, expressed as the expected likelihood ratio under $\mathcal{B}^0$.
-By definition, the latter is equal to the empirical Kullback-Leibler divergence of the two distributions.
-
-We will define the change of distribution in terms of the empirical log-likelihood for our case.
-Then, we will show how to replace the log-likelihood by the empirical Kullback-Leibler divergence.
-So let us first introduce the empirical Kullback-Leibler divergence.
-
-Let every $\nu_i, \nu_i'$ be dominated by the Lebesgue measure $\lambda$.
-Then their density functions are given by $f_i = \frac{\der \nu_i}{\der \lambda}$ and $f_i' = \frac{\der \nu_i'}{\der \lambda}$ respectively.
-For $T \geq t \geq 0$, define the empirical Kullback-Leibler divergence as
-
-\begin{align*}
-\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log(\frac{\der \nu_k'}{\der \nu_k}(X_{k,s})) \\
-& = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
-& = \frac{1}{t} \log \big( \prod_{s=1}^{t} \frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
-& \stackrel{\text{iid}}{=} \frac{1}{t} \log \big( \frac{f_k'(X_{k,1}, \dots,X_{k,t})}{f_k(X_{k,1}, \dots,X_{k,t})} \big) \\
-& = \frac{1}{t} \log \big( \text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k) \big)
-\end{align*}
-
-Since we consider Gaussian distributions with variance 1, we have density functions $f_i(x) \propto \exp \big(-\frac{1}{2} (x-\Delta_i)^2\big)$ and $f_i'(x) \propto \exp \big(-\frac{1}{2} (x+\Delta_i)^2\big)$.
-Plugging this into the above definition of the empirical Kullback-Leibler divergence, we easily see
-
-\begin{align*}
-\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{\exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2\big)}{\exp \big(-\frac{1}{2} (X_{k,s}-\Delta_k)^2\big)} \big) \\
-& = \frac{1}{t} \sum_{s=1}^{t} \log \big( \exp(-\frac{1}{2} (X_{k,s}+\Delta_k)^2 + \frac{1}{2} (X_{k,s}-\Delta_k)^2) \big) \\
-& = - \frac{1}{t} \sum_{s=1}^{t} 2 X_{k,s} \Delta_k
-\end{align*}
-
-### Change of Distribution
-
-We are now ready to state the change of distribution.
-As alluded to above, we consider how the probability changes for the event $\mathcal{A}_i$ when we move from $\mathcal{B}^0$ to $\mathcal{B}^i$.
-When flipping arm $i$, we only changed the samples of this arm, that is, the first $T_i$ observations we got from arm $i$ the algorithm took.
-The change of distribution is then defined as:
-
-\begin{align*}
-\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \text{LR}((X_{i,1}, \dots,X_{i,T_i}), \nu_i', \nu_i) ] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ]
-\end{align*}
-
-Obviously, $\hat{\KL}_{i,T_i}$ depends on the realized samples $X_{i,1}, \dots,X_{i,T_i}$.
-Consequently, we need to find a bound on $\hat{\KL}_{i,T_i}$ itself to incorporate the uncertainty involved in this metric.
-
-### Concentration of the Empirical Kullback-Leibler Divergence
-
-For our problem, the Kullback-Leibler divergence of $\nu_k'$ from $\nu_k$ is given by $\KL_k := KL(\nu_k', \nu_k) = 2\Delta_k^2$.
-
-It is easy to see that
-
-\begin{equation*}
-|\hat{\KL}_{k,t} - \KL_{k,t}| = |-\frac{2}{t} \Delta_k \sum_{s=1}^{t}(X_{k,s} - \Delta_k)|
-\end{equation*}
-
-itself is a normally distributed random variable with mean zero and a variance decreasing in $t$.
-Thus, one can show as in Locatelli et al.
-(2016) that $\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4$ for the event
-
-\begin{equation}
-\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}}\}. \label{LocatelliTheorem1EventXi}
-\end{equation}
-
-Thus, in order to bound the empirical Kullback-Leibler divergence in our change of measure, we can consider the intersection of $\mathcal{A}_i$ and $\xi$ as follows and plug in the bound on event $\xi$:
-
-\begin{align*}
-\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
-\end{align*}
-
-Two things are left to do: With $T_i$, we still have one random variable left which we cannot leave in our bound.
-Second, we are actually not interested in $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$ but in $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$.
-
-### Bounding $T_i$ for $\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$
-
-Part of our bound is $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$, so let's continue with that.
-In general it holds that $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K}\sum_{i=1}^K X_i$.
-Thus we can write:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
-& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
-& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
-\end{align*}
-
-where the second line is again the intersection of $\mathcal{A}_i$ and $\xi$ as before in order to apply the change of distribution in the third line.
-
-What is left to show before we have our final bound is a bound on $T_i$.
-To show that any algorithm has a certain bound on its error, it only makes sense that every arm has to pulled at least a certain amount of times.
-Consequently, no arm should be pulled exclusively.
-
-First, let $a = \Delta_i \sqrt{T_i}$ and $b = 4\sqrt{\log((4\log(T)+1)K)}$. Then use $ab \leq a^2 + b^2$ to write $ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)$. And so:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) ]
-\end{align*}
-
-Furthermore, we know that the sum of the individual arm pulls has to be equal to the overall number of pulls (equal to the budget in the fixed budget sense), $\sum_i T_i = T$, and furthermore we know that $T_i>0$.
-The latter holds since any reasonable algorithm has to check each arm at least once in our setup.
-This is because we need to check each arm's performance in comparison to the threshold.
-Thus it is easy to show that $\exists i: T_i \leq \frac{T}{H \Delta_i^2} = \frac{T}{(\sum_{i=1}^{K} \Delta_i^{-2}) \Delta_i^2}$.
-To see this, assume the opposite: $\forall i: T_i > T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2}$.
-This implies however $\sum_{i=1}^K T_i > \sum_{i=1}^K T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2} = T \cdot 1 = T$ which is a contradiction.
-
-So we can write $(\Delta_i \sqrt{T_i})^2 \leq \frac{T}{H}$. We use $\mathcal{A} = \cap_{i=1}^K \mathcal{A}_i$ to write:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}{K} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big]
-\end{align*}
-
-We write $\frac{1}{K} \sum_{i=1}^K \exp(-3T_i \Delta_i^2) \geq \frac{1}{K} \sum_{i=1}^K \exp(-3 T/H) = \exp(-3 T/H)$. Thus:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i) \exp(-16 \log(4(\log(T)+1)K)) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
-& = \mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
-\end{align*}
-
-### Bringing everything together
-
-Consider again the risk which we need to bound from equation \eqref{LocatelliTheorem1ExpRegret}.
-We bound the maximum expected loss over all $\mathcal{B}_i$.
-By again using the fact that in general $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K} \sum_{i = 1}^K X_i$, we plug in our previous calculations:
-
-\begin{align}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \label{LocatelliTheorem1DefinitionOfRisk}
-\end{align}
-
-From \eqref{LocatelliTheorem1EventXi} we know that for any $i \in \{0, \dots, K\}$, $\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4$.
-Following the argument in Locatelli et al.
-(2016), we now consider two cases: $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2$ and $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2$.
-In the former case, we can plug in the two probabilities into \eqref{LocatelliTheorem1DefinitionOfRisk}.
-If $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2$ and $\mathbb{P}_{\mathcal{B}^0}(\xi) \geq 3/4$, then $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \geq 1/4$.
-Thus:
-
-\begin{align*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \\
-& \geq \frac{1}{8} \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
-\end{align*}
-
-where we drop the second summand of the second line so that the inequality holds.
-
-On the other hand, when $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2$, then we know that $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \leq 1/2$ for any $\mathbb{P}_{\mathcal{B}^0}(\xi)$.
-At the same time $1-\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \geq 1/2$.
-Consequently, $1/4 \leq \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \leq 1/2$, while
-$\frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) \geq 0$.
-And so the stronger lower bound in that case is, as noticed by Locatelli et al.
-(2016), given simply by
-
-\begin{align*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \\
-& \geq \frac{1}{2}
-\end{align*}
-
 ## Upper Bound: Theorem and Proof
@@
 \newpage
-
-# Kullback-Leibler Complexity of Pure Exploration
-
-In the previous chapter, we have discussed the thresholding bandit problem as presented in Locatelli et al.
-(2016).
-Doing so, we came across the complexity term $H = \sum_{i=1}^{K} \Delta_i^{-2}$.
-Furthermore, we have noted the fact that an algorithm and bounds based on *only* the gap between the respective mean and the threshold are useful in the case of sub-Gaussian problems.
-Furthermore, even for the case of Bernoulli arms, which are sub-Gaussian since their feedback is bounded on $[0,1]$, the gap $\Delta$ becomes less and less appropriate for situations in which both $\mu$ of the Bernoulli, and $\tau$ are very close to 0 or 1.
-
-Even though the complexity $H$ enjoys popularity in the literature of the best $m$ arm identification problem, $m \geq 1$, Kaufmann et al.
-(2016) show explicitly that $H$ is mainly useful for problems of Gaussian distributions.
-Indeed, they go so far as to define new measures of complexity that are based on information theoretic measures Using those they then display $H$ as an approximation to their measures in the case of Gaussian distributions.
-In turn, this makes apparent that especially Bernoulli distributions with small means have to be treated differently.
-
-For the current chapter, we will adopt the notation of Kaufmann et al. (2016) so that it will be easier to compare the arguments.
-
-## Complexity of Best-Arm and Top-*m* Identification
-
-Instead of the thresholding bandit problem, we now consider the problem of identifying the best $m$ out of $K$ arms, that is, the Top-$m$ problem.
-While we previously looked at a fixed budget formulation, we now mainly focus on a fixed confidence problem.
-That is, we hold the confidence $1-\delta$ fixed at which a strategy returns the correct $m$ arms while trying to find them in a way that minimizes the sample complexity $\mathbb{E}_{\nu}[\tau]$, that is, the expected number of overall draws of the arms.
-$\tau$ is also called the stopping time of the algorithm.
-Algorithms are supposed to find $\mathcal{S}_m^*$, the set of the $m$ arms with the largest means.
-If we let $(\mu_1, \dots, \mu_K)$ be the vector of the means of the arms, then let $(\mu_{[1]}, \dots, \mu_{[K]})$ be the tuple in which the means are arranged in decreasing order.
-For the rest of this chapter, we consider only settings with arms for which $\mu_{[m]} > \mu_{[m+1]}$; that is, the set of the top $m$ arms, $\mathcal{S}_m^*$, is unique.
-After the sampling phase, we require any algorithm to return the set $\hat{S}_m \subset \{1,\dots,K\}$ of $m$ arms that the algorithm believes to have the largest means.
-In the case of fixed confidence, we fix $\delta$ at the beginning, such that the algorithm only stops sampling when $\mathbb{P}_{\nu}(\hat{S}_m = \mathcal{S}_m^*) \geq 1-\delta$.
-We try to find algorithms who fulfill this as quickly as possible; that is, they minimize the expected stopping time (or number of draws), $\mathbb{E}_{\nu}[\tau]$.
-
-To arrive at the new measure of complexity proposed by Kaufmann et al.
-(2016), it will actually make sense to first follow their arguments to a general lower bound on the sample complexity $\mathbb{E}_{\nu}[\tau]$ in the case of fixed confidence problems.
-This bound is given in their Theorem 4 (for common confidence levels of $\delta \leq 0.15$).
-
-\begin{theorem}[Theorem 4, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem4}
-Let $\nu \in \mathcal{M}_m$, where $\mathcal{M}_m$ is the set of uniquely identifiable bandit models described above.
-Assume that $\mathcal{P}$ satisfies the continuity conditions in Assumption 3.
-Any $\delta$-PAC algorithm on $\mathcal{M}_m$ satisfies, for $\delta \leq 0.15$:
-
-\begin{equation*}
-\mathbb{E}_{\nu}[\tau] \geq \Big[ \sum_{a \in \mathcal{S}^*_m} \frac{1}{KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}^*_m} \frac{1}{KL(\nu_a, \nu_{[m]})} \Big] \der(1-\delta, \delta),
-\end{equation*}
-
-where $\der(x,y) := x \log(x/y) + (1-x) \log((1-x)/(1-y))$ is the binary relative entropy, with the convention that $\der(0,0) = \der(1,1) = 0$.
-\end{theorem}
-
-To proof this statement, we assume as before that the arms are ordered by their means decreasing in size.
-For a given $\delta$-PAC algorithm $\mathcal{A} = ((A_t), \tau, \hat{S}_m)$, and under the continuity conditions (compare Kaufmann et al.
-(2016)), there exists for every arm $a \in \{1, \dots, K\}$ an alternative model $\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)$.
-In this alternative model, only arm $a$ is modified in accordance with the continuity conditions.
-Modified in such a way that measured by the Kullback-Leibler divergence, the arm $\nu_{m+1}$ is now closer to $\nu_a$ than $\nu_a'$ is to $\nu_a$, if $\mu_a > \mu_{m+1}$ (consequently, $\mu_a' < \mu_{m+1}$).
-On the other hand, if $\mu_a < \mu_{m}$, then $\nu_a'$ will be moved away from $\nu_a$ just enough so that $\nu_a$ is closer to $\nu_m$ than to $\nu_a'$ (consequently, $\mu_a' > \mu_m$).
-These changes in distribution make the original set of optimal arms, $\{1,\dots,m\}$ no longer optimal under the alternative model $\nu'$.
-Given that the algorithm returns $\hat{S}_m$, we know that for the event $\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})$ (which is element of the by the stopping time $\tau$ induced $\sigma$-Algebra $\mathcal{F}_{\tau}$), that $\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta$ and $\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta$ (because fixed confidence $\delta$!).
-
-To now give the lower bound on the expected number of samples, $\mathbb{E}_{\nu}[\tau]$, we employ the general lemma given by the authors for such changes in distribution in bandit models.
-
-\begin{lemma}[Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma1}
-Let $\nu$ and $\nu'$ be two bandit models with $K$ arms such that for all $a$, the distributions $\nu_a$ and $\nu_a'$ are mutually absolutely continuous.
-For any almost-surely finite stopping time $\sigma$ with respect to $(\mathcal{F}_t)$,
-
-\begin{equation*}
-\sum_{a=1}^{K} \mathbb{E}_{\nu} [N_a(\sigma)] \KL(\nu_a, \nu_a') \geq \sup_{\mathcal{E} \in \mathcal{F}_{\sigma}} \der (\mathbb{P}_{\nu}(\mathcal{E}), \mathbb{P}_{\nu'}(\mathcal{E})),
-\end{equation*}
-
-where $\der(x,y)$ is the binary relative entropy as defined above.
-\end{lemma}
-
-We can apply this lemma directly on the expected number of draws for each arm, $\mathbb{E}_{\nu}[N_a]$.
-For each arm $a$, we thus have $\KL(\nu_a, \nu_a') \mathbb{E}_{\nu}[N_a] \geq \der (1-\delta, \delta)$.
-Using the definition of the alternative model above, we get for every small but fixed $\alpha > 0$, for every arm $a \in \{1, \dots, K\}$ and each arm $b \in \{m+1, \dots, K\}$:
-
-\begin{equation*}
-\mathbb{E}_{\nu}[N_a] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_a, \nu_{m+1}) + \alpha}
-\end{equation*}
-
-and
-
-\begin{equation*}
-\mathbb{E}_{\nu}[N_b] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_b, \nu_{m}) + \alpha}.
-\end{equation*}
-
-We can then let $\alpha \to 0$, sum the bounds on the individual arms to get the bound on the overall number of draws:
-
-\begin{equation*}
-\mathbb{E}_{\nu}[\tau] = \sum_{a=1}^K \mathbb{E}_{\nu}[N_a] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \der(1-\delta, \delta)
-\end{equation*}
-
-Given that we will be naturally interested in either very high or very low confidence of our algorithm, that is, $P_\nu(\mathcal{E})$ is either close to 0 or 1, it is possible to use the following approximation to the binary relative entropy:
-
-\begin{equation}\label{bre_approx}
-\forall x \in [0,1], \quad \der(x,1-x) = \der(1-x,x) \geq \log \frac{1}{2.4x}
-\end{equation}
-
-And so the final lower bound can be written as
-
-\begin{equation*}
-\mathbb{E}_{\nu}[\tau] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
-\end{equation*}
-
-```{r, echo = FALSE}
-x <- seq(0,1,by = 0.001)
-bre <- function(x) x * log(x/(1-x)) + (1-x) * log((1-x)/x)
-plot(x,bre(x), type = "l", ylab = "Binary Relative Entropy")
-lines(x, log(1/(2.4*x)), col = "red")
-abline(v = 0.15, lty = 2)
-```
-
-Given this general lower bound for the sampling complexity, or expected number of draws, it makes sense to define the complexity of a Top-$m$ bandit problem using the Kullback-Leibler divergence.
-After all, besides the number of arms and the experimenter-chosen confidence, it is just how close arms are with respect to each other in terms of Kullback-Leibler divergence that influences the sampling complexity.
-And in general, a problem requiring more samples is of course considered to be more complex (at least with respect to the samples, which is what needs to be optimized).
-
-Thus, following Kaufmann et al. (2016), define the complexity $\kappa_C(\nu)$ for the fixed confidence setting as
-
-\begin{equation}
-\kappa_C(\nu) = \inf_{A \, \text{PAC}} \lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\nu}[\tau_{\delta}]}{\log \frac{1}{\delta}}.
-\end{equation}
-
-So if we were to plug in the lower bound on the sampling complexity, we would arrive at a complexity measure that basically depends only on the Kullback-Leibler measuring for each arm how far it is away from the border between the two groups of arms.
-To see this, consider the lower bound on the complexity measure given in Kaufmann et al.
-(2016):
-
-\begin{equation*}
-\kappa_C(\nu) \geq \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})}
-\end{equation*}
-
-Given this description, we can already note that an intuitive extension of this complexity notion to the thresholding bandit problem might involve replacing $\mu_{[m]}$ and $\mu_{[m+1]}$ by the actual threshold $\tau$ (notation in Locatelli et al.) that divides the group above the threshold from the group below the threshold.
-In that case, the previously used $\alpha$ might be very similar to the $\epsilon$ used in Locatelli et al.
-(2016).
-
-To get there, however, at least two important steps remain. First, we need to define a complexity for the fixed budget problem. Second, we need to create algorithms that can match the lower bound.
-
-Kaufmann et al.
-are able to provide a bound on their complexity measure in the fixed budget case, however only in the case of **two-armed** bandit models.
-As demanded in their paper, a fixed-budget algorithm is called consistent if the failure probability $p_t(\nu) := \mathbb{P}_{\nu}(\hat{S}_m \neq S^*_m)$ tends to zero as the number of samples goes to infinity.
-Also, define the complexity in the fixed-budget setting as follows:
-
-\begin{equation}
-\kappa_B(\nu) = \inf_{A \, \text{consistent}} \big(\lim_{t \to \infty} \sup - \frac{1}{t} \log p_t(\nu)\big)^{-1}.
-\end{equation}
-
-Given this definition, one can interpret the bound given in Theorem 12 of Kaufmann et al. directly as a lower bound on the complexity $\kappa_B(\nu)$ (note the inverse).
-
-\begin{theorem}[Theorem 12, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem12}
-Let $\nu = (\nu_1, \nu_2)$ be a two-armed bandit model such that $\mu_1 > \mu_2$. In the fixed-budget setting, any consistent algorithm satisfies:
-
-\begin{equation*}
-\lim_{t \to \infty} \sup - \frac{1}{t} \log p_t(\nu) \leq \inf_{(\nu_1', \nu_2') \in \mathcal{M}: \mu_1' < \mu_2'} \frac{\KL(\nu_1', \nu_1) + \KL(\nu_2', \nu_2)}{2}
-\end{equation*}
-\end{theorem}
-
-For a proof, consider first the two different bandit models, $\nu$ and $\nu'$, where we fix without loss of generality that $a^* = 1$ is the best arm in $\nu$, while $a^* = 2$ in $\nu'$.
-Note that in this case we don't necessarily try to fool the algorithm by a change of distribution.
-Indeed, we want the algorithm $\mathcal{A}$ to be consistent for both problems.
-Since we are in the fixed-budget setting, the stopping time is fixed at $\tau = t$.
-Even though the correct decision differs between the two problems, we focus on the event $A = (\hat{S}_1 = 1)$.
-Given the formulation in Kaufmann et al.
-(2016), we have $A \in \mathcal{F}_t = \mathcal{F}_{\tau}$.
-Now, we can apply Lemma 1 as before, as it in essense gives a measure of how different two bandit models are.
-Here, we want to know how different $\nu$ is from $\nu'$, and so, given we have only two arms,
-
-\begin{equation*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2', \nu_2) \geq \der(\mathbb{P}_{\nu'}(A),\mathbb{P}_{\nu}(A)))
-\end{equation*}
-
-The expectations were chosen with respect to $\nu'$ in order to allow the for the following: We have $p_t(\nu) = 1 - \mathbb{P}_{\nu}(A)$ and $p_t(\nu') = \mathbb{P}_{\nu'}(A)$ (since $A$ is wrong in $\nu'$).
-But since algorithm $\mathcal{A}$ is consistent for both $\nu$ and $\nu'$, we know that there should exist some number of samples such that the probability of event $A$ is bigger in setting $\nu$ (where it is the correct decision), than in setting $\nu'$ (where this would be a wrong decision and failure).
-Thus, for every $\epsilon > 0$, there exists $t_0(\epsilon)$ such that for all $t \geq t_0(\epsilon)$, $\mathbb{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)$.
-Consequently, if we plug in the bound of $\epsilon$ for $\mathbb{P}_{\nu'}(A)$, then
-
-\begin{align*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2', \nu_2) & \geq \der(\epsilon,1-p_t(\nu))) \\
-& = \epsilon \log \frac{\epsilon}{1-p_t(\nu)} + (1-\epsilon) \log \frac{1-\epsilon}{p_t(\nu)} \\
-& \geq (1-\epsilon) \log \frac{1-\epsilon}{p_t(\nu)} + \epsilon \log \epsilon.
-\end{align*}
-
-Let $\epsilon$ go to zero so that
-
-\begin{align*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2', \nu_2)
-& \geq \log \frac{1}{p_t(\nu)} = -\log p_t(\nu).
-\end{align*}
-
-Dividing both sides by $t$ and taking the limsup, we arrive at
-
-\begin{align*}
-\lim_{t \to 0} \sup - \frac{1}{t} \log p_t(\nu)
-& \leq \lim_{t \to 0} \sup \frac{1}{t} \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)] \KL(\nu_a', \nu_a) \\
-& \leq \max_{a=1,2} \KL(\nu_a', \nu_a),
-\end{align*}
-
-where the last line follows from the fact that the $\frac{1}{t} \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)]$ part creates a weighted average of the two divergences $\KL(\nu_a', \nu_a)$.
-As noted in Kaufmann et al.
-(2016), one arrives at the final result by choosing $\mu_1'$, $\mu_2'$ so that $| \KL(\nu_1', \nu_1) - \KL(\nu_2', \nu_2) |$ is as small as possible.
-
-Note that while deriving the lower bound on the complexity measure, we have also derived the following lower bound on the failure probability for the two-armed fixed-budget bandit:
-
-\begin{equation*}
-p_t(\nu) \geq \exp \big(- \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)] \KL(\nu_a', \nu_a) \big)
-\end{equation*}
-
-or, to not rely on the share of samples attributed to each arm,
-
-\begin{equation*}
-p_t(\nu) \geq \exp \big(- \max_{a=1,2} \KL(\nu_a', \nu_a) \big).
-\end{equation*}
-
-**Mention something about the fact that we were not able to do this for more than 2 arms and top-m bandits. How could it be extended to that? How could it be extended to the threshold bandit?**
-
-As noted by Kaufmann et al.
-(2016), the advantage of this lower bound is that it makes the complexity in the fixed-confidence and the fixed-budget setting directly comparable.
-The disadvantage of course being that the result only holds for two-armed models.
-While the authors were not able to derive directly comparable lower bounds for the Top-$m$ case, they did derive a first lower bound in the Gaussian case with equal variances.
-While we would like to move beyond Gaussian distributions in the work at hand, the idea for the proof might show a way of how the ideas can be transferred to the thresholding bandit problem.
-We first state the result and then discuss the proof.
-
-\begin{lemma}[Lemma 15, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma15}
-Let $\nu$ and $\nu'$ be two bandit models such that $S^*_m(\nu) \neq S*_m(\nu')$. Then
-
-\begin{equation*}
-\max \big( \mathbb{P}_{\nu}(S \neq S^*_m(\nu)), \mathbb{P}_{\nu'}(S \neq S^*_m(\nu')) \big) \geq \frac{1}{4} \exp \Big(-\sum_{a=1}^{K} \mathbb{E}_{\nu}[N_a] \KL(\nu_a, \nu_a') \Big).
-\end{equation*}
-\end{lemma}
-
-The following theorem only holds in the case of Gaussian bandit models with equal known variance.
-
-\begin{theorem}[Theorem 17, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem17}
-
-Let $\mathcal{M}_m = \{\nu = (\nu_1, \dots, \nu_K): \nu_a = \mathcal{N}(\mu_a, \sigma^2), \mu_a \in \mathbb{R}, \mu_{[m]}\neq \mu_{[m+1]}\}.$ Furthermore, let $\nu$ be such that $\mu_1 > \dots > \mu_m > \mu_{m+1} > \dots > \mu_K$, and let
-
-\begin{equation*}
-H +(\nu) = \sum_{a=1}^m \frac{2\sigma^2}{(\mu_a - \mu_{m+1})^2}, \quad H^-(\nu) = \sum_{a=m+1}^K \frac{2\sigma^2}{(\mu_m - \mu_a)^2} \quad
-and \quad
-H(\nu) = H^+(\nu) + H^-(\nu).
-\end{equation*}
-
-There exists $a \in {1, \dots, m}$ and $b \in \{m+1, \dots, K\}$ such that the bandit model $\nu^{[a,b]}$ described in Figure 4 (Kaufmann et al., 2016) satisfies $H(\nu^{[a,b]}) < H(\nu)$ and is such that
-
-\begin{equation*}
-\max \big( p_t(\nu),p_t(\nu^{[a,b]})\big) \geq \frac{1}{4} \exp \big(-\frac{4t}{\bar{H}(\nu)}\big), \quad where \quad \bar{H}(\nu) = \frac{H(\nu) \min(H^+(\nu),H^-(\nu))}{H(\nu)+\min(H^+(\nu),H^-(\nu))}
-\end{equation*}
-\end{theorem}
-
-Given that we are again in the Top-$m$ setting, the proof idea is similar to the proof of Theorem \ref{theorem:KaufmannEtAlTheorem4} in that we again consider problems where we switch arms around the limit seperating the two groups of arms as given implicitly by $\mu_{[m]}$ and $\mu_{[m+1]}$.
-The hope here being that these methods could be applied to the thresholding bandit problem where the threshold of course gives the limit between the arms above and below the threshold.
-As we have seen in chapter 1, this flip around the threshold was of course used in the proof of the lower bound in Theorem 1 of Locatelli et al.
-(2016).
-However, there, again, the distributions were assumed to be Gaussian.
-This brings the big advantage that the Kullback-Leibler divergence becomes symmetric, and the feedback can take values on all $\mathbb{R}$.
-And by using the complexity measure $H(\nu)$, it is also clear that there exists an arm that is undersampled with respect to its contribution to the overall complexity of the problem (or sampled exactly according to its contribution), which leads to leads to a convenient upper bound on this arms number of draws which is again employed in both the proof of Theorem \ref{theorem:KaufmannEtAlTheorem17} and in Locatelli et al.
-(2016).
-It is not clear yet, whether the same can also be done with other complexity measures.
-
-We do not repeat the proof here for now.
-
-See p20!
-
-What remains is to present algorithms that are able to match the lower bounds derived so far.
-
-### Matching algorithm strategies
-
-Given these lower bounds, all that is left is to find algorithms which are able to match the complexity. Sadly, not straightforward for Bernoullis.
-
-Kaufmann et al.
-(2016) do not present algorithms matching the lower bound of Theorem \ref{theorem:KaufmannEtAlTheorem17}.
-They do consider algorithms that connect to Theorem \ref{theorem:KaufmannEtAlTheorem4} and Theorem \ref{theorem:KaufmannEtAlTheorem12}.
-
-Given that Locatelli et al.
-(2016), and thus the problem we mostly consider in this thesis, is in the fixed-budget setting, we are most interested in the matching strategies for Theorem \ref{theorem:KaufmannEtAlTheorem12}.
-However, given that the lower bound applies only to two-armed bandits, the algorithms are of limited practical interest.
-Furthermore, the algorithms proposed require knowledge that is in general not available upfront.
-
-For the example of Gaussian distributions, the knowledge of the (potentially different) variance is assumed which enables a strategy that pulls each arm proportional to its variance.
-
-Even worse is the case of Bernoulli two-armed bandit models where the proposed algorithm requires knowledge about the true parameters of the distributions.
-That this limits the practical interest is also noted by the authors of Kaufmann et al.
-(2016).
-Thus, they suggest to use uniform sampling strategies in the case of two-armed Bernoulli bandits, and show that there is not much to be lost by doing so.
-
-Thus, Kaufmann et al.
-(2016) join a number of other papers like Audibert et al.
-(2010) and Kaufmann and Kalyanakrishnan (2013) which struggle to find matching strategies in the fixed-budget setting that do not rely on knowledge of parameters or the complexity of the problem.
-
-In contrast, Kaufmann et al.
-(2016) are able to show that their complexity measure derived for the fixed-confidence setting, $\kappa_C(\nu)$, can be upper-bounded using the upper bound of the sample complexity (number of pulls) given for the KL-LUCB algorithm in Kaufmann and Kalyanakrishnan (2013).
-Consequently, in the case of exponential family bandits, the complexity $\kappa_C(\nu)$ is bounded as given in equation (6) in Kaufmann et al.
-(2016):
-
-\begin{equation*}
-\sum_{a \in S^*_m} \frac{1}{K(\theta_a, \theta_{[m+1]})} + \sum_{a \notin S^*_m} \frac{1}{K(\theta_a,\theta_{[m]})} \leq \kappa_C(\nu) \leq 24 \min_{\theta \in [\theta_{[m+1]},\theta_{[m]}]} \sum_{a=1}^{K} \frac{1}{K^*(\theta_a, \theta)},
-\end{equation*}
-
-where $K(\theta, \theta') = \KL(\nu_{\theta}, \nu_{\theta'})$ for $(\theta, \theta') \in \Theta^2$ was defined as the shorthand for the Kullback-Leibler divergence for two distributions from the exponential family parameterized by $\theta$ and $\theta'$ respectively.
-$K^*(\theta,\theta') = K(\theta^*, \theta)$ is the Chernoff distribution between the two distributions, where $\theta^*$ is chosen so that $K(\theta^*,\theta) = K(\theta^*, \theta')$.
-
-## Optimal Best Arm Identification
-
-A very similar application of the KL divergence has been given in Garivier and Kaufmann (2016) to derive a lower bound on the sample complexity in the case of best arm identification.
-In particular, the transportation Lemma 1 is used again.
-And a matching algorithm for $K \geq 2$ arms is proposed.
-
-Talk about:
-- Not a simple sum of squares
-- Idea of algorithm: Equalize the probability of all wrong decisions
-
-In Garivier and Kaufmann (2016), the authors are able to derive a somewhat similar lower bound on the sample complexity of a $K$-armed bandit in the single best arm identification problem with fixed confidence.
-Additionally, they provide a $\delta$-PAC algorithm achieving said bound asymptotically.
-
-In particular, the authors pick up Lemma 1 from Kaufmann et al.
-(2016) -- which we discussed above -- to derive the lower bound.
-While presenting these results, we try to stick as much as possible with the notation used so far.
-In particular, we let for distributions $\nu_{\theta}$ from a canonical exponential family, which can be parameterized by its mean $\stackrel{.}{b}(\theta) = \mu$ and thus be written as $\nu^{\mu}$; for these, we continue to write the Kullback-Leibler divergence as
-
-\begin{equation*}
-\KL(\mu, \mu') = \KL(\nu^{\mu},\nu^{\mu'}) = \KL(\nu_{\theta},\nu_{\theta'}) = \KL(\nu, \nu')
-\end{equation*}
-
-while $d(x,y)$ continues to represent the binary relative entropy.
-
-As we will consider only problems with exponential family distributions, the distributions can be parameterized by their means.
-Therefore, if we let $\mathcal{S}$ to be a set of bandit models with $K$ distributions each, then each model is fully defined by a vector $\bm{\mu} = (\mu_1, \dots, \mu_K)$.
-Assume that every $\bm{\mu} \in \mathcal{S}$ has a unique maximum given by $a^*(\bm{\mu})$ such that $\mu_{a^*} > \max_{a \neq a^*(\bm{\mu})} \mu_a$.
-In order to fix the confidence, we specify the risk $\delta$.
-The strategies corresponding to this risk are called $\delta$-PAC if for every $\bm{\mu} \in \mathcal{S}$, $\mathbb{P}_{\bm{\mu}}(\tau_{\delta} < \infty) = 1$ (the strategy ends surely after a finite number of samples) and $\mathbb{P}_{\bm{\mu}}(\hat{a}_{\tau_{\delta}} \neq a^*) \leq \delta$ (the probability of picking not the optimal arm is smaller than the fixed risk).
-As in Garivier and Kaufmann (2016), we introduce the set of problems for which the optimal arm is different from the one in $\bm{\mu}$:
-
-\begin{equation*}
-\text{Alt}(\bm{\mu}) := \{\bm{\lambda} \in \mathcal{S}: a^*(\bm{\lambda}) \neq a^*(\bm{\mu})\}
-\end{equation*}
-
-where $\bm{\lambda}$ is the vector of means defining the distributions of the alternative problem to $\bm{\mu}$.
-Lastly, we have the set of probability distributions on the arms $\mathcal{A}$: $\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}$.
-\marginpar{Give more intuition for what these probability distributions are} We are now ready to state the theorem.
-
-\begin{theorem}[Theorem 1, Garivier and Kaufmann, 2016] \label{theorem:GarivierKaufmannTheorem1}
-Let $\delta \in (0,1)$. For any $\delta$-PAC strategy and any bandit model $\bm{\mu} \in \mathcal{S}$,
-
-\begin{equation*}
-\mathbb{E}_{\bm{\mu}} [\tau_{\delta}] \geq T^*(\bm{\mu}) \text{\em{d}}(\delta,1-\delta),
-\end{equation*}
-
-where
-
-\begin{equation} \label{eq:GarivierKaufmann_Theorem1_Game}
-T^*(\bm{\mu})^{-1} := \sup_{w \in \Sigma_K} \inf_{\bm{\lambda} \in \text{\em{Alt}}(\bm{\mu})} \left( \sum_{a=1}^K w_a \text{\em{KL}}(\mu_a, \lambda_a)\right).
-\end{equation}
-\end{theorem}
-
-And so we see that the two bounds on the sample complexity (one for Top-$m$, one for best arm identification) differ only in the way that they build the sum of Kullback-Leibler divergences over the $K$ arms.
-In contrast to Theorem \ref{theorem:KaufmannEtAlTheorem4}, here the contribution of each arm through its KL-divergence is weighted.
-The difference is that while we were able to very clearly describe the change of distribution in the Top-$m$ case for each arm -- for each arm, we specified an alternative model that yields a new set of $m$ optimal arms -- we now consider all alternative models that yield a different best arm than the model $\bm{\mu}$.
-In the previous theorem, we sum over the complexity of each individual arm, as the change in distribution only ever touches one arm, thus leading to a KL-divergence of 0 for the other arms while still changing the optimal set.
-Here, we consider all instances of alternative models $\bm{\lambda}$, and thus also those in which several arms are modified (and thus have a KL-divergence unequal 0 in the result of Lemma 1).
-
-*Proof of Theorem \ref{theorem:GarivierKaufmannTheorem1}*: As stated before, we let $\delta \in (0,1)$, $\bm{\mu} \in \mathcal{S}$, and only consider $\delta$-PAC strategies.
-As before, $N_a(t)$ describes the random number of pulls of arm $a$ until time $t$, for all $t\geq 1$.
-Again, Lemma \ref{theorem:KaufmannEtAlLemma1} states how the failure probability $\delta$ relates to the expected number of draws of each arm given two models which differ in their optimal arm, and where it is evaluated based on the Kullback-Leibler divergence for each pair of arms how much the two models differ:
-
-\begin{equation*}
-\forall \lambda \in \mathcal{S}: a^*(\lambda) \neq a^*(\mu), \sum_{a=1}^K \KL(\mu_a,\lambda_a)\mathbb{E}_{\bm{\mu}}[N_a(\tau_{\delta})] \geq \d(\delta, 1- \delta).
-\end{equation*}
-
-As mentioned, we now do not consider a specific alternative for each arm, but instead look at the infimum over all the possible alternatives, and use the fact that $\mathbb{E}_{\bm{\mu}}[\tau_{\delta}] = \sum_{a=1}^K \mathbb{E}_{\bm{\mu}}[N_a(\tau_{\delta})]$:
-
-\begin{align*}
-\der(\delta, 1-\delta) & \leq \inf_{\lambda \in \text{Alt}(\bm{\mu})} \mathbb{E}_{\bm{\mu}}[\tau_{\delta}] \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[\tau_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
-& = \mathbb{E}_{\bm{\mu}}[\tau_{\delta}] \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[\tau_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
-& \leq \mathbb{E}_{\bm{\mu}}[\tau_{\delta}] \sup_{w \in \Sigma_K} \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K w_a \KL(\mu_a, \lambda_a)\Big).
-\end{align*}
-
-As stated in Garivier and Kaufmann (2016), the term $\frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[\tau_{\delta}]}$ gives the fraction of draws each arm receives.
-This value, however, depends on the used algorithm.
-To make it hold for any $\delta$-PAC algorithm, it is replaced by the supremum over $\Sigma_K$, which is the distribution over these fractions for any $\mathcal{A}$, that is, for any $\delta$-PAC strategy.
-
-This lower bound can be interpreted as a Minimax game, where the experimenter has to choose the share of samples he attributes to each arm in a way that is optimal given that nature will respond and choose the most difficult alternative model given his weights.
-Thus, to make the lower bound practical, it is a matter of finding the optimal weights $w^*(\bm{\mu})$.
-This step did not occur in the previous lower bound, as the alternative models were made specific by changing the distribution of one arm with respect to the "border" between the two groups of arms.
-
-In any case, the existence of the optimal weights suggests an algorithm that keeps track of the share of samples that is attributed to each arm and makes sure that it stays close to the optimum until some decision rule assures that the $\delta$-PAC condition is fulfilled.
-
-Indeed, the optimal weights will lead to a sampling structure in which arms are drawn in such a way ensuring that their individual failure probabilities are at the same level.
-Take a situation where the currently best arm $\hat{\mu}_1$ is the best arm.
-Then, we calculate for each arm the risk that actually it is better than arm 1.
-Since the arms are assumed to be independent, the we only have to compare every arm individually to arm 1.
-Given that, it makes sense that we don't want to disregard an arm that has a high probability of being better than arm 1.
-Assuming arm 1 is actually the best arm, we would an algorithm that ensures a low failure probability on all arms, thus equalizing the failure probability for every arm compared to arm 1.
-
-This is exactly what happens when we look for the proportions $w \in \Sigma_K$ that minimize the cost from a change in distributions, that is, the term $F(\bm{\mu}, \bm{w}) = \inf_{\bm{\lambda} \in \text{Alt}(\bm{\mu})} \Big(\sum_{a= 1}^K w_a \KL(\mu_a, \lambda_a)\Big)$.
-In the proof of Lemma 3 of Garivier and Kaufmann, it is shown that nature, selecting the alternative model $bm{\lambda}$ will always pick an alternative model in which only a single arm $a$ is changed such that $\lambda_a > \lambda_1$ since
-
-\begin{align*}
-T^*(\bm{\mu})^{-1} & = \sup_{w \in \Sigma_K} \min_{a \neq 1} \inf_{\bm{\lambda} \in \mathcal{S}: \lambda_a > \lambda_1} \sum_{a=1}^K w_a \KL(\mu_a, \lambda_a)  \\
-& = \sup_{w \in \Sigma_K} \min_{a \neq 1} \inf_{\bm{\lambda}: \lambda_a \geq \lambda_1} [w_1 \KL(\mu_1, \lambda_1)+w_a \KL(\mu_a, \lambda_a)].
-\end{align*}
-
-Consequently, $w$ will be chosen so as to minimize $T^*(\bm{\mu})$ no matter which arm $a$ was picked.
-It is a minimax game, so the ideal solution is to keep for each arm $a \neq 1$ the term $w_1 \KL(\mu_1, \lambda_1) + w_a \KL(\mu_a, \lambda_a)$ at the same level.
-Garivier and Kaufmann show that this can be written in terms of the Jenson-Shannon divergence, defined for every $\alpha \in [0,1]$ as
-
-\begin{equation*}
-I_{\alpha}(\mu_1, \mu_2) := \alpha \KL(\mu_1, \alpha \mu_1 + (1-\alpha) \mu_2) + (1-\alpha) \KL(\mu_2, \alpha \mu_1 + (1-\alpha) \mu_2).
-\end{equation*}
-
-Using this notation, the optimal proportions can be written as 
-\begin{equation*}
-w^*(\bm{\mu}) = \arg \max_{w \in \Sigma_K} \min_{a \neq 1} (w_1 + w_a) I_{\frac{w_1}{w_1+w_a}}(\mu_1, \mu_a)
-\end{equation*}
-
-which let's us furthermore conclude that these quantities are equal for all $a,b \in \{2,\dots, K\}$ with
-\begin{equation*}
-(w_1^* + w_a^*) I_{\frac{w_1^*}{w_1^*+w_a^*}}(\mu_1, \mu_a) = (w_1^* + w_b^*) I_{\frac{w_1^*}{w_1^*+w_b^*}}(\mu_1, \mu_b),
-\end{equation*}
-
-which is simply the statement in Lemma 4 of Garivier and Kaufmann (2016).
-
-And so by assuring the reader that there are ways to compute $w_a^*$ and $T^*$ given $\bm{\mu}$ (see chapter 2.2 in Garivier and Kaufmann (2016)), we can now introduce the *Track-and-Stop* strategy given in Garivier and Kaufmann (2016) that is able to match the lower bound by the intuition given above.
-
-When going from theory to algorithm, the obvious problem is of course that we do no longer know $\bm{\mu}$ and thus cannot simply calculate the optimal weights.
-Instead, we are estimating the maximum likelihood estimates $\hat{\mu}(t) = (\hat{\mu}_1(t), \dots, \hat{\mu}_K(t))$ of the true mean at the current round $t$ and need to base our weights based on these.
-It is however problematic to rely on these sample means as we are inherently unsure about them.
-And so wrong estimates, which naturally occur most easily in the beginning when not many samples have been pulled, are prone to lead to wrong weights.
-Thus, if a wrong estimate $\hat{\mu}_a$ for arm $a$ leads to a small weight $w_a$, then neither the estimate nor the weight will be correct soon.
-Thus, Kaufmann and Garivier conclude that "a naive plug-in sampling rule sometimes fails".
-They propose to enforce a certain minimum level of exploration to make sure that arms that erroneously received a very small weight will be further explored regardless.
-
-A very intuitive fix to this problem is the solution proposed in Lemma 8 of Garivier and Kaufmann (2016), with their $D-Tracking$ rule.
-Basically, whenever an arm has received a very low number of pulls $N_a(t)$ given the number of iterations so far, $t$ and the number of arms $K$ that have to share the samples, pull the arm that has received the smallest amount of samples so far.
-Else, pull the arm which number of pulls so far $N_a(t)$ is the furthest away from what its optimal share $t\cdot w^*_a(\hat{\bm{\mu}}(t))$ would be.
-Given this sampling rule, the authors can show in their Proposition 9 that the empirical proportion of draws converges in probability to the optimal weights given the true means.
-
-When combining this sampling rule with an appropriate stopping rule, the authors are able to prove in Theorem 14 an upper bound on the expected sampling complexity $\mathbb{E}_{\mu}[\tau_{\delta}]$.
-The stopping rule ensures that the algorithm explores sufficiently to promise a risk smaller than $\delta$, while stopping as soon as possible.
-Given that the sampling rule is independent of this stopping rule, the rule boils down to a statistical test at every iteration and thus is a sequential test based on the current estimate of $\hat{\bm{\mu}}$.
-The Chernoff's Stopping Rule proposed in Garivier and Kaufmann (2016) calculates for each arm $a\in \mathcal{A}$ the Generalized Likelihood Ratio statistic with every arm $b \in \mathcal{A}^{\setminus a}$, which for $\hat{\mu}_a(t) \geq \hat{\mu}_b(t)$ can be written as
-
-\begin{equation*}
-Z_{a,b}(t) = - Z_{b,a} = N_a(t) \KL(\hat{\mu}_a(t),\hat{\mu}_{a,b}(t)) + N_b(t) \KL(\hat{\mu}_{b}(t), \hat{\mu}_{a,b}(t)),
-\end{equation*}
-
-where
-
-\begin{equation*}
-\hat{\mu}_{a,b}(t) := \frac{N_a(t)}{N_a(t) + N_b(t)}\hat{\mu}_a + \frac{N_b(t)}{N_a(t) + N_b(t)}\hat{\mu}_b.
-\end{equation*}
-
-Consequently, a sensible idea for a stopping rule would be that there has to be an arm $a \in \mathcal{A}$ for which $Z_{a,b} \geq 0 \forall b \in \mathcal{A}^{\setminus a}$ (which is always fulfilled if there is a uniquely best arm), and, additionally, we demand that for this arm the smallest of the $(K-1)$ test statistics has to be larger than an exploration threshold $\beta(t, \delta)$.
-Consequently, the final number of samples $\tau_{\delta}$ of an algorithm is given by:
-
-\begin{equation*}
-\tau_{\delta} = \inf \{t \in \mathbb{N}: \exists a \in \mathcal{A}, \forall b\in \mathcal{A}^{\setminus a}, Z_{a,b}(t) > \beta(t, \delta)\}
-\end{equation*}
-
-Demanding that the optimal exploration threshold increases in rounds $t$ (if we have more samples, require more certainty; also, punish for failing previous tests) and decreases in the risk $\delta$, and does so at a diminishing rate, the optimal threshold derived in Theorem 10 of Garivier and Kaufmann (2016) makes sense intuitively:
-
-\begin{equation*}
-\beta(t, \delta) = \log \Big(\frac{2t(K-1)}{\delta}\Big).
-\end{equation*}
-
-With this, we can state the final theorem of the chapter, which gives the upper bound matching the lower bound in Theorem \ref{theorem:GarivierKaufmannTheorem1} for small risk values $\delta$ using the D-Tracking rule and Chernoff's stopping rule with the exploration term given in the previous equation:
-
-\begin{theorem}[Theorem 14, Garivier and Kaufmann, 2016] \label{theorem:GarivierAndKaufmannTheorem14}
-Let $\bm{\mu}$ be an exponential family bandit model.
-Let $\alpha \in [1, e/2]$ and $r(t) = O(t^{\alpha})$.
-Using Chernoff's stopping rule with $\beta(t,\delta) = \log(r(t)/\delta)$ and the sampling rule C-Tracking or D-Tracking,
-
-\begin{equation*}
-\lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\bm{\mu}}[\tau_{\delta}]}{\log(1/\delta)} \leq \alpha T^*(\mu).
-\end{equation*}
-\end{theorem}
-
-## Conclusion of Complexity of Best Arm Identification
-
-Overall, the two papers presented in this chapter make significant contributions to identifying the top-$1$ or the top-$m$ arms in a multi-armed bandit setting.
-Their contribution is primarily based on including the Kullback-Leibler divergence in the derivation of bounds and the matching algorithms and thus going beyond a sum of squared gaps which is most practical only in the case of Gaussian distributions.
-While the contribution in the fixed-budget setting was limited to the two-armed bandit case, the authors derive general lower bounds in the fixed-confidence setting which are primarily based on Lemma \ref{theorem:KaufmannEtAlLemma1}.
-Lemma \ref{theorem:KaufmannEtAlLemma1} is able to measure the "transportation cost" (see Garivier and Kaufmann, 2016) of moving from one distribution to another one in terms of Kullback-Leibler divergence.
-This transportation cost will increase the expected stopping time, and so the experimenter has to be careful when selecting which arm to sample.
-By picking proportions $w^*(\bm{\mu})$ that minimize the transportation cost, a solution is found with as few iterations as possible.
-
-With respect to the optimal proportions we have derived some characteristics that now allow for a few interpretations.
-First, we have demanded that the algorithm keeps arms proportions in a way that equalizes the failure probability of every arm with respect to the best arm.
-This is basically similar to keeping the weighted Jensen-Shannon divergence at the same level which was shown in Lemma 4 of Garivier and Kaufmann (2016) and which we have repeated above.
-The fact that the risk plays an important role at any round of the algorithm suggests the possibility of turning the algorithm into an anytime algorithm.
-That is, instead of relying on Chernoff's stopping rule to end the algorithm at one point, and not being able to stop the algorithm before that and receiving a meaningful result, one would be able to stop the algorithm at any iteration, and receive both the recommended best arm and a confidence level.
-Second, the idea of comparing each arm to the best arm and based on that keeping the failure probabilities at a flat level seems transferrable to the thresholding bandit problem.
-Indeed, it might even be easier as the best arm does not have to be estimated; thus, the risk with respect to this estimate goes away.
-Instead, every arm will be compared to the threshold.
-One idea might be to compute for each arm $a$ the probability that the mean $\mu_a$ is actually on the other side of the threshold as currently suggested by $\hat{\mu}_a(t)$.
-This is independent of the other arms.
-And so a strategy might be to draw arms such that their failure probabilities are at the same level (draw whatever arm has the highest failure probability).
-We will come back to this idea in chapter 3.
-
-Using the information from the lower bound of how well any $\delta$-PAC algorithm can potentially be, the authors design algorithms matching these lower bounds.
-In the case of Top-$m$ identification, a simple application of the existing KL-LUCB algorithm works.
-In the case of best arm identification, the lower bound provides a way of calculating the optimal proportions in which the arms need to be pulled.
-Consequently, a matching algorithm can be set up so that it draws arms in these proportions, and so that it is robust against estimation errors of the plug-in estimates.
-Combining this sampling rule with an appropriate stopping rule makes for a $\delta$-PAC algorithm that matches the lower bound, where the upper bound in Theorem \ref{theorem:GarivierAndKaufmannTheorem14} matches the lower bound from Theorem \ref{theorem:GarivierKaufmannTheorem1} using equation \eqref{bre_approx}.
-
-\newpage
-
-# Extensions to the Thresholding Bandit Problem
-
-## Introduction
-
-We have introduced the thresholding bandit problem in chapter 1.
-The APT algorith described in Locatelli et al.
-(2016) is able to match a lower bound (be more specific!) given in the same paper, and has several favorable characteristics such as its overall simplicity and it being an anytime algorithm.
-However, the bounds on the expected loss assume the arms' distributions to be $R$-sub-Gaussian.
-This is reflected in the algorithm's complexity measure $H = \sum_{i=1}^K (\Delta_i^{\tau, \epsilon})^{-2}$, where $\Delta_i^{\tau,\epsilon} = |\mu_i - \tau| + \epsilon$, which -- given the known threshold $\tau \pm \epsilon$ -- only depends on the distribution's mean.
-This is appropriate for Gaussian arms with equal variances, but potentially inefficient for other kinds of distributions.
-
-In the case of Gaussian distributions with varying variances, for example, it makes sense to take the variance into account; after all, given two Gaussians with equal mean, intuitively we would prefer to get a sample from the distribution of larger variance.
-
-In the case of Gaussians, the complexity $H$ is nice also because it reflects the Kullback-Leibler divergence between two Gaussians.
-And since Bernoulli distributions are bounded on the interval $[0,1]$, they are consequently sub-Gaussian, meaning that their Kullback-Leibler divergence can be approximated by the Gaussian one.
-However, while Bernoullis are sub-Gaussian, the approximation of their divergence by the Gaussian divergence becomes less and less optimal as the parameter (and thus mean) goes to $0$ or $1$, as shown in chapter 1.
-And while online advertisements might not be an obvious use case for thresholding bandits, they are just one real life scenario dominated by Bernoulli distributions with very small parameters.
-Thus it is worthwile to adapt current solutions of the thresholding bandit problem to cases in which the Gaussian Kullback-Leibler divergence is no longer an appropriate approximation.
-
-Large motiviation for the idea of adjusting the complexity measure (and thus the algorithms) to distributions more generally based on the Kullback-Leibler divergence stems from the work discussed in chapter 2, complexity measures were defined for the pure exploration bandits in terms of the Kullback-Leibler divergence.
-Based on this, the authors were for example able to point our differences between Gaussian and Bernoulli bandits.
-We expect that results in a similar vain could be derived for thresholding bandits.
-
-To this end, in the following, we first present an extension of mean based algorithms to an algorithm that incorporates empirical variances as described in Mukherjee et al.
-(2017).
-Afterwards, we propose and discuss potential further improvements based on Kullback-Leibler divergence and Bayesian posterior distributions.
-Finally, we compare the performance of different algorithms based on simulations and real world data sets.
-
-## Variance Based Algorithms for Thresholding Bandits
-
-### Augmented-UCB Algorithm
-
-Mukherjee et al.
-(2017) propose an algorithm based on variance estimates called Augmented-UCB (AugUCB).
-The setting in which the algorithm is proposed is very similar to the setting in Locatelli et al.
-(2016).
-The algorithm itself, however, differs heavily from the APT algorithm.
-So is AugUCB for example not an anytime algorithm.
-Furthermore, arms can be deleted in every round if there are "far enough" away from the mean.
-Both the decision of which arm is played in a given round, and whether an arm is removed from the active set of arm, is based not only on the empirical mean estimate $\mu_i(t)$, but also on a term $s_i$ that is increasing linearly in the estimated standard deviation.
-While the APT algorithm plays the arm minimizing the quantity $B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t) = \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau| + \epsilon)$, AugUCB plays the arm minimizing the quantity $(\hat{\Delta}_i(t) - 2s_i)$, where $s_i$ is based on the variance estimate $\hat{v}_i$, and an exploration $\psi_m$ term linear in $T$, and an elimination parameter $\rho$ (compare Algorithm 1 in Mukherjee et al., 2017):
-
-\begin{equation*}
-s_i = \sqrt{\frac{\rho \psi_m (\hat{v}_i + 1) \log(T \epsilon_m)}{4n_i}}
-\end{equation*}
-
-Consequently, the authors also introduce complexity measures which take the variance into account.
-From Gabillon et al.
-(2011) they use $H_{\sigma, 1}= \sum_{i=1}^K \frac{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}{\Delta_i^2}$.
-Furthermore, with $\stackrel{\sim}{\Delta}_i^2 = \frac{\Delta_i^2}{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}$, and with $\stackrel{\sim}{\Delta}_{(i)}$ being an increasing ordering of $\stackrel{\sim}{\Delta}_i$, the authors define a complexity corresponding to $H_{CSAR,2}$ in Chen et al.
-(2014):
-
-\begin{equation*}
-H_{\sigma,2} = \max_{i \ in \mathcal{A}} \frac{i}{\stackrel{\sim}{\Delta}_{(i)}^2}.
-\end{equation*}
-
-While the latter complexity appears in the provided upper bound on the AugUCB algorithm's expected loss, it could be replaced by $H_{\sigma, 1}$ since $H_{\sigma, 2} \leq H_{\sigma,1}$.
-$H_{\sigma,1}$ is of course more directly comparable to the complexity $H$ that we are used to.
-
-While in the case of the APT algorithm the number of times a specific arm has been drawn $T_i$ measures how concentrated the estimated mean is around the true mean (and thus for large $T_i$ an arm is no longer drawn even if $\hat{\mu}$ is close to $\tau$); in the case of the AugUCB algorithm this is regulated by the combination of the variance estimate $\hat{v}_i$ and the exploration factor $\psi_m$, where they ensure that certain arms are no longer pulled when the algorithm is sufficiently confident in its knowledge about the true mean.
-Therefore, when using a very similar favorable event in the proof of their upper bound, Mukherjee et al.
-(2017) have to bound the probability that an an arm is not removed from the active set after the a certain number of rounds -- even though the arm is above (respectively below) the threshold.
-If this probability is low, then this means that the algorithm is able to be certain about an arm's true mean *quickly* by employing variance estimates.
-In comparison, Locatelli et al (2016) used bounds on on how often arms are drawn ($T_i$) to give a bound on the probability of the favorable event.
-In order to derive the bound, Mukherjee et al.
-(2017) use the Bernstein inequality.
-
-It has to be noted that Mukherjee et al.
-(2017) have to assume that the distributions have rewards bounded in $[0,1]$ in order to derive the bound on the probability that an arm has not been eliminated correctly in round $T_i$.
-Thus, the distributions for which their upper bound holds are a subset of the sub-Gaussian distributions considered in Locatelli et al.
-(2016).
-However, it is not that the authors need to assume that the rewards are in $[0,1]$, but this was assumed so that the variance of the distribution is in $[0,1]$.
-Thus, the upper bound holds in particular for Gaussian distributions with variance $\sigma^2 \in [0,1]$.
-
-Based on this assumption, the authors show that the probability that an arm has not been eliminated after $m_i$ rounds is given by (compare equation (2) in Mukherjee et al., 2017):
-
-\begin{equation} \label{Mukherjee2017Equation2}
-\mathbb{P}(\hat{\mu}_i > \mu_i + 2s_i) \leq \mathbb{P} (\hat{\mu}_i > \mu_i + 2\bar{s}_i) + \mathbb{P}(\hat{v}_i \geq \sigma^2_i + \sqrt{\rho \epsilon_{T_i}})
-\end{equation}
-
-Compare Mukherjee et al.
-(2017) for the notation.
-Then it becomes clear that the left part of the RHS gives the probability that the mean estimate is out of wack, while the right term gives the probability that the variance is overestimated.
-The first term is bounded by the Bernstein inequality.
-In the cumulative regret setting, there exists a similar decomposition that bounds the expected number of pulls of a suboptimal arm.
-Compare for example chapter 3.1 in "Thompson Sampling: An Asymptotically Optimal Finite Time Analysis" by Kaufmann, Korda and Munos (2012).
-There they decompose the expected number of draws of an suboptimal arm for an optimistic (UCB like) into the probability that the optimal arm's mean is underestimated, and the probability that the UCB of the suboptimal arm is still very large.
-To give bounds for UCB algorithms, it is then shown that these two terms show a certain convergence.
-Mukherjee et al.
-do similarly for their variance based algorithm in the thresholding setting.
-
-(since the AugUCB eliminates arms, it is interesting to see how it behaves when the underlying CTR changes over time...)
-
--> Happens for exponential distribution
-
-### Anytime Parameter-free Empirical Variance Guided Algorithm
-
-Another algorithm for the thresholding bandit problem is introduced in Zhong et al.
-(2017).
-Indeed, they discuss several variations of their algorithm which extend their central idea to applications in which several samples need to be pulled in a parallel and asynchronous fashion.
-An easy example known from the multi-armed bandit literature (SOURCE????!!??!?!?!) is a website where different versions are served to customers and each version is an arm in the bandit setting.
-If the feedback that is observed by the algorithm is whether or not a user makes a purchase, then it is likely that a new user arrives before the feedback for the previous user has been observed.
-The algorithm has to pull the next arm before the feedback of the previous arm has been observed.
-With their variants the authors approach this problem of having to take asynchronous and parallel actions.
-But their algorithm can also be reduced to a simpler version that can be compared directly with the problem described in Locatelli et al.
-(2016) where we assume the problem of the feedback lag away.
-
-This simpler version is the anytime parameter-free version of their Empirical Variance Guided Algorithm (EVT$_{pf}$).
-The EVT$_{pf}$ algorithm is a smart extension of the APT algorithm to an approach that takes the empirical variance of the arms into account and deduces an upper bound through Bernstein bounds.
-
-In order to describe their algorithm, we adapt a formulation used in Zhong et al.
-(2017) to describe the index used by the algorithms in a more general fashion.
-Write the index $B_i(t)$ of arm $i$ at round $t$ as previously as
-
-$$
-B_i(t) = S_i(t) D_i(t),
-$$
-
-where $D_i(t)$ is some measure of the distance between the mean $\mu_i$ or the distribution $\nu_i$ of the arm $i$ from the threshold $\tau$, while $S_i(t)$ is some confidence value.
-Thus, for the APT algorithm, if we let $\epsilon = 0$ as in Zhong et al.
-(2016), we have
-
-$$
-D_i^{APT}(t) = \hat{\Delta}_i(t) = |\hat{\mu}_i(t) - \tau| \quad \land \quad S_i^{APT}(t) = \sqrt{T_i(t)}
-$$
-
-We see that $D_i(t)$ is the probably most straightforward distance between the sample mean and the threshold, while $S_i(t)$ increases over time, as we become more confident in our sample mean, and thus ensures that we do not continue pulling the same arm forever.
-
-Based on this, we can now easily compare APT to EVT$_{pf}$ for which the index can be written as:
-
-$$
-D_i^{EVT}(t) = \hat{\Delta}_i(t) = |\hat{\mu}_i(t) - \tau| \quad \land \quad S_i^{EVT}(t) = \Big(\frac{1}{T_i(t) + \sqrt{\frac{1}{T_i(t)}}\hat{\sigma}_{i}(t)}\Big)^{-1}
-$$
-
-or equivalently as
-
-$$
-D_i^{EVT}(t) = \sqrt{\hat{\sigma}^2_{i}(t) + \hat{\Delta}_i(t)} - \hat{\sigma}_i(t) \quad \land \quad S_i^{EVT} = \sqrt{T_i(t)}
-$$
-
-We see that in both formulations either the distance term $D_i$ or the confidence term $S_i$ between the two algorithms is equivalent.
-While the empirical variance is a natural confidence measure -- and thus makes sense in the $S_i^{EVT}$ part in the first equation -- it also describes the shape of the distribution and thus is also a measure of how far the distribution (in contrast to just the mean) is away from the threshold, and thus can belong to $D_i^{EVT}$.
-We will focus on the latter formulation for the remaining paper.
-
-In comparison with the APT algorithm, the EVT$_{pf}$ algorithm adds the empirical variance into the index to measure how well we can expect the distribution (and the mean) to be seperated from the threshold; it serves as a crude measure of distance between threshold and distribution.
-We note that for a Bernoulli distributed random variable, $D_i^{EVT}$ is decreasing as the mean approaches the threshold.
-Similar should hold in general for bounded variables as the variance and the mean are linked by the distance of the mean to the bound of the support (in contrast to, for example, a normal distributed random variable where a change in the mean does not correspond to a change in the variance).
-This is important as the bounds of the EVT$_{pf}$ algorithm only hold for random variables bounded in $[0,1]$.
-
-```{r EVT_Index_Bernoulli, echo = FALSE}
-bfun <- function(mu, tau) sqrt((mu*(1-mu))^2 + abs(tau-mu)) - mu*(1-mu)
-plot(seq(0,1,0.0001), bfun(0,seq(0,1,0.0001)), type = "l",
-     xlab = "Sample Mean", ylab = "Distance $D_i(t)$", main = "Variation over tau")
-for(i in 1:length(seq(0,1,by=0.1))) {
-  lines(seq(0,1,0.0001), bfun(seq(0,1,by=0.1)[i], seq(0,1,0.0001)), 
-        col = rainbow(length(seq(0,1,by=0.1)))[i])
-}
-```
-
-By defining a new complexity measure $H^{\text{EVT}_{pf}}$ for the EVT$_{pf}$ algorithm, Zhong et al.
-(2017) are able to derive an upper bound on the expected loss of the algorithm.
-Let the complexity increase in the variance and decrease in the distance of the mean from the threshold such that
-
-$$
-H^{\text{EVT}_{pf}} = \sum_{i=1}^K h_i^{\text{EVT}_{pf}} = \sum_{i=1}^K (\sigma_i^2\Delta_i^{-2} + \Delta_i^{-1}).
-$$
-
-Then one can state the following theorem.
-
-\begin{theorem}[Theorem 5, Zhong et al., 2017] 
-\label{theorem:ZhongEtAl2017Theorem5}
-Let $K > 0$, $T > 2K$, and consider a thresholding bandit problem. Assume that all arms of the problem are bounded in $[0,1]$. Then the probability of an error is bounded as
-
-\begin{equation*}
-\mathbb{E}[L] \leq TK \exp\Big(-C\frac{T}{H^{\text{EVT}_{pf}}}\Big),
-\end{equation*}
-
-where $C$ is some positive constant.
-\end{theorem}
-
-The authors approach the proof very similarly as Locatelli et al.
-(2016) in the proof of their lower bound.
-They define favorable events that hold with large probability, make sure the same separation condition holds for them given that each arm is pulled often enough.
-Additionally to a favorable event that bounds the deviation between sample mean and population mean, they define a second event on which the sample standard deviation is close to the population standard deviation.
-This is bounded in large probability by a Bernstein inequality.
-The union of the two events then serves as the favorable event in the remainder of their proof.
-
-Given a lower bound that is also adapted to the new complexity $H^{\text{EVT}_{pf}}$, the authors show that the EVT$_pf$ algorithm is optimal.
-Furthermore, they compare their algorithms in experiments against the APT algorithm.
-The experiments use data generated from uniform distributions.
-Each experiment compares 100 arms with variances picked at random from a range of possible variances.
-Over three experiments, the range of variances is varied from small to large, where the authors expect their algorithm to show the largest advantage compared to APT on the problem with small variances.
-Interestingly, they report the largest advantage of their variance based algorithms in comparison to APT when the variances are very small; given they only consider problems bounded on a support of $[0,1]$, $\sigma_i \ll 1$.
-In this case the problem complexity $H^{\text{EVT}_{pf}}$ can be much smaller than $H^{APT}$ -- the EVT algorithm profits more from distributions that are simple to estimate in terms of their variance than the APT algorithm does.
-
-When comparing the two complexities for example for Bernoulli random variables against some fixed threshold, we see that the smaller complexity of the EVT$_{pf}$ algorithm implies in particular that EVT$_{pf}$ could be able to cope with distributions of parameter $\mu$ close to $\tau$ much better than APT.
-
-```{r Hevt_Hapt_Comparison, echo = FALSE, message = FALSE}
-hevt <- function(mu, tau) {
-  (mu*(1-mu))^2 * (abs(mu-tau))^{-2} + abs(mu-tau)^{-1}
-}
-
-hapt <- function(mu, tau) {
-  abs(mu-tau)^{-2}
-}
-
-plot(seq(0.1,0.9,0.0001), 
-     hapt(seq(0.1,0.9,0.0001), 0.5), type = "l",
-     ylim = c(0,400), ylab = "Complexity", xlab = "Bernoulli Mean",
-     main = "APT vs EVT Complexity for tau = 0.5")
-lines(c(seq(0.1,0.9,0.0001)), 
-      hevt(c(seq(0.1,0.9,0.0001)), 0.5),
-      col = "blue")
-abline(v = 0.5, lty = 2)
-```
-
-## Likelihood Ratio for Exponential Family Distributions
-
-We now present an approach that builds on the idea of the likelihood ratio statistic for hypothesis tests.
-We first present the general idea of likelihood ratio based tests, and then introduce our new algorithm for the thresholding bandit problem.
-
-### Likelihood Ratio-based Hypothesis Tests
-
-In a standard parametric testing problem, we have drawn an iid sample $x = (x_1, ..., x_T)$, where each $x_i$ is a realization from the random variable $X_i$.
-We assume that $X_i$ follows some probability distribution $Q(\theta)$ paramaterized by a vector $\theta$.
-Let $q(x;\theta)$ be the density function corresponding to the distribution.
-In a standard hypothesis test, we test whether an alternative parameterization is more likely than the parameterization given by the null hypothesis.
-That is, we test
-
-$$
-H_0: \quad \theta = \theta_{H_0} \qquad \text{vs.} \qquad H_1: \quad \theta = \theta_{H_1}
-$$
-
-In order to assess whether the $H_0$ hypothesis can be rejected, one computes the likelihood $L(x|\theta)$ of the observed sample under both parameterizations: $L_{H_0} = L(x|\theta = \theta_{H_0}) = \prod_{i=1}^T q(x_i|\theta_{H_0})$ and $L_{H_1} = L(x|\theta = \theta_{H_1}) = \prod_{i=1}^T q(x_i|\theta_{H_1})$.
-The likelihood ratio test statistic is then given as
-
-$$
-LR(\theta_{H_0}|| \theta_{H_1}) = \frac{L_{H_0}}{L_{H_1}} = \prod_{i=1}^T\frac{q(x_i|\theta_{H_0})}{ q(x_i|\theta_{H_1})}.
-$$
-The intuition behind the test of course being that, if the true parameterization is $H_1$ and not $H_0$, then the likelihood $L_{H_1}$ should be larger than $L_{H_0}$.
-A small enough likelihood ratio would thus lead us to a rejection of the null hypothesis, while a large likelihood ratio is evidence in favor of the null hypothesis.
-
-By considering $lr = -2\log(LR(\theta_{H_0}|| \theta_{H_1}))$, one has a statistic that is $\chi^2$ distributed with degrees of freedom that depend on the null and alternative hypothesis.
-Assessing whether the null hypothesis can be rejected with large confidence thus becomes straightforward.
-
-### Likelihood Ratio-based Thresholding Bandit
-
-The simple concept of the likelihood-ratio test serves as foundation for a new sampling strategy that can be applied to the thresholding bandit problem.
-In contrast to the cumulative regret problem, or even the best arm identification problem, we have some sort of null hypothesis for the distributions in the thresholding bandit problem.
-In case of no information and no observed samples, the null hypothesis might simply be that all distributions have a mean that equals the threshold.
-By observing samples, we then want to test whether the mean of the distributions is different from the threshold $\tau$ in either direction.
-Once we are sure that there is a difference, we do not want to continue to test.
-Instead, we would like to focus our sampling effort on a different arm where we are not as sure.
-The likelihood ratio quantifies how "significant"" of a difference there is between the threshold $\tau$ and the current sample mean $\hat{\mu}_i(t)$ of an arm.
-Given that we plug in the sample mean, that is, the maximum likelihood estimator for the true mean for many distributions, the likelihood ratio will be smaller than 1 and decrease in sample size even if the threshold and sample mean are constant.
-
-Due to these characteristics, the likelihood ratio can serve as a natural index for sampling strategies. Thus write as index
-
-$$
-B_i(t) = LR(\tau|| \hat{\mu}_i(t)) = \prod_{i=1}^T\frac{q(x_i|\tau)}{ q(x_i|\hat{\mu}_i(t))}
-$$
-
-and pull at round $t$ the arm $i^* = \arg \max_i B_i(t)$.
-As we described in the previous paragraph, we have $B_i(t) \leq 1$, $t \uparrow \rightarrow B_i(t) \downarrow$, and $|\hat{\mu}_i(t) - \tau| \uparrow \rightarrow B_i(t) \downarrow$.
-Consequently, by choosing the arm that maximizes $B_i(t)$, we choose an arm for which we either have not collected many samples, or where the sample mean is close to the threshold $\tau$.
-In this sense, a strategy based on the likelihood ratio is of course very reminiscient of the index employed by the APT algorithm.
-Indeed, assuming the samples are normally distributed with the same variance for the distribution $\nu_i$ under both $H_0$ and $H_1$, then $-\log(LR(\tau||\hat{\mu}_i(t)))$ equals the index in APT.
-Why then would one use the likelihood based strategy?
-
-Given that the APT index and the likelihood-ratio based index are only equivalent for normally distributed random variables with fixed standard deviation, the new strategy promises efficiency improvements whenever the true distribution is known and different from the normal distribution.
-The most important example are Bernoulli arms with small means as discussed before.
-Here, it is also easy to assume that the true distribution is known upfront.
-Similarly, the likelihood ratio statistic can be used for other univariate distributions of the exponential family.
-But we also propose a version for the Normal distribution with unknown mean.
-
-We now focus on the case where the distributions $\nu_{\theta_1}, ..., \nu_{\theta_K}$ are all the same canonical exponential family of distributions with scalar parameter $\theta_i \in \Theta$.
-The probability density function of the absolutely continuous distribution $\nu_{\theta_i}$ with regard to a dominating measure $\rho$ on $\mathbb{R}$ is given by $q(x|\theta) = h(x) \exp(T(x)\theta - b(\theta))$.
-As described in Cappé et al.
-(2013), citing Lehmann and Casella (1998), the derivative $b'(\theta)$ of $b(\theta)$ is an increasing continuous function such that the expected value $\mathbb{E}(\nu_{\theta}) = b'(\theta)$ for all $\theta \in \Theta$.
-Given that $b'(x)$ is strictly convex, we have a one-to-one relation between $b'(\theta)$ and $\mathbb{E}(\nu_{\theta})$ through the continuous inverse $b'^{-1}(\theta)$.
-Consequently, one can just as well parameterize the distribution its mean $\mu = \mathbb{\nu_{\theta}}$ and write $\nu_{b'^{-1}(\mu)}$ with the probability density function
-
-$$
-q(x|b'^{-1}(\mu)) = h(x) \exp(T(x) b'^{-1}(\mu) - b(b'^{-1}(\mu))).
-$$
-
-This lets us write the likelihood ratio for the exponential family distributions as
-
-$$
-LR(b'^{-1}(\mu_0)||b'^{-1}(\mu_1)) = \prod_{i=1}^n \frac{\exp(T(x_i) b'^{-1}(\mu_0) - b(b'^{-1}(\mu_0)))}{\exp(T(x_i) b'^{-1}(\mu_1) - b(b'^{-1}(\mu_1)))}
-$$
-
-or if we write it as negative log-likelihood ratio:
-
-$$
--\log(LR) = n\Big(b\big(b'^{-1}(\mu_0)) - b(b'^{-1}(\mu_1)\big)\Big) - \Big(b'^{-1}(\mu_0)-b'^{-1}(\mu_1)\Big)\sum_{i=1}^nT(x_i)
-$$
-
-As we will see now, this statistic is easily derived for many specific distributions.
-
-#### Example 1: Bernoulli Distribution
-
-We have $T(x_i) = x_i$, $\theta = \log(\mu/(1-\mu))$, $\Theta = (0,1)$, $b(\theta) = \log(1+\exp(\theta))$, and $\mu \in (0,1)$. Then $b'(\theta) = \mu$, and we can write
-
-$$
--\log(LR(\mu_0||\mu_1)) = n(\log\Big(\frac{1-\mu_0}{1-\mu_1}\Big)) - \Big(\log(\frac{\mu_0}{1-\mu_0}) - \log(\frac{\mu_1}{1-\mu_1})\Big)\sum_{i=1}^{n}x_i = (1-\hat{\mu})\log\Big(\frac{1-\mu_1}{1-\mu_0}\Big) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0})
-$$
-
-We observe that, if we let $\mu_0 = \tau$ and $\mu_1 = \hat{\mu}$, then
-
-$$
--\log(LR(\tau||\hat{\mu})) = KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = d(\hat{\mu},\tau)
-$$
-
-#### Example 2: Poisson Distribution
-
-We have $T(x_i) = x_i$, $\theta = \log(\mu)$, $\Theta = \mathbb{R}$, $b(\theta) = \exp(\theta)$, and $\mu \in (0, +\infty)$. Then $b'(\theta) = \mu$, and we can write:
-
-$$
--\log(LR(\mu_0||\mu_1)) = n(\mu_0 - \mu_1) - (\log(\mu_0) - \log(\mu_1))\sum_{i=1}^n x_i = (\mu_0 - \mu_1) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}\Big)
-$$
-
-We observe that, if we let $\mu_0 = \tau$ and $\mu_1 = \hat{\mu}$, then
-
-$$
--\log(LR(\tau||\hat{\mu})) = KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = d(\hat{\mu},\tau) = (\tau - \hat{\mu}) + \hat{\mu}\log\Big(\frac{\hat{\mu}}{\tau}\Big)
-$$
-
-#### Example 3: Normal distributions with known variance $\sigma^2$
-
-We have $T(x_i) = x_i$, $\theta = \mu/\sigma^2$, $\Theta = \mathbb{R}$, $b(\theta) = \sigma^2\theta^2/2$, $\mu \in \mathbb{R}$. Then $b'(\theta) = \mu$, and we can write
-
-$$
--\log(LR(\mu_0||\mu_1)) = n (\frac{\mu_0^2}{2\sigma^2} - \frac{\mu_1^2}{2\sigma^2}) - (\frac{\mu_0}{\sigma^2} - \frac{\mu_1}{\sigma^2})\sum_{i=1}^nx_i = \frac{1}{2\sigma^2}\Big(\mu_0^2-\mu_1^2 - 2\mu_0\hat{\mu} + 2\mu_1\hat{\mu}\Big)
-$$
-
-And again, if we let $\mu_1 = \hat{\mu}$ and $\mu_0 = \tau$, then
-
-$$
--\log(LR(\tau||\hat{\mu})) = KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = d(\hat{\mu},\tau) = \frac{(\hat{\mu} - \tau)^2}{2\sigma^2}.
-$$
-
-# Experiments
-
-## Real Data
-
-We show two experiments that were performed on real data.
-While most papers in the multi-armed bandit literature resort to synthetic data to assess the performance of algorithms -- just as we have done in the previous chapter -- we have tried to acquire real world data.
-This data is what bandit algorithms are used for in practice, and does not fulfill the standard independence and identical distribution assumptions as nicely.
-The real data thus can be considered a first robustness test for the algorithms.
-
-### The Data Set
-
-The data have been collected by the German ecommerce company [Amorelie](https://amorelie.de) as part of standard website performance tracking.
-For 197 selected products, we have the number of users visiting each product's detail page (PDP) at a given minute.
-The data set we use here has been collected during the entire month of November 2016.
-It can be considered time series data collected at minutely frequency.
-Thus the data contain 43200 observations per product, and overall 8510400 observations.
-
-Given that we want to run an offline comparison of bandit algorithms, it is important to have at each time point an observation for each arm.
-Given that, it is easy to evaluate the perfomance of algorithms that make different decisions at different point in times and thus do not observe the same samples.
-By having an observation for each arm at any given time point, each algorithm had at least the opportunity to observe a certain sample.
-Other papers (CITE YAHOO!) have solved this problem by using a sample drawn uniformly during for example an A/B test.
-Then, if the next observation in the sample is not from the same arm that the algorithm would like to draw from, observations are discarded until the next observation from the selected arm.
-
-The choice of having basically multiple time series data as the sample leads to a simple way of running the algorithms just as often on the data as for simulated data.
-In particular, the goal is to perform 5000 runs over the sample to confidently assess the performance.
-Since we wanted to preserve the potential time dependency of the data, a simple resampling of the data was not an option to create the needed 5000 variations of the sample.
-Thus what we did instead was a form of time series cross validation.
-To preserve the autocorrelation, one can create different samples of $X$ observations by sliding a window of size $X$ over the time series.
-Moving the window one period (in our case minute) at a time, one ensures that no sample shares start and end observation with another sample.
-In particular, this means for a given bandit strategy and two samples that the observations that the algorithm collects as feedback during the two initialization phases differ from sample to sample and are never the same.
-This is because during initialization every strategy pulls arms $1, ..., K$ once in this order.
-
-While the data is count data (the number of visits to a PDP during a given minute), we binarize the data by applying a certain threshold.
-If the counts is above this threshold, the observation becomes a $1$, else $0$.
-Thus we have a binary time series of length 43200 for each of the 197 products.
-Given that the number of visitors that come to a given PDP is likely to vary by time of day and by day, and in general over time, we expect that the mean of the time series to not be stable over time.
-For example, less visitors will come during night than during evening, thus leading to a decreasein the average.
-On the other hand, more users may visit the site during a weekend, thus leading to a spike on Saturdays and Sundays.
-Because of the latter time dependency, it is best practice to run online A/B tests for at least a week, or an integer multiple of weeks, so as to take into account the weekly seasonality in the time series.
-For this reason, the experiments we present below were run on $60 \cdot 24 \cdot 7 = 10080$ observations for each arm, so as to have a sample for one full week.
-
-We can look at summary statistics for the sample means of the 197 products over the month of November to get a first idea of the data we are dealing with.
-We see that most products have a low mean, which is very common also for actual conversion rate data that would be tested with A/B tests or multi-armed bandits.
-Yet the sample of products contains a few outliers with very large view rates, with a maximum rate of 78%.
-If we used a threshold $\gamma$ to binarize the count data, then this means that on average every fourth minute the count of visitors was below $\gamma$ for this product.
-On the other hand, we conclude that using thresholding bandit strategies to test the products against a threshold of for example $\tau = \frac{2}{60} = 0.333$ or $\tau = \frac{5}{60} = 0.083$ is likely to create more complex problems than a threshold of, say, $\tau = \frac{15}{60} = 0.25$ would.
-
-```{r amo_data_summary, echo = FALSE, message = FALSE}
-load(file = "/Users/timradtke/Desktop/thesis_data/pv_summary.Rda")
-
-knitr::kable(pv_summary, digits = 3, col.names = c("Mean", "Minimum", "25% Quantile", "Median", "75% Quantile", "Maximum"), caption = "Summary Statistics for View Rates of 197 Products")
-```
-
-### Experiment 1: $\tau = \frac{2}{60}$
-
-In this first experiment, we pick ten arms randomly from the set of 197 arms.
-The experiment is run on these 10 arms with a budget of $T=10080$ samples during each of the $5000$ iterations for which we repeat the experiment.
-Given the time series cross-validation idea described above, this means that in total, $15080$ observations of the available $43200$ available observations per arm are used in training.
-In the thresholding bandit problem, we classify arms as below or above a threshold.
-Thus we can evaluate the strategies also based on whether their classifications are correct in a holdout sample.
-As this holdout sample, we can use the 10080 observations in our data set that follow the first 15080 observations used in training.
-In the table below, we present the count rates of the ten products for both training and test samples.
-
-```{r experiment1_arm_means, echo = FALSE, message = FALSE}
-
-load("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/data_amo3_mean_firsthalf.Rda")
-load("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/data_amo3_mean_secondhalf.Rda")
-
-Training <- data_amo3_mean_firsthalf
-Test <- data_amo3_mean_secondhalf
-tau <- 2/60
-TrainingMinusTau <- Training - tau
-
-knitr::kable(rbind(Training, Test, TrainingMinusTau), digits = 3, col.names = names(data_amo3_mean_firsthalf),
-             caption = "Count rates for ten products for both training and test sample.")
-
-```
-
-We see that while the rates do vary across samples, they are relatively stable which is likely due to the fact that the samples come from an entire week's worth of observations.
-In particular, since we test against a threshold of $\tau = \frac{2}{60} = 0.333$ in this experiment, the classifications of arms do not differ across training and test data.
-A correct classification after training will be correct in the test set.
-For the rest of the analysis, we thus evaluate the performance using the training rates.
-
-When comparing the rates against the threshold, we see that three products are below the already small threshold.
-Product $V64$ seems to be especially difficult to classify correctly, even without time dependency.
-On the other hand, arms $V119$ and $V118$ should be much easier than the rest.
-
-In order to visualize the time dependency that we expect for our samples, we plot a moving average of the mean of the time series for the first week of data.
-To remove the daily seasonality, we select a moving average window of $60\cdot24 = 1440$ observations.
-To make the time dependency even more obvious, we contrast the actual data against synthetic data generated using the sample means of the actual data.
-
-The graph again underlines that arm $V64$ is likely to be very difficult to classify given that it's moving average even crosses the threshold twice.
-The same is true for arm $V139$, which is not visible when considering the overall mean alone.
-Furthermore, arms $V159$ and $V189$ come very close to the threshold at times.
-
-```{r, echo = FALSE, message = FALSE}
-library(zoo)
-library(tidyr)
-library(dplyr)
-library(ggplot2)
-load("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/data_amo3_wide.Rda")
-
-real_daily <- data.frame(index = 1:8641,
-                                lapply(data_amo3_wide[1:10080,], FUN = rollapply, 
-                                       width = 24*60, mean)) %>%
-  gather(arm, mean, -index) %>%
-  mutate(source = rep("Real", 86410))
-
-real_means <- colMeans(data_amo3_wide[1:10080,])
-tau_amo3 <- 2/60
-
-syn_data <- data.frame(rep(NA, times = 10080))
-set.seed(124632728)
-for(i in 1:length(real_means)) {
-  syn_data[[i]] <- as.numeric(purrr::rbernoulli(10080, p  = real_means[i]))
-}
-names(syn_data) <- names(data_amo3_wide)
-
-syn_daily <- data.frame(source = rep("Synthetic", 8641),
-                        index = 1:8641,
-                        lapply(syn_data, FUN = zoo::rollapply, width = 24*60, mean)) %>%
-  gather(arm, mean, -index, -source)
-
-rbind(real_daily, syn_daily) %>%
-  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
-  geom_line(size = 0.4) +
-  geom_hline(aes(yintercept = tau_amo3), linetype = 2) +
-  facet_grid(.~source) + 
-  labs(title = "Moving average over 24*60 observations (1 day)", 
-       subtitle = "Horizontal bar indicates the threshold.", 
-       x = "Index", y = "One day moving average")
-```
-
-### Experiment 2: $\tau = \frac{5}{60}$

### 2017-08-25 Thesis/Draft.Rmd
Add Introduction

@@
    - \usepackage{bbm}
+   - \usepackage[lined,boxed]{algorithm2e}
    - \newtheorem{theorem}{Theorem}
@@
     toc: true
-    toc_depth: 3
+    toc_depth: 2
     #latex_engine: xelatex
@@
 
+\newpage
+
+"In general, we look for a new law by the following process: First we guess it.
+Then we – now don't laugh, that's really true.
+Then we compute the consequences of the guess to see what, if this is right, if this law that we guessed is right, to see what it would imply.
+And then we compare the computation results to nature, or we say compare to experiment or experience, compare it directly with observations to see if it works.
+If it disagrees with experiment, it's wrong.
+In that simple statement is the key to science.
+It doesn't make any difference how beautiful your guess is, it doesn't make any difference how smart you are, who made the guess, or what his name is.
+If it disagrees with experiment, it's wrong.
+That's all there is to it."
+
+- Richard Feynman in *Richard Feynman Messenger Lectures at Cornell University: The Character of Physical Law. Chapter 7, Seeking New Laws*.
+
+\newpage
+
+# Abbreviations
+
+Kullback-Leibler divergence between distributions $\nu_i$ and $\nu_j$: $\KL(\nu_i||\nu_j)$.
+
+Binary relative entropy: $d(x,y) := x \log(x/y) + (1-x) \log((1-x)/(1-y))$, where $d(0,0) = d(1,1) = 0$.
+
+Kullback-Leibler divergence for two Bernoulli distributions parameterized by their means $\mu_i$ and $\mu_j$: $KL_{Ber}(\nu_i||\nu_j) = d(\mu_i, \mu_j)$.
+
+\newpage
+
+# Introduction to Sequential Sampling and Multi-Armed Bandits
+
+The thesis at hand joins the ranks of a large literature concerned with the general problem of sequential sampling.
+One is familiar with the idea of "batch sampling", where the entire sample is gathered first and analyzed only after the last sample has become available.
+However, as noted in Chernoff (1958), many situations arise in which one would like to gather feedback from samples as they are drawn so as to influence the choice of the next sample.
+The two fundamental characteristics of the latter sampling process are that it is sequential and adaptive.
+Since observations are drawn in sequence, one has a chance to observe the observations drawn so far in order to adapt the decision of what sample one would like to observe next.
+
+This makes sequential sampling especially relevant in situations where there is a inherent cost to drawing an observation.
+The classical example that of clinical trials in which a researcher tests two drugs on patients to observe which one performs better.
+Not only is it difficult to gather patients, but also one would like to adapt the sampling such that as soon as possible more patients receive the better drug so that more patients are cured.
+As noted in Cappé et al.
+(2013), this example dates back to Thompson (1933, 1935).
+Such problems are known as multi-armed bandit problems in which the sampling is adapted so as to minimize the cumulative regret: In the case of the drug tests, one would like to sample the two drugs in a way to find the best drug as soon as possible and then to test this drug more and more often and more often than the worse drug.
+This would lead to cumulatively more healthy patients then when both drugs are tested uniformly and thus minimize the regret from treating a patient with an ineffective drug.
+
+Instead of drugs, can consider two or more unknown distributions (which we call arms in the multi-armed bandit problem).
+These distributions have different means, and one can draw samples sequentially from the distributions in order to estimate their means.
+One would like to play the distribution with the highest mean to minimize the cumulative regret measure.
+How can we organize the sampling in order to achieve this goal?
+
+While Gittins (1979) presents an Bayesian-optimal solution, the Upper-Confidence Bound algorithms pioneered by Agrawal (1995) and Auer, Cesa-Bianchi and Fischer (2002) lead to a blooming literature on multi-armed bandit problems that has been picked up to solve modern problems in website and advertising optimization, where advertisers try to allocate their advertising optimally so as to reduce regret from showing poorly converting advertisements.
+Several algorithms as the KL-UCB algorithm based on Kullback-Leibler divergence upper confidence intervals (Cappé et al., 2013) or the Bayes-UCB algorithm (Kaufmann et al., 2012)  have followed and been shown to be optimal as they reach the lower bound introduced in Lai and Robbins (1985) and Burnetas and Katehakis (1996).
+
+These algorithms have in common that they compute after any sample an index for each of the unknown distributions.
+This index is based solely on the past (observed) data, and then used to pick the distribution from which the next observation should be drawn.
+Using these indexes, the algorithms can sequentially sample and adapt the future strategies to observations as they are gathered.
+
+Other algorithms based on indices can be used on related problems.
+Instead of minimizing cumulative regret, it might be more interesting to find the best arm, that is, the distribution with the largest mean, with as few samples as possible and with confidence as large as possible.
+This is particularly useful when there is not necessarily a cost from initially picking a lower mean, but when drawing any sample is costly, and one needs to explore the distributions as efficiently as possible.
+The need for strategies other than uniform sampling arises: Do not continue to sample distributions that we are confident about.
+As such, the best arm identification problem is very similar to the problem faced in Bayesian Optimization: Training large neural networks is costly in terms of time and computation, and so the parameter space needs to be explored with as few samples as possible.
+(Zhang et al., 2017; Brochu et al., 2010).
+
+The problem of best arm identification is very related to statistical hypothesis testing as noted by Chernoff (1958) since in the end, one has to make a decision about how the means of distributions relate to each other.
+The main difference of course being that the sampling procedure becomes integrated into the evaluation of the distributions.
+Given the focus on exploration, the problem is usually described with a loss function different from cumulative regret.
+Audibert et al.
+(2010) introduce a soft measure called *simple regret* based on which they describe UCB policies.
+Other authors investigate hard, binary measures that are equal to 1 when the best arm has not been identified (Russo, 2016; Garivier and Kaufmann, 2016).
+These binary measures correspond to the probability of the identified arm being the best, and thus inherently related to hypothesis testing.
+The problem of best arm identification can readily be extended to the so called Top-$m$ problem of identifying the best $m$ of $K$ arms (Kaufmann and Kalyanakrishnan, 2013; Kaufmann et al.
+2016).
+
+In this thesis, we consider the thresholding bandit problem.
+Instead of identifying the best $m$ out of $K$ arms, one aims to find all out of $K$ distributions that have a mean larger than a threshold fixed upfront.
+In the form described in Locatelli et al.
+(2016), algorithms in the thresholding bandit problem are evaluated against a binary loss function penalizing whenever an arm has not been classified correctly as being above the threshold and thus focus on exploration similar to algorithms employed for best arm identification.
+Indeed, Locatelli et al.
+(2016) show how their thresholding algorithm can be used for best arm identification when the mean of the best arm is known upfront.
+
+In the following, we first present the thresholding bandit problem in detail.
+To then extend upon the algorithm proposed by Locatelli et al.
+(2016), we first explore how the Kullback-Leibler divergence has been employed in the best arm identification literature by Garivier and Kaufmann (2016) and Kaufmann et al.
+(2016).
+We shortly describe two variance based algorithms for the thresholding bandit problem introduced in Mukherjee et al.
+(2017) and Zhang et al.
+(2017), before introducing the new Simple Likelihood Ratio algorithm.
+We end with experiments to examine the performance of different algorithms.
+
+\newpage
+
 # Thresholding Bandit Problem
@@
 (2016) can be considered a variant of a variant.
-It can be framed into the wider literature of *Pure Exploration* multi-armed bandit problems.
+It can be framed inside of the wider literature of *Pure Exploration* multi-armed bandit problems.
 In particular, it shares characteristics with the *Top-$m$* problem.
@@
 In any case, the problem boils down to the following.
-As standard in multi-armed bandit problems, we have $K$ arms $\mathcal{A} = \{1, \dots K\}$.
+As usual in multi-armed bandit problems, we have $K$ arms $\mathcal{A} = \{1, \dots K\}$.
 We can pull arm $k$ at time $t$ to collect feedback in form of the random variable $X_{k,t}$ which is distributed according to the arm's distribution $\nu_k$.
@@
 Indeed, in the thresholding problem, the difficulty of the problem naturally depends on how close (the means of the) distributions are to the fixed threshold.
-Intuitively, the closer a mean $\mu_i$ is to the threshold $\tau$, the more difficult it will be to distinguish the two successfully based on samples from the distribution $\nu_i$.
-For the case of the sub-Gaussian distributions, a natural measure of this distance is given by simply $\Delta_i = |\tau - \mu_i| + \epsilon$, where $\epsilon$ defines a $2\epsilon$ interval around the threshold $\tau$ in which we allow ourselves to make a mistake at no cost.
-
-If we extend this idea to the set of arms $i \in \{1,...,K\}$ of a given bandit problem, a natural measure of the overall diffulty of the problem, or the problem's complexity, might be given by $H = \sum_{i=1}^{K} \Delta_i^{-2}$.
-In particular, it shows that just adding additional arms leads to an increase in complexity (since we need to sample more of them), just as smaller $\Delta_i$ will increase the complexity as arms become harder to classify.
-(WHERE DOES THIS COMPLEXITY ORIGINALLY COME FROM?)
+Intuitively, the closer a mean $\mu_i$ is to the threshold $\tau$, the more difficult it is to distinguish the two successfully based on samples from the distribution $\nu_i$.
+A straightforward measure of this distance is given by $\Delta_i = |\tau - \mu_i| + \epsilon$, where $\epsilon$ defines a $2\epsilon$ interval around the threshold $\tau$ in which we allow ourselves to make a mistake at no cost.
+In the case of sub-Gaussian distributions, this distance is not only simple but can be interpreted very naturally as we will come to understand later.
+
+If we extend this idea to the set of arms $i \in \{1,...,K\}$ in a given bandit problem, a measure of the overall diffulty of the problem, or the problem's complexity, might be given by $H = \sum_{i=1}^{K} \Delta_i^{-2}$.
+In particular, it shows that just adding additional arms leads to an increase in complexity (since we need a larger budget to sample each arm the same number of times as before).
+Likewise, a smaller $\Delta_i$ increases the complexity as arms become harder to classify.
+Choosing the complexity measure in this way fits the distance measure $\Delta_i$ and turn out to be useful in the proof of an upper bound for the APT algorithm presented in Locatelli et al.
+(2016).
 
@@
 The notion of regret considered in the thresholding bandit, however, is more akin to the simple regret in pure exploration bandits or the error probability in sequential hypothesis testing.
-Indeed, one can most easily describe the regret in the thresholding case as the probability of making a misclassification of any arm.
-Or, more rigorously, let us define the set of all arms with mean larger than the threshold, $\mathcal{S}_\tau = \{i \in \mathcal{A}: \mu_i \geq \tau\}$.
+Indeed, one can most easily describe the regret in the thresholding case as the probability of misclassifying any arm.
+Or, more rigorously, define the set of all arms with mean larger than the threshold, $\mathcal{S}_\tau = \{i \in \mathcal{A}: \mu_i \geq \tau\}$.
 Consequently, $\mathcal{S}_\tau^C = \{i \in \mathcal{A}: \mu_i < \tau\}$.
@@
 
-From there, it is natural to define the expected regret/loss as $\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \land (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset))$.
+Now, the expected regret/loss is defined as $\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \land (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset))$.
 This, of course, is the mentioned probability of making a mistake.
-
-ADD REMARK ON WHAT THIS IMPLIES WITH REGARD TO THE MEANS
 
@@
 At this point, we have defined the fixed budget thresholding bandit setup for any algorithm in the case of sub-Gaussian distributions.
-We thus proceed to describe the algorithm proposed in Locatelli et al.
+We thus proceed to describe the APT algorithm proposed in Locatelli et al.
 (2016).
@@
 ## The APT Algorithm
+
+\IncMargin{1em}
+\begin{algorithm}
+\SetKwData{Left}{left}\SetKwData{This}{this}\SetKwData{Up}{up}
+\SetKwFunction{Union}{Union}\SetKwFunction{FindCompress}{FindCompress}
+\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
+\Input{$\tau$, $\epsilon$}
+\Output{$\hat{S}_{\tau} = \{k: \hat{\mu}_k(T) \geq \tau\}$}
+\BlankLine
+\emph{Pull each arm once}\;
+\For{$t = K+1$ \KwTo $T$}{
+  \emph{Pull arm $I_t = \arg \min_{k\leq K} B_k^{APT}(t) = \sqrt{T_k(t)} \sqrt{|\hat{\mu}_i(t) - \tau|+\epsilon}$}\;
+  \emph{Observe reward $X \sim \nu_{I_t}$}\;
+}
+\caption{Anytime Parameter-free Thresholding Algorithm (Locatelli et al., 2016)}\label{algo_apt}
+\end{algorithm}\DecMargin{1em}
 
@@
 From the general setup, we already know how the algorithm will end.
-After it has drawn $T$ samples, the algorithm makes its decision of which arms to include in the return sets solely on basis of the empirical means $\hat{\mu}_i(T)$ estimated based on the samples drawn until time $T$.
-Furthermore, the threshold and interval around the threshold were fixed upfront and serve as argument to the algorithm: $(\tau, \epsilon)$.
+After it has drawn $T$ samples, the algorithm makes a decision of which arms to include in the return sets on basis of the empirical means $\hat{\mu}_i(T)$ estimated based on the samples drawn until time $T$.
+Furthermore, the threshold and interval around the threshold are fixed upfront and serve as argument to the algorithm: $(\tau, \epsilon)$.
 For a given arm $i$ and a given time $t$, we let $T_i(t)$ represent the number of samples drawn from arm $i$ until time $t$ (including).
-Consequently, the empirical mean of arm $i$ at time $t$ is given by $\mu_i = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}$ where $X_{i,s}$ is the feedback sampled from distribution $\nu_i$ when the arm is pulled for the $s$-th time.
+Consequently, the empirical mean of arm $i$ at time $t$ is given by $\hat{\mu}_i(t) = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}$ where $X_{i,s}$ is the feedback sampled from distribution $\nu_i$ when the arm is pulled for the $s$-th time.
 
@@
 In this way, the algorithm tries to distribute the budget $T$ over all arms so as to define a sampling rule optimizing the confidence of the final decision.
-This is Glivenko-Cantelli and the CLT making sure $B_i(t+1)$ is not degenerate.
-(?)
 
@@
 This, for example, is the case for Bernoulli distributions at very small parameters $\mu$.
-By looking at the graphical examples below it becomes obvious that the Kullback-Leibler divergence of Bernoullis starts to lose any similarity to the plain quadratic approximation.
-The second graph then shows that the actual Kullback-Leibler divergence of Bernoullis also has lost any symmetry over this range of parameter values.
-Given that Bernoulli distributions with very small parameter values arise naturally in many applications in website optimization and advertising click-through modeling, there is a need to tackle this problem.
-
-Refer also to page 6 in Kaufmann et al. (2016): "This information-theoretic lower bound permits to interpret the quantity $H(\nu)$ defined in (2) as a subgaussian approximation".
+By looking at the graphical examples below it becomes obvious that the Kullback-Leibler divergence between Bernoulli distributions starts to lose any similarity to the quadratic approximation.
+The second graph then shows that the actual Kullback-Leibler divergence of Bernoulli distributions loses any symmetry over this range of parameter values.
+Given that Bernoulli distributions with very small parameter values arise naturally in many applications in website optimization, advertising click-through modeling, or anomaly detection in time series, there is a need to tackle this problem.
+
+Refer also to page 6 in Kaufmann et al.
+(2016): "This information-theoretic lower bound permits to interpret the quantity $H(\nu)$ defined in (2) as a subgaussian approximation".
+In the case of Normal distributions with known and equal mean, it holds that the Kullback-Leibler divergence between $\nu_i$ and $\nu_j$, parameterized by $\mu_i$ and $\mu_j$, can be written as
+
+$$
+\KL_{Normal}(\nu_i || \nu_j) = 2(\mu_i - \mu_j)^2.
+$$
+
+Writing $\mu_j = \tau$ and $\epsilon = 0$, we see that the APT algorithm essentially measures the KL-divergence between two Normal distributions.
+For two Bernoulli distributions $\nu_i$ and $\nu_j$, parameterized by $\mu_i$ and $\mu_j=\tau$, we write
+
+$$
+\KL_{Ber}(\nu_i||\nu_j) = \mu_i \log(\frac{\mu_i}{\tau}) + (1-\mu_i) \log(\frac{1-\mu_i}{1-\tau})
+$$
+
+In the case of $\tau = 0.5$, the latter KL-divergence is symmetric in its first argument, and thus can be well approximated by Pinsker's inequality:
+
+$$
+\KL_{Ber}(\nu_i||\nu_j) \geq 2(\mu_i - \tau)^2.
+$$
+
+This shows how the distance measure used in the APT algorithm, and consequently the complexity $H$, is a useful approximation of the KL-divergence for sub-Gaussian distributions.
+However, this approximation suffers as the distributions less and less similar to Gaussian distributions.
+Thus similarly to how UCB algorithms in the cumulative regret setting have been extended to KL-UCB algorithms (compare Cappé et al., 2013), also the APT algorithm offers room for improvement.
 
@@
 Then, in chapter 3, we will come back to the problem of using the Kullback-Leibler divergence in the thresholding bandit setting.
+To conclude chapter 1, we proof the lower bound and upper bound for the APT algorithm as presented Theorem 1 and Theorem 2 in Locatelli et al.
+(2016).
 
@@
 
-## Upper Bound: Theorem and Proof
+## Upper Bound on Expected Loss of APT
 
@@
 
-*Proof of Theorem \ref{theorem:LocatelliTheorem4}:* To prove above theorem, we first define a favorable event $\xi$ on which we hope
-to make a loss with only a small probability. Indeed, it is the event for which
-we want to upper bound the expected loss. As we want to find an upper bound for
-the expected loss of the APT algorithm, the event corresponds to the decision
-made by it.
-Given that the APT algorithm's sampling rule and final decision is based on the empirical mean of each arm, it will have low expected regret, if it finds empirical mean estimates $\hat{\mu}_i(t) = \frac{1}{s} \sum_{t=1}^s X_{i,t}$
-that are close to the true means $\mu_i$ of the arms. Then, we would
-expect arms with $\hat{\mu}_i(T) > \tau + \epsilon$ to be classified correctly, and
-arms with $\hat{\mu}_i(T) < \tau - \epsilon$ to be rejected.
-
-Indeed, we have $\mathbb{E}(\mathcal{L}(T)) = P(S_{\tau + \epsilon} \cap
-\hat{S}_\tau^C \neq \emptyset \lor S_{\tau-\epsilon}^C \cap \hat{S}_{\tau} \neq
-\emptyset)$. But this just corresponds to $P(\{\exists i: ((\mu_i <
-\tau-\epsilon) \land(\hat{\mu}_i \geq \tau)) \lor ((\mu_i > \tau + \epsilon)
-\land (\hat{\mu}_i < \tau)))$. Each of the two $(...)\lor(...)$ conditions
-corresponds to $| \hat{\mu}_i - \mu_i | \geq \epsilon$. It follows that the
-expected loss can be rewritten as: $\mathbb{E}(\mathcal{L}(T)) = P(\exists i,
-\exists s: |\hat{\mu}_{i,s} - \mu_i | \geq \epsilon) = P(\xi^C)$. This is
-exactly the probability of classifying at least one arm incorrectly which
-results in a loss of size 1.
-
-Thus we define as the favorable event as:
-
-\begin{equation} 
-\xi = \{\forall i, \forall s: | \hat{\mu}_{i,s} - \mu_i | \leq
-\epsilon\} 
-\end{equation}
-
-Furthermore, if we write $\xi_{i,s} = \{ |\hat{\mu}_{i,s}-\mu_i | \leq \epsilon
-\}$, then the following holds by a union bound.
-
-\begin{equation} 
-P(\xi) = P(\cap_i \cap_s \xi_{i,s}) = 1 - P(\cup_i \cup_s
-\xi_{i,s}^C) \geq 1 - \sum_i \sum_s P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon)
-\label{theorem2_prob_fav_event} 
-\end{equation}
-
-Furthermore, for any $i \in \{1, \dots, K\}$, for any $s \in \{1, \dots,
-T(i)\}$, with $X_{it}$ being the random sample from the R-sub-Gaussian
-distribution $v_i$ at time $t$:
-
-\begin{equation} 
-P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon) = P(| (\frac{1}{s}
-\sum_{t=1}^{s} X_{it} - \mu_i) | \geq \epsilon) = P(| \sum_{t=1}^{s} (X_{it} -
-\mu_i) | \geq s \epsilon) 
-\end{equation}
-
-where the latter can be bounded by a Hoeffding inequality:
-
-\begin{equation} 
-P(| \sum_{t=1}^{s} (X_{it} - \mu_i) | \geq s \epsilon) \leq
-2\exp (-\frac{\epsilon^2 s}{2 R^2}) \label{theorem2_hoeffding} 
-\end{equation}
-
-The Hoeffding inequality as used here is as follows (compare chapter 2.4 in [David Pollard (2015)](http://www.stat.yale.edu/~pollard/Books/Mini/Basic.pdf)):
-
-\begin{lemma}[Hoeffding's Inequality] \label{lemma:HoeffdingInequality}
-Consider $X_1, \dots, X_T$ independent random variables from R-sub-Gaussian distributions $\nu_i$ with mean $\mu_i$. Then, for any $\epsilon > 0$,
-
-\begin{equation*}
-\mathbb{P} \Big( | \sum_{i = 1}^T (X_i - \mu_i) | \geq \epsilon \Big) \leq 2\exp \Big(\frac{-\epsilon^2}{2T R^2}\Big).
-\end{equation*}
-\end{lemma}
-
-Plugging equation \eqref{theorem2_hoeffding} back into equation \eqref{theorem2_prob_fav_event},
-we get:
-\begin{equation}
-P(\xi) \geq 1 - \sum_i \sum_s P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon) \geq 1 - 2 \sum_i \sum_s \exp (-\frac{\epsilon^2 s}{2 R^2})
-\end{equation}
-
-Now, in order to match the performance of the lower bound on the expected loss derived in Theorem \ref{theorem:Locatelli2016Theorem1}, we will choose $\epsilon = \sqrt{\frac{T \delta^2}{Hs}}$. Thus:
-
-\begin{equation}
-P(\xi) \geq 1 - 2 \sum_i \sum_s \exp (-\frac{\epsilon^2 s}{2 R^2}) = 1 - 2 \sum_i \sum_s \exp (-\frac{T \delta^2}{2 R^2 H}) \geq 1 - TK \exp(-\frac{T\delta^2}{2R^2H})
-\end{equation}
-
-Thus, we do not exactly get the bound from Locatelli et al. (2016) because we used the Hoeffding inequality instead of the martingale bound; but the the method should be clear.
-
-What is left now is to show that the favorable event still holds under the proposed $\epsilon$, that is, we need to show that under $P(\xi) \geq 1 - TK \exp(-\frac{T\delta^2}{2R^2H})$ we still reject arms that are under $\tau - \epsilon$ and accept those above $\tau + \epsilon$.
-
-### Step 2: Lower Bound on Number of Pulls of Difficult Arm
-
-In order to see that arms are correctly classified with large probability, we need to show that they are are pulled sufficiently often, that is, we have a degree of exploration for each arm $i$ that allows us to identify its characteristics.
-To see this, rewrite the favorable event of a single arm as follows with $s = T(i)$:
-
-\begin{equation}
-\xi_{i,s} = \{ |\hat{\mu}_{i,s}-\mu_i | \leq \epsilon \} = \{ |\hat{\mu}_{i,s} - \mu_i | \leq \sqrt{\frac{T \delta^2}{H T(i)}}\}
-\end{equation}
-
-To make sure that this deviation is small enough, we need to show that at time $T$, all $T(i)$ have a sufficient lower bound and thus all arms $i$ have been explored sufficiently to classify correctly with probability larger $TK \exp(-\frac{T\delta^2}{2R^2H})$.
-
-To start off, notice that due to the initialization of the APT algorithm, every $T_i(T) \geq 1$.
-Furthermore, we have assumed that $T>2K$.
-Now, at time $T$, consider an arm $k$ that has been pulled $T_k(T) -1 \geq \frac{(T-K)}{H \Delta^2_k}$ times.
-That is, it has been pulled at least proportionally to it's contribution to the overall hardness of the problem $H$.
-Recall $H = \sum_{i=1}^K(|\mu_i - \tau|+\epsilon)^-2$ and $\delta^2_i = (|\mu_i - \tau | + \epsilon)^2$.
-To see that such arm $k$ exists, assume it does not.
-Then
-
-\begin{equation*}
-T_i(T) - 1 < \frac{T-K}{H \Delta_i^2} \forall i
-\end{equation*}
-\begin{equation*}
-T- K = \sum_{i=1}^{K} T_i(T) - 1 < \sum_{i=1}^{K} \frac{T-K}{H \Delta_i^2} = \frac{T-K}{H \Delta_i^2} \sum_{i=1}^{K} \frac{1}{\Delta_i^2} = T-K
-\end{equation*}
-
-which is a contradiction.
-
-Consequently, using the assumption $T>2K$ from above, we have
-
-\begin{equation*}
-T_k(T) \geq T_k(T) - 1 \geq \frac{T-K}{H \Delta^2_k} = \frac{T}{2H\Delta_k^2}
-\end{equation*}
-
-This states a lower bound on the amount of pulls $T_k(t)$ for an arm $k$ that contributes more than average to the overall hardness of the problem.
-
-### Step 3: Lower Bound on Number of Pulls of Simple Arm
-
-Next, we would like to derive bounds on the number of pulls of the remaining arms $i$ at the time $t$, the last pull of arm $k$.
-To do so, consider that we are on the favorable event $\xi$.
-For every arm $i$, it holds:
-
-\begin{equation}
-|\hat{\mu}_i(t) - \mu_i | \leq \sqrt{\frac{T \delta^2}{HT_i(t)}} \label{step3_favorable_event} 
-\end{equation}
-
-As described in Locatelli et al., using the reverse triangle inequality, we can write
-
-\begin{IEEEeqnarray*}{rCl}
-|\hat{\mu}_i(t) - \mu_i | & = & | (\hat{\mu}_i(t) - \tau) - (\mu_i-\tau) |
-\\
-& \geq & | |\hat{\mu}_i(t) - \tau| - |\mu_i-\tau| |
-\\
-& = & | (|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i-\tau| - \epsilon) |
-\\
-& = & | \hat{\Delta}_i(t) - \Delta_i |
-\end{IEEEeqnarray*}
-
-Consequently, we can again employ the hardness of the task to start deriving bounds on the number of pulls of the arms:
-
-\begin{equation*}
-| \hat{\Delta}_i(t) - \Delta_i | \leq |\hat{\mu}_i(t) - \mu_i | \sqrt{\frac{T \delta^2}{HT_i(t)}}
-\end{equation*}
-
-From this, we get
-
-\begin{IEEEeqnarray*}{rlCrl}
-\Delta_i - \sqrt{\frac{T \delta^2}{HT_i(t)}} & \leq & \hat{\Delta}_i(t) & \leq & \Delta_i + \sqrt{\frac{T \delta^2}{HT_i(t)}}
-\end{IEEEeqnarray*}
-
-and in particular for the arm $k$ discussed above
-
-\begin{IEEEeqnarray}{rlCrl}
-\Delta_k - \sqrt{\frac{T \delta^2}{HT_k(t)}} & \leq & \hat{\Delta}_k(t) & \leq & \Delta_k + \sqrt{\frac{T \delta^2}{HT_k(t)}} \label{delta_hat_k_bounds}
-\end{IEEEeqnarray}
-
-To bound $T_i(t)$, it is helpful to compare $\Delta_i$ and $\Delta_k$ at time $t$.
-From the definition of the APT algorithm, we know that since arm $k$ has been pulled at time $t$ ("Pull arm $I_{t+1} = \arg \min_i \mathcal{B}_i (t+1)$"):
-
-\begin{IEEEeqnarray*}{rCl}
-\mathcal{B}_k(t) & \leq & \mathcal{B}_i(t)
-\\
-\sqrt{T_k(t)} \hat{\Delta}_k(t) & \leq & \sqrt{T_i(t)} \hat{\Delta}_i(t)
-\end{IEEEeqnarray*}
-
-Thus, every arm $i$ has a lower bound on it's number of pulls given by the lower bound for arm $k$ proportional with it's inverse relative estimated hardness $\hat{\Delta}_k(t) / \hat{\Delta}_i(t)$.
-We can easily derive a lower bound for the left hand side by plugging in \eqref{delta_hat_k_bounds}:
-
-\begin{IEEEeqnarray}{rCl}
-\sqrt{T_k(t)} (\Delta_k - \sqrt{\frac{T \delta^2}{HT_k(t)}}) & \leq & \mathcal{B}_k(t) 
-\\
-\sqrt{\frac{T}{2H\Delta_k^2}} (\Delta_k - \sqrt{2}\Delta_k \delta) & = & \sqrt{\frac{T}{H}} (\frac{1}{\sqrt{2}} - \delta)
-\\
-& \leq & \mathcal{B}_k(t)
-\end{IEEEeqnarray}
-
-since $T_k(t) \geq T/(2H\Delta^2_k)$ and $\sqrt{T \delta^2 / (HT_k(t))} \geq \sqrt{T \delta^2 / (H\frac{T}{2H \Delta^2_k})} = \sqrt{2}\Delta_k \delta$.
-
-Next, upper bound $\mathcal{B}_i(t)$. In contrast to $T_k(t)$, there is no lower bound for $T_i(t)$ available yet that we could plug in. Thus we derive:
-
-\begin{IEEEeqnarray*}{rCl}
-\mathcal{B}_i(t) & = & \sqrt{T_i(t)} \hat{\Delta}_i(t) 
-\\
-& \leq & \sqrt{T_i(t)} (\Delta_i + \sqrt{\frac{T \delta^2}{H T_i(t)}})
-\\
-& = & \sqrt{T_i(t)} \Delta_i + \delta \sqrt{\frac{T}{H}}
-\end{IEEEeqnarray*}
-
-Combining the two bounds, we get a lower bound on the pulls for every other arm $i$:
-
-\begin{IEEEeqnarray*}{rCl}
-\Delta_i \sqrt{T_i(t)} + \delta \sqrt{\frac{T}{H}} & \geq & (\frac{1}{\sqrt{2}} - \delta) \sqrt{\frac{T}{H}}
-\\
-\sqrt{T_i(t)} & \geq & (\frac{1}{\sqrt{2}} - 2\delta) \sqrt{\frac{T}{H}} \frac{1}{\Delta_i}
-\\ 
-& & \text{(choose $2\delta > 1 / \sqrt{2}$ such that RHS is greater 0)}
-% \\
-% T_i(t) & \geq & (\frac{1}{2} - 2\sqrt{2} \delta + 4\delta^2) \underbrace{\frac{T}{H} \frac{1}{\Delta_i^2}}_\text{$i$'s share of the budget}
-% \\
-% T_i(t) & \geq & (1 - 4 \sqrt{2} \delta + 8\delta^2) \frac{T}{2H} \frac{1}{\Delta_i^2}
-\end{IEEEeqnarray*}
-
-### Conclusion
-
-As stated before, we require the lower bound on $T_i(t)$ in order to show that $|\hat{\mu}_i(t) - \mu_i | \leq \sqrt{frac{T \delta^2}{H T_i(t)}}$ holds for all $i$.
-So if we now simply plug in the derived lower bound, we get:
-
-\begin{equation*}
-\mu_i - \Delta_i (\frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}) \leq \hat{\mu}_i(t) \leq \mu_i + \Delta_i (\frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta})
-\end{equation*}
-
-and with $\lambda := (\frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}) > 0$:
-
-\begin{equation*}
-\mu_i - \Delta_i \lambda \leq \hat{\mu}_i(t) \leq \mu_i + \Delta_i \lambda
-\end{equation*}
-
-Under this formulation on $\xi$, do we accept arms with $\mu_i \geq \tau + \epsilon$? For these arms holds that $\Delta_i = \mu_i - \tau + \epsilon$. Consequently:
-
-\begin{IEEEeqnarray*}{rCl}
-\mu_i - (\mu_i - \tau + \epsilon) \lambda & \leq & \hat{\mu}_i(t) 
-\\ 
-\hat{\mu}_i(t) & \geq & \tau \lambda + \mu (1-\lambda) - \epsilon \lambda
-\end{IEEEeqnarray*}
-
-The arms are accepted if
-
-\begin{IEEEeqnarray*}{rCl}
-\hat{\mu}_i(t) - \epsilon & \geq & 0
-\end{IEEEeqnarray*}
-
-Or equivalently as long as
-
-\begin{IEEEeqnarray*}{rCl}
-\tau \lambda + \mu(1-\lambda) - \epsilon \lambda - \tau & \geq & 0
-\\
-\lambda & \leq & \frac{1}{2}
-\end{IEEEeqnarray*}
+*Proof of Theorem \ref{theorem:LocatelliTheorem4}:*
+
+In order to upper bound the expected loss of the APT algorithm, we want to find an event on which the algorithm would correctly seperate arms from the threshold, that is, on the event a seperation condition holds.
+We then want to show that with large probability, this *favorable* event does indeed hold.
+Consequently, the expected loss (probability of an error) will correspond to the probability that the favorable event does not hold after all as this leads the seperation condition to fail, and the algorithm to classify at least one arm incorrectly.
+
+While this is the general idea, we have to jump between seperation condition, favorable event, and large probability.
+
+### Separation Condition
+
+As noted in Zhong et al. (2017), a simple requirement to correctly classify arms at the final round is the following. For every arm $i \in \{1, ..., K\}$ at round $T$,
+
+$$
+\hat{\mu}_{i,T_i(n)} \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
+$$
+or
+
+$$
+\hat{\mu}_{i,T_i(n)} \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
+$$
+Or simply in terms of the gap between the arm and the threshold as used as index by the algorithm,
+
+$$
+| \hat{\mu}_{i, T_i(n)} - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
+$$
+
+Intuitively, the conditions make sense as they ensure that the current mean estimate is closer to the true mean than to the threshold.
+Consequently, there is no possible arrangement left in which the condition would hold, but the arm be classified incorrectly.
+Assuming $\mu_i < \tau$ and $\epsilon = 0$, an incorrect classification would require $\mu_i < \tau \leq \hat{\mu_i}$.
+But then  $| \hat{\mu}_{i, T_i(n)} - \mu_i | \geq |\mu_i - \tau|$, violating the separation condition.
+
+Thus, we need to show that in the very final round, this condition holds for every arm $i \in \{1,...,K\}$ with large probability.
+Or more precisely, we need to derive a bound on the probability with which this does not hold.
+
+### The Favorable Event
+
+The separation condition gives a good idea of what event we need to hold in order to make a correct classification.
+The smaller the deviation of the empirical mean from the population mean, the more difficult it is for the classification to be wrong.
+Moreover, if the mean and empirical mean are identical, then the classification is correct independent of the threshold.
+And furthermore, the closer the mean and the threshold are, the better the estimate must be for a correct classification.
+
+Having to bound the absolute deviation of the sample mean from the population mean is a very thankful operation. Define the favorable event $\xi$ as
+
+$$
+\xi = \Big\{\forall i \in \mathbb{A}, \forall s \in \{1,...,T\} : |\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}} \Big\}.
+$$
+
+We want the probability that this favorable event occurs to be large, that is, the probability that the deviation is small, such that the separation condition holds with large probability.
+Indeed, we bound the deviation for *all* arms $i \leq K$ and for *every* round $s \leq T$.
+Using some Chernoff Hoeffding bounds, we are able to write
+
+$$
+\mathbb{P}(\xi) \geq 1 - 2(\log(T) +1)K \exp(-\frac{T\delta^2}{2R^2H})
+$$
+
+### Need to Bound $T_i$
+
+We now have that with large probability, the favorable event holds. On the favorable event, we have for every arm $i$:
+
+$$
+| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}
+$$
+
+The deviation of arm $i$ at time $t$ depends on how large $H$, $T$, and $T_i(t)$ are.
+While $t$, $H$, $T$ are deterministic, the number of times arm $i$ has been pulled at round $t$, $T_i(t)$, is a random variable.
+In order to know how large the probability of the favorable event is (and thus the error probability), we need to know what realistic values for $T_i(t)$ will be.
+Put differently: To ensure a deviation smaller than $\sqrt{\frac{T\delta^2}{HT_i(t)}}$ for arm $i$, we need to ensure that arm $i$ has been pulled at least $T_i(t)$ times.
+As usual in multi-armed bandits, and different from uniform sampling, the number of pulls is a random variable that also depends on how often other arms are pulled.
+In general, we do not want each arm to be pulled an equal amount, but each arm should be pulled some times, and not too many times.
+This especially holds for our exploration setting.
+
+Thus, in order to check that the deviation of arm $i$ really is small enough for the separation condition to hold on the favorable event, we need to bound the number of pulls of every arm from below.
+
+### Characteristics of a Frequently Pulled Arm (Lower Bound on $T_k(T)$)
+
+Given that we do not follow a uniform sampling strategy, we know that at time $T$, some arms will have been pulled more frequently than others.
+In particular, some arms will have been pulled more than $T/K$ times.
+How often an arm is pulled can be related to the individual arm's contribution to the overall complexity measure.
+Let $h_i$ be a measure of arm $i$'s individual problem complexity and write for the overall problem complexity
+
+$$
+H = \sum_{i = 1}^{K} h_i.
+$$
+
+Then arm $i$ contributes a share of $h_i/H$ to the overall problem complexity.
+We can now show that there exists an arm that has been pulled at least as often as the share of his complexity contribution.
+
+Given the initialization of the APT algorithm, every arm is pulled once initially.
+Consequently, there is a budget of $T-K$ rounds left after the initialization.
+As shown in Locatelli et al.
+(2016), there exists an arm $k$ that has been pulled after the initialization ($\geq 2$ pulls) and for which at the final round $T$ holds: $T_k(T) - 1 \geq \frac{(T-K)h_k}{H}$.
+This can be shown by a quick contradiction proof.
+Assume the opposite, that is
+
+$$
+\forall i \in \{1,...,K\}: T_i(T) - 1 < \frac{(T-K)h_i}{H}
+$$
+
+Consequently, at time $T$, we would have pulled across all arms $\sum_{i=1}^KT_i(T)-1$ times. If the previous assumption holds, we would not have used the entire budget:
+
+$$
+\sum_{i=1}^K T_i(T)-1 < \sum_{i=1}^K \frac{(T-K)h_i}{H} = (T-K)\sum_{i=1}^K \frac{h_i}{H} = T-K
+$$
+
+This is a contradiction, since as an requirement to the algorithm we have that $\sum_{i=1}^K T_i(T)-1 = (T-K)$, that is, we use the entire budget of samples.
+
+Another such requirement has been that $T>2K$. Plugging this in gives 
+$$
+T_k(T) - 1 \geq \frac{(T-K)h_k}{H} \leq \frac{(T-1/2T)h_k}{H} = \frac{Th_i}{2H}
+$$
+
+Now we know how often the arm has been pulled at the very end.
+That does not mean that $k$ has been pulled at time $T$.
+Thus we consider the time $t \leq T$ at which arm $k$ is pulled for the last time.
+We get (!!!!!SHOOOOWWW THIIIISSSS!!!!!!!!!)
+
+$$
+T_k(t) \geq T_k(T) - 1 \geq \frac{Th_i}{2H}.
+$$
+
+This gives us a lower bound on how often arms are pulled that are pulled frequently relative to their contribution to the problem complexity.
+Now we need a lower bound on $T_i(T)$ for every other arm $i$.
+
+### Lower Bound on $T_i(T)$
+
+Consider again as before the round $t$ in which arm $k$ is pulled for the very last time.
+Since the APT algorithm minimizes at every round $s$ the index $B_j(s)$, and pulls the arm with the smallest index, we know that arm $k$ must have had the smallest index at round $t$.
+We have:
+
+$$
+B_k(t) \leq B_i(t) \Leftrightarrow \sqrt{T_k(t)}\hat{\Delta}_k(t) \leq \sqrt{T_i(t)} \hat{\Delta}_i(t)
+$$
+
+One can already expect that this can be used to derive a lower bound on $T_i(t)$ on the RHS, and this is exactly what we do.
+
+On the LHS, we will plug in the lower bound for $T_k(t)$ derived before.
+Additionally bounding $\Delta_k(t)$ from below, and $\hat{\Delta}_i(t)$ from above using the favorable event will give the desired lower bound.
+
+Thus assume we are on the favorable event $\xi$ with large probability. we consequently have
+
+$$
+| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}.
+$$
+
+As shown in Locatelli et al. (2016), one can use the reverse triangle inequality to get:
+
+$$
+|\hat{\mu}_i(t) - \mu_i| = |(\hat{\mu}_i(t) - \tau) - (\mu_i - \tau)| \geq || \hat{\mu}_i(t) - \tau | - |\mu_i - \tau|| \geq |(|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i - \tau| + \epsilon)| \geq |\hat{\Delta}_i(t) - \Delta_i|
+$$
+
+If we combine this with the favorable event, we get
+
+$$
+\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}} \leq \hat{\Delta}_k(t) \leq \Delta_k + \sqrt{\frac{T\delta^2}{HT_k(t)}}
+$$
+
+and similar for $\hat{\Delta}_i$.
+
+We can now lower bound the LHS of the indices as
+
+$$
+\Big(\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}}\Big) \sqrt{T_k(t)} \leq B_k(t)
+$$
+
+$$
+\Big(\Delta_k - \sqrt{\frac{2}{h_k}}\delta \Big) \sqrt{\frac{Th_k}{2H}} \leq B_k(t)
+$$
+
+At this point, it is useful to have a well chosen complexity measure. If we set $h_i = \frac{1}{\Delta_i^2}$ as in Locatelli et al. (2016), we get
+
+$$
+\Big(\Delta_k - \sqrt{2}\delta \Delta \Big) \sqrt{\frac{T}{2H\Delta_k^2}} \leq B_k(t)
+$$
+
+which can be now be reduced to a form that is not specific to $k$:
+
+$$
+\Big( \frac{1}{\sqrt{2}} - \delta \Big) \sqrt{\frac{T}{H}} \leq B_k(t).
+$$
+
+Now we need to get rid of $\hat{\Delta}_i$ in order to bound $T_i(t)$. Thus, we bound the RHS again using the favorable event much as we did for the LHS:
+
+$$
+B_i(t) = \hat{\Delta}_i \sqrt{T_i(t)} \leq \Big(\Delta_i + \sqrt{\frac{T\delta^2}{HT_i(t)}}\Big) \sqrt{T_i(t)} \leq \Delta_i \sqrt{T_i(t)} + \delta \sqrt{\frac{T}{H}}
+$$
+
+As in Locatelli et al. (2016) we use the fact that by definition $\Delta$ and $\hat{\Delta}$ are positive in order to square both sides and write
+
+$$
+(1 - 2\sqrt{2}\delta)^2 \frac{T}{2H\Delta^2_i} \leq T_i(t) \leq T_i(T)
+$$
+
+We thus have derived a lower bound on the amount of pulls for any arm.
+That means that we can show that no arm is pulled an insufficient amount of times with large probability, and that consequently the favorable event hold and the estimated mean is sufficienctly separated from the threshold.
+
+### Check Separation Condition
+
+As the last step, we need to check whether the lower bound on the pulls of any arm suffices to ensure that the separation condition holds on the favorable event.
+That means, given $T_i(T) \geq (1-2\sqrt{2}\delta)^2 \frac{T}{2H\Delta_i^2}$, do we have $|\hat{\mu}_i(T) - \mu | \leq \frac{\Delta}{2}$ on the favorable event $\xi = \Big\{|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}}\Big\}$?
+
+To check, we plug the lower bound into the favorable event and get
+
+$$
+|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}} \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}
+$$
+Using $\delta = (4\sqrt{2})^-1$ as in Locatelli et al. (2016), we get
+
+$$
+|\hat{\mu}_i - \mu | \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta} \leq \frac{1}{2}\Delta_i.
+$$
+
+Thus the separation condition still holds for this value of $\delta$.
+
+### Upper Bound on Error Probability
+
+We have seen that on the favorable event $\xi$, which holds with large probability $\mathbb{P}(\xi)$, the separation condition holds as all arms have been pulled a sufficient number of times, such that their estimated mean is close to the true mean.
+All arms are classified correctly, and the algorithm does not suffer a loss.
+On the other hand, we make an error whenever the favorable event does not hold after all; that is, the deviation bound for the mean does not hold.
+At least one arm is misclassified and the arm suffers a loss.
+This occurs with probability $1-\mathbb{P}(\xi)$.
+Consequently, the expected loss is upper bounded by
+
+$$
+\mathbb{E}[L] = 1 - \mathbb{P}(\xi) \leq 2(\log(T)+1)K \exp(-\frac{1}{64R^2}\frac{T}{H}).
+$$
 
@@
 
-In the previous chapter, we have discussed the thresholding bandit problem as presented in Locatelli et al.
+In the previous chapter, we discussed the thresholding bandit problem as presented in Locatelli et al.
 (2016).
 Doing so, we came across the complexity term $H = \sum_{i=1}^{K} \Delta_i^{-2}$.
-Furthermore, we have noted the fact that an algorithm and bounds based on *only* the gap between the respective mean and the threshold are useful in the case of sub-Gaussian problems.
-Furthermore, even for the case of Bernoulli arms, which are sub-Gaussian since their feedback is bounded on $[0,1]$, the gap $\Delta$ becomes less and less appropriate for situations in which both $\mu$ of the Bernoulli, and $\tau$ are very close to 0 or 1.
+Furthermore, we noted the fact that an algorithm and bounds based on *only* the gap between the respective mean and the threshold are useful in the case of sub-Gaussian problems.
+Furthermore, even for the case of Bernoulli arms, which are sub-Gaussian since their feedback is bounded on $[0,1]$, the gap $\Delta$ becomes less and less appropriate in situations in which both $\mu$ of the Bernoulli, and $\tau$ are very close to 0 or 1.
 
@@
 (2016) show explicitly that $H$ is mainly useful for problems of Gaussian distributions.
-Indeed, they go so far as to define new measures of complexity that are based on information theoretic measures Using those they then display $H$ as an approximation to their measures in the case of Gaussian distributions.
-In turn, this makes apparent that especially Bernoulli distributions with small means have to be treated differently.
-
-For the current chapter, we will adopt the notation of Kaufmann et al. (2016) so that it will be easier to compare the arguments.
+Indeed, they go so far as to define new measures of complexity that are based on information theoretic measures.
+Using these, they then frame $H$ as an approximation to their measures in the case of Gaussian distributions.
+This underlines the fact that Bernoulli distributions with small means have to be treated differently than Gaussian distributions.
+
+For the current chapter, we adopt the notation of Kaufmann et al. (2016) to ease a comparison with their arguments.
 
@@
 Instead of the thresholding bandit problem, we now consider the problem of identifying the best $m$ out of $K$ arms, that is, the Top-$m$ problem.
-While we previously looked at a fixed budget formulation, we now mainly focus on a fixed confidence problem.
-That is, we hold the confidence $1-\delta$ fixed at which a strategy returns the correct $m$ arms while trying to find them in a way that minimizes the sample complexity $\mathbb{E}_{\nu}[\tau]$, that is, the expected number of overall draws of the arms.
+While we previously looked at a fixed budget formulation, we now mainly focus on a fixed confidence problem: We hold the confidence $1-\delta$ fixed at which a strategy returns the correct $m$ arms while trying to reach this confidence in a way that minimizes the sample complexity $\mathbb{E}_{\nu}[\tau]$, that is, the expected number of overall draws of the arms.
 $\tau$ is also called the stopping time of the algorithm.
-Algorithms are supposed to find $\mathcal{S}_m^*$, the set of the $m$ arms with the largest means.
+The goal of algorithms is to identify $\mathcal{S}_m^*$, the set of the $m$ arms with the largest means.
 If we let $(\mu_1, \dots, \mu_K)$ be the vector of the means of the arms, then let $(\mu_{[1]}, \dots, \mu_{[K]})$ be the tuple in which the means are arranged in decreasing order.
-For the rest of this chapter, we consider only settings with arms for which $\mu_{[m]} > \mu_{[m+1]}$; that is, the set of the top $m$ arms, $\mathcal{S}_m^*$, is unique.
+For the rest of this chapter, we consider only settings with arms for which $\mu_{[m]} > \mu_{[m+1]}$; we demand the set of the top $m$ arms, $\mathcal{S}_m^*$, to be unique.
 After the sampling phase, we require any algorithm to return the set $\hat{S}_m \subset \{1,\dots,K\}$ of $m$ arms that the algorithm believes to have the largest means.
 In the case of fixed confidence, we fix $\delta$ at the beginning, such that the algorithm only stops sampling when $\mathbb{P}_{\nu}(\hat{S}_m = \mathcal{S}_m^*) \geq 1-\delta$.
-We try to find algorithms who fulfill this as quickly as possible; that is, they minimize the expected stopping time (or number of draws), $\mathbb{E}_{\nu}[\tau]$.
+We try to find algorithms who fulfill this condition as quickly as possible.
+Algorithms which minimize the expected stopping time (or number of draws), $\mathbb{E}_{\nu}[\tau]$.
 
@@
 
-To proof this statement, we assume as before that the arms are ordered by their means decreasing in size.
+To prove this statement, we assume as before that the arms are ordered by their means decreasing in size.
 For a given $\delta$-PAC algorithm $\mathcal{A} = ((A_t), \tau, \hat{S}_m)$, and under the continuity conditions (compare Kaufmann et al.
@@
 In this alternative model, only arm $a$ is modified in accordance with the continuity conditions.
-Modified in such a way that measured by the Kullback-Leibler divergence, the arm $\nu_{m+1}$ is now closer to $\nu_a$ than $\nu_a'$ is to $\nu_a$, if $\mu_a > \mu_{m+1}$ (consequently, $\mu_a' < \mu_{m+1}$).
+Modified in such a way, the arm $\nu_{m+1}$ is now closer to $\nu_a$ as measured by the Kullback-Leibler divergence than $\nu_a'$ is to $\nu_a$, if $\mu_a > \mu_{m+1}$ (consequently, $\mu_a' < \mu_{m+1}$).
 On the other hand, if $\mu_a < \mu_{m}$, then $\nu_a'$ will be moved away from $\nu_a$ just enough so that $\nu_a$ is closer to $\nu_m$ than to $\nu_a'$ (consequently, $\mu_a' > \mu_m$).
-These changes in distribution make the original set of optimal arms, $\{1,\dots,m\}$ no longer optimal under the alternative model $\nu'$.
-Given that the algorithm returns $\hat{S}_m$, we know that for the event $\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})$ (which is element of the by the stopping time $\tau$ induced $\sigma$-Algebra $\mathcal{F}_{\tau}$), that $\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta$ and $\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta$ (because fixed confidence $\delta$!).
-
-To now give the lower bound on the expected number of samples, $\mathbb{E}_{\nu}[\tau]$, we employ the general lemma given by the authors for such changes in distribution in bandit models.
+These changes in distribution make the original set of optimal arms, $\{1,\dots,m\}$, no longer optimal under the alternative model $\nu'$.
+Given that the algorithm returns $\hat{S}_m$, we know that for the event $\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})$ (which is element of the $\sigma$-Algebra $\mathcal{F}_{\tau}$ induced by the stopping time $\tau$), that $\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta$ and $\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta$ (because fixed confidence $\delta$!).
+
+To now give the lower bound on the expected number of samples, $\mathbb{E}_{\nu}[\tau]$, we employ the general Lemma given by the authors for such changes in distribution in bandit models.
 
@@
 
-where $\der(x,y)$ is the binary relative entropy as defined above.
+where $d(x,y)$ is the binary relative entropy as defined above.
 \end{lemma}
 
-We can apply this lemma directly on the expected number of draws for each arm, $\mathbb{E}_{\nu}[N_a]$.
-For each arm $a$, we thus have $\KL(\nu_a, \nu_a') \mathbb{E}_{\nu}[N_a] \geq \der (1-\delta, \delta)$.
+We can apply this Lemma directly on the expected number of draws for each arm, $\mathbb{E}_{\nu}[N_a]$.
+For each arm $a$, we thus have $\KL(\nu_a, \nu_a') \mathbb{E}_{\nu}[N_a] \geq d(1-\delta, \delta)$.
 Using the definition of the alternative model above, we get for every small but fixed $\alpha > 0$, for every arm $a \in \{1, \dots, K\}$ and each arm $b \in \{m+1, \dots, K\}$:
@@
 After all, besides the number of arms and the experimenter-chosen confidence, it is just how close arms are with respect to each other in terms of Kullback-Leibler divergence that influences the sampling complexity.
-And in general, a problem requiring more samples is of course considered to be more complex (at least with respect to the samples, which is what needs to be optimized).
 
@@
 
-So if we were to plug in the lower bound on the sampling complexity, we would arrive at a complexity measure that basically depends only on the Kullback-Leibler measuring for each arm how far it is away from the border between the two groups of arms.
+By plugging in the lower bound on the sampling complexity, we arrive at a complexity measure that depends only on the Kullback-Leibler measuring for each arm how far it is away from the border between the two groups of arms.
 To see this, consider the lower bound on the complexity measure given in Kaufmann et al.
@@
 Given this description, we can already note that an intuitive extension of this complexity notion to the thresholding bandit problem might involve replacing $\mu_{[m]}$ and $\mu_{[m+1]}$ by the actual threshold $\tau$ (notation in Locatelli et al.) that divides the group above the threshold from the group below the threshold.
-In that case, the previously used $\alpha$ might be very similar to the $\epsilon$ used in Locatelli et al.
+In this sense, the previously used $\alpha$ is similar to the $\epsilon$ used in Locatelli et al.
 (2016).
 
-To get there, however, at least two important steps remain. First, we need to define a complexity for the fixed budget problem. Second, we need to create algorithms that can match the lower bound.
+Before we get to an extension of the thresholding bandit problem, however, at least two important steps remain.
+First, we need to define a complexity for the fixed budget problem.
+Second, we need to create algorithms that can match the lower bound.
 
@@
 
+\IncMargin{1em}
+\begin{algorithm}
+\SetKwData{Left}{left}\SetKwData{This}{this}\SetKwData{Up}{up}
+\SetKwFunction{Union}{Union}\SetKwFunction{FindCompress}{FindCompress}
+\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
+\Input{$\tau$, $\epsilon$}
+\Output{$\hat{S}_{\tau} = \{k: \hat{\mu}_k(T) \geq \tau\}$}
+\BlankLine
+\emph{Pull each arm once}\;
+\For{$t = K+1$ \KwTo $T$}{
+  \emph{Pull arm $I_t = \arg \min_{k\leq K} B_k^{SLR}(t) = T_k(t) \KL(\hat{\mu}_k(t) || \tau)$}\;
+  \emph{Observe reward $X \sim \nu_{I_t}$}\;
+}
+\caption{SLR algorithm for univariate exponential family of distributions}\label{algo_slr_1d}
+\end{algorithm}\DecMargin{1em}
+
 ### 2D-SLR Algorithm for Normal Distributions with Unknown Mean and Unknown Variance
@@
 In particular, as for the Anytime Parameter Free algorithm, there are no parameters which would need to be tuned upfront as is usually the case for upper-confidence bound based algorithms.
+
+Additionally, the Simple Likelihood Strategy offers an intuitive interpretation if we consider the index written in the form proposed by Zhang et al. (2017). Write the index again as
+
+$$
+B_i(t) = S_i(t) D_i(t),
+$$
+
+where $S_i(t)$ is a confidence term of the estimate of the arm $i$ at time $t$, and $D_i(t)$ is a measure of distance between the distribution of arm $i$ and the threshold $\tau$.
+The index of the Simple Likelihood Ratio strategy for univariate exponential family distributions can then be written with
+
+$$
+S_i(t) = T_i(t)
+$$
+
+and
+
+$$
+D_i(t) = \KL(\hat{\mu}_i(t)||\tau),
+$$
+where we employ the number of pulls so far for a given arm as the confidence measure, while the Kullback-Leibler divergence fulfills its role as distance between distributions.
+The larger the KL-divergence, the less inclined we are to draw the arm; the same holds, if we have pulled an arm many times.
+Since the KL-divergence reduces to the squared distance between means for Normal distributions of known variance, the SLR and APT algorithms are identical in this case.
 
@@
 the iterations the arm was pulled in that round.")
-
 ```
@@
 
+```{r, echo = FALSE}
+set.seed(3795969)
+tau_pois2 <- 0.4
+epsilon_pois2 <- 0
+mu_pois2 <- rexp(20, 1/0.7)
+
+knitr::kable(t(sort(mu_pois2)), digits = 4, col.names = paste0("V", 1:20), caption = "Means of Poisson arms in simulation 5 compared to a threshold of 0.4.")
+```
+
 ```{r simulation5_results, echo = FALSE}
@@
 load(paste0(current_path, "pois2_comp_APT.Rda"))
-#load(paste0(current_path, "pois2_comp_EVT.Rda"))
+load(paste0(current_path, "pois2_comp_EVT.Rda"))
 #load(paste0(current_path, "pois2_comp_UNIFORM.Rda"))
 
-alg_names <- c(rep("APT", 7981), rep("SLR", 9981))
-index <- c(20:8000, 20:10000)
-alg_res <- log(c(pois2_comp_APT, pois2_comp_LR))
+alg_names <- c(rep(c("APT", "SLR"), each = 9981), rep("EVT", 9961))
+index <- c(rep(20:10000, times = 2), 40:10000)
+alg_res <- log(c(pois2_comp_APT, pois2_comp_LR, pois2_comp_EVT))
 pois2_comp_res <- data.frame(index = index, names = alg_names, 
@@
        subtitle = "Horizontal bar indicates the threshold.", 
-       x = "Index", y = "One day moving average")
+       x = "Index", y = "One day moving average") +
+  theme(legend.position = "bottom")
+
+amo4_cummean_real <- data_amo4_wide[1:10080,] %>% tbl_df() %>%
+  mutate_each(funs(cummean)) %>%
+  mutate(index = 1:10080) %>%
+  gather(arm, mean, -index) %>%
+  mutate(source = rep("Real", 100800))
+
+amo4_cummean_syn <- syn_data %>% tbl_df() %>%
+  mutate_each(funs(cummean)) %>%
+  mutate(index = 1:10080) %>%
+  gather(arm, mean, -index) %>%
+  mutate(source = rep("Synthetic", 100800))
+
+rbind(amo4_cummean_real, amo4_cummean_syn) %>%
+  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
+  geom_line(size = 0.4) +
+  geom_hline(aes(yintercept = tau_amo4), linetype = 2) +
+  facet_grid(.~source) + 
+  labs(title = "Running average of 10080 observations (1 week)", 
+       subtitle = "Horizontal bar indicates the threshold.", 
+       x = "Index", y = "Running average") +
+  ylim(c(0,0.3)) +
+  theme(legend.position = "bottom")
+
+amo4_cummean_real_12hrs <- data_amo4_wide[721:10800,] %>% 
+  tbl_df() %>%
+  mutate_each(funs(cummean)) %>%
+  mutate(index = 1:10080) %>%
+  gather(arm, mean, -index) %>%
+  mutate(source = rep("Real", 100800))
+
+rbind(amo4_cummean_real_12hrs, amo4_cummean_syn) %>%
+  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
+  geom_line(size = 0.4) +
+  geom_hline(aes(yintercept = tau_amo4), linetype = 2) +
+  facet_grid(.~source) + 
+  labs(title = "Running average of 10080 observations (1 week), 12hrs later", 
+       subtitle = "Horizontal bar indicates the threshold.", 
+       x = "Index", y = "Running average") +
+  ylim(c(0,0.3)) +
+  theme(legend.position = "bottom")
+
+load("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/data_amo4_shuffled_wide.Rda")
+
+set.seed(214237)
+shuffle_idx <- sample(1:(24*60), 24*60)
+data_amo4_shuffled_wide[1:1440,] <- data_amo4_shuffled_wide[shuffle_idx,]
+
+amo4_shuffled_cummean_real <- data_amo4_shuffled_wide[1:10080,] %>% tbl_df() %>%
+  mutate_each(funs(cummean)) %>%
+  mutate(index = 1:10080) %>%
+  gather(arm, mean, -index) %>%
+  mutate(source = rep("Real", 100800))
+
+rbind(amo4_shuffled_cummean_real, amo4_cummean_syn) %>%
+  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
+  geom_line(size = 0.4) +
+  geom_hline(aes(yintercept = tau_amo4), linetype = 2) +
+  facet_grid(.~source) + 
+  labs(title = "Running average of 10080 observations (1 week), 12hrs later", 
+       subtitle = "Horizontal bar indicates the threshold.", 
+       x = "Index", y = "Running average") +
+  ylim(c(0,0.3)) +
+  theme(legend.position = "bottom")
+
 ```
@@
 ```
+
+# Conclusion
+
+# Notes
+
+The authors thank Alexandra Carpentier, Andrea Locatelli, and Urun Dogan for many hours of valuable feedback and ideas. <3

### 2017-08-25 Thesis/Draft.tex
Add Introduction

@@
 \usepackage{bbm}
+\usepackage[lined,boxed]{algorithm2e}
 \newtheorem{theorem}{Theorem}
@@
 \hypersetup{linkcolor=black}
-\setcounter{tocdepth}{3}
+\setcounter{tocdepth}{2}
 \tableofcontents
 }
+\newpage
+
+``In general, we look for a new law by the following process: First we
+guess it. Then we -- now don't laugh, that's really true. Then we
+compute the consequences of the guess to see what, if this is right, if
+this law that we guessed is right, to see what it would imply. And then
+we compare the computation results to nature, or we say compare to
+experiment or experience, compare it directly with observations to see
+if it works. If it disagrees with experiment, it's wrong. In that simple
+statement is the key to science. It doesn't make any difference how
+beautiful your guess is, it doesn't make any difference how smart you
+are, who made the guess, or what his name is. If it disagrees with
+experiment, it's wrong. That's all there is to it.''
+
+\begin{itemize}
+\tightlist
+\item
+  Richard Feynman in \emph{Richard Feynman Messenger Lectures at Cornell
+  University: The Character of Physical Law. Chapter 7, Seeking New
+  Laws}.
+\end{itemize}
+
+\newpage
+
+\section{Abbreviations}\label{abbreviations}
+
+Kullback-Leibler divergence between distributions \(\nu_i\) and
+\(\nu_j\): \(\KL(\nu_i||\nu_j)\).
+
+Binary relative entropy:
+\(d(x,y) := x \log(x/y) + (1-x) \log((1-x)/(1-y))\), where
+\(d(0,0) = d(1,1) = 0\).
+
+Kullback-Leibler divergence for two Bernoulli distributions
+parameterized by their means \(\mu_i\) and \(\mu_j\):
+\(KL_{Ber}(\nu_i||\nu_j) = d(\mu_i, \mu_j)\).
+
+\newpage
+
+\section{Introduction to Sequential Sampling and Multi-Armed
+Bandits}\label{introduction-to-sequential-sampling-and-multi-armed-bandits}
+
+The thesis at hand joins the ranks of a large literature concerned with
+the general problem of sequential sampling. One is familiar with the
+idea of ``batch sampling'', where the entire sample is gathered first
+and analyzed only after the last sample has become available. However,
+as noted in Chernoff (1958), many situations arise in which one would
+like to gather feedback from samples as they are drawn so as to
+influence the choice of the next sample. The two fundamental
+characteristics of the latter sampling process are that it is sequential
+and adaptive. Since observations are drawn in sequence, one has a chance
+to observe the observations drawn so far in order to adapt the decision
+of what sample one would like to observe next.
+
+This makes sequential sampling especially relevant in situations where
+there is a inherent cost to drawing an observation. The classical
+example that of clinical trials in which a researcher tests two drugs on
+patients to observe which one performs better. Not only is it difficult
+to gather patients, but also one would like to adapt the sampling such
+that as soon as possible more patients receive the better drug so that
+more patients are cured. As noted in Cappé et al. (2013), this example
+dates back to Thompson (1933, 1935). Such problems are known as
+multi-armed bandit problems in which the sampling is adapted so as to
+minimize the cumulative regret: In the case of the drug tests, one would
+like to sample the two drugs in a way to find the best drug as soon as
+possible and then to test this drug more and more often and more often
+than the worse drug. This would lead to cumulatively more healthy
+patients then when both drugs are tested uniformly and thus minimize the
+regret from treating a patient with an ineffective drug.
+
+Instead of drugs, can consider two or more unknown distributions (which
+we call arms in the multi-armed bandit problem). These distributions
+have different means, and one can draw samples sequentially from the
+distributions in order to estimate their means. One would like to play
+the distribution with the highest mean to minimize the cumulative regret
+measure. How can we organize the sampling in order to achieve this goal?
+
+While Gittins (1979) presents an Bayesian-optimal solution, the
+Upper-Confidence Bound algorithms pioneered by Agrawal (1995) and Auer,
+Cesa-Bianchi and Fischer (2002) lead to a blooming literature on
+multi-armed bandit problems that has been picked up to solve modern
+problems in website and advertising optimization, where advertisers try
+to allocate their advertising optimally so as to reduce regret from
+showing poorly converting advertisements. Several algorithms as the
+KL-UCB algorithm based on Kullback-Leibler divergence upper confidence
+intervals (Cappé et al., 2013) or the Bayes-UCB algorithm (Kaufmann et
+al., 2012) have followed and been shown to be optimal as they reach the
+lower bound introduced in Lai and Robbins (1985) and Burnetas and
+Katehakis (1996).
+
+These algorithms have in common that they compute after any sample an
+index for each of the unknown distributions. This index is based solely
+on the past (observed) data, and then used to pick the distribution from
+which the next observation should be drawn. Using these indexes, the
+algorithms can sequentially sample and adapt the future strategies to
+observations as they are gathered.
+
+Other algorithms based on indices can be used on related problems.
+Instead of minimizing cumulative regret, it might be more interesting to
+find the best arm, that is, the distribution with the largest mean, with
+as few samples as possible and with confidence as large as possible.
+This is particularly useful when there is not necessarily a cost from
+initially picking a lower mean, but when drawing any sample is costly,
+and one needs to explore the distributions as efficiently as possible.
+The need for strategies other than uniform sampling arises: Do not
+continue to sample distributions that we are confident about. As such,
+the best arm identification problem is very similar to the problem faced
+in Bayesian Optimization: Training large neural networks is costly in
+terms of time and computation, and so the parameter space needs to be
+explored with as few samples as possible. (Zhang et al., 2017; Brochu et
+al., 2010).
+
+The problem of best arm identification is very related to statistical
+hypothesis testing as noted by Chernoff (1958) since in the end, one has
+to make a decision about how the means of distributions relate to each
+other. The main difference of course being that the sampling procedure
+becomes integrated into the evaluation of the distributions. Given the
+focus on exploration, the problem is usually described with a loss
+function different from cumulative regret. Audibert et al. (2010)
+introduce a soft measure called \emph{simple regret} based on which they
+describe UCB policies. Other authors investigate hard, binary measures
+that are equal to 1 when the best arm has not been identified (Russo,
+2016; Garivier and Kaufmann, 2016).
+
+The problem of best arm identification can readily be extended to the so
+called Top-\(m\) problem of identifying the best \(m\) of \(K\) arms.
+
+\begin{itemize}
+\item
+  Chernoff -\textgreater{} Sequential Sampling; as mentioned by Russo;
+  Garivier and Kaufmann
+\item
+  Thompson
+\item
+  Optimality for Stochastic Cumulative Regret
+\item
+  UCB, KL-UCB, Thompson Sampling
+\end{itemize}
+
+-\textgreater{} Many variations: Infinite-armed, adversarial, dueling
+
+\begin{itemize}
+\item
+  Best Arm Identification
+\item
+  Top-\(m\) Identification
+\item
+  Thresholding Bandit Problem
+\item
+  Maybe an example?
+\end{itemize}
+
+\newpage
+
 \section{Thresholding Bandit Problem}\label{thresholding-bandit-problem}
@@
 The \emph{Thresholding Bandit Problem} described in Locatelli et al.
-(2016) can be considered a variant of a variant. It can be framed into
-the wider literature of \emph{Pure Exploration} multi-armed bandit
+(2016) can be considered a variant of a variant. It can be framed inside
+of the wider literature of \emph{Pure Exploration} multi-armed bandit
 problems. In particular, it shares characteristics with the
@@
 
-In any case, the problem boils down to the following. As standard in
+In any case, the problem boils down to the following. As usual in
 multi-armed bandit problems, we have \(K\) arms
@@
 the) distributions are to the fixed threshold. Intuitively, the closer a
-mean \(\mu_i\) is to the threshold \(\tau\), the more difficult it will
-be to distinguish the two successfully based on samples from the
-distribution \(\nu_i\). For the case of the sub-Gaussian distributions,
-a natural measure of this distance is given by simply
+mean \(\mu_i\) is to the threshold \(\tau\), the more difficult it is to
+distinguish the two successfully based on samples from the distribution
+\(\nu_i\). A straightforward measure of this distance is given by
 \(\Delta_i = |\tau - \mu_i| + \epsilon\), where \(\epsilon\) defines a
 \(2\epsilon\) interval around the threshold \(\tau\) in which we allow
-ourselves to make a mistake at no cost.
-
-If we extend this idea to the set of arms \(i \in \{1,...,K\}\) of a
-given bandit problem, a natural measure of the overall diffulty of the
-problem, or the problem's complexity, might be given by
+ourselves to make a mistake at no cost. In the case of sub-Gaussian
+distributions, this distance is not only simple but can be interpreted
+very naturally as we will come to understand later.
+
+If we extend this idea to the set of arms \(i \in \{1,...,K\}\) in a
+given bandit problem, a measure of the overall diffulty of the problem,
+or the problem's complexity, might be given by
 \(H = \sum_{i=1}^{K} \Delta_i^{-2}\). In particular, it shows that just
 adding additional arms leads to an increase in complexity (since we need
-to sample more of them), just as smaller \(\Delta_i\) will increase the
-complexity as arms become harder to classify. (WHERE DOES THIS
-COMPLEXITY ORIGINALLY COME FROM?)
+a larger budget to sample each arm the same number of times as before).
+Likewise, a smaller \(\Delta_i\) increases the complexity as arms become
+harder to classify. Choosing the complexity measure in this way fits the
+distance measure \(\Delta_i\) and turn out to be useful in the proof of
+an upper bound for the APT algorithm presented in Locatelli et al.
+(2016).
 
@@
 can most easily describe the regret in the thresholding case as the
-probability of making a misclassification of any arm. Or, more
-rigorously, let us define the set of all arms with mean larger than the
-threshold,
+probability of misclassifying any arm. Or, more rigorously, define the
+set of all arms with mean larger than the threshold,
 \(\mathcal{S}_\tau = \{i \in \mathcal{A}: \mu_i \geq \tau\}\).
@@
 
-From there, it is natural to define the expected regret/loss as
+Now, the expected regret/loss is defined as
 \(\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \land (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset))\).
 This, of course, is the mentioned probability of making a mistake.
-
-ADD REMARK ON WHAT THIS IMPLIES WITH REGARD TO THE MEANS
 
@@
 setup for any algorithm in the case of sub-Gaussian distributions. We
-thus proceed to describe the algorithm proposed in Locatelli et al.
+thus proceed to describe the APT algorithm proposed in Locatelli et al.
 (2016).
@@
 \subsection{The APT Algorithm}\label{the-apt-algorithm}
+
+\IncMargin{1em}
+
+\begin{algorithm}
+\SetKwData{Left}{left}\SetKwData{This}{this}\SetKwData{Up}{up}
+\SetKwFunction{Union}{Union}\SetKwFunction{FindCompress}{FindCompress}
+\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
+\Input{$\tau$, $\epsilon$}
+\Output{$\hat{S}_{\tau} = \{k: \hat{\mu}_k(T) \geq \tau\}$}
+\BlankLine
+\emph{Pull each arm once}\;
+\For{$t = K+1$ \KwTo $T$}{
+  \emph{Pull arm $I_t = \arg \min_{k\leq K} B_k^{APT}(t) = \sqrt{T_k(t)} \sqrt{|\hat{\mu}_i(t) - \tau|+\epsilon}$}\;
+  \emph{Observe reward $X \sim \nu_{I_t}$}\;
+}
+\caption{Anytime Parameter-free Thresholding Algorithm (Locatelli et al., 2016)}\label{algo_apt}
+\end{algorithm}
+
+\DecMargin{1em}
 
@@
 From the general setup, we already know how the algorithm will end.
-After it has drawn \(T\) samples, the algorithm makes its decision of
-which arms to include in the return sets solely on basis of the
-empirical means \(\hat{\mu}_i(T)\) estimated based on the samples drawn
-until time \(T\). Furthermore, the threshold and interval around the
-threshold were fixed upfront and serve as argument to the algorithm:
+After it has drawn \(T\) samples, the algorithm makes a decision of
+which arms to include in the return sets on basis of the empirical means
+\(\hat{\mu}_i(T)\) estimated based on the samples drawn until time
+\(T\). Furthermore, the threshold and interval around the threshold are
+fixed upfront and serve as argument to the algorithm:
 \((\tau, \epsilon)\). For a given arm \(i\) and a given time \(t\), we
@@
 \(i\) at time \(t\) is given by
-\(\mu_i = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}\) where
+\(\hat{\mu}_i(t) = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}\) where
 \(X_{i,s}\) is the feedback sampled from distribution \(\nu_i\) when the
@@
 over all arms so as to define a sampling rule optimizing the confidence
-of the final decision. This is Glivenko-Cantelli and the CLT making sure
-\(B_i(t+1)\) is not degenerate. (?)
+of the final decision.
 
@@
 very small parameters \(\mu\). By looking at the graphical examples
-below it becomes obvious that the Kullback-Leibler divergence of
-Bernoullis starts to lose any similarity to the plain quadratic
+below it becomes obvious that the Kullback-Leibler divergence between
+Bernoulli distributions starts to lose any similarity to the quadratic
 approximation. The second graph then shows that the actual
-Kullback-Leibler divergence of Bernoullis also has lost any symmetry
-over this range of parameter values. Given that Bernoulli distributions
-with very small parameter values arise naturally in many applications in
-website optimization and advertising click-through modeling, there is a
-need to tackle this problem.
+Kullback-Leibler divergence of Bernoulli distributions loses any
+symmetry over this range of parameter values. Given that Bernoulli
+distributions with very small parameter values arise naturally in many
+applications in website optimization, advertising click-through
+modeling, or anomaly detection in time series, there is a need to tackle
+this problem.
 
@@
 information-theoretic lower bound permits to interpret the quantity
-\(H(\nu)\) defined in (2) as a subgaussian approximation''.
+\(H(\nu)\) defined in (2) as a subgaussian approximation''. In the case
+of Normal distributions with known and equal mean, it holds that the
+Kullback-Leibler divergence between \(\nu_i\) and \(\nu_j\),
+parameterized by \(\mu_i\) and \(\mu_j\), can be written as
+
+\[
+\KL_{Normal}(\nu_i || \nu_j) = 2(\mu_i - \mu_j)^2.
+\]
+
+Writing \(\mu_j = \tau\) and \(\epsilon = 0\), we see that the APT
+algorithm essentially measures the KL-divergence between two Normal
+distributions. For two Bernoulli distributions \(\nu_i\) and \(\nu_j\),
+parameterized by \(\mu_i\) and \(\mu_j=\tau\), we write
+
+\[
+\KL_{Ber}(\nu_i||\nu_j) = \mu_i \log(\frac{\mu_i}{\tau}) + (1-\mu_i) \log(\frac{1-\mu_i}{1-\tau})
+\]
+
+In the case of \(\tau = 0.5\), the latter KL-divergence is symmetric in
+its first argument, and thus can be well approximated by Pinsker's
+inequality:
+
+\[
+\KL_{Ber}(\nu_i||\nu_j) \geq 2(\mu_i - \tau)^2.
+\]
+
+This shows how the distance measure used in the APT algorithm, and
+consequently the complexity \(H\), is a useful approximation of the
+KL-divergence for sub-Gaussian distributions. However, this
+approximation suffers as the distributions less and less similar to
+Gaussian distributions. Thus similarly to how UCB algorithms in the
+cumulative regret setting have been extended to KL-UCB algorithms
+(compare Cappé et al., 2013), also the APT algorithm offers room for
+improvement.
 
@@
 in chapter 3, we will come back to the problem of using the
-Kullback-Leibler divergence in the thresholding bandit setting.
+Kullback-Leibler divergence in the thresholding bandit setting. To
+conclude chapter 1, we proof the lower bound and upper bound for the APT
+algorithm as presented Theorem 1 and Theorem 2 in Locatelli et al.
+(2016).
 
@@
 
-\subsection{Upper Bound: Theorem and
-Proof}\label{upper-bound-theorem-and-proof}
+\subsection{Upper Bound on Expected Loss of
+APT}\label{upper-bound-on-expected-loss-of-apt}
 
@@
 
-\emph{Proof of Theorem \ref{theorem:LocatelliTheorem4}:} To prove above
-theorem, we first define a favorable event \(\xi\) on which we hope to
-make a loss with only a small probability. Indeed, it is the event for
-which we want to upper bound the expected loss. As we want to find an
-upper bound for the expected loss of the APT algorithm, the event
-corresponds to the decision made by it. Given that the APT algorithm's
-sampling rule and final decision is based on the empirical mean of each
-arm, it will have low expected regret, if it finds empirical mean
-estimates \(\hat{\mu}_i(t) = \frac{1}{s} \sum_{t=1}^s X_{i,t}\) that are
-close to the true means \(\mu_i\) of the arms. Then, we would expect
-arms with \(\hat{\mu}_i(T) > \tau + \epsilon\) to be classified
-correctly, and arms with \(\hat{\mu}_i(T) < \tau - \epsilon\) to be
-rejected.
-
-Indeed, we have
-\(\mathbb{E}(\mathcal{L}(T)) = P(S_{\tau + \epsilon} \cap \hat{S}_\tau^C \neq \emptyset \lor S_{\tau-\epsilon}^C \cap \hat{S}_{\tau} \neq \emptyset)\).
-But this just corresponds to
-\(P(\{\exists i: ((\mu_i < \tau-\epsilon) \land(\hat{\mu}_i \geq \tau)) \lor ((\mu_i > \tau + \epsilon) \land (\hat{\mu}_i < \tau)))\).
-Each of the two \((...)\lor(...)\) conditions corresponds to
-\(| \hat{\mu}_i - \mu_i | \geq \epsilon\). It follows that the expected
-loss can be rewritten as:
-\(\mathbb{E}(\mathcal{L}(T)) = P(\exists i, \exists s: |\hat{\mu}_{i,s} - \mu_i | \geq \epsilon) = P(\xi^C)\).
-This is exactly the probability of classifying at least one arm
-incorrectly which results in a loss of size 1.
-
-Thus we define as the favorable event as:
-
-\begin{equation} 
-\xi = \{\forall i, \forall s: | \hat{\mu}_{i,s} - \mu_i | \leq
-\epsilon\} 
-\end{equation}
-
-Furthermore, if we write
-\(\xi_{i,s} = \{ |\hat{\mu}_{i,s}-\mu_i | \leq \epsilon \}\), then the
-following holds by a union bound.
-
-\begin{equation} 
-P(\xi) = P(\cap_i \cap_s \xi_{i,s}) = 1 - P(\cup_i \cup_s
-\xi_{i,s}^C) \geq 1 - \sum_i \sum_s P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon)
-\label{theorem2_prob_fav_event} 
-\end{equation}
-
-Furthermore, for any \(i \in \{1, \dots, K\}\), for any
-\(s \in \{1, \dots, T(i)\}\), with \(X_{it}\) being the random sample
-from the R-sub-Gaussian distribution \(v_i\) at time \(t\):
-
-\begin{equation} 
-P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon) = P(| (\frac{1}{s}
-\sum_{t=1}^{s} X_{it} - \mu_i) | \geq \epsilon) = P(| \sum_{t=1}^{s} (X_{it} -
-\mu_i) | \geq s \epsilon) 
-\end{equation}
-
-where the latter can be bounded by a Hoeffding inequality:
-
-\begin{equation} 
-P(| \sum_{t=1}^{s} (X_{it} - \mu_i) | \geq s \epsilon) \leq
-2\exp (-\frac{\epsilon^2 s}{2 R^2}) \label{theorem2_hoeffding} 
-\end{equation}
-
-The Hoeffding inequality as used here is as follows (compare chapter 2.4
-in \href{http://www.stat.yale.edu/~pollard/Books/Mini/Basic.pdf}{David
-Pollard (2015)}):
-
-\begin{lemma}[Hoeffding's Inequality] \label{lemma:HoeffdingInequality}
-Consider $X_1, \dots, X_T$ independent random variables from R-sub-Gaussian distributions $\nu_i$ with mean $\mu_i$. Then, for any $\epsilon > 0$,
-
-\begin{equation*}
-\mathbb{P} \Big( | \sum_{i = 1}^T (X_i - \mu_i) | \geq \epsilon \Big) \leq 2\exp \Big(\frac{-\epsilon^2}{2T R^2}\Big).
-\end{equation*}
-\end{lemma}
-
-Plugging equation \eqref{theorem2_hoeffding} back into equation
-\eqref{theorem2_prob_fav_event}, we get:
-
-\begin{equation}
-P(\xi) \geq 1 - \sum_i \sum_s P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon) \geq 1 - 2 \sum_i \sum_s \exp (-\frac{\epsilon^2 s}{2 R^2})
-\end{equation}
-
-Now, in order to match the performance of the lower bound on the
-expected loss derived in Theorem \ref{theorem:Locatelli2016Theorem1}, we
-will choose \(\epsilon = \sqrt{\frac{T \delta^2}{Hs}}\). Thus:
-
-\begin{equation}
-P(\xi) \geq 1 - 2 \sum_i \sum_s \exp (-\frac{\epsilon^2 s}{2 R^2}) = 1 - 2 \sum_i \sum_s \exp (-\frac{T \delta^2}{2 R^2 H}) \geq 1 - TK \exp(-\frac{T\delta^2}{2R^2H})
-\end{equation}
-
-Thus, we do not exactly get the bound from Locatelli et al. (2016)
-because we used the Hoeffding inequality instead of the martingale
-bound; but the the method should be clear.
-
-What is left now is to show that the favorable event still holds under
-the proposed \(\epsilon\), that is, we need to show that under
-\(P(\xi) \geq 1 - TK \exp(-\frac{T\delta^2}{2R^2H})\) we still reject
-arms that are under \(\tau - \epsilon\) and accept those above
-\(\tau + \epsilon\).
-
-\subsubsection{Step 2: Lower Bound on Number of Pulls of Difficult
-Arm}\label{step-2-lower-bound-on-number-of-pulls-of-difficult-arm}
-
-In order to see that arms are correctly classified with large
-probability, we need to show that they are are pulled sufficiently
-often, that is, we have a degree of exploration for each arm \(i\) that
-allows us to identify its characteristics. To see this, rewrite the
-favorable event of a single arm as follows with \(s = T(i)\):
-
-\begin{equation}
-\xi_{i,s} = \{ |\hat{\mu}_{i,s}-\mu_i | \leq \epsilon \} = \{ |\hat{\mu}_{i,s} - \mu_i | \leq \sqrt{\frac{T \delta^2}{H T(i)}}\}
-\end{equation}
-
-To make sure that this deviation is small enough, we need to show that
-at time \(T\), all \(T(i)\) have a sufficient lower bound and thus all
-arms \(i\) have been explored sufficiently to classify correctly with
-probability larger \(TK \exp(-\frac{T\delta^2}{2R^2H})\).
-
-To start off, notice that due to the initialization of the APT
-algorithm, every \(T_i(T) \geq 1\). Furthermore, we have assumed that
-\(T>2K\). Now, at time \(T\), consider an arm \(k\) that has been pulled
-\(T_k(T) -1 \geq \frac{(T-K)}{H \Delta^2_k}\) times. That is, it has
-been pulled at least proportionally to it's contribution to the overall
-hardness of the problem \(H\). Recall
-\(H = \sum_{i=1}^K(|\mu_i - \tau|+\epsilon)^-2\) and
-\(\delta^2_i = (|\mu_i - \tau | + \epsilon)^2\). To see that such arm
-\(k\) exists, assume it does not. Then
-
-\begin{equation*}
-T_i(T) - 1 < \frac{T-K}{H \Delta_i^2} \forall i
-\end{equation*}\begin{equation*}
-T- K = \sum_{i=1}^{K} T_i(T) - 1 < \sum_{i=1}^{K} \frac{T-K}{H \Delta_i^2} = \frac{T-K}{H \Delta_i^2} \sum_{i=1}^{K} \frac{1}{\Delta_i^2} = T-K
-\end{equation*}
-
-which is a contradiction.
-
-Consequently, using the assumption \(T>2K\) from above, we have
-
-\begin{equation*}
-T_k(T) \geq T_k(T) - 1 \geq \frac{T-K}{H \Delta^2_k} = \frac{T}{2H\Delta_k^2}
-\end{equation*}
-
-This states a lower bound on the amount of pulls \(T_k(t)\) for an arm
-\(k\) that contributes more than average to the overall hardness of the
-problem.
-
-\subsubsection{Step 3: Lower Bound on Number of Pulls of Simple
-Arm}\label{step-3-lower-bound-on-number-of-pulls-of-simple-arm}
-
-Next, we would like to derive bounds on the number of pulls of the
-remaining arms \(i\) at the time \(t\), the last pull of arm \(k\). To
-do so, consider that we are on the favorable event \(\xi\). For every
-arm \(i\), it holds:
-
-\begin{equation}
-|\hat{\mu}_i(t) - \mu_i | \leq \sqrt{\frac{T \delta^2}{HT_i(t)}} \label{step3_favorable_event} 
-\end{equation}
-
-As described in Locatelli et al., using the reverse triangle inequality,
-we can write
-
-\begin{IEEEeqnarray*}{rCl}
-|\hat{\mu}_i(t) - \mu_i | & = & | (\hat{\mu}_i(t) - \tau) - (\mu_i-\tau) |
-\\
-& \geq & | |\hat{\mu}_i(t) - \tau| - |\mu_i-\tau| |
-\\
-& = & | (|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i-\tau| - \epsilon) |
-\\
-& = & | \hat{\Delta}_i(t) - \Delta_i |
-\end{IEEEeqnarray*}
-
-Consequently, we can again employ the hardness of the task to start
-deriving bounds on the number of pulls of the arms:
-
-\begin{equation*}
-| \hat{\Delta}_i(t) - \Delta_i | \leq |\hat{\mu}_i(t) - \mu_i | \sqrt{\frac{T \delta^2}{HT_i(t)}}
-\end{equation*}
-
-From this, we get
-
-\begin{IEEEeqnarray*}{rlCrl}
-\Delta_i - \sqrt{\frac{T \delta^2}{HT_i(t)}} & \leq & \hat{\Delta}_i(t) & \leq & \Delta_i + \sqrt{\frac{T \delta^2}{HT_i(t)}}
-\end{IEEEeqnarray*}
-
-and in particular for the arm \(k\) discussed above
-
-\begin{IEEEeqnarray}{rlCrl}
-\Delta_k - \sqrt{\frac{T \delta^2}{HT_k(t)}} & \leq & \hat{\Delta}_k(t) & \leq & \Delta_k + \sqrt{\frac{T \delta^2}{HT_k(t)}} \label{delta_hat_k_bounds}
-\end{IEEEeqnarray}
-
-To bound \(T_i(t)\), it is helpful to compare \(\Delta_i\) and
-\(\Delta_k\) at time \(t\). From the definition of the APT algorithm, we
-know that since arm \(k\) has been pulled at time \(t\) (``Pull arm
-\(I_{t+1} = \arg \min_i \mathcal{B}_i (t+1)\)''):
-
-\begin{IEEEeqnarray*}{rCl}
-\mathcal{B}_k(t) & \leq & \mathcal{B}_i(t)
-\\
-\sqrt{T_k(t)} \hat{\Delta}_k(t) & \leq & \sqrt{T_i(t)} \hat{\Delta}_i(t)
-\end{IEEEeqnarray*}
-
-Thus, every arm \(i\) has a lower bound on it's number of pulls given by
-the lower bound for arm \(k\) proportional with it's inverse relative
-estimated hardness \(\hat{\Delta}_k(t) / \hat{\Delta}_i(t)\). We can
-easily derive a lower bound for the left hand side by plugging in
-\eqref{delta_hat_k_bounds}:
-
-\begin{IEEEeqnarray}{rCl}
-\sqrt{T_k(t)} (\Delta_k - \sqrt{\frac{T \delta^2}{HT_k(t)}}) & \leq & \mathcal{B}_k(t) 
-\\
-\sqrt{\frac{T}{2H\Delta_k^2}} (\Delta_k - \sqrt{2}\Delta_k \delta) & = & \sqrt{\frac{T}{H}} (\frac{1}{\sqrt{2}} - \delta)
-\\
-& \leq & \mathcal{B}_k(t)
-\end{IEEEeqnarray}
-
-since \(T_k(t) \geq T/(2H\Delta^2_k)\) and
-\(\sqrt{T \delta^2 / (HT_k(t))} \geq \sqrt{T \delta^2 / (H\frac{T}{2H \Delta^2_k})} = \sqrt{2}\Delta_k \delta\).
-
-Next, upper bound \(\mathcal{B}_i(t)\). In contrast to \(T_k(t)\), there
-is no lower bound for \(T_i(t)\) available yet that we could plug in.
-Thus we derive:
-
-\begin{IEEEeqnarray*}{rCl}
-\mathcal{B}_i(t) & = & \sqrt{T_i(t)} \hat{\Delta}_i(t) 
-\\
-& \leq & \sqrt{T_i(t)} (\Delta_i + \sqrt{\frac{T \delta^2}{H T_i(t)}})
-\\
-& = & \sqrt{T_i(t)} \Delta_i + \delta \sqrt{\frac{T}{H}}
-\end{IEEEeqnarray*}
-
-Combining the two bounds, we get a lower bound on the pulls for every
-other arm \(i\):
-
-\begin{IEEEeqnarray*}{rCl}
-\Delta_i \sqrt{T_i(t)} + \delta \sqrt{\frac{T}{H}} & \geq & (\frac{1}{\sqrt{2}} - \delta) \sqrt{\frac{T}{H}}
-\\
-\sqrt{T_i(t)} & \geq & (\frac{1}{\sqrt{2}} - 2\delta) \sqrt{\frac{T}{H}} \frac{1}{\Delta_i}
-\\ 
-& & \text{(choose $2\delta > 1 / \sqrt{2}$ such that RHS is greater 0)}
-% \\
-% T_i(t) & \geq & (\frac{1}{2} - 2\sqrt{2} \delta + 4\delta^2) \underbrace{\frac{T}{H} \frac{1}{\Delta_i^2}}_\text{$i$'s share of the budget}
-% \\
-% T_i(t) & \geq & (1 - 4 \sqrt{2} \delta + 8\delta^2) \frac{T}{2H} \frac{1}{\Delta_i^2}
-\end{IEEEeqnarray*}
-
-\subsubsection{Conclusion}\label{conclusion}
-
-As stated before, we require the lower bound on \(T_i(t)\) in order to
-show that
-\(|\hat{\mu}_i(t) - \mu_i | \leq \sqrt{frac{T \delta^2}{H T_i(t)}}\)
-holds for all \(i\). So if we now simply plug in the derived lower
-bound, we get:
-
-\begin{equation*}
-\mu_i - \Delta_i (\frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}) \leq \hat{\mu}_i(t) \leq \mu_i + \Delta_i (\frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta})
-\end{equation*}
-
-and with \(\lambda := (\frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}) > 0\):
-
-\begin{equation*}
-\mu_i - \Delta_i \lambda \leq \hat{\mu}_i(t) \leq \mu_i + \Delta_i \lambda
-\end{equation*}
-
-Under this formulation on \(\xi\), do we accept arms with
-\(\mu_i \geq \tau + \epsilon\)? For these arms holds that
-\(\Delta_i = \mu_i - \tau + \epsilon\). Consequently:
-
-\begin{IEEEeqnarray*}{rCl}
-\mu_i - (\mu_i - \tau + \epsilon) \lambda & \leq & \hat{\mu}_i(t) 
-\\ 
-\hat{\mu}_i(t) & \geq & \tau \lambda + \mu (1-\lambda) - \epsilon \lambda
-\end{IEEEeqnarray*}
-
-The arms are accepted if
-
-\begin{IEEEeqnarray*}{rCl}
-\hat{\mu}_i(t) - \epsilon & \geq & 0
-\end{IEEEeqnarray*}
-
-Or equivalently as long as
-
-\begin{IEEEeqnarray*}{rCl}
-\tau \lambda + \mu(1-\lambda) - \epsilon \lambda - \tau & \geq & 0
-\\
-\lambda & \leq & \frac{1}{2}
-\end{IEEEeqnarray*}
+\emph{Proof of Theorem \ref{theorem:LocatelliTheorem4}:}
+
+In order to upper bound the expected loss of the APT algorithm, we want
+to find an event on which the algorithm would correctly seperate arms
+from the threshold, that is, on the event a seperation condition holds.
+We then want to show that with large probability, this \emph{favorable}
+event does indeed hold. Consequently, the expected loss (probability of
+an error) will correspond to the probability that the favorable event
+does not hold after all as this leads the seperation condition to fail,
+and the algorithm to classify at least one arm incorrectly.
+
+While this is the general idea, we have to jump between seperation
+condition, favorable event, and large probability.
+
+\subsubsection{Separation Condition}\label{separation-condition}
+
+As noted in Zhong et al. (2017), a simple requirement to correctly
+classify arms at the final round is the following. For every arm
+\(i \in \{1, ..., K\}\) at round \(T\),
+
+\[
+\hat{\mu}_{i,T_i(n)} \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
+\] or
+
+\[
+\hat{\mu}_{i,T_i(n)} \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
+\] Or simply in terms of the gap between the arm and the threshold as
+used as index by the algorithm,
+
+\[
+| \hat{\mu}_{i, T_i(n)} - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
+\]
+
+Intuitively, the conditions make sense as they ensure that the current
+mean estimate is closer to the true mean than to the threshold.
+Consequently, there is no possible arrangement left in which the
+condition would hold, but the arm be classified incorrectly. Assuming
+\(\mu_i < \tau\) and \(\epsilon = 0\), an incorrect classification would
+require \(\mu_i < \tau \leq \hat{\mu_i}\). But then
+\(| \hat{\mu}_{i, T_i(n)} - \mu_i | \geq |\mu_i - \tau|\), violating the
+separation condition.
+
+Thus, we need to show that in the very final round, this condition holds
+for every arm \(i \in \{1,...,K\}\) with large probability. Or more
+precisely, we need to derive a bound on the probability with which this
+does not hold.
+
+\subsubsection{The Favorable Event}\label{the-favorable-event}
+
+The separation condition gives a good idea of what event we need to hold
+in order to make a correct classification. The smaller the deviation of
+the empirical mean from the population mean, the more difficult it is
+for the classification to be wrong. Moreover, if the mean and empirical
+mean are identical, then the classification is correct independent of
+the threshold. And furthermore, the closer the mean and the threshold
+are, the better the estimate must be for a correct classification.
+
+Having to bound the absolute deviation of the sample mean from the
+population mean is a very thankful operation. Define the favorable event
+\(\xi\) as
+
+\[
+\xi = \Big\{\forall i \in \mathbb{A}, \forall s \in \{1,...,T\} : |\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}} \Big\}.
+\]
+
+We want the probability that this favorable event occurs to be large,
+that is, the probability that the deviation is small, such that the
+separation condition holds with large probability. Indeed, we bound the
+deviation for \emph{all} arms \(i \leq K\) and for \emph{every} round
+\(s \leq T\). Using some Chernoff Hoeffding bounds, we are able to write
+
+\[
+\mathbb{P}(\xi) \geq 1 - 2(\log(T) +1)K \exp(-\frac{T\delta^2}{2R^2H})
+\]
+
+\subsubsection{\texorpdfstring{Need to Bound
+\(T_i\)}{Need to Bound T\_i}}\label{need-to-bound-t_i}
+
+We now have that with large probability, the favorable event holds. On
+the favorable event, we have for every arm \(i\):
+
+\[
+| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}
+\]
+
+The deviation of arm \(i\) at time \(t\) depends on how large \(H\),
+\(T\), and \(T_i(t)\) are. While \(t\), \(H\), \(T\) are deterministic,
+the number of times arm \(i\) has been pulled at round \(t\),
+\(T_i(t)\), is a random variable. In order to know how large the
+probability of the favorable event is (and thus the error probability),
+we need to know what realistic values for \(T_i(t)\) will be. Put
+differently: To ensure a deviation smaller than
+\(\sqrt{\frac{T\delta^2}{HT_i(t)}}\) for arm \(i\), we need to ensure
+that arm \(i\) has been pulled at least \(T_i(t)\) times. As usual in
+multi-armed bandits, and different from uniform sampling, the number of
+pulls is a random variable that also depends on how often other arms are
+pulled. In general, we do not want each arm to be pulled an equal
+amount, but each arm should be pulled some times, and not too many
+times. This especially holds for our exploration setting.
+
+Thus, in order to check that the deviation of arm \(i\) really is small
+enough for the separation condition to hold on the favorable event, we
+need to bound the number of pulls of every arm from below.
+
+\subsubsection{\texorpdfstring{Characteristics of a Frequently Pulled
+Arm (Lower Bound on
+\(T_k(T)\))}{Characteristics of a Frequently Pulled Arm (Lower Bound on T\_k(T))}}\label{characteristics-of-a-frequently-pulled-arm-lower-bound-on-t_kt}
+
+Given that we do not follow a uniform sampling strategy, we know that at
+time \(T\), some arms will have been pulled more frequently than others.
+In particular, some arms will have been pulled more than \(T/K\) times.
+How often an arm is pulled can be related to the individual arm's
+contribution to the overall complexity measure. Let \(h_i\) be a measure
+of arm \(i\)'s individual problem complexity and write for the overall
+problem complexity
+
+\[
+H = \sum_{i = 1}^{K} h_i.
+\]
+
+Then arm \(i\) contributes a share of \(h_i/H\) to the overall problem
+complexity. We can now show that there exists an arm that has been
+pulled at least as often as the share of his complexity contribution.
+
+Given the initialization of the APT algorithm, every arm is pulled once
+initially. Consequently, there is a budget of \(T-K\) rounds left after
+the initialization. As shown in Locatelli et al. (2016), there exists an
+arm \(k\) that has been pulled after the initialization (\(\geq 2\)
+pulls) and for which at the final round \(T\) holds:
+\(T_k(T) - 1 \geq \frac{(T-K)h_k}{H}\). This can be shown by a quick
+contradiction proof. Assume the opposite, that is
+
+\[
+\forall i \in \{1,...,K\}: T_i(T) - 1 < \frac{(T-K)h_i}{H}
+\]
+
+Consequently, at time \(T\), we would have pulled across all arms
+\(\sum_{i=1}^KT_i(T)-1\) times. If the previous assumption holds, we
+would not have used the entire budget:
+
+\[
+\sum_{i=1}^K T_i(T)-1 < \sum_{i=1}^K \frac{(T-K)h_i}{H} = (T-K)\sum_{i=1}^K \frac{h_i}{H} = T-K
+\]
+
+This is a contradiction, since as an requirement to the algorithm we
+have that \(\sum_{i=1}^K T_i(T)-1 = (T-K)\), that is, we use the entire
+budget of samples.
+
+Another such requirement has been that \(T>2K\). Plugging this in gives
+\[
+T_k(T) - 1 \geq \frac{(T-K)h_k}{H} \leq \frac{(T-1/2T)h_k}{H} = \frac{Th_i}{2H}
+\]
+
+Now we know how often the arm has been pulled at the very end. That does
+not mean that \(k\) has been pulled at time \(T\). Thus we consider the
+time \(t \leq T\) at which arm \(k\) is pulled for the last time. We get
+(!!!!!SHOOOOWWW THIIIISSSS!!!!!!!!!)
+
+\[
+T_k(t) \geq T_k(T) - 1 \geq \frac{Th_i}{2H}.
+\]
+
+This gives us a lower bound on how often arms are pulled that are pulled
+frequently relative to their contribution to the problem complexity. Now
+we need a lower bound on \(T_i(T)\) for every other arm \(i\).
+
+\subsubsection{\texorpdfstring{Lower Bound on
+\(T_i(T)\)}{Lower Bound on T\_i(T)}}\label{lower-bound-on-t_it}
+
+Consider again as before the round \(t\) in which arm \(k\) is pulled
+for the very last time. Since the APT algorithm minimizes at every round
+\(s\) the index \(B_j(s)\), and pulls the arm with the smallest index,
+we know that arm \(k\) must have had the smallest index at round \(t\).
+We have:
+
+\[
+B_k(t) \leq B_i(t) \Leftrightarrow \sqrt{T_k(t)}\hat{\Delta}_k(t) \leq \sqrt{T_i(t)} \hat{\Delta}_i(t)
+\]
+
+One can already expect that this can be used to derive a lower bound on
+\(T_i(t)\) on the RHS, and this is exactly what we do.
+
+On the LHS, we will plug in the lower bound for \(T_k(t)\) derived
+before. Additionally bounding \(\Delta_k(t)\) from below, and
+\(\hat{\Delta}_i(t)\) from above using the favorable event will give the
+desired lower bound.
+
+Thus assume we are on the favorable event \(\xi\) with large
+probability. we consequently have
+
+\[
+| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}.
+\]
+
+As shown in Locatelli et al. (2016), one can use the reverse triangle
+inequality to get:
+
+\[
+|\hat{\mu}_i(t) - \mu_i| = |(\hat{\mu}_i(t) - \tau) - (\mu_i - \tau)| \geq || \hat{\mu}_i(t) - \tau | - |\mu_i - \tau|| \geq |(|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i - \tau| + \epsilon)| \geq |\hat{\Delta}_i(t) - \Delta_i|
+\]
+
+If we combine this with the favorable event, we get
+
+\[
+\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}} \leq \hat{\Delta}_k(t) \leq \Delta_k + \sqrt{\frac{T\delta^2}{HT_k(t)}}
+\]
+
+and similar for \(\hat{\Delta}_i\).
+
+We can now lower bound the LHS of the indices as
+
+\[
+\Big(\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}}\Big) \sqrt{T_k(t)} \leq B_k(t)
+\]
+
+\[
+\Big(\Delta_k - \sqrt{\frac{2}{h_k}}\delta \Big) \sqrt{\frac{Th_k}{2H}} \leq B_k(t)
+\]
+
+At this point, it is useful to have a well chosen complexity measure. If
+we set \(h_i = \frac{1}{\Delta_i^2}\) as in Locatelli et al. (2016), we
+get
+
+\[
+\Big(\Delta_k - \sqrt{2}\delta \Delta \Big) \sqrt{\frac{T}{2H\Delta_k^2}} \leq B_k(t)
+\]
+
+which can be now be reduced to a form that is not specific to \(k\):
+
+\[
+\Big( \frac{1}{\sqrt{2}} - \delta \Big) \sqrt{\frac{T}{H}} \leq B_k(t).
+\]
+
+Now we need to get rid of \(\hat{\Delta}_i\) in order to bound
+\(T_i(t)\). Thus, we bound the RHS again using the favorable event much
+as we did for the LHS:
+
+\[
+B_i(t) = \hat{\Delta}_i \sqrt{T_i(t)} \leq \Big(\Delta_i + \sqrt{\frac{T\delta^2}{HT_i(t)}}\Big) \sqrt{T_i(t)} \leq \Delta_i \sqrt{T_i(t)} + \delta \sqrt{\frac{T}{H}}
+\]
+
+As in Locatelli et al. (2016) we use the fact that by definition
+\(\Delta\) and \(\hat{\Delta}\) are positive in order to square both
+sides and write
+
+\[
+(1 - 2\sqrt{2}\delta)^2 \frac{T}{2H\Delta^2_i} \leq T_i(t) \leq T_i(T)
+\]
+
+We thus have derived a lower bound on the amount of pulls for any arm.
+That means that we can show that no arm is pulled an insufficient amount
+of times with large probability, and that consequently the favorable
+event hold and the estimated mean is sufficienctly separated from the
+threshold.
+
+\subsubsection{Check Separation
+Condition}\label{check-separation-condition}
+
+As the last step, we need to check whether the lower bound on the pulls
+of any arm suffices to ensure that the separation condition holds on the
+favorable event. That means, given
+\(T_i(T) \geq (1-2\sqrt{2}\delta)^2 \frac{T}{2H\Delta_i^2}\), do we have
+\(|\hat{\mu}_i(T) - \mu | \leq \frac{\Delta}{2}\) on the favorable event
+\(\xi = \Big\{|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}}\Big\}\)?
+
+To check, we plug the lower bound into the favorable event and get
+
+\[
+|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}} \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}
+\] Using \(\delta = (4\sqrt{2})^-1\) as in Locatelli et al. (2016), we
+get
+
+\[
+|\hat{\mu}_i - \mu | \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta} \leq \frac{1}{2}\Delta_i.
+\]
+
+Thus the separation condition still holds for this value of \(\delta\).
+
+\subsubsection{Upper Bound on Error
+Probability}\label{upper-bound-on-error-probability}
+
+We have seen that on the favorable event \(\xi\), which holds with large
+probability \(\mathbb{P}(\xi)\), the separation condition holds as all
+arms have been pulled a sufficient number of times, such that their
+estimated mean is close to the true mean. All arms are classified
+correctly, and the algorithm does not suffer a loss. On the other hand,
+we make an error whenever the favorable event does not hold after all;
+that is, the deviation bound for the mean does not hold. At least one
+arm is misclassified and the arm suffers a loss. This occurs with
+probability \(1-\mathbb{P}(\xi)\). Consequently, the expected loss is
+upper bounded by
+
+\[
+\mathbb{E}[L] = 1 - \mathbb{P}(\xi) \leq 2(\log(T)+1)K \exp(-\frac{1}{64R^2}\frac{T}{H}).
+\]
 
@@
 
-In the previous chapter, we have discussed the thresholding bandit
-problem as presented in Locatelli et al. (2016). Doing so, we came
-across the complexity term \(H = \sum_{i=1}^{K} \Delta_i^{-2}\).
-Furthermore, we have noted the fact that an algorithm and bounds based
-on \emph{only} the gap between the respective mean and the threshold are
-useful in the case of sub-Gaussian problems. Furthermore, even for the
-case of Bernoulli arms, which are sub-Gaussian since their feedback is
-bounded on \([0,1]\), the gap \(\Delta\) becomes less and less
-appropriate for situations in which both \(\mu\) of the Bernoulli, and
-\(\tau\) are very close to 0 or 1.
+In the previous chapter, we discussed the thresholding bandit problem as
+presented in Locatelli et al. (2016). Doing so, we came across the
+complexity term \(H = \sum_{i=1}^{K} \Delta_i^{-2}\). Furthermore, we
+noted the fact that an algorithm and bounds based on \emph{only} the gap
+between the respective mean and the threshold are useful in the case of
+sub-Gaussian problems. Furthermore, even for the case of Bernoulli arms,
+which are sub-Gaussian since their feedback is bounded on \([0,1]\), the
+gap \(\Delta\) becomes less and less appropriate in situations in which
+both \(\mu\) of the Bernoulli, and \(\tau\) are very close to 0 or 1.
 
@@
 Gaussian distributions. Indeed, they go so far as to define new measures
-of complexity that are based on information theoretic measures Using
-those they then display \(H\) as an approximation to their measures in
-the case of Gaussian distributions. In turn, this makes apparent that
-especially Bernoulli distributions with small means have to be treated
-differently.
-
-For the current chapter, we will adopt the notation of Kaufmann et al.
-(2016) so that it will be easier to compare the arguments.
+of complexity that are based on information theoretic measures. Using
+these, they then frame \(H\) as an approximation to their measures in
+the case of Gaussian distributions. This underlines the fact that
+Bernoulli distributions with small means have to be treated differently
+than Gaussian distributions.
+
+For the current chapter, we adopt the notation of Kaufmann et al. (2016)
+to ease a comparison with their arguments.
 
@@
 problem. While we previously looked at a fixed budget formulation, we
-now mainly focus on a fixed confidence problem. That is, we hold the
-confidence \(1-\delta\) fixed at which a strategy returns the correct
-\(m\) arms while trying to find them in a way that minimizes the sample
+now mainly focus on a fixed confidence problem: We hold the confidence
+\(1-\delta\) fixed at which a strategy returns the correct \(m\) arms
+while trying to reach this confidence in a way that minimizes the sample
 complexity \(\mathbb{E}_{\nu}[\tau]\), that is, the expected number of
 overall draws of the arms. \(\tau\) is also called the stopping time of
-the algorithm. Algorithms are supposed to find \(\mathcal{S}_m^*\), the
-set of the \(m\) arms with the largest means. If we let
-\((\mu_1, \dots, \mu_K)\) be the vector of the means of the arms, then
-let \((\mu_{[1]}, \dots, \mu_{[K]})\) be the tuple in which the means
-are arranged in decreasing order. For the rest of this chapter, we
-consider only settings with arms for which \(\mu_{[m]} > \mu_{[m+1]}\);
-that is, the set of the top \(m\) arms, \(\mathcal{S}_m^*\), is unique.
-After the sampling phase, we require any algorithm to return the set
-\(\hat{S}_m \subset \{1,\dots,K\}\) of \(m\) arms that the algorithm
-believes to have the largest means. In the case of fixed confidence, we
-fix \(\delta\) at the beginning, such that the algorithm only stops
-sampling when
+the algorithm. The goal of algorithms is to identify
+\(\mathcal{S}_m^*\), the set of the \(m\) arms with the largest means.
+If we let \((\mu_1, \dots, \mu_K)\) be the vector of the means of the
+arms, then let \((\mu_{[1]}, \dots, \mu_{[K]})\) be the tuple in which
+the means are arranged in decreasing order. For the rest of this
+chapter, we consider only settings with arms for which
+\(\mu_{[m]} > \mu_{[m+1]}\); we demand the set of the top \(m\) arms,
+\(\mathcal{S}_m^*\), to be unique. After the sampling phase, we require
+any algorithm to return the set \(\hat{S}_m \subset \{1,\dots,K\}\) of
+\(m\) arms that the algorithm believes to have the largest means. In the
+case of fixed confidence, we fix \(\delta\) at the beginning, such that
+the algorithm only stops sampling when
 \(\mathbb{P}_{\nu}(\hat{S}_m = \mathcal{S}_m^*) \geq 1-\delta\). We try
-to find algorithms who fulfill this as quickly as possible; that is,
-they minimize the expected stopping time (or number of draws),
-\(\mathbb{E}_{\nu}[\tau]\).
+to find algorithms who fulfill this condition as quickly as possible.
+Algorithms which minimize the expected stopping time (or number of
+draws), \(\mathbb{E}_{\nu}[\tau]\).
 
@@
 
-To proof this statement, we assume as before that the arms are ordered
+To prove this statement, we assume as before that the arms are ordered
 by their means decreasing in size. For a given \(\delta\)-PAC algorithm
@@
 In this alternative model, only arm \(a\) is modified in accordance with
-the continuity conditions. Modified in such a way that measured by the
-Kullback-Leibler divergence, the arm \(\nu_{m+1}\) is now closer to
-\(\nu_a\) than \(\nu_a'\) is to \(\nu_a\), if \(\mu_a > \mu_{m+1}\)
+the continuity conditions. Modified in such a way, the arm \(\nu_{m+1}\)
+is now closer to \(\nu_a\) as measured by the Kullback-Leibler
+divergence than \(\nu_a'\) is to \(\nu_a\), if \(\mu_a > \mu_{m+1}\)
 (consequently, \(\mu_a' < \mu_{m+1}\)). On the other hand, if
@@
 (consequently, \(\mu_a' > \mu_m\)). These changes in distribution make
-the original set of optimal arms, \(\{1,\dots,m\}\) no longer optimal
+the original set of optimal arms, \(\{1,\dots,m\}\), no longer optimal
 under the alternative model \(\nu'\). Given that the algorithm returns
@@
 \(\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})\) (which is element of the
-by the stopping time \(\tau\) induced \(\sigma\)-Algebra
-\(\mathcal{F}_{\tau}\)), that
-\(\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta\) and
+\(\sigma\)-Algebra \(\mathcal{F}_{\tau}\) induced by the stopping time
+\(\tau\)), that \(\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta\) and
 \(\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta\) (because fixed confidence
@@
 To now give the lower bound on the expected number of samples,
-\(\mathbb{E}_{\nu}[\tau]\), we employ the general lemma given by the
+\(\mathbb{E}_{\nu}[\tau]\), we employ the general Lemma given by the
 authors for such changes in distribution in bandit models.
@@
 
-where $\der(x,y)$ is the binary relative entropy as defined above.
+where $d(x,y)$ is the binary relative entropy as defined above.
 \end{lemma}
 
-We can apply this lemma directly on the expected number of draws for
+We can apply this Lemma directly on the expected number of draws for
 each arm, \(\mathbb{E}_{\nu}[N_a]\). For each arm \(a\), we thus have
-\(\KL(\nu_a, \nu_a') \mathbb{E}_{\nu}[N_a] \geq \der (1-\delta, \delta)\).
+\(\KL(\nu_a, \nu_a') \mathbb{E}_{\nu}[N_a] \geq d(1-\delta, \delta)\).
 Using the definition of the alternative model above, we get for every
@@
 how close arms are with respect to each other in terms of
-Kullback-Leibler divergence that influences the sampling complexity. And
-in general, a problem requiring more samples is of course considered to
-be more complex (at least with respect to the samples, which is what
-needs to be optimized).
+Kullback-Leibler divergence that influences the sampling complexity.
 
@@
 
-So if we were to plug in the lower bound on the sampling complexity, we
-would arrive at a complexity measure that basically depends only on the
-Kullback-Leibler measuring for each arm how far it is away from the
-border between the two groups of arms. To see this, consider the lower
-bound on the complexity measure given in Kaufmann et al. (2016):
+By plugging in the lower bound on the sampling complexity, we arrive at
+a complexity measure that depends only on the Kullback-Leibler measuring
+for each arm how far it is away from the border between the two groups
+of arms. To see this, consider the lower bound on the complexity measure
+given in Kaufmann et al. (2016):
 
@@
 threshold \(\tau\) (notation in Locatelli et al.) that divides the group
-above the threshold from the group below the threshold. In that case,
-the previously used \(\alpha\) might be very similar to the \(\epsilon\)
-used in Locatelli et al. (2016).
-
-To get there, however, at least two important steps remain. First, we
-need to define a complexity for the fixed budget problem. Second, we
-need to create algorithms that can match the lower bound.
+above the threshold from the group below the threshold. In this sense,
+the previously used \(\alpha\) is similar to the \(\epsilon\) used in
+Locatelli et al. (2016).
+
+Before we get to an extension of the thresholding bandit problem,
+however, at least two important steps remain. First, we need to define a
+complexity for the fixed budget problem. Second, we need to create
+algorithms that can match the lower bound.
 
@@
 
+\IncMargin{1em}
+
+\begin{algorithm}
+\SetKwData{Left}{left}\SetKwData{This}{this}\SetKwData{Up}{up}
+\SetKwFunction{Union}{Union}\SetKwFunction{FindCompress}{FindCompress}
+\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
+\Input{$\tau$, $\epsilon$}
+\Output{$\hat{S}_{\tau} = \{k: \hat{\mu}_k(T) \geq \tau\}$}
+\BlankLine
+\emph{Pull each arm once}\;
+\For{$t = K+1$ \KwTo $T$}{
+  \emph{Pull arm $I_t = \arg \min_{k\leq K} B_k^{SLR}(t) = T_k(t) \KL(\hat{\mu}_k(t) || \tau)$}\;
+  \emph{Observe reward $X \sim \nu_{I_t}$}\;
+}
+\caption{SLR algorithm for univariate exponential family of distributions}\label{algo_slr_1d}
+\end{algorithm}
+
+\DecMargin{1em}
+
 \subsubsection{2D-SLR Algorithm for Normal Distributions with Unknown
@@
 \]
+
+Given that in all other cases the Simple Likelihood Strategy is able to
+take more information about the distributions into account through the
+Kullback-Leibler divergence (in the case of the exponential family of
+distributions), the algorithm is expected to improve upon the Anytime
+Parameter Free strategy.
+
+As mentioned before, this improvement comes only at the cost of knowing
+the correct distribution upfront. In particular, as for the Anytime
+Parameter Free algorithm, there are no parameters which would need to be
+tuned upfront as is usually the case for upper-confidence bound based
+algorithms.
+
+Additionally, the Simple Likelihood Strategy offers an intuitive
+interpretation if we consider the index written in the form proposed by
+Zhang et al. (2017). Write the index again as
+
+\[
+B_i(t) = S_i(t) D_i(t),
+\]
+
+where \(S_i(t)\) is a confidence term of the estimate of the arm \(i\)
+at time \(t\), and \(D_i(t)\) is a measure of distance between the
+distribution of arm \(i\) and the threshold \(\tau\). The index of the
+Simple Likelihood Ratio strategy for univariate exponential family
+distributions can then be written with
+
+\[
+S_i(t) = T_i(t)
+\]
+
+and
+
+\[
+D_i(t) = \KL(\hat{\mu}_i(t)||\tau),
+\] where we employ the number of pulls so far for a given arm as the
+confidence measure, while the Kullback-Leibler divergence fulfills its
+role as distance between distributions. The larger the KL-divergence,
+the less inclined we are to draw the arm; the same holds, if we have
+pulled an arm many times. Since the KL-divergence reduces to the squared
+distance between means for Normal distributions of known variance, the
+SLR and APT algorithms are identical in this case.
+
+As we see in the experiments that follow, the Simple Likelihood Strategy
+is able to improve significantly upon the Anytime Parameter Free
+strategy in many cases.
 
@@
 \(\tau = 1\)}{Experiment 5: Poisson Distribution with \textbackslash{}tau = 1}}\label{experiment-5-poisson-distribution-with-tau-1}
+
+\begin{longtable}[]{@{}rrrrrrrrrrrrrrrrrrrr@{}}
+\caption{Means of Poisson arms in simulation 5 compared to a threshold
+of 0.4.}\tabularnewline
+\toprule
+V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10 & V11 & V12 & V13 & V14
+& V15 & V16 & V17 & V18 & V19 & V20\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10 & V11 & V12 & V13 & V14
+& V15 & V16 & V17 & V18 & V19 & V20\tabularnewline
+\midrule
+\endhead
+0.0072 & 0.0576 & 0.0613 & 0.0925 & 0.1452 & 0.1559 & 0.1869 & 0.1958 &
+0.2235 & 0.2467 & 0.2664 & 0.3008 & 0.4295 & 0.4948 & 0.5857 & 0.6904 &
+0.7609 & 0.785 & 0.8878 & 1.7114\tabularnewline
+\bottomrule
+\end{longtable}
 
@@
 
-\includegraphics{Draft_files/figure-latex/unnamed-chunk-6-1.pdf}
+\includegraphics{Draft_files/figure-latex/unnamed-chunk-7-1.pdf}
 
@@
 
-\includegraphics{Draft_files/figure-latex/unnamed-chunk-7-1.pdf}
-
 \includegraphics{Draft_files/figure-latex/unnamed-chunk-8-1.pdf}
+\includegraphics{Draft_files/figure-latex/unnamed-chunk-8-2.pdf}
+\includegraphics{Draft_files/figure-latex/unnamed-chunk-8-3.pdf}
+\includegraphics{Draft_files/figure-latex/unnamed-chunk-8-4.pdf}
+
+\includegraphics{Draft_files/figure-latex/unnamed-chunk-9-1.pdf}
 
@@
 
-\includegraphics{Draft_files/figure-latex/unnamed-chunk-9-1.pdf}
+\includegraphics{Draft_files/figure-latex/unnamed-chunk-10-1.pdf}
+
+\section{Conclusion}\label{conclusion}
+
+\section{Notes}\label{notes}
+
+The authors thank Alexandra Carpentier, Andrea Locatelli, and Urun Dogan
+for many hours of valuable feedback and ideas. \textless{}3
 

### 2017-08-25 Thesis/Literature.Rmd
Add Introduction

---
title: "Literature"
output: pdf_document
---

Hermann Chernoff (1958). Sequential Design of Experiments. The Annals of Mathematical Statistics.

Thompson, W. R. (1933). On the likelihood that one unknown probability exceeds another in view of the evidence of two samples. Biometrika 25 285–294.
Thompson, W. R. (1935). On the Theory of Apportionment. Amer. J. Math. 57 450–456.
MR1507085

Gittins, J. C. (1979). Bandit processes and dynamic allocation indices (with discussion).
J. R. Stat. Soc. Ser. B Stat. Methodol. 41 148–177. MR0547241

Burnetas, A. N. and Katehakis, M. N. (1996). Optimal adaptive policies for sequential allocation problems. Adv. in Appl. Math. 17 122–142. MR1390571

Lai, T. L. and Robbins, H. (1985). Asymptotically efficient adaptive allocation rules.
Adv. in Appl. Math. 6 4–22. MR0776826

Robbins, H. (1952). Some aspects of the sequential design of experiments. Bull. Amer.
Math. Soc. (N.S.) 58 527–535. MR0050246

Capp ́e, O., Garivier, A., Maillard, O.-A., Munos, R. and Stoltz, G. (2013). Supple-
ment to “Kullback–Leibler upper confidence bounds for optimal sequential allocation.”
DOI:10.1214/13-AOS1119SUPP.

Capp ́e, O., Garivier, A., Maillard, O.-A., Munos, R. and Stoltz, G. (2013). Kullback–Leibler upper confidence bounds for optimal sequential allocation.

Emilie Kaufmann, Olivier Cappé, and Aurélien Garivier (2012). On Bayesian Upper Confidence Bounds for Bandit Problems. Proceedings of the 15th International Conference on Artificial Intelligence and Statistics.

Eric Brochu, Vlad M. Cora and Nando de Freitas (2010). A Tutorial on Bayesian Optimization of Expensive Cost Functions, with Application to Active User Modeling and Hierarchical Reinforcement Learning
arXiv:1012.2599v1

Jean-Yves Audibert, Sébastien Bubeck, Rémi Munos (2010). Best Arm Identification in Multi-Armed Bandits.

Russo (2016)

Garivier and Kaufmann (2016)

(Kaufmann and Kalyanakrishnan, 2013;

Kaufmann et al. 2016)

Locatelli et al. (2016)

### 2017-08-25 AugUCB/run_parallelized_from_data.R

@@ -60,6 +60,45 @@ compare_to_ground_truth <- function(true_means, sim_res, tau, epsilon) {
 
 #############################################################################
 
+# Instead of using the hard loss function from Locatelli et al. (2016),
+# use a loss that's more similar to simple regret (deviation from true mean)
+# for those that are classified wrong
+get_simple_regret <- function(true_means, sim_res, tau, epsilon) {
+  message(paste0("Comparing ", length(sim_res), " simulations."))
+  true_classification_up <- which(true_means > tau+epsilon)
+  true_classification_down <- which(true_means < tau-epsilon)
+  
+  get_iter_error <- function(x, true_class_up, true_class_down) {
+    wrong_class_index <- (true_means >= tau & x < tau) | (true_means < tau & x >= tau)
+    sum(abs(x-true_means)[wrong_class_index])
+  }
+  
+  get_error <- function(res_df, ...) {
+    apply(res_df$mean_storage, 1, get_iter_error, ...)
+  }
+  
+  comp_list <- lapply(sim_res, get_error, 
+                      true_class_up = true_classification_up, 
+                      true_class_down = true_classification_down)
+  
+  comp_mean <- rowMeans(as.data.frame(comp_list, 
+                                      col.names = 1:length(comp_list)))
+  
+  return(list(mean = comp_mean, full = comp_list))
+}
+
+#testt <- gex_APT
+#res <- get_simple_regret(mu_gex, testt, tau_gex, epsilon_gex)
+
+#set.seed(93468734)
+#tau_exp2 <- 1
+#epsilon_exp2 <- 0
+#mu_exp2 <- rexp(20, 1)
+#load(paste0(current_path, "exp2_EVT.Rda"))
+#res <- get_simple_regret(mu_exp2, exp2_EVT, tau_exp2, epsilon_exp2)
+#plot(res$mean)
+#############################################################################
+
 # Get the average performance over all simulations
 
 # expect a list of matrices of size rounds x K as input from the simulations,

### 2017-08-25 Thesis/McDiarmidBoundSimulation.R

@@ -1,0 +1,55 @@
+diarmid <- function(x, tau) {
+  n <- length(x)
+  mu <- ifelse(mean(x) == 1,
+               1-1/(n)^2, mean(x))
+  mu <- ifelse(mu == 0,
+               1/(n)^2, mu)
+  abs(
+    mu*log(mu/(mu-1/n)) +
+      (1-mu)*log((1-mu)/(1-mu+1/n)) +
+      1/n*log((1-tau)/tau) +
+      1/n*log((mu-1/n)/(1-mu+1/n))
+  )
+}
+
+y <- c(1,purrr::rbernoulli(10000,0.05))
+
+plot(c(1,10000), c(-15,0), type = "n")
+for(i in 1:10000) {
+  points(i, log(diarmid(y[1:i], 0.1)), pch = 19, cex = 0.1)
+}
+
+y <- purrr::rbernoulli(10000,0.01)
+
+plot(c(1,10000), c(1,20), type = "n")
+for(i in 1:10000) {
+  points(i, diarmid(y[1:i], 0.1), pch = 19, cex = 0.5)
+}
+
+y <- purrr::rbernoulli(10000,0.001)
+
+plot(c(1,10000), c(1,20), type = "n")
+for(i in 1:10000) {
+  points(i, diarmid(y[1:i], 0.1), pch = 19, cex = 0.5)
+}
+
+y <- purrr::rbernoulli(10000,0.01)
+
+plot(c(1,10000), c(1,20), type = "n")
+for(i in 1:10000) {
+  points(i, diarmid(y[1:i], 0.4), pch = 19, cex = 0.5)
+}
+
+
+
+plot(c(1,100000), c(0,0.2), type = "n")
+for(j in seq(0.001,0.999, by = 0.05)) {
+  y <- purrr::rbernoulli(100000,j)
+  for(i in seq(10,100000, by=50)) {
+    points(i, diarmid(y[1:i], 0.5), pch = 19, cex = 0.1)
+  }
+}
+
+
+plot(3:100, log(-log(1-0.5/(3:100))), type = "l")
+lines(3:100, log(0.5/(3:100)), col = "red")

### 2017-08-25 synthetic_experiments/exponential/exp_exp_2.R

@@ -35,6 +35,7 @@ load(paste0(current_path, "exp2_comp_LR.Rda"))
 load(paste0(current_path, "exp2_comp_APT.Rda"))
 load(paste0(current_path, "exp2_comp_EVT.Rda"))
 load(paste0(current_path, "exp2_comp_UNIFORM.Rda"))
+load(paste0(current_path, "exp2_comp_AugUCB.Rda"))
 
 plot(c(0,4000), c(0, -8), type = "n")
 abline(h=log(0.01), lty = 2)

### 2017-08-25 synthetic_experiments/gaussian/exp_gex.R

@@ -12,19 +12,26 @@ current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis
 set.seed(45844069)
 tau_gex <- 0
 epsilon_gex <- 0
-(mu_gex <- rnorm(10, 0, 0.4))
-(sd_gex <- sqrt(1/rgamma(10, 2, 0.1)))
+(mu_gex <- rnorm(20, 0, 0.3))
+(sd_gex <- sqrt(1/rgamma(50, 2, 0.1)))
 
 sd_gex <- sd_gex[order(mu_gex)]
 mu_gex <- mu_gex[order(mu_gex)]
 
 rbind(mu_gex, sd_gex)
 
-plot(c(-1,1), c(0,4), type = "n")
+plot(c(-2,2), c(0,2), type = "n")
 for (i in 1:length(mu_gex)) {
   lines(seq(-2,2,0.0001), dnorm(seq(-2,2,0.0001), mu_gex[order(mu_gex)][i], 
                                 sd_gex[order(mu_gex)][i]),
-        col = rainbow(10)[i])
+        col = rainbow(50)[i])
+}
+
+plot(c(-2,2), c(0,2), type = "n")
+for (i in 1:length(mu_gex)) {
+  lines(seq(-2,2,0.0001), dnorm(seq(-2,2,0.0001), mu_gex[order(sd_gex)][i], 
+                                sd_gex[order(sd_gex)][i]),
+        col = rainbow(50)[i])
 }
 
 data_gex <- list()
@@ -39,30 +46,40 @@ for(j in 1:5000) {
 gc()
 
 ########################################################################
+
+
+
+########################################################################
 # Gaussian Likelihood Ratio 2D-SLR
 
-system.time(gex_LR <- para_bandit_sim_LR_gaussian(data = data_gex, 
-                                                   rounds = 10000, 
+system.time(gex_LR <- para_bandit_sim_LR_gaussian(data = data_gex[1:1000], 
+                                                   rounds = 8000, 
                                                    tau = tau_gex, 
                                                    epsilon = epsilon_gex))
 
-save(gex_LR, file = paste0(current_path, "gex_LR.Rda"))
+#save(gex_LR, file = paste0(current_path, "gex_LR.Rda"))
 gex_comp_LR <- compare_to_ground_truth(mu_gex, gex_LR, 
                                         tau_gex, epsilon_gex)$mean
-save(gex_comp_LR, file = paste0(current_path, "gex_comp_LR.Rda"))
[…]

### 2017-08-25 synthetic_experiments/gaussian/exp_gexs.R

@@ -1,0 +1,106 @@
+########################################################################
+# load functions
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/gaussian/"
+
+########################################################################
+# Create the data
+
+set.seed(45844069)
+tau_gexs <- 0.5
+epsilon_gexs <- 0
+(mu_gexs <- c(0.1,0.3,0.4,0.4,0.45,0.55,0.6,0.6,0.7,0.9))
+(sd_gexs <- c(0.9,0.9,0.9,0.2,0.9,0.45,0.1,0.45,0.45,0.45))
+
+sd_gexs <- sd_gexs[order(mu_gexs)]
+mu_gexs <- mu_gexs[order(mu_gexs)]
+
+rbind(mu_gexs, sd_gexs)
+
+plot(c(-2,2), c(0,2), type = "n")
+for (i in 1:length(mu_gexs)) {
+  lines(seq(-2,2,0.0001), dnorm(seq(-2,2,0.0001), mu_gexs[order(mu_gexs)][i], 
+                                sd_gexs[order(mu_gexs)][i]),
+        col = rainbow(50)[i])
+}
+abline(v = tau_gexs, lty = 2)
+
+plot(c(-2,2), c(0,2), type = "n")
+for (i in 1:length(mu_gexs)) {
+  lines(seq(-2,2,0.0001), dnorm(seq(-2,2,0.0001), mu_gexs[order(sd_gexs)][i], 
+                                sd_gexs[order(sd_gexs)][i]),
+        col = rainbow(50)[i])
+}
+abline(v = tau_gexs, lty = 2)
+
+data_gexs <- list()
+for(j in 1:5000) {
+  curr_data <- data.frame(rep(NA, times = 10000))
+  for(i in 1:length(mu_gexs)) {
+    curr_data[[i]] <- as.numeric(rnorm(10000, mu_gexs[i], sd_gexs[i]))
+  }
+  names(curr_data) <- paste0("V", rep(1:length(mu_gexs)))
+  data_gexs[[j]] <- curr_data
+}
+gc()
+
+########################################################################
+
[…]

### 2017-08-25 synthetic_experiments/poisson/exp_pois_2.R

@@ -36,9 +36,11 @@ load(paste0(current_path, "pois2_comp_LR.Rda"))
 load(paste0(current_path, "pois2_comp_APT.Rda"))
 load(paste0(current_path, "pois2_comp_EVT.Rda"))
 
-plot(c(0,10000), c(0, -8), type = "n")
+plot(c(0,10000), c(0, -7), type = "n")
+abline(h=log(0.1), lty = 2)
 abline(h=log(0.01), lty = 2)
-lines(log(pois2_comp_APT), col = "black")
+lines(log(pois2_comp_UNIFORM), col = "black")
+lines(log(pois2_comp_APT), col = "darkgreen")
 lines(log(pois2_comp_LR), col = "blue")
 lines(log(pois2_comp_EVT), col = "red")
 

### 2017-08-26 Thesis/Draft.Rmd
Rewritten Setup

@@
 
-# Thresholding Bandit Problem
-
-The *Thresholding Bandit Problem* described in Locatelli et al.
-(2016) can be considered a variant of a variant.
-It can be framed inside of the wider literature of *Pure Exploration* multi-armed bandit problems.
-In particular, it shares characteristics with the *Top-$m$* problem.
-This problem is concerned with finding the $m$ best arms as described by the means of their corresponding distributions.
-This in turn is similar to the *combinatorial bandit* problem, which also aims at finding the $m$ best arms.
-However, it is able to pull several arms at once: Think of an online shop that shows five recommended products on a product detail page.
-These five recommended products might each be represented by an arm, and we look for the products with the largest mean conversion rate.
-The thresholding bandit problem we discuss here, however, is concerned with pulling a single arm at a time.
-And so a more appropriate situation is that of a website presenting a banner.
-Again, think of an online shop trying to promote a certain category.
-The content team came up with a number of different designs for the banner, and it's not clear how many click-throughs they will gather.
-
-The idea now is that we would like to classify the banners into two distinct groups: A group with mean conversion rates $\mu_i$ below threshold $\tau$, and a group with mean conversion rates $\mu_i$ above threshold $\tau$.
-This might be the optimization problem when we are concerned with not falling below a certain minimum level click-through rate with the banners we're choosing.
-
-If it turns out that in general we can find relatively quickly whether arms are above or below a threshold, then this kind of test can be used to safeguard against very bad versions in a test.
-Before we move to a Top-$m$ test, we might want to run a thresholding version and then continue only with the arms classified into the group above the threshold.
-This might be justified when adjusting parts of the checkout process of an online shop, where the conversion rate or the average order value should not drop below a threshold.
+# Thresholding Bandit Problem \label{Chapter_TBM}
+
+To introduce the thresholding bandit problem, consider a game in which the learner is tasked to find those slot machines within a row of $K$ slot machines in a casino that give a mean payoff larger than a fixed threshold $\tau$, for example $\tau = 0$.
+The learner cannot pull all slot machines at the same time.
+Instead, he acquires samples sequentially from one slot machine at a time to learn about their payoff structure.
+The learner has a budget of $T$ slot machine pulls.
+After $t-1$ samples, the learner has observed $T_i(t-1)$ samples from slot machine $i$.
+The payoffs $X_{i,1}, ..., X_{i,T_i(t-1)}$ are drawn from the payoff distribution $\nu_i$ underlying the slot machine $i$.
+At time $t$, the learner considers the payoffs he observed so far in order to choose the next slot machine he would like to pull.
+His decision is lead by the goal to classify the slot machines with distribution $\nu_i$ and mean payoff $\mu_i$ after $T$ samples as being above or below the threshold with error probability as small as possible.
+
+The thresholding bandit problem can thus be framed in the wide literature on sequential sampling strategies.
+While its name is reminiscient of the multi-armed bandit setting, the thresholding bandit problem is more akin to best arm identification and Top-$m$ identification problems due to its focus on exploration: While the classical multi-armed bandit problems are concerned with cumulative regret which increases *during* sampling, best arm identification and thresholding bandits collect loss only once *after* the sampling procedure (compare Garivier and Kaufmann, 2016; Kaufmann et al., 2016; Kaufmann and Kalyanakrishnan, 2013).
+Furthermore, as there arises an implicit threshold between the means of the $m$-th best arm and the $m+1$-th best arm (Kaufmann et al., 2016; Kaufmann and Kalyanakrishnan, 2013), algorithms for the Top-$m$ identification problem classify arms at least implicitly as being above or below a threshold.
+The two settings are thus very related.
 
 ## Setup
+
+Consider a setting of $i=1, ..., K$ unknown probability distributions $\nu_i$.
+To stick with the idea of multi-armed bandits, we call those distributions arms, and observations from those arms rewards (Bubeck and Cesa-Bianchi, 2012).
+The learner is interested in learning about the structure of the arms; in particular, he would like to estimate the means $\mu_1, ..., \mu_K$ by sequentially drawing observations $X_{i,1}, X_{i,2}, ...$ from each arm.
+However, at time $t$ the learner cannot observe a reward from every distribution but must select a single arm $I_t$ from which he would like to observe the reward $X_{I_t,t}$.
+An adaptive sampling strategy makes the decision of which arm to pull usually by computing an index $B_i(t)$ for each arm.
+If $T_i(t)$ is the number of samples observed until time $t$ for arm $i$, then $B_i(t)$ is a function of the past rewards $X_{i,1}, ..., X_{i,T_i(t)}$ observed for arm $i$, and w.l.o.g.
+$I_t = \arg \min_{i = 1,...K} B_i(t)$.
+The set of indices can be called strategy (Kaufmann et al., 2012) which makes it clear that the strategy is adapted as more observations are collected.
+Strategies of this kind are also called index policies.
+
+What index proves to be useful is determined by the loss function with which the decisions of the algorithm are evaluated.
+While many problems are concerned with finding the arm with the largest mean $\mu_i$, in which algorithms collect loss either cumulatively (Auer and Cesa-Bianchi, 2012) or once at the end of the sampling (Kaufmann et al., 2016), the thresholding bandit problem considers a slightly different loss function.
+Consider a fixed threshold value $\tau \in \mathbb{R}$ and an epsilon interval $\tau \pm \epsilon$ around the threshold for $\epsilon \geq 0$.
+
+------------ Old
 
@@
 
-**Remark**: Obviously, the APT algorithm tends to pull arms more often with corresponding mean close to the threshold and interval (small $\hat{\Delta}_i(t))$.
+The APT algorithm tends to pull arms more often with corresponding mean close to the threshold and interval (small $\hat{\Delta}_i(t))$.
 This makes sure that more evidence is gathered on arms which appear to be inherently difficult to classify based on the samples collected until time $T_i(t)$, as these arms stifle the confidence the most.
@@
 In this way, the algorithm tries to distribute the budget $T$ over all arms so as to define a sampling rule optimizing the confidence of the final decision.
+
+Locatelli et al. (2016) show that the APT algorithm is optimal in the sense that the upper bound on its expected loss reaches the lower bound for the expected loss.
+
+\newpage
+
+## Lower Bound: Theorem and Proof
+
+\begin{theorem}[Theorem 1, Locatelli et al., 2016] 
+\label{theorem:Locatelli2016Theorem1}
+For any sequence of gaps $(d_k)_k$, define a finite set of problems with Gaussian distributions with means corresponding to the gaps, and with variance 1.
+Lower bound the largest probability of error among these problems for the best possible algorithm as follows.
+Let $K,T \geq 0$.
+Let for any $i \leq K$, $d_i \geq 0$.
+Let $\tau \in \mathbb{R}, \epsilon > 0$.
+
+For $0 \leq i \leq K$, we write $\mathcal{B}^i$ for the problem where the distribution of arm $j \in \{1, \dots, K\}$ is $\mathcal{N}(\tau+d_i+\epsilon, 1)$ if $i \neq j$ and $\mathcal{N}(\tau-d_i-\epsilon, 1)$ otherwise.
+For all these problems, $H := H_{\tau, \epsilon} = \sum_i (d_i+2\epsilon)^{-2}$ is the same by definition.
+
+It holds that for any bandit algorithm,
+
+\begin{equation*}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) \geq \exp(-3T/H-4 \log(12(\log(T)+1)K)),
+\end{equation*}
+
+where $\mathbb{E}_{\mathcal{B}^i}$ is the expectation according to the samples of problem $\mathcal{B}^i$.
+\end{theorem}
+
+*Proof of Theorem \ref{theorem:Locatelli2016Theorem1}*: In Theorem \ref{theorem:Locatelli2016Theorem1} of Locatelli et al.
+(2016), a lower bound for the thresholding bandit problem is shown.
+The basic idea is as follows.
+The problem formulation considered in the paper describes bandit problems for sub-Gaussian distributions.
+To show a lower bound, we show that every algorithm is expected to make a certain error even if we restrict ourselves to a very restricted scenario.
+Even then, any algorithm will have a certain level of risk with which it cannot distinguish between the actual setting and slightly changed settings (under which the former answer leads to regret).
+
+To be more specific, consider a case in which we set $\tau = 0$ and $\epsilon = 0$ w.l.o.g.
+If we then choose all arms to have normally distributed feedback with means $\mu_i$, we see that for each arm $i$ the distance from the threshold is given by $\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i$.
+Thus, assuming a variance of 1 for every arm, we have for every arm the distribution $\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)$.
+Furthermore, define for each arm $i \in \{1, \dots, K\}$ the alternative distribution $\nu_i' = \mathcal{N}(-\Delta_i,1)$.
+It is easy to see that in this case, this is equivalent to a "flip around the threshold".
+Arms that originally have a mean larger than the threshold have a mean smaller than the threshold after the flip.
+
+The idea now is that every arm $i \in \{1,\dots,K\}$ generates a sample for every time point $t\in \{1, \dots, T\}$ from its distribution $\nu_i$ before the algorithm starts to choose arms.
+Thus, we have a $T \times K$ table of realized observations from the product distribution given by $\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K$.
+This is a product distribution where the $K$ different means all lie above the threshold.
+We would hope that an algorithm classifies the means accordingly.
+However, we will show in what follows that any algorithm makes a certain error by not being able to distinguish $\mathcal{B}^0$ from at least one of $K$ alternative product distributions $\mathcal{B}^i, i \in \{1, \dots, K\}$, of which each differs only slightly in one arm from the original distribution, and has the same overall complexity (as defined by $H = \sum_{i=1}^K (\Delta_i)^{-2}$).
+We require $K$ different distributions so that an arm sampling arm $i$ very often for some reason will not have a smaller lower bound by chance.
+
+For each of the $K$ arms, we introduce an alternative model of the following kind.
+Before the start of the algorithm, we introduce a slight variation in the setup.
+The idea is similar to how one can switch arms in the pure exploration setup for multi-armed bandits (compare Audibert et al., 2010; Garivier & Kaufmann, 2016) to "confuse" any algorithm without introducing additional complexity to the specified problem.
+However, since we do not compare arms directly with each other in the thresholding bandit problem (switching arms would still keep all means above the threshold), we instead need to flip an arm $i$ with respect to the threshold in order to get the alternative model $\mathcal{B}_i$.
+Since the threshold is $\tau = 0$, we have for the flipped arm the new distribution $\nu_i'$ as defined above.
+Indeed, we can define the new product distribution $B^i = \nu_1^i \otimes \dots \otimes \nu_K^i$ where for $k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}$.
+This flipping of the arm corresponds to multiplying all random variables $X_{i,t}$ of arm $i$ by $-1$.
+
+As in Locatelli et al.
+(2016), we let for $i \leq K$, $\mathbb{P}_{\mathcal{B}^i}$ define the probability distribution describing all samples that a bandit strategy can potentially collect up to horizon $T$, i.e.
+according to the samples $(X_{k,s})_{k\leq K, s \leq T} \sim (\mathcal{B}^i)^{\otimes T}$.
+$(T_k)_{k\leq K}$ denotes the number of samples collected on arm $k$ until time $T$.
+
+### Reminder about the goal of the proof
+
+At this point, we have defined a finite set of problems of Gaussian distributions with fixed variance 1 for a given set of set of gaps between the means of the distributions and the threshold, $(d_k)_k$.
+We will now proof a lower bound on the worst case regret of any algorithm; that is, the maximum error probability that even the best algorithm makes on this problem.
+
+### Statistical Decision
+
+Given our formulation of the regret, the expected regret $\mathbb{E}[\mathcal{L}(T)]$ corresponds directly to the probability of making a wrong classification of any of the $K$ means.
+In general, let $g$ be a binary decision function, and define $\Omega = \{g = 0\}$ and $\Omega^C = \{g = 1\}$.
+Assume that the decision $T$ distinguishes between two states of the world, $H_0$ and $H_1$.
+Then our overall error probability is given by $P_{H_0}(g=1) + P_{H_1}(g = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)$.
+
+In our case, $H_0$ may correspond to the state in which we have $\mathcal{B}^0$, and $H_1$ corresponds to the case where any arm has been flipped, $\mathcal{B}^i$.
+Furthermore, we consider the events in which the algorithm, making the decision, classifies arm $i$ as being above the threshold: $\mathcal{A}_i = \{i \in \hat{S}_\tau\}$.
+The event on which all arms are being classified as above the threshold is consequently given by $\mathcal{A} = \bigcap \mathcal{A}_i$.
+However, Theorem 1 does not bound the overall regret, but the maximum error probability on the $K+1$ different models.
+We can write this now as
+
+\begin{align}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big) \\
+& = \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
+\end{align}
+
+In order to give a bound on above equation, we start by considering $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$.
+This probability can be written as the expected change in the likelihood of observed data when moving from distribution $P_{\mathcal{B}_0}$ to $P_{\mathcal{B}_i}$, times the probability under the original state.
+In other words, the probability of event $\mathcal{A}_i$ under state $\mathcal{B}^i$ is given as the probability of $\mathcal{A}_i$ under the (original) state $\mathcal{B}^0$ multiplied by a factor.
+This factor describes whether the new distribution increases or decreases the probability of the event, and is given by the change in the data likelihoods due to moving from $\mathcal{B}^0$ to $\mathcal{B}^i$, expressed as the expected likelihood ratio under $\mathcal{B}^0$.
+By definition, the latter is equal to the empirical Kullback-Leibler divergence of the two distributions.
+
+We will define the change of distribution in terms of the empirical log-likelihood for our case.
+Then, we will show how to replace the log-likelihood by the empirical Kullback-Leibler divergence.
+So let us first introduce the empirical Kullback-Leibler divergence.
+
+Let every $\nu_i, \nu_i'$ be dominated by the Lebesgue measure $\lambda$.
+Then their density functions are given by $f_i = \frac{\der \nu_i}{\der \lambda}$ and $f_i' = \frac{\der \nu_i'}{\der \lambda}$ respectively.
+For $T \geq t \geq 0$, define the empirical Kullback-Leibler divergence as
+
+\begin{align*}
+\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log(\frac{\der \nu_k'}{\der \nu_k}(X_{k,s})) \\
+& = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
+& = \frac{1}{t} \log \big( \prod_{s=1}^{t} \frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
+& \stackrel{\text{iid}}{=} \frac{1}{t} \log \big( \frac{f_k'(X_{k,1}, \dots,X_{k,t})}{f_k(X_{k,1}, \dots,X_{k,t})} \big) \\
+& = \frac{1}{t} \log \big( \text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k) \big)
+\end{align*}
+
+Since we consider Gaussian distributions with variance 1, we have density functions $f_i(x) \propto \exp \big(-\frac{1}{2} (x-\Delta_i)^2\big)$ and $f_i'(x) \propto \exp \big(-\frac{1}{2} (x+\Delta_i)^2\big)$.
+Plugging this into the above definition of the empirical Kullback-Leibler divergence, we easily see
+
+\begin{align*}
+\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{\exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2\big)}{\exp \big(-\frac{1}{2} (X_{k,s}-\Delta_k)^2\big)} \big) \\
+& = \frac{1}{t} \sum_{s=1}^{t} \log \big( \exp(-\frac{1}{2} (X_{k,s}+\Delta_k)^2 + \frac{1}{2} (X_{k,s}-\Delta_k)^2) \big) \\
+& = - \frac{1}{t} \sum_{s=1}^{t} 2 X_{k,s} \Delta_k
+\end{align*}
+
+### Change of Distribution
+
+We are now ready to state the change of distribution.
+As alluded to above, we consider how the probability changes for the event $\mathcal{A}_i$ when we move from $\mathcal{B}^0$ to $\mathcal{B}^i$.
+When flipping arm $i$, we only changed the samples of this arm, that is, the first $T_i$ observations we got from arm $i$ the algorithm took.
+The change of distribution is then defined as:
+
+\begin{align*}
+\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \text{LR}((X_{i,1}, \dots,X_{i,T_i}), \nu_i', \nu_i) ] \\
+& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ]
+\end{align*}
+
+Obviously, $\hat{\KL}_{i,T_i}$ depends on the realized samples $X_{i,1}, \dots,X_{i,T_i}$.
+Consequently, we need to find a bound on $\hat{\KL}_{i,T_i}$ itself to incorporate the uncertainty involved in this metric.
+
+### Concentration of the Empirical Kullback-Leibler Divergence
+
+For our problem, the Kullback-Leibler divergence of $\nu_k'$ from $\nu_k$ is given by $\KL_k := KL(\nu_k', \nu_k) = 2\Delta_k^2$.
+
+It is easy to see that
+
+\begin{equation*}
+|\hat{\KL}_{k,t} - \KL_{k,t}| = |-\frac{2}{t} \Delta_k \sum_{s=1}^{t}(X_{k,s} - \Delta_k)|
+\end{equation*}
+
+itself is a normally distributed random variable with mean zero and a variance decreasing in $t$.
+Thus, one can show as in Locatelli et al.
+(2016) that $\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4$ for the event
+
+\begin{equation}
+\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}}\}. \label{LocatelliTheorem1EventXi}
+\end{equation}
+
+Thus, in order to bound the empirical Kullback-Leibler divergence in our change of measure, we can consider the intersection of $\mathcal{A}_i$ and $\xi$ as follows and plug in the bound on event $\xi$:
+
+\begin{align*}
+\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
+& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
+& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
+\end{align*}
+
+Two things are left to do: With $T_i$, we still have one random variable left which we cannot leave in our bound.
+Second, we are actually not interested in $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$ but in $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$.
+
+### Bounding $T_i$ for $\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$
+
+Part of our bound is $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$, so let's continue with that.
+In general it holds that $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K}\sum_{i=1}^K X_i$.
+Thus we can write:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
+& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
+& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
+\end{align*}
+
+where the second line is again the intersection of $\mathcal{A}_i$ and $\xi$ as before in order to apply the change of distribution in the third line.
+
+What is left to show before we have our final bound is a bound on $T_i$.
+To show that any algorithm has a certain bound on its error, it only makes sense that every arm has to pulled at least a certain amount of times.
+Consequently, no arm should be pulled exclusively.
+
+First, let $a = \Delta_i \sqrt{T_i}$ and $b = 4\sqrt{\log((4\log(T)+1)K)}$. Then use $ab \leq a^2 + b^2$ to write $ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)$. And so:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) ]
+\end{align*}
+
+Furthermore, we know that the sum of the individual arm pulls has to be equal to the overall number of pulls (equal to the budget in the fixed budget sense), $\sum_i T_i = T$, and furthermore we know that $T_i>0$.
+The latter holds since any reasonable algorithm has to check each arm at least once in our setup.
+This is because we need to check each arm's performance in comparison to the threshold.
+Thus it is easy to show that $\exists i: T_i \leq \frac{T}{H \Delta_i^2} = \frac{T}{(\sum_{i=1}^{K} \Delta_i^{-2}) \Delta_i^2}$.
+To see this, assume the opposite: $\forall i: T_i > T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2}$.
+This implies however $\sum_{i=1}^K T_i > \sum_{i=1}^K T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2} = T \cdot 1 = T$ which is a contradiction.
+
+So we can write $(\Delta_i \sqrt{T_i})^2 \leq \frac{T}{H}$. We use $\mathcal{A} = \cap_{i=1}^K \mathcal{A}_i$ to write:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big] \\
+& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}{K} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big]
+\end{align*}
+
+We write $\frac{1}{K} \sum_{i=1}^K \exp(-3T_i \Delta_i^2) \geq \frac{1}{K} \sum_{i=1}^K \exp(-3 T/H) = \exp(-3 T/H)$. Thus:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i) \exp(-16 \log(4(\log(T)+1)K)) ] \\
+& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
+& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
+& = \mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
+\end{align*}
+
+### Bringing everything together
+
+Consider again the risk which we need to bound from equation \eqref{LocatelliTheorem1ExpRegret}.
+We bound the maximum expected loss over all $\mathcal{B}_i$.
+By again using the fact that in general $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K} \sum_{i = 1}^K X_i$, we plug in our previous calculations:
+
+\begin{align}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
+& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \label{LocatelliTheorem1DefinitionOfRisk}
+\end{align}
+
+From \eqref{LocatelliTheorem1EventXi} we know that for any $i \in \{0, \dots, K\}$, $\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4$.
+Following the argument in Locatelli et al.
+(2016), we now consider two cases: $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2$ and $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2$.
+In the former case, we can plug in the two probabilities into \eqref{LocatelliTheorem1DefinitionOfRisk}.
+If $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2$ and $\mathbb{P}_{\mathcal{B}^0}(\xi) \geq 3/4$, then $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \geq 1/4$.
+Thus:
+
+\begin{align*}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
+& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \\
+& \geq \frac{1}{8} \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
+\end{align*}
+
+where we drop the second summand of the second line so that the inequality holds.
+
+On the other hand, when $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2$, then we know that $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \leq 1/2$ for any $\mathbb{P}_{\mathcal{B}^0}(\xi)$.
+At the same time $1-\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \geq 1/2$.
+Consequently, $1/4 \leq \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \leq 1/2$, while
+$\frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) \geq 0$.
+And so the stronger lower bound in that case is, as noticed by Locatelli et al.
+(2016), given simply by
+
+\begin{align*}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
+& \geq 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \\
+& \geq \frac{1}{2}
+\end{align*}
+
+\newpage
+
+## Upper Bound on Expected Loss of APT
+
+\begin{theorem}[Locatelli et al., 2016] \label{theorem:LocatelliTheorem4}
+Let $K \geq 0$, $T \geq 2K$, and consider a problem $\mathbb{B}$. Assume that
+all arms $\nu_k$ of the problem are R-sub-Gaussian with means $\mu_k$. Let $\tau
+\in \mathbb{R}, \epsilon \geq 0$.
+
+Algorithm APT's expected loss is upper bounded on this problem as 
+\begin{equation*} \mathbb{E}(\mathcal{L}(T)) \leq \exp
+(-\frac{1}{64R^2}\frac{T}{H} + 2 \log (T) + 1)K)) \end{equation*}
+
+where we remind that $H = \sum_i (|\mu_i - \tau | + \epsilon)^{-2}$ and where
+$\mathbb{E}$ is the expectation according to the samples of the problem.
+\end{theorem}
+
+*Proof of Theorem \ref{theorem:LocatelliTheorem4}:*
+
+In order to upper bound the expected loss of the APT algorithm, we want to find an event on which the algorithm would correctly seperate arms from the threshold, that is, on the event a seperation condition holds.
+We then want to show that with large probability, this *favorable* event does indeed hold.
+Consequently, the expected loss (probability of an error) will correspond to the probability that the favorable event does not hold after all as this leads the seperation condition to fail, and the algorithm to classify at least one arm incorrectly.
+
+While this is the general idea, we have to jump between seperation condition, favorable event, and large probability.
+
+### Separation Condition
+
+As noted in Zhong et al. (2017), a simple requirement to correctly classify arms at the final round is the following. For every arm $i \in \{1, ..., K\}$ at round $T$,
+
+$$
+\hat{\mu}_{i,T_i(n)} \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
+$$
+or
+
+$$
+\hat{\mu}_{i,T_i(n)} \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
+$$
+Or simply in terms of the gap between the arm and the threshold as used as index by the algorithm,
+
+$$
+| \hat{\mu}_{i, T_i(n)} - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
+$$
+
+Intuitively, the conditions make sense as they ensure that the current mean estimate is closer to the true mean than to the threshold.
+Consequently, there is no possible arrangement left in which the condition would hold, but the arm be classified incorrectly.
+Assuming $\mu_i < \tau$ and $\epsilon = 0$, an incorrect classification would require $\mu_i < \tau \leq \hat{\mu_i}$.
+But then  $| \hat{\mu}_{i, T_i(n)} - \mu_i | \geq |\mu_i - \tau|$, violating the separation condition.
+
+Thus, we need to show that in the very final round, this condition holds for every arm $i \in \{1,...,K\}$ with large probability.
+Or more precisely, we need to derive a bound on the probability with which this does not hold.
+
+### The Favorable Event
+
+The separation condition gives a good idea of what event we need to hold in order to make a correct classification.
+The smaller the deviation of the empirical mean from the population mean, the more difficult it is for the classification to be wrong.
+Moreover, if the mean and empirical mean are identical, then the classification is correct independent of the threshold.
+And furthermore, the closer the mean and the threshold are, the better the estimate must be for a correct classification.
+
+Having to bound the absolute deviation of the sample mean from the population mean is a very thankful operation. Define the favorable event $\xi$ as
+
+$$
+\xi = \Big\{\forall i \in \mathbb{A}, \forall s \in \{1,...,T\} : |\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}} \Big\}.
+$$
+
+We want the probability that this favorable event occurs to be large, that is, the probability that the deviation is small, such that the separation condition holds with large probability.
+Indeed, we bound the deviation for *all* arms $i \leq K$ and for *every* round $s \leq T$.
+Using some Chernoff Hoeffding bounds, we are able to write
+
+$$
+\mathbb{P}(\xi) \geq 1 - 2(\log(T) +1)K \exp(-\frac{T\delta^2}{2R^2H})
+$$
+
+### Need to Bound $T_i$
+
+We now have that with large probability, the favorable event holds. On the favorable event, we have for every arm $i$:
+
+$$
+| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}
+$$
+
+The deviation of arm $i$ at time $t$ depends on how large $H$, $T$, and $T_i(t)$ are.
+While $t$, $H$, $T$ are deterministic, the number of times arm $i$ has been pulled at round $t$, $T_i(t)$, is a random variable.
+In order to know how large the probability of the favorable event is (and thus the error probability), we need to know what realistic values for $T_i(t)$ will be.
+Put differently: To ensure a deviation smaller than $\sqrt{\frac{T\delta^2}{HT_i(t)}}$ for arm $i$, we need to ensure that arm $i$ has been pulled at least $T_i(t)$ times.
+As usual in multi-armed bandits, and different from uniform sampling, the number of pulls is a random variable that also depends on how often other arms are pulled.
+In general, we do not want each arm to be pulled an equal amount, but each arm should be pulled some times, and not too many times.
+This especially holds for our exploration setting.
+
+Thus, in order to check that the deviation of arm $i$ really is small enough for the separation condition to hold on the favorable event, we need to bound the number of pulls of every arm from below.
+
+### Characteristics of a Frequently Pulled Arm (Lower Bound on $T_k(T)$)
+
+Given that we do not follow a uniform sampling strategy, we know that at time $T$, some arms will have been pulled more frequently than others.
+In particular, some arms will have been pulled more than $T/K$ times.
+How often an arm is pulled can be related to the individual arm's contribution to the overall complexity measure.
+Let $h_i$ be a measure of arm $i$'s individual problem complexity and write for the overall problem complexity
+
+$$
+H = \sum_{i = 1}^{K} h_i.
+$$
+
+Then arm $i$ contributes a share of $h_i/H$ to the overall problem complexity.
+We can now show that there exists an arm that has been pulled at least as often as the share of his complexity contribution.
+
+Given the initialization of the APT algorithm, every arm is pulled once initially.
+Consequently, there is a budget of $T-K$ rounds left after the initialization.
+As shown in Locatelli et al.
+(2016), there exists an arm $k$ that has been pulled after the initialization ($\geq 2$ pulls) and for which at the final round $T$ holds: $T_k(T) - 1 \geq \frac{(T-K)h_k}{H}$.
+This can be shown by a quick contradiction proof.
+Assume the opposite, that is
+
+$$
+\forall i \in \{1,...,K\}: T_i(T) - 1 < \frac{(T-K)h_i}{H}
+$$
+
+Consequently, at time $T$, we would have pulled across all arms $\sum_{i=1}^KT_i(T)-1$ times. If the previous assumption holds, we would not have used the entire budget:
+
+$$
+\sum_{i=1}^K T_i(T)-1 < \sum_{i=1}^K \frac{(T-K)h_i}{H} = (T-K)\sum_{i=1}^K \frac{h_i}{H} = T-K
+$$
+
+This is a contradiction, since as an requirement to the algorithm we have that $\sum_{i=1}^K T_i(T)-1 = (T-K)$, that is, we use the entire budget of samples.
+
+Another such requirement has been that $T>2K$. Plugging this in gives 
+$$
+T_k(T) - 1 \geq \frac{(T-K)h_k}{H} \leq \frac{(T-1/2T)h_k}{H} = \frac{Th_i}{2H}
+$$
+
+Now we know how often the arm has been pulled at the very end.
+That does not mean that $k$ has been pulled at time $T$.
+Thus we consider the time $t \leq T$ at which arm $k$ is pulled for the last time.
+We get (!!!!!SHOOOOWWW THIIIISSSS!!!!!!!!!)
+
+$$
+T_k(t) \geq T_k(T) - 1 \geq \frac{Th_i}{2H}.
+$$
+
+This gives us a lower bound on how often arms are pulled that are pulled frequently relative to their contribution to the problem complexity.
+Now we need a lower bound on $T_i(T)$ for every other arm $i$.
+
+### Lower Bound on $T_i(T)$
+
+Consider again as before the round $t$ in which arm $k$ is pulled for the very last time.
+Since the APT algorithm minimizes at every round $s$ the index $B_j(s)$, and pulls the arm with the smallest index, we know that arm $k$ must have had the smallest index at round $t$.
+We have:
+
+$$
+B_k(t) \leq B_i(t) \Leftrightarrow \sqrt{T_k(t)}\hat{\Delta}_k(t) \leq \sqrt{T_i(t)} \hat{\Delta}_i(t)
+$$
+
+One can already expect that this can be used to derive a lower bound on $T_i(t)$ on the RHS, and this is exactly what we do.
+
+On the LHS, we will plug in the lower bound for $T_k(t)$ derived before.
+Additionally bounding $\Delta_k(t)$ from below, and $\hat{\Delta}_i(t)$ from above using the favorable event will give the desired lower bound.
+
+Thus assume we are on the favorable event $\xi$ with large probability. we consequently have
+
+$$
+| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}.
+$$
+
+As shown in Locatelli et al. (2016), one can use the reverse triangle inequality to get:
+
+$$
+|\hat{\mu}_i(t) - \mu_i| = |(\hat{\mu}_i(t) - \tau) - (\mu_i - \tau)| \geq || \hat{\mu}_i(t) - \tau | - |\mu_i - \tau|| \geq |(|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i - \tau| + \epsilon)| \geq |\hat{\Delta}_i(t) - \Delta_i|
+$$
+
+If we combine this with the favorable event, we get
+
+$$
+\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}} \leq \hat{\Delta}_k(t) \leq \Delta_k + \sqrt{\frac{T\delta^2}{HT_k(t)}}
+$$
+
+and similar for $\hat{\Delta}_i$.
+
+We can now lower bound the LHS of the indices as
+
+$$
+\Big(\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}}\Big) \sqrt{T_k(t)} \leq B_k(t)
+$$
+
+$$
+\Big(\Delta_k - \sqrt{\frac{2}{h_k}}\delta \Big) \sqrt{\frac{Th_k}{2H}} \leq B_k(t)
+$$
+
+At this point, it is useful to have a well chosen complexity measure. If we set $h_i = \frac{1}{\Delta_i^2}$ as in Locatelli et al. (2016), we get
+
+$$
+\Big(\Delta_k - \sqrt{2}\delta \Delta \Big) \sqrt{\frac{T}{2H\Delta_k^2}} \leq B_k(t)
+$$
+
+which can be now be reduced to a form that is not specific to $k$:
+
+$$
+\Big( \frac{1}{\sqrt{2}} - \delta \Big) \sqrt{\frac{T}{H}} \leq B_k(t).
+$$
+
+Now we need to get rid of $\hat{\Delta}_i$ in order to bound $T_i(t)$. Thus, we bound the RHS again using the favorable event much as we did for the LHS:
+
+$$
+B_i(t) = \hat{\Delta}_i \sqrt{T_i(t)} \leq \Big(\Delta_i + \sqrt{\frac{T\delta^2}{HT_i(t)}}\Big) \sqrt{T_i(t)} \leq \Delta_i \sqrt{T_i(t)} + \delta \sqrt{\frac{T}{H}}
+$$
+
+As in Locatelli et al. (2016) we use the fact that by definition $\Delta$ and $\hat{\Delta}$ are positive in order to square both sides and write
+
+$$
+(1 - 2\sqrt{2}\delta)^2 \frac{T}{2H\Delta^2_i} \leq T_i(t) \leq T_i(T)
+$$
+
+We thus have derived a lower bound on the amount of pulls for any arm.
+That means that we can show that no arm is pulled an insufficient amount of times with large probability, and that consequently the favorable event hold and the estimated mean is sufficienctly separated from the threshold.
+
+### Check Separation Condition
+
+As the last step, we need to check whether the lower bound on the pulls of any arm suffices to ensure that the separation condition holds on the favorable event.
+That means, given $T_i(T) \geq (1-2\sqrt{2}\delta)^2 \frac{T}{2H\Delta_i^2}$, do we have $|\hat{\mu}_i(T) - \mu | \leq \frac{\Delta}{2}$ on the favorable event $\xi = \Big\{|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}}\Big\}$?
+
+To check, we plug the lower bound into the favorable event and get
+
+$$
+|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}} \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}
+$$
+Using $\delta = (4\sqrt{2})^-1$ as in Locatelli et al. (2016), we get
+
+$$
+|\hat{\mu}_i - \mu | \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta} \leq \frac{1}{2}\Delta_i.
+$$
+
+Thus the separation condition still holds for this value of $\delta$.
+
+### Upper Bound on Error Probability
+
+We have seen that on the favorable event $\xi$, which holds with large probability $\mathbb{P}(\xi)$, the separation condition holds as all arms have been pulled a sufficient number of times, such that their estimated mean is close to the true mean.
+All arms are classified correctly, and the algorithm does not suffer a loss.
+On the other hand, we make an error whenever the favorable event does not hold after all; that is, the deviation bound for the mean does not hold.
+At least one arm is misclassified and the arm suffers a loss.
+This occurs with probability $1-\mathbb{P}(\xi)$.
+Consequently, the expected loss is upper bounded by
+
+$$
+\mathbb{E}[L] = 1 - \mathbb{P}(\xi) \leq 2(\log(T)+1)K \exp(-\frac{1}{64R^2}\frac{T}{H}).
+$$
 
@@
 ```
-
-## Lower Bound: Theorem and Proof
-
-\begin{theorem}[Theorem 1, Locatelli et al., 2016] 
-\label{theorem:Locatelli2016Theorem1}
-For any sequence of gaps $(d_k)_k$, define a finite set of problems with Gaussian distributions with means corresponding to the gaps, and with variance 1.
-Lower bound the largest probability of error among these problems for the best possible algorithm as follows.
-Let $K,T \geq 0$.
-Let for any $i \leq K$, $d_i \geq 0$.
-Let $\tau \in \mathbb{R}, \epsilon > 0$.
-
-For $0 \leq i \leq K$, we write $\mathcal{B}^i$ for the problem where the distribution of arm $j \in \{1, \dots, K\}$ is $\mathcal{N}(\tau+d_i+\epsilon, 1)$ if $i \neq j$ and $\mathcal{N}(\tau-d_i-\epsilon, 1)$ otherwise.
-For all these problems, $H := H_{\tau, \epsilon} = \sum_i (d_i+2\epsilon)^{-2}$ is the same by definition.
-
-It holds that for any bandit algorithm,
-
-\begin{equation*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) \geq \exp(-3T/H-4 \log(12(\log(T)+1)K)),
-\end{equation*}
-
-where $\mathbb{E}_{\mathcal{B}^i}$ is the expectation according to the samples of problem $\mathcal{B}^i$.
-\end{theorem}
-
-*Proof of Theorem \ref{theorem:Locatelli2016Theorem1}*: In Theorem \ref{theorem:Locatelli2016Theorem1} of Locatelli et al.
-(2016), a lower bound for the thresholding bandit problem is shown.
-The basic idea is as follows.
-The problem formulation considered in the paper describes bandit problems for sub-Gaussian distributions.
-To show a lower bound, we show that every algorithm is expected to make a certain error even if we restrict ourselves to a very restricted scenario.
-Even then, any algorithm will have a certain level of risk with which it cannot distinguish between the actual setting and slightly changed settings (under which the former answer leads to regret).
-
-To be more specific, consider a case in which we set $\tau = 0$ and $\epsilon = 0$ w.l.o.g.
-If we then choose all arms to have normally distributed feedback with means $\mu_i$, we see that for each arm $i$ the distance from the threshold is given by $\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i$.
-Thus, assuming a variance of 1 for every arm, we have for every arm the distribution $\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)$.
-Furthermore, define for each arm $i \in \{1, \dots, K\}$ the alternative distribution $\nu_i' = \mathcal{N}(-\Delta_i,1)$.
-It is easy to see that in this case, this is equivalent to a "flip around the threshold".
-Arms that originally have a mean larger than the threshold have a mean smaller than the threshold after the flip.
-
-The idea now is that every arm $i \in \{1,\dots,K\}$ generates a sample for every time point $t\in \{1, \dots, T\}$ from its distribution $\nu_i$ before the algorithm starts to choose arms.
-Thus, we have a $T \times K$ table of realized observations from the product distribution given by $\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K$.
-This is a product distribution where the $K$ different means all lie above the threshold.
-We would hope that an algorithm classifies the means accordingly.
-However, we will show in what follows that any algorithm makes a certain error by not being able to distinguish $\mathcal{B}^0$ from at least one of $K$ alternative product distributions $\mathcal{B}^i, i \in \{1, \dots, K\}$, of which each differs only slightly in one arm from the original distribution, and has the same overall complexity (as defined by $H = \sum_{i=1}^K (\Delta_i)^{-2}$).
-We require $K$ different distributions so that an arm sampling arm $i$ very often for some reason will not have a smaller lower bound by chance.
-
-For each of the $K$ arms, we introduce an alternative model of the following kind.
-Before the start of the algorithm, we introduce a slight variation in the setup.
-The idea is similar to how one can switch arms in the pure exploration setup for multi-armed bandits (compare Audibert et al., 2010; Garivier & Kaufmann, 2016) to "confuse" any algorithm without introducing additional complexity to the specified problem.
-However, since we do not compare arms directly with each other in the thresholding bandit problem (switching arms would still keep all means above the threshold), we instead need to flip an arm $i$ with respect to the threshold in order to get the alternative model $\mathcal{B}_i$.
-Since the threshold is $\tau = 0$, we have for the flipped arm the new distribution $\nu_i'$ as defined above.
-Indeed, we can define the new product distribution $B^i = \nu_1^i \otimes \dots \otimes \nu_K^i$ where for $k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}$.
-This flipping of the arm corresponds to multiplying all random variables $X_{i,t}$ of arm $i$ by $-1$.
-
-As in Locatelli et al.
-(2016), we let for $i \leq K$, $\mathbb{P}_{\mathcal{B}^i}$ define the probability distribution describing all samples that a bandit strategy can potentially collect up to horizon $T$, i.e.
-according to the samples $(X_{k,s})_{k\leq K, s \leq T} \sim (\mathcal{B}^i)^{\otimes T}$.
-$(T_k)_{k\leq K}$ denotes the number of samples collected on arm $k$ until time $T$.
-
-### Reminder about the goal of the proof
-
-At this point, we have defined a finite set of problems of Gaussian distributions with fixed variance 1 for a given set of set of gaps between the means of the distributions and the threshold, $(d_k)_k$.
-We will now proof a lower bound on the worst case regret of any algorithm; that is, the maximum error probability that even the best algorithm makes on this problem.
-
-### Statistical Decision
-
-Given our formulation of the regret, the expected regret $\mathbb{E}[\mathcal{L}(T)]$ corresponds directly to the probability of making a wrong classification of any of the $K$ means.
-In general, let $g$ be a binary decision function, and define $\Omega = \{g = 0\}$ and $\Omega^C = \{g = 1\}$.
-Assume that the decision $T$ distinguishes between two states of the world, $H_0$ and $H_1$.
-Then our overall error probability is given by $P_{H_0}(g=1) + P_{H_1}(g = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)$.
-
-In our case, $H_0$ may correspond to the state in which we have $\mathcal{B}^0$, and $H_1$ corresponds to the case where any arm has been flipped, $\mathcal{B}^i$.
-Furthermore, we consider the events in which the algorithm, making the decision, classifies arm $i$ as being above the threshold: $\mathcal{A}_i = \{i \in \hat{S}_\tau\}$.
-The event on which all arms are being classified as above the threshold is consequently given by $\mathcal{A} = \bigcap \mathcal{A}_i$.
-However, Theorem 1 does not bound the overall regret, but the maximum error probability on the $K+1$ different models.
-We can write this now as
-
-\begin{align}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big) \\
-& = \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
-\end{align}
-
-In order to give a bound on above equation, we start by considering $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$.
-This probability can be written as the expected change in the likelihood of observed data when moving from distribution $P_{\mathcal{B}_0}$ to $P_{\mathcal{B}_i}$, times the probability under the original state.
-In other words, the probability of event $\mathcal{A}_i$ under state $\mathcal{B}^i$ is given as the probability of $\mathcal{A}_i$ under the (original) state $\mathcal{B}^0$ multiplied by a factor.
-This factor describes whether the new distribution increases or decreases the probability of the event, and is given by the change in the data likelihoods due to moving from $\mathcal{B}^0$ to $\mathcal{B}^i$, expressed as the expected likelihood ratio under $\mathcal{B}^0$.
-By definition, the latter is equal to the empirical Kullback-Leibler divergence of the two distributions.
-
-We will define the change of distribution in terms of the empirical log-likelihood for our case.
-Then, we will show how to replace the log-likelihood by the empirical Kullback-Leibler divergence.
-So let us first introduce the empirical Kullback-Leibler divergence.
-
-Let every $\nu_i, \nu_i'$ be dominated by the Lebesgue measure $\lambda$.
-Then their density functions are given by $f_i = \frac{\der \nu_i}{\der \lambda}$ and $f_i' = \frac{\der \nu_i'}{\der \lambda}$ respectively.
-For $T \geq t \geq 0$, define the empirical Kullback-Leibler divergence as
-
-\begin{align*}
-\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log(\frac{\der \nu_k'}{\der \nu_k}(X_{k,s})) \\
-& = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
-& = \frac{1}{t} \log \big( \prod_{s=1}^{t} \frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
-& \stackrel{\text{iid}}{=} \frac{1}{t} \log \big( \frac{f_k'(X_{k,1}, \dots,X_{k,t})}{f_k(X_{k,1}, \dots,X_{k,t})} \big) \\
-& = \frac{1}{t} \log \big( \text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k) \big)
-\end{align*}
-
-Since we consider Gaussian distributions with variance 1, we have density functions $f_i(x) \propto \exp \big(-\frac{1}{2} (x-\Delta_i)^2\big)$ and $f_i'(x) \propto \exp \big(-\frac{1}{2} (x+\Delta_i)^2\big)$.
-Plugging this into the above definition of the empirical Kullback-Leibler divergence, we easily see
-
-\begin{align*}
-\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{\exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2\big)}{\exp \big(-\frac{1}{2} (X_{k,s}-\Delta_k)^2\big)} \big) \\
-& = \frac{1}{t} \sum_{s=1}^{t} \log \big( \exp(-\frac{1}{2} (X_{k,s}+\Delta_k)^2 + \frac{1}{2} (X_{k,s}-\Delta_k)^2) \big) \\
-& = - \frac{1}{t} \sum_{s=1}^{t} 2 X_{k,s} \Delta_k
-\end{align*}
-
-### Change of Distribution
-
-We are now ready to state the change of distribution.
-As alluded to above, we consider how the probability changes for the event $\mathcal{A}_i$ when we move from $\mathcal{B}^0$ to $\mathcal{B}^i$.
-When flipping arm $i$, we only changed the samples of this arm, that is, the first $T_i$ observations we got from arm $i$ the algorithm took.
-The change of distribution is then defined as:
-
-\begin{align*}
-\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \text{LR}((X_{i,1}, \dots,X_{i,T_i}), \nu_i', \nu_i) ] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ]
-\end{align*}
-
-Obviously, $\hat{\KL}_{i,T_i}$ depends on the realized samples $X_{i,1}, \dots,X_{i,T_i}$.
-Consequently, we need to find a bound on $\hat{\KL}_{i,T_i}$ itself to incorporate the uncertainty involved in this metric.
-
-### Concentration of the Empirical Kullback-Leibler Divergence
-
-For our problem, the Kullback-Leibler divergence of $\nu_k'$ from $\nu_k$ is given by $\KL_k := KL(\nu_k', \nu_k) = 2\Delta_k^2$.
-
-It is easy to see that
-
-\begin{equation*}
-|\hat{\KL}_{k,t} - \KL_{k,t}| = |-\frac{2}{t} \Delta_k \sum_{s=1}^{t}(X_{k,s} - \Delta_k)|
-\end{equation*}
-
-itself is a normally distributed random variable with mean zero and a variance decreasing in $t$.
-Thus, one can show as in Locatelli et al.
-(2016) that $\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4$ for the event
-
-\begin{equation}
-\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}}\}. \label{LocatelliTheorem1EventXi}
-\end{equation}
-
-Thus, in order to bound the empirical Kullback-Leibler divergence in our change of measure, we can consider the intersection of $\mathcal{A}_i$ and $\xi$ as follows and plug in the bound on event $\xi$:
-
-\begin{align*}
-\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
-\end{align*}
-
-Two things are left to do: With $T_i$, we still have one random variable left which we cannot leave in our bound.
-Second, we are actually not interested in $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$ but in $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$.
-
-### Bounding $T_i$ for $\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$
-
-Part of our bound is $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$, so let's continue with that.
-In general it holds that $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K}\sum_{i=1}^K X_i$.
-Thus we can write:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
-& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
-& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
-\end{align*}
-
-where the second line is again the intersection of $\mathcal{A}_i$ and $\xi$ as before in order to apply the change of distribution in the third line.
-
-What is left to show before we have our final bound is a bound on $T_i$.
-To show that any algorithm has a certain bound on its error, it only makes sense that every arm has to pulled at least a certain amount of times.
-Consequently, no arm should be pulled exclusively.
-
-First, let $a = \Delta_i \sqrt{T_i}$ and $b = 4\sqrt{\log((4\log(T)+1)K)}$. Then use $ab \leq a^2 + b^2$ to write $ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)$. And so:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) ]
-\end{align*}
-
-Furthermore, we know that the sum of the individual arm pulls has to be equal to the overall number of pulls (equal to the budget in the fixed budget sense), $\sum_i T_i = T$, and furthermore we know that $T_i>0$.
-The latter holds since any reasonable algorithm has to check each arm at least once in our setup.
-This is because we need to check each arm's performance in comparison to the threshold.
-Thus it is easy to show that $\exists i: T_i \leq \frac{T}{H \Delta_i^2} = \frac{T}{(\sum_{i=1}^{K} \Delta_i^{-2}) \Delta_i^2}$.
-To see this, assume the opposite: $\forall i: T_i > T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2}$.
-This implies however $\sum_{i=1}^K T_i > \sum_{i=1}^K T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2} = T \cdot 1 = T$ which is a contradiction.
-
-So we can write $(\Delta_i \sqrt{T_i})^2 \leq \frac{T}{H}$. We use $\mathcal{A} = \cap_{i=1}^K \mathcal{A}_i$ to write:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}{K} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big]
-\end{align*}
-
-We write $\frac{1}{K} \sum_{i=1}^K \exp(-3T_i \Delta_i^2) \geq \frac{1}{K} \sum_{i=1}^K \exp(-3 T/H) = \exp(-3 T/H)$. Thus:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i) \exp(-16 \log(4(\log(T)+1)K)) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
-& = \mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
-\end{align*}
-
-### Bringing everything together
-
-Consider again the risk which we need to bound from equation \eqref{LocatelliTheorem1ExpRegret}.
-We bound the maximum expected loss over all $\mathcal{B}_i$.
-By again using the fact that in general $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K} \sum_{i = 1}^K X_i$, we plug in our previous calculations:
-
-\begin{align}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \label{LocatelliTheorem1DefinitionOfRisk}
-\end{align}
-
-From \eqref{LocatelliTheorem1EventXi} we know that for any $i \in \{0, \dots, K\}$, $\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4$.
-Following the argument in Locatelli et al.
-(2016), we now consider two cases: $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2$ and $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2$.
-In the former case, we can plug in the two probabilities into \eqref{LocatelliTheorem1DefinitionOfRisk}.
-If $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2$ and $\mathbb{P}_{\mathcal{B}^0}(\xi) \geq 3/4$, then $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \geq 1/4$.
-Thus:
-
-\begin{align*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \\
-& \geq \frac{1}{8} \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
-\end{align*}
-
-where we drop the second summand of the second line so that the inequality holds.
-
-On the other hand, when $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2$, then we know that $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \leq 1/2$ for any $\mathbb{P}_{\mathcal{B}^0}(\xi)$.
-At the same time $1-\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \geq 1/2$.
-Consequently, $1/4 \leq \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \leq 1/2$, while
-$\frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) \geq 0$.
-And so the stronger lower bound in that case is, as noticed by Locatelli et al.
-(2016), given simply by
-
-\begin{align*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \\
-& \geq \frac{1}{2}
-\end{align*}
-
-## Upper Bound on Expected Loss of APT
-
-\begin{theorem}[Locatelli et al., 2016] \label{theorem:LocatelliTheorem4}
-Let $K \geq 0$, $T \geq 2K$, and consider a problem $\mathbb{B}$. Assume that
-all arms $\nu_k$ of the problem are R-sub-Gaussian with means $\mu_k$. Let $\tau
-\in \mathbb{R}, \epsilon \geq 0$.
-
-Algorithm APT's expected loss is upper bounded on this problem as 
-\begin{equation*} \mathbb{E}(\mathcal{L}(T)) \leq \exp
-(-\frac{1}{64R^2}\frac{T}{H} + 2 \log (T) + 1)K)) \end{equation*}
-
-where we remind that $H = \sum_i (|\mu_i - \tau | + \epsilon)^{-2}$ and where
-$\mathbb{E}$ is the expectation according to the samples of the problem.
-\end{theorem}
-
-*Proof of Theorem \ref{theorem:LocatelliTheorem4}:*
-
-In order to upper bound the expected loss of the APT algorithm, we want to find an event on which the algorithm would correctly seperate arms from the threshold, that is, on the event a seperation condition holds.
-We then want to show that with large probability, this *favorable* event does indeed hold.
-Consequently, the expected loss (probability of an error) will correspond to the probability that the favorable event does not hold after all as this leads the seperation condition to fail, and the algorithm to classify at least one arm incorrectly.
-
-While this is the general idea, we have to jump between seperation condition, favorable event, and large probability.
-
-### Separation Condition
-
-As noted in Zhong et al. (2017), a simple requirement to correctly classify arms at the final round is the following. For every arm $i \in \{1, ..., K\}$ at round $T$,
-
-$$
-\hat{\mu}_{i,T_i(n)} \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
-$$
-or
-
-$$
-\hat{\mu}_{i,T_i(n)} \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
-$$
-Or simply in terms of the gap between the arm and the threshold as used as index by the algorithm,
-
-$$
-| \hat{\mu}_{i, T_i(n)} - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
-$$
-
-Intuitively, the conditions make sense as they ensure that the current mean estimate is closer to the true mean than to the threshold.
-Consequently, there is no possible arrangement left in which the condition would hold, but the arm be classified incorrectly.
-Assuming $\mu_i < \tau$ and $\epsilon = 0$, an incorrect classification would require $\mu_i < \tau \leq \hat{\mu_i}$.
-But then  $| \hat{\mu}_{i, T_i(n)} - \mu_i | \geq |\mu_i - \tau|$, violating the separation condition.
-
-Thus, we need to show that in the very final round, this condition holds for every arm $i \in \{1,...,K\}$ with large probability.
-Or more precisely, we need to derive a bound on the probability with which this does not hold.
-
-### The Favorable Event
-
-The separation condition gives a good idea of what event we need to hold in order to make a correct classification.
-The smaller the deviation of the empirical mean from the population mean, the more difficult it is for the classification to be wrong.
-Moreover, if the mean and empirical mean are identical, then the classification is correct independent of the threshold.
-And furthermore, the closer the mean and the threshold are, the better the estimate must be for a correct classification.
-
-Having to bound the absolute deviation of the sample mean from the population mean is a very thankful operation. Define the favorable event $\xi$ as
-
-$$
-\xi = \Big\{\forall i \in \mathbb{A}, \forall s \in \{1,...,T\} : |\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}} \Big\}.
-$$
-
-We want the probability that this favorable event occurs to be large, that is, the probability that the deviation is small, such that the separation condition holds with large probability.
-Indeed, we bound the deviation for *all* arms $i \leq K$ and for *every* round $s \leq T$.
-Using some Chernoff Hoeffding bounds, we are able to write
-
-$$
-\mathbb{P}(\xi) \geq 1 - 2(\log(T) +1)K \exp(-\frac{T\delta^2}{2R^2H})
-$$
-
-### Need to Bound $T_i$
-
-We now have that with large probability, the favorable event holds. On the favorable event, we have for every arm $i$:
-
-$$
-| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}
-$$
-
-The deviation of arm $i$ at time $t$ depends on how large $H$, $T$, and $T_i(t)$ are.
-While $t$, $H$, $T$ are deterministic, the number of times arm $i$ has been pulled at round $t$, $T_i(t)$, is a random variable.
-In order to know how large the probability of the favorable event is (and thus the error probability), we need to know what realistic values for $T_i(t)$ will be.
-Put differently: To ensure a deviation smaller than $\sqrt{\frac{T\delta^2}{HT_i(t)}}$ for arm $i$, we need to ensure that arm $i$ has been pulled at least $T_i(t)$ times.
-As usual in multi-armed bandits, and different from uniform sampling, the number of pulls is a random variable that also depends on how often other arms are pulled.
-In general, we do not want each arm to be pulled an equal amount, but each arm should be pulled some times, and not too many times.
-This especially holds for our exploration setting.
-
-Thus, in order to check that the deviation of arm $i$ really is small enough for the separation condition to hold on the favorable event, we need to bound the number of pulls of every arm from below.
-
-### Characteristics of a Frequently Pulled Arm (Lower Bound on $T_k(T)$)
-
-Given that we do not follow a uniform sampling strategy, we know that at time $T$, some arms will have been pulled more frequently than others.
-In particular, some arms will have been pulled more than $T/K$ times.
-How often an arm is pulled can be related to the individual arm's contribution to the overall complexity measure.
-Let $h_i$ be a measure of arm $i$'s individual problem complexity and write for the overall problem complexity
-
-$$
-H = \sum_{i = 1}^{K} h_i.
-$$
-
-Then arm $i$ contributes a share of $h_i/H$ to the overall problem complexity.
-We can now show that there exists an arm that has been pulled at least as often as the share of his complexity contribution.
-
-Given the initialization of the APT algorithm, every arm is pulled once initially.
-Consequently, there is a budget of $T-K$ rounds left after the initialization.
-As shown in Locatelli et al.
-(2016), there exists an arm $k$ that has been pulled after the initialization ($\geq 2$ pulls) and for which at the final round $T$ holds: $T_k(T) - 1 \geq \frac{(T-K)h_k}{H}$.
-This can be shown by a quick contradiction proof.
-Assume the opposite, that is
-
-$$
-\forall i \in \{1,...,K\}: T_i(T) - 1 < \frac{(T-K)h_i}{H}
-$$
-
-Consequently, at time $T$, we would have pulled across all arms $\sum_{i=1}^KT_i(T)-1$ times. If the previous assumption holds, we would not have used the entire budget:
-
-$$
-\sum_{i=1}^K T_i(T)-1 < \sum_{i=1}^K \frac{(T-K)h_i}{H} = (T-K)\sum_{i=1}^K \frac{h_i}{H} = T-K
-$$
-
-This is a contradiction, since as an requirement to the algorithm we have that $\sum_{i=1}^K T_i(T)-1 = (T-K)$, that is, we use the entire budget of samples.
-
-Another such requirement has been that $T>2K$. Plugging this in gives 
-$$
-T_k(T) - 1 \geq \frac{(T-K)h_k}{H} \leq \frac{(T-1/2T)h_k}{H} = \frac{Th_i}{2H}
-$$
-
-Now we know how often the arm has been pulled at the very end.
-That does not mean that $k$ has been pulled at time $T$.
-Thus we consider the time $t \leq T$ at which arm $k$ is pulled for the last time.
-We get (!!!!!SHOOOOWWW THIIIISSSS!!!!!!!!!)
-
-$$
-T_k(t) \geq T_k(T) - 1 \geq \frac{Th_i}{2H}.
-$$
-
-This gives us a lower bound on how often arms are pulled that are pulled frequently relative to their contribution to the problem complexity.
-Now we need a lower bound on $T_i(T)$ for every other arm $i$.
-
-### Lower Bound on $T_i(T)$
-
-Consider again as before the round $t$ in which arm $k$ is pulled for the very last time.
-Since the APT algorithm minimizes at every round $s$ the index $B_j(s)$, and pulls the arm with the smallest index, we know that arm $k$ must have had the smallest index at round $t$.
-We have:
-
-$$
-B_k(t) \leq B_i(t) \Leftrightarrow \sqrt{T_k(t)}\hat{\Delta}_k(t) \leq \sqrt{T_i(t)} \hat{\Delta}_i(t)
-$$
-
-One can already expect that this can be used to derive a lower bound on $T_i(t)$ on the RHS, and this is exactly what we do.
-
-On the LHS, we will plug in the lower bound for $T_k(t)$ derived before.
-Additionally bounding $\Delta_k(t)$ from below, and $\hat{\Delta}_i(t)$ from above using the favorable event will give the desired lower bound.
-
-Thus assume we are on the favorable event $\xi$ with large probability. we consequently have
-
-$$
-| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}.
-$$
-
-As shown in Locatelli et al. (2016), one can use the reverse triangle inequality to get:
-
-$$
-|\hat{\mu}_i(t) - \mu_i| = |(\hat{\mu}_i(t) - \tau) - (\mu_i - \tau)| \geq || \hat{\mu}_i(t) - \tau | - |\mu_i - \tau|| \geq |(|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i - \tau| + \epsilon)| \geq |\hat{\Delta}_i(t) - \Delta_i|
-$$
-
-If we combine this with the favorable event, we get
-
-$$
-\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}} \leq \hat{\Delta}_k(t) \leq \Delta_k + \sqrt{\frac{T\delta^2}{HT_k(t)}}
-$$
-
-and similar for $\hat{\Delta}_i$.
-
-We can now lower bound the LHS of the indices as
-
-$$
-\Big(\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}}\Big) \sqrt{T_k(t)} \leq B_k(t)
-$$
-
-$$
-\Big(\Delta_k - \sqrt{\frac{2}{h_k}}\delta \Big) \sqrt{\frac{Th_k}{2H}} \leq B_k(t)
-$$
-
-At this point, it is useful to have a well chosen complexity measure. If we set $h_i = \frac{1}{\Delta_i^2}$ as in Locatelli et al. (2016), we get
-
-$$
-\Big(\Delta_k - \sqrt{2}\delta \Delta \Big) \sqrt{\frac{T}{2H\Delta_k^2}} \leq B_k(t)
-$$
-
-which can be now be reduced to a form that is not specific to $k$:
-
-$$
-\Big( \frac{1}{\sqrt{2}} - \delta \Big) \sqrt{\frac{T}{H}} \leq B_k(t).
-$$
-
-Now we need to get rid of $\hat{\Delta}_i$ in order to bound $T_i(t)$. Thus, we bound the RHS again using the favorable event much as we did for the LHS:
-
-$$
-B_i(t) = \hat{\Delta}_i \sqrt{T_i(t)} \leq \Big(\Delta_i + \sqrt{\frac{T\delta^2}{HT_i(t)}}\Big) \sqrt{T_i(t)} \leq \Delta_i \sqrt{T_i(t)} + \delta \sqrt{\frac{T}{H}}
-$$
-
-As in Locatelli et al. (2016) we use the fact that by definition $\Delta$ and $\hat{\Delta}$ are positive in order to square both sides and write
-
-$$
-(1 - 2\sqrt{2}\delta)^2 \frac{T}{2H\Delta^2_i} \leq T_i(t) \leq T_i(T)
-$$
-
-We thus have derived a lower bound on the amount of pulls for any arm.
-That means that we can show that no arm is pulled an insufficient amount of times with large probability, and that consequently the favorable event hold and the estimated mean is sufficienctly separated from the threshold.
-
-### Check Separation Condition
-
-As the last step, we need to check whether the lower bound on the pulls of any arm suffices to ensure that the separation condition holds on the favorable event.
-That means, given $T_i(T) \geq (1-2\sqrt{2}\delta)^2 \frac{T}{2H\Delta_i^2}$, do we have $|\hat{\mu}_i(T) - \mu | \leq \frac{\Delta}{2}$ on the favorable event $\xi = \Big\{|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}}\Big\}$?
-
-To check, we plug the lower bound into the favorable event and get
-
-$$
-|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}} \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}
-$$
-Using $\delta = (4\sqrt{2})^-1$ as in Locatelli et al. (2016), we get
-
-$$
-|\hat{\mu}_i - \mu | \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta} \leq \frac{1}{2}\Delta_i.
-$$
-
-Thus the separation condition still holds for this value of $\delta$.
-
-### Upper Bound on Error Probability
-
-We have seen that on the favorable event $\xi$, which holds with large probability $\mathbb{P}(\xi)$, the separation condition holds as all arms have been pulled a sufficient number of times, such that their estimated mean is close to the true mean.
-All arms are classified correctly, and the algorithm does not suffer a loss.
-On the other hand, we make an error whenever the favorable event does not hold after all; that is, the deviation bound for the mean does not hold.
-At least one arm is misclassified and the arm suffers a loss.
-This occurs with probability $1-\mathbb{P}(\xi)$.
-Consequently, the expected loss is upper bounded by
-
-$$
-\mathbb{E}[L] = 1 - \mathbb{P}(\xi) \leq 2(\log(T)+1)K \exp(-\frac{1}{64R^2}\frac{T}{H}).
-$$
 

### 2017-08-26 synthetic_experiments/gaussian/exp_loc6g.R

@@ -58,14 +58,14 @@ rbind(table(loc6g_APT[[2]]$arm_sequence), mu_loc6g, sd_loc6g)
 ########################################################################
 # Gaussian Likelihood Ratio 2D-SLR
 
-system.time(loc6g_LR <- para_bandit_sim_LR_gaussian(data = data_loc6g[1:500], 
-                                                   rounds = 3000, 
-                                                   tau = tau_loc6g, 
-                                                   epsilon = epsilon_loc6g))
+system.time(loc6g_LR <- para_bandit_sim_LR_gaussian(data = data_loc6g, 
+                                                    rounds = 10000, 
+                                                    tau = tau_loc6g, 
+                                                    epsilon = epsilon_loc6g))
 
 save(loc6g_LR, file = paste0(current_path, "loc6g_LR.Rda"))
 loc6g_comp_LR <- compare_to_ground_truth(mu_loc6g, loc6g_LR, 
-                                        tau_loc6g, epsilon_loc6g)$mean
+                                         tau_loc6g, epsilon_loc6g)$mean
 save(loc6g_comp_LR, file = paste0(current_path, "loc6g_comp_LR.Rda"))
 rm(loc6g_LR)
 gc()
@@ -73,8 +73,8 @@ gc()
 ########################################################################
 # Anytime Parameter Free (Locatelli et. al, 2016)
 
-system.time(loc6g_APT <- para_bandit_sim_APT(data = data_loc6g[1:500], 
-                                            rounds = 3000, 
+system.time(loc6g_APT <- para_bandit_sim_APT(data = data_loc6g, 
+                                            rounds = 10000, 
                                             tau = tau_loc6g, 
                                             epsilon = epsilon_loc6g,
                                             do_verbose = TRUE))
@@ -88,8 +88,8 @@ gc()
 ########################################################################
 # Uniform Sampling
 
-system.time(loc6g_UNIFORM <- para_bandit_sim_uniform(data = data_loc6g[1:500], 
-                                                    rounds = 3000))
+system.time(loc6g_UNIFORM <- para_bandit_sim_uniform(data = data_loc6g, 
+                                                    rounds = 10000))
 save(loc6g_UNIFORM, file = paste0(current_path, "loc6g_UNIFORM.Rda"))
[…]

### 2017-08-26 Thesis/Draft.Rmd
Update APT section

@@
 title: "Draft"
-author: "Tim Radtke"
-date: "5/28/2017"
 header-includes:
@@
    - \usepackage{bbm}
+   - \usepackage{hyperref}
    - \usepackage[lined,boxed]{algorithm2e}
    - \newtheorem{theorem}{Theorem}
+   - \newtheorem{definition}{Definition}
    - \newtheorem{lemma}{Lemma}
@@
 
-# Introduction to Sequential Sampling and Multi-Armed Bandits
+# Introduction \label{chap:Introduction}
 
@@
 
-# Thresholding Bandit Problem \label{Chapter_TBM}
+# Thresholding Bandit Problem \label{chap:ThresholdingBanditProblem}
 
@@
 At time $t$, the learner considers the payoffs he observed so far in order to choose the next slot machine he would like to pull.
-His decision is lead by the goal to classify the slot machines with distribution $\nu_i$ and mean payoff $\mu_i$ after $T$ samples as being above or below the threshold with error probability as small as possible.
+His decision is lead by the goal to classify the slot machines with distribution $\nu_i$ and mean payoff $\mu_i = \mathbb{E}_{X \sim \nu_i}[X]$ after $T$ samples as being above or below the threshold with error probability as small as possible.
 
@@
 
-## Setup
-
-Consider a setting of $i=1, ..., K$ unknown probability distributions $\nu_i$.
+## Setup \label{sec:Setup}
+
+Consider a setting with a set of $\mathbb{A}=\{1, ..., K\}$ unknown probability distributions $\nu_i, i \in \mathbb{A}$.
 To stick with the idea of multi-armed bandits, we call those distributions arms, and observations from those arms rewards (Bubeck and Cesa-Bianchi, 2012).
@@
 Consider a fixed threshold value $\tau \in \mathbb{R}$ and an epsilon interval $\tau \pm \epsilon$ around the threshold for $\epsilon \geq 0$.
-
------------- Old
-
-In any case, the problem boils down to the following.
-As usual in multi-armed bandit problems, we have $K$ arms $\mathcal{A} = \{1, \dots K\}$.
-We can pull arm $k$ at time $t$ to collect feedback in form of the random variable $X_{k,t}$ which is distributed according to the arm's distribution $\nu_k$.
-In general, we are concerned with estimating for each arm $i$ the mean $\mu_i$ of its distribution $\nu_i$.
-In contrast to most bandit problems, however, we do not directly compare arms with each other by comparing their means.
-That would for example be the case for pure exploration bandits, where it is necessary to compare the arms because one aims to find the best one relative to the others.
-In the case of the thresholding bandit, however, we compare each arm's mean $\mu_i$ individually against the threshold $\tau \in \mathbb{R}$ which is known and fixed before the experiment.
-One might compare this to a pure exploration bandit in which the mean of the best arm is known upfront.
-We will see later that this fact leads to advantages in the design of algorithms which are not as readily available in other bandit settings.
-
-In Locatelli (2016), the arms' distributions are assumed to follow an $R$-sub-Gaussian distribution.
-Under this assumption, the authors are able to proof a general lower bound as well as an algorithm with a matching upper bound.
-Both hinge upon the *complexity* of a given problem.
-Since bandit problems can differ in the number of the arms $K$ and the means of each arm, some pose easier identification problems than others.
-Indeed, in the thresholding problem, the difficulty of the problem naturally depends on how close (the means of the) distributions are to the fixed threshold.
-Intuitively, the closer a mean $\mu_i$ is to the threshold $\tau$, the more difficult it is to distinguish the two successfully based on samples from the distribution $\nu_i$.
-A straightforward measure of this distance is given by $\Delta_i = |\tau - \mu_i| + \epsilon$, where $\epsilon$ defines a $2\epsilon$ interval around the threshold $\tau$ in which we allow ourselves to make a mistake at no cost.
-In the case of sub-Gaussian distributions, this distance is not only simple but can be interpreted very naturally as we will come to understand later.
-
-If we extend this idea to the set of arms $i \in \{1,...,K\}$ in a given bandit problem, a measure of the overall diffulty of the problem, or the problem's complexity, might be given by $H = \sum_{i=1}^{K} \Delta_i^{-2}$.
-In particular, it shows that just adding additional arms leads to an increase in complexity (since we need a larger budget to sample each arm the same number of times as before).
-Likewise, a smaller $\Delta_i$ increases the complexity as arms become harder to classify.
-Choosing the complexity measure in this way fits the distance measure $\Delta_i$ and turn out to be useful in the proof of an upper bound for the APT algorithm presented in Locatelli et al.
-(2016).
-
-We also see that this definition may lose relevancy as we move away from $R$-sub-Gaussian distributions.
-(ADD QUICK EXAMPLE OF WHAT CHANGES; REFER TO LATER PART AND DESCRIBE THIS AS THE MOTIVATION OF THE PAPER)
-
-Another characteristic uniquely identifying bandit problems is the regret measure that we aim to optimize.
-As explained during the introduction, multi-armed bandits traditionally optimize cumulative regret.
-The notion of regret considered in the thresholding bandit, however, is more akin to the simple regret in pure exploration bandits or the error probability in sequential hypothesis testing.
-Indeed, one can most easily describe the regret in the thresholding case as the probability of misclassifying any arm.
-Or, more rigorously, define the set of all arms with mean larger than the threshold, $\mathcal{S}_\tau = \{i \in \mathcal{A}: \mu_i \geq \tau\}$.
-Consequently, $\mathcal{S}_\tau^C = \{i \in \mathcal{A}: \mu_i < \tau\}$.
-At the end of the sampling rule/procedure (!!we have not mentioned yet the fact that we're in the fixed budget case!!), we demand that any algorithm returns the two corresponding *estimated* sets: $\hat{\mathcal{S}}_{\tau} = \{i \in \mathcal{A}: \hat{\mu}_i \geq \tau\}$, as well as $\hat{\mathcal{S}}_{\tau}^C = \{i \in \mathcal{A}: \hat{\mu}_i < \tau\}$.
-We simply demand an answer to the question which arms have means above the threshold $/tau$, and which arms lie below  $\tau$.
-Let $T$ be the overall number of samples the algorithm is allowed to pull.
-We define the loss as $\mathcal{L}(T) = \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset\}} \cdot \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset\}}$.
-That is, we compare the return set with the true set and collect a loss of 1 if any arm with a true mean outside the $2\epsilon$ interval around $\tau$ was misclassified.
-It is important to realize that arms with means inside the $2 \epsilon$ interval may be misclassified without it affecting the loss.
-These arms are considered close enough to the threshold that we do not care whether they lie above or below.
-
-ADD A GRAPHIC THAT VISUALIZES THE ESTIMATED AND THE REQUIRED RETURN SETS
-
-Now, the expected regret/loss is defined as $\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \land (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset))$.
-This, of course, is the mentioned probability of making a mistake.
-
-Lastly, it is to mention that we are considering the fixed-budget version of the thresholding bandit problem.
-We thus fix the number of samples that the algorithm will pull upfront at $T$.
-The task of the algorithm is then to find a sampling rule or strategy which distributes the budget $T$ among the $K$ arms in such a way that the expected regret, or the error probability, is minimized.
-In other terms, the algorithm aims to use the $T$ samples in a way that lets him return the two sets $\hat{\mathcal{S}}_{\tau}$ and $\hat{\mathcal{S}}_{\tau}^C$ with as much confidence as possible.
-This again shows the contrast to the fixed confidence setting in which one fixes the confidence level upfront and lets the algorithm draw as many samples as necessary to reach the required confidence.
-
-At this point, we have defined the fixed budget thresholding bandit setup for any algorithm in the case of sub-Gaussian distributions.
-We thus proceed to describe the APT algorithm proposed in Locatelli et al.
-(2016).
-
-## The APT Algorithm
+As mentioned in the introduction, the learner is tasked with classifying arms as having a mean $\mu_i$ larger or smaller than $\tau$.
+To describe which arms are above the threshold, we introduce the following set notation (compare Locatelli et al., 2016): Let $\mathcal{S}_{\tau}$ be the set of distributions in $mathbb{A}$ with mean larger than the threshold: $\mathcal{S}_{\tau} := \{i \in \mathbb{A}, \mu_i \geq \tau\}$.
+Consequently, the complement is given by the arms with mean below the threshold, $\mathcal{S}^C_{\tau} := \{i \in \mathbb{A}, \mu_i < \tau\}$.
+
+The thresholding problem for the learner is now to use a budget of overall $T$ samples (or rounds) to explore the different arms.
+After this exploration phase, the learner has to return a set of arms that he believes to have a mean above the threshold.
+The problem can thus be described by the threshold $\tau$ and a precision $\epsilon$.
+When evaluating the classification of the learner, arms with mean inside of the epsilon interval will not be considered.
+The learner only has to distinguish the means from the threshold correctly up to the precision $\epsilon$.
+Thus, the algorithm is not evaluated against $\mathcal{S}_{\tau}$ and $\mathcal{S}^C_{\tau}$, but needs to distinguish $\mathcal{S}_{\tau+\epsilon}$ from $\mathcal{S}^C_{\tau-\epsilon}$.
+As in Locatelli et al.
+(2016), whenever we say that "an arm is over the threshold", we mean that the mean of the arm is over the threshold.
+
+The learner's classification is returned as the set $\hat{\mathcal{S}}_{\tau} := \hat{\mathcal{S}}_{\tau}(T) \subset \mathbb{A}$ after $T$ rounds; that is, the set of arms estimated to be over the threshold.
+The classification is evaluated against the loss given as (Locatelli et al., 2016):
+
+$$
+\mathcal{L}(T) = \mathbbm{1}{(\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \lor (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset)}
+$$
+
+In order to perform well, a learner has to identify all arms that are over the threshold as such, and to not claim arms as being over the threshold if they actually are below the threshold.
+Due to the precision $\epsilon$, the loss is not influenced by arms which are too close to the threshold $\tau$, that is, arms inside of the $\tau \pm \epsilon$ interval.
+If either $\hat{\mathcal{S}}_{\tau}$ contains an arm below $(\tau - \epsilon)$, or $\hat{\mathcal{S}}^C_{\tau}$ contains an arm above $(\tau + \epsilon)$, a loss of $1$ is accrued.
+Else, all arms outside the epsilon interval are classified correctly and the loss is equal to $0$.
+In the case of $\epsilon = 0$, all arms need to be classified correctly to not endure any loss.
+
+Algorithms for this thresholding problem can be compared based on their expected loss.
+Let $\mathbb{E}$ be the expectation with regard to the samples $X_{i,1}, ..., X_{i,T}$ collected by the algorithm.
+The expected loss is then given as
+
+$$
+\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}\big((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \lor(\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset)\big),
+$$
+
+which corresponds to the probability of making a wrong classification.
+Both the probability of not identifying an arm that is actually over the threshold, as well as the probability of accepting an arm as over the threshold when it is not are evaluated.
+The oracle strategy would evaluate all arms correctly with an error probability of $0$ (Locatelli et al., 2016).
+
+At this point, we have introduced the general thresholding bandit problem setting which we will use throughout the thesis.
+The setting might be extended by different assumptions to make certain algorithms or bounds feasible.
+For that reason, Locatelli et al.
+(2016) assume that the distributions $\nu_i, i \in \mathbb{A}$ are $R$-sub-Gaussian.
+Under this assumption, the authors are able to prove a lower bound on the largest probability of error of the best algorithm in the setting we have just introduced, as well as an upper bound on the performance of their APT algorithm we will introduce in the following chapter.
+As in their paper, we define $R$-sub-Gaussian and assume it in the description of their algorithm and bounds:
+
+\begin{definition}[$R$-sub-Gaussian distribution] 
+\label{definition:rsubgaussian}
+Let $R > 0$. A distribution $\nu$ is $R$-sub-Gaussian if for all $t \in \mathbb{R}$ we have
+\begin{equation*}
+\mathbb{E}_{X \sim \nu}[\exp(tX - t\mathbb{E}[X])] \leq \exp(R^2t^2/2).
+\end{equation*}
+\end{definition}
+
+As noted by Locatelli et al.
+(2016), this ensures that the mean $\mu_i$ of the distributions $\nu_i$ considered in our problem are finite.
+$R$-sub-Gaussian distributions furthermore offer concentration inequalities for the concentration of the empirical mean to the true mean, which makes it possible to deduce the bounds presented by the authors and repeated below.
+The family of $R$-sub-Gaussian distributions encompasses Gaussian distributions of variance $R^2$ for $R \in \mathbb{R}$, as well as all bounded distributions, with the important case of Bernoulli distributions.
+
+Having described the thresholding bandit setting as well as the assumption of $R$-sub-Gaussianity, we can now proceed to describe the *Anytime Parameter-free Thresholding* (APT) algorithm proposed in Locatelli et al.
+(2016) for the thresholding bandit problem.
+
+## The Anytime Parameter-free Thresholding Algorithm \label{sec:TheAPTAlgorithm}
+
+In the following we describe the *Anytime Parameter-free Thresholding* (APT) algorithm proposed in Locatelli et al.
+(2016), which is a simple yet effective algorithm and displays some very favorable characteristics when compared to alternative algorithms.
+
+We fix the threshold $\tau$ and epsilon interval around the threshold given by $\epsilon$ upfront, and supply them as arguments to the algorithm: $(\tau, \epsilon)$.
+Based on the general thresholding problem, we demand that the algorithm draws samples $X_{i,t}$ for $T$ rounds from the distributions $\nu_i, i\in \mathbb{A}$.
+For a given arm $i$ and a given time $t$, we let $T_i(t)$ represent the number of samples drawn from arm $i$ until time $t$ (including).
+Consequently, the empirical mean of arm $i$ at time $t$ is given by $\hat{\mu}_i(t) = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}$ where $X_{i,s}$ is the feedback sampled from distribution $\nu_i$ when the arm is pulled for the $s$-th time.
+In the case of the APT algorithm, the decision $\hat{\mathcal{S}}_{\tau}$ is based on the empirical means $\hat{\mu}_i(T)$ estimated from the samples drawn up to time $T$: $\hat{\mathcal{S}}_{\tau} := \hat{\mathcal{S}}_{\tau}(T) = \{i \in \mathbb{A}, \hat{\mu}_i(T) \geq \tau\}$.
+
+As we see in algorithm \ref{alg:APT}, the APT algorithm initiates by pulling each arm once.
+Then, for each $t > K$, it calculates for every arm the values $T_i(t)$ and $\hat{\mu}_i(t)$.
+Based on the empirical mean, the algorithm computes the estimated gap between the mean and the threshold as $\hat{\Delta}_i(t) = \hat{\Delta}_i^{\tau, \epsilon}(t) = |\mu_i(t) - \tau| + \epsilon$.
+The decision of which arm is sampled next is then based on the value $B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t)$: the algorithm pulls arm $I_{t+1} = \arg \min_{i\leq K} B_i(t+1)$ minimizing this decision quantity.
+After overall $T$ pulls, the algorithm returns the sets described in the general setup, $\hat{\mathcal{S}}_{\tau}$ and $\hat{\mathcal{S}}^C_{\tau}$.
 
@@
 \For{$t = K+1$ \KwTo $T$}{
-  \emph{Pull arm $I_t = \arg \min_{k\leq K} B_k^{APT}(t) = \sqrt{T_k(t)} \sqrt{|\hat{\mu}_i(t) - \tau|+\epsilon}$}\;
+  \emph{Pull arm $I_t = \arg \min_{k\leq K} B_k^{APT}(t) = \sqrt{T_k(t)} (|\hat{\mu}_i(t) - \tau|+\epsilon)$}\;
   \emph{Observe reward $X \sim \nu_{I_t}$}\;
 }
-\caption{Anytime Parameter-free Thresholding Algorithm (Locatelli et al., 2016)}\label{algo_apt}
+\caption{Anytime Parameter-free Thresholding Algorithm (Locatelli et al., 2016)}\label{alg:APT}
 \end{algorithm}\DecMargin{1em}
 
-In the following we describe the *Anytime Parameter-free Thresholding* (APT) algorithm proposed in Locatelli et al.
-(2016), which is a simple yet effective algorithm and displays some very favorable characteristics when compared with alternative algorithms.
-
-From the general setup, we already know how the algorithm will end.
-After it has drawn $T$ samples, the algorithm makes a decision of which arms to include in the return sets on basis of the empirical means $\hat{\mu}_i(T)$ estimated based on the samples drawn until time $T$.
-Furthermore, the threshold and interval around the threshold are fixed upfront and serve as argument to the algorithm: $(\tau, \epsilon)$.
-For a given arm $i$ and a given time $t$, we let $T_i(t)$ represent the number of samples drawn from arm $i$ until time $t$ (including).
-Consequently, the empirical mean of arm $i$ at time $t$ is given by $\hat{\mu}_i(t) = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}$ where $X_{i,s}$ is the feedback sampled from distribution $\nu_i$ when the arm is pulled for the $s$-th time.
-
-To be specific, the APT algorithm initiates by pulling each arm once.
-Then, for each $t > K$, it calculates for every arm the values $T_i(t)$ and $\mu_i(t)$.
-Based on the empirical mean, the algorithm computes the estimated gap between the mean and the threshold as $\hat{\Delta}_i(t) = \hat{\Delta}_i^{\tau, \epsilon}(t) = |\mu_i(t) - \tau| + \epsilon$.
-The decision of which arm is sampled next is then based on the value $B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t)$: the algorithm pulls arm $I_{t+1} = \arg \min_{i\leq K} B_i(t+1)$ minimizing this decision quantity.
-After $T$ pulls overall, the arm returns the sets described in the general setup, $\hat{\mathcal{S}}_{\tau}$ and $\hat{\mathcal{S}}^C_{\tau}$.
-
-The APT algorithm tends to pull arms more often with corresponding mean close to the threshold and interval (small $\hat{\Delta}_i(t))$.
-This makes sure that more evidence is gathered on arms which appear to be inherently difficult to classify based on the samples collected until time $T_i(t)$, as these arms stifle the confidence the most.
-That is, until we have collected enough evidence to make a confident classification even if the mean is truly close to the threshold.
-In that case, $\sqrt{T_i(t)}$ will raise $B_i(t+1)$.
-Consequently, other arms farther away from the threshold will be sampled again.
-In this way, the algorithm tries to distribute the budget $T$ over all arms so as to define a sampling rule optimizing the confidence of the final decision.
-
-Locatelli et al. (2016) show that the APT algorithm is optimal in the sense that the upper bound on its expected loss reaches the lower bound for the expected loss.
+Just like the general index policies mentioned in \autoref{sec:Setup}, we see that the APT algorithm adapts its strategy using an index $B_i(t+1)$ for each arm that is based entirely on the observations observed until time $t$.
+Given the arm with the smallest index is pulled at round $t+1$, we observe that arms that are estimated to be further away from the threshold $\tau$ as measured by the absolute distance to their empirical mean $\hat{\mu}_i$, $\hat{\Delta}_i(t)$, are pulled less often.
+Intuitively, it is easier to classify arms as below or above $\tau$ when their mean is far away from the threshold.
+In contrast to the uniform sampling strategy, APT will gather more evidence for arms which appear to be inherently more difficult to classify.
+Likewise, APT tends to pull arms less often which it already pulled considerably often as measured by $T_i(t)$.
+If arm $i$ has been pulled more often than arm $j$, then we should in general be more confident in its estimated mean and the corresponding distance to the threshold.
+If we are confident in $i$, then it is better to explore other arms by drawing an observation from arm $j$.
+By adapting its sampling strategy in this way during the sequential sampling process, the APT algorithm minimizes the probability of error $\mathbb{E}[\mathcal{L}(T)]$ after $T$ samples have been observed.
+
+The previous paragraph describes how arms close to the threshold are intuitively more difficult to classify.
+In the index employed by the APT algorithm, the distance between an arm and the threshold is measured by the absolute distance $\hat{\Delta}_i(t)$ between the (estimated) mean of the arm and the threshold $\tau$ (and the epsilon interval).
+Given that one compares $B_i^{APT}$ with $B_j^{APT}$, one could just as well measure the distance by the squared distance, $\hat{\Delta}_i(t)^2$.
+When the APT algorithm realizes that an arm has a mean close to the threshold, then this arm requires more attention than an arm far away from the threshold; the confidence in the empirical mean has to be larger.
+Or the empirical mean has to be better concentrated around the true mean.
+Otherwise it is easier to make a mistake on this arm.
+To gain this confidence, the arm requires more samples, and thus a larger share of the overall $T$ samples available.
+With this intuition, it makes sense to measure the complexity of a thresholding problem: If we knew upfront how complex a given set of arms is, we knew whether we can expect a small or large probability of error given our budget $T$.
+Also, for example in the best arm identification problem, there exist algorithms which take the complexity of a problem as input.
+Based on the complexity they then adapt their sampling strategy.
+See for example the UCB-E algorithm in Audibert et al.
+(2010) for the best arm identification problem, or the KL-LUCB-E algorithm in Kaufmann and Kalyanakrishnan (2013) as extension to the Top-$m$ problem.
+
+While the APT algorithm does not require the complexity to be known upfront (which would be problematic), it is necessary to define the complexity to deduce the upper bound on its probability of error.
+Similar to the distance measure used in the algorithm's index, we define the gap $\Delta_i^{\tau,\epsilon}$ between arm $i$ and the threshold $\tau \pm \epsilon$ as
+
+$$
+\Delta_i := \Delta_i^{\tau,\epsilon} = |\mu_i - \tau| + \epsilon
+$$
+
+Given this gap, Locatelli et al. (2016) define the complexity $H_{\tau, \epsilon}$ for the thresholding bandit problem naturally as
+
+$$
+H := H_{\tau, \epsilon} = \sum_{i=1}^K \frac{1}{(\Delta_i^{\tau,\epsilon})^2}.
+$$
+
+Note that the complexity of the problem increases in the number of arms $K$ and decreases in the gap $\Delta_i^{\tau,\epsilon}$.
+Consequently, when we require a smaller precision, that is, we increase $\epsilon$, the hardness decreases.
+Furthermore, we see that each arm contributes its individual complexity, $h_i^{\tau,\epsilon} = \frac{1}{(\Delta_i^{\tau,\epsilon})^2}$ linearly into the problem.
+Thus, if the complexity $H$ is a good measure of the actual problem complexity, and we knew upfront which arm has which mean, we could allocate the "optimal" share of the budget, $T \cdot h_i /H$ to arm $i$.
+However, since we do not know neither $\mu_i$ nor $H$, the best we can do is to adapt our allocation of samples more and more towards this optimum as we observe samples.
+
+At this point, one can question whether the measure of complexity $H$ proposed in Locatelli et al.
+(2016) is a good measure of the "true" problem complexity.
+In the following \autoref{sec:UpperBoundLocatelli}, we will show the upper bound on the probability of error for the APT algorithm and see how the complexity $H$ arises naturally for the APT algorithm.
+In \autoref{sec:LowerBoundLocatelli} we then show the lower bound presented in Locatelli et al.
+(2016) and that the APT algorithm is optimal in that it matches the lower bound.
+We discuss the results and the APT algorithm further in \autoref{sec:DiscussionLocatelli}.
+
+## Upper Bound for the APT Algorithm \label{sec:UpperBoundLocatelli}
+
+In this chapter we present the upper bound on the APT algorithm proven in Locatelli et al.
+(2016).
+The upper bound is on the probability of error that the algorithm has after $T$ rounds of sampling for a problem with arms that are assumed to be $R$-sub-Gaussian.
+The bound depends also on the complexity of the problem, and we show in the proof that given the index of the APT algorithm as defined in \autoref{sec:TheAPTAlgorithm}, the complexity $H$ is an appropriate measure.
+
+We now state the theorem as in Locatelli et al. (2016) and present a proof.
+
+\begin{theorem}[Theorem 2, Locatelli et al., 2016] \label{theorem:LocatelliTheorem4}
+Let $K \geq 0$, $T \geq 2K$, and consider a problem $\mathcal{B}$.
+Assume that all arms $\nu_i$ of the problem are R-sub-Gaussian with means $\mu_i$.
+Let $\tau \in \mathbb{R}, \epsilon \geq 0$.
+Algorithm APT's expected loss is upper bounded on this problem as
+\begin{equation*} \mathbb{E}(\mathcal{L}(T)) \leq \exp
+(-\frac{1}{64R^2}\frac{T}{H} + 2 \log (T) + 1)K)) \end{equation*}
+
+where we remind that $H = \sum_i (|\mu_i - \tau | + \epsilon)^{-2}$ and where
+$\mathbb{E}$ is the expectation according to the samples of the problem.
+\end{theorem}
+
+### Proof of Theorem \ref{theorem:LocatelliTheorem4}
+
+In order to upper bound the expected loss of the APT algorithm, we want to define an event on which the algorithm correctly seperates arms from the threshold, that is, a separation condition holds on this event.
+We then want to show that this *favorable* event does indeed hold with large probability.
+Consequently, APT's probability of error will correspond to the probability that the favorable event does not hold, as this leads to a failure of the seperation condition, and consequently to an incorrect classification of at least one arm by the algorithm.
+We start by defining the separation condition.
+
+### Separation Condition
+
+As noted in Zhong et al. (2017), a simple requirement to correctly classify arms at the final round is the following. For every arm $i \in \{1, ..., K\}$ after the final round $T$, require
+$$
+\hat{\mu}_{i,T_i(n)} \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
+$$
+or
+$$
+\hat{\mu}_{i,T_i(n)} \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
+$$
+Or simply in terms of the gap between the arm and the threshold as used in the index by the APT algorithm:
+$$
+| \hat{\mu}_{i, T_i(n)} - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
+$$
+
+Intuitively, this condition makes sense as it ensures that the current mean estimate is closer to the true mean than to the threshold.
+Consequently, there is no arrangement possible in which the arm is classified wrong while the separation condition holds.
+Assuming $\mu_i < \tau$ and $\epsilon = 0$, an incorrect classification would require $\mu_i < \tau \leq \hat{\mu_i}$.
+But then  $| \hat{\mu}_{i, T_i(n)} - \mu_i | \geq |\mu_i - \tau|$, which violates the separation condition.
+
+Thus, we need to show that this condition holds for every arm $i \in \{1,...,K\}$ with large probability after the final round $T$.
+In different words, we need to derive an upper bound on the probability with which this condition does not hold.
+
+### The Favorable Event
+
+The separation condition describes what event needs to hold in order for the APT algorithm to make a correct classification: The smaller the deviation of the empirical mean from the population mean, the more difficult it is for the classification to be wrong.
+Moreover, if the mean and empirical mean are identical, then the classification is correct independent of the threshold.
+Also, the closer the mean to the threshold, the better the estimate has to be for a correct classification to be likely.
+To bound the absolute deviation of the empirical mean from the true mean, we define the favorable event $\xi$ as
+
+$$
+\xi = \Big\{\forall i \in \mathbb{A}, \forall s \in \{1,...,T\} : |\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}} \Big\}.
+$$
+
+The probability that this favorable event occurs should be large, or equivalently, the probability that the deviation is small should be large.
+Then it follows that the separation condition holds with large probability.
+
+- Show Chernoff/Hoeffding bound detailed
+- Show union bound to get deviation for all arms $i \leq K$ and every round $s \leq T$
+
+$$
+\mathbb{P}(\xi) \geq 1 - 2(\log(T) +1)K \exp(-\frac{T\delta^2}{2R^2H})
+$$
+
+### Need to Bound $T_i$
+
+We now have that with large probability the favorable event holds. On the favorable event, we have for every arm $i$:
+
+$$
+| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}
+$$
+
+The deviation of arm $i$ at time $t$ depends on how large $H$, $T$, and $T_i(t)$ are.
+While $t$, $H$, $T$ are deterministic, the number of times arm $i$ has been pulled at round $t$, $T_i(t)$, is a random variable.
+In order to know how large the probability of the favorable event is (and thus the error probability), we need to know the value of $T_i(t)$, or at least bound a range of potential values.
+Put differently: To ensure a deviation smaller than $\sqrt{\frac{T\delta^2}{HT_i(t)}}$ for arm $i$, we need to ensure that arm $i$ has been pulled at least $T_i(t)$ times.
+As usual in multi-armed bandits, and different from uniform sampling, the number of pulls is a random variable that also depends on how often other arms are pulled.
+In general, we do not want each arm to be pulled an equal amount, but each arm should be pulled some times, and not too many times.
+
+Thus, in order to check that the deviation of arm $i$ really is small enough for the separation condition to hold on the favorable event, we need to bound the number of pulls of every arm from below.
+
+### Characteristics of a Frequently Pulled Arm (Lower Bound on $T_k(T)$)
+
+Given that we do not follow a uniform sampling strategy, we know that at time $T$, some arms will have been pulled more frequently than others.
+In particular, some arms will have been pulled more than $T/K$ times.
+How often an arm is pulled can be related to the individual arm's contribution to the overall complexity measure.
+Let $h_i$ be a measure of arm $i$'s individual problem complexity and write for the overall problem complexity $H = \sum_{i = 1}^{K} h_i$.
+Then arm $i$ contributes a share of $h_i/H$ to the overall problem complexity.
+We can now show that there exists an arm that has been pulled at least as often as the share of his complexity contribution.
+
+Given the initialization of the APT algorithm, every arm is pulled once initially.
+Consequently, there is a budget of $T-K$ rounds left after the initialization.
+As shown in Locatelli et al.
+(2016), there exists an arm $k$ that has been pulled after the initialization ($\geq 2$ pulls) and for which at the final round $T$ it holds: $T_k(T) - 1 \geq \frac{(T-K)h_k}{H}$.
+This can be shown by a contradiction.
+Assume that the opposite holds, that is
+
+$$
+\forall i \in \{1,...,K\}: T_i(T) - 1 < \frac{(T-K)h_i}{H}
+$$
+
+Consequently, at time $T$, we would have pulled across all arms $\sum_{i=1}^KT_i(T)-1$ times. If the previous assumption holds, we would not have used the entire budget:
+
+$$
+\sum_{i=1}^K T_i(T)-1 < \sum_{i=1}^K \frac{(T-K)h_i}{H} = (T-K)\sum_{i=1}^K \frac{h_i}{H} = T-K
+$$
+
+This is a contradiction, since as an requirement to the algorithm we have that $\sum_{i=1}^K T_i(T)-1 = (T-K)$, that is, we use the entire budget of samples.
+
+Furthermore, we have assumed $T>2K$ in the statement of Theorem \ref{theorem:LocatelliTheorem4}. Plugging this in gives 
+$$
+T_k(T) - 1 \geq \frac{(T-K)h_k}{H} \geq \frac{(T-1/2T)h_k}{H} = \frac{Th_i}{2H}
+$$
+
+Now we know how often the arm has been pulled at the very end.
+That does not mean that $k$ has been pulled at time $T$.
+Thus we consider the time $t \leq T$ at which arm $k$ is pulled for the last time.
+We get
+
+$$
+T_k(t) \geq T_k(T) - 1 \geq \frac{Th_i}{2H}.
+$$
+
+This gives us a lower bound on how often arms are pulled that are pulled frequently relative to their contribution to the problem complexity.
+Now we need a lower bound on $T_i(T)$ for every other arm $i$.
+
+### Lower Bound on $T_i(T)$
+
+Consider again as before the round $t$ at which arm $k$ is pulled for the very last time.
+Since the APT algorithm minimizes at every round $s \geq K+1$ the index $B_j(s)$, and pulls the arm with the smallest index, we know that arm $k$ must have had the smallest index at round $t$.
+We have:
+
+$$
+B_k(t) \leq B_i(t) \Leftrightarrow \sqrt{T_k(t)}\hat{\Delta}_k(t) \leq \sqrt{T_i(t)} \hat{\Delta}_i(t)
+$$
+
+One can already expect that this can be used to derive a lower bound on $T_i(t)$ on the RHS, and this is exactly what we do.
+On the LHS, we plug in the lower bound for $T_k(t)$ derived before.
+Additionally bounding $\Delta_k(t)$ from below, and $\hat{\Delta}_i(t)$ from above using the favorable event will give the desired lower bound.
+
+Thus assume we are on the favorable event $\xi$ with large probability. we consequently have
+
+$$
+| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}.
+$$
+
+As shown in Locatelli et al. (2016), one can use the reverse triangle inequality to get:
+
+\begin{align*}
+|\hat{\mu}_i(t) - \mu_i| & = & |(\hat{\mu}_i(t) - \tau) - (\mu_i - \tau)| \\
+& \geq & || \hat{\mu}_i(t) - \tau | - |\mu_i - \tau|| \\
+& \geq & |(|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i - \tau| + \epsilon)| \\
+& \geq & |\hat{\Delta}_i(t) - \Delta_i|
+\end{align*}
+
+If we combine this with the favorable event, we get
+
+$$
+\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}} \leq \hat{\Delta}_k(t) \leq \Delta_k + \sqrt{\frac{T\delta^2}{HT_k(t)}}
+$$
+
+and similar for $\hat{\Delta}_i$. We can now lower bound the LHS of the indices as
+
+\begin{align*}
+B_k(t) & \geq & \Big(\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}}\Big) \sqrt{T_k(t)} \\
+& \geq & \Big(\Delta_k - \sqrt{\frac{2}{h_k}}\delta \Big)
+\end{align*}
+
+At this point, it is useful to have a well chosen complexity measure. If we set $h_i = \frac{1}{\Delta_i^2}$ as in Locatelli et al. (2016), we get
+
+$$
+\Big(\Delta_k - \sqrt{2}\delta \Delta \Big) \sqrt{\frac{T}{2H\Delta_k^2}} \leq B_k(t)
+$$
+
+which can be now be reduced to a form that is not specific to $k$:
+
+$$
+\Big( \frac{1}{\sqrt{2}} - \delta \Big) \sqrt{\frac{T}{H}} \leq B_k(t).
+$$
+
+Now we need to remove $\hat{\Delta}_i$ in order to bound $T_i(t)$. Thus, we bound the RHS again using the favorable event much as we did for the LHS:
+
+$$
+B_i(t) = \hat{\Delta}_i \sqrt{T_i(t)} \leq \Big(\Delta_i + \sqrt{\frac{T\delta^2}{HT_i(t)}}\Big) \sqrt{T_i(t)} \leq \Delta_i \sqrt{T_i(t)} + \delta \sqrt{\frac{T}{H}}
+$$
+
+As in Locatelli et al. (2016) we use the fact that by definition $\Delta$ and $\hat{\Delta}$ are positive in order to square both sides and write
+
+$$
+(1 - 2\sqrt{2}\delta)^2 \frac{T}{2H\Delta^2_i} \leq T_i(t) \leq T_i(T)
+$$
+
+We thus have derived a lower bound on the amount of pulls for any arm.
+That means that we can show that no arm is pulled an insufficient amount of times with large probability, and that consequently the favorable event hold and the estimated mean is sufficienctly separated from the threshold.
+
+### Check Separation Condition
+
+As the last step, we need to check whether the lower bound on the pulls of any arm suffices to ensure that the separation condition holds on the favorable event.
+That means, given $T_i(T) \geq (1-2\sqrt{2}\delta)^2 \frac{T}{2H\Delta_i^2}$, do we have $|\hat{\mu}_i(T) - \mu | \leq \frac{\Delta}{2}$ on the favorable event $\xi = \Big\{|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}}\Big\}$?
+To check, we plug the lower bound into the favorable event and get
+
+$$
+|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}} \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}
+$$
+Using $\delta = (4\sqrt{2})^-1$ as in Locatelli et al. (2016), we have that the separation condition holds exactly:
+
+$$
+|\hat{\mu}_i - \mu | \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta} \leq \frac{1}{2}\Delta_i.
+$$
+
+### Upper Bound on Error Probability
+
+We have seen that on the favorable event $\xi$, which holds with large probability $\mathbb{P}(\xi)$, the separation condition holds as all arms have been pulled a sufficient number of times, such that their estimated mean is close to the true mean.
+All arms are classified correctly, and the algorithm does not suffer a loss.
+On the other hand, we make an error whenever the favorable event does not hold after all; that is, the deviation bound for the mean does not hold.
+At least one arm is misclassified and the arm suffers a loss.
+This occurs with probability $1-\mathbb{P}(\xi)$.
+Consequently, the expected loss is upper bounded by
+
+$$
+\mathbb{E}[L] = 1 - \mathbb{P}(\xi) \leq 2(\log(T)+1)K \exp(-\frac{1}{64R^2}\frac{T}{H}).
+$$
 
@@
 
-## Lower Bound: Theorem and Proof
+## Lower Bound: Theorem and Proof \label{sec:LowerBoundLocatelli}
 
@@
 
-## Upper Bound on Expected Loss of APT
-
-\begin{theorem}[Locatelli et al., 2016] \label{theorem:LocatelliTheorem4}
-Let $K \geq 0$, $T \geq 2K$, and consider a problem $\mathbb{B}$. Assume that
-all arms $\nu_k$ of the problem are R-sub-Gaussian with means $\mu_k$. Let $\tau
-\in \mathbb{R}, \epsilon \geq 0$.
-
-Algorithm APT's expected loss is upper bounded on this problem as 
-\begin{equation*} \mathbb{E}(\mathcal{L}(T)) \leq \exp
-(-\frac{1}{64R^2}\frac{T}{H} + 2 \log (T) + 1)K)) \end{equation*}
-
-where we remind that $H = \sum_i (|\mu_i - \tau | + \epsilon)^{-2}$ and where
-$\mathbb{E}$ is the expectation according to the samples of the problem.
-\end{theorem}
-
-*Proof of Theorem \ref{theorem:LocatelliTheorem4}:*
-
-In order to upper bound the expected loss of the APT algorithm, we want to find an event on which the algorithm would correctly seperate arms from the threshold, that is, on the event a seperation condition holds.
-We then want to show that with large probability, this *favorable* event does indeed hold.
-Consequently, the expected loss (probability of an error) will correspond to the probability that the favorable event does not hold after all as this leads the seperation condition to fail, and the algorithm to classify at least one arm incorrectly.
-
-While this is the general idea, we have to jump between seperation condition, favorable event, and large probability.
-
-### Separation Condition
-
-As noted in Zhong et al. (2017), a simple requirement to correctly classify arms at the final round is the following. For every arm $i \in \{1, ..., K\}$ at round $T$,
-
-$$
-\hat{\mu}_{i,T_i(n)} \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
-$$
-or
-
-$$
-\hat{\mu}_{i,T_i(n)} \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
-$$
-Or simply in terms of the gap between the arm and the threshold as used as index by the algorithm,
-
-$$
-| \hat{\mu}_{i, T_i(n)} - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
-$$
-
-Intuitively, the conditions make sense as they ensure that the current mean estimate is closer to the true mean than to the threshold.
-Consequently, there is no possible arrangement left in which the condition would hold, but the arm be classified incorrectly.
-Assuming $\mu_i < \tau$ and $\epsilon = 0$, an incorrect classification would require $\mu_i < \tau \leq \hat{\mu_i}$.
-But then  $| \hat{\mu}_{i, T_i(n)} - \mu_i | \geq |\mu_i - \tau|$, violating the separation condition.
-
-Thus, we need to show that in the very final round, this condition holds for every arm $i \in \{1,...,K\}$ with large probability.
-Or more precisely, we need to derive a bound on the probability with which this does not hold.
-
-### The Favorable Event
-
-The separation condition gives a good idea of what event we need to hold in order to make a correct classification.
-The smaller the deviation of the empirical mean from the population mean, the more difficult it is for the classification to be wrong.
-Moreover, if the mean and empirical mean are identical, then the classification is correct independent of the threshold.
-And furthermore, the closer the mean and the threshold are, the better the estimate must be for a correct classification.
-
-Having to bound the absolute deviation of the sample mean from the population mean is a very thankful operation. Define the favorable event $\xi$ as
-
-$$
-\xi = \Big\{\forall i \in \mathbb{A}, \forall s \in \{1,...,T\} : |\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}} \Big\}.
-$$
-
-We want the probability that this favorable event occurs to be large, that is, the probability that the deviation is small, such that the separation condition holds with large probability.
-Indeed, we bound the deviation for *all* arms $i \leq K$ and for *every* round $s \leq T$.
-Using some Chernoff Hoeffding bounds, we are able to write
-
-$$
-\mathbb{P}(\xi) \geq 1 - 2(\log(T) +1)K \exp(-\frac{T\delta^2}{2R^2H})
-$$
-
-### Need to Bound $T_i$
-
-We now have that with large probability, the favorable event holds. On the favorable event, we have for every arm $i$:
-
-$$
-| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}
-$$
-
-The deviation of arm $i$ at time $t$ depends on how large $H$, $T$, and $T_i(t)$ are.
-While $t$, $H$, $T$ are deterministic, the number of times arm $i$ has been pulled at round $t$, $T_i(t)$, is a random variable.
-In order to know how large the probability of the favorable event is (and thus the error probability), we need to know what realistic values for $T_i(t)$ will be.
-Put differently: To ensure a deviation smaller than $\sqrt{\frac{T\delta^2}{HT_i(t)}}$ for arm $i$, we need to ensure that arm $i$ has been pulled at least $T_i(t)$ times.
-As usual in multi-armed bandits, and different from uniform sampling, the number of pulls is a random variable that also depends on how often other arms are pulled.
-In general, we do not want each arm to be pulled an equal amount, but each arm should be pulled some times, and not too many times.
-This especially holds for our exploration setting.
-
-Thus, in order to check that the deviation of arm $i$ really is small enough for the separation condition to hold on the favorable event, we need to bound the number of pulls of every arm from below.
-
-### Characteristics of a Frequently Pulled Arm (Lower Bound on $T_k(T)$)
-
-Given that we do not follow a uniform sampling strategy, we know that at time $T$, some arms will have been pulled more frequently than others.
-In particular, some arms will have been pulled more than $T/K$ times.
-How often an arm is pulled can be related to the individual arm's contribution to the overall complexity measure.
-Let $h_i$ be a measure of arm $i$'s individual problem complexity and write for the overall problem complexity
-
-$$
-H = \sum_{i = 1}^{K} h_i.
-$$
-
-Then arm $i$ contributes a share of $h_i/H$ to the overall problem complexity.
-We can now show that there exists an arm that has been pulled at least as often as the share of his complexity contribution.
-
-Given the initialization of the APT algorithm, every arm is pulled once initially.
-Consequently, there is a budget of $T-K$ rounds left after the initialization.
-As shown in Locatelli et al.
-(2016), there exists an arm $k$ that has been pulled after the initialization ($\geq 2$ pulls) and for which at the final round $T$ holds: $T_k(T) - 1 \geq \frac{(T-K)h_k}{H}$.
-This can be shown by a quick contradiction proof.
-Assume the opposite, that is
-
-$$
-\forall i \in \{1,...,K\}: T_i(T) - 1 < \frac{(T-K)h_i}{H}
-$$
-
-Consequently, at time $T$, we would have pulled across all arms $\sum_{i=1}^KT_i(T)-1$ times. If the previous assumption holds, we would not have used the entire budget:
-
-$$
-\sum_{i=1}^K T_i(T)-1 < \sum_{i=1}^K \frac{(T-K)h_i}{H} = (T-K)\sum_{i=1}^K \frac{h_i}{H} = T-K
-$$
-
-This is a contradiction, since as an requirement to the algorithm we have that $\sum_{i=1}^K T_i(T)-1 = (T-K)$, that is, we use the entire budget of samples.
-
-Another such requirement has been that $T>2K$. Plugging this in gives 
-$$
-T_k(T) - 1 \geq \frac{(T-K)h_k}{H} \leq \frac{(T-1/2T)h_k}{H} = \frac{Th_i}{2H}
-$$
-
-Now we know how often the arm has been pulled at the very end.
-That does not mean that $k$ has been pulled at time $T$.
-Thus we consider the time $t \leq T$ at which arm $k$ is pulled for the last time.
-We get (!!!!!SHOOOOWWW THIIIISSSS!!!!!!!!!)
-
-$$
-T_k(t) \geq T_k(T) - 1 \geq \frac{Th_i}{2H}.
-$$
-
-This gives us a lower bound on how often arms are pulled that are pulled frequently relative to their contribution to the problem complexity.
-Now we need a lower bound on $T_i(T)$ for every other arm $i$.
-
-### Lower Bound on $T_i(T)$
-
-Consider again as before the round $t$ in which arm $k$ is pulled for the very last time.
-Since the APT algorithm minimizes at every round $s$ the index $B_j(s)$, and pulls the arm with the smallest index, we know that arm $k$ must have had the smallest index at round $t$.
-We have:
-
-$$
-B_k(t) \leq B_i(t) \Leftrightarrow \sqrt{T_k(t)}\hat{\Delta}_k(t) \leq \sqrt{T_i(t)} \hat{\Delta}_i(t)
-$$
-
-One can already expect that this can be used to derive a lower bound on $T_i(t)$ on the RHS, and this is exactly what we do.
-
-On the LHS, we will plug in the lower bound for $T_k(t)$ derived before.
-Additionally bounding $\Delta_k(t)$ from below, and $\hat{\Delta}_i(t)$ from above using the favorable event will give the desired lower bound.
-
-Thus assume we are on the favorable event $\xi$ with large probability. we consequently have
-
-$$
-| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}.
-$$
-
-As shown in Locatelli et al. (2016), one can use the reverse triangle inequality to get:
-
-$$
-|\hat{\mu}_i(t) - \mu_i| = |(\hat{\mu}_i(t) - \tau) - (\mu_i - \tau)| \geq || \hat{\mu}_i(t) - \tau | - |\mu_i - \tau|| \geq |(|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i - \tau| + \epsilon)| \geq |\hat{\Delta}_i(t) - \Delta_i|
-$$
-
-If we combine this with the favorable event, we get
-
-$$
-\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}} \leq \hat{\Delta}_k(t) \leq \Delta_k + \sqrt{\frac{T\delta^2}{HT_k(t)}}
-$$
-
-and similar for $\hat{\Delta}_i$.
-
-We can now lower bound the LHS of the indices as
-
-$$
-\Big(\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}}\Big) \sqrt{T_k(t)} \leq B_k(t)
-$$
-
-$$
-\Big(\Delta_k - \sqrt{\frac{2}{h_k}}\delta \Big) \sqrt{\frac{Th_k}{2H}} \leq B_k(t)
-$$
-
-At this point, it is useful to have a well chosen complexity measure. If we set $h_i = \frac{1}{\Delta_i^2}$ as in Locatelli et al. (2016), we get
-
-$$
-\Big(\Delta_k - \sqrt{2}\delta \Delta \Big) \sqrt{\frac{T}{2H\Delta_k^2}} \leq B_k(t)
-$$
-
-which can be now be reduced to a form that is not specific to $k$:
-
-$$
-\Big( \frac{1}{\sqrt{2}} - \delta \Big) \sqrt{\frac{T}{H}} \leq B_k(t).
-$$
-
-Now we need to get rid of $\hat{\Delta}_i$ in order to bound $T_i(t)$. Thus, we bound the RHS again using the favorable event much as we did for the LHS:
-
-$$
-B_i(t) = \hat{\Delta}_i \sqrt{T_i(t)} \leq \Big(\Delta_i + \sqrt{\frac{T\delta^2}{HT_i(t)}}\Big) \sqrt{T_i(t)} \leq \Delta_i \sqrt{T_i(t)} + \delta \sqrt{\frac{T}{H}}
-$$
-
-As in Locatelli et al. (2016) we use the fact that by definition $\Delta$ and $\hat{\Delta}$ are positive in order to square both sides and write
-
-$$
-(1 - 2\sqrt{2}\delta)^2 \frac{T}{2H\Delta^2_i} \leq T_i(t) \leq T_i(T)
-$$
-
-We thus have derived a lower bound on the amount of pulls for any arm.
-That means that we can show that no arm is pulled an insufficient amount of times with large probability, and that consequently the favorable event hold and the estimated mean is sufficienctly separated from the threshold.
-
-### Check Separation Condition
-
-As the last step, we need to check whether the lower bound on the pulls of any arm suffices to ensure that the separation condition holds on the favorable event.
-That means, given $T_i(T) \geq (1-2\sqrt{2}\delta)^2 \frac{T}{2H\Delta_i^2}$, do we have $|\hat{\mu}_i(T) - \mu | \leq \frac{\Delta}{2}$ on the favorable event $\xi = \Big\{|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}}\Big\}$?
-
-To check, we plug the lower bound into the favorable event and get
-
-$$
-|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}} \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}
-$$
-Using $\delta = (4\sqrt{2})^-1$ as in Locatelli et al. (2016), we get
-
-$$
-|\hat{\mu}_i - \mu | \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta} \leq \frac{1}{2}\Delta_i.
-$$
-
-Thus the separation condition still holds for this value of $\delta$.
-
-### Upper Bound on Error Probability
-
-We have seen that on the favorable event $\xi$, which holds with large probability $\mathbb{P}(\xi)$, the separation condition holds as all arms have been pulled a sufficient number of times, such that their estimated mean is close to the true mean.
-All arms are classified correctly, and the algorithm does not suffer a loss.
-On the other hand, we make an error whenever the favorable event does not hold after all; that is, the deviation bound for the mean does not hold.
-At least one arm is misclassified and the arm suffers a loss.
-This occurs with probability $1-\mathbb{P}(\xi)$.
-Consequently, the expected loss is upper bounded by
-
-$$
-\mathbb{E}[L] = 1 - \mathbb{P}(\xi) \leq 2(\log(T)+1)K \exp(-\frac{1}{64R^2}\frac{T}{H}).
-$$
-
-## Discussion
+## Discussion \label{sec:DiscussionLocatelli}
 

### 2017-08-26 Thesis/Draft.tex
Update APT section

@@
             pdftitle={Draft},
-            pdfauthor={Tim Radtke},
             colorlinks=true,
@@
   \posttitle{\par}
-  \author{Tim Radtke}
-  \preauthor{\centering\large\emph}
-  \postauthor{\par}
-  \predate{\centering\large\emph}
-  \postdate{\par}
-  \date{5/28/2017}
+  \author{}
+  \preauthor{}\postauthor{}
+  \date{}
+  \predate{}\postdate{}
 
@@
 \usepackage{bbm}
+\usepackage{hyperref}
 \usepackage[lined,boxed]{algorithm2e}
 \newtheorem{theorem}{Theorem}
+\newtheorem{definition}{Definition}
 \newtheorem{lemma}{Lemma}
@@
 
-\section{Introduction to Sequential Sampling and Multi-Armed
-Bandits}\label{introduction-to-sequential-sampling-and-multi-armed-bandits}
+\section{\texorpdfstring{Introduction
+\label{chap:Introduction}}{Introduction }}\label{introduction}
 
@@
 that are equal to 1 when the best arm has not been identified (Russo,
-2016; Garivier and Kaufmann, 2016).
-
-The problem of best arm identification can readily be extended to the so
-called Top-\(m\) problem of identifying the best \(m\) of \(K\) arms.
-
-\begin{itemize}
-\item
-  Chernoff -\textgreater{} Sequential Sampling; as mentioned by Russo;
-  Garivier and Kaufmann
-\item
-  Thompson
-\item
-  Optimality for Stochastic Cumulative Regret
-\item
-  UCB, KL-UCB, Thompson Sampling
-\end{itemize}
-
--\textgreater{} Many variations: Infinite-armed, adversarial, dueling
-
-\begin{itemize}
-\item
-  Best Arm Identification
-\item
-  Top-\(m\) Identification
-\item
-  Thresholding Bandit Problem
-\item
-  Maybe an example?
-\end{itemize}
+2016; Garivier and Kaufmann, 2016). These binary measures correspond to
+the probability of the identified arm being the best, and thus
+inherently related to hypothesis testing. The problem of best arm
+identification can readily be extended to the so called Top-\(m\)
+problem of identifying the best \(m\) of \(K\) arms (Kaufmann and
+Kalyanakrishnan, 2013; Kaufmann et al. 2016).
+
+In this thesis, we consider the thresholding bandit problem. Instead of
+identifying the best \(m\) out of \(K\) arms, one aims to find all out
+of \(K\) distributions that have a mean larger than a threshold fixed
+upfront. In the form described in Locatelli et al. (2016), algorithms in
+the thresholding bandit problem are evaluated against a binary loss
+function penalizing whenever an arm has not been classified correctly as
+being above the threshold and thus focus on exploration similar to
+algorithms employed for best arm identification. Indeed, Locatelli et
+al. (2016) show how their thresholding algorithm can be used for best
+arm identification when the mean of the best arm is known upfront.
+
+In the following, we first present the thresholding bandit problem in
+detail. To then extend upon the algorithm proposed by Locatelli et al.
+(2016), we first explore how the Kullback-Leibler divergence has been
+employed in the best arm identification literature by Garivier and
+Kaufmann (2016) and Kaufmann et al. (2016). We shortly describe two
+variance based algorithms for the thresholding bandit problem introduced
+in Mukherjee et al. (2017) and Zhang et al. (2017), before introducing
+the new Simple Likelihood Ratio algorithm. We end with experiments to
+examine the performance of different algorithms.
 
@@
 
-\section{Thresholding Bandit Problem}\label{thresholding-bandit-problem}
-
-The \emph{Thresholding Bandit Problem} described in Locatelli et al.
-(2016) can be considered a variant of a variant. It can be framed inside
-of the wider literature of \emph{Pure Exploration} multi-armed bandit
-problems. In particular, it shares characteristics with the
-\emph{Top-\(m\)} problem. This problem is concerned with finding the
-\(m\) best arms as described by the means of their corresponding
-distributions. This in turn is similar to the \emph{combinatorial
-bandit} problem, which also aims at finding the \(m\) best arms.
-However, it is able to pull several arms at once: Think of an online
-shop that shows five recommended products on a product detail page.
-These five recommended products might each be represented by an arm, and
-we look for the products with the largest mean conversion rate. The
-thresholding bandit problem we discuss here, however, is concerned with
-pulling a single arm at a time. And so a more appropriate situation is
-that of a website presenting a banner. Again, think of an online shop
-trying to promote a certain category. The content team came up with a
-number of different designs for the banner, and it's not clear how many
-click-throughs they will gather.
-
-The idea now is that we would like to classify the banners into two
-distinct groups: A group with mean conversion rates \(\mu_i\) below
-threshold \(\tau\), and a group with mean conversion rates \(\mu_i\)
-above threshold \(\tau\). This might be the optimization problem when we
-are concerned with not falling below a certain minimum level
-click-through rate with the banners we're choosing.
-
-If it turns out that in general we can find relatively quickly whether
-arms are above or below a threshold, then this kind of test can be used
-to safeguard against very bad versions in a test. Before we move to a
-Top-\(m\) test, we might want to run a thresholding version and then
-continue only with the arms classified into the group above the
-threshold. This might be justified when adjusting parts of the checkout
-process of an online shop, where the conversion rate or the average
-order value should not drop below a threshold.
-
-\subsection{Setup}\label{setup}
-
-In any case, the problem boils down to the following. As usual in
-multi-armed bandit problems, we have \(K\) arms
-\(\mathcal{A} = \{1, \dots K\}\). We can pull arm \(k\) at time \(t\) to
-collect feedback in form of the random variable \(X_{k,t}\) which is
-distributed according to the arm's distribution \(\nu_k\). In general,
-we are concerned with estimating for each arm \(i\) the mean \(\mu_i\)
-of its distribution \(\nu_i\). In contrast to most bandit problems,
-however, we do not directly compare arms with each other by comparing
-their means. That would for example be the case for pure exploration
-bandits, where it is necessary to compare the arms because one aims to
-find the best one relative to the others. In the case of the
-thresholding bandit, however, we compare each arm's mean \(\mu_i\)
-individually against the threshold \(\tau \in \mathbb{R}\) which is
-known and fixed before the experiment. One might compare this to a pure
-exploration bandit in which the mean of the best arm is known upfront.
-We will see later that this fact leads to advantages in the design of
-algorithms which are not as readily available in other bandit settings.
-
-In Locatelli (2016), the arms' distributions are assumed to follow an
-\(R\)-sub-Gaussian distribution. Under this assumption, the authors are
-able to proof a general lower bound as well as an algorithm with a
-matching upper bound. Both hinge upon the \emph{complexity} of a given
-problem. Since bandit problems can differ in the number of the arms
-\(K\) and the means of each arm, some pose easier identification
-problems than others. Indeed, in the thresholding problem, the
-difficulty of the problem naturally depends on how close (the means of
-the) distributions are to the fixed threshold. Intuitively, the closer a
-mean \(\mu_i\) is to the threshold \(\tau\), the more difficult it is to
-distinguish the two successfully based on samples from the distribution
-\(\nu_i\). A straightforward measure of this distance is given by
-\(\Delta_i = |\tau - \mu_i| + \epsilon\), where \(\epsilon\) defines a
-\(2\epsilon\) interval around the threshold \(\tau\) in which we allow
-ourselves to make a mistake at no cost. In the case of sub-Gaussian
-distributions, this distance is not only simple but can be interpreted
-very naturally as we will come to understand later.
-
-If we extend this idea to the set of arms \(i \in \{1,...,K\}\) in a
-given bandit problem, a measure of the overall diffulty of the problem,
-or the problem's complexity, might be given by
-\(H = \sum_{i=1}^{K} \Delta_i^{-2}\). In particular, it shows that just
-adding additional arms leads to an increase in complexity (since we need
-a larger budget to sample each arm the same number of times as before).
-Likewise, a smaller \(\Delta_i\) increases the complexity as arms become
-harder to classify. Choosing the complexity measure in this way fits the
-distance measure \(\Delta_i\) and turn out to be useful in the proof of
-an upper bound for the APT algorithm presented in Locatelli et al.
-(2016).
-
-We also see that this definition may lose relevancy as we move away from
-\(R\)-sub-Gaussian distributions. (ADD QUICK EXAMPLE OF WHAT CHANGES;
-REFER TO LATER PART AND DESCRIBE THIS AS THE MOTIVATION OF THE PAPER)
-
-Another characteristic uniquely identifying bandit problems is the
-regret measure that we aim to optimize. As explained during the
-introduction, multi-armed bandits traditionally optimize cumulative
-regret. The notion of regret considered in the thresholding bandit,
-however, is more akin to the simple regret in pure exploration bandits
-or the error probability in sequential hypothesis testing. Indeed, one
-can most easily describe the regret in the thresholding case as the
-probability of misclassifying any arm. Or, more rigorously, define the
-set of all arms with mean larger than the threshold,
-\(\mathcal{S}_\tau = \{i \in \mathcal{A}: \mu_i \geq \tau\}\).
-Consequently,
-\(\mathcal{S}_\tau^C = \{i \in \mathcal{A}: \mu_i < \tau\}\). At the end
-of the sampling rule/procedure (!!we have not mentioned yet the fact
-that we're in the fixed budget case!!), we demand that any algorithm
-returns the two corresponding \emph{estimated} sets:
-\(\hat{\mathcal{S}}_{\tau} = \{i \in \mathcal{A}: \hat{\mu}_i \geq \tau\}\),
-as well as
-\(\hat{\mathcal{S}}_{\tau}^C = \{i \in \mathcal{A}: \hat{\mu}_i < \tau\}\).
-We simply demand an answer to the question which arms have means above
-the threshold \(/tau\), and which arms lie below \(\tau\). Let \(T\) be
-the overall number of samples the algorithm is allowed to pull. We
-define the loss as
-\(\mathcal{L}(T) = \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset\}} \cdot \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset\}}\).
-That is, we compare the return set with the true set and collect a loss
-of 1 if any arm with a true mean outside the \(2\epsilon\) interval
-around \(\tau\) was misclassified. It is important to realize that arms
-with means inside the \(2 \epsilon\) interval may be misclassified
-without it affecting the loss. These arms are considered close enough to
-the threshold that we do not care whether they lie above or below.
-
-ADD A GRAPHIC THAT VISUALIZES THE ESTIMATED AND THE REQUIRED RETURN SETS
-
-Now, the expected regret/loss is defined as
-\(\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \land (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset))\).
-This, of course, is the mentioned probability of making a mistake.
-
-Lastly, it is to mention that we are considering the fixed-budget
-version of the thresholding bandit problem. We thus fix the number of
-samples that the algorithm will pull upfront at \(T\). The task of the
-algorithm is then to find a sampling rule or strategy which distributes
-the budget \(T\) among the \(K\) arms in such a way that the expected
-regret, or the error probability, is minimized. In other terms, the
-algorithm aims to use the \(T\) samples in a way that lets him return
-the two sets \(\hat{\mathcal{S}}_{\tau}\) and
-\(\hat{\mathcal{S}}_{\tau}^C\) with as much confidence as possible. This
-again shows the contrast to the fixed confidence setting in which one
-fixes the confidence level upfront and lets the algorithm draw as many
-samples as necessary to reach the required confidence.
-
-At this point, we have defined the fixed budget thresholding bandit
-setup for any algorithm in the case of sub-Gaussian distributions. We
-thus proceed to describe the APT algorithm proposed in Locatelli et al.
-(2016).
-
-\subsection{The APT Algorithm}\label{the-apt-algorithm}
+\section{\texorpdfstring{Thresholding Bandit Problem
+\label{chap:ThresholdingBanditProblem}}{Thresholding Bandit Problem }}\label{thresholding-bandit-problem}
+
+To introduce the thresholding bandit problem, consider a game in which
+the learner is tasked to find those slot machines within a row of \(K\)
+slot machines in a casino that give a mean payoff larger than a fixed
+threshold \(\tau\), for example \(\tau = 0\). The learner cannot pull
+all slot machines at the same time. Instead, he acquires samples
+sequentially from one slot machine at a time to learn about their payoff
+structure. The learner has a budget of \(T\) slot machine pulls. After
+\(t-1\) samples, the learner has observed \(T_i(t-1)\) samples from slot
+machine \(i\). The payoffs \(X_{i,1}, ..., X_{i,T_i(t-1)}\) are drawn
+from the payoff distribution \(\nu_i\) underlying the slot machine
+\(i\). At time \(t\), the learner considers the payoffs he observed so
+far in order to choose the next slot machine he would like to pull. His
+decision is lead by the goal to classify the slot machines with
+distribution \(\nu_i\) and mean payoff
+\(\mu_i = \mathbb{E}_{X \sim \nu_i}[X]\) after \(T\) samples as being
+above or below the threshold with error probability as small as
+possible.
+
+The thresholding bandit problem can thus be framed in the wide
+literature on sequential sampling strategies. While its name is
+reminiscient of the multi-armed bandit setting, the thresholding bandit
+problem is more akin to best arm identification and Top-\(m\)
+identification problems due to its focus on exploration: While the
+classical multi-armed bandit problems are concerned with cumulative
+regret which increases \emph{during} sampling, best arm identification
+and thresholding bandits collect loss only once \emph{after} the
+sampling procedure (compare Garivier and Kaufmann, 2016; Kaufmann et
+al., 2016; Kaufmann and Kalyanakrishnan, 2013). Furthermore, as there
+arises an implicit threshold between the means of the \(m\)-th best arm
+and the \(m+1\)-th best arm (Kaufmann et al., 2016; Kaufmann and
+Kalyanakrishnan, 2013), algorithms for the Top-\(m\) identification
+problem classify arms at least implicitly as being above or below a
+threshold. The two settings are thus very related.
+
+\subsection{\texorpdfstring{Setup
+\label{sec:Setup}}{Setup }}\label{setup}
+
+Consider a setting with a set of \(\mathbb{A}=\{1, ..., K\}\) unknown
+probability distributions \(\nu_i, i \in \mathbb{A}\). To stick with the
+idea of multi-armed bandits, we call those distributions arms, and
+observations from those arms rewards (Bubeck and Cesa-Bianchi, 2012).
+The learner is interested in learning about the structure of the arms;
+in particular, he would like to estimate the means \(\mu_1, ..., \mu_K\)
+by sequentially drawing observations \(X_{i,1}, X_{i,2}, ...\) from each
+arm. However, at time \(t\) the learner cannot observe a reward from
+every distribution but must select a single arm \(I_t\) from which he
+would like to observe the reward \(X_{I_t,t}\). An adaptive sampling
+strategy makes the decision of which arm to pull usually by computing an
+index \(B_i(t)\) for each arm. If \(T_i(t)\) is the number of samples
+observed until time \(t\) for arm \(i\), then \(B_i(t)\) is a function
+of the past rewards \(X_{i,1}, ..., X_{i,T_i(t)}\) observed for arm
+\(i\), and w.l.o.g. \(I_t = \arg \min_{i = 1,...K} B_i(t)\). The set of
+indices can be called strategy (Kaufmann et al., 2012) which makes it
+clear that the strategy is adapted as more observations are collected.
+Strategies of this kind are also called index policies.
+
+What index proves to be useful is determined by the loss function with
+which the decisions of the algorithm are evaluated. While many problems
+are concerned with finding the arm with the largest mean \(\mu_i\), in
+which algorithms collect loss either cumulatively (Auer and
+Cesa-Bianchi, 2012) or once at the end of the sampling (Kaufmann et al.,
+2016), the thresholding bandit problem considers a slightly different
+loss function. Consider a fixed threshold value \(\tau \in \mathbb{R}\)
+and an epsilon interval \(\tau \pm \epsilon\) around the threshold for
+\(\epsilon \geq 0\). As mentioned in the introduction, the learner is
+tasked with classifying arms as having a mean \(\mu_i\) larger or
+smaller than \(\tau\). To describe which arms are above the threshold,
+we introduce the following set notation (compare Locatelli et al.,
+2016): Let \(\mathcal{S}_{\tau}\) be the set of distributions in
+\(mathbb{A}\) with mean larger than the threshold:
+\(\mathcal{S}_{\tau} := \{i \in \mathbb{A}, \mu_i \geq \tau\}\).
+Consequently, the complement is given by the arms with mean below the
+threshold,
+\(\mathcal{S}^C_{\tau} := \{i \in \mathbb{A}, \mu_i < \tau\}\).
+
+The thresholding problem for the learner is now to use a budget of
+overall \(T\) samples (or rounds) to explore the different arms. After
+this exploration phase, the learner has to return a set of arms that he
+believes to have a mean above the threshold. The problem can thus be
+described by the threshold \(\tau\) and a precision \(\epsilon\). When
+evaluating the classification of the learner, arms with mean inside of
+the epsilon interval will not be considered. The learner only has to
+distinguish the means from the threshold correctly up to the precision
+\(\epsilon\). Thus, the algorithm is not evaluated against
+\(\mathcal{S}_{\tau}\) and \(\mathcal{S}^C_{\tau}\), but needs to
+distinguish \(\mathcal{S}_{\tau+\epsilon}\) from
+\(\mathcal{S}^C_{\tau-\epsilon}\). As in Locatelli et al. (2016),
+whenever we say that ``an arm is over the threshold'', we mean that the
+mean of the arm is over the threshold.
+
+The learner's classification is returned as the set
+\(\hat{\mathcal{S}}_{\tau} := \hat{\mathcal{S}}_{\tau}(T) \subset \mathbb{A}\)
+after \(T\) rounds; that is, the set of arms estimated to be over the
+threshold. The classification is evaluated against the loss given as
+(Locatelli et al., 2016):
+
+\[
+\mathcal{L}(T) = \mathbbm{1}{(\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \lor (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset)}
+\]
+
+In order to perform well, a learner has to identify all arms that are
+over the threshold as such, and to not claim arms as being over the
+threshold if they actually are below the threshold. Due to the precision
+\(\epsilon\), the loss is not influenced by arms which are too close to
+the threshold \(\tau\), that is, arms inside of the
+\(\tau \pm \epsilon\) interval. If either \(\hat{\mathcal{S}}_{\tau}\)
+contains an arm below \((\tau - \epsilon)\), or
+\(\hat{\mathcal{S}}^C_{\tau}\) contains an arm above
+\((\tau + \epsilon)\), a loss of \(1\) is accrued. Else, all arms
+outside the epsilon interval are classified correctly and the loss is
+equal to \(0\). In the case of \(\epsilon = 0\), all arms need to be
+classified correctly to not endure any loss.
+
+Algorithms for this thresholding problem can be compared based on their
+expected loss. Let \(\mathbb{E}\) be the expectation with regard to the
+samples \(X_{i,1}, ..., X_{i,T}\) collected by the algorithm. The
+expected loss is then given as
+
+\[
+\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}\big((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \lor(\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset)\big),
+\]
+
+which corresponds to the probability of making a wrong classification.
+Both the probability of not identifying an arm that is actually over the
+threshold, as well as the probability of accepting an arm as over the
+threshold when it is not are evaluated. The oracle strategy would
+evaluate all arms correctly with an error probability of \(0\)
+(Locatelli et al., 2016).
+
+At this point, we have introduced the general thresholding bandit
+problem setting which we will use throughout the thesis. The setting
+might be extended by different assumptions to make certain algorithms or
+bounds feasible. For that reason, Locatelli et al. (2016) assume that
+the distributions \(\nu_i, i \in \mathbb{A}\) are \(R\)-sub-Gaussian.
+Under this assumption, the authors are able to prove a lower bound on
+the largest probability of error of the best algorithm in the setting we
+have just introduced, as well as an upper bound on the performance of
+their APT algorithm we will introduce in the following chapter. As in
+their paper, we define \(R\)-sub-Gaussian and assume it in the
+description of their algorithm and bounds:
+
+\begin{definition}[$R$-sub-Gaussian distribution] 
+\label{definition:rsubgaussian}
+Let $R > 0$. A distribution $\nu$ is $R$-sub-Gaussian if for all $t \in \mathbb{R}$ we have
+\begin{equation*}
+\mathbb{E}_{X \sim \nu}[\exp(tX - t\mathbb{E}[X])] \leq \exp(R^2t^2/2).
+\end{equation*}
+\end{definition}
+
+As noted by Locatelli et al. (2016), this ensures that the mean
+\(\mu_i\) of the distributions \(\nu_i\) considered in our problem are
+finite. \(R\)-sub-Gaussian distributions furthermore offer concentration
+inequalities for the concentration of the empirical mean to the true
+mean, which makes it possible to deduce the bounds presented by the
+authors and repeated below. The family of \(R\)-sub-Gaussian
+distributions encompasses Gaussian distributions of variance \(R^2\) for
+\(R \in \mathbb{R}\), as well as all bounded distributions, with the
+important case of Bernoulli distributions.
+
+Having described the thresholding bandit setting as well as the
+assumption of \(R\)-sub-Gaussianity, we can now proceed to describe the
+\emph{Anytime Parameter-free Thresholding} (APT) algorithm proposed in
+Locatelli et al. (2016) for the thresholding bandit problem.
+
+\subsection{\texorpdfstring{The Anytime Parameter-free Thresholding
+Algorithm
+\label{sec:TheAPTAlgorithm}}{The Anytime Parameter-free Thresholding Algorithm }}\label{the-anytime-parameter-free-thresholding-algorithm}
+
+In the following we describe the \emph{Anytime Parameter-free
+Thresholding} (APT) algorithm proposed in Locatelli et al. (2016), which
+is a simple yet effective algorithm and displays some very favorable
+characteristics when compared to alternative algorithms.
+
+We fix the threshold \(\tau\) and epsilon interval around the threshold
+given by \(\epsilon\) upfront, and supply them as arguments to the
+algorithm: \((\tau, \epsilon)\). Based on the general thresholding
+problem, we demand that the algorithm draws samples \(X_{i,t}\) for
+\(T\) rounds from the distributions \(\nu_i, i\in \mathbb{A}\). For a
+given arm \(i\) and a given time \(t\), we let \(T_i(t)\) represent the
+number of samples drawn from arm \(i\) until time \(t\) (including).
+Consequently, the empirical mean of arm \(i\) at time \(t\) is given by
+\(\hat{\mu}_i(t) = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}\) where
+\(X_{i,s}\) is the feedback sampled from distribution \(\nu_i\) when the
+arm is pulled for the \(s\)-th time. In the case of the APT algorithm,
+the decision \(\hat{\mathcal{S}}_{\tau}\) is based on the empirical
+means \(\hat{\mu}_i(T)\) estimated from the samples drawn up to time
+\(T\):
+\(\hat{\mathcal{S}}_{\tau} := \hat{\mathcal{S}}_{\tau}(T) = \{i \in \mathbb{A}, \hat{\mu}_i(T) \geq \tau\}\).
+
+As we see in algorithm \ref{alg:APT}, the APT algorithm initiates by
+pulling each arm once. Then, for each \(t > K\), it calculates for every
+arm the values \(T_i(t)\) and \(\hat{\mu}_i(t)\). Based on the empirical
+mean, the algorithm computes the estimated gap between the mean and the
+threshold as
+\(\hat{\Delta}_i(t) = \hat{\Delta}_i^{\tau, \epsilon}(t) = |\mu_i(t) - \tau| + \epsilon\).
+The decision of which arm is sampled next is then based on the value
+\(B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t)\): the algorithm pulls arm
+\(I_{t+1} = \arg \min_{i\leq K} B_i(t+1)\) minimizing this decision
+quantity. After overall \(T\) pulls, the algorithm returns the sets
+described in the general setup, \(\hat{\mathcal{S}}_{\tau}\) and
+\(\hat{\mathcal{S}}^C_{\tau}\).
 
@@
 \For{$t = K+1$ \KwTo $T$}{
-  \emph{Pull arm $I_t = \arg \min_{k\leq K} B_k^{APT}(t) = \sqrt{T_k(t)} \sqrt{|\hat{\mu}_i(t) - \tau|+\epsilon}$}\;
+  \emph{Pull arm $I_t = \arg \min_{k\leq K} B_k^{APT}(t) = \sqrt{T_k(t)} (|\hat{\mu}_i(t) - \tau|+\epsilon)$}\;
   \emph{Observe reward $X \sim \nu_{I_t}$}\;
 }
-\caption{Anytime Parameter-free Thresholding Algorithm (Locatelli et al., 2016)}\label{algo_apt}
+\caption{Anytime Parameter-free Thresholding Algorithm (Locatelli et al., 2016)}\label{alg:APT}
 \end{algorithm}
@@
 
-In the following we describe the \emph{Anytime Parameter-free
-Thresholding} (APT) algorithm proposed in Locatelli et al. (2016), which
-is a simple yet effective algorithm and displays some very favorable
-characteristics when compared with alternative algorithms.
-
-From the general setup, we already know how the algorithm will end.
-After it has drawn \(T\) samples, the algorithm makes a decision of
-which arms to include in the return sets on basis of the empirical means
-\(\hat{\mu}_i(T)\) estimated based on the samples drawn until time
-\(T\). Furthermore, the threshold and interval around the threshold are
-fixed upfront and serve as argument to the algorithm:
-\((\tau, \epsilon)\). For a given arm \(i\) and a given time \(t\), we
-let \(T_i(t)\) represent the number of samples drawn from arm \(i\)
-until time \(t\) (including). Consequently, the empirical mean of arm
-\(i\) at time \(t\) is given by
-\(\hat{\mu}_i(t) = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}\) where
-\(X_{i,s}\) is the feedback sampled from distribution \(\nu_i\) when the
-arm is pulled for the \(s\)-th time.
-
-To be specific, the APT algorithm initiates by pulling each arm once.
-Then, for each \(t > K\), it calculates for every arm the values
-\(T_i(t)\) and \(\mu_i(t)\). Based on the empirical mean, the algorithm
-computes the estimated gap between the mean and the threshold as
-\(\hat{\Delta}_i(t) = \hat{\Delta}_i^{\tau, \epsilon}(t) = |\mu_i(t) - \tau| + \epsilon\).
-The decision of which arm is sampled next is then based on the value
-\(B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t)\): the algorithm pulls arm
-\(I_{t+1} = \arg \min_{i\leq K} B_i(t+1)\) minimizing this decision
-quantity. After \(T\) pulls overall, the arm returns the sets described
-in the general setup, \(\hat{\mathcal{S}}_{\tau}\) and
-\(\hat{\mathcal{S}}^C_{\tau}\).
-
-\textbf{Remark}: Obviously, the APT algorithm tends to pull arms more
-often with corresponding mean close to the threshold and interval (small
-\(\hat{\Delta}_i(t))\). This makes sure that more evidence is gathered
-on arms which appear to be inherently difficult to classify based on the
-samples collected until time \(T_i(t)\), as these arms stifle the
-confidence the most. That is, until we have collected enough evidence to
-make a confident classification even if the mean is truly close to the
-threshold. In that case, \(\sqrt{T_i(t)}\) will raise \(B_i(t+1)\).
-Consequently, other arms farther away from the threshold will be sampled
-again. In this way, the algorithm tries to distribute the budget \(T\)
-over all arms so as to define a sampling rule optimizing the confidence
-of the final decision.
-
-\subsection{Discussion}\label{discussion}
+Just like the general index policies mentioned in \autoref{sec:Setup},
+we see that the APT algorithm adapts its strategy using an index
+\(B_i(t+1)\) for each arm that is based entirely on the observations
+observed until time \(t\). Given the arm with the smallest index is
+pulled at round \(t+1\), we observe that arms that are estimated to be
+further away from the threshold \(\tau\) as measured by the absolute
+distance to their empirical mean \(\hat{\mu}_i\), \(\hat{\Delta}_i(t)\),
+are pulled less often. Intuitively, it is easier to classify arms as
+below or above \(\tau\) when their mean is far away from the threshold.
+In contrast to the uniform sampling strategy, APT will gather more
+evidence for arms which appear to be inherently more difficult to
+classify. Likewise, APT tends to pull arms less often which it already
+pulled considerably often as measured by \(T_i(t)\). If arm \(i\) has
+been pulled more often than arm \(j\), then we should in general be more
+confident in its estimated mean and the corresponding distance to the
+threshold. If we are confident in \(i\), then it is better to explore
+other arms by drawing an observation from arm \(j\). By adapting its
+sampling strategy in this way during the sequential sampling process,
+the APT algorithm minimizes the probability of error
+\(\mathbb{E}[\mathcal{L}(T)]\) after \(T\) samples have been observed.
+
+The previous paragraph describes how arms close to the threshold are
+intuitively more difficult to classify. In the index employed by the APT
+algorithm, the distance between an arm and the threshold is measured by
+the absolute distance \(\hat{\Delta}_i(t)\) between the (estimated) mean
+of the arm and the threshold \(\tau\) (and the epsilon interval). Given
+that one compares \(B_i^{APT}\) with \(B_j^{APT}\), one could just as
+well measure the distance by the squared distance,
+\(\hat{\Delta}_i(t)^2\). When the APT algorithm realizes that an arm has
+a mean close to the threshold, then this arm requires more attention
+than an arm far away from the threshold; the confidence in the empirical
+mean has to be larger. Or the empirical mean has to be better
+concentrated around the true mean. Otherwise it is easier to make a
+mistake on this arm. To gain this confidence, the arm requires more
+samples, and thus a larger share of the overall \(T\) samples available.
+With this intuition, it makes sense to measure the complexity of a
+thresholding problem: If we knew upfront how complex a given set of arms
+is, we knew whether we can expect a small or large probability of error
+given our budget \(T\). Also, for example in the best arm identification
+problem, there exist algorithms which take the complexity of a problem
+as input. Based on the complexity they then adapt their sampling
+strategy. See for example the UCB-E algorithm in Audibert et al. (2010)
+for the best arm identification problem, or the KL-LUCB-E algorithm in
+Kaufmann and Kalyanakrishnan (2013) as extension to the Top-\(m\)
+problem.
+
+While the APT algorithm does not require the complexity to be known
+upfront (which would be problematic), it is necessary to define the
+complexity to deduce the upper bound on its probability of error.
+Similar to the distance measure used in the algorithm's index, we define
+the gap \(\Delta_i^{\tau,\epsilon}\) between arm \(i\) and the threshold
+\(\tau \pm \epsilon\) as
+
+\[
+\Delta_i := \Delta_i^{\tau,\epsilon} = |\mu_i - \tau| + \epsilon
+\]
+
+Given this gap, Locatelli et al. (2016) define the complexity
+\(H_{\tau, \epsilon}\) for the thresholding bandit problem naturally as
+
+\[
+H := H_{\tau, \epsilon} = \sum_{i=1}^K \frac{1}{(\Delta_i^{\tau,\epsilon})^2}.
+\]
+
+Note that the complexity of the problem increases in the number of arms
+\(K\) and decreases in the gap \(\Delta_i^{\tau,\epsilon}\).
+Consequently, when we require a smaller precision, that is, we increase
+\(\epsilon\), the hardness decreases. Furthermore, we see that each arm
+contributes its individual complexity,
+\(h_i^{\tau,\epsilon} = \frac{1}{(\Delta_i^{\tau,\epsilon})^2}\)
+linearly into the problem. Thus, if the complexity \(H\) is a good
+measure of the actual problem complexity, and we knew upfront which arm
+has which mean, we could allocate the ``optimal'' share of the budget,
+\(T \cdot h_i /H\) to arm \(i\). However, since we do not know neither
+\(\mu_i\) nor \(H\), the best we can do is to adapt our allocation of
+samples more and more towards this optimum as we observe samples.
+
+At this point, one can question whether the measure of complexity \(H\)
+proposed in Locatelli et al. (2016) is a good measure of the ``true''
+problem complexity. In the following \autoref{sec:UpperBoundLocatelli},
+we will show the upper bound on the probability of error for the APT
+algorithm and see how the complexity \(H\) arises naturally for the APT
+algorithm. In \autoref{sec:LowerBoundLocatelli} we then show the lower
+bound presented in Locatelli et al. (2016) and that the APT algorithm is
+optimal in that it matches the lower bound. We discuss the results and
+the APT algorithm further in \autoref{sec:DiscussionLocatelli}.
+
+\subsection{\texorpdfstring{Upper Bound for the APT Algorithm
+\label{sec:UpperBoundLocatelli}}{Upper Bound for the APT Algorithm }}\label{upper-bound-for-the-apt-algorithm}
+
+In this chapter we present the upper bound on the APT algorithm proven
+in Locatelli et al. (2016). The upper bound is on the probability of
+error that the algorithm has after \(T\) rounds of sampling for a
+problem with arms that are assumed to be \(R\)-sub-Gaussian. The bound
+depends also on the complexity of the problem, and we show in the proof
+that given the index of the APT algorithm as defined in
+\autoref{sec:TheAPTAlgorithm}, the complexity \(H\) is an appropriate
+measure.
+
+We now state the theorem as in Locatelli et al. (2016) and present a
+proof.
+
+\begin{theorem}[Theorem 2, Locatelli et al., 2016] \label{theorem:LocatelliTheorem4}
+Let $K \geq 0$, $T \geq 2K$, and consider a problem $\mathcal{B}$.
+Assume that all arms $\nu_i$ of the problem are R-sub-Gaussian with means $\mu_i$.
+Let $\tau \in \mathbb{R}, \epsilon \geq 0$.
+Algorithm APT's expected loss is upper bounded on this problem as
+\begin{equation*} \mathbb{E}(\mathcal{L}(T)) \leq \exp
+(-\frac{1}{64R^2}\frac{T}{H} + 2 \log (T) + 1)K)) \end{equation*}
+
+where we remind that $H = \sum_i (|\mu_i - \tau | + \epsilon)^{-2}$ and where
+$\mathbb{E}$ is the expectation according to the samples of the problem.
+\end{theorem}
+
+\subsubsection{\texorpdfstring{Proof of Theorem
+\ref{theorem:LocatelliTheorem4}}{Proof of Theorem }}\label{proof-of-theorem}
+
+In order to upper bound the expected loss of the APT algorithm, we want
+to define an event on which the algorithm correctly seperates arms from
+the threshold, that is, a separation condition holds on this event. We
+then want to show that this \emph{favorable} event does indeed hold with
+large probability. Consequently, APT's probability of error will
+correspond to the probability that the favorable event does not hold, as
+this leads to a failure of the seperation condition, and consequently to
+an incorrect classification of at least one arm by the algorithm. We
+start by defining the separation condition.
+
+\subsubsection{Separation Condition}\label{separation-condition}
+
+As noted in Zhong et al. (2017), a simple requirement to correctly
+classify arms at the final round is the following. For every arm
+\(i \in \{1, ..., K\}\) after the final round \(T\), require \[
+\hat{\mu}_{i,T_i(n)} \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
+\] or \[
+\hat{\mu}_{i,T_i(n)} \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
+\] Or simply in terms of the gap between the arm and the threshold as
+used in the index by the APT algorithm: \[
+| \hat{\mu}_{i, T_i(n)} - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
+\]
+
+Intuitively, this condition makes sense as it ensures that the current
+mean estimate is closer to the true mean than to the threshold.
+Consequently, there is no arrangement possible in which the arm is
+classified wrong while the separation condition holds. Assuming
+\(\mu_i < \tau\) and \(\epsilon = 0\), an incorrect classification would
+require \(\mu_i < \tau \leq \hat{\mu_i}\). But then
+\(| \hat{\mu}_{i, T_i(n)} - \mu_i | \geq |\mu_i - \tau|\), which
+violates the separation condition.
+
+Thus, we need to show that this condition holds for every arm
+\(i \in \{1,...,K\}\) with large probability after the final round
+\(T\). In different words, we need to derive an upper bound on the
+probability with which this condition does not hold.
+
+\subsubsection{The Favorable Event}\label{the-favorable-event}
+
+The separation condition describes what event needs to hold in order for
+the APT algorithm to make a correct classification: The smaller the
+deviation of the empirical mean from the population mean, the more
+difficult it is for the classification to be wrong. Moreover, if the
+mean and empirical mean are identical, then the classification is
+correct independent of the threshold. Also, the closer the mean to the
+threshold, the better the estimate has to be for a correct
+classification to be likely. To bound the absolute deviation of the
+empirical mean from the true mean, we define the favorable event \(\xi\)
+as
+
+\[
+\xi = \Big\{\forall i \in \mathbb{A}, \forall s \in \{1,...,T\} : |\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}} \Big\}.
+\]
+
+The probability that this favorable event occurs should be large, or
+equivalently, the probability that the deviation is small should be
+large. Then it follows that the separation condition holds with large
+probability.
+
+\begin{itemize}
+\tightlist
+\item
+  Show Chernoff/Hoeffding bound detailed
+\item
+  Show union bound to get deviation for all arms \(i \leq K\) and every
+  round \(s \leq T\)
+\end{itemize}
+
+\[
+\mathbb{P}(\xi) \geq 1 - 2(\log(T) +1)K \exp(-\frac{T\delta^2}{2R^2H})
+\]
+
+\subsubsection{\texorpdfstring{Need to Bound
+\(T_i\)}{Need to Bound T\_i}}\label{need-to-bound-t_i}
+
+We now have that with large probability the favorable event holds. On
+the favorable event, we have for every arm \(i\):
+
+\[
+| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}
+\]
+
+The deviation of arm \(i\) at time \(t\) depends on how large \(H\),
+\(T\), and \(T_i(t)\) are. While \(t\), \(H\), \(T\) are deterministic,
+the number of times arm \(i\) has been pulled at round \(t\),
+\(T_i(t)\), is a random variable. In order to know how large the
+probability of the favorable event is (and thus the error probability),
+we need to know the value of \(T_i(t)\), or at least bound a range of
+potential values. Put differently: To ensure a deviation smaller than
+\(\sqrt{\frac{T\delta^2}{HT_i(t)}}\) for arm \(i\), we need to ensure
+that arm \(i\) has been pulled at least \(T_i(t)\) times. As usual in
+multi-armed bandits, and different from uniform sampling, the number of
+pulls is a random variable that also depends on how often other arms are
+pulled. In general, we do not want each arm to be pulled an equal
+amount, but each arm should be pulled some times, and not too many
+times.
+
+Thus, in order to check that the deviation of arm \(i\) really is small
+enough for the separation condition to hold on the favorable event, we
+need to bound the number of pulls of every arm from below.
+
+\subsubsection{\texorpdfstring{Characteristics of a Frequently Pulled
+Arm (Lower Bound on
+\(T_k(T)\))}{Characteristics of a Frequently Pulled Arm (Lower Bound on T\_k(T))}}\label{characteristics-of-a-frequently-pulled-arm-lower-bound-on-t_kt}
+
+Given that we do not follow a uniform sampling strategy, we know that at
+time \(T\), some arms will have been pulled more frequently than others.
+In particular, some arms will have been pulled more than \(T/K\) times.
+How often an arm is pulled can be related to the individual arm's
+contribution to the overall complexity measure. Let \(h_i\) be a measure
+of arm \(i\)'s individual problem complexity and write for the overall
+problem complexity \(H = \sum_{i = 1}^{K} h_i\). Then arm \(i\)
+contributes a share of \(h_i/H\) to the overall problem complexity. We
+can now show that there exists an arm that has been pulled at least as
+often as the share of his complexity contribution.
+
+Given the initialization of the APT algorithm, every arm is pulled once
+initially. Consequently, there is a budget of \(T-K\) rounds left after
+the initialization. As shown in Locatelli et al. (2016), there exists an
+arm \(k\) that has been pulled after the initialization (\(\geq 2\)
+pulls) and for which at the final round \(T\) it holds:
+\(T_k(T) - 1 \geq \frac{(T-K)h_k}{H}\). This can be shown by a
+contradiction. Assume that the opposite holds, that is
+
+\[
+\forall i \in \{1,...,K\}: T_i(T) - 1 < \frac{(T-K)h_i}{H}
+\]
+
+Consequently, at time \(T\), we would have pulled across all arms
+\(\sum_{i=1}^KT_i(T)-1\) times. If the previous assumption holds, we
+would not have used the entire budget:
+
+\[
+\sum_{i=1}^K T_i(T)-1 < \sum_{i=1}^K \frac{(T-K)h_i}{H} = (T-K)\sum_{i=1}^K \frac{h_i}{H} = T-K
+\]
+
+This is a contradiction, since as an requirement to the algorithm we
+have that \(\sum_{i=1}^K T_i(T)-1 = (T-K)\), that is, we use the entire
+budget of samples.
+
+Furthermore, we have assumed \(T>2K\) in the statement of Theorem
+\ref{theorem:LocatelliTheorem4}. Plugging this in gives \[
+T_k(T) - 1 \geq \frac{(T-K)h_k}{H} \geq \frac{(T-1/2T)h_k}{H} = \frac{Th_i}{2H}
+\]
+
+Now we know how often the arm has been pulled at the very end. That does
+not mean that \(k\) has been pulled at time \(T\). Thus we consider the
+time \(t \leq T\) at which arm \(k\) is pulled for the last time. We get
+
+\[
+T_k(t) \geq T_k(T) - 1 \geq \frac{Th_i}{2H}.
+\]
+
+This gives us a lower bound on how often arms are pulled that are pulled
+frequently relative to their contribution to the problem complexity. Now
+we need a lower bound on \(T_i(T)\) for every other arm \(i\).
+
+\subsubsection{\texorpdfstring{Lower Bound on
+\(T_i(T)\)}{Lower Bound on T\_i(T)}}\label{lower-bound-on-t_it}
+
+Consider again as before the round \(t\) at which arm \(k\) is pulled
+for the very last time. Since the APT algorithm minimizes at every round
+\(s \geq K+1\) the index \(B_j(s)\), and pulls the arm with the smallest
+index, we know that arm \(k\) must have had the smallest index at round
+\(t\). We have:
+
+\[
+B_k(t) \leq B_i(t) \Leftrightarrow \sqrt{T_k(t)}\hat{\Delta}_k(t) \leq \sqrt{T_i(t)} \hat{\Delta}_i(t)
+\]
+
+One can already expect that this can be used to derive a lower bound on
+\(T_i(t)\) on the RHS, and this is exactly what we do. On the LHS, we
+plug in the lower bound for \(T_k(t)\) derived before. Additionally
+bounding \(\Delta_k(t)\) from below, and \(\hat{\Delta}_i(t)\) from
+above using the favorable event will give the desired lower bound.
+
+Thus assume we are on the favorable event \(\xi\) with large
+probability. we consequently have
+
+\[
+| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}.
+\]
+
+As shown in Locatelli et al. (2016), one can use the reverse triangle
+inequality to get:
+
+\begin{align*}
+|\hat{\mu}_i(t) - \mu_i| & = & |(\hat{\mu}_i(t) - \tau) - (\mu_i - \tau)| \\
+& \geq & || \hat{\mu}_i(t) - \tau | - |\mu_i - \tau|| \\
+& \geq & |(|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i - \tau| + \epsilon)| \\
+& \geq & |\hat{\Delta}_i(t) - \Delta_i|
+\end{align*}
+
+If we combine this with the favorable event, we get
+
+\[
+\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}} \leq \hat{\Delta}_k(t) \leq \Delta_k + \sqrt{\frac{T\delta^2}{HT_k(t)}}
+\]
+
+and similar for \(\hat{\Delta}_i\). We can now lower bound the LHS of
+the indices as
+
+\begin{align*}
+B_k(t) & \geq & \Big(\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}}\Big) \sqrt{T_k(t)} \\
+& \geq & \Big(\Delta_k - \sqrt{\frac{2}{h_k}}\delta \Big)
+\end{align*}
+
+At this point, it is useful to have a well chosen complexity measure. If
+we set \(h_i = \frac{1}{\Delta_i^2}\) as in Locatelli et al. (2016), we
+get
+
+\[
+\Big(\Delta_k - \sqrt{2}\delta \Delta \Big) \sqrt{\frac{T}{2H\Delta_k^2}} \leq B_k(t)
+\]
+
+which can be now be reduced to a form that is not specific to \(k\):
+
+\[
+\Big( \frac{1}{\sqrt{2}} - \delta \Big) \sqrt{\frac{T}{H}} \leq B_k(t).
+\]
+
+Now we need to remove \(\hat{\Delta}_i\) in order to bound \(T_i(t)\).
+Thus, we bound the RHS again using the favorable event much as we did
+for the LHS:
+
+\[
+B_i(t) = \hat{\Delta}_i \sqrt{T_i(t)} \leq \Big(\Delta_i + \sqrt{\frac{T\delta^2}{HT_i(t)}}\Big) \sqrt{T_i(t)} \leq \Delta_i \sqrt{T_i(t)} + \delta \sqrt{\frac{T}{H}}
+\]
+
+As in Locatelli et al. (2016) we use the fact that by definition
+\(\Delta\) and \(\hat{\Delta}\) are positive in order to square both
+sides and write
+
+\[
+(1 - 2\sqrt{2}\delta)^2 \frac{T}{2H\Delta^2_i} \leq T_i(t) \leq T_i(T)
+\]
+
+We thus have derived a lower bound on the amount of pulls for any arm.
+That means that we can show that no arm is pulled an insufficient amount
+of times with large probability, and that consequently the favorable
+event hold and the estimated mean is sufficienctly separated from the
+threshold.
+
+\subsubsection{Check Separation
+Condition}\label{check-separation-condition}
+
+As the last step, we need to check whether the lower bound on the pulls
+of any arm suffices to ensure that the separation condition holds on the
+favorable event. That means, given
+\(T_i(T) \geq (1-2\sqrt{2}\delta)^2 \frac{T}{2H\Delta_i^2}\), do we have
+\(|\hat{\mu}_i(T) - \mu | \leq \frac{\Delta}{2}\) on the favorable event
+\(\xi = \Big\{|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}}\Big\}\)?
+To check, we plug the lower bound into the favorable event and get
+
+\[
+|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}} \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}
+\] Using \(\delta = (4\sqrt{2})^-1\) as in Locatelli et al. (2016), we
+have that the separation condition holds exactly:
+
+\[
+|\hat{\mu}_i - \mu | \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta} \leq \frac{1}{2}\Delta_i.
+\]
+
+\subsubsection{Upper Bound on Error
+Probability}\label{upper-bound-on-error-probability}
+
+We have seen that on the favorable event \(\xi\), which holds with large
+probability \(\mathbb{P}(\xi)\), the separation condition holds as all
+arms have been pulled a sufficient number of times, such that their
+estimated mean is close to the true mean. All arms are classified
+correctly, and the algorithm does not suffer a loss. On the other hand,
+we make an error whenever the favorable event does not hold after all;
+that is, the deviation bound for the mean does not hold. At least one
+arm is misclassified and the arm suffers a loss. This occurs with
+probability \(1-\mathbb{P}(\xi)\). Consequently, the expected loss is
+upper bounded by
+
+\[
+\mathbb{E}[L] = 1 - \mathbb{P}(\xi) \leq 2(\log(T)+1)K \exp(-\frac{1}{64R^2}\frac{T}{H}).
+\]
+
+\newpage
+
+\subsection{\texorpdfstring{Lower Bound: Theorem and Proof
+\label{sec:LowerBoundLocatelli}}{Lower Bound: Theorem and Proof }}\label{lower-bound-theorem-and-proof}
+
+\begin{theorem}[Theorem 1, Locatelli et al., 2016] 
+\label{theorem:Locatelli2016Theorem1}
+For any sequence of gaps $(d_k)_k$, define a finite set of problems with Gaussian distributions with means corresponding to the gaps, and with variance 1.
+Lower bound the largest probability of error among these problems for the best possible algorithm as follows.
+Let $K,T \geq 0$.
+Let for any $i \leq K$, $d_i \geq 0$.
+Let $\tau \in \mathbb{R}, \epsilon > 0$.
+
+For $0 \leq i \leq K$, we write $\mathcal{B}^i$ for the problem where the distribution of arm $j \in \{1, \dots, K\}$ is $\mathcal{N}(\tau+d_i+\epsilon, 1)$ if $i \neq j$ and $\mathcal{N}(\tau-d_i-\epsilon, 1)$ otherwise.
+For all these problems, $H := H_{\tau, \epsilon} = \sum_i (d_i+2\epsilon)^{-2}$ is the same by definition.
+
+It holds that for any bandit algorithm,
+
+\begin{equation*}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) \geq \exp(-3T/H-4 \log(12(\log(T)+1)K)),
+\end{equation*}
+
+where $\mathbb{E}_{\mathcal{B}^i}$ is the expectation according to the samples of problem $\mathcal{B}^i$.
+\end{theorem}
+
+\emph{Proof of Theorem \ref{theorem:Locatelli2016Theorem1}}: In Theorem
+\ref{theorem:Locatelli2016Theorem1} of Locatelli et al. (2016), a lower
+bound for the thresholding bandit problem is shown. The basic idea is as
+follows. The problem formulation considered in the paper describes
+bandit problems for sub-Gaussian distributions. To show a lower bound,
+we show that every algorithm is expected to make a certain error even if
+we restrict ourselves to a very restricted scenario. Even then, any
+algorithm will have a certain level of risk with which it cannot
+distinguish between the actual setting and slightly changed settings
+(under which the former answer leads to regret).
+
+To be more specific, consider a case in which we set \(\tau = 0\) and
+\(\epsilon = 0\) w.l.o.g. If we then choose all arms to have normally
+distributed feedback with means \(\mu_i\), we see that for each arm
+\(i\) the distance from the threshold is given by
+\(\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i\). Thus, assuming a
+variance of 1 for every arm, we have for every arm the distribution
+\(\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)\). Furthermore,
+define for each arm \(i \in \{1, \dots, K\}\) the alternative
+distribution \(\nu_i' = \mathcal{N}(-\Delta_i,1)\). It is easy to see
+that in this case, this is equivalent to a ``flip around the
+threshold''. Arms that originally have a mean larger than the threshold
+have a mean smaller than the threshold after the flip.
+
+The idea now is that every arm \(i \in \{1,\dots,K\}\) generates a
+sample for every time point \(t\in \{1, \dots, T\}\) from its
+distribution \(\nu_i\) before the algorithm starts to choose arms. Thus,
+we have a \(T \times K\) table of realized observations from the product
+distribution given by
+\(\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K\).
+This is a product distribution where the \(K\) different means all lie
+above the threshold. We would hope that an algorithm classifies the
+means accordingly. However, we will show in what follows that any
+algorithm makes a certain error by not being able to distinguish
+\(\mathcal{B}^0\) from at least one of \(K\) alternative product
+distributions \(\mathcal{B}^i, i \in \{1, \dots, K\}\), of which each
+differs only slightly in one arm from the original distribution, and has
+the same overall complexity (as defined by
+\(H = \sum_{i=1}^K (\Delta_i)^{-2}\)). We require \(K\) different
+distributions so that an arm sampling arm \(i\) very often for some
+reason will not have a smaller lower bound by chance.
+
+For each of the \(K\) arms, we introduce an alternative model of the
+following kind. Before the start of the algorithm, we introduce a slight
+variation in the setup. The idea is similar to how one can switch arms
+in the pure exploration setup for multi-armed bandits (compare Audibert
+et al., 2010; Garivier \& Kaufmann, 2016) to ``confuse'' any algorithm
+without introducing additional complexity to the specified problem.
+However, since we do not compare arms directly with each other in the
+thresholding bandit problem (switching arms would still keep all means
+above the threshold), we instead need to flip an arm \(i\) with respect
+to the threshold in order to get the alternative model
+\(\mathcal{B}_i\). Since the threshold is \(\tau = 0\), we have for the
+flipped arm the new distribution \(\nu_i'\) as defined above. Indeed, we
+can define the new product distribution
+\(B^i = \nu_1^i \otimes \dots \otimes \nu_K^i\) where for
+\(k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}\).
+This flipping of the arm corresponds to multiplying all random variables
+\(X_{i,t}\) of arm \(i\) by \(-1\).
+
+As in Locatelli et al. (2016), we let for \(i \leq K\),
+\(\mathbb{P}_{\mathcal{B}^i}\) define the probability distribution
+describing all samples that a bandit strategy can potentially collect up
+to horizon \(T\), i.e.~according to the samples
+\((X_{k,s})_{k\leq K, s \leq T} \sim (\mathcal{B}^i)^{\otimes T}\).
+\((T_k)_{k\leq K}\) denotes the number of samples collected on arm \(k\)
+until time \(T\).
+
+\subsubsection{Reminder about the goal of the
+proof}\label{reminder-about-the-goal-of-the-proof}
+
+At this point, we have defined a finite set of problems of Gaussian
+distributions with fixed variance 1 for a given set of set of gaps
+between the means of the distributions and the threshold, \((d_k)_k\).
+We will now proof a lower bound on the worst case regret of any
+algorithm; that is, the maximum error probability that even the best
+algorithm makes on this problem.
+
+\subsubsection{Statistical Decision}\label{statistical-decision}
+
+Given our formulation of the regret, the expected regret
+\(\mathbb{E}[\mathcal{L}(T)]\) corresponds directly to the probability
+of making a wrong classification of any of the \(K\) means. In general,
+let \(g\) be a binary decision function, and define
+\(\Omega = \{g = 0\}\) and \(\Omega^C = \{g = 1\}\). Assume that the
+decision \(T\) distinguishes between two states of the world, \(H_0\)
+and \(H_1\). Then our overall error probability is given by
+\(P_{H_0}(g=1) + P_{H_1}(g = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)\).
+
+In our case, \(H_0\) may correspond to the state in which we have
+\(\mathcal{B}^0\), and \(H_1\) corresponds to the case where any arm has
+been flipped, \(\mathcal{B}^i\). Furthermore, we consider the events in
+which the algorithm, making the decision, classifies arm \(i\) as being
+above the threshold: \(\mathcal{A}_i = \{i \in \hat{S}_\tau\}\). The
+event on which all arms are being classified as above the threshold is
+consequently given by \(\mathcal{A} = \bigcap \mathcal{A}_i\). However,
+Theorem 1 does not bound the overall regret, but the maximum error
+probability on the \(K+1\) different models. We can write this now as
+
+\begin{align}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big) \\
+& = \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
+\end{align}
+
+In order to give a bound on above equation, we start by considering
+\(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\). This probability can be
+written as the expected change in the likelihood of observed data when
+moving from distribution \(P_{\mathcal{B}_0}\) to \(P_{\mathcal{B}_i}\),
+times the probability under the original state. In other words, the
+probability of event \(\mathcal{A}_i\) under state \(\mathcal{B}^i\) is
+given as the probability of \(\mathcal{A}_i\) under the (original) state
+\(\mathcal{B}^0\) multiplied by a factor. This factor describes whether
+the new distribution increases or decreases the probability of the
+event, and is given by the change in the data likelihoods due to moving
+from \(\mathcal{B}^0\) to \(\mathcal{B}^i\), expressed as the expected
+likelihood ratio under \(\mathcal{B}^0\). By definition, the latter is
+equal to the empirical Kullback-Leibler divergence of the two
+distributions.
+
+We will define the change of distribution in terms of the empirical
+log-likelihood for our case. Then, we will show how to replace the
+log-likelihood by the empirical Kullback-Leibler divergence. So let us
+first introduce the empirical Kullback-Leibler divergence.
+
+Let every \(\nu_i, \nu_i'\) be dominated by the Lebesgue measure
+\(\lambda\). Then their density functions are given by
+\(f_i = \frac{\der \nu_i}{\der \lambda}\) and
+\(f_i' = \frac{\der \nu_i'}{\der \lambda}\) respectively. For
+\(T \geq t \geq 0\), define the empirical Kullback-Leibler divergence as
+
+\begin{align*}
+\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log(\frac{\der \nu_k'}{\der \nu_k}(X_{k,s})) \\
+& = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
+& = \frac{1}{t} \log \big( \prod_{s=1}^{t} \frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
+& \stackrel{\text{iid}}{=} \frac{1}{t} \log \big( \frac{f_k'(X_{k,1}, \dots,X_{k,t})}{f_k(X_{k,1}, \dots,X_{k,t})} \big) \\
+& = \frac{1}{t} \log \big( \text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k) \big)
+\end{align*}
+
+Since we consider Gaussian distributions with variance 1, we have
+density functions
+\(f_i(x) \propto \exp \big(-\frac{1}{2} (x-\Delta_i)^2\big)\) and
+\(f_i'(x) \propto \exp \big(-\frac{1}{2} (x+\Delta_i)^2\big)\). Plugging
+this into the above definition of the empirical Kullback-Leibler
+divergence, we easily see
+
+\begin{align*}
+\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{\exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2\big)}{\exp \big(-\frac{1}{2} (X_{k,s}-\Delta_k)^2\big)} \big) \\
+& = \frac{1}{t} \sum_{s=1}^{t} \log \big( \exp(-\frac{1}{2} (X_{k,s}+\Delta_k)^2 + \frac{1}{2} (X_{k,s}-\Delta_k)^2) \big) \\
+& = - \frac{1}{t} \sum_{s=1}^{t} 2 X_{k,s} \Delta_k
+\end{align*}
+
+\subsubsection{Change of Distribution}\label{change-of-distribution}
+
+We are now ready to state the change of distribution. As alluded to
+above, we consider how the probability changes for the event
+\(\mathcal{A}_i\) when we move from \(\mathcal{B}^0\) to
+\(\mathcal{B}^i\). When flipping arm \(i\), we only changed the samples
+of this arm, that is, the first \(T_i\) observations we got from arm
+\(i\) the algorithm took. The change of distribution is then defined as:
+
+\begin{align*}
+\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \text{LR}((X_{i,1}, \dots,X_{i,T_i}), \nu_i', \nu_i) ] \\
+& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ]
+\end{align*}
+
+Obviously, \(\hat{\KL}_{i,T_i}\) depends on the realized samples
+\(X_{i,1}, \dots,X_{i,T_i}\). Consequently, we need to find a bound on
+\(\hat{\KL}_{i,T_i}\) itself to incorporate the uncertainty involved in
+this metric.
+
+\subsubsection{Concentration of the Empirical Kullback-Leibler
+Divergence}\label{concentration-of-the-empirical-kullback-leibler-divergence}
+
+For our problem, the Kullback-Leibler divergence of \(\nu_k'\) from
+\(\nu_k\) is given by \(\KL_k := KL(\nu_k', \nu_k) = 2\Delta_k^2\).
+
+It is easy to see that
+
+\begin{equation*}
+|\hat{\KL}_{k,t} - \KL_{k,t}| = |-\frac{2}{t} \Delta_k \sum_{s=1}^{t}(X_{k,s} - \Delta_k)|
+\end{equation*}
+
+itself is a normally distributed random variable with mean zero and a
+variance decreasing in \(t\). Thus, one can show as in Locatelli et al.
+(2016) that \(\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4\) for the event
+
+\begin{equation}
+\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}}\}. \label{LocatelliTheorem1EventXi}
+\end{equation}
+
+Thus, in order to bound the empirical Kullback-Leibler divergence in our
+change of measure, we can consider the intersection of \(\mathcal{A}_i\)
+and \(\xi\) as follows and plug in the bound on event \(\xi\):
+
+\begin{align*}
+\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
+& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
+& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
+\end{align*}
+
+Two things are left to do: With \(T_i\), we still have one random
+variable left which we cannot leave in our bound. Second, we are
+actually not interested in \(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)
+but in
+\(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\).
+
+\subsubsection{\texorpdfstring{Bounding \(T_i\) for
+\(\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)}{Bounding T\_i for \textbackslash{}max\_\{i \textbackslash{}in \textbackslash{}\{1,\textbackslash{}dots,K\textbackslash{}\}\}\textbackslash{}mathbb\{P\}\_\{\textbackslash{}mathcal\{B\}\^{}i\}(\textbackslash{}mathcal\{A\}\_i)}}\label{bounding-t_i-for-max_i-in-1dotskmathbbp_mathcalbimathcala_i}
+
+Part of our bound is
+\(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\),
+so let's continue with that. In general it holds that
+\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K}\sum_{i=1}^K X_i\).
+Thus we can write:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
+& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
+& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
+\end{align*}
+
+where the second line is again the intersection of \(\mathcal{A}_i\) and
+\(\xi\) as before in order to apply the change of distribution in the
+third line.
+
+What is left to show before we have our final bound is a bound on
+\(T_i\). To show that any algorithm has a certain bound on its error, it
+only makes sense that every arm has to pulled at least a certain amount
+of times. Consequently, no arm should be pulled exclusively.
+
+First, let \(a = \Delta_i \sqrt{T_i}\) and
+\(b = 4\sqrt{\log((4\log(T)+1)K)}\). Then use \(ab \leq a^2 + b^2\) to
+write \(ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)\). And so:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) ]
+\end{align*}
+
+Furthermore, we know that the sum of the individual arm pulls has to be
+equal to the overall number of pulls (equal to the budget in the fixed
+budget sense), \(\sum_i T_i = T\), and furthermore we know that
+\(T_i>0\). The latter holds since any reasonable algorithm has to check
+each arm at least once in our setup. This is because we need to check
+each arm's performance in comparison to the threshold. Thus it is easy
+to show that
+\(\exists i: T_i \leq \frac{T}{H \Delta_i^2} = \frac{T}{(\sum_{i=1}^{K} \Delta_i^{-2}) \Delta_i^2}\).
+To see this, assume the opposite:
+\(\forall i: T_i > T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2}\). This
+implies however
+\(\sum_{i=1}^K T_i > \sum_{i=1}^K T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2} = T \cdot 1 = T\)
+which is a contradiction.
+
+So we can write \((\Delta_i \sqrt{T_i})^2 \leq \frac{T}{H}\). We use
+\(\mathcal{A} = \cap_{i=1}^K \mathcal{A}_i\) to write:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big] \\
+& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}{K} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big]
+\end{align*}
+
+We write
+\(\frac{1}{K} \sum_{i=1}^K \exp(-3T_i \Delta_i^2) \geq \frac{1}{K} \sum_{i=1}^K \exp(-3 T/H) = \exp(-3 T/H)\).
+Thus:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i) \exp(-16 \log(4(\log(T)+1)K)) ] \\
+& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
+& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
+& = \mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
+\end{align*}
+
+\subsubsection{Bringing everything
+together}\label{bringing-everything-together}
+
+Consider again the risk which we need to bound from equation
+\eqref{LocatelliTheorem1ExpRegret}. We bound the maximum expected loss
+over all \(\mathcal{B}_i\). By again using the fact that in general
+\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K} \sum_{i = 1}^K X_i\),
+we plug in our previous calculations:
+
+\begin{align}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
+& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \label{LocatelliTheorem1DefinitionOfRisk}
+\end{align}
+
+From \eqref{LocatelliTheorem1EventXi} we know that for any
+\(i \in \{0, \dots, K\}\), \(\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4\).
+Following the argument in Locatelli et al. (2016), we now consider two
+cases: \(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2\) and
+\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2\). In the former
+case, we can plug in the two probabilities into
+\eqref{LocatelliTheorem1DefinitionOfRisk}. If
+\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2\) and
+\(\mathbb{P}_{\mathcal{B}^0}(\xi) \geq 3/4\), then
+\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \geq 1/4\). Thus:
+
+\begin{align*}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
+& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \\
+& \geq \frac{1}{8} \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
+\end{align*}
+
+where we drop the second summand of the second line so that the
+inequality holds.
+
+On the other hand, when
+\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2\), then we know that
+\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \leq 1/2\) for any
+\(\mathbb{P}_{\mathcal{B}^0}(\xi)\). At the same time
+\(1-\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \geq 1/2\).
+Consequently,
+\(1/4 \leq \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \leq 1/2\),
+while
+\(\frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) \geq 0\).
+And so the stronger lower bound in that case is, as noticed by Locatelli
+et al. (2016), given simply by
+
+\begin{align*}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
+& \geq 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \\
+& \geq \frac{1}{2}
+\end{align*}
+
+\newpage
+
+\subsection{\texorpdfstring{Discussion
+\label{sec:DiscussionLocatelli}}{Discussion }}\label{discussion}
 
@@
 \includegraphics{Draft_files/figure-latex/unnamed-chunk-2-1.pdf}
-
-\subsection{Lower Bound: Theorem and
-Proof}\label{lower-bound-theorem-and-proof}
-
-\begin{theorem}[Theorem 1, Locatelli et al., 2016] 
-\label{theorem:Locatelli2016Theorem1}
-For any sequence of gaps $(d_k)_k$, define a finite set of problems with Gaussian distributions with means corresponding to the gaps, and with variance 1.
-Lower bound the largest probability of error among these problems for the best possible algorithm as follows.
-Let $K,T \geq 0$.
-Let for any $i \leq K$, $d_i \geq 0$.
-Let $\tau \in \mathbb{R}, \epsilon > 0$.
-
-For $0 \leq i \leq K$, we write $\mathcal{B}^i$ for the problem where the distribution of arm $j \in \{1, \dots, K\}$ is $\mathcal{N}(\tau+d_i+\epsilon, 1)$ if $i \neq j$ and $\mathcal{N}(\tau-d_i-\epsilon, 1)$ otherwise.
-For all these problems, $H := H_{\tau, \epsilon} = \sum_i (d_i+2\epsilon)^{-2}$ is the same by definition.
-
-It holds that for any bandit algorithm,
-
-\begin{equation*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) \geq \exp(-3T/H-4 \log(12(\log(T)+1)K)),
-\end{equation*}
-
-where $\mathbb{E}_{\mathcal{B}^i}$ is the expectation according to the samples of problem $\mathcal{B}^i$.
-\end{theorem}
-
-\emph{Proof of Theorem \ref{theorem:Locatelli2016Theorem1}}: In Theorem
-\ref{theorem:Locatelli2016Theorem1} of Locatelli et al. (2016), a lower
-bound for the thresholding bandit problem is shown. The basic idea is as
-follows. The problem formulation considered in the paper describes
-bandit problems for sub-Gaussian distributions. To show a lower bound,
-we show that every algorithm is expected to make a certain error even if
-we restrict ourselves to a very restricted scenario. Even then, any
-algorithm will have a certain level of risk with which it cannot
-distinguish between the actual setting and slightly changed settings
-(under which the former answer leads to regret).
-
-To be more specific, consider a case in which we set \(\tau = 0\) and
-\(\epsilon = 0\) w.l.o.g. If we then choose all arms to have normally
-distributed feedback with means \(\mu_i\), we see that for each arm
-\(i\) the distance from the threshold is given by
-\(\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i\). Thus, assuming a
-variance of 1 for every arm, we have for every arm the distribution
-\(\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)\). Furthermore,
-define for each arm \(i \in \{1, \dots, K\}\) the alternative
-distribution \(\nu_i' = \mathcal{N}(-\Delta_i,1)\). It is easy to see
-that in this case, this is equivalent to a ``flip around the
-threshold''. Arms that originally have a mean larger than the threshold
-have a mean smaller than the threshold after the flip.
-
-The idea now is that every arm \(i \in \{1,\dots,K\}\) generates a
-sample for every time point \(t\in \{1, \dots, T\}\) from its
-distribution \(\nu_i\) before the algorithm starts to choose arms. Thus,
-we have a \(T \times K\) table of realized observations from the product
-distribution given by
-\(\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K\).
-This is a product distribution where the \(K\) different means all lie
-above the threshold. We would hope that an algorithm classifies the
-means accordingly. However, we will show in what follows that any
-algorithm makes a certain error by not being able to distinguish
-\(\mathcal{B}^0\) from at least one of \(K\) alternative product
-distributions \(\mathcal{B}^i, i \in \{1, \dots, K\}\), of which each
-differs only slightly in one arm from the original distribution, and has
-the same overall complexity (as defined by
-\(H = \sum_{i=1}^K (\Delta_i)^{-2}\)). We require \(K\) different
-distributions so that an arm sampling arm \(i\) very often for some
-reason will not have a smaller lower bound by chance.
-
-For each of the \(K\) arms, we introduce an alternative model of the
-following kind. Before the start of the algorithm, we introduce a slight
-variation in the setup. The idea is similar to how one can switch arms
-in the pure exploration setup for multi-armed bandits (compare Audibert
-et al., 2010; Garivier \& Kaufmann, 2016) to ``confuse'' any algorithm
-without introducing additional complexity to the specified problem.
-However, since we do not compare arms directly with each other in the
-thresholding bandit problem (switching arms would still keep all means
-above the threshold), we instead need to flip an arm \(i\) with respect
-to the threshold in order to get the alternative model
-\(\mathcal{B}_i\). Since the threshold is \(\tau = 0\), we have for the
-flipped arm the new distribution \(\nu_i'\) as defined above. Indeed, we
-can define the new product distribution
-\(B^i = \nu_1^i \otimes \dots \otimes \nu_K^i\) where for
-\(k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}\).
-This flipping of the arm corresponds to multiplying all random variables
-\(X_{i,t}\) of arm \(i\) by \(-1\).
-
-As in Locatelli et al. (2016), we let for \(i \leq K\),
-\(\mathbb{P}_{\mathcal{B}^i}\) define the probability distribution
-describing all samples that a bandit strategy can potentially collect up
-to horizon \(T\), i.e.~according to the samples
-\((X_{k,s})_{k\leq K, s \leq T} \sim (\mathcal{B}^i)^{\otimes T}\).
-\((T_k)_{k\leq K}\) denotes the number of samples collected on arm \(k\)
-until time \(T\).
-
-\subsubsection{Reminder about the goal of the
-proof}\label{reminder-about-the-goal-of-the-proof}
-
-At this point, we have defined a finite set of problems of Gaussian
-distributions with fixed variance 1 for a given set of set of gaps
-between the means of the distributions and the threshold, \((d_k)_k\).
-We will now proof a lower bound on the worst case regret of any
-algorithm; that is, the maximum error probability that even the best
-algorithm makes on this problem.
-
-\subsubsection{Statistical Decision}\label{statistical-decision}
-
-Given our formulation of the regret, the expected regret
-\(\mathbb{E}[\mathcal{L}(T)]\) corresponds directly to the probability
-of making a wrong classification of any of the \(K\) means. In general,
-let \(g\) be a binary decision function, and define
-\(\Omega = \{g = 0\}\) and \(\Omega^C = \{g = 1\}\). Assume that the
-decision \(T\) distinguishes between two states of the world, \(H_0\)
-and \(H_1\). Then our overall error probability is given by
-\(P_{H_0}(g=1) + P_{H_1}(g = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)\).
-
-In our case, \(H_0\) may correspond to the state in which we have
-\(\mathcal{B}^0\), and \(H_1\) corresponds to the case where any arm has
-been flipped, \(\mathcal{B}^i\). Furthermore, we consider the events in
-which the algorithm, making the decision, classifies arm \(i\) as being
-above the threshold: \(\mathcal{A}_i = \{i \in \hat{S}_\tau\}\). The
-event on which all arms are being classified as above the threshold is
-consequently given by \(\mathcal{A} = \bigcap \mathcal{A}_i\). However,
-Theorem 1 does not bound the overall regret, but the maximum error
-probability on the \(K+1\) different models. We can write this now as
-
-\begin{align}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big) \\
-& = \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
-\end{align}
-
-In order to give a bound on above equation, we start by considering
-\(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\). This probability can be
-written as the expected change in the likelihood of observed data when
-moving from distribution \(P_{\mathcal{B}_0}\) to \(P_{\mathcal{B}_i}\),
-times the probability under the original state. In other words, the
-probability of event \(\mathcal{A}_i\) under state \(\mathcal{B}^i\) is
-given as the probability of \(\mathcal{A}_i\) under the (original) state
-\(\mathcal{B}^0\) multiplied by a factor. This factor describes whether
-the new distribution increases or decreases the probability of the
-event, and is given by the change in the data likelihoods due to moving
-from \(\mathcal{B}^0\) to \(\mathcal{B}^i\), expressed as the expected
-likelihood ratio under \(\mathcal{B}^0\). By definition, the latter is
-equal to the empirical Kullback-Leibler divergence of the two
-distributions.
-
-We will define the change of distribution in terms of the empirical
-log-likelihood for our case. Then, we will show how to replace the
-log-likelihood by the empirical Kullback-Leibler divergence. So let us
-first introduce the empirical Kullback-Leibler divergence.
-
-Let every \(\nu_i, \nu_i'\) be dominated by the Lebesgue measure
-\(\lambda\). Then their density functions are given by
-\(f_i = \frac{\der \nu_i}{\der \lambda}\) and
-\(f_i' = \frac{\der \nu_i'}{\der \lambda}\) respectively. For
-\(T \geq t \geq 0\), define the empirical Kullback-Leibler divergence as
-
-\begin{align*}
-\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log(\frac{\der \nu_k'}{\der \nu_k}(X_{k,s})) \\
-& = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
-& = \frac{1}{t} \log \big( \prod_{s=1}^{t} \frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
-& \stackrel{\text{iid}}{=} \frac{1}{t} \log \big( \frac{f_k'(X_{k,1}, \dots,X_{k,t})}{f_k(X_{k,1}, \dots,X_{k,t})} \big) \\
-& = \frac{1}{t} \log \big( \text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k) \big)
-\end{align*}
-
-Since we consider Gaussian distributions with variance 1, we have
-density functions
-\(f_i(x) \propto \exp \big(-\frac{1}{2} (x-\Delta_i)^2\big)\) and
-\(f_i'(x) \propto \exp \big(-\frac{1}{2} (x+\Delta_i)^2\big)\). Plugging
-this into the above definition of the empirical Kullback-Leibler
-divergence, we easily see
-
-\begin{align*}
-\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{\exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2\big)}{\exp \big(-\frac{1}{2} (X_{k,s}-\Delta_k)^2\big)} \big) \\
-& = \frac{1}{t} \sum_{s=1}^{t} \log \big( \exp(-\frac{1}{2} (X_{k,s}+\Delta_k)^2 + \frac{1}{2} (X_{k,s}-\Delta_k)^2) \big) \\
-& = - \frac{1}{t} \sum_{s=1}^{t} 2 X_{k,s} \Delta_k
-\end{align*}
-
-\subsubsection{Change of Distribution}\label{change-of-distribution}
-
-We are now ready to state the change of distribution. As alluded to
-above, we consider how the probability changes for the event
-\(\mathcal{A}_i\) when we move from \(\mathcal{B}^0\) to
-\(\mathcal{B}^i\). When flipping arm \(i\), we only changed the samples
-of this arm, that is, the first \(T_i\) observations we got from arm
-\(i\) the algorithm took. The change of distribution is then defined as:
-
-\begin{align*}
-\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \text{LR}((X_{i,1}, \dots,X_{i,T_i}), \nu_i', \nu_i) ] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ]
-\end{align*}
-
-Obviously, \(\hat{\KL}_{i,T_i}\) depends on the realized samples
-\(X_{i,1}, \dots,X_{i,T_i}\). Consequently, we need to find a bound on
-\(\hat{\KL}_{i,T_i}\) itself to incorporate the uncertainty involved in
-this metric.
-
-\subsubsection{Concentration of the Empirical Kullback-Leibler
-Divergence}\label{concentration-of-the-empirical-kullback-leibler-divergence}
-
-For our problem, the Kullback-Leibler divergence of \(\nu_k'\) from
-\(\nu_k\) is given by \(\KL_k := KL(\nu_k', \nu_k) = 2\Delta_k^2\).
-
-It is easy to see that
-
-\begin{equation*}
-|\hat{\KL}_{k,t} - \KL_{k,t}| = |-\frac{2}{t} \Delta_k \sum_{s=1}^{t}(X_{k,s} - \Delta_k)|
-\end{equation*}
-
-itself is a normally distributed random variable with mean zero and a
-variance decreasing in \(t\). Thus, one can show as in Locatelli et al.
-(2016) that \(\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4\) for the event
-
-\begin{equation}
-\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}}\}. \label{LocatelliTheorem1EventXi}
-\end{equation}
-
-Thus, in order to bound the empirical Kullback-Leibler divergence in our
-change of measure, we can consider the intersection of \(\mathcal{A}_i\)
-and \(\xi\) as follows and plug in the bound on event \(\xi\):
-
-\begin{align*}
-\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
-\end{align*}
-
-Two things are left to do: With \(T_i\), we still have one random
-variable left which we cannot leave in our bound. Second, we are
-actually not interested in \(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)
-but in
-\(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\).
-
-\subsubsection{\texorpdfstring{Bounding \(T_i\) for
-\(\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)}{Bounding T\_i for \textbackslash{}max\_\{i \textbackslash{}in \textbackslash{}\{1,\textbackslash{}dots,K\textbackslash{}\}\}\textbackslash{}mathbb\{P\}\_\{\textbackslash{}mathcal\{B\}\^{}i\}(\textbackslash{}mathcal\{A\}\_i)}}\label{bounding-t_i-for-max_i-in-1dotskmathbbp_mathcalbimathcala_i}
-
-Part of our bound is
-\(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\),
-so let's continue with that. In general it holds that
-\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K}\sum_{i=1}^K X_i\).
-Thus we can write:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
-& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
-& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
-\end{align*}
-
-where the second line is again the intersection of \(\mathcal{A}_i\) and
-\(\xi\) as before in order to apply the change of distribution in the
-third line.
-
-What is left to show before we have our final bound is a bound on
-\(T_i\). To show that any algorithm has a certain bound on its error, it
-only makes sense that every arm has to pulled at least a certain amount
-of times. Consequently, no arm should be pulled exclusively.
-
-First, let \(a = \Delta_i \sqrt{T_i}\) and
-\(b = 4\sqrt{\log((4\log(T)+1)K)}\). Then use \(ab \leq a^2 + b^2\) to
-write \(ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)\). And so:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) ]
-\end{align*}
-
-Furthermore, we know that the sum of the individual arm pulls has to be
-equal to the overall number of pulls (equal to the budget in the fixed
-budget sense), \(\sum_i T_i = T\), and furthermore we know that
-\(T_i>0\). The latter holds since any reasonable algorithm has to check
-each arm at least once in our setup. This is because we need to check
-each arm's performance in comparison to the threshold. Thus it is easy
-to show that
-\(\exists i: T_i \leq \frac{T}{H \Delta_i^2} = \frac{T}{(\sum_{i=1}^{K} \Delta_i^{-2}) \Delta_i^2}\).
-To see this, assume the opposite:
-\(\forall i: T_i > T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2}\). This
-implies however
-\(\sum_{i=1}^K T_i > \sum_{i=1}^K T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2} = T \cdot 1 = T\)
-which is a contradiction.
-
-So we can write \((\Delta_i \sqrt{T_i})^2 \leq \frac{T}{H}\). We use
-\(\mathcal{A} = \cap_{i=1}^K \mathcal{A}_i\) to write:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}{K} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big]
-\end{align*}
-
-We write
-\(\frac{1}{K} \sum_{i=1}^K \exp(-3T_i \Delta_i^2) \geq \frac{1}{K} \sum_{i=1}^K \exp(-3 T/H) = \exp(-3 T/H)\).
-Thus:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i) \exp(-16 \log(4(\log(T)+1)K)) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
-& = \mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
-\end{align*}
-
-\subsubsection{Bringing everything
-together}\label{bringing-everything-together}
-
-Consider again the risk which we need to bound from equation
-\eqref{LocatelliTheorem1ExpRegret}. We bound the maximum expected loss
-over all \(\mathcal{B}_i\). By again using the fact that in general
-\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K} \sum_{i = 1}^K X_i\),
-we plug in our previous calculations:
-
-\begin{align}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \label{LocatelliTheorem1DefinitionOfRisk}
-\end{align}
-
-From \eqref{LocatelliTheorem1EventXi} we know that for any
-\(i \in \{0, \dots, K\}\), \(\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4\).
-Following the argument in Locatelli et al. (2016), we now consider two
-cases: \(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2\) and
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2\). In the former
-case, we can plug in the two probabilities into
-\eqref{LocatelliTheorem1DefinitionOfRisk}. If
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2\) and
-\(\mathbb{P}_{\mathcal{B}^0}(\xi) \geq 3/4\), then
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \geq 1/4\). Thus:
-
-\begin{align*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \\
-& \geq \frac{1}{8} \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
-\end{align*}
-
-where we drop the second summand of the second line so that the
-inequality holds.
-
-On the other hand, when
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2\), then we know that
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \leq 1/2\) for any
-\(\mathbb{P}_{\mathcal{B}^0}(\xi)\). At the same time
-\(1-\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \geq 1/2\).
-Consequently,
-\(1/4 \leq \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \leq 1/2\),
-while
-\(\frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) \geq 0\).
-And so the stronger lower bound in that case is, as noticed by Locatelli
-et al. (2016), given simply by
-
-\begin{align*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \\
-& \geq \frac{1}{2}
-\end{align*}
-
-\subsection{Upper Bound on Expected Loss of
-APT}\label{upper-bound-on-expected-loss-of-apt}
-
-\begin{theorem}[Locatelli et al., 2016] \label{theorem:LocatelliTheorem4}
-Let $K \geq 0$, $T \geq 2K$, and consider a problem $\mathbb{B}$. Assume that
-all arms $\nu_k$ of the problem are R-sub-Gaussian with means $\mu_k$. Let $\tau
-\in \mathbb{R}, \epsilon \geq 0$.
-
-Algorithm APT's expected loss is upper bounded on this problem as 
-\begin{equation*} \mathbb{E}(\mathcal{L}(T)) \leq \exp
-(-\frac{1}{64R^2}\frac{T}{H} + 2 \log (T) + 1)K)) \end{equation*}
-
-where we remind that $H = \sum_i (|\mu_i - \tau | + \epsilon)^{-2}$ and where
-$\mathbb{E}$ is the expectation according to the samples of the problem.
-\end{theorem}
-
-\emph{Proof of Theorem \ref{theorem:LocatelliTheorem4}:}
-
-In order to upper bound the expected loss of the APT algorithm, we want
-to find an event on which the algorithm would correctly seperate arms
-from the threshold, that is, on the event a seperation condition holds.
-We then want to show that with large probability, this \emph{favorable}
-event does indeed hold. Consequently, the expected loss (probability of
-an error) will correspond to the probability that the favorable event
-does not hold after all as this leads the seperation condition to fail,
-and the algorithm to classify at least one arm incorrectly.
-
-While this is the general idea, we have to jump between seperation
-condition, favorable event, and large probability.
-
-\subsubsection{Separation Condition}\label{separation-condition}
-
-As noted in Zhong et al. (2017), a simple requirement to correctly
-classify arms at the final round is the following. For every arm
-\(i \in \{1, ..., K\}\) at round \(T\),
-
-\[
-\hat{\mu}_{i,T_i(n)} \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
-\] or
-
-\[
-\hat{\mu}_{i,T_i(n)} \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
-\] Or simply in terms of the gap between the arm and the threshold as
-used as index by the algorithm,
-
-\[
-| \hat{\mu}_{i, T_i(n)} - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
-\]
-
-Intuitively, the conditions make sense as they ensure that the current
-mean estimate is closer to the true mean than to the threshold.
-Consequently, there is no possible arrangement left in which the
-condition would hold, but the arm be classified incorrectly. Assuming
-\(\mu_i < \tau\) and \(\epsilon = 0\), an incorrect classification would
-require \(\mu_i < \tau \leq \hat{\mu_i}\). But then
-\(| \hat{\mu}_{i, T_i(n)} - \mu_i | \geq |\mu_i - \tau|\), violating the
-separation condition.
-
-Thus, we need to show that in the very final round, this condition holds
-for every arm \(i \in \{1,...,K\}\) with large probability. Or more
-precisely, we need to derive a bound on the probability with which this
-does not hold.
-
-\subsubsection{The Favorable Event}\label{the-favorable-event}
-
-The separation condition gives a good idea of what event we need to hold
-in order to make a correct classification. The smaller the deviation of
-the empirical mean from the population mean, the more difficult it is
-for the classification to be wrong. Moreover, if the mean and empirical
-mean are identical, then the classification is correct independent of
-the threshold. And furthermore, the closer the mean and the threshold
-are, the better the estimate must be for a correct classification.
-
-Having to bound the absolute deviation of the sample mean from the
-population mean is a very thankful operation. Define the favorable event
-\(\xi\) as
-
-\[
-\xi = \Big\{\forall i \in \mathbb{A}, \forall s \in \{1,...,T\} : |\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}} \Big\}.
-\]
-
-We want the probability that this favorable event occurs to be large,
-that is, the probability that the deviation is small, such that the
-separation condition holds with large probability. Indeed, we bound the
-deviation for \emph{all} arms \(i \leq K\) and for \emph{every} round
-\(s \leq T\). Using some Chernoff Hoeffding bounds, we are able to write
-
-\[
-\mathbb{P}(\xi) \geq 1 - 2(\log(T) +1)K \exp(-\frac{T\delta^2}{2R^2H})
-\]
-
-\subsubsection{\texorpdfstring{Need to Bound
-\(T_i\)}{Need to Bound T\_i}}\label{need-to-bound-t_i}
-
-We now have that with large probability, the favorable event holds. On
-the favorable event, we have for every arm \(i\):
-
-\[
-| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}
-\]
-
-The deviation of arm \(i\) at time \(t\) depends on how large \(H\),
-\(T\), and \(T_i(t)\) are. While \(t\), \(H\), \(T\) are deterministic,
-the number of times arm \(i\) has been pulled at round \(t\),
-\(T_i(t)\), is a random variable. In order to know how large the
-probability of the favorable event is (and thus the error probability),
-we need to know what realistic values for \(T_i(t)\) will be. Put
-differently: To ensure a deviation smaller than
-\(\sqrt{\frac{T\delta^2}{HT_i(t)}}\) for arm \(i\), we need to ensure
-that arm \(i\) has been pulled at least \(T_i(t)\) times. As usual in
-multi-armed bandits, and different from uniform sampling, the number of
-pulls is a random variable that also depends on how often other arms are
-pulled. In general, we do not want each arm to be pulled an equal
-amount, but each arm should be pulled some times, and not too many
-times. This especially holds for our exploration setting.
-
-Thus, in order to check that the deviation of arm \(i\) really is small
-enough for the separation condition to hold on the favorable event, we
-need to bound the number of pulls of every arm from below.
-
-\subsubsection{\texorpdfstring{Characteristics of a Frequently Pulled
-Arm (Lower Bound on
-\(T_k(T)\))}{Characteristics of a Frequently Pulled Arm (Lower Bound on T\_k(T))}}\label{characteristics-of-a-frequently-pulled-arm-lower-bound-on-t_kt}
-
-Given that we do not follow a uniform sampling strategy, we know that at
-time \(T\), some arms will have been pulled more frequently than others.
-In particular, some arms will have been pulled more than \(T/K\) times.
-How often an arm is pulled can be related to the individual arm's
-contribution to the overall complexity measure. Let \(h_i\) be a measure
-of arm \(i\)'s individual problem complexity and write for the overall
-problem complexity
-
-\[
-H = \sum_{i = 1}^{K} h_i.
-\]
-
-Then arm \(i\) contributes a share of \(h_i/H\) to the overall problem
-complexity. We can now show that there exists an arm that has been
-pulled at least as often as the share of his complexity contribution.
-
-Given the initialization of the APT algorithm, every arm is pulled once
-initially. Consequently, there is a budget of \(T-K\) rounds left after
-the initialization. As shown in Locatelli et al. (2016), there exists an
-arm \(k\) that has been pulled after the initialization (\(\geq 2\)
-pulls) and for which at the final round \(T\) holds:
-\(T_k(T) - 1 \geq \frac{(T-K)h_k}{H}\). This can be shown by a quick
-contradiction proof. Assume the opposite, that is
-
-\[
-\forall i \in \{1,...,K\}: T_i(T) - 1 < \frac{(T-K)h_i}{H}
-\]
-
-Consequently, at time \(T\), we would have pulled across all arms
-\(\sum_{i=1}^KT_i(T)-1\) times. If the previous assumption holds, we
-would not have used the entire budget:
-
-\[
-\sum_{i=1}^K T_i(T)-1 < \sum_{i=1}^K \frac{(T-K)h_i}{H} = (T-K)\sum_{i=1}^K \frac{h_i}{H} = T-K
-\]
-
-This is a contradiction, since as an requirement to the algorithm we
-have that \(\sum_{i=1}^K T_i(T)-1 = (T-K)\), that is, we use the entire
-budget of samples.
-
-Another such requirement has been that \(T>2K\). Plugging this in gives
-\[
-T_k(T) - 1 \geq \frac{(T-K)h_k}{H} \leq \frac{(T-1/2T)h_k}{H} = \frac{Th_i}{2H}
-\]
-
-Now we know how often the arm has been pulled at the very end. That does
-not mean that \(k\) has been pulled at time \(T\). Thus we consider the
-time \(t \leq T\) at which arm \(k\) is pulled for the last time. We get
-(!!!!!SHOOOOWWW THIIIISSSS!!!!!!!!!)
-
-\[
-T_k(t) \geq T_k(T) - 1 \geq \frac{Th_i}{2H}.
-\]
-
-This gives us a lower bound on how often arms are pulled that are pulled
-frequently relative to their contribution to the problem complexity. Now
-we need a lower bound on \(T_i(T)\) for every other arm \(i\).
-
-\subsubsection{\texorpdfstring{Lower Bound on
-\(T_i(T)\)}{Lower Bound on T\_i(T)}}\label{lower-bound-on-t_it}
-
-Consider again as before the round \(t\) in which arm \(k\) is pulled
-for the very last time. Since the APT algorithm minimizes at every round
-\(s\) the index \(B_j(s)\), and pulls the arm with the smallest index,
-we know that arm \(k\) must have had the smallest index at round \(t\).
-We have:
-
-\[
-B_k(t) \leq B_i(t) \Leftrightarrow \sqrt{T_k(t)}\hat{\Delta}_k(t) \leq \sqrt{T_i(t)} \hat{\Delta}_i(t)
-\]
-
-One can already expect that this can be used to derive a lower bound on
-\(T_i(t)\) on the RHS, and this is exactly what we do.
-
-On the LHS, we will plug in the lower bound for \(T_k(t)\) derived
-before. Additionally bounding \(\Delta_k(t)\) from below, and
-\(\hat{\Delta}_i(t)\) from above using the favorable event will give the
-desired lower bound.
-
-Thus assume we are on the favorable event \(\xi\) with large
-probability. we consequently have
-
-\[
-| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}.
-\]
-
-As shown in Locatelli et al. (2016), one can use the reverse triangle
-inequality to get:
-
-\[
-|\hat{\mu}_i(t) - \mu_i| = |(\hat{\mu}_i(t) - \tau) - (\mu_i - \tau)| \geq || \hat{\mu}_i(t) - \tau | - |\mu_i - \tau|| \geq |(|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i - \tau| + \epsilon)| \geq |\hat{\Delta}_i(t) - \Delta_i|
-\]
-
-If we combine this with the favorable event, we get
-
-\[
-\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}} \leq \hat{\Delta}_k(t) \leq \Delta_k + \sqrt{\frac{T\delta^2}{HT_k(t)}}
-\]
-
-and similar for \(\hat{\Delta}_i\).
-
-We can now lower bound the LHS of the indices as
-
-\[
-\Big(\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}}\Big) \sqrt{T_k(t)} \leq B_k(t)
-\]
-
-\[
-\Big(\Delta_k - \sqrt{\frac{2}{h_k}}\delta \Big) \sqrt{\frac{Th_k}{2H}} \leq B_k(t)
-\]
-
-At this point, it is useful to have a well chosen complexity measure. If
-we set \(h_i = \frac{1}{\Delta_i^2}\) as in Locatelli et al. (2016), we
-get
-
-\[
-\Big(\Delta_k - \sqrt{2}\delta \Delta \Big) \sqrt{\frac{T}{2H\Delta_k^2}} \leq B_k(t)
-\]
-
-which can be now be reduced to a form that is not specific to \(k\):
-
-\[
-\Big( \frac{1}{\sqrt{2}} - \delta \Big) \sqrt{\frac{T}{H}} \leq B_k(t).
-\]
-
-Now we need to get rid of \(\hat{\Delta}_i\) in order to bound
-\(T_i(t)\). Thus, we bound the RHS again using the favorable event much
-as we did for the LHS:
-
-\[
-B_i(t) = \hat{\Delta}_i \sqrt{T_i(t)} \leq \Big(\Delta_i + \sqrt{\frac{T\delta^2}{HT_i(t)}}\Big) \sqrt{T_i(t)} \leq \Delta_i \sqrt{T_i(t)} + \delta \sqrt{\frac{T}{H}}
-\]
-
-As in Locatelli et al. (2016) we use the fact that by definition
-\(\Delta\) and \(\hat{\Delta}\) are positive in order to square both
-sides and write
-
-\[
-(1 - 2\sqrt{2}\delta)^2 \frac{T}{2H\Delta^2_i} \leq T_i(t) \leq T_i(T)
-\]
-
-We thus have derived a lower bound on the amount of pulls for any arm.
-That means that we can show that no arm is pulled an insufficient amount
-of times with large probability, and that consequently the favorable
-event hold and the estimated mean is sufficienctly separated from the
-threshold.
-
-\subsubsection{Check Separation
-Condition}\label{check-separation-condition}
-
-As the last step, we need to check whether the lower bound on the pulls
-of any arm suffices to ensure that the separation condition holds on the
-favorable event. That means, given
-\(T_i(T) \geq (1-2\sqrt{2}\delta)^2 \frac{T}{2H\Delta_i^2}\), do we have
-\(|\hat{\mu}_i(T) - \mu | \leq \frac{\Delta}{2}\) on the favorable event
-\(\xi = \Big\{|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}}\Big\}\)?
-
-To check, we plug the lower bound into the favorable event and get
-
-\[
-|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}} \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}
-\] Using \(\delta = (4\sqrt{2})^-1\) as in Locatelli et al. (2016), we
-get
-
-\[
-|\hat{\mu}_i - \mu | \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta} \leq \frac{1}{2}\Delta_i.
-\]
-
-Thus the separation condition still holds for this value of \(\delta\).
-
-\subsubsection{Upper Bound on Error
-Probability}\label{upper-bound-on-error-probability}
-
-We have seen that on the favorable event \(\xi\), which holds with large
-probability \(\mathbb{P}(\xi)\), the separation condition holds as all
-arms have been pulled a sufficient number of times, such that their
-estimated mean is close to the true mean. All arms are classified
-correctly, and the algorithm does not suffer a loss. On the other hand,
-we make an error whenever the favorable event does not hold after all;
-that is, the deviation bound for the mean does not hold. At least one
-arm is misclassified and the arm suffers a loss. This occurs with
-probability \(1-\mathbb{P}(\xi)\). Consequently, the expected loss is
-upper bounded by
-
-\[
-\mathbb{E}[L] = 1 - \mathbb{P}(\xi) \leq 2(\log(T)+1)K \exp(-\frac{1}{64R^2}\frac{T}{H}).
-\]
 
@@
 
-\subsection{Introduction}\label{introduction}
+\subsection{Introduction}\label{introduction-1}
 

### 2017-08-26 real_experiments/real_exp_1week_2_shuffled.R

@@ -53,6 +53,7 @@ save(data_amo4_shuffled_mean_secondhalf, file = paste0(current_path, "data_amo4_
 rm(pv_list, pv_own_means, pv_next_means, pv_products_wide)
 gc()
 
+load(paste0(current_path, "data_amo4_mean_firsthalf.Rda"))
 load(paste0(current_path, "data_amo4_shuffled_mean_firsthalf.Rda"))
 load(paste0(current_path, "data_amo4_shuffled_mean_secondhalf.Rda"))
 load(paste0(current_path, "data_amo4_shuffled_own_means.Rda"))
@@ -63,9 +64,9 @@ epsilon_amo4_shuffled <- 0
 ########################################################################
 # Standard Likelihood Ratio
 system.time(amo4_shuffled_LR <- para_bandit_sim_LR(data = data_amo4_shuffled, 
-                                          rounds = 10080, 
-                                          tau = tau_amo4_shuffled, 
-                                          epsilon = epsilon_amo4_shuffled))
+                                                   rounds = 10080, 
+                                                   tau = tau_amo4_shuffled, 
+                                                   epsilon = epsilon_amo4_shuffled))
 
 save(amo4_shuffled_LR, file = paste0(current_path, "amo4_shuffled_LR.Rda"))
 #load(file = paste0(current_path, "amo4_shuffled_LR.Rda"))
@@ -258,9 +259,9 @@ gc()
 
 round(data_amo4_shuffled_mean_firsthalf - tau_amo4_shuffled,2)
 
-load(paste0(current_path, "amo4_shuffled_comp_UNIFORM.Rda"))
+load(paste0(current_path, "amo4_comp_UNIFORM.Rda"))
 load(paste0(current_path, "amo4_shuffled_comp_APT.Rda"))
-load(paste0(current_path, "amo4_shuffled_comp_LR.Rda"))
+load(paste0(current_path, "amo4_comp_LR.Rda"))
 load(paste0(current_path, "amo4_shuffled_comp_AugUCB.Rda"))
 load(paste0(current_path, "amo4_shuffled_comp_EVT.Rda"))
 load(paste0(current_path, "amo4_shuffled_comp_BUCB.Rda"))
@@ -270,9 +271,10 @@ lines(log(amo4_shuffled_comp_UNIFORM), col = "black")
 lines(log(amo4_shuffled_comp_APT), col = "blue")
[…]

### 2017-08-27 Thesis/Draft.Rmd
add hoeffding bound

@@
 
-- Show Chernoff/Hoeffding bound detailed
-- Show union bound to get deviation for all arms $i \leq K$ and every round $s \leq T$
+We know that $X_i$ are $R$-sub-Gaussian by assumption. That is, we have
+
+$$
+\mathbb{E}[\exp (tX_{i,s}-t\mathbb{E}[X_{i,s}])] = \mathbb{E}[\exp (t(X_{i,s}-\mathbb{E}[X_{i,s}]))] \leq \exp (R^2t^2/2)
+$$
+
+where the RHS is the moment-generating function of the random variable $X_{i,s}-\mathbb{E}[X_{i,s}]$.
+While Höffding's Lemma and Höffding's Inequality are commonly applied to bounded random variables $Z$ with $\mathbb{P}(a\leq Z \leq b) = 1$ and $\mathbb{E}[Z] = 0$, we see that $Z$ are $R$-sub-Gaussian with $R^2 = \frac{(a-b)^2}{4}$.
+Using this last equality, we can easily apply Höffding's Inequality to our case.
+
+\begin{lemma}[Höffding's Inequality (Kloft Lecture Notes)] \label{lemma:HoeffdingsInequality}
+Let $X_1, ..., X_s$ be independent, identically distributed random variables with mean $\mathbb{E}[X_t] = \mu$ and $\mathbb{P}(a_t \leq X_t - \mathbb{E}[X] \leq b_t) = 1$.
+Denote their empirical mean by $\bar{X}_s=\frac{1}{s}\sum_{t=1}^{s}X_t$.
+Then, for any $\gamma > 0$, we have the following concentration inequality:
+
+\begin{equation*}
+\mathbb{P}(|\bar{X}_s - \mu| \geq \gamma) \leq 2\exp (-2s^2\gamma^2/\sum_{t=1}^s(b_t - a_t)^2).
+\end{equation*}
+\end{lemma}
+
+If we replace $\sum_{t=1}^s(b_t - a_t)^2$ by $4sR^2$, we have the concentration inequality for our $R$-sub-Gaussian random variables:
+
+$$
+\mathbb{P}(|\bar{X}_s - \mu| \geq \gamma) \leq 2\exp (-\frac{s\gamma^2}{2R^2}).
+$$
+
+Writing $\gamma = \sqrt{\frac{T\delta^2}{Hs}}$, we get for the favorable event $\xi_i = \{|\bar{X}_s - \mu| \leq \sqrt{\frac{T\delta^2}{Hs}}\}$ of an individual arm $i$, for each $i \in \mathbb{A}$ and each $s \in \{1, ..., T\}$:
+
+$$
+\mathbb{P}(\xi_i) = \mathbb{P}\Big(|\bar{X}_{i,s} - \mu_i| \leq \sqrt{\frac{T\delta^2}{Hs}}\Big) \geq 1 - 2\exp (-\frac{T\delta^2}{2R^2H}),
+$$
+where $T$ is again the total budget of samples, and $H$ the complexity. Now let
+
+$$
+\tilde{\xi} = \Big\{\forall i \in \mathbb{A}: |\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}} \Big\}.
+$$
+
+To derive the probability of event $\tilde{\xi}$, we apply a union bound on $\mathbb{P}(\cup_{i=1}^K \xi_i^C)$:
+
+\begin{align*}
+\mathbb{P}(\tilde{\xi}) & = & 1-\mathbb{P}(\xi^C) \\
+& = & 1-\mathbb{P}(\cup_{i=1}^K \xi_i^C) \\
+& \geq & 1 - \sum_{i=1}^K \mathbb{P}(\xi_i^C) \\
+& \geq & 1 - 2K\exp (-\frac{T\delta^2}{2R^2H})
+\end{align*}
+
+We could use the same union bound a second time to bound over all $s \in \{1, ..., T\}$ and derive for the favorable event $\xi$:
+
+$$
+\mathbb{P}(\xi) \geq 1 - 2TK \exp(-\frac{T\delta^2}{2R^2H})
+$$
+
+Locatelli et al. (2016) use instead of Höffding's inequality a Sub-Gaussian martingale inequality including a peeling argument in order to derive a better bound of
 
@@
 $$
+
+This bound is non-trivial for much smaller values of $T$, and we will use it in the following.
 
@@
 \newpage
+
+We now present the lower bound given in Locatelli et al.
+(2016) for the thresholding bandit problem.
+In order to derive the bound, a problem is specified to show that the error of the lower bound is attained even in this specific problem.
+In particular, for a set of problems with Gaussian distributions of variance $1$, the largest probability of error on these problems that the best algorithm exhibits is still at least as large as the lower bound.
 
@@
 This makes the algorithm immediately applicable in practice while it still enjoys its upper bound on the expected regret.
-This is in particular worth highlighting when comparing APT to algorithms used in the pure exploration bandit setting.
-There, many algorithms require knowledge about the corresponding complexity upfront.
-The problem however being, that to know the complexity, the experimenter has to know all means up to a permutation of the arms (for example, see Audibert et al., 2010).
-This, of course, is not given in practice and thus alternative algorithms try to estimate the complexity online which is not a desirable solution either as especially in the beginning plug-in estimates based on the estimated means may lead to wrong estimates of the complexity and consequently budget allocation based on mistaken beliefs (compare Garivier and Kaufmann, 2016).
-
-Furthermore, Locatelli et al. (2016) were able to present an upper bound for the APT algorithm matching the lower bound in their Theorem 1. Proofs of both bounds are given below.
-
-Where the APT algorithm shows room for improvement is when it comes to settings with distributions that are not sub-Gaussian.
-This is mentioned in Locatelli et al.
+This is in particular worth highlighting when comparing APT to algorithms used in the best arm identification or Top-$m$ setting.
+As alluded to in \autoref{sec:TheAPTAlgorithm}, many algorithms that fix the sampling budget upfront (i.e., fixed budget algorithms as UCB-E or KL-LUCB-E) require knowledge about the corresponding complexity upfront (Audibert et al., 2010; Kaufmann and Kalyanakrishnan, 2013).
+The problem however being, that to know the complexity, the experimenter has to know all means up to a permutation of the arms.
+This, of course, is not given in practice.
+Thus alternative algorithms try to estimate the complexity online which can be difficult as especially in the beginning plug-in estimates based on the estimated means may lead to wrong estimates of the complexity, which in turn leads to poor budget allocation based on mistaken beliefs (compare Garivier and Kaufmann, 2016).
+On the other hand, the sequential sampling strategy has to rely on some estimate.
+While the APT algorithm does not explicitly estimate the complexity, the gaps that serve as index are essentially the same.
+Faced not with sub-Gaussian but more heavy-tailed distributions, these estimates might well lead to poor performance.
+
+Here, the APT algorithm shows room for improvement, as also mentioned in Locatelli et al.
 (2016).
-In general, the problem becomes that the assumptions for the bounds no longer hold; furthermore, the statistic $B_i(t+1)$, and the term $\hat{\Delta}_i(t)$ are motivated by (sub-)Gaussian distributions.
-The more one moves away from Gaussian-like distributions, the less appropriate this term becomes, however.
-In particular, the empirical mean will be less concentrated around the true mean and more impacted by outliers which are more likely under non sub-Gaussian distributions.
+The problem is that the assumptions for the bounds no longer hold as arms are less sub-Gaussian; of course the complexity $H$ and the term $\hat{\Delta}_i(t)$ in the algorithm's index are motivated by sub-Gaussian distributions.
+The more one moves away from those, the less appropriate these quantities become.
+In particular, the empirical mean will be less (or not at all) concentrated around the true mean and more impacted by outliers which are more likely under non sub-Gaussian distributions.
 Locatelli et al.
 (2016) thus refers to Bubeck et al.
-(2013) which considers solutions for multi-armed bandits that are based on heavy-tail distributions.
+(2013a) which considers solutions for multi-armed bandits that are based on heavy-tail distributions.
 By using more robust estimators of the mean, one could equip the APT algorithm to deal with such distributions.
 
-Another step towards dealing with non sub-Gaussianity is made by Mukherjee et al.
-(2017) who use an estimate of the variance additionally to the empirical mean in their Augmented UCB solution.
-Utilizing this additional information, the algorithm seems to perform better than for example APT, going from simulation results displayed in the paper.
-However, the simulations deal exclusively with normal distributions, as the variance has to be bounded for the upper bound of the Augmented UCB to hold.
-We will continue to discuss the Augmented UCB solution in chapter 3.
+Both Mukherjee et al.
+(2017) as well as Zhong et al.
+(2017) use estimates of the variance of the arms for their algorithms for the thresholding bandit problem and try to thereby improve upon the performance of the APT algorithm.
+While their simulations show promising results, their bounds rely on the assumption of bounded reward distributions.
+Thus their algorithms are not necessarily able to improve upon the assumption of sub-Gaussian distributions made by Locatelli et al.
+(2016).
+We will continue to discuss their results in \autoref{chap:VarianceBasedAlgorithms}.
 
@@
 This, for example, is the case for Bernoulli distributions at very small parameters $\mu$.
-By looking at the graphical examples below it becomes obvious that the Kullback-Leibler divergence between Bernoulli distributions starts to lose any similarity to the quadratic approximation.
-The second graph then shows that the actual Kullback-Leibler divergence of Bernoulli distributions loses any symmetry over this range of parameter values.
-Given that Bernoulli distributions with very small parameter values arise naturally in many applications in website optimization, advertising click-through modeling, or anomaly detection in time series, there is a need to tackle this problem.
-
-Refer also to page 6 in Kaufmann et al.
-(2016): "This information-theoretic lower bound permits to interpret the quantity $H(\nu)$ defined in (2) as a subgaussian approximation".
-In the case of Normal distributions with known and equal mean, it holds that the Kullback-Leibler divergence between $\nu_i$ and $\nu_j$, parameterized by $\mu_i$ and $\mu_j$, can be written as
-
-$$
-\KL_{Normal}(\nu_i || \nu_j) = 2(\mu_i - \mu_j)^2.
+We have for the Kullback-Leibler divergence of two Gaussian distributions $\nu_i$ and $\nu_j$ of mean $\mu_i$ and $\mu_j$ with equal variance:
+
+$$
+\KL_{N}(\nu_i || \nu_j) = 2(\mu_i - \mu_j)^2.
 $$
@@
 
-In the case of $\tau = 0.5$, the latter KL-divergence is symmetric in its first argument, and thus can be well approximated by Pinsker's inequality:
+In the case of $\tau = 0.5$, the latter KL-divergence is symmetric in its first argument, and thus can be relatively well approximated by Pinsker's inequality (SHOW IN GRAPH!):
 
@@
 
-This shows how the distance measure used in the APT algorithm, and consequently the complexity $H$, is a useful approximation of the KL-divergence for sub-Gaussian distributions.
-However, this approximation suffers as the distributions less and less similar to Gaussian distributions.
+This is of course equal to the Gaussian KL-divergence described before.
+This approximation, however, suffers for heavily for very small values of $\mu_i$ and $\tau$.
+In particular, the Bernoulli KL-divergence becomes asymmetric in its first argument as $\tau \neq 0.5$.
+Thus, in contrast to the complexity measure $H$ based on the Gaussian KL-divergence, a complexity measure based on the Bernoulli KL-divergence would evaluate two arms as differently difficult if their absolute distance to the threshold is the same, but they lie on different sides of the threshold.
+
 Thus similarly to how UCB algorithms in the cumulative regret setting have been extended to KL-UCB algorithms (compare Cappé et al., 2013), also the APT algorithm offers room for improvement.
-
-And so a potential approach can be to use the Kullback-Leibler divergence as measure similar to the methods proposed in Kaufmann et al.
-(2015).
-They proposed Kullback-Leibler based approaches for the pure exploration bandit setting, which we will describe in chapter 2.
-Then, in chapter 3, we will come back to the problem of using the Kullback-Leibler divergence in the thresholding bandit setting.
-To conclude chapter 1, we proof the lower bound and upper bound for the APT algorithm as presented Theorem 1 and Theorem 2 in Locatelli et al.
+As a more explicit example of such adaptation, consider the case of Top-$m$ identification described in Kaufmann et al.
 (2016).
+The authors develop a lower bound based on KL-divergence, and note that "This information-theoretic lower bound permits to interpret the quantity $H(\nu)$ [...] as a subgaussian approximation".
+Given that Bernoulli distributions with very small parameter values arise naturally in many applications, an improvement in this regard would be valuable.
+
+In what follows, we first examine in \autoref{chap:KullbackLeiblerPureExploration} how information theoretic quantities are employed in the best arm identification and Top-$m$ problem as detailed in Kaufmann and Garivier (2016) and Kaufmann et al.
+(2016).
+Before introducing a new algorithm for the thresholding bandit problem based on Kullback-Leibler divergences in \autoref{sec:LikelihoodRatioForExponentialFamily}, we first describe the variance-based approaches in \autoref{chap:VarianceBasedAlgorithms}.
 
@@
 
-# Kullback-Leibler Complexity of Pure Exploration
+# Kullback-Leibler Complexity of Pure Exploration \label{chap:KullbackLeiblerPureExploration}
 
@@
 
-## Variance Based Algorithms for Thresholding Bandits
-
-### Augmented-UCB Algorithm
+## Variance Based Algorithms for Thresholding Bandits \label{chap:VarianceBasedAlgorithms}
+
+### Augmented-UCB Algorithm \label{sec:AugUCBAlgorithm}
 
@@
 
-### Anytime Parameter-free Empirical Variance Guided Algorithm
+### Anytime Parameter-free Empirical Variance Guided Algorithm \label{sec:EVTAlgorithm}
 
@@
 
-## Likelihood Ratio for Exponential Family Distributions
+## Likelihood Ratio for Exponential Family Distributions \label{sec:LikelihoodRatioForExponentialFamily}
 
@@
        subtitle = "5000 iterations; a value of 1000 means that in 20% of 
-the iterations the arm was pulled in that round.")
+the iterations the arm was pulled in that round.") +
+  theme(legend.position = "bottom")
+
+rbind(loc6nt_BUCB_c15_ma, loc6nt_BUCB_ma, loc6nt_BUCB_c5_ma) %>%
+  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
+  geom_line(size = 0.3) +
+  facet_grid(.~algorithm) +
+  labs(x = "Index", y = "10 Rounds Moving Average",
+       title = "Average Number of Pulls Allocated to Each Arm per Round",
+       subtitle = "5000 iterations; a value of 1000 means that in 20% of 
+       the iterations the arm was pulled in that round.")+
+  theme(legend.position = "bottom")
 ```
@@
 load(paste0(current_path, "exp2_comp_UNIFORM.Rda"))
-
-alg_names <- c(rep(c("Uniform", "APT","SLR"), 
+load(paste0(current_path, "exp2_comp_AugUCB.Rda"))
+
+alg_names <- c(rep(c("Uniform", "APT","SLR", "AugUCB"), 
                    each = 3981), rep("EVT", 3961))
-index <- c(rep(20:4000, times = 3), 40:4000)
-alg_res <- log(c(exp2_comp_UNIFORM, exp2_comp_APT, exp2_comp_LR, exp2_comp_EVT))
+index <- c(rep(20:4000, times = 4), 40:4000)
+alg_res <- log(c(exp2_comp_UNIFORM, exp2_comp_APT, exp2_comp_LR,
+                 exp2_comp_AugUCB, exp2_comp_EVT))
 exp2_comp_res <- data.frame(index = index, names = alg_names, 
@@
 load(paste0(current_path, "pois2_comp_EVT.Rda"))
-#load(paste0(current_path, "pois2_comp_UNIFORM.Rda"))
-
-alg_names <- c(rep(c("APT", "SLR"), each = 9981), rep("EVT", 9961))
-index <- c(rep(20:10000, times = 2), 40:10000)
-alg_res <- log(c(pois2_comp_APT, pois2_comp_LR, pois2_comp_EVT))
+load(paste0(current_path, "pois2_comp_UNIFORM.Rda"))
+
+alg_names <- c(rep(c("Uniform", "APT", "SLR"), each = 9981), 
+               rep("EVT", 9961))
+index <- c(rep(20:10000, times = 3), 40:10000)
+alg_res <- log(c(pois2_comp_UNIFORM, pois2_comp_APT, 
+                 pois2_comp_LR, pois2_comp_EVT))
 pois2_comp_res <- data.frame(index = index, names = alg_names, 

### 2017-08-27 Thesis/Draft.tex
add hoeffding bound

@@
 
-\begin{itemize}
-\tightlist
-\item
-  Show Chernoff/Hoeffding bound detailed
-\item
-  Show union bound to get deviation for all arms \(i \leq K\) and every
-  round \(s \leq T\)
-\end{itemize}
+We know that \(X_i\) are \(R\)-sub-Gaussian by assumption. That is, we
+have
+
+\[
+\mathbb{E}[\exp (tX_{i,s}-t\mathbb{E}[X_{i,s}])] = \mathbb{E}[\exp (t(X_{i,s}-\mathbb{E}[X_{i,s}]))] \leq \exp (R^2t^2/2)
+\]
+
+where the RHS is the moment-generating function of the random variable
+\(X_{i,s}-\mathbb{E}[X_{i,s}]\). While Höffding's Lemma and Höffding's
+Inequality are commonly applied to bounded random variables \(Z\) with
+\(\mathbb{P}(a\leq Z \leq b) = 1\) and \(\mathbb{E}[Z] = 0\), we see
+that \(Z\) are \(R\)-sub-Gaussian with \(R^2 = \frac{(a-b)^2}{4}\).
+Using this last equality, we can easily apply Höffding's Inequality to
+our case.
+
+\begin{lemma}[Höffding's Inequality (Kloft Lecture Notes)] \label{lemma:HoeffdingsInequality}
+Let $X_1, ..., X_s$ be independent, identically distributed random variables with mean $\mathbb{E}[X_t] = \mu$ and $\mathbb{P}(a_t \leq X_t - \mathbb{E}[X] \leq b_t) = 1$.
+Denote their empirical mean by $\bar{X}_s=\frac{1}{s}\sum_{t=1}^{s}X_t$.
+Then, for any $\gamma > 0$, we have the following concentration inequality:
+
+\begin{equation*}
+\mathbb{P}(|\bar{X}_s - \mu| \geq \gamma) \leq 2\exp (-2s^2\gamma^2/\sum_{t=1}^s(b_t - a_t)^2).
+\end{equation*}
+\end{lemma}
+
+If we replace \(\sum_{t=1}^s(b_t - a_t)^2\) by \(4sR^2\), we have the
+concentration inequality for our \(R\)-sub-Gaussian random variables:
+
+\[
+\mathbb{P}(|\bar{X}_s - \mu| \geq \gamma) \leq 2\exp (-\frac{s\gamma^2}{2R^2}).
+\]
+
+Writing \(\gamma = \sqrt{\frac{T\delta^2}{Hs}}\), we get for the
+favorable event
+\(\xi_i = \{|\bar{X}_s - \mu| \leq \sqrt{\frac{T\delta^2}{Hs}}\}\) of an
+individual arm \(i\), for each \(i \in \mathbb{A}\) and each
+\(s \in \{1, ..., T\}\):
+
+\[
+\mathbb{P}(\xi_i) = \mathbb{P}\Big(|\bar{X}_{i,s} - \mu_i| \leq \sqrt{\frac{T\delta^2}{Hs}}\Big) \geq 1 - 2\exp (-\frac{T\delta^2}{2R^2H}),
+\] where \(T\) is again the total budget of samples, and \(H\) the
+complexity. Now let
+
+\[
+\tilde{\xi} = \Big\{\forall i \in \mathbb{A}: |\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}} \Big\}.
+\]
+
+To derive the probability of event \(\tilde{\xi}\), we apply a union
+bound on \(\mathbb{P}(\cup_{i=1}^K \xi_i^C)\):
+
+\begin{align*}
+\mathbb{P}(\tilde{\xi}) & = & 1-\mathbb{P}(\xi^C) \\
+& = & 1-\mathbb{P}(\cup_{i=1}^K \xi_i^C) \\
+& \geq & 1 - \sum_{i=1}^K \mathbb{P}(\xi_i^C) \\
+& \geq & 1 - 2K\exp (-\frac{T\delta^2}{2R^2H})
+\end{align*}
+
+We could use the same union bound a second time to bound over all
+\(s \in \{1, ..., T\}\) and derive for the favorable event \(\xi\):
+
+\[
+\mathbb{P}(\xi) \geq 1 - 2TK \exp(-\frac{T\delta^2}{2R^2H})
+\]
+
+Locatelli et al. (2016) use instead of Höffding's inequality a
+Sub-Gaussian martingale inequality including a peeling argument in order
+to derive a better bound of
 
@@
 \]
+
+This bound is non-trivial for much smaller values of \(T\), and we will
+use it in the following.
 
@@
 \newpage
+
+We now present the lower bound given in Locatelli et al. (2016) for the
+thresholding bandit problem. In order to derive the bound, a problem is
+specified to show that the error of the lower bound is attained even in
+this specific problem. In particular, for a set of problems with
+Gaussian distributions of variance \(1\), the largest probability of
+error on these problems that the best algorithm exhibits is still at
+least as large as the lower bound.
 
@@
 upper bound on the expected regret. This is in particular worth
-highlighting when comparing APT to algorithms used in the pure
-exploration bandit setting. There, many algorithms require knowledge
-about the corresponding complexity upfront. The problem however being,
-that to know the complexity, the experimenter has to know all means up
-to a permutation of the arms (for example, see Audibert et al., 2010).
-This, of course, is not given in practice and thus alternative
-algorithms try to estimate the complexity online which is not a
-desirable solution either as especially in the beginning plug-in
+highlighting when comparing APT to algorithms used in the best arm
+identification or Top-\(m\) setting. As alluded to in
+\autoref{sec:TheAPTAlgorithm}, many algorithms that fix the sampling
+budget upfront (i.e., fixed budget algorithms as UCB-E or KL-LUCB-E)
+require knowledge about the corresponding complexity upfront (Audibert
+et al., 2010; Kaufmann and Kalyanakrishnan, 2013). The problem however
+being, that to know the complexity, the experimenter has to know all
+means up to a permutation of the arms. This, of course, is not given in
+practice. Thus alternative algorithms try to estimate the complexity
+online which can be difficult as especially in the beginning plug-in
 estimates based on the estimated means may lead to wrong estimates of
-the complexity and consequently budget allocation based on mistaken
-beliefs (compare Garivier and Kaufmann, 2016).
-
-Furthermore, Locatelli et al. (2016) were able to present an upper bound
-for the APT algorithm matching the lower bound in their Theorem 1.
-Proofs of both bounds are given below.
-
-Where the APT algorithm shows room for improvement is when it comes to
-settings with distributions that are not sub-Gaussian. This is mentioned
-in Locatelli et al. (2016). In general, the problem becomes that the
-assumptions for the bounds no longer hold; furthermore, the statistic
-\(B_i(t+1)\), and the term \(\hat{\Delta}_i(t)\) are motivated by
-(sub-)Gaussian distributions. The more one moves away from Gaussian-like
-distributions, the less appropriate this term becomes, however. In
-particular, the empirical mean will be less concentrated around the true
-mean and more impacted by outliers which are more likely under non
-sub-Gaussian distributions. Locatelli et al. (2016) thus refers to
-Bubeck et al. (2013) which considers solutions for multi-armed bandits
-that are based on heavy-tail distributions. By using more robust
-estimators of the mean, one could equip the APT algorithm to deal with
-such distributions.
-
-Another step towards dealing with non sub-Gaussianity is made by
-Mukherjee et al. (2017) who use an estimate of the variance additionally
-to the empirical mean in their Augmented UCB solution. Utilizing this
-additional information, the algorithm seems to perform better than for
-example APT, going from simulation results displayed in the paper.
-However, the simulations deal exclusively with normal distributions, as
-the variance has to be bounded for the upper bound of the Augmented UCB
-to hold. We will continue to discuss the Augmented UCB solution in
-chapter 3.
+the complexity, which in turn leads to poor budget allocation based on
+mistaken beliefs (compare Garivier and Kaufmann, 2016). On the other
+hand, the sequential sampling strategy has to rely on some estimate.
+While the APT algorithm does not explicitly estimate the complexity, the
+gaps that serve as index are essentially the same. Faced not with
+sub-Gaussian but more heavy-tailed distributions, these estimates might
+well lead to poor performance.
+
+Here, the APT algorithm shows room for improvement, as also mentioned in
+Locatelli et al. (2016). The problem is that the assumptions for the
+bounds no longer hold as arms are less sub-Gaussian; of course the
+complexity \(H\) and the term \(\hat{\Delta}_i(t)\) in the algorithm's
+index are motivated by sub-Gaussian distributions. The more one moves
+away from those, the less appropriate these quantities become. In
+particular, the empirical mean will be less (or not at all) concentrated
+around the true mean and more impacted by outliers which are more likely
+under non sub-Gaussian distributions. Locatelli et al. (2016) thus
+refers to Bubeck et al. (2013a) which considers solutions for
+multi-armed bandits that are based on heavy-tail distributions. By using
+more robust estimators of the mean, one could equip the APT algorithm to
+deal with such distributions.
+
+Both Mukherjee et al. (2017) as well as Zhong et al. (2017) use
+estimates of the variance of the arms for their algorithms for the
+thresholding bandit problem and try to thereby improve upon the
+performance of the APT algorithm. While their simulations show promising
+results, their bounds rely on the assumption of bounded reward
+distributions. Thus their algorithms are not necessarily able to improve
+upon the assumption of sub-Gaussian distributions made by Locatelli et
+al. (2016). We will continue to discuss their results in
+\autoref{chap:VarianceBasedAlgorithms}.
 
@@
 Gaussian. This, for example, is the case for Bernoulli distributions at
-very small parameters \(\mu\). By looking at the graphical examples
-below it becomes obvious that the Kullback-Leibler divergence between
-Bernoulli distributions starts to lose any similarity to the quadratic
-approximation. The second graph then shows that the actual
-Kullback-Leibler divergence of Bernoulli distributions loses any
-symmetry over this range of parameter values. Given that Bernoulli
-distributions with very small parameter values arise naturally in many
-applications in website optimization, advertising click-through
-modeling, or anomaly detection in time series, there is a need to tackle
-this problem.
-
-Refer also to page 6 in Kaufmann et al. (2016): ``This
-information-theoretic lower bound permits to interpret the quantity
-\(H(\nu)\) defined in (2) as a subgaussian approximation''. In the case
-of Normal distributions with known and equal mean, it holds that the
-Kullback-Leibler divergence between \(\nu_i\) and \(\nu_j\),
-parameterized by \(\mu_i\) and \(\mu_j\), can be written as
-
-\[
-\KL_{Normal}(\nu_i || \nu_j) = 2(\mu_i - \mu_j)^2.
+very small parameters \(\mu\). We have for the Kullback-Leibler
+divergence of two Gaussian distributions \(\nu_i\) and \(\nu_j\) of mean
+\(\mu_i\) and \(\mu_j\) with equal variance:
+
+\[
+\KL_{N}(\nu_i || \nu_j) = 2(\mu_i - \mu_j)^2.
 \]
@@
 In the case of \(\tau = 0.5\), the latter KL-divergence is symmetric in
-its first argument, and thus can be well approximated by Pinsker's
-inequality:
+its first argument, and thus can be relatively well approximated by
+Pinsker's inequality (SHOW IN GRAPH!):
 
@@
 
-This shows how the distance measure used in the APT algorithm, and
-consequently the complexity \(H\), is a useful approximation of the
-KL-divergence for sub-Gaussian distributions. However, this
-approximation suffers as the distributions less and less similar to
-Gaussian distributions. Thus similarly to how UCB algorithms in the
-cumulative regret setting have been extended to KL-UCB algorithms
-(compare Cappé et al., 2013), also the APT algorithm offers room for
-improvement.
-
-And so a potential approach can be to use the Kullback-Leibler
-divergence as measure similar to the methods proposed in Kaufmann et al.
-(2015). They proposed Kullback-Leibler based approaches for the pure
-exploration bandit setting, which we will describe in chapter 2. Then,
-in chapter 3, we will come back to the problem of using the
-Kullback-Leibler divergence in the thresholding bandit setting. To
-conclude chapter 1, we proof the lower bound and upper bound for the APT
-algorithm as presented Theorem 1 and Theorem 2 in Locatelli et al.
-(2016).
+This is of course equal to the Gaussian KL-divergence described before.
+This approximation, however, suffers for heavily for very small values
+of \(\mu_i\) and \(\tau\). In particular, the Bernoulli KL-divergence
+becomes asymmetric in its first argument as \(\tau \neq 0.5\). Thus, in
+contrast to the complexity measure \(H\) based on the Gaussian
+KL-divergence, a complexity measure based on the Bernoulli KL-divergence
+would evaluate two arms as differently difficult if their absolute
+distance to the threshold is the same, but they lie on different sides
+of the threshold.
+
+Thus similarly to how UCB algorithms in the cumulative regret setting
+have been extended to KL-UCB algorithms (compare Cappé et al., 2013),
+also the APT algorithm offers room for improvement. As a more explicit
+example of such adaptation, consider the case of Top-\(m\)
+identification described in Kaufmann et al. (2016). The authors develop
+a lower bound based on KL-divergence, and note that ``This
+information-theoretic lower bound permits to interpret the quantity
+\(H(\nu)\) {[}\ldots{}{]} as a subgaussian approximation''. Given that
+Bernoulli distributions with very small parameter values arise naturally
+in many applications, an improvement in this regard would be valuable.
+
+In what follows, we first examine in
+\autoref{chap:KullbackLeiblerPureExploration} how information theoretic
+quantities are employed in the best arm identification and Top-\(m\)
+problem as detailed in Kaufmann and Garivier (2016) and Kaufmann et al.
+(2016). Before introducing a new algorithm for the thresholding bandit
+problem based on Kullback-Leibler divergences in
+\autoref{sec:LikelihoodRatioForExponentialFamily}, we first describe the
+variance-based approaches in \autoref{sec:VarianceBasedAlgorithms}.
 
@@
 
-\section{Kullback-Leibler Complexity of Pure
-Exploration}\label{kullback-leibler-complexity-of-pure-exploration}
+\section{\texorpdfstring{Kullback-Leibler Complexity of Pure Exploration
+\label{chap:KullbackLeiblerPureExploration}}{Kullback-Leibler Complexity of Pure Exploration }}\label{kullback-leibler-complexity-of-pure-exploration}
 
@@
 
-\subsection{Variance Based Algorithms for Thresholding
-Bandits}\label{variance-based-algorithms-for-thresholding-bandits}
-
-\subsubsection{Augmented-UCB Algorithm}\label{augmented-ucb-algorithm}
+\subsection{\texorpdfstring{Variance Based Algorithms for Thresholding
+Bandits
+\label{chap:VarianceBasedAlgorithms}}{Variance Based Algorithms for Thresholding Bandits }}\label{variance-based-algorithms-for-thresholding-bandits}
+
+\subsubsection{\texorpdfstring{Augmented-UCB Algorithm
+\label{sec:AugUCBAlgorithm}}{Augmented-UCB Algorithm }}\label{augmented-ucb-algorithm}
 
@@
 
-\subsubsection{Anytime Parameter-free Empirical Variance Guided
-Algorithm}\label{anytime-parameter-free-empirical-variance-guided-algorithm}
+\subsubsection{\texorpdfstring{Anytime Parameter-free Empirical Variance
+Guided Algorithm
+\label{sec:EVTAlgorithm}}{Anytime Parameter-free Empirical Variance Guided Algorithm }}\label{anytime-parameter-free-empirical-variance-guided-algorithm}
 
@@
 
-\subsection{Likelihood Ratio for Exponential Family
-Distributions}\label{likelihood-ratio-for-exponential-family-distributions}
+\subsection{\texorpdfstring{Likelihood Ratio for Exponential Family
+Distributions
+\label{sec:LikelihoodRatioForExponentialFamily}}{Likelihood Ratio for Exponential Family Distributions }}\label{likelihood-ratio-for-exponential-family-distributions}
 
@@
 \includegraphics{Draft_files/figure-latex/unnamed-chunk-4-1.pdf}
+\includegraphics{Draft_files/figure-latex/unnamed-chunk-4-2.pdf}
 

### 2017-08-27 synthetic_experiments/cal_algs_verylong_6_no_tau.R

@@ -52,6 +52,8 @@ gc()
 # Plot the results
 
 load(paste0(current_path, "/loc6nt_comp_BUCB_horizon_7000.Rda"))
+load(paste0(current_path, "/loc6nt_comp_BUCB_horizon_c5_7000.Rda"))
+load(paste0(current_path, "/loc6nt_comp_BUCB_horizon_c15_7000.Rda"))
 load(paste0(current_path, "/loc6nt_comp_AugUCB_7000.Rda"))
 load(paste0(current_path, "/loc6nt_comp_KLUCB370_5000.Rda"))
 load(paste0(current_path, "/loc6nt_comp_UNIFORM_7000.Rda"))
@@ -60,6 +62,8 @@ load(paste0(current_path, "/loc6nt_comp_LR_7000.Rda"))
 
 plot(c(0,7000), c(0, -5), type = "n")
 lines(log(loc6nt_comp_BUCB_horizon_7000), col = "blue")
+lines(log(loc6nt_comp_BUCB_horizon_c5_7000), col = "lightblue")
+lines(log(loc6nt_comp_BUCB_horizon_c15_7000), col = "darkblue")
 #lines(log(loc6nt_comp_BUCB_horizon), col = "lightblue")
 #lines(log(loc6nt_comp_APT), col = "pink")
 lines(log(loc6nt_comp_LR_7000), col = "green")
@@ -106,6 +110,48 @@ save(loc6nt_comp_BUCB_horizon_7000, file = paste0(current_path,
                                                   "loc6nt_comp_BUCB_horizon_7000.Rda"))
 
 ########################################################################
+# Try a different exploration parameter for BUCB
+
+loc6nt_BUCB_horizon_c5_7000 <- para_bandit_sim_bucb(data = data_list6, 
+                                                 rounds = 7000, 
+                                                 rate = "inverse_horizon_c",
+                                                 tau = tau_loc6nt, 
+                                                 epsilon = epsilon_loc6nt, 
+                                                 alpha = tau_loc6nt, 
+                                                 beta = 1-tau_loc6nt,
+                                                 const = 5)
+save(loc6nt_BUCB_horizon_c5_7000, 
+     file = paste0(current_path, "loc6nt_BUCB_horizon_c5_7000.Rda"))
+loc6nt_comp_BUCB_horizon_c5_7000 <- compare_to_ground_truth(mean_loc6nt, 
+                                                         loc6nt_BUCB_horizon_c5_7000,
[…]

### 2017-08-27 synthetic_experiments/poisson/exp_pois_2.R

@@ -35,6 +35,7 @@ gc()
 load(paste0(current_path, "pois2_comp_LR.Rda"))
 load(paste0(current_path, "pois2_comp_APT.Rda"))
 load(paste0(current_path, "pois2_comp_EVT.Rda"))
+load(paste0(current_path, "pois2_comp_UNIFORM.Rda"))
 
 plot(c(0,10000), c(0, -7), type = "n")
 abline(h=log(0.1), lty = 2)

### 2017-08-28 Thesis/Draft.Rmd
Edit AugUCB chapter

@@
 
-\newpage
-
 We now present the lower bound given in Locatelli et al.
@@
 
-\newpage
-
 ## Discussion \label{sec:DiscussionLocatelli}
+
+- Mention Optimality (Upper Bound matches lower bound)
+- Anytime
 
@@
 
-In the case of $\tau = 0.5$, the latter KL-divergence is symmetric in its first argument, and thus can be relatively well approximated by Pinsker's inequality (SHOW IN GRAPH!):
+In the case of $\tau = 0.5$, the latter KL-divergence is symmetric in its first argument, and thus can be relatively well approximated by Pinsker's inequality:
 
@@
 
-```{r, echo = FALSE}
+```{r KLApproximationComparison, echo = FALSE, message = FALSE, out.width = '80%', fig.align = "center", fig.cap= "The approximation of the Bernoulli KL-divergence by the Gaussian KL-divergence works well if the second argument is equal to 0.5.
+Else we observe poor approximation in both value and symmetry.
+This becomes more obvious as the arguments move away from 0.5."}
+library(dplyr)
+library(tidyr)
+library(ggplot2)
 KL_ber <- function(p,q) p*log(p/q) + (1-p)*log((1-p)/(1-q))
-par(mfcol = c(1,2))
-
-plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1), type = "n", asp = 1,
-     xlab = "p_1", ylab = "KL(Ber(p_1),Ber(p_2))", main = "KL of Bernoullis")
-for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
-  lines(seq(0.00001,0.3, by = 0.000005),
-       KL_ber(seq(0.00001,0.3, by = 0.000005),i))
-}
-
-plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1), type = "n", asp = 1,
-     xlab = "p_1", ylab = "(p_1 - p_2)^2", main = "Gaussian approx.\n KL of Bernoullis")
-for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
-  lines(seq(0.00001,0.3, by = 0.000005),
-        (seq(0.00001,0.3, by = 0.000005)-i)^2)
-}
-par(mfcol = c(1,1))
+KL_gauss <- function(p,q) 2*(p-q)^2
+
+kldf <- data.frame(mu = rep(seq(0.00001, 0.99999, 
+                                length.out = 10000), 2),
+                   tau = c(rep(0.5, 10000), rep(0.05, 10000)))
+
+kldf_long <- kldf %>% mutate(Gaussian = KL_gauss(mu, tau),
+                             Bernoulli = KL_ber(mu, tau)) %>%
+  gather(key = KL_Type, value = KL, -mu, -tau) %>%
+  mutate(tau = as.character(tau))
+
+kldf2 <- data.frame(mu = rep(seq(0.00001, 0.09999, 
+                                length.out = 10000), 1),
+                   tau = c(rep(0.05, 10000)))
+
+kldf2_long <- kldf2 %>% mutate(Gaussian = KL_gauss(mu, tau),
+                              Bernoulli = KL_ber(mu, tau)) %>%
+  gather(key = KL_Type, value = KL, -mu, -tau) %>%
+  mutate(tau = as.character(tau))
+
+kldf_total <- cbind.data.frame(level = c(rep("Global", 40000),
+                                         rep("Local", 20000)),
+                               rbind.data.frame(kldf_long, kldf2_long))
+
+ggplot(kldf_total, aes(x = mu, y = KL, 
+                      group = interaction(KL_Type, tau))) +
+  facet_grid(level~., scales = "free") +
+  geom_line(aes(color = tau, linetype = KL_Type)) +
+  labs(x = "First argument of KL-divergence",
+       y = "KL-divergence",
+       title = "Comparison of Bernoulli KL-divergence and 
+Gaussian Approximation")  +
+  theme_bw() +
+  theme(legend.position = "bottom") +
+  scale_color_discrete(name = "Second argument of KL-divergence") +
+  scale_linetype_discrete(name = "Type of KL-divergence") +
+  guides(color = guide_legend(title.position = "top"),
+         linetype = guide_legend(title.position = "top"))
 ```
-
-```{r, echo = FALSE}
-KL_ber <- function(p,q) p*log(p/q) + (1-p)*log((1-p)/(1-q))
-par(mfcol = c(1,2))
-
-plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1), type = "n", asp = 1,
-     xlab = "p_1", ylab = "KL(Ber(p_2),Ber(p_1))", main = "KL of Bernoullis")
-for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
-  lines(seq(0.00001,0.3, by = 0.000005),
-        KL_ber(i,seq(0.00001,0.3, by = 0.000005)))
-}
-
-plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1), type = "n", asp = 1,
-     xlab = "p_1", ylab = "(p_2 - p_1)^2", main = "Gaussian approx.\n KL of Bernoullis")
-for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
-  lines(seq(0.00001,0.3, by = 0.000005),
-        (i-seq(0.00001,0.3, by = 0.000005))^2)
-}
-par(mfcol = c(1,1))
-```
-
-\newpage
 
@@
 Lastly, we have the set of probability distributions on the arms $\mathcal{A}$: $\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}$.
-\marginpar{Give more intuition for what these probability distributions are} We are now ready to state the theorem.
+We are now ready to state the theorem.
 
@@
 
-# Extensions to the Thresholding Bandit Problem
-
-## Introduction
-
-We have introduced the thresholding bandit problem in chapter 1.
-The APT algorith described in Locatelli et al.
-(2016) is able to match a lower bound (be more specific!) given in the same paper, and has several favorable characteristics such as its overall simplicity and it being an anytime algorithm.
-However, the bounds on the expected loss assume the arms' distributions to be $R$-sub-Gaussian.
-This is reflected in the algorithm's complexity measure $H = \sum_{i=1}^K (\Delta_i^{\tau, \epsilon})^{-2}$, where $\Delta_i^{\tau,\epsilon} = |\mu_i - \tau| + \epsilon$, which -- given the known threshold $\tau \pm \epsilon$ -- only depends on the distribution's mean.
-This is appropriate for Gaussian arms with equal variances, but potentially inefficient for other kinds of distributions.
+# Extensions to the Thresholding Bandit Problem \label{chap:Extensions}
+
+## Introduction \label{sec:ExtensionsIntroduction}
+
+In \autoref{chap:ThresholdingBanditProblem} we have introduced the thresholding bandit problem as proposed in Locatelli et al.
+(2016) alongside the APT algorithm.
+We have seen that the upper bound on the APT algorithm matches the lower bound for the thresholding bandit problem given in Locatelli et al.
+(2016).
+The algorithm also exhibits favorable characteristics such that its upper bound holds at any stopping time, and that it does not require any parameter to be known upfront.
+However, we have seen that the index and the complexity term $H$ employed by the APT algorithm are the most effective for $R$-sub-Gaussian distributions.
+Both are related to the KL-divergence between two Gaussian distributions of equal variance.
+Given that this sub-Gaussian approximation can be poor in certain cases, we motivated the use of information theoretic measures in an algorithm's index (compare \autoref{sec:DiscussionLocatelli}).
+
+Another goal can be to compare the distributions with the threshold based not only on the empirical mean -- as done by the APT algorithm.
+A logical extension is for example the empirical variance.
+After all arms do not necessarily have the same variance, even if they are sub-Gaussian.
+And given two arms for which we estimate the same mean, we would prefer to draw more samples from the arm with the larger variance.
 
@@
 
-In the case of Gaussians, the complexity $H$ is nice also because it reflects the Kullback-Leibler divergence between two Gaussians.
-And since Bernoulli distributions are bounded on the interval $[0,1]$, they are consequently sub-Gaussian, meaning that their Kullback-Leibler divergence can be approximated by the Gaussian one.
-However, while Bernoullis are sub-Gaussian, the approximation of their divergence by the Gaussian divergence becomes less and less optimal as the parameter (and thus mean) goes to $0$ or $1$, as shown in chapter 1.
-And while online advertisements might not be an obvious use case for thresholding bandits, they are just one real life scenario dominated by Bernoulli distributions with very small parameters.
-Thus it is worthwile to adapt current solutions of the thresholding bandit problem to cases in which the Gaussian Kullback-Leibler divergence is no longer an appropriate approximation.
-
-Large motiviation for the idea of adjusting the complexity measure (and thus the algorithms) to distributions more generally based on the Kullback-Leibler divergence stems from the work discussed in chapter 2, complexity measures were defined for the pure exploration bandits in terms of the Kullback-Leibler divergence.
-Based on this, the authors were for example able to point our differences between Gaussian and Bernoulli bandits.
-We expect that results in a similar vain could be derived for thresholding bandits.
-
-To this end, in the following, we first present an extension of mean based algorithms to an algorithm that incorporates empirical variances as described in Mukherjee et al.
+For these reasons, in the following, we first present in \autoref{sec:VarianceBasedAlgorithms} two algorithms which incorporate empirical variances as described in Mukherjee et al.
+(2017) and Zhong et al.
 (2017).
-Afterwards, we propose and discuss potential further improvements based on Kullback-Leibler divergence and Bayesian posterior distributions.
-Finally, we compare the performance of different algorithms based on simulations and real world data sets.
-
-## Variance Based Algorithms for Thresholding Bandits \label{chap:VarianceBasedAlgorithms}
+We then introduce a new algorithm based on the concept of likelihood ratios in \autoref{sec:LikelihoodRatioForExponentialFamily}.
+Finally, we compare the performance of different algorithms based on simulations and real world data sets in \autoref{chap:Experiments}.
+
+## Variance Based Algorithms for the Thresholding Bandit \label{sec:VarianceBasedAlgorithms}
 
@@
 
-Mukherjee et al.
-(2017) propose an algorithm based on variance estimates called Augmented-UCB (AugUCB).
-The setting in which the algorithm is proposed is very similar to the setting in Locatelli et al.
+Combining learnings from the APT and other algorithms, Mukherjee et al.
+(2017) propose the Augmented-UCB (AugUCB) algorithm based on variance estimates for the thresholding bandit problem.
+The setting they consider is thus very similar to the setting in Locatelli et al.
 (2016).
-The algorithm itself, however, differs heavily from the APT algorithm.
-So is AugUCB for example not an anytime algorithm.
-Furthermore, arms can be deleted in every round if there are "far enough" away from the mean.
-Both the decision of which arm is played in a given round, and whether an arm is removed from the active set of arm, is based not only on the empirical mean estimate $\mu_i(t)$, but also on a term $s_i$ that is increasing linearly in the estimated standard deviation.
-While the APT algorithm plays the arm minimizing the quantity $B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t) = \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau| + \epsilon)$, AugUCB plays the arm minimizing the quantity $(\hat{\Delta}_i(t) - 2s_i)$, where $s_i$ is based on the variance estimate $\hat{v}_i$, and an exploration $\psi_m$ term linear in $T$, and an elimination parameter $\rho$ (compare Algorithm 1 in Mukherjee et al., 2017):
-
-\begin{equation*}
-s_i = \sqrt{\frac{\rho \psi_m (\hat{v}_i + 1) \log(T \epsilon_m)}{4n_i}}
+The main difference being that, while Locatelli et al.
+(2016) assume $R$-sub-Gaussian reward distributions, Mukherjee et al.
+(2017) assume rewards to be bounded in $[0,1]$, which makes the AugUCB applicable to less distributions.
+The AugUCB algorithm itself differs significantly from the APT algorithm.
+The two main ideas it employs are first, upper confidence bounds based on the Bernstein inequality and empirical variance estimates to compute the index based on which an arm is chosen at every round.
+Second, if an arm estimate is "far enough away" from the threshold as measured by the confidence bounds, it will be "eliminated", and no longer be pulled until the end of the budget.
+Both ideas are based not only on the empirical mean estimate $\mu_i(t)$, but also on a term $s_i$ that is increasing linearly in the estimated standard deviation.
+While the APT algorithm plays the arm minimizing the quantity $B_i^{APT}(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t) = \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau| + \epsilon)$, AugUCB plays the arm minimizing the quantity $\hat{\Delta}_i(t) - 2s_i$, where $s_i$ is based on the variance estimate $\hat{v}_i$, and an exploration $\psi_m$ term linear in $T$, as well as an elimination parameter $\rho$ (compare Algorithm 1 in Mukherjee et al., 2017):
+
+\begin{equation*}
+s_i = \sqrt{\frac{\rho \psi_m (\hat{v}_i + 1) \log(T \epsilon_m)}{4n_i}}.
 \end{equation*}
@@
 (2011) they use $H_{\sigma, 1}= \sum_{i=1}^K \frac{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}{\Delta_i^2}$.
-Furthermore, with $\stackrel{\sim}{\Delta}_i^2 = \frac{\Delta_i^2}{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}$, and with $\stackrel{\sim}{\Delta}_{(i)}$ being an increasing ordering of $\stackrel{\sim}{\Delta}_i$, the authors define a complexity corresponding to $H_{CSAR,2}$ in Chen et al.
+Furthermore, with $\stackrel{\sim}{\Delta}_i^2 = \frac{\Delta_i^2}{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}$, where $\stackrel{\sim}{\Delta}_{(i)}$ is an increasing ordering of $\stackrel{\sim}{\Delta}_i$, the authors define a complexity corresponding to $H_{CSAR,2}$ in Chen et al.
 (2014):
@@
 \begin{equation*}
-H_{\sigma,2} = \max_{i \ in \mathcal{A}} \frac{i}{\stackrel{\sim}{\Delta}_{(i)}^2}.
+H_{\sigma,2} = \max_{i \in \mathcal{A}} \frac{i}{\stackrel{\sim}{\Delta}_{(i)}^2}.
 \end{equation*}
@@
 While the latter complexity appears in the provided upper bound on the AugUCB algorithm's expected loss, it could be replaced by $H_{\sigma, 1}$ since $H_{\sigma, 2} \leq H_{\sigma,1}$.
-$H_{\sigma,1}$ is of course more directly comparable to the complexity $H$ that we are used to.
-
-While in the case of the APT algorithm the number of times a specific arm has been drawn $T_i$ measures how concentrated the estimated mean is around the true mean (and thus for large $T_i$ an arm is no longer drawn even if $\hat{\mu}$ is close to $\tau$); in the case of the AugUCB algorithm this is regulated by the combination of the variance estimate $\hat{v}_i$ and the exploration factor $\psi_m$, where they ensure that certain arms are no longer pulled when the algorithm is sufficiently confident in its knowledge about the true mean.
+$H_{\sigma,1}$ is more easily compared to the complexity $H$ defined in Locatelli et al.
+(2016).
+Essentially, every arm's complexity contribution is additionally scaled by a term increasing in the arm's variance (see also the graph comparing the complexity terms of APT, AugUCB, and EVT algorithms below).
+
+In the case of the APT algorithm the number of times a specific arm has been drawn $T_i$ measures how concentrated the estimated mean is around the true mean (and thus for large $T_i$ an arm is no longer drawn even if $\hat{\mu}$ is close to $\tau$).
+This exploration is regulated by the combination of the variance estimate $\hat{v}_i$ and the exploration factor $\psi_m$ in the case of the AugUCB algorithm.
+The terms ensure that certain arms are no longer pulled when the algorithm is sufficiently confident in the location of true mean.
+Indeed, the AugUCB algorithm goes a little further than the APT algorithm in that it eliminates arms (no longer considers them in sampling) when a separation condition is estimated to hold.
+The same separation condition of estimated mean away from the threshold is used in the authors' upper bound proof and is reminiscient of the separation condition used in Locatelli et al.'s (2016) upper bound proof.
+
 Therefore, when using a very similar favorable event in the proof of their upper bound, Mukherjee et al.
 (2017) have to bound the probability that an an arm is not removed from the active set after the a certain number of rounds -- even though the arm is above (respectively below) the threshold.
-If this probability is low, then this means that the algorithm is able to be certain about an arm's true mean *quickly* by employing variance estimates.
+If this probability is low, then the algorithm is able to be certain about an arm's true mean by employing variance estimates.
 In comparison, Locatelli et al (2016) used bounds on on how often arms are drawn ($T_i$) to give a bound on the probability of the favorable event.
@@
 (2017) have to assume that the distributions have rewards bounded in $[0,1]$ in order to derive the bound on the probability that an arm has not been eliminated correctly in round $T_i$.
-Thus, the distributions for which their upper bound holds are a subset of the sub-Gaussian distributions considered in Locatelli et al.
+Else it would not be possible to upper bound the $s_i$ term by $\Delta_i/4$ as Mukherjee et al.
+do in their proof.
+Thus, the distributions for which their upper bound holds are a subset of the $R$-sub-Gaussian distributions considered in Locatelli et al.
 (2016).
-However, it is not that the authors need to assume that the rewards are in $[0,1]$, but this was assumed so that the variance of the distribution is in $[0,1]$.
-Thus, the upper bound holds in particular for Gaussian distributions with variance $\sigma^2 \in [0,1]$.
+However, while the authors demand in their setting that the rewards are bounded in $[0,1]$, it seems that the upper bound only requires the arms' variances to be bounded in $[0,1]$ such that $\hat{v}_i \in [0,1]$.
+Thus, the upper bound should hold in particular for Gaussian distributions with variance $\sigma^2 \in [0,1]$.
+Consequently, the simulations by Mukherjee et al.
+are performed on Gaussian arms with variance smaller than one.
 
@@
 The first term is bounded by the Bernstein inequality.
-In the cumulative regret setting, there exists a similar decomposition that bounds the expected number of pulls of a suboptimal arm.
-Compare for example chapter 3.1 in "Thompson Sampling: An Asymptotically Optimal Finite Time Analysis" by Kaufmann, Korda and Munos (2012).
-There they decompose the expected number of draws of an suboptimal arm for an optimistic (UCB like) into the probability that the optimal arm's mean is underestimated, and the probability that the UCB of the suboptimal arm is still very large.
-To give bounds for UCB algorithms, it is then shown that these two terms show a certain convergence.
+In the cumulative regret setting, there exists a similar decomposition for algorithms based on upper confidence bounds.
+There, the expected number of pulls of a suboptimal arm is bounded.
+Compare for example chapter 3.1 in Kaufmann, Korda and Munos (2012), in which the authors decompose the expected number of draws of an suboptimal arm into the probability that the optimal arm's mean is underestimated, and the probability that the upper confidence bound of the suboptimal arm is still very large.
+To give bounds for UCB algorithms, certain convergence rates are shown for these two probabilities.
 Mukherjee et al.
-do similarly for their variance based algorithm in the thresholding setting.
-
-(since the AugUCB eliminates arms, it is interesting to see how it behaves when the underlying CTR changes over time...)
-
--> Happens for exponential distribution
+do similarly for their upper confidence algorithm in the thresholding setting.
 
@@
 
-```{r EVT_Index_Bernoulli, echo = FALSE}
+```{r EVT_Index_Bernoulli, echo = FALSE, message = FALSE, warning = FALSE, fig.align = "center", out.width='80%', fig.cap = "This graph displays the distance part of the index of the APT, SLR, and EVT algorithms.
+While EVT's distance is based on both the empirical mean and empirical variance, the empirical mean determines the variance in the case of Bernoullis.
+We see that the distance of both EVT and SLR has an asymmetric behavior."}
 bfun <- function(mu, tau) sqrt((mu*(1-mu))^2 + abs(tau-mu)) - mu*(1-mu)
-plot(seq(0,1,0.0001), bfun(0,seq(0,1,0.0001)), type = "l",
-     xlab = "Sample Mean", ylab = "Distance $D_i(t)$", main = "Variation over tau")
-for(i in 1:length(seq(0,1,by=0.1))) {
-  lines(seq(0,1,0.0001), bfun(seq(0,1,by=0.1)[i], seq(0,1,0.0001)), 
-        col = rainbow(length(seq(0,1,by=0.1)))[i])
-}
+KL_ber <- function(p,q) p*log(p/q) + (1-p)*log((1-p)/(1-q))
+KL_gauss <- function(p,q) 2*(p-q)^2
+
+evtdf <- data.frame(mu = seq(0.0000001,0.5,length.out = 10000),
+                    tau = rep(0.1, 10000)) %>%
+  mutate(APT = KL_gauss(mu, tau),
+         SLR = KL_ber(mu, tau),
+         EVT = bfun(mu, tau)) %>%
+  gather(key = Algorithm, value = Distance, -mu, -tau) %>%
+  mutate(tau = as.character(tau))
+
+ggplot(evtdf, aes(x = mu, y = Distance, 
+                  group = Algorithm, color = Algorithm,
+                  linetype = Algorithm)) +
+  geom_line() +
+  labs(title = "Comparison of Distance Measures by Algorithm",
+       subtitle = "For Bernoulli arms and a threshold at 0.1.",
+       x = "Empirical Mean Estimate") +
+  theme_bw() +
+  theme(legend.position = "bottom")
 ```
@@
 
-```{r Hevt_Hapt_Comparison, echo = FALSE, message = FALSE}
+```{r Hevt_Hapt_Comparison, echo = FALSE, message = FALSE, fig.align="center", out.width = '80%', fig.cap = "This graph compares the complexity terms used in the APT, AugUCB, and EVT algorithms respectively.
+We observe that as the mean of the arm's distribution is closer to the threshold, the complexity of the problem increases much less rapidly for the EVT algorithm.
+Thus, the EVT should be able to cope with arms close to the threshold better than the APT algorithm.
+The complexity displayed for the AugUCB is an upper bound on the complexity used in the upper bound of Mukherjee et al.
+(2017)."}
 hevt <- function(mu, tau) {
@@
 
-plot(seq(0.1,0.9,0.0001), 
-     hapt(seq(0.1,0.9,0.0001), 0.5), type = "l",
-     ylim = c(0,400), ylab = "Complexity", xlab = "Bernoulli Mean",
-     main = "APT vs EVT Complexity for tau = 0.5")
-lines(c(seq(0.1,0.9,0.0001)), 
-      hevt(c(seq(0.1,0.9,0.0001)), 0.5),
-      col = "blue")
-abline(v = 0.5, lty = 2)
+haugucb <- function(mu, tau) {
+  vars <- mu*(1-mu)
+  (sqrt(vars) + sqrt(vars + (16/3)*(abs(mu-tau))))/(abs(mu-tau)^2)
+}
+
+hcompdf <- data.frame(mu = seq(0.1,0.9,length.out = 10000),
+                      tau = rep(0.5, 10000)) %>%
+  mutate(APT = hapt(mu, tau),
+         EVT = hevt(mu, tau),
+         AugUCB = haugucb(mu, tau)) %>%
+  gather(key = Algorithm, value = Complexity, -mu, -tau)
+
+ggplot(hcompdf, aes(x = mu, y = Complexity, group = Algorithm,
+                    color = Algorithm, linetype = Algorithm)) +
+  geom_line() +
+  geom_vline(aes(xintercept = 0.5), linetype = 2) +
+  ylim(c(0,400)) +
+  theme_bw() +
+  theme(legend.position = "bottom") +
+  labs(x = "Mean", title = "Comparison of Complexity Terms",
+       subtitle = "Complexity of single Bernoulli arm for APT and EVT and a threshold at 0.5.")
 ```
@@
 
-# Experiments
-
-## Synthetic Data
+# Experiments \label{chap:Experiments}
+
+## Synthetic Data \label{sec:SyntheticData}
 
@@
 
-```{r simulation1_results, echo = FALSE}
+```{r simulation1_results, echo = FALSE, fig.align = "center", out.width = '80%'}
 library(ggplot2)
@@
   coord_cartesian(xlim = c(0,2000)) +
-  scale_color_discrete(name = "Algorithm")
+  scale_color_discrete(name = "Algorithm") + 
+  theme_bw() +
+  theme(legend.position = "bottom")
 
@@
 
-```{r simulation2_results, echo = FALSE}
+```{r simulation2_results, echo = FALSE, fig.align = "center", out.width = '80%'}
 library(ggplot2)
@@
        y = "log(Error)", x = "Round Index") +
-  scale_color_discrete(name = "Algorithm")
+  scale_color_discrete(name = "Algorithm") +
+  theme_bw() + 
+  theme(legend.position = "bottom")
 ```
 
-```{r, echo = FALSE, message = FALSE}
+```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%'}
 load(file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/loc6nt_ma.Rda")
@@
 rbind(loc6nt_APT_ma, loc6nt_LR_ma) %>%
-  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
+  rename(Arm = arm) %>%
+  ggplot(aes(x = index, y = mean, group = Arm, color = Arm)) +
   geom_line(size = 0.3) +
@@
 the iterations the arm was pulled in that round.") +
+  theme_bw() +
   theme(legend.position = "bottom")
-
+```
+
+```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%'}
 rbind(loc6nt_BUCB_c15_ma, loc6nt_BUCB_ma, loc6nt_BUCB_c5_ma) %>%
-  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
+  rename(Arm = arm) %>%
+  ggplot(aes(x = index, y = mean, group = Arm, color = Arm)) +
   geom_line(size = 0.3) +
@@
        subtitle = "5000 iterations; a value of 1000 means that in 20% of 
-       the iterations the arm was pulled in that round.")+
+       the iterations the arm was pulled in that round.") +
+  theme_bw() +
   theme(legend.position = "bottom")
@@
 
-```{r simulation3_results, echo = FALSE}
+```{r simulation3_results, echo = FALSE, fig.align = "center", out.width = '80%'}
 library(ggplot2)
@@
                  loc7nt_comp_BUCB_horizon_10000, loc7nt_comp_EVT))
-loc7nt_comp_res <- data.frame(index = index, names = alg_names, 
+loc7nt_comp_res <- data.frame(index = index, Algorithm = alg_names, 
                             results = alg_res)
 ggplot(loc7nt_comp_res, aes(x = index, y = results)) + 
-  geom_line(aes(group = names, color = names)) +
+  geom_line(aes(group = Algorithm, color = Algorithm)) +
   geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
-  geom_vline(aes(xintercept = 7000), linetype = 2) +
   labs(title = "Results of Synthetic Experiment 3", 
@@
                         tau,' = 0.01 and 11 arms. Dashed line at Error = 0.1.')), 
-       y = "log(Error)", x = "Round Index")
+       y = "log(Error)", x = "Round Index") +
+  theme_bw() +
+  theme(legend.position = "bottom")
 ```
@@
 
-```{r simulation4_results, echo = FALSE}
+```{r simulation4_results, echo = FALSE, fig.align = "center", out.width = '80%'}
 library(ggplot2)
@@
                  exp2_comp_AugUCB, exp2_comp_EVT))
-exp2_comp_res <- data.frame(index = index, names = alg_names, 
+exp2_comp_res <- data.frame(index = index, Algorithm = alg_names, 
                             results = alg_res)
 ggplot(exp2_comp_res, aes(x = index, y = results)) + 
-  geom_line(aes(group = names, color = names)) +
+  geom_line(aes(group = Algorithm, color = Algorithm)) +
   geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
@@
                         tau,' = 1 and 20 arms. Dashed line at Error = 0.1.')), 
-       y = "log(Error)", x = "Round Index")
+       y = "log(Error)", x = "Round Index") +
+  theme_bw() +
+  theme(legend.position = "bottom")
 ```
@@
 
-```{r simulation5_results, echo = FALSE}
+```{r simulation5_results, echo = FALSE, fig.align = "center", out.width = '80%'}
 library(ggplot2)
@@
                  pois2_comp_LR, pois2_comp_EVT))
-pois2_comp_res <- data.frame(index = index, names = alg_names, 
+pois2_comp_res <- data.frame(index = index, Algorithm = alg_names, 
                             results = alg_res)
 ggplot(pois2_comp_res, aes(x = index, y = results)) + 
-  geom_line(aes(group = names, color = names)) +
+  geom_line(aes(group = Algorithm, color = Algorithm)) +
   geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
-  labs(title = "Results of Experiment 4", 
+  labs(title = "Results of Experiment 5", 
        subtitle = expression(paste("Poisson distributed arms; ", 
                         tau,' = 0.4 and 20 arms. Dashed line at Error = 0.1.')), 
-       y = "log(Error)", x = "Round Index")
+       y = "log(Error)", x = "Round Index") +
+  theme_bw() +
+  theme(legend.position = "bottom")
 ```
@@
 
-```{r, echo = FALSE, message = FALSE}
+```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%'}
 library(zoo)
@@
   gather(arm, mean, -index) %>%
-  mutate(source = rep("Real", 86410))
+  mutate(source = rep("Real", 86410)) %>%
+  rename(Arm = arm)
 
@@
                         lapply(syn_data, FUN = zoo::rollapply, width = 24*60, mean)) %>%
-  gather(arm, mean, -index, -source)
+  gather(arm, mean, -index, -source) %>%
+  rename(Arm = arm)
 
 rbind(real_daily, syn_daily) %>%
-  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
+  ggplot(aes(x = index, y = mean, group = Arm, color = Arm)) +
   geom_line(size = 0.4) +
@@
        subtitle = "Horizontal bar indicates the threshold.", 
-       x = "Index", y = "One day moving average")
+       x = "Index", y = "One day moving average") +
+  theme_bw() +
+  theme(legend.position = "bottom")
 ```
@@
 
-```{r, echo = FALSE}
+```{r, echo = FALSE, fig.align = "center", out.width = '80%'}
 library(ggplot2)
@@
 alg_res <- log(c(amo3_comp_UNIFORM, amo3_comp_APT, amo3_comp_AugUCB, amo3_comp_LR, amo3_comp_BUCB, amo3_comp_EVT))
-loc3_comp_res <- data.frame(index = index, names = alg_names, 
+loc3_comp_res <- data.frame(index = index, Algorithm = alg_names, 
                             results = alg_res)
 ggplot(loc3_comp_res, aes(x = index, y = results)) + 
-  geom_line(aes(group = names, color = names)) +
+  geom_line(aes(group = Algorithm, color = Algorithm)) +
   geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
   labs(title = "Results of Real Data Experiment 1", 
-       subtitle = paste0("Sample Mean Complexity of "), 
-       y = "log(Error)", x = "Round Index")
+       subtitle = paste0("Dashed Line indicates Error = 0.1."), 
+       y = "log(Error)", x = "Round Index") +
+  theme_bw() +
+  theme(legend.position = "bottom")
 ```
@@
 real_daily <- data.frame(index = 1:8641,
-                                lapply(data_amo4_wide[1:10080,], FUN = rollapply, 
+                                lapply(data_amo4_wide[1:10080,], 
+                                       FUN = rollapply, 
                                        width = 24*60, mean)) %>%
@@
 rbind(real_daily, syn_daily) %>%
-  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
+  rename(Arm = arm) %>%
+  ggplot(aes(x = index, y = mean, group = Arm, color = Arm)) +
   geom_line(size = 0.4) +
@@
        x = "Index", y = "One day moving average") +
+  theme_bw() +
   theme(legend.position = "bottom")
@@
 rbind(amo4_cummean_real, amo4_cummean_syn) %>%
-  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
+  rename(Arm = arm) %>%
+  ggplot(aes(x = index, y = mean, group = Arm, color = Arm)) +
   geom_line(size = 0.4) +
@@
   ylim(c(0,0.3)) +
+  theme_bw() +
   theme(legend.position = "bottom")
@@
 rbind(amo4_cummean_real_12hrs, amo4_cummean_syn) %>%
-  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
+  rename(Arm = arm) %>%
+  ggplot(aes(x = index, y = mean, group = Arm, color = Arm)) +
   geom_line(size = 0.4) +
@@
 
-amo4_shuffled_cummean_real <- data_amo4_shuffled_wide[1:10080,] %>% tbl_df() %>%
+amo4_shuffled_cummean_real <- data_amo4_shuffled_wide[1:10080,] %>%
+  tbl_df() %>%
   mutate_each(funs(cummean)) %>%
@@
 rbind(amo4_shuffled_cummean_real, amo4_cummean_syn) %>%
-  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
+  rename(Arm = arm) %>%
+  ggplot(aes(x = index, y = mean, group = Arm, color = Arm)) +
   geom_line(size = 0.4) +
@@
   ylim(c(0,0.3)) +
+  theme_bw() +
   theme(legend.position = "bottom")
-
 ```
 
-```{r, echo = FALSE}
+```{r, echo = FALSE, fig.align = "center", out.width = '80%'}
 library(ggplot2)
@@
                                names = alg_names, results = alg_res)
-loc4total <- rbind(loc4_comp_res, loc4sim_comp_res)
+loc4total <- rbind(loc4_comp_res, loc4sim_comp_res) %>%
+  rename(Algorithm = names)
 
 ggplot(loc4total, aes(x = index, y = results, 
-                      group = names, color = names)) + 
+                      group = Algorithm, color = Algorithm)) + 
   geom_line() +
@@
   labs(title = "Results of Real Data Experiment 2", 
-       subtitle = paste0("Sample Mean Complexity of "), 
-       y = "log(Error)", x = "Round Index")
+       subtitle = paste0("Dashed line indicates Error = 0.1."), 
+       y = "log(Error)", x = "Round Index") +
+  theme_bw() +
+  theme(legend.position = "bottom")
 ```
@@
   labs(x = "Index", y = "10 Rounds Moving Average",
-       title = "Average Number of Pulls Allocated to Each Arm per Round")
+       title = "Average Number of Pulls Allocated to Each Arm per Round") +
+  theme_bw()
 ```
 
-```{r, echo = FALSE}
+```{r, echo = FALSE, fig.align = "center", out.width = '80%'}
 load(file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/amo4_arm_seq_ma.Rda")
@@
        title = "Share of Iterations Pulling an Arm at a Given Round") +
+  theme_bw() +
   theme(legend.position = "bottom") +
-  scale_color_discrete(name = "Arms")
+  scale_color_discrete(name = "Arm")
 ```
@@
 
-The authors thank Alexandra Carpentier, Andrea Locatelli, and Urun Dogan for many hours of valuable feedback and ideas. <3
+The author thanks Alexandra Carpentier, Andrea Locatelli, and Urun Dogan for many hours of valuable feedback and ideas. <3

### 2017-08-28 Thesis/Draft.tex
Edit AugUCB chapter

@@
 
-\newpage
-
 We now present the lower bound given in Locatelli et al. (2016) for the
@@
 
-\newpage
-
 \subsection{\texorpdfstring{Discussion
 \label{sec:DiscussionLocatelli}}{Discussion }}\label{discussion}
+
+\begin{itemize}
+\tightlist
+\item
+  Mention Optimality (Upper Bound matches lower bound)
+\item
+  Anytime
+\end{itemize}
 
@@
 its first argument, and thus can be relatively well approximated by
-Pinsker's inequality (SHOW IN GRAPH!):
+Pinsker's inequality:
 
@@
 \autoref{sec:LikelihoodRatioForExponentialFamily}, we first describe the
-variance-based approaches in \autoref{sec:VarianceBasedAlgorithms}.
-
-\includegraphics{Draft_files/figure-latex/unnamed-chunk-1-1.pdf}
-
-\includegraphics{Draft_files/figure-latex/unnamed-chunk-2-1.pdf}
-
-\newpage
+variance-based approaches in \autoref{chap:VarianceBasedAlgorithms}.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/KLApproximationComparison-1}
+
+}
+
+\caption{The approximation of the Bernoulli KL-divergence by the Gaussian KL-divergence works well if the second argument is equal to 0.5.
+Else we observe poor approximation in both value and symmetry.
+This becomes more obvious as the arguments move away from 0.5.}\label{fig:KLApproximationComparison}
+\end{figure}
 
@@
 
-\includegraphics{Draft_files/figure-latex/unnamed-chunk-3-1.pdf}
+\includegraphics{Draft_files/figure-latex/unnamed-chunk-1-1.pdf}
 
@@
 probability distributions on the arms \(\mathcal{A}\):
-\(\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}\).
-\marginpar{Give more intuition for what these probability distributions are}
-We are now ready to state the theorem.
+\(\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}\). We are
+now ready to state the theorem.
 
@@
 
-\section{Extensions to the Thresholding Bandit
-Problem}\label{extensions-to-the-thresholding-bandit-problem}
-
-\subsection{Introduction}\label{introduction-1}
-
-We have introduced the thresholding bandit problem in chapter 1. The APT
-algorith described in Locatelli et al. (2016) is able to match a lower
-bound (be more specific!) given in the same paper, and has several
-favorable characteristics such as its overall simplicity and it being an
-anytime algorithm. However, the bounds on the expected loss assume the
-arms' distributions to be \(R\)-sub-Gaussian. This is reflected in the
-algorithm's complexity measure
-\(H = \sum_{i=1}^K (\Delta_i^{\tau, \epsilon})^{-2}\), where
-\(\Delta_i^{\tau,\epsilon} = |\mu_i - \tau| + \epsilon\), which -- given
-the known threshold \(\tau \pm \epsilon\) -- only depends on the
-distribution's mean. This is appropriate for Gaussian arms with equal
-variances, but potentially inefficient for other kinds of distributions.
+\section{\texorpdfstring{Extensions to the Thresholding Bandit Problem
+\label{chap:Extensions}}{Extensions to the Thresholding Bandit Problem }}\label{extensions-to-the-thresholding-bandit-problem}
+
+\subsection{\texorpdfstring{Introduction
+\label{sec:ExtensionsIntroduction}}{Introduction }}\label{introduction-1}
+
+In \autoref{chap:ThresholdingBanditProblem} we have introduced the
+thresholding bandit problem as proposed in Locatelli et al. (2016)
+alongside the APT algorithm. We have seen that the upper bound on the
+APT algorithm matches the lower bound for the thresholding bandit
+problem given in Locatelli et al. (2016). The algorithm also exhibits
+favorable characteristics such that its upper bound holds at any
+stopping time, and that it does not require any parameter to be known
+upfront. However, we have seen that the index and the complexity term
+\(H\) employed by the APT algorithm are the most effective for
+\(R\)-sub-Gaussian distributions. Both are related to the KL-divergence
+between two Gaussian distributions of equal variance. Given that this
+sub-Gaussian approximation can be poor in certain cases, we motivated
+the use of information theoretic measures in an algorithm's index
+(compare \autoref{sec:DiscussionLocatelli}).
+
+Another goal can be to compare the distributions with the threshold
+based not only on the empirical mean -- as done by the APT algorithm. A
+logical extension is for example the empirical variance. After all arms
+do not necessarily have the same variance, even if they are
+sub-Gaussian. And given two arms for which we estimate the same mean, we
+would prefer to draw more samples from the arm with the larger variance.
 
@@
 
-In the case of Gaussians, the complexity \(H\) is nice also because it
-reflects the Kullback-Leibler divergence between two Gaussians. And
-since Bernoulli distributions are bounded on the interval \([0,1]\),
-they are consequently sub-Gaussian, meaning that their Kullback-Leibler
-divergence can be approximated by the Gaussian one. However, while
-Bernoullis are sub-Gaussian, the approximation of their divergence by
-the Gaussian divergence becomes less and less optimal as the parameter
-(and thus mean) goes to \(0\) or \(1\), as shown in chapter 1. And while
-online advertisements might not be an obvious use case for thresholding
-bandits, they are just one real life scenario dominated by Bernoulli
-distributions with very small parameters. Thus it is worthwile to adapt
-current solutions of the thresholding bandit problem to cases in which
-the Gaussian Kullback-Leibler divergence is no longer an appropriate
-approximation.
-
-Large motiviation for the idea of adjusting the complexity measure (and
-thus the algorithms) to distributions more generally based on the
-Kullback-Leibler divergence stems from the work discussed in chapter 2,
-complexity measures were defined for the pure exploration bandits in
-terms of the Kullback-Leibler divergence. Based on this, the authors
-were for example able to point our differences between Gaussian and
-Bernoulli bandits. We expect that results in a similar vain could be
-derived for thresholding bandits.
-
-To this end, in the following, we first present an extension of mean
-based algorithms to an algorithm that incorporates empirical variances
-as described in Mukherjee et al. (2017). Afterwards, we propose and
-discuss potential further improvements based on Kullback-Leibler
-divergence and Bayesian posterior distributions. Finally, we compare the
-performance of different algorithms based on simulations and real world
-data sets.
-
-\subsection{\texorpdfstring{Variance Based Algorithms for Thresholding
-Bandits
-\label{chap:VarianceBasedAlgorithms}}{Variance Based Algorithms for Thresholding Bandits }}\label{variance-based-algorithms-for-thresholding-bandits}
+For these reasons, in the following, we first present in
+\autoref{sec:VarianceBasedAlgorithms} two algorithms which incorporate
+empirical variances as described in Mukherjee et al. (2017) and Zhong et
+al. (2017). We then introduce a new algorithm based on the concept of
+likelihood ratios in \autoref{sec:LikelihoodRatioForExponentialFamily}.
+Finally, we compare the performance of different algorithms based on
+simulations and real world data sets in \autoref{chap:Experiments}.
+
+\subsection{\texorpdfstring{Variance Based Algorithms for the
+Thresholding Bandit
+\label{sec:VarianceBasedAlgorithms}}{Variance Based Algorithms for the Thresholding Bandit }}\label{variance-based-algorithms-for-the-thresholding-bandit}
 
@@
 
-Mukherjee et al. (2017) propose an algorithm based on variance estimates
-called Augmented-UCB (AugUCB). The setting in which the algorithm is
-proposed is very similar to the setting in Locatelli et al. (2016). The
-algorithm itself, however, differs heavily from the APT algorithm. So is
-AugUCB for example not an anytime algorithm. Furthermore, arms can be
-deleted in every round if there are ``far enough'' away from the mean.
-Both the decision of which arm is played in a given round, and whether
-an arm is removed from the active set of arm, is based not only on the
-empirical mean estimate \(\mu_i(t)\), but also on a term \(s_i\) that is
-increasing linearly in the estimated standard deviation. While the APT
-algorithm plays the arm minimizing the quantity
-\(B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t) = \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau| + \epsilon)\),
+Combining learnings from the APT and other algorithms, Mukherjee et al.
+(2017) propose the Augmented-UCB (AugUCB) algorithm based on variance
+estimates for the thresholding bandit problem. The setting they consider
+is thus very similar to the setting in Locatelli et al. (2016). The main
+difference being that, while Locatelli et al. (2016) assume
+\(R\)-sub-Gaussian reward distributions, Mukherjee et al. (2017) assume
+rewards to be bounded in \([0,1]\), which makes the AugUCB applicable to
+less distributions. The AugUCB algorithm itself differs significantly
+from the APT algorithm. The two main ideas it employs are first, upper
+confidence bounds based on the Bernstein inequality and empirical
+variance estimates to compute the index based on which an arm is chosen
+at every round. Second, if an arm estimate is ``far enough away'' from
+the threshold as measured by the confidence bounds, it will be
+``eliminated'', and no longer be pulled until the end of the budget.
+Both ideas are based not only on the empirical mean estimate
+\(\mu_i(t)\), but also on a term \(s_i\) that is increasing linearly in
+the estimated standard deviation. While the APT algorithm plays the arm
+minimizing the quantity
+\(B_i^{APT}(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t) = \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau| + \epsilon)\),
 AugUCB plays the arm minimizing the quantity
-\((\hat{\Delta}_i(t) - 2s_i)\), where \(s_i\) is based on the variance
+\(\hat{\Delta}_i(t) - 2s_i\), where \(s_i\) is based on the variance
 estimate \(\hat{v}_i\), and an exploration \(\psi_m\) term linear in
-\(T\), and an elimination parameter \(\rho\) (compare Algorithm 1 in
-Mukherjee et al., 2017):
+\(T\), as well as an elimination parameter \(\rho\) (compare Algorithm 1
+in Mukherjee et al., 2017):
 
 \begin{equation*}
-s_i = \sqrt{\frac{\rho \psi_m (\hat{v}_i + 1) \log(T \epsilon_m)}{4n_i}}
+s_i = \sqrt{\frac{\rho \psi_m (\hat{v}_i + 1) \log(T \epsilon_m)}{4n_i}}.
 \end{equation*}
@@
 \(\stackrel{\sim}{\Delta}_i^2 = \frac{\Delta_i^2}{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}\),
-and with \(\stackrel{\sim}{\Delta}_{(i)}\) being an increasing ordering
-of \(\stackrel{\sim}{\Delta}_i\), the authors define a complexity
+where \(\stackrel{\sim}{\Delta}_{(i)}\) is an increasing ordering of
+\(\stackrel{\sim}{\Delta}_i\), the authors define a complexity
 corresponding to \(H_{CSAR,2}\) in Chen et al. (2014):
@@
 \(H_{\sigma, 1}\) since \(H_{\sigma, 2} \leq H_{\sigma,1}\).
-\(H_{\sigma,1}\) is of course more directly comparable to the complexity
-\(H\) that we are used to.
-
-While in the case of the APT algorithm the number of times a specific
-arm has been drawn \(T_i\) measures how concentrated the estimated mean
-is around the true mean (and thus for large \(T_i\) an arm is no longer
-drawn even if \(\hat{\mu}\) is close to \(\tau\)); in the case of the
-AugUCB algorithm this is regulated by the combination of the variance
-estimate \(\hat{v}_i\) and the exploration factor \(\psi_m\), where they
-ensure that certain arms are no longer pulled when the algorithm is
-sufficiently confident in its knowledge about the true mean. Therefore,
-when using a very similar favorable event in the proof of their upper
-bound, Mukherjee et al. (2017) have to bound the probability that an an
-arm is not removed from the active set after the a certain number of
-rounds -- even though the arm is above (respectively below) the
-threshold. If this probability is low, then this means that the
-algorithm is able to be certain about an arm's true mean \emph{quickly}
-by employing variance estimates. In comparison, Locatelli et al (2016)
-used bounds on on how often arms are drawn (\(T_i\)) to give a bound on
-the probability of the favorable event. In order to derive the bound,
-Mukherjee et al. (2017) use the Bernstein inequality.
+\(H_{\sigma,1}\) is more easily compared to the complexity \(H\) defined
+in Locatelli et al. (2016). Essentially, every arm's complexity
+contribution is additionally scaled by a term increasing in the arm's
+variance (see also the graph comparing the complexity terms of APT,
+AugUCB, and EVT algorithms below).
+
+In the case of the APT algorithm the number of times a specific arm has
+been drawn \(T_i\) measures how concentrated the estimated mean is
+around the true mean (and thus for large \(T_i\) an arm is no longer
+drawn even if \(\hat{\mu}\) is close to \(\tau\)). This exploration is
+regulated by the combination of the variance estimate \(\hat{v}_i\) and
+the exploration factor \(\psi_m\) in the case of the AugUCB algorithm.
+The terms ensure that certain arms are no longer pulled when the
+algorithm is sufficiently confident in the location of true mean.
+Indeed, the AugUCB algorithm goes a little further than the APT
+algorithm in that it eliminates arms (no longer considers them in
+sampling) when a separation condition is estimated to hold. The same
+separation condition of estimated mean away from the threshold is used
+in the authors' upper bound proof and is reminiscient of the separation
+condition used in Locatelli et al.'s (2016) upper bound proof.
+
+Therefore, when using a very similar favorable event in the proof of
+their upper bound, Mukherjee et al. (2017) have to bound the probability
+that an an arm is not removed from the active set after the a certain
+number of rounds -- even though the arm is above (respectively below)
+the threshold. If this probability is low, then the algorithm is able to
+be certain about an arm's true mean by employing variance estimates. In
+comparison, Locatelli et al (2016) used bounds on on how often arms are
+drawn (\(T_i\)) to give a bound on the probability of the favorable
+event. In order to derive the bound, Mukherjee et al. (2017) use the
+Bernstein inequality.
 
@@
 bound on the probability that an arm has not been eliminated correctly
-in round \(T_i\). Thus, the distributions for which their upper bound
-holds are a subset of the sub-Gaussian distributions considered in
-Locatelli et al. (2016). However, it is not that the authors need to
-assume that the rewards are in \([0,1]\), but this was assumed so that
-the variance of the distribution is in \([0,1]\). Thus, the upper bound
-holds in particular for Gaussian distributions with variance
-\(\sigma^2 \in [0,1]\).
+in round \(T_i\). Else it would not be possible to upper bound the
+\(s_i\) term by \(\Delta_i/4\) as Mukherjee et al. do in their proof.
+Thus, the distributions for which their upper bound holds are a subset
+of the \(R\)-sub-Gaussian distributions considered in Locatelli et al.
+(2016). However, while the authors demand in their setting that the
+rewards are bounded in \([0,1]\), it seems that the upper bound only
+requires the arms' variances to be bounded in \([0,1]\) such that
+\(\hat{v}_i \in [0,1]\). Thus, the upper bound should hold in particular
+for Gaussian distributions with variance \(\sigma^2 \in [0,1]\).
+Consequently, the simulations by Mukherjee et al. are performed on
+Gaussian arms with variance smaller than one.
 
@@
 Bernstein inequality. In the cumulative regret setting, there exists a
-similar decomposition that bounds the expected number of pulls of a
-suboptimal arm. Compare for example chapter 3.1 in ``Thompson Sampling:
-An Asymptotically Optimal Finite Time Analysis'' by Kaufmann, Korda and
-Munos (2012). There they decompose the expected number of draws of an
-suboptimal arm for an optimistic (UCB like) into the probability that
-the optimal arm's mean is underestimated, and the probability that the
-UCB of the suboptimal arm is still very large. To give bounds for UCB
-algorithms, it is then shown that these two terms show a certain
-convergence. Mukherjee et al. do similarly for their variance based
+similar decomposition for algorithms based on upper confidence bounds.
+There, the expected number of pulls of a suboptimal arm is bounded.
+Compare for example chapter 3.1 in Kaufmann, Korda and Munos (2012), in
+which the authors decompose the expected number of draws of an
+suboptimal arm into the probability that the optimal arm's mean is
+underestimated, and the probability that the upper confidence bound of
+the suboptimal arm is still very large. To give bounds for UCB
+algorithms, certain convergence rates are shown for these two
+probabilities. Mukherjee et al. do similarly for their upper confidence
 algorithm in the thresholding setting.
-
-(since the AugUCB eliminates arms, it is interesting to see how it
-behaves when the underlying CTR changes over time\ldots{})
-
--\textgreater{} Happens for exponential distribution
 
@@
 
-\includegraphics{Draft_files/figure-latex/EVT_Index_Bernoulli-1.pdf}
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/EVT_Index_Bernoulli-1}
+
+}
+
+\caption{This graph displays the distance part of the index of the APT, SLR, and EVT algorithms.
+While EVT's distance is based on both the empirical mean and empirical variance, the empirical mean determines the variance in the case of Bernoullis.
+We see that the distance of both EVT and SLR has an asymmetric behavior.}\label{fig:EVT_Index_Bernoulli}
+\end{figure}
 
@@
 
-\includegraphics{Draft_files/figure-latex/Hevt_Hapt_Comparison-1.pdf}
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/Hevt_Hapt_Comparison-1}
+
+}
+
+\caption{This graph compares the complexity terms used in the APT, AugUCB, and EVT algorithms respectively.
+We observe that as the mean of the arm's distribution is closer to the threshold, the complexity of the problem increases much less rapidly for the EVT algorithm.
+Thus, the EVT should be able to cope with arms close to the threshold better than the APT algorithm.
+The complexity displayed for the AugUCB is an upper bound on the complexity used in the upper bound of Mukherjee et al.
+(2017).}\label{fig:Hevt_Hapt_Comparison}
+\end{figure}
 
@@
 
-\section{Experiments}\label{experiments}
-
-\subsection{Synthetic Data}\label{synthetic-data}
+\section{\texorpdfstring{Experiments
+\label{chap:Experiments}}{Experiments }}\label{experiments}
+
+\subsection{\texorpdfstring{Synthetic Data
+\label{sec:SyntheticData}}{Synthetic Data }}\label{synthetic-data}
 
@@
 
-\includegraphics{Draft_files/figure-latex/simulation1_results-1.pdf}
+\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation1_results-1} \end{center}
 
@@
 
-\includegraphics{Draft_files/figure-latex/simulation2_results-1.pdf}
-
-\includegraphics{Draft_files/figure-latex/unnamed-chunk-4-1.pdf}
-\includegraphics{Draft_files/figure-latex/unnamed-chunk-4-2.pdf}
+\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation2_results-1} \end{center}
+
+\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-2-1} \end{center}
+
+\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-3-1} \end{center}
 
@@
 
-\includegraphics{Draft_files/figure-latex/simulation3_results-1.pdf}
+\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation3_results-1} \end{center}
 
@@
 
-\includegraphics{Draft_files/figure-latex/simulation4_results-1.pdf}
+\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation4_results-1} \end{center}
 
@@
 
-\includegraphics{Draft_files/figure-latex/simulation5_results-1.pdf}
+\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation5_results-1} \end{center}
 
@@
 
-\includegraphics{Draft_files/figure-latex/unnamed-chunk-6-1.pdf}
+\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-5-1} \end{center}
 
@@
 
-\includegraphics{Draft_files/figure-latex/unnamed-chunk-7-1.pdf}
+\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-6-1} \end{center}
 
@@
 
-\includegraphics{Draft_files/figure-latex/unnamed-chunk-8-1.pdf}
-\includegraphics{Draft_files/figure-latex/unnamed-chunk-8-2.pdf}
-\includegraphics{Draft_files/figure-latex/unnamed-chunk-8-3.pdf}
-\includegraphics{Draft_files/figure-latex/unnamed-chunk-8-4.pdf}
-
-\includegraphics{Draft_files/figure-latex/unnamed-chunk-9-1.pdf}
+\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-7-1} \end{center}
+
+\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-7-2} \end{center}
+
+\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-7-3} \end{center}
+
+\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-7-4} \end{center}
+
+\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-8-1} \end{center}
 
@@
 
-\includegraphics{Draft_files/figure-latex/unnamed-chunk-10-1.pdf}
+\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-9-1} \end{center}
 
@@
 
-The authors thank Alexandra Carpentier, Andrea Locatelli, and Urun Dogan
+The author thanks Alexandra Carpentier, Andrea Locatelli, and Urun Dogan
 for many hours of valuable feedback and ideas. \textless{}3

### 2017-08-28 Thesis/Literature.Rmd
Rewritten Setup
add hoeffding bound
Edit AugUCB chapter

@@
 
+Bubeck, S. and Cesa-Bianchi, N. (2012). Regret analysis of stochastic and nonstochastic multi-armed bandit problems. Foundations and Trends in Machine Learning 5 1–122.
+
 Russo (2016)
@@
 Locatelli et al. (2016)
+
+Zhong et al. (2017)
+
+Bubeck, Sébastien, Cesa-Bianchi, Nicolo, and Lugosi, Gábor. Bandits with heavy tail. Information Theory, IEEE Transactions on, 59(11):7711-7717, 2013a.
+
+Mukherjee et al. (2017)
+
+Victor Gabillon, Mohammad Ghavamzadeh, Alessandro Lazaric, and Sébastien Bubeck. Multi-bandit best arm identification. In *Advances in Neural Information Processing Systems, pages 2222-2230, 2011.
+
+Shouyuan Chen, Tian Lin, Irwin King, Michael R Lyu, and Wei Chen. Combinatorial pure exploration of multi-armed bandits. In *Advances in Neural Information Processing Systems, pages 379-387, 2014.
+
+"Thompson Sampling: An Asymptotically Optimal Finite Time Analysis" by Kaufmann, Korda and Munos (2012)
+
+Lihong Li, Wei Chu, John Langford, Robert E.
+Schapire.
+A Contextual-Bandit Approach to Personalized News Article Recommendation.
+WWW 2010, April 26–30, 2010, Raleigh, North Carolina, USA.
+ACM 978-1-60558-799-8/10/04.

### 2017-08-28 Thesis/Draft.Rmd
Update SLR section

@@
    - \newcommand{\der}{\,\text{d}}
+   - \newcommand*{\Alignyesnumber}{\refstepcounter{equation}\tag{\theequation}}%
    #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
@@
 
-Another algorithm for the thresholding bandit problem is introduced in Zhong et al.
+Another algorithm for the thresholding bandit problem employing empirical variance estimates is introduced in Zhong et al.
 (2017).
-Indeed, they discuss several variations of their algorithm which extend their central idea to applications in which several samples need to be pulled in a parallel and asynchronous fashion.
-An easy example known from the multi-armed bandit literature (SOURCE????!!??!?!?!) is a website where different versions are served to customers and each version is an arm in the bandit setting.
+Indeed, the authors discuss several variations of their algorithm which extend their central idea to applications in which several samples need to be pulled in a parallel and asynchronous fashion.
+An standard example known from the multi-armed bandit literature (see for example Li et al.
+(2010)) is a website for which different versions are served to visitors and each version is an arm in the bandit setting.
 If the feedback that is observed by the algorithm is whether or not a user makes a purchase, then it is likely that a new user arrives before the feedback for the previous user has been observed.
@@
 But their algorithm can also be reduced to a simpler version that can be compared directly with the problem described in Locatelli et al.
-(2016) where we assume the problem of the feedback lag away.
-
-This simpler version is the anytime parameter-free version of their Empirical Variance Guided Algorithm (EVT$_{pf}$).
-The EVT$_{pf}$ algorithm is a smart extension of the APT algorithm to an approach that takes the empirical variance of the arms into account and deduces an upper bound through Bernstein bounds.
+(2016) where the feedback lag is assumed to be zero.
+
+This simpler version is the parameter-free version of their Empirical Variance Guided Algorithm (EVT$_{pf}$).
+The EVT$_{pf}$ algorithm is an extension of the APT algorithm that takes the empirical variance of the arms into account and deduces an upper bound through empirical Bernstein bounds in a proof following the model of the one described in Locatelli et al.
+(2016).
 
@@
 (2017) to describe the index used by the algorithms in a more general fashion.
-Write the index $B_i(t)$ of arm $i$ at round $t$ as previously as
-
-$$
-B_i(t) = S_i(t) D_i(t),
-$$
-
-where $D_i(t)$ is some measure of the distance between the mean $\mu_i$ or the distribution $\nu_i$ of the arm $i$ from the threshold $\tau$, while $S_i(t)$ is some confidence value.
+Write the index $B_i(t+1)$ of arm $i$ at round $t$ as previously as
+
+$$
+B_i(t+1) = S_i(t) D_i(t),
+$$
+
+where $D_i(t)$ is some measure of the distance between the mean $\mu_i$ or the distribution $\nu_i$ of arm $i$ from the threshold $\tau$, while $S_i(t)$ is some confidence value measuring how confident we can be in $.
 Thus, for the APT algorithm, if we let $\epsilon = 0$ as in Zhong et al.
@@
 $$
-D_i^{APT}(t) = \hat{\Delta}_i(t) = |\hat{\mu}_i(t) - \tau| \quad \land \quad S_i^{APT}(t) = \sqrt{T_i(t)}
+D_i^{APT}(t) = \hat{\Delta}_i(t) = |\hat{\mu}_i(t) - \tau| \quad \text{and} \quad S_i^{APT}(t) = \sqrt{T_i(t)}
 $$
@@
 $$
-D_i^{EVT}(t) = \hat{\Delta}_i(t) = |\hat{\mu}_i(t) - \tau| \quad \land \quad S_i^{EVT}(t) = \Big(\frac{1}{T_i(t) + \sqrt{\frac{1}{T_i(t)}}\hat{\sigma}_{i}(t)}\Big)^{-1}
-$$
-
-or equivalently as
-
-$$
-D_i^{EVT}(t) = \sqrt{\hat{\sigma}^2_{i}(t) + \hat{\Delta}_i(t)} - \hat{\sigma}_i(t) \quad \land \quad S_i^{EVT} = \sqrt{T_i(t)}
-$$
-
-We see that in both formulations either the distance term $D_i$ or the confidence term $S_i$ between the two algorithms is equivalent.
-While the empirical variance is a natural confidence measure -- and thus makes sense in the $S_i^{EVT}$ part in the first equation -- it also describes the shape of the distribution and thus is also a measure of how far the distribution (in contrast to just the mean) is away from the threshold, and thus can belong to $D_i^{EVT}$.
-We will focus on the latter formulation for the remaining paper.
-
-In comparison with the APT algorithm, the EVT$_{pf}$ algorithm adds the empirical variance into the index to measure how well we can expect the distribution (and the mean) to be seperated from the threshold; it serves as a crude measure of distance between threshold and distribution.
-We note that for a Bernoulli distributed random variable, $D_i^{EVT}$ is decreasing as the mean approaches the threshold.
+D_i^{EVT_{pf}}(t) = \sqrt{\hat{\sigma}^2_{i}(t) + \hat{\Delta}_i(t)} - \hat{\sigma}_i(t) \quad \text{and} \quad S_i^{EVT_{pf}} = \sqrt{T_i(t)}
+$$
+
+We see that both algorithms employ the same confidence term.
+The empirical variance describes the shape of the distribution and thus is a measure of how far the distribution (in contrast to just the mean) is away from the threshold.
+It consequently makes sense to have it appear in $D_i^{EVT}$.
+And in contrast to the APT algorithm, the EVT$_{pf}$ algorithm consequently takes more information about the arms into account than just their mean.
+As mentioned previously, this should especially be valuable whenever arms have indeed different variances.
+Similar (very roughly) to how the Kullback-Leibler divergence measures distances between distributions, the $D_i^{EVT}$ including the empirical variance serves as a crude measure of distance between threshold and distribution.
+We note that for a Bernoulli distributed random variable, $D_i^{EVT}$ is always decreasing as the mean approaches the threshold (compare the figure 2).
 Similar should hold in general for bounded variables as the variance and the mean are linked by the distance of the mean to the bound of the support (in contrast to, for example, a normal distributed random variable where a change in the mean does not correspond to a change in the variance).
 This is important as the bounds of the EVT$_{pf}$ algorithm only hold for random variables bounded in $[0,1]$.
+In contrast to the AugUCB, this restriction is not just on the variance of the arm but explicitly on the reward itself in the current version that builds on empirical Bernstein bounds as shown in Maurer and Pontil (2009).
 
@@
 (2016) in the proof of their lower bound.
-They define favorable events that hold with large probability, make sure the same separation condition holds for them given that each arm is pulled often enough.
+They define favorable events that hold with large probability, and ensure that the same separation condition as in Locatelli et al.
+holds for them given that each arm is pulled sufficiently often.
 Additionally to a favorable event that bounds the deviation between sample mean and population mean, they define a second event on which the sample standard deviation is close to the population standard deviation.
-This is bounded in large probability by a Bernstein inequality.
+This is bounded in large probability by an empirical Bernstein inequality (Maurer and Pontil, 2009).
 The union of the two events then serves as the favorable event in the remainder of their proof.
 
-Given a lower bound that is also adapted to the new complexity $H^{\text{EVT}_{pf}}$, the authors show that the EVT$_pf$ algorithm is optimal.
-Furthermore, they compare their algorithms in experiments against the APT algorithm.
+Given a lower bound adapted to the new complexity $H^{\text{EVT}_{pf}}$, the Zhong et al.
+(2017) show that the EVT$_pf$ algorithm is optimal in that its upper bound matches the lower bound.
+Furthermore, they compare their algorithm in experiments against the APT algorithm.
 The experiments use data generated from uniform distributions.
@@
 
-When comparing the two complexities for example for Bernoulli random variables against some fixed threshold, we see that the smaller complexity of the EVT$_{pf}$ algorithm implies in particular that EVT$_{pf}$ could be able to cope with distributions of parameter $\mu$ close to $\tau$ much better than APT.
-
-```{r Hevt_Hapt_Comparison, echo = FALSE, message = FALSE, fig.align="center", out.width = '80%', fig.cap = "This graph compares the complexity terms used in the APT, AugUCB, and EVT algorithms respectively.
-We observe that as the mean of the arm's distribution is closer to the threshold, the complexity of the problem increases much less rapidly for the EVT algorithm.
+When comparing the two complexities for example for Bernoulli random variables against some fixed threshold, we see that the smaller complexity of the EVT$_{pf}$ algorithm implies in particular that EVT$_{pf}$ could be able to cope with distributions of parameter $\mu$ close to $\tau$ much better than APT (compare figure 3).
+
+```{r Hevt_Hapt_Comparison, echo = FALSE, message = FALSE, fig.align="center", out.width = '70%', fig.cap = "Comparing the complexity terms used in the APT, AugUCB, and EVT algorithms, we observe that the problem complexity of the EVT algorithm increases much less rapidly than for the other algorithms.
 Thus, the EVT should be able to cope with arms close to the threshold better than the APT algorithm.
@@
 
-## Likelihood Ratio for Exponential Family Distributions \label{sec:LikelihoodRatioForExponentialFamily}
-
-We now present an approach that builds on the idea of the likelihood ratio statistic for hypothesis tests.
-We first present the general idea of likelihood ratio based tests, and then introduce our new algorithm for the thresholding bandit problem.
-
-### Likelihood Ratio-based Hypothesis Tests
+## Likelihood Ratio for Sequential Sampling \label{sec:LikelihoodRatioForExponentialFamily}
+
+We now present a new sequential sampling algorithm for the fixed budget thresholding bandit problem that builds on the idea of the likelihood ratio statistic for hypothesis tests.
+We first shortly describe the general idea of likelihood ratio based tests, to then introduce this new algorithm for the thresholding bandit problem, which we call Simple Likelihood Ratio (SLR) algorithm.
+
+### Likelihood Ratio-based Hypothesis Tests \label{sec:LRTests}
 
@@
 Let $q(x;\theta)$ be the density function corresponding to the distribution.
-In a standard hypothesis test, we test whether an alternative parameterization is more likely than the parameterization given by the null hypothesis.
+We would like to test whether an alternative parameterization is more likely than the parameterization given by the null hypothesis.
 That is, we test
@@
 
-In order to assess whether the $H_0$ hypothesis can be rejected, one computes the likelihood $L(x|\theta)$ of the observed sample under both parameterizations: $L_{H_0} = L(x|\theta = \theta_{H_0}) = \prod_{i=1}^T q(x_i|\theta_{H_0})$ and $L_{H_1} = L(x|\theta = \theta_{H_1}) = \prod_{i=1}^T q(x_i|\theta_{H_1})$.
+In order to assess whether the $H_0$ hypothesis can be rejected, one computes the likelihood $L(x|\theta)$ of the observed sample under both parameterizations: $L_{H_0} = L(x|\theta = \theta_{H_0}) = \prod_{i=1}^T q(x_i|\theta_{H_0})$ and $L_{H_1} = L(x|\theta = \theta_{H_1}) = \prod_{s=1}^T q(x_s|\theta_{H_1})$.
 The likelihood ratio test statistic is then given as
@@
 $$
-LR(\theta_{H_0}|| \theta_{H_1}) = \frac{L_{H_0}}{L_{H_1}} = \prod_{i=1}^T\frac{q(x_i|\theta_{H_0})}{ q(x_i|\theta_{H_1})}.
-$$
-The intuition behind the test of course being that, if the true parameterization is $H_1$ and not $H_0$, then the likelihood $L_{H_1}$ should be larger than $L_{H_0}$.
+LR_T(\theta_{H_0}|| \theta_{H_1}) = \frac{L_{H_0}}{L_{H_1}} = \prod_{s=1}^T\frac{q(x_s|\theta_{H_0})}{ q(x_s|\theta_{H_1})}.
+$$
+
+and is used in the optimal test of two hypotheses as shown by the Neyman-Pearson lemma (see chapter 11, Theorem 11.7.1 in Cover and Thomas, 2006).
+
+The intuition behind the test of course being that, if the true parameterization is $H_1$ and not $H_0$, then the likelihood $L_{T,H_1}$ should be larger than $L_{T,H_0}$.
 A small enough likelihood ratio would thus lead us to a rejection of the null hypothesis, while a large likelihood ratio is evidence in favor of the null hypothesis.
 
-By considering $lr = -2\log(LR(\theta_{H_0}|| \theta_{H_1}))$, one has a statistic that is $\chi^2$ distributed with degrees of freedom that depend on the null and alternative hypothesis.
-Assessing whether the null hypothesis can be rejected with large confidence thus becomes straightforward.
-
-### Likelihood Ratio-based Thresholding Bandit
-
-The simple concept of the likelihood-ratio test serves as foundation for a new sampling strategy that can be applied to the thresholding bandit problem.
-In contrast to the cumulative regret problem, or even the best arm identification problem, we have some sort of null hypothesis for the distributions in the thresholding bandit problem.
-In case of no information and no observed samples, the null hypothesis might simply be that all distributions have a mean that equals the threshold.
-By observing samples, we then want to test whether the mean of the distributions is different from the threshold $\tau$ in either direction.
-Once we are sure that there is a difference, we do not want to continue to test.
-Instead, we would like to focus our sampling effort on a different arm where we are not as sure.
-The likelihood ratio quantifies how "significant"" of a difference there is between the threshold $\tau$ and the current sample mean $\hat{\mu}_i(t)$ of an arm.
-Given that we plug in the sample mean, that is, the maximum likelihood estimator for the true mean for many distributions, the likelihood ratio will be smaller than 1 and decrease in sample size even if the threshold and sample mean are constant.
-
-Due to these characteristics, the likelihood ratio can serve as a natural index for sampling strategies. Thus write as index
-
-$$
-B_i(t) = LR(\tau|| \hat{\mu}_i(t)) = \prod_{i=1}^T\frac{q(x_i|\tau)}{ q(x_i|\hat{\mu}_i(t))}
-$$
-
-and pull at round $t$ the arm $i^* = \arg \max_i B_i(t)$.
-As we described in the previous paragraph, we have $B_i(t) \leq 1$, $t \uparrow \rightarrow B_i(t) \downarrow$, and $|\hat{\mu}_i(t) - \tau| \uparrow \rightarrow B_i(t) \downarrow$.
-Consequently, by choosing the arm that maximizes $B_i(t)$, we choose an arm for which we either have not collected many samples, or where the sample mean is close to the threshold $\tau$.
-In this sense, a strategy based on the likelihood ratio is of course very reminiscient of the index employed by the APT algorithm.
+Furthermore, the likelihood ratio is inherently linked to information theoretic quantities and divergence measures.
+Assuming that $Q$ is a discrete distribution with support $\chi$, one can write the negative log-likelihood ratio as (compare Cover and Thomas, 2006)
+
+\begin{align*}
+-\log(LR_T(\theta_{H_0}|| \theta_{H_1}) & = & \sum_{i=1}^T \log(\frac{q(x_s|\theta_{H_0})}{ q(x_s|\theta_{H_1})}) \\
+& = & \sum_{a \in \chi} T q(a|\hat{\theta}) \log(\frac{q(a|\theta_{H_0})}{ q(a|\theta_{H_1})}) \\
+& = & \sum_{a \in \chi} T q(a|\hat{\theta}) \log(\frac{q(a|\theta_{H_0})}{ q(a|\theta_{H_1})}\frac{q(a|\hat{\theta})}{ q(a|\hat{\theta})}) \\
+& = & T \KL(q(\hat{\theta})||q(\theta_{H_0})) - T \KL(q(\hat{\theta})||q(\theta_{H_1})),
+\end{align*}
+
+where $\hat{\theta}$ is the maximum likelihood estimate of the parameter $\theta$ given the sample $x$.
+If we hold the $H_0$ hypothesis fixed and set $\theta_{H_1} = \hat{\theta}$ as often done in praxis, then with $\KL(Q(\hat{\theta})||Q(\hat{\theta})) = 0$:
+
+$$
+-\log(LR_T(\theta_{H_0}|| \theta_{H_1})) = -\log(LR_T(\theta_{H_0}|| \hat{\theta})) = \KL(Q(\hat{\theta}||Q(\theta_{H_0}))
+$$
+
+Furthermore, we have for any distributions $Q_{H_0}$ and $Q_{H_1}$ for a sample $x$ sampled from the $H_0$ distribution, that
+
+$$
+\frac{1}{n} \log(LR_T(\theta_{H_0}||\theta_{H_1})) \rightarrow \KL(Q(\theta_{H_0})||Q(\theta_{H_1})) \quad \text{in probability},
+$$
+
+by the law of large numbers (or asymptotic equipartition property) for the Kullback-Leibler divergence as in Theorem 11.8.1 in Cover and Thomas (2006).
+Lastly, based on the characteristics shown before, for frequentist tests the Kullback-Leibler divergence between $Q(\theta_{H_0})$ and $Q(\theta_{H_1})$ gives the best possible exponent for the error of the second type given a fixed error of the first type.
+This is the result of the Chernoff-Stein Lemma (Theorem 11.8.3, Cover and Thomas, 2006), which is reminiscient of the complexity $\kappa_B$ derived by Kaufmann et al.
+(2016) and as described in \autoref{chap:KullbackLeiblerPureExploration}:
+
+\begin{theorem}[Chernoff-Stein Lemma] \label{theorem:ChernoffStein}
+Let $X_1, X_2, ..., X_n$ be i.i.d.
+distributed according to $Q$.
+Consider the hypothesis test between two alternatives, $Q=P_1$ and $Q=P_2$, where $\KL(P_1||P_2) < \infty$.
+Let $A_n \subseteq \chi^n$ be an acceptance region for hypothesis $H_1$.
+Let the probabilities of error be $\alpha_n = P_1^n(A_n^C)$, and $\beta_n = P_2^n(A_n)$, and for $0< \epsilon <1/2$, define $\beta_n^{\epsilon} = \min_{A_n \subseteq \chi^n, \alpha_n < \epsilon} \beta_n$.
+Then
+
+$$
+\text{lim}_{n\rightarrow \infty} \frac{1}{n} \log \beta_n^{\epsilon} = - \KL(P_1||P_2)
+$$
+\end{theorem}
+
+### Likelihood Ratio as Index in Sequential Sampling
+
+We now employ the concept of the likelihood-ratio test for a new sequential sampling strategy for the thresholding bandit problem.
+In contrast to the cumulative regret problem or the best arm identification problem, the thresholding bandit problem offers a natural $H_0$ hypothesis for the arms' distributions: the threshold $\tau$.
+Given that we want to classify the arms against the threshold, and given that $\tau$ is known and fixed, we can set a null hypothesis that is a function of $\tau$.
+In the simplest case, the distributions are parameterized by their mean $\theta_i = \mu_i$, and we set $\theta_{i,H_0} = \tau$ for all arms.
+The likelihood ratio then quantifies how "significant" of a difference there is between the threshold $\tau$ and the current sample mean $\hat{\mu}_i(t)$ of an arm, assuming distributions for which the maximum likelihood estimate of the mean is given by the empirical mean.
+In these cases, the likelihood ratio will be smaller than 1 and decrease in sample size even if the threshold and sample mean are constant.
+
+Due to these characteristics, the likelihood ratio can serve as a natural index for sampling strategies.
+Consider the setting described in \autoref{sec:Setup} and \autoref{sec:TheAPTAlgorithm} though without assuming $R$-sub-Gaussian distributions.
+Consider $B_i^{APT}$ and compare it to
+
+$$
+B_i^{LR}(t+1) = LR(\tau|| \hat{\mu}_i(t)) = \prod_{i=1}^T\frac{q(x_i|\tau)}{ q(x_i|\hat{\mu}_i(t))}.
+$$
+
+We have $B_i(t) \leq 1$, $t \uparrow \rightarrow B_i(t) \downarrow$, and $|\hat{\mu}_i(t) - \tau| \uparrow \rightarrow B_i(t) \downarrow$.
+Consequently, by choosing the arm that maximizes $B_i(t)$, we choose an arm for which we either have not collected many samples, or for which the sample mean is close to the threshold $\tau$.
+In this sense, a strategy based on the likelihood ratio is reminiscient of the index employed by the APT algorithm.
 Indeed, assuming the samples are normally distributed with the same variance for the distribution $\nu_i$ under both $H_0$ and $H_1$, then $-\log(LR(\tau||\hat{\mu}_i(t)))$ equals the index in APT.
@@
 Given that the APT index and the likelihood-ratio based index are only equivalent for normally distributed random variables with fixed standard deviation, the new strategy promises efficiency improvements whenever the true distribution is known and different from the normal distribution.
-The most important example are Bernoulli arms with small means as discussed before.
-Here, it is also easy to assume that the true distribution is known upfront.
-Similarly, the likelihood ratio statistic can be used for other univariate distributions of the exponential family.
-But we also propose a version for the Normal distribution with unknown mean.
-
-We now focus on the case where the distributions $\nu_{\theta_1}, ..., \nu_{\theta_K}$ are all the same canonical exponential family of distributions with scalar parameter $\theta_i \in \Theta$.
+The most important example are Bernoulli arms with small means as motivated.
+While the likelihood ratio can in theory be used for any distributions, and arms could even have different classes of distributions, the class of distribution has to be known upfront for every arm.
+Given the role of the threshold $\tau$ and the goal of classification of the mean against $\tau$, the likelihood ratio strategy is arguably most naturally employed on distributions parameterized by their mean.
+In the following descriptions, we thus focus on univariate distributions of the exponential family.
+Additionally, we also propose a version for the Normal distribution with unknown mean.
+Before we describe the algorithm, we show that the likelihood ratio has a very convenient form for this family of distributions.
+
+### Likelihood Ratio for Univariate Exponential Family of Distributions
+
+We now focus on a thresholding bandit problem where the arms are distributed according to $\nu_{\theta_1}, ..., \nu_{\theta_K}$, which are all from the same canonical exponential family of distributions with scalar parameter $\theta_i \in \Theta$.
 The probability density function of the absolutely continuous distribution $\nu_{\theta_i}$ with regard to a dominating measure $\rho$ on $\mathbb{R}$ is given by $q(x|\theta) = h(x) \exp(T(x)\theta - b(\theta))$.
@@
 Given that $b'(x)$ is strictly convex, we have a one-to-one relation between $b'(\theta)$ and $\mathbb{E}(\nu_{\theta})$ through the continuous inverse $b'^{-1}(\theta)$.
-Consequently, one can just as well parameterize the distribution its mean $\mu = \mathbb{\nu_{\theta}}$ and write $\nu_{b'^{-1}(\mu)}$ with the probability density function
+Consequently, one can just as well parameterize the distribution its mean $\mu = \mathbb{\nu_{\theta}}$ and write $\nu_{b'^{-1}(\mu)}$ with the probability density function (compare Cappé et al., 2013)
 
@@
 
-As we will see now, this statistic is easily derived for many specific distributions.
-
-#### Example 1: Bernoulli Distribution
+As we will see now, this statistic takes a very convenient closed form for many common distributions.
+
+**Example 1: Bernoulli Distribution**
 
@@
 
-$$
--\log(LR(\mu_0||\mu_1)) = n(\log\Big(\frac{1-\mu_0}{1-\mu_1}\Big)) - \Big(\log(\frac{\mu_0}{1-\mu_0}) - \log(\frac{\mu_1}{1-\mu_1})\Big)\sum_{i=1}^{n}x_i = n \Big( (1-\hat{\mu})\log\Big(\frac{1-\mu_1}{1-\mu_0}\Big) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}) \Big)
-$$
-
-We observe that, if we let $\mu_0 = \tau$ and $\mu_1 = \hat{\mu}$, then
+\begin{align*}
+-\log(LR(\mu_0||\mu_1)) & = & n(\log\Big(\frac{1-\mu_0}{1-\mu_1}\Big)) - \Big(\log(\frac{\mu_0}{1-\mu_0}) - \log(\frac{\mu_1}{1-\mu_1})\Big)\sum_{i=1}^{n}x_i \\
+& = & n \Big( (1-\hat{\mu})\log\Big(\frac{1-\mu_1}{1-\mu_0}\Big) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}) \Big)
+\end{align*}
+
+We observe that, if we let $\mu_0 = \tau$ and $\mu_1 = \hat{\mu}$ (compare \autoref{sec:LRTests}), then
 
@@
 
-#### Example 2: Poisson Distribution
+**Example 2: Poisson Distribution**
 
@@
 
-We observe that, if we let $\mu_0 = \tau$ and $\mu_1 = \hat{\mu}$, then
+We observe that, if we let $\mu_0 = \tau$ and $\mu_1 = \hat{\mu}$ (compare \autoref{sec:LRTests}), then
 
@@
 
-#### Example 3: Normal distributions with known variance $\sigma^2$
+**Example 3: Normal distributions with known variance $\sigma^2$**
 
@@
 
-And again, if we let $\mu_1 = \hat{\mu}$ and $\mu_0 = \tau$, then
+And again, even though the distribution is continuous (compare \autoref{sec:LRTests}), if we let $\mu_1 = \hat{\mu}$ and $\mu_0 = \tau$, then
 
@@
 
-#### Example 4: Gamma distributions with known shape parameter $\alpha$
+**Example 4: Gamma distributions with known shape parameter $\alpha$**
 
@@
 $$
-And again, if we let $\mu_1 = \hat{\mu}$ and $\mu_0 = \tau$, then
+
+And again, even though the distribution is continuous (compare \autoref{sec:LRTests}), if we let $\mu_1 = \hat{\mu}$ and $\mu_0 = \tau$, then
 
@@
 
-Given these results for the exponential family of distributions, we can now define the SLR (Simple Likelihood Ratio) algorithm.
-
-### 1D-SLR Algorithm for One-Dimensional Exponential Family of Distributions
-
-Very similar to the APT algorithm, the SLR algorithm receives as input the definition of the problem $(\tau, \epsilon)$ (compare Locatelli et al., 2016).
-Additionally, the algorithm receives as input the name of the distribution that the arms follow, as well as potential additional parameters ($\sigma_1, ..., \sigma_K$ for Normal distributions, $\alpha_1, ..., \alpha_K$ for Gamma distributions).
-We assume that each arm follows the same kind of distribution, with potentially different parameters $\theta_1, ..., \theta_K$.
-The algorithm pulls each arm once.
+Given these results for the exponential family of distributions, we can now define the Simple Likelihood Ratio algorithm.
+
+## 1D-Simple Likelihood Ratio Algorithm \label{sec:1DSLR}
+
+Consider again the setting in \autoref{sec:Setup} though without the assumption of $R$-sub-Gaussian distributions.
+Instead, assume that the class of distributions that the arms $i \in \mathbb{A}$ follow is known upfront.
+For the 1D-SLR algorithm, we restrict the potential classes to the univariate exponential family of distributions and write the class generally as $\nu(\mu, \theta)$.
+Here, $\theta$ describes additional parameters known upfront, as for example $\sigma_1, ..., \sigma_K$ for Normal distributions, or $\alpha_1, ..., \alpha_K$ for Gamma distributions.
+Additionally to $\nu(\mu)$, the 1D-SLR algorithm receives as input the definition of the problem $(\tau, \epsilon)$ (compare Locatelli et al., 2016).
+As initialization, the algorithm pulls each arm once.
 At time $t>K$, the algorithm updates the number of pulls for arm $i$ at time $t$, $T_i(t)$, for each arm, as well as the empirical mean $\hat{\mu}_i(t)$ of arm $i$ after $T_i(t)$ pulls.
 The empirical mean is calculated for each arm $k\in \{1,...,K\}$ as $\hat{\mu}_i(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)} x_{i,s}$, with $T_i(t) = \sum_{s=1}^{t}\mathbb{I}(I_s = i)$.
+It serves as maximum likelihood estimate of the arm's mean.
 As in Locatelli et al.
@@
 
-$$
-B_i^{SLR}(t+1) = \mathbb{I}(\hat{\mu}\geq \tau)(-\log\big(LR(\tau-\epsilon||\hat{\mu}_i(t))\big) + \mathbb{I}(\hat{\mu}< \tau)(-\log\big(LR(\tau+\epsilon||\hat{\mu}_i(t))\big) = T_i(t) \Big( \mathbb{I}(\hat{\mu}\geq \tau)\cdot KL(\nu_{b'^{-1}(\hat{\mu}(t))}||\nu_{b'^{-1}(\tau-\epsilon)}) + \mathbb{I}(\hat{\mu} < \tau)\cdot KL(\nu_{b'^{-1}(\hat{\mu}(t))}||\nu_{b'^{-1}(\tau+\epsilon)}) \Big).
-$$
+\begin{align*}
+B_i^{SLR}(t+1) & = \mathbb{I}(\hat{\mu}\geq \tau)(-\log\big(LR(\tau-\epsilon||\hat{\mu}_i(t))\big) \\
+& \quad +\: \mathbb{I}(\hat{\mu} <\tau)(-\log\big(LR(\tau+\epsilon||\hat{\mu}_i(t))\big) \\
+& = T_i(t) \Big( \mathbb{I}(\hat{\mu}\geq \tau)\cdot KL(\nu_{b'^{-1}(\hat{\mu}(t))}||\nu_{b'^{-1}(\tau-\epsilon)}) \\
+& \quad +\: \mathbb{I}(\hat{\mu} < \tau)\cdot KL(\nu_{b'^{-1}(\hat{\mu}(t))}||\nu_{b'^{-1}(\tau+\epsilon)}) \Big) \Alignyesnumber\label{eqn:SLRIndex}.
+\end{align*}
 
 The next arm to be pulled is the minimizer of the index $B_i^{SLR}(t+1)$, $I_{t+1} = \arg \min_{i\leq K} B_i(t+1)$.
-At the end of the horizon $T$, the algorithm outputs the set of arms $\hat{S}_\tau = \{k: \hat{\mu}_k(T) \geq \tau\}$.
+At the end of the horizon $T$, the algorithm outputs the set of arms $\hat{S}_\tau = \{i \in \mathbb{A},  \hat{\mu}_i(T) \geq \tau\}$.
 
@@
 \begin{algorithm}
-\SetKwData{Left}{left}\SetKwData{This}{this}\SetKwData{Up}{up}
-\SetKwFunction{Union}{Union}\SetKwFunction{FindCompress}{FindCompress}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
-\Input{$\tau$, $\epsilon$}
-\Output{$\hat{S}_{\tau} = \{k: \hat{\mu}_k(T) \geq \tau\}$}
+\Input{$\tau$, $\epsilon$, class of distributions $\nu(\mu, \theta)$, $\theta_i \: \forall i \in \mathbb{A}$}
+\Output{$\hat{S}_\tau = \{i \in \mathbb{A},  \hat{\mu}_i(T) \geq \tau\}$}
 \BlankLine
@@
 \For{$t = K+1$ \KwTo $T$}{
-  \emph{Pull arm $I_t = \arg \min_{k\leq K} B_k^{SLR}(t) = T_k(t) \KL(\hat{\mu}_k(t) || \tau)$}\;
+  \emph{Pull arm $I_t = \arg \min_{i\leq K} B_i^{SLR}(t)$ as in \autoref{eqn:SLRIndex}}\;
   \emph{Observe reward $X \sim \nu_{I_t}$}\;
@@
 
-### 2D-SLR Algorithm for Normal Distributions with Unknown Mean and Unknown Variance
+## 2D-SLR Algorithm for Normal Distributions
 
@@
 
-Now, at each round $t$, the algorithm computes $T_i(t)$ and $\hat{\mu}_i(t)$ as before, but additionally the empirical variances $\sigma_{\tau,i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\tau)^2$ and $\hat{\sigma}_{i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\hat{\mu})^2$.
+Now, at each round $t$, the algorithm computes $T_i(t)$ and $\hat{\mu}_i(t)$ as before, and additionally the empirical variances $\sigma_{\tau,i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\tau)^2$ and $\hat{\sigma}_{i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\hat{\mu})^2$.
 The index is then given by
 
-$$
-B_i^{2DSLR}(t+1) = -\log(LR(\tau, \sigma_{\tau,i}^2(t)||\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t))) = T_i(t) \log\Big(\frac{\sigma_{\tau,i}^2(t)}{\hat{\sigma}_i^2(t)}\Big) = T_i(t) KL(\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t)||\tau, \sigma_{\tau,i}^2(t))
-$$
-
-(SHOW THAT THE NOTATION CAN BE ABUSED AND THE KL WRITTEN THIS WAY BECAUSE UNIQUELY DEFINED BY MEAN AND VARIANCE)
-
-Then, as for the univariate case, the next arm to be pulled is the minimizer of the index $B_i^{2DSLR}(t+1)$, $I_{t+1} = \arg \min_{i\leq K} B_i(t+1)$.
-At the end of the horizon $T$, the algorithm outputs the set of arms $\hat{S}_\tau = \{k: \hat{\mu}_k(T) \geq \tau\}$.
+\begin{align*}
+B_i^{SLR_{2D}}(t+1) & = -\log\big(LR(\tau, \sigma_{\tau,i}^2(t)||\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t))\big) \\
+& = T_i(t) \log\Big(\frac{\sigma_{\tau,i}^2(t)}{\hat{\sigma}_i^2(t)}\Big) \\
+& = T_i(t) \KL\big(N(\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t))||N(\tau, \sigma_{\tau,i}^2(t))\big)
+\end{align*}
+
+Then, as for the univariate case, the next arm to be pulled is the minimizer of the index $B_i^{2DSLR}(t+1)$, $I_{t+1} = \arg \min_{i \leq K} B_i(t+1)$.
+At the end of the horizon $T$, the algorithm outputs the set of arms $\hat{S}_\tau = \{i \in \mathbb{A}, \hat{\mu}_i(T) \geq \tau\}$.
 

### 2017-08-28 Thesis/Draft.tex
Update SLR section

@@
 \newcommand{\der}{\,\text{d}}
+\newcommand*{\Alignyesnumber}{\refstepcounter{equation}\tag{\theequation}}%
 
@@
 
-Another algorithm for the thresholding bandit problem is introduced in
-Zhong et al. (2017). Indeed, they discuss several variations of their
-algorithm which extend their central idea to applications in which
-several samples need to be pulled in a parallel and asynchronous
-fashion. An easy example known from the multi-armed bandit literature
-(SOURCE????!!??!?!?!) is a website where different versions are served
-to customers and each version is an arm in the bandit setting. If the
-feedback that is observed by the algorithm is whether or not a user
-makes a purchase, then it is likely that a new user arrives before the
-feedback for the previous user has been observed. The algorithm has to
-pull the next arm before the feedback of the previous arm has been
-observed. With their variants the authors approach this problem of
-having to take asynchronous and parallel actions. But their algorithm
-can also be reduced to a simpler version that can be compared directly
-with the problem described in Locatelli et al. (2016) where we assume
-the problem of the feedback lag away.
-
-This simpler version is the anytime parameter-free version of their
-Empirical Variance Guided Algorithm (EVT\(_{pf}\)). The EVT\(_{pf}\)
-algorithm is a smart extension of the APT algorithm to an approach that
-takes the empirical variance of the arms into account and deduces an
-upper bound through Bernstein bounds.
+Another algorithm for the thresholding bandit problem employing
+empirical variance estimates is introduced in Zhong et al. (2017).
+Indeed, the authors discuss several variations of their algorithm which
+extend their central idea to applications in which several samples need
+to be pulled in a parallel and asynchronous fashion. An standard example
+known from the multi-armed bandit literature (see for example Li et al.
+(2010)) is a website for which different versions are served to visitors
+and each version is an arm in the bandit setting. If the feedback that
+is observed by the algorithm is whether or not a user makes a purchase,
+then it is likely that a new user arrives before the feedback for the
+previous user has been observed. The algorithm has to pull the next arm
+before the feedback of the previous arm has been observed. With their
+variants the authors approach this problem of having to take
+asynchronous and parallel actions. But their algorithm can also be
+reduced to a simpler version that can be compared directly with the
+problem described in Locatelli et al. (2016) where the feedback lag is
+assumed to be zero.
+
+This simpler version is the parameter-free version of their Empirical
+Variance Guided Algorithm (EVT\(_{pf}\)). The EVT\(_{pf}\) algorithm is
+an extension of the APT algorithm that takes the empirical variance of
+the arms into account and deduces an upper bound through empirical
+Bernstein bounds in a proof following the model of the one described in
+Locatelli et al. (2016).
 
@@
 Zhong et al. (2017) to describe the index used by the algorithms in a
-more general fashion. Write the index \(B_i(t)\) of arm \(i\) at round
+more general fashion. Write the index \(B_i(t+1)\) of arm \(i\) at round
 \(t\) as previously as
@@
 \[
-B_i(t) = S_i(t) D_i(t),
+B_i(t+1) = S_i(t) D_i(t),
 \]
@@
 where \(D_i(t)\) is some measure of the distance between the mean
-\(\mu_i\) or the distribution \(\nu_i\) of the arm \(i\) from the
-threshold \(\tau\), while \(S_i(t)\) is some confidence value. Thus, for
-the APT algorithm, if we let \(\epsilon = 0\) as in Zhong et al. (2016),
-we have
-
-\[
-D_i^{APT}(t) = \hat{\Delta}_i(t) = |\hat{\mu}_i(t) - \tau| \quad \land \quad S_i^{APT}(t) = \sqrt{T_i(t)}
+\(\mu_i\) or the distribution \(\nu_i\) of arm \(i\) from the threshold
+\(\tau\), while \(S_i(t)\) is some confidence value measuring how
+confident we can be in \$. Thus, for the APT algorithm, if we let
+\(\epsilon = 0\) as in Zhong et al. (2016), we have
+
+\[
+D_i^{APT}(t) = \hat{\Delta}_i(t) = |\hat{\mu}_i(t) - \tau| \quad \text{and} \quad S_i^{APT}(t) = \sqrt{T_i(t)}
 \]
@@
 \[
-D_i^{EVT}(t) = \hat{\Delta}_i(t) = |\hat{\mu}_i(t) - \tau| \quad \land \quad S_i^{EVT}(t) = \Big(\frac{1}{T_i(t) + \sqrt{\frac{1}{T_i(t)}}\hat{\sigma}_{i}(t)}\Big)^{-1}
-\]
-
-or equivalently as
-
-\[
-D_i^{EVT}(t) = \sqrt{\hat{\sigma}^2_{i}(t) + \hat{\Delta}_i(t)} - \hat{\sigma}_i(t) \quad \land \quad S_i^{EVT} = \sqrt{T_i(t)}
-\]
-
-We see that in both formulations either the distance term \(D_i\) or the
-confidence term \(S_i\) between the two algorithms is equivalent. While
-the empirical variance is a natural confidence measure -- and thus makes
-sense in the \(S_i^{EVT}\) part in the first equation -- it also
-describes the shape of the distribution and thus is also a measure of
-how far the distribution (in contrast to just the mean) is away from the
-threshold, and thus can belong to \(D_i^{EVT}\). We will focus on the
-latter formulation for the remaining paper.
-
-In comparison with the APT algorithm, the EVT\(_{pf}\) algorithm adds
-the empirical variance into the index to measure how well we can expect
-the distribution (and the mean) to be seperated from the threshold; it
-serves as a crude measure of distance between threshold and
-distribution. We note that for a Bernoulli distributed random variable,
-\(D_i^{EVT}\) is decreasing as the mean approaches the threshold.
-Similar should hold in general for bounded variables as the variance and
-the mean are linked by the distance of the mean to the bound of the
-support (in contrast to, for example, a normal distributed random
-variable where a change in the mean does not correspond to a change in
-the variance). This is important as the bounds of the EVT\(_{pf}\)
-algorithm only hold for random variables bounded in \([0,1]\).
+D_i^{EVT_{pf}}(t) = \sqrt{\hat{\sigma}^2_{i}(t) + \hat{\Delta}_i(t)} - \hat{\sigma}_i(t) \quad \text{and} \quad S_i^{EVT_{pf}} = \sqrt{T_i(t)}
+\]
+
+We see that both algorithms employ the same confidence term. The
+empirical variance describes the shape of the distribution and thus is a
+measure of how far the distribution (in contrast to just the mean) is
+away from the threshold. It consequently makes sense to have it appear
+in \(D_i^{EVT}\). And in contrast to the APT algorithm, the EVT\(_{pf}\)
+algorithm consequently takes more information about the arms into
+account than just their mean. As mentioned previously, this should
+especially be valuable whenever arms have indeed different variances.
+Similar (very roughly) to how the Kullback-Leibler divergence measures
+distances between distributions, the \(D_i^{EVT}\) including the
+empirical variance serves as a crude measure of distance between
+threshold and distribution. We note that for a Bernoulli distributed
+random variable, \(D_i^{EVT}\) is always decreasing as the mean
+approaches the threshold (compare the figure 2). Similar should hold in
+general for bounded variables as the variance and the mean are linked by
+the distance of the mean to the bound of the support (in contrast to,
+for example, a normal distributed random variable where a change in the
+mean does not correspond to a change in the variance). This is important
+as the bounds of the EVT\(_{pf}\) algorithm only hold for random
+variables bounded in \([0,1]\). In contrast to the AugUCB, this
+restriction is not just on the variance of the arm but explicitly on the
+reward itself in the current version that builds on empirical Bernstein
+bounds as shown in Maurer and Pontil (2009).
 
@@
 in the proof of their lower bound. They define favorable events that
-hold with large probability, make sure the same separation condition
-holds for them given that each arm is pulled often enough. Additionally
-to a favorable event that bounds the deviation between sample mean and
-population mean, they define a second event on which the sample standard
-deviation is close to the population standard deviation. This is bounded
-in large probability by a Bernstein inequality. The union of the two
-events then serves as the favorable event in the remainder of their
-proof.
-
-Given a lower bound that is also adapted to the new complexity
-\(H^{\text{EVT}_{pf}}\), the authors show that the EVT\(_pf\) algorithm
-is optimal. Furthermore, they compare their algorithms in experiments
+hold with large probability, and ensure that the same separation
+condition as in Locatelli et al. holds for them given that each arm is
+pulled sufficiently often. Additionally to a favorable event that bounds
+the deviation between sample mean and population mean, they define a
+second event on which the sample standard deviation is close to the
+population standard deviation. This is bounded in large probability by
+an empirical Bernstein inequality (Maurer and Pontil, 2009). The union
+of the two events then serves as the favorable event in the remainder of
+their proof.
+
+Given a lower bound adapted to the new complexity
+\(H^{\text{EVT}_{pf}}\), the Zhong et al. (2017) show that the
+EVT\(_pf\) algorithm is optimal in that its upper bound matches the
+lower bound. Furthermore, they compare their algorithm in experiments
 against the APT algorithm. The experiments use data generated from
@@
 EVT\(_{pf}\) could be able to cope with distributions of parameter
-\(\mu\) close to \(\tau\) much better than APT.
+\(\mu\) close to \(\tau\) much better than APT (compare figure 3).
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/Hevt_Hapt_Comparison-1}
+{\centering \includegraphics[width=0.7\linewidth]{Draft_files/figure-latex/Hevt_Hapt_Comparison-1}
 
@@
 
-\caption{This graph compares the complexity terms used in the APT, AugUCB, and EVT algorithms respectively.
-We observe that as the mean of the arm's distribution is closer to the threshold, the complexity of the problem increases much less rapidly for the EVT algorithm.
+\caption{Comparing the complexity terms used in the APT, AugUCB, and EVT algorithms, we observe that the problem complexity of the EVT algorithm increases much less rapidly than for the other algorithms.
 Thus, the EVT should be able to cope with arms close to the threshold better than the APT algorithm.
@@
 
-\subsection{\texorpdfstring{Likelihood Ratio for Exponential Family
-Distributions
-\label{sec:LikelihoodRatioForExponentialFamily}}{Likelihood Ratio for Exponential Family Distributions }}\label{likelihood-ratio-for-exponential-family-distributions}
-
-We now present an approach that builds on the idea of the likelihood
-ratio statistic for hypothesis tests. We first present the general idea
-of likelihood ratio based tests, and then introduce our new algorithm
-for the thresholding bandit problem.
-
-\subsubsection{Likelihood Ratio-based Hypothesis
-Tests}\label{likelihood-ratio-based-hypothesis-tests}
+\subsection{\texorpdfstring{Likelihood Ratio for Sequential Sampling
+\label{sec:LikelihoodRatioForExponentialFamily}}{Likelihood Ratio for Sequential Sampling }}\label{likelihood-ratio-for-sequential-sampling}
+
+We now present a new sequential sampling algorithm for the fixed budget
+thresholding bandit problem that builds on the idea of the likelihood
+ratio statistic for hypothesis tests. We first shortly describe the
+general idea of likelihood ratio based tests, to then introduce this new
+algorithm for the thresholding bandit problem, which we call Simple
+Likelihood Ratio (SLR) algorithm.
+
+\subsubsection{\texorpdfstring{Likelihood Ratio-based Hypothesis Tests
+\label{sec:LRTests}}{Likelihood Ratio-based Hypothesis Tests }}\label{likelihood-ratio-based-hypothesis-tests}
 
@@
 \(q(x;\theta)\) be the density function corresponding to the
-distribution. In a standard hypothesis test, we test whether an
-alternative parameterization is more likely than the parameterization
-given by the null hypothesis. That is, we test
+distribution. We would like to test whether an alternative
+parameterization is more likely than the parameterization given by the
+null hypothesis. That is, we test
 
@@
 and
-\(L_{H_1} = L(x|\theta = \theta_{H_1}) = \prod_{i=1}^T q(x_i|\theta_{H_1})\).
+\(L_{H_1} = L(x|\theta = \theta_{H_1}) = \prod_{s=1}^T q(x_s|\theta_{H_1})\).
 The likelihood ratio test statistic is then given as
@@
 \[
-LR(\theta_{H_0}|| \theta_{H_1}) = \frac{L_{H_0}}{L_{H_1}} = \prod_{i=1}^T\frac{q(x_i|\theta_{H_0})}{ q(x_i|\theta_{H_1})}.
-\] The intuition behind the test of course being that, if the true
+LR_T(\theta_{H_0}|| \theta_{H_1}) = \frac{L_{H_0}}{L_{H_1}} = \prod_{s=1}^T\frac{q(x_s|\theta_{H_0})}{ q(x_s|\theta_{H_1})}.
+\]
+
+and is used in the optimal test of two hypotheses as shown by the
+Neyman-Pearson lemma (see chapter 11, Theorem 11.7.1 in Cover and
+Thomas, 2006).
+
+The intuition behind the test of course being that, if the true
 parameterization is \(H_1\) and not \(H_0\), then the likelihood
-\(L_{H_1}\) should be larger than \(L_{H_0}\). A small enough likelihood
-ratio would thus lead us to a rejection of the null hypothesis, while a
-large likelihood ratio is evidence in favor of the null hypothesis.
-
-By considering \(lr = -2\log(LR(\theta_{H_0}|| \theta_{H_1}))\), one has
-a statistic that is \(\chi^2\) distributed with degrees of freedom that
-depend on the null and alternative hypothesis. Assessing whether the
-null hypothesis can be rejected with large confidence thus becomes
-straightforward.
-
-\subsubsection{Likelihood Ratio-based Thresholding
-Bandit}\label{likelihood-ratio-based-thresholding-bandit}
-
-The simple concept of the likelihood-ratio test serves as foundation for
-a new sampling strategy that can be applied to the thresholding bandit
-problem. In contrast to the cumulative regret problem, or even the best
-arm identification problem, we have some sort of null hypothesis for the
-distributions in the thresholding bandit problem. In case of no
-information and no observed samples, the null hypothesis might simply be
-that all distributions have a mean that equals the threshold. By
-observing samples, we then want to test whether the mean of the
-distributions is different from the threshold \(\tau\) in either
-direction. Once we are sure that there is a difference, we do not want
-to continue to test. Instead, we would like to focus our sampling effort
-on a different arm where we are not as sure. The likelihood ratio
-quantifies how ``significant''" of a difference there is between the
+\(L_{T,H_1}\) should be larger than \(L_{T,H_0}\). A small enough
+likelihood ratio would thus lead us to a rejection of the null
+hypothesis, while a large likelihood ratio is evidence in favor of the
+null hypothesis.
+
+Furthermore, the likelihood ratio is inherently linked to information
+theoretic quantities and divergence measures. Assuming that \(Q\) is a
+discrete distribution with support \(\chi\), one can write the negative
+log-likelihood ratio as (compare Cover and Thomas, 2006)
+
+\begin{align*}
+-\log(LR_T(\theta_{H_0}|| \theta_{H_1}) & = & \sum_{i=1}^T \log(\frac{q(x_s|\theta_{H_0})}{ q(x_s|\theta_{H_1})}) \\
+& = & \sum_{a \in \chi} T q(a|\hat{\theta}) \log(\frac{q(a|\theta_{H_0})}{ q(a|\theta_{H_1})}) \\
+& = & \sum_{a \in \chi} T q(a|\hat{\theta}) \log(\frac{q(a|\theta_{H_0})}{ q(a|\theta_{H_1})}\frac{q(a|\hat{\theta})}{ q(a|\hat{\theta})}) \\
+& = & T \KL(q(\hat{\theta})||q(\theta_{H_0})) - T \KL(q(\hat{\theta})||q(\theta_{H_1})),
+\end{align*}
+
+where \(\hat{\theta}\) is the maximum likelihood estimate of the
+parameter \(\theta\) given the sample \(x\). If we hold the \(H_0\)
+hypothesis fixed and set \(\theta_{H_1} = \hat{\theta}\) as often done
+in praxis, then with \(\KL(Q(\hat{\theta})||Q(\hat{\theta})) = 0\):
+
+\[
+-\log(LR_T(\theta_{H_0}|| \theta_{H_1})) = -\log(LR_T(\theta_{H_0}|| \hat{\theta})) = \KL(Q(\hat{\theta}||Q(\theta_{H_0}))
+\]
+
+Furthermore, we have for any distributions \(Q_{H_0}\) and \(Q_{H_1}\)
+for a sample \(x\) sampled from the \(H_0\) distribution, that
+
+\[
+\frac{1}{n} \log(LR_T(\theta_{H_0}||\theta_{H_1})) \rightarrow \KL(Q(\theta_{H_0})||Q(\theta_{H_1})) \quad \text{in probability},
+\]
+
+by the law of large numbers (or asymptotic equipartition property) for
+the Kullback-Leibler divergence as in Theorem 11.8.1 in Cover and Thomas
+(2006). Lastly, based on the characteristics shown before, for
+frequentist tests the Kullback-Leibler divergence between
+\(Q(\theta_{H_0})\) and \(Q(\theta_{H_1})\) gives the best possible
+exponent for the error of the second type given a fixed error of the
+first type. This is the result of the Chernoff-Stein Lemma (Theorem
+11.8.3, Cover and Thomas, 2006), which is reminiscient of the complexity
+\(\kappa_B\) derived by Kaufmann et al. (2016) and as described in
+\autoref{chap:KullbackLeiblerPureExploration}:
+
+\begin{theorem}[Chernoff-Stein Lemma] \label{theorem:ChernoffStein}
+Let $X_1, X_2, ..., X_n$ be i.i.d.
+distributed according to $Q$.
+Consider the hypothesis test between two alternatives, $Q=P_1$ and $Q=P_2$, where $\KL(P_1||P_2) < \infty$.
+Let $A_n \subseteq \chi^n$ be an acceptance region for hypothesis $H_1$.
+Let the probabilities of error be $\alpha_n = P_1^n(A_n^C)$, and $\beta_n = P_2^n(A_n)$, and for $0< \epsilon <1/2$, define $\beta_n^{\epsilon} = \min_{A_n \subseteq \chi^n, \alpha_n < \epsilon} \beta_n$.
+Then
+
+$$
+\text{lim}_{n\rightarrow \infty} \frac{1}{n} \log \beta_n^{\epsilon} = - \KL(P_1||P_2)
+$$
+\end{theorem}
+
+\subsubsection{Likelihood Ratio as Index in Sequential
+Sampling}\label{likelihood-ratio-as-index-in-sequential-sampling}
+
+We now employ the concept of the likelihood-ratio test for a new
+sequential sampling strategy for the thresholding bandit problem. In
+contrast to the cumulative regret problem or the best arm identification
+problem, the thresholding bandit problem offers a natural \(H_0\)
+hypothesis for the arms' distributions: the threshold \(\tau\). Given
+that we want to classify the arms against the threshold, and given that
+\(\tau\) is known and fixed, we can set a null hypothesis that is a
+function of \(\tau\). In the simplest case, the distributions are
+parameterized by their mean \(\theta_i = \mu_i\), and we set
+\(\theta_{i,H_0} = \tau\) for all arms. The likelihood ratio then
+quantifies how ``significant'' of a difference there is between the
 threshold \(\tau\) and the current sample mean \(\hat{\mu}_i(t)\) of an
-arm. Given that we plug in the sample mean, that is, the maximum
-likelihood estimator for the true mean for many distributions, the
-likelihood ratio will be smaller than 1 and decrease in sample size even
-if the threshold and sample mean are constant.
+arm, assuming distributions for which the maximum likelihood estimate of
+the mean is given by the empirical mean. In these cases, the likelihood
+ratio will be smaller than 1 and decrease in sample size even if the
+threshold and sample mean are constant.
 
 Due to these characteristics, the likelihood ratio can serve as a
-natural index for sampling strategies. Thus write as index
-
-\[
-B_i(t) = LR(\tau|| \hat{\mu}_i(t)) = \prod_{i=1}^T\frac{q(x_i|\tau)}{ q(x_i|\hat{\mu}_i(t))}
-\]
-
-and pull at round \(t\) the arm \(i^* = \arg \max_i B_i(t)\). As we
-described in the previous paragraph, we have \(B_i(t) \leq 1\),
-\(t \uparrow \rightarrow B_i(t) \downarrow\), and
-\(|\hat{\mu}_i(t) - \tau| \uparrow \rightarrow B_i(t) \downarrow\).
+natural index for sampling strategies. Consider the setting described in
+\autoref{sec:Setup} and \autoref{sec:TheAPTAlgorithm} though without
+assuming \(R\)-sub-Gaussian distributions. Consider \(B_i^{APT}\) and
+compare it to
+
+\[
+B_i^{LR}(t+1) = LR(\tau|| \hat{\mu}_i(t)) = \prod_{i=1}^T\frac{q(x_i|\tau)}{ q(x_i|\hat{\mu}_i(t))}.
+\]
+
+We have \(B_i(t) \leq 1\), \(t \uparrow \rightarrow B_i(t) \downarrow\),
+and \(|\hat{\mu}_i(t) - \tau| \uparrow \rightarrow B_i(t) \downarrow\).
 Consequently, by choosing the arm that maximizes \(B_i(t)\), we choose
-an arm for which we either have not collected many samples, or where the
-sample mean is close to the threshold \(\tau\). In this sense, a
-strategy based on the likelihood ratio is of course very reminiscient of
-the index employed by the APT algorithm. Indeed, assuming the samples
-are normally distributed with the same variance for the distribution
-\(\nu_i\) under both \(H_0\) and \(H_1\), then
-\(-\log(LR(\tau||\hat{\mu}_i(t)))\) equals the index in APT. Why then
-would one use the likelihood based strategy?
+an arm for which we either have not collected many samples, or for which
+the sample mean is close to the threshold \(\tau\). In this sense, a
+strategy based on the likelihood ratio is reminiscient of the index
+employed by the APT algorithm. Indeed, assuming the samples are normally
+distributed with the same variance for the distribution \(\nu_i\) under
+both \(H_0\) and \(H_1\), then \(-\log(LR(\tau||\hat{\mu}_i(t)))\)
+equals the index in APT. Why then would one use the likelihood based
+strategy?
 
@@
 distribution. The most important example are Bernoulli arms with small
-means as discussed before. Here, it is also easy to assume that the true
-distribution is known upfront. Similarly, the likelihood ratio statistic
-can be used for other univariate distributions of the exponential
-family. But we also propose a version for the Normal distribution with
-unknown mean.
-
-We now focus on the case where the distributions
-\(\nu_{\theta_1}, ..., \nu_{\theta_K}\) are all the same canonical
-exponential family of distributions with scalar parameter
-\(\theta_i \in \Theta\). The probability density function of the
-absolutely continuous distribution \(\nu_{\theta_i}\) with regard to a
-dominating measure \(\rho\) on \(\mathbb{R}\) is given by
-\(q(x|\theta) = h(x) \exp(T(x)\theta - b(\theta))\). As described in
+means as motivated. While the likelihood ratio can in theory be used for
+any distributions, and arms could even have different classes of
+distributions, the class of distribution has to be known upfront for
+every arm. Given the role of the threshold \(\tau\) and the goal of
+classification of the mean against \(\tau\), the likelihood ratio
+strategy is arguably most naturally employed on distributions
+parameterized by their mean. In the following descriptions, we thus
+focus on univariate distributions of the exponential family.
+Additionally, we also propose a version for the Normal distribution with
+unknown mean. Before we describe the algorithm, we show that the
+likelihood ratio has a very convenient form for this family of
+distributions.
+
+\subsubsection{Likelihood Ratio for Univariate Exponential Family of
+Distributions}\label{likelihood-ratio-for-univariate-exponential-family-of-distributions}
+
+We now focus on a thresholding bandit problem where the arms are
+distributed according to \(\nu_{\theta_1}, ..., \nu_{\theta_K}\), which
+are all from the same canonical exponential family of distributions with
+scalar parameter \(\theta_i \in \Theta\). The probability density
+function of the absolutely continuous distribution \(\nu_{\theta_i}\)
+with regard to a dominating measure \(\rho\) on \(\mathbb{R}\) is given
+by \(q(x|\theta) = h(x) \exp(T(x)\theta - b(\theta))\). As described in
 Cappé et al. (2013), citing Lehmann and Casella (1998), the derivative
@@
 distribution its mean \(\mu = \mathbb{\nu_{\theta}}\) and write
-\(\nu_{b'^{-1}(\mu)}\) with the probability density function
+\(\nu_{b'^{-1}(\mu)}\) with the probability density function (compare
+Cappé et al., 2013)
 
@@
 
-As we will see now, this statistic is easily derived for many specific
-distributions.
-
-\paragraph{Example 1: Bernoulli
-Distribution}\label{example-1-bernoulli-distribution}
+As we will see now, this statistic takes a very convenient closed form
+for many common distributions.
+
+\textbf{Example 1: Bernoulli Distribution}
 
@@
 
-\[
--\log(LR(\mu_0||\mu_1)) = n(\log\Big(\frac{1-\mu_0}{1-\mu_1}\Big)) - \Big(\log(\frac{\mu_0}{1-\mu_0}) - \log(\frac{\mu_1}{1-\mu_1})\Big)\sum_{i=1}^{n}x_i = n \Big( (1-\hat{\mu})\log\Big(\frac{1-\mu_1}{1-\mu_0}\Big) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}) \Big)
-\]
-
-We observe that, if we let \(\mu_0 = \tau\) and \(\mu_1 = \hat{\mu}\),
-then
+\begin{align*}
+-\log(LR(\mu_0||\mu_1)) & = & n(\log\Big(\frac{1-\mu_0}{1-\mu_1}\Big)) - \Big(\log(\frac{\mu_0}{1-\mu_0}) - \log(\frac{\mu_1}{1-\mu_1})\Big)\sum_{i=1}^{n}x_i \\
+& = & n \Big( (1-\hat{\mu})\log\Big(\frac{1-\mu_1}{1-\mu_0}\Big) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}) \Big)
+\end{align*}
+
+We observe that, if we let \(\mu_0 = \tau\) and \(\mu_1 = \hat{\mu}\)
+(compare \autoref{sec:LRTests}), then
 
@@
 
-\paragraph{Example 2: Poisson
-Distribution}\label{example-2-poisson-distribution}
+\textbf{Example 2: Poisson Distribution}
 
@@
 
-We observe that, if we let \(\mu_0 = \tau\) and \(\mu_1 = \hat{\mu}\),
-then
+We observe that, if we let \(\mu_0 = \tau\) and \(\mu_1 = \hat{\mu}\)
+(compare \autoref{sec:LRTests}), then
 
@@
 
-\paragraph{\texorpdfstring{Example 3: Normal distributions with known
-variance
-\(\sigma^2\)}{Example 3: Normal distributions with known variance \textbackslash{}sigma\^{}2}}\label{example-3-normal-distributions-with-known-variance-sigma2}
+\textbf{Example 3: Normal distributions with known variance
+\(\sigma^2\)}
 
@@
 
-And again, if we let \(\mu_1 = \hat{\mu}\) and \(\mu_0 = \tau\), then
+And again, even though the distribution is continuous (compare
+\autoref{sec:LRTests}), if we let \(\mu_1 = \hat{\mu}\) and
+\(\mu_0 = \tau\), then
 
@@
 
-\paragraph{\texorpdfstring{Example 4: Gamma distributions with known
-shape parameter
-\(\alpha\)}{Example 4: Gamma distributions with known shape parameter \textbackslash{}alpha}}\label{example-4-gamma-distributions-with-known-shape-parameter-alpha}
+\textbf{Example 4: Gamma distributions with known shape parameter
+\(\alpha\)}
 
@@
 -\log(LR(\mu_0||\mu_1)) = n\alpha(-\log(\frac{\alpha}{\mu_0}) - \log(\frac{\mu_1}{\alpha})) - (-\frac{\alpha}{\mu_0} + \frac{\alpha}{\mu_1})\sum_{i=1}^{n}x_i = n\alpha \Big(\log\big(\frac{\mu_0}{\mu_1}\big) - \frac{\hat{\mu}}{\mu_1} + \frac{\hat{\mu}}{\mu_0}\Big).
-\] And again, if we let \(\mu_1 = \hat{\mu}\) and \(\mu_0 = \tau\), then
+\]
+
+And again, even though the distribution is continuous (compare
+\autoref{sec:LRTests}), if we let \(\mu_1 = \hat{\mu}\) and
+\(\mu_0 = \tau\), then
 
@@
 Given these results for the exponential family of distributions, we can
-now define the SLR (Simple Likelihood Ratio) algorithm.
-
-\subsubsection{1D-SLR Algorithm for One-Dimensional Exponential Family
-of
-Distributions}\label{d-slr-algorithm-for-one-dimensional-exponential-family-of-distributions}
-
-Very similar to the APT algorithm, the SLR algorithm receives as input
-the definition of the problem \((\tau, \epsilon)\) (compare Locatelli et
-al., 2016). Additionally, the algorithm receives as input the name of
-the distribution that the arms follow, as well as potential additional
-parameters (\(\sigma_1, ..., \sigma_K\) for Normal distributions,
-\(\alpha_1, ..., \alpha_K\) for Gamma distributions). We assume that
-each arm follows the same kind of distribution, with potentially
-different parameters \(\theta_1, ..., \theta_K\). The algorithm pulls
-each arm once. At time \(t>K\), the algorithm updates the number of
-pulls for arm \(i\) at time \(t\), \(T_i(t)\), for each arm, as well as
-the empirical mean \(\hat{\mu}_i(t)\) of arm \(i\) after \(T_i(t)\)
-pulls. The empirical mean is calculated for each arm
-\(k\in \{1,...,K\}\) as
+now define the Simple Likelihood Ratio algorithm.
+
+\subsection{\texorpdfstring{1D-Simple Likelihood Ratio Algorithm
+\label{sec:1DSLR}}{1D-Simple Likelihood Ratio Algorithm }}\label{d-simple-likelihood-ratio-algorithm}
+
+Consider again the setting in \autoref{sec:Setup} though without the
+assumption of \(R\)-sub-Gaussian distributions. Instead, assume that the
+class of distributions that the arms \(i \in \mathbb{A}\) follow is
+known upfront. For the 1D-SLR algorithm, we restrict the potential
+classes to the univariate exponential family of distributions and write
+the class generally as \(\nu(\mu, \theta)\). Here, \(\theta\) describes
+additional parameters known upfront, as for example
+\(\sigma_1, ..., \sigma_K\) for Normal distributions, or
+\(\alpha_1, ..., \alpha_K\) for Gamma distributions. Additionally to
+\(\nu(\mu)\), the 1D-SLR algorithm receives as input the definition of
+the problem \((\tau, \epsilon)\) (compare Locatelli et al., 2016). As
+initialization, the algorithm pulls each arm once. At time \(t>K\), the
+algorithm updates the number of pulls for arm \(i\) at time \(t\),
+\(T_i(t)\), for each arm, as well as the empirical mean
+\(\hat{\mu}_i(t)\) of arm \(i\) after \(T_i(t)\) pulls. The empirical
+mean is calculated for each arm \(k\in \{1,...,K\}\) as
 \(\hat{\mu}_i(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)} x_{i,s}\), with
-\(T_i(t) = \sum_{s=1}^{t}\mathbb{I}(I_s = i)\). As in Locatelli et al.
-(2016), the \(X_{i,s}\) is the sample received when pulling arm \(i\)
-for the \(s\)-th time. Depending on the distribution, the algorithm then
+\(T_i(t) = \sum_{s=1}^{t}\mathbb{I}(I_s = i)\). It serves as maximum
+likelihood estimate of the arm's mean. As in Locatelli et al. (2016),
+the \(X_{i,s}\) is the sample received when pulling arm \(i\) for the
+\(s\)-th time. Depending on the distribution, the algorithm then
 computes the index
 
-\[
-B_i^{SLR}(t+1) = \mathbb{I}(\hat{\mu}\geq \tau)(-\log\big(LR(\tau-\epsilon||\hat{\mu}_i(t))\big) + \mathbb{I}(\hat{\mu}< \tau)(-\log\big(LR(\tau+\epsilon||\hat{\mu}_i(t))\big) = T_i(t) \Big( \mathbb{I}(\hat{\mu}\geq \tau)\cdot KL(\nu_{b'^{-1}(\hat{\mu}(t))}||\nu_{b'^{-1}(\tau-\epsilon)}) + \mathbb{I}(\hat{\mu} < \tau)\cdot KL(\nu_{b'^{-1}(\hat{\mu}(t))}||\nu_{b'^{-1}(\tau+\epsilon)}) \Big).
-\]
+\begin{align*}
+B_i^{SLR}(t+1) & = \mathbb{I}(\hat{\mu}\geq \tau)(-\log\big(LR(\tau-\epsilon||\hat{\mu}_i(t))\big) \\
+& \quad +\: \mathbb{I}(\hat{\mu} <\tau)(-\log\big(LR(\tau+\epsilon||\hat{\mu}_i(t))\big) \\
+& = T_i(t) \Big( \mathbb{I}(\hat{\mu}\geq \tau)\cdot KL(\nu_{b'^{-1}(\hat{\mu}(t))}||\nu_{b'^{-1}(\tau-\epsilon)}) \\
+& \quad +\: \mathbb{I}(\hat{\mu} < \tau)\cdot KL(\nu_{b'^{-1}(\hat{\mu}(t))}||\nu_{b'^{-1}(\tau+\epsilon)}) \Big) \Alignyesnumber\label{eqn:SLRIndex}.
+\end{align*}
 
@@
 end of the horizon \(T\), the algorithm outputs the set of arms
-\(\hat{S}_\tau = \{k: \hat{\mu}_k(T) \geq \tau\}\).
+\(\hat{S}_\tau = \{i \in \mathbb{A}, \hat{\mu}_i(T) \geq \tau\}\).
 
@@
 
-\subsubsection{2D-SLR Algorithm for Normal Distributions with Unknown
-Mean and Unknown
-Variance}\label{d-slr-algorithm-for-normal-distributions-with-unknown-mean-and-unknown-variance}
+\subsection{2D-SLR Algorithm for Normal
+Distributions}\label{d-slr-algorithm-for-normal-distributions}
 
@@
 Now, at each round \(t\), the algorithm computes \(T_i(t)\) and
-\(\hat{\mu}_i(t)\) as before, but additionally the empirical variances
+\(\hat{\mu}_i(t)\) as before, and additionally the empirical variances
 \(\sigma_{\tau,i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\tau)^2\)
@@
 
-\[
-B_i^{2DSLR}(t+1) = -\log(LR(\tau, \sigma_{\tau,i}^2(t)||\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t))) = T_i(t) \log\Big(\frac{\sigma_{\tau,i}^2(t)}{\hat{\sigma}_i^2(t)}\Big) = T_i(t) KL(\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t)||\tau, \sigma_{\tau,i}^2(t))
-\]
-
-(SHOW THAT THE NOTATION CAN BE ABUSED AND THE KL WRITTEN THIS WAY
-BECAUSE UNIQUELY DEFINED BY MEAN AND VARIANCE)
+\begin{align*}
+B_i^{SLR_{2D}}(t+1) & = -\log(LR(\tau, \sigma_{\tau,i}^2(t)||\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t))) \\
+& = T_i(t) \log\Big(\frac{\sigma_{\tau,i}^2(t)}{\hat{\sigma}_i^2(t)}\Big) \\
+& = T_i(t) KL(N(\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t))||N(\tau, \sigma_{\tau,i}^2(t)))
+\end{align*}
 

### 2017-08-31 Thesis/Draft.Rmd
Add D-Tracking Rule

@@
     #latex_engine: xelatex
-fontsize: 12pt
+fontsize: 11pt
 urlcolor: blue
@@
 
-# Thresholding Bandit Problem \label{chap:ThresholdingBanditProblem}
+# The Thresholding Bandit Problem \label{chap:ThresholdingBanditProblem}
 
@@
 \begin{equation*} \mathbb{E}(\mathcal{L}(T)) \leq \exp
-(-\frac{1}{64R^2}\frac{T}{H} + 2 \log (T) + 1)K)) \end{equation*}
+\Big(-\frac{1}{64R^2}\frac{T}{H} + 2 \log((\log(T) + 1)K)\Big) \end{equation*}
 
@@
 \begin{align*}
-\mathbb{P}(\tilde{\xi}) & = & 1-\mathbb{P}(\xi^C) \\
-& = & 1-\mathbb{P}(\cup_{i=1}^K \xi_i^C) \\
-& \geq & 1 - \sum_{i=1}^K \mathbb{P}(\xi_i^C) \\
-& \geq & 1 - 2K\exp (-\frac{T\delta^2}{2R^2H})
+\mathbb{P}(\tilde{\xi}) & = 1-\mathbb{P}(\xi^C) \\
+& = 1-\mathbb{P}(\cup_{i=1}^K \xi_i^C) \\
+& \geq 1 - \sum_{i=1}^K \mathbb{P}(\xi_i^C) \\
+& \geq 1 - 2K\exp (-\frac{T\delta^2}{2R^2H})
 \end{align*}
@@
 \begin{align*}
-|\hat{\mu}_i(t) - \mu_i| & = & |(\hat{\mu}_i(t) - \tau) - (\mu_i - \tau)| \\
-& \geq & || \hat{\mu}_i(t) - \tau | - |\mu_i - \tau|| \\
-& \geq & |(|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i - \tau| + \epsilon)| \\
-& \geq & |\hat{\Delta}_i(t) - \Delta_i|
+|\hat{\mu}_i(t) - \mu_i| & = |(\hat{\mu}_i(t) - \tau) - (\mu_i - \tau)| \\
+& \geq || \hat{\mu}_i(t) - \tau | - |\mu_i - \tau|| \\
+& \geq |(|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i - \tau| + \epsilon)| \\
+& \geq |\hat{\Delta}_i(t) - \Delta_i|
 \end{align*}
@@
 \begin{align*}
-B_k(t) & \geq & \Big(\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}}\Big) \sqrt{T_k(t)} \\
-& \geq & \Big(\Delta_k - \sqrt{\frac{2}{h_k}}\delta \Big)
+B_k(t) & \geq \Big(\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}}\Big) \sqrt{T_k(t)} \\
+& \geq \Big(\Delta_k - \sqrt{\frac{2}{h_k}}\delta \Big)
 \end{align*}
@@
 
-## Lower Bound: Theorem and Proof \label{sec:LowerBoundLocatelli}
+## Lower Bound for the Thresholding Bandit Problem \label{sec:LowerBoundLocatelli}
+
+Locatelli et al.
+(2016) also provide a general lower bound on the probability of error in the thresholding bandit problem.
+The bound is derived for a specified set of problems through a change in distribution as common in the multi-armed bandit literature (compare for example Audibert et al., 2010, or Kaufmann et al., 2016).
+For any of these problems, the largest probability of error that the best algorithm incurs is still lower bounded by the bound given below.
 
@@
 
-*Proof of Theorem \ref{theorem:Locatelli2016Theorem1}*: In Theorem \ref{theorem:Locatelli2016Theorem1} of Locatelli et al.
-(2016), a lower bound for the thresholding bandit problem is shown.
-The basic idea is as follows.
-The problem formulation considered in the paper describes bandit problems for sub-Gaussian distributions.
-To show a lower bound, we show that every algorithm is expected to make a certain error even if we restrict ourselves to a very restricted scenario.
-Even then, any algorithm will have a certain level of risk with which it cannot distinguish between the actual setting and slightly changed settings (under which the former answer leads to regret).
-
-To be more specific, consider a case in which we set $\tau = 0$ and $\epsilon = 0$ w.l.o.g.
-If we then choose all arms to have normally distributed feedback with means $\mu_i$, we see that for each arm $i$ the distance from the threshold is given by $\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i$.
-Thus, assuming a variance of 1 for every arm, we have for every arm the distribution $\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)$.
-Furthermore, define for each arm $i \in \{1, \dots, K\}$ the alternative distribution $\nu_i' = \mathcal{N}(-\Delta_i,1)$.
-It is easy to see that in this case, this is equivalent to a "flip around the threshold".
-Arms that originally have a mean larger than the threshold have a mean smaller than the threshold after the flip.
-
-The idea now is that every arm $i \in \{1,\dots,K\}$ generates a sample for every time point $t\in \{1, \dots, T\}$ from its distribution $\nu_i$ before the algorithm starts to choose arms.
-Thus, we have a $T \times K$ table of realized observations from the product distribution given by $\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K$.
-This is a product distribution where the $K$ different means all lie above the threshold.
-We would hope that an algorithm classifies the means accordingly.
-However, we will show in what follows that any algorithm makes a certain error by not being able to distinguish $\mathcal{B}^0$ from at least one of $K$ alternative product distributions $\mathcal{B}^i, i \in \{1, \dots, K\}$, of which each differs only slightly in one arm from the original distribution, and has the same overall complexity (as defined by $H = \sum_{i=1}^K (\Delta_i)^{-2}$).
-We require $K$ different distributions so that an arm sampling arm $i$ very often for some reason will not have a smaller lower bound by chance.
-
-For each of the $K$ arms, we introduce an alternative model of the following kind.
-Before the start of the algorithm, we introduce a slight variation in the setup.
-The idea is similar to how one can switch arms in the pure exploration setup for multi-armed bandits (compare Audibert et al., 2010; Garivier & Kaufmann, 2016) to "confuse" any algorithm without introducing additional complexity to the specified problem.
-However, since we do not compare arms directly with each other in the thresholding bandit problem (switching arms would still keep all means above the threshold), we instead need to flip an arm $i$ with respect to the threshold in order to get the alternative model $\mathcal{B}_i$.
-Since the threshold is $\tau = 0$, we have for the flipped arm the new distribution $\nu_i'$ as defined above.
-Indeed, we can define the new product distribution $B^i = \nu_1^i \otimes \dots \otimes \nu_K^i$ where for $k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}$.
-This flipping of the arm corresponds to multiplying all random variables $X_{i,t}$ of arm $i$ by $-1$.
-
-As in Locatelli et al.
-(2016), we let for $i \leq K$, $\mathbb{P}_{\mathcal{B}^i}$ define the probability distribution describing all samples that a bandit strategy can potentially collect up to horizon $T$, i.e.
-according to the samples $(X_{k,s})_{k\leq K, s \leq T} \sim (\mathcal{B}^i)^{\otimes T}$.
-$(T_k)_{k\leq K}$ denotes the number of samples collected on arm $k$ until time $T$.
-
-### Reminder about the goal of the proof
-
-At this point, we have defined a finite set of problems of Gaussian distributions with fixed variance 1 for a given set of set of gaps between the means of the distributions and the threshold, $(d_k)_k$.
-We will now proof a lower bound on the worst case regret of any algorithm; that is, the maximum error probability that even the best algorithm makes on this problem.
-
-### Statistical Decision
-
-Given our formulation of the regret, the expected regret $\mathbb{E}[\mathcal{L}(T)]$ corresponds directly to the probability of making a wrong classification of any of the $K$ means.
-In general, let $g$ be a binary decision function, and define $\Omega = \{g = 0\}$ and $\Omega^C = \{g = 1\}$.
-Assume that the decision $T$ distinguishes between two states of the world, $H_0$ and $H_1$.
-Then our overall error probability is given by $P_{H_0}(g=1) + P_{H_1}(g = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)$.
-
-In our case, $H_0$ may correspond to the state in which we have $\mathcal{B}^0$, and $H_1$ corresponds to the case where any arm has been flipped, $\mathcal{B}^i$.
-Furthermore, we consider the events in which the algorithm, making the decision, classifies arm $i$ as being above the threshold: $\mathcal{A}_i = \{i \in \hat{S}_\tau\}$.
-The event on which all arms are being classified as above the threshold is consequently given by $\mathcal{A} = \bigcap \mathcal{A}_i$.
-However, Theorem 1 does not bound the overall regret, but the maximum error probability on the $K+1$ different models.
-We can write this now as
-
-\begin{align}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big) \\
-& = \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
-\end{align}
-
-In order to give a bound on above equation, we start by considering $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$.
-This probability can be written as the expected change in the likelihood of observed data when moving from distribution $P_{\mathcal{B}_0}$ to $P_{\mathcal{B}_i}$, times the probability under the original state.
-In other words, the probability of event $\mathcal{A}_i$ under state $\mathcal{B}^i$ is given as the probability of $\mathcal{A}_i$ under the (original) state $\mathcal{B}^0$ multiplied by a factor.
-This factor describes whether the new distribution increases or decreases the probability of the event, and is given by the change in the data likelihoods due to moving from $\mathcal{B}^0$ to $\mathcal{B}^i$, expressed as the expected likelihood ratio under $\mathcal{B}^0$.
-By definition, the latter is equal to the empirical Kullback-Leibler divergence of the two distributions.
-
-We will define the change of distribution in terms of the empirical log-likelihood for our case.
-Then, we will show how to replace the log-likelihood by the empirical Kullback-Leibler divergence.
-So let us first introduce the empirical Kullback-Leibler divergence.
-
-Let every $\nu_i, \nu_i'$ be dominated by the Lebesgue measure $\lambda$.
-Then their density functions are given by $f_i = \frac{\der \nu_i}{\der \lambda}$ and $f_i' = \frac{\der \nu_i'}{\der \lambda}$ respectively.
-For $T \geq t \geq 0$, define the empirical Kullback-Leibler divergence as
-
-\begin{align*}
-\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log(\frac{\der \nu_k'}{\der \nu_k}(X_{k,s})) \\
-& = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
-& = \frac{1}{t} \log \big( \prod_{s=1}^{t} \frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
-& \stackrel{\text{iid}}{=} \frac{1}{t} \log \big( \frac{f_k'(X_{k,1}, \dots,X_{k,t})}{f_k(X_{k,1}, \dots,X_{k,t})} \big) \\
-& = \frac{1}{t} \log \big( \text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k) \big)
-\end{align*}
-
-Since we consider Gaussian distributions with variance 1, we have density functions $f_i(x) \propto \exp \big(-\frac{1}{2} (x-\Delta_i)^2\big)$ and $f_i'(x) \propto \exp \big(-\frac{1}{2} (x+\Delta_i)^2\big)$.
-Plugging this into the above definition of the empirical Kullback-Leibler divergence, we easily see
-
-\begin{align*}
-\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{\exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2\big)}{\exp \big(-\frac{1}{2} (X_{k,s}-\Delta_k)^2\big)} \big) \\
-& = \frac{1}{t} \sum_{s=1}^{t} \log \big( \exp(-\frac{1}{2} (X_{k,s}+\Delta_k)^2 + \frac{1}{2} (X_{k,s}-\Delta_k)^2) \big) \\
-& = - \frac{1}{t} \sum_{s=1}^{t} 2 X_{k,s} \Delta_k
-\end{align*}
-
-### Change of Distribution
-
-We are now ready to state the change of distribution.
-As alluded to above, we consider how the probability changes for the event $\mathcal{A}_i$ when we move from $\mathcal{B}^0$ to $\mathcal{B}^i$.
-When flipping arm $i$, we only changed the samples of this arm, that is, the first $T_i$ observations we got from arm $i$ the algorithm took.
-The change of distribution is then defined as:
-
-\begin{align*}
-\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \text{LR}((X_{i,1}, \dots,X_{i,T_i}), \nu_i', \nu_i) ] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ]
-\end{align*}
-
-Obviously, $\hat{\KL}_{i,T_i}$ depends on the realized samples $X_{i,1}, \dots,X_{i,T_i}$.
-Consequently, we need to find a bound on $\hat{\KL}_{i,T_i}$ itself to incorporate the uncertainty involved in this metric.
-
-### Concentration of the Empirical Kullback-Leibler Divergence
-
-For our problem, the Kullback-Leibler divergence of $\nu_k'$ from $\nu_k$ is given by $\KL_k := KL(\nu_k', \nu_k) = 2\Delta_k^2$.
-
-It is easy to see that
-
-\begin{equation*}
-|\hat{\KL}_{k,t} - \KL_{k,t}| = |-\frac{2}{t} \Delta_k \sum_{s=1}^{t}(X_{k,s} - \Delta_k)|
-\end{equation*}
-
-itself is a normally distributed random variable with mean zero and a variance decreasing in $t$.
-Thus, one can show as in Locatelli et al.
-(2016) that $\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4$ for the event
-
-\begin{equation}
-\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}}\}. \label{LocatelliTheorem1EventXi}
-\end{equation}
-
-Thus, in order to bound the empirical Kullback-Leibler divergence in our change of measure, we can consider the intersection of $\mathcal{A}_i$ and $\xi$ as follows and plug in the bound on event $\xi$:
-
-\begin{align*}
-\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
-\end{align*}
-
-Two things are left to do: With $T_i$, we still have one random variable left which we cannot leave in our bound.
-Second, we are actually not interested in $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$ but in $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$.
-
-### Bounding $T_i$ for $\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$
-
-Part of our bound is $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$, so let's continue with that.
-In general it holds that $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K}\sum_{i=1}^K X_i$.
-Thus we can write:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
-& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
-& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
-\end{align*}
-
-where the second line is again the intersection of $\mathcal{A}_i$ and $\xi$ as before in order to apply the change of distribution in the third line.
-
-What is left to show before we have our final bound is a bound on $T_i$.
-To show that any algorithm has a certain bound on its error, it only makes sense that every arm has to pulled at least a certain amount of times.
-Consequently, no arm should be pulled exclusively.
-
-First, let $a = \Delta_i \sqrt{T_i}$ and $b = 4\sqrt{\log((4\log(T)+1)K)}$. Then use $ab \leq a^2 + b^2$ to write $ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)$. And so:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) ]
-\end{align*}
-
-Furthermore, we know that the sum of the individual arm pulls has to be equal to the overall number of pulls (equal to the budget in the fixed budget sense), $\sum_i T_i = T$, and furthermore we know that $T_i>0$.
-The latter holds since any reasonable algorithm has to check each arm at least once in our setup.
-This is because we need to check each arm's performance in comparison to the threshold.
-Thus it is easy to show that $\exists i: T_i \leq \frac{T}{H \Delta_i^2} = \frac{T}{(\sum_{i=1}^{K} \Delta_i^{-2}) \Delta_i^2}$.
-To see this, assume the opposite: $\forall i: T_i > T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2}$.
-This implies however $\sum_{i=1}^K T_i > \sum_{i=1}^K T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2} = T \cdot 1 = T$ which is a contradiction.
-
-So we can write $(\Delta_i \sqrt{T_i})^2 \leq \frac{T}{H}$. We use $\mathcal{A} = \cap_{i=1}^K \mathcal{A}_i$ to write:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}{K} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big]
-\end{align*}
-
-We write $\frac{1}{K} \sum_{i=1}^K \exp(-3T_i \Delta_i^2) \geq \frac{1}{K} \sum_{i=1}^K \exp(-3 T/H) = \exp(-3 T/H)$. Thus:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i) \exp(-16 \log(4(\log(T)+1)K)) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
-& = \mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
-\end{align*}
-
-### Bringing everything together
-
-Consider again the risk which we need to bound from equation \eqref{LocatelliTheorem1ExpRegret}.
-We bound the maximum expected loss over all $\mathcal{B}_i$.
-By again using the fact that in general $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K} \sum_{i = 1}^K X_i$, we plug in our previous calculations:
-
-\begin{align}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \label{LocatelliTheorem1DefinitionOfRisk}
-\end{align}
-
-From \eqref{LocatelliTheorem1EventXi} we know that for any $i \in \{0, \dots, K\}$, $\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4$.
-Following the argument in Locatelli et al.
-(2016), we now consider two cases: $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2$ and $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2$.
-In the former case, we can plug in the two probabilities into \eqref{LocatelliTheorem1DefinitionOfRisk}.
-If $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2$ and $\mathbb{P}_{\mathcal{B}^0}(\xi) \geq 3/4$, then $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \geq 1/4$.
-Thus:
-
-\begin{align*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \\
-& \geq \frac{1}{8} \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
-\end{align*}
-
-where we drop the second summand of the second line so that the inequality holds.
-
-On the other hand, when $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2$, then we know that $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \leq 1/2$ for any $\mathbb{P}_{\mathcal{B}^0}(\xi)$.
-At the same time $1-\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \geq 1/2$.
-Consequently, $1/4 \leq \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \leq 1/2$, while
-$\frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) \geq 0$.
-And so the stronger lower bound in that case is, as noticed by Locatelli et al.
-(2016), given simply by
-
-\begin{align*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \\
-& \geq \frac{1}{2}
-\end{align*}
+A proof of the lower bound is given in the Appendix in \autoref{sec:AppendixAPTLB}.
+
+If we write the lower bound as $LB = 12(\log(T)+1)K)\exp(-3T/H)\exp(-4) = C_{LB}(\log(T)+1)K\exp(-T/H)$ and the upper bound as
+$UB = (\log(T)+1)K \exp(2) \exp(-\frac{1}{64R^2}\frac{T}{H}) = C_{UB}(\log(T)+1)K\exp(-T/H)$, we see that $LB$ and $UB$ match up to multiplicative constants and the $(\log(T)+1)K$ term which is negligiable in comparison with the exponent for large $T$ as shown in Locatelli et al.
+(2016), which makes the APT algorithm order optimal.
 
@@
 (2016).
-Before introducing a new algorithm for the thresholding bandit problem based on Kullback-Leibler divergences in \autoref{sec:LikelihoodRatioForExponentialFamily}, we first describe the variance-based approaches in \autoref{chap:VarianceBasedAlgorithms}.
+Before introducing a new algorithm for the thresholding bandit problem based on Kullback-Leibler divergences in \autoref{sec:LikelihoodRatioForExponentialFamily}, we first describe the variance-based approaches in \autoref{sec:VarianceBasedAlgorithms}.
 
@@
 
-# Kullback-Leibler Complexity of Pure Exploration \label{chap:KullbackLeiblerPureExploration}
-
-In the previous chapter, we discussed the thresholding bandit problem as presented in Locatelli et al.
+# Information Theoretic Complexity of Pure Exploration Bandits \label{chap:KullbackLeiblerPureExploration}
+
+The previous chapter introduces the thresholding bandit problem as described in Locatelli et al.
+(2016), and with the APT strategy a first algorithm that is simple, yet order-optimal for large budgets.
+However, we end with the conclusion that a distance measure between the distributions and the threshold based on the Kullback-Leibler divergence might be more useful than the simple gap $\Delta^2_i = (\mu_i - \tau_i)^2$ employed so far.
+Indeed, citing Kaufmann et al.
+(2016), we note that the complexity $H$ used so far can be considered a sub-Gaussian approximation of a better complexity measure based on information theoretic measures like the Kullback-Leibler divergence.
+
+In order to give more intuition to why that is the case, and in what ways information theoretic measures can be introduced to measure the complexity of bandit problems, we now turn to Kaufmann et al.
+(2016) and Garivier and Kaufmann (2016).
+The latter describes a strategy based on Kullback-Leibler divergences for the best-arm identification problem, while the first derives complexity measures based on the divergence.
+Ideally, their work offers methods that can inform our work of extending the thresholding bandit problem.
+In what follows, we adopt the notation of Kaufmann et al.
+(2016) to ease a comparison with their arguments.
+
+## Complexity Measures for Best-Arm and Top-*m* Identification \label{sec:KaufmannEtAl2016}
+
+Instead of the thresholding bandit problem, Kaufmann et al.
+(2016) consider the problem of identifying the best $m$ out of $K$ arms, that is, the Top-$m$ problem.
+They describe their a bandit model $\nu$ also by $K$ arms characterized by probability distributions $\nu_a$, $a \in \{1,...,K\}$ with mean $\mu_a$.
+As before, a learner decides at any time step $t=1,2,...,$ an arm $A_t \in \{1,...,K\}$ for which he observes the independent reward $Z_{t} \sim \nu_{A_t}$.
+The learner aims to find the $m$ out of $K$ arms with the largest expected reward.
+This set of arm indices is denoted by $\mathcal{S}_m^*$.
+Kaufmann et al.
+write the in decreasing order sorted means $(\mu_{1}, ..., \mu_{K})$ as the K-tuple $(\mu_{[1]}, ..., \mu_{[K]})$.
+Based on this, they require that $\mu_{[m]} > \mu_{[m+1]}$ such that the solution $\mathcal{S}_m^*$ is unique.
+The class of bandit problems $\nu$ for which the latter condition holds is called $\mathcal{M}_m$ by Kaufmann et al.
+At the end of the sampling procedure, after $T$ samples (denoted by $\tau$ in Kaufmann et al.) the learner is required to return a classification $\hat{\mathcal{S}}_m$.
+This classification is then evaluated by the loss function $\mathcal{L}(T) = \mathbb{I}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m)$.
+This binary loss is of course very similar to the loss in the thresholding bandit problem.
+We can now define a strategy of the learner as $\mathcal{A} = ((A_t), T, \hat{\mathcal{S}}_m)$: The strategy defines how he chooses an arm, how many samples are observed, and how the arms are classified in the end.
+
+When introducing the thresholding bandit setting, we did not mention the fact that the budget $T$ does not need to be fixed upfront.
+Indeed, the setting in which the budget is *not* fixed upfront might be more popular among the best arm identification and top-$m$ literature.
+This setting is called *fixed-confidence*, while the setting we considered so far is called *fixed-budget*.
+In the fixed-budget setting, we run algorithms for $T$ samples and then compare them based on their expected loss, $\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m) =: p_t(\nu)$ as we have seen in $\autoref{sec:Setup}$.
+Alternatively, consider a $\delta$-PAC strategy $\mathcal{A}(\delta)$for which holds for every problem $\nu \in \mathcal{M}_m$ that the classification holds at least with confidence level $1-\delta$, that is, $\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta$.
+The strategy has to achieve this level of confidence in its prediction before it is allowed to stop sampling.
+This is the fixed-confidence case, in which the budget $T$ is no longer fixed upfront, but becomes a random variable.
+We compare algorithms by their expected number of draws $\mathbb{E}_{\nu}[T_{\delta}]$ and prefer those which arrive at the confidence level $1-\delta$ with a smaller expected budget.
+
+Following Kaufmann et al.
+(2016), in the fixed confidence setting, a family of strategies $A = (\mathcal{A}(\delta))_{\delta \in (0,1)}$ is called PAC if for every $\delta$, $\mathcal{A}(\delta)$ is $\delta$-PAC.
+On the other hand, in the fixed budget setting, a family of strategies $A = (\mathcal{A}(t))_{t \in \mathbb{N}}$ is called consistent if $p_t(\nu) \rightarrow 0$ as $t \rightarrow \infty$ for every problem $\nu \in \mathcal{M}_m$.
+
+Given this setup, we can now follow the arguments of Kaufmann et al.
+(2016) to deduce complexity measures for the top-$m$ problem.
+As alluded to earlier, these complexity measures will rely on the Kullback-Leibler divergence in contrast to the complexity $H$ used by Locatelli et al.
 (2016).
-Doing so, we came across the complexity term $H = \sum_{i=1}^{K} \Delta_i^{-2}$.
-Furthermore, we noted the fact that an algorithm and bounds based on *only* the gap between the respective mean and the threshold are useful in the case of sub-Gaussian problems.
-Furthermore, even for the case of Bernoulli arms, which are sub-Gaussian since their feedback is bounded on $[0,1]$, the gap $\Delta$ becomes less and less appropriate in situations in which both $\mu$ of the Bernoulli, and $\tau$ are very close to 0 or 1.
-
-Even though the complexity $H$ enjoys popularity in the literature of the best $m$ arm identification problem, $m \geq 1$, Kaufmann et al.
-(2016) show explicitly that $H$ is mainly useful for problems of Gaussian distributions.
-Indeed, they go so far as to define new measures of complexity that are based on information theoretic measures.
-Using these, they then frame $H$ as an approximation to their measures in the case of Gaussian distributions.
-This underlines the fact that Bernoulli distributions with small means have to be treated differently than Gaussian distributions.
-
-For the current chapter, we adopt the notation of Kaufmann et al. (2016) to ease a comparison with their arguments.
-
-## Complexity of Best-Arm and Top-*m* Identification
-
-Instead of the thresholding bandit problem, we now consider the problem of identifying the best $m$ out of $K$ arms, that is, the Top-$m$ problem.
-While we previously looked at a fixed budget formulation, we now mainly focus on a fixed confidence problem: We hold the confidence $1-\delta$ fixed at which a strategy returns the correct $m$ arms while trying to reach this confidence in a way that minimizes the sample complexity $\mathbb{E}_{\nu}[\tau]$, that is, the expected number of overall draws of the arms.
-$\tau$ is also called the stopping time of the algorithm.
-The goal of algorithms is to identify $\mathcal{S}_m^*$, the set of the $m$ arms with the largest means.
-If we let $(\mu_1, \dots, \mu_K)$ be the vector of the means of the arms, then let $(\mu_{[1]}, \dots, \mu_{[K]})$ be the tuple in which the means are arranged in decreasing order.
-For the rest of this chapter, we consider only settings with arms for which $\mu_{[m]} > \mu_{[m+1]}$; we demand the set of the top $m$ arms, $\mathcal{S}_m^*$, to be unique.
-After the sampling phase, we require any algorithm to return the set $\hat{S}_m \subset \{1,\dots,K\}$ of $m$ arms that the algorithm believes to have the largest means.
-In the case of fixed confidence, we fix $\delta$ at the beginning, such that the algorithm only stops sampling when $\mathbb{P}_{\nu}(\hat{S}_m = \mathcal{S}_m^*) \geq 1-\delta$.
-We try to find algorithms who fulfill this condition as quickly as possible.
-Algorithms which minimize the expected stopping time (or number of draws), $\mathbb{E}_{\nu}[\tau]$.
-
-To arrive at the new measure of complexity proposed by Kaufmann et al.
-(2016), it will actually make sense to first follow their arguments to a general lower bound on the sample complexity $\mathbb{E}_{\nu}[\tau]$ in the case of fixed confidence problems.
+Also, when discussing $H$, we so far described it as complexity as it measures the difficulty of the problem by measuring the distance between arms and the threshold.
+Kaufmann et al.
+approach complexity instead from how many samples (what error probability) one can expect to need in the fixed confidence (fixed budget) setting.
+Thus, in order to arrive at their new measure of complexity, it makes sense to first follow their arguments to a general lower bound on the sample complexity $\mathbb{E}_{\nu}[\tau]$ in the case of fixed confidence top-$m$ problems.
 This bound is given in their Theorem 4 (for common confidence levels of $\delta \leq 0.15$).
@@
 This brings the big advantage that the Kullback-Leibler divergence becomes symmetric, and the feedback can take values on all $\mathbb{R}$.
-And by using the complexity measure $H(\nu)$, it is also clear that there exists an arm that is undersampled with respect to its contribution to the overall complexity of the problem (or sampled exactly according to its contribution), which leads to leads to a convenient upper bound on this arms number of draws which is again employed in both the proof of Theorem \ref{theorem:KaufmannEtAlTheorem17} and in Locatelli et al.
+And by using the complexity measure $H(\nu)$, it is also clear that there exists an arm that is undersampled with respect to its contribution to the overall complexity of the problem (or sampled exactly according to its contribution), which leads to a convenient upper bound on this arms number of draws which is again employed in both the proof of Theorem \ref{theorem:KaufmannEtAlTheorem17} and in Locatelli et al.
 (2016).
@@
 Given a lower bound adapted to the new complexity $H^{\text{EVT}_{pf}}$, the Zhong et al.
-(2017) show that the EVT$_pf$ algorithm is optimal in that its upper bound matches the lower bound.
+(2017) show that the EVT$_{pf}$ algorithm is optimal in that its upper bound matches the lower bound.
 Furthermore, they compare their algorithm in experiments against the APT algorithm.
@@
 Interestingly, they report the largest advantage of their variance based algorithms in comparison to APT when the variances are very small; given they only consider problems bounded on a support of $[0,1]$, $\sigma_i \ll 1$.
-In this case the problem complexity $H^{\text{EVT}_{pf}}$ can be much smaller than $H^{APT}$ -- the EVT algorithm profits more from distributions that are simple to estimate in terms of their variance than the APT algorithm does.
+In this case the problem complexity $H^{\text{EVT}_{pf}}$ can be much smaller than $H^{APT}$ -- the EVT$_{pf}$ algorithm profits more from distributions that are simple to estimate in terms of their variance than the APT algorithm does.
 
@@
 \begin{align*}
--\log(LR_T(\theta_{H_0}|| \theta_{H_1}) & = & \sum_{i=1}^T \log(\frac{q(x_s|\theta_{H_0})}{ q(x_s|\theta_{H_1})}) \\
-& = & \sum_{a \in \chi} T q(a|\hat{\theta}) \log(\frac{q(a|\theta_{H_0})}{ q(a|\theta_{H_1})}) \\
-& = & \sum_{a \in \chi} T q(a|\hat{\theta}) \log(\frac{q(a|\theta_{H_0})}{ q(a|\theta_{H_1})}\frac{q(a|\hat{\theta})}{ q(a|\hat{\theta})}) \\
-& = & T \KL(q(\hat{\theta})||q(\theta_{H_0})) - T \KL(q(\hat{\theta})||q(\theta_{H_1})),
+-\log(LR_T(\theta_{H_0}|| \theta_{H_1}) & = \sum_{i=1}^T \log(\frac{q(x_s|\theta_{H_0})}{ q(x_s|\theta_{H_1})}) \\
+& = \sum_{a \in \chi} T q(a|\hat{\theta}) \log(\frac{q(a|\theta_{H_0})}{ q(a|\theta_{H_1})}) \\
+& = \sum_{a \in \chi} T q(a|\hat{\theta}) \log(\frac{q(a|\theta_{H_0})}{ q(a|\theta_{H_1})}\frac{q(a|\hat{\theta})}{ q(a|\hat{\theta})}) \\
+& = T \KL(q(\hat{\theta})||q(\theta_{H_0})) - T \KL(q(\hat{\theta})||q(\theta_{H_1})),
 \end{align*}
@@
 
-### Likelihood Ratio for Univariate Exponential Family of Distributions
+### Likelihood Ratio for Univariate Exponential Family of Distributions \label{sec:LRforUnivariateExponentialFamily}
 
@@
 \begin{align*}
--\log(LR(\mu_0||\mu_1)) & = & n(\log\Big(\frac{1-\mu_0}{1-\mu_1}\Big)) - \Big(\log(\frac{\mu_0}{1-\mu_0}) - \log(\frac{\mu_1}{1-\mu_1})\Big)\sum_{i=1}^{n}x_i \\
-& = & n \Big( (1-\hat{\mu})\log\Big(\frac{1-\mu_1}{1-\mu_0}\Big) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}) \Big)
+-\log(LR(\mu_0||\mu_1)) & = n(\log\Big(\frac{1-\mu_0}{1-\mu_1}\Big)) - \Big(\log(\frac{\mu_0}{1-\mu_0}) - \log(\frac{\mu_1}{1-\mu_1})\Big)\sum_{i=1}^{n}x_i \\
+& = n \Big( (1-\hat{\mu})\log\Big(\frac{1-\mu_1}{1-\mu_0}\Big) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}) \Big)
 \end{align*}
@@
 & = T_i(t) \Big( \mathbb{I}(\hat{\mu}\geq \tau)\cdot KL(\nu_{b'^{-1}(\hat{\mu}(t))}||\nu_{b'^{-1}(\tau-\epsilon)}) \\
-& \quad +\: \mathbb{I}(\hat{\mu} < \tau)\cdot KL(\nu_{b'^{-1}(\hat{\mu}(t))}||\nu_{b'^{-1}(\tau+\epsilon)}) \Big) \Alignyesnumber\label{eqn:SLRIndex}.
+& \quad \quad +\: \mathbb{I}(\hat{\mu} < \tau)\cdot KL(\nu_{b'^{-1}(\hat{\mu}(t))}||\nu_{b'^{-1}(\tau+\epsilon)}) \Big) \Alignyesnumber\label{eqn:SLRIndex}.
 \end{align*}
@@
 In the case of Normal distributions with unknown mean and unknown variance, given that the variance and mean estimate are linked, we can use $H_0: \mu = \tau \land \sigma^2 = \sigma^2_{\tau} = \frac{1}{n}\sum_{i=1}^{n}(x_i-\tau)^2$ and the alternative hypothesis based on the maximum likelihood estimates $H_1: \mu = \hat{\mu} \land \sigma^2 = \hat{\sigma}^2 = \frac{1}{n}\sum_{i=1}^{n}(x_i-\hat{\mu})^2$.
-
-In the following, we assume $\epsilon = 0$.
-
-Now, at each round $t$, the algorithm computes $T_i(t)$ and $\hat{\mu}_i(t)$ as before, and additionally the empirical variances $\sigma_{\tau,i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\tau)^2$ and $\hat{\sigma}_{i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\hat{\mu})^2$.
-The index is then given by
+In the following, we assume $\epsilon = 0$ for simplicity.
+
+At each round $t$, the algorithm computes $T_i(t)$ and $\hat{\mu}_i(t)$ as before, and additionally the empirical variances $\sigma_{\tau,i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\tau)^2$ and $\hat{\sigma}_{i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\hat{\mu})^2$, where $\hat{\sigma}_{i}^2(t) < \sigma_{\tau,i}^2(t)$ if $\hat{\mu} \neq \tau$ since $\hat{\mu}$ is the maximum likelihood estimate.
+The index is then
 
@@
 & = T_i(t) \log\Big(\frac{\sigma_{\tau,i}^2(t)}{\hat{\sigma}_i^2(t)}\Big) \\
-& = T_i(t) \KL\big(N(\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t))||N(\tau, \sigma_{\tau,i}^2(t))\big)
+& = T_i(t) \KL\big(N(\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t))||N(\tau, \sigma_{\tau,i}^2(t))\big) \Alignyesnumber\label{eqn:SLR2DIndex}
 \end{align*}
 
-Then, as for the univariate case, the next arm to be pulled is the minimizer of the index $B_i^{2DSLR}(t+1)$, $I_{t+1} = \arg \min_{i \leq K} B_i(t+1)$.
+Then, as for the univariate case, the next arm to be pulled is the minimizer of the index $B_i^{SLR_{2D}}(t+1)$, $I_{t+1} = \arg \min_{i \leq K} B_i(t+1)$.
 At the end of the horizon $T$, the algorithm outputs the set of arms $\hat{S}_\tau = \{i \in \mathbb{A}, \hat{\mu}_i(T) \geq \tau\}$.
 
-### Discussion
+\IncMargin{1em}
+\begin{algorithm}
+\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
+\Input{\emph{$\tau$, $\epsilon$, $\nu(\mu, \theta) = N(\mu,\sigma^2) \, \forall i \in \mathbb{A}$, where $\mu$ and $\sigma^2$ are unknown}}
+\Output{$\hat{S}_\tau = \{i \in \mathbb{A},  \hat{\mu}_i(T) \geq \tau\}$}
+\BlankLine
+\emph{Pull each arm twice}\;
+\For{$t = 2K+1$ \KwTo $T$}{
+\For{$i = 1$ \KwTo $K$}{
+  \emph{Compute $\hat{\sigma}^2_{i}(t)$}\;
+  \If{$\hat{\sigma}^2_{i}(t) = 0$}{\emph{Set $\hat{\sigma}^2_{i}(t) = 1/T$}}
+}
+  \emph{Pull arm $I_t = \arg \min_{i\leq K} B_i^{SLR_{2D}}(t)$ as in \autoref{eqn:SLR2DIndex}}\;
+  \emph{Observe reward $X \sim \nu_{I_t}$}\;
+}
+\caption{2D-SLR algorithm for Normal distributions with unknown mean and unknown variance}\label{algo_slr_2d}
+\end{algorithm}\DecMargin{1em}
+
+## Discussion
 
 At the beginning of this thesis, we set out to find an algorithm that improves upon the Anytime Parameter Free algorithm introduced in Locatelli et al.
-(2016) for the thresholding bandit problem in two directions.
-First, we wanted to make the algorithm perform better in problems that are not well approximated as sub-Gaussian; that is, in particular a problem with Bernoulli arms with small means and low threshold.
-Unsurprisingly, this meant that we need to find a solution that takes more into account than just the sample mean.
-With the Simple Likelihood Ratio strategy, we propose an algorithm that fulfills that goal at the cost of being distribution specific.
-
-The Simple Likelihood Ratio strategy requires the knowledge of the class of distribution upfront, just as other algorithms require parameters.
-While this is likely to be a negligiable problem in the case of $\{0,1\}$ observations which can be modeled reasonably by Bernoulli distributions if we are only interested in estimating the mean, it can be more difficult to know the true class of distribution upfront when the random variables can take values in $\mathbb{R}$.
+(2016) for the thresholding bandit problem in two points.
+First, we wanted to make the algorithm perform better in problems with arms that are not well approximated as sub-Gaussian; in particular a problem with Bernoulli arms of small means, and with a threshold close to 0.
+We thus tried to find a strategy that takes more information about the arms into account than purely the sample mean.
+With the Simple Likelihood Ratio strategy, we propose an algorithm that fulfills this goal at the cost of being distribution specific.
+
+The SLR strategy requires the knowledge of the class of distribution upfront, just as other algorithms require parameters.
+While this is likely to be a negligiable problem in the case of $\{0,1\}$ observations whose mean can be modeled reasonably by Bernoulli distributions, it can be more difficult to know the true class of distributions upfront when $\nu_i$ are continuous distributions.
 We have shown however, that the SLR strategy can be adapted to all univariate distributions in the exponential family of distributions.
@@
 
-Furthermore, the Simple Likelihood Ratio strategy reduces to the Anytime Parameter Free strategy in the case where arms are normally distributed with equal variance that is known upfront.
+Furthermore, the SLR strategy reduces to the APT strategy in the case where arms are normally distributed with equal variance that is known upfront.
 In that case we have as index (compare example 3 above):
-
 $$
@@
 
-$$
-B_i^{SLR}(t) < B_j^{SLR}(t) \Leftrightarrow 
-T_i(t)\frac{(\hat{\mu}_i(t) - \tau)^2}{2\sigma^2} < T_j(t)\frac{(\hat{\mu}_j(t) - \tau)^2}{2\sigma^2} 
-\Leftrightarrow 
-\sqrt{T_i(t)}\sqrt{(\hat{\mu}_i(t) - \tau)^2} < \sqrt{T_j(t)}\sqrt{(\hat{\mu}_j(t) - \tau)^2}
-\Leftrightarrow 
+\begin{align*}
+B_i^{SLR}(t) < B_j^{SLR}(t) & \Leftrightarrow 
+T_i(t)\frac{(\hat{\mu}_i(t) - \tau)^2}{2\sigma^2} < T_j(t)\frac{(\hat{\mu}_j(t) - \tau)^2}{2\sigma^2} \Alignyesnumber\label{eqn:SLRWithKnownVar}\\
+& \Leftrightarrow 
+\sqrt{T_i(t)}\sqrt{(\hat{\mu}_i(t) - \tau)^2} < \sqrt{T_j(t)}\sqrt{(\hat{\mu}_j(t) - \tau)^2} \\
+& \Leftrightarrow 
 B_i^{APT}(t) < B_j^{APT}(t)
-$$
-
-Given that in all other cases the Simple Likelihood Strategy is able to take more information about the distributions into account through the Kullback-Leibler divergence (in the case of the exponential family of distributions), the algorithm is expected to improve upon the Anytime Parameter Free strategy.
+\end{align*}
+
+Given that in all other cases the SLR is able to take more information about the distributions into account through the Kullback-Leibler divergence (in the case of the exponential family of distributions), the algorithm is expected to improve upon the APT strategy.
+Just consider a situation of known, but different variances for Normal distributions.
+Then we had in \autoref{eqn:SLRWithKnownVar} $\sigma_i^2$ and $\sigma_j^2$ instead of $\sigma^2$, which should lead to more pulls of the arm with larger variance.
+This is not taken into account by APT.
 
 As mentioned before, this improvement comes only at the cost of knowing the correct distribution upfront.
-In particular, as for the Anytime Parameter Free algorithm, there are no parameters which would need to be tuned upfront as is usually the case for upper-confidence bound based algorithms.
-
-Additionally, the Simple Likelihood Strategy offers an intuitive interpretation if we consider the index written in the form proposed by Zhang et al. (2017). Write the index again as
-
+In particular, as for the APT algorithm, there are no parameters which need to be tuned upfront as is usually the case for upper-confidence bound based algorithms (see for example UCB-E in Audibert et al., 2010).
+
+Additionally, the index used in the SLR algorithm offers the same interpretation considered in \autoref{sec:EVTAlgorithm}. Write the index again as
 $$
@@
 $$
-
 where $S_i(t)$ is a confidence term of the estimate of the arm $i$ at time $t$, and $D_i(t)$ is a measure of distance between the distribution of arm $i$ and the threshold $\tau$.
 The index of the Simple Likelihood Ratio strategy for univariate exponential family distributions can then be written with
-
-$$
-S_i(t) = T_i(t)
-$$
-
-and
-
-$$
+$$
+S_i(t) = T_i(t) \quad \text{and} \quad
 D_i(t) = \KL(\hat{\mu}_i(t)||\tau),
 $$
-where we employ the number of pulls so far for a given arm as the confidence measure, while the Kullback-Leibler divergence fulfills its role as distance between distributions.
-The larger the KL-divergence, the less inclined we are to draw the arm; the same holds, if we have pulled an arm many times.
+where we employ the number of pulls so far for a given arm as the confidence measure, while the Kullback-Leibler divergence fulfills its role as distance measure between distributions (see also Figure 2).
+The larger the Kullback-Leibler divergence, the less inclined we are to draw the arm; the same holds, if we have pulled an arm many times.
 Since the KL-divergence reduces to the squared distance between means for Normal distributions of known variance, the SLR and APT algorithms are identical in this case.
 
-As we see in the experiments that follow, the Simple Likelihood Strategy is able to improve significantly upon the Anytime Parameter Free strategy in many cases.
+As we see in the experiments that follow, the SLR strategy is able to improve significantly upon the APT strategy in many cases.
 
@@
 
+We now compare the algorithms introduced in the previous chapters in simulations and experiments against each other to evaluate their performance.
+We first perform experiments on synthetic data in \autoref{sec:SyntheticData}.
+We then use Bernoulli time series data collected by the online shop Amorelie to evaluate the algorithms on real world data in \autoref{sec:RealData}.
+
+We compare the empirical performance of the SLR algorithm not only against the APT algorithm, but also against the variance-based algorithms.
+Thus we also compare the variance-based algorithms for the first time directly against each other.
+As benchmark, the uniform sampling strategy is included.
+Additionally, we include the Bayes-UCB algorithm introduced in Kaufmann et al.
+(2012) for the cumulative regret setting.
+See \autoref{sec:AppendixBUCB} in the appendix for how their Algorithm 1 is adapted to the thresholding bandit problem.
+
 ## Synthetic Data \label{sec:SyntheticData}
 
-In order to evaluate the empirical performance of the proposed algorithms, we run the algorithm on synthetic data as is usual.
-We compare its performance on this data not only against the APT algorithm, but also against the variance-based algorithms.
-Thus we also compare the variance-based algorithms for the first time directly against each other instead of just relative to the APT algorithm.
-
-Each of the experiments is repeated for 5000 iterations.
-Depending on the experiment, the observations are generated randomly by some distribution of the exponential family of distributions.
-As we were originally concerned with improving upon APT with respect to non-sub-Gaussian distributions, the first experiments focus on Bernoulli distributions, and especially those with small means.
-We then go on to show with experiments on Gaussian, Exponential, and Poisson data that the SLR algorithm is able to improve upon APT given that we know the true kind of distribution.
-
-### Experiment 1: Bernoulli with $\tau = 0.5$
+Every experiment presented is repeated for 5000 iterations.
+Depending on the experiment, the observations are generated randomly by a given exponential family of distributions.
+As we are primarily concerned with improving upon APT with respect to non-sub-Gaussian distributions, the first three experiments focus on Bernoulli distributions, especially those with small means.
+We then go on to show with experiments on data from the Exponential distribution and Poisson distribution that the SLR algorithm is able to improve upon APT given that we know the true kind of distribution.
+
+### Simulation 1: Bernoulli with $\tau = 0.5$
 
@@
 We compare ten Bernoulli arms that move away from the threshold at $\tau = 0.5$ geometrically with $\mu_{1:4} = 0.4-0.2^{1:4}$, $\mu_5 = 0.45$, $\mu_6 = 0.55$, and $\mu_{7:10} = 0.6 + 0.2^{5-1:4}$.
-We run the standard APT algorithm with $\epsilon = 0.1$, as well as SLR with $\epsilon = 0.1$.
-We compare those additionally to Augmented-UCB with the standard parameter choice of $\rho = 1/3$ as used by its authors in Mukherjee et al.
+We run the standard APT algorithm as well as the SLR algorithm with $\epsilon = 0.1$.
+We compare them to the AugUCB algorithm with the parameter choice of $\rho = 1/3$ as used by its authors in Mukherjee et al.
 (2017).
-We run the parameter-free version of the Empirical Variance Guided algorithm without any feedback delay, thus making it directly comparable to the other algorithms.
-The Bayes-UCB algorithm takes as prior a Beta distribution with parameters $\alpha_0 = \tau$ and $\beta_0 = 1 - \tau$, thus leading to a mean of the prior distribution at $\tau$ while keeping the prior as weak as possible.
-Lastly, we run the uniform sampling strategy as the naive benchmark.
+We run the parameter-free EVT$_pf$ algorithm without feedback delay, thus making it directly comparable to the other algorithms.
+The Bayes-UCB algorithm takes as prior a Beta distribution with parameters $\alpha_0 = \tau$ and $\beta_0 = 1 - \tau$, thus leading to a mean of the prior distribution at $\frac{\alpha_0}{\alpha_0+\beta_0}=\tau$ while keeping the prior as weak as possible.
+Lastly, we run the uniform sampling strategy as a benchmark.
 
@@
 
-This first experiment gives an experiment where all algorithms should perform well.
-The problem is not very difficult, and due to the threshold at $\tau = 0.5$, the Bernoulli distribution can be perfectly approximated by a Gaussian.
+This first experiment is a problem in which all algorithms should be able to perform well.
+The problem is not very difficult, and due to the threshold at $\tau = 0.5$, the Bernoulli distribution can be well approximated by a Gaussian.
 This thus is the perfect environment for the APT algorithm.
 
-As the next figure shows, essentially all methods converge rapidly to an error rate of zero.
-Except for the uniform method that clearly lacks behind.
-We also observe that the variance based algorithms (Augmented UCB and EVT) lag behind at first.
-Augmented UCB is able to adjust its sampling scheme after 1000 iterations and rapdily improves to the level of APT.
+As the next figure shows, essentially all methods converge rapidly to an error rate of very close to zero.
+That is, except for the uniform strategy that clearly lacks behind.
+We also observe that the variance based algorithms (AugUCB and EVT) lag behind at first.
+AugUCB is able to adjust its sampling scheme only after 1000 iterations but then rapdily improves to the level of APT.
 EVT takes about 250 samples more to start a quick descend to the performance of the other algorithms.
-All of this, however, happens below an error rate of 0.01.
+All of this, however, happens after the algorithms are below an error rate of 0.01.
 While the SLR algorithm improves upon APT, the improvement is a slight one, and not very large in terms of budget difference.
-This underlines that the scenario at hand is the ideal one for the APT algorithm.
-
-```{r simulation1_results, echo = FALSE, fig.align = "center", out.width = '80%'}
+This underlines that the scenario at hand is ideal for the APT algorithm.
+
+```{r simulation1_results, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for simulation 1."}
 library(ggplot2)
@@
 
-### Experiment 2: Bernoulli with $\tau = 0.05$
+### Simulation 2: Bernoulli with $\tau = 0.05$
 
 In the second experiment, we compare the same algorithms as in the first experiment.
-Again, we classify 10 arms, but this time against a threshold of $\tau = 0.05$ and without an epsilon interval, $\epsilon = 0$.
-Consequently, we choose the distributions for the arms to be much smaller too, and arrange them symmetrically around the threshold.
+Again, we classify 10 arms, but this time against a threshold of $\tau = 0.05$ and without an epsilon interval, $\epsilon = 0$ (which generally rewards algorithms for pulling arms close to the threshold).
+We choose the means of the arms to be much smaller too, and arrange them symmetrically around the threshold.
 While the distributions are bounded and thus still sub-Gaussian, the Normal approximation should be poor in comparison to the previous case.
 We expect an improvement for the SLR algorithm compared to APT as it takes the Bernoulli characteristics into account.
-For example, even though the arms are symmetrically distributed around the threshold in terms of absolute distance, they are not symmetrically around the threshold in terms of their Kullback-Leibler divergence given the threshold is unequal 0.5.
-Thus we expect the SLR algorithm to not pull them equally.
-Furthermore, we expect an improvement for the variance-based algorithms, as the variances are now smaller than in experiment 1, which should at least benefit the EVT algorithm given its theoretical analysis.
+In particular, even though the arms are symmetrically distributed around the threshold in terms of absolute distance, they are not symmetrically around the threshold in terms of their Kullback-Leibler divergence (compare Figure 2).
+Thus we expect the SLR algorithm to not pull them symmetrically.
+Furthermore, we expect an improvement for the variance-based algorithms, as the variances are now smaller than in experiment 1, which should at least benefit the EVT algorithm given its theoretical analysis in Zhong et al.
+(2017).
+
+```{r loc6nt_data_summary, echo = FALSE, message = FALSE}
+mean_loc6nt <- c(0.001, 0.005, 0.01, 0.015,
+                 0.04, 0.06,
+                 0.085, 0.09, 0.095, 0.099)
+
+knitr::kable(t(mean_loc6nt), digits = 3, col.names = paste0("V", 1:10), caption = "Mean of arms in simulation 2 classified against threshold of 0.05.")
+```
 
@@
 We see that the problem appears to be significantly more difficult in general.
-The variance based algorithms perform maybe surprisingly bad; EVT even worse than uniform sampling nearly until the horizon, while Augmented UCB takes a long time to adjust away from uniform sampling.
-Both algorithms perform worse than APT after 7000 rounds.
+The performance of the variance based algorithms is surprisingly poor; EVT performs even worse than uniform sampling nearly until the horizon, while Augmented UCB takes a long time to adjust away from uniform sampling.
+Both algorithms perform worse than APT after 7000 samples.
 One potential reason for this might be the fact that the index used by the EVT algorithm reduces to $B_i^{EVT}(t) = \sqrt{T_i(t)} \cdot \sqrt{|\hat{\mu}_i(t) - \tau|}$ if $\hat{\sigma}_i^2(t) = 0$, which, given Bernoulli arms with small means, could be the case for long runs of the algorithm.
-In contrast, the index of the APT algorithm is  $B_i^{APT}(t) = \sqrt{T_i(t)} \cdot |\hat{\mu}_i(t) - \tau|$.
-
-One interesting observation, that we will observe in all experiments with synthetic Bernoulli arms, is the superior performance of the Bayes-UCB algorithm adapted from Kaufmann and Kalyanakrishnan (2013) which was originally designed for cumulative regret problems.
+This seems suboptimal given the index of the APT algorithm is $B_i^{APT}(t) = \sqrt{T_i(t)} \cdot |\hat{\mu}_i(t) - \tau|$.
+
+One interesting observation, that we will observe in all experiments with synthetic Bernoulli arms, is the superior performance of the Bayes-UCB algorithm adapted from Kaufmann et al.
+(2012) which was originally designed for cumulative regret problems.
 Nonetheless, the algorithm will again and again proof to be the best performing.
+Compare with \autoref{sec:AppendixBUCB} for more analysis on the behavior of the Bayes-UCB algorithm on simulation 2.
+In particular, consider Figures 17 and 18 which show for individual arms, the distribution of pulls for that arm across simulations.
+These distributions highlight that both the APT and SLR fail in many iterations of the simulations to pull arms frequently enough to estimate their correct mean.
+The APT algorithm pulls the most difficult arm (Arm 6) in more than 5% of the simulations only once (during initialization).
+Consider arm 6 returns $X_{6,1} = 1$ as its first observation.
+Then $B_6(t+1) = 1 \cdot |1-0.05| = 0.95$.
+It will then not be pulled for a long time because the index is very large.
+Indeed, consider some arm that has been pulled 4000 times with $\mu_i(4000) = 0.03$.
+Then $B_i(t+1) = \sqrt{2000} \cdot |0.05-0.03| \approx 0.89$.
+Then even though we have basically no evidence for the performance of arm $6$, we would continue to pull arm $i$.
+Similar holds for the SLR algorithm.
+For both, the distribution of pulls for arm 6 is very flat across the interval of $[1,6000]$ pulls.
+In contrast, the distribution of pulls looks normally distributed for the Bayes-UCB algorithm with the mode between 2100 and 2300 pulls.
+The numerical problem that can arise for the APT and SLR algorithms might be weakened by the combination of a (weak) prior that shrinks the mean estimates, and the way in which quantiles are based on the posterior.
+Similar distributions are also reported for arms 1 and 10 in the appendix.
 
 While the Bayes-UCB performance is impressive, we observe that also the Simple Likelihood Ratio strategy improves considerably upon the alternative strategies.
-SLR reaches the average empirical error of 0.1 within the budget, and the improvement is exponential within the entire budget; in contrast to APT which appears to improve linearly in the observations.
+SLR reaches the average empirical error of 0.1 within the budget, and it improves at an exponential rate within the entire budget; in contrast to APT which appears to improve linearly in the observations.
 At the end of the budget, the difference in the empirical error is nearly 10% between the two strategies.
 
-In order to assess how the SLR strategy improves upon the APT algorithm, we can use the fact that we have run the experiment for 5000 iterations.
-We thus can look at how often each arm was pulled by a strategy at any given round.
+In order to assess how the SLR strategy improves upon the APT algorithm, it is useful to look at how often the algorithm pulls each arm.
+Given that we run the simulation 5000 times, we can compare across simulations how often an algorithm pulls each arm at a given round.
 Across the 5000 iterations, the algorithm should pull at any given iteration the arm most often that it thinks is the most difficult to classify.
-In the figure below, we plot the resulting curves where the value at an iteration is the 10-round moving average to remove some unimportant variation.
-
-We see that both APT and SLR correctly single out the two arms that are much closer to the threshold than the remaining arms and allocate most of the budget to them.
+In the figure below, we plot the resulting curves where the value at an iteration is the 10-round moving average to remove some variation.
+
+We see that both APT and SLR correctly single out the two arms that are much closer to the threshold than the remaining arms, and allocate most of the budget to them.
 However, while SLR keeps the two arms constant at two different levels (about 1900 for arm 5 and about 2500 for arm 6), APT at first pulls arm 5 much more than arm 6.
-Then, the budget allocated to the two arms appears to converge to about 2000.
-Given that the two arms are symmetric around the threshold, it makes sense that APT would allocate the same exploration effort to both of them.
-And given that the variation of arm 5 away from the threshold is limited from below by zero, it is much easier for arm 6 to have an empirical mean larger than it's true mean, and thus to have a larger index than arm 5.
+Then, for *both* arms, the budget allocated to them appears to converge to about 2000.
+Given that the two arms are symmetric around the threshold, it makes sense that APT would allocate the same exploration effort to them.
+And given that the variation of arm 5 away from the threshold is limited from below by zero, it is much easier for arm 6 to have an empirical mean larger than its true mean, and thus to have a larger index than arm 5.
 Consequently, APT would prefer to sample arm 5.
@@
 Furthermore, the SLR algorithm appears to quickly find the correct share that it has to allocate to the two arms.
-In contrast to APT which continues to adjust the shares across the entire budget.
+This is in contrast to APT which continues to adjust the shares across the entire budget.
 
 Additionally, we can observe that the SLR strategy starts to drop arms much quicker than APT, and it drops arm 1 to 3 first, which again underlines the effect of the asymmetric Kullback-Leibler divergence.
-If we consider arm 3 and arm 8, we have $d(0.01||0.05) \approx 0.025$ while $d(0.09||0.05) = 0.014$.
+If we consider arm 3 and arm 8, we have $d_3(0.01||0.05) \approx 0.025$ while $d_8(0.09||0.05) = 0.014$.
 The divergence is much smaller for arm 8.
-The asymmetry is even more dramatic for arm 1 and arm 10 with $d(0.001||0.05) \approx 0.046$ and $d(0.099||0.05) \approx 0.020$; in terms of the divergence, the distance between arm 1 and the threshold is twice as far as between arm 10 and the threshold.
+The asymmetry is even more dramatic for arm 1 and arm 10 with $d_1(0.001||0.05) \approx 0.046$ and $d_{10}(0.099||0.05) \approx 0.020$; in terms of the divergence, the distance between arm 1 and the threshold is twice as far as between arm 10 and the threshold.
 APT considers them to be equally distant from the threshold.
 
-```{r loc6nt_data_summary, echo = FALSE, message = FALSE}
-mean_loc6nt <- c(0.001, 0.005, 0.01, 0.015,
-                 0.04, 0.06,
-                 0.085, 0.09, 0.095, 0.099)
-
-knitr::kable(t(mean_loc6nt), digits = 3, col.names = paste0("V", 1:10), caption = "Mean of arms in simulation 2 classified against threshold of 0.05.")
-```
-
-```{r simulation2_results, echo = FALSE, fig.align = "center", out.width = '80%'}
+```{r simulation2_results, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for simulation 2."}
 library(ggplot2)
@@
 
-```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%'}
+```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Budget allocation across arms for APT and SLR algorithms in simulation 2."}
 load(file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/loc6nt_ma.Rda")
@@
 
-```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%'}
-rbind(loc6nt_BUCB_c15_ma, loc6nt_BUCB_ma, loc6nt_BUCB_c5_ma) %>%
-  rename(Arm = arm) %>%
-  ggplot(aes(x = index, y = mean, group = Arm, color = Arm)) +
-  geom_line(size = 0.3) +
-  facet_grid(.~algorithm) +
-  labs(x = "Index", y = "10 Rounds Moving Average",
-       title = "Average Number of Pulls Allocated to Each Arm per Round",
-       subtitle = "5000 iterations; a value of 1000 means that in 20% of 
-       the iterations the arm was pulled in that round.") +
-  theme_bw() +
-  theme(legend.position = "bottom")
-```
-
-### Experiment 3: Bernoulli with $\tau = 0.01$
+### Simulation 3: Bernoulli with $\tau = 0.01$
 
@@
 
-If we look at the performance after 7000 rounds, we see that the problem appears to be slightly more difficult compared to the previous one.
-We see that up until this point the variance-based strategies cannot improve upon APT.
-Also, SLR has not yet crossed the 10% empirical error.
-However, we observe that in the following rounds EVT decreases at an exponential rate and thus crosses the error of APT and continues to improve upon it.
-At the end of the budget, the improvement of SLR compared to the other algorithms is again very large, and likely to increase.
-However, Bayes-UCB is again the best performing algorithm and is improving at a faster rate than SLR.
-As in the previous experiment, Bayes-UCB and SLR show significant improvements on this Bernoulli problem with very small means and threshold compared to APT in particular.
-
 ```{r loc7nt_data_summary, echo = FALSE, message = FALSE}
@@
 
-knitr::kable(t(mean_loc7nt), digits = 4, col.names = paste0("V", 1:11), caption = "Mean of arms in simulation 2 compared to a threshold of 0.01.")
+knitr::kable(t(mean_loc7nt), digits = 4, col.names = paste0("V", 1:11), caption = "Mean of arms in simulation 3 compared to a threshold of 0.01.")
 ```
 
-```{r simulation3_results, echo = FALSE, fig.align = "center", out.width = '80%'}
+Looking at the performance after 7000 rounds, we see that the problem appears to be slightly more difficult compared to the previous one.
+We see that up until this point the variance-based strategies cannot improve upon APT.
+Also, SLR has not yet crossed the 10% empirical error.
+We observe that in the following rounds EVT decreases at an exponential rate and thus crosses the error of APT and continues to improve.
+At the end of the budget, the improvement of SLR compared to the other algorithms is again large, and likely to increase.
+However, Bayes-UCB is again the best performing algorithm and is improving at a faster rate than SLR.
+As in the previous experiment, Bayes-UCB and SLR show significant improvements on this Bernoulli problem with very small means and threshold compared to APT in particular.
+
+```{r simulation3_results, echo = FALSE, fig.align = "center", out.width = '80%', , fig.cap = "Performance comparison of algorithms for simulation 3."}
 library(ggplot2)
@@
 
-## Experiment 4: Exponential Distribution with $\tau = 1$
-
-```{r simulation4_results, echo = FALSE, fig.align = "center", out.width = '80%'}
+### Simulations 4 and 5: Exponential and Poisson Distributions
+
+In \autoref{sec:LRforUnivariateExponentialFamily}, we show that the likelihood ratio has a very useful form for the univariate exponential family of distributions, which allows us to use the SLR algorithm not only on Bernoulli arms, but also on Exponential or Poisson distributions, for example.
+In simulation 4, we consider Exponential distributions, in simulation 5, we test the algorithms on Poisson distributions.
+
+We run the same algorithms as before except for Bayes-UCB (even though it should certainly be possible to adapt it to these case based on a Gamma prior).
+In the case of the Exponential arms, we classify against $\tau = 1$ and have sampled their mean parameters of the arms from an Exponential distribution with rate $\theta = 1$.
+The Poisson arms are classified against a threshold of $\tau = 0.4$, with the mean parameters being sampled from an Exponential distribution with mean $\mu = 0.7$.
+In both cases, we classify 20 arms.
+
+For the Exponential arms, APT crosses the 0.1 error mark first, followed by the AugUCB algorithm.
+All algorithms perform better than uniform sampling.
+After more than half of the budget, the SLR algorithm jumps in performance and performs better than APT and AugUCB.
+Indeed, the AugUCB basically stops improving after half of the budget.
+This is a consequence of it eliminating arms it believes to know very well.
+This happens at an error rate of less than $0.01$.
+On average, the AugUCB samples only for 2564 rounds of the budget of 4000 rounds across the 5000 simulations.
+
+The early elimination (when compared to the Bernoulli experiments) might be caused by the fact that the AugUCB assumes the variance of the arms to be in $[0,1]$, which does not hold for half of the arms in the experiment.
+Similar goes for the EVT algorithm which is only able to catch up at the very end of the budget.
+
+```{r simulation4_results, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for simulation 4."}
 library(ggplot2)
@@
 
-## Experiment 5: Poisson Distribution with $\tau = 1$
-
-```{r, echo = FALSE}
-set.seed(3795969)
-tau_pois2 <- 0.4
-epsilon_pois2 <- 0
-mu_pois2 <- rexp(20, 1/0.7)
-
-knitr::kable(t(sort(mu_pois2)), digits = 4, col.names = paste0("V", 1:20), caption = "Means of Poisson arms in simulation 5 compared to a threshold of 0.4.")
-```
-
-```{r simulation5_results, echo = FALSE, fig.align = "center", out.width = '80%'}
+In the case of Poisson arms, the performance of the arms is more clear cut.
+As expected, SLR improves APT and the other strategies.
+APT outperforms the EVT algorithm, which occurs even though the variance of all arms considered in this experiment is in $[0,1]$.
+But similarly to the Bernoulli simulations, the EVT might again have a hard time dealing with sequences of observations that are all equal to $0$ for a long time.
+After about 1000 observations, APT and EVT appear to improve at about the same rate, but APT had a much better initial exploration phase.
+
+```{r simulation5_results, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for simulation 5."}
 library(ggplot2)
@@
 
-## Real Data
-
-We show two experiments that were performed on real data.
-While most papers in the multi-armed bandit literature resort to synthetic data to assess the performance of algorithms -- just as we have done in the previous chapter -- we have tried to acquire real world data.
-This data is what bandit algorithms are used for in practice, and does not fulfill the standard independence and identical distribution assumptions as nicely.
-The real data thus can be considered a first robustness test for the algorithms.
+## Real Data \label{sec:RealData}
+
+In the following, we present the results of two experiments performed on a real world data set.
+While most new multi-armed bandit algorithms are assessed on synthetic data, as we have done in \autoref{sec:SyntheticData}, a real world data set is useful to observe how algorithms perform in presence of, for example, not fully i.i.d.
+samples.
+While of course every company tries to make their experiments as ideal as possible, there will always be problems.
+Thus our experiments serve as a first robustness check on the algorithms introduced before.
 
@@
 
-The data have been collected by the German ecommerce company [Amorelie](https://amorelie.de) as part of standard website performance tracking.
-For 197 selected products, we have the number of users visiting each product's detail page (PDP) at a given minute.
+Data have been collected by the German online shop [Amorelie](https://amorelie.de) as part of standard website analytics.
+For 197 selected products, we observe the number of users visiting each product's detail page (PDP) at a given minute.
 The data set we use here has been collected during the entire month of November 2016.
@@
 
-Given that we want to run an offline comparison of bandit algorithms, it is important to have at each time point an observation for each arm.
+Since we want to run an offline comparison of bandit algorithms, it is important to have at each time point an observation for each arm.
 Given that, it is easy to evaluate the perfomance of algorithms that make different decisions at different point in times and thus do not observe the same samples.
 By having an observation for each arm at any given time point, each algorithm had at least the opportunity to observe a certain sample.
-Other papers (CITE YAHOO!) have solved this problem by using a sample drawn uniformly during for example an A/B test.
+Other papers (for example, Li et al., 2011) have solved this problem by using a sample drawn uniformly during, for example, an A/B test.
 Then, if the next observation in the sample is not from the same arm that the algorithm would like to draw from, observations are discarded until the next observation from the selected arm.
 
-The choice of having basically multiple time series data as the sample leads to a simple way of running the algorithms just as often on the data as for simulated data.
-In particular, the goal is to perform 5000 runs over the sample to confidently assess the performance.
-Since we wanted to preserve the potential time dependency of the data, a simple resampling of the data was not an option to create the needed 5000 variations of the sample.
-Thus what we did instead was a form of time series cross validation.
+The choice of using what is basically multiple time series data as the sample offers a simple way of running the algorithms just as often on the data as for simulated data.
+The goal is to perform 5000 runs over the sample to confidently assess the performance.
+Since we want to preserve the potential time dependency of the data, a simple resampling of the data is not an option to create the needed 5000 variations of the sample.
+Instead we perform time series cross validation.
 To preserve the autocorrelation, one can create different samples of $X$ observations by sliding a window of size $X$ over the time series.
-Moving the window one period (in our case minute) at a time, one ensures that no sample shares start and end observation with another sample.
-In particular, this means for a given bandit strategy and two samples that the observations that the algorithm collects as feedback during the two initialization phases differ from sample to sample and are never the same.
-This is because during initialization every strategy pulls arms $1, ..., K$ once in this order.
+Moving the window one period (in our case one minute) at a time, one ensures that no sample shares start and end observation with another sample.
+In particular, this means for a given bandit strategy and two samples that the observations that the algorithm collects as feedback during the initialization phases differ from sample to sample and are never the same.
+This is because during initialization every strategy pulls arms $1, ..., K$ (or $1,...,2K$ for EVT) once in this order.
 
 While the data is count data (the number of visits to a PDP during a given minute), we binarize the data by applying a certain threshold.
-If the counts is above this threshold, the observation becomes a $1$, else $0$.
+If the count is above this threshold, the new observation is $1$, else $0$.
 Thus we have a binary time series of length 43200 for each of the 197 products.
 Given that the number of visitors that come to a given PDP is likely to vary by time of day and by day, and in general over time, we expect that the mean of the time series to not be stable over time.
-For example, less visitors will come during night than during evening, thus leading to a decreasein the average.
+For example, less visitors will come during night than during the evening.
+This leads to a decrease in the average, and a daily seasonality.
 On the other hand, more users may visit the site during a weekend, thus leading to a spike on Saturdays and Sundays.
@@
 
-We can look at summary statistics for the sample means of the 197 products over the month of November to get a first idea of the data we are dealing with.
-We see that most products have a low mean, which is very common also for actual conversion rate data that would be tested with A/B tests or multi-armed bandits.
+We can look at summary statistics for the sample means of the 197 products over the month of November to get a first impression of the data we are dealing with.
+We see that most products have a small mean, which is very common also for actual conversion rate or click-through rate data that can be tested with A/B tests or multi-armed bandits.
 Yet the sample of products contains a few outliers with very large view rates, with a maximum rate of 78%.
@@
 
-### Experiment 1: $\tau = \frac{2}{60}$
-
-In this first experiment, we pick ten arms randomly from the set of 197 arms.
-The experiment is run on these 10 arms with a budget of $T=10080$ samples during each of the $5000$ iterations for which we repeat the experiment.
-Given the time series cross-validation idea described above, this means that in total, $15080$ observations of the available $43200$ available observations per arm are used in training.
+### Experiment 1
+
+In the first experiment, we pick ten arms randomly from the set of 197 arms.
+The experiment is run with a budget of $T=10080$ samples during each of the $5000$ iterations for which we repeat the experiment.
+Given the time series cross-validation idea described above, this means that in total, $15080$ observations of the $43200$ available observations per arm are used in training.
 In the thresholding bandit problem, we classify arms as below or above a threshold.
@@
 
-knitr::kable(rbind(Training, Test, TrainingMinusTau)[,order(Training)], digits = 3, col.names = names(data_amo3_mean_firsthalf)[order(Training)],
+#knitr::kable(rbind(Training, Test, TrainingMinusTau)[,order(Training)], digits = 3, col.names = names(data_amo3_mean_firsthalf)[order(Training)],
+#             caption = "Count rates for ten products for both training and test sample.")
+knitr::kable(rbind(Training, Test)[,order(Training)], digits = 3, col.names = names(data_amo3_mean_firsthalf)[order(Training)],
              caption = "Count rates for ten products for both training and test sample.")
@@
 
-We see that while the rates do vary across samples, they are relatively stable which is likely due to the fact that the samples come from an entire week's worth of observations.
+We see that while the rates do vary across training and test samples, they are relatively stable which is likely due to the fact that the samples come from an entire week's worth of observations.
 In particular, since we test against a threshold of $\tau = \frac{2}{60} = 0.333$ in this experiment, the classifications of arms do not differ across training and test data.
@@
 
-```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%'}
+```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Rolling average for the arms used in experiment 1."}
 library(zoo)
@@
 The distribution is sub-Gaussian for the APT algorithm, bounded between $0$ and $1$ for the variance-based algorithms, and assumed to be Bernoulli for the SLR algorithm.
-Additionally, we use the B-UCB algorithm as it performed often best on the synthetic data.
+Additionally, we use the Bayes-UCB algorithm as it performed best on the synthetic data.
 
@@
 (2017), that is, $\rho = 1/3$.
-For B-UCB we set the prior to $\alpha = \tau$ and $\beta = 1-\tau$.
+For B-UCB we set the prior to $\alpha_0 = \tau$ and $\beta_0 = 1-\tau$, and pick $c=1$.
 All other algorithms are parameter free.
 
-The corresponding results are shown in the next figure.
-
-```{r, echo = FALSE, fig.align = "center", out.width = '80%'}
+```{r, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for experiment 1."}
 library(ggplot2)
@@
 
-Compared to the previous simulations with synthetic data, the results are dramatic.
-First of all, we see that all strategies perform not well.
-All of them end above the 10% error mark after 1 week of data.
+Compared to the previous simulations with synthetic data, the results are dramatically poor.
+First of all, we see that all strategies perform poorly.
+All of them end above the 10% error rate mark after 1 week of data.
 Second, the uniform sampling strategy fares best when evaluated against the sample mean of all observations used during training.
@@
 Given that the highs and lows run very much parallel for the different models, it stands to reason that this effect is caused by the variation in means of the arms over time.
-Indeed, roughly comparing the error curves to the moving averages in the previous figure, the increase in errors after round $5000$ and the decreasing error after round $7500$ seems to line up more or less with the fluctuations observed in the data.
+Indeed, roughly comparing the error curves to the moving averages in the previous figure, the increase in errors after round $5000$ and the decreasing error after round $7500$ seems to line up with the fluctuations observed in the data.
 Given that we evaluate the models against a sample mean of all observations, it is not surprising that the uniform sampling strategy has a certain advantage when it comes to "factoring out" the seasonalities.
 In contrast, the adaptive sampling schemes try to adapt more or less quickly to the changes in the means; a feature that would be valuable in a cumulative regret multi-armed bandit setting.
-Here, however, it leads to wrong estimates of the sample mean.
+Here, however, it leads to wrong estimates of the overall sample mean.
 
 If we focus on a comparison of adaptive sampling strategies and less on their globally bad performance, we see that the variance based strategies perform worse than APT and SLR.
-Very dramatic is the behavior of the Augmented-UCB algorithm, which first seems to perform well; that, however, is a result of it mostly pulling arms uniformly, until it starts to adapt its sampling and discarding arms after nearly 5000 rounds.
-The result is a dramatic increase in error which leads to the worst performs at the end of the budget.
-The difference between APT, SLR, and EVT is not very large, and their performance fluctuates in sync.
+Very dramatic is the behavior of the Augmented-UCB algorithm, which first seems to perform well; this, however, is a result of it mostly pulling arms uniformly, until it starts to adapt its sampling and discarding arms after nearly 5000 rounds.
+The result is a dramatic increase in error which leads to the worst performance at the budget horizon.
+The difference between APT, SLR, and EVT is small, and their performance fluctuates in sync.
 None of them is really able to converge due to the changes in the underlying means.
-Advantageous only seems to be the fact that their behavior is less erratic than that of the Augmented-UCB strategy given that they do not discard arms.
-
-### Experiment 2: $\tau = \frac{5}{60}$
+Advantageous only seems to be the fact that their behavior is less erratic than that of the AugUCB strategy given that they do not discard arms.
+
+### Experiment 2
 
@@
 We increase the threshold to $\tau = \frac{5}{60} = 0.833$ to make the problem in general slightly easier, and again pick 10 arms at random from the data set of 197 arms.
-We again use a rolling window of $10080$ observations to create $5000$ iterations and look at the training and test sample means as in Experiment 1.
+We again use a sliding window of $10080$ observations to create $5000$ iterations and look at the training and test sample means as in the previous experiment.
 
@@
 
-knitr::kable(rbind(Training, Test, TrainingMinusTau)[,order(Training)], digits = 3, col.names = names(data_amo4_mean_firsthalf)[order(Training)],
+#knitr::kable(rbind(Training, Test, TrainingMinusTau)[,order(Training)], #digits = 3, col.names = names(data_amo4_mean_firsthalf)[order(Training)],
+#             caption = "Count rates for ten products for both training #and test sample.")
+
+knitr::kable(rbind(Training, Test)[,order(Training)], digits = 3, col.names = names(data_amo4_mean_firsthalf)[order(Training)],
              caption = "Count rates for ten products for both training and test sample.")
@@
 But these fluctuations are clearly much larger and systematic than those observed for synthetic data with the same sample means.
-While the moving average of product $V159$ in the synthetic data has a valley after index 5000, this can be explained by the natural variance (which increases as the mean is closer to $0.5$).
 
@@
 The uniform sampling strategy performs the best.
-The adaptive sampling strategies perform bad, do not converge, and end above the 10% error mark.
-This time, Augmented-UCB is not (yet) the worst performing strategy, but equally erratic after it actually adapts its sampling.
+The adaptive sampling strategies perform bad, do not converge, and end above the 10% error rate mark.
+This time, AugUCB is not (yet) the worst performing strategy, but equally erratic after it eventually adapts its sampling.
 This time around, it even has two spikes in its adaptive phase.
@@
 This mirrors its performance observed in the previous simulations with synthetic data.
-Also all other strategies perform clearly better now, and their error rates are strictly decreasing.
+Also all other adaptive strategies perform clearly better now, and their error rates are strictly decreasing.
 Interestingly, the uniform sampling scheme is now much worse than in the experiment on real data; it does no longer have the advantage of sampling the different mean phases at a representative rate.
-Instead, it is no in its original position of serving as upper bound on the error rate.
-Excluding Bayes-UCB, we see that the SLR algorithm performs better the best, followed by the variance-based algorithms.
+Excluding Bayes-UCB, we see that the SLR algorithm performs the best, followed by the variance-based algorithms.
 APT comes in at the same error rate as uniform sampling.
@@
 
-```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%'}
+```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Rolling average of arms used in experiment 2."}
 library(zoo)
@@
   theme(legend.position = "bottom")
-
+```
+
+```{r, include = FALSE, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Rolling average of arms used in experiment 2."}
 amo4_cummean_real <- data_amo4_wide[1:10080,] %>% tbl_df() %>%
@@
   theme(legend.position = "bottom")
-
+```
+
+```{r, include = FALSE, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Rolling average of arms used in experiment 2."}
 amo4_cummean_real_12hrs <- data_amo4_wide[721:10800,] %>% 
@@
   theme(legend.position = "bottom")
-
+```
+
+```{r, include = FALSE, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Rolling average of arms used in experiment 2."}
 load("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/data_amo4_shuffled_wide.Rda")
@@
 
-```{r, echo = FALSE, fig.align = "center", out.width = '80%'}
+```{r, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance results of algorithms in experiment 2."}
 library(ggplot2)
@@
 
-We can try to understand why some strategies fail, while showing significant improvements on synthetic data.
-Given that we run 5000 iterations of the experiment, we can assess in how many of these iterations a given arm was pulled at a given round.
-Comparing these sampling shares across algorithms may give us hints to as to why algorithms perform a certain way.
-Given the setup with 5000 iterations and 10 arms in the current experiment, we would expect for the uniform strategy on average 500 pulls for each arm in every round.
-Given this benchmark, we can now look at how the other strategies split their budget.
-In the figures below, we have plotted not the absolute pulls per round, but have applied a 10-round moving average to remove some of the fluctuation in the plotted lines.
+Again using a plot of the pulls at each round across the 5000 simulations in Figure 17, we can try to understand why some strategies perform well on synthetic data, but poorly on the time series data.
 
 We observe that the patterns across algorithms are quite similar, while the patterns are very different across data sets.
-Given that arm $V149$ is clearly the most difficult arm to classify due to its closeness to the threshold $\tau$, all algorithms focus a major share of their budget on this arm.
+On the synthetic data, given that arm $V149$ is clearly the most difficult arm to classify due to its closeness to the threshold $\tau$, all algorithms focus a major share of their budget on this arm.
 The speed at which they start to do so, however, differs.
 Perhaps surprisingly, the best performing Bayes-UCB algorithm increases its focus on arm $V149$ the slowest, while in many iterations spending budget on exploring other arms.
-Surprisingly because Bayes-UCB is designed for the cumulative regret problem.
+This is surprising as the Bayes-UCB algorithm's exploration factor was originally conceived for the cumulative regret problem.
 Thus one would expect it to explore *less* than other algorithms.
@@
 
-One striking feature of the EVT algorithm seems to be the overall iterations and budget allocated to arm $V32$, which, as we have seen, has a sample mean of zero.
 Something that might be hidden by this aggregated view of all 5000 iterations are a share of iterations in which the EVT completely fails by exploring wrong arms for long periods.
@@
 
-```{r ShareOfPullsAtEachIteration, echo = FALSE, include = FALSE}
+```{r ShareOfPullsAtEachIteration, echo = FALSE, include = FALSE, fig.cap = "Budget allocation of algorithms across arms on real and synthetic data in experiment 2."}
 load(file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/amo4_arm_seq_ma.Rda")
@@
 
-```{r, echo = FALSE, fig.align = "center", out.width = '80%'}
+```{r, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Budget allocation of algorithms across arms on real and synthetic data in experiment 2."}
 load(file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/amo4_arm_seq_ma.Rda")
@@
 
+### Experiments Conclusion
+
+In the two previous experiments, we observe that the real time series data poses a major hurdle for the adaptive sampling algorithms.
+It seems that the poor performance can be mostly explained by the seasonality and sudden changes in the samples over time.
+The observations clearly are not i.i.d.
+sampled.
+However, the effect might be overly stark due to the fact that we use minutely time series data, which leads to observations even when in minutes when there are few or no users (during night).
+In contrast, the daily seasonality might be less represented in an actual online experiment observations are only drawn when there is an actual visitor on the site (and a proper conversion rate would fluctuate less than the count of visitors on a given product page).
+
+Furthermore, some of the problems in dealing with the fluctuating distributions might be specific to the thresholding bandit problem as opposed to the cumulative regret or best-arm identification problems.
+In the experiments above, we observe that the order of the arms is mostly unaffected by the seasonalities and fluctuations, which would mean that the best arm could still be identified.
+In contrast, given that all arms are individually classified against the *fixed* threshold, a weekly seasonality can declare a correct classification on the first half of the sample null and void on the second half of the sample.
+
 # Conclusion
@@
 
-The author thanks Alexandra Carpentier, Andrea Locatelli, and Urun Dogan for many hours of valuable feedback and ideas. <3
+The author thanks Alexandra Carpentier, Andrea Locatelli, and Urun Dogan for many hours of valuable feedback and ideas.
+
+# References
+
+# Appendix
+
+## Proof of Thresholding Bandit Lower Bound \label{sec:AppendixAPTLB}
+
+We now give a proof for the lower bound for the thresholding bandit problem stated in \autoref{theorem:Locatelli2016Theorem1}.
+
+*Proof of Theorem \ref{theorem:Locatelli2016Theorem1}*: Locatelli et al.
+(2016) derive a lower bound for the thresholding bandit problem.
+We restate the proof here.
+The idea is as follows.
+The problem formulation considered in the paper describes bandit problems for $R$-sub-Gaussian distributions.
+To show a lower bound, we show that every algorithm is expected to make a certain error even if we consider a very restricted scenario.
+Even then, the best algorithm will have a maximum error probability with which it cannot distinguish between the actual setting and slightly changed settings (under which the answer for the true setting leads to a misclassification).
+
+Consider the thresholding bandit setting as in \autoref{sec:Setup}.
+More specifically, consider a problem in which all arms follow Normal distributions $\nu_i$ with mean $\mu_i$ and variance $\sigma^2 = 1$.
+"in which w"e set $\tau = 0$ and $\epsilon = 0$ w.l.o.g.
+Consequently, for each arm $i$ the distance from the threshold is given by $\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i$.
+Thus, we have for every arm the distribution $\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)$.
+Furthermore, define for each arm $i \in \{1, \dots, K\}$ the alternative distribution $\nu_i' = \mathcal{N}(-\Delta_i,1)$.
+It is easy to see that this is equivalent to a "flip around the threshold".
+Arms that originally have a mean larger than the threshold have a mean smaller than the threshold after the flip.
+
+The intuition now is that every arm $i \in \{1,\dots,K\}$ generates a sample for every time point $t\in \{1, \dots, T\}$ from its distribution $\nu_i$ before the algorithm starts to choose arms.
+Thus, we have a $T \times K$ table of realized observations from the product distribution given by $\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K$.
+This is a product distribution where the $K$ different means are all above the threshold.
+We would hope that an algorithm classifies the means accordingly.
+However, we will show in what follows that any algorithm makes a certain error by not being able to distinguish $\mathcal{B}^0$ from at least one of $K$ alternative product distributions $\mathcal{B}^i, i \in \{1, \dots, K\}$, of which each differs only slightly in one arm from the original distribution, and has the same overall complexity (as defined by $H = \sum_{i=1}^K (\Delta_i)^{-2}$).
+We require $K$ different distributions so that an algorithm sampling arm $i$ very often for some reason will not have a smaller lower bound by chance.
+
+For each of the $K$ arms, we introduce an alternative model of the following kind.
+Before the start of the algorithm, we introduce a slight variation in the setup.
+The idea is similar to how one can switch arms in the pure exploration setup for multi-armed bandits (compare Audibert et al., 2010; Garivier & Kaufmann, 2016) to "confuse" any algorithm without introducing additional complexity to the specified problem.
+However, since we do not compare arms directly with each other in the thresholding bandit problem (switching arms would still keep all means above the threshold), we instead need to flip an arm $i$ with respect to the threshold in order to get the alternative model $\mathcal{B}_i$.
+Since the threshold is $\tau = 0$, we have for the flipped arm the new distribution $\nu_i'$ as defined above.
+Indeed, define the new product distribution $B^i = \nu_1^i \otimes \dots \otimes \nu_K^i$ where for $k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}$.
+This arm flip corresponds to multiplying all $X_{i,t}$ of arm $i$ by $-1$.
+
+As in Locatelli et al.
+(2016), let for $i \leq K$, $\mathbb{P}_{\mathcal{B}^i}$ be the probability distribution describing all samples that a bandit strategy can potentially collect up to horizon $T$, i.e.
+according to the samples $(X_{k,s})_{k\leq K, s \leq T} \sim (\mathcal{B}^i)^{\otimes T}$.
+$(T_k)_{k\leq K}$ denotes the number of samples collected on arm $k$ until time $T$.
+
+At this point, we have defined a finite set of problems of Gaussian distributions with fixed variance 1 for a given set of set of gaps between the means of the distributions and the threshold, $(\Delta_k)_k$.
+We now proof a lower bound on the worst case regret of any algorithm; that is, the maximum error probability that even the best algorithm makes on this problem.
+
+### Statistical Decision
+
+The expected loss in our thresholding bandit setting, $\mathbb{E}[\mathcal{L}(T)]$, corresponds directly to the probability of making a wrong classification of any of the $K$ means.
+In general, given a binary decision function $g$, define events $\Omega = \{g = 0\}$ and $\Omega^C = \{g = 1\}$.
+Assume that the decision $g$ distinguishes between two states of the world, $H_0$ and $H_1$.
+Then an overall error probability can be seperated into $P_{H_0}(g=1) + P_{H_1}(g = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)$.
+
+In our case, $H_0$ may correspond to the state in which we have $\mathcal{B}^0$, and $H_1$ corresponds to the case where any arm has been flipped, $\mathcal{B}^i$.
+Furthermore, we consider the events in which the algorithm classifies arm $i$ as being above the threshold: $\mathcal{A}_i = \{i \in \hat{S}_\tau\}$.
+The event on which all arms are being classified as above the threshold is consequently given by $\mathcal{A} = \bigcap_{i=1}^K \mathcal{A}_i$.
+We could thus separate the error probability $\mathbb{E}[\mathcal{L}(T)]$ into $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$ and $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C)$.
+However, Theorem 1 does not bound the overall regret, but the maximum error probability on the $K+1$ different models.
+We can write this now as
+
+\begin{align}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big) \\
+& = \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
+\end{align}
+
+### Empirical Kullback-Leibler Divergence
+
+In order to give a bound on the previous equation, we start by considering $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$.
+This probability can be written as the expected change in the likelihood of observed data when moving from distribution $P_{\mathcal{B}_0}$ to $P_{\mathcal{B}_i}$, times the probability under the original state.
+In other words, the probability of event $\mathcal{A}_i$ under state $\mathcal{B}^i$ is given as the probability of $\mathcal{A}_i$ under the (original) state $\mathcal{B}^0$ multiplied by a factor.
+This factor describes whether the new distribution increases or decreases the probability of the event, and is given by the change in the data likelihoods due to moving from $\mathcal{B}^0$ to $\mathcal{B}^i$, expressed as the expected likelihood ratio under $\mathcal{B}^0$.
+By definition, the latter is equal to the empirical Kullback-Leibler divergence of the two distributions.
+
+We will define the change of distribution in terms of the empirical log-likelihood for our case.
+Then, we will show how to replace the log-likelihood by the empirical Kullback-Leibler divergence.
+Let us first introduce the empirical Kullback-Leibler divergence.
+
+Let every $\nu_i, \nu_i'$ be dominated by the Lebesgue measure $\lambda$.
+Then their density functions are given by $f_i = \frac{\der \nu_i}{\der \lambda}$ and $f_i' = \frac{\der \nu_i'}{\der \lambda}$ respectively.
+For $T \geq t \geq 0$, define the empirical Kullback-Leibler divergence for an i.i.d.
+sample $X_{k,1}, \dots,X_{k,t}$ as
+
+\begin{align*}
+\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log(\frac{\der \nu_k'}{\der \nu_k}(X_{k,s})) \\
+& = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
+& = \frac{1}{t} \log \big( \prod_{s=1}^{t} \frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
+& \stackrel{\text{iid}}{=} \frac{1}{t} \log \big( \frac{f_k'(X_{k,1}, \dots,X_{k,t})}{f_k(X_{k,1}, \dots,X_{k,t})} \big) \\
+& = \frac{1}{t} \log \big( \text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k) \big),
+\end{align*}
+
+where $\text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k)$ is the likelihood ratio for the sample.
+
+Since we consider Gaussian distributions with variance $\sigma^2 = 1$, we have density functions $f_i(x) \propto \exp \big(-\frac{1}{2} (x-\Delta_i)^2\big)$ and $f_i'(x) \propto \exp \big(-\frac{1}{2} (x+\Delta_i)^2\big)$.
+Plugging this into the above definition of the empirical Kullback-Leibler divergence, we easily see
+
+\begin{align*}
+\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log \Big(\frac{\exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2\big)}{\exp \big(-\frac{1}{2} (X_{k,s}-\Delta_k)^2\big)} \Big) \\
+& = \frac{1}{t} \sum_{s=1}^{t} \log \Big( \exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2 + \frac{1}{2} (X_{k,s}-\Delta_k)^2 \big) \Big) \\
+& = - \frac{1}{t} \sum_{s=1}^{t} 2 X_{k,s} \Delta_k
+\end{align*}
+
+### Change of Distribution
+
+We are now ready to state the change of distribution.
+As alluded to above, we consider how the probability changes for the event $\mathcal{A}_i$ when we move from $\mathcal{B}^0$ to $\mathcal{B}^i$.
+When flipping arm $i$, we only change the samples of this arm, that is, the first $T_i$ observations that the algorithm draws from arm $i$.
+The change of distribution is then defined as:
+
+\begin{align*}
+\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \text{LR}((X_{i,1}, \dots,X_{i,T_i}), \nu_i', \nu_i) ] \\
+& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ]
+\end{align*}
+
+Obviously, $\hat{\KL}_{i,T_i}$ depends on the realized samples $X_{i,1}, \dots,X_{i,T_i}$.
+Consequently, we need to find a bound on $\hat{\KL}_{i,T_i}$ itself to incorporate the uncertainty involved in this metric.
+
+### Concentration of the Empirical Kullback-Leibler Divergence
+
+For our problem, the Kullback-Leibler divergence of $\nu_k'$ from $\nu_k$ is given by $\KL_k := \KL(\nu_k', \nu_k) = 2\Delta_k^2$, and consequently
+
+\begin{equation*}
+|\hat{\KL}_{k,t} - \KL_{k,t}| = |-\frac{2}{t} \Delta_k \sum_{s=1}^{t}(X_{k,s} - \Delta_k)|
+\end{equation*}
+
+itself is a normally distributed random variable with mean zero and a variance decreasing in $t$.
+Thus, one can show as in Locatelli et al.
+(2016) that $\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4$ for the event
+
+\begin{equation}
+\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}}\}. \label{LocatelliTheorem1EventXi}
+\end{equation}
+
+Thus, in order to bound the empirical Kullback-Leibler divergence in our change of measure, we can consider the intersection of $\mathcal{A}_i$ and $\xi$ as follows and plug in the bound on event $\xi$:
+
+\begin{align*}
+\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
+& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
+& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
+\end{align*}
+
+Two things are left to do: With $T_i$, we still have one random variable left which we cannot leave in our bound.
+Second, we are actually not interested in $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$ but in $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$.
+
+### Bounding $T_i$ for $\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$
+
+We are actually interested in bounding $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$.
+In general it holds that $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K}\sum_{i=1}^K X_i$.
+Thus we can write:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
+& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
+& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
+\end{align*}
+
+where the second line is again the intersection of $\mathcal{A}_i$ and $\xi$ as before, such that we can apply the change of distribution in the third line.
+
+What is left to show is a bound on $T_i$.
+Given that we want to show that even the best algorithm makes an error on at least one of the problems (one of the arms), it makes sense to show that $T_i$ is upper bounded.
+This implies that no arm can be infinitely sampled; we cannot reach full confidence in any arm, and a residual error probability should remain.
+
+First, let $a = \Delta_i \sqrt{T_i}$ and $b = 4\sqrt{\log((4\log(T)+1)K)}$. Then use $ab \leq a^2 + b^2$ to write $ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)$. And so:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) ]
+\end{align*}
+
+Furthermore, we know that the sum of the individual arm pulls has to be equal to the overall number of pulls (equal to the budget in the fixed budget sense), $\sum_i T_i = T$, and furthermore we know that $T_i>0$.
+The latter holds since any reasonable algorithm has to check each arm at least once in our setup.
+Thus it is easy to show that $\exists i: T_i \leq \frac{T}{H \Delta_i^2} = \frac{T}{(\sum_{i=1}^{K} \Delta_i^{-2}) \Delta_i^2}$.
+To see this, assume the opposite: $\forall i: T_i > T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2}$.
+This implies however $\sum_{i=1}^K T_i > \sum_{i=1}^K T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2} = T \cdot 1 = T$ which is a contradiction.
+
+So we can write $(\Delta_i \sqrt{T_i})^2 \leq \frac{T}{H}$. We use $\mathcal{A} = \cap_{i=1}^K \mathcal{A}_i$ to write:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big] \\
+& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big]
+\end{align*}
+
+We write $\frac{1}{K} \sum_{i=1}^K \exp(-3T_i \Delta_i^2) \geq \frac{1}{K} \sum_{i=1}^K \exp(-3 T/H) = \exp(-3 T/H)$. Thus:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \Big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i) \exp \big(-16 \log(4(\log(T)+1)K)\big) \Big] \\
+& \geq \mathbb{E}_{\mathcal{B}^0} \Big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp \big(- 3 \frac{T}{H}\big) \exp \big(-16 \log(4(\log(T)+1)K)\big) \Big] \\
+& = \mathbb{E}_{\mathcal{B}^0} \Big[\mathbbm{1}_{\mathcal{A} \cap \xi} \exp \big(- 3 \frac{T}{H}\big) \exp \big(-16 \log(4(\log(T)+1)K)\big) \Big] \\
+& = \mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp \Big(- 3 \frac{T}{H} -16 \log \big(4(\log(T)+1)K\big)\Big)
+\end{align*}
+
+### Bringing everything together
+
+Consider again the risk which we need to bound from equation \eqref{LocatelliTheorem1ExpRegret}.
+We bound the maximum expected loss over all $\mathcal{B}_i$.
+By using again the fact that in general $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K} \sum_{i = 1}^K X_i$, we plug into our previous calculations:
+
+\begin{align}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
+& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp \Big(- 3 \frac{T}{H} -16 \log \big(4(\log(T)+1)K\big)\Big) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \label{LocatelliTheorem1DefinitionOfRisk}
+\end{align}
+
+From \eqref{LocatelliTheorem1EventXi} we know that for any $i \in \{0, \dots, K\}$, $\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4$.
+Following the argument in Locatelli et al.
+(2016), we now consider two cases: $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2$ and $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2$.
+In the former case, we can plug in the two probabilities into \eqref{LocatelliTheorem1DefinitionOfRisk}.
+If $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2$ and $\mathbb{P}_{\mathcal{B}^0}(\xi) \geq 3/4$, then $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \geq 1/4$.
+Thus:
+
+\begin{align*}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
+& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \\
+& \geq \frac{1}{8} \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
+\end{align*}
+
+where we drop the second summand of the second line so that the inequality holds.
+
+On the other hand, when $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2$, then we know that $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \leq 1/2$ for any $\mathbb{P}_{\mathcal{B}^0}(\xi)$.
+At the same time $1-\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \geq 1/2$.
+Consequently, $1/4 \leq \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \leq 1/2$, while
+$\frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) \geq 0$.
+And so the stronger lower bound in that case is, as noticed by Locatelli et al.
+(2016), given simply by
+
+\begin{align*}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
+& \geq 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \\
+& \geq \frac{1}{2}
+\end{align*}
+
+## Bayes-UCB Algorithm for the Thresholding Bandit Problem \label{sec:AppendixBUCB}
+
+We show how the Bayes-UCB algorithm (Algorithm 1, Kaufmann et al., 2012) is adopted to the thresholding bandit problem to be used in the experiments in chapter \autoref{chap:Experiments}.
+
+We adopt their Algorithm 1 for Bernoulli distributions as follows:
+
+\IncMargin{1em}
+\begin{algorithm}
+\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
+\Input{\emph{$\tau$, $\epsilon$, $T$, $\Pi^0$ (initial prior on $\mu$), $c$ (parameters of the quantile)}}
+\Output{$\hat{S}_\tau = \{i \in \mathbb{A},  \hat{\mu}_i(T) \geq \tau\}$}
+\BlankLine
+\emph{Pull each arm once}\;
+\For{$t = K+1$ \KwTo $T$}{
+\For{$i = 1$ \KwTo $K$}{
+  \emph{Compute $q_i(t) = Q\Big(1-\frac{1}{t(\log T)^c}, \lambda_i^{t-1}\Big)$}\;
+  \emph{Compute $B_i(t) = $}\;
+  \If{$\hat{\sigma}^2_{i}(t) = 0$}{\emph{Set $\hat{\sigma}^2_{i}(t) = 1/T$}}
+}
+  \emph{Pull arm $I_t = \arg \min_{i\leq K} B_i^{SLR_{2D}}(t)$ as in \autoref{eqn:SLR2DIndex}}\;
+  \emph{Observe reward $X \sim \nu_{I_t}$}\;
+}
+\caption{2D-SLR algorithm for Normal distributions with unknown mean and unknown variance}\label{algo_slr_2d}
+\end{algorithm}\DecMargin{1em}
+
+## Empirical Analysis of the Bayes-UCB Algorithm in Simulation 2
+
+In order to assess the excellent performance of the Bayes-UCB algorithm, which comes at a surprise given that is is designed for the cumulative regret setting and thus should tend to explore the arms to less, we also plot the budget allocation of three different Bayes-UCB versions.
+The three versions differ in the quantile parameter $c$ (compare \autoref{sec:AppendixBUCB}) for which we set here $c \in \{1/5, 1, 5\}$ to explore more or less.
+In Kaufmann et al.
+(2012), the cumulative regret upper bound for the Bayes-UCB is shown for $c\geq 5$, though they report that the choice of $c=0$ worked much better in their experiments.
+In our problem, it makes also sense that the versions with smaller quantiles (smaller $c$) tend to perform better than
+
+```{r simulation2_results_bucb, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for simulation 2."}
+library(ggplot2)
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
+
+load(paste0(current_path, "loc6nt_comp_BUCB_horizon_7000.Rda"))
+load(paste0(current_path, "loc6nt_comp_BUCB_horizon_c5_7000.Rda"))
+load(paste0(current_path, "loc6nt_comp_BUCB_horizon_c15_7000.Rda"))
+#load(paste0(current_path, "loc6nt_comp_BUCB_horizon_7000.Rda"))
+
+alg_names <- c(rep(c("BUCB_C0.25", "BUCB_C1", "BUCB_C5"), 
+                   each = 6991))
+index <- c(rep(10:7000, times = 3))
+alg_res <- log(c(loc6nt_comp_BUCB_horizon_c15_7000,
+                 loc6nt_comp_BUCB_horizon_7000,
+                 loc6nt_comp_BUCB_horizon_c5_7000))
+loc6nt_comp_res <- data.frame(index = index, names = alg_names, 
+                            results = alg_res)
+ggplot(loc6nt_comp_res, aes(x = index, y = results)) + 
+  geom_line(aes(group = names, color = names)) +
+  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
+  labs(title = "Results of Synthetic Experiment 2", 
+       subtitle = expression(paste("Difficult scenario for APT; ", 
+                                   tau,' = 0.05 and 10 arms. Dashed line at Error = 0.1.')), 
+       y = "log(Error)", x = "Round Index") +
+  scale_color_discrete(name = "Algorithm") +
+  theme_bw() + 
+  theme(legend.position = "bottom")
+```
+
+```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Budget allocation for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter c."}
+rbind(loc6nt_BUCB_c15_ma, loc6nt_BUCB_ma, loc6nt_BUCB_c5_ma) %>%
+  rename(Arm = arm) %>%
+  ggplot(aes(x = index, y = mean, group = Arm, color = Arm)) +
+  geom_line(size = 0.3) +
+  facet_grid(.~algorithm) +
+  labs(x = "Index", y = "10 Rounds Moving Average",
+       title = "Average Number of Pulls Allocated to Each Arm per Round",
+       subtitle = "5000 iterations; a value of 1000 means that in 20% of 
+       the iterations the arm was pulled in that round.") +
+  theme_bw() +
+  theme(legend.position = "bottom")
+```
+
+## Empirical Comparison of APT, SLR, and Bayes-UCB in Experiment 2
+
+```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Budget allocation for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter c."}
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
+
+load(paste0(current_path, "loc6nt_pulls_of_arms_vis.Rda"))
+
+pulls_arm_6_long %>%
+  ggplot(aes(x = Pulls)) +
+  geom_histogram(binwidth = 100) +
+  facet_grid(.~Algorithm, scales = "free_y") +
+  geom_vline(aes(xintercept = 7000/10), linetype = 2) +
+  labs(x = "Pulls", y = "Count", 
+       title = "Distribution of Pulls of Arm 6 Across Simulations",
+       subtitle = "Binwidth = 100. Budget = 7000. 5000 Simulations.
+Vertical line indicates pulls by uniform sampling given 10 arms in experiment.") +
+  theme_bw()
+```
+
+```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Budget allocation for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter c."}
+
+cbind.data.frame(
+  Arm = rep(c("01", "10"), each = 15000),
+  rbind.data.frame(pulls_arm_1_long, pulls_arm_10_long),
+  stringsAsFactors = FALSE
+) %>% 
+  ggplot(aes(x = Pulls, group = Arm)) +
+  geom_histogram(binwidth = 50) +
+  facet_grid(Arm~Algorithm, scales = "free_y")+
+  geom_vline(aes(xintercept = 7000/10), linetype = 2) +
+  labs(x = "Pulls", y = "Count", 
+       title = "Distribution of Pulls of Arms 1 and 10 Across Simulations",
+       subtitle = "Binwidth = 50. Budget = 7000. 5000 Simulations.
+Vertical line indicates pulls by uniform sampling given 10 arms in experiment.") +
+  theme_bw()
+```

### 2017-08-31 Thesis/Draft.tex
Add D-Tracking Rule

@@
-\documentclass[12pt,]{article}
+\documentclass[11pt,]{article}
 \usepackage{lmodern}
@@
 
-\section{\texorpdfstring{Thresholding Bandit Problem
-\label{chap:ThresholdingBanditProblem}}{Thresholding Bandit Problem }}\label{thresholding-bandit-problem}
+\section{\texorpdfstring{The Thresholding Bandit Problem
+\label{chap:ThresholdingBanditProblem}}{The Thresholding Bandit Problem }}\label{the-thresholding-bandit-problem}
 
@@
 
-\subsection{\texorpdfstring{Lower Bound: Theorem and Proof
-\label{sec:LowerBoundLocatelli}}{Lower Bound: Theorem and Proof }}\label{lower-bound-theorem-and-proof}
+\subsection{\texorpdfstring{Lower Bound for the Thresholding Bandit
+Problem
+\label{sec:LowerBoundLocatelli}}{Lower Bound for the Thresholding Bandit Problem }}\label{lower-bound-for-the-thresholding-bandit-problem}
+
+Locatelli et al. (2016) also provide a general lower bound on the
+probability of error in the thresholding bandit problem. The bound is
+derived for a specified set of problems through a change in distribution
+as common in the multi-armed bandit literature (compare for example
+Audibert et al., 2010, or Kaufmann et al., 2016). For any of these
+problems, the largest probability of error that the best algorithm
+incurs is still lower bounded by the bound given below.
 
@@
 
-\emph{Proof of Theorem \ref{theorem:Locatelli2016Theorem1}}: In Theorem
-\ref{theorem:Locatelli2016Theorem1} of Locatelli et al. (2016), a lower
-bound for the thresholding bandit problem is shown. The basic idea is as
-follows. The problem formulation considered in the paper describes
-bandit problems for sub-Gaussian distributions. To show a lower bound,
-we show that every algorithm is expected to make a certain error even if
-we restrict ourselves to a very restricted scenario. Even then, any
-algorithm will have a certain level of risk with which it cannot
-distinguish between the actual setting and slightly changed settings
-(under which the former answer leads to regret).
-
-To be more specific, consider a case in which we set \(\tau = 0\) and
-\(\epsilon = 0\) w.l.o.g. If we then choose all arms to have normally
-distributed feedback with means \(\mu_i\), we see that for each arm
-\(i\) the distance from the threshold is given by
-\(\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i\). Thus, assuming a
-variance of 1 for every arm, we have for every arm the distribution
-\(\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)\). Furthermore,
-define for each arm \(i \in \{1, \dots, K\}\) the alternative
-distribution \(\nu_i' = \mathcal{N}(-\Delta_i,1)\). It is easy to see
-that in this case, this is equivalent to a ``flip around the
-threshold''. Arms that originally have a mean larger than the threshold
-have a mean smaller than the threshold after the flip.
-
-The idea now is that every arm \(i \in \{1,\dots,K\}\) generates a
-sample for every time point \(t\in \{1, \dots, T\}\) from its
-distribution \(\nu_i\) before the algorithm starts to choose arms. Thus,
-we have a \(T \times K\) table of realized observations from the product
-distribution given by
-\(\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K\).
-This is a product distribution where the \(K\) different means all lie
-above the threshold. We would hope that an algorithm classifies the
-means accordingly. However, we will show in what follows that any
-algorithm makes a certain error by not being able to distinguish
-\(\mathcal{B}^0\) from at least one of \(K\) alternative product
-distributions \(\mathcal{B}^i, i \in \{1, \dots, K\}\), of which each
-differs only slightly in one arm from the original distribution, and has
-the same overall complexity (as defined by
-\(H = \sum_{i=1}^K (\Delta_i)^{-2}\)). We require \(K\) different
-distributions so that an arm sampling arm \(i\) very often for some
-reason will not have a smaller lower bound by chance.
-
-For each of the \(K\) arms, we introduce an alternative model of the
-following kind. Before the start of the algorithm, we introduce a slight
-variation in the setup. The idea is similar to how one can switch arms
-in the pure exploration setup for multi-armed bandits (compare Audibert
-et al., 2010; Garivier \& Kaufmann, 2016) to ``confuse'' any algorithm
-without introducing additional complexity to the specified problem.
-However, since we do not compare arms directly with each other in the
-thresholding bandit problem (switching arms would still keep all means
-above the threshold), we instead need to flip an arm \(i\) with respect
-to the threshold in order to get the alternative model
-\(\mathcal{B}_i\). Since the threshold is \(\tau = 0\), we have for the
-flipped arm the new distribution \(\nu_i'\) as defined above. Indeed, we
-can define the new product distribution
-\(B^i = \nu_1^i \otimes \dots \otimes \nu_K^i\) where for
-\(k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}\).
-This flipping of the arm corresponds to multiplying all random variables
-\(X_{i,t}\) of arm \(i\) by \(-1\).
-
-As in Locatelli et al. (2016), we let for \(i \leq K\),
-\(\mathbb{P}_{\mathcal{B}^i}\) define the probability distribution
-describing all samples that a bandit strategy can potentially collect up
-to horizon \(T\), i.e.~according to the samples
-\((X_{k,s})_{k\leq K, s \leq T} \sim (\mathcal{B}^i)^{\otimes T}\).
-\((T_k)_{k\leq K}\) denotes the number of samples collected on arm \(k\)
-until time \(T\).
-
-\subsubsection{Reminder about the goal of the
-proof}\label{reminder-about-the-goal-of-the-proof}
-
-At this point, we have defined a finite set of problems of Gaussian
-distributions with fixed variance 1 for a given set of set of gaps
-between the means of the distributions and the threshold, \((d_k)_k\).
-We will now proof a lower bound on the worst case regret of any
-algorithm; that is, the maximum error probability that even the best
-algorithm makes on this problem.
-
-\subsubsection{Statistical Decision}\label{statistical-decision}
-
-Given our formulation of the regret, the expected regret
-\(\mathbb{E}[\mathcal{L}(T)]\) corresponds directly to the probability
-of making a wrong classification of any of the \(K\) means. In general,
-let \(g\) be a binary decision function, and define
-\(\Omega = \{g = 0\}\) and \(\Omega^C = \{g = 1\}\). Assume that the
-decision \(T\) distinguishes between two states of the world, \(H_0\)
-and \(H_1\). Then our overall error probability is given by
-\(P_{H_0}(g=1) + P_{H_1}(g = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)\).
-
-In our case, \(H_0\) may correspond to the state in which we have
-\(\mathcal{B}^0\), and \(H_1\) corresponds to the case where any arm has
-been flipped, \(\mathcal{B}^i\). Furthermore, we consider the events in
-which the algorithm, making the decision, classifies arm \(i\) as being
-above the threshold: \(\mathcal{A}_i = \{i \in \hat{S}_\tau\}\). The
-event on which all arms are being classified as above the threshold is
-consequently given by \(\mathcal{A} = \bigcap \mathcal{A}_i\). However,
-Theorem 1 does not bound the overall regret, but the maximum error
-probability on the \(K+1\) different models. We can write this now as
-
-\begin{align}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big) \\
-& = \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
-\end{align}
-
-In order to give a bound on above equation, we start by considering
-\(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\). This probability can be
-written as the expected change in the likelihood of observed data when
-moving from distribution \(P_{\mathcal{B}_0}\) to \(P_{\mathcal{B}_i}\),
-times the probability under the original state. In other words, the
-probability of event \(\mathcal{A}_i\) under state \(\mathcal{B}^i\) is
-given as the probability of \(\mathcal{A}_i\) under the (original) state
-\(\mathcal{B}^0\) multiplied by a factor. This factor describes whether
-the new distribution increases or decreases the probability of the
-event, and is given by the change in the data likelihoods due to moving
-from \(\mathcal{B}^0\) to \(\mathcal{B}^i\), expressed as the expected
-likelihood ratio under \(\mathcal{B}^0\). By definition, the latter is
-equal to the empirical Kullback-Leibler divergence of the two
-distributions.
-
-We will define the change of distribution in terms of the empirical
-log-likelihood for our case. Then, we will show how to replace the
-log-likelihood by the empirical Kullback-Leibler divergence. So let us
-first introduce the empirical Kullback-Leibler divergence.
-
-Let every \(\nu_i, \nu_i'\) be dominated by the Lebesgue measure
-\(\lambda\). Then their density functions are given by
-\(f_i = \frac{\der \nu_i}{\der \lambda}\) and
-\(f_i' = \frac{\der \nu_i'}{\der \lambda}\) respectively. For
-\(T \geq t \geq 0\), define the empirical Kullback-Leibler divergence as
-
-\begin{align*}
-\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log(\frac{\der \nu_k'}{\der \nu_k}(X_{k,s})) \\
-& = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
-& = \frac{1}{t} \log \big( \prod_{s=1}^{t} \frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
-& \stackrel{\text{iid}}{=} \frac{1}{t} \log \big( \frac{f_k'(X_{k,1}, \dots,X_{k,t})}{f_k(X_{k,1}, \dots,X_{k,t})} \big) \\
-& = \frac{1}{t} \log \big( \text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k) \big)
-\end{align*}
-
-Since we consider Gaussian distributions with variance 1, we have
-density functions
-\(f_i(x) \propto \exp \big(-\frac{1}{2} (x-\Delta_i)^2\big)\) and
-\(f_i'(x) \propto \exp \big(-\frac{1}{2} (x+\Delta_i)^2\big)\). Plugging
-this into the above definition of the empirical Kullback-Leibler
-divergence, we easily see
-
-\begin{align*}
-\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{\exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2\big)}{\exp \big(-\frac{1}{2} (X_{k,s}-\Delta_k)^2\big)} \big) \\
-& = \frac{1}{t} \sum_{s=1}^{t} \log \big( \exp(-\frac{1}{2} (X_{k,s}+\Delta_k)^2 + \frac{1}{2} (X_{k,s}-\Delta_k)^2) \big) \\
-& = - \frac{1}{t} \sum_{s=1}^{t} 2 X_{k,s} \Delta_k
-\end{align*}
-
-\subsubsection{Change of Distribution}\label{change-of-distribution}
-
-We are now ready to state the change of distribution. As alluded to
-above, we consider how the probability changes for the event
-\(\mathcal{A}_i\) when we move from \(\mathcal{B}^0\) to
-\(\mathcal{B}^i\). When flipping arm \(i\), we only changed the samples
-of this arm, that is, the first \(T_i\) observations we got from arm
-\(i\) the algorithm took. The change of distribution is then defined as:
-
-\begin{align*}
-\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \text{LR}((X_{i,1}, \dots,X_{i,T_i}), \nu_i', \nu_i) ] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ]
-\end{align*}
-
-Obviously, \(\hat{\KL}_{i,T_i}\) depends on the realized samples
-\(X_{i,1}, \dots,X_{i,T_i}\). Consequently, we need to find a bound on
-\(\hat{\KL}_{i,T_i}\) itself to incorporate the uncertainty involved in
-this metric.
-
-\subsubsection{Concentration of the Empirical Kullback-Leibler
-Divergence}\label{concentration-of-the-empirical-kullback-leibler-divergence}
-
-For our problem, the Kullback-Leibler divergence of \(\nu_k'\) from
-\(\nu_k\) is given by \(\KL_k := KL(\nu_k', \nu_k) = 2\Delta_k^2\).
-
-It is easy to see that
-
-\begin{equation*}
-|\hat{\KL}_{k,t} - \KL_{k,t}| = |-\frac{2}{t} \Delta_k \sum_{s=1}^{t}(X_{k,s} - \Delta_k)|
-\end{equation*}
-
-itself is a normally distributed random variable with mean zero and a
-variance decreasing in \(t\). Thus, one can show as in Locatelli et al.
-(2016) that \(\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4\) for the event
-
-\begin{equation}
-\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}}\}. \label{LocatelliTheorem1EventXi}
-\end{equation}
-
-Thus, in order to bound the empirical Kullback-Leibler divergence in our
-change of measure, we can consider the intersection of \(\mathcal{A}_i\)
-and \(\xi\) as follows and plug in the bound on event \(\xi\):
-
-\begin{align*}
-\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
-\end{align*}
-
-Two things are left to do: With \(T_i\), we still have one random
-variable left which we cannot leave in our bound. Second, we are
-actually not interested in \(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)
-but in
-\(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\).
-
-\subsubsection{\texorpdfstring{Bounding \(T_i\) for
-\(\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)}{Bounding T\_i for \textbackslash{}max\_\{i \textbackslash{}in \textbackslash{}\{1,\textbackslash{}dots,K\textbackslash{}\}\}\textbackslash{}mathbb\{P\}\_\{\textbackslash{}mathcal\{B\}\^{}i\}(\textbackslash{}mathcal\{A\}\_i)}}\label{bounding-t_i-for-max_i-in-1dotskmathbbp_mathcalbimathcala_i}
-
-Part of our bound is
-\(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\),
-so let's continue with that. In general it holds that
-\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K}\sum_{i=1}^K X_i\).
-Thus we can write:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
-& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
-& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
-\end{align*}
-
-where the second line is again the intersection of \(\mathcal{A}_i\) and
-\(\xi\) as before in order to apply the change of distribution in the
-third line.
-
-What is left to show before we have our final bound is a bound on
-\(T_i\). To show that any algorithm has a certain bound on its error, it
-only makes sense that every arm has to pulled at least a certain amount
-of times. Consequently, no arm should be pulled exclusively.
-
-First, let \(a = \Delta_i \sqrt{T_i}\) and
-\(b = 4\sqrt{\log((4\log(T)+1)K)}\). Then use \(ab \leq a^2 + b^2\) to
-write \(ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)\). And so:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) ]
-\end{align*}
-
-Furthermore, we know that the sum of the individual arm pulls has to be
-equal to the overall number of pulls (equal to the budget in the fixed
-budget sense), \(\sum_i T_i = T\), and furthermore we know that
-\(T_i>0\). The latter holds since any reasonable algorithm has to check
-each arm at least once in our setup. This is because we need to check
-each arm's performance in comparison to the threshold. Thus it is easy
-to show that
-\(\exists i: T_i \leq \frac{T}{H \Delta_i^2} = \frac{T}{(\sum_{i=1}^{K} \Delta_i^{-2}) \Delta_i^2}\).
-To see this, assume the opposite:
-\(\forall i: T_i > T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2}\). This
-implies however
-\(\sum_{i=1}^K T_i > \sum_{i=1}^K T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2} = T \cdot 1 = T\)
-which is a contradiction.
-
-So we can write \((\Delta_i \sqrt{T_i})^2 \leq \frac{T}{H}\). We use
-\(\mathcal{A} = \cap_{i=1}^K \mathcal{A}_i\) to write:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}{K} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big]
-\end{align*}
-
-We write
-\(\frac{1}{K} \sum_{i=1}^K \exp(-3T_i \Delta_i^2) \geq \frac{1}{K} \sum_{i=1}^K \exp(-3 T/H) = \exp(-3 T/H)\).
-Thus:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i) \exp(-16 \log(4(\log(T)+1)K)) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
-& = \mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
-\end{align*}
-
-\subsubsection{Bringing everything
-together}\label{bringing-everything-together}
-
-Consider again the risk which we need to bound from equation
-\eqref{LocatelliTheorem1ExpRegret}. We bound the maximum expected loss
-over all \(\mathcal{B}_i\). By again using the fact that in general
-\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K} \sum_{i = 1}^K X_i\),
-we plug in our previous calculations:
-
-\begin{align}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \label{LocatelliTheorem1DefinitionOfRisk}
-\end{align}
-
-From \eqref{LocatelliTheorem1EventXi} we know that for any
-\(i \in \{0, \dots, K\}\), \(\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4\).
-Following the argument in Locatelli et al. (2016), we now consider two
-cases: \(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2\) and
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2\). In the former
-case, we can plug in the two probabilities into
-\eqref{LocatelliTheorem1DefinitionOfRisk}. If
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2\) and
-\(\mathbb{P}_{\mathcal{B}^0}(\xi) \geq 3/4\), then
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \geq 1/4\). Thus:
-
-\begin{align*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \\
-& \geq \frac{1}{8} \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
-\end{align*}
-
-where we drop the second summand of the second line so that the
-inequality holds.
-
-On the other hand, when
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2\), then we know that
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \leq 1/2\) for any
-\(\mathbb{P}_{\mathcal{B}^0}(\xi)\). At the same time
-\(1-\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \geq 1/2\).
-Consequently,
-\(1/4 \leq \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \leq 1/2\),
-while
-\(\frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) \geq 0\).
-And so the stronger lower bound in that case is, as noticed by Locatelli
-et al. (2016), given simply by
-
-\begin{align*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \\
-& \geq \frac{1}{2}
-\end{align*}
+A proof of the lower bound is given in the Appendix in
+\autoref{sec:AppendixAPTLB}.
+
+If we write the lower bound as
+\(LB = 12(\log(T)+1)K)\exp(-3T/H)\exp(-4) = C_{LB}(\log(T)+1)K\exp(-T/H)\)
+and the upper bound as
+\(UB = (\log(T)+1)K \exp(2) \exp(-\frac{1}{64R^2}\frac{T}{H}) = C_{UB}(\log(T)+1)K\exp(-T/H)\),
+we see that \(LB\) and \(UB\) match up to multiplicative constants and
+the \((\log(T)+1)K\) term which is negligiable in comparison with the
+exponent for large \(T\) as shown in Locatelli et al. (2016), which
+makes the APT algorithm order optimal.
 
@@
 \autoref{sec:LikelihoodRatioForExponentialFamily}, we first describe the
-variance-based approaches in \autoref{chap:VarianceBasedAlgorithms}.
+variance-based approaches in \autoref{sec:VarianceBasedAlgorithms}.
 
@@
 
-\section{\texorpdfstring{Kullback-Leibler Complexity of Pure Exploration
-\label{chap:KullbackLeiblerPureExploration}}{Kullback-Leibler Complexity of Pure Exploration }}\label{kullback-leibler-complexity-of-pure-exploration}
-
-In the previous chapter, we discussed the thresholding bandit problem as
-presented in Locatelli et al. (2016). Doing so, we came across the
-complexity term \(H = \sum_{i=1}^{K} \Delta_i^{-2}\). Furthermore, we
-noted the fact that an algorithm and bounds based on \emph{only} the gap
-between the respective mean and the threshold are useful in the case of
-sub-Gaussian problems. Furthermore, even for the case of Bernoulli arms,
-which are sub-Gaussian since their feedback is bounded on \([0,1]\), the
-gap \(\Delta\) becomes less and less appropriate in situations in which
-both \(\mu\) of the Bernoulli, and \(\tau\) are very close to 0 or 1.
-
-Even though the complexity \(H\) enjoys popularity in the literature of
-the best \(m\) arm identification problem, \(m \geq 1\), Kaufmann et al.
-(2016) show explicitly that \(H\) is mainly useful for problems of
-Gaussian distributions. Indeed, they go so far as to define new measures
-of complexity that are based on information theoretic measures. Using
-these, they then frame \(H\) as an approximation to their measures in
-the case of Gaussian distributions. This underlines the fact that
-Bernoulli distributions with small means have to be treated differently
-than Gaussian distributions.
-
-For the current chapter, we adopt the notation of Kaufmann et al. (2016)
-to ease a comparison with their arguments.
-
-\subsection{\texorpdfstring{Complexity of Best-Arm and Top-\emph{m}
-Identification}{Complexity of Best-Arm and Top-m Identification}}\label{complexity-of-best-arm-and-top-m-identification}
-
-Instead of the thresholding bandit problem, we now consider the problem
-of identifying the best \(m\) out of \(K\) arms, that is, the Top-\(m\)
-problem. While we previously looked at a fixed budget formulation, we
-now mainly focus on a fixed confidence problem: We hold the confidence
-\(1-\delta\) fixed at which a strategy returns the correct \(m\) arms
-while trying to reach this confidence in a way that minimizes the sample
-complexity \(\mathbb{E}_{\nu}[\tau]\), that is, the expected number of
-overall draws of the arms. \(\tau\) is also called the stopping time of
-the algorithm. The goal of algorithms is to identify
-\(\mathcal{S}_m^*\), the set of the \(m\) arms with the largest means.
-If we let \((\mu_1, \dots, \mu_K)\) be the vector of the means of the
-arms, then let \((\mu_{[1]}, \dots, \mu_{[K]})\) be the tuple in which
-the means are arranged in decreasing order. For the rest of this
-chapter, we consider only settings with arms for which
-\(\mu_{[m]} > \mu_{[m+1]}\); we demand the set of the top \(m\) arms,
-\(\mathcal{S}_m^*\), to be unique. After the sampling phase, we require
-any algorithm to return the set \(\hat{S}_m \subset \{1,\dots,K\}\) of
-\(m\) arms that the algorithm believes to have the largest means. In the
-case of fixed confidence, we fix \(\delta\) at the beginning, such that
-the algorithm only stops sampling when
-\(\mathbb{P}_{\nu}(\hat{S}_m = \mathcal{S}_m^*) \geq 1-\delta\). We try
-to find algorithms who fulfill this condition as quickly as possible.
-Algorithms which minimize the expected stopping time (or number of
-draws), \(\mathbb{E}_{\nu}[\tau]\).
-
-To arrive at the new measure of complexity proposed by Kaufmann et al.
-(2016), it will actually make sense to first follow their arguments to a
-general lower bound on the sample complexity \(\mathbb{E}_{\nu}[\tau]\)
-in the case of fixed confidence problems. This bound is given in their
-Theorem 4 (for common confidence levels of \(\delta \leq 0.15\)).
+\section{\texorpdfstring{Information Theoretic Complexity of Pure
+Exploration Bandits
+\label{chap:KullbackLeiblerPureExploration}}{Information Theoretic Complexity of Pure Exploration Bandits }}\label{information-theoretic-complexity-of-pure-exploration-bandits}
+
+The previous chapter introduces the thresholding bandit problem as
+described in Locatelli et al. (2016), and with the APT strategy a first
+algorithm that is simple, yet order-optimal for large budgets. However,
+we end with the conclusion that a distance measure between the
+distributions and the threshold based on the Kullback-Leibler divergence
+might be more useful than the simple gap
+\(\Delta^2_i = (\mu_i - \tau_i)^2\) employed so far. Indeed, citing
+Kaufmann et al. (2016), we note that the complexity \(H\) used so far
+can be considered a sub-Gaussian approximation of a better complexity
+measure based on information theoretic measures like the
+Kullback-Leibler divergence.
+
+In order to give more intuition to why that is the case, and in what
+ways information theoretic measures can be introduced to measure the
+complexity of bandit problems, we now turn to Kaufmann et al. (2016) and
+Garivier and Kaufmann (2016). The latter describes a strategy based on
+Kullback-Leibler divergences for the best-arm identification problem,
+while the first derives complexity measures based on the divergence.
+Ideally, their work offers methods that can inform our work of extending
+the thresholding bandit problem. In what follows, we adopt the notation
+of Kaufmann et al. (2016) to ease a comparison with their arguments.
+
+\subsection{\texorpdfstring{Complexity Measures for Best-Arm and
+Top-\emph{m} Identification
+\label{sec:KaufmannEtAl2016}}{Complexity Measures for Best-Arm and Top-m Identification }}\label{complexity-measures-for-best-arm-and-top-m-identification}
+
+Instead of the thresholding bandit problem, Kaufmann et al. (2016)
+consider the problem of identifying the best \(m\) out of \(K\) arms,
+that is, the Top-\(m\) problem. They describe their a bandit model
+\(\nu\) also by \(K\) arms characterized by probability distributions
+\(\nu_a\), \(a \in \{1,...,K\}\) with mean \(\mu_a\). As before, a
+learner decides at any time step \(t=1,2,...,\) an arm
+\(A_t \in \{1,...,K\}\) for which he observes the independent reward
+\(Z_{t} \sim \nu_{A_t}\). The learner aims to find the \(m\) out of
+\(K\) arms with the largest expected reward. This set of arm indices is
+denoted by \(\mathcal{S}_m^*\). Kaufmann et al. write the in decreasing
+order sorted means \((\mu_{1}, ..., \mu_{K})\) as the K-tuple
+\((\mu_{[1]}, ..., \mu_{[K]})\). Based on this, they require that
+\(\mu_{[m]} > \mu_{[m+1]}\) such that the solution \(\mathcal{S}_m^*\)
+is unique. The class of bandit problems \(\nu\) for which the latter
+condition holds is called \(\mathcal{M}_m\) by Kaufmann et al. At the
+end of the sampling procedure, after \(T\) samples (denoted by \(\tau\)
+in Kaufmann et al.) the learner is required to return a classification
+\(\hat{\mathcal{S}}_m\). This classification is then evaluated by the
+loss function
+\(\mathcal{L}(T) = \mathbb{I}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m)\).
+This binary loss is of course very similar to the loss in the
+thresholding bandit problem. We can now define a strategy of the learner
+as \(\mathcal{A} = ((A_t), T, \hat{\mathcal{S}}_m)\): The strategy
+defines how he chooses an arm, how many samples are observed, and how
+the arms are classified in the end.
+
+When introducing the thresholding bandit setting, we did not mention the
+fact that the budget \(T\) does not need to be fixed upfront. Indeed,
+the setting in which the budget is \emph{not} fixed upfront might be
+more popular among the best arm identification and top-\(m\) literature.
+This setting is called \emph{fixed-confidence}, while the setting we
+considered so far is called \emph{fixed-budget}. In the fixed-budget
+setting, we run algorithms for \(T\) samples and then compare them based
+on their expected loss,
+\(\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m) =: p_t(\nu)\)
+as we have seen in \(\autoref{sec:Setup}\). Alternatively, consider a
+\(\delta\)-PAC strategy \(\mathcal{A}(\delta)\)for which holds for every
+problem \(\nu \in \mathcal{M}_m\) that the classification holds at least
+with confidence level \(1-\delta\), that is,
+\(\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta\). The
+strategy has to achieve this level of confidence in its prediction
+before it is allowed to stop sampling. This is the fixed-confidence
+case, in which the budget \(T\) is no longer fixed upfront, but becomes
+a random variable. We compare algorithms by their expected number of
+draws \(\mathbb{E}_{\nu}[T_{\delta}]\) and prefer those which arrive at
+the confidence level \(1-\delta\) with a smaller expected budget.
+
+Following Kaufmann et al. (2016), in the fixed confidence setting, a
+family of strategies \(A = (\mathcal{A}(\delta))_{\delta \in (0,1)}\) is
+called PAC if for every \(\delta\), \(\mathcal{A}(\delta)\) is
+\(\delta\)-PAC. On the other hand, in the fixed budget setting, a family
+of strategies \(A = (\mathcal{A}(t))_{t \in \mathbb{N}}\) is called
+consistent if \(p_t(\nu) \rightarrow 0\) as \(t \rightarrow \infty\) for
+every problem \(\nu \in \mathcal{M}_m\).
+
+Given this setup, we can now follow the arguments of Kaufmann et al.
+(2016) to deduce complexity measures for the top-\(m\) problem. As
+alluded to earlier, these complexity measures will rely on the
+Kullback-Leibler divergence in contrast to the complexity \(H\) used by
+Locatelli et al. (2016). Also, when discussing \(H\), we so far
+described it as complexity as it measures the difficulty of the problem
+by measuring the distance between arms and the threshold. Kaufmann et
+al. approach complexity instead from how many samples (what error
+probability) one can expect to need in the fixed confidence (fixed
+budget) setting. Thus, in order to arrive at their new measure of
+complexity, it makes sense to first follow their arguments to a general
+lower bound on the sample complexity \(\mathbb{E}_{\nu}[\tau]\) in the
+case of fixed confidence top-\(m\) problems. This bound is given in
+their Theorem 4 (for common confidence levels of \(\delta \leq 0.15\)).
 
@@
 its contribution to the overall complexity of the problem (or sampled
-exactly according to its contribution), which leads to leads to a
-convenient upper bound on this arms number of draws which is again
-employed in both the proof of Theorem
-\ref{theorem:KaufmannEtAlTheorem17} and in Locatelli et al. (2016). It
-is not clear yet, whether the same can also be done with other
-complexity measures.
+exactly according to its contribution), which leads to a convenient
+upper bound on this arms number of draws which is again employed in both
+the proof of Theorem \ref{theorem:KaufmannEtAlTheorem17} and in
+Locatelli et al. (2016). It is not clear yet, whether the same can also
+be done with other complexity measures.
 
@@
 \(H^{\text{EVT}_{pf}}\), the Zhong et al. (2017) show that the
-EVT\(_pf\) algorithm is optimal in that its upper bound matches the
+EVT\(_{pf}\) algorithm is optimal in that its upper bound matches the
 lower bound. Furthermore, they compare their algorithm in experiments
@@
 In this case the problem complexity \(H^{\text{EVT}_{pf}}\) can be much
-smaller than \(H^{APT}\) -- the EVT algorithm profits more from
+smaller than \(H^{APT}\) -- the EVT\(_{pf}\) algorithm profits more from
 distributions that are simple to estimate in terms of their variance
@@
 
-\subsubsection{Likelihood Ratio for Univariate Exponential Family of
-Distributions}\label{likelihood-ratio-for-univariate-exponential-family-of-distributions}
+\subsubsection{\texorpdfstring{Likelihood Ratio for Univariate
+Exponential Family of Distributions
+\label{sec:LRforUnivariateExponentialFamily}}{Likelihood Ratio for Univariate Exponential Family of Distributions }}\label{likelihood-ratio-for-univariate-exponential-family-of-distributions}
 
@@
 \(H_1: \mu = \hat{\mu} \land \sigma^2 = \hat{\sigma}^2 = \frac{1}{n}\sum_{i=1}^{n}(x_i-\hat{\mu})^2\).
-
-In the following, we assume \(\epsilon = 0\).
-
-Now, at each round \(t\), the algorithm computes \(T_i(t)\) and
+In the following, we assume \(\epsilon = 0\) for simplicity.
+
+At each round \(t\), the algorithm computes \(T_i(t)\) and
 \(\hat{\mu}_i(t)\) as before, and additionally the empirical variances
@@
 and
-\(\hat{\sigma}_{i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\hat{\mu})^2\).
-The index is then given by
+\(\hat{\sigma}_{i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\hat{\mu})^2\),
+where \(\hat{\sigma}_{i}^2(t) < \sigma_{\tau,i}^2(t)\) if
+\(\hat{\mu} \neq \tau\) since \(\hat{\mu}\) is the maximum likelihood
+estimate. The index is then
 
 \begin{align*}
-B_i^{SLR_{2D}}(t+1) & = -\log(LR(\tau, \sigma_{\tau,i}^2(t)||\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t))) \\
+B_i^{SLR_{2D}}(t+1) & = -\log\big(LR(\tau, \sigma_{\tau,i}^2(t)||\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t))\big) \\
 & = T_i(t) \log\Big(\frac{\sigma_{\tau,i}^2(t)}{\hat{\sigma}_i^2(t)}\Big) \\
-& = T_i(t) KL(N(\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t))||N(\tau, \sigma_{\tau,i}^2(t)))
+& = T_i(t) \KL\big(N(\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t))||N(\tau, \sigma_{\tau,i}^2(t))\big) \Alignyesnumber\label{eqn:SLR2DIndex}
 \end{align*}
@@
 Then, as for the univariate case, the next arm to be pulled is the
-minimizer of the index \(B_i^{2DSLR}(t+1)\),
-\(I_{t+1} = \arg \min_{i\leq K} B_i(t+1)\). At the end of the horizon
+minimizer of the index \(B_i^{SLR_{2D}}(t+1)\),
+\(I_{t+1} = \arg \min_{i \leq K} B_i(t+1)\). At the end of the horizon
 \(T\), the algorithm outputs the set of arms
-\(\hat{S}_\tau = \{k: \hat{\mu}_k(T) \geq \tau\}\).
-
-\subsubsection{Discussion}\label{discussion-1}
+\(\hat{S}_\tau = \{i \in \mathbb{A}, \hat{\mu}_i(T) \geq \tau\}\).
+
+\IncMargin{1em}
+
+\begin{algorithm}
+\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
+\Input{\emph{$\tau$, $\epsilon$, $\nu(\mu, \theta) = N(\mu,\sigma^2) \, \forall i \in \mathbb{A}$, where $\mu$ and $\sigma^2$ are unknown}}
+\Output{$\hat{S}_\tau = \{i \in \mathbb{A},  \hat{\mu}_i(T) \geq \tau\}$}
+\BlankLine
+\emph{Pull each arm twice}\;
+\For{$t = 2K+1$ \KwTo $T$}{
+\For{$i = 1$ \KwTo $K$}{
+  \emph{Compute $\hat{\sigma}^2_{i}(t)$}\;
+  \If{$\hat{\sigma}^2_{i}(t) = 0$}{\emph{Set $\hat{\sigma}^2_{i}(t) = 1/T$}}
+}
+  \emph{Pull arm $I_t = \arg \min_{i\leq K} B_i^{SLR_{2D}}(t)$ as in \autoref{eqn:SLR2DIndex}}\;
+  \emph{Observe reward $X \sim \nu_{I_t}$}\;
+}
+\caption{2D-SLR algorithm for Normal distributions with unknown mean and unknown variance}\label{algo_slr_2d}
+\end{algorithm}
+
+\DecMargin{1em}
+
+\subsection{Discussion}\label{discussion-1}
 
@@
 Locatelli et al. (2016) for the thresholding bandit problem in two
-directions. First, we wanted to make the algorithm perform better in
-problems that are not well approximated as sub-Gaussian; that is, in
-particular a problem with Bernoulli arms with small means and low
-threshold. Unsurprisingly, this meant that we need to find a solution
-that takes more into account than just the sample mean. With the Simple
-Likelihood Ratio strategy, we propose an algorithm that fulfills that
-goal at the cost of being distribution specific.
-
-The Simple Likelihood Ratio strategy requires the knowledge of the class
-of distribution upfront, just as other algorithms require parameters.
-While this is likely to be a negligiable problem in the case of
-\(\{0,1\}\) observations which can be modeled reasonably by Bernoulli
-distributions if we are only interested in estimating the mean, it can
-be more difficult to know the true class of distribution upfront when
-the random variables can take values in \(\mathbb{R}\). We have shown
-however, that the SLR strategy can be adapted to all univariate
-distributions in the exponential family of distributions. The algorithm
-even offers a natural adaptation to the problem of normal distributions
-with unknown mean and unknown variance.
-
-Furthermore, the Simple Likelihood Ratio strategy reduces to the Anytime
-Parameter Free strategy in the case where arms are normally distributed
-with equal variance that is known upfront. In that case we have as index
-(compare example 3 above):
-
-\[
+points. First, we wanted to make the algorithm perform better in
+problems with arms that are not well approximated as sub-Gaussian; in
+particular a problem with Bernoulli arms of small means, and with a
+threshold close to 0. We thus tried to find a strategy that takes more
+information about the arms into account than purely the sample mean.
+With the Simple Likelihood Ratio strategy, we propose an algorithm that
+fulfills this goal at the cost of being distribution specific.
+
+The SLR strategy requires the knowledge of the class of distribution
+upfront, just as other algorithms require parameters. While this is
+likely to be a negligiable problem in the case of \(\{0,1\}\)
+observations whose mean can be modeled reasonably by Bernoulli
+distributions, it can be more difficult to know the true class of
+distributions upfront when \(\nu_i\) are continuous distributions. We
+have shown however, that the SLR strategy can be adapted to all
+univariate distributions in the exponential family of distributions. The
+algorithm even offers a natural adaptation to the problem of normal
+distributions with unknown mean and unknown variance.
+
+Furthermore, the SLR strategy reduces to the APT strategy in the case
+where arms are normally distributed with equal variance that is known
+upfront. In that case we have as index (compare example 3 above): \[
 B_i^{SLR}(t) = T_i(t)\frac{(\hat{\mu}_i(t) - \tau)^2}{2\sigma^2}.
@@
 
-\[
-B_i^{SLR}(t) < B_j^{SLR}(t) \Leftrightarrow 
-T_i(t)\frac{(\hat{\mu}_i(t) - \tau)^2}{2\sigma^2} < T_j(t)\frac{(\hat{\mu}_j(t) - \tau)^2}{2\sigma^2} 
-\Leftrightarrow 
-\sqrt{T_i(t)}\sqrt{(\hat{\mu}_i(t) - \tau)^2} < \sqrt{T_j(t)}\sqrt{(\hat{\mu}_j(t) - \tau)^2}
-\Leftrightarrow 
+\begin{align*}
+B_i^{SLR}(t) < B_j^{SLR}(t) & \Leftrightarrow 
+T_i(t)\frac{(\hat{\mu}_i(t) - \tau)^2}{2\sigma^2} < T_j(t)\frac{(\hat{\mu}_j(t) - \tau)^2}{2\sigma^2} \Alignyesnumber\label{eqn:SLRWithKnownVar}\\
+& \Leftrightarrow 
+\sqrt{T_i(t)}\sqrt{(\hat{\mu}_i(t) - \tau)^2} < \sqrt{T_j(t)}\sqrt{(\hat{\mu}_j(t) - \tau)^2} \\
+& \Leftrightarrow 
 B_i^{APT}(t) < B_j^{APT}(t)
-\]
-
-Given that in all other cases the Simple Likelihood Strategy is able to
-take more information about the distributions into account through the
-Kullback-Leibler divergence (in the case of the exponential family of
-distributions), the algorithm is expected to improve upon the Anytime
-Parameter Free strategy.
+\end{align*}
+
+Given that in all other cases the SLR is able to take more information
+about the distributions into account through the Kullback-Leibler
+divergence (in the case of the exponential family of distributions), the
+algorithm is expected to improve upon the APT strategy. Just consider a
+situation of known, but different variances for Normal distributions.
+Then we had in \autoref{eqn:SLRWithKnownVar} \(\sigma_i^2\) and
+\(\sigma_j^2\) instead of \(\sigma^2\), which should lead to more pulls
+of the arm with larger variance. This is not taken into account by APT.
 
 As mentioned before, this improvement comes only at the cost of knowing
-the correct distribution upfront. In particular, as for the Anytime
-Parameter Free algorithm, there are no parameters which would need to be
-tuned upfront as is usually the case for upper-confidence bound based
-algorithms.
-
-Additionally, the Simple Likelihood Strategy offers an intuitive
-interpretation if we consider the index written in the form proposed by
-Zhang et al. (2017). Write the index again as
-
-\[
+the correct distribution upfront. In particular, as for the APT
+algorithm, there are no parameters which need to be tuned upfront as is
+usually the case for upper-confidence bound based algorithms (see for
+example UCB-E in Audibert et al., 2010).
+
+Additionally, the index used in the SLR algorithm offers the same
+interpretation considered in \autoref{sec:EVTAlgorithm}. Write the index
+again as \[
 B_i(t) = S_i(t) D_i(t),
-\]
-
-where \(S_i(t)\) is a confidence term of the estimate of the arm \(i\)
-at time \(t\), and \(D_i(t)\) is a measure of distance between the
+\] where \(S_i(t)\) is a confidence term of the estimate of the arm
+\(i\) at time \(t\), and \(D_i(t)\) is a measure of distance between the
 distribution of arm \(i\) and the threshold \(\tau\). The index of the
 Simple Likelihood Ratio strategy for univariate exponential family
-distributions can then be written with
-
-\[
-S_i(t) = T_i(t)
-\]
-
-and
-
-\[
+distributions can then be written with \[
+S_i(t) = T_i(t) \quad \text{and} \quad
 D_i(t) = \KL(\hat{\mu}_i(t)||\tau),
@@
 confidence measure, while the Kullback-Leibler divergence fulfills its
-role as distance between distributions. The larger the KL-divergence,
-the less inclined we are to draw the arm; the same holds, if we have
-pulled an arm many times. Since the KL-divergence reduces to the squared
-distance between means for Normal distributions of known variance, the
-SLR and APT algorithms are identical in this case.
-
-As we see in the experiments that follow, the Simple Likelihood Strategy
-is able to improve significantly upon the Anytime Parameter Free
-strategy in many cases.
+role as distance measure between distributions (see also Figure 2). The
+larger the Kullback-Leibler divergence, the less inclined we are to draw
+the arm; the same holds, if we have pulled an arm many times. Since the
+KL-divergence reduces to the squared distance between means for Normal
+distributions of known variance, the SLR and APT algorithms are
+identical in this case.
+
+As we see in the experiments that follow, the SLR strategy is able to
+improve significantly upon the APT strategy in many cases.
 
@@
 
+We now compare the algorithms introduced in the previous chapters in
+simulations and experiments against each other to evaluate their
+performance. We first perform experiments on synthetic data in
+\autoref{sec:SyntheticData}. We then use Bernoulli time series data
+collected by the online shop Amorelie to evaluate the algorithms on real
+world data in \autoref{sec:RealData}.
+
+We compare the empirical performance of the SLR algorithm not only
+against the APT algorithm, but also against the variance-based
+algorithms. Thus we also compare the variance-based algorithms for the
+first time directly against each other. As benchmark, the uniform
+sampling strategy is included. Additionally, we include the Bayes-UCB
+algorithm introduced in Kaufmann et al. (2012) for the cumulative regret
+setting. See \autoref{sec:AppendixBUCB} in the appendix for how their
+Algorithm 1 is adapted to the thresholding bandit problem.
+
 \subsection{\texorpdfstring{Synthetic Data
@@
 
-In order to evaluate the empirical performance of the proposed
-algorithms, we run the algorithm on synthetic data as is usual. We
-compare its performance on this data not only against the APT algorithm,
-but also against the variance-based algorithms. Thus we also compare the
-variance-based algorithms for the first time directly against each other
-instead of just relative to the APT algorithm.
-
-Each of the experiments is repeated for 5000 iterations. Depending on
-the experiment, the observations are generated randomly by some
-distribution of the exponential family of distributions. As we were
-originally concerned with improving upon APT with respect to
-non-sub-Gaussian distributions, the first experiments focus on Bernoulli
-distributions, and especially those with small means. We then go on to
-show with experiments on Gaussian, Exponential, and Poisson data that
-the SLR algorithm is able to improve upon APT given that we know the
-true kind of distribution.
-
-\subsubsection{\texorpdfstring{Experiment 1: Bernoulli with
-\(\tau = 0.5\)}{Experiment 1: Bernoulli with \textbackslash{}tau = 0.5}}\label{experiment-1-bernoulli-with-tau-0.5}
+Every experiment presented is repeated for 5000 iterations. Depending on
+the experiment, the observations are generated randomly by a given
+exponential family of distributions. As we are primarily concerned with
+improving upon APT with respect to non-sub-Gaussian distributions, the
+first three experiments focus on Bernoulli distributions, especially
+those with small means. We then go on to show with experiments on data
+from the Exponential distribution and Poisson distribution that the SLR
+algorithm is able to improve upon APT given that we know the true kind
+of distribution.
+
+\subsubsection{\texorpdfstring{Simulation 1: Bernoulli with
+\(\tau = 0.5\)}{Simulation 1: Bernoulli with \textbackslash{}tau = 0.5}}\label{simulation-1-bernoulli-with-tau-0.5}
 
@@
 \(\mu_5 = 0.45\), \(\mu_6 = 0.55\), and
-\(\mu_{7:10} = 0.6 + 0.2^{5-1:4}\). We run the standard APT algorithm
-with \(\epsilon = 0.1\), as well as SLR with \(\epsilon = 0.1\). We
-compare those additionally to Augmented-UCB with the standard parameter
-choice of \(\rho = 1/3\) as used by its authors in Mukherjee et al.
-(2017). We run the parameter-free version of the Empirical Variance
-Guided algorithm without any feedback delay, thus making it directly
+\(\mu_{7:10} = 0.6 + 0.2^{5-1:4}\). We run the standard APT algorithm as
+well as the SLR algorithm with \(\epsilon = 0.1\). We compare them to
+the AugUCB algorithm with the parameter choice of \(\rho = 1/3\) as used
+by its authors in Mukherjee et al. (2017). We run the parameter-free
+EVT\(_pf\) algorithm without feedback delay, thus making it directly
 comparable to the other algorithms. The Bayes-UCB algorithm takes as
@@
 \(\beta_0 = 1 - \tau\), thus leading to a mean of the prior distribution
-at \(\tau\) while keeping the prior as weak as possible. Lastly, we run
-the uniform sampling strategy as the naive benchmark.
+at \(\frac{\alpha_0}{\alpha_0+\beta_0}=\tau\) while keeping the prior as
+weak as possible. Lastly, we run the uniform sampling strategy as a
+benchmark.
 
@@
 
-This first experiment gives an experiment where all algorithms should
-perform well. The problem is not very difficult, and due to the
-threshold at \(\tau = 0.5\), the Bernoulli distribution can be perfectly
+This first experiment is a problem in which all algorithms should be
+able to perform well. The problem is not very difficult, and due to the
+threshold at \(\tau = 0.5\), the Bernoulli distribution can be well
 approximated by a Gaussian. This thus is the perfect environment for the
@@
 As the next figure shows, essentially all methods converge rapidly to an
-error rate of zero. Except for the uniform method that clearly lacks
-behind. We also observe that the variance based algorithms (Augmented
-UCB and EVT) lag behind at first. Augmented UCB is able to adjust its
-sampling scheme after 1000 iterations and rapdily improves to the level
-of APT. EVT takes about 250 samples more to start a quick descend to the
-performance of the other algorithms. All of this, however, happens below
-an error rate of 0.01. While the SLR algorithm improves upon APT, the
-improvement is a slight one, and not very large in terms of budget
-difference. This underlines that the scenario at hand is the ideal one
-for the APT algorithm.
-
-\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation1_results-1} \end{center}
-
-\subsubsection{\texorpdfstring{Experiment 2: Bernoulli with
-\(\tau = 0.05\)}{Experiment 2: Bernoulli with \textbackslash{}tau = 0.05}}\label{experiment-2-bernoulli-with-tau-0.05}
+error rate of very close to zero. That is, except for the uniform
+strategy that clearly lacks behind. We also observe that the variance
+based algorithms (AugUCB and EVT) lag behind at first. AugUCB is able to
+adjust its sampling scheme only after 1000 iterations but then rapdily
+improves to the level of APT. EVT takes about 250 samples more to start
+a quick descend to the performance of the other algorithms. All of this,
+however, happens after the algorithms are below an error rate of 0.01.
+While the SLR algorithm improves upon APT, the improvement is a slight
+one, and not very large in terms of budget difference. This underlines
+that the scenario at hand is ideal for the APT algorithm.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation1_results-1}
+
+}
+
+\caption{Performance comparison of algorithms for simulation 1.}\label{fig:simulation1_results}
+\end{figure}
+
+\subsubsection{\texorpdfstring{Simulation 2: Bernoulli with
+\(\tau = 0.05\)}{Simulation 2: Bernoulli with \textbackslash{}tau = 0.05}}\label{simulation-2-bernoulli-with-tau-0.05}
 
@@
 threshold of \(\tau = 0.05\) and without an epsilon interval,
-\(\epsilon = 0\). Consequently, we choose the distributions for the arms
-to be much smaller too, and arrange them symmetrically around the
-threshold. While the distributions are bounded and thus still
-sub-Gaussian, the Normal approximation should be poor in comparison to
-the previous case. We expect an improvement for the SLR algorithm
-compared to APT as it takes the Bernoulli characteristics into account.
-For example, even though the arms are symmetrically distributed around
-the threshold in terms of absolute distance, they are not symmetrically
-around the threshold in terms of their Kullback-Leibler divergence given
-the threshold is unequal 0.5. Thus we expect the SLR algorithm to not
-pull them equally. Furthermore, we expect an improvement for the
-variance-based algorithms, as the variances are now smaller than in
-experiment 1, which should at least benefit the EVT algorithm given its
-theoretical analysis.
-
-The figure below shows the performance of all algorithms. We see that
-the problem appears to be significantly more difficult in general. The
-variance based algorithms perform maybe surprisingly bad; EVT even worse
-than uniform sampling nearly until the horizon, while Augmented UCB
-takes a long time to adjust away from uniform sampling. Both algorithms
-perform worse than APT after 7000 rounds. One potential reason for this
-might be the fact that the index used by the EVT algorithm reduces to
-\(B_i^{EVT}(t) = \sqrt{T_i(t)} \cdot \sqrt{|\hat{\mu}_i(t) - \tau|}\) if
-\(\hat{\sigma}_i^2(t) = 0\), which, given Bernoulli arms with small
-means, could be the case for long runs of the algorithm. In contrast,
-the index of the APT algorithm is
-\(B_i^{APT}(t) = \sqrt{T_i(t)} \cdot |\hat{\mu}_i(t) - \tau|\).
-
-One interesting observation, that we will observe in all experiments
-with synthetic Bernoulli arms, is the superior performance of the
-Bayes-UCB algorithm adapted from Kaufmann and Kalyanakrishnan (2013)
-which was originally designed for cumulative regret problems.
-Nonetheless, the algorithm will again and again proof to be the best
-performing.
-
-While the Bayes-UCB performance is impressive, we observe that also the
-Simple Likelihood Ratio strategy improves considerably upon the
-alternative strategies. SLR reaches the average empirical error of 0.1
-within the budget, and the improvement is exponential within the entire
-budget; in contrast to APT which appears to improve linearly in the
-observations. At the end of the budget, the difference in the empirical
-error is nearly 10\% between the two strategies.
-
-In order to assess how the SLR strategy improves upon the APT algorithm,
-we can use the fact that we have run the experiment for 5000 iterations.
-We thus can look at how often each arm was pulled by a strategy at any
-given round. Across the 5000 iterations, the algorithm should pull at
-any given iteration the arm most often that it thinks is the most
-difficult to classify. In the figure below, we plot the resulting curves
-where the value at an iteration is the 10-round moving average to remove
-some unimportant variation.
-
-We see that both APT and SLR correctly single out the two arms that are
-much closer to the threshold than the remaining arms and allocate most
-of the budget to them. However, while SLR keeps the two arms constant at
-two different levels (about 1900 for arm 5 and about 2500 for arm 6),
-APT at first pulls arm 5 much more than arm 6. Then, the budget
-allocated to the two arms appears to converge to about 2000. Given that
-the two arms are symmetric around the threshold, it makes sense that APT
-would allocate the same exploration effort to both of them. And given
-that the variation of arm 5 away from the threshold is limited from
-below by zero, it is much easier for arm 6 to have an empirical mean
-larger than it's true mean, and thus to have a larger index than arm 5.
-Consequently, APT would prefer to sample arm 5. This, however, is wrong
-in terms of Kullback-Leibler divergence. Measured by the divergence, arm
-6 is closer to the threshold than arm 5, thus harder to classify, and
-consequently preferred by the SLR algorithm. Furthermore, the SLR
-algorithm appears to quickly find the correct share that it has to
-allocate to the two arms. In contrast to APT which continues to adjust
-the shares across the entire budget.
-
-Additionally, we can observe that the SLR strategy starts to drop arms
-much quicker than APT, and it drops arm 1 to 3 first, which again
-underlines the effect of the asymmetric Kullback-Leibler divergence. If
-we consider arm 3 and arm 8, we have \(d(0.01||0.05) \approx 0.025\)
-while \(d(0.09||0.05) = 0.014\). The divergence is much smaller for arm
-8. The asymmetry is even more dramatic for arm 1 and arm 10 with
-\(d(0.001||0.05) \approx 0.046\) and \(d(0.099||0.05) \approx 0.020\);
-in terms of the divergence, the distance between arm 1 and the threshold
-is twice as far as between arm 10 and the threshold. APT considers them
-to be equally distant from the threshold.
+\(\epsilon = 0\) (which generally rewards algorithms for pulling arms
+close to the threshold). We choose the means of the arms to be much
+smaller too, and arrange them symmetrically around the threshold. While
+the distributions are bounded and thus still sub-Gaussian, the Normal
+approximation should be poor in comparison to the previous case. We
+expect an improvement for the SLR algorithm compared to APT as it takes
+the Bernoulli characteristics into account. In particular, even though
+the arms are symmetrically distributed around the threshold in terms of
+absolute distance, they are not symmetrically around the threshold in
+terms of their Kullback-Leibler divergence (compare Figure 2). Thus we
+expect the SLR algorithm to not pull them symmetrically. Furthermore, we
+expect an improvement for the variance-based algorithms, as the
+variances are now smaller than in experiment 1, which should at least
+benefit the EVT algorithm given its theoretical analysis in Zhong et al.
+(2017).
 
@@
 
-\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation2_results-1} \end{center}
-
-\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-2-1} \end{center}
-
-\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-3-1} \end{center}
-
-\subsubsection{\texorpdfstring{Experiment 3: Bernoulli with
-\(\tau = 0.01\)}{Experiment 3: Bernoulli with \textbackslash{}tau = 0.01}}\label{experiment-3-bernoulli-with-tau-0.01}
+The figure below shows the performance of all algorithms. We see that
+the problem appears to be significantly more difficult in general. The
+performance of the variance based algorithms is surprisingly poor; EVT
+performs even worse than uniform sampling nearly until the horizon,
+while Augmented UCB takes a long time to adjust away from uniform
+sampling. Both algorithms perform worse than APT after 7000 samples. One
+potential reason for this might be the fact that the index used by the
+EVT algorithm reduces to
+\(B_i^{EVT}(t) = \sqrt{T_i(t)} \cdot \sqrt{|\hat{\mu}_i(t) - \tau|}\) if
+\(\hat{\sigma}_i^2(t) = 0\), which, given Bernoulli arms with small
+means, could be the case for long runs of the algorithm. This seems
+suboptimal given the index of the APT algorithm is
+\(B_i^{APT}(t) = \sqrt{T_i(t)} \cdot |\hat{\mu}_i(t) - \tau|\).
+
+One interesting observation, that we will observe in all experiments
+with synthetic Bernoulli arms, is the superior performance of the
+Bayes-UCB algorithm adapted from Kaufmann et al. (2012) which was
+originally designed for cumulative regret problems. Nonetheless, the
+algorithm will again and again proof to be the best performing. Compare
+with \autoref{sec:AppendixBUCB} for more analysis on the behavior of the
+Bayes-UCB algorithm on simulation 2. In particular, consider Figures 17
+and 18 which show for individual arms, the distribution of pulls for
+that arm across simulations. These distributions highlight that both the
+APT and SLR fail in many iterations of the simulations to pull arms
+frequently enough to estimate their correct mean. The APT algorithm
+pulls the most difficult arm (Arm 6) in more than 5\% of the simulations
+only once (during initialization). Consider arm 6 returns
+\(X_{6,1} = 1\) as its first observation. Then
+\(B_6(t+1) = 1 \cdot |1-0.05| = 0.95\). It will then not be pulled for a
+long time because the index is very large. Indeed, consider some arm
+that has been pulled 4000 times with \(\mu_i(4000) = 0.03\). Then
+\(B_i(t+1) = \sqrt{2000} \cdot |0.05-0.03| \approx 0.89\). Then even
+though we have basically no evidence for the performance of arm \(6\),
+we would continue to pull arm \(i\). Similar holds for the SLR
+algorithm. For both, the distribution of pulls for arm 6 is very flat
+across the interval of \([1,6000]\) pulls. In contrast, the distribution
+of pulls looks normally distributed for the Bayes-UCB algorithm with the
+mode between 2100 and 2300 pulls. The numerical problem that can arise
+for the APT and SLR algorithms might be weakened by the combination of a
+(weak) prior that shrinks the mean estimates, and the way in which
+quantiles are based on the posterior. Similar distributions are also
+reported for arms 1 and 10 in the appendix.
+
+While the Bayes-UCB performance is impressive, we observe that also the
+Simple Likelihood Ratio strategy improves considerably upon the
+alternative strategies. SLR reaches the average empirical error of 0.1
+within the budget, and it improves at an exponential rate within the
+entire budget; in contrast to APT which appears to improve linearly in
+the observations. At the end of the budget, the difference in the
+empirical error is nearly 10\% between the two strategies.
+
+In order to assess how the SLR strategy improves upon the APT algorithm,
+it is useful to look at how often the algorithm pulls each arm. Given
+that we run the simulation 5000 times, we can compare across simulations
+how often an algorithm pulls each arm at a given round. Across the 5000
+iterations, the algorithm should pull at any given iteration the arm
+most often that it thinks is the most difficult to classify. In the
+figure below, we plot the resulting curves where the value at an
+iteration is the 10-round moving average to remove some variation.
+
+We see that both APT and SLR correctly single out the two arms that are
+much closer to the threshold than the remaining arms, and allocate most
+of the budget to them. However, while SLR keeps the two arms constant at
+two different levels (about 1900 for arm 5 and about 2500 for arm 6),
+APT at first pulls arm 5 much more than arm 6. Then, for \emph{both}
+arms, the budget allocated to them appears to converge to about 2000.
+Given that the two arms are symmetric around the threshold, it makes
+sense that APT would allocate the same exploration effort to them. And
+given that the variation of arm 5 away from the threshold is limited
+from below by zero, it is much easier for arm 6 to have an empirical
+mean larger than its true mean, and thus to have a larger index than arm
+5. Consequently, APT would prefer to sample arm 5. This, however, is
+wrong in terms of Kullback-Leibler divergence. Measured by the
+divergence, arm 6 is closer to the threshold than arm 5, thus harder to
+classify, and consequently preferred by the SLR algorithm. Furthermore,
+the SLR algorithm appears to quickly find the correct share that it has
+to allocate to the two arms. This is in contrast to APT which continues
+to adjust the shares across the entire budget.
+
+Additionally, we can observe that the SLR strategy starts to drop arms
+much quicker than APT, and it drops arm 1 to 3 first, which again
+underlines the effect of the asymmetric Kullback-Leibler divergence. If
+we consider arm 3 and arm 8, we have \(d_3(0.01||0.05) \approx 0.025\)
+while \(d_8(0.09||0.05) = 0.014\). The divergence is much smaller for
+arm 8. The asymmetry is even more dramatic for arm 1 and arm 10 with
+\(d_1(0.001||0.05) \approx 0.046\) and
+\(d_{10}(0.099||0.05) \approx 0.020\); in terms of the divergence, the
+distance between arm 1 and the threshold is twice as far as between arm
+10 and the threshold. APT considers them to be equally distant from the
+threshold.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation2_results-1}
+
+}
+
+\caption{Performance comparison of algorithms for simulation 2.}\label{fig:simulation2_results}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-2-1}
+
+}
+
+\caption{Budget allocation across arms for APT and SLR algorithms in simulation 2.}\label{fig:unnamed-chunk-2}
+\end{figure}
+
+\subsubsection{\texorpdfstring{Simulation 3: Bernoulli with
+\(\tau = 0.01\)}{Simulation 3: Bernoulli with \textbackslash{}tau = 0.01}}\label{simulation-3-bernoulli-with-tau-0.01}
 
@@
 
-If we look at the performance after 7000 rounds, we see that the problem
-appears to be slightly more difficult compared to the previous one. We
-see that up until this point the variance-based strategies cannot
-improve upon APT. Also, SLR has not yet crossed the 10\% empirical
-error. However, we observe that in the following rounds EVT decreases at
-an exponential rate and thus crosses the error of APT and continues to
-improve upon it. At the end of the budget, the improvement of SLR
-compared to the other algorithms is again very large, and likely to
-increase. However, Bayes-UCB is again the best performing algorithm and
-is improving at a faster rate than SLR. As in the previous experiment,
-Bayes-UCB and SLR show significant improvements on this Bernoulli
-problem with very small means and threshold compared to APT in
-particular.
-
 \begin{longtable}[]{@{}rrrrrrrrrrr@{}}
-\caption{Mean of arms in simulation 2 compared to a threshold of
+\caption{Mean of arms in simulation 3 compared to a threshold of
 0.01.}\tabularnewline
@@
 
-\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation3_results-1} \end{center}
-
-\subsection{\texorpdfstring{Experiment 4: Exponential Distribution with
-\(\tau = 1\)}{Experiment 4: Exponential Distribution with \textbackslash{}tau = 1}}\label{experiment-4-exponential-distribution-with-tau-1}
-
-\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation4_results-1} \end{center}
-
-\subsection{\texorpdfstring{Experiment 5: Poisson Distribution with
-\(\tau = 1\)}{Experiment 5: Poisson Distribution with \textbackslash{}tau = 1}}\label{experiment-5-poisson-distribution-with-tau-1}
-
-\begin{longtable}[]{@{}rrrrrrrrrrrrrrrrrrrr@{}}
-\caption{Means of Poisson arms in simulation 5 compared to a threshold
-of 0.4.}\tabularnewline
-\toprule
-V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10 & V11 & V12 & V13 & V14
-& V15 & V16 & V17 & V18 & V19 & V20\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10 & V11 & V12 & V13 & V14
-& V15 & V16 & V17 & V18 & V19 & V20\tabularnewline
-\midrule
-\endhead
-0.0072 & 0.0576 & 0.0613 & 0.0925 & 0.1452 & 0.1559 & 0.1869 & 0.1958 &
-0.2235 & 0.2467 & 0.2664 & 0.3008 & 0.4295 & 0.4948 & 0.5857 & 0.6904 &
-0.7609 & 0.785 & 0.8878 & 1.7114\tabularnewline
-\bottomrule
-\end{longtable}
-
-\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation5_results-1} \end{center}
-
-\subsection{Real Data}\label{real-data}
-
-We show two experiments that were performed on real data. While most
-papers in the multi-armed bandit literature resort to synthetic data to
-assess the performance of algorithms -- just as we have done in the
-previous chapter -- we have tried to acquire real world data. This data
-is what bandit algorithms are used for in practice, and does not fulfill
-the standard independence and identical distribution assumptions as
-nicely. The real data thus can be considered a first robustness test for
-the algorithms.
+Looking at the performance after 7000 rounds, we see that the problem
+appears to be slightly more difficult compared to the previous one. We
+see that up until this point the variance-based strategies cannot
+improve upon APT. Also, SLR has not yet crossed the 10\% empirical
+error. We observe that in the following rounds EVT decreases at an
+exponential rate and thus crosses the error of APT and continues to
+improve. At the end of the budget, the improvement of SLR compared to
+the other algorithms is again large, and likely to increase. However,
+Bayes-UCB is again the best performing algorithm and is improving at a
+faster rate than SLR. As in the previous experiment, Bayes-UCB and SLR
+show significant improvements on this Bernoulli problem with very small
+means and threshold compared to APT in particular.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation3_results-1}
+
+}
+
+\caption{Performance comparison of algorithms for simulation 3.}\label{fig:simulation3_results}
+\end{figure}
+
+\subsubsection{Simulations 4 and 5: Exponential and Poisson
+Distributions}\label{simulations-4-and-5-exponential-and-poisson-distributions}
+
+In \autoref{sec:LRforUnivariateExponentialFamily}, we show that the
+likelihood ratio has a very useful form for the univariate exponential
+family of distributions, which allows us to use the SLR algorithm not
+only on Bernoulli arms, but also on Exponential or Poisson
+distributions, for example. In simulation 4, we consider Exponential
+distributions, in simulation 5, we test the algorithms on Poisson
+distributions.
+
+We run the same algorithms as before except for Bayes-UCB (even though
+it should certainly be possible to adapt it to these case based on a
+Gamma prior). In the case of the Exponential arms, we classify against
+\(\tau = 1\) and have sampled their mean parameters of the arms from an
+Exponential distribution with rate \(\theta = 1\). The Poisson arms are
+classified against a threshold of \(\tau = 0.4\), with the mean
+parameters being sampled from an Exponential distribution with mean
+\(\mu = 0.7\). In both cases, we classify 20 arms.
+
+For the Exponential arms, APT crosses the 0.1 error mark first, followed
+by the AugUCB algorithm. All algorithms perform better than uniform
+sampling. After more than half of the budget, the SLR algorithm jumps in
+performance and performs better than APT and AugUCB. Indeed, the AugUCB
+basically stops improving after half of the budget. This is a
+consequence of it eliminating arms it believes to know very well. This
+happens at an error rate of less than \(0.01\). On average, the AugUCB
+samples only for 2564 rounds of the budget of 4000 rounds across the
+5000 simulations.
+
+The early elimination (when compared to the Bernoulli experiments) might
+be caused by the fact that the AugUCB assumes the variance of the arms
+to be in \([0,1]\), which does not hold for half of the arms in the
+experiment. Similar goes for the EVT algorithm which is only able to
+catch up at the very end of the budget.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation4_results-1}
+
+}
+
+\caption{Performance comparison of algorithms for simulation 4.}\label{fig:simulation4_results}
+\end{figure}
+
+In the case of Poisson arms, the performance of the arms is more clear
+cut. As expected, SLR improves APT and the other strategies. APT
+outperforms the EVT algorithm, which occurs even though the variance of
+all arms considered in this experiment is in \([0,1]\). But similarly to
+the Bernoulli simulations, the EVT might again have a hard time dealing
+with sequences of observations that are all equal to \(0\) for a long
+time. After about 1000 observations, APT and EVT appear to improve at
+about the same rate, but APT had a much better initial exploration
+phase.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation5_results-1}
+
+}
+
+\caption{Performance comparison of algorithms for simulation 5.}\label{fig:simulation5_results}
+\end{figure}
+
+\subsection{\texorpdfstring{Real Data
+\label{sec:RealData}}{Real Data }}\label{real-data}
+
+In the following, we present the results of two experiments performed on
+a real world data set. While most new multi-armed bandit algorithms are
+assessed on synthetic data, as we have done in
+\autoref{sec:SyntheticData}, a real world data set is useful to observe
+how algorithms perform in presence of, for example, not fully i.i.d.
+samples. While of course every company tries to make their experiments
+as ideal as possible, there will always be problems. Thus our
+experiments serve as a first robustness check on the algorithms
+introduced before.
 
@@
 
-The data have been collected by the German ecommerce company
+Data have been collected by the German online shop
 \href{https://amorelie.de}{Amorelie} as part of standard website
-performance tracking. For 197 selected products, we have the number of
-users visiting each product's detail page (PDP) at a given minute. The
-data set we use here has been collected during the entire month of
-November 2016. It can be considered time series data collected at
-minutely frequency. Thus the data contain 43200 observations per
-product, and overall 8510400 observations.
-
-Given that we want to run an offline comparison of bandit algorithms, it
-is important to have at each time point an observation for each arm.
-Given that, it is easy to evaluate the perfomance of algorithms that
-make different decisions at different point in times and thus do not
-observe the same samples. By having an observation for each arm at any
-given time point, each algorithm had at least the opportunity to observe
-a certain sample. Other papers (CITE YAHOO!) have solved this problem by
-using a sample drawn uniformly during for example an A/B test. Then, if
-the next observation in the sample is not from the same arm that the
-algorithm would like to draw from, observations are discarded until the
-next observation from the selected arm.
-
-The choice of having basically multiple time series data as the sample
-leads to a simple way of running the algorithms just as often on the
-data as for simulated data. In particular, the goal is to perform 5000
-runs over the sample to confidently assess the performance. Since we
-wanted to preserve the potential time dependency of the data, a simple
-resampling of the data was not an option to create the needed 5000
-variations of the sample. Thus what we did instead was a form of time
-series cross validation. To preserve the autocorrelation, one can create
-different samples of \(X\) observations by sliding a window of size
-\(X\) over the time series. Moving the window one period (in our case
-minute) at a time, one ensures that no sample shares start and end
-observation with another sample. In particular, this means for a given
-bandit strategy and two samples that the observations that the algorithm
-collects as feedback during the two initialization phases differ from
-sample to sample and are never the same. This is because during
-initialization every strategy pulls arms \(1, ..., K\) once in this
-order.
+analytics. For 197 selected products, we observe the number of users
+visiting each product's detail page (PDP) at a given minute. The data
+set we use here has been collected during the entire month of November
+2016. It can be considered time series data collected at minutely
+frequency. Thus the data contain 43200 observations per product, and
+overall 8510400 observations.
+
+Since we want to run an offline comparison of bandit algorithms, it is
+important to have at each time point an observation for each arm. Given
+that, it is easy to evaluate the perfomance of algorithms that make
+different decisions at different point in times and thus do not observe
+the same samples. By having an observation for each arm at any given
+time point, each algorithm had at least the opportunity to observe a
+certain sample. Other papers (for example, Li et al., 2011) have solved
+this problem by using a sample drawn uniformly during, for example, an
+A/B test. Then, if the next observation in the sample is not from the
+same arm that the algorithm would like to draw from, observations are
+discarded until the next observation from the selected arm.
+
+The choice of using what is basically multiple time series data as the
+sample offers a simple way of running the algorithms just as often on
+the data as for simulated data. The goal is to perform 5000 runs over
+the sample to confidently assess the performance. Since we want to
+preserve the potential time dependency of the data, a simple resampling
+of the data is not an option to create the needed 5000 variations of the
+sample. Instead we perform time series cross validation. To preserve the
+autocorrelation, one can create different samples of \(X\) observations
+by sliding a window of size \(X\) over the time series. Moving the
+window one period (in our case one minute) at a time, one ensures that
+no sample shares start and end observation with another sample. In
+particular, this means for a given bandit strategy and two samples that
+the observations that the algorithm collects as feedback during the
+initialization phases differ from sample to sample and are never the
+same. This is because during initialization every strategy pulls arms
+\(1, ..., K\) (or \(1,...,2K\) for EVT) once in this order.
 
@@
 given minute), we binarize the data by applying a certain threshold. If
-the counts is above this threshold, the observation becomes a \(1\),
-else \(0\). Thus we have a binary time series of length 43200 for each
-of the 197 products. Given that the number of visitors that come to a
-given PDP is likely to vary by time of day and by day, and in general
-over time, we expect that the mean of the time series to not be stable
-over time. For example, less visitors will come during night than during
-evening, thus leading to a decreasein the average. On the other hand,
-more users may visit the site during a weekend, thus leading to a spike
-on Saturdays and Sundays. Because of the latter time dependency, it is
-best practice to run online A/B tests for at least a week, or an integer
-multiple of weeks, so as to take into account the weekly seasonality in
-the time series. For this reason, the experiments we present below were
-run on \(60 \cdot 24 \cdot 7 = 10080\) observations for each arm, so as
-to have a sample for one full week.
+the count is above this threshold, the new observation is \(1\), else
+\(0\). Thus we have a binary time series of length 43200 for each of the
+197 products. Given that the number of visitors that come to a given PDP
+is likely to vary by time of day and by day, and in general over time,
+we expect that the mean of the time series to not be stable over time.
+For example, less visitors will come during night than during the
+evening. This leads to a decrease in the average, and a daily
+seasonality. On the other hand, more users may visit the site during a
+weekend, thus leading to a spike on Saturdays and Sundays. Because of
+the latter time dependency, it is best practice to run online A/B tests
+for at least a week, or an integer multiple of weeks, so as to take into
+account the weekly seasonality in the time series. For this reason, the
+experiments we present below were run on \(60 \cdot 24 \cdot 7 = 10080\)
+observations for each arm, so as to have a sample for one full week.
 
 We can look at summary statistics for the sample means of the 197
-products over the month of November to get a first idea of the data we
-are dealing with. We see that most products have a low mean, which is
-very common also for actual conversion rate data that would be tested
-with A/B tests or multi-armed bandits. Yet the sample of products
-contains a few outliers with very large view rates, with a maximum rate
-of 78\%. If we used a threshold \(\gamma\) to binarize the count data,
-then this means that on average every fourth minute the count of
-visitors was below \(\gamma\) for this product. On the other hand, we
-conclude that using thresholding bandit strategies to test the products
-against a threshold of for example \(\tau = \frac{2}{60} = 0.333\) or
-\(\tau = \frac{5}{60} = 0.083\) is likely to create more complex
-problems than a threshold of, say, \(\tau = \frac{15}{60} = 0.25\)
-would.
+products over the month of November to get a first impression of the
+data we are dealing with. We see that most products have a small mean,
+which is very common also for actual conversion rate or click-through
+rate data that can be tested with A/B tests or multi-armed bandits. Yet
+the sample of products contains a few outliers with very large view
+rates, with a maximum rate of 78\%. If we used a threshold \(\gamma\) to
+binarize the count data, then this means that on average every fourth
+minute the count of visitors was below \(\gamma\) for this product. On
+the other hand, we conclude that using thresholding bandit strategies to
+test the products against a threshold of for example
+\(\tau = \frac{2}{60} = 0.333\) or \(\tau = \frac{5}{60} = 0.083\) is
+likely to create more complex problems than a threshold of, say,
+\(\tau = \frac{15}{60} = 0.25\) would.
 
@@
 
-\subsubsection{\texorpdfstring{Experiment 1:
-\(\tau = \frac{2}{60}\)}{Experiment 1: \textbackslash{}tau = \textbackslash{}frac\{2\}\{60\}}}\label{experiment-1-tau-frac260}
-
-In this first experiment, we pick ten arms randomly from the set of 197
-arms. The experiment is run on these 10 arms with a budget of
-\(T=10080\) samples during each of the \(5000\) iterations for which we
-repeat the experiment. Given the time series cross-validation idea
-described above, this means that in total, \(15080\) observations of the
-available \(43200\) available observations per arm are used in training.
-In the thresholding bandit problem, we classify arms as below or above a
-threshold. Thus we can evaluate the strategies also based on whether
-their classifications are correct in a holdout sample. As this holdout
-sample, we can use the 10080 observations in our data set that follow
-the first 15080 observations used in training. In the table below, we
-present the count rates of the ten products for both training and test
-samples.
+\subsubsection{Experiment 1}\label{experiment-1}
+
+In the first experiment, we pick ten arms randomly from the set of 197
+arms. The experiment is run with a budget of \(T=10080\) samples during
+each of the \(5000\) iterations for which we repeat the experiment.
+Given the time series cross-validation idea described above, this means
+that in total, \(15080\) observations of the \(43200\) available
+observations per arm are used in training. In the thresholding bandit
+problem, we classify arms as below or above a threshold. Thus we can
+evaluate the strategies also based on whether their classifications are
+correct in a holdout sample. As this holdout sample, we can use the
+10080 observations in our data set that follow the first 15080
+observations used in training. In the table below, we present the count
+rates of the ten products for both training and test samples.
 
@@
 0.150 & 0.130\tabularnewline
-TrainingMinusTau & -0.033 & -0.021 & -0.006 & 0.019 & 0.026 & 0.038 &
-0.038 & 0.068 & 0.123 & 0.125\tabularnewline
 \bottomrule
@@
 
-We see that while the rates do vary across samples, they are relatively
-stable which is likely due to the fact that the samples come from an
-entire week's worth of observations. In particular, since we test
-against a threshold of \(\tau = \frac{2}{60} = 0.333\) in this
-experiment, the classifications of arms do not differ across training
-and test data. A correct classification after training will be correct
-in the test set. For the rest of the analysis, we thus evaluate the
-performance using the training rates.
+We see that while the rates do vary across training and test samples,
+they are relatively stable which is likely due to the fact that the
+samples come from an entire week's worth of observations. In particular,
+since we test against a threshold of \(\tau = \frac{2}{60} = 0.333\) in
+this experiment, the classifications of arms do not differ across
+training and test data. A correct classification after training will be
+correct in the test set. For the rest of the analysis, we thus evaluate
+the performance using the training rates.
 
@@
 
-\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-5-1} \end{center}
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-3-1}
+
+}
+
+\caption{Rolling average for the arms used in experiment 1.}\label{fig:unnamed-chunk-3}
+\end{figure}
 
@@
 the variance-based algorithms, and assumed to be Bernoulli for the SLR
-algorithm. Additionally, we use the B-UCB algorithm as it performed
-often best on the synthetic data.
+algorithm. Additionally, we use the Bayes-UCB algorithm as it performed
+best on the synthetic data.
 
@@
 we use the parameters as in Mukherjee et al. (2017), that is,
-\(\rho = 1/3\). For B-UCB we set the prior to \(\alpha = \tau\) and
-\(\beta = 1-\tau\). All other algorithms are parameter free.
-
-The corresponding results are shown in the next figure.
-
-\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-6-1} \end{center}
+\(\rho = 1/3\). For B-UCB we set the prior to \(\alpha_0 = \tau\) and
+\(\beta_0 = 1-\tau\), and pick \(c=1\). All other algorithms are
+parameter free.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-4-1}
+
+}
+
+\caption{Performance comparison of algorithms for experiment 1.}\label{fig:unnamed-chunk-4}
+\end{figure}
 
 Compared to the previous simulations with synthetic data, the results
-are dramatic. First of all, we see that all strategies perform not well.
-All of them end above the 10\% error mark after 1 week of data. Second,
-the uniform sampling strategy fares best when evaluated against the
-sample mean of all observations used during training. This of course is
-the opposite of what we would like to see, and the opposite of what we
-saw on the synthetic data, where we were able to improve upon the naive
-strategy. Third, again in contrast to the results on synthetic data, we
-observe non-monotonicity in the error curves. Given that the highs and
-lows run very much parallel for the different models, it stands to
-reason that this effect is caused by the variation in means of the arms
-over time. Indeed, roughly comparing the error curves to the moving
-averages in the previous figure, the increase in errors after round
-\(5000\) and the decreasing error after round \(7500\) seems to line up
-more or less with the fluctuations observed in the data. Given that we
+are dramatically poor. First of all, we see that all strategies perform
+poorly. All of them end above the 10\% error rate mark after 1 week of
+data. Second, the uniform sampling strategy fares best when evaluated
+against the sample mean of all observations used during training. This
+of course is the opposite of what we would like to see, and the opposite
+of what we saw on the synthetic data, where we were able to improve upon
+the naive strategy. Third, again in contrast to the results on synthetic
+data, we observe non-monotonicity in the error curves. Given that the
+highs and lows run very much parallel for the different models, it
+stands to reason that this effect is caused by the variation in means of
+the arms over time. Indeed, roughly comparing the error curves to the
+moving averages in the previous figure, the increase in errors after
+round \(5000\) and the decreasing error after round \(7500\) seems to
+line up with the fluctuations observed in the data. Given that we
 evaluate the models against a sample mean of all observations, it is not
@@
 regret multi-armed bandit setting. Here, however, it leads to wrong
-estimates of the sample mean.
+estimates of the overall sample mean.
 
@@
 strategies perform worse than APT and SLR. Very dramatic is the behavior
-of the Augmented-UCB algorithm, which first seems to perform well; that,
+of the Augmented-UCB algorithm, which first seems to perform well; this,
 however, is a result of it mostly pulling arms uniformly, until it
@@
 rounds. The result is a dramatic increase in error which leads to the
-worst performs at the end of the budget. The difference between APT,
-SLR, and EVT is not very large, and their performance fluctuates in
-sync. None of them is really able to converge due to the changes in the
-underlying means. Advantageous only seems to be the fact that their
-behavior is less erratic than that of the Augmented-UCB strategy given
-that they do not discard arms.
-
-\subsubsection{\texorpdfstring{Experiment 2:
-\(\tau = \frac{5}{60}\)}{Experiment 2: \textbackslash{}tau = \textbackslash{}frac\{5\}\{60\}}}\label{experiment-2-tau-frac560}
+worst performance at the budget horizon. The difference between APT,
+SLR, and EVT is small, and their performance fluctuates in sync. None of
+them is really able to converge due to the changes in the underlying
+means. Advantageous only seems to be the fact that their behavior is
+less erratic than that of the AugUCB strategy given that they do not
+discard arms.
+
+\subsubsection{Experiment 2}\label{experiment-2}
 
@@
 general slightly easier, and again pick 10 arms at random from the data
-set of 197 arms. We again use a rolling window of \(10080\) observations
+set of 197 arms. We again use a sliding window of \(10080\) observations
 to create \(5000\) iterations and look at the training and test sample
-means as in Experiment 1.
+means as in the previous experiment.
 
@@
 \endhead
-Training & 0.000 & 0.000 & 0.012 & 0.044 & 0.049 & 0.053 & 0.055 & 0.095
-& 0.123 & 0.199\tabularnewline
-Test & 0.013 & 0.000 & 0.011 & 0.040 & 0.049 & 0.063 & 0.060 & 0.114 &
-0.137 & 0.202\tabularnewline
-TrainingMinusTau & -0.083 & -0.083 & -0.071 & -0.039 & -0.035 & -0.030 &
--0.028 & 0.011 & 0.039 & 0.116\tabularnewline
+Training & 0.000 & 0 & 0.012 & 0.044 & 0.049 & 0.053 & 0.055 & 0.095 &
+0.123 & 0.199\tabularnewline
+Test & 0.013 & 0 & 0.011 & 0.040 & 0.049 & 0.063 & 0.060 & 0.114 & 0.137
+& 0.202\tabularnewline
 \bottomrule
@@
 much larger and systematic than those observed for synthetic data with
-the same sample means. While the moving average of product \(V159\) in
-the synthetic data has a valley after index 5000, this can be explained
-by the natural variance (which increases as the mean is closer to
-\(0.5\)).
+the same sample means.
 
@@
 strategy performs the best. The adaptive sampling strategies perform
-bad, do not converge, and end above the 10\% error mark. This time,
-Augmented-UCB is not (yet) the worst performing strategy, but equally
-erratic after it actually adapts its sampling. This time around, it even
-has two spikes in its adaptive phase. Again, APT, SLR, and EVT perform
-in sync and more or less equally bad, with EVT slightly better than APT
-and SLR this time around. Interestingly, Bayes-UCB performs clearly
-worst of all strategies. Its performance changes at the same time as
+bad, do not converge, and end above the 10\% error rate mark. This time,
+AugUCB is not (yet) the worst performing strategy, but equally erratic
+after it eventually adapts its sampling. This time around, it even has
+two spikes in its adaptive phase. Again, APT, SLR, and EVT perform in
+sync and more or less equally bad, with EVT slightly better than APT and
+SLR this time around. Interestingly, Bayes-UCB performs clearly worst of
+all strategies. Its performance changes at the same time as
 Augmented-UCB starts to adapt its sampling strategy, near round 7000.
@@
 mirrors its performance observed in the previous simulations with
-synthetic data. Also all other strategies perform clearly better now,
-and their error rates are strictly decreasing. Interestingly, the
-uniform sampling scheme is now much worse than in the experiment on real
-data; it does no longer have the advantage of sampling the different
-mean phases at a representative rate. Instead, it is no in its original
-position of serving as upper bound on the error rate. Excluding
-Bayes-UCB, we see that the SLR algorithm performs better the best,
-followed by the variance-based algorithms. APT comes in at the same
-error rate as uniform sampling. While the difference between SLR and EVT
-are less than 2\% (1.2\% vs 3\%), the difference to uniform sampling
-(10\%) is relevant. The performance of 10\% error rate is achieved by
-SLR about 1000 observations earlier than by EVT.
-
-\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-7-1} \end{center}
-
-\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-7-2} \end{center}
-
-\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-7-3} \end{center}
-
-\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-7-4} \end{center}
-
-\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-8-1} \end{center}
-
-We can try to understand why some strategies fail, while showing
-significant improvements on synthetic data. Given that we run 5000
-iterations of the experiment, we can assess in how many of these
-iterations a given arm was pulled at a given round. Comparing these
-sampling shares across algorithms may give us hints to as to why
-algorithms perform a certain way. Given the setup with 5000 iterations
-and 10 arms in the current experiment, we would expect for the uniform
-strategy on average 500 pulls for each arm in every round. Given this
-benchmark, we can now look at how the other strategies split their
-budget. In the figures below, we have plotted not the absolute pulls per
-round, but have applied a 10-round moving average to remove some of the
-fluctuation in the plotted lines.
+synthetic data. Also all other adaptive strategies perform clearly
+better now, and their error rates are strictly decreasing.
+Interestingly, the uniform sampling scheme is now much worse than in the
+experiment on real data; it does no longer have the advantage of
+sampling the different mean phases at a representative rate. Excluding
+Bayes-UCB, we see that the SLR algorithm performs the best, followed by
+the variance-based algorithms. APT comes in at the same error rate as
+uniform sampling. While the difference between SLR and EVT are less than
+2\% (1.2\% vs 3\%), the difference to uniform sampling (10\%) is
+relevant. The performance of 10\% error rate is achieved by SLR about
+1000 observations earlier than by EVT.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-5-1}
+
+}
+
+\caption{Rolling average of arms used in experiment 2.}\label{fig:unnamed-chunk-5}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-9-1}
+
+}
+
+\caption{Performance results of algorithms in experiment 2.}\label{fig:unnamed-chunk-9}
+\end{figure}
+
+Again using a plot of the pulls at each round across the 5000
+simulations in Figure 17, we can try to understand why some strategies
+perform well on synthetic data, but poorly on the time series data.
 
 We observe that the patterns across algorithms are quite similar, while
-the patterns are very different across data sets. Given that arm
-\(V149\) is clearly the most difficult arm to classify due to its
-closeness to the threshold \(\tau\), all algorithms focus a major share
-of their budget on this arm. The speed at which they start to do so,
-however, differs. Perhaps surprisingly, the best performing Bayes-UCB
-algorithm increases its focus on arm \(V149\) the slowest, while in many
-iterations spending budget on exploring other arms. Surprisingly because
-Bayes-UCB is designed for the cumulative regret problem. Thus one would
+the patterns are very different across data sets. On the synthetic data,
+given that arm \(V149\) is clearly the most difficult arm to classify
+due to its closeness to the threshold \(\tau\), all algorithms focus a
+major share of their budget on this arm. The speed at which they start
+to do so, however, differs. Perhaps surprisingly, the best performing
+Bayes-UCB algorithm increases its focus on arm \(V149\) the slowest,
+while in many iterations spending budget on exploring other arms. This
+is surprising as the Bayes-UCB algorithm's exploration factor was
+originally conceived for the cumulative regret problem. Thus one would
 expect it to explore \emph{less} than other algorithms. But its
@@
 
-One striking feature of the EVT algorithm seems to be the overall
-iterations and budget allocated to arm \(V32\), which, as we have seen,
-has a sample mean of zero. Something that might be hidden by this
-aggregated view of all 5000 iterations are a share of iterations in
-which the EVT completely fails by exploring wrong arms for long periods.
-This effect might even be more drastic for the APT algorithm. Even
-though it seems as if its behavior is very similar to SLR and EVT, the
-overall performance is not better than the performance of uniform
-sampling. Taking this reasoning into account, one can hypothesize that
-the Bayes-UCB algorithm finds the most difficult arm uniformly across
-most iterations as the rounds increase, while other algorithms either
-find the most difficult arm right away or never and thus have many
-iterations that end with a misclassification.
+Something that might be hidden by this aggregated view of all 5000
+iterations are a share of iterations in which the EVT completely fails
+by exploring wrong arms for long periods. This effect might even be more
+drastic for the APT algorithm. Even though it seems as if its behavior
+is very similar to SLR and EVT, the overall performance is not better
+than the performance of uniform sampling. Taking this reasoning into
+account, one can hypothesize that the Bayes-UCB algorithm finds the most
+difficult arm uniformly across most iterations as the rounds increase,
+while other algorithms either find the most difficult arm right away or
+never and thus have many iterations that end with a misclassification.
 
@@
 
-\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-9-1} \end{center}
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-10-1}
+
+}
+
+\caption{Budget allocation of algorithms across arms on real and synthetic data in experiment 2.}\label{fig:unnamed-chunk-10}
+\end{figure}
+
+\subsubsection{Experiments Conclusion}\label{experiments-conclusion}
+
+In the two previous experiments, we observe that the real time series
+data poses a major hurdle for the adaptive sampling algorithms. It seems
+that the poor performance can be mostly explained by the seasonality and
+sudden changes in the samples over time. The observations clearly are
+not i.i.d. sampled. However, the effect might be overly stark due to the
+fact that we use minutely time series data, which leads to observations
+even when in minutes when there are few or no users (during night). In
+contrast, the daily seasonality might be less represented in an actual
+online experiment observations are only drawn when there is an actual
+visitor on the site (and a proper conversion rate would fluctuate less
+than the count of visitors on a given product page).
+
+Furthermore, some of the problems in dealing with the fluctuating
+distributions might be specific to the thresholding bandit problem as
+opposed to the cumulative regret or best-arm identification problems. In
+the experiments above, we observe that the order of the arms is mostly
+unaffected by the seasonalities and fluctuations, which would mean that
+the best arm could still be identified. In contrast, given that all arms
+are individually classified against the \emph{fixed} threshold, a weekly
+seasonality can declare a correct classification on the first half of
+the sample null and void on the second half of the sample.
 
@@
 The author thanks Alexandra Carpentier, Andrea Locatelli, and Urun Dogan
-for many hours of valuable feedback and ideas. \textless{}3
+for many hours of valuable feedback and ideas.
+
+\section{References}\label{references}
+
+\section{Appendix}\label{appendix}
+
+\subsection{\texorpdfstring{Proof of Thresholding Bandit Lower Bound
+\label{sec:AppendixAPTLB}}{Proof of Thresholding Bandit Lower Bound }}\label{proof-of-thresholding-bandit-lower-bound}
+
+We now give a proof for the lower bound for the thresholding bandit
+problem stated in \autoref{theorem:Locatelli2016Theorem1}.
+
+\emph{Proof of Theorem \ref{theorem:Locatelli2016Theorem1}}: Locatelli
+et al. (2016) derive a lower bound for the thresholding bandit problem.
+We restate the proof here. The idea is as follows. The problem
+formulation considered in the paper describes bandit problems for
+\(R\)-sub-Gaussian distributions. To show a lower bound, we show that
+every algorithm is expected to make a certain error even if we consider
+a very restricted scenario. Even then, the best algorithm will have a
+maximum error probability with which it cannot distinguish between the
+actual setting and slightly changed settings (under which the answer for
+the true setting leads to a misclassification).
+
+Consider the thresholding bandit setting as in \autoref{sec:Setup}. More
+specifically, consider a problem in which all arms follow Normal
+distributions \(\nu_i\) with mean \(\mu_i\) and variance
+\(\sigma^2 = 1\). ``in which w''e set \(\tau = 0\) and \(\epsilon = 0\)
+w.l.o.g. Consequently, for each arm \(i\) the distance from the
+threshold is given by \(\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i\).
+Thus, we have for every arm the distribution
+\(\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)\). Furthermore,
+define for each arm \(i \in \{1, \dots, K\}\) the alternative
+distribution \(\nu_i' = \mathcal{N}(-\Delta_i,1)\). It is easy to see
+that this is equivalent to a ``flip around the threshold''. Arms that
+originally have a mean larger than the threshold have a mean smaller
+than the threshold after the flip.
+
+The intuition now is that every arm \(i \in \{1,\dots,K\}\) generates a
+sample for every time point \(t\in \{1, \dots, T\}\) from its
+distribution \(\nu_i\) before the algorithm starts to choose arms. Thus,
+we have a \(T \times K\) table of realized observations from the product
+distribution given by
+\(\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K\).
+This is a product distribution where the \(K\) different means are all
+above the threshold. We would hope that an algorithm classifies the
+means accordingly. However, we will show in what follows that any
+algorithm makes a certain error by not being able to distinguish
+\(\mathcal{B}^0\) from at least one of \(K\) alternative product
+distributions \(\mathcal{B}^i, i \in \{1, \dots, K\}\), of which each
+differs only slightly in one arm from the original distribution, and has
+the same overall complexity (as defined by
+\(H = \sum_{i=1}^K (\Delta_i)^{-2}\)). We require \(K\) different
+distributions so that an algorithm sampling arm \(i\) very often for
+some reason will not have a smaller lower bound by chance.
+
+For each of the \(K\) arms, we introduce an alternative model of the
+following kind. Before the start of the algorithm, we introduce a slight
+variation in the setup. The idea is similar to how one can switch arms
+in the pure exploration setup for multi-armed bandits (compare Audibert
+et al., 2010; Garivier \& Kaufmann, 2016) to ``confuse'' any algorithm
+without introducing additional complexity to the specified problem.
+However, since we do not compare arms directly with each other in the
+thresholding bandit problem (switching arms would still keep all means
+above the threshold), we instead need to flip an arm \(i\) with respect
+to the threshold in order to get the alternative model
+\(\mathcal{B}_i\). Since the threshold is \(\tau = 0\), we have for the
+flipped arm the new distribution \(\nu_i'\) as defined above. Indeed,
+define the new product distribution
+\(B^i = \nu_1^i \otimes \dots \otimes \nu_K^i\) where for
+\(k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}\).
+This arm flip corresponds to multiplying all \(X_{i,t}\) of arm \(i\) by
+\(-1\).
+
+As in Locatelli et al. (2016), let for \(i \leq K\),
+\(\mathbb{P}_{\mathcal{B}^i}\) be the probability distribution
+describing all samples that a bandit strategy can potentially collect up
+to horizon \(T\), i.e.~according to the samples
+\((X_{k,s})_{k\leq K, s \leq T} \sim (\mathcal{B}^i)^{\otimes T}\).
+\((T_k)_{k\leq K}\) denotes the number of samples collected on arm \(k\)
+until time \(T\).
+
+At this point, we have defined a finite set of problems of Gaussian
+distributions with fixed variance 1 for a given set of set of gaps
+between the means of the distributions and the threshold,
+\((\Delta_k)_k\). We now proof a lower bound on the worst case regret of
+any algorithm; that is, the maximum error probability that even the best
+algorithm makes on this problem.
+
+\subsubsection{Statistical Decision}\label{statistical-decision}
+
+The expected loss in our thresholding bandit setting,
+\(\mathbb{E}[\mathcal{L}(T)]\), corresponds directly to the probability
+of making a wrong classification of any of the \(K\) means. In general,
+given a binary decision function \(g\), define events
+\(\Omega = \{g = 0\}\) and \(\Omega^C = \{g = 1\}\). Assume that the
+decision \(g\) distinguishes between two states of the world, \(H_0\)
+and \(H_1\). Then an overall error probability can be seperated into
+\(P_{H_0}(g=1) + P_{H_1}(g = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)\).
+
+In our case, \(H_0\) may correspond to the state in which we have
+\(\mathcal{B}^0\), and \(H_1\) corresponds to the case where any arm has
+been flipped, \(\mathcal{B}^i\). Furthermore, we consider the events in
+which the algorithm classifies arm \(i\) as being above the threshold:
+\(\mathcal{A}_i = \{i \in \hat{S}_\tau\}\). The event on which all arms
+are being classified as above the threshold is consequently given by
+\(\mathcal{A} = \bigcap_{i=1}^K \mathcal{A}_i\). We could thus separate
+the error probability \(\mathbb{E}[\mathcal{L}(T)]\) into
+\(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\) and
+\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C)\). However, Theorem 1 does
+not bound the overall regret, but the maximum error probability on the
+\(K+1\) different models. We can write this now as
+
+\begin{align}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big) \\
+& = \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
+\end{align}
+
+\subsubsection{Empirical Kullback-Leibler
+Divergence}\label{empirical-kullback-leibler-divergence}
+
+In order to give a bound on the previous equation, we start by
+considering \(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\). This
+probability can be written as the expected change in the likelihood of
+observed data when moving from distribution \(P_{\mathcal{B}_0}\) to
+\(P_{\mathcal{B}_i}\), times the probability under the original state.
+In other words, the probability of event \(\mathcal{A}_i\) under state
+\(\mathcal{B}^i\) is given as the probability of \(\mathcal{A}_i\) under
+the (original) state \(\mathcal{B}^0\) multiplied by a factor. This
+factor describes whether the new distribution increases or decreases the
+probability of the event, and is given by the change in the data
+likelihoods due to moving from \(\mathcal{B}^0\) to \(\mathcal{B}^i\),
+expressed as the expected likelihood ratio under \(\mathcal{B}^0\). By
+definition, the latter is equal to the empirical Kullback-Leibler
+divergence of the two distributions.
+
+We will define the change of distribution in terms of the empirical
+log-likelihood for our case. Then, we will show how to replace the
+log-likelihood by the empirical Kullback-Leibler divergence. Let us
+first introduce the empirical Kullback-Leibler divergence.
+
+Let every \(\nu_i, \nu_i'\) be dominated by the Lebesgue measure
+\(\lambda\). Then their density functions are given by
+\(f_i = \frac{\der \nu_i}{\der \lambda}\) and
+\(f_i' = \frac{\der \nu_i'}{\der \lambda}\) respectively. For
+\(T \geq t \geq 0\), define the empirical Kullback-Leibler divergence
+for an i.i.d. sample \(X_{k,1}, \dots,X_{k,t}\) as
+
+\begin{align*}
+\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log(\frac{\der \nu_k'}{\der \nu_k}(X_{k,s})) \\
+& = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
+& = \frac{1}{t} \log \big( \prod_{s=1}^{t} \frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
+& \stackrel{\text{iid}}{=} \frac{1}{t} \log \big( \frac{f_k'(X_{k,1}, \dots,X_{k,t})}{f_k(X_{k,1}, \dots,X_{k,t})} \big) \\
+& = \frac{1}{t} \log \big( \text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k) \big),
+\end{align*}
+
+where \(\text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k)\) is the
+likelihood ratio for the sample.
+
+Since we consider Gaussian distributions with variance \(\sigma^2 = 1\),
+we have density functions
+\(f_i(x) \propto \exp \big(-\frac{1}{2} (x-\Delta_i)^2\big)\) and
+\(f_i'(x) \propto \exp \big(-\frac{1}{2} (x+\Delta_i)^2\big)\). Plugging
+this into the above definition of the empirical Kullback-Leibler
+divergence, we easily see
+
+\begin{align*}
+\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log \Big(\frac{\exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2\big)}{\exp \big(-\frac{1}{2} (X_{k,s}-\Delta_k)^2\big)} \Big) \\
+& = \frac{1}{t} \sum_{s=1}^{t} \log \Big( \exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2 + \frac{1}{2} (X_{k,s}-\Delta_k)^2 \big) \Big) \\
+& = - \frac{1}{t} \sum_{s=1}^{t} 2 X_{k,s} \Delta_k
+\end{align*}
+
+\subsubsection{Change of Distribution}\label{change-of-distribution}
+
+We are now ready to state the change of distribution. As alluded to
+above, we consider how the probability changes for the event
+\(\mathcal{A}_i\) when we move from \(\mathcal{B}^0\) to
+\(\mathcal{B}^i\). When flipping arm \(i\), we only change the samples
+of this arm, that is, the first \(T_i\) observations that the algorithm
+draws from arm \(i\). The change of distribution is then defined as:
+
+\begin{align*}
+\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \text{LR}((X_{i,1}, \dots,X_{i,T_i}), \nu_i', \nu_i) ] \\
+& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ]
+\end{align*}
+
+Obviously, \(\hat{\KL}_{i,T_i}\) depends on the realized samples
+\(X_{i,1}, \dots,X_{i,T_i}\). Consequently, we need to find a bound on
+\(\hat{\KL}_{i,T_i}\) itself to incorporate the uncertainty involved in
+this metric.
+
+\subsubsection{Concentration of the Empirical Kullback-Leibler
+Divergence}\label{concentration-of-the-empirical-kullback-leibler-divergence}
+
+For our problem, the Kullback-Leibler divergence of \(\nu_k'\) from
+\(\nu_k\) is given by \(\KL_k := \KL(\nu_k', \nu_k) = 2\Delta_k^2\), and
+consequently
+
+\begin{equation*}
+|\hat{\KL}_{k,t} - \KL_{k,t}| = |-\frac{2}{t} \Delta_k \sum_{s=1}^{t}(X_{k,s} - \Delta_k)|
+\end{equation*}
+
+itself is a normally distributed random variable with mean zero and a
+variance decreasing in \(t\). Thus, one can show as in Locatelli et al.
+(2016) that \(\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4\) for the event
+
+\begin{equation}
+\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}}\}. \label{LocatelliTheorem1EventXi}
+\end{equation}
+
+Thus, in order to bound the empirical Kullback-Leibler divergence in our
+change of measure, we can consider the intersection of \(\mathcal{A}_i\)
+and \(\xi\) as follows and plug in the bound on event \(\xi\):
+
+\begin{align*}
+\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
+& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
+& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
+\end{align*}
+
+Two things are left to do: With \(T_i\), we still have one random
+variable left which we cannot leave in our bound. Second, we are
+actually not interested in \(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)
+but in
+\(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\).
+
+\subsubsection{\texorpdfstring{Bounding \(T_i\) for
+\(\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)}{Bounding T\_i for \textbackslash{}max\_\{i \textbackslash{}in \textbackslash{}\{1,\textbackslash{}dots,K\textbackslash{}\}\}\textbackslash{}mathbb\{P\}\_\{\textbackslash{}mathcal\{B\}\^{}i\}(\textbackslash{}mathcal\{A\}\_i)}}\label{bounding-t_i-for-max_i-in-1dotskmathbbp_mathcalbimathcala_i}
+
+We are actually interested in bounding
+\(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\).
+In general it holds that
+\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K}\sum_{i=1}^K X_i\).
+Thus we can write:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
+& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
+& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
+\end{align*}
+
+where the second line is again the intersection of \(\mathcal{A}_i\) and
+\(\xi\) as before, such that we can apply the change of distribution in
+the third line.
+
+What is left to show is a bound on \(T_i\). Given that we want to show
+that even the best algorithm makes an error on at least one of the
+problems (one of the arms), it makes sense to show that \(T_i\) is upper
+bounded. This implies that no arm can be infinitely sampled; we cannot
+reach full confidence in any arm, and a residual error probability
+should remain.
+
+First, let \(a = \Delta_i \sqrt{T_i}\) and
+\(b = 4\sqrt{\log((4\log(T)+1)K)}\). Then use \(ab \leq a^2 + b^2\) to
+write \(ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)\). And so:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) ]
+\end{align*}
+
+Furthermore, we know that the sum of the individual arm pulls has to be
+equal to the overall number of pulls (equal to the budget in the fixed
+budget sense), \(\sum_i T_i = T\), and furthermore we know that
+\(T_i>0\). The latter holds since any reasonable algorithm has to check
+each arm at least once in our setup. Thus it is easy to show that
+\(\exists i: T_i \leq \frac{T}{H \Delta_i^2} = \frac{T}{(\sum_{i=1}^{K} \Delta_i^{-2}) \Delta_i^2}\).
+To see this, assume the opposite:
+\(\forall i: T_i > T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2}\). This
+implies however
+\(\sum_{i=1}^K T_i > \sum_{i=1}^K T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2} = T \cdot 1 = T\)
+which is a contradiction.
+
+So we can write \((\Delta_i \sqrt{T_i})^2 \leq \frac{T}{H}\). We use
+\(\mathcal{A} = \cap_{i=1}^K \mathcal{A}_i\) to write:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big] \\
+& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big]
+\end{align*}
+
+We write
+\(\frac{1}{K} \sum_{i=1}^K \exp(-3T_i \Delta_i^2) \geq \frac{1}{K} \sum_{i=1}^K \exp(-3 T/H) = \exp(-3 T/H)\).
+Thus:
+
+\begin{align*}
+\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \Big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i) \exp \big(-16 \log(4(\log(T)+1)K)\big) \Big] \\
+& \geq \mathbb{E}_{\mathcal{B}^0} \Big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp \big(- 3 \frac{T}{H}\big) \exp \big(-16 \log(4(\log(T)+1)K)\big) \Big] \\
+& = \mathbb{E}_{\mathcal{B}^0} \Big[\mathbbm{1}_{\mathcal{A} \cap \xi} \exp \big(- 3 \frac{T}{H}\big) \exp \big(-16 \log(4(\log(T)+1)K)\big) \Big] \\
+& = \mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp \Big(- 3 \frac{T}{H} -16 \log \big(4(\log(T)+1)K\big)\Big)
+\end{align*}
+
+\subsubsection{Bringing everything
+together}\label{bringing-everything-together}
+
+Consider again the risk which we need to bound from equation
+\eqref{LocatelliTheorem1ExpRegret}. We bound the maximum expected loss
+over all \(\mathcal{B}_i\). By using again the fact that in general
+\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K} \sum_{i = 1}^K X_i\),
+we plug into our previous calculations:
+
+\begin{align}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
+& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp \Big(- 3 \frac{T}{H} -16 \log \big(4(\log(T)+1)K\big)\Big) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \label{LocatelliTheorem1DefinitionOfRisk}
+\end{align}
+
+From \eqref{LocatelliTheorem1EventXi} we know that for any
+\(i \in \{0, \dots, K\}\), \(\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4\).
+Following the argument in Locatelli et al. (2016), we now consider two
+cases: \(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2\) and
+\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2\). In the former
+case, we can plug in the two probabilities into
+\eqref{LocatelliTheorem1DefinitionOfRisk}. If
+\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2\) and
+\(\mathbb{P}_{\mathcal{B}^0}(\xi) \geq 3/4\), then
+\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \geq 1/4\). Thus:
+
+\begin{align*}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
+& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \\
+& \geq \frac{1}{8} \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
+\end{align*}
+
+where we drop the second summand of the second line so that the
+inequality holds.
+
+On the other hand, when
+\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2\), then we know that
+\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \leq 1/2\) for any
+\(\mathbb{P}_{\mathcal{B}^0}(\xi)\). At the same time
+\(1-\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \geq 1/2\).
+Consequently,
+\(1/4 \leq \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \leq 1/2\),
+while
+\(\frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) \geq 0\).
+And so the stronger lower bound in that case is, as noticed by Locatelli
+et al. (2016), given simply by
+
+\begin{align*}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
+& \geq 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \\
+& \geq \frac{1}{2}
+\end{align*}
+
+\subsection{\texorpdfstring{Bayes-UCB Algorithm for the Thresholding
+Bandit Problem
+\label{sec:AppendixBUCB}}{Bayes-UCB Algorithm for the Thresholding Bandit Problem }}\label{bayes-ucb-algorithm-for-the-thresholding-bandit-problem}
+
+We show how the Bayes-UCB algorithm (Algorithm 1, Kaufmann et al., 2012)
+is adopted to the thresholding bandit problem to be used in the
+experiments in chapter \autoref{chap:Experiments}.
+
+We adopt their Algorithm 1 for Bernoulli distributions as follows:
+
+\IncMargin{1em}
+
+\begin{algorithm}
+\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
+\Input{\emph{$\tau$, $\epsilon$, $T$, $\Pi^0$ (initial prior on $\mu$), $c$ (parameters of the quantile)}}
+\Output{$\hat{S}_\tau = \{i \in \mathbb{A},  \hat{\mu}_i(T) \geq \tau\}$}
+\BlankLine
+\emph{Pull each arm once}\;
+\For{$t = K+1$ \KwTo $T$}{
+\For{$i = 1$ \KwTo $K$}{
+  \emph{Compute $q_i(t) = Q\Big(1-\frac{1}{t(\log T)^c}, \lambda_i^{t-1}\Big)$}\;
+  \emph{Compute $B_i(t) = $}\;
+  \If{$\hat{\sigma}^2_{i}(t) = 0$}{\emph{Set $\hat{\sigma}^2_{i}(t) = 1/T$}}
+}
+  \emph{Pull arm $I_t = \arg \min_{i\leq K} B_i^{SLR_{2D}}(t)$ as in \autoref{eqn:SLR2DIndex}}\;
+  \emph{Observe reward $X \sim \nu_{I_t}$}\;
+}
+\caption{2D-SLR algorithm for Normal distributions with unknown mean and unknown variance}\label{algo_slr_2d}
+\end{algorithm}
+
+\DecMargin{1em}
+
+\subsection{Empirical Analysis of the Bayes-UCB Algorithm in Simulation
+2}\label{empirical-analysis-of-the-bayes-ucb-algorithm-in-simulation-2}
+
+In order to assess the excellent performance of the Bayes-UCB algorithm,
+which comes at a surprise given that is is designed for the cumulative
+regret setting and thus should tend to explore the arms to less, we also
+plot the budget allocation of three different Bayes-UCB versions. The
+three versions differ in the quantile parameter \(c\) (compare
+\autoref{sec:AppendixBUCB}) for which we set here
+\(c \in \{1/5, 1, 5\}\) to explore more or less. In Kaufmann et al.
+(2012), the cumulative regret upper bound for the Bayes-UCB is shown for
+\(c\geq 5\), though they report that the choice of \(c=0\) worked much
+better in their experiments. In our problem, it makes also sense that
+the versions with smaller quantiles (smaller \(c\)) tend to perform
+better than
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation2_results_bucb-1}
+
+}
+
+\caption{Performance comparison of algorithms for simulation 2.}\label{fig:simulation2_results_bucb}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-11-1}
+
+}
+
+\caption{Budget allocation for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter c.}\label{fig:unnamed-chunk-11}
+\end{figure}
+
+\subsection{Empirical Comparison of APT, SLR, and Bayes-UCB in
+Experiment
+2}\label{empirical-comparison-of-apt-slr-and-bayes-ucb-in-experiment-2}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-12-1}
+
+}
+
+\caption{Budget allocation for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter c.}\label{fig:unnamed-chunk-12}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-13-1}
+
+}
+
+\caption{Budget allocation for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter c.}\label{fig:unnamed-chunk-13}
+\end{figure}
 

### 2017-08-31 AugUCB/run_parallelized_from_data.R

@@ -260,6 +260,30 @@ para_bandit_sim_LR <- function(data, seed = NA, do_verbose = FALSE, ...) {
   return(res)
 }
 
+para_bandit_sim_LRD <- function(data, seed = NA, do_verbose = FALSE, ...) {
+  require(foreach)
+  require(doParallel)
+  
+  # assume that data is a list of data frames
+  reps <- length(data)
+  
+  gc()
+  cl <- makeCluster(max(1,detectCores()-1))
+  registerDoParallel(cl)
+  res <- foreach(j = 1:reps, #.errorhandling = 'remove',
+                 .export = c("LRD_bandit_from_tsdata", "get_next_arm_lr",
+                             "get_min", "lr_ber"), 
+                 .verbose = do_verbose, .inorder = TRUE) %dopar% {
+                   alg_res <- LRD_bandit_from_tsdata(data = data[[j]], 
+                                                    seed = 512+j, ...)
+                   list(mean_storage = alg_res$mean_storage,
+                        arm_sequence = alg_res$arm_sequence,
+                        input_data = data[[j]])
+                 }
+  stopCluster(cl)
+  return(res)
+}
+
 para_bandit_sim_LR_gaussian <- function(data, seed = NA, do_verbose = FALSE, ...) {
   require(foreach)
   require(doParallel)

### 2017-08-31 synthetic_experiments/cal_algs_verylong_6_no_tau.R

@@ -35,6 +35,138 @@ for(j in 1:5000) {
 }
 
 ########################################################################
+
+load(paste0(current_path, "/loc6nt_BUCB_horizon_7000.Rda"))
+load(paste0(current_path, "/loc6nt_AugUCB_7000.Rda"))
+load(paste0(current_path, "/loc6nt_UNIFORM_7000.Rda"))
+load(paste0(current_path, "/loc6nt_APT_7000.Rda"))
+load(paste0(current_path, "/loc6nt_LR_7000.Rda"))
+load(paste0(current_path, "/loc6nt_EVT.Rda"))
+
+table(loc6nt_LR_7000[[1]]$arm_sequence)
+table(loc6nt_LR_7000[[2]]$arm_sequence)
+table(loc6nt_LR_7000[[3]]$arm_sequence)
+table(loc6nt_LR_7000[[4]]$arm_sequence)
+table(loc6nt_LR_7000[[5]]$arm_sequence)
+tail(loc6nt_LR_7000[[5]]$mean_storage)
+
+library(ggplot2)
+library(ggjoy)
+library(dplyr)
+library(tidyr)
+
+pulls_of_arm_6_LR <- vector(length = 5000)
+for(i in 1:5000){
+  pulls_of_arm_6_LR[i] <- table(loc6nt_LR_7000[[i]]$arm_sequence)[6]
+}
+summary(pulls_of_arm_6_LR)
+quantile(pulls_of_arm_6_LR, 0.05)
+
+pulls_of_arm_6_APT <- vector(length = 5000)
+for(i in 1:5000){
+  pulls_of_arm_6_APT[i] <- table(loc6nt_APT_7000[[i]]$arm_sequence)[6]
+}
+summary(pulls_of_arm_6_APT)
+quantile(pulls_of_arm_6_APT, 0.05)
+
+pulls_of_arm_6_BUCB <- vector(length = 5000)
+for(i in 1:5000){
+  pulls_of_arm_6_BUCB[i] <- table(loc6nt_BUCB_horizon_7000[[i]]$arm_sequence)[6]
+}
+summary(pulls_of_arm_6_BUCB)
+quantile(pulls_of_arm_6_BUCB, 0.05)
+
+pulls_arm_6 <- data.frame(APT = pulls_of_arm_6_APT,
+                          SLR = pulls_of_arm_6_LR,
+                          BUCB = pulls_of_arm_6_BUCB)
+
[…]

### 2017-09-03 Thesis/Corollary.Rmd
Add corollary for lower bound

---
title: "Corollary"
header-includes:
   #- \documentclass[a4paper,twoside,english]{article}
   - \usepackage[retainorgcmds]{IEEEtrantools}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{bbm}
   - \usepackage{hyperref}
   - \usepackage[lined,boxed]{algorithm2e}
   - \newtheorem{theorem}{Theorem}
   - \newtheorem{definition}{Definition}
   - \newtheorem{lemma}{Lemma}
   - \newtheorem{corollary}{Corollary}
   - \newcommand{\KL}{\,\text{KL}}
   - \newcommand{\der}{\,\text{d}}
   - \newcommand*{\Alignyesnumber}{\refstepcounter{equation}\tag{\theequation}}%
   #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
   #- \usepackage{fontspec}
   #-   \setmainfont{Arial}
keep_tex: TRUE
output:
  pdf_document:
    number_sections: true
    keep_tex: true
    toc: true
    toc_depth: 2
    #latex_engine: xelatex
fontsize: 12pt
urlcolor: blue
---

\begin{corollary}
Let $\nu = \nu_1$ be a one-armed thresholding bandit model where $\tau$ is the threshold fixed upfront. Let $\nu$ be from the univariate canonical exponential family of distributions such that it can be parameterized by its mean, $\mu_1$, and the Kullback-Leibler divergence between distributions $\nu_1$ and $\nu_1'$ can be written as $\KL(\nu_1', \nu_1) = \KL(\mu_1', \mu_1)$. In the fixed budget setting, any consistent algorithm satisfies:

$$
\lim_{t \rightarrow \infty}- \frac{1}{t} \log p_t(\nu) \leq \KL(\tau, \mu_1)
$$
\end{corollary}

**Proof**: The proof follows closely the proof of Theorem

### 2017-09-03 Thesis/CorollaryProof.Rmd
Add corollary for lower bound

---
title: "Corollary"
header-includes:
   #- \documentclass[a4paper,twoside,english]{article}
   - \usepackage[retainorgcmds]{IEEEtrantools}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{bbm}
   - \usepackage{hyperref}
   - \usepackage[lined,boxed]{algorithm2e}
   - \newtheorem{theorem}{Theorem}
   - \newtheorem{definition}{Definition}
   - \newtheorem{lemma}{Lemma}
   - \newtheorem{corollary}{Corollary}
   - \newcommand{\KL}{\,\text{KL}}
   - \newcommand{\der}{\,\text{d}}
   - \newcommand*{\Alignyesnumber}{\refstepcounter{equation}\tag{\theequation}}%
   #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
   #- \usepackage{fontspec}
   #-   \setmainfont{Arial}
keep_tex: TRUE
output:
  pdf_document:
    number_sections: true
    keep_tex: true
    toc: true
    toc_depth: 2
    #latex_engine: xelatex
fontsize: 12pt
urlcolor: blue
---

\begin{corollary}
Let $\nu = \nu_1$ be a one-armed thresholding bandit model where $\tau$ is the threshold fixed upfront. Let $\nu$ be from the univariate canonical exponential family of distributions such that it can be parameterized by its mean, $\mu_1$, and the Kullback-Leibler divergence between distributions $\nu_1$ and $\nu_1'$ can be written as $\KL(\nu_1', \nu_1) = \KL(\mu_1', \mu_1)$. In the fixed budget setting, any consistent algorithm satisfies:

$$
- \frac{1}{t} \log p_t(\nu) \leq \KL(\tau, \mu_1)
$$
\end{corollary}

**Proof**: The proof follows closely the proof of Theorem 12 in Kaufmann et al. (2016) and is again an application of their transportation Lemma, Lemma 2.

Consider the one-armed bandit problem, $K = 1$ with the canonical exponential family of distributions distribution $\nu_1$ parameterized by its mean $\mu_1$. Furthermore, given we are in the thresholding bandit problem, we have a threshold $\tau$ against which the arm is classified. Assume w.l.o.g. that for $\nu_1$, $\mu_1 \geq \tau$. Thus, $\mathcal{S}_{\tau}^* = \{1\}$. After $T$ rounds, a consistent algorithm returns with error probability $p_T(\nu)$ the guess $\hat{\mathcal{S}}_{\tau}$. Thus, we have for the event $A = (\hat{\mathcal{S}}_\tau = \{1\})$ the probability $\mathbb{P}_{\nu}(A)$. On the other hand, define the alternative model $\nu'$ with mean $\mu_1' < \tau$ such that the correct classification from $\nu$ is now wrong: $\mathcal{S}_{\tau}^* {'} = (\mathcal{S}_{\tau}^*)^C = \{\emptyset\}$. Consequently, since the algorithm is still consistent on this problem, we have that $\mathbb{P}_{\nu'}(A) = p_t(\nu')$. Thus, we expect that as we let $t$ increase, $\mathbb{P}_{\nu'}(A)$ will decrease while $\mathbb{P}_{\nu}(A)$ will increase.

Indeed, given we consider only consistent algorithms, there should exist a number of samples for which the probability of the correct decision in problem $\nu$ is larger than the error probability in problem $\nu'$, that is: for every $\epsilon > 0$, there exists $t_0(\epsilon)$ such that for all $t \geq t_0(\epsilon)$ we have

\begin{equation*}
\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_{\nu}(A). \label{eq:BoundForCorollary}
\end{equation*}

Now, consider again Lemma 2 in Kaufmann et al. (2016). If we let the algorithm be such that $T = t$, we can apply the Lemma to the stopping time $\sigma = t$ a.s. and the event $A$ to get

$$
\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)).
$$

We can lower bound the RHS by using the bound on $\mathbb{P}_{\nu'}(A)$ given in \eqref{eq:BoundForCorollary} and the monotonicity of the binary relative entropy. We get:

\begin{align*}
\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) & = t \KL(\nu_1', \nu_1) \\
& \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)) \\
& \geq d(\epsilon, 1- p_t(\nu)) \\
& = \epsilon \log\Big(\frac{\epsilon}{1-p_t(\nu)}\Big) + (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) \\
& \geq (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) + \epsilon \log(\epsilon) \\
\end{align*}

Letting $\epsilon \rightarrow 0$, we get

$$
t \KL(\nu_1', \nu_1) \geq \log \Big(\frac{1}{p_t(\nu)}\Big) = -\log p_t(\nu).
$$
To make the bound as tight as possible, we choose the alternative model that minimizes $\KL(\nu_1', \nu_1)$ while still ensuring that $\mathcal{S}_{\tau}^* {'} = \{\emptyset\}$. In our case of the thresholding bandit with univariate exponential family distributions, this is given by choosing $\mu_1' = \tau$. By pluggin in, we get the result:

$$
t \KL(\tau, \mu_1) \geq -\log p_t(\nu).
$$

\begin{corollary}
Let $\nu = (\nu_1, ..., \nu_K)$ be a $K$-armed thresholding bandit problem in which $\tau$ is the threshold fixed upfront. For $i \in \{1,...,K\}$, let $\nu_i$ be from the univariate canonical exponential family of distributions such that it can be parameterized by its mean, $\mu_i$, and the Kullback-Leibler divergence between distributions $\nu_i$ and $\nu_i'$ can be written as $\KL(\nu_i, \nu_i') = \KL(\mu_i, \mu_i')$. In the fixed budget setting, every consistent algorithm satisfies:

$$
\lim_{t \rightarrow \infty} -\frac{1}{t} \log p_t(\nu) \leq \max_{a \in \{1,...,K\}} \KL(\tau, \mu_a)
$$
\end{corollary}

**Proof**: The proof is very similar to the proof of the corollary for $K=1$. However, the alternative model needs more motivation than in the case of a single arm. But first, consider again that we are in the thresholding bandit problem with $K$ arms of univariate canonical exponential family distributions that are parameterized by their means $\mu_1, ..., \mu_K$ for the original problem $\nu = (\nu_1, ..., \nu_K)$. W.l.o.g, assume that all arms are above the threshold, that is, $\mu_1 \geq \tau, ..., \mu_K \geq \tau$. Then $\mathcal{S}_{\tau}^* = \{1, ... , K\}$. The correct classification returned after $t$ rounds is thus the event $A = (\hat{\mathcal{S}}_{\tau} = \{1, ..., K\})$. We can now consider Lemma 2. The RHS is maximized when the alternative model is chosen such that $d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A))$ is maximized. Given the event $A$ as defined before, this is the case when $\mathbb{P}_{\nu'}(A)$ is as small as possible. For consistent algorithms, this is the case when $\nu'$ is chosen such that all $\mu_1' < \tau, ..., \mu_K' < \tau$. Then even classifying a single arm correctly under $\nu$ would lead to a mistake in $\nu'$. Consequently, $A$ is the most unlikely classification for a consistent algorithm for the problem $\nu'$. We thus expect for any consistent algorithm that $\mathbb{P}_{\nu}(A)$ becomes large and $\mathbb{P}_{\nu'}(A)$ becomes small as the number of observations $t$ increases. Again, for every $\epsilon > 0$, there exists $t_0(\epsilon)$ such that for all $t \geq t_0(\epsilon)$ we have $\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)$. This allows us to now use Lemma 1 as previously:

\begin{align*}
\sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\nu_i', \nu_i) & \geq \sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\tau, \mu_i) \\
& \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)) \\
& \geq d(\epsilon, 1-p_t(\nu)) \\
& = \epsilon \log \Big(\frac{\epsilon}{1-p_t(\nu)}\Big) + (1-\epsilon) \log \Big( \frac{1-\epsilon}{p_t(\nu)}\Big) \\
& \geq (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) + \epsilon \log(\epsilon)
\end{align*}

We let $\epsilon \rightarrow 0$, divide by $t$ and take the limsup on both sides as in Kaufmann et al. (2016):

\begin{align*}
\lim_{t \rightarrow \infty} \sup - \frac{1}{t} \log p_t(\nu) & \leq \lim_{t \rightarrow \infty} \sup \frac{1}{t} \sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\tau, \mu_i) \\
& \leq \max_{i \in \{1,...,K\}} \KL(\tau, \mu_i)
\end{align*}

Though, since for the alternative problem $\nu'$ we have for every $i \in \{1,...,K\}$ that $\mu_i = \tau$, it should hold for any consistent algorithm that $\mathbb{E}_{\nu'}[N_i(t)] = \frac{t}{K}$, that is, every arm receives an equal amount of the budget. In that case, the above equation simplifies to

$$
- \frac{1}{t} \log p_t(\nu) \leq \frac{1}{t} \sum_{i=1}^K \frac{t}{K}\KL(\tau, \mu_i) = \frac{\sum_{i=1}^{K} \KL(\tau, \mu_i)}{K},
$$

that is, the complexity is given by the simple average of the Kullback-Leibler distances of the threshold with regard to the respective distributions. This relates well to the lower bound that Kaufmann et al. (2016) describe in their Theorem 12 for consistent algorithms using *uniform* sampling strategies; in our case, however, it is explained by the fact that under the alternative model, every consistent algorithm should adapt to a uniform sampling strategy. Thus our bound holds for any consistent strategy.

### 2017-09-03 Thesis/CorollaryProof.tex
Add corollary for lower bound

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={Corollary},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{Corollary}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{hyperref}
\usepackage[lined,boxed]{algorithm2e}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newcommand{\KL}{\,\text{KL}}
\newcommand{\der}{\,\text{d}}
\newcommand*{\Alignyesnumber}{\refstepcounter{equation}\tag{\theequation}}%

\begin{document}
\maketitle

{
\hypersetup{linkcolor=black}
\setcounter{tocdepth}{2}
\tableofcontents
}
\begin{corollary}
Let $\nu = \nu_1$ be a one-armed thresholding bandit model where $\tau$ is the threshold fixed upfront. Let $\nu$ be from the univariate canonical exponential family of distributions such that it can be parameterized by its mean, $\mu_1$, and the Kullback-Leibler divergence between distributions $\nu_1$ and $\nu_1'$ can be written as $\KL(\nu_1', \nu_1) = \KL(\mu_1', \mu_1)$. In the fixed budget setting, any consistent algorithm satisfies:

$$
- \frac{1}{t} \log p_t(\nu) \leq \KL(\tau, \mu_1)
$$
\end{corollary}

\textbf{Proof}: The proof follows closely the proof of Theorem 12 in
Kaufmann et al. (2016) and is again an application of their
transportation Lemma, Lemma 2.

Consider the one-armed bandit problem, \(K = 1\) with the canonical
exponential family of distributions distribution \(\nu_1\) parameterized
by its mean \(\mu_1\). Furthermore, given we are in the thresholding
bandit problem, we have a threshold \(\tau\) against which the arm is
classified. Assume w.l.o.g. that for \(\nu_1\), \(\mu_1 \geq \tau\).
Thus, \(\mathcal{S}_{\tau}^* = \{1\}\). After \(T\) rounds, a consistent
algorithm returns with error probability \(p_T(\nu)\) the guess
\(\hat{\mathcal{S}}_{\tau}\). Thus, we have for the event
\(A = (\hat{\mathcal{S}}_\tau = \{1\})\) the probability
\(\mathbb{P}_{\nu}(A)\). On the other hand, define the alternative model
\(\nu'\) with mean \(\mu_1' < \tau\) such that the correct
classification from \(\nu\) is now wrong:
\(\mathcal{S}_{\tau}^* {'} = (\mathcal{S}_{\tau}^*)^C = \{\emptyset\}\).
Consequently, since the algorithm is still consistent on this problem,
we have that \(\mathbb{P}_{\nu'}(A) = p_t(\nu')\). Thus, we expect that
as we let \(t\) increase, \(\mathbb{P}_{\nu'}(A)\) will decrease while
\(\mathbb{P}_{\nu}(A)\) will increase.

Indeed, given we consider only consistent algorithms, there should exist
a number of samples for which the probability of the correct decision in
problem \(\nu\) is larger than the error probability in problem
\(\nu'\), that is: for every \(\epsilon > 0\), there exists
\(t_0(\epsilon)\) such that for all \(t \geq t_0(\epsilon)\) we have

\begin{equation*}
\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_{\nu}(A). \label{eq:BoundForCorollary}
\end{equation*}

Now, consider again Lemma 2 in Kaufmann et al. (2016). If we let the
algorithm be such that \(T = t\), we can apply the Lemma to the stopping
time \(\sigma = t\) a.s. and the event \(A\) to get

\[
\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)).
\]

We can lower bound the RHS by using the bound on
\(\mathbb{P}_{\nu'}(A)\) given in \eqref{eq:BoundForCorollary} and the
monotonicity of the binary relative entropy. We get:

\begin{align*}
\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) & = t \KL(\nu_1', \nu_1) \\
& \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)) \\
& \geq d(\epsilon, 1- p_t(\nu)) \\
& = \epsilon \log\Big(\frac{\epsilon}{1-p_t(\nu)}\Big) + (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) \\
& \geq (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) + \epsilon \log(\epsilon) \\
\end{align*}

Letting \(\epsilon \rightarrow 0\), we get

\[
t \KL(\nu_1', \nu_1) \geq \log \Big(\frac{1}{p_t(\nu)}\Big) = -\log p_t(\nu).
\] To make the bound as tight as possible, we choose the alternative
model that minimizes \(\KL(\nu_1', \nu_1)\) while still ensuring that
\(\mathcal{S}_{\tau}^* {'} = \{\emptyset\}\). In our case of the
thresholding bandit with univariate exponential family distributions,
this is given by choosing \(\mu_1' = \tau\). By pluggin in, we get the
result:

\[
t \KL(\tau, \mu_1) \geq -\log p_t(\nu).
\]

\begin{corollary}
Let $\nu = (\nu_1, ..., \nu_K)$ be a $K$-armed thresholding bandit problem in which $\tau$ is the threshold fixed upfront. For $i \in \{1,...,K\}$, let $\nu_i$ be from the univariate canonical exponential family of distributions such that it can be parameterized by its mean, $\mu_i$, and the Kullback-Leibler divergence between distributions $\nu_i$ and $\nu_i'$ can be written as $\KL(\nu_i, \nu_i') = \KL(\mu_i, \mu_i')$. In the fixed budget setting, every consistent algorithm satisfies:

$$
\lim_{t \rightarrow \infty} -\frac{1}{t} \log p_t(\nu) \leq \max_{a \in \{1,...,K\}} \KL(\tau, \mu_a)
$$
\end{corollary}

\textbf{Proof}: The proof is very similar to the proof of the corollary
for \(K=1\). However, the alternative model needs more motivation than
in the case of a single arm. But first, consider again that we are in
the thresholding bandit problem with \(K\) arms of univariate canonical
exponential family distributions that are parameterized by their means
\(\mu_1, ..., \mu_K\) for the original problem
\(\nu = (\nu_1, ..., \nu_K)\). W.l.o.g, assume that all arms are above
the threshold, that is, \(\mu_1 \geq \tau, ..., \mu_K \geq \tau\). Then
\(\mathcal{S}_{\tau}^* = \{1, ... , K\}\). The correct classification
returned after \(t\) rounds is thus the event
\(A = (\hat{\mathcal{S}}_{\tau} = \{1, ..., K\})\). We can now consider
Lemma 2. The RHS is maximized when the alternative model is chosen such
that \(d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A))\) is maximized.
Given the event \(A\) as defined before, this is the case when
\(\mathbb{P}_{\nu'}(A)\) is as small as possible. For consistent
algorithms, this is the case when \(\nu'\) is chosen such that all
\(\mu_1' < \tau, ..., \mu_K' < \tau\). Then even classifying a single
arm correctly under \(\nu\) would lead to a mistake in \(\nu'\).
Consequently, \(A\) is the most unlikely classification for a consistent
algorithm for the problem \(\nu'\). We thus expect for any consistent
algorithm that \(\mathbb{P}_{\nu}(A)\) becomes large and
\(\mathbb{P}_{\nu'}(A)\) becomes small as the number of observations
\(t\) increases. Again, for every \(\epsilon > 0\), there exists
\(t_0(\epsilon)\) such that for all \(t \geq t_0(\epsilon)\) we have
\(\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)\). This
allows us to now use Lemma 1 as previously:

\begin{align*}
\sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\nu_i', \nu_i) & \geq \sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\tau, \nu_i) \\
& \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)) \\
& \geq d(\epsilon, 1-p_t(\nu)) \\
& = \epsilon \log \Big(\frac{\epsilon}{1-p_t(\nu)}\Big) + (1-\epsilon) \log \Big( \frac{1-\epsilon}{p_t(\nu)}\Big) \\
& \geq (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) + \epsilon \log(\epsilon)
\end{align*}

We let \(\epsilon \rightarrow 0\), divide by \(t\) and take the limsup
on both sides as in Kaufmann et al. (2016):

\begin{align*}
\lim_{t \rightarrow \infty} \sup - \frac{1}{t} \log p_t(\nu) & \leq \lim_{t \rightarrow \infty} \sup \frac{1}{t} \sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\tau, \nu_i) \\
& \leq \max_{i \in \{1,...,K\}} \KL(\tau, \nu_i)
\end{align*}

\end{document}

### 2017-09-03 Thesis/Draft.Rmd
Add corollary for lower bound

@@
    - \newtheorem{lemma}{Lemma}
+   - \newtheorem{corollary}{Corollary}
    - \newcommand{\KL}{\,\text{KL}}
@@
 \Input{$\tau$, $\epsilon$}
-\Output{$\hat{S}_{\tau} = \{k: \hat{\mu}_k(T) \geq \tau\}$}
+\Output{$\hat{S}_{\tau} = \{i \in \{1,...,K\}, \hat{\mu}_i(T) \geq \tau\}$}
 \BlankLine
@@
 \For{$t = K+1$ \KwTo $T$}{
-  \emph{Pull arm $I_t = \arg \min_{k\leq K} B_k^{APT}(t) = \sqrt{T_k(t)} (|\hat{\mu}_i(t) - \tau|+\epsilon)$}\;
-  \emph{Observe reward $X \sim \nu_{I_t}$}\;
+  \emph{Pull arm $I_t = \arg \min_{i \in A} B_i^{APT}(t) = \arg \min_{i \in A} \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau|+\epsilon)$}\;
+  \emph{Observe reward $X_t \sim \nu_{I_t}$}\;
 }
 \caption{Anytime Parameter-free Thresholding Algorithm (Locatelli et al., 2016)}\label{alg:APT}
-\end{algorithm}\DecMargin{1em}
+\end{algorithm}
+\DecMargin{1em}
 
@@
 $$
-\hat{\mu}_{i,T_i(n)} \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
+\hat{\mu}_{i}(T) \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
 $$
@@
 $$
-\hat{\mu}_{i,T_i(n)} \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
+\hat{\mu}_{i}(T) \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
 $$
@@
 $$
-| \hat{\mu}_{i, T_i(n)} - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
+| \hat{\mu}_{i}(T) - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
 $$
@@
 Assuming $\mu_i < \tau$ and $\epsilon = 0$, an incorrect classification would require $\mu_i < \tau \leq \hat{\mu_i}$.
-But then  $| \hat{\mu}_{i, T_i(n)} - \mu_i | \geq |\mu_i - \tau|$, which violates the separation condition.
+But then  $| \hat{\mu}_{i}(T) - \mu_i | \geq |\mu_i - \tau|$, which violates the separation condition.
 
@@
 $$
-T_k(T) - 1 \geq \frac{(T-K)h_k}{H} \geq \frac{(T-1/2T)h_k}{H} = \frac{Th_i}{2H}
+T_k(T) - 1 \geq \frac{(T-K)h_k}{H} \geq \frac{(T-1/2T)h_k}{H} = \frac{Th_k}{2H}
 $$
@@
 $$
-T_k(t) \geq T_k(T) - 1 \geq \frac{Th_i}{2H}.
+T_k(t) \geq T_k(T) - 1 \geq \frac{Th_k}{2H}.
 $$
@@
 $$
-\mathbb{E}[L] = 1 - \mathbb{P}(\xi) \leq 2(\log(T)+1)K \exp(-\frac{1}{64R^2}\frac{T}{H}).
+\mathbb{E}[\mathcal{L}(T)] = 1 - \mathbb{P}(\xi) \leq 2(\log(T)+1)K \exp(-\frac{1}{64R^2}\frac{T}{H}).
 $$
@@
 Indeed, the setting in which the budget is *not* fixed upfront might be more popular among the best arm identification and top-$m$ literature.
-This setting is called *fixed-confidence*, while the setting we considered so far is called *fixed-budget*.
-In the fixed-budget setting, we run algorithms for $T$ samples and then compare them based on their expected loss, $\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m) =: p_t(\nu)$ as we have seen in $\autoref{sec:Setup}$.
+This setting is called *fixed confidence*, while the setting we considered so far is called *fixed budget*.
+In the fixed budget setting, we run algorithms for $T$ samples and then compare them based on their expected loss, $\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m) =: p_t(\nu)$ as we have seen in $\autoref{sec:Setup}$.
 Alternatively, consider a $\delta$-PAC strategy $\mathcal{A}(\delta)$for which holds for every problem $\nu \in \mathcal{M}_m$ that the classification holds at least with confidence level $1-\delta$, that is, $\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta$.
 The strategy has to achieve this level of confidence in its prediction before it is allowed to stop sampling.
-This is the fixed-confidence case, in which the budget $T$ is no longer fixed upfront, but becomes a random variable.
+This is the fixed confidence case, in which the budget $T$ is no longer fixed upfront, but becomes a random variable.
 We compare algorithms by their expected number of draws $\mathbb{E}_{\nu}[T_{\delta}]$ and prefer those which arrive at the confidence level $1-\delta$ with a smaller expected budget.
@@
 
-To prove this statement, we assume as before that the arms are ordered by their means decreasing in size.
-For a given $\delta$-PAC algorithm $\mathcal{A} = ((A_t), \tau, \hat{S}_m)$, and under the continuity conditions (compare Kaufmann et al.
-(2016)), there exists for every arm $a \in \{1, \dots, K\}$ an alternative model $\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)$.
-In this alternative model, only arm $a$ is modified in accordance with the continuity conditions.
-Modified in such a way, the arm $\nu_{m+1}$ is now closer to $\nu_a$ as measured by the Kullback-Leibler divergence than $\nu_a'$ is to $\nu_a$, if $\mu_a > \mu_{m+1}$ (consequently, $\mu_a' < \mu_{m+1}$).
+To prove this statement for a given $\delta$-PAC algorithm $\mathcal{A}$, we assume certain continuity conditions (compare Kaufmann et al.
+(2016)), with which there exists for every arm $a \in \{1, \dots, K\}$ an alternative model $\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)$.
+In this alternative model, in accordance with the continuity conditions, only arm $a$ is modified.
+After the modification, the arm $\nu_{m+1}$ is now closer to $\nu_a$ as measured by the Kullback-Leibler divergence than $\nu_a'$ is to $\nu_a$, if $\mu_a > \mu_{m+1}$ (consequently, $\mu_a' < \mu_{m+1}$).
 On the other hand, if $\mu_a < \mu_{m}$, then $\nu_a'$ will be moved away from $\nu_a$ just enough so that $\nu_a$ is closer to $\nu_m$ than to $\nu_a'$ (consequently, $\mu_a' > \mu_m$).
 These changes in distribution make the original set of optimal arms, $\{1,\dots,m\}$, no longer optimal under the alternative model $\nu'$.
-Given that the algorithm returns $\hat{S}_m$, we know that for the event $\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})$ (which is element of the $\sigma$-Algebra $\mathcal{F}_{\tau}$ induced by the stopping time $\tau$), that $\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta$ and $\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta$ (because fixed confidence $\delta$!).
-
+To compare this to the thresholding bandit problem, assume that arms $\nu_{m}$ and $\nu_{m+1}$ indirectly define a threshold $\tau \in (\mu_{m+1},\mu_m)$.
+Then, by creating an alternative problem as described here, we flip arm $a$ around the implied threshold $\tau$ (compare the lower bound proof in \autoref{sec:AppendixAPTLB}).
+
+Given that the strategy returns $\hat{S}_m$, we know that for the event $\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})$ (which is element of the $\sigma$-Algebra $\mathcal{F}_{T}$ induced by the stopping time $T$), that $\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta$ and $\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta$ (because fixed confidence $\delta$!).
 To now give the lower bound on the expected number of samples, $\mathbb{E}_{\nu}[\tau]$, we employ the general Lemma given by the authors for such changes in distribution in bandit models.
@@
 \begin{equation*}
-\mathbb{E}_{\nu}[\tau] = \sum_{a=1}^K \mathbb{E}_{\nu}[N_a] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \der(1-\delta, \delta)
-\end{equation*}
-
-Given that we will be naturally interested in either very high or very low confidence of our algorithm, that is, $P_\nu(\mathcal{E})$ is either close to 0 or 1, it is possible to use the following approximation to the binary relative entropy:
+\mathbb{E}_{\nu}[T] = \sum_{a=1}^K \mathbb{E}_{\nu}[N_a] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \der(1-\delta, \delta)
+\end{equation*}
+
+Given that we will be naturally interested in either very high or very low confidence of our algorithm, that is, $P_\nu(\mathcal{E})$ is either close to 0 or 1, it is possible to use the following approximation to the binary relative entropy given in Kaufmann et al.
+(2016):
 
 \begin{equation}\label{bre_approx}
-\forall x \in [0,1], \quad \der(x,1-x) = \der(1-x,x) \geq \log \frac{1}{2.4x}
+\forall x \in [0,1], \quad \der(x,1-x) = \der(1-x,x) \geq \log \frac{1}{2.4x}.
 \end{equation}
 
-And so the final lower bound can be written as
-
-\begin{equation*}
-\mathbb{E}_{\nu}[\tau] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
-\end{equation*}
-
-```{r, echo = FALSE}
-x <- seq(0,1,by = 0.001)
-bre <- function(x) x * log(x/(1-x)) + (1-x) * log((1-x)/x)
-plot(x,bre(x), type = "l", ylab = "Binary Relative Entropy")
-lines(x, log(1/(2.4*x)), col = "red")
-abline(v = 0.15, lty = 2)
-```
-
-Given this general lower bound for the sampling complexity, or expected number of draws, it makes sense to define the complexity of a Top-$m$ bandit problem using the Kullback-Leibler divergence.
-After all, besides the number of arms and the experimenter-chosen confidence, it is just how close arms are with respect to each other in terms of Kullback-Leibler divergence that influences the sampling complexity.
-
-Thus, following Kaufmann et al. (2016), define the complexity $\kappa_C(\nu)$ for the fixed confidence setting as
+This allows us to write the lower bound on the expected stopping time as:
+
+\begin{equation*}
+\mathbb{E}_{\nu}[T] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
+\end{equation*}
+
+Given this lower bound, it becomes clear that the complexity of the top-$m$ problem can be lower bounded by the Kullback-Leibler divergence between arms and the implied threshold between the $m$-th best arm and the $(m+1)$-th best arm.
+After all, the latter gives a lower bound on the effort (in terms of expected number of samples) required to achieve a certain confidence level.
+And a problem that requires a larger effort can be described as more complex.
+Indeed, in the case of fixed confidence problems, Kaufmann et al.
+(2016) describe problems as having a larger *sampling complexity*.
+
+Following Kaufmann et al. (2016), we can now define the complexity $\kappa_C(\nu)$ for the fixed confidence setting as
 
 \begin{equation}
-\kappa_C(\nu) = \inf_{A \, \text{PAC}} \lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\nu}[\tau_{\delta}]}{\log \frac{1}{\delta}}.
+\kappa_C(\nu) = \inf_{A \, \text{PAC}} \lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\nu}[T{\delta}]}{\log \frac{1}{\delta}}. \label{eq:KappaC}
 \end{equation}
 
-By plugging in the lower bound on the sampling complexity, we arrive at a complexity measure that depends only on the Kullback-Leibler measuring for each arm how far it is away from the border between the two groups of arms.
-To see this, consider the lower bound on the complexity measure given in Kaufmann et al.
+This definition makes sense if we consider the fact that the confidence level $\delta$ is experimenter chosen and thus not relevant in describing the complexity.
+Thus, by including $\log(1/\delta)$ explicitly in \eqref{eq:KappaC}, we get rid of the confidence term in the lower bound on $\mathbb{E}_{\nu}[T]$ after plugging it into \eqref{eq:KappaC}.
+We arrive at the lower bound on the complexity measure given in Kaufmann et al.
 (2016):
@@
 
-Given this description, we can already note that an intuitive extension of this complexity notion to the thresholding bandit problem might involve replacing $\mu_{[m]}$ and $\mu_{[m+1]}$ by the actual threshold $\tau$ (notation in Locatelli et al.) that divides the group above the threshold from the group below the threshold.
-In this sense, the previously used $\alpha$ is similar to the $\epsilon$ used in Locatelli et al.
-(2016).
-
-Before we get to an extension of the thresholding bandit problem, however, at least two important steps remain.
-First, we need to define a complexity for the fixed budget problem.
-Second, we need to create algorithms that can match the lower bound.
-
-Kaufmann et al.
-are able to provide a bound on their complexity measure in the fixed budget case, however only in the case of **two-armed** bandit models.
-As demanded in their paper, a fixed-budget algorithm is called consistent if the failure probability $p_t(\nu) := \mathbb{P}_{\nu}(\hat{S}_m \neq S^*_m)$ tends to zero as the number of samples goes to infinity.
-Also, define the complexity in the fixed-budget setting as follows:
+Given this description, we would expect that a complexity measure in a fixed confidence thresholding bandit probem might involve replacing $\mu_{[m]}$ and $\mu_{[m+1]}$ by the actual threshold $\tau$ that divides the group above the threshold from the group below the threshold.
+
+However, given the problem formulation in Locatelli et al.
+(2016), we are mainly interested in complexity measures and algorithms for the fixed budget setting.
+As we will see now, the results of Kaufmann et al.
+(2016) are more limited for this case.
+While the authors are able to provide a bound on their complexity measure in the fixed budget case, it only applies to the case of *two-armed* bandit models.
+Consider a consistent fixed budget strategy $\mathcal{A}$ ($p_t(\nu)$ tends to zero as $t \rightarrow \infty$), and define the complexity in the fixed budget setting as follows:
 
@@
 
-Given this definition, one can interpret the bound given in Theorem 12 of Kaufmann et al. directly as a lower bound on the complexity $\kappa_B(\nu)$ (note the inverse).
+While we included the experimenter-fixed $\delta$ in the definition of $\kappa_C$, we now include the experimenter-fixed $T$ in the definition of $\kappa_B$ to disregard it in the complexity measure after plugging in the lower bound on $p_t(\nu)$.
+The resulting lower bound given in Theorem 12 of Kaufmann et al.
+(2016):
 
 \begin{theorem}[Theorem 12, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem12}
-Let $\nu = (\nu_1, \nu_2)$ be a two-armed bandit model such that $\mu_1 > \mu_2$. In the fixed-budget setting, any consistent algorithm satisfies:
+Let $\nu = (\nu_1, \nu_2)$ be a two-armed bandit model such that $\mu_1 > \mu_2$. In the fixed budget setting, any consistent algorithm satisfies:
 
@@
 
-For a proof, consider first the two different bandit models, $\nu$ and $\nu'$, where we fix without loss of generality that $a^* = 1$ is the best arm in $\nu$, while $a^* = 2$ in $\nu'$.
+For a proof, consider first the two different bandit models, $\nu$ and $\nu'$, where we fix w.l.o.g.
+$a^* = 1$ as the best arm in $\nu$, while $a^* = 2$ in $\nu'$.
 Note that in this case we don't necessarily try to fool the algorithm by a change of distribution.
 Indeed, we want the algorithm $\mathcal{A}$ to be consistent for both problems.
-Since we are in the fixed-budget setting, the stopping time is fixed at $\tau = t$.
+Since we are in the fixed budget setting, the stopping time is fixed at $T = t$.
 Even though the correct decision differs between the two problems, we focus on the event $A = (\hat{S}_1 = 1)$.
-Given the formulation in Kaufmann et al.
-(2016), we have $A \in \mathcal{F}_t = \mathcal{F}_{\tau}$.
-Now, we can apply Lemma 1 as before, as it in essense gives a measure of how different two bandit models are.
+Now, we can apply Lemma 1 as before, as it in essence gives a measure of how different two bandit models are.
 Here, we want to know how different $\nu$ is from $\nu'$, and so, given we have only two arms,
@@
 
-The expectations were chosen with respect to $\nu'$ in order to allow the for the following: We have $p_t(\nu) = 1 - \mathbb{P}_{\nu}(A)$ and $p_t(\nu') = \mathbb{P}_{\nu'}(A)$ (since $A$ is wrong in $\nu'$).
-But since algorithm $\mathcal{A}$ is consistent for both $\nu$ and $\nu'$, we know that there should exist some number of samples such that the probability of event $A$ is bigger in setting $\nu$ (where it is the correct decision), than in setting $\nu'$ (where this would be a wrong decision and failure).
-Thus, for every $\epsilon > 0$, there exists $t_0(\epsilon)$ such that for all $t \geq t_0(\epsilon)$, $\mathbb{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)$.
+The expectations were chosen with respect to $\nu'$ in order to allow for the following: We have $p_t(\nu) = 1 - \mathbb{P}_{\nu}(A)$ and $p_t(\nu') = \mathbb{P}_{\nu'}(A)$ (since $A$ is wrong in $\nu'$).
+But since algorithm $\mathcal{A}$ is consistent for both $\nu$ and $\nu'$, we know that there should exist some number of samples such that the probability of event $A$ is bigger in setting $\nu$ (where it is the correct decision) than in setting $\nu'$ (where this would be a wrong decision and failure).
+Thus, for every $\epsilon > 0$, there exists $t_0(\epsilon)$ such that for all $t \geq t_0(\epsilon)$, $\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)$.
 Consequently, if we plug in the bound of $\epsilon$ for $\mathbb{P}_{\nu'}(A)$, then
@@
 
-Note that while deriving the lower bound on the complexity measure, we have also derived the following lower bound on the failure probability for the two-armed fixed-budget bandit:
+Note that while deriving the lower bound on the complexity measure, we have also derived the following lower bound on the failure probability for the two-armed fixed budget bandit:
 
@@
 
-**Mention something about the fact that we were not able to do this for more than 2 arms and top-m bandits. How could it be extended to that? How could it be extended to the threshold bandit?**
-
 As noted by Kaufmann et al.
-(2016), the advantage of this lower bound is that it makes the complexity in the fixed-confidence and the fixed-budget setting directly comparable.
+(2016), the advantage of this lower bound is that it makes the complexity in the fixed confidence and the fixed budget setting directly comparable.
 The disadvantage of course being that the result only holds for two-armed models.
-While the authors were not able to derive directly comparable lower bounds for the Top-$m$ case, they did derive a first lower bound in the Gaussian case with equal variances.
-While we would like to move beyond Gaussian distributions in the work at hand, the idea for the proof might show a way of how the ideas can be transferred to the thresholding bandit problem.
-We first state the result and then discuss the proof.
-
-\begin{lemma}[Lemma 15, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma15}
-Let $\nu$ and $\nu'$ be two bandit models such that $S^*_m(\nu) \neq S*_m(\nu')$. Then
-
-\begin{equation*}
-\max \big( \mathbb{P}_{\nu}(S \neq S^*_m(\nu)), \mathbb{P}_{\nu'}(S \neq S^*_m(\nu')) \big) \geq \frac{1}{4} \exp \Big(-\sum_{a=1}^{K} \mathbb{E}_{\nu}[N_a] \KL(\nu_a, \nu_a') \Big).
-\end{equation*}
-\end{lemma}
-
-The following theorem only holds in the case of Gaussian bandit models with equal known variance.
-
-\begin{theorem}[Theorem 17, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem17}
-
-Let $\mathcal{M}_m = \{\nu = (\nu_1, \dots, \nu_K): \nu_a = \mathcal{N}(\mu_a, \sigma^2), \mu_a \in \mathbb{R}, \mu_{[m]}\neq \mu_{[m+1]}\}.$ Furthermore, let $\nu$ be such that $\mu_1 > \dots > \mu_m > \mu_{m+1} > \dots > \mu_K$, and let
-
-\begin{equation*}
-H +(\nu) = \sum_{a=1}^m \frac{2\sigma^2}{(\mu_a - \mu_{m+1})^2}, \quad H^-(\nu) = \sum_{a=m+1}^K \frac{2\sigma^2}{(\mu_m - \mu_a)^2} \quad
-and \quad
-H(\nu) = H^+(\nu) + H^-(\nu).
-\end{equation*}
-
-There exists $a \in {1, \dots, m}$ and $b \in \{m+1, \dots, K\}$ such that the bandit model $\nu^{[a,b]}$ described in Figure 4 (Kaufmann et al., 2016) satisfies $H(\nu^{[a,b]}) < H(\nu)$ and is such that
-
-\begin{equation*}
-\max \big( p_t(\nu),p_t(\nu^{[a,b]})\big) \geq \frac{1}{4} \exp \big(-\frac{4t}{\bar{H}(\nu)}\big), \quad where \quad \bar{H}(\nu) = \frac{H(\nu) \min(H^+(\nu),H^-(\nu))}{H(\nu)+\min(H^+(\nu),H^-(\nu))}
-\end{equation*}
-\end{theorem}
-
-Given that we are again in the Top-$m$ setting, the proof idea is similar to the proof of Theorem \ref{theorem:KaufmannEtAlTheorem4} in that we again consider problems where we switch arms around the limit seperating the two groups of arms as given implicitly by $\mu_{[m]}$ and $\mu_{[m+1]}$.
-The hope here being that these methods could be applied to the thresholding bandit problem where the threshold of course gives the limit between the arms above and below the threshold.
-As we have seen in chapter 1, this flip around the threshold was of course used in the proof of the lower bound in Theorem 1 of Locatelli et al.
-(2016).
-However, there, again, the distributions were assumed to be Gaussian.
-This brings the big advantage that the Kullback-Leibler divergence becomes symmetric, and the feedback can take values on all $\mathbb{R}$.
-And by using the complexity measure $H(\nu)$, it is also clear that there exists an arm that is undersampled with respect to its contribution to the overall complexity of the problem (or sampled exactly according to its contribution), which leads to a convenient upper bound on this arms number of draws which is again employed in both the proof of Theorem \ref{theorem:KaufmannEtAlTheorem17} and in Locatelli et al.
-(2016).
-It is not clear yet, whether the same can also be done with other complexity measures.
-
-We do not repeat the proof here for now.
-
-See p20!
-
-What remains is to present algorithms that are able to match the lower bounds derived so far.
+While the authors are not able to derive directly comparable lower bounds for the top-$m$ case, they derive a first lower bound in the Gaussian case with equal variances, which we describe shortly in the appendix in \autoref{sec:KaufmannLBTopMGaussian}.
+
+Before we discuss the strategies of Kaufmann et al. (2016) matching the lower bounds, we now show how lower bounds can be derived very similarly for the fixed budget thresholding problem.
+
+### Lower Bound for Fixed Budget Thresholding Problem
+
+In order to derive a bound for the fixed budget problem, Kaufmann et al.
+(2016) have focused on the case of the two-armed bandit which is the most simple version of the top-$m$ problem.
+Less than two arms do not make sense, since then this single arm will always be the best arm.
+In the case of the thresholding bandit, however, a single-armed problem makes still some sense in that we still have to classify this arm correctly with respect to the threshold.
+Thus, we can show the following corollary which gives the a bound on the complexity of the single-armed thresholding bandit.
+
+\begin{corollary}
+Let $\nu = \nu_1$ be a one-armed thresholding bandit model where $\tau$ is the threshold fixed upfront.
+Let $\nu$ be from the univariate canonical exponential family of distributions such that it can be parameterized by its mean, $\mu_1$, and the Kullback-Leibler divergence between distributions $\nu_1$ and $\nu_1'$ can be written as $\KL(\nu_1', \nu_1) = \KL(\mu_1', \mu_1)$.
+In the fixed budget setting, any consistent algorithm satisfies:
+
+$$
+- \frac{1}{t} \log p_t(\nu) \leq \KL(\tau, \mu_1)
+$$
+\end{corollary}
+
+This of course is basically the Chernoff-Stein Lemma for the hypothesis test of two alternatives (compare chapter 11 in Cover and Thomas, 2006).
+
+But as we see in the following corollary, we can extend the lower bound to the $K$-armed fixed budget thresholding bandit problem, which stands in contrast to the fact that for the top-$m$ problem, it is only possible to show the lower bound for two arms.
+
+\begin{corollary}
+Let $\nu = (\nu_1, ..., \nu_K)$ be a $K$-armed thresholding bandit problem in which $\tau$ is the threshold fixed upfront.
+For $i \in \{1,...,K\}$, let $\nu_i$ be from the univariate canonical exponential family of distributions such that it can be parameterized by its mean, $\mu_i$, and the Kullback-Leibler divergence between distributions $\nu_i$ and $\nu_i'$ can be written as $\KL(\nu_i, \nu_i') = \KL(\mu_i, \mu_i')$.
+In the fixed budget setting, every consistent algorithm satisfies:
+
+$$
+\lim_{t \rightarrow \infty} -\frac{1}{t} \log p_t(\nu) \leq \max_{a \in \{1,...,K\}} \KL(\tau, \mu_a)
+$$
+\end{corollary}
+
+Given the lower bounds on the sampling complexity and error probability, as well as the complexity measures, we now turn to sampling strategies that are designed to match these lower bounds.
 
 ### Matching algorithm strategies
-
-Given these lower bounds, all that is left is to find algorithms which are able to match the complexity. Sadly, not straightforward for Bernoullis.
 
@@
 They do consider algorithms that connect to Theorem \ref{theorem:KaufmannEtAlTheorem4} and Theorem \ref{theorem:KaufmannEtAlTheorem12}.
-
-Given that Locatelli et al.
-(2016), and thus the problem we mostly consider in this thesis, is in the fixed-budget setting, we are most interested in the matching strategies for Theorem \ref{theorem:KaufmannEtAlTheorem12}.
-However, given that the lower bound applies only to two-armed bandits, the algorithms are of limited practical interest.
-Furthermore, the algorithms proposed require knowledge that is in general not available upfront.
-
-For the example of Gaussian distributions, the knowledge of the (potentially different) variance is assumed which enables a strategy that pulls each arm proportional to its variance.
-
-Even worse is the case of Bernoulli two-armed bandit models where the proposed algorithm requires knowledge about the true parameters of the distributions.
+Given that we aim to extend the fixed budget thresholding bandit problem, we are most interested in the matching strategies for Theorem \ref{theorem:KaufmannEtAlTheorem12}.
+However, given that this lower bound applies only to two-armed bandits, the algorithms proposed by Kaufmann et al.
+(2016) are of limited practical interest.
+Furthermore, the proposed strategies require knowledge that is in general not available upfront: For Gaussian distributions, the knowledge of the (potentially different) variance is assumed which enables a strategy that pulls each arm proportional to its variance.
+
+Even more difficult are the assumptions in the case of Bernoulli two-armed bandit models: The proposed algorithm requires knowledge about the true parameters of the distributions.
 That this limits the practical interest is also noted by the authors of Kaufmann et al.
@@
 (2016) join a number of other papers like Audibert et al.
-(2010) and Kaufmann and Kalyanakrishnan (2013) which struggle to find matching strategies in the fixed-budget setting that do not rely on knowledge of parameters or the complexity of the problem.
+(2010) and Kaufmann and Kalyanakrishnan (2013) which struggle to find matching strategies in the fixed budget setting that do not rely on knowledge of parameters or the complexity of the problem.
 
 In contrast, Kaufmann et al.
-(2016) are able to show that their complexity measure derived for the fixed-confidence setting, $\kappa_C(\nu)$, can be upper-bounded using the upper bound of the sample complexity (number of pulls) given for the KL-LUCB algorithm in Kaufmann and Kalyanakrishnan (2013).
+(2016) are able to show that their complexity measure derived for the fixed confidence setting, $\kappa_C(\nu)$, can be upper-bounded using the upper bound given for the KL-LUCB algorithm in Kaufmann and Kalyanakrishnan (2013).
 Consequently, in the case of exponential family bandits, the complexity $\kappa_C(\nu)$ is bounded as given in equation (6) in Kaufmann et al.
@@
 
-## Optimal Best Arm Identification
-
-A very similar application of the KL divergence has been given in Garivier and Kaufmann (2016) to derive a lower bound on the sample complexity in the case of best arm identification.
-In particular, the transportation Lemma 1 is used again.
-And a matching algorithm for $K \geq 2$ arms is proposed.
-
-Talk about:
-- Not a simple sum of squares
-- Idea of algorithm: Equalize the probability of all wrong decisions
-
-In Garivier and Kaufmann (2016), the authors are able to derive a somewhat similar lower bound on the sample complexity of a $K$-armed bandit in the single best arm identification problem with fixed confidence.
-Additionally, they provide a $\delta$-PAC algorithm achieving said bound asymptotically.
-
-In particular, the authors pick up Lemma 1 from Kaufmann et al.
-(2016) -- which we discussed above -- to derive the lower bound.
-While presenting these results, we try to stick as much as possible with the notation used so far.
-In particular, we let for distributions $\nu_{\theta}$ from a canonical exponential family, which can be parameterized by its mean $\stackrel{.}{b}(\theta) = \mu$ and thus be written as $\nu^{\mu}$; for these, we continue to write the Kullback-Leibler divergence as
-
-\begin{equation*}
-\KL(\mu, \mu') = \KL(\nu^{\mu},\nu^{\mu'}) = \KL(\nu_{\theta},\nu_{\theta'}) = \KL(\nu, \nu')
-\end{equation*}
-
-while $d(x,y)$ continues to represent the binary relative entropy.
-
-As we will consider only problems with exponential family distributions, the distributions can be parameterized by their means.
-Therefore, if we let $\mathcal{S}$ to be a set of bandit models with $K$ distributions each, then each model is fully defined by a vector $\bm{\mu} = (\mu_1, \dots, \mu_K)$.
+## Optimal Best Arm Identification \label{sec:OptimalBestArmIdentification}
+
+Instead of discussing the KL-LUCB algorithm for the fixed confidence top-$m$ problem, we shift our focus slightly onto the fixed confidence best arm identification problem, which is discussed in Garivier and Kaufmann (2016).
+The authors derive again a lower bound on the sample complexity using again the Lemma \autoref{theorem:KaufmannEtAlLemma1}.
+Furthermore, they propose a matching strategy for $K \geq 2$ arms.
+
+The setting differs slightly from the setting considered in Kaufmann et al.
+(2016).
+In particular, Garivier and Kaufmann (2016) focus on distributions $\nu_{\theta}$ from the univariate canonical exponential family of distributions, which can be parameterized by their mean $\stackrel{.}{b}(\theta) = \mu$, and thus can be written as $\nu^{\mu}$; for these, we write the Kullback-Leibler divergence as (compare \autoref{sec:LRforUnivariateExponentialFamily} and Cappé et al., 2013)
+
+\begin{equation*}
+\KL(\mu, \mu') = \KL(\nu_{\mu},\nu_{\mu'}) = \KL(\nu_{\theta},\nu_{\theta'}) = \KL(\nu, \nu').
+\end{equation*}
+
+Furthermore, if we let $\mathcal{S}$ to be a set of bandit models with $K$ distributions each, then each model is fully defined by a vector $\bm{\mu} = (\mu_1, \dots, \mu_K)$.
 Assume that every $\bm{\mu} \in \mathcal{S}$ has a unique maximum given by $a^*(\bm{\mu})$ such that $\mu_{a^*} > \max_{a \neq a^*(\bm{\mu})} \mu_a$.
 In order to fix the confidence, we specify the risk $\delta$.
-The strategies corresponding to this risk are called $\delta$-PAC if for every $\bm{\mu} \in \mathcal{S}$, $\mathbb{P}_{\bm{\mu}}(\tau_{\delta} < \infty) = 1$ (the strategy ends surely after a finite number of samples) and $\mathbb{P}_{\bm{\mu}}(\hat{a}_{\tau_{\delta}} \neq a^*) \leq \delta$ (the probability of picking not the optimal arm is smaller than the fixed risk).
-As in Garivier and Kaufmann (2016), we introduce the set of problems for which the optimal arm is different from the one in $\bm{\mu}$:
+Similar to the top-$m$ case considered before, strategies corresponding to this risk are called $\delta$-PAC if for every $\bm{\mu} \in \mathcal{S}$, the strategy ends surely after a finite number of samples, $\mathbb{P}_{\bm{\mu}}(T_{\delta} < \infty) = 1$, and the error probability is at least as small as the fixed risk level, $\mathbb{P}_{\bm{\mu}}(\hat{a}_{T_{\delta}} \neq a^*) \leq \delta$.
+In order to derive the lower bound on the expected number of samples $\mathbb{E}[T]$ through a change in distributions, we introduce the set of problems for which the optimal arm is different from $\bm{\mu}$:
 
@@
 where $\bm{\lambda}$ is the vector of means defining the distributions of the alternative problem to $\bm{\mu}$.
-Lastly, we have the set of probability distributions on the arms $\mathcal{A}$: $\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}$.
-We are now ready to state the theorem.
+Lastly, we have the set of probability distributions on the arms $\{1,...,K\}$: $\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}$.
+Each $w_i$ corresponds to the fraction of overall samples that the arm $i$ receives.
+We are now ready to state the lower bound:
 
@@
 \begin{equation*}
-\mathbb{E}_{\bm{\mu}} [\tau_{\delta}] \geq T^*(\bm{\mu}) \text{\em{d}}(\delta,1-\delta),
+\mathbb{E}_{\bm{\mu}} [T_{\delta}] \geq T^*(\bm{\mu}) \text{\em{d}}(\delta,1-\delta),
 \end{equation*}
@@
 
-And so we see that the two bounds on the sample complexity (one for Top-$m$, one for best arm identification) differ only in the way that they build the sum of Kullback-Leibler divergences over the $K$ arms.
+We see that the two bounds on the sample complexity (one for Top-$m$, one for best arm identification) differ only in the way in which they build the sum of Kullback-Leibler divergences over the $K$ arms.
 In contrast to Theorem \ref{theorem:KaufmannEtAlTheorem4}, here the contribution of each arm through its KL-divergence is weighted.
-The difference is that while we were able to very clearly describe the change of distribution in the Top-$m$ case for each arm -- for each arm, we specified an alternative model that yields a new set of $m$ optimal arms -- we now consider all alternative models that yield a different best arm than the model $\bm{\mu}$.
+The difference is that while we were able to very clearly describe the change of distribution in the Top-$m$ case for each arm -- we specified an alternative model for each arm that yields a new set of $m$ optimal arms -- we now consider all alternative models that yield a different best arm than the model $\bm{\mu}$.
 In the previous theorem, we sum over the complexity of each individual arm, as the change in distribution only ever touches one arm, thus leading to a KL-divergence of 0 for the other arms while still changing the optimal set.
@@
 As before, $N_a(t)$ describes the random number of pulls of arm $a$ until time $t$, for all $t\geq 1$.
-Again, Lemma \ref{theorem:KaufmannEtAlLemma1} states how the failure probability $\delta$ relates to the expected number of draws of each arm given two models which differ in their optimal arm, and where it is evaluated based on the Kullback-Leibler divergence for each pair of arms how much the two models differ:
-
-\begin{equation*}
-\forall \lambda \in \mathcal{S}: a^*(\lambda) \neq a^*(\mu), \sum_{a=1}^K \KL(\mu_a,\lambda_a)\mathbb{E}_{\bm{\mu}}[N_a(\tau_{\delta})] \geq \d(\delta, 1- \delta).
+Again, Lemma \ref{theorem:KaufmannEtAlLemma1} states how the risk $\delta$ relates to the expected number of draws of each arm given two models which differ in their optimal arm.
+How much the two models differ is evaluated based on the Kullback-Leibler divergence for each pair of arms:
+
+\begin{equation*}
+\forall \lambda \in \mathcal{S}: a^*(\lambda) \neq a^*(\mu), \sum_{a=1}^K \KL(\mu_a,\lambda_a)\mathbb{E}_{\bm{\mu}}[N_a(T_{\delta})] \geq \d(\delta, 1- \delta).
 \end{equation*}
@@
 Thus, to make the lower bound practical, it is a matter of finding the optimal weights $w^*(\bm{\mu})$.
-This step did not occur in the previous lower bound, as the alternative models were made specific by changing the distribution of one arm with respect to the "border" between the two groups of arms.
-
-In any case, the existence of the optimal weights suggests an algorithm that keeps track of the share of samples that is attributed to each arm and makes sure that it stays close to the optimum until some decision rule assures that the $\delta$-PAC condition is fulfilled.
-
-Indeed, the optimal weights will lead to a sampling structure in which arms are drawn in such a way ensuring that their individual failure probabilities are at the same level.
-Take a situation where the currently best arm $\hat{\mu}_1$ is the best arm.
-Then, we calculate for each arm the risk that actually it is better than arm 1.
-Since the arms are assumed to be independent, the we only have to compare every arm individually to arm 1.
-Given that, it makes sense that we don't want to disregard an arm that has a high probability of being better than arm 1.
-Assuming arm 1 is actually the best arm, we would an algorithm that ensures a low failure probability on all arms, thus equalizing the failure probability for every arm compared to arm 1.
+This step did not occur in the lower bound for the top-$m$ problem since the alternative models were specified by changing the distribution of one arm with respect to the "border" between the two groups of arms.
+
+The existence of the optimal weights suggests an algorithm that keeps track of the share of samples that is attributed to each arm and makes sure that it stays close to the optimum until some decision rule assures that the $\delta$-PAC condition is fulfilled.
+
+Indeed, the optimal weights will lead to a sampling structure in which arms are drawn in a way that ensures that their individual probability of error stays at the same level.
+An arm more distant from the optimal arm in terms of Kullback-Leibler divergence should receive a smaller share of the samples to achieve the same error probability as an arm closer to the optimal arm.
 
 This is exactly what happens when we look for the proportions $w \in \Sigma_K$ that minimize the cost from a change in distributions, that is, the term $F(\bm{\mu}, \bm{w}) = \inf_{\bm{\lambda} \in \text{Alt}(\bm{\mu})} \Big(\sum_{a= 1}^K w_a \KL(\mu_a, \lambda_a)\Big)$.
-In the proof of Lemma 3 of Garivier and Kaufmann, it is shown that nature, selecting the alternative model $bm{\lambda}$ will always pick an alternative model in which only a single arm $a$ is changed such that $\lambda_a > \lambda_1$ since
+In the proof of Lemma 3 of Garivier and Kaufmann, it is shown that nature, selecting the alternative model $\bm{\lambda}$ will always pick an alternative model in which only a single arm $a$ is changed such that $\lambda_a > \lambda_1$ since
 
@@
 And so by assuring the reader that there are ways to compute $w_a^*$ and $T^*$ given $\bm{\mu}$ (see chapter 2.2 in Garivier and Kaufmann (2016)), we can now introduce the *Track-and-Stop* strategy given in Garivier and Kaufmann (2016) that is able to match the lower bound by the intuition given above.
+The main idea of the *Track-and-Stop* algorithm is now to keep track of the optimal shares for each arm by equalizing the error probabilies for each arm.
 
@@
 
-A very intuitive fix to this problem is the solution proposed in Lemma 8 of Garivier and Kaufmann (2016), with their $D-Tracking$ rule.
-Basically, whenever an arm has received a very low number of pulls $N_a(t)$ given the number of iterations so far, $t$ and the number of arms $K$ that have to share the samples, pull the arm that has received the smallest amount of samples so far.
+A very intuitive fix to this problem is the solution proposed in Lemma 8 of Garivier and Kaufmann (2016) with their $D-Tracking$ rule.
+Whenever an arm has received a very low number of pulls $N_a(t)$ given the number of iterations so far, $t$, and the number of arms $K$ that have to share the samples, pull the arm that has received the smallest amount of samples so far.
 Else, pull the arm which number of pulls so far $N_a(t)$ is the furthest away from what its optimal share $t\cdot w^*_a(\hat{\bm{\mu}}(t))$ would be.
@@
 
-When combining this sampling rule with an appropriate stopping rule, the authors are able to prove in Theorem 14 an upper bound on the expected sampling complexity $\mathbb{E}_{\mu}[\tau_{\delta}]$.
+When combining this sampling rule with an appropriate stopping rule, the authors are able to prove in Theorem 14 an upper bound on the expected sampling complexity $\mathbb{E}_{\mu}[T_{\delta}]$.
 The stopping rule ensures that the algorithm explores sufficiently to promise a risk smaller than $\delta$, while stopping as soon as possible.
 Given that the sampling rule is independent of this stopping rule, the rule boils down to a statistical test at every iteration and thus is a sequential test based on the current estimate of $\hat{\bm{\mu}}$.
-The Chernoff's Stopping Rule proposed in Garivier and Kaufmann (2016) calculates for each arm $a\in \mathcal{A}$ the Generalized Likelihood Ratio statistic with every arm $b \in \mathcal{A}^{\setminus a}$, which for $\hat{\mu}_a(t) \geq \hat{\mu}_b(t)$ can be written as
+The Chernoff's Stopping Rule proposed in Garivier and Kaufmann (2016) calculates for each arm $a\in \{1,...K\}$ the Generalized Likelihood Ratio statistic with every arm $b \in \mathcal{A}^{\setminus a}$, which for $\hat{\mu}_a(t) \geq \hat{\mu}_b(t)$ can be written as
 
@@
 
-Consequently, a sensible idea for a stopping rule would be that there has to be an arm $a \in \mathcal{A}$ for which $Z_{a,b} \geq 0 \forall b \in \mathcal{A}^{\setminus a}$ (which is always fulfilled if there is a uniquely best arm), and, additionally, we demand that for this arm the smallest of the $(K-1)$ test statistics has to be larger than an exploration threshold $\beta(t, \delta)$.
-Consequently, the final number of samples $\tau_{\delta}$ of an algorithm is given by:
-
-\begin{equation*}
-\tau_{\delta} = \inf \{t \in \mathbb{N}: \exists a \in \mathcal{A}, \forall b\in \mathcal{A}^{\setminus a}, Z_{a,b}(t) > \beta(t, \delta)\}
+Consequently, a sensible idea for a stopping rule would be that there has to be an arm $a \in \{1,...,K\}$ for which $Z_{a,b} \geq 0 \, \forall  b \in \{1,...,K\}^{\setminus a}$ (which is always fulfilled if there is a uniquely best arm), and, additionally, we demand that for this arm the smallest of the $(K-1)$ test statistics has to be larger than an exploration threshold $\beta(t, \delta)$.
+Consequently, the final number of samples $T_{\delta}$ of an algorithm is given by:
+
+\begin{equation*}
+T_{\delta} = \inf \{t \in \mathbb{N}: \exists a \in \mathcal{A}, \forall b\in \mathcal{A}^{\setminus a}, Z_{a,b}(t) > \beta(t, \delta)\}
 \end{equation*}
@@
 Let $\alpha \in [1, e/2]$ and $r(t) = O(t^{\alpha})$.
-Using Chernoff's stopping rule with $\beta(t,\delta) = \log(r(t)/\delta)$ and the sampling rule C-Tracking or D-Tracking,
-
-\begin{equation*}
-\lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\bm{\mu}}[\tau_{\delta}]}{\log(1/\delta)} \leq \alpha T^*(\mu).
+Using Chernoff's stopping rule with $\beta(t,\delta) = \log(r(t)/\delta)$ and the sampling rule D-Tracking,
+
+\begin{equation*}
+\lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\bm{\mu}}[T_{\delta}]}{\log(1/\delta)} \leq \alpha T^*(\mu).
 \end{equation*}
@@
 Their contribution is primarily based on including the Kullback-Leibler divergence in the derivation of bounds and the matching algorithms and thus going beyond a sum of squared gaps which is most practical only in the case of Gaussian distributions.
-While the contribution in the fixed-budget setting was limited to the two-armed bandit case, the authors derive general lower bounds in the fixed-confidence setting which are primarily based on Lemma \ref{theorem:KaufmannEtAlLemma1}.
+While the contribution in the fixed budget setting was limited to the two-armed bandit case, the authors derive general lower bounds in the fixed confidence setting which are primarily based on Lemma \ref{theorem:KaufmannEtAlLemma1}.
 Lemma \ref{theorem:KaufmannEtAlLemma1} is able to measure the "transportation cost" (see Garivier and Kaufmann, 2016) of moving from one distribution to another one in terms of Kullback-Leibler divergence.
@@
   \emph{Pull arm $I_t = \arg \min_{i\leq K} B_i^{SLR}(t)$ as in \autoref{eqn:SLRIndex}}\;
-  \emph{Observe reward $X \sim \nu_{I_t}$}\;
+  \emph{Observe reward $X_t \sim \nu_{I_t}$}\;
 }
@@
   \emph{Pull arm $I_t = \arg \min_{i\leq K} B_i^{SLR_{2D}}(t)$ as in \autoref{eqn:SLR2DIndex}}\;
-  \emph{Observe reward $X \sim \nu_{I_t}$}\;
+  \emph{Observe reward $X_t \sim \nu_{I_t}$}\;
 }
@@
 
+We show empirically that part of this problem can be alleviated by including the D-Tracking rule proposed by Garivier and Kaufmann (2016) and discussed in \autoref{sec:OptimalBestArmIdentification} into the SLR algorithm.
+
 While the Bayes-UCB performance is impressive, we observe that also the Simple Likelihood Ratio strategy improves considerably upon the alternative strategies.
@@
 load(paste0(current_path, "loc6nt_comp_LR_7000.Rda"))
+load(paste0(current_path, "loc6nt_comp_LRD.Rda"))
 load(paste0(current_path, "loc6nt_comp_EVT.Rda"))
 
-alg_names <- c(rep(c("Uniform", "APT", "AugUCB","SLR", "B-UCB"), 
+alg_names <- c(rep(c("Uniform", "APT", "AugUCB","SLR", "SLR-D", "B-UCB"), 
                    each = 6991), rep("EVT", 6981))
-index <- c(rep(10:7000, times = 5), 20:7000)
+index <- c(rep(10:7000, times = 6), 20:7000)
 alg_res <- log(c(loc6nt_comp_UNIFORM_7000, loc6nt_comp_APT_7000,
                  loc6nt_comp_AugUCB_7000, loc6nt_comp_LR_7000,
+                 loc6nt_comp_LRD,
                  loc6nt_comp_BUCB_horizon_7000, loc6nt_comp_EVT))
@@
 load(file = paste0(current_path, "loc7nt_comp_LR_10000.Rda"))
+load(file = paste0(current_path, "loc7nt_comp_LRD_10000.Rda"))
 load(file = paste0(current_path, "loc7nt_comp_BUCB_horizon_10000.Rda"))
@@
 
-alg_names <- c(rep(c("Uniform", "APT", "AugUCB", "SLR", "B-UCB"), 
+alg_names <- c(rep(c("Uniform", "APT", "AugUCB", "SLR", "SLR-D", "B-UCB"), 
                    each = 9990), rep("EVT", times = 9979))
-index <- c(rep(11:10000, times = 5), 22:10000)
+index <- c(rep(11:10000, times = 6), 22:10000)
 alg_res <- log(c(loc7nt_comp_UNIFORM_10000, loc7nt_comp_APT_10000,
                  loc7nt_comp_AugUCB_10000, loc7nt_comp_LR_10000,
+                 loc7nt_comp_LRD_10000,
                  loc7nt_comp_BUCB_horizon_10000, loc7nt_comp_EVT))
@@
 \end{align*}
+
+## Lower Bound on Probability of Error in FB-Top-$m$ with Gaussian Arms \label{sec:KaufmannLBTopMGaussian}
+
+While we would like to move beyond Gaussian distributions in the work at hand, the idea for the proof might show a way of how the ideas can be transferred to the thresholding bandit problem.
+We first state the result and then discuss the proof.
+
+\begin{lemma}[Lemma 15, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma15}
+Let $\nu$ and $\nu'$ be two bandit models such that $S^*_m(\nu) \neq S^*_m(\nu')$. Then
+
+\begin{equation*}
+\max \big( \mathbb{P}_{\nu}(S \neq S^*_m(\nu)), \mathbb{P}_{\nu'}(S \neq S^*_m(\nu')) \big) \geq \frac{1}{4} \exp \Big(-\sum_{a=1}^{K} \mathbb{E}_{\nu}[N_a] \KL(\nu_a, \nu_a') \Big).
+\end{equation*}
+\end{lemma}
+
+The following theorem only holds in the case of Gaussian bandit models with equal known variance.
+
+\begin{theorem}[Theorem 17, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem17}
+
+Let $\mathcal{M}_m = \{\nu = (\nu_1, \dots, \nu_K): \nu_a = \mathcal{N}(\mu_a, \sigma^2), \mu_a \in \mathbb{R}, \mu_{[m]}\neq \mu_{[m+1]}\}.$ Furthermore, let $\nu$ be such that $\mu_1 > \dots > \mu_m > \mu_{m+1} > \dots > \mu_K$, and let
+
+\begin{equation*}
+H^+(\nu) = \sum_{a=1}^m \frac{2\sigma^2}{(\mu_a - \mu_{m+1})^2}, \quad H^-(\nu) = \sum_{a=m+1}^K \frac{2\sigma^2}{(\mu_m - \mu_a)^2} \quad
+and \quad
+H(\nu) = H^+(\nu) + H^-(\nu).
+\end{equation*}
+
+There exists $a \in \{1, \dots, m\}$ and $b \in \{m+1, \dots, K\}$ such that the bandit model $\nu^{[a,b]}$ described in Figure 4 (Kaufmann et al., 2016) satisfies $H(\nu^{[a,b]}) < H(\nu)$ and is such that
+
+\begin{equation*}
+\max \big( p_t(\nu),p_t(\nu^{[a,b]})\big) \geq \frac{1}{4} \exp \big(-\frac{4t}{\bar{H}(\nu)}\big), \quad where \quad \bar{H}(\nu) = \frac{H(\nu) \min(H^+(\nu),H^-(\nu))}{H(\nu)+\min(H^+(\nu),H^-(\nu))}
+\end{equation*}
+\end{theorem}
+
+Given that we are again in the Top-$m$ setting, the proof idea is similar to the proof of Theorem \ref{theorem:KaufmannEtAlTheorem4} in that we again consider problems in which we switch arms around the threshold implied by $\mu_{[m]}$ and $\mu_{[m+1]}$.
+Given that, one might hope to apply a similar proof to the thresholding bandit problem.
+As we see in \autoref{sec:AppendixAPTLB}, a flip around the threshold is used in the proof of the lower bound in Theorem 1 of Locatelli et al.
+(2016).
+However, there, again, the distributions are assumed to be Gaussian.
+This brings the big advantage that the Kullback-Leibler divergence is symmetric, and the feedback can take values on all $\mathbb{R}$.
+This is important, as is allows us to easily define alternative problems by a flip around the threshold with the same complexity as the original problem.
+This would not hold for KL-divergences that are not symmetric (e.g., for Bernoulli arms).
+For the full proof, refer to page 20 in Kaufmann et al.
+(2016).
+
+## Proof of Corollary 1
+
+**Proof**: The proof follows closely the proof of Theorem 12 in Kaufmann et al. (2016) and is again an application of their transportation Lemma, Lemma 2.
+
+Consider the one-armed bandit problem, $K = 1$ with the canonical exponential family of distributions distribution $\nu_1$ parameterized by its mean $\mu_1$.
+Furthermore, given we are in the thresholding bandit problem, we have a threshold $\tau$ against which the arm is classified.
+Assume w.l.o.g.
+that for $\nu_1$, $\mu_1 \geq \tau$.
+Thus, $\mathcal{S}_{\tau}^* = \{1\}$.
+After $T$ rounds, a consistent algorithm returns with error probability $p_T(\nu)$ the guess $\hat{\mathcal{S}}_{\tau}$.
+Thus, we have for the event $A = (\hat{\mathcal{S}}_\tau = \{1\})$ the probability $\mathbb{P}_{\nu}(A)$.
+On the other hand, define the alternative model $\nu'$ with mean $\mu_1' < \tau$ such that the correct classification from $\nu$ is now wrong: $\mathcal{S}_{\tau}^* {'} = (\mathcal{S}_{\tau}^*)^C = \{\emptyset\}$.
+Consequently, since the algorithm is still consistent on this problem, we have that $\mathbb{P}_{\nu'}(A) = p_t(\nu')$.
+Thus, we expect that as we let $t$ increase, $\mathbb{P}_{\nu'}(A)$ will decrease while $\mathbb{P}_{\nu}(A)$ will increase.
+
+Indeed, given we consider only consistent algorithms, there should exist a number of samples for which the probability of the correct decision in problem $\nu$ is larger than the error probability in problem $\nu'$, that is: for every $\epsilon > 0$, there exists $t_0(\epsilon)$ such that for all $t \geq t_0(\epsilon)$ we have
+
+\begin{equation}
+\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_{\nu}(A). \label{eq:BoundForCorollary}
+\end{equation}
+
+Now, consider again Lemma 2 in Kaufmann et al. (2016). If we let the algorithm be such that $T = t$, we can apply the Lemma to the stopping time $\sigma = t$ a.s. and the event $A$ to get
+
+$$
+\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)).
+$$
+
+We can lower bound the RHS by using the bound on $\mathbb{P}_{\nu'}(A)$ given in \eqref{eq:BoundForCorollary} and the monotonicity of the binary relative entropy. We get:
+
+\begin{align*}
+\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) & = t \KL(\nu_1', \nu_1) \\
+& \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)) \\
+& \geq d(\epsilon, 1- p_t(\nu)) \\
+& = \epsilon \log\Big(\frac{\epsilon}{1-p_t(\nu)}\Big) + (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) \\
+& \geq (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) + \epsilon \log(\epsilon) \\
+\end{align*}
+
+Letting $\epsilon \rightarrow 0$, we get
+
+$$
+t \KL(\nu_1', \nu_1) \geq \log \Big(\frac{1}{p_t(\nu)}\Big) = -\log p_t(\nu).
+$$
+To make the bound as tight as possible, we choose the alternative model that minimizes $\KL(\nu_1', \nu_1)$ while still ensuring that $\mathcal{S}_{\tau}^* {'} = \{\emptyset\}$.
+In our case of the thresholding bandit with univariate exponential family distributions, this is given by choosing $\mu_1' = \tau$.
+By pluggin in, we get the result:
+
+$$
+t \KL(\tau, \mu_1) \geq -\log p_t(\nu).
+$$
 
@@
 cbind.data.frame(
-  Arm = rep(c("01", "10"), each = 15000),
+  Arm = rep(c("01", "10"), each = 20000),
   rbind.data.frame(pulls_arm_1_long, pulls_arm_10_long),

### 2017-09-03 Thesis/Draft.tex
Add corollary for lower bound

@@
 \newtheorem{lemma}{Lemma}
+\newtheorem{corollary}{Corollary}
 \newcommand{\KL}{\,\text{KL}}
@@
 more popular among the best arm identification and top-\(m\) literature.
-This setting is called \emph{fixed-confidence}, while the setting we
-considered so far is called \emph{fixed-budget}. In the fixed-budget
+This setting is called \emph{fixed confidence}, while the setting we
+considered so far is called \emph{fixed budget}. In the fixed budget
 setting, we run algorithms for \(T\) samples and then compare them based
@@
 strategy has to achieve this level of confidence in its prediction
-before it is allowed to stop sampling. This is the fixed-confidence
+before it is allowed to stop sampling. This is the fixed confidence
 case, in which the budget \(T\) is no longer fixed upfront, but becomes
@@
 
-To prove this statement, we assume as before that the arms are ordered
-by their means decreasing in size. For a given \(\delta\)-PAC algorithm
-\(\mathcal{A} = ((A_t), \tau, \hat{S}_m)\), and under the continuity
-conditions (compare Kaufmann et al. (2016)), there exists for every arm
+To prove this statement for a given \(\delta\)-PAC algorithm
+\(\mathcal{A}\), we assume certain continuity conditions (compare
+Kaufmann et al. (2016)), with which there exists for every arm
 \(a \in \{1, \dots, K\}\) an alternative model
 \(\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)\).
-In this alternative model, only arm \(a\) is modified in accordance with
-the continuity conditions. Modified in such a way, the arm \(\nu_{m+1}\)
-is now closer to \(\nu_a\) as measured by the Kullback-Leibler
-divergence than \(\nu_a'\) is to \(\nu_a\), if \(\mu_a > \mu_{m+1}\)
-(consequently, \(\mu_a' < \mu_{m+1}\)). On the other hand, if
-\(\mu_a < \mu_{m}\), then \(\nu_a'\) will be moved away from \(\nu_a\)
-just enough so that \(\nu_a\) is closer to \(\nu_m\) than to \(\nu_a'\)
-(consequently, \(\mu_a' > \mu_m\)). These changes in distribution make
-the original set of optimal arms, \(\{1,\dots,m\}\), no longer optimal
-under the alternative model \(\nu'\). Given that the algorithm returns
-\(\hat{S}_m\), we know that for the event
-\(\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})\) (which is element of the
-\(\sigma\)-Algebra \(\mathcal{F}_{\tau}\) induced by the stopping time
-\(\tau\)), that \(\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta\) and
+In this alternative model, in accordance with the continuity conditions,
+only arm \(a\) is modified. After the modification, the arm
+\(\nu_{m+1}\) is now closer to \(\nu_a\) as measured by the
+Kullback-Leibler divergence than \(\nu_a'\) is to \(\nu_a\), if
+\(\mu_a > \mu_{m+1}\) (consequently, \(\mu_a' < \mu_{m+1}\)). On the
+other hand, if \(\mu_a < \mu_{m}\), then \(\nu_a'\) will be moved away
+from \(\nu_a\) just enough so that \(\nu_a\) is closer to \(\nu_m\) than
+to \(\nu_a'\) (consequently, \(\mu_a' > \mu_m\)). These changes in
+distribution make the original set of optimal arms, \(\{1,\dots,m\}\),
+no longer optimal under the alternative model \(\nu'\). To compare this
+to the thresholding bandit problem, assume that arms \(\nu_{m}\) and
+\(\nu_{m+1}\) indirectly define a threshold
+\(\tau \in (\mu_{m+1},\mu_m)\). Then, by creating an alternative problem
+as described here, we flip arm \(a\) around the implied threshold
+\(\tau\) (compare the lower bound proof in \autoref{sec:AppendixAPTLB}).
+
+Given that the strategy returns \(\hat{S}_m\), we know that for the
+event \(\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})\) (which is element
+of the \(\sigma\)-Algebra \(\mathcal{F}_{T}\) induced by the stopping
+time \(T\)), that \(\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta\) and
 \(\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta\) (because fixed confidence
-\(\delta\)!).
-
-To now give the lower bound on the expected number of samples,
-\(\mathbb{E}_{\nu}[\tau]\), we employ the general Lemma given by the
-authors for such changes in distribution in bandit models.
+\(\delta\)!). To now give the lower bound on the expected number of
+samples, \(\mathbb{E}_{\nu}[\tau]\), we employ the general Lemma given
+by the authors for such changes in distribution in bandit models.
 
@@
 \begin{equation*}
-\mathbb{E}_{\nu}[\tau] = \sum_{a=1}^K \mathbb{E}_{\nu}[N_a] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \der(1-\delta, \delta)
+\mathbb{E}_{\nu}[T] = \sum_{a=1}^K \mathbb{E}_{\nu}[N_a] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \der(1-\delta, \delta)
 \end{equation*}
@@
 either close to 0 or 1, it is possible to use the following
-approximation to the binary relative entropy:
+approximation to the binary relative entropy given in Kaufmann et al.
+(2016):
 
 \begin{equation}\label{bre_approx}
-\forall x \in [0,1], \quad \der(x,1-x) = \der(1-x,x) \geq \log \frac{1}{2.4x}
+\forall x \in [0,1], \quad \der(x,1-x) = \der(1-x,x) \geq \log \frac{1}{2.4x}.
 \end{equation}
 
-And so the final lower bound can be written as
+This allows us to write the lower bound on the expected stopping time
+as:
 
 \begin{equation*}
-\mathbb{E}_{\nu}[\tau] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
+\mathbb{E}_{\nu}[T] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
 \end{equation*}
 
-\includegraphics{Draft_files/figure-latex/unnamed-chunk-1-1.pdf}
-
-Given this general lower bound for the sampling complexity, or expected
-number of draws, it makes sense to define the complexity of a Top-\(m\)
-bandit problem using the Kullback-Leibler divergence. After all, besides
-the number of arms and the experimenter-chosen confidence, it is just
-how close arms are with respect to each other in terms of
-Kullback-Leibler divergence that influences the sampling complexity.
-
-Thus, following Kaufmann et al. (2016), define the complexity
+Given this lower bound, it becomes clear that the complexity of the
+top-\(m\) problem can be lower bounded by the Kullback-Leibler
+divergence between arms and the implied threshold between the \(m\)-th
+best arm and the \((m+1)\)-th best arm. After all, the latter gives a
+lower bound on the effort (in terms of expected number of samples)
+required to achieve a certain confidence level. And a problem that
+requires a larger effort can be described as more complex. Indeed, in
+the case of fixed confidence problems, Kaufmann et al. (2016) describe
+problems as having a larger \emph{sampling complexity}.
+
+Following Kaufmann et al. (2016), we can now define the complexity
 \(\kappa_C(\nu)\) for the fixed confidence setting as
@@
 \begin{equation}
-\kappa_C(\nu) = \inf_{A \, \text{PAC}} \lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\nu}[\tau_{\delta}]}{\log \frac{1}{\delta}}.
+\kappa_C(\nu) = \inf_{A \, \text{PAC}} \lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\nu}[T{\delta}]}{\log \frac{1}{\delta}}. \label{eq:KappaC}
 \end{equation}
 
-By plugging in the lower bound on the sampling complexity, we arrive at
-a complexity measure that depends only on the Kullback-Leibler measuring
-for each arm how far it is away from the border between the two groups
-of arms. To see this, consider the lower bound on the complexity measure
-given in Kaufmann et al. (2016):
+This definition makes sense if we consider the fact that the confidence
+level \(\delta\) is experimenter chosen and thus not relevant in
+describing the complexity. Thus, by including \(\log(1/\delta)\)
+explicitly in \eqref{eq:KappaC}, we get rid of the confidence term in
+the lower bound on \(\mathbb{E}_{\nu}[T]\) after plugging it into
+\eqref{eq:KappaC}. We arrive at the lower bound on the complexity
+measure given in Kaufmann et al. (2016):
 
@@
 
-Given this description, we can already note that an intuitive extension
-of this complexity notion to the thresholding bandit problem might
-involve replacing \(\mu_{[m]}\) and \(\mu_{[m+1]}\) by the actual
-threshold \(\tau\) (notation in Locatelli et al.) that divides the group
-above the threshold from the group below the threshold. In this sense,
-the previously used \(\alpha\) is similar to the \(\epsilon\) used in
-Locatelli et al. (2016).
-
-Before we get to an extension of the thresholding bandit problem,
-however, at least two important steps remain. First, we need to define a
-complexity for the fixed budget problem. Second, we need to create
-algorithms that can match the lower bound.
-
-Kaufmann et al. are able to provide a bound on their complexity measure
-in the fixed budget case, however only in the case of \textbf{two-armed}
-bandit models. As demanded in their paper, a fixed-budget algorithm is
-called consistent if the failure probability
-\(p_t(\nu) := \mathbb{P}_{\nu}(\hat{S}_m \neq S^*_m)\) tends to zero as
-the number of samples goes to infinity. Also, define the complexity in
-the fixed-budget setting as follows:
+Given this description, we would expect that a complexity measure in a
+fixed confidence thresholding bandit probem might involve replacing
+\(\mu_{[m]}\) and \(\mu_{[m+1]}\) by the actual threshold \(\tau\) that
+divides the group above the threshold from the group below the
+threshold.
+
+However, given the problem formulation in Locatelli et al. (2016), we
+are mainly interested in complexity measures and algorithms for the
+fixed budget setting. As we will see now, the results of Kaufmann et al.
+(2016) are more limited for this case. While the authors are able to
+provide a bound on their complexity measure in the fixed budget case, it
+only applies to the case of \emph{two-armed} bandit models. Consider a
+consistent fixed budget strategy \(\mathcal{A}\) (\(p_t(\nu)\) tends to
+zero as \(t \rightarrow \infty\)), and define the complexity in the
+fixed budget setting as follows:
 
@@
 
-Given this definition, one can interpret the bound given in Theorem 12
-of Kaufmann et al. directly as a lower bound on the complexity
-\(\kappa_B(\nu)\) (note the inverse).
+While we included the experimenter-fixed \(\delta\) in the definition of
+\(\kappa_C\), we now include the experimenter-fixed \(T\) in the
+definition of \(\kappa_B\) to disregard it in the complexity measure
+after plugging in the lower bound on \(p_t(\nu)\). The resulting lower
+bound given in Theorem 12 of Kaufmann et al. (2016):
 
 \begin{theorem}[Theorem 12, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem12}
-Let $\nu = (\nu_1, \nu_2)$ be a two-armed bandit model such that $\mu_1 > \mu_2$. In the fixed-budget setting, any consistent algorithm satisfies:
+Let $\nu = (\nu_1, \nu_2)$ be a two-armed bandit model such that $\mu_1 > \mu_2$. In the fixed budget setting, any consistent algorithm satisfies:
 
@@
 For a proof, consider first the two different bandit models, \(\nu\) and
-\(\nu'\), where we fix without loss of generality that \(a^* = 1\) is
-the best arm in \(\nu\), while \(a^* = 2\) in \(\nu'\). Note that in
-this case we don't necessarily try to fool the algorithm by a change of
-distribution. Indeed, we want the algorithm \(\mathcal{A}\) to be
-consistent for both problems. Since we are in the fixed-budget setting,
-the stopping time is fixed at \(\tau = t\). Even though the correct
-decision differs between the two problems, we focus on the event
-\(A = (\hat{S}_1 = 1)\). Given the formulation in Kaufmann et al.
-(2016), we have \(A \in \mathcal{F}_t = \mathcal{F}_{\tau}\). Now, we
-can apply Lemma 1 as before, as it in essense gives a measure of how
+\(\nu'\), where we fix w.l.o.g. \(a^* = 1\) as the best arm in \(\nu\),
+while \(a^* = 2\) in \(\nu'\). Note that in this case we don't
+necessarily try to fool the algorithm by a change of distribution.
+Indeed, we want the algorithm \(\mathcal{A}\) to be consistent for both
+problems. Since we are in the fixed budget setting, the stopping time is
+fixed at \(T = t\). Even though the correct decision differs between the
+two problems, we focus on the event \(A = (\hat{S}_1 = 1)\). Now, we can
+apply Lemma 1 as before, as it in essence gives a measure of how
 different two bandit models are. Here, we want to know how different
@@
 The expectations were chosen with respect to \(\nu'\) in order to allow
-the for the following: We have \(p_t(\nu) = 1 - \mathbb{P}_{\nu}(A)\)
-and \(p_t(\nu') = \mathbb{P}_{\nu'}(A)\) (since \(A\) is wrong in
-\(\nu'\)). But since algorithm \(\mathcal{A}\) is consistent for both
-\(\nu\) and \(\nu'\), we know that there should exist some number of
-samples such that the probability of event \(A\) is bigger in setting
-\(\nu\) (where it is the correct decision), than in setting \(\nu'\)
-(where this would be a wrong decision and failure). Thus, for every
-\(\epsilon > 0\), there exists \(t_0(\epsilon)\) such that for all
+for the following: We have \(p_t(\nu) = 1 - \mathbb{P}_{\nu}(A)\) and
+\(p_t(\nu') = \mathbb{P}_{\nu'}(A)\) (since \(A\) is wrong in \(\nu'\)).
+But since algorithm \(\mathcal{A}\) is consistent for both \(\nu\) and
+\(\nu'\), we know that there should exist some number of samples such
+that the probability of event \(A\) is bigger in setting \(\nu\) (where
+it is the correct decision) than in setting \(\nu'\) (where this would
+be a wrong decision and failure). Thus, for every \(\epsilon > 0\),
+there exists \(t_0(\epsilon)\) such that for all
 \(t \geq t_0(\epsilon)\),
-\(\mathbb{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)\). Consequently,
-if we plug in the bound of \(\epsilon\) for \(\mathbb{P}_{\nu'}(A)\),
-then
+\(\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)\).
+Consequently, if we plug in the bound of \(\epsilon\) for
+\(\mathbb{P}_{\nu'}(A)\), then
 
@@
 have also derived the following lower bound on the failure probability
-for the two-armed fixed-budget bandit:
+for the two-armed fixed budget bandit:
 
@@
 
-\textbf{Mention something about the fact that we were not able to do
-this for more than 2 arms and top-m bandits. How could it be extended to
-that? How could it be extended to the threshold bandit?}
-
 As noted by Kaufmann et al. (2016), the advantage of this lower bound is
-that it makes the complexity in the fixed-confidence and the
-fixed-budget setting directly comparable. The disadvantage of course
-being that the result only holds for two-armed models. While the authors
-were not able to derive directly comparable lower bounds for the
-Top-\(m\) case, they did derive a first lower bound in the Gaussian case
-with equal variances. While we would like to move beyond Gaussian
-distributions in the work at hand, the idea for the proof might show a
-way of how the ideas can be transferred to the thresholding bandit
-problem. We first state the result and then discuss the proof.
-
-\begin{lemma}[Lemma 15, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma15}
-Let $\nu$ and $\nu'$ be two bandit models such that $S^*_m(\nu) \neq S*_m(\nu')$. Then
-
-\begin{equation*}
-\max \big( \mathbb{P}_{\nu}(S \neq S^*_m(\nu)), \mathbb{P}_{\nu'}(S \neq S^*_m(\nu')) \big) \geq \frac{1}{4} \exp \Big(-\sum_{a=1}^{K} \mathbb{E}_{\nu}[N_a] \KL(\nu_a, \nu_a') \Big).
-\end{equation*}
-\end{lemma}
-
-The following theorem only holds in the case of Gaussian bandit models
-with equal known variance.
-
-\begin{theorem}[Theorem 17, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem17}
-
-Let $\mathcal{M}_m = \{\nu = (\nu_1, \dots, \nu_K): \nu_a = \mathcal{N}(\mu_a, \sigma^2), \mu_a \in \mathbb{R}, \mu_{[m]}\neq \mu_{[m+1]}\}.$ Furthermore, let $\nu$ be such that $\mu_1 > \dots > \mu_m > \mu_{m+1} > \dots > \mu_K$, and let
-
-\begin{equation*}
-H +(\nu) = \sum_{a=1}^m \frac{2\sigma^2}{(\mu_a - \mu_{m+1})^2}, \quad H^-(\nu) = \sum_{a=m+1}^K \frac{2\sigma^2}{(\mu_m - \mu_a)^2} \quad
-and \quad
-H(\nu) = H^+(\nu) + H^-(\nu).
-\end{equation*}
-
-There exists $a \in {1, \dots, m}$ and $b \in \{m+1, \dots, K\}$ such that the bandit model $\nu^{[a,b]}$ described in Figure 4 (Kaufmann et al., 2016) satisfies $H(\nu^{[a,b]}) < H(\nu)$ and is such that
-
-\begin{equation*}
-\max \big( p_t(\nu),p_t(\nu^{[a,b]})\big) \geq \frac{1}{4} \exp \big(-\frac{4t}{\bar{H}(\nu)}\big), \quad where \quad \bar{H}(\nu) = \frac{H(\nu) \min(H^+(\nu),H^-(\nu))}{H(\nu)+\min(H^+(\nu),H^-(\nu))}
-\end{equation*}
-\end{theorem}
-
-Given that we are again in the Top-\(m\) setting, the proof idea is
-similar to the proof of Theorem \ref{theorem:KaufmannEtAlTheorem4} in
-that we again consider problems where we switch arms around the limit
-seperating the two groups of arms as given implicitly by \(\mu_{[m]}\)
-and \(\mu_{[m+1]}\). The hope here being that these methods could be
-applied to the thresholding bandit problem where the threshold of course
-gives the limit between the arms above and below the threshold. As we
-have seen in chapter 1, this flip around the threshold was of course
-used in the proof of the lower bound in Theorem 1 of Locatelli et al.
-(2016). However, there, again, the distributions were assumed to be
-Gaussian. This brings the big advantage that the Kullback-Leibler
-divergence becomes symmetric, and the feedback can take values on all
-\(\mathbb{R}\). And by using the complexity measure \(H(\nu)\), it is
-also clear that there exists an arm that is undersampled with respect to
-its contribution to the overall complexity of the problem (or sampled
-exactly according to its contribution), which leads to a convenient
-upper bound on this arms number of draws which is again employed in both
-the proof of Theorem \ref{theorem:KaufmannEtAlTheorem17} and in
-Locatelli et al. (2016). It is not clear yet, whether the same can also
-be done with other complexity measures.
-
-We do not repeat the proof here for now.
-
-See p20!
-
-What remains is to present algorithms that are able to match the lower
-bounds derived so far.
+that it makes the complexity in the fixed confidence and the fixed
+budget setting directly comparable. The disadvantage of course being
+that the result only holds for two-armed models. While the authors are
+not able to derive directly comparable lower bounds for the top-\(m\)
+case, they derive a first lower bound in the Gaussian case with equal
+variances, which we describe shortly in the appendix in
+\autoref{sec:KaufmannLBTopMGaussian}.
+
+Before we discuss the strategies of Kaufmann et al. (2016) matching the
+lower bounds, we now show how lower bounds can be derived very similarly
+for the fixed budget thresholding problem.
+
+\subsubsection{Lower Bound for Fixed Budget Thresholding
+Problem}\label{lower-bound-for-fixed-budget-thresholding-problem}
+
+In order to derive a bound for the fixed budget problem, Kaufmann et al.
+(2016) have focused on the case of the two-armed bandit which is the
+most simple version of the top-\(m\) problem. Less than two arms do not
+make sense, since then this single arm will always be the best arm. In
+the case of the thresholding bandit, however, a single-armed problem
+makes still some sense in that we still have to classify this arm
+correctly with respect to the threshold. Thus, we can show the following
+corollary which gives the a bound on the complexity of the single-armed
+thresholding bandit.
+
+\begin{corollary}
+Let $\nu = \nu_1$ be a one-armed thresholding bandit model where $\tau$ is the threshold fixed upfront.
+Let $\nu$ be from the univariate canonical exponential family of distributions such that it can be parameterized by its mean, $\mu_1$, and the Kullback-Leibler divergence between distributions $\nu_1$ and $\nu_1'$ can be written as $\KL(\nu_1', \nu_1) = \KL(\mu_1', \mu_1)$.
+In the fixed budget setting, any consistent algorithm satisfies:
+
+$$
+\lim_{t \rightarrow \infty}- \frac{1}{t} \log p_t(\nu) \leq \KL(\tau, \mu_1)
+$$
+\end{corollary}
+
+This of course is basically the Chernoff-Stein Lemma for the hypothesis
+test of two alternatives (compare chapter 11 in Cover and Thomas, 2006).
+
+But as we see in the following corollary, we can extend the lower bound
+to the \(K\)-armed fixed budget thresholding bandit problem, which
+stands in contrast to the fact that for the top-\(m\) problem, it is
+only possible to show the lower bound for two arms.
+
+\begin{corollary}
+Let $\nu = (\nu_1, ..., \nu_K)$ be a $K$-armed thresholding bandit problem in which $\tau$ is the threshold fixed upfront.
+For $i \in \{1,...,K\}$, let $\nu_i$ be from the univariate canonical exponential family of distributions such that it can be parameterized by its mean, $\mu_i$, and the Kullback-Leibler divergence between distributions $\nu_i$ and $\nu_i'$ can be written as $\KL(\nu_i, \nu_i') = \KL(\mu_i, \mu_i')$.
+In the fixed budget setting, every consistent algorithm satisfies:
+
+$$
+\lim_{t \rightarrow \infty} -\frac{1}{t} \log p_t(\nu) \leq \max_{a \in \{1,...,K\}} \KL(\tau, \mu_a)
+$$
+\end{corollary}
+
+Given the lower bounds on the sampling complexity and error probability,
+as well as the complexity measures, we now turn to sampling strategies
+that are designed to match these lower bounds.
 
@@
 strategies}\label{matching-algorithm-strategies}
-
-Given these lower bounds, all that is left is to find algorithms which
-are able to match the complexity. Sadly, not straightforward for
-Bernoullis.
 
@@
 algorithms that connect to Theorem \ref{theorem:KaufmannEtAlTheorem4}
-and Theorem \ref{theorem:KaufmannEtAlTheorem12}.
-
-Given that Locatelli et al. (2016), and thus the problem we mostly
-consider in this thesis, is in the fixed-budget setting, we are most
+and Theorem \ref{theorem:KaufmannEtAlTheorem12}. Given that we aim to
+extend the fixed budget thresholding bandit problem, we are most
 interested in the matching strategies for Theorem
-\ref{theorem:KaufmannEtAlTheorem12}. However, given that the lower bound
-applies only to two-armed bandits, the algorithms are of limited
-practical interest. Furthermore, the algorithms proposed require
-knowledge that is in general not available upfront.
-
-For the example of Gaussian distributions, the knowledge of the
+\ref{theorem:KaufmannEtAlTheorem12}. However, given that this lower
+bound applies only to two-armed bandits, the algorithms proposed by
+Kaufmann et al. (2016) are of limited practical interest. Furthermore,
+the proposed strategies require knowledge that is in general not
+available upfront: For Gaussian distributions, the knowledge of the
 (potentially different) variance is assumed which enables a strategy
@@
 
-Even worse is the case of Bernoulli two-armed bandit models where the
-proposed algorithm requires knowledge about the true parameters of the
-distributions. That this limits the practical interest is also noted by
-the authors of Kaufmann et al. (2016). Thus, they suggest to use uniform
-sampling strategies in the case of two-armed Bernoulli bandits, and show
-that there is not much to be lost by doing so.
+Even more difficult are the assumptions in the case of Bernoulli
+two-armed bandit models: The proposed algorithm requires knowledge about
+the true parameters of the distributions. That this limits the practical
+interest is also noted by the authors of Kaufmann et al. (2016). Thus,
+they suggest to use uniform sampling strategies in the case of two-armed
+Bernoulli bandits, and show that there is not much to be lost by doing
+so.
 
@@
 et al. (2010) and Kaufmann and Kalyanakrishnan (2013) which struggle to
-find matching strategies in the fixed-budget setting that do not rely on
+find matching strategies in the fixed budget setting that do not rely on
 knowledge of parameters or the complexity of the problem.
@@
 In contrast, Kaufmann et al. (2016) are able to show that their
-complexity measure derived for the fixed-confidence setting,
-\(\kappa_C(\nu)\), can be upper-bounded using the upper bound of the
-sample complexity (number of pulls) given for the KL-LUCB algorithm in
-Kaufmann and Kalyanakrishnan (2013). Consequently, in the case of
-exponential family bandits, the complexity \(\kappa_C(\nu)\) is bounded
-as given in equation (6) in Kaufmann et al. (2016):
+complexity measure derived for the fixed confidence setting,
+\(\kappa_C(\nu)\), can be upper-bounded using the upper bound given for
+the KL-LUCB algorithm in Kaufmann and Kalyanakrishnan (2013).
+Consequently, in the case of exponential family bandits, the complexity
+\(\kappa_C(\nu)\) is bounded as given in equation (6) in Kaufmann et al.
+(2016):
 
@@
 
-\subsection{Optimal Best Arm
-Identification}\label{optimal-best-arm-identification}
-
-A very similar application of the KL divergence has been given in
-Garivier and Kaufmann (2016) to derive a lower bound on the sample
-complexity in the case of best arm identification. In particular, the
-transportation Lemma 1 is used again. And a matching algorithm for
-\(K \geq 2\) arms is proposed.
-
-Talk about: - Not a simple sum of squares - Idea of algorithm: Equalize
-the probability of all wrong decisions
-
-In Garivier and Kaufmann (2016), the authors are able to derive a
-somewhat similar lower bound on the sample complexity of a \(K\)-armed
-bandit in the single best arm identification problem with fixed
-confidence. Additionally, they provide a \(\delta\)-PAC algorithm
-achieving said bound asymptotically.
-
-In particular, the authors pick up Lemma 1 from Kaufmann et al. (2016)
--- which we discussed above -- to derive the lower bound. While
-presenting these results, we try to stick as much as possible with the
-notation used so far. In particular, we let for distributions
-\(\nu_{\theta}\) from a canonical exponential family, which can be
-parameterized by its mean \(\stackrel{.}{b}(\theta) = \mu\) and thus be
-written as \(\nu^{\mu}\); for these, we continue to write the
-Kullback-Leibler divergence as
+\subsection{\texorpdfstring{Optimal Best Arm Identification
+\label{sec:OptimalBestArmIdentification}}{Optimal Best Arm Identification }}\label{optimal-best-arm-identification}
+
+Instead of discussing the KL-LUCB algorithm for the fixed confidence
+top-\(m\) problem, we shift our focus slightly onto the fixed confidence
+best arm identification problem, which is discussed in Garivier and
+Kaufmann (2016). The authors derive again a lower bound on the sample
+complexity using again the Lemma \autoref{theorem:KaufmannEtAlLemma1}.
+Furthermore, they propose a matching strategy for \(K \geq 2\) arms.
+
+The setting differs slightly from the setting considered in Kaufmann et
+al. (2016). In particular, Garivier and Kaufmann (2016) focus on
+distributions \(\nu_{\theta}\) from the univariate canonical exponential
+family of distributions, which can be parameterized by their mean
+\(\stackrel{.}{b}(\theta) = \mu\), and thus can be written as
+\(\nu^{\mu}\); for these, we write the Kullback-Leibler divergence as
+(compare \autoref{sec:LRforUnivariateExponentialFamily} and Cappé et
+al., 2013)
 
 \begin{equation*}
-\KL(\mu, \mu') = \KL(\nu^{\mu},\nu^{\mu'}) = \KL(\nu_{\theta},\nu_{\theta'}) = \KL(\nu, \nu')
+\KL(\mu, \mu') = \KL(\nu_{\mu},\nu_{\mu'}) = \KL(\nu_{\theta},\nu_{\theta'}) = \KL(\nu, \nu').
 \end{equation*}
 
-while \(d(x,y)\) continues to represent the binary relative entropy.
-
-As we will consider only problems with exponential family distributions,
-the distributions can be parameterized by their means. Therefore, if we
-let \(\mathcal{S}\) to be a set of bandit models with \(K\)
-distributions each, then each model is fully defined by a vector
+Furthermore, if we let \(\mathcal{S}\) to be a set of bandit models with
+\(K\) distributions each, then each model is fully defined by a vector
 \(\bm{\mu} = (\mu_1, \dots, \mu_K)\). Assume that every
@@
 \(\mu_{a^*} > \max_{a \neq a^*(\bm{\mu})} \mu_a\). In order to fix the
-confidence, we specify the risk \(\delta\). The strategies corresponding
-to this risk are called \(\delta\)-PAC if for every
-\(\bm{\mu} \in \mathcal{S}\),
-\(\mathbb{P}_{\bm{\mu}}(\tau_{\delta} < \infty) = 1\) (the strategy ends
-surely after a finite number of samples) and
-\(\mathbb{P}_{\bm{\mu}}(\hat{a}_{\tau_{\delta}} \neq a^*) \leq \delta\)
-(the probability of picking not the optimal arm is smaller than the
-fixed risk). As in Garivier and Kaufmann (2016), we introduce the set of
-problems for which the optimal arm is different from the one in
+confidence, we specify the risk \(\delta\). Similar to the top-\(m\)
+case considered before, strategies corresponding to this risk are called
+\(\delta\)-PAC if for every \(\bm{\mu} \in \mathcal{S}\), the strategy
+ends surely after a finite number of samples,
+\(\mathbb{P}_{\bm{\mu}}(T_{\delta} < \infty) = 1\), and the error
+probability is at least as small as the fixed risk level,
+\(\mathbb{P}_{\bm{\mu}}(\hat{a}_{T_{\delta}} \neq a^*) \leq \delta\). In
+order to derive the lower bound on the expected number of samples
+\(\mathbb{E}[T]\) through a change in distributions, we introduce the
+set of problems for which the optimal arm is different from
 \(\bm{\mu}\):
@@
 of the alternative problem to \(\bm{\mu}\). Lastly, we have the set of
-probability distributions on the arms \(\mathcal{A}\):
-\(\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}\). We are
-now ready to state the theorem.
+probability distributions on the arms \(\{1,...,K\}\):
+\(\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}\). Each
+\(w_i\) corresponds to the fraction of overall samples that the arm
+\(i\) receives. We are now ready to state the lower bound:
 
@@
 
-And so we see that the two bounds on the sample complexity (one for
-Top-\(m\), one for best arm identification) differ only in the way that
-they build the sum of Kullback-Leibler divergences over the \(K\) arms.
-In contrast to Theorem \ref{theorem:KaufmannEtAlTheorem4}, here the
+We see that the two bounds on the sample complexity (one for Top-\(m\),
+one for best arm identification) differ only in the way in which they
+build the sum of Kullback-Leibler divergences over the \(K\) arms. In
+contrast to Theorem \ref{theorem:KaufmannEtAlTheorem4}, here the
 contribution of each arm through its KL-divergence is weighted. The
 difference is that while we were able to very clearly describe the
-change of distribution in the Top-\(m\) case for each arm -- for each
-arm, we specified an alternative model that yields a new set of \(m\)
-optimal arms -- we now consider all alternative models that yield a
-different best arm than the model \(\bm{\mu}\). In the previous theorem,
-we sum over the complexity of each individual arm, as the change in
-distribution only ever touches one arm, thus leading to a KL-divergence
-of 0 for the other arms while still changing the optimal set. Here, we
-consider all instances of alternative models \(\bm{\lambda}\), and thus
-also those in which several arms are modified (and thus have a
-KL-divergence unequal 0 in the result of Lemma 1).
+change of distribution in the Top-\(m\) case for each arm -- we
+specified an alternative model for each arm that yields a new set of
+\(m\) optimal arms -- we now consider all alternative models that yield
+a different best arm than the model \(\bm{\mu}\). In the previous
+theorem, we sum over the complexity of each individual arm, as the
+change in distribution only ever touches one arm, thus leading to a
+KL-divergence of 0 for the other arms while still changing the optimal
+set. Here, we consider all instances of alternative models
+\(\bm{\lambda}\), and thus also those in which several arms are modified
+(and thus have a KL-divergence unequal 0 in the result of Lemma 1).
 
@@
 of arm \(a\) until time \(t\), for all \(t\geq 1\). Again, Lemma
-\ref{theorem:KaufmannEtAlLemma1} states how the failure probability
-\(\delta\) relates to the expected number of draws of each arm given two
-models which differ in their optimal arm, and where it is evaluated
-based on the Kullback-Leibler divergence for each pair of arms how much
-the two models differ:
+\ref{theorem:KaufmannEtAlLemma1} states how the risk \(\delta\) relates
+to the expected number of draws of each arm given two models which
+differ in their optimal arm. How much the two models differ is evaluated
+based on the Kullback-Leibler divergence for each pair of arms:
 
 \begin{equation*}
-\forall \lambda \in \mathcal{S}: a^*(\lambda) \neq a^*(\mu), \sum_{a=1}^K \KL(\mu_a,\lambda_a)\mathbb{E}_{\bm{\mu}}[N_a(\tau_{\delta})] \geq \d(\delta, 1- \delta).
+\forall \lambda \in \mathcal{S}: a^*(\lambda) \neq a^*(\mu), \sum_{a=1}^K \KL(\mu_a,\lambda_a)\mathbb{E}_{\bm{\mu}}[N_a(T_{\delta})] \geq \d(\delta, 1- \delta).
 \end{equation*}
@@
 the lower bound practical, it is a matter of finding the optimal weights
-\(w^*(\bm{\mu})\). This step did not occur in the previous lower bound,
-as the alternative models were made specific by changing the
-distribution of one arm with respect to the ``border'' between the two
-groups of arms.
-
-In any case, the existence of the optimal weights suggests an algorithm
-that keeps track of the share of samples that is attributed to each arm
-and makes sure that it stays close to the optimum until some decision
-rule assures that the \(\delta\)-PAC condition is fulfilled.
+\(w^*(\bm{\mu})\). This step did not occur in the lower bound for the
+top-\(m\) problem since the alternative models were specified by
+changing the distribution of one arm with respect to the ``border''
+between the two groups of arms.
+
+The existence of the optimal weights suggests an algorithm that keeps
+track of the share of samples that is attributed to each arm and makes
+sure that it stays close to the optimum until some decision rule assures
+that the \(\delta\)-PAC condition is fulfilled.
 
 Indeed, the optimal weights will lead to a sampling structure in which
-arms are drawn in such a way ensuring that their individual failure
-probabilities are at the same level. Take a situation where the
-currently best arm \(\hat{\mu}_1\) is the best arm. Then, we calculate
-for each arm the risk that actually it is better than arm 1. Since the
-arms are assumed to be independent, the we only have to compare every
-arm individually to arm 1. Given that, it makes sense that we don't want
-to disregard an arm that has a high probability of being better than arm
-1. Assuming arm 1 is actually the best arm, we would an algorithm that
-ensures a low failure probability on all arms, thus equalizing the
-failure probability for every arm compared to arm 1.
+arms are drawn in a way that ensures that their individual probability
+of error stays at the same level. An arm more distant from the optimal
+arm in terms of Kullback-Leibler divergence should receive a smaller
+share of the samples to achieve the same error probability as an arm
+closer to the optimal arm.
 
@@
 In the proof of Lemma 3 of Garivier and Kaufmann, it is shown that
-nature, selecting the alternative model \(bm{\lambda}\) will always pick
-an alternative model in which only a single arm \(a\) is changed such
-that \(\lambda_a > \lambda_1\) since
+nature, selecting the alternative model \(\bm{\lambda}\) will always
+pick an alternative model in which only a single arm \(a\) is changed
+such that \(\lambda_a > \lambda_1\) since
 
@@
 in Garivier and Kaufmann (2016) that is able to match the lower bound by
-the intuition given above.
+the intuition given above. The main idea of the \emph{Track-and-Stop}
+algorithm is now to keep track of the optimal shares for each arm by
+equalizing the error probabilies for each arm.
 
@@
 A very intuitive fix to this problem is the solution proposed in Lemma 8
-of Garivier and Kaufmann (2016), with their \(D-Tracking\) rule.
-Basically, whenever an arm has received a very low number of pulls
-\(N_a(t)\) given the number of iterations so far, \(t\) and the number
-of arms \(K\) that have to share the samples, pull the arm that has
-received the smallest amount of samples so far. Else, pull the arm which
-number of pulls so far \(N_a(t)\) is the furthest away from what its
-optimal share \(t\cdot w^*_a(\hat{\bm{\mu}}(t))\) would be. Given this
-sampling rule, the authors can show in their Proposition 9 that the
-empirical proportion of draws converges in probability to the optimal
-weights given the true means.
+of Garivier and Kaufmann (2016) with their \(D-Tracking\) rule. Whenever
+an arm has received a very low number of pulls \(N_a(t)\) given the
+number of iterations so far, \(t\), and the number of arms \(K\) that
+have to share the samples, pull the arm that has received the smallest
+amount of samples so far. Else, pull the arm which number of pulls so
+far \(N_a(t)\) is the furthest away from what its optimal share
+\(t\cdot w^*_a(\hat{\bm{\mu}}(t))\) would be. Given this sampling rule,
+the authors can show in their Proposition 9 that the empirical
+proportion of draws converges in probability to the optimal weights
+given the true means.
 
@@
 authors are able to prove in Theorem 14 an upper bound on the expected
-sampling complexity \(\mathbb{E}_{\mu}[\tau_{\delta}]\). The stopping
-rule ensures that the algorithm explores sufficiently to promise a risk
+sampling complexity \(\mathbb{E}_{\mu}[T_{\delta}]\). The stopping rule
+ensures that the algorithm explores sufficiently to promise a risk
 smaller than \(\delta\), while stopping as soon as possible. Given that
@@
 Stopping Rule proposed in Garivier and Kaufmann (2016) calculates for
-each arm \(a\in \mathcal{A}\) the Generalized Likelihood Ratio statistic
+each arm \(a\in \{1,...K\}\) the Generalized Likelihood Ratio statistic
 with every arm \(b \in \mathcal{A}^{\setminus a}\), which for
@@
 Consequently, a sensible idea for a stopping rule would be that there
-has to be an arm \(a \in \mathcal{A}\) for which
-\(Z_{a,b} \geq 0 \forall b \in \mathcal{A}^{\setminus a}\) (which is
+has to be an arm \(a \in \{1,...,K\}\) for which
+\(Z_{a,b} \geq 0 \, \forall b \in \{1,...,K\}^{\setminus a}\) (which is
 always fulfilled if there is a uniquely best arm), and, additionally, we
@@
 has to be larger than an exploration threshold \(\beta(t, \delta)\).
-Consequently, the final number of samples \(\tau_{\delta}\) of an
-algorithm is given by:
+Consequently, the final number of samples \(T_{\delta}\) of an algorithm
+is given by:
 
 \begin{equation*}
-\tau_{\delta} = \inf \{t \in \mathbb{N}: \exists a \in \mathcal{A}, \forall b\in \mathcal{A}^{\setminus a}, Z_{a,b}(t) > \beta(t, \delta)\}
+T_{\delta} = \inf \{t \in \mathbb{N}: \exists a \in \mathcal{A}, \forall b\in \mathcal{A}^{\setminus a}, Z_{a,b}(t) > \beta(t, \delta)\}
 \end{equation*}
@@
 Let $\alpha \in [1, e/2]$ and $r(t) = O(t^{\alpha})$.
-Using Chernoff's stopping rule with $\beta(t,\delta) = \log(r(t)/\delta)$ and the sampling rule C-Tracking or D-Tracking,
+Using Chernoff's stopping rule with $\beta(t,\delta) = \log(r(t)/\delta)$ and the sampling rule D-Tracking,
 
 \begin{equation*}
-\lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\bm{\mu}}[\tau_{\delta}]}{\log(1/\delta)} \leq \alpha T^*(\mu).
+\lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\bm{\mu}}[T_{\delta}]}{\log(1/\delta)} \leq \alpha T^*(\mu).
 \end{equation*}
@@
 which is most practical only in the case of Gaussian distributions.
-While the contribution in the fixed-budget setting was limited to the
+While the contribution in the fixed budget setting was limited to the
 two-armed bandit case, the authors derive general lower bounds in the
-fixed-confidence setting which are primarily based on Lemma
+fixed confidence setting which are primarily based on Lemma
 \ref{theorem:KaufmannEtAlLemma1}. Lemma \ref{theorem:KaufmannEtAlLemma1}
@@
 
+We show empirically that part of this problem can be alleviated by
+including the D-Tracking rule proposed by Garivier and Kaufmann (2016)
+and discussed in \autoref{sec:OptimalBestArmIdentification} into the SLR
+algorithm.
+
 While the Bayes-UCB performance is impressive, we observe that also the
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-2-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-1-1}
 
@@
 
-\caption{Budget allocation across arms for APT and SLR algorithms in simulation 2.}\label{fig:unnamed-chunk-2}
+\caption{Budget allocation across arms for APT and SLR algorithms in simulation 2.}\label{fig:unnamed-chunk-1}
 \end{figure}
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-3-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-2-1}
 
@@
 
-\caption{Rolling average for the arms used in experiment 1.}\label{fig:unnamed-chunk-3}
+\caption{Rolling average for the arms used in experiment 1.}\label{fig:unnamed-chunk-2}
 \end{figure}
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-4-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-3-1}
 
@@
 
-\caption{Performance comparison of algorithms for experiment 1.}\label{fig:unnamed-chunk-4}
+\caption{Performance comparison of algorithms for experiment 1.}\label{fig:unnamed-chunk-3}
 \end{figure}
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-5-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-4-1}
 
@@
 
-\caption{Rolling average of arms used in experiment 2.}\label{fig:unnamed-chunk-5}
+\caption{Rolling average of arms used in experiment 2.}\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-9-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-8-1}
 
@@
 
-\caption{Performance results of algorithms in experiment 2.}\label{fig:unnamed-chunk-9}
+\caption{Performance results of algorithms in experiment 2.}\label{fig:unnamed-chunk-8}
 \end{figure}
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-10-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-9-1}
 
@@
 
-\caption{Budget allocation of algorithms across arms on real and synthetic data in experiment 2.}\label{fig:unnamed-chunk-10}
+\caption{Budget allocation of algorithms across arms on real and synthetic data in experiment 2.}\label{fig:unnamed-chunk-9}
 \end{figure}
@@
 
+\subsection{\texorpdfstring{Lower Bound on Probability of Error in
+FB-Top-\(m\) with Gaussian Arms
+\label{sec:KaufmannLBTopMGaussian}}{Lower Bound on Probability of Error in FB-Top-m with Gaussian Arms }}\label{lower-bound-on-probability-of-error-in-fb-top-m-with-gaussian-arms}
+
+While we would like to move beyond Gaussian distributions in the work at
+hand, the idea for the proof might show a way of how the ideas can be
+transferred to the thresholding bandit problem. We first state the
+result and then discuss the proof.
+
+\begin{lemma}[Lemma 15, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma15}
+Let $\nu$ and $\nu'$ be two bandit models such that $S^*_m(\nu) \neq S^*_m(\nu')$. Then
+
+\begin{equation*}
+\max \big( \mathbb{P}_{\nu}(S \neq S^*_m(\nu)), \mathbb{P}_{\nu'}(S \neq S^*_m(\nu')) \big) \geq \frac{1}{4} \exp \Big(-\sum_{a=1}^{K} \mathbb{E}_{\nu}[N_a] \KL(\nu_a, \nu_a') \Big).
+\end{equation*}
+\end{lemma}
+
+The following theorem only holds in the case of Gaussian bandit models
+with equal known variance.
+
+\begin{theorem}[Theorem 17, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem17}
+
+Let $\mathcal{M}_m = \{\nu = (\nu_1, \dots, \nu_K): \nu_a = \mathcal{N}(\mu_a, \sigma^2), \mu_a \in \mathbb{R}, \mu_{[m]}\neq \mu_{[m+1]}\}.$ Furthermore, let $\nu$ be such that $\mu_1 > \dots > \mu_m > \mu_{m+1} > \dots > \mu_K$, and let
+
+\begin{equation*}
+H^+(\nu) = \sum_{a=1}^m \frac{2\sigma^2}{(\mu_a - \mu_{m+1})^2}, \quad H^-(\nu) = \sum_{a=m+1}^K \frac{2\sigma^2}{(\mu_m - \mu_a)^2} \quad
+and \quad
+H(\nu) = H^+(\nu) + H^-(\nu).
+\end{equation*}
+
+There exists $a \in \{1, \dots, m\}$ and $b \in \{m+1, \dots, K\}$ such that the bandit model $\nu^{[a,b]}$ described in Figure 4 (Kaufmann et al., 2016) satisfies $H(\nu^{[a,b]}) < H(\nu)$ and is such that
+
+\begin{equation*}
+\max \big( p_t(\nu),p_t(\nu^{[a,b]})\big) \geq \frac{1}{4} \exp \big(-\frac{4t}{\bar{H}(\nu)}\big), \quad where \quad \bar{H}(\nu) = \frac{H(\nu) \min(H^+(\nu),H^-(\nu))}{H(\nu)+\min(H^+(\nu),H^-(\nu))}
+\end{equation*}
+\end{theorem}
+
+Given that we are again in the Top-\(m\) setting, the proof idea is
+similar to the proof of Theorem \ref{theorem:KaufmannEtAlTheorem4} in
+that we again consider problems in which we switch arms around the
+threshold implied by \(\mu_{[m]}\) and \(\mu_{[m+1]}\). Given that, one
+might hope to apply a similar proof to the thresholding bandit problem.
+As we see in \autoref{sec:AppendixAPTLB}, a flip around the threshold is
+used in the proof of the lower bound in Theorem 1 of Locatelli et al.
+(2016). However, there, again, the distributions are assumed to be
+Gaussian. This brings the big advantage that the Kullback-Leibler
+divergence is symmetric, and the feedback can take values on all
+\(\mathbb{R}\). This is important, as is allows us to easily define
+alternative problems by a flip around the threshold with the same
+complexity as the original problem. This would not hold for
+KL-divergences that are not symmetric (e.g., for Bernoulli arms). For
+the full proof, refer to page 20 in Kaufmann et al. (2016).
+
+\subsection{Proof of Corollary 1}\label{proof-of-corollary-1}
+
+\textbf{Proof}: The proof follows closely the proof of Theorem 12 in
+Kaufmann et al. (2016) and is again an application of their
+transportation Lemma, Lemma 2.
+
+Consider the one-armed bandit problem, \(K = 1\) with the canonical
+exponential family of distributions distribution \(\nu_1\) parameterized
+by its mean \(\mu_1\). Furthermore, given we are in the thresholding
+bandit problem, we have a threshold \(\tau\) against which the arm is
+classified. Assume w.l.o.g. that for \(\nu_1\), \(\mu_1 \geq \tau\).
+Thus, \(\mathcal{S}_{\tau}^* = \{1\}\). After \(T\) rounds, a consistent
+algorithm returns with error probability \(p_T(\nu)\) the guess
+\(\hat{\mathcal{S}}_{\tau}\). Thus, we have for the event
+\(A = (\hat{\mathcal{S}}_\tau = \{1\})\) the probability
+\(\mathbb{P}_{\nu}(A)\). On the other hand, define the alternative model
+\(\nu'\) with mean \(\mu_1' < \tau\) such that the correct
+classification from \(\nu\) is now wrong:
+\(\mathcal{S}_{\tau}^* {'} = (\mathcal{S}_{\tau}^*)^C = \{\emptyset\}\).
+Consequently, since the algorithm is still consistent on this problem,
+we have that \(\mathbb{P}_{\nu'}(A) = p_t(\nu')\). Thus, we expect that
+as we let \(t\) increase, \(\mathbb{P}_{\nu'}(A)\) will decrease while
+\(\mathbb{P}_{\nu}(A)\) will increase.
+
+Indeed, given we consider only consistent algorithms, there should exist
+a number of samples for which the probability of the correct decision in
+problem \(\nu\) is larger than the error probability in problem
+\(\nu'\), that is: for every \(\epsilon > 0\), there exists
+\(t_0(\epsilon)\) such that for all \(t \geq t_0(\epsilon)\) we have
+
+\begin{equation}
+\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_{\nu}(A). \label{eq:BoundForCorollary}
+\end{equation}
+
+Now, consider again Lemma 2 in Kaufmann et al. (2016). If we let the
+algorithm be such that \(T = t\), we can apply the Lemma to the stopping
+time \(\sigma = t\) a.s. and the event \(A\) to get
+
+\[
+\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)).
+\]
+
+We can lower bound the RHS by using the bound on
+\(\mathbb{P}_{\nu'}(A)\) given in \eqref{eq:BoundForCorollary} and the
+monotonicity of the binary relative entropy. We get:
+
+\begin{align*}
+\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) & = t \KL(\nu_1', \nu_1) \\
+& \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)) \\
+& \geq d(\epsilon, 1- p_t(\nu)) \\
+& = \epsilon \log\Big(\frac{\epsilon}{1-p_t(\nu)}\Big) + (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) \\
+& \geq (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) + \epsilon \log(\epsilon) \\
+\end{align*}
+
+Letting \(\epsilon \rightarrow 0\), we get
+
+\[
+t \KL(\nu_1', \nu_1) \geq \log \Big(\frac{1}{p_t(\nu)}\Big) = -\log p_t(\nu).
+\] To make the bound as tight as possible, we choose the alternative
+model that minimizes \(\KL(\nu_1', \nu_1)\) while still ensuring that
+\(\mathcal{S}_{\tau}^* {'} = \{\emptyset\}\). In our case of the
+thresholding bandit with univariate exponential family distributions,
+this is given by choosing \(\mu_1' = \tau\). By pluggin in, we get the
+result:
+
+\[
+t \KL(\tau, \mu_1) \geq -\log p_t(\nu).
+\]
+
 \subsection{\texorpdfstring{Bayes-UCB Algorithm for the Thresholding
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-11-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-10-1}
 
@@
 
-\caption{Budget allocation for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter c.}\label{fig:unnamed-chunk-11}
+\caption{Budget allocation for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter c.}\label{fig:unnamed-chunk-10}
 \end{figure}
@@
 
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-11-1}
+
+}
+
+\caption{Budget allocation for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter c.}\label{fig:unnamed-chunk-11}
+\end{figure}
+
+\begin{figure}
+
 {\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-12-1}
@@
 
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-13-1}
-
-}
-
-\caption{Budget allocation for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter c.}\label{fig:unnamed-chunk-13}
-\end{figure}
-
 \end{document}

### 2017-09-03 Thesis/experiment_postprocessing/loc6nt_postprocessing.R

@@ -53,6 +53,13 @@ save(loc6nt_LR_arm_seq, file = "/Users/timradtke/Dropbox/1Master/Master Thesis/t
 rm(loc6nt_LR_7000, loc6nt_LR_arm_seq)
 gc()
 
+load(paste0(current_path, "loc6nt_LRD.Rda"))
+loc6nt_LRD_arm_seq <- data.frame(t(laply(loc6nt_LRD, 
+                                        function(x) x$arm_sequence)))
+save(loc6nt_LRD_arm_seq, file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/loc6nt_LRD_arm_seq.Rda")
+rm(loc6nt_LRD, loc6nt_LRD_arm_seq)
+gc()
+
 
 ##########################################################
 
@@ -86,6 +93,26 @@ loc6nt_LR_ma <- data.frame(algorithm = rep("SLR",6981),
                            lapply(loc6nt_LR_arm_seq_summary[,-1], FUN = zoo::rollapply, width = 10, mean)) %>%
   gather(arm, mean, -index, -algorithm)
 
+load("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/loc6nt_LRD_arm_seq.Rda")
+
+loc6nt_LRD_arm_seq_summary <- loc6nt_LRD_arm_seq %>% 
+  tbl_df() %>% 
+  mutate(index = 1:7000) %>%
+  gather(key = iter, value = arm, -index) %>%
+  dplyr::filter(index > 10) %>%
+  dplyr::group_by(arm, index) %>%
+  dplyr::summarize(n = n()) %>%
+  ungroup() %>% 
+  spread(arm, n) %>%
+  as.data.frame()
+
+names(loc6nt_LRD_arm_seq_summary)[-1] <- c(paste0("V0", 1:9), "V10")
+
+loc6nt_LRD_ma <- data.frame(algorithm = rep("SLR-D",6981),
+                           index = 1:6981,
+                           lapply(loc6nt_LRD_arm_seq_summary[,-1], FUN = zoo::rollapply, width = 10, mean)) %>%
+  gather(arm, mean, -index, -algorithm)
+
[…]

### 2017-09-03 synthetic_experiments/cal_algs_verylong_6_no_tau.R

@@ -37,11 +37,9 @@ for(j in 1:5000) {
 ########################################################################
 
 load(paste0(current_path, "/loc6nt_BUCB_horizon_7000.Rda"))
-load(paste0(current_path, "/loc6nt_AugUCB_7000.Rda"))
-load(paste0(current_path, "/loc6nt_UNIFORM_7000.Rda"))
 load(paste0(current_path, "/loc6nt_APT_7000.Rda"))
 load(paste0(current_path, "/loc6nt_LR_7000.Rda"))
-load(paste0(current_path, "/loc6nt_EVT.Rda"))
+load(paste0(current_path, "/loc6nt_LRD.Rda"))
 
 table(loc6nt_LR_7000[[1]]$arm_sequence)
 table(loc6nt_LR_7000[[2]]$arm_sequence)
@@ -76,8 +74,14 @@ for(i in 1:5000){
 summary(pulls_of_arm_6_BUCB)
 quantile(pulls_of_arm_6_BUCB, 0.05)
 
+pulls_of_arm_6_LRD <- vector(length = 5000)
+for(i in 1:5000){
+  pulls_of_arm_6_LRD[i] <- table(loc6nt_LRD[[i]]$arm_sequence)[6]
+}
+
 pulls_arm_6 <- data.frame(APT = pulls_of_arm_6_APT,
                           SLR = pulls_of_arm_6_LR,
+                          SLRD = pulls_of_arm_6_LRD,
                           BUCB = pulls_of_arm_6_BUCB)
 
 pulls_arm_6 %>% gather(key = "Algorithm", value = "Pulls") %>%
@@ -88,6 +92,11 @@ pulls_arm_6 %>% gather(key = "Algorithm", value = "Pulls") %>%
 pulls_of_arm_1_LR <- vector(length = 5000)
 for(i in 1:5000){
   pulls_of_arm_1_LR[i] <- table(loc6nt_LR_7000[[i]]$arm_sequence)[1]
+}
+
+pulls_of_arm_1_LRD <- vector(length = 5000)
+for(i in 1:5000){
+  pulls_of_arm_1_LRD[i] <- table(loc6nt_LRD[[i]]$arm_sequence)[1]
 }
 
 pulls_of_arm_1_APT <- vector(length = 5000)
@@ -102,6 +111,7 @@ for(i in 1:5000){
 
 pulls_arm_1 <- data.frame(APT = pulls_of_arm_1_APT,
                           SLR = pulls_of_arm_1_LR,
[…]

### 2017-09-03 synthetic_experiments/cal_algs_verylong_7_no_tau.R

@@ -82,6 +82,21 @@ rm(loc7nt_LR_10000, loc7nt_comp_LR_10000)
 gc()
 
 ########################################################################
+# Standard Likelihood Ratio with D-Tracking Rule
+system.time(loc7nt_LRD_10000 <- para_bandit_sim_LRD(data = data_list7_10000, 
+                                                  rounds = 10000, 
+                                                  tau = tau_loc7nt, 
+                                                  epsilon = epsilon_loc7nt))
+
+save(loc7nt_LRD_10000, file = paste0(current_path, "loc7nt_LRD_10000.Rda"))
+loc7nt_comp_LRD_10000 <- compare_to_ground_truth(mean_loc7nt, loc7nt_LRD_10000, 
+                                                tau_loc7nt, epsilon_loc7nt)$mean
+save(loc7nt_comp_LRD_10000, file = paste0(current_path, 
+                                         "loc7nt_comp_LRD_10000.Rda"))
+rm(loc7nt_LRD_10000)
+gc()
+
+########################################################################
 # Standard Uniform
 system.time(loc7nt_UNIFORM_10000 <- para_bandit_sim_uniform(data = data_list7_10000, 
                                                          rounds = 10000))
@@ -146,6 +161,7 @@ save(loc7nt_comp_AugUCB_10000, file = paste0(current_path,
 load(file = paste0(current_path, "loc7nt_comp_UNIFORM_10000.Rda"))
 load(file = paste0(current_path, "loc7nt_comp_APT_10000.Rda"))
 load(file = paste0(current_path, "loc7nt_comp_LR_10000.Rda"))
+load(file = paste0(current_path, "loc7nt_comp_LRD_10000.Rda"))
 load(file = paste0(current_path, "loc7nt_comp_BUCB_horizon_10000.Rda"))
 load(file = paste0(current_path, "loc7nt_comp_AugUCB_10000.Rda"))
 load(file = paste0(current_path, "loc7nt_comp_EVT.Rda"))
@@ -155,5 +171,6 @@ lines(log(loc7nt_comp_BUCB_horizon_10000), col = "green")
 lines(log(loc7nt_comp_UNIFORM_10000), col = "darkblue")
 lines(log(loc7nt_comp_APT_10000), col = "red")
 lines(log(loc7nt_comp_LR_10000), col = "darkred")
+lines(log(loc7nt_comp_LRD_10000), col = "darkgreen")
[…]

### 2017-09-04 Thesis/Draft.Rmd
Edit second chapter

@@
 
+Define exponential family of distributions
+
+Define KL Divergence for this family
+
 \newpage
@@
 
-# Information Theoretic Complexity of Pure Exploration Bandits \label{chap:KullbackLeiblerPureExploration}
+# Information Theoretic Approaches to Pure Exploration Bandits \label{chap:KullbackLeiblerPureExploration}
 
@@
 
-## Complexity Measures for Best-Arm and Top-*m* Identification \label{sec:KaufmannEtAl2016}
+## Information Theoretic Complexity Measures in Top-$m$ Problems \label{sec:KaufmannEtAl2016}
 
 Instead of the thresholding bandit problem, Kaufmann et al.
-(2016) consider the problem of identifying the best $m$ out of $K$ arms, that is, the Top-$m$ problem.
-They describe their a bandit model $\nu$ also by $K$ arms characterized by probability distributions $\nu_a$, $a \in \{1,...,K\}$ with mean $\mu_a$.
-As before, a learner decides at any time step $t=1,2,...,$ an arm $A_t \in \{1,...,K\}$ for which he observes the independent reward $Z_{t} \sim \nu_{A_t}$.
+(2016) consider the problem of identifying the best $m$ out of $K$ arms, that is, the top-$m$ problem.
+They describe their bandit model $\nu$ by $K$ arms characterized by probability distributions $\nu_a$, $a \in \{1,...,K\}$, with mean $\mu_a$.
+A learner picks at any time step $t=1,2,...,$ an arm $A_t \in \{1,...,K\}$ for which he observes the independent reward $Z_{t} \sim \nu_{A_t}$.
 The learner aims to find the $m$ out of $K$ arms with the largest expected reward.
@@
 Kaufmann et al.
-write the in decreasing order sorted means $(\mu_{1}, ..., \mu_{K})$ as the K-tuple $(\mu_{[1]}, ..., \mu_{[K]})$.
+write the means $(\mu_{1}, ..., \mu_{K})$ sorted in decreasing order as the K-tuple $(\mu_{[1]}, ..., \mu_{[K]})$.
 Based on this, they require that $\mu_{[m]} > \mu_{[m+1]}$ such that the solution $\mathcal{S}_m^*$ is unique.
@@
 This classification is then evaluated by the loss function $\mathcal{L}(T) = \mathbb{I}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m)$.
-This binary loss is of course very similar to the loss in the thresholding bandit problem.
-We can now define a strategy of the learner as $\mathcal{A} = ((A_t), T, \hat{\mathcal{S}}_m)$: The strategy defines how he chooses an arm, how many samples are observed, and how the arms are classified in the end.
+This binary loss is similar to the loss in the thresholding bandit.
+We can now define a strategy of the learner as $\mathcal{A} = ((A_t), T, \hat{\mathcal{S}}_m)$: The strategy defines how an arm is chosen, how many samples are observed, and how the arms are eventually classified.
 
@@
 In the fixed budget setting, we run algorithms for $T$ samples and then compare them based on their expected loss, $\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m) =: p_t(\nu)$ as we have seen in $\autoref{sec:Setup}$.
-Alternatively, consider a $\delta$-PAC strategy $\mathcal{A}(\delta)$for which holds for every problem $\nu \in \mathcal{M}_m$ that the classification holds at least with confidence level $1-\delta$, that is, $\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta$.
+Alternatively, consider a $\delta$-PAC strategy $\mathcal{A}(\delta)$for which it holds for every problem $\nu \in \mathcal{M}_m$ that the classification holds at least with confidence level $1-\delta$, that is, $\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta$.
 The strategy has to achieve this level of confidence in its prediction before it is allowed to stop sampling.
-This is the fixed confidence case, in which the budget $T$ is no longer fixed upfront, but becomes a random variable.
-We compare algorithms by their expected number of draws $\mathbb{E}_{\nu}[T_{\delta}]$ and prefer those which arrive at the confidence level $1-\delta$ with a smaller expected budget.
-
-Following Kaufmann et al.
-(2016), in the fixed confidence setting, a family of strategies $A = (\mathcal{A}(\delta))_{\delta \in (0,1)}$ is called PAC if for every $\delta$, $\mathcal{A}(\delta)$ is $\delta$-PAC.
+This is the fixed confidence case, in which the budget $T$ is no longer fixed upfront, but turns into a random variable.
+Algorithms are then compared by their expected number of draws $\mathbb{E}_{\nu}[T_{\delta}]$ and we prefer those which achieve the confidence level $1-\delta$ with a smaller expected budget.
+
+In the fixed confidence setting, a family of strategies $A = (\mathcal{A}(\delta))_{\delta \in (0,1)}$ is called PAC if for every $\delta$, $\mathcal{A}(\delta)$ is $\delta$-PAC.
 On the other hand, in the fixed budget setting, a family of strategies $A = (\mathcal{A}(t))_{t \in \mathbb{N}}$ is called consistent if $p_t(\nu) \rightarrow 0$ as $t \rightarrow \infty$ for every problem $\nu \in \mathcal{M}_m$.
@@
 Given this setup, we can now follow the arguments of Kaufmann et al.
-(2016) to deduce complexity measures for the top-$m$ problem.
-As alluded to earlier, these complexity measures will rely on the Kullback-Leibler divergence in contrast to the complexity $H$ used by Locatelli et al.
+(2016) to derive complexity measures for the top-$m$ problem.
+As alluded to earlier, these complexity measures will rely on the KL-divergence in contrast to the complexity $H$ used by Locatelli et al.
 (2016).
-Also, when discussing $H$, we so far described it as complexity as it measures the difficulty of the problem by measuring the distance between arms and the threshold.
-Kaufmann et al.
-approach complexity instead from how many samples (what error probability) one can expect to need in the fixed confidence (fixed budget) setting.
-Thus, in order to arrive at their new measure of complexity, it makes sense to first follow their arguments to a general lower bound on the sample complexity $\mathbb{E}_{\nu}[\tau]$ in the case of fixed confidence top-$m$ problems.
-This bound is given in their Theorem 4 (for common confidence levels of $\delta \leq 0.15$).
+When discussing $H$, its motivation is that it represents the difficulty of the problem by measuring the distance between arms and the threshold.
+Instead, Kaufmann et al.
+approach complexity by how many samples (what error probability) one will need in the fixed confidence (fixed budget) setting.
+In order to arrive at their new measure of complexity, it makes sense to first follow their arguments to a general lower bound on the sample complexity $\mathbb{E}_{\nu}[\tau]$ which is given in their Theorem 4:
 
@@
 \begin{equation*}
-\mathbb{E}_{\nu}[\tau] \geq \Big[ \sum_{a \in \mathcal{S}^*_m} \frac{1}{KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}^*_m} \frac{1}{KL(\nu_a, \nu_{[m]})} \Big] \der(1-\delta, \delta),
+\mathbb{E}_{\nu}[\tau] \geq \Big[ \sum_{a \in \mathcal{S}^*_m} \frac{1}{\KL(\nu_a || \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}^*_m} \frac{1}{\KL(\nu_a || \nu_{[m]})} \Big] \der(1-\delta, \delta),
 \end{equation*}
-
-where $\der(x,y) := x \log(x/y) + (1-x) \log((1-x)/(1-y))$ is the binary relative entropy, with the convention that $\der(0,0) = \der(1,1) = 0$.
 \end{theorem}
@@
 To prove this statement for a given $\delta$-PAC algorithm $\mathcal{A}$, we assume certain continuity conditions (compare Kaufmann et al.
-(2016)), with which there exists for every arm $a \in \{1, \dots, K\}$ an alternative model $\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)$.
+(2016)) under which there exists for every arm $a \in \{1, \dots, K\}$ an alternative model $\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)$.
 In this alternative model, in accordance with the continuity conditions, only arm $a$ is modified.
@@
 
-Given that the strategy returns $\hat{S}_m$, we know that for the event $\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})$ (which is element of the $\sigma$-Algebra $\mathcal{F}_{T}$ induced by the stopping time $T$), that $\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta$ and $\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta$ (because fixed confidence $\delta$!).
-To now give the lower bound on the expected number of samples, $\mathbb{E}_{\nu}[\tau]$, we employ the general Lemma given by the authors for such changes in distribution in bandit models.
-
-\begin{lemma}[Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma1}
+Given the strategy returns $\hat{S}_m$, we know that for the event $\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})$ (which is element of the $\sigma$-Algebra $\mathcal{F}_{T}$ induced by the stopping time $T$), that $\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta$ and $\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta$ (because fixed confidence $\delta$!).
+To give the lower bound on the expected number of samples, $\mathbb{E}_{\nu}[\tau]$, we employ the general Lemma given by the authors for such changes in distribution in bandit models.
+
+\begin{lemma}[Lemma 1, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma1}
 Let $\nu$ and $\nu'$ be two bandit models with $K$ arms such that for all $a$, the distributions $\nu_a$ and $\nu_a'$ are mutually absolutely continuous.
@@
 \begin{equation*}
-\sum_{a=1}^{K} \mathbb{E}_{\nu} [N_a(\sigma)] \KL(\nu_a, \nu_a') \geq \sup_{\mathcal{E} \in \mathcal{F}_{\sigma}} \der (\mathbb{P}_{\nu}(\mathcal{E}), \mathbb{P}_{\nu'}(\mathcal{E})),
+\sum_{a=1}^{K} \mathbb{E}_{\nu} [N_a(\sigma)] \KL(\nu_a|| \nu_a') \geq \sup_{\mathcal{E} \in \mathcal{F}_{\sigma}} \der (\mathbb{P}_{\nu}(\mathcal{E}), \mathbb{P}_{\nu'}(\mathcal{E})).
 \end{equation*}
-
-where $d(x,y)$ is the binary relative entropy as defined above.
 \end{lemma}
 
-We can apply this Lemma directly on the expected number of draws for each arm, $\mathbb{E}_{\nu}[N_a]$.
+We apply this Lemma directly on the expected number of draws for each arm, $\mathbb{E}_{\nu}[N_a]$.
 For each arm $a$, we thus have $\KL(\nu_a, \nu_a') \mathbb{E}_{\nu}[N_a] \geq d(1-\delta, \delta)$.
-Using the definition of the alternative model above, we get for every small but fixed $\alpha > 0$, for every arm $a \in \{1, \dots, K\}$ and each arm $b \in \{m+1, \dots, K\}$:
+Using the definition of the alternative model above, we get for every small but fixed $\alpha > 0$, every arm $a \in \{1, \dots, K\}$ and $b \in \{m+1, \dots, K\}$:
 
 \begin{equation*}
-\mathbb{E}_{\nu}[N_a] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_a, \nu_{m+1}) + \alpha}
+\mathbb{E}_{\nu}[N_a] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_a || \nu_{m+1}) + \alpha} \quad \text{and} \quad \mathbb{E}_{\nu}[N_b] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_b || \nu_{m}) + \alpha}.
 \end{equation*}
 
-and
+Let $\alpha \to 0$, sum the individual arms' bounds to get the bound on the overall number of draws:
 
 \begin{equation*}
-\mathbb{E}_{\nu}[N_b] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_b, \nu_{m}) + \alpha}.
-\end{equation*}
-
-We can then let $\alpha \to 0$, sum the bounds on the individual arms to get the bound on the overall number of draws:
-
-\begin{equation*}
-\mathbb{E}_{\nu}[T] = \sum_{a=1}^K \mathbb{E}_{\nu}[N_a] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \der(1-\delta, \delta)
+\mathbb{E}_{\nu}[T] = \sum_{a=1}^K \mathbb{E}_{\nu}[N_a] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m]})} \Big) \der(1-\delta, \delta)
 \end{equation*}
@@
 \begin{equation*}
-\mathbb{E}_{\nu}[T] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
+\mathbb{E}_{\nu}[T] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
 \end{equation*}
 
-Given this lower bound, it becomes clear that the complexity of the top-$m$ problem can be lower bounded by the Kullback-Leibler divergence between arms and the implied threshold between the $m$-th best arm and the $(m+1)$-th best arm.
-After all, the latter gives a lower bound on the effort (in terms of expected number of samples) required to achieve a certain confidence level.
-And a problem that requires a larger effort can be described as more complex.
+Given this lower bound, it is clear that the complexity of the top-$m$ problem can be lower bounded by the KL-divergence between arms and the implied threshold between the $m$-th best arm and the $(m+1)$-th best arm.
+The latter gives a lower bound on the effort (in terms of expected number of samples) required to achieve a certain confidence level, where a problem that requires a larger effort is described as more complex.
 Indeed, in the case of fixed confidence problems, Kaufmann et al.
@@
 
-Following Kaufmann et al. (2016), we can now define the complexity $\kappa_C(\nu)$ for the fixed confidence setting as
+Following Kaufmann et al. (2016), we define the complexity $\kappa_C(\nu)$ in the fixed confidence setting as
 
 \begin{equation}
-\kappa_C(\nu) = \inf_{A \, \text{PAC}} \lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\nu}[T{\delta}]}{\log \frac{1}{\delta}}. \label{eq:KappaC}
+\kappa_C(\nu) = \inf_{A \, \text{PAC}} \limsup_{\delta \to 0} \frac{\mathbb{E}_{\nu}[T_{\delta}]}{\log \frac{1}{\delta}}. \label{eq:KappaC}
 \end{equation}
@@
 \begin{equation*}
-\kappa_C(\nu) \geq \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})}
+\kappa_C(\nu) \geq \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a || \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a || \nu_{[m]})}
 \end{equation*}
@@
 Given this description, we would expect that a complexity measure in a fixed confidence thresholding bandit probem might involve replacing $\mu_{[m]}$ and $\mu_{[m+1]}$ by the actual threshold $\tau$ that divides the group above the threshold from the group below the threshold.
-
-However, given the problem formulation in Locatelli et al.
-(2016), we are mainly interested in complexity measures and algorithms for the fixed budget setting.
-As we will see now, the results of Kaufmann et al.
+But given the setting in Locatelli et al.
+(2016), we are mainly interested in complexity measures and algorithms for the fixed budget problem.
+The results of Kaufmann et al.
 (2016) are more limited for this case.
 While the authors are able to provide a bound on their complexity measure in the fixed budget case, it only applies to the case of *two-armed* bandit models.
+
 Consider a consistent fixed budget strategy $\mathcal{A}$ ($p_t(\nu)$ tends to zero as $t \rightarrow \infty$), and define the complexity in the fixed budget setting as follows:
@@
 \begin{equation}
-\kappa_B(\nu) = \inf_{A \, \text{consistent}} \big(\lim_{t \to \infty} \sup - \frac{1}{t} \log p_t(\nu)\big)^{-1}.
+\kappa_B(\nu) = \inf_{A \, \text{consistent}} \Big(\limsup_{t \to \infty} - \frac{1}{t} \log p_t(\nu)\Big)^{-1}.
 \end{equation}
 
-While we included the experimenter-fixed $\delta$ in the definition of $\kappa_C$, we now include the experimenter-fixed $T$ in the definition of $\kappa_B$ to disregard it in the complexity measure after plugging in the lower bound on $p_t(\nu)$.
+While we included the experimenter-fixed $\delta$ in the definition of $\kappa_C$, we now include the fixed $T$ in the definition of $\kappa_B$ to disregard it in the complexity measure after plugging in the lower bound on $p_t(\nu)$.
 The resulting lower bound given in Theorem 12 of Kaufmann et al.
@@
 \begin{equation*}
-\lim_{t \to \infty} \sup - \frac{1}{t} \log p_t(\nu) \leq \inf_{(\nu_1', \nu_2') \in \mathcal{M}: \mu_1' < \mu_2'} \frac{\KL(\nu_1', \nu_1) + \KL(\nu_2', \nu_2)}{2}
+\limsup_{t \to \infty} - \frac{1}{t} \log p_t(\nu) \leq \inf_{(\nu_1', \nu_2') \in \mathcal{M}: \mu_1' < \mu_2'} \max \big\{\KL(\nu_1' || \nu_1), \KL(\nu_2' || \nu_2)\big\}
 \end{equation*}
@@
 $a^* = 1$ as the best arm in $\nu$, while $a^* = 2$ in $\nu'$.
-Note that in this case we don't necessarily try to fool the algorithm by a change of distribution.
-Indeed, we want the algorithm $\mathcal{A}$ to be consistent for both problems.
+We require the algorithm $\mathcal{A}$ to be consistent for both problems.
 Since we are in the fixed budget setting, the stopping time is fixed at $T = t$.
-Even though the correct decision differs between the two problems, we focus on the event $A = (\hat{S}_1 = 1)$.
-Now, we can apply Lemma 1 as before, as it in essence gives a measure of how different two bandit models are.
-Here, we want to know how different $\nu$ is from $\nu'$, and so, given we have only two arms,
+The correct decision differs between the two problems, and we focus on the event $A = (\hat{S}_1 = 1)$.
+Now, we can apply Lemma 1 from Kaufmann et al.
+(2016) as before, as it gives a measure of how different two bandit models are (it bounds the change in distribution).
+Here, we want to know how different $\nu$ is from $\nu'$, and, given we have only two arms,
 
 \begin{equation*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2', \nu_2) \geq \der(\mathbb{P}_{\nu'}(A),\mathbb{P}_{\nu}(A)))
+\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1'|| \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2'|| \nu_2) \geq \der(\mathbb{P}_{\nu'}(A),\mathbb{P}_{\nu}(A)))
 \end{equation*}
@@
 \begin{align*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2', \nu_2) & \geq \der(\epsilon,1-p_t(\nu))) \\
+\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1' || \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2' || \nu_2) & \geq \der(\epsilon,1-p_t(\nu))) \\
 & = \epsilon \log \frac{\epsilon}{1-p_t(\nu)} + (1-\epsilon) \log \frac{1-\epsilon}{p_t(\nu)} \\
@@
 \begin{align*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2', \nu_2)
+\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1' || \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2' || \nu_2)
 & \geq \log \frac{1}{p_t(\nu)} = -\log p_t(\nu).
@@
 \begin{align*}
-\lim_{t \to 0} \sup - \frac{1}{t} \log p_t(\nu)
-& \leq \lim_{t \to 0} \sup \frac{1}{t} \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)] \KL(\nu_a', \nu_a) \\
-& \leq \max_{a=1,2} \KL(\nu_a', \nu_a),
+\limsup_{t \to \infty} - \frac{1}{t} \log p_t(\nu)
+& \leq \limsup_{t \to 0} \frac{1}{t} \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)] \KL(\nu_a' || \nu_a) \\
+& \leq \max_{a=1,2} \KL(\nu_a' || \nu_a),
 \end{align*}
@@
 (2016), one arrives at the final result by choosing $\mu_1'$, $\mu_2'$ so that $| \KL(\nu_1', \nu_1) - \KL(\nu_2', \nu_2) |$ is as small as possible.
-
-Note that while deriving the lower bound on the complexity measure, we have also derived the following lower bound on the failure probability for the two-armed fixed budget bandit:
-
-\begin{equation*}
-p_t(\nu) \geq \exp \big(- \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)] \KL(\nu_a', \nu_a) \big)
-\end{equation*}
-
-or, to not rely on the share of samples attributed to each arm,
-
-\begin{equation*}
-p_t(\nu) \geq \exp \big(- \max_{a=1,2} \KL(\nu_a', \nu_a) \big).
-\end{equation*}
 
@@
 
-Before we discuss the strategies of Kaufmann et al. (2016) matching the lower bounds, we now show how lower bounds can be derived very similarly for the fixed budget thresholding problem.
-
-### Lower Bound for Fixed Budget Thresholding Problem
+Before we discuss algorithms given in Kaufmann et al. (2016) that match the lower bounds, we show how lower bounds can be derived very similarly for the fixed budget thresholding problem.
+
+### Lower Bound for Fixed Budget Thresholding Problem \label{sec:LBTBP}
 
 In order to derive a bound for the fixed budget problem, Kaufmann et al.
-(2016) have focused on the case of the two-armed bandit which is the most simple version of the top-$m$ problem.
-Less than two arms do not make sense, since then this single arm will always be the best arm.
-In the case of the thresholding bandit, however, a single-armed problem makes still some sense in that we still have to classify this arm correctly with respect to the threshold.
-Thus, we can show the following corollary which gives the a bound on the complexity of the single-armed thresholding bandit.
+(2016) have focused on the setting with two arms which is the most simple version of the top-$m$ problem.
+Less than two arms do not make sense, since the single arm is by definition the best arm.
+In the case of the thresholding bandit, however, a single-armed problem makes still at least limited sense in that we still have to classify this arm correctly with respect to the threshold.
+Thus, we can show the following corollary which gives a bound on the complexity of the single-armed thresholding bandit.
 
@@
 Let $\nu = \nu_1$ be a one-armed thresholding bandit model where $\tau$ is the threshold fixed upfront.
-Let $\nu$ be from the univariate canonical exponential family of distributions such that it can be parameterized by its mean, $\mu_1$, and the Kullback-Leibler divergence between distributions $\nu_1$ and $\nu_1'$ can be written as $\KL(\nu_1', \nu_1) = \KL(\mu_1', \mu_1)$.
-In the fixed budget setting, any consistent algorithm satisfies:
-
-$$
-- \frac{1}{t} \log p_t(\nu) \leq \KL(\tau, \mu_1)
-$$
-\end{corollary}
-
-This of course is basically the Chernoff-Stein Lemma for the hypothesis test of two alternatives (compare chapter 11 in Cover and Thomas, 2006).
+Let $\nu$ be from the univariate exponential family of distributions such that $\nu_1$ can be parameterized by its mean, $\mu_1$, and the Kullback-Leibler divergence between distributions $\nu_1$ and $\nu_1'$ can be written as $\KL(\nu_1', \nu_1) = \KL(\mu_1', \mu_1)$.
+In the fixed budget setting, any consistent algorithm ($p_t(\nu) \rightarrow 0$ as $t \rightarrow \infty$) satisfies:
+
+$$
+- \frac{1}{t} \log p_t(\nu) \leq \KL(\tau || \mu_1)
+$$
+\end{corollary}\label{corollary:LB1TBP}
+
+This is basically the Chernoff-Stein Lemma for the hypothesis test of two alternatives (compare chapter 11 in Cover and Thomas, 2006, or \autoref{theorem:ChernoffStein}).
+We arrive at this result as the one-armed bandit does not require sequential sampling: The single arm receives all samples.
+$\mathbb{E}_{\nu'}[N_1(t)]$ is not a random variable but equals $T$.
 
 But as we see in the following corollary, we can extend the lower bound to the $K$-armed fixed budget thresholding bandit problem, which stands in contrast to the fact that for the top-$m$ problem, it is only possible to show the lower bound for two arms.
+The result is based on an alternative setting $\nu'$ in which all arms have means $\mu' = \tau$ such that their expected number of pulls corresponds to uniform sampling, $\mathbb{E}_{\nu'}[N_i(t)] = T/K$.
 
@@
 Let $\nu = (\nu_1, ..., \nu_K)$ be a $K$-armed thresholding bandit problem in which $\tau$ is the threshold fixed upfront.
-For $i \in \{1,...,K\}$, let $\nu_i$ be from the univariate canonical exponential family of distributions such that it can be parameterized by its mean, $\mu_i$, and the Kullback-Leibler divergence between distributions $\nu_i$ and $\nu_i'$ can be written as $\KL(\nu_i, \nu_i') = \KL(\mu_i, \mu_i')$.
-In the fixed budget setting, every consistent algorithm satisfies:
-
-$$
-\lim_{t \rightarrow \infty} -\frac{1}{t} \log p_t(\nu) \leq \max_{a \in \{1,...,K\}} \KL(\tau, \mu_a)
-$$
-\end{corollary}
-
-Given the lower bounds on the sampling complexity and error probability, as well as the complexity measures, we now turn to sampling strategies that are designed to match these lower bounds.
-
-### Matching algorithm strategies
+For $i \in \{1,...,K\}$, let $\nu_i$ be from the univariate exponential family of distributions such that $\nu_i$ can be parameterized by its mean, $\mu_i$, and the Kullback-Leibler divergence between distributions $\nu_i$ and $\nu_i'$ can be written as $\KL(\nu_i, \nu_i') = \KL(\mu_i, \mu_i')$.
+In the fixed budget setting, any consistent algorithm satisfies:
+
+$$
+\limsup_{t \rightarrow \infty} -\frac{1}{t} \log p_t(\nu) \leq \max_{a \in \{1,...,K\}} \KL(\tau || \mu_a)
+$$
+
+or
+
+$$
+- \frac{1}{t} \log p_t(\nu) \leq \frac{1}{K}\sum_{i=1}^{K} \KL(\tau || \mu_i),
+$$
+\end{corollary}\label{corollary:LBKTBP}
+
+We present the proofs of \autoref{sec:LBTBP} in the appendix in \autoref{sec:corollaryLBTBPproof}.
+Corresponding to the complexity measures defined in equation $(1)$ of Kaufmann et al.
+(2016), we can define the complexity $\kappa_{TBP}(\nu)$ in the thresholding bandit problem and lower bound it:
+
+$$
+\kappa_{TBP}(\nu) = \inf_{A \text{ consistent}} \Big(\limsup_{t \rightarrow \infty} - \frac{1}{t} \log p_t(\nu)\Big)^{-1} \geq K \Big(\sum_{i=1}^{K} \KL(\tau||\mu_i)\Big)^{-1}
+$$
+
+### Strategies Matching the Top-$m$ Lower Bound
 
@@
 Thus, Kaufmann et al.
-(2016) join a number of other papers like Audibert et al.
+(2016) joins other papers like Audibert et al.
 (2010) and Kaufmann and Kalyanakrishnan (2013) which struggle to find matching strategies in the fixed budget setting that do not rely on knowledge of parameters or the complexity of the problem.
@@
 In contrast, Kaufmann et al.
-(2016) are able to show that their complexity measure derived for the fixed confidence setting, $\kappa_C(\nu)$, can be upper-bounded using the upper bound given for the KL-LUCB algorithm in Kaufmann and Kalyanakrishnan (2013).
-Consequently, in the case of exponential family bandits, the complexity $\kappa_C(\nu)$ is bounded as given in equation (6) in Kaufmann et al.
+(2016) are able to show that their complexity measure derived for the fixed confidence setting, $\kappa_C(\nu)$, can be upper-bounded using the bound given for the KL-LUCB algorithm in Kaufmann and Kalyanakrishnan (2013).
+In the case of exponential family bandits, the complexity $\kappa_C(\nu)$ is bounded as given in equation (6) in Kaufmann et al.
 (2016):
@@
 \begin{equation*}
-\sum_{a \in S^*_m} \frac{1}{K(\theta_a, \theta_{[m+1]})} + \sum_{a \notin S^*_m} \frac{1}{K(\theta_a,\theta_{[m]})} \leq \kappa_C(\nu) \leq 24 \min_{\theta \in [\theta_{[m+1]},\theta_{[m]}]} \sum_{a=1}^{K} \frac{1}{K^*(\theta_a, \theta)},
+\sum_{a \in S^*_m} \frac{1}{\KL(\theta_a || \theta_{[m+1]})} + \sum_{a \notin S^*_m} \frac{1}{\KL(\theta_a || \theta_{[m]})} \leq \kappa_C(\nu) \leq 24 \min_{\theta \in [\theta_{[m+1]},\theta_{[m]}]} \sum_{a=1}^{K} \frac{1}{\KL^*(\theta_a || \theta)},
 \end{equation*}
 
-where $K(\theta, \theta') = \KL(\nu_{\theta}, \nu_{\theta'})$ for $(\theta, \theta') \in \Theta^2$ was defined as the shorthand for the Kullback-Leibler divergence for two distributions from the exponential family parameterized by $\theta$ and $\theta'$ respectively.
-$K^*(\theta,\theta') = K(\theta^*, \theta)$ is the Chernoff distribution between the two distributions, where $\theta^*$ is chosen so that $K(\theta^*,\theta) = K(\theta^*, \theta')$.
-
-## Optimal Best Arm Identification \label{sec:OptimalBestArmIdentification}
-
-Instead of discussing the KL-LUCB algorithm for the fixed confidence top-$m$ problem, we shift our focus slightly onto the fixed confidence best arm identification problem, which is discussed in Garivier and Kaufmann (2016).
-The authors derive again a lower bound on the sample complexity using again the Lemma \autoref{theorem:KaufmannEtAlLemma1}.
+where again we write with slight abuse of notation $\KL(\theta || \theta') = \KL(\nu_{\theta}|| \nu_{\theta'})$ for $(\theta, \theta') \in \Theta^2$ as the shorthand for the KL-divergence of two distributions from the exponential family parameterized by $\theta$ and $\theta'$ respectively.
+$\KL^*(\theta || \theta') = \KL(\theta^* || \theta)$ is the Chernoff information between the two distributions, where $\theta^*$ is chosen so that $\KL(\theta^* || \theta) = \KL(\theta^* || \theta')$.
+
+## Information Theoretic Approach to Best Arm Identification \label{sec:OptimalBestArmIdentification}
+
+Instead of discussing the KL-LUCB algorithm for the fixed confidence top-$m$ problem, we shift our focus onto the fixed confidence best arm identification problem, as discussed in Garivier and Kaufmann (2016).
+The authors also derive a lower bound on the sample complexity using the Lemma \autoref{theorem:KaufmannEtAlLemma1}.
 Furthermore, they propose a matching strategy for $K \geq 2$ arms.
@@
 (2016).
-In particular, Garivier and Kaufmann (2016) focus on distributions $\nu_{\theta}$ from the univariate canonical exponential family of distributions, which can be parameterized by their mean $\stackrel{.}{b}(\theta) = \mu$, and thus can be written as $\nu^{\mu}$; for these, we write the Kullback-Leibler divergence as (compare \autoref{sec:LRforUnivariateExponentialFamily} and Cappé et al., 2013)
-
-\begin{equation*}
-\KL(\mu, \mu') = \KL(\nu_{\mu},\nu_{\mu'}) = \KL(\nu_{\theta},\nu_{\theta'}) = \KL(\nu, \nu').
-\end{equation*}
+In particular, Garivier and Kaufmann (2016) focus on distributions $\nu_{\theta}$ from the univariate canonical exponential family of distributions, which can be parameterized by their mean $\mu$, and thus can be written as $\nu_{\mu}$; as before, we simplify the notation of the KL-divergence for these distributions to $\KL(\nu || \nu') = \KL(\mu || \mu')$.
 
@@
 Assume that every $\bm{\mu} \in \mathcal{S}$ has a unique maximum given by $a^*(\bm{\mu})$ such that $\mu_{a^*} > \max_{a \neq a^*(\bm{\mu})} \mu_a$.
-In order to fix the confidence, we specify the risk $\delta$.
+In order to fix the confidence $1-\delta$, we specify the risk $\delta$.
 Similar to the top-$m$ case considered before, strategies corresponding to this risk are called $\delta$-PAC if for every $\bm{\mu} \in \mathcal{S}$, the strategy ends surely after a finite number of samples, $\mathbb{P}_{\bm{\mu}}(T_{\delta} < \infty) = 1$, and the error probability is at least as small as the fixed risk level, $\mathbb{P}_{\bm{\mu}}(\hat{a}_{T_{\delta}} \neq a^*) \leq \delta$.
-In order to derive the lower bound on the expected number of samples $\mathbb{E}[T]$ through a change in distributions, we introduce the set of problems for which the optimal arm is different from $\bm{\mu}$:
+In order to derive the lower bound on the expected number of samples $\mathbb{E}[T]$ through a change in distributions, we introduce the set of alternative problems for which the optimal arm is different from $\bm{\mu}$:
 
 \begin{equation*}
-\text{Alt}(\bm{\mu}) := \{\bm{\lambda} \in \mathcal{S}: a^*(\bm{\lambda}) \neq a^*(\bm{\mu})\}
+\text{Alt}(\bm{\mu}) := \{\bm{\lambda} \in \mathcal{S}: a^*(\bm{\lambda}) \neq a^*(\bm{\mu})\},
 \end{equation*}
 
-where $\bm{\lambda}$ is the vector of means defining the distributions of the alternative problem to $\bm{\mu}$.
+where $\bm{\lambda}$ is the vector of means defining the distributions of the alternative problem.
 Lastly, we have the set of probability distributions on the arms $\{1,...,K\}$: $\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}$.
-Each $w_i$ corresponds to the fraction of overall samples that the arm $i$ receives.
-We are now ready to state the lower bound:
+Each $w_i$ corresponds to the fraction of overall samples that arm $i$ receives.
+We now state the lower bound:
 
@@
 \begin{equation} \label{eq:GarivierKaufmann_Theorem1_Game}
-T^*(\bm{\mu})^{-1} := \sup_{w \in \Sigma_K} \inf_{\bm{\lambda} \in \text{\em{Alt}}(\bm{\mu})} \left( \sum_{a=1}^K w_a \text{\em{KL}}(\mu_a, \lambda_a)\right).
+T^*(\bm{\mu})^{-1} := \sup_{w \in \Sigma_K} \inf_{\bm{\lambda} \in \text{\em{Alt}}(\bm{\mu})} \left( \sum_{a=1}^K w_a \text{\em{KL}}(\mu_a|| \lambda_a)\right).
 \end{equation}
@@
 
-We see that the two bounds on the sample complexity (one for Top-$m$, one for best arm identification) differ only in the way in which they build the sum of Kullback-Leibler divergences over the $K$ arms.
+We see that the two bounds given in Theorem \ref{theorem:KaufmannEtAlTheorem4} and Theorem \ref{theorem:GarivierKaufmannTheorem1} on the sample complexity differ only in the way in which they sum the Kullback-Leibler divergences over the $K$ arms.
 In contrast to Theorem \ref{theorem:KaufmannEtAlTheorem4}, here the contribution of each arm through its KL-divergence is weighted.
-The difference is that while we were able to very clearly describe the change of distribution in the Top-$m$ case for each arm -- we specified an alternative model for each arm that yields a new set of $m$ optimal arms -- we now consider all alternative models that yield a different best arm than the model $\bm{\mu}$.
-In the previous theorem, we sum over the complexity of each individual arm, as the change in distribution only ever touches one arm, thus leading to a KL-divergence of 0 for the other arms while still changing the optimal set.
-Here, we consider all instances of alternative models $\bm{\lambda}$, and thus also those in which several arms are modified (and thus have a KL-divergence unequal 0 in the result of Lemma 1).
-
-*Proof of Theorem \ref{theorem:GarivierKaufmannTheorem1}*: As stated before, we let $\delta \in (0,1)$, $\bm{\mu} \in \mathcal{S}$, and only consider $\delta$-PAC strategies.
+The difference is that while we were able to clearly describe the change of distribution in the top-$m$ case for each arm -- we specified an alternative model for each arm that yields a new set of $m$ optimal arms -- we now consider all alternative models that yield a different best arm than the model $\bm{\mu}$.
+In the previous theorem, we sum over the complexity of each individual arm, since the change in distribution only affects one arm at a time, thus leading to a KL-divergence of 0 for the other arms while still changing the optimal set.
+Now, we consider all instances of alternative models $\bm{\lambda}$, and thus also those in which several arms are modified (and thus have a KL-divergence unequal 0 in the result of Lemma 1).
+
+To proof Theorem \ref{theorem:GarivierKaufmannTheorem1}, we let $\delta \in (0,1)$, $\bm{\mu} \in \mathcal{S}$, and only consider $\delta$-PAC strategies.
 As before, $N_a(t)$ describes the random number of pulls of arm $a$ until time $t$, for all $t\geq 1$.
 Again, Lemma \ref{theorem:KaufmannEtAlLemma1} states how the risk $\delta$ relates to the expected number of draws of each arm given two models which differ in their optimal arm.
-How much the two models differ is evaluated based on the Kullback-Leibler divergence for each pair of arms:
+How much the two models differ is evaluated based on the KL-divergence for each pair of arms:
 
@@
 
-As mentioned, we now do not consider a specific alternative for each arm, but instead look at the infimum over all the possible alternatives, and use the fact that $\mathbb{E}_{\bm{\mu}}[\tau_{\delta}] = \sum_{a=1}^K \mathbb{E}_{\bm{\mu}}[N_a(\tau_{\delta})]$:
+As mentioned, we now do not consider a specific alternative for each arm, but instead look at the infimum over all the possible alternatives, and use the fact that $\mathbb{E}_{\bm{\mu}}[T_{\delta}] = \sum_{a=1}^K \mathbb{E}_{\bm{\mu}}[N_a(T_{\delta})]$:
 
 \begin{align*}
-\der(\delta, 1-\delta) & \leq \inf_{\lambda \in \text{Alt}(\bm{\mu})} \mathbb{E}_{\bm{\mu}}[\tau_{\delta}] \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[\tau_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
-& = \mathbb{E}_{\bm{\mu}}[\tau_{\delta}] \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[\tau_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
-& \leq \mathbb{E}_{\bm{\mu}}[\tau_{\delta}] \sup_{w \in \Sigma_K} \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K w_a \KL(\mu_a, \lambda_a)\Big).
+\der(\delta, 1-\delta) & \leq \inf_{\lambda \in \text{Alt}(\bm{\mu})} \mathbb{E}_{\bm{\mu}}[T_{\delta}] \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[T_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
+& = \mathbb{E}_{\bm{\mu}}[T_{\delta}] \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[T_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
+& \leq \mathbb{E}_{\bm{\mu}}[T_{\delta}] \sup_{w \in \Sigma_K} \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K w_a \KL(\mu_a, \lambda_a)\Big).
 \end{align*}
 
-As stated in Garivier and Kaufmann (2016), the term $\frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[\tau_{\delta}]}$ gives the fraction of draws each arm receives.
+As stated in Garivier and Kaufmann (2016), the term $\frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[T_{\delta}]}$ gives the fraction of draws each arm receives.
 This value, however, depends on the used algorithm.
@@
 
-This lower bound can be interpreted as a Minimax game, where the experimenter has to choose the share of samples he attributes to each arm in a way that is optimal given that nature will respond and choose the most difficult alternative model given his weights.
+This lower bound can be interpreted as a minimax game^[See the presentation by Aurélien Garivier at COLT 2016: <https://youtu.be/eLyrrYqJlkE>], where the experimenter has to choose the share of samples he attributes to each arm in a way that is optimal given that nature will respond and choose the most difficult alternative model given his weights.
 Thus, to make the lower bound practical, it is a matter of finding the optimal weights $w^*(\bm{\mu})$.
@@
 
-Indeed, the optimal weights will lead to a sampling structure in which arms are drawn in a way that ensures that their individual probability of error stays at the same level.
+Indeed, the optimal weights will lead to a sampling structure in which arms are drawn such that their individual probabilities of error stay at the same level.
 An arm more distant from the optimal arm in terms of Kullback-Leibler divergence should receive a smaller share of the samples to achieve the same error probability as an arm closer to the optimal arm.
 
-This is exactly what happens when we look for the proportions $w \in \Sigma_K$ that minimize the cost from a change in distributions, that is, the term $F(\bm{\mu}, \bm{w}) = \inf_{\bm{\lambda} \in \text{Alt}(\bm{\mu})} \Big(\sum_{a= 1}^K w_a \KL(\mu_a, \lambda_a)\Big)$.
-In the proof of Lemma 3 of Garivier and Kaufmann, it is shown that nature, selecting the alternative model $\bm{\lambda}$ will always pick an alternative model in which only a single arm $a$ is changed such that $\lambda_a > \lambda_1$ since
+This is what happens when we look for proportions $w \in \Sigma_K$ that minimize the cost from a change in distributions, that is, the term $F(\bm{\mu}, \bm{w}) = \inf_{\bm{\lambda} \in \text{Alt}(\bm{\mu})} \Big(\sum_{a= 1}^K w_a \KL(\mu_a, \lambda_a)\Big)$.
+In the proof of Lemma 3 of Garivier and Kaufmann, it is shown that nature, selecting the alternative model $\bm{\lambda}$, will always pick an alternative model in which only a single arm $a$ is changed such that $\lambda_a > \lambda_1$ since
 
@@
 T^*(\bm{\mu})^{-1} & = \sup_{w \in \Sigma_K} \min_{a \neq 1} \inf_{\bm{\lambda} \in \mathcal{S}: \lambda_a > \lambda_1} \sum_{a=1}^K w_a \KL(\mu_a, \lambda_a)  \\
-& = \sup_{w \in \Sigma_K} \min_{a \neq 1} \inf_{\bm{\lambda}: \lambda_a \geq \lambda_1} [w_1 \KL(\mu_1, \lambda_1)+w_a \KL(\mu_a, \lambda_a)].
+& = \sup_{w \in \Sigma_K} \min_{a \neq 1} \inf_{\bm{\lambda}: \lambda_a \geq \lambda_1} [w_1 \KL(\mu_1, \lambda_1)+w_a \KL(\mu_a, \lambda_a)]. \Alignyesnumber\label{eqn:ComplexityTrackStopStrategy}
 \end{align*}
@@
 \begin{equation*}
-I_{\alpha}(\mu_1, \mu_2) := \alpha \KL(\mu_1, \alpha \mu_1 + (1-\alpha) \mu_2) + (1-\alpha) \KL(\mu_2, \alpha \mu_1 + (1-\alpha) \mu_2).
+I_{\alpha}(\mu_1, \mu_2) := \alpha \KL(\mu_1 || \alpha \mu_1 + (1-\alpha) \mu_2) + (1-\alpha) \KL(\mu_2 || \alpha \mu_1 + (1-\alpha) \mu_2).
 \end{equation*}
@@
 
-And so by assuring the reader that there are ways to compute $w_a^*$ and $T^*$ given $\bm{\mu}$ (see chapter 2.2 in Garivier and Kaufmann (2016)), we can now introduce the *Track-and-Stop* strategy given in Garivier and Kaufmann (2016) that is able to match the lower bound by the intuition given above.
+And so by assuring the reader that there are ways to compute $w_a^*$ and $T^*$ given $\bm{\mu}$ (see chapter 2.2 in Garivier and Kaufmann (2016)), we can now introduce the *Track-and-Stop* strategy given in Garivier and Kaufmann (2016) that is able to match the lower bound.
 The main idea of the *Track-and-Stop* algorithm is now to keep track of the optimal shares for each arm by equalizing the error probabilies for each arm.
 
-When going from theory to algorithm, the obvious problem is of course that we do no longer know $\bm{\mu}$ and thus cannot simply calculate the optimal weights.
-Instead, we are estimating the maximum likelihood estimates $\hat{\mu}(t) = (\hat{\mu}_1(t), \dots, \hat{\mu}_K(t))$ of the true mean at the current round $t$ and need to base our weights based on these.
-It is however problematic to rely on these sample means as we are inherently unsure about them.
+When going from theory to algorithm, the obvious problem is that we no longer know the true parameters $\bm{\mu}$ and cannot calculate the optimal weights.
+Instead, we have to estimate the maximum likelihood estimates $\hat{\mu}(t) = (\hat{\mu}_1(t), \dots, \hat{\mu}_K(t))$ of the true mean at the current round $t$ and need to base our sample weights on them.
+It is however problematic to rely on the sample means as we are inherently unsure about them.
 And so wrong estimates, which naturally occur most easily in the beginning when not many samples have been pulled, are prone to lead to wrong weights.
-Thus, if a wrong estimate $\hat{\mu}_a$ for arm $a$ leads to a small weight $w_a$, then neither the estimate nor the weight will be correct soon.
+Thus, if a wrong estimate $\hat{\mu}_a$ for arm $a$ leads to a small weight $w_a$, then after a few more rounds neither the estimate nor the weight will be correct.
 Thus, Kaufmann and Garivier conclude that "a naive plug-in sampling rule sometimes fails".
-They propose to enforce a certain minimum level of exploration to make sure that arms that erroneously received a very small weight will be further explored regardless.
-
-A very intuitive fix to this problem is the solution proposed in Lemma 8 of Garivier and Kaufmann (2016) with their $D-Tracking$ rule.
-Whenever an arm has received a very low number of pulls $N_a(t)$ given the number of iterations so far, $t$, and the number of arms $K$ that have to share the samples, pull the arm that has received the smallest amount of samples so far.
-Else, pull the arm which number of pulls so far $N_a(t)$ is the furthest away from what its optimal share $t\cdot w^*_a(\hat{\bm{\mu}}(t))$ would be.
+They propose to enforce a certain minimum level of exploration to ensure that arms that erroneously received a very small weight will be further explored regardless.
+
+A very intuitive solution to this problem is proposed in Lemma 8 of Garivier and Kaufmann (2016) with the $D-Tracking$ rule.
+Whenever some arm has received a very small number of pulls $N_a(t)$ given the number of iterations $t$ so far, and the number of arms $K$ that have to share the samples, pull the arm that has received the smallest amount of samples so far.
+Else, pull the arm whose number of pulls so far $N_a(t)$ is the farthest away from what its optimal share $t\cdot w^*_a(\hat{\bm{\mu}}(t))$ would be.
 Given this sampling rule, the authors can show in their Proposition 9 that the empirical proportion of draws converges in probability to the optimal weights given the true means.
@@
 Given that the sampling rule is independent of this stopping rule, the rule boils down to a statistical test at every iteration and thus is a sequential test based on the current estimate of $\hat{\bm{\mu}}$.
-The Chernoff's Stopping Rule proposed in Garivier and Kaufmann (2016) calculates for each arm $a\in \{1,...K\}$ the Generalized Likelihood Ratio statistic with every arm $b \in \mathcal{A}^{\setminus a}$, which for $\hat{\mu}_a(t) \geq \hat{\mu}_b(t)$ can be written as
+Chernoff's Stopping Rule proposed in Garivier and Kaufmann (2016) calculates for each arm $a\in \{1,...K\}$ the Generalized Likelihood Ratio statistic with every arm $b \in \mathcal{A}^{\setminus a}$, which for $\hat{\mu}_a(t) \geq \hat{\mu}_b(t)$ can be written as
 
 \begin{equation*}
-Z_{a,b}(t) = - Z_{b,a} = N_a(t) \KL(\hat{\mu}_a(t),\hat{\mu}_{a,b}(t)) + N_b(t) \KL(\hat{\mu}_{b}(t), \hat{\mu}_{a,b}(t)),
+Z_{a,b}(t) = - Z_{b,a} = N_a(t) \KL(\hat{\mu}_a(t) || \hat{\mu}_{a,b}(t)) + N_b(t) \KL(\hat{\mu}_{b}(t) || \hat{\mu}_{a,b}(t)),
 \end{equation*}
@@
 \begin{equation*}
-\hat{\mu}_{a,b}(t) := \frac{N_a(t)}{N_a(t) + N_b(t)}\hat{\mu}_a + \frac{N_b(t)}{N_a(t) + N_b(t)}\hat{\mu}_b.
+\hat{\mu}_{a,b}(t) := \frac{N_a(t)}{N_a(t) + N_b(t)}\hat{\mu}_a(t) + \frac{N_b(t)}{N_a(t) + N_b(t)}\hat{\mu}_b(t).
 \end{equation*}
 
-Consequently, a sensible idea for a stopping rule would be that there has to be an arm $a \in \{1,...,K\}$ for which $Z_{a,b} \geq 0 \, \forall  b \in \{1,...,K\}^{\setminus a}$ (which is always fulfilled if there is a uniquely best arm), and, additionally, we demand that for this arm the smallest of the $(K-1)$ test statistics has to be larger than an exploration threshold $\beta(t, \delta)$.
-Consequently, the final number of samples $T_{\delta}$ of an algorithm is given by:
+Consequently, a sensible idea for a stopping rule would be that there has to be an arm $a \in \{1,...,K\}$ for which $Z_{a,b} \geq 0 \text{ for all }  b \in \{1,...,K\}^{\setminus a}$ (which is always fulfilled if there is a uniquely best arm), and we demand that for this arm the smallest of the $(K-1)$ test statistics has to be larger than an exploration threshold $\beta(t, \delta)$.
+The final sampling round $T_{\delta}$ of the algorithm is given by:
 
@@
 
-Demanding that the optimal exploration threshold increases in rounds $t$ (if we have more samples, require more certainty; also, punish for failing previous tests) and decreases in the risk $\delta$, and does so at a diminishing rate, the optimal threshold derived in Theorem 10 of Garivier and Kaufmann (2016) makes sense intuitively:
+Demanding that the optimal exploration threshold increases in rounds $t$ (if we have more samples, require more certainty; punish for failing previous tests) and decreases in risk $\delta$ at a diminishing rate, the optimal exploration rate for Bernoulli arms derived in Theorem 10 of Garivier and Kaufmann (2016) is intuitive:
 
@@
 \begin{equation*}
-\lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\bm{\mu}}[T_{\delta}]}{\log(1/\delta)} \leq \alpha T^*(\mu).
+\limsup_{\delta \to 0} \frac{\mathbb{E}_{\bm{\mu}}[T_{\delta}]}{\log(1/\delta)} \leq \alpha T^*(\mu), \quad \text{with } T^*(\mu) \text{ as defined in equation \ref{eqn:ComplexityTrackStopStrategy}}.
 \end{equation*}
@@
 
-## Conclusion of Complexity of Best Arm Identification
+## Conclusion
 
 Overall, the two papers presented in this chapter make significant contributions to identifying the top-$1$ or the top-$m$ arms in a multi-armed bandit setting.
-Their contribution is primarily based on including the Kullback-Leibler divergence in the derivation of bounds and the matching algorithms and thus going beyond a sum of squared gaps which is most practical only in the case of Gaussian distributions.
-While the contribution in the fixed budget setting was limited to the two-armed bandit case, the authors derive general lower bounds in the fixed confidence setting which are primarily based on Lemma \ref{theorem:KaufmannEtAlLemma1}.
+Their contribution is primarily based on including the Kullback-Leibler divergence and Chernoff information as information theoretic measures in the derivation of bounds and the matching algorithms.
+Thereby, they go beyond a sum of squared gaps which is most relevant only in the case of Gaussian distributions.
+While the contribution in the fixed budget setting is limited to the two-armed bandit case, the authors derive general lower bounds in the fixed confidence setting.
+All bounds presented are primarily based on Lemma \ref{theorem:KaufmannEtAlLemma1}.
 Lemma \ref{theorem:KaufmannEtAlLemma1} is able to measure the "transportation cost" (see Garivier and Kaufmann, 2016) of moving from one distribution to another one in terms of Kullback-Leibler divergence.
-This transportation cost will increase the expected stopping time, and so the experimenter has to be careful when selecting which arm to sample.
-By picking proportions $w^*(\bm{\mu})$ that minimize the transportation cost, a solution is found with as few iterations as possible.
-
-With respect to the optimal proportions we have derived some characteristics that now allow for a few interpretations.
-First, we have demanded that the algorithm keeps arms proportions in a way that equalizes the failure probability of every arm with respect to the best arm.
-This is basically similar to keeping the weighted Jensen-Shannon divergence at the same level which was shown in Lemma 4 of Garivier and Kaufmann (2016) and which we have repeated above.
-The fact that the risk plays an important role at any round of the algorithm suggests the possibility of turning the algorithm into an anytime algorithm.
-That is, instead of relying on Chernoff's stopping rule to end the algorithm at one point, and not being able to stop the algorithm before that and receiving a meaningful result, one would be able to stop the algorithm at any iteration, and receive both the recommended best arm and a confidence level.
-Second, the idea of comparing each arm to the best arm and based on that keeping the failure probabilities at a flat level seems transferrable to the thresholding bandit problem.
-Indeed, it might even be easier as the best arm does not have to be estimated; thus, the risk with respect to this estimate goes away.
-Instead, every arm will be compared to the threshold.
-One idea might be to compute for each arm $a$ the probability that the mean $\mu_a$ is actually on the other side of the threshold as currently suggested by $\hat{\mu}_a(t)$.
-This is independent of the other arms.
-And so a strategy might be to draw arms such that their failure probabilities are at the same level (draw whatever arm has the highest failure probability).
-We will come back to this idea in chapter 3.
-
-Using the information from the lower bound of how well any $\delta$-PAC algorithm can potentially be, the authors design algorithms matching these lower bounds.
-In the case of Top-$m$ identification, a simple application of the existing KL-LUCB algorithm works.
-In the case of best arm identification, the lower bound provides a way of calculating the optimal proportions in which the arms need to be pulled.
-Consequently, a matching algorithm can be set up so that it draws arms in these proportions, and so that it is robust against estimation errors of the plug-in estimates.
-Combining this sampling rule with an appropriate stopping rule makes for a $\delta$-PAC algorithm that matches the lower bound, where the upper bound in Theorem \ref{theorem:GarivierAndKaufmannTheorem14} matches the lower bound from Theorem \ref{theorem:GarivierKaufmannTheorem1} using equation \eqref{bre_approx}.
-
-\newpage
+It is a bound on the expected likelihood ratio term that appears when changes in distribution are applied.
+
+In the case of the fixed budget top-$m$ arm identification problem, we have seen that the derivation of a lower bound on the complexity term is mostly limited by the difficulty of defining an alternative problem $\nu'$ to $\nu$ that fits into the Lemma \ref{theorem:KaufmannEtAlLemma1}.
+But given the intuition that in top-$m$ problems the $m$-th best arm and the $(m+1)$-th best arm define an implied threshold between the two groups of arms, we were able to apply the ideas of Kaufmann et al.
+(2016) to our fixed budget thresholding bandit problem.
+In contrast to their problem, arms are classified against the known threshold $\tau$, which makes it possible to define an alternative problem $\nu'$ in which we do not have to change arms with respect to each other, but only with respect to $\tau$.
+This has lead us to the simple lower bound on the problem complexity for the thresholding bandit problem with exponential family distributions given in Corollary \ref{corollary:LBKTBP}.
+
+In the best arm identification problem discussed by Garivier and Kaufmann (2016), we were introduced to the idea of comparing each arm to the best arm, and evaluating the difference between the best arm and the other arms based on the Generalized Likelihood Ratio test.
+This idea seems transferrable to the thresholding bandit problem.
+Indeed, it might even be easier as the best arm does not have to be estimated; instead, we would compare each arm to the threshold $\tau$.
+Intuitively, one can frame this problem for each arm individually as an hypothesis test between the maximum likelihood estimate of the mean and the threshold $\tau$.
+We will come back to this idea in \autoref{sec:LikelihoodRatioForExponentialFamily}.
+
+Lastly, we observe that Garivier and Kaufmann (2016) support their algorithm's main strategy by an additional D-Tracking rule which protects them against poor estimates in the beginning of the sampling.
+Such rule should be mostly unnecessary, for example, the cumulative regret setting, as algorithms there rely on upper confidence bound estimates.
+This is not the case for the Track-and-Stop strategy introduced in Garivier and Kaufmann, and neither for our Simple Likelihood Ratio strategy introduced in \autoref{sec:1DSLR}.
+In \autoref{sec:Simulation2}, we show empirically that the performance of the Simple Likelihood Ratio strategy can be further improved by naively adding the D-Tracking rule to it.
 
@@
 
-### Simulation 2: Bernoulli with $\tau = 0.05$
+### Simulation 2: Bernoulli with $\tau = 0.05$ \label{sec:Simulation2}
 
@@
 
-# Notes
-
-The author thanks Alexandra Carpentier, Andrea Locatelli, and Urun Dogan for many hours of valuable feedback and ideas.
+# Acknowledgements
+
+We thank Alexandra Carpentier, Andrea Locatelli, and Urun Dogan for many hours of fruitful discussions and ideas.
+We thank Carlo Alberto Dall'Amico for bringing our attention to multi-armed bandits in the first place.
+Sonoma Internet GmbH (Amorelie) supported this work by giving the authors access to the discussed data set.
 
@@
 
-## Proof of Corollary 1
+## Lower Bound for Thresholding Bandit Problem with KL-divergence \label{sec:corollaryLBTBPproof}
+
+### Lower Bound for One-Armed Thresholding Bandit \label{sec:corollaryLB1TBPproof}
 
@@
 
-\begin{equation}
+\begin{equation*}
 \mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_{\nu}(A). \label{eq:BoundForCorollary}
-\end{equation}
+\end{equation*}
 
@@
 $$
+
+### Lower Bound for $K$-Armed Thresholding Bandit \label{sec:corollaryLBKTBPproof}
+
+**Proof**: The proof is very similar to the proof of the corollary for $K=1$.
+However, the alternative model needs more motivation than in the case of a single arm.
+But first, consider again that we are in the thresholding bandit problem with $K$ arms of univariate canonical exponential family distributions that are parameterized by their means $\mu_1, ..., \mu_K$ for the original problem $\nu = (\nu_1, ..., \nu_K)$.
+W.l.o.g, assume that all arms are above the threshold, that is, $\mu_1 \geq \tau, ..., \mu_K \geq \tau$.
+Then $\mathcal{S}_{\tau}^* = \{1, ...
+, K\}$.
+The correct classification returned after $t$ rounds is thus the event $A = (\hat{\mathcal{S}}_{\tau} = \{1, ..., K\})$.
+We can now consider Lemma 2.
+The RHS is maximized when the alternative model is chosen such that $d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A))$ is maximized.
+Given the event $A$ as defined before, this is the case when $\mathbb{P}_{\nu'}(A)$ is as small as possible.
+For consistent algorithms, this is the case when $\nu'$ is chosen such that all $\mu_1' < \tau, ..., \mu_K' < \tau$.
+Then even classifying a single arm correctly under $\nu$ would lead to a mistake in $\nu'$.
+Consequently, $A$ is the most unlikely classification for a consistent algorithm for the problem $\nu'$.
+We thus expect for any consistent algorithm that $\mathbb{P}_{\nu}(A)$ becomes large and $\mathbb{P}_{\nu'}(A)$ becomes small as the number of observations $t$ increases.
+Again, for every $\epsilon > 0$, there exists $t_0(\epsilon)$ such that for all $t \geq t_0(\epsilon)$ we have $\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)$.
+This allows us to now use Lemma 1 as previously:
+
+\begin{align*}
+\sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\nu_i', \nu_i) & \geq \sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\tau, \mu_i) \\
+& \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)) \\
+& \geq d(\epsilon, 1-p_t(\nu)) \\
+& = \epsilon \log \Big(\frac{\epsilon}{1-p_t(\nu)}\Big) + (1-\epsilon) \log \Big( \frac{1-\epsilon}{p_t(\nu)}\Big) \\
+& \geq (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) + \epsilon \log(\epsilon)
+\end{align*}
+
+We let $\epsilon \rightarrow 0$, divide by $t$ and take the limsup on both sides as in Kaufmann et al. (2016):
+
+\begin{align*}
+\lim_{t \rightarrow \infty} \sup - \frac{1}{t} \log p_t(\nu) & \leq \lim_{t \rightarrow \infty} \sup \frac{1}{t} \sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\tau, \mu_i) \\
+& \leq \max_{i \in \{1,...,K\}} \KL(\tau, \mu_i)
+\end{align*}
+
+Though, since for the alternative problem $\nu'$ we have for every $i \in \{1,...,K\}$ that $\mu_i = \tau$, it should hold for any consistent algorithm that $\mathbb{E}_{\nu'}[N_i(t)] = \frac{t}{K}$, that is, every arm receives an equal amount of the budget.
+In that case, the above equation simplifies to
+
+$$
+- \frac{1}{t} \log p_t(\nu) \leq \frac{1}{t} \sum_{i=1}^K \frac{t}{K}\KL(\tau, \mu_i) = \frac{1}{K} \sum_{i=1}^{K} \KL(\tau, \mu_i),
+$$
+
+that is, the complexity is given by the simple average of the Kullback-Leibler distances of the threshold with regard to the respective distributions.
+This relates well to the lower bound that Kaufmann et al.
+(2016) describe in their Theorem 12 for consistent algorithms using *uniform* sampling strategies; in our case, however, it is explained by the fact that under the alternative model, every consistent algorithm should adapt to a uniform sampling strategy.
+Thus our bound holds for any consistent strategy.
 
@@
 ```
+
+## SLR Algorithm with D-Tracking Rule
+
+\IncMargin{1em}
+\begin{algorithm}
+\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
+\Input{$\tau$, $\epsilon$, class of distributions $\nu(\mu, \theta)$, $\theta_i \: \forall i \in \mathbb{A}$}
+\Output{$\hat{S}_\tau = \{i \in \mathbb{A},  \hat{\mu}_i(T) \geq \tau\}$}
+\BlankLine
+\emph{Pull each arm once}\;
+\For{$t = K+1$ \KwTo $T$}{
+  \emph{Calculate $U_t = \{i \in \mathbb{A}, T_i(t) < \sqrt{t} - K/2\}$}\;
+  \emph{Set $I_t = \arg \min_{i \in \mathbb{A}} B_i^{SLR}(t)$ as in \autoref{eqn:SLRIndex}}\;
+  \If{$U_t \neq \emptyset$}{Set $I_t = \arg \min_{i \in \mathbb{A}} T_i(t)$}
+  \emph{Pull arm $I_t$}\;
+  \emph{Observe reward $X_t \sim \nu_{I_t}$}\;
+}
+\caption{SLR algorithm with D-Tracking Rule (Garivier and Kaufmann, 2016)} \label{algo_slr_1d_dTracking}
+\end{algorithm}
+\DecMargin{1em}

### 2017-09-04 Thesis/Draft.tex
Edit second chapter

@@
 \For{$t = K+1$ \KwTo $T$}{
-  \emph{Pull arm $I_t = \arg \min_{k\leq K} B_k^{APT}(t) = \sqrt{T_k(t)} (|\hat{\mu}_i(t) - \tau|+\epsilon)$}\;
-  \emph{Observe reward $X \sim \nu_{I_t}$}\;
+  \emph{Pull arm $I_t = \arg \min_{i \in A} B_i^{APT}(t) = \arg \min_{i \in A} \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau|+\epsilon)$}\;
+  \emph{Observe reward $X_t \sim \nu_{I_t}$}\;
 }
@@
 \(i \in \{1, ..., K\}\) after the final round \(T\), require \[
-\hat{\mu}_{i,T_i(n)} \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
+\hat{\mu}_{i}(T) \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
 \] or \[
-\hat{\mu}_{i,T_i(n)} \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
+\hat{\mu}_{i}(T) \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
 \] Or simply in terms of the gap between the arm and the threshold as
 used in the index by the APT algorithm: \[
-| \hat{\mu}_{i, T_i(n)} - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
+| \hat{\mu}_{i}(T) - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
 \]
@@
 require \(\mu_i < \tau \leq \hat{\mu_i}\). But then
-\(| \hat{\mu}_{i, T_i(n)} - \mu_i | \geq |\mu_i - \tau|\), which
-violates the separation condition.
+\(| \hat{\mu}_{i}(T) - \mu_i | \geq |\mu_i - \tau|\), which violates the
+separation condition.
 
@@
 \ref{theorem:LocatelliTheorem4}. Plugging this in gives \[
-T_k(T) - 1 \geq \frac{(T-K)h_k}{H} \geq \frac{(T-1/2T)h_k}{H} = \frac{Th_i}{2H}
+T_k(T) - 1 \geq \frac{(T-K)h_k}{H} \geq \frac{(T-1/2T)h_k}{H} = \frac{Th_k}{2H}
 \]
@@
 \[
-T_k(t) \geq T_k(T) - 1 \geq \frac{Th_i}{2H}.
+T_k(t) \geq T_k(T) - 1 \geq \frac{Th_k}{2H}.
 \]
@@
 \[
-\mathbb{E}[L] = 1 - \mathbb{P}(\xi) \leq 2(\log(T)+1)K \exp(-\frac{1}{64R^2}\frac{T}{H}).
+\mathbb{E}[\mathcal{L}(T)] = 1 - \mathbb{P}(\xi) \leq 2(\log(T)+1)K \exp(-\frac{1}{64R^2}\frac{T}{H}).
 \]
@@
 
-\section{\texorpdfstring{Information Theoretic Complexity of Pure
+\section{\texorpdfstring{Information Theoretic Approaches to Pure
 Exploration Bandits
-\label{chap:KullbackLeiblerPureExploration}}{Information Theoretic Complexity of Pure Exploration Bandits }}\label{information-theoretic-complexity-of-pure-exploration-bandits}
+\label{chap:KullbackLeiblerPureExploration}}{Information Theoretic Approaches to Pure Exploration Bandits }}\label{information-theoretic-approaches-to-pure-exploration-bandits}
 
@@
 
-\subsection{\texorpdfstring{Complexity Measures for Best-Arm and
-Top-\emph{m} Identification
-\label{sec:KaufmannEtAl2016}}{Complexity Measures for Best-Arm and Top-m Identification }}\label{complexity-measures-for-best-arm-and-top-m-identification}
+\subsection{\texorpdfstring{Information Theoretic Complexity Measures in
+Top-\(m\) Problems
+\label{sec:KaufmannEtAl2016}}{Information Theoretic Complexity Measures in Top-m Problems }}\label{information-theoretic-complexity-measures-in-top-m-problems}
 
@@
 consider the problem of identifying the best \(m\) out of \(K\) arms,
-that is, the Top-\(m\) problem. They describe their a bandit model
-\(\nu\) also by \(K\) arms characterized by probability distributions
-\(\nu_a\), \(a \in \{1,...,K\}\) with mean \(\mu_a\). As before, a
-learner decides at any time step \(t=1,2,...,\) an arm
-\(A_t \in \{1,...,K\}\) for which he observes the independent reward
-\(Z_{t} \sim \nu_{A_t}\). The learner aims to find the \(m\) out of
-\(K\) arms with the largest expected reward. This set of arm indices is
-denoted by \(\mathcal{S}_m^*\). Kaufmann et al. write the in decreasing
-order sorted means \((\mu_{1}, ..., \mu_{K})\) as the K-tuple
-\((\mu_{[1]}, ..., \mu_{[K]})\). Based on this, they require that
-\(\mu_{[m]} > \mu_{[m+1]}\) such that the solution \(\mathcal{S}_m^*\)
-is unique. The class of bandit problems \(\nu\) for which the latter
-condition holds is called \(\mathcal{M}_m\) by Kaufmann et al. At the
-end of the sampling procedure, after \(T\) samples (denoted by \(\tau\)
-in Kaufmann et al.) the learner is required to return a classification
-\(\hat{\mathcal{S}}_m\). This classification is then evaluated by the
-loss function
+that is, the top-\(m\) problem. They describe their bandit model \(\nu\)
+by \(K\) arms characterized by probability distributions \(\nu_a\),
+\(a \in \{1,...,K\}\), with mean \(\mu_a\). A learner picks at any time
+step \(t=1,2,...,\) an arm \(A_t \in \{1,...,K\}\) for which he observes
+the independent reward \(Z_{t} \sim \nu_{A_t}\). The learner aims to
+find the \(m\) out of \(K\) arms with the largest expected reward. This
+set of arm indices is denoted by \(\mathcal{S}_m^*\). Kaufmann et al.
+write the means \((\mu_{1}, ..., \mu_{K})\) sorted in decreasing order
+as the K-tuple \((\mu_{[1]}, ..., \mu_{[K]})\). Based on this, they
+require that \(\mu_{[m]} > \mu_{[m+1]}\) such that the solution
+\(\mathcal{S}_m^*\) is unique. The class of bandit problems \(\nu\) for
+which the latter condition holds is called \(\mathcal{M}_m\) by Kaufmann
+et al. At the end of the sampling procedure, after \(T\) samples
+(denoted by \(\tau\) in Kaufmann et al.) the learner is required to
+return a classification \(\hat{\mathcal{S}}_m\). This classification is
+then evaluated by the loss function
 \(\mathcal{L}(T) = \mathbb{I}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m)\).
-This binary loss is of course very similar to the loss in the
-thresholding bandit problem. We can now define a strategy of the learner
-as \(\mathcal{A} = ((A_t), T, \hat{\mathcal{S}}_m)\): The strategy
-defines how he chooses an arm, how many samples are observed, and how
-the arms are classified in the end.
+This binary loss is similar to the loss in the thresholding bandit. We
+can now define a strategy of the learner as
+\(\mathcal{A} = ((A_t), T, \hat{\mathcal{S}}_m)\): The strategy defines
+how an arm is chosen, how many samples are observed, and how the arms
+are eventually classified.
 
@@
 as we have seen in \(\autoref{sec:Setup}\). Alternatively, consider a
-\(\delta\)-PAC strategy \(\mathcal{A}(\delta)\)for which holds for every
-problem \(\nu \in \mathcal{M}_m\) that the classification holds at least
-with confidence level \(1-\delta\), that is,
+\(\delta\)-PAC strategy \(\mathcal{A}(\delta)\)for which it holds for
+every problem \(\nu \in \mathcal{M}_m\) that the classification holds at
+least with confidence level \(1-\delta\), that is,
 \(\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta\). The
@@
 before it is allowed to stop sampling. This is the fixed confidence
-case, in which the budget \(T\) is no longer fixed upfront, but becomes
-a random variable. We compare algorithms by their expected number of
-draws \(\mathbb{E}_{\nu}[T_{\delta}]\) and prefer those which arrive at
-the confidence level \(1-\delta\) with a smaller expected budget.
-
-Following Kaufmann et al. (2016), in the fixed confidence setting, a
-family of strategies \(A = (\mathcal{A}(\delta))_{\delta \in (0,1)}\) is
-called PAC if for every \(\delta\), \(\mathcal{A}(\delta)\) is
-\(\delta\)-PAC. On the other hand, in the fixed budget setting, a family
-of strategies \(A = (\mathcal{A}(t))_{t \in \mathbb{N}}\) is called
-consistent if \(p_t(\nu) \rightarrow 0\) as \(t \rightarrow \infty\) for
-every problem \(\nu \in \mathcal{M}_m\).
+case, in which the budget \(T\) is no longer fixed upfront, but turns
+into a random variable. Algorithms are then compared by their expected
+number of draws \(\mathbb{E}_{\nu}[T_{\delta}]\) and we prefer those
+which achieve the confidence level \(1-\delta\) with a smaller expected
+budget.
+
+In the fixed confidence setting, a family of strategies
+\(A = (\mathcal{A}(\delta))_{\delta \in (0,1)}\) is called PAC if for
+every \(\delta\), \(\mathcal{A}(\delta)\) is \(\delta\)-PAC. On the
+other hand, in the fixed budget setting, a family of strategies
+\(A = (\mathcal{A}(t))_{t \in \mathbb{N}}\) is called consistent if
+\(p_t(\nu) \rightarrow 0\) as \(t \rightarrow \infty\) for every problem
+\(\nu \in \mathcal{M}_m\).
 
 Given this setup, we can now follow the arguments of Kaufmann et al.
-(2016) to deduce complexity measures for the top-\(m\) problem. As
+(2016) to derive complexity measures for the top-\(m\) problem. As
 alluded to earlier, these complexity measures will rely on the
-Kullback-Leibler divergence in contrast to the complexity \(H\) used by
-Locatelli et al. (2016). Also, when discussing \(H\), we so far
-described it as complexity as it measures the difficulty of the problem
-by measuring the distance between arms and the threshold. Kaufmann et
-al. approach complexity instead from how many samples (what error
-probability) one can expect to need in the fixed confidence (fixed
-budget) setting. Thus, in order to arrive at their new measure of
+KL-divergence in contrast to the complexity \(H\) used by Locatelli et
+al. (2016). When discussing \(H\), its motivation is that it represents
+the difficulty of the problem by measuring the distance between arms and
+the threshold. Instead, Kaufmann et al. approach complexity by how many
+samples (what error probability) one will need in the fixed confidence
+(fixed budget) setting. In order to arrive at their new measure of
 complexity, it makes sense to first follow their arguments to a general
-lower bound on the sample complexity \(\mathbb{E}_{\nu}[\tau]\) in the
-case of fixed confidence top-\(m\) problems. This bound is given in
-their Theorem 4 (for common confidence levels of \(\delta \leq 0.15\)).
+lower bound on the sample complexity \(\mathbb{E}_{\nu}[\tau]\) which is
+given in their Theorem 4:
 
@@
 \(\mathcal{A}\), we assume certain continuity conditions (compare
-Kaufmann et al. (2016)), with which there exists for every arm
+Kaufmann et al. (2016)) under which there exists for every arm
 \(a \in \{1, \dots, K\}\) an alternative model
@@
 
-Given that the strategy returns \(\hat{S}_m\), we know that for the
-event \(\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})\) (which is element
-of the \(\sigma\)-Algebra \(\mathcal{F}_{T}\) induced by the stopping
-time \(T\)), that \(\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta\) and
+Given the strategy returns \(\hat{S}_m\), we know that for the event
+\(\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})\) (which is element of the
+\(\sigma\)-Algebra \(\mathcal{F}_{T}\) induced by the stopping time
+\(T\)), that \(\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta\) and
 \(\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta\) (because fixed confidence
-\(\delta\)!). To now give the lower bound on the expected number of
-samples, \(\mathbb{E}_{\nu}[\tau]\), we employ the general Lemma given
-by the authors for such changes in distribution in bandit models.
-
-\begin{lemma}[Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma1}
+\(\delta\)!). To give the lower bound on the expected number of samples,
+\(\mathbb{E}_{\nu}[\tau]\), we employ the general Lemma given by the
+authors for such changes in distribution in bandit models.
+
+\begin{lemma}[Lemma 1, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma1}
 Let $\nu$ and $\nu'$ be two bandit models with $K$ arms such that for all $a$, the distributions $\nu_a$ and $\nu_a'$ are mutually absolutely continuous.
@@
 \begin{equation*}
-\sum_{a=1}^{K} \mathbb{E}_{\nu} [N_a(\sigma)] \KL(\nu_a, \nu_a') \geq \sup_{\mathcal{E} \in \mathcal{F}_{\sigma}} \der (\mathbb{P}_{\nu}(\mathcal{E}), \mathbb{P}_{\nu'}(\mathcal{E})),
+\sum_{a=1}^{K} \mathbb{E}_{\nu} [N_a(\sigma)] \KL(\nu_a|| \nu_a') \geq \sup_{\mathcal{E} \in \mathcal{F}_{\sigma}} \der (\mathbb{P}_{\nu}(\mathcal{E}), \mathbb{P}_{\nu'}(\mathcal{E})).
 \end{equation*}
-
-where $d(x,y)$ is the binary relative entropy as defined above.
 \end{lemma}
 
-We can apply this Lemma directly on the expected number of draws for
-each arm, \(\mathbb{E}_{\nu}[N_a]\). For each arm \(a\), we thus have
+We apply this Lemma directly on the expected number of draws for each
+arm, \(\mathbb{E}_{\nu}[N_a]\). For each arm \(a\), we thus have
 \(\KL(\nu_a, \nu_a') \mathbb{E}_{\nu}[N_a] \geq d(1-\delta, \delta)\).
 Using the definition of the alternative model above, we get for every
-small but fixed \(\alpha > 0\), for every arm \(a \in \{1, \dots, K\}\)
-and each arm \(b \in \{m+1, \dots, K\}\):
+small but fixed \(\alpha > 0\), every arm \(a \in \{1, \dots, K\}\) and
+\(b \in \{m+1, \dots, K\}\):
 
 \begin{equation*}
-\mathbb{E}_{\nu}[N_a] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_a, \nu_{m+1}) + \alpha}
+\mathbb{E}_{\nu}[N_a] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_a || \nu_{m+1}) + \alpha} \quad \text{and} \quad \mathbb{E}_{\nu}[N_b] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_b || \nu_{m}) + \alpha}.
 \end{equation*}
 
-and
+Let \(\alpha \to 0\), sum the individual arms' bounds to get the bound
+on the overall number of draws:
 
 \begin{equation*}
-\mathbb{E}_{\nu}[N_b] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_b, \nu_{m}) + \alpha}.
-\end{equation*}
-
-We can then let \(\alpha \to 0\), sum the bounds on the individual arms
-to get the bound on the overall number of draws:
-
-\begin{equation*}
-\mathbb{E}_{\nu}[T] = \sum_{a=1}^K \mathbb{E}_{\nu}[N_a] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \der(1-\delta, \delta)
+\mathbb{E}_{\nu}[T] = \sum_{a=1}^K \mathbb{E}_{\nu}[N_a] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m]})} \Big) \der(1-\delta, \delta)
 \end{equation*}
@@
 \begin{equation*}
-\mathbb{E}_{\nu}[T] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
+\mathbb{E}_{\nu}[T] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
 \end{equation*}
 
-Given this lower bound, it becomes clear that the complexity of the
-top-\(m\) problem can be lower bounded by the Kullback-Leibler
-divergence between arms and the implied threshold between the \(m\)-th
-best arm and the \((m+1)\)-th best arm. After all, the latter gives a
-lower bound on the effort (in terms of expected number of samples)
-required to achieve a certain confidence level. And a problem that
-requires a larger effort can be described as more complex. Indeed, in
-the case of fixed confidence problems, Kaufmann et al. (2016) describe
-problems as having a larger \emph{sampling complexity}.
-
-Following Kaufmann et al. (2016), we can now define the complexity
-\(\kappa_C(\nu)\) for the fixed confidence setting as
+Given this lower bound, it is clear that the complexity of the top-\(m\)
+problem can be lower bounded by the KL-divergence between arms and the
+implied threshold between the \(m\)-th best arm and the \((m+1)\)-th
+best arm. The latter gives a lower bound on the effort (in terms of
+expected number of samples) required to achieve a certain confidence
+level, where a problem that requires a larger effort is described as
+more complex. Indeed, in the case of fixed confidence problems, Kaufmann
+et al. (2016) describe problems as having a larger \emph{sampling
+complexity}.
+
+Following Kaufmann et al. (2016), we define the complexity
+\(\kappa_C(\nu)\) in the fixed confidence setting as
 
 \begin{equation}
-\kappa_C(\nu) = \inf_{A \, \text{PAC}} \lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\nu}[T{\delta}]}{\log \frac{1}{\delta}}. \label{eq:KappaC}
+\kappa_C(\nu) = \inf_{A \, \text{PAC}} \limsup_{\delta \to 0} \frac{\mathbb{E}_{\nu}[T{\delta}]}{\log \frac{1}{\delta}}. \label{eq:KappaC}
 \end{equation}
@@
 divides the group above the threshold from the group below the
-threshold.
-
-However, given the problem formulation in Locatelli et al. (2016), we
-are mainly interested in complexity measures and algorithms for the
-fixed budget setting. As we will see now, the results of Kaufmann et al.
-(2016) are more limited for this case. While the authors are able to
-provide a bound on their complexity measure in the fixed budget case, it
-only applies to the case of \emph{two-armed} bandit models. Consider a
-consistent fixed budget strategy \(\mathcal{A}\) (\(p_t(\nu)\) tends to
-zero as \(t \rightarrow \infty\)), and define the complexity in the
-fixed budget setting as follows:
+threshold. But given the setting in Locatelli et al. (2016), we are
+mainly interested in complexity measures and algorithms for the fixed
+budget problem. The results of Kaufmann et al. (2016) are more limited
+for this case. While the authors are able to provide a bound on their
+complexity measure in the fixed budget case, it only applies to the case
+of \emph{two-armed} bandit models.
+
+Consider a consistent fixed budget strategy \(\mathcal{A}\)
+(\(p_t(\nu)\) tends to zero as \(t \rightarrow \infty\)), and define the
+complexity in the fixed budget setting as follows:
 
 \begin{equation}
-\kappa_B(\nu) = \inf_{A \, \text{consistent}} \big(\lim_{t \to \infty} \sup - \frac{1}{t} \log p_t(\nu)\big)^{-1}.
+\kappa_B(\nu) = \inf_{A \, \text{consistent}} \big(\limsup_{t \to \infty} - \frac{1}{t} \log p_t(\nu)\big)^{-1}.
 \end{equation}
@@
 While we included the experimenter-fixed \(\delta\) in the definition of
-\(\kappa_C\), we now include the experimenter-fixed \(T\) in the
-definition of \(\kappa_B\) to disregard it in the complexity measure
-after plugging in the lower bound on \(p_t(\nu)\). The resulting lower
-bound given in Theorem 12 of Kaufmann et al. (2016):
+\(\kappa_C\), we now include the fixed \(T\) in the definition of
+\(\kappa_B\) to disregard it in the complexity measure after plugging in
+the lower bound on \(p_t(\nu)\). The resulting lower bound given in
+Theorem 12 of Kaufmann et al. (2016):
 
@@
 \(\nu'\), where we fix w.l.o.g. \(a^* = 1\) as the best arm in \(\nu\),
-while \(a^* = 2\) in \(\nu'\). Note that in this case we don't
-necessarily try to fool the algorithm by a change of distribution.
-Indeed, we want the algorithm \(\mathcal{A}\) to be consistent for both
-problems. Since we are in the fixed budget setting, the stopping time is
-fixed at \(T = t\). Even though the correct decision differs between the
-two problems, we focus on the event \(A = (\hat{S}_1 = 1)\). Now, we can
-apply Lemma 1 as before, as it in essence gives a measure of how
-different two bandit models are. Here, we want to know how different
-\(\nu\) is from \(\nu'\), and so, given we have only two arms,
+while \(a^* = 2\) in \(\nu'\). We require the algorithm \(\mathcal{A}\)
+to be consistent for both problems. Since we are in the fixed budget
+setting, the stopping time is fixed at \(T = t\). The correct decision
+differs between the two problems, and we focus on the event
+\(A = (\hat{S}_1 = 1)\). Now, we can apply Lemma 1 from Kaufmann et al.
+(2016) as before, as it gives a measure of how different two bandit
+models are (it bounds the change in distribution). Here, we want to know
+how different \(\nu\) is from \(\nu'\), and, given we have only two
+arms,
 
 \begin{equation*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2', \nu_2) \geq \der(\mathbb{P}_{\nu'}(A),\mathbb{P}_{\nu}(A)))
+\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1'|| \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2'|| \nu_2) \geq \der(\mathbb{P}_{\nu'}(A),\mathbb{P}_{\nu}(A)))
 \end{equation*}
@@
 \(| \KL(\nu_1', \nu_1) - \KL(\nu_2', \nu_2) |\) is as small as possible.
-
-Note that while deriving the lower bound on the complexity measure, we
-have also derived the following lower bound on the failure probability
-for the two-armed fixed budget bandit:
-
-\begin{equation*}
-p_t(\nu) \geq \exp \big(- \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)] \KL(\nu_a', \nu_a) \big)
-\end{equation*}
-
-or, to not rely on the share of samples attributed to each arm,
-
-\begin{equation*}
-p_t(\nu) \geq \exp \big(- \max_{a=1,2} \KL(\nu_a', \nu_a) \big).
-\end{equation*}
 
@@
 
-Before we discuss the strategies of Kaufmann et al. (2016) matching the
-lower bounds, we now show how lower bounds can be derived very similarly
+Before we discuss algorithms given in Kaufmann et al. (2016) that match
+the lower bounds, we show how lower bounds can be derived very similarly
 for the fixed budget thresholding problem.
 
-\subsubsection{Lower Bound for Fixed Budget Thresholding
-Problem}\label{lower-bound-for-fixed-budget-thresholding-problem}
+\subsubsection{\texorpdfstring{Lower Bound for Fixed Budget Thresholding
+Problem
+\label{sec:LBTBP}}{Lower Bound for Fixed Budget Thresholding Problem }}\label{lower-bound-for-fixed-budget-thresholding-problem}
 
 In order to derive a bound for the fixed budget problem, Kaufmann et al.
-(2016) have focused on the case of the two-armed bandit which is the
-most simple version of the top-\(m\) problem. Less than two arms do not
-make sense, since then this single arm will always be the best arm. In
-the case of the thresholding bandit, however, a single-armed problem
-makes still some sense in that we still have to classify this arm
+(2016) have focused on the setting with two arms which is the most
+simple version of the top-\(m\) problem. Less than two arms do not make
+sense, since the single arm is by definition the best arm. In the case
+of the thresholding bandit, however, a single-armed problem makes still
+at least limited sense in that we still have to classify this arm
 correctly with respect to the threshold. Thus, we can show the following
-corollary which gives the a bound on the complexity of the single-armed
+corollary which gives a bound on the complexity of the single-armed
 thresholding bandit.
@@
 Let $\nu = \nu_1$ be a one-armed thresholding bandit model where $\tau$ is the threshold fixed upfront.
-Let $\nu$ be from the univariate canonical exponential family of distributions such that it can be parameterized by its mean, $\mu_1$, and the Kullback-Leibler divergence between distributions $\nu_1$ and $\nu_1'$ can be written as $\KL(\nu_1', \nu_1) = \KL(\mu_1', \mu_1)$.
-In the fixed budget setting, any consistent algorithm satisfies:
+Let $\nu$ be from the univariate exponential family of distributions such that $\nu_1$ can be parameterized by its mean, $\mu_1$, and the Kullback-Leibler divergence between distributions $\nu_1$ and $\nu_1'$ can be written as $\KL(\nu_1', \nu_1) = \KL(\mu_1', \mu_1)$.
+In the fixed budget setting, any consistent algorithm ($p_t(\nu) \rightarrow 0$ as $t \rightarrow \infty$) satisfies:
 
 $$
-\lim_{t \rightarrow \infty}- \frac{1}{t} \log p_t(\nu) \leq \KL(\tau, \mu_1)
+- \frac{1}{t} \log p_t(\nu) \leq \KL(\tau || \mu_1)
 $$
@@
 
-This of course is basically the Chernoff-Stein Lemma for the hypothesis
-test of two alternatives (compare chapter 11 in Cover and Thomas, 2006).
+\label{corollary:LB1TBP}
+
+This is basically the Chernoff-Stein Lemma for the hypothesis test of
+two alternatives (compare chapter 11 in Cover and Thomas, 2006, or
+\autoref{theorem:ChernoffStein}). We arrive at this result as the
+one-armed bandit does not require sequential sampling: The single arm
+receives all samples. \(\mathbb{E}_{\nu'}[N_1(t)]\) is not a random
+variable but equals \(T\).
 
@@
 stands in contrast to the fact that for the top-\(m\) problem, it is
-only possible to show the lower bound for two arms.
+only possible to show the lower bound for two arms. The result is based
+on an alternative setting \(\nu'\) in which all arms have means
+\(\mu' = \tau\) such that their expected number of pulls corresponds to
+uniform sampling, \(\mathbb{E}_{\nu'}[N_i(t)] = T/K\).
 
@@
 Let $\nu = (\nu_1, ..., \nu_K)$ be a $K$-armed thresholding bandit problem in which $\tau$ is the threshold fixed upfront.
-For $i \in \{1,...,K\}$, let $\nu_i$ be from the univariate canonical exponential family of distributions such that it can be parameterized by its mean, $\mu_i$, and the Kullback-Leibler divergence between distributions $\nu_i$ and $\nu_i'$ can be written as $\KL(\nu_i, \nu_i') = \KL(\mu_i, \mu_i')$.
-In the fixed budget setting, every consistent algorithm satisfies:
+For $i \in \{1,...,K\}$, let $\nu_i$ be from the univariate exponential family of distributions such that $\nu_i$ can be parameterized by its mean, $\mu_i$, and the Kullback-Leibler divergence between distributions $\nu_i$ and $\nu_i'$ can be written as $\KL(\nu_i, \nu_i') = \KL(\mu_i, \mu_i')$.
+In the fixed budget setting, any consistent algorithm satisfies:
 
 $$
-\lim_{t \rightarrow \infty} -\frac{1}{t} \log p_t(\nu) \leq \max_{a \in \{1,...,K\}} \KL(\tau, \mu_a)
+\limsup_{t \rightarrow \infty} -\frac{1}{t} \log p_t(\nu) \leq \max_{a \in \{1,...,K\}} \KL(\tau || \mu_a)
+$$
+
+or
+
+$$
+- \frac{1}{t} \log p_t(\nu) \leq \frac{1}{K}\sum_{i=1}^{K} \KL(\tau || \mu_i),
 $$
@@
 
-Given the lower bounds on the sampling complexity and error probability,
-as well as the complexity measures, we now turn to sampling strategies
-that are designed to match these lower bounds.
-
-\subsubsection{Matching algorithm
-strategies}\label{matching-algorithm-strategies}
+\label{corollary:LBKTBP}
+
+We present the proofs of \autoref{sec:LBTBP} in the appendix in
+\autoref{sec:corollaryLBTBPproof}. Corresponding to the complexity
+measures defined in equation \((1)\) of Kaufmann et al. (2016), we can
+define the complexity \(\kappa_{TBP}(\nu)\) in the thresholding bandit
+problem and lower bound it:
+
+\[
+\kappa_{TBP}(\nu) = \inf_{A consistent} \Big(\limsup_{t \rightarrow \infty} - \frac{1}{t} \log p_t(\nu)\Big)^{-1} \geq K \Big(\sum_{i=1}^{K} \KL(\tau||\mu_i)\Big)^{-1}
+\]
+
+\subsubsection{\texorpdfstring{Strategies Matching the Top-\(m\) Lower
+Bound}{Strategies Matching the Top-m Lower Bound}}\label{strategies-matching-the-top-m-lower-bound}
 
@@
 
-Thus, Kaufmann et al. (2016) join a number of other papers like Audibert
-et al. (2010) and Kaufmann and Kalyanakrishnan (2013) which struggle to
-find matching strategies in the fixed budget setting that do not rely on
+Thus, Kaufmann et al. (2016) joins other papers like Audibert et al.
+(2010) and Kaufmann and Kalyanakrishnan (2013) which struggle to find
+matching strategies in the fixed budget setting that do not rely on
 knowledge of parameters or the complexity of the problem.
@@
 complexity measure derived for the fixed confidence setting,
-\(\kappa_C(\nu)\), can be upper-bounded using the upper bound given for
-the KL-LUCB algorithm in Kaufmann and Kalyanakrishnan (2013).
-Consequently, in the case of exponential family bandits, the complexity
-\(\kappa_C(\nu)\) is bounded as given in equation (6) in Kaufmann et al.
-(2016):
+\(\kappa_C(\nu)\), can be upper-bounded using the bound given for the
+KL-LUCB algorithm in Kaufmann and Kalyanakrishnan (2013). In the case of
+exponential family bandits, the complexity \(\kappa_C(\nu)\) is bounded
+as given in equation (6) in Kaufmann et al. (2016):
 
 \begin{equation*}
-\sum_{a \in S^*_m} \frac{1}{K(\theta_a, \theta_{[m+1]})} + \sum_{a \notin S^*_m} \frac{1}{K(\theta_a,\theta_{[m]})} \leq \kappa_C(\nu) \leq 24 \min_{\theta \in [\theta_{[m+1]},\theta_{[m]}]} \sum_{a=1}^{K} \frac{1}{K^*(\theta_a, \theta)},
+\sum_{a \in S^*_m} \frac{1}{\KL(\theta_a || \theta_{[m+1]})} + \sum_{a \notin S^*_m} \frac{1}{\KL(\theta_a || \theta_{[m]})} \leq \kappa_C(\nu) \leq 24 \min_{\theta \in [\theta_{[m+1]},\theta_{[m]}]} \sum_{a=1}^{K} \frac{1}{\KL^*(\theta_a || \theta)},
 \end{equation*}
 
-where \(K(\theta, \theta') = \KL(\nu_{\theta}, \nu_{\theta'})\) for
-\((\theta, \theta') \in \Theta^2\) was defined as the shorthand for the
-Kullback-Leibler divergence for two distributions from the exponential
-family parameterized by \(\theta\) and \(\theta'\) respectively.
-\(K^*(\theta,\theta') = K(\theta^*, \theta)\) is the Chernoff
-distribution between the two distributions, where \(\theta^*\) is chosen
-so that \(K(\theta^*,\theta) = K(\theta^*, \theta')\).
-
-\subsection{\texorpdfstring{Optimal Best Arm Identification
-\label{sec:OptimalBestArmIdentification}}{Optimal Best Arm Identification }}\label{optimal-best-arm-identification}
+where again we write with slight abuse of notation
+\(\KL(\theta || \theta') = \KL(\nu_{\theta}|| \nu_{\theta'})\) for
+\((\theta, \theta') \in \Theta^2\) as the shorthand for the
+KL-divergence of two distributions from the exponential family
+parameterized by \(\theta\) and \(\theta'\) respectively.
+\(\KL^*(\theta || \theta') = \KL(\theta^* || \theta)\) is the Chernoff
+information between the two distributions, where \(\theta^*\) is chosen
+so that \(\KL(\theta^* || \theta) = \KL(\theta^* || \theta')\).
+
+\subsection{\texorpdfstring{Information Theoretic Approach to Best Arm
+Identification
+\label{sec:OptimalBestArmIdentification}}{Information Theoretic Approach to Best Arm Identification }}\label{information-theoretic-approach-to-best-arm-identification}
 
 Instead of discussing the KL-LUCB algorithm for the fixed confidence
-top-\(m\) problem, we shift our focus slightly onto the fixed confidence
-best arm identification problem, which is discussed in Garivier and
-Kaufmann (2016). The authors derive again a lower bound on the sample
-complexity using again the Lemma \autoref{theorem:KaufmannEtAlLemma1}.
-Furthermore, they propose a matching strategy for \(K \geq 2\) arms.
+top-\(m\) problem, we shift our focus onto the fixed confidence best arm
+identification problem, as discussed in Garivier and Kaufmann (2016).
+The authors also derive a lower bound on the sample complexity using the
+Lemma \autoref{theorem:KaufmannEtAlLemma1}. Furthermore, they propose a
+matching strategy for \(K \geq 2\) arms.
 
@@
 family of distributions, which can be parameterized by their mean
-\(\stackrel{.}{b}(\theta) = \mu\), and thus can be written as
-\(\nu^{\mu}\); for these, we write the Kullback-Leibler divergence as
-(compare \autoref{sec:LRforUnivariateExponentialFamily} and Cappé et
-al., 2013)
-
-\begin{equation*}
-\KL(\mu, \mu') = \KL(\nu_{\mu},\nu_{\mu'}) = \KL(\nu_{\theta},\nu_{\theta'}) = \KL(\nu, \nu').
-\end{equation*}
+\(\mu\), and thus can be written as \(\nu_{\mu}\); as before, we
+simplify the notation of the KL-divergence for these distributions to
+\(\KL(\nu || \nu') = \KL(\mu || \mu')\).
 
@@
 \(\mu_{a^*} > \max_{a \neq a^*(\bm{\mu})} \mu_a\). In order to fix the
-confidence, we specify the risk \(\delta\). Similar to the top-\(m\)
-case considered before, strategies corresponding to this risk are called
-\(\delta\)-PAC if for every \(\bm{\mu} \in \mathcal{S}\), the strategy
-ends surely after a finite number of samples,
+confidence \(1-\delta\), we specify the risk \(\delta\). Similar to the
+top-\(m\) case considered before, strategies corresponding to this risk
+are called \(\delta\)-PAC if for every \(\bm{\mu} \in \mathcal{S}\), the
+strategy ends surely after a finite number of samples,
 \(\mathbb{P}_{\bm{\mu}}(T_{\delta} < \infty) = 1\), and the error
@@
 \(\mathbb{E}[T]\) through a change in distributions, we introduce the
-set of problems for which the optimal arm is different from
+set of alternative problems for which the optimal arm is different from
 \(\bm{\mu}\):
@@
 \begin{equation*}
-\text{Alt}(\bm{\mu}) := \{\bm{\lambda} \in \mathcal{S}: a^*(\bm{\lambda}) \neq a^*(\bm{\mu})\}
+\text{Alt}(\bm{\mu}) := \{\bm{\lambda} \in \mathcal{S}: a^*(\bm{\lambda}) \neq a^*(\bm{\mu})\},
 \end{equation*}
@@
 where \(\bm{\lambda}\) is the vector of means defining the distributions
-of the alternative problem to \(\bm{\mu}\). Lastly, we have the set of
-probability distributions on the arms \(\{1,...,K\}\):
+of the alternative problem. Lastly, we have the set of probability
+distributions on the arms \(\{1,...,K\}\):
 \(\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}\). Each
-\(w_i\) corresponds to the fraction of overall samples that the arm
-\(i\) receives. We are now ready to state the lower bound:
+\(w_i\) corresponds to the fraction of overall samples that arm \(i\)
+receives. We now state the lower bound:
 
@@
 
-We see that the two bounds on the sample complexity (one for Top-\(m\),
-one for best arm identification) differ only in the way in which they
-build the sum of Kullback-Leibler divergences over the \(K\) arms. In
-contrast to Theorem \ref{theorem:KaufmannEtAlTheorem4}, here the
-contribution of each arm through its KL-divergence is weighted. The
-difference is that while we were able to very clearly describe the
-change of distribution in the Top-\(m\) case for each arm -- we
-specified an alternative model for each arm that yields a new set of
-\(m\) optimal arms -- we now consider all alternative models that yield
-a different best arm than the model \(\bm{\mu}\). In the previous
-theorem, we sum over the complexity of each individual arm, as the
-change in distribution only ever touches one arm, thus leading to a
-KL-divergence of 0 for the other arms while still changing the optimal
-set. Here, we consider all instances of alternative models
-\(\bm{\lambda}\), and thus also those in which several arms are modified
-(and thus have a KL-divergence unequal 0 in the result of Lemma 1).
-
-\emph{Proof of Theorem \ref{theorem:GarivierKaufmannTheorem1}}: As
-stated before, we let \(\delta \in (0,1)\),
-\(\bm{\mu} \in \mathcal{S}\), and only consider \(\delta\)-PAC
-strategies. As before, \(N_a(t)\) describes the random number of pulls
-of arm \(a\) until time \(t\), for all \(t\geq 1\). Again, Lemma
-\ref{theorem:KaufmannEtAlLemma1} states how the risk \(\delta\) relates
-to the expected number of draws of each arm given two models which
-differ in their optimal arm. How much the two models differ is evaluated
-based on the Kullback-Leibler divergence for each pair of arms:
+We see that the two bounds given in Theorem
+\ref{theorem:KaufmannEtAlTheorem4} and Theorem
+\ref{theorem:GarivierKaufmannTheorem1} on the sample complexity differ
+only in the way in which they sum the Kullback-Leibler divergences over
+the \(K\) arms. In contrast to Theorem
+\ref{theorem:KaufmannEtAlTheorem4}, here the contribution of each arm
+through its KL-divergence is weighted. The difference is that while we
+were able to clearly describe the change of distribution in the
+top-\(m\) case for each arm -- we specified an alternative model for
+each arm that yields a new set of \(m\) optimal arms -- we now consider
+all alternative models that yield a different best arm than the model
+\(\bm{\mu}\). In the previous theorem, we sum over the complexity of
+each individual arm, since the change in distribution only affects one
+arm at a time, thus leading to a KL-divergence of 0 for the other arms
+while still changing the optimal set. Now, we consider all instances of
+alternative models \(\bm{\lambda}\), and thus also those in which
+several arms are modified (and thus have a KL-divergence unequal 0 in
+the result of Lemma 1).
+
+To proof Theorem \ref{theorem:GarivierKaufmannTheorem1}, we let
+\(\delta \in (0,1)\), \(\bm{\mu} \in \mathcal{S}\), and only consider
+\(\delta\)-PAC strategies. As before, \(N_a(t)\) describes the random
+number of pulls of arm \(a\) until time \(t\), for all \(t\geq 1\).
+Again, Lemma \ref{theorem:KaufmannEtAlLemma1} states how the risk
+\(\delta\) relates to the expected number of draws of each arm given two
+models which differ in their optimal arm. How much the two models differ
+is evaluated based on the KL-divergence for each pair of arms:
 
@@
 and use the fact that
-\(\mathbb{E}_{\bm{\mu}}[\tau_{\delta}] = \sum_{a=1}^K \mathbb{E}_{\bm{\mu}}[N_a(\tau_{\delta})]\):
+\(\mathbb{E}_{\bm{\mu}}[T_{\delta}] = \sum_{a=1}^K \mathbb{E}_{\bm{\mu}}[N_a(T_{\delta})]\):
 
 \begin{align*}
-\der(\delta, 1-\delta) & \leq \inf_{\lambda \in \text{Alt}(\bm{\mu})} \mathbb{E}_{\bm{\mu}}[\tau_{\delta}] \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[\tau_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
-& = \mathbb{E}_{\bm{\mu}}[\tau_{\delta}] \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[\tau_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
-& \leq \mathbb{E}_{\bm{\mu}}[\tau_{\delta}] \sup_{w \in \Sigma_K} \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K w_a \KL(\mu_a, \lambda_a)\Big).
+\der(\delta, 1-\delta) & \leq \inf_{\lambda \in \text{Alt}(\bm{\mu})} \mathbb{E}_{\bm{\mu}}[T_{\delta}] \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[T_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
+& = \mathbb{E}_{\bm{\mu}}[T_{\delta}] \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[T_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
+& \leq \mathbb{E}_{\bm{\mu}}[T_{\delta}] \sup_{w \in \Sigma_K} \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K w_a \KL(\mu_a, \lambda_a)\Big).
 \end{align*}
@@
 As stated in Garivier and Kaufmann (2016), the term
-\(\frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[\tau_{\delta}]}\)
+\(\frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[T_{\delta}]}\)
 gives the fraction of draws each arm receives. This value, however,
@@
 
-This lower bound can be interpreted as a Minimax game, where the
-experimenter has to choose the share of samples he attributes to each
-arm in a way that is optimal given that nature will respond and choose
-the most difficult alternative model given his weights. Thus, to make
-the lower bound practical, it is a matter of finding the optimal weights
+This lower bound can be interpreted as a minimax game\footnote{See the
+  presentation by Aurélien Garivier at COLT 2016:
+  \url{https://youtu.be/eLyrrYqJlkE}}, where the experimenter has to
+choose the share of samples he attributes to each arm in a way that is
+optimal given that nature will respond and choose the most difficult
+alternative model given his weights. Thus, to make the lower bound
+practical, it is a matter of finding the optimal weights
 \(w^*(\bm{\mu})\). This step did not occur in the lower bound for the
@@
 Indeed, the optimal weights will lead to a sampling structure in which
-arms are drawn in a way that ensures that their individual probability
-of error stays at the same level. An arm more distant from the optimal
-arm in terms of Kullback-Leibler divergence should receive a smaller
-share of the samples to achieve the same error probability as an arm
-closer to the optimal arm.
-
-This is exactly what happens when we look for the proportions
-\(w \in \Sigma_K\) that minimize the cost from a change in
-distributions, that is, the term
+arms are drawn such that their individual probabilities of error stay at
+the same level. An arm more distant from the optimal arm in terms of
+Kullback-Leibler divergence should receive a smaller share of the
+samples to achieve the same error probability as an arm closer to the
+optimal arm.
+
+This is what happens when we look for proportions \(w \in \Sigma_K\)
+that minimize the cost from a change in distributions, that is, the term
 \(F(\bm{\mu}, \bm{w}) = \inf_{\bm{\lambda} \in \text{Alt}(\bm{\mu})} \Big(\sum_{a= 1}^K w_a \KL(\mu_a, \lambda_a)\Big)\).
 In the proof of Lemma 3 of Garivier and Kaufmann, it is shown that
-nature, selecting the alternative model \(\bm{\lambda}\) will always
+nature, selecting the alternative model \(\bm{\lambda}\), will always
 pick an alternative model in which only a single arm \(a\) is changed
@@
 (2016)), we can now introduce the \emph{Track-and-Stop} strategy given
-in Garivier and Kaufmann (2016) that is able to match the lower bound by
-the intuition given above. The main idea of the \emph{Track-and-Stop}
-algorithm is now to keep track of the optimal shares for each arm by
-equalizing the error probabilies for each arm.
-
-When going from theory to algorithm, the obvious problem is of course
-that we do no longer know \(\bm{\mu}\) and thus cannot simply calculate
-the optimal weights. Instead, we are estimating the maximum likelihood
+in Garivier and Kaufmann (2016) that is able to match the lower bound.
+The main idea of the \emph{Track-and-Stop} algorithm is now to keep
+track of the optimal shares for each arm by equalizing the error
+probabilies for each arm.
+
+When going from theory to algorithm, the obvious problem is that we no
+longer know the true parameters \(\bm{\mu}\) and cannot calculate the
+optimal weights. Instead, we have to estimate the maximum likelihood
 estimates \(\hat{\mu}(t) = (\hat{\mu}_1(t), \dots, \hat{\mu}_K(t))\) of
-the true mean at the current round \(t\) and need to base our weights
-based on these. It is however problematic to rely on these sample means
+the true mean at the current round \(t\) and need to base our sample
+weights on them. It is however problematic to rely on the sample means
 as we are inherently unsure about them. And so wrong estimates, which
@@
 estimate \(\hat{\mu}_a\) for arm \(a\) leads to a small weight \(w_a\),
-then neither the estimate nor the weight will be correct soon. Thus,
-Kaufmann and Garivier conclude that ``a naive plug-in sampling rule
-sometimes fails''. They propose to enforce a certain minimum level of
-exploration to make sure that arms that erroneously received a very
-small weight will be further explored regardless.
-
-A very intuitive fix to this problem is the solution proposed in Lemma 8
-of Garivier and Kaufmann (2016) with their \(D-Tracking\) rule. Whenever
-an arm has received a very low number of pulls \(N_a(t)\) given the
-number of iterations so far, \(t\), and the number of arms \(K\) that
+then after a few more rounds neither the estimate nor the weight will be
+correct. Thus, Kaufmann and Garivier conclude that ``a naive plug-in
+sampling rule sometimes fails''. They propose to enforce a certain
+minimum level of exploration to ensure that arms that erroneously
+received a very small weight will be further explored regardless.
+
+A very intuitive solution to this problem is proposed in Lemma 8 of
+Garivier and Kaufmann (2016) with the \(D-Tracking\) rule. Whenever some
+arm has received a very small number of pulls \(N_a(t)\) given the
+number of iterations \(t\) so far, and the number of arms \(K\) that
 have to share the samples, pull the arm that has received the smallest
-amount of samples so far. Else, pull the arm which number of pulls so
-far \(N_a(t)\) is the furthest away from what its optimal share
+amount of samples so far. Else, pull the arm whose number of pulls so
+far \(N_a(t)\) is the farthest away from what its optimal share
 \(t\cdot w^*_a(\hat{\bm{\mu}}(t))\) would be. Given this sampling rule,
@@
 down to a statistical test at every iteration and thus is a sequential
-test based on the current estimate of \(\hat{\bm{\mu}}\). The Chernoff's
+test based on the current estimate of \(\hat{\bm{\mu}}\). Chernoff's
 Stopping Rule proposed in Garivier and Kaufmann (2016) calculates for
@@
 \begin{equation*}
-Z_{a,b}(t) = - Z_{b,a} = N_a(t) \KL(\hat{\mu}_a(t),\hat{\mu}_{a,b}(t)) + N_b(t) \KL(\hat{\mu}_{b}(t), \hat{\mu}_{a,b}(t)),
+Z_{a,b}(t) = - Z_{b,a} = N_a(t) \KL(\hat{\mu}_a(t) || \hat{\mu}_{a,b}(t)) + N_b(t) \KL(\hat{\mu}_{b}(t) || \hat{\mu}_{a,b}(t)),
 \end{equation*}
@@
 \begin{equation*}
-\hat{\mu}_{a,b}(t) := \frac{N_a(t)}{N_a(t) + N_b(t)}\hat{\mu}_a + \frac{N_b(t)}{N_a(t) + N_b(t)}\hat{\mu}_b.
+\hat{\mu}_{a,b}(t) := \frac{N_a(t)}{N_a(t) + N_b(t)}\hat{\mu}_a(t) + \frac{N_b(t)}{N_a(t) + N_b(t)}\hat{\mu}_b(t).
 \end{equation*}
@@
 has to be an arm \(a \in \{1,...,K\}\) for which
-\(Z_{a,b} \geq 0 \, \forall b \in \{1,...,K\}^{\setminus a}\) (which is
-always fulfilled if there is a uniquely best arm), and, additionally, we
+\(Z_{a,b} \geq 0 \text{ for all } b \in \{1,...,K\}^{\setminus a}\)
+(which is always fulfilled if there is a uniquely best arm), and we
 demand that for this arm the smallest of the \((K-1)\) test statistics
-has to be larger than an exploration threshold \(\beta(t, \delta)\).
-Consequently, the final number of samples \(T_{\delta}\) of an algorithm
-is given by:
+has to be larger than an exploration threshold \(\beta(t, \delta)\). The
+final sampling round \(T_{\delta}\) of the algorithm is given by:
 
@@
 Demanding that the optimal exploration threshold increases in rounds
-\(t\) (if we have more samples, require more certainty; also, punish for
-failing previous tests) and decreases in the risk \(\delta\), and does
-so at a diminishing rate, the optimal threshold derived in Theorem 10 of
-Garivier and Kaufmann (2016) makes sense intuitively:
+\(t\) (if we have more samples, require more certainty; punish for
+failing previous tests) and decreases in risk \(\delta\) at a
+diminishing rate, the optimal threshold derived in Theorem 10 of
+Garivier and Kaufmann (2016) is intuitive:
 
@@
 
-\subsection{Conclusion of Complexity of Best Arm
-Identification}\label{conclusion-of-complexity-of-best-arm-identification}
+\subsection{Conclusion}\label{conclusion}
 
@@
 multi-armed bandit setting. Their contribution is primarily based on
-including the Kullback-Leibler divergence in the derivation of bounds
-and the matching algorithms and thus going beyond a sum of squared gaps
-which is most practical only in the case of Gaussian distributions.
-While the contribution in the fixed budget setting was limited to the
-two-armed bandit case, the authors derive general lower bounds in the
-fixed confidence setting which are primarily based on Lemma
+including the Kullback-Leibler divergence and Chernoff information as
+information theoretic measures in the derivation of bounds and the
+matching algorithms. Thereby, they go beyond a sum of squared gaps which
+is most relevant only in the case of Gaussian distributions. While the
+contribution in the fixed budget setting is limited to the two-armed
+bandit case, the authors derive general lower bounds in the fixed
+confidence setting. All bounds presented are primarily based on Lemma
 \ref{theorem:KaufmannEtAlLemma1}. Lemma \ref{theorem:KaufmannEtAlLemma1}
@@
 Kaufmann, 2016) of moving from one distribution to another one in terms
-of Kullback-Leibler divergence. This transportation cost will increase
-the expected stopping time, and so the experimenter has to be careful
-when selecting which arm to sample. By picking proportions
-\(w^*(\bm{\mu})\) that minimize the transportation cost, a solution is
-found with as few iterations as possible.
-
-With respect to the optimal proportions we have derived some
-characteristics that now allow for a few interpretations. First, we have
-demanded that the algorithm keeps arms proportions in a way that
-equalizes the failure probability of every arm with respect to the best
-arm. This is basically similar to keeping the weighted Jensen-Shannon
-divergence at the same level which was shown in Lemma 4 of Garivier and
-Kaufmann (2016) and which we have repeated above. The fact that the risk
-plays an important role at any round of the algorithm suggests the
-possibility of turning the algorithm into an anytime algorithm. That is,
-instead of relying on Chernoff's stopping rule to end the algorithm at
-one point, and not being able to stop the algorithm before that and
-receiving a meaningful result, one would be able to stop the algorithm
-at any iteration, and receive both the recommended best arm and a
-confidence level. Second, the idea of comparing each arm to the best arm
-and based on that keeping the failure probabilities at a flat level
+of Kullback-Leibler divergence. It is a bound on the expected likelihood
+ratio term that appears when changes in distribution are applied.
+
+In the case of the fixed budget top-\(m\) arm identification problem, we
+have seen that the derivation of a lower bound on the complexity term is
+mostly limited by the difficulty of defining an alternative problem
+\(\nu'\) to \(\nu\) that fits into the Lemma
+\ref{theorem:KaufmannEtAlLemma1}. But given the intuition that in
+top-\(m\) problems the \(m\)-th best arm and the \((m+1)\)-th best arm
+define an implied threshold between the two groups of arms, we were able
+to apply the ideas of Kaufmann et al. (2016) to our fixed budget
+thresholding bandit problem. In contrast to their problem, arms are
+classified against the known threshold \(\tau\), which makes it possible
+to define an alternative problem \(\nu'\) in which we do not have to
+change arms with respect to each other, but only with respect to
+\(\tau\). This has lead us to the simple lower bound on the problem
+complexity for the thresholding bandit problem with exponential family
+distributions given in Corollary \ref{corollary:LBKTBP}.
+
+In the best arm identification problem discussed by Garivier and
+Kaufmann (2016), we were introduced to the idea of comparing each arm to
+the best arm, and evaluating the difference between the best arm and the
+other arms based on the Generalized Likelihood Ratio test. This idea
 seems transferrable to the thresholding bandit problem. Indeed, it might
-even be easier as the best arm does not have to be estimated; thus, the
-risk with respect to this estimate goes away. Instead, every arm will be
-compared to the threshold. One idea might be to compute for each arm
-\(a\) the probability that the mean \(\mu_a\) is actually on the other
-side of the threshold as currently suggested by \(\hat{\mu}_a(t)\). This
-is independent of the other arms. And so a strategy might be to draw
-arms such that their failure probabilities are at the same level (draw
-whatever arm has the highest failure probability). We will come back to
-this idea in chapter 3.
-
-Using the information from the lower bound of how well any
-\(\delta\)-PAC algorithm can potentially be, the authors design
-algorithms matching these lower bounds. In the case of Top-\(m\)
-identification, a simple application of the existing KL-LUCB algorithm
-works. In the case of best arm identification, the lower bound provides
-a way of calculating the optimal proportions in which the arms need to
-be pulled. Consequently, a matching algorithm can be set up so that it
-draws arms in these proportions, and so that it is robust against
-estimation errors of the plug-in estimates. Combining this sampling rule
-with an appropriate stopping rule makes for a \(\delta\)-PAC algorithm
-that matches the lower bound, where the upper bound in Theorem
-\ref{theorem:GarivierAndKaufmannTheorem14} matches the lower bound from
-Theorem \ref{theorem:GarivierKaufmannTheorem1} using equation
-\eqref{bre_approx}.
-
-\newpage
+even be easier as the best arm does not have to be estimated; instead,
+we would compare each arm to the threshold \(\tau\). Intuitively, one
+can frame this problem for each arm individually as an hypothesis test
+between the maximum likelihood estimate of the mean and the threshold
+\(\tau\). We will come back to this idea in
+\autoref{sec:LikelihoodRatioForExponentialFamily}.
+
+Lastly, we observe that Garivier and Kaufmann (2016) support their
+algorithm's main strategy by an additional D-Tracking rule which
+protects them against poor estimates in the beginning of the sampling.
+Such rule should be mostly unnecessary, for example, the cumulative
+regret setting, as algorithms there rely on upper confidence bound
+estimates. This is not the case for the Track-and-Stop strategy
+introduced in Garivier and Kaufmann, and neither for our Simple
+Likelihood Ratio strategy introduced in \autoref{sec:1DSLR}. In
+\autoref{sec:Simulation2}, we show empirically that the performance of
+the Simple Likelihood Ratio strategy can be further improved by naively
+adding the D-Tracking rule to it.
 
@@
 \subsubsection{\texorpdfstring{Simulation 2: Bernoulli with
-\(\tau = 0.05\)}{Simulation 2: Bernoulli with \textbackslash{}tau = 0.05}}\label{simulation-2-bernoulli-with-tau-0.05}
+\(\tau = 0.05\)
+\label{sec:Simulation2}}{Simulation 2: Bernoulli with \textbackslash{}tau = 0.05 }}\label{simulation-2-bernoulli-with-tau-0.05}
 
@@
 
-\section{Conclusion}\label{conclusion}
-
-\section{Notes}\label{notes}
-
-The author thanks Alexandra Carpentier, Andrea Locatelli, and Urun Dogan
-for many hours of valuable feedback and ideas.
+\section{Conclusion}\label{conclusion-1}
+
+\section{Acknowledgements}\label{acknowledgements}
+
+We thank Alexandra Carpentier, Andrea Locatelli, and Urun Dogan for many
+hours of fruitful discussions and ideas. We thank Carlo Alberto
+Dall'Amico for bringing our attention to multi-armed bandits in the
+first place. Sonoma Internet GmbH (Amorelie) supported this work by
+giving the authors access to the discussed data set.
 
@@
 
-\subsection{Proof of Corollary 1}\label{proof-of-corollary-1}
+\subsection{\texorpdfstring{Lower Bound for Thresholding Bandit Problem
+with KL-divergence
+\label{sec:corollaryLBTBPproof}}{Lower Bound for Thresholding Bandit Problem with KL-divergence }}\label{lower-bound-for-thresholding-bandit-problem-with-kl-divergence}
+
+\subsubsection{\texorpdfstring{Lower Bound for One-Armed Thresholding
+Bandit
+\label{sec:corollaryLB1TBPproof}}{Lower Bound for One-Armed Thresholding Bandit }}\label{lower-bound-for-one-armed-thresholding-bandit}
 
@@
 \]
+
+\subsubsection{\texorpdfstring{Lower Bound for \(K\)-Armed Thresholding
+Bandit
+\label{sec:corollaryLBKTBPproof}}{Lower Bound for K-Armed Thresholding Bandit }}\label{lower-bound-for-k-armed-thresholding-bandit}
+
+\textbf{Proof}: The proof is very similar to the proof of the corollary
+for \(K=1\). However, the alternative model needs more motivation than
+in the case of a single arm. But first, consider again that we are in
+the thresholding bandit problem with \(K\) arms of univariate canonical
+exponential family distributions that are parameterized by their means
+\(\mu_1, ..., \mu_K\) for the original problem
+\(\nu = (\nu_1, ..., \nu_K)\). W.l.o.g, assume that all arms are above
+the threshold, that is, \(\mu_1 \geq \tau, ..., \mu_K \geq \tau\). Then
+\(\mathcal{S}_{\tau}^* = \{1, ... , K\}\). The correct classification
+returned after \(t\) rounds is thus the event
+\(A = (\hat{\mathcal{S}}_{\tau} = \{1, ..., K\})\). We can now consider
+Lemma 2. The RHS is maximized when the alternative model is chosen such
+that \(d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A))\) is maximized.
+Given the event \(A\) as defined before, this is the case when
+\(\mathbb{P}_{\nu'}(A)\) is as small as possible. For consistent
+algorithms, this is the case when \(\nu'\) is chosen such that all
+\(\mu_1' < \tau, ..., \mu_K' < \tau\). Then even classifying a single
+arm correctly under \(\nu\) would lead to a mistake in \(\nu'\).
+Consequently, \(A\) is the most unlikely classification for a consistent
+algorithm for the problem \(\nu'\). We thus expect for any consistent
+algorithm that \(\mathbb{P}_{\nu}(A)\) becomes large and
+\(\mathbb{P}_{\nu'}(A)\) becomes small as the number of observations
+\(t\) increases. Again, for every \(\epsilon > 0\), there exists
+\(t_0(\epsilon)\) such that for all \(t \geq t_0(\epsilon)\) we have
+\(\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)\). This
+allows us to now use Lemma 1 as previously:
+
+\begin{align*}
+\sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\nu_i', \nu_i) & \geq \sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\tau, \mu_i) \\
+& \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)) \\
+& \geq d(\epsilon, 1-p_t(\nu)) \\
+& = \epsilon \log \Big(\frac{\epsilon}{1-p_t(\nu)}\Big) + (1-\epsilon) \log \Big( \frac{1-\epsilon}{p_t(\nu)}\Big) \\
+& \geq (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) + \epsilon \log(\epsilon)
+\end{align*}
+
+We let \(\epsilon \rightarrow 0\), divide by \(t\) and take the limsup
+on both sides as in Kaufmann et al. (2016):
+
+\begin{align*}
+\lim_{t \rightarrow \infty} \sup - \frac{1}{t} \log p_t(\nu) & \leq \lim_{t \rightarrow \infty} \sup \frac{1}{t} \sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\tau, \mu_i) \\
+& \leq \max_{i \in \{1,...,K\}} \KL(\tau, \mu_i)
+\end{align*}
+
+Though, since for the alternative problem \(\nu'\) we have for every
+\(i \in \{1,...,K\}\) that \(\mu_i = \tau\), it should hold for any
+consistent algorithm that \(\mathbb{E}_{\nu'}[N_i(t)] = \frac{t}{K}\),
+that is, every arm receives an equal amount of the budget. In that case,
+the above equation simplifies to
+
+\[
+- \frac{1}{t} \log p_t(\nu) \leq \frac{1}{t} \sum_{i=1}^K \frac{t}{K}\KL(\tau, \mu_i) = \frac{1}{K} \sum_{i=1}^{K} \KL(\tau, \mu_i),
+\]
+
+that is, the complexity is given by the simple average of the
+Kullback-Leibler distances of the threshold with regard to the
+respective distributions. This relates well to the lower bound that
+Kaufmann et al. (2016) describe in their Theorem 12 for consistent
+algorithms using \emph{uniform} sampling strategies; in our case,
+however, it is explained by the fact that under the alternative model,
+every consistent algorithm should adapt to a uniform sampling strategy.
+Thus our bound holds for any consistent strategy.
 
@@
 
+\subsection{SLR Algorithm with D-Tracking
+Rule}\label{slr-algorithm-with-d-tracking-rule}
+
+\IncMargin{1em}
+
+\begin{algorithm}
+\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
+\Input{$\tau$, $\epsilon$, class of distributions $\nu(\mu, \theta)$, $\theta_i \: \forall i \in \mathbb{A}$}
+\Output{$\hat{S}_\tau = \{i \in \mathbb{A},  \hat{\mu}_i(T) \geq \tau\}$}
+\BlankLine
+\emph{Pull each arm once}\;
+\For{$t = K+1$ \KwTo $T$}{
+  \emph{Calculate $U_t = \{i \in \mathbb{A}, T_i(t) < \sqrt{t} - K/2\}$}\;
+  \emph{Set $I_t = \arg \min_{i \in \mathbb{A}} B_i^{SLR}(t)$ as in \autoref{eqn:SLRIndex}}\;
+  \If{$U_t \neq \emptyset$}{Set $I_t = \arg \min_{i \in \mathbb{A}} T_i(t)$}
+  \emph{Pull arm $I_t$}\;
+  \emph{Observe reward $X_t \sim \nu_{I_t}$}\;
+}
+\caption{SLR algorithm with D-Tracking Rule (Garivier and Kaufmann, 2016)} \label{algo_slr_1d_dTracking}
+\end{algorithm}
+
+\DecMargin{1em}
+
 \end{document}

### 2017-09-04 synthetic_experiments/cal_algs_verylong_6_no_tau.R

@@ -221,6 +221,7 @@ lines(log(loc6nt_comp_LRD), col = "darkgreen")
 lines(log(loc6nt_comp_APT_7000), col = "red")
 lines(log(loc6nt_comp_UNIFORM_7000), col = "black")
 abline(h=log(0.1))
+lines(log(loc6nt_comp_PI), col = "orange")
 #lines(log(loc6nt_comp_AugUCB), col = "grey")
 lines(log(loc6nt_comp_AugUCB_7000), col = "grey")
 #lines(log(loc6nt_comp_KLUCB7), col = "green")

### 2017-09-08 Thesis/Draft.Rmd
Add descriptions to Appendix

@@
 
-The thesis at hand joins the ranks of a large literature concerned with the general problem of sequential sampling.
+The thesis at hand joins a large literature concerned with the problem of sequential sampling.
 One is familiar with the idea of "batch sampling", where the entire sample is gathered first and analyzed only after the last sample has become available.
-However, as noted in Chernoff (1958), many situations arise in which one would like to gather feedback from samples as they are drawn so as to influence the choice of the next sample.
+However, as noted in Chernoff (1958), many situations arise in which one would like to gather feedback from samples as they are drawn, so as to influence the choice of the next sample.
 The two fundamental characteristics of the latter sampling process are that it is sequential and adaptive.
-Since observations are drawn in sequence, one has a chance to observe the observations drawn so far in order to adapt the decision of what sample one would like to observe next.
-
-This makes sequential sampling especially relevant in situations where there is a inherent cost to drawing an observation.
-The classical example that of clinical trials in which a researcher tests two drugs on patients to observe which one performs better.
-Not only is it difficult to gather patients, but also one would like to adapt the sampling such that as soon as possible more patients receive the better drug so that more patients are cured.
+Since observations are drawn in sequence, one has a chance to analyze past observations in order to adapt the decision of what sample one would like to observe next.
+
+This makes sequential sampling especially relevant in situations where there is an inherent cost to obtaining samples.
+The classical example is that of clinical trials in which a researcher tests two drugs on patients to observe which one performs better.
+Not only is it difficult to gather enough patients, but one would also like to adapt the sampling such that as soon as possible more patients receive the better drug and are cured.
 As noted in Cappé et al.
@@
 Such problems are known as multi-armed bandit problems in which the sampling is adapted so as to minimize the cumulative regret: In the case of the drug tests, one would like to sample the two drugs in a way to find the best drug as soon as possible and then to test this drug more and more often and more often than the worse drug.
-This would lead to cumulatively more healthy patients then when both drugs are tested uniformly and thus minimize the regret from treating a patient with an ineffective drug.
-
-Instead of drugs, can consider two or more unknown distributions (which we call arms in the multi-armed bandit problem).
+This would lead to cumulatively more healthy patients than testing both drugs uniformly; it would minimize the regret from treating patients with an ineffective drug.
+
+Instead of drugs, one can consider two or more unknown distributions (which we call arms in the multi-armed bandit problem in analogy with the one-armed bandit slot machine).
 These distributions have different means, and one can draw samples sequentially from the distributions in order to estimate their means.
-One would like to play the distribution with the highest mean to minimize the cumulative regret measure.
-How can we organize the sampling in order to achieve this goal?
-
-While Gittins (1979) presents an Bayesian-optimal solution, the Upper-Confidence Bound algorithms pioneered by Agrawal (1995) and Auer, Cesa-Bianchi and Fischer (2002) lead to a blooming literature on multi-armed bandit problems that has been picked up to solve modern problems in website and advertising optimization, where advertisers try to allocate their advertising optimally so as to reduce regret from showing poorly converting advertisements.
-Several algorithms as the KL-UCB algorithm based on Kullback-Leibler divergence upper confidence intervals (Cappé et al., 2013) or the Bayes-UCB algorithm (Kaufmann et al., 2012)  have followed and been shown to be optimal as they reach the lower bound introduced in Lai and Robbins (1985) and Burnetas and Katehakis (1996).
-
-These algorithms have in common that they compute after any sample an index for each of the unknown distributions.
-This index is based solely on the past (observed) data, and then used to pick the distribution from which the next observation should be drawn.
-Using these indexes, the algorithms can sequentially sample and adapt the future strategies to observations as they are gathered.
-
-Other algorithms based on indices can be used on related problems.
-Instead of minimizing cumulative regret, it might be more interesting to find the best arm, that is, the distribution with the largest mean, with as few samples as possible and with confidence as large as possible.
-This is particularly useful when there is not necessarily a cost from initially picking a lower mean, but when drawing any sample is costly, and one needs to explore the distributions as efficiently as possible.
-The need for strategies other than uniform sampling arises: Do not continue to sample distributions that we are confident about.
-As such, the best arm identification problem is very similar to the problem faced in Bayesian Optimization: Training large neural networks is costly in terms of time and computation, and so the parameter space needs to be explored with as few samples as possible.
+To minimize the cumulative regret measure, one would like to play the distribution with the highest mean as much as possible (*Exploitation*).
+At the same time, however, one has to sample all arms at least a little, so as to initially find the best arm (*Exploration*).
+Any algorithm thus has to handle a trade-off between exploration and exploitation to minimize the regret.
+How can we organize the sampling in order to achieve this task?
+
+While Gittins (1979) presents an Bayesian-optimal solution to the cumulative regret problem, the Upper-Confidence Bound (UCB) algorithms pioneered by Agrawal (1995) and Auer, Cesa-Bianchi and Fischer (2002) have lead to a blooming literature on multi-armed bandit problems that has been picked up to solve modern problems in website and advertising optimization, where advertisers try to allocate their advertising optimally so as to reduce regret from showing poorly converting advertisements.
+Several algorithms like the KL-UCB algorithm based on Kullback-Leibler divergence upper confidence intervals (Cappé et al., 2013) or the Bayes-UCB algorithm (Kaufmann et al., 2012)  have followed and been shown to be optimal as they reach the lower bound introduced in Lai and Robbins (1985) and Burnetas and Katehakis (1996).
+
+These algorithms have in common that they compute after every new sample an index for each of the unknown distributions.
+This index is based solely on the past (observed) data, and then used to pick the distribution from which the next sample should be drawn.
+Using these indexes, algorithms can sample sequentially and adapt their strategies to observations as they are collected.
+
+Similar algorithms based on indexes can be used on related problems.
+Instead of minimizing cumulative regret, it can be of interest to find the best arm, that is, the distribution with the largest mean -- with as few samples as possible and with confidence as large as possible.
+This is particularly useful when there is not a cost from testing arms with lower mean, but when drawing any sample is costly.
+Thus one needs to explore the distributions as efficiently as possible.
+Exploitation is not necessary, and the setting is thus referred to as *Pure Exploration*.
+The need for strategies other than uniform sampling arises: One does not want to continue to sample distributions that one is confident in.
+This setting is related to the problem faced in Bayesian Optimization: Training large neural networks is costly in terms of time and computation, and so the parameter space needs to be explored with as few samples as possible.
 (Zhang et al., 2017; Brochu et al., 2010).
-
-The problem of best arm identification is very related to statistical hypothesis testing as noted by Chernoff (1958) since in the end, one has to make a decision about how the means of distributions relate to each other.
-The main difference of course being that the sampling procedure becomes integrated into the evaluation of the distributions.
-Given the focus on exploration, the problem is usually described with a loss function different from cumulative regret.
+The problem of best arm identification is also very related to statistical hypothesis testing as noted by Chernoff (1958) since one has to make a decision about how the means of distributions relate to each other.
+The main difference being that the bandit setting includes the testing procedure in the sampling process.
+
+Given the focus on exploration, the pure exploration problem is usually described with a loss function different from the one in the cumulative regret settings.
 Audibert et al.
 (2010) introduce a soft measure called *simple regret* based on which they describe UCB policies.
-Other authors investigate hard, binary measures that are equal to 1 when the best arm has not been identified (Russo, 2016; Garivier and Kaufmann, 2016).
+Other authors investigate binary measures that are equal to 1 when the best arm has not been identified (Russo, 2016; Garivier and Kaufmann, 2016).
 These binary measures correspond to the probability of the identified arm being the best, and thus inherently related to hypothesis testing.
@@
 In this thesis, we consider the thresholding bandit problem.
-Instead of identifying the best $m$ out of $K$ arms, one aims to find all out of $K$ distributions that have a mean larger than a threshold fixed upfront.
+Instead of identifying the best $m$ out of $K$ arms, we aim to find all distributions out of $K$ that have a mean at least as large as a threshold fixed upfront.
 In the form described in Locatelli et al.
-(2016), algorithms in the thresholding bandit problem are evaluated against a binary loss function penalizing whenever an arm has not been classified correctly as being above the threshold and thus focus on exploration similar to algorithms employed for best arm identification.
+(2016), algorithms in the thresholding bandit problem are evaluated against a binary loss function penalizing whenever an arm has not been classified correctly as being above or below the threshold, and thus focus on exploration similar to algorithms employed for best arm identification.
 Indeed, Locatelli et al.
@@
 
-In the following, we first present the thresholding bandit problem in detail.
+In the following, we first present the thresholding bandit problem in detail in \autoref{chap:ThresholdingBanditProblem}.
 To then extend upon the algorithm proposed by Locatelli et al.
-(2016), we first explore how the Kullback-Leibler divergence has been employed in the best arm identification literature by Garivier and Kaufmann (2016) and Kaufmann et al.
-(2016).
-We shortly describe two variance based algorithms for the thresholding bandit problem introduced in Mukherjee et al.
+(2016) and discussed in \autoref{sec:TheAPTAlgorithm}, we first explore in \autoref{chap:KullbackLeiblerPureExploration} how the Kullback-Leibler divergence has been employed in the best arm identification literature by Garivier and Kaufmann (2016) and Kaufmann et al.
+(2016) as this will lead us to our own extension.
+We shortly describe in \autoref{sec:VarianceBasedAlgorithms} two variance-based algorithms for the thresholding bandit problem introduced in Mukherjee et al.
 (2017) and Zhang et al.
-(2017), before introducing the new Simple Likelihood Ratio algorithm.
-We end with experiments to examine the performance of different algorithms.
+(2017), before introducing the new Simple Likelihood Ratio algorithm in \autoref{sec:LRforUnivariateExponentialFamily}.
+We end in \autoref{chap:Experiments} with experiments to examine the performance of different algorithms.
 
@@
 
-To introduce the thresholding bandit problem, consider a game in which the learner is tasked to find those slot machines within a row of $K$ slot machines in a casino that give a mean payoff larger than a fixed threshold $\tau$, for example $\tau = 0$.
+To introduce the thresholding bandit problem, consider a game in which the learner is tasked to find the slot machines within a row of $K$ slot machines in a casino that give a mean payoff larger than a fixed threshold $\tau$, for example $\tau = 0$.
 The learner cannot pull all slot machines at the same time.
 Instead, he acquires samples sequentially from one slot machine at a time to learn about their payoff structure.
-The learner has a budget of $T$ slot machine pulls.
+The learner has a budget of $T>K$ slot machine pulls.
 After $t-1$ samples, the learner has observed $T_i(t-1)$ samples from slot machine $i$.
@@
 At time $t$, the learner considers the payoffs he observed so far in order to choose the next slot machine he would like to pull.
-His decision is lead by the goal to classify the slot machines with distribution $\nu_i$ and mean payoff $\mu_i = \mathbb{E}_{X \sim \nu_i}[X]$ after $T$ samples as being above or below the threshold with error probability as small as possible.
-
-The thresholding bandit problem can thus be framed in the wide literature on sequential sampling strategies.
-While its name is reminiscient of the multi-armed bandit setting, the thresholding bandit problem is more akin to best arm identification and Top-$m$ identification problems due to its focus on exploration: While the classical multi-armed bandit problems are concerned with cumulative regret which increases *during* sampling, best arm identification and thresholding bandits collect loss only once *after* the sampling procedure (compare Garivier and Kaufmann, 2016; Kaufmann et al., 2016; Kaufmann and Kalyanakrishnan, 2013).
-Furthermore, as there arises an implicit threshold between the means of the $m$-th best arm and the $m+1$-th best arm (Kaufmann et al., 2016; Kaufmann and Kalyanakrishnan, 2013), algorithms for the Top-$m$ identification problem classify arms at least implicitly as being above or below a threshold.
-The two settings are thus very related.
+Her decision is lead by the goal to classify the slot machines with distribution $\nu_i$ and mean payoff $\mu_i = \mathbb{E}_{X \sim \nu_i}[X]$ after $T$ samples as being above or below the threshold with error probability as small as possible.
+
+The thresholding bandit problem can thus be framed in the literature on sequential sampling strategies.
+Even though its name is reminiscient of the multi-armed bandit setting, the thresholding bandit problem is more akin to best arm identification and top-$m$ identification problems due to its focus on exploration: While the classical multi-armed bandit problems are concerned with cumulative regret which increases *during* sampling, best arm identification and thresholding bandits collect loss only once *after* the sampling procedure (compare Garivier and Kaufmann, 2016; Kaufmann et al., 2016; Kaufmann and Kalyanakrishnan, 2013).
+As we will see in \autoref{chap:KullbackLeiblerPureExploration} there arises an implicit threshold between the means of the $m$-th best arm and the $m+1$-th best arm in the top-$m$ identification problem (Kaufmann et al., 2016; Kaufmann and Kalyanakrishnan, 2013).
+Because of this, the two settings are very related.
 
@@
 Consider a setting with a set of $\mathbb{A}=\{1, ..., K\}$ unknown probability distributions $\nu_i, i \in \mathbb{A}$.
-To stick with the idea of multi-armed bandits, we call those distributions arms, and observations from those arms rewards (Bubeck and Cesa-Bianchi, 2012).
-The learner is interested in learning about the structure of the arms; in particular, he would like to estimate the means $\mu_1, ..., \mu_K$ by sequentially drawing observations $X_{i,1}, X_{i,2}, ...$ from each arm.
-However, at time $t$ the learner cannot observe a reward from every distribution but must select a single arm $I_t$ from which he would like to observe the reward $X_{I_t,t}$.
-An adaptive sampling strategy makes the decision of which arm to pull usually by computing an index $B_i(t)$ for each arm.
-If $T_i(t)$ is the number of samples observed until time $t$ for arm $i$, then $B_i(t)$ is a function of the past rewards $X_{i,1}, ..., X_{i,T_i(t)}$ observed for arm $i$, and w.l.o.g.
+To stick with the idea of multi-armed bandits, we call the distributions arms, and observations from the arms rewards (Bubeck and Cesa-Bianchi, 2012).
+The learner is interested in learning about the structure of the arms; in particular, she would like to estimate the means $\mu_1, ..., \mu_K$ by sequentially drawing observations $X_{i,1}, X_{i,2}, ...$ from the different arms.
+However, at time $t$ the learner cannot observe a reward from every distribution but must select a single arm $I_t$ from which she would like to observe the reward $X_{I_t,t}$.
+Often, adaptive sampling strategies makes the decision of which arm to pull by computing an index $B_i(t)$ for each arm.
+If $T_i(t)$ is the number of samples observed until time $t$ for arm $i$, then is $B_i(t)$ a function of the past rewards $X_{i,1}, ..., X_{i,T_i(t)}$ observed for arm $i$, and w.l.o.g.
 $I_t = \arg \min_{i = 1,...K} B_i(t)$.
-The set of indices can be called strategy (Kaufmann et al., 2012) which makes it clear that the strategy is adapted as more observations are collected.
+The set of indexes can be called strategy (Kaufmann et al., 2012) which makes it clear that the strategy is adapted as more observations are collected.
 Strategies of this kind are also called index policies.
 
-What index proves to be useful is determined by the loss function with which the decisions of the algorithm are evaluated.
-While many problems are concerned with finding the arm with the largest mean $\mu_i$, in which algorithms collect loss either cumulatively (Auer and Cesa-Bianchi, 2012) or once at the end of the sampling (Kaufmann et al., 2016), the thresholding bandit problem considers a slightly different loss function.
+Which index proves to be useful is determined by the loss function with which the decisions of the algorithm are evaluated.
+Many problems are concerned with finding the arm with the largest mean $\mu_i^*$ while collecting loss either cumulatively during (Auer and Cesa-Bianchi, 2012) or once at the end of the sampling (Kaufmann et al., 2016).
+The thresholding bandit problem considers a slightly different loss function.
 Consider a fixed threshold value $\tau \in \mathbb{R}$ and an epsilon interval $\tau \pm \epsilon$ around the threshold for $\epsilon \geq 0$.
 As mentioned in the introduction, the learner is tasked with classifying arms as having a mean $\mu_i$ larger or smaller than $\tau$.
-To describe which arms are above the threshold, we introduce the following set notation (compare Locatelli et al., 2016): Let $\mathcal{S}_{\tau}$ be the set of distributions in $mathbb{A}$ with mean larger than the threshold: $\mathcal{S}_{\tau} := \{i \in \mathbb{A}, \mu_i \geq \tau\}$.
-Consequently, the complement is given by the arms with mean below the threshold, $\mathcal{S}^C_{\tau} := \{i \in \mathbb{A}, \mu_i < \tau\}$.
+As in Locatelli et al.
+(2016), whenever we say that "an arm is over the threshold", we say that the mean of the arm is over the threshold.
+To describe which arms are over the threshold, we also introduce the following set notation: Let $\mathcal{S}_{u}$ be the set of distributions in $\mathbb{A}$ with mean larger than some $u \in \mathbb{R}$: $\mathcal{S}_{u} := \{i \in \mathbb{A}, \mu_i \geq u\}$.
+Consequently, the complement is given by the arms with mean below $u$, $\mathcal{S}^C_{u} := \{i \in \mathbb{A}, \mu_i < u\}$.
 
 The thresholding problem for the learner is now to use a budget of overall $T$ samples (or rounds) to explore the different arms.
-After this exploration phase, the learner has to return a set of arms that he believes to have a mean above the threshold.
-The problem can thus be described by the threshold $\tau$ and a precision $\epsilon$.
-When evaluating the classification of the learner, arms with mean inside of the epsilon interval will not be considered.
-The learner only has to distinguish the means from the threshold correctly up to the precision $\epsilon$.
+After this exploration phase, the learner returns a set of arms that she believes to be over the threshold.
+When evaluating the classification of the learner, arms with mean inside of the epsilon interval $\tau \pm \epsilon$ will not be considered.
+The learner only has to correctly distinguish the means from the threshold up to the precision given by $\epsilon$.
 Thus, the algorithm is not evaluated against $\mathcal{S}_{\tau}$ and $\mathcal{S}^C_{\tau}$, but needs to distinguish $\mathcal{S}_{\tau+\epsilon}$ from $\mathcal{S}^C_{\tau-\epsilon}$.
-As in Locatelli et al.
-(2016), whenever we say that "an arm is over the threshold", we mean that the mean of the arm is over the threshold.
 
@@
 $$
-\mathcal{L}(T) = \mathbbm{1}{(\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \lor (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset)}
+\mathcal{L}(T) = \mathbbm{1}{\big((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \lor (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset)\big)}
 $$
@@
 In order to perform well, a learner has to identify all arms that are over the threshold as such, and to not claim arms as being over the threshold if they actually are below the threshold.
-Due to the precision $\epsilon$, the loss is not influenced by arms which are too close to the threshold $\tau$, that is, arms inside of the $\tau \pm \epsilon$ interval.
+Due to the precision $\epsilon$, the loss is not influenced by arms which are very close to the threshold $\tau$ as measured by $\epsilon$, that is, arms inside of the $\tau \pm \epsilon$ interval.
 If either $\hat{\mathcal{S}}_{\tau}$ contains an arm below $(\tau - \epsilon)$, or $\hat{\mathcal{S}}^C_{\tau}$ contains an arm above $(\tau + \epsilon)$, a loss of $1$ is accrued.
 Else, all arms outside the epsilon interval are classified correctly and the loss is equal to $0$.
-In the case of $\epsilon = 0$, all arms need to be classified correctly to not endure any loss.
+In the case of $\epsilon = 0$, all arms need to be classified correctly to not collect any loss.
 
@@
 
-which corresponds to the probability of making a wrong classification.
-Both the probability of not identifying an arm that is actually over the threshold, as well as the probability of accepting an arm as over the threshold when it is not are evaluated.
+which corresponds to the probability of making at least one wrong classification.
+Both the probability of not identifying an arm that is actually over the threshold, as well as the probability of accepting an arm as over the threshold when it is not, are evaluated.
 The oracle strategy would evaluate all arms correctly with an error probability of $0$ (Locatelli et al., 2016).
@@
 At this point, we have introduced the general thresholding bandit problem setting which we will use throughout the thesis.
-The setting might be extended by different assumptions to make certain algorithms or bounds feasible.
+The setting can be extended by different assumptions to make certain algorithms or bounds feasible.
 For that reason, Locatelli et al.
 (2016) assume that the distributions $\nu_i, i \in \mathbb{A}$ are $R$-sub-Gaussian.
-Under this assumption, the authors are able to prove a lower bound on the largest probability of error of the best algorithm in the setting we have just introduced, as well as an upper bound on the performance of their APT algorithm we will introduce in the following chapter.
-As in their paper, we define $R$-sub-Gaussian and assume it in the description of their algorithm and bounds:
+Under this assumption, the authors are able to prove a lower bound on the largest probability of error of the best algorithm in the setting we have just introduced, as well as an upper bound on the performance of their APT algorithm which we will introduce in the following chapter.
+As in their paper, we define $R$-sub-Gaussian and assume it in the description of the their algorithm and bounds:
 
@@
 (2016), this ensures that the mean $\mu_i$ of the distributions $\nu_i$ considered in our problem are finite.
-$R$-sub-Gaussian distributions furthermore offer concentration inequalities for the concentration of the empirical mean to the true mean, which makes it possible to deduce the bounds presented by the authors and repeated below.
+$R$-sub-Gaussian distributions offer concentration inequalities for the concentration of the empirical mean around the true mean, which makes it possible to deduce the bounds presented by the authors and repeated below.
 The family of $R$-sub-Gaussian distributions encompasses Gaussian distributions of variance $R^2$ for $R \in \mathbb{R}$, as well as all bounded distributions, with the important case of Bernoulli distributions.
@@
 In contrast to the uniform sampling strategy, APT will gather more evidence for arms which appear to be inherently more difficult to classify.
-Likewise, APT tends to pull arms less often which it already pulled considerably often as measured by $T_i(t)$.
+Likewise, APT tends to less often pull arms which it already pulled considerably often as measured by $T_i(t)$.
 If arm $i$ has been pulled more often than arm $j$, then we should in general be more confident in its estimated mean and the corresponding distance to the threshold.
@@
 In the index employed by the APT algorithm, the distance between an arm and the threshold is measured by the absolute distance $\hat{\Delta}_i(t)$ between the (estimated) mean of the arm and the threshold $\tau$ (and the epsilon interval).
-Given that one compares $B_i^{APT}$ with $B_j^{APT}$, one could just as well measure the distance by the squared distance, $\hat{\Delta}_i(t)^2$.
 When the APT algorithm realizes that an arm has a mean close to the threshold, then this arm requires more attention than an arm far away from the threshold; the confidence in the empirical mean has to be larger.
@@
 To gain this confidence, the arm requires more samples, and thus a larger share of the overall $T$ samples available.
-With this intuition, it makes sense to measure the complexity of a thresholding problem: If we knew upfront how complex a given set of arms is, we knew whether we can expect a small or large probability of error given our budget $T$.
+With this intuition, it makes sense to measure the complexity of a thresholding problem: If we knew upfront how complex a given set of arms is, we would know whether to expect a small or large probability of error given our budget $T$.
 Also, for example in the best arm identification problem, there exist algorithms which take the complexity of a problem as input.
@@
 See for example the UCB-E algorithm in Audibert et al.
-(2010) for the best arm identification problem, or the KL-LUCB-E algorithm in Kaufmann and Kalyanakrishnan (2013) as extension to the Top-$m$ problem.
-
-While the APT algorithm does not require the complexity to be known upfront (which would be problematic), it is necessary to define the complexity to deduce the upper bound on its probability of error.
+(2010) for the best arm identification problem, or the KL-LUCB-E algorithm in Kaufmann and Kalyanakrishnan (2013) as extension to the top-$m$ problem.
+
+While the APT algorithm does not require the complexity to be known upfront (which would be problematic as it is not known upfront), it is necessary to define the complexity to deduce the upper bound on its probability of error.
 Similar to the distance measure used in the algorithm's index, we define the gap $\Delta_i^{\tau,\epsilon}$ between arm $i$ and the threshold $\tau \pm \epsilon$ as
@@
 Note that the complexity of the problem increases in the number of arms $K$ and decreases in the gap $\Delta_i^{\tau,\epsilon}$.
-Consequently, when we require a smaller precision, that is, we increase $\epsilon$, the hardness decreases.
+Consequently, when we require less precision, that is, we increase $\epsilon$, the hardness decreases.
 Furthermore, we see that each arm contributes its individual complexity, $h_i^{\tau,\epsilon} = \frac{1}{(\Delta_i^{\tau,\epsilon})^2}$ linearly into the problem.
 Thus, if the complexity $H$ is a good measure of the actual problem complexity, and we knew upfront which arm has which mean, we could allocate the "optimal" share of the budget, $T \cdot h_i /H$ to arm $i$.
-However, since we do not know neither $\mu_i$ nor $H$, the best we can do is to adapt our allocation of samples more and more towards this optimum as we observe samples.
+However, since we do not know neither $\mu_i$ nor $H$ upfront, the best we can do is to adapt our allocation of samples more and more towards this optimum as we observe samples.
 
@@
 
-In this chapter we present the upper bound on the APT algorithm proven in Locatelli et al.
+In this chapter we present the upper bound on the probability of error that the APT algorithm incurs, as proven in Locatelli et al.
 (2016).
@@
 
-and similar for $\hat{\Delta}_i$. We can now lower bound the LHS of the indices as
+and similar for $\hat{\Delta}_i$. We can now lower bound the LHS of the indexes as
 
@@
 The learner aims to find the $m$ out of $K$ arms with the largest expected reward.
-This set of arm indices is denoted by $\mathcal{S}_m^*$.
+This set of arm indexes is denoted by $\mathcal{S}_m^*$.
 Kaufmann et al.
@@
 $$
-In order to decide at time $t$ which arm to draw next, we necessarily compare the indices of arm $i$ and arm $j$. Assume w.l.o.g. that $B_i^{SLR}(t) < B_j^{SLR}(t)$. Then:
+In order to decide at time $t$ which arm to draw next, we necessarily compare the indexes of arm $i$ and arm $j$. Assume w.l.o.g. that $B_i^{SLR}(t) < B_j^{SLR}(t)$. Then:
 
@@
 (2012) for the cumulative regret setting.
-See \autoref{sec:AppendixBUCB} in the appendix for how their Algorithm 1 is adapted to the thresholding bandit problem.
+See \autoref{sec:AppendixBUCB} in the appendix for how we adapt the Bayes-UCB algorithm to the thresholding bandit problem.
 
@@
 
-Every experiment presented is repeated for 5000 iterations.
-Depending on the experiment, the observations are generated randomly by a given exponential family of distributions.
-As we are primarily concerned with improving upon APT with respect to non-sub-Gaussian distributions, the first three experiments focus on Bernoulli distributions, especially those with small means.
-We then go on to show with experiments on data from the Exponential distribution and Poisson distribution that the SLR algorithm is able to improve upon APT given that we know the true kind of distribution.
-
-### Simulation 1: Bernoulli with $\tau = 0.5$
+Each of the following five simulations is repeated for 5000 iterations.
+Depending on the simulation, the observations are generated randomly by a given exponential family of distributions.
+As we are primarily concerned with improving upon APT with respect to non-sub-Gaussian distributions, the first three simulations focus on Bernoulli distributions, especially those with small means.
+We then go on to show with experiments on data from the Exponential distribution and Poisson distribution that the SLR strategy can be adapted to other distributions as well.
+
+### Simulation 1: Bernoulli Arms and $\tau = 0.5$
 
 The first experiment is equal to experiment 3 in Locatelli et al.
-(2016).
+(2016) to achieve a baseline comparison.
 We compare ten Bernoulli arms that move away from the threshold at $\tau = 0.5$ geometrically with $\mu_{1:4} = 0.4-0.2^{1:4}$, $\mu_5 = 0.45$, $\mu_6 = 0.55$, and $\mu_{7:10} = 0.6 + 0.2^{5-1:4}$.
@@
 (2017).
-We run the parameter-free EVT$_pf$ algorithm without feedback delay, thus making it directly comparable to the other algorithms.
-The Bayes-UCB algorithm takes as prior a Beta distribution with parameters $\alpha_0 = \tau$ and $\beta_0 = 1 - \tau$, thus leading to a mean of the prior distribution at $\frac{\alpha_0}{\alpha_0+\beta_0}=\tau$ while keeping the prior as weak as possible.
+We run the parameter-free EVT$_{pf}$ algorithm without feedback delay, thus making it directly comparable to the other algorithms.
+The Bayes-UCB algorithm is run with $c=1$ and takes as prior a Beta distribution with parameters $\alpha_0 = \tau$ and $\beta_0 = 1 - \tau$, thus leading to a mean of the prior distribution at $\frac{\alpha_0}{\alpha_0+\beta_0}=\tau$ while keeping the prior as weak as possible.
 Lastly, we run the uniform sampling strategy as a benchmark.
@@
 ```{r loc2_data_summary, echo = FALSE, message = FALSE}
+get_apt_complexity <- function(x, tau, epsilon) {
+  gaps <- abs(x-tau)+epsilon
+  sum(1/gaps^2)
+}
+
 mean_loc2 <- c(0.4-0.2^(1:4),
@@
 
+H_loc2 <- get_apt_complexity(mean_loc2, 0.5, 0.1)
+
 knitr::kable(t(mean_loc2), digits = 3, col.names = paste0("V", 1:10), caption = "Mean of arms in simulation 1.")
@@
 This first experiment is a problem in which all algorithms should be able to perform well.
-The problem is not very difficult, and due to the threshold at $\tau = 0.5$, the Bernoulli distribution can be well approximated by a Gaussian.
-This thus is the perfect environment for the APT algorithm.
-
-As the next figure shows, essentially all methods converge rapidly to an error rate of very close to zero.
-That is, except for the uniform strategy that clearly lacks behind.
+The problem is not very difficult with $H_1^{APT} \approx$ `r round(H_loc2)`, and due to $\tau = 0.5$, the Bernoulli distribution can be well approximated by a Gaussian.
+This is the perfect environment for the APT algorithm.
+
+As the next figure shows, essentially all methods converge rapidly to an error rate of very close to zero, where the error rate is the share of the 5000 simulations on which the classification of the algorithm is wrong.
+Only the uniform strategy that clearly lacks behind.
 We also observe that the variance based algorithms (AugUCB and EVT) lag behind at first.
@@
   geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
-  labs(title = "Results of Synthetic Experiment 1", 
-       subtitle = expression(paste("Ideal scenario for APT; ", 
-                                   tau,' = 0.5')), 
+  labs(subtitle = "Dashed Line indicates Error = 0.1.",
        y = "log(Error)", x = "Round Index") + 
@@
   scale_color_discrete(name = "Algorithm") + 
-  theme_bw() +
-  theme(legend.position = "bottom")
+  theme_bw() #+
+  #theme(legend.position = "bottom")
 
@@
 
-### Simulation 2: Bernoulli with $\tau = 0.05$ \label{sec:Simulation2}
+### Simulation 2: Bernoulli Arms and $\tau = 0.05$ \label{sec:Simulation2}
+
+```{r loc6nt_data_summary, echo = FALSE, message = FALSE}
+mean_loc6nt <- c(0.001, 0.005, 0.01, 0.015,
+                 0.04, 0.06,
+                 0.085, 0.09, 0.095, 0.099)
+
+H_loc6 <- get_apt_complexity(mean_loc6nt, 0.05, 0)
+
+knitr::kable(t(mean_loc6nt), digits = 3, col.names = paste0("V", 1:10), caption = "Mean of arms in simulation 2 classified against threshold of 0.05.")
+```
 
@@
 While the distributions are bounded and thus still sub-Gaussian, the Normal approximation should be poor in comparison to the previous case.
-We expect an improvement for the SLR algorithm compared to APT as it takes the Bernoulli characteristics into account.
+We expect an improvement for SLR compared to APT as SLR takes the Bernoulli characteristics into account.
 In particular, even though the arms are symmetrically distributed around the threshold in terms of absolute distance, they are not symmetrically around the threshold in terms of their Kullback-Leibler divergence (compare Figure 2).
 Thus we expect the SLR algorithm to not pull them symmetrically.
-Furthermore, we expect an improvement for the variance-based algorithms, as the variances are now smaller than in experiment 1, which should at least benefit the EVT algorithm given its theoretical analysis in Zhong et al.
+Furthermore, we expect an improvement for the variance-based algorithms, as the variances are now smaller than in the first simulation, which should benefit the EVT algorithm given its theoretical analysis in Zhong et al.
 (2017).
 
-```{r loc6nt_data_summary, echo = FALSE, message = FALSE}
-mean_loc6nt <- c(0.001, 0.005, 0.01, 0.015,
-                 0.04, 0.06,
-                 0.085, 0.09, 0.095, 0.099)
-
-knitr::kable(t(mean_loc6nt), digits = 3, col.names = paste0("V", 1:10), caption = "Mean of arms in simulation 2 classified against threshold of 0.05.")
-```
-
 The figure below shows the performance of all algorithms.
-We see that the problem appears to be significantly more difficult in general.
-The performance of the variance based algorithms is surprisingly poor; EVT performs even worse than uniform sampling nearly until the horizon, while Augmented UCB takes a long time to adjust away from uniform sampling.
+The results underline that this problem is much harder in general ($H_2^{APT} \approx 24703$).
+The performance of the variance based algorithms is surprisingly poor; EVT performs even worse than uniform sampling until close to the horizon, while Augmented UCB takes a long time to adjust away from uniform sampling.
 Both algorithms perform worse than APT after 7000 samples.
-One potential reason for this might be the fact that the index used by the EVT algorithm reduces to $B_i^{EVT}(t) = \sqrt{T_i(t)} \cdot \sqrt{|\hat{\mu}_i(t) - \tau|}$ if $\hat{\sigma}_i^2(t) = 0$, which, given Bernoulli arms with small means, could be the case for long runs of the algorithm.
-This seems suboptimal given the index of the APT algorithm is $B_i^{APT}(t) = \sqrt{T_i(t)} \cdot |\hat{\mu}_i(t) - \tau|$.
-
-One interesting observation, that we will observe in all experiments with synthetic Bernoulli arms, is the superior performance of the Bayes-UCB algorithm adapted from Kaufmann et al.
-(2012) which was originally designed for cumulative regret problems.
-Nonetheless, the algorithm will again and again proof to be the best performing.
-Compare with \autoref{sec:AppendixBUCB} for more analysis on the behavior of the Bayes-UCB algorithm on simulation 2.
-In particular, consider Figures 17 and 18 which show for individual arms, the distribution of pulls for that arm across simulations.
-These distributions highlight that both the APT and SLR fail in many iterations of the simulations to pull arms frequently enough to estimate their correct mean.
-The APT algorithm pulls the most difficult arm (Arm 6) in more than 5% of the simulations only once (during initialization).
-Consider arm 6 returns $X_{6,1} = 1$ as its first observation.
-Then $B_6(t+1) = 1 \cdot |1-0.05| = 0.95$.
-It will then not be pulled for a long time because the index is very large.
-Indeed, consider some arm that has been pulled 4000 times with $\mu_i(4000) = 0.03$.
-Then $B_i(t+1) = \sqrt{2000} \cdot |0.05-0.03| \approx 0.89$.
-Then even though we have basically no evidence for the performance of arm $6$, we would continue to pull arm $i$.
-Similar holds for the SLR algorithm.
-For both, the distribution of pulls for arm 6 is very flat across the interval of $[1,6000]$ pulls.
-In contrast, the distribution of pulls looks normally distributed for the Bayes-UCB algorithm with the mode between 2100 and 2300 pulls.
-The numerical problem that can arise for the APT and SLR algorithms might be weakened by the combination of a (weak) prior that shrinks the mean estimates, and the way in which quantiles are based on the posterior.
-Similar distributions are also reported for arms 1 and 10 in the appendix.
-
-We show empirically that part of this problem can be alleviated by including the D-Tracking rule proposed by Garivier and Kaufmann (2016) and discussed in \autoref{sec:OptimalBestArmIdentification} into the SLR algorithm.
-
-While the Bayes-UCB performance is impressive, we observe that also the Simple Likelihood Ratio strategy improves considerably upon the alternative strategies.
+
+The Simple Likelihood Ratio strategy improves considerably upon the alternative strategies.
 SLR reaches the average empirical error of 0.1 within the budget, and it improves at an exponential rate within the entire budget; in contrast to APT which appears to improve linearly in the observations.
@@
 
-In order to assess how the SLR strategy improves upon the APT algorithm, it is useful to look at how often the algorithm pulls each arm.
+In order to assess how the SLR strategy improves upon the APT algorithm, it is useful to look at how the algorithms allocate their sampling budget across arms.
 Given that we run the simulation 5000 times, we can compare across simulations how often an algorithm pulls each arm at a given round.
-Across the 5000 iterations, the algorithm should pull at any given iteration the arm most often that it thinks is the most difficult to classify.
-In the figure below, we plot the resulting curves where the value at an iteration is the 10-round moving average to remove some variation.
-
-We see that both APT and SLR correctly single out the two arms that are much closer to the threshold than the remaining arms, and allocate most of the budget to them.
-However, while SLR keeps the two arms constant at two different levels (about 1900 for arm 5 and about 2500 for arm 6), APT at first pulls arm 5 much more than arm 6.
-Then, for *both* arms, the budget allocated to them appears to converge to about 2000.
+During the 5000 iterations, the algorithm should pull at any given iteration the arm most often that it thinks is the most difficult to classify.
+In Figure 6, we plot the resulting curves where the y-axis shows a 10-round moving average of the pulls to remove some variation.
+
+The graph shows that both APT and SLR correctly single out the two arms closest to the threshold, and allocate most of the budget to them.
+However, while SLR keeps the two arms constant at two different levels (about 1900 for arm 5 and about 2500 for arm 6), APT at first pulls arm 5 more often than arm 6.
+Then, for *both* arms, the budget appears to converge to about 2000.
 Given that the two arms are symmetric around the threshold, it makes sense that APT would allocate the same exploration effort to them.
-And given that the variation of arm 5 away from the threshold is limited from below by zero, it is much easier for arm 6 to have an empirical mean larger than its true mean, and thus to have a larger index than arm 5.
+And given that the variation of arm 5 away from the threshold is limited from below by zero, it is much easier for arm 6 to have an empirical mean larger than its true mean, and thus to have a larger index than arm 5 in the beginning.
 Consequently, APT would prefer to sample arm 5.
@@
 The divergence is much smaller for arm 8.
-The asymmetry is even more dramatic for arm 1 and arm 10 with $d_1(0.001||0.05) \approx 0.046$ and $d_{10}(0.099||0.05) \approx 0.020$; in terms of the divergence, the distance between arm 1 and the threshold is twice as far as between arm 10 and the threshold.
+The asymmetry is even more dramatic for arm 1 and arm 10 with $d_1(0.001||0.05) \approx 0.046$ and $d_{10}(0.099||0.05) \approx 0.020$: In terms of the divergence, the distance between arm 1 and the threshold is twice as far as between arm 10 and the threshold.
 APT considers them to be equally distant from the threshold.
 
-```{r simulation2_results, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for simulation 2."}
+One interesting observation, that we will observe in all simulations with Bernoulli arms, is the superior performance of the Bayes-UCB algorithm adapted from Kaufmann et al.
+(2012) which was originally designed for cumulative regret problems.
+Nonetheless, the algorithm proves again and again to be the best performing.
+Compare with \autoref{sec:AppendixBUCB} for more analysis on the behavior of the Bayes-UCB algorithm in simulation 2.
+In particular, consider Figures 17 and 18 which show for individual arms the distribution of pulls for that arm across simulations.
+The distributions highlight that both the APT and SLR fail in many iterations of the simulations to pull arms frequently enough to estimate their correct mean.
+The APT algorithm pulls the most difficult arm (Arm 6) in more than 5% of the simulations only once (during initialization).
+Consider arm 6 returns $X_{6,1} = 1$ as its first observation.
+Then $B_6(t+1) = 1 \cdot |1-0.05| = 0.95$.
+It will then not be pulled for a long time because its index is very large.
+Indeed, consider some arm that has been pulled 4000 times with $\mu_i(4000) = 0.03$.
+Then $B_i(t+1) = \sqrt{2000} \cdot |0.05-0.03| \approx 0.89$.
+Even though we have basically no evidence for the performance of arm $6$, we would continue to pull arm $i$.
+Similar holds for the SLR algorithm.
+For both, the distribution of pulls for arm 6 is very flat across the interval of $[1,6000]$ pulls.
+In contrast, the distribution of pulls appears normally distributed for the Bayes-UCB algorithm with the mode between 2100 and 2300 pulls.
+The numerical problem that arises for the APT and SLR algorithms might be weakened for the Bayes-UCB algorithm by the combination of a (weak) prior that shrinks the mean estimates, and the way in which quantiles are based on the posterior.
+Also, the fact alone that it is based on confidence bounds of the empirical mean, instead of the empirical mean itself.
+We show in the appendix that the problem does not only occur for arm 6.
+
+Empirically, part of this problem can be alleviated by including the D-Tracking rule proposed by Garivier and Kaufmann (2016) and discussed in \autoref{sec:OptimalBestArmIdentification} into the SLR algorithm, as it ensures that no arm is ``left behind'' in terms of samples.
+Figure 5 shows a significant improvement for the SLR-D algorithm in comparison to the SLR algorithm without D-Tracking.
+However, the algorithm still does not reach the performance of Bayes-UCB.
+
+Lastly, we remark on the shape of the error curve of the uniform strategy.
+Even though the uniform strategy samples arms at random from the set of arms with the least observations at any round, we observe a sawtooth pattern for simulation 2 and 3.
+This is an artifact of the comparison against the threshold of $0.05$ and $0.01$ respectively, combined with the discrete $0$ and $1$ observations.
+Take for example an arm with a true mean of $\mu = 0.06$ compared against $\tau = 0.05$.
+Let's say the arm observes the first 1 after 15 samples, $X_{15} = 1$, such that $\hat{\mu}(15) = 1/15 \approx 0.067$.
+At this point, it is correctly classified as above the arm.
+Even if the next samples are zeroes, it will continue to be correctly classified until observation 20.
+At that point, $\hat{\mu}(20)$ = 1/20 = 0.05.
+By observing one more observation, the arm will be classified as below the threshold, since then $\hat{\mu}(21) = 1/21 < 0.05 = \tau$.
+The classification is suddenly wrong for no particular reason, and a sudden spike in the error curve occurs.
+In the graph of simulation 3 it is obvious that the spike occurs with a period length of about 100 samples, which corresponds to $\tau = 0.01=1/100$.
+This explains why we do not observe such a pattern in the first simulation with $\tau = 0.5$, or for the continuous Exponential distribution in simulation 4.
+
+```{r simulation2_results, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for simulations 2 and 3. Note the different x-axes."}
 library(ggplot2)
@@
 
-alg_names <- c(rep(c("Uniform", "APT", "AugUCB","SLR", "SLR-D", "B-UCB"), 
+alg_names <- c(rep(c("Uniform", "APT", "AugUCB",
+                     "SLR", "SLR-D", "B-UCB"), 
                    each = 6991), rep("EVT", 6981))
@@
                  loc6nt_comp_BUCB_horizon_7000, loc6nt_comp_EVT))
-loc6nt_comp_res <- data.frame(index = index, names = alg_names, 
+loc6nt_comp_res <- data.frame(index = index, Algorithm = alg_names, 
                             results = alg_res)
-ggplot(loc6nt_comp_res, aes(x = index, y = results)) + 
-  geom_line(aes(group = names, color = names)) +
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
+
+load(file = paste0(current_path, "loc7nt_comp_UNIFORM_10000.Rda"))
+load(file = paste0(current_path, "loc7nt_comp_APT_10000.Rda"))
+load(file = paste0(current_path, "loc7nt_comp_LR_10000.Rda"))
+load(file = paste0(current_path, "loc7nt_comp_LRD_10000.Rda"))
+load(file = paste0(current_path, "loc7nt_comp_BUCB_horizon_10000.Rda"))
+load(file = paste0(current_path, "loc7nt_comp_AugUCB_10000.Rda"))
+load(file = paste0(current_path, "loc7nt_comp_EVT.Rda"))
+
+alg_names <- c(rep(c("Uniform", "APT", "AugUCB", 
+                     "SLR", "SLR-D", "B-UCB"), 
+                   each = 9990), rep("EVT", times = 9979))
+index <- c(rep(11:10000, times = 6), 22:10000)
+alg_res <- log(c(loc7nt_comp_UNIFORM_10000, loc7nt_comp_APT_10000,
+                 loc7nt_comp_AugUCB_10000, loc7nt_comp_LR_10000,
+                 loc7nt_comp_LRD_10000,
+                 loc7nt_comp_BUCB_horizon_10000, loc7nt_comp_EVT))
+loc7nt_comp_res <- data.frame(index = index, Algorithm = alg_names, 
+                            results = alg_res)
+
+sim23_res <- rbind.data.frame(loc6nt_comp_res, loc7nt_comp_res)
+sim23_res$Simulation <- c(rep("Simulation 2", 48927), rep("Simulation 3", 69919))
+
+ggplot(sim23_res, aes(x = index, y = results)) + 
+  geom_line(aes(group = Algorithm, color = Algorithm)) +
   geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
-  labs(title = "Results of Synthetic Experiment 2", 
-       subtitle = expression(paste("Difficult scenario for APT; ", 
-                                   tau,' = 0.05 and 10 arms. Dashed line at Error = 0.1.')), 
+  facet_grid(.~Simulation, scales = "free") +
+  labs(subtitle = "Dashed Line indicates Error = 0.1.",
        y = "log(Error)", x = "Round Index") +
@@
   facet_grid(.~algorithm) +
-  labs(x = "Index", y = "10 Rounds Moving Average",
-       title = "Average Number of Pulls Allocated to Each Arm per Round",
-       subtitle = "5000 iterations; a value of 1000 means that in 20% of 
-the iterations the arm was pulled in that round.") +
+  labs(x = "Index", y = "10 Rounds Moving Average"#,
+       #title = "Average Number of Pulls Allocated to Each Arm per Round",
+       #subtitle = "5000 iterations; a value of 1000 means that in 20% of 
+#the iterations the arm was pulled in that round."
+) +
   theme_bw() +
@@
 
-### Simulation 3: Bernoulli with $\tau = 0.01$
-
-In the third experiment, we lower the threshold further to $\tau = 0.1$ and arrange the arms on a $\log_{10}$ scale around it.
-Again, there is no epsilon interval.
-We add one additional arm, thus now classifying eleven arms.
-We run the same arms as previously.
-Notice that the experiment horizon is now $10000$ rounds instead of $7000$ rounds as in the previous experiment.
-We test the same algorithms used in the previous two experiments.
+### Simulation 3: Bernoulli Arms and $\tau = 0.01$
+
+In the third experiment, we lower the threshold further to $\tau = 0.01$ and arrange now $K=11$ arms on a $\log_{10}$ scale around it.
+Again, we set $\epsilon = 0$.
+We compare the same algorithms as previously with the settings adapted to $\tau$ and $\epsilon$ accordingly.
+Notice that the experiment horizon is now $T=10000$ rounds instead of $T=7000$ rounds in the previous experiment.
 
@@
 
-knitr::kable(t(mean_loc7nt), digits = 4, col.names = paste0("V", 1:11), caption = "Mean of arms in simulation 3 compared to a threshold of 0.01.")
+mean_loc7nt_char <- c("10^-4", "10^-3.5", "10^-3.25", "10^-3", "10^-2.75", "10^-2.5", "10^-2.25", "10^-1.85", "10^-1.75", "10^-1.5", "10^-1")
+
+#get_apt_complexity(mean_loc7nt, 0.01, 0)
+
+knitr::kable(t(mean_loc7nt), digits = 4, col.names = paste0("V", 1:11), caption = "Mean of arms in simulation 3.")
 ```
 
-Looking at the performance after 7000 rounds, we see that the problem appears to be slightly more difficult compared to the previous one.
+Looking at the performance after 7000 rounds, we see that the problem appears to be slightly more difficult compared to the previous one ($H_3^{APT} \approx 210359$).
 We see that up until this point the variance-based strategies cannot improve upon APT.
@@
 As in the previous experiment, Bayes-UCB and SLR show significant improvements on this Bernoulli problem with very small means and threshold compared to APT in particular.
-
-```{r simulation3_results, echo = FALSE, fig.align = "center", out.width = '80%', , fig.cap = "Performance comparison of algorithms for simulation 3."}
+Furthermore, the observation that the SLR algorithm with D-Tracking rule performs better than without is replicated.
+
+```{r simulation3_results, echo = FALSE, include = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for simulation 3."}
 library(ggplot2)
@@
   geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
-  labs(title = "Results of Synthetic Experiment 3", 
-       subtitle = expression(paste("Difficult scenario for APT; ", 
-                        tau,' = 0.01 and 11 arms. Dashed line at Error = 0.1.')), 
+  labs(subtitle = "Dashed Line indicates Error = 0.1.", 
        y = "log(Error)", x = "Round Index") +
-  theme_bw() +
-  theme(legend.position = "bottom")
+  theme_bw() #+
+  #theme(legend.position = "bottom")
 ```
@@
 
-In \autoref{sec:LRforUnivariateExponentialFamily}, we show that the likelihood ratio has a very useful form for the univariate exponential family of distributions, which allows us to use the SLR algorithm not only on Bernoulli arms, but also on Exponential or Poisson distributions, for example.
+In \autoref{sec:LRforUnivariateExponentialFamily}, we show that the likelihood ratio has a very useful form for the one-parameter exponential family of distributions, which allows us to use the SLR algorithm not only on Bernoulli arms, but also on Exponential or Poisson distributions, for example.
 In simulation 4, we consider Exponential distributions, in simulation 5, we test the algorithms on Poisson distributions.
@@
 We run the same algorithms as before except for Bayes-UCB (even though it should certainly be possible to adapt it to these case based on a Gamma prior).
-In the case of the Exponential arms, we classify against $\tau = 1$ and have sampled their mean parameters of the arms from an Exponential distribution with rate $\theta = 1$.
+In the case of the Exponential arms, we classify against $\tau = 1$ and have sampled the arms' mean parameters from an Exponential distribution with rate $\theta = 1$.
 The Poisson arms are classified against a threshold of $\tau = 0.4$, with the mean parameters being sampled from an Exponential distribution with mean $\mu = 0.7$.
@@
 
-For the Exponential arms, APT crosses the 0.1 error mark first, followed by the AugUCB algorithm.
+For the Exponential arms, APT crosses the 10% error mark first, followed by the AugUCB algorithm.
 All algorithms perform better than uniform sampling.
@@
 
-```{r simulation4_results, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for simulation 4."}
+```{r simulation4_results, include = FALSE, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for simulation 4."}
 library(ggplot2)
@@
   geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
-  labs(title = "Results of Experiment 4", 
-       subtitle = expression(paste("Exponential distributed arms; ", 
-                        tau,' = 1 and 20 arms. Dashed line at Error = 0.1.')), 
+  labs(subtitle = "Dashed Line indicates Error = 0.1.",
+       y = "log(Error)", x = "Round Index") +
+  theme_bw()# +
+  #theme(legend.position = "bottom")
+```
+
+In the case of Poisson arms, the performance of the arms is more clear cut.
+As expected, SLR improves upon APT.
+APT outperforms the EVT algorithm, which occurs even though the variance of all arms considered in this experiment is in $[0,1]$.
+After about 1000 observations, APT and EVT appear to improve at about the same rate, but APT has a much better initial exploration phase.
+Given the previous simulations, it is surprising to see the Augmented-UCB algorithm to come ahead after $T=10000$ observations.
+After about half the budget, the same pattern as before occurs where there is a drastic change in sampling behavior.
+This suffices to outpace both APT and SLR.
+
+```{r simulation5_results, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for simulations 4 and 5. Note the different x-axes."}
+library(ggplot2)
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/exponential/"
+
+load(paste0(current_path, "exp2_comp_LR.Rda"))
+load(paste0(current_path, "exp2_comp_APT.Rda"))
+load(paste0(current_path, "exp2_comp_EVT.Rda"))
+load(paste0(current_path, "exp2_comp_UNIFORM.Rda"))
+load(paste0(current_path, "exp2_comp_AugUCB.Rda"))
+
+alg_names <- c(rep(c("Uniform", "APT","SLR", "AugUCB"), 
+                   each = 3981), rep("EVT", 3961))
+index <- c(rep(20:4000, times = 4), 40:4000)
+alg_res <- log(c(exp2_comp_UNIFORM, exp2_comp_APT, exp2_comp_LR,
+                 exp2_comp_AugUCB, exp2_comp_EVT))
+exp2_comp_res <- data.frame(index = index, Algorithm = alg_names, 
+                            results = alg_res)
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/poisson/"
+
+load(paste0(current_path, "pois2_comp_LR.Rda"))
+load(paste0(current_path, "pois2_comp_APT.Rda"))
+load(paste0(current_path, "pois2_comp_EVT.Rda"))
+load(paste0(current_path, "pois2_comp_UNIFORM.Rda"))
+load(paste0(current_path, "pois2_comp_AugUCB.Rda"))
+
+alg_names <- c(rep(c("Uniform", "APT", "SLR", "AugUCB"), each = 9981), 
+               rep("EVT", 9961))
+index <- c(rep(20:10000, times = 4), 40:10000)
+alg_res <- log(c(pois2_comp_UNIFORM, pois2_comp_APT, 
+                 pois2_comp_LR, pois2_comp_AugUCB, pois2_comp_EVT))
+pois2_comp_res <- data.frame(index = index, Algorithm = alg_names, 
+                            results = alg_res)
+
+exp45_res <- rbind.data.frame(exp2_comp_res, pois2_comp_res)
+exp45_res$Distribution <- c(rep("Exponential", 19885), rep("Poisson", 49885))
+
+ggplot(exp45_res, aes(x = index, y = results)) + 
+  geom_line(aes(group = Algorithm, color = Algorithm)) +
+  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
+  facet_grid(.~Distribution, scales = "free") +
+  labs(#title = "Results of Experiment 5", 
+       subtitle = "Dashed line at Error = 0.1.", 
        y = "log(Error)", x = "Round Index") +
@@
 
-In the case of Poisson arms, the performance of the arms is more clear cut.
-As expected, SLR improves APT and the other strategies.
-APT outperforms the EVT algorithm, which occurs even though the variance of all arms considered in this experiment is in $[0,1]$.
-But similarly to the Bernoulli simulations, the EVT might again have a hard time dealing with sequences of observations that are all equal to $0$ for a long time.
-After about 1000 observations, APT and EVT appear to improve at about the same rate, but APT had a much better initial exploration phase.
-
-```{r simulation5_results, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for simulation 5."}
-library(ggplot2)
-current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/poisson/"
-
-load(paste0(current_path, "pois2_comp_LR.Rda"))
-load(paste0(current_path, "pois2_comp_APT.Rda"))
-load(paste0(current_path, "pois2_comp_EVT.Rda"))
-load(paste0(current_path, "pois2_comp_UNIFORM.Rda"))
-
-alg_names <- c(rep(c("Uniform", "APT", "SLR"), each = 9981), 
-               rep("EVT", 9961))
-index <- c(rep(20:10000, times = 3), 40:10000)
-alg_res <- log(c(pois2_comp_UNIFORM, pois2_comp_APT, 
-                 pois2_comp_LR, pois2_comp_EVT))
-pois2_comp_res <- data.frame(index = index, Algorithm = alg_names, 
-                            results = alg_res)
-ggplot(pois2_comp_res, aes(x = index, y = results)) + 
-  geom_line(aes(group = Algorithm, color = Algorithm)) +
-  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
-  labs(title = "Results of Experiment 5", 
-       subtitle = expression(paste("Poisson distributed arms; ", 
-                        tau,' = 0.4 and 20 arms. Dashed line at Error = 0.1.')), 
-       y = "log(Error)", x = "Round Index") +
-  theme_bw() +
-  theme(legend.position = "bottom")
-```
-
-## Real Data \label{sec:RealData}
+## Experiments on Web Analytics Data \label{sec:RealData}
 
 In the following, we present the results of two experiments performed on a real world data set.
-While most new multi-armed bandit algorithms are assessed on synthetic data, as we have done in \autoref{sec:SyntheticData}, a real world data set is useful to observe how algorithms perform in presence of, for example, not fully i.i.d.
+While most multi-armed bandit algorithms are assessed on synthetic data, as we have done in \autoref{sec:SyntheticData}, a real world data set is useful to observe how algorithms perform in presence of, for example, not perfectly i.i.d.
 samples.
-While of course every company tries to make their experiments as ideal as possible, there will always be problems.
+Every company of course tries to run their algorithms under settings as ideal as possible, but there will always be problems.
 Thus our experiments serve as a first robustness check on the algorithms introduced before.
@@
 Data have been collected by the German online shop [Amorelie](https://amorelie.de) as part of standard website analytics.
-For 197 selected products, we observe the number of users visiting each product's detail page (PDP) at a given minute.
+For 197 selected products, we observe the number of users visiting each product's detail page (PDP) during a given minute.
 The data set we use here has been collected during the entire month of November 2016.
@@
 The goal is to perform 5000 runs over the sample to confidently assess the performance.
-Since we want to preserve the potential time dependency of the data, a simple resampling of the data is not an option to create the needed 5000 variations of the sample.
+Since we would like to preserve potential time dependencies in the data, a simple resampling of the data is not an option to create the needed 5000 variations of the sample.
 Instead we perform time series cross validation.
@@
 
-While the data is count data (the number of visits to a PDP during a given minute), we binarize the data by applying a certain threshold.
+```{r, echo = FALSE}
+load("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/arms_example_binary.Rda")
+
+knitr::kable(arms_example_binary, caption = "Example of the binary time series data for five products.")
+```
+
+While the data set consists of count data (the number of visits to a PDP during a given minute), we binarize the data by applying a certain threshold.
 If the count is above this threshold, the new observation is $1$, else $0$.
-Thus we have a binary time series of length 43200 for each of the 197 products.
-Given that the number of visitors that come to a given PDP is likely to vary by time of day and by day, and in general over time, we expect that the mean of the time series to not be stable over time.
-For example, less visitors will come during night than during the evening.
-This leads to a decrease in the average, and a daily seasonality.
+Thus we have a binary time series of length $60\cdot 24 \cdot 30 = 43200$ for each of the 197 products.
+Given that the number of visitors that reach a given PDP is likely to vary by time of day and by day, and in general over time, we expect the mean of the time series to not be stable over time.
+For example, less visitors visit during night than during the evening.
+This leads to a decrease in the average number of visits, and creates a daily seasonality.
 On the other hand, more users may visit the site during a weekend, thus leading to a spike on Saturdays and Sundays.
-Because of the latter time dependency, it is best practice to run online A/B tests for at least a week, or an integer multiple of weeks, so as to take into account the weekly seasonality in the time series.
-For this reason, the experiments we present below were run on $60 \cdot 24 \cdot 7 = 10080$ observations for each arm, so as to have a sample for one full week.
-
-We can look at summary statistics for the sample means of the 197 products over the month of November to get a first impression of the data we are dealing with.
+Because of the latter time dependency, it is best practice to run online A/B tests for at least a week^[See for example the "A/B Testing in the Wild" presentation by Emily Robinson, <https://youtu.be/SF-ryGgLOgQ>], or an integer multiple of weeks, so as to take into account the weekly seasonality in the time series.
+For this reason, the experiments we present below are run on $60 \cdot 24 \cdot 7 = 10080$ observations for each arm, so as to have a sample for one full week.
+
+We can look at summary statistics for the sample means of the 197 products over the month of November to get a first impression of the binary data we are dealing with.
 We see that most products have a small mean, which is very common also for actual conversion rate or click-through rate data that can be tested with A/B tests or multi-armed bandits.
@@
 If we used a threshold $\gamma$ to binarize the count data, then this means that on average every fourth minute the count of visitors was below $\gamma$ for this product.
-On the other hand, we conclude that using thresholding bandit strategies to test the products against a threshold of for example $\tau = \frac{2}{60} = 0.333$ or $\tau = \frac{5}{60} = 0.083$ is likely to create more complex problems than a threshold of, say, $\tau = \frac{15}{60} = 0.25$ would.
+On the other hand, we conclude that using thresholding bandit strategies to test the products against a threshold of for example $\tau = \frac{2}{60} = 0.0333$ or $\tau = \frac{5}{60} = 0.083$ is likely to create more complex problems than a threshold of, say, $\tau = \frac{15}{60} = 0.25$ would.
 
@@
 In the first experiment, we pick ten arms randomly from the set of 197 arms.
-The experiment is run with a budget of $T=10080$ samples during each of the $5000$ iterations for which we repeat the experiment.
+The experiment is run with a budget of $T=10080$ samples for each of the $5000$ iterations for which we repeat the experiment.
 Given the time series cross-validation idea described above, this means that in total, $15080$ observations of the $43200$ available observations per arm are used in training.
 In the thresholding bandit problem, we classify arms as below or above a threshold.
-Thus we can evaluate the strategies also based on whether their classifications are correct in a holdout sample.
+Thus we can evaluate the strategies also based on whether their classifications are correct in a holdout sample (the time period after training).
 As this holdout sample, we can use the 10080 observations in our data set that follow the first 15080 observations used in training.
@@
 knitr::kable(rbind(Training, Test)[,order(Training)], digits = 3, col.names = names(data_amo3_mean_firsthalf)[order(Training)],
-             caption = "Count rates for ten products for both training and test sample.")
+             caption = "Training and test sample means for experiment 1.")
 
@@
 We see that while the rates do vary across training and test samples, they are relatively stable which is likely due to the fact that the samples come from an entire week's worth of observations.
-In particular, since we test against a threshold of $\tau = \frac{2}{60} = 0.333$ in this experiment, the classifications of arms do not differ across training and test data.
+In particular, since we test against a threshold of $\tau = \frac{2}{60} = 0.0333$ in this experiment, the true classifications of arms do not differ across training and test data.
 A correct classification after training will be correct in the test set.
@@
 
-When comparing the rates against the threshold, we see that three products are below the already small threshold.
+```{r, include = FALSE}
+#When comparing the rates against the threshold, we see that three products are below the already small threshold.
 Product $V64$ seems to be especially difficult to classify correctly, even without time dependency.
 On the other hand, arms $V119$ and $V118$ should be much easier than the rest.
+```
 
 In order to visualize the time dependency that we expect for our samples, we plot a moving average of the mean of the time series for the first week of data.
-To remove the daily seasonality, we select a moving average window of $60\cdot24 = 1440$ observations.
+To remove daily seasonality, we select a sliding window of $60\cdot24 = 1440$ observations.
 To make the time dependency even more obvious, we contrast the actual data against synthetic data generated using the sample means of the actual data.
 
-The graph again underlines that arm $V64$ is likely to be very difficult to classify given that it's moving average even crosses the threshold twice.
-The same is true for arm $V139$, which is not visible when considering the overall mean alone.
+The graph again underlines that arm $V64$ is likely to be very difficult to classify given that its moving average crosses the threshold twice.
+The same is true for arm $V139$, which is not visible when looking at the overall mean alone.
 Furthermore, arms $V159$ and $V189$ come very close to the threshold at times.
 
-```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Rolling average for the arms used in experiment 1."}
+```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Moving average for the arms used in experiment 1."}
 library(zoo)
@@
   facet_grid(.~source) + 
-  labs(title = "Moving average over 24*60 observations (1 day)", 
-       subtitle = "Horizontal bar indicates the threshold.", 
+  labs(#title = "Moving average over 24*60 observations (1 day)", 
+       subtitle = "Dashed line indicates the threshold.", 
        x = "Index", y = "One day moving average") +
@@
 These difficulties seem to have a large impact on the performance of all algorithms.
-Given that the data are $\{0,1\}$ observations, we can compare all algorithms in a setting in which one expects all assumptions to hold before having observed the data.
-The distribution is sub-Gaussian for the APT algorithm, bounded between $0$ and $1$ for the variance-based algorithms, and assumed to be Bernoulli for the SLR algorithm.
+Given that the data are binary observations, we can compare all algorithms in a setting in which one expects all assumptions to hold before having observed the data: The distributions are sub-Gaussian for the APT algorithm, bounded between $0$ and $1$ for the variance-based algorithms, and assumed to be Bernoulli for the SLR algorithm.
 Additionally, we use the Bayes-UCB algorithm as it performed best on the synthetic data.
-
 We set $\epsilon = 0$, and $\tau = 2/60$.
@@
 (2017), that is, $\rho = 1/3$.
-For B-UCB we set the prior to $\alpha_0 = \tau$ and $\beta_0 = 1-\tau$, and pick $c=1$.
-All other algorithms are parameter free.
+For Bayes-UCB we set the prior to $\alpha_0 = \tau$ and $\beta_0 = 1-\tau$, and pick $c=1$.
 
@@
   geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
-  labs(title = "Results of Real Data Experiment 1", 
+  labs(#title = "Results of Real Data Experiment 1", 
        subtitle = paste0("Dashed Line indicates Error = 0.1."), 
        y = "log(Error)", x = "Round Index") +
-  theme_bw() +
-  theme(legend.position = "bottom")
+  theme_bw()
 ```
@@
 Third, again in contrast to the results on synthetic data, we observe non-monotonicity in the error curves.
-Given that the highs and lows run very much parallel for the different models, it stands to reason that this effect is caused by the variation in means of the arms over time.
+Given that the highs and lows for the different models run mostly parallel, it stands to reason that this effect is caused by the variation in means of the arms over time.
 Indeed, roughly comparing the error curves to the moving averages in the previous figure, the increase in errors after round $5000$ and the decreasing error after round $7500$ seems to line up with the fluctuations observed in the data.
 Given that we evaluate the models against a sample mean of all observations, it is not surprising that the uniform sampling strategy has a certain advantage when it comes to "factoring out" the seasonalities.
-In contrast, the adaptive sampling schemes try to adapt more or less quickly to the changes in the means; a feature that would be valuable in a cumulative regret multi-armed bandit setting.
+In contrast, the adaptive sampling schemes try to adapt more or less quickly to the changes in the means--a feature that would be valuable in a cumulative regret multi-armed bandit setting.
 Here, however, it leads to wrong estimates of the overall sample mean.
@@
 If we focus on a comparison of adaptive sampling strategies and less on their globally bad performance, we see that the variance based strategies perform worse than APT and SLR.
-Very dramatic is the behavior of the Augmented-UCB algorithm, which first seems to perform well; this, however, is a result of it mostly pulling arms uniformly, until it starts to adapt its sampling and discarding arms after nearly 5000 rounds.
+Very dramatic is the behavior of the Augmented-UCB algorithm, which first seems to perform well; this, however, is a result of it pulling arms mostly uniformly, until it starts to adapt its sampling and discarding arms after nearly 5000 rounds.
 The result is a dramatic increase in error which leads to the worst performance at the budget horizon.
-The difference between APT, SLR, and EVT is small, and their performance fluctuates in sync.
+The differences between APT, SLR, and EVT are small, and their performance fluctuates in sync.
 None of them is really able to converge due to the changes in the underlying means.
@@
 knitr::kable(rbind(Training, Test)[,order(Training)], digits = 3, col.names = names(data_amo4_mean_firsthalf)[order(Training)],
-             caption = "Count rates for ten products for both training and test sample.")
+             caption = "Training and test sample means for experiment 2.")
 
@@
 As in the previous experiment, we can also take a look at the one day moving averages of the arms to quickly assess the time dependency of the means.
-Given that the data here are collected at the same time points as the data used in the previous experiment, it is not surprising to see a similar spike in means during the second half of the observations with the maximum moving average around index 7500.
-We also observe that these fluctuations are heavier for products with in general larger means (that is, more visitors on the website).
-But these fluctuations are clearly much larger and systematic than those observed for synthetic data with the same sample means.
-
-Given the moving averages and the previous experiment, the performance results of Experiment 2 shown in the next figure are not surprising.
+Given those and the previous experiment, the performance results of Experiment 2 shown in Figure 13 are not surprising.
 We recognize the same structure as previously.
@@
 Interestingly, Bayes-UCB performs clearly worst of all strategies.
-Its performance changes at the same time as Augmented-UCB starts to adapt its sampling strategy, near round 7000.
-
+Its performance changes at the same time as AugUCB starts to adapt its sampling strategy.
 This last fact is of particular interest, as Bayes-UCB is dramatically better than the other strategies in experiments on synthetic data.
-On the right hand side of the same figure, the performance of the algorithms on synthetic data from Bernoulli distributions with the same sample mean is depicted.
-On this data, Bayes-UCB performs very well, ending at an average error of about 0.1% of the simulations.
+
+On the right hand side of figure 13, the performance of the algorithms on synthetic data from Bernoulli distributions is depicted.
+These synthetic samples were sampled from distributions with mean equal to the sample means of the real data.
+We thereby create similar samples that are perfectly i.i.d.
+On this data, Bayes-UCB performs very well, ending at an average error rate of about 0.1%.
 This mirrors its performance observed in the previous simulations with synthetic data.
 Also all other adaptive strategies perform clearly better now, and their error rates are strictly decreasing.
-Interestingly, the uniform sampling scheme is now much worse than in the experiment on real data; it does no longer have the advantage of sampling the different mean phases at a representative rate.
+Interestingly, the uniform sampling scheme is now clearly worse than in the experiment on real data; it does no longer have the advantage of sampling the different mean phases at a representative rate.
 Excluding Bayes-UCB, we see that the SLR algorithm performs the best, followed by the variance-based algorithms.
 APT comes in at the same error rate as uniform sampling.
-While the difference between SLR and EVT are less than 2% (1.2% vs 3%), the difference to uniform sampling (10%) is relevant.
-The performance of 10% error rate is achieved by SLR about 1000 observations earlier than by EVT.
-
-```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Rolling average of arms used in experiment 2."}
+While the difference between SLR and EVT is less than 2% (1.2% vs 3%), the difference to uniform sampling (10%) is relevant.
+The error rate of 10% is achieved by SLR about 1000 observations earlier than by EVT.
+
+```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Moving average of arms used in experiment 2. Dashed line indicates the threshold."}
 library(zoo)
@@
   facet_grid(.~source) + 
-  labs(title = "Moving average over 24*60 observations (1 day)", 
+  labs(#title = "Moving average over 24*60 observations (1 day)", 
        subtitle = "Horizontal bar indicates the threshold.", 
@@
   facet_grid(.~source) + 
-  labs(title = "Running average of 10080 observations (1 week)", 
+  labs(#title = "Running average of 10080 observations (1 week)", 
        subtitle = "Horizontal bar indicates the threshold.", 
@@
   facet_grid(.~source) + 
-  labs(title = "Running average of 10080 observations (1 week), 12hrs later", 
+  labs(#title = "Running average of 10080 observations (1 week), 12hrs later", 
        subtitle = "Horizontal bar indicates the threshold.", 
@@
   geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
-  labs(title = "Results of Real Data Experiment 2", 
+  labs(#title = "Results of Real Data Experiment 2", 
        subtitle = paste0("Dashed line indicates Error = 0.1."), 
@@
 
-Again using a plot of the pulls at each round across the 5000 simulations in Figure 17, we can try to understand why some strategies perform well on synthetic data, but poorly on the time series data.
+Using a plot of the pulls at each round across the 5000 simulations in Figure 14, as we did for simulation 2, we can try to understand why some strategies perform well on synthetic data, but poorly on the time series data.
 
@@
 It seems that the poor performance can be mostly explained by the seasonality and sudden changes in the samples over time.
-The observations clearly are not i.i.d.
-sampled.
-However, the effect might be overly stark due to the fact that we use minutely time series data, which leads to observations even when in minutes when there are few or no users (during night).
+The observations clearly do not correspond to i.i.d.
+Bernoulli samples, but have large time dependencies.
+However, the effect might be overly stark due to the fact that we use minutely time series data, which leads to observations even in minutes when there are few or no users on the website (during night).
 In contrast, the daily seasonality might be less represented in an actual online experiment observations are only drawn when there is an actual visitor on the site (and a proper conversion rate would fluctuate less than the count of visitors on a given product page).
@@
 Furthermore, some of the problems in dealing with the fluctuating distributions might be specific to the thresholding bandit problem as opposed to the cumulative regret or best-arm identification problems.
-In the experiments above, we observe that the order of the arms is mostly unaffected by the seasonalities and fluctuations, which would mean that the best arm could still be identified.
+In the experiments above, we observe that the order of the arms is mostly unaffected by the seasonalities and fluctuations, which implies that the best arm could still be identified.
 In contrast, given that all arms are individually classified against the *fixed* threshold, a weekly seasonality can declare a correct classification on the first half of the sample null and void on the second half of the sample.
@@
 
-We thank Alexandra Carpentier, Andrea Locatelli, and Urun Dogan for many hours of fruitful discussions and ideas.
+We thank Alexandra Carpentier, Andrea Locatelli, Urun Dogan, and Marius Kloft for many hours of fruitful discussions and ideas.
 We thank Carlo Alberto Dall'Amico for bringing our attention to multi-armed bandits in the first place.
@@
 
+\newpage
+
 # References
+
+\newpage
 
@@
 \end{align*}
-
-## Lower Bound on Probability of Error in FB-Top-$m$ with Gaussian Arms \label{sec:KaufmannLBTopMGaussian}
-
-While we would like to move beyond Gaussian distributions in the work at hand, the idea for the proof might show a way of how the ideas can be transferred to the thresholding bandit problem.
-We first state the result and then discuss the proof.
-
-\begin{lemma}[Lemma 15, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma15}
-Let $\nu$ and $\nu'$ be two bandit models such that $S^*_m(\nu) \neq S^*_m(\nu')$. Then
-
-\begin{equation*}
-\max \big( \mathbb{P}_{\nu}(S \neq S^*_m(\nu)), \mathbb{P}_{\nu'}(S \neq S^*_m(\nu')) \big) \geq \frac{1}{4} \exp \Big(-\sum_{a=1}^{K} \mathbb{E}_{\nu}[N_a] \KL(\nu_a, \nu_a') \Big).
-\end{equation*}
-\end{lemma}
-
-The following theorem only holds in the case of Gaussian bandit models with equal known variance.
-
-\begin{theorem}[Theorem 17, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem17}
-
-Let $\mathcal{M}_m = \{\nu = (\nu_1, \dots, \nu_K): \nu_a = \mathcal{N}(\mu_a, \sigma^2), \mu_a \in \mathbb{R}, \mu_{[m]}\neq \mu_{[m+1]}\}.$ Furthermore, let $\nu$ be such that $\mu_1 > \dots > \mu_m > \mu_{m+1} > \dots > \mu_K$, and let
-
-\begin{equation*}
-H^+(\nu) = \sum_{a=1}^m \frac{2\sigma^2}{(\mu_a - \mu_{m+1})^2}, \quad H^-(\nu) = \sum_{a=m+1}^K \frac{2\sigma^2}{(\mu_m - \mu_a)^2} \quad
-and \quad
-H(\nu) = H^+(\nu) + H^-(\nu).
-\end{equation*}
-
-There exists $a \in \{1, \dots, m\}$ and $b \in \{m+1, \dots, K\}$ such that the bandit model $\nu^{[a,b]}$ described in Figure 4 (Kaufmann et al., 2016) satisfies $H(\nu^{[a,b]}) < H(\nu)$ and is such that
-
-\begin{equation*}
-\max \big( p_t(\nu),p_t(\nu^{[a,b]})\big) \geq \frac{1}{4} \exp \big(-\frac{4t}{\bar{H}(\nu)}\big), \quad where \quad \bar{H}(\nu) = \frac{H(\nu) \min(H^+(\nu),H^-(\nu))}{H(\nu)+\min(H^+(\nu),H^-(\nu))}
-\end{equation*}
-\end{theorem}
-
-Given that we are again in the Top-$m$ setting, the proof idea is similar to the proof of Theorem \ref{theorem:KaufmannEtAlTheorem4} in that we again consider problems in which we switch arms around the threshold implied by $\mu_{[m]}$ and $\mu_{[m+1]}$.
-Given that, one might hope to apply a similar proof to the thresholding bandit problem.
-As we see in \autoref{sec:AppendixAPTLB}, a flip around the threshold is used in the proof of the lower bound in Theorem 1 of Locatelli et al.
-(2016).
-However, there, again, the distributions are assumed to be Gaussian.
-This brings the big advantage that the Kullback-Leibler divergence is symmetric, and the feedback can take values on all $\mathbb{R}$.
-This is important, as is allows us to easily define alternative problems by a flip around the threshold with the same complexity as the original problem.
-This would not hold for KL-divergences that are not symmetric (e.g., for Bernoulli arms).
-For the full proof, refer to page 20 in Kaufmann et al.
-(2016).
 
@@
 $$
+
 To make the bound as tight as possible, we choose the alternative model that minimizes $\KL(\nu_1', \nu_1)$ while still ensuring that $\mathcal{S}_{\tau}^* {'} = \{\emptyset\}$.
-In our case of the thresholding bandit with univariate exponential family distributions, this is given by choosing $\mu_1' = \tau$.
+In our case of the thresholding bandit with one-parameter exponential family distributions, this is given by choosing $\mu_1' \rightarrow \tau$ (not equal to $\tau$ since else the classification of $\nu_1$ is again correct).
 By pluggin in, we get the result:
@@
 $$
-t \KL(\tau, \mu_1) \geq -\log p_t(\nu).
+t \KL(\tau, \mu_1) \geq -\log p_t(\nu) \quad \text{for} \; \mu_1' \rightarrow \tau.
 $$
@@
 
-We show how the Bayes-UCB algorithm (Algorithm 1, Kaufmann et al., 2012) is adopted to the thresholding bandit problem to be used in the experiments in chapter \autoref{chap:Experiments}.
-
-We adopt their Algorithm 1 for Bernoulli distributions as follows:
+We show how the Bayes-UCB algorithm (Algorithm 1, Kaufmann et al., 2012) is adapted to the thresholding bandit problem to be used in the experiments in chapter \autoref{chap:Experiments}.
+The adapted version of their Algorithm 1 is given in Algorithm 4 below.
+In particular, notice that we not only calculate upper quantiles $q_i^u(t)$, but also lower quantiles $q_i^l(t)$, as we have to be able to compare against $\tau$ from both sides.
+These quantiles rely on the posterior distributions $\lambda_i^t$ for each mean $\mu_i$.
+In our case, we employ Beta prior distributions as conjugate prior for the Bernoulli distributions in simulations 1 to 3 and initialize them with parameters $\alpha_0$ and $\beta_0$.
+See the setup in Kaufmann et al.
+(2012), especially equation (3), to see how the posterior distribution is updated in every round.
 
@@
 \For{$i = 1$ \KwTo $K$}{
-  \emph{Compute $q_i(t) = Q\Big(1-\frac{1}{t(\log T)^c}, \lambda_i^{t-1}\Big)$}\;
-  \emph{Compute $B_i(t) = $}\;
-  \If{$\hat{\sigma}^2_{i}(t) = 0$}{\emph{Set $\hat{\sigma}^2_{i}(t) = 1/T$}}
+  \emph{Compute $q_i^u(t) = Q\Big(1-\frac{1}{t(\log T)^c}, \lambda_i^{t-1}\Big)$ and $q_i^l(t) = Q\Big(\frac{1}{t(\log T)^c}, \lambda_i^{t-1}\Big)$}\;
+  \emph{Compute $B_i^{BUCB}(t) = (\tau - q_i^l(t))\cdot\mathbb{I}(\hat{\mu}_i(t) \geq \tau) + (q_i^u(t) - \tau)\cdot\mathbb{I}(\hat{\mu}_i(t) < \tau)$}\;
 }
-  \emph{Pull arm $I_t = \arg \min_{i\leq K} B_i^{SLR_{2D}}(t)$ as in \autoref{eqn:SLR2DIndex}}\;
-  \emph{Observe reward $X \sim \nu_{I_t}$}\;
+  \emph{Pull arm $I_t = \arg \max_{i\leq K} B_i^{BUCB}(t)$}\;
+  \emph{Observe reward $X \sim \nu_{I_t}$ and update $\Pi^t$}\;
 }
-\caption{2D-SLR algorithm for Normal distributions with unknown mean and unknown variance}\label{algo_slr_2d}
+\caption{Bayes-UCB algorithm from Kaufmann et al. (2012) adapted to the thresholding bandit problem.}\label{bayesucb_tbp}
 \end{algorithm}\DecMargin{1em}
@@
 
-In order to assess the excellent performance of the Bayes-UCB algorithm, which comes at a surprise given that is is designed for the cumulative regret setting and thus should tend to explore the arms to less, we also plot the budget allocation of three different Bayes-UCB versions.
-The three versions differ in the quantile parameter $c$ (compare \autoref{sec:AppendixBUCB}) for which we set here $c \in \{1/5, 1, 5\}$ to explore more or less.
+In order to assess the excellent performance of the Bayes-UCB algorithm, which comes at a surprise given that is is designed for the cumulative regret setting and thus should tend to explore the arms to less, we run the Bayes-UCB algorithm for simulation 2 with three different choices of the parameter.
+In Figure 13, we see the performance results of the three versions, whereas Figure 14 shows how the algorithm allocates its budget across the arms over time.
+The three versions differ in the quantile parameter $c$ (compare \autoref{sec:AppendixBUCB}) for which we choose $c \in \{1/5, 1, 5\}$ to explore more or less.
 In Kaufmann et al.
 (2012), the cumulative regret upper bound for the Bayes-UCB is shown for $c\geq 5$, though they report that the choice of $c=0$ worked much better in their experiments.
-In our problem, it makes also sense that the versions with smaller quantiles (smaller $c$) tend to perform better than
+In our problem, it makes also sense that the versions with smaller quantiles (smaller $c$) tend to perform better, as these correspond to more exploration of the arms.
+In this particular simulation, the choices of $c=1/5$ and $c=1$ perform very similar.
+We see that the worse performance of $c=5$ can be attributed to a initial phase of sampling primarily the arms with mean below the threshold.
+This comes from the fact that the Bernoulli and Beta distributions are bounded between $0$ and $1$, with $\tau$ very close to $0$.
+Thus, the index $B_i^{BUCB}(t)$ cannot be larger than $\tau$ for arms with $\hat{\mu}_i(t) \geq \tau$.
+For arms with $\hat{\mu}_i(t) < \tau$, however, the index can be as large as $B_i^{BUCB}(t) = 0.95$.
+This leads to the effect seen in Figure 14: Due to $c=5$, the indexes are based on very large quantiles even in the beginning, which leads to large indexes for the arms with small means.
+This however is not the ideal sampling behavior.
+The other two variants adapt much better due to their smaller quantiles (and more exploration).
 
@@
   geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
-  labs(title = "Results of Synthetic Experiment 2", 
-       subtitle = expression(paste("Difficult scenario for APT; ", 
-                                   tau,' = 0.05 and 10 arms. Dashed line at Error = 0.1.')), 
+  labs(#title = "Results of Synthetic Experiment 2", 
+       subtitle = "Dashed line at Error = 0.1.", 
        y = "log(Error)", x = "Round Index") +
   scale_color_discrete(name = "Algorithm") +
-  theme_bw() + 
-  theme(legend.position = "bottom")
+  theme_bw() 
 ```
 
-```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Budget allocation for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter c."}
+```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Budget allocation across arms for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter."}
 rbind(loc6nt_BUCB_c15_ma, loc6nt_BUCB_ma, loc6nt_BUCB_c5_ma) %>%
@@
   facet_grid(.~algorithm) +
-  labs(x = "Index", y = "10 Rounds Moving Average",
-       title = "Average Number of Pulls Allocated to Each Arm per Round",
-       subtitle = "5000 iterations; a value of 1000 means that in 20% of 
-       the iterations the arm was pulled in that round.") +
+  labs(x = "Index", y = "10 Rounds Moving Average"#,
+       #title = "Average Number of Pulls Allocated to Each Arm per Round",
+       #subtitle = "5000 iterations; a value of 1000 means that in 20% of 
+       #the iterations the arm was pulled in that round."
+       ) +
   theme_bw() +
@@
 
-## Empirical Comparison of APT, SLR, and Bayes-UCB in Experiment 2
-
-```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Budget allocation for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter c."}
+## Empirical Comparison of APT, SLR, and Bayes-UCB in Simulation 2
+
+We can compare the different algorithms used in Simulation 2 based on the overall number of pulls of each arm.
+In the best case, an algorithm would sample an arm for the optimal share of the budget, in every simulation.
+This is of course not the case, since the number of pulls of a given arm at the end of the budget, $T_i(T)$, is a random variable for adaptive sampling strategies.
+Given the 5000 iterations conducted in simulation 2, we can plot the empirical distribution of this random variable for different arms.
+
+In Figure 15, we show the distribution of $T_6(T)$ for algorithms APT, Bayes-UCB, and SLR.
+We see that the distribution of the Bayes-UCB algorithm is much better concentrated around the optimal share of the budget, and has a bell curve shape.
+In contrast, the distributions of APT and SLR are much less concentrated but flat and wide, and spread across a very large interval.
+Both algorithms have several iterations in which they draw arm 6, the most difficult arm only a single time (during initialization).
+This happens for APT more than 5% of the iterations, and leads to the spike on the very left of the graph.
+In order to cope at least a little bit with this problem, we have also run the SLR algorithm with the D-Tracking rule as introduced in Garivier and Kaufmann (2016).
+The effect is nearly not noticeable in Figure 15, but the minimum number of observations is not clearly bounded away from 0.
+The effect on the performance was described before and is very noticeable in comparison to SLR without D-Tracking.
+However, even with D-Tracking the performance of Bayes-UCB is not reached.
+We describe SLR with D-Tracking in Algorithm 5.
+
+```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Empirical distribution of pulls of arm 6 in simulation 2 by different algorithms."}
 current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
@@
   geom_vline(aes(xintercept = 7000/10), linetype = 2) +
-  labs(x = "Pulls", y = "Count", 
-       title = "Distribution of Pulls of Arm 6 Across Simulations",
-       subtitle = "Binwidth = 100. Budget = 7000. 5000 Simulations.
-Vertical line indicates pulls by uniform sampling given 10 arms in experiment.") +
+  labs(x = "Pulls", y = "Count"#, 
+       #title = "Distribution of Pulls of Arm 6 Across Simulations",
+       #subtitle = "Binwidth = 100. Budget = 7000. 5000 Simulations.
+#Vertical line indicates pulls by uniform sampling given 10 arms in experiment."
+) +
   theme_bw()
@@
 
-```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Budget allocation for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter c."}
+```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Empirical distribution of pulls of arms 1 and 10 in simulation 2 by different algorithms."}
 
@@
   geom_vline(aes(xintercept = 7000/10), linetype = 2) +
-  labs(x = "Pulls", y = "Count", 
-       title = "Distribution of Pulls of Arms 1 and 10 Across Simulations",
-       subtitle = "Binwidth = 50. Budget = 7000. 5000 Simulations.
-Vertical line indicates pulls by uniform sampling given 10 arms in experiment.") +
+  labs(x = "Pulls", y = "Count"#, 
+       #title = "Distribution of Pulls of Arms 1 and 10 Across Simulations",
+       #subtitle = "Binwidth = 50. Budget = 7000. 5000 Simulations.
+#Vertical line indicates pulls by uniform sampling given 10 arms in experiment."
+) +
   theme_bw()
@@
 \DecMargin{1em}
+
+## Means in Simulations 4 and 5
+
+We give here the means of the distributions used in simulations 4 and 5 for completeness.
+
+```{r, echo = FALSE, fig.align = "center", out.width = '80%'}
+library(ggplot2)
+
+set.seed(93468734)
+tau_exp2 <- 1
+epsilon_exp2 <- 0
+mu_exp2 <- rexp(20, 1)
+
+knitr::kable(t(sort(mu_exp2)[1:10]), digits = 4, col.names = paste0("V", 1:10), caption = "Mean of Exponential arms 1 to 10 in simulation 4.")
+
+knitr::kable(t(sort(mu_exp2)[11:20]), digits = 4, col.names = paste0("V", 11:20), caption = "Mean of Exponential arms 11 to 20 in simulation 4.")
+
+set.seed(3795969)
+tau_pois2 <- 0.4
+epsilon_pois2 <- 0
+mu_pois2 <- rexp(20, 1/0.7)
+
+knitr::kable(t(sort(mu_pois2)[1:10]), digits = 4, col.names = paste0("V", 1:10), caption = "Mean of Poisson arms 1 to 10 in simulation 5.")
+
+knitr::kable(t(sort(mu_pois2)[11:20]), digits = 4, col.names = paste0("V", 11:20), caption = "Mean of Poisson arms 11 to 20 in simulation 10.")
+```

### 2017-09-08 Thesis/Draft.tex
Add descriptions to Appendix

@@
 
-The thesis at hand joins the ranks of a large literature concerned with
-the general problem of sequential sampling. One is familiar with the
-idea of ``batch sampling'', where the entire sample is gathered first
-and analyzed only after the last sample has become available. However,
-as noted in Chernoff (1958), many situations arise in which one would
-like to gather feedback from samples as they are drawn so as to
-influence the choice of the next sample. The two fundamental
-characteristics of the latter sampling process are that it is sequential
-and adaptive. Since observations are drawn in sequence, one has a chance
-to observe the observations drawn so far in order to adapt the decision
-of what sample one would like to observe next.
+The thesis at hand joins a large literature concerned with the problem
+of sequential sampling. One is familiar with the idea of ``batch
+sampling'', where the entire sample is gathered first and analyzed only
+after the last sample has become available. However, as noted in
+Chernoff (1958), many situations arise in which one would like to gather
+feedback from samples as they are drawn, so as to influence the choice
+of the next sample. The two fundamental characteristics of the latter
+sampling process are that it is sequential and adaptive. Since
+observations are drawn in sequence, one has a chance to analyze past
+observations in order to adapt the decision of what sample one would
+like to observe next.
 
 This makes sequential sampling especially relevant in situations where
-there is a inherent cost to drawing an observation. The classical
-example that of clinical trials in which a researcher tests two drugs on
+there is an inherent cost to obtaining samples. The classical example is
+that of clinical trials in which a researcher tests two drugs on
 patients to observe which one performs better. Not only is it difficult
-to gather patients, but also one would like to adapt the sampling such
-that as soon as possible more patients receive the better drug so that
-more patients are cured. As noted in Cappé et al. (2013), this example
-dates back to Thompson (1933, 1935). Such problems are known as
-multi-armed bandit problems in which the sampling is adapted so as to
-minimize the cumulative regret: In the case of the drug tests, one would
-like to sample the two drugs in a way to find the best drug as soon as
-possible and then to test this drug more and more often and more often
-than the worse drug. This would lead to cumulatively more healthy
-patients then when both drugs are tested uniformly and thus minimize the
-regret from treating a patient with an ineffective drug.
-
-Instead of drugs, can consider two or more unknown distributions (which
-we call arms in the multi-armed bandit problem). These distributions
-have different means, and one can draw samples sequentially from the
-distributions in order to estimate their means. One would like to play
-the distribution with the highest mean to minimize the cumulative regret
-measure. How can we organize the sampling in order to achieve this goal?
-
-While Gittins (1979) presents an Bayesian-optimal solution, the
-Upper-Confidence Bound algorithms pioneered by Agrawal (1995) and Auer,
-Cesa-Bianchi and Fischer (2002) lead to a blooming literature on
-multi-armed bandit problems that has been picked up to solve modern
-problems in website and advertising optimization, where advertisers try
-to allocate their advertising optimally so as to reduce regret from
-showing poorly converting advertisements. Several algorithms as the
-KL-UCB algorithm based on Kullback-Leibler divergence upper confidence
-intervals (Cappé et al., 2013) or the Bayes-UCB algorithm (Kaufmann et
-al., 2012) have followed and been shown to be optimal as they reach the
-lower bound introduced in Lai and Robbins (1985) and Burnetas and
-Katehakis (1996).
-
-These algorithms have in common that they compute after any sample an
-index for each of the unknown distributions. This index is based solely
-on the past (observed) data, and then used to pick the distribution from
-which the next observation should be drawn. Using these indexes, the
-algorithms can sequentially sample and adapt the future strategies to
-observations as they are gathered.
-
-Other algorithms based on indices can be used on related problems.
-Instead of minimizing cumulative regret, it might be more interesting to
-find the best arm, that is, the distribution with the largest mean, with
-as few samples as possible and with confidence as large as possible.
-This is particularly useful when there is not necessarily a cost from
-initially picking a lower mean, but when drawing any sample is costly,
-and one needs to explore the distributions as efficiently as possible.
-The need for strategies other than uniform sampling arises: Do not
-continue to sample distributions that we are confident about. As such,
-the best arm identification problem is very similar to the problem faced
-in Bayesian Optimization: Training large neural networks is costly in
-terms of time and computation, and so the parameter space needs to be
-explored with as few samples as possible. (Zhang et al., 2017; Brochu et
-al., 2010).
-
-The problem of best arm identification is very related to statistical
-hypothesis testing as noted by Chernoff (1958) since in the end, one has
+to gather enough patients, but one would also like to adapt the sampling
+such that as soon as possible more patients receive the better drug and
+are cured. As noted in Cappé et al. (2013), this example dates back to
+Thompson (1933, 1935). Such problems are known as multi-armed bandit
+problems in which the sampling is adapted so as to minimize the
+cumulative regret: In the case of the drug tests, one would like to
+sample the two drugs in a way to find the best drug as soon as possible
+and then to test this drug more and more often and more often than the
+worse drug. This would lead to cumulatively more healthy patients than
+testing both drugs uniformly; it would minimize the regret from treating
+patients with an ineffective drug.
+
+Instead of drugs, one can consider two or more unknown distributions
+(which we call arms in the multi-armed bandit problem in analogy with
+the one-armed bandit slot machine). These distributions have different
+means, and one can draw samples sequentially from the distributions in
+order to estimate their means. To minimize the cumulative regret
+measure, one would like to play the distribution with the highest mean
+as much as possible (\emph{Exploitation}). At the same time, however,
+one has to sample all arms at least a little, so as to initially find
+the best arm (\emph{Exploration}). Any algorithm thus has to handle a
+trade-off between exploration and exploitation to minimize the regret.
+How can we organize the sampling in order to achieve this task?
+
+While Gittins (1979) presents an Bayesian-optimal solution to the
+cumulative regret problem, the Upper-Confidence Bound (UCB) algorithms
+pioneered by Agrawal (1995) and Auer, Cesa-Bianchi and Fischer (2002)
+have lead to a blooming literature on multi-armed bandit problems that
+has been picked up to solve modern problems in website and advertising
+optimization, where advertisers try to allocate their advertising
+optimally so as to reduce regret from showing poorly converting
+advertisements. Several algorithms like the KL-UCB algorithm based on
+Kullback-Leibler divergence upper confidence intervals (Cappé et al.,
+2013) or the Bayes-UCB algorithm (Kaufmann et al., 2012) have followed
+and been shown to be optimal as they reach the lower bound introduced in
+Lai and Robbins (1985) and Burnetas and Katehakis (1996).
+
+These algorithms have in common that they compute after every new sample
+an index for each of the unknown distributions. This index is based
+solely on the past (observed) data, and then used to pick the
+distribution from which the next sample should be drawn. Using these
+indexes, algorithms can sample sequentially and adapt their strategies
+to observations as they are collected.
+
+Similar algorithms based on indexes can be used on related problems.
+Instead of minimizing cumulative regret, it can be of interest to find
+the best arm, that is, the distribution with the largest mean -- with as
+few samples as possible and with confidence as large as possible. This
+is particularly useful when there is not a cost from testing arms with
+lower mean, but when drawing any sample is costly. Thus one needs to
+explore the distributions as efficiently as possible. Exploitation is
+not necessary, and the setting is thus referred to as \emph{Pure
+Exploration}. The need for strategies other than uniform sampling
+arises: One does not want to continue to sample distributions that one
+is confident in. This setting is related to the problem faced in
+Bayesian Optimization: Training large neural networks is costly in terms
+of time and computation, and so the parameter space needs to be explored
+with as few samples as possible. (Zhang et al., 2017; Brochu et al.,
+2010). The problem of best arm identification is also very related to
+statistical hypothesis testing as noted by Chernoff (1958) since one has
 to make a decision about how the means of distributions relate to each
-other. The main difference of course being that the sampling procedure
-becomes integrated into the evaluation of the distributions. Given the
-focus on exploration, the problem is usually described with a loss
-function different from cumulative regret. Audibert et al. (2010)
-introduce a soft measure called \emph{simple regret} based on which they
-describe UCB policies. Other authors investigate hard, binary measures
-that are equal to 1 when the best arm has not been identified (Russo,
-2016; Garivier and Kaufmann, 2016). These binary measures correspond to
-the probability of the identified arm being the best, and thus
-inherently related to hypothesis testing. The problem of best arm
-identification can readily be extended to the so called Top-\(m\)
-problem of identifying the best \(m\) of \(K\) arms (Kaufmann and
-Kalyanakrishnan, 2013; Kaufmann et al. 2016).
+other. The main difference being that the bandit setting includes the
+testing procedure in the sampling process.
+
+Given the focus on exploration, the pure exploration problem is usually
+described with a loss function different from the one in the cumulative
+regret settings. Audibert et al. (2010) introduce a soft measure called
+\emph{simple regret} based on which they describe UCB policies. Other
+authors investigate binary measures that are equal to 1 when the best
+arm has not been identified (Russo, 2016; Garivier and Kaufmann, 2016).
+These binary measures correspond to the probability of the identified
+arm being the best, and thus inherently related to hypothesis testing.
+The problem of best arm identification can readily be extended to the so
+called Top-\(m\) problem of identifying the best \(m\) of \(K\) arms
+(Kaufmann and Kalyanakrishnan, 2013; Kaufmann et al. 2016).
 
 In this thesis, we consider the thresholding bandit problem. Instead of
-identifying the best \(m\) out of \(K\) arms, one aims to find all out
-of \(K\) distributions that have a mean larger than a threshold fixed
-upfront. In the form described in Locatelli et al. (2016), algorithms in
-the thresholding bandit problem are evaluated against a binary loss
-function penalizing whenever an arm has not been classified correctly as
-being above the threshold and thus focus on exploration similar to
-algorithms employed for best arm identification. Indeed, Locatelli et
-al. (2016) show how their thresholding algorithm can be used for best
-arm identification when the mean of the best arm is known upfront.
+identifying the best \(m\) out of \(K\) arms, we aim to find all
+distributions out of \(K\) that have a mean at least as large as a
+threshold fixed upfront. In the form described in Locatelli et al.
+(2016), algorithms in the thresholding bandit problem are evaluated
+against a binary loss function penalizing whenever an arm has not been
+classified correctly as being above or below the threshold, and thus
+focus on exploration similar to algorithms employed for best arm
+identification. Indeed, Locatelli et al. (2016) show how their
+thresholding algorithm can be used for best arm identification when the
+mean of the best arm is known upfront.
 
 In the following, we first present the thresholding bandit problem in
-detail. To then extend upon the algorithm proposed by Locatelli et al.
-(2016), we first explore how the Kullback-Leibler divergence has been
-employed in the best arm identification literature by Garivier and
-Kaufmann (2016) and Kaufmann et al. (2016). We shortly describe two
-variance based algorithms for the thresholding bandit problem introduced
-in Mukherjee et al. (2017) and Zhang et al. (2017), before introducing
-the new Simple Likelihood Ratio algorithm. We end with experiments to
-examine the performance of different algorithms.
+detail in \autoref{chap:ThresholdingBanditProblem}. To then extend upon
+the algorithm proposed by Locatelli et al. (2016) and discussed in
+\autoref{sec:TheAPTAlgorithm}, we first explore in
+\autoref{chap:KullbackLeiblerPureExploration} how the Kullback-Leibler
+divergence has been employed in the best arm identification literature
+by Garivier and Kaufmann (2016) and Kaufmann et al. (2016) as this will
+lead us to our own extension. We shortly describe in
+\autoref{sec:VarianceBasedAlgorithms} two variance-based algorithms for
+the thresholding bandit problem introduced in Mukherjee et al. (2017)
+and Zhang et al. (2017), before introducing the new Simple Likelihood
+Ratio algorithm in \autoref{sec:LRforUnivariateExponentialFamily}. We
+end in \autoref{chap:Experiments} with experiments to examine the
+performance of different algorithms.
 
@@
 To introduce the thresholding bandit problem, consider a game in which
-the learner is tasked to find those slot machines within a row of \(K\)
+the learner is tasked to find the slot machines within a row of \(K\)
 slot machines in a casino that give a mean payoff larger than a fixed
@@
 sequentially from one slot machine at a time to learn about their payoff
-structure. The learner has a budget of \(T\) slot machine pulls. After
+structure. The learner has a budget of \(T>K\) slot machine pulls. After
 \(t-1\) samples, the learner has observed \(T_i(t-1)\) samples from slot
@@
 \(i\). At time \(t\), the learner considers the payoffs he observed so
-far in order to choose the next slot machine he would like to pull. His
+far in order to choose the next slot machine he would like to pull. Her
 decision is lead by the goal to classify the slot machines with
@@
 
-The thresholding bandit problem can thus be framed in the wide
-literature on sequential sampling strategies. While its name is
-reminiscient of the multi-armed bandit setting, the thresholding bandit
-problem is more akin to best arm identification and Top-\(m\)
-identification problems due to its focus on exploration: While the
-classical multi-armed bandit problems are concerned with cumulative
-regret which increases \emph{during} sampling, best arm identification
-and thresholding bandits collect loss only once \emph{after} the
-sampling procedure (compare Garivier and Kaufmann, 2016; Kaufmann et
-al., 2016; Kaufmann and Kalyanakrishnan, 2013). Furthermore, as there
-arises an implicit threshold between the means of the \(m\)-th best arm
-and the \(m+1\)-th best arm (Kaufmann et al., 2016; Kaufmann and
-Kalyanakrishnan, 2013), algorithms for the Top-\(m\) identification
-problem classify arms at least implicitly as being above or below a
-threshold. The two settings are thus very related.
+The thresholding bandit problem can thus be framed in the literature on
+sequential sampling strategies. Even though its name is reminiscient of
+the multi-armed bandit setting, the thresholding bandit problem is more
+akin to best arm identification and top-\(m\) identification problems
+due to its focus on exploration: While the classical multi-armed bandit
+problems are concerned with cumulative regret which increases
+\emph{during} sampling, best arm identification and thresholding bandits
+collect loss only once \emph{after} the sampling procedure (compare
+Garivier and Kaufmann, 2016; Kaufmann et al., 2016; Kaufmann and
+Kalyanakrishnan, 2013). As we will see in
+\autoref{chap:KullbackLeiblerPureExploration} there arises an implicit
+threshold between the means of the \(m\)-th best arm and the \(m+1\)-th
+best arm in the top-\(m\) identification problem (Kaufmann et al., 2016;
+Kaufmann and Kalyanakrishnan, 2013). Because of this, the two settings
+are very related.
 
@@
 probability distributions \(\nu_i, i \in \mathbb{A}\). To stick with the
-idea of multi-armed bandits, we call those distributions arms, and
-observations from those arms rewards (Bubeck and Cesa-Bianchi, 2012).
-The learner is interested in learning about the structure of the arms;
-in particular, he would like to estimate the means \(\mu_1, ..., \mu_K\)
-by sequentially drawing observations \(X_{i,1}, X_{i,2}, ...\) from each
-arm. However, at time \(t\) the learner cannot observe a reward from
-every distribution but must select a single arm \(I_t\) from which he
-would like to observe the reward \(X_{I_t,t}\). An adaptive sampling
-strategy makes the decision of which arm to pull usually by computing an
-index \(B_i(t)\) for each arm. If \(T_i(t)\) is the number of samples
-observed until time \(t\) for arm \(i\), then \(B_i(t)\) is a function
-of the past rewards \(X_{i,1}, ..., X_{i,T_i(t)}\) observed for arm
-\(i\), and w.l.o.g. \(I_t = \arg \min_{i = 1,...K} B_i(t)\). The set of
-indices can be called strategy (Kaufmann et al., 2012) which makes it
+idea of multi-armed bandits, we call the distributions arms, and
+observations from the arms rewards (Bubeck and Cesa-Bianchi, 2012). The
+learner is interested in learning about the structure of the arms; in
+particular, she would like to estimate the means \(\mu_1, ..., \mu_K\)
+by sequentially drawing observations \(X_{i,1}, X_{i,2}, ...\) from the
+different arms. However, at time \(t\) the learner cannot observe a
+reward from every distribution but must select a single arm \(I_t\) from
+which she would like to observe the reward \(X_{I_t,t}\). Often,
+adaptive sampling strategies makes the decision of which arm to pull by
+computing an index \(B_i(t)\) for each arm. If \(T_i(t)\) is the number
+of samples observed until time \(t\) for arm \(i\), then is \(B_i(t)\) a
+function of the past rewards \(X_{i,1}, ..., X_{i,T_i(t)}\) observed for
+arm \(i\), and w.l.o.g. \(I_t = \arg \min_{i = 1,...K} B_i(t)\). The set
+of indexes can be called strategy (Kaufmann et al., 2012) which makes it
 clear that the strategy is adapted as more observations are collected.
@@
 
-What index proves to be useful is determined by the loss function with
-which the decisions of the algorithm are evaluated. While many problems
-are concerned with finding the arm with the largest mean \(\mu_i\), in
-which algorithms collect loss either cumulatively (Auer and
-Cesa-Bianchi, 2012) or once at the end of the sampling (Kaufmann et al.,
-2016), the thresholding bandit problem considers a slightly different
-loss function. Consider a fixed threshold value \(\tau \in \mathbb{R}\)
-and an epsilon interval \(\tau \pm \epsilon\) around the threshold for
+Which index proves to be useful is determined by the loss function with
+which the decisions of the algorithm are evaluated. Many problems are
+concerned with finding the arm with the largest mean \(\mu_i^*\) while
+collecting loss either cumulatively during (Auer and Cesa-Bianchi, 2012)
+or once at the end of the sampling (Kaufmann et al., 2016). The
+thresholding bandit problem considers a slightly different loss
+function. Consider a fixed threshold value \(\tau \in \mathbb{R}\) and
+an epsilon interval \(\tau \pm \epsilon\) around the threshold for
 \(\epsilon \geq 0\). As mentioned in the introduction, the learner is
 tasked with classifying arms as having a mean \(\mu_i\) larger or
-smaller than \(\tau\). To describe which arms are above the threshold,
-we introduce the following set notation (compare Locatelli et al.,
-2016): Let \(\mathcal{S}_{\tau}\) be the set of distributions in
-\(mathbb{A}\) with mean larger than the threshold:
-\(\mathcal{S}_{\tau} := \{i \in \mathbb{A}, \mu_i \geq \tau\}\).
-Consequently, the complement is given by the arms with mean below the
-threshold,
-\(\mathcal{S}^C_{\tau} := \{i \in \mathbb{A}, \mu_i < \tau\}\).
+smaller than \(\tau\). As in Locatelli et al. (2016), whenever we say
+that ``an arm is over the threshold'', we say that the mean of the arm
+is over the threshold. To describe which arms are over the threshold, we
+also introduce the following set notation: Let \(\mathcal{S}_{u}\) be
+the set of distributions in \(\mathbb{A}\) with mean larger than some
+\(u \in \mathbb{R}\):
+\(\mathcal{S}_{u} := \{i \in \mathbb{A}, \mu_i \geq u\}\). Consequently,
+the complement is given by the arms with mean below \(u\),
+\(\mathcal{S}^C_{u} := \{i \in \mathbb{A}, \mu_i < u\}\).
 
@@
 overall \(T\) samples (or rounds) to explore the different arms. After
-this exploration phase, the learner has to return a set of arms that he
-believes to have a mean above the threshold. The problem can thus be
-described by the threshold \(\tau\) and a precision \(\epsilon\). When
-evaluating the classification of the learner, arms with mean inside of
-the epsilon interval will not be considered. The learner only has to
-distinguish the means from the threshold correctly up to the precision
-\(\epsilon\). Thus, the algorithm is not evaluated against
+this exploration phase, the learner returns a set of arms that she
+believes to be over the threshold. When evaluating the classification of
+the learner, arms with mean inside of the epsilon interval
+\(\tau \pm \epsilon\) will not be considered. The learner only has to
+correctly distinguish the means from the threshold up to the precision
+given by \(\epsilon\). Thus, the algorithm is not evaluated against
 \(\mathcal{S}_{\tau}\) and \(\mathcal{S}^C_{\tau}\), but needs to
 distinguish \(\mathcal{S}_{\tau+\epsilon}\) from
-\(\mathcal{S}^C_{\tau-\epsilon}\). As in Locatelli et al. (2016),
-whenever we say that ``an arm is over the threshold'', we mean that the
-mean of the arm is over the threshold.
+\(\mathcal{S}^C_{\tau-\epsilon}\).
 
@@
 \[
-\mathcal{L}(T) = \mathbbm{1}{(\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \lor (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset)}
+\mathcal{L}(T) = \mathbbm{1}{\big((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \lor (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset)\big)}
 \]
@@
 threshold if they actually are below the threshold. Due to the precision
-\(\epsilon\), the loss is not influenced by arms which are too close to
-the threshold \(\tau\), that is, arms inside of the
-\(\tau \pm \epsilon\) interval. If either \(\hat{\mathcal{S}}_{\tau}\)
-contains an arm below \((\tau - \epsilon)\), or
-\(\hat{\mathcal{S}}^C_{\tau}\) contains an arm above
-\((\tau + \epsilon)\), a loss of \(1\) is accrued. Else, all arms
+\(\epsilon\), the loss is not influenced by arms which are very close to
+the threshold \(\tau\) as measured by \(\epsilon\), that is, arms inside
+of the \(\tau \pm \epsilon\) interval. If either
+\(\hat{\mathcal{S}}_{\tau}\) contains an arm below
+\((\tau - \epsilon)\), or \(\hat{\mathcal{S}}^C_{\tau}\) contains an arm
+above \((\tau + \epsilon)\), a loss of \(1\) is accrued. Else, all arms
 outside the epsilon interval are classified correctly and the loss is
 equal to \(0\). In the case of \(\epsilon = 0\), all arms need to be
-classified correctly to not endure any loss.
+classified correctly to not collect any loss.
 
@@
 
-which corresponds to the probability of making a wrong classification.
-Both the probability of not identifying an arm that is actually over the
-threshold, as well as the probability of accepting an arm as over the
-threshold when it is not are evaluated. The oracle strategy would
-evaluate all arms correctly with an error probability of \(0\)
-(Locatelli et al., 2016).
+which corresponds to the probability of making at least one wrong
+classification. Both the probability of not identifying an arm that is
+actually over the threshold, as well as the probability of accepting an
+arm as over the threshold when it is not, are evaluated. The oracle
+strategy would evaluate all arms correctly with an error probability of
+\(0\) (Locatelli et al., 2016).
 
 At this point, we have introduced the general thresholding bandit
-problem setting which we will use throughout the thesis. The setting
-might be extended by different assumptions to make certain algorithms or
+problem setting which we will use throughout the thesis. The setting can
+be extended by different assumptions to make certain algorithms or
 bounds feasible. For that reason, Locatelli et al. (2016) assume that
@@
 have just introduced, as well as an upper bound on the performance of
-their APT algorithm we will introduce in the following chapter. As in
-their paper, we define \(R\)-sub-Gaussian and assume it in the
-description of their algorithm and bounds:
+their APT algorithm which we will introduce in the following chapter. As
+in their paper, we define \(R\)-sub-Gaussian and assume it in the
+description of the their algorithm and bounds:
 
@@
 \(\mu_i\) of the distributions \(\nu_i\) considered in our problem are
-finite. \(R\)-sub-Gaussian distributions furthermore offer concentration
-inequalities for the concentration of the empirical mean to the true
+finite. \(R\)-sub-Gaussian distributions offer concentration
+inequalities for the concentration of the empirical mean around the true
 mean, which makes it possible to deduce the bounds presented by the
@@
 evidence for arms which appear to be inherently more difficult to
-classify. Likewise, APT tends to pull arms less often which it already
+classify. Likewise, APT tends to less often pull arms which it already
 pulled considerably often as measured by \(T_i(t)\). If arm \(i\) has
@@
 the absolute distance \(\hat{\Delta}_i(t)\) between the (estimated) mean
-of the arm and the threshold \(\tau\) (and the epsilon interval). Given
-that one compares \(B_i^{APT}\) with \(B_j^{APT}\), one could just as
-well measure the distance by the squared distance,
-\(\hat{\Delta}_i(t)^2\). When the APT algorithm realizes that an arm has
-a mean close to the threshold, then this arm requires more attention
-than an arm far away from the threshold; the confidence in the empirical
-mean has to be larger. Or the empirical mean has to be better
-concentrated around the true mean. Otherwise it is easier to make a
-mistake on this arm. To gain this confidence, the arm requires more
-samples, and thus a larger share of the overall \(T\) samples available.
-With this intuition, it makes sense to measure the complexity of a
-thresholding problem: If we knew upfront how complex a given set of arms
-is, we knew whether we can expect a small or large probability of error
-given our budget \(T\). Also, for example in the best arm identification
-problem, there exist algorithms which take the complexity of a problem
-as input. Based on the complexity they then adapt their sampling
-strategy. See for example the UCB-E algorithm in Audibert et al. (2010)
-for the best arm identification problem, or the KL-LUCB-E algorithm in
-Kaufmann and Kalyanakrishnan (2013) as extension to the Top-\(m\)
-problem.
+of the arm and the threshold \(\tau\) (and the epsilon interval). When
+the APT algorithm realizes that an arm has a mean close to the
+threshold, then this arm requires more attention than an arm far away
+from the threshold; the confidence in the empirical mean has to be
+larger. Or the empirical mean has to be better concentrated around the
+true mean. Otherwise it is easier to make a mistake on this arm. To gain
+this confidence, the arm requires more samples, and thus a larger share
+of the overall \(T\) samples available. With this intuition, it makes
+sense to measure the complexity of a thresholding problem: If we knew
+upfront how complex a given set of arms is, we would know whether to
+expect a small or large probability of error given our budget \(T\).
+Also, for example in the best arm identification problem, there exist
+algorithms which take the complexity of a problem as input. Based on the
+complexity they then adapt their sampling strategy. See for example the
+UCB-E algorithm in Audibert et al. (2010) for the best arm
+identification problem, or the KL-LUCB-E algorithm in Kaufmann and
+Kalyanakrishnan (2013) as extension to the top-\(m\) problem.
 
 While the APT algorithm does not require the complexity to be known
-upfront (which would be problematic), it is necessary to define the
-complexity to deduce the upper bound on its probability of error.
-Similar to the distance measure used in the algorithm's index, we define
-the gap \(\Delta_i^{\tau,\epsilon}\) between arm \(i\) and the threshold
-\(\tau \pm \epsilon\) as
+upfront (which would be problematic as it is not known upfront), it is
+necessary to define the complexity to deduce the upper bound on its
+probability of error. Similar to the distance measure used in the
+algorithm's index, we define the gap \(\Delta_i^{\tau,\epsilon}\)
+between arm \(i\) and the threshold \(\tau \pm \epsilon\) as
 
@@
 \(K\) and decreases in the gap \(\Delta_i^{\tau,\epsilon}\).
-Consequently, when we require a smaller precision, that is, we increase
+Consequently, when we require less precision, that is, we increase
 \(\epsilon\), the hardness decreases. Furthermore, we see that each arm
@@
 \(T \cdot h_i /H\) to arm \(i\). However, since we do not know neither
-\(\mu_i\) nor \(H\), the best we can do is to adapt our allocation of
-samples more and more towards this optimum as we observe samples.
+\(\mu_i\) nor \(H\) upfront, the best we can do is to adapt our
+allocation of samples more and more towards this optimum as we observe
+samples.
 
@@
 
-In this chapter we present the upper bound on the APT algorithm proven
-in Locatelli et al. (2016). The upper bound is on the probability of
-error that the algorithm has after \(T\) rounds of sampling for a
-problem with arms that are assumed to be \(R\)-sub-Gaussian. The bound
-depends also on the complexity of the problem, and we show in the proof
-that given the index of the APT algorithm as defined in
-\autoref{sec:TheAPTAlgorithm}, the complexity \(H\) is an appropriate
-measure.
+In this chapter we present the upper bound on the probability of error
+that the APT algorithm incurs, as proven in Locatelli et al. (2016). The
+upper bound is on the probability of error that the algorithm has after
+\(T\) rounds of sampling for a problem with arms that are assumed to be
+\(R\)-sub-Gaussian. The bound depends also on the complexity of the
+problem, and we show in the proof that given the index of the APT
+algorithm as defined in \autoref{sec:TheAPTAlgorithm}, the complexity
+\(H\) is an appropriate measure.
 
@@
 and similar for \(\hat{\Delta}_i\). We can now lower bound the LHS of
-the indices as
+the indexes as
 
@@
 find the \(m\) out of \(K\) arms with the largest expected reward. This
-set of arm indices is denoted by \(\mathcal{S}_m^*\). Kaufmann et al.
+set of arm indexes is denoted by \(\mathcal{S}_m^*\). Kaufmann et al.
 write the means \((\mu_{1}, ..., \mu_{K})\) sorted in decreasing order
@@
 \begin{equation}
-\kappa_C(\nu) = \inf_{A \, \text{PAC}} \limsup_{\delta \to 0} \frac{\mathbb{E}_{\nu}[T{\delta}]}{\log \frac{1}{\delta}}. \label{eq:KappaC}
+\kappa_C(\nu) = \inf_{A \, \text{PAC}} \limsup_{\delta \to 0} \frac{\mathbb{E}_{\nu}[T_{\delta}]}{\log \frac{1}{\delta}}. \label{eq:KappaC}
 \end{equation}
@@
 \begin{equation}
-\kappa_B(\nu) = \inf_{A \, \text{consistent}} \big(\limsup_{t \to \infty} - \frac{1}{t} \log p_t(\nu)\big)^{-1}.
+\kappa_B(\nu) = \inf_{A \, \text{consistent}} \Big(\limsup_{t \to \infty} - \frac{1}{t} \log p_t(\nu)\Big)^{-1}.
 \end{equation}
@@
 \[
-\kappa_{TBP}(\nu) = \inf_{A consistent} \Big(\limsup_{t \rightarrow \infty} - \frac{1}{t} \log p_t(\nu)\Big)^{-1} \geq K \Big(\sum_{i=1}^{K} \KL(\tau||\mu_i)\Big)^{-1}
+\kappa_{TBP}(\nu) = \inf_{A \text{ consistent}} \Big(\limsup_{t \rightarrow \infty} - \frac{1}{t} \log p_t(\nu)\Big)^{-1} \geq K \Big(\sum_{i=1}^{K} \KL(\tau||\mu_i)\Big)^{-1}
 \]
@@
 failing previous tests) and decreases in risk \(\delta\) at a
-diminishing rate, the optimal threshold derived in Theorem 10 of
-Garivier and Kaufmann (2016) is intuitive:
+diminishing rate, the optimal exploration rate for Bernoulli arms
+derived in Theorem 10 of Garivier and Kaufmann (2016) is intuitive:
 
@@
 \] In order to decide at time \(t\) which arm to draw next, we
-necessarily compare the indices of arm \(i\) and arm \(j\). Assume
+necessarily compare the indexes of arm \(i\) and arm \(j\). Assume
 w.l.o.g. that \(B_i^{SLR}(t) < B_j^{SLR}(t)\). Then:
@@
 algorithm introduced in Kaufmann et al. (2012) for the cumulative regret
-setting. See \autoref{sec:AppendixBUCB} in the appendix for how their
-Algorithm 1 is adapted to the thresholding bandit problem.
+setting. See \autoref{sec:AppendixBUCB} in the appendix for how we adapt
+the Bayes-UCB algorithm to the thresholding bandit problem.
 
@@
 
-Every experiment presented is repeated for 5000 iterations. Depending on
-the experiment, the observations are generated randomly by a given
-exponential family of distributions. As we are primarily concerned with
-improving upon APT with respect to non-sub-Gaussian distributions, the
-first three experiments focus on Bernoulli distributions, especially
-those with small means. We then go on to show with experiments on data
-from the Exponential distribution and Poisson distribution that the SLR
-algorithm is able to improve upon APT given that we know the true kind
-of distribution.
-
-\subsubsection{\texorpdfstring{Simulation 1: Bernoulli with
-\(\tau = 0.5\)}{Simulation 1: Bernoulli with \textbackslash{}tau = 0.5}}\label{simulation-1-bernoulli-with-tau-0.5}
-
-The first experiment is equal to experiment 3 in Locatelli et al.
-(2016). We compare ten Bernoulli arms that move away from the threshold
-at \(\tau = 0.5\) geometrically with \(\mu_{1:4} = 0.4-0.2^{1:4}\),
-\(\mu_5 = 0.45\), \(\mu_6 = 0.55\), and
+Each of the following five simulations is repeated for 5000 iterations.
+Depending on the simulation, the observations are generated randomly by
+a given exponential family of distributions. As we are primarily
+concerned with improving upon APT with respect to non-sub-Gaussian
+distributions, the first three simulations focus on Bernoulli
+distributions, especially those with small means. We then go on to show
+with experiments on data from the Exponential distribution and Poisson
+distribution that the SLR strategy can be adapted to other distributions
+as well.
+
+\subsubsection{\texorpdfstring{Simulation 1: Bernoulli Arms and
+\(\tau = 0.5\)}{Simulation 1: Bernoulli Arms and \textbackslash{}tau = 0.5}}\label{simulation-1-bernoulli-arms-and-tau-0.5}
+
+The first experiment is equal to experiment 3 in Locatelli et al. (2016)
+to achieve a baseline comparison. We compare ten Bernoulli arms that
+move away from the threshold at \(\tau = 0.5\) geometrically with
+\(\mu_{1:4} = 0.4-0.2^{1:4}\), \(\mu_5 = 0.45\), \(\mu_6 = 0.55\), and
 \(\mu_{7:10} = 0.6 + 0.2^{5-1:4}\). We run the standard APT algorithm as
@@
 by its authors in Mukherjee et al. (2017). We run the parameter-free
-EVT\(_pf\) algorithm without feedback delay, thus making it directly
-comparable to the other algorithms. The Bayes-UCB algorithm takes as
-prior a Beta distribution with parameters \(\alpha_0 = \tau\) and
-\(\beta_0 = 1 - \tau\), thus leading to a mean of the prior distribution
-at \(\frac{\alpha_0}{\alpha_0+\beta_0}=\tau\) while keeping the prior as
-weak as possible. Lastly, we run the uniform sampling strategy as a
-benchmark.
+EVT\(_{pf}\) algorithm without feedback delay, thus making it directly
+comparable to the other algorithms. The Bayes-UCB algorithm is run with
+\(c=1\) and takes as prior a Beta distribution with parameters
+\(\alpha_0 = \tau\) and \(\beta_0 = 1 - \tau\), thus leading to a mean
+of the prior distribution at \(\frac{\alpha_0}{\alpha_0+\beta_0}=\tau\)
+while keeping the prior as weak as possible. Lastly, we run the uniform
+sampling strategy as a benchmark.
 
@@
 This first experiment is a problem in which all algorithms should be
-able to perform well. The problem is not very difficult, and due to the
-threshold at \(\tau = 0.5\), the Bernoulli distribution can be well
-approximated by a Gaussian. This thus is the perfect environment for the
-APT algorithm.
+able to perform well. The problem is not very difficult with
+\(H_1^{APT} \approx\) 232, and due to \(\tau = 0.5\), the Bernoulli
+distribution can be well approximated by a Gaussian. This is the perfect
+environment for the APT algorithm.
 
 As the next figure shows, essentially all methods converge rapidly to an
-error rate of very close to zero. That is, except for the uniform
-strategy that clearly lacks behind. We also observe that the variance
-based algorithms (AugUCB and EVT) lag behind at first. AugUCB is able to
-adjust its sampling scheme only after 1000 iterations but then rapdily
-improves to the level of APT. EVT takes about 250 samples more to start
-a quick descend to the performance of the other algorithms. All of this,
-however, happens after the algorithms are below an error rate of 0.01.
-While the SLR algorithm improves upon APT, the improvement is a slight
-one, and not very large in terms of budget difference. This underlines
-that the scenario at hand is ideal for the APT algorithm.
+error rate of very close to zero, where the error rate is the share of
+the 5000 simulations on which the classification of the algorithm is
+wrong. Only the uniform strategy that clearly lacks behind. We also
+observe that the variance based algorithms (AugUCB and EVT) lag behind
+at first. AugUCB is able to adjust its sampling scheme only after 1000
+iterations but then rapdily improves to the level of APT. EVT takes
+about 250 samples more to start a quick descend to the performance of
+the other algorithms. All of this, however, happens after the algorithms
+are below an error rate of 0.01. While the SLR algorithm improves upon
+APT, the improvement is a slight one, and not very large in terms of
+budget difference. This underlines that the scenario at hand is ideal
+for the APT algorithm.
 
@@
 
-\subsubsection{\texorpdfstring{Simulation 2: Bernoulli with
+\subsubsection{\texorpdfstring{Simulation 2: Bernoulli Arms and
 \(\tau = 0.05\)
-\label{sec:Simulation2}}{Simulation 2: Bernoulli with \textbackslash{}tau = 0.05 }}\label{simulation-2-bernoulli-with-tau-0.05}
-
-In the second experiment, we compare the same algorithms as in the first
-experiment. Again, we classify 10 arms, but this time against a
-threshold of \(\tau = 0.05\) and without an epsilon interval,
-\(\epsilon = 0\) (which generally rewards algorithms for pulling arms
-close to the threshold). We choose the means of the arms to be much
-smaller too, and arrange them symmetrically around the threshold. While
-the distributions are bounded and thus still sub-Gaussian, the Normal
-approximation should be poor in comparison to the previous case. We
-expect an improvement for the SLR algorithm compared to APT as it takes
-the Bernoulli characteristics into account. In particular, even though
-the arms are symmetrically distributed around the threshold in terms of
-absolute distance, they are not symmetrically around the threshold in
-terms of their Kullback-Leibler divergence (compare Figure 2). Thus we
-expect the SLR algorithm to not pull them symmetrically. Furthermore, we
-expect an improvement for the variance-based algorithms, as the
-variances are now smaller than in experiment 1, which should at least
-benefit the EVT algorithm given its theoretical analysis in Zhong et al.
-(2017).
+\label{sec:Simulation2}}{Simulation 2: Bernoulli Arms and \textbackslash{}tau = 0.05 }}\label{simulation-2-bernoulli-arms-and-tau-0.05}
 
@@
 
-The figure below shows the performance of all algorithms. We see that
-the problem appears to be significantly more difficult in general. The
-performance of the variance based algorithms is surprisingly poor; EVT
-performs even worse than uniform sampling nearly until the horizon,
-while Augmented UCB takes a long time to adjust away from uniform
-sampling. Both algorithms perform worse than APT after 7000 samples. One
-potential reason for this might be the fact that the index used by the
-EVT algorithm reduces to
-\(B_i^{EVT}(t) = \sqrt{T_i(t)} \cdot \sqrt{|\hat{\mu}_i(t) - \tau|}\) if
-\(\hat{\sigma}_i^2(t) = 0\), which, given Bernoulli arms with small
-means, could be the case for long runs of the algorithm. This seems
-suboptimal given the index of the APT algorithm is
-\(B_i^{APT}(t) = \sqrt{T_i(t)} \cdot |\hat{\mu}_i(t) - \tau|\).
-
-One interesting observation, that we will observe in all experiments
-with synthetic Bernoulli arms, is the superior performance of the
-Bayes-UCB algorithm adapted from Kaufmann et al. (2012) which was
-originally designed for cumulative regret problems. Nonetheless, the
-algorithm will again and again proof to be the best performing. Compare
-with \autoref{sec:AppendixBUCB} for more analysis on the behavior of the
-Bayes-UCB algorithm on simulation 2. In particular, consider Figures 17
-and 18 which show for individual arms, the distribution of pulls for
-that arm across simulations. These distributions highlight that both the
-APT and SLR fail in many iterations of the simulations to pull arms
-frequently enough to estimate their correct mean. The APT algorithm
-pulls the most difficult arm (Arm 6) in more than 5\% of the simulations
-only once (during initialization). Consider arm 6 returns
-\(X_{6,1} = 1\) as its first observation. Then
-\(B_6(t+1) = 1 \cdot |1-0.05| = 0.95\). It will then not be pulled for a
-long time because the index is very large. Indeed, consider some arm
-that has been pulled 4000 times with \(\mu_i(4000) = 0.03\). Then
-\(B_i(t+1) = \sqrt{2000} \cdot |0.05-0.03| \approx 0.89\). Then even
-though we have basically no evidence for the performance of arm \(6\),
-we would continue to pull arm \(i\). Similar holds for the SLR
-algorithm. For both, the distribution of pulls for arm 6 is very flat
-across the interval of \([1,6000]\) pulls. In contrast, the distribution
-of pulls looks normally distributed for the Bayes-UCB algorithm with the
-mode between 2100 and 2300 pulls. The numerical problem that can arise
-for the APT and SLR algorithms might be weakened by the combination of a
-(weak) prior that shrinks the mean estimates, and the way in which
-quantiles are based on the posterior. Similar distributions are also
-reported for arms 1 and 10 in the appendix.
-
-We show empirically that part of this problem can be alleviated by
-including the D-Tracking rule proposed by Garivier and Kaufmann (2016)
-and discussed in \autoref{sec:OptimalBestArmIdentification} into the SLR
-algorithm.
-
-While the Bayes-UCB performance is impressive, we observe that also the
-Simple Likelihood Ratio strategy improves considerably upon the
+In the second experiment, we compare the same algorithms as in the first
+experiment. Again, we classify 10 arms, but this time against a
+threshold of \(\tau = 0.05\) and without an epsilon interval,
+\(\epsilon = 0\) (which generally rewards algorithms for pulling arms
+close to the threshold). We choose the means of the arms to be much
+smaller too, and arrange them symmetrically around the threshold. While
+the distributions are bounded and thus still sub-Gaussian, the Normal
+approximation should be poor in comparison to the previous case. We
+expect an improvement for SLR compared to APT as SLR takes the Bernoulli
+characteristics into account. In particular, even though the arms are
+symmetrically distributed around the threshold in terms of absolute
+distance, they are not symmetrically around the threshold in terms of
+their Kullback-Leibler divergence (compare Figure 2). Thus we expect the
+SLR algorithm to not pull them symmetrically. Furthermore, we expect an
+improvement for the variance-based algorithms, as the variances are now
+smaller than in the first simulation, which should benefit the EVT
+algorithm given its theoretical analysis in Zhong et al. (2017).
+
+The figure below shows the performance of all algorithms. The results
+underline that this problem is much harder in general
+(\(H_2^{APT} \approx 24703\)). The performance of the variance based
+algorithms is surprisingly poor; EVT performs even worse than uniform
+sampling until close to the horizon, while Augmented UCB takes a long
+time to adjust away from uniform sampling. Both algorithms perform worse
+than APT after 7000 samples.
+
+The Simple Likelihood Ratio strategy improves considerably upon the
 alternative strategies. SLR reaches the average empirical error of 0.1
@@
 In order to assess how the SLR strategy improves upon the APT algorithm,
-it is useful to look at how often the algorithm pulls each arm. Given
-that we run the simulation 5000 times, we can compare across simulations
-how often an algorithm pulls each arm at a given round. Across the 5000
-iterations, the algorithm should pull at any given iteration the arm
-most often that it thinks is the most difficult to classify. In the
-figure below, we plot the resulting curves where the value at an
-iteration is the 10-round moving average to remove some variation.
-
-We see that both APT and SLR correctly single out the two arms that are
-much closer to the threshold than the remaining arms, and allocate most
-of the budget to them. However, while SLR keeps the two arms constant at
-two different levels (about 1900 for arm 5 and about 2500 for arm 6),
-APT at first pulls arm 5 much more than arm 6. Then, for \emph{both}
-arms, the budget allocated to them appears to converge to about 2000.
-Given that the two arms are symmetric around the threshold, it makes
-sense that APT would allocate the same exploration effort to them. And
-given that the variation of arm 5 away from the threshold is limited
-from below by zero, it is much easier for arm 6 to have an empirical
-mean larger than its true mean, and thus to have a larger index than arm
-5. Consequently, APT would prefer to sample arm 5. This, however, is
-wrong in terms of Kullback-Leibler divergence. Measured by the
-divergence, arm 6 is closer to the threshold than arm 5, thus harder to
-classify, and consequently preferred by the SLR algorithm. Furthermore,
-the SLR algorithm appears to quickly find the correct share that it has
-to allocate to the two arms. This is in contrast to APT which continues
-to adjust the shares across the entire budget.
+it is useful to look at how the algorithms allocate their sampling
+budget across arms. Given that we run the simulation 5000 times, we can
+compare across simulations how often an algorithm pulls each arm at a
+given round. During the 5000 iterations, the algorithm should pull at
+any given iteration the arm most often that it thinks is the most
+difficult to classify. In Figure 6, we plot the resulting curves where
+the y-axis shows a 10-round moving average of the pulls to remove some
+variation.
+
+The graph shows that both APT and SLR correctly single out the two arms
+closest to the threshold, and allocate most of the budget to them.
+However, while SLR keeps the two arms constant at two different levels
+(about 1900 for arm 5 and about 2500 for arm 6), APT at first pulls arm
+5 more often than arm 6. Then, for \emph{both} arms, the budget appears
+to converge to about 2000. Given that the two arms are symmetric around
+the threshold, it makes sense that APT would allocate the same
+exploration effort to them. And given that the variation of arm 5 away
+from the threshold is limited from below by zero, it is much easier for
+arm 6 to have an empirical mean larger than its true mean, and thus to
+have a larger index than arm 5 in the beginning. Consequently, APT would
+prefer to sample arm 5. This, however, is wrong in terms of
+Kullback-Leibler divergence. Measured by the divergence, arm 6 is closer
+to the threshold than arm 5, thus harder to classify, and consequently
+preferred by the SLR algorithm. Furthermore, the SLR algorithm appears
+to quickly find the correct share that it has to allocate to the two
+arms. This is in contrast to APT which continues to adjust the shares
+across the entire budget.
 
@@
 \(d_1(0.001||0.05) \approx 0.046\) and
-\(d_{10}(0.099||0.05) \approx 0.020\); in terms of the divergence, the
+\(d_{10}(0.099||0.05) \approx 0.020\): In terms of the divergence, the
 distance between arm 1 and the threshold is twice as far as between arm
@@
 
+One interesting observation, that we will observe in all simulations
+with Bernoulli arms, is the superior performance of the Bayes-UCB
+algorithm adapted from Kaufmann et al. (2012) which was originally
+designed for cumulative regret problems. Nonetheless, the algorithm
+proves again and again to be the best performing. Compare with
+\autoref{sec:AppendixBUCB} for more analysis on the behavior of the
+Bayes-UCB algorithm in simulation 2. In particular, consider Figures 17
+and 18 which show for individual arms the distribution of pulls for that
+arm across simulations. The distributions highlight that both the APT
+and SLR fail in many iterations of the simulations to pull arms
+frequently enough to estimate their correct mean. The APT algorithm
+pulls the most difficult arm (Arm 6) in more than 5\% of the simulations
+only once (during initialization). Consider arm 6 returns
+\(X_{6,1} = 1\) as its first observation. Then
+\(B_6(t+1) = 1 \cdot |1-0.05| = 0.95\). It will then not be pulled for a
+long time because its index is very large. Indeed, consider some arm
+that has been pulled 4000 times with \(\mu_i(4000) = 0.03\). Then
+\(B_i(t+1) = \sqrt{2000} \cdot |0.05-0.03| \approx 0.89\). Even though
+we have basically no evidence for the performance of arm \(6\), we would
+continue to pull arm \(i\). Similar holds for the SLR algorithm. For
+both, the distribution of pulls for arm 6 is very flat across the
+interval of \([1,6000]\) pulls. In contrast, the distribution of pulls
+appears normally distributed for the Bayes-UCB algorithm with the mode
+between 2100 and 2300 pulls. The numerical problem that arises for the
+APT and SLR algorithms might be weakened for the Bayes-UCB algorithm by
+the combination of a (weak) prior that shrinks the mean estimates, and
+the way in which quantiles are based on the posterior. Also, the fact
+alone that it is based on confidence bounds of the empirical mean,
+instead of the empirical mean itself. We show in the appendix that the
+problem does not only occur for arm 6.
+
+Empirically, part of this problem can be alleviated by including the
+D-Tracking rule proposed by Garivier and Kaufmann (2016) and discussed
+in \autoref{sec:OptimalBestArmIdentification} into the SLR algorithm, as
+it ensures that no arm is ``left behind'' in terms of samples. Figure 5
+shows a significant improvement for the SLR-D algorithm in comparison to
+the SLR algorithm without D-Tracking. However, the algorithm still does
+not reach the performance of Bayes-UCB.
+
+Lastly, we remark on the shape of the error curve of the uniform
+strategy. Even though the uniform strategy samples arms at random from
+the set of arms with the least observations at any round, we observe a
+sawtooth pattern for simulation 2 and 3. This is an artifact of the
+comparison against the threshold of \(0.05\) and \(0.01\) respectively,
+combined with the discrete \(0\) and \(1\) observations. Take for
+example an arm with a true mean of \(\mu = 0.06\) compared against
+\(\tau = 0.05\). Let's say the arm observes the first 1 after 15
+samples, \(X_{15} = 1\), such that
+\(\hat{\mu}(15) = 1/15 \approx 0.067\). At this point, it is correctly
+classified as above the arm. Even if the next samples are zeroes, it
+will continue to be correctly classified until observation 20. At that
+point, \(\hat{\mu}(20)\) = 1/20 = 0.05. By observing one more
+observation, the arm will be classified as below the threshold, since
+then \(\hat{\mu}(21) = 1/21 < 0.05 = \tau\). The classification is
+suddenly wrong for no particular reason, and a sudden spike in the error
+curve occurs. In the graph of simulation 3 it is obvious that the spike
+occurs with a period length of about 100 samples, which corresponds to
+\(\tau = 0.01=1/100\). This explains why we do not observe such a
+pattern in the first simulation with \(\tau = 0.5\), or for the
+continuous Exponential distribution in simulation 4.
+
 \begin{figure}
@@
 
-\caption{Performance comparison of algorithms for simulation 2.}\label{fig:simulation2_results}
+\caption{Performance comparison of algorithms for simulations 2 and 3. Note the different x-axes.}\label{fig:simulation2_results}
 \end{figure}
@@
 
-\subsubsection{\texorpdfstring{Simulation 3: Bernoulli with
-\(\tau = 0.01\)}{Simulation 3: Bernoulli with \textbackslash{}tau = 0.01}}\label{simulation-3-bernoulli-with-tau-0.01}
+\subsubsection{\texorpdfstring{Simulation 3: Bernoulli Arms and
+\(\tau = 0.01\)}{Simulation 3: Bernoulli Arms and \textbackslash{}tau = 0.01}}\label{simulation-3-bernoulli-arms-and-tau-0.01}
 
 In the third experiment, we lower the threshold further to
-\(\tau = 0.1\) and arrange the arms on a \(\log_{10}\) scale around it.
-Again, there is no epsilon interval. We add one additional arm, thus now
-classifying eleven arms. We run the same arms as previously. Notice that
-the experiment horizon is now \(10000\) rounds instead of \(7000\)
-rounds as in the previous experiment. We test the same algorithms used
-in the previous two experiments.
+\(\tau = 0.01\) and arrange now \(K=11\) arms on a \(\log_{10}\) scale
+around it. Again, we set \(\epsilon = 0\). We compare the same
+algorithms as previously with the settings adapted to \(\tau\) and
+\(\epsilon\) accordingly. Notice that the experiment horizon is now
+\(T=10000\) rounds instead of \(T=7000\) rounds in the previous
+experiment.
 
 \begin{longtable}[]{@{}rrrrrrrrrrr@{}}
-\caption{Mean of arms in simulation 3 compared to a threshold of
-0.01.}\tabularnewline
+\caption{Mean of arms in simulation 3.}\tabularnewline
 \toprule
@@
 Looking at the performance after 7000 rounds, we see that the problem
-appears to be slightly more difficult compared to the previous one. We
-see that up until this point the variance-based strategies cannot
-improve upon APT. Also, SLR has not yet crossed the 10\% empirical
-error. We observe that in the following rounds EVT decreases at an
-exponential rate and thus crosses the error of APT and continues to
-improve. At the end of the budget, the improvement of SLR compared to
-the other algorithms is again large, and likely to increase. However,
-Bayes-UCB is again the best performing algorithm and is improving at a
-faster rate than SLR. As in the previous experiment, Bayes-UCB and SLR
-show significant improvements on this Bernoulli problem with very small
-means and threshold compared to APT in particular.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation3_results-1}
-
-}
-
-\caption{Performance comparison of algorithms for simulation 3.}\label{fig:simulation3_results}
-\end{figure}
+appears to be slightly more difficult compared to the previous one
+(\(H_3^{APT} \approx 210359\)). We see that up until this point the
+variance-based strategies cannot improve upon APT. Also, SLR has not yet
+crossed the 10\% empirical error. We observe that in the following
+rounds EVT decreases at an exponential rate and thus crosses the error
+of APT and continues to improve. At the end of the budget, the
+improvement of SLR compared to the other algorithms is again large, and
+likely to increase. However, Bayes-UCB is again the best performing
+algorithm and is improving at a faster rate than SLR. As in the previous
+experiment, Bayes-UCB and SLR show significant improvements on this
+Bernoulli problem with very small means and threshold compared to APT in
+particular. Furthermore, the observation that the SLR algorithm with
+D-Tracking rule performs better than without is replicated.
 
@@
 In \autoref{sec:LRforUnivariateExponentialFamily}, we show that the
-likelihood ratio has a very useful form for the univariate exponential
-family of distributions, which allows us to use the SLR algorithm not
-only on Bernoulli arms, but also on Exponential or Poisson
+likelihood ratio has a very useful form for the one-parameter
+exponential family of distributions, which allows us to use the SLR
+algorithm not only on Bernoulli arms, but also on Exponential or Poisson
 distributions, for example. In simulation 4, we consider Exponential
@@
 Gamma prior). In the case of the Exponential arms, we classify against
-\(\tau = 1\) and have sampled their mean parameters of the arms from an
+\(\tau = 1\) and have sampled the arms' mean parameters from an
 Exponential distribution with rate \(\theta = 1\). The Poisson arms are
@@
 
-For the Exponential arms, APT crosses the 0.1 error mark first, followed
-by the AugUCB algorithm. All algorithms perform better than uniform
-sampling. After more than half of the budget, the SLR algorithm jumps in
-performance and performs better than APT and AugUCB. Indeed, the AugUCB
-basically stops improving after half of the budget. This is a
+For the Exponential arms, APT crosses the 10\% error mark first,
+followed by the AugUCB algorithm. All algorithms perform better than
+uniform sampling. After more than half of the budget, the SLR algorithm
+jumps in performance and performs better than APT and AugUCB. Indeed,
+the AugUCB basically stops improving after half of the budget. This is a
 consequence of it eliminating arms it believes to know very well. This
@@
 
+In the case of Poisson arms, the performance of the arms is more clear
+cut. As expected, SLR improves upon APT. APT outperforms the EVT
+algorithm, which occurs even though the variance of all arms considered
+in this experiment is in \([0,1]\). After about 1000 observations, APT
+and EVT appear to improve at about the same rate, but APT has a much
+better initial exploration phase. Given the previous simulations, it is
+surprising to see the Augmented-UCB algorithm to come ahead after
+\(T=10000\) observations. After about half the budget, the same pattern
+as before occurs where there is a drastic change in sampling behavior.
+This suffices to outpace both APT and SLR.
+
 \begin{figure}
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation4_results-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation5_results-1}
 
@@
 
-\caption{Performance comparison of algorithms for simulation 4.}\label{fig:simulation4_results}
+\caption{Performance comparison of algorithms for simulations 4 and 5. Note the different x-axes.}\label{fig:simulation5_results}
 \end{figure}
 
-In the case of Poisson arms, the performance of the arms is more clear
-cut. As expected, SLR improves APT and the other strategies. APT
-outperforms the EVT algorithm, which occurs even though the variance of
-all arms considered in this experiment is in \([0,1]\). But similarly to
-the Bernoulli simulations, the EVT might again have a hard time dealing
-with sequences of observations that are all equal to \(0\) for a long
-time. After about 1000 observations, APT and EVT appear to improve at
-about the same rate, but APT had a much better initial exploration
-phase.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation5_results-1}
-
-}
-
-\caption{Performance comparison of algorithms for simulation 5.}\label{fig:simulation5_results}
-\end{figure}
-
-\subsection{\texorpdfstring{Real Data
-\label{sec:RealData}}{Real Data }}\label{real-data}
+\subsection{\texorpdfstring{Experiments on Web Analytics Data
+\label{sec:RealData}}{Experiments on Web Analytics Data }}\label{experiments-on-web-analytics-data}
 
 In the following, we present the results of two experiments performed on
-a real world data set. While most new multi-armed bandit algorithms are
+a real world data set. While most multi-armed bandit algorithms are
 assessed on synthetic data, as we have done in
 \autoref{sec:SyntheticData}, a real world data set is useful to observe
-how algorithms perform in presence of, for example, not fully i.i.d.
-samples. While of course every company tries to make their experiments
-as ideal as possible, there will always be problems. Thus our
-experiments serve as a first robustness check on the algorithms
+how algorithms perform in presence of, for example, not perfectly i.i.d.
+samples. Every company of course tries to run their algorithms under
+settings as ideal as possible, but there will always be problems. Thus
+our experiments serve as a first robustness check on the algorithms
 introduced before.
@@
 analytics. For 197 selected products, we observe the number of users
-visiting each product's detail page (PDP) at a given minute. The data
-set we use here has been collected during the entire month of November
-2016. It can be considered time series data collected at minutely
-frequency. Thus the data contain 43200 observations per product, and
-overall 8510400 observations.
+visiting each product's detail page (PDP) during a given minute. The
+data set we use here has been collected during the entire month of
+November 2016. It can be considered time series data collected at
+minutely frequency. Thus the data contain 43200 observations per
+product, and overall 8510400 observations.
 
@@
 the data as for simulated data. The goal is to perform 5000 runs over
-the sample to confidently assess the performance. Since we want to
-preserve the potential time dependency of the data, a simple resampling
-of the data is not an option to create the needed 5000 variations of the
+the sample to confidently assess the performance. Since we would like to
+preserve potential time dependencies in the data, a simple resampling of
+the data is not an option to create the needed 5000 variations of the
 sample. Instead we perform time series cross validation. To preserve the
@@
 
-While the data is count data (the number of visits to a PDP during a
-given minute), we binarize the data by applying a certain threshold. If
-the count is above this threshold, the new observation is \(1\), else
-\(0\). Thus we have a binary time series of length 43200 for each of the
-197 products. Given that the number of visitors that come to a given PDP
-is likely to vary by time of day and by day, and in general over time,
-we expect that the mean of the time series to not be stable over time.
-For example, less visitors will come during night than during the
-evening. This leads to a decrease in the average, and a daily
-seasonality. On the other hand, more users may visit the site during a
-weekend, thus leading to a spike on Saturdays and Sundays. Because of
-the latter time dependency, it is best practice to run online A/B tests
-for at least a week, or an integer multiple of weeks, so as to take into
-account the weekly seasonality in the time series. For this reason, the
-experiments we present below were run on \(60 \cdot 24 \cdot 7 = 10080\)
-observations for each arm, so as to have a sample for one full week.
+\begin{longtable}[]{@{}llrrrrr@{}}
+\caption{Example of the binary time series data for five
+products.}\tabularnewline
+\toprule
+& SessionDateTime & V104 & V110 & V150 & V112 & V154\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+& SessionDateTime & V104 & V110 & V150 & V112 & V154\tabularnewline
+\midrule
+\endhead
+1000 & 2016-11-01 16:39:00 & 0 & 0 & 0 & 0 & 0\tabularnewline
+1001 & 2016-11-01 16:40:00 & 0 & 0 & 0 & 0 & 1\tabularnewline
+1002 & 2016-11-01 16:41:00 & 0 & 0 & 0 & 0 & 1\tabularnewline
+1003 & 2016-11-01 16:42:00 & 0 & 0 & 0 & 0 & 0\tabularnewline
+1004 & 2016-11-01 16:43:00 & 0 & 0 & 1 & 0 & 1\tabularnewline
+1005 & 2016-11-01 16:44:00 & 0 & 0 & 0 & 0 & 0\tabularnewline
+\bottomrule
+\end{longtable}
+
+While the data set consists of count data (the number of visits to a PDP
+during a given minute), we binarize the data by applying a certain
+threshold. If the count is above this threshold, the new observation is
+\(1\), else \(0\). Thus we have a binary time series of length
+\(60\cdot 24 \cdot 30 = 43200\) for each of the 197 products. Given that
+the number of visitors that reach a given PDP is likely to vary by time
+of day and by day, and in general over time, we expect the mean of the
+time series to not be stable over time. For example, less visitors visit
+during night than during the evening. This leads to a decrease in the
+average number of visits, and creates a daily seasonality. On the other
+hand, more users may visit the site during a weekend, thus leading to a
+spike on Saturdays and Sundays. Because of the latter time dependency,
+it is best practice to run online A/B tests for at least a
+week\footnote{See for example the ``A/B Testing in the Wild''
+  presentation by Emily Robinson, \url{https://youtu.be/SF-ryGgLOgQ}},
+or an integer multiple of weeks, so as to take into account the weekly
+seasonality in the time series. For this reason, the experiments we
+present below are run on \(60 \cdot 24 \cdot 7 = 10080\) observations
+for each arm, so as to have a sample for one full week.
 
@@
 products over the month of November to get a first impression of the
-data we are dealing with. We see that most products have a small mean,
-which is very common also for actual conversion rate or click-through
-rate data that can be tested with A/B tests or multi-armed bandits. Yet
-the sample of products contains a few outliers with very large view
-rates, with a maximum rate of 78\%. If we used a threshold \(\gamma\) to
-binarize the count data, then this means that on average every fourth
-minute the count of visitors was below \(\gamma\) for this product. On
-the other hand, we conclude that using thresholding bandit strategies to
-test the products against a threshold of for example
-\(\tau = \frac{2}{60} = 0.333\) or \(\tau = \frac{5}{60} = 0.083\) is
+binary data we are dealing with. We see that most products have a small
+mean, which is very common also for actual conversion rate or
+click-through rate data that can be tested with A/B tests or multi-armed
+bandits. Yet the sample of products contains a few outliers with very
+large view rates, with a maximum rate of 78\%. If we used a threshold
+\(\gamma\) to binarize the count data, then this means that on average
+every fourth minute the count of visitors was below \(\gamma\) for this
+product. On the other hand, we conclude that using thresholding bandit
+strategies to test the products against a threshold of for example
+\(\tau = \frac{2}{60} = 0.0333\) or \(\tau = \frac{5}{60} = 0.083\) is
 likely to create more complex problems than a threshold of, say,
@@
 In the first experiment, we pick ten arms randomly from the set of 197
-arms. The experiment is run with a budget of \(T=10080\) samples during
+arms. The experiment is run with a budget of \(T=10080\) samples for
 each of the \(5000\) iterations for which we repeat the experiment.
@@
 evaluate the strategies also based on whether their classifications are
-correct in a holdout sample. As this holdout sample, we can use the
-10080 observations in our data set that follow the first 15080
-observations used in training. In the table below, we present the count
-rates of the ten products for both training and test samples.
+correct in a holdout sample (the time period after training). As this
+holdout sample, we can use the 10080 observations in our data set that
+follow the first 15080 observations used in training. In the table
+below, we present the count rates of the ten products for both training
+and test samples.
 
 \begin{longtable}[]{@{}lrrrrrrrrrr@{}}
-\caption{Count rates for ten products for both training and test
-sample.}\tabularnewline
+\caption{Training and test sample means for experiment
+1.}\tabularnewline
 \toprule
@@
 samples come from an entire week's worth of observations. In particular,
-since we test against a threshold of \(\tau = \frac{2}{60} = 0.333\) in
-this experiment, the classifications of arms do not differ across
+since we test against a threshold of \(\tau = \frac{2}{60} = 0.0333\) in
+this experiment, the true classifications of arms do not differ across
 training and test data. A correct classification after training will be
@@
 
-When comparing the rates against the threshold, we see that three
-products are below the already small threshold. Product \(V64\) seems to
-be especially difficult to classify correctly, even without time
-dependency. On the other hand, arms \(V119\) and \(V118\) should be much
-easier than the rest.
-
 In order to visualize the time dependency that we expect for our
 samples, we plot a moving average of the mean of the time series for the
-first week of data. To remove the daily seasonality, we select a moving
-average window of \(60\cdot24 = 1440\) observations. To make the time
-dependency even more obvious, we contrast the actual data against
-synthetic data generated using the sample means of the actual data.
+first week of data. To remove daily seasonality, we select a sliding
+window of \(60\cdot24 = 1440\) observations. To make the time dependency
+even more obvious, we contrast the actual data against synthetic data
+generated using the sample means of the actual data.
 
 The graph again underlines that arm \(V64\) is likely to be very
-difficult to classify given that it's moving average even crosses the
+difficult to classify given that its moving average crosses the
 threshold twice. The same is true for arm \(V139\), which is not visible
-when considering the overall mean alone. Furthermore, arms \(V159\) and
+when looking at the overall mean alone. Furthermore, arms \(V159\) and
 \(V189\) come very close to the threshold at times.
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-2-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-4-1}
 
@@
 
-\caption{Rolling average for the arms used in experiment 1.}\label{fig:unnamed-chunk-2}
+\caption{Moving average for the arms used in experiment 1.}\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 These difficulties seem to have a large impact on the performance of all
-algorithms. Given that the data are \(\{0,1\}\) observations, we can
-compare all algorithms in a setting in which one expects all assumptions
-to hold before having observed the data. The distribution is
-sub-Gaussian for the APT algorithm, bounded between \(0\) and \(1\) for
-the variance-based algorithms, and assumed to be Bernoulli for the SLR
+algorithms. Given that the data are binary observations, we can compare
+all algorithms in a setting in which one expects all assumptions to hold
+before having observed the data: The distributions are sub-Gaussian for
+the APT algorithm, bounded between \(0\) and \(1\) for the
+variance-based algorithms, and assumed to be Bernoulli for the SLR
 algorithm. Additionally, we use the Bayes-UCB algorithm as it performed
-best on the synthetic data.
-
-We set \(\epsilon = 0\), and \(\tau = 2/60\). For the AugUCB algorithm
-we use the parameters as in Mukherjee et al. (2017), that is,
-\(\rho = 1/3\). For B-UCB we set the prior to \(\alpha_0 = \tau\) and
-\(\beta_0 = 1-\tau\), and pick \(c=1\). All other algorithms are
-parameter free.
+best on the synthetic data. We set \(\epsilon = 0\), and
+\(\tau = 2/60\). For the AugUCB algorithm we use the parameters as in
+Mukherjee et al. (2017), that is, \(\rho = 1/3\). For Bayes-UCB we set
+the prior to \(\alpha_0 = \tau\) and \(\beta_0 = 1-\tau\), and pick
+\(c=1\).
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-3-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-5-1}
 
@@
 
-\caption{Performance comparison of algorithms for experiment 1.}\label{fig:unnamed-chunk-3}
+\caption{Performance comparison of algorithms for experiment 1.}\label{fig:unnamed-chunk-5}
 \end{figure}
@@
 data, we observe non-monotonicity in the error curves. Given that the
-highs and lows run very much parallel for the different models, it
-stands to reason that this effect is caused by the variation in means of
-the arms over time. Indeed, roughly comparing the error curves to the
-moving averages in the previous figure, the increase in errors after
-round \(5000\) and the decreasing error after round \(7500\) seems to
-line up with the fluctuations observed in the data. Given that we
-evaluate the models against a sample mean of all observations, it is not
-surprising that the uniform sampling strategy has a certain advantage
-when it comes to ``factoring out'' the seasonalities. In contrast, the
-adaptive sampling schemes try to adapt more or less quickly to the
-changes in the means; a feature that would be valuable in a cumulative
-regret multi-armed bandit setting. Here, however, it leads to wrong
-estimates of the overall sample mean.
+highs and lows for the different models run mostly parallel, it stands
+to reason that this effect is caused by the variation in means of the
+arms over time. Indeed, roughly comparing the error curves to the moving
+averages in the previous figure, the increase in errors after round
+\(5000\) and the decreasing error after round \(7500\) seems to line up
+with the fluctuations observed in the data. Given that we evaluate the
+models against a sample mean of all observations, it is not surprising
+that the uniform sampling strategy has a certain advantage when it comes
+to ``factoring out'' the seasonalities. In contrast, the adaptive
+sampling schemes try to adapt more or less quickly to the changes in the
+means--a feature that would be valuable in a cumulative regret
+multi-armed bandit setting. Here, however, it leads to wrong estimates
+of the overall sample mean.
 
@@
 of the Augmented-UCB algorithm, which first seems to perform well; this,
-however, is a result of it mostly pulling arms uniformly, until it
+however, is a result of it pulling arms mostly uniformly, until it
 starts to adapt its sampling and discarding arms after nearly 5000
 rounds. The result is a dramatic increase in error which leads to the
-worst performance at the budget horizon. The difference between APT,
-SLR, and EVT is small, and their performance fluctuates in sync. None of
-them is really able to converge due to the changes in the underlying
+worst performance at the budget horizon. The differences between APT,
+SLR, and EVT are small, and their performance fluctuates in sync. None
+of them is really able to converge due to the changes in the underlying
 means. Advantageous only seems to be the fact that their behavior is
@@
 \begin{longtable}[]{@{}lrrrrrrrrrr@{}}
-\caption{Count rates for ten products for both training and test
-sample.}\tabularnewline
+\caption{Training and test sample means for experiment
+2.}\tabularnewline
 \toprule
@@
 moving averages of the arms to quickly assess the time dependency of the
-means. Given that the data here are collected at the same time points as
-the data used in the previous experiment, it is not surprising to see a
-similar spike in means during the second half of the observations with
-the maximum moving average around index 7500. We also observe that these
-fluctuations are heavier for products with in general larger means (that
-is, more visitors on the website). But these fluctuations are clearly
-much larger and systematic than those observed for synthetic data with
-the same sample means.
-
-Given the moving averages and the previous experiment, the performance
-results of Experiment 2 shown in the next figure are not surprising. We
-recognize the same structure as previously. The uniform sampling
-strategy performs the best. The adaptive sampling strategies perform
-bad, do not converge, and end above the 10\% error rate mark. This time,
-AugUCB is not (yet) the worst performing strategy, but equally erratic
-after it eventually adapts its sampling. This time around, it even has
-two spikes in its adaptive phase. Again, APT, SLR, and EVT perform in
-sync and more or less equally bad, with EVT slightly better than APT and
-SLR this time around. Interestingly, Bayes-UCB performs clearly worst of
-all strategies. Its performance changes at the same time as
-Augmented-UCB starts to adapt its sampling strategy, near round 7000.
-
-This last fact is of particular interest, as Bayes-UCB is dramatically
-better than the other strategies in experiments on synthetic data. On
-the right hand side of the same figure, the performance of the
-algorithms on synthetic data from Bernoulli distributions with the same
-sample mean is depicted. On this data, Bayes-UCB performs very well,
-ending at an average error of about 0.1\% of the simulations. This
-mirrors its performance observed in the previous simulations with
-synthetic data. Also all other adaptive strategies perform clearly
-better now, and their error rates are strictly decreasing.
-Interestingly, the uniform sampling scheme is now much worse than in the
-experiment on real data; it does no longer have the advantage of
-sampling the different mean phases at a representative rate. Excluding
-Bayes-UCB, we see that the SLR algorithm performs the best, followed by
-the variance-based algorithms. APT comes in at the same error rate as
-uniform sampling. While the difference between SLR and EVT are less than
-2\% (1.2\% vs 3\%), the difference to uniform sampling (10\%) is
-relevant. The performance of 10\% error rate is achieved by SLR about
-1000 observations earlier than by EVT.
+means. Given those and the previous experiment, the performance results
+of Experiment 2 shown in Figure 13 are not surprising. We recognize the
+same structure as previously. The uniform sampling strategy performs the
+best. The adaptive sampling strategies perform bad, do not converge, and
+end above the 10\% error rate mark. This time, AugUCB is not (yet) the
+worst performing strategy, but equally erratic after it eventually
+adapts its sampling. This time around, it even has two spikes in its
+adaptive phase. Again, APT, SLR, and EVT perform in sync and more or
+less equally bad, with EVT slightly better than APT and SLR this time
+around. Interestingly, Bayes-UCB performs clearly worst of all
+strategies. Its performance changes at the same time as AugUCB starts to
+adapt its sampling strategy. This last fact is of particular interest,
+as Bayes-UCB is dramatically better than the other strategies in
+experiments on synthetic data.
+
+On the right hand side of figure 13, the performance of the algorithms
+on synthetic data from Bernoulli distributions is depicted. These
+synthetic samples were sampled from distributions with mean equal to the
+sample means of the real data. We thereby create similar samples that
+are perfectly i.i.d. On this data, Bayes-UCB performs very well, ending
+at an average error rate of about 0.1\%. This mirrors its performance
+observed in the previous simulations with synthetic data. Also all other
+adaptive strategies perform clearly better now, and their error rates
+are strictly decreasing. Interestingly, the uniform sampling scheme is
+now clearly worse than in the experiment on real data; it does no longer
+have the advantage of sampling the different mean phases at a
+representative rate. Excluding Bayes-UCB, we see that the SLR algorithm
+performs the best, followed by the variance-based algorithms. APT comes
+in at the same error rate as uniform sampling. While the difference
+between SLR and EVT is less than 2\% (1.2\% vs 3\%), the difference to
+uniform sampling (10\%) is relevant. The error rate of 10\% is achieved
+by SLR about 1000 observations earlier than by EVT.
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-4-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-6-1}
 
@@
 
-\caption{Rolling average of arms used in experiment 2.}\label{fig:unnamed-chunk-4}
+\caption{Moving average of arms used in experiment 2. Dashed line indicates the threshold.}\label{fig:unnamed-chunk-6}
 \end{figure}
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-8-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-10-1}
 
@@
 
-\caption{Performance results of algorithms in experiment 2.}\label{fig:unnamed-chunk-8}
+\caption{Performance results of algorithms in experiment 2.}\label{fig:unnamed-chunk-10}
 \end{figure}
 
-Again using a plot of the pulls at each round across the 5000
-simulations in Figure 17, we can try to understand why some strategies
-perform well on synthetic data, but poorly on the time series data.
+Using a plot of the pulls at each round across the 5000 simulations in
+Figure 14, as we did for simulation 2, we can try to understand why some
+strategies perform well on synthetic data, but poorly on the time series
+data.
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-9-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-11-1}
 
@@
 
-\caption{Budget allocation of algorithms across arms on real and synthetic data in experiment 2.}\label{fig:unnamed-chunk-9}
+\caption{Budget allocation of algorithms across arms on real and synthetic data in experiment 2.}\label{fig:unnamed-chunk-11}
 \end{figure}
@@
 that the poor performance can be mostly explained by the seasonality and
-sudden changes in the samples over time. The observations clearly are
-not i.i.d. sampled. However, the effect might be overly stark due to the
-fact that we use minutely time series data, which leads to observations
-even when in minutes when there are few or no users (during night). In
-contrast, the daily seasonality might be less represented in an actual
-online experiment observations are only drawn when there is an actual
-visitor on the site (and a proper conversion rate would fluctuate less
-than the count of visitors on a given product page).
+sudden changes in the samples over time. The observations clearly do not
+correspond to i.i.d. Bernoulli samples, but have large time
+dependencies. However, the effect might be overly stark due to the fact
+that we use minutely time series data, which leads to observations even
+in minutes when there are few or no users on the website (during night).
+In contrast, the daily seasonality might be less represented in an
+actual online experiment observations are only drawn when there is an
+actual visitor on the site (and a proper conversion rate would fluctuate
+less than the count of visitors on a given product page).
 
@@
 the experiments above, we observe that the order of the arms is mostly
-unaffected by the seasonalities and fluctuations, which would mean that
-the best arm could still be identified. In contrast, given that all arms
-are individually classified against the \emph{fixed} threshold, a weekly
+unaffected by the seasonalities and fluctuations, which implies that the
+best arm could still be identified. In contrast, given that all arms are
+individually classified against the \emph{fixed} threshold, a weekly
 seasonality can declare a correct classification on the first half of
@@
 
-We thank Alexandra Carpentier, Andrea Locatelli, and Urun Dogan for many
-hours of fruitful discussions and ideas. We thank Carlo Alberto
-Dall'Amico for bringing our attention to multi-armed bandits in the
-first place. Sonoma Internet GmbH (Amorelie) supported this work by
+We thank Alexandra Carpentier, Andrea Locatelli, Urun Dogan, and Marius
+Kloft for many hours of fruitful discussions and ideas. We thank Carlo
+Alberto Dall'Amico for bringing our attention to multi-armed bandits in
+the first place. Sonoma Internet GmbH (Amorelie) supported this work by
 giving the authors access to the discussed data set.
 
+\newpage
+
 \section{References}\label{references}
+
+\newpage
 
@@
 
-\subsection{\texorpdfstring{Lower Bound on Probability of Error in
-FB-Top-\(m\) with Gaussian Arms
-\label{sec:KaufmannLBTopMGaussian}}{Lower Bound on Probability of Error in FB-Top-m with Gaussian Arms }}\label{lower-bound-on-probability-of-error-in-fb-top-m-with-gaussian-arms}
-
-While we would like to move beyond Gaussian distributions in the work at
-hand, the idea for the proof might show a way of how the ideas can be
-transferred to the thresholding bandit problem. We first state the
-result and then discuss the proof.
-
-\begin{lemma}[Lemma 15, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma15}
-Let $\nu$ and $\nu'$ be two bandit models such that $S^*_m(\nu) \neq S^*_m(\nu')$. Then
-
-\begin{equation*}
-\max \big( \mathbb{P}_{\nu}(S \neq S^*_m(\nu)), \mathbb{P}_{\nu'}(S \neq S^*_m(\nu')) \big) \geq \frac{1}{4} \exp \Big(-\sum_{a=1}^{K} \mathbb{E}_{\nu}[N_a] \KL(\nu_a, \nu_a') \Big).
-\end{equation*}
-\end{lemma}
-
-The following theorem only holds in the case of Gaussian bandit models
-with equal known variance.
-
-\begin{theorem}[Theorem 17, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem17}
-
-Let $\mathcal{M}_m = \{\nu = (\nu_1, \dots, \nu_K): \nu_a = \mathcal{N}(\mu_a, \sigma^2), \mu_a \in \mathbb{R}, \mu_{[m]}\neq \mu_{[m+1]}\}.$ Furthermore, let $\nu$ be such that $\mu_1 > \dots > \mu_m > \mu_{m+1} > \dots > \mu_K$, and let
-
-\begin{equation*}
-H^+(\nu) = \sum_{a=1}^m \frac{2\sigma^2}{(\mu_a - \mu_{m+1})^2}, \quad H^-(\nu) = \sum_{a=m+1}^K \frac{2\sigma^2}{(\mu_m - \mu_a)^2} \quad
-and \quad
-H(\nu) = H^+(\nu) + H^-(\nu).
-\end{equation*}
-
-There exists $a \in \{1, \dots, m\}$ and $b \in \{m+1, \dots, K\}$ such that the bandit model $\nu^{[a,b]}$ described in Figure 4 (Kaufmann et al., 2016) satisfies $H(\nu^{[a,b]}) < H(\nu)$ and is such that
-
-\begin{equation*}
-\max \big( p_t(\nu),p_t(\nu^{[a,b]})\big) \geq \frac{1}{4} \exp \big(-\frac{4t}{\bar{H}(\nu)}\big), \quad where \quad \bar{H}(\nu) = \frac{H(\nu) \min(H^+(\nu),H^-(\nu))}{H(\nu)+\min(H^+(\nu),H^-(\nu))}
-\end{equation*}
-\end{theorem}
-
-Given that we are again in the Top-\(m\) setting, the proof idea is
-similar to the proof of Theorem \ref{theorem:KaufmannEtAlTheorem4} in
-that we again consider problems in which we switch arms around the
-threshold implied by \(\mu_{[m]}\) and \(\mu_{[m+1]}\). Given that, one
-might hope to apply a similar proof to the thresholding bandit problem.
-As we see in \autoref{sec:AppendixAPTLB}, a flip around the threshold is
-used in the proof of the lower bound in Theorem 1 of Locatelli et al.
-(2016). However, there, again, the distributions are assumed to be
-Gaussian. This brings the big advantage that the Kullback-Leibler
-divergence is symmetric, and the feedback can take values on all
-\(\mathbb{R}\). This is important, as is allows us to easily define
-alternative problems by a flip around the threshold with the same
-complexity as the original problem. This would not hold for
-KL-divergences that are not symmetric (e.g., for Bernoulli arms). For
-the full proof, refer to page 20 in Kaufmann et al. (2016).
-
 \subsection{\texorpdfstring{Lower Bound for Thresholding Bandit Problem
@@
 t \KL(\nu_1', \nu_1) \geq \log \Big(\frac{1}{p_t(\nu)}\Big) = -\log p_t(\nu).
-\] To make the bound as tight as possible, we choose the alternative
-model that minimizes \(\KL(\nu_1', \nu_1)\) while still ensuring that
+\]
+
+To make the bound as tight as possible, we choose the alternative model
+that minimizes \(\KL(\nu_1', \nu_1)\) while still ensuring that
 \(\mathcal{S}_{\tau}^* {'} = \{\emptyset\}\). In our case of the
-thresholding bandit with univariate exponential family distributions,
-this is given by choosing \(\mu_1' = \tau\). By pluggin in, we get the
-result:
-
-\[
-t \KL(\tau, \mu_1) \geq -\log p_t(\nu).
+thresholding bandit with one-parameter exponential family distributions,
+this is given by choosing \(\mu_1' \rightarrow \tau\) (not equal to
+\(\tau\) since else the classification of \(\nu_1\) is again correct).
+By pluggin in, we get the result:
+
+\[
+t \KL(\tau, \mu_1) \geq -\log p_t(\nu) \quad \text{for} \; \mu_1' \rightarrow \tau.
 \]
@@
 We show how the Bayes-UCB algorithm (Algorithm 1, Kaufmann et al., 2012)
-is adopted to the thresholding bandit problem to be used in the
-experiments in chapter \autoref{chap:Experiments}.
-
-We adopt their Algorithm 1 for Bernoulli distributions as follows:
+is adapted to the thresholding bandit problem to be used in the
+experiments in chapter \autoref{chap:Experiments}. The adapted version
+of their Algorithm 1 is given in Algorithm 4 below. In particular,
+notice that we not only calculate upper quantiles \(q_i^u(t)\), but also
+lower quantiles \(q_i^l(t)\), as we have to be able to compare against
+\(\tau\) from both sides. These quantiles rely on the posterior
+distributions \(\lambda_i^t\) for each mean \(\mu_i\). In our case, we
+employ Beta prior distributions as conjugate prior for the Bernoulli
+distributions in simulations 1 to 3 and initialize them with parameters
+\(\alpha_0\) and \(\beta_0\). See the setup in Kaufmann et al. (2012),
+especially equation (3), to see how the posterior distribution is
+updated in every round.
 
@@
 \For{$i = 1$ \KwTo $K$}{
-  \emph{Compute $q_i(t) = Q\Big(1-\frac{1}{t(\log T)^c}, \lambda_i^{t-1}\Big)$}\;
-  \emph{Compute $B_i(t) = $}\;
-  \If{$\hat{\sigma}^2_{i}(t) = 0$}{\emph{Set $\hat{\sigma}^2_{i}(t) = 1/T$}}
+  \emph{Compute $q_i^u(t) = Q\Big(1-\frac{1}{t(\log T)^c}, \lambda_i^{t-1}\Big)$ and $q_i^l(t) = Q\Big(\frac{1}{t(\log T)^c}, \lambda_i^{t-1}\Big)$}\;
+  \emph{Compute $B_i^{BUCB}(t) = (\tau - q_i^l(t))\cdot\mathbb{I}(\hat{\mu}_i(t) \geq \tau) + (q_i^u(t) - \tau)\cdot\mathbb{I}(\hat{\mu}_i(t) < \tau)$}\;
 }
-  \emph{Pull arm $I_t = \arg \min_{i\leq K} B_i^{SLR_{2D}}(t)$ as in \autoref{eqn:SLR2DIndex}}\;
-  \emph{Observe reward $X \sim \nu_{I_t}$}\;
+  \emph{Pull arm $I_t = \arg \max_{i\leq K} B_i^{BUCB}(t)$}\;
+  \emph{Observe reward $X \sim \nu_{I_t}$ and update $\Pi^t$}\;
 }
-\caption{2D-SLR algorithm for Normal distributions with unknown mean and unknown variance}\label{algo_slr_2d}
+\caption{Bayes-UCB algorithm from Kaufmann et al. (2012) adapted to the thresholding bandit problem.}\label{bayesucb_tbp}
 \end{algorithm}
@@
 which comes at a surprise given that is is designed for the cumulative
-regret setting and thus should tend to explore the arms to less, we also
-plot the budget allocation of three different Bayes-UCB versions. The
-three versions differ in the quantile parameter \(c\) (compare
-\autoref{sec:AppendixBUCB}) for which we set here
+regret setting and thus should tend to explore the arms to less, we run
+the Bayes-UCB algorithm for simulation 2 with three different choices of
+the parameter. In Figure 13, we see the performance results of the three
+versions, whereas Figure 14 shows how the algorithm allocates its budget
+across the arms over time. The three versions differ in the quantile
+parameter \(c\) (compare \autoref{sec:AppendixBUCB}) for which we choose
 \(c \in \{1/5, 1, 5\}\) to explore more or less. In Kaufmann et al.
@@
 the versions with smaller quantiles (smaller \(c\)) tend to perform
-better than
+better, as these correspond to more exploration of the arms. In this
+particular simulation, the choices of \(c=1/5\) and \(c=1\) perform very
+similar. We see that the worse performance of \(c=5\) can be attributed
+to a initial phase of sampling primarily the arms with mean below the
+threshold. This comes from the fact that the Bernoulli and Beta
+distributions are bounded between \(0\) and \(1\), with \(\tau\) very
+close to \(0\). Thus, the index \(B_i^{BUCB}(t)\) cannot be larger than
+\(\tau\) for arms with \(\hat{\mu}_i(t) \geq \tau\). For arms with
+\(\hat{\mu}_i(t) < \tau\), however, the index can be as large as
+\(B_i^{BUCB}(t) = 0.95\). This leads to the effect seen in Figure 14:
+Due to \(c=5\), the indexes are based on very large quantiles even in
+the beginning, which leads to large indexes for the arms with small
+means. This however is not the ideal sampling behavior. The other two
+variants adapt much better due to their smaller quantiles (and more
+exploration).
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-10-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-12-1}
 
@@
 
-\caption{Budget allocation for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter c.}\label{fig:unnamed-chunk-10}
+\caption{Budget allocation across arms for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter.}\label{fig:unnamed-chunk-12}
 \end{figure}
@@
 \subsection{Empirical Comparison of APT, SLR, and Bayes-UCB in
-Experiment
-2}\label{empirical-comparison-of-apt-slr-and-bayes-ucb-in-experiment-2}
+Simulation
+2}\label{empirical-comparison-of-apt-slr-and-bayes-ucb-in-simulation-2}
+
+We can compare the different algorithms used in Simulation 2 based on
+the overall number of pulls of each arm. In the best case, an algorithm
+would sample an arm for the optimal share of the budget, in every
+simulation. This is of course not the case, since the number of pulls of
+a given arm at the end of the budget, \(T_i(T)\), is a random variable
+for adaptive sampling strategies. Given the 5000 iterations conducted in
+simulation 2, we can plot the empirical distribution of this random
+variable for different arms.
+
+In Figure 15, we show the distribution of \(T_6(T)\) for algorithms APT,
+Bayes-UCB, and SLR. We see that the distribution of the Bayes-UCB
+algorithm is much better concentrated around the optimal share of the
+budget, and has a bell curve shape. In contrast, the distributions of
+APT and SLR are much less concentrated but flat and wide, and spread
+across a very large interval. Both algorithms have several iterations in
+which they draw arm 6, the most difficult arm only a single time (during
+initialization). This happens for APT more than 5\% of the iterations,
+and leads to the spike on the very left of the graph. In order to cope
+at least a little bit with this problem, we have also run the SLR
+algorithm with the D-Tracking rule as introduced in Garivier and
+Kaufmann (2016). The effect is nearly not noticeable in Figure 15, but
+the minimum number of observations is not clearly bounded away from 0.
+The effect on the performance was described before and is very
+noticeable in comparison to SLR without D-Tracking. However, even with
+D-Tracking the performance of Bayes-UCB is not reached. We describe SLR
+with D-Tracking in Algorithm 5.
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-11-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-13-1}
 
@@
 
-\caption{Budget allocation for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter c.}\label{fig:unnamed-chunk-11}
+\caption{Empirical distribution of pulls of arm 6 in simulation 2 by different algorithms.}\label{fig:unnamed-chunk-13}
 \end{figure}
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-12-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-14-1}
 
@@
 
-\caption{Budget allocation for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter c.}\label{fig:unnamed-chunk-12}
+\caption{Empirical distribution of pulls of arms 1 and 10 in simulation 2 by different algorithms.}\label{fig:unnamed-chunk-14}
 \end{figure}
@@
 
+\subsection{Means in Simulations 4 and
+5}\label{means-in-simulations-4-and-5}
+
+We give here the means of the distributions used in simulations 4 and 5
+for completeness.
+
+\begin{longtable}[]{@{}rrrrrrrrrr@{}}
+\caption{Mean of Exponential arms 1 to 10 in simulation
+4.}\tabularnewline
+\toprule
+V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
+\midrule
+\endhead
+0.176 & 0.2233 & 0.2407 & 0.3026 & 0.3359 & 0.35 & 0.3705 & 0.5497 &
+0.7374 & 0.8758\tabularnewline
+\bottomrule
+\end{longtable}
+
+\begin{longtable}[]{@{}rrrrrrrrrr@{}}
+\caption{Mean of Exponential arms 11 to 20 in simulation
+4.}\tabularnewline
+\toprule
+V11 & V12 & V13 & V14 & V15 & V16 & V17 & V18 & V19 & V20\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+V11 & V12 & V13 & V14 & V15 & V16 & V17 & V18 & V19 & V20\tabularnewline
+\midrule
+\endhead
+1.1419 & 1.2168 & 1.4021 & 1.6445 & 1.6868 & 1.9661 & 1.9716 & 3.2218 &
+3.2907 & 4.055\tabularnewline
+\bottomrule
+\end{longtable}
+
+\begin{longtable}[]{@{}rrrrrrrrrr@{}}
+\caption{Mean of Poisson arms 1 to 10 in simulation 5.}\tabularnewline
+\toprule
+V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
+\midrule
+\endhead
+0.0072 & 0.0576 & 0.0613 & 0.0925 & 0.1452 & 0.1559 & 0.1869 & 0.1958 &
+0.2235 & 0.2467\tabularnewline
+\bottomrule
+\end{longtable}
+
+\begin{longtable}[]{@{}rrrrrrrrrr@{}}
+\caption{Mean of Poisson arms 11 to 20 in simulation 10.}\tabularnewline
+\toprule
+V11 & V12 & V13 & V14 & V15 & V16 & V17 & V18 & V19 & V20\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+V11 & V12 & V13 & V14 & V15 & V16 & V17 & V18 & V19 & V20\tabularnewline
+\midrule
+\endhead
+0.2664 & 0.3008 & 0.4295 & 0.4948 & 0.5857 & 0.6904 & 0.7609 & 0.785 &
+0.8878 & 1.7114\tabularnewline
+\bottomrule
+\end{longtable}
+
 \end{document}

### 2017-09-10 Thesis/Draft.Rmd
Add References

@@
 ---
-title: "Draft"
+title: "On Pure Exploration, Thresholding Bandits, and Kullback-Leibler Divergence"
 header-includes:
@@
 
+\vspace*{10\baselineskip}
+
 "In general, we look for a new law by the following process: First we guess it.
@@
 
-# Abbreviations
-
-Kullback-Leibler divergence between distributions $\nu_i$ and $\nu_j$: $\KL(\nu_i||\nu_j)$.
-
-Binary relative entropy: $d(x,y) := x \log(x/y) + (1-x) \log((1-x)/(1-y))$, where $d(0,0) = d(1,1) = 0$.
-
-Kullback-Leibler divergence for two Bernoulli distributions parameterized by their means $\mu_i$ and $\mu_j$: $KL_{Ber}(\nu_i||\nu_j) = d(\mu_i, \mu_j)$.
-
-Define exponential family of distributions
-
-Define KL Divergence for this family
-
-\newpage
-
 # Introduction \label{chap:Introduction}
@@
 
-This makes sequential sampling especially relevant in situations where there is an inherent cost to obtaining samples.
+This makes sequential sampling especially relevant in situations where there is an inherent cost to obtaining samples, or where only a limited amount of samples can be collected.
 The classical example is that of clinical trials in which a researcher tests two drugs on patients to observe which one performs better.
@@
 In this thesis, we consider the thresholding bandit problem.
-Instead of identifying the best $m$ out of $K$ arms, we aim to find all distributions out of $K$ that have a mean at least as large as a threshold fixed upfront.
+While the name is reminiscient of the cumulative regret multi-armed bandit, the problem is more similar to the top-$m$ problem.
+But instead of identifying the best $m$ out of $K$ arms, one aims to find all distributions out of $K$ that have a mean at least as large as a fixed threshold.
+Given that an implicit threshold arises in the top-$m$ problem between the $m$-th best and the $(m+1)$-th best arm (Kaufmann et al., 2016), the two problems share many characteristics.
+We discuss this in more detail in \autoref{chap:KullbackLeiblerPureExploration}.
 In the form described in Locatelli et al.
@@
 
-To introduce the thresholding bandit problem, consider a game in which the learner is tasked to find the slot machines within a row of $K$ slot machines in a casino that give a mean payoff larger than a fixed threshold $\tau$, for example $\tau = 0$.
-The learner cannot pull all slot machines at the same time.
-Instead, he acquires samples sequentially from one slot machine at a time to learn about their payoff structure.
-The learner has a budget of $T>K$ slot machine pulls.
-After $t-1$ samples, the learner has observed $T_i(t-1)$ samples from slot machine $i$.
-The payoffs $X_{i,1}, ..., X_{i,T_i(t-1)}$ are drawn from the payoff distribution $\nu_i$ underlying the slot machine $i$.
-At time $t$, the learner considers the payoffs he observed so far in order to choose the next slot machine he would like to pull.
-Her decision is lead by the goal to classify the slot machines with distribution $\nu_i$ and mean payoff $\mu_i = \mathbb{E}_{X \sim \nu_i}[X]$ after $T$ samples as being above or below the threshold with error probability as small as possible.
-
-The thresholding bandit problem can thus be framed in the literature on sequential sampling strategies.
-Even though its name is reminiscient of the multi-armed bandit setting, the thresholding bandit problem is more akin to best arm identification and top-$m$ identification problems due to its focus on exploration: While the classical multi-armed bandit problems are concerned with cumulative regret which increases *during* sampling, best arm identification and thresholding bandits collect loss only once *after* the sampling procedure (compare Garivier and Kaufmann, 2016; Kaufmann et al., 2016; Kaufmann and Kalyanakrishnan, 2013).
-As we will see in \autoref{chap:KullbackLeiblerPureExploration} there arises an implicit threshold between the means of the $m$-th best arm and the $m+1$-th best arm in the top-$m$ identification problem (Kaufmann et al., 2016; Kaufmann and Kalyanakrishnan, 2013).
-Because of this, the two settings are very related.
-
-## Setup \label{sec:Setup}
+## An Example
+
+To introduce the thresholding bandit problem, consider a common situation among internet-based companies.
+These companies often collect user feedback to offer reviews and ratings on websites or in apps, or collect it to improve their services.
+Netflix lets users rate movies with "Thumbs up" and "Thumbs down", apps like Clue ask users a question per day to learn to predict the user's health and mood.
+An online shop might give customers a one-question survey after they make a purchase.
+Finally, Foursquare and Yelp ask users to rate coffee shops, bars, and restaurants.
+
+Consider the problem the latter companies face.
+Whenever a user reports that she visited a restaurant, the app would like to ask questions about her experience.
+To give a simple example, assume users are not willing to answer more than one question per restaurant visit, and the app would like to find out two things: Does the restaurant have good service?
+Is the restaurant trendy?
+
+If the feedback that users can give is restricted to binary "Yes" or "No" answers, then we can model the feedback as Bernoulli random variables
+
+$$
+X_{\text{service}} \sim \text{Ber}(\mu_{\text{service}}) \quad \text{and} \quad X_{\text{trendy}} \sim \text{Ber}(\mu_{\text{trendy}}).
+$$
+
+The app will then display a "Good service" or "This place is trendy" description for the restaurant if $\mu_{\text{service}}$ and $\mu_{\text{trendy}}$ are estimated to be above a certain threshold, for example $\tau = 0.5$.
+That is, more than half of the people would describe the place as having good service, or as trendy.
+
+To make the app as useful as possible to other users, this information should be shown as quickly as possible.
+But even though the app has thousands of users, not that many people visit a specific restaurant, and even less people report this back to the app.
+Thus the company only has a limited budget of $T$ potential users from which to collect samples $X_{\text{service}}$ and $X_{\text{trendy}}$ from.
+How can the company ask these $T$ questions to be as confident as possible in its classification, that is, in the information it displays?
+
+A straightforward way of sampling users would be to ask the two questions in a round-robin fashion: Ask for "Service", then for "Trendy", then for "Service", ...
+Given 100 users, 50 users give feedback on the service level, 50 users report on the trendiness level.
+This however is unlikely to be optimal with respect to the confidence after 100 samples.
+Given that the company asks the users sequentially, there is the option to adapt the sampling strategy over time: If the first ten users report $\sum_{s=1}^{10}X_{\text{service},s}=10$, while $\sum_{s=1}^{10}X_{\text{trendy},s}=5$, then the company might already be quite confident that $\mu_{\text{service}} \geq \tau = 0.5$, while this is less clear for $\mu_{\text{trendy}}$.
+Instead of continuously sampling both questions, it might be more useful to collect more feedback on the trendiness level so as to figure out its position relative to the threshold.
+After all, the company would like to use the 100 samples to maximize its confidence in both displayed tips.
+
+Finding the optimal sequential sampling strategy to classify distributions against a threshold with as much confidence as possible after a limited budget of samples is the problem described above, and the problem described by the thresholding bandit problem which we discuss for the remainder of this thesis.
+In the following section, we define the general setting of the thresholding bandit problem.
+
+## General Setting \label{sec:Setup}
 
@@
 To stick with the idea of multi-armed bandits, we call the distributions arms, and observations from the arms rewards (Bubeck and Cesa-Bianchi, 2012).
-The learner is interested in learning about the structure of the arms; in particular, she would like to estimate the means $\mu_1, ..., \mu_K$ by sequentially drawing observations $X_{i,1}, X_{i,2}, ...$ from the different arms.
+The learner is interested in learning about the structure of the arms; in particular, she would like to estimate the means $\mu_1, ..., \mu_K$ by sequentially drawing observations $X_{i,1}, X_{i,2}, ...$ from the different arms, where $X_{i} \sim \nu_i$.
 However, at time $t$ the learner cannot observe a reward from every distribution but must select a single arm $I_t$ from which she would like to observe the reward $X_{I_t,t}$.
@@
 
-### Proof of Theorem \ref{theorem:LocatelliTheorem4}
+### Proof of Theorem \ref{theorem:LocatelliTheorem4} \label{sec:UpperBoundProof}
 
@@
 Then arm $i$ contributes a share of $h_i/H$ to the overall problem complexity.
-We can now show that there exists an arm that has been pulled at least as often as the share of his complexity contribution.
+We can now show that there exists an arm that has been pulled at least as often as the share of its complexity contribution.
 
@@
 
-### Check Separation Condition
+### Check Separation Condition \label{sec:CheckSeparationCondition}
 
@@
 $UB = (\log(T)+1)K \exp(2) \exp(-\frac{1}{64R^2}\frac{T}{H}) = C_{UB}(\log(T)+1)K\exp(-T/H)$, we see that $LB$ and $UB$ match up to multiplicative constants and the $(\log(T)+1)K$ term which is negligiable in comparison with the exponent for large $T$ as shown in Locatelli et al.
-(2016), which makes the APT algorithm order optimal.
+(2016).
+This makes the APT algorithm order optimal.
 
@@
 
-- Mention Optimality (Upper Bound matches lower bound)
-- Anytime
-
 One of the APT algorithm's main features is its simplicity.
-The sampling rule is very straightforward, and, as highlighted in Locatelli et al.
+The sampling rule is straightforward, and, as highlighted in Locatelli et al.
 (2016), it does not require any knowledge about the type of sub-Gaussianity $R$, or the complexity $H$ upfront.
 This makes the algorithm immediately applicable in practice while it still enjoys its upper bound on the expected regret.
-This is in particular worth highlighting when comparing APT to algorithms used in the best arm identification or Top-$m$ setting.
-As alluded to in \autoref{sec:TheAPTAlgorithm}, many algorithms that fix the sampling budget upfront (i.e., fixed budget algorithms as UCB-E or KL-LUCB-E) require knowledge about the corresponding complexity upfront (Audibert et al., 2010; Kaufmann and Kalyanakrishnan, 2013).
-The problem however being, that to know the complexity, the experimenter has to know all means up to a permutation of the arms.
+This is in particular worth highlighting when comparing APT to algorithms used in the best arm identification or top-$m$ setting.
+As alluded to in \autoref{sec:TheAPTAlgorithm}, many algorithms that fix the sampling budget upfront (i.e., fixed budget algorithms as UCB-E or KL-LUCB-E) require knowledge about the complexity upfront (Audibert et al., 2010; Kaufmann and Kalyanakrishnan, 2013).
+The problem however being that to know the complexity, the experimenter has to know all means up to a permutation of the arms.
 This, of course, is not given in practice.
@@
 While the APT algorithm does not explicitly estimate the complexity, the gaps that serve as index are essentially the same.
-Faced not with sub-Gaussian but more heavy-tailed distributions, these estimates might well lead to poor performance.
-
-Here, the APT algorithm shows room for improvement, as also mentioned in Locatelli et al.
-(2016).
-The problem is that the assumptions for the bounds no longer hold as arms are less sub-Gaussian; of course the complexity $H$ and the term $\hat{\Delta}_i(t)$ in the algorithm's index are motivated by sub-Gaussian distributions.
-The more one moves away from those, the less appropriate these quantities become.
+Empirically, we see in \autoref{chap:Experiments} that the problem described by Garivier and Kaufmann (2016) does also occur for the APT strategy.
+Faced not with sub-Gaussian but with more heavy-tailed distributions, this sensitivity is likely to increase.
+
+Furthermore, as mentioned in Locatelli et al.
+(2016), the assumptions for the bounds no longer hold as arms become less sub-Gaussian; the complexity $H$ and the term $\hat{\Delta}_i(t)$ in the algorithm's index are both motivated by sub-Gaussian distributions.
+The more a problem deviates from those, the less appropriate the quantities become.
 In particular, the empirical mean will be less (or not at all) concentrated around the true mean and more impacted by outliers which are more likely under non sub-Gaussian distributions.
@@
 (2016) thus refers to Bubeck et al.
-(2013a) which considers solutions for multi-armed bandits that are based on heavy-tail distributions.
+(2013a) which consider solutions for multi-armed bandits that are based on heavy-tail distributions.
 By using more robust estimators of the mean, one could equip the APT algorithm to deal with such distributions.
@@
 (2016).
-We will continue to discuss their results in \autoref{chap:VarianceBasedAlgorithms}.
+We will continue to discuss their results in \autoref{sec:VarianceBasedAlgorithms}.
 
@@
 $$
-\KL_{N}(\nu_i || \nu_j) = 2(\mu_i - \mu_j)^2.
+\KL_{\mathcal{N}}(\nu_i || \nu_j) = 2(\mu_i - \mu_j)^2.
 $$
@@
 $$
-\KL_{Ber}(\nu_i||\nu_j) = \mu_i \log(\frac{\mu_i}{\tau}) + (1-\mu_i) \log(\frac{1-\mu_i}{1-\tau})
+\KL_{\text{Ber}}(\nu_i||\nu_j) = \mu_i \log(\frac{\mu_i}{\tau}) + (1-\mu_i) \log(\frac{1-\mu_i}{1-\tau})
 $$
@@
 $$
-\KL_{Ber}(\nu_i||\nu_j) \geq 2(\mu_i - \tau)^2.
-$$
-
-This is of course equal to the Gaussian KL-divergence described before.
-This approximation, however, suffers for heavily for very small values of $\mu_i$ and $\tau$.
-In particular, the Bernoulli KL-divergence becomes asymmetric in its first argument as $\tau \neq 0.5$.
+\KL_{\text{Ber}}(\nu_i||\nu_j) \geq 2(\mu_i - \tau)^2.
+$$
+
+This is equal to the Gaussian KL-divergence described before.
+The approximation, however, suffers heavily for very small values of $\mu_i$ and $\tau$.
+In particular, the Bernoulli KL-divergence becomes asymmetric in its first argument when $\tau \neq 0.5$.
 Thus, in contrast to the complexity measure $H$ based on the Gaussian KL-divergence, a complexity measure based on the Bernoulli KL-divergence would evaluate two arms as differently difficult if their absolute distance to the threshold is the same, but they lie on different sides of the threshold.
 
-Thus similarly to how UCB algorithms in the cumulative regret setting have been extended to KL-UCB algorithms (compare Cappé et al., 2013), also the APT algorithm offers room for improvement.
-As a more explicit example of such adaptation, consider the case of Top-$m$ identification described in Kaufmann et al.
+Thus similarly to how UCB algorithms in the cumulative regret setting have been extended to KL-UCB algorithms (Cappé et al., 2013), the APT algorithm offers room for improvement, too.
+As a more explicit example of such adaptation, consider the case of top-$m$ identification described in Kaufmann et al.
 (2016).
 The authors develop a lower bound based on KL-divergence, and note that "This information-theoretic lower bound permits to interpret the quantity $H(\nu)$ [...] as a subgaussian approximation".
-Given that Bernoulli distributions with very small parameter values arise naturally in many applications, an improvement in this regard would be valuable.
-
-In what follows, we first examine in \autoref{chap:KullbackLeiblerPureExploration} how information theoretic quantities are employed in the best arm identification and Top-$m$ problem as detailed in Kaufmann and Garivier (2016) and Kaufmann et al.
+Given that Bernoulli distributions with very small or very large parameter values arise naturally in many applications, an improvement in this regard would be valuable.
+
+In what follows, we first examine in \autoref{chap:KullbackLeiblerPureExploration} how information theoretic quantities are employed in the best arm identification and top-$m$ problem as detailed in Kaufmann and Garivier (2016) and Kaufmann et al.
 (2016).
@@
   labs(x = "First argument of KL-divergence",
-       y = "KL-divergence",
-       title = "Comparison of Bernoulli KL-divergence and 
-Gaussian Approximation")  +
+       y = "KL-divergence"#,
+       #title = "Comparison of Bernoulli KL-divergence and Gaussian Approximation"
+       )  +
   theme_bw() +
-  theme(legend.position = "bottom") +
-  scale_color_discrete(name = "Second argument of KL-divergence") +
-  scale_linetype_discrete(name = "Type of KL-divergence") +
+  #theme(legend.position = "bottom") +
+  scale_color_discrete(name = "Second argument \nof KL-divergence") +
+  scale_linetype_discrete(name = "Type of \nKL-divergence") +
   guides(color = guide_legend(title.position = "top"),
@@
 
+\newpage
+
 # Information Theoretic Approaches to Pure Exploration Bandits \label{chap:KullbackLeiblerPureExploration}
@@
 The previous chapter introduces the thresholding bandit problem as described in Locatelli et al.
-(2016), and with the APT strategy a first algorithm that is simple, yet order-optimal for large budgets.
-However, we end with the conclusion that a distance measure between the distributions and the threshold based on the Kullback-Leibler divergence might be more useful than the simple gap $\Delta^2_i = (\mu_i - \tau_i)^2$ employed so far.
+(2016), and the APT strategy as a first algorithm that is simple, yet order-optimal for large budgets.
+However, we end with the conclusion that a KL-divergence based measure of the distance between the distributions and the threshold might be more useful than the simple gap $\Delta^2_i = (\mu_i - \tau_i)^2$ employed so far.
 Indeed, citing Kaufmann et al.
-(2016), we note that the complexity $H$ used so far can be considered a sub-Gaussian approximation of a better complexity measure based on information theoretic measures like the Kullback-Leibler divergence.
-
-In order to give more intuition to why that is the case, and in what ways information theoretic measures can be introduced to measure the complexity of bandit problems, we now turn to Kaufmann et al.
+(2016), we note that the complexity $H$ -- and thus the gaps -- used so far can be considered a sub-Gaussian approximation of a better complexity measure based on information theoretic measures like the Kullback-Leibler divergence.
+
+In order to give more intuition to why that is the case, and in which ways information theoretic measures can be introduced to measure the complexity of bandit problems, we now turn to Kaufmann et al.
 (2016) and Garivier and Kaufmann (2016).
 The latter describes a strategy based on Kullback-Leibler divergences for the best-arm identification problem, while the first derives complexity measures based on the divergence.
-Ideally, their work offers methods that can inform our work of extending the thresholding bandit problem.
+Their work offers methods that can inform our goal of extending the thresholding bandit problem.
 In what follows, we adopt the notation of Kaufmann et al.
@@
 (2016) consider the problem of identifying the best $m$ out of $K$ arms, that is, the top-$m$ problem.
-They describe their bandit model $\nu$ by $K$ arms characterized by probability distributions $\nu_a$, $a \in \{1,...,K\}$, with mean $\mu_a$.
-A learner picks at any time step $t=1,2,...,$ an arm $A_t \in \{1,...,K\}$ for which he observes the independent reward $Z_{t} \sim \nu_{A_t}$.
+They describe their bandit model $\nu = (\nu_1,...,\nu_K)$ by $K$ arms characterized by probability distributions $\nu_i$, $i \in \mathbb{A} = \{1,...,K\}$, with mean $\mu_i$.
+A learner picks at any time step $t=1,2,...,$ an arm $I_t \in \{1,...,K\}$ for which she observes the independent reward $X_{t} \sim \nu_{I_t}$.
 The learner aims to find the $m$ out of $K$ arms with the largest expected reward.
@@
 The class of bandit problems $\nu$ for which the latter condition holds is called $\mathcal{M}_m$ by Kaufmann et al.
-At the end of the sampling procedure, after $T$ samples (denoted by $\tau$ in Kaufmann et al.) the learner is required to return a classification $\hat{\mathcal{S}}_m$.
+At the end of the sampling procedure, after $T$ samples, the learner is required to return a classification $\hat{\mathcal{S}}_m$.
 This classification is then evaluated by the loss function $\mathcal{L}(T) = \mathbb{I}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m)$.
 This binary loss is similar to the loss in the thresholding bandit.
-We can now define a strategy of the learner as $\mathcal{A} = ((A_t), T, \hat{\mathcal{S}}_m)$: The strategy defines how an arm is chosen, how many samples are observed, and how the arms are eventually classified.
-
-When introducing the thresholding bandit setting, we did not mention the fact that the budget $T$ does not need to be fixed upfront.
-Indeed, the setting in which the budget is *not* fixed upfront might be more popular among the best arm identification and top-$m$ literature.
-This setting is called *fixed confidence*, while the setting we considered so far is called *fixed budget*.
+We can now define a strategy of the learner as $\mathcal{S} = ((I_t), T, \hat{\mathcal{S}}_m)$: The strategy defines how an arm is chosen, how many samples are observed, and how the arms are eventually classified.
+
+When introducing the thresholding bandit setting, we did not mention the fact that there exists an alternative setting in which the budget $T$ is not fixed upfront.
+This setting is called *fixed confidence*, while the case we considered so far is called *fixed budget*.
 In the fixed budget setting, we run algorithms for $T$ samples and then compare them based on their expected loss, $\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m) =: p_t(\nu)$ as we have seen in $\autoref{sec:Setup}$.
-Alternatively, consider a $\delta$-PAC strategy $\mathcal{A}(\delta)$for which it holds for every problem $\nu \in \mathcal{M}_m$ that the classification holds at least with confidence level $1-\delta$, that is, $\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta$.
+Alternatively, consider a $\delta$-PAC strategy $\mathcal{S}(\delta)$for which it holds for every problem $\nu \in \mathcal{M}_m$ that the classification holds at least with confidence level $1-\delta$, that is, $\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta$.
 The strategy has to achieve this level of confidence in its prediction before it is allowed to stop sampling.
-This is the fixed confidence case, in which the budget $T$ is no longer fixed upfront, but turns into a random variable.
+This is the fixed confidence case, in which the budget $T=T_{\delta}$ is no longer fixed upfront, but becomes a random variable.
 Algorithms are then compared by their expected number of draws $\mathbb{E}_{\nu}[T_{\delta}]$ and we prefer those which achieve the confidence level $1-\delta$ with a smaller expected budget.
 
-In the fixed confidence setting, a family of strategies $A = (\mathcal{A}(\delta))_{\delta \in (0,1)}$ is called PAC if for every $\delta$, $\mathcal{A}(\delta)$ is $\delta$-PAC.
-On the other hand, in the fixed budget setting, a family of strategies $A = (\mathcal{A}(t))_{t \in \mathbb{N}}$ is called consistent if $p_t(\nu) \rightarrow 0$ as $t \rightarrow \infty$ for every problem $\nu \in \mathcal{M}_m$.
+In the fixed confidence setting, a family of strategies $S = (\mathcal{S}(\delta))_{\delta \in (0,1)}$ is called PAC if for every $\delta$, $\mathcal{S}(\delta)$ is $\delta$-PAC.
+On the other hand, in the fixed budget setting, a family of strategies $S = (\mathcal{S}(t))_{t \in \mathbb{N}}$ is called consistent if $p_t(\nu) \rightarrow 0$ as $t \rightarrow \infty$ for every problem $\nu \in \mathcal{M}_m$.
 
@@
 approach complexity by how many samples (what error probability) one will need in the fixed confidence (fixed budget) setting.
-In order to arrive at their new measure of complexity, it makes sense to first follow their arguments to a general lower bound on the sample complexity $\mathbb{E}_{\nu}[\tau]$ which is given in their Theorem 4:
+In order to arrive at their new measure of complexity, it makes sense to first follow their arguments to a general lower bound on the sample complexity $\mathbb{E}_{\nu}[T]$ which is given in their Theorem 4.
+Here, $\mathcal{P}$ refers to a set of probability measures for which Kaufmann et al.
+(2016) assume certain continuity conditions in their Assumption 3, and $\nu_i \in \mathcal{P}$.
+In the following, $d(x,1-x) = x\log(\frac{x}{1-x}) + (1-x) \log(\frac{1-x}{x})$ is the binary KL-divergence.
 
@@
 
-To prove this statement for a given $\delta$-PAC algorithm $\mathcal{A}$, we assume certain continuity conditions (compare Kaufmann et al.
-(2016)) under which there exists for every arm $a \in \{1, \dots, K\}$ an alternative model $\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)$.
-In this alternative model, in accordance with the continuity conditions, only arm $a$ is modified.
-After the modification, the arm $\nu_{m+1}$ is now closer to $\nu_a$ as measured by the Kullback-Leibler divergence than $\nu_a'$ is to $\nu_a$, if $\mu_a > \mu_{m+1}$ (consequently, $\mu_a' < \mu_{m+1}$).
-On the other hand, if $\mu_a < \mu_{m}$, then $\nu_a'$ will be moved away from $\nu_a$ just enough so that $\nu_a$ is closer to $\nu_m$ than to $\nu_a'$ (consequently, $\mu_a' > \mu_m$).
+To prove this statement for a given $\delta$-PAC strategy $\mathcal{S}$, we assume certain continuity conditions (compare Kaufmann et al.
+(2016)) under which there exists for every arm $i \in \{1, \dots, K\}$ an alternative model $\nu' = (\nu_1, \dots, \nu_{i-1}, \nu_i', \nu_{i+1}, \dots, \nu_K)$.
+In this alternative model, in accordance with the continuity conditions, only arm $i$ is modified.
+After the modification, the arm $\nu_{m+1}$ is now closer to $\nu_i$ as measured by the Kullback-Leibler divergence than $\nu_i'$ is to $\nu_i$, if $\mu_i > \mu_{m+1}$ (consequently, $\mu_i' < \mu_{m+1}$).
+On the other hand, if $\mu_a < \mu_{m}$, then $\nu_a'$ will be moved away from $\nu_i$ just enough so that $\nu_i$ is closer to $\nu_m$ than to $\nu_i'$ (consequently, $\mu_i' > \mu_m$).
 These changes in distribution make the original set of optimal arms, $\{1,\dots,m\}$, no longer optimal under the alternative model $\nu'$.
 To compare this to the thresholding bandit problem, assume that arms $\nu_{m}$ and $\nu_{m+1}$ indirectly define a threshold $\tau \in (\mu_{m+1},\mu_m)$.
-Then, by creating an alternative problem as described here, we flip arm $a$ around the implied threshold $\tau$ (compare the lower bound proof in \autoref{sec:AppendixAPTLB}).
+Then, by creating an alternative problem as described here, we flip arm $i$ around the implied threshold $\tau$ (compare the lower bound proof in \autoref{sec:AppendixAPTLB}).
 
@@
 \begin{lemma}[Lemma 1, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma1}
-Let $\nu$ and $\nu'$ be two bandit models with $K$ arms such that for all $a$, the distributions $\nu_a$ and $\nu_a'$ are mutually absolutely continuous.
+Let $\nu$ and $\nu'$ be two bandit models with $K$ arms such that for all $i$, the distributions $\nu_i$ and $\nu_i'$ are mutually absolutely continuous.
 For any almost-surely finite stopping time $\sigma$ with respect to $(\mathcal{F}_t)$,
@@
 \begin{equation*}
-\sum_{a=1}^{K} \mathbb{E}_{\nu} [N_a(\sigma)] \KL(\nu_a|| \nu_a') \geq \sup_{\mathcal{E} \in \mathcal{F}_{\sigma}} \der (\mathbb{P}_{\nu}(\mathcal{E}), \mathbb{P}_{\nu'}(\mathcal{E})).
+\sum_{i=1}^{K} \mathbb{E}_{\nu} [N_i(\sigma)] \KL(\nu_i|| \nu_i') \geq \sup_{\mathcal{E} \in \mathcal{F}_{\sigma}} d(\mathbb{P}_{\nu}(\mathcal{E}), \mathbb{P}_{\nu'}(\mathcal{E})).
 \end{equation*}
@@
 
-We apply this Lemma directly on the expected number of draws for each arm, $\mathbb{E}_{\nu}[N_a]$.
-For each arm $a$, we thus have $\KL(\nu_a, \nu_a') \mathbb{E}_{\nu}[N_a] \geq d(1-\delta, \delta)$.
-Using the definition of the alternative model above, we get for every small but fixed $\alpha > 0$, every arm $a \in \{1, \dots, K\}$ and $b \in \{m+1, \dots, K\}$:
+We apply this Lemma directly on the expected number of draws for each arm, $\mathbb{E}_{\nu}[N_i]$.
+For each arm $a$, we thus have $\KL(\nu_i, \nu_i') \mathbb{E}_{\nu}[N_i] \geq d(1-\delta, \delta)$.
+Using the definition of the alternative model above, we get for every small but fixed $\alpha > 0$, every arm $i \in \{1, \dots, K\}$ and $j \in \{m+1, \dots, K\}$:
 
 \begin{equation*}
-\mathbb{E}_{\nu}[N_a] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_a || \nu_{m+1}) + \alpha} \quad \text{and} \quad \mathbb{E}_{\nu}[N_b] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_b || \nu_{m}) + \alpha}.
+\mathbb{E}_{\nu}[T_i] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_i || \nu_{m+1}) + \alpha} \quad \text{and} \quad \mathbb{E}_{\nu}[T_j] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_j || \nu_{m}) + \alpha}.
 \end{equation*}
@@
 \begin{equation*}
-\mathbb{E}_{\nu}[T] = \sum_{a=1}^K \mathbb{E}_{\nu}[N_a] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m]})} \Big) \der(1-\delta, \delta)
+\mathbb{E}_{\nu}[T] = \sum_{i=1}^K \mathbb{E}_{\nu}[T_i] \geq \Big( \sum_{i \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_i|| \nu_{[m+1]})} + \sum_{i \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_i|| \nu_{[m]})} \Big) d(1-\delta, \delta)
 \end{equation*}
@@
 \begin{equation}\label{bre_approx}
-\forall x \in [0,1], \quad \der(x,1-x) = \der(1-x,x) \geq \log \frac{1}{2.4x}.
+\forall x \in [0,1], \quad d(x,1-x) = d(1-x,x) \geq \log \frac{1}{2.4x}.
 \end{equation}
@@
 \begin{equation*}
-\mathbb{E}_{\nu}[T] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
+\mathbb{E}_{\nu}[T] \geq \Big( \sum_{i \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_i|| \nu_{[m+1]})} + \sum_{i \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_i|| \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
 \end{equation*}
@@
 Given this lower bound, it is clear that the complexity of the top-$m$ problem can be lower bounded by the KL-divergence between arms and the implied threshold between the $m$-th best arm and the $(m+1)$-th best arm.
-The latter gives a lower bound on the effort (in terms of expected number of samples) required to achieve a certain confidence level, where a problem that requires a larger effort is described as more complex.
+The last equation gives a lower bound on the effort (in terms of expected number of samples) required to achieve a certain confidence level, where a problem that requires a larger effort is described as more complex.
 Indeed, in the case of fixed confidence problems, Kaufmann et al.
 (2016) describe problems as having a larger *sampling complexity*.
-
-Following Kaufmann et al. (2016), we define the complexity $\kappa_C(\nu)$ in the fixed confidence setting as
+Following Kaufmann et al.
+(2016), we define the complexity $\kappa_C(\nu)$ in the fixed confidence setting as
 
 \begin{equation}
-\kappa_C(\nu) = \inf_{A \, \text{PAC}} \limsup_{\delta \to 0} \frac{\mathbb{E}_{\nu}[T_{\delta}]}{\log \frac{1}{\delta}}. \label{eq:KappaC}
+\kappa_C(\nu) = \inf_{S \, \text{PAC}} \limsup_{\delta \to 0} \frac{\mathbb{E}_{\nu}[T_{\delta}]}{\log \frac{1}{\delta}}. \label{eq:KappaC}
 \end{equation}
@@
 
-Consider a consistent fixed budget strategy $\mathcal{A}$ ($p_t(\nu)$ tends to zero as $t \rightarrow \infty$), and define the complexity in the fixed budget setting as follows:
+Consider a consistent fixed budget strategy $\mathcal{S}$ ($p_t(\nu)$ tends to zero as $t \rightarrow \infty$), and define the complexity in the fixed budget setting as follows:
 
@@
 The resulting lower bound given in Theorem 12 of Kaufmann et al.
-(2016):
+(2016).
+We see that the best exponent with which the error $p_t(\nu)$ decreases as $t \rightarrow \infty$ is based on Kullback-Leibler divergences:
 
@@
 For a proof, consider first the two different bandit models, $\nu$ and $\nu'$, where we fix w.l.o.g.
-$a^* = 1$ as the best arm in $\nu$, while $a^* = 2$ in $\nu'$.
-We require the algorithm $\mathcal{A}$ to be consistent for both problems.
+$i^* = 1$ as the best arm in $\nu$, while $i^* = 2$ in $\nu'$.
+We require the algorithm $\mathcal{S}$ to be consistent for both problems.
 Since we are in the fixed budget setting, the stopping time is fixed at $T = t$.
@@
 \begin{equation*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1'|| \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2'|| \nu_2) \geq \der(\mathbb{P}_{\nu'}(A),\mathbb{P}_{\nu}(A)))
+\mathbb{E}_{\nu'}[T_1(t)]\KL(\nu_1'|| \nu_1) + \mathbb{E}_{\nu'}[T_2(t)]\KL(\nu_2'|| \nu_2) \geq \der(\mathbb{P}_{\nu'}(A),\mathbb{P}_{\nu}(A)))
 \end{equation*}
 
-The expectations were chosen with respect to $\nu'$ in order to allow for the following: We have $p_t(\nu) = 1 - \mathbb{P}_{\nu}(A)$ and $p_t(\nu') = \mathbb{P}_{\nu'}(A)$ (since $A$ is wrong in $\nu'$).
+The expectations were chosen with respect to $\nu'$ in order to allow for the following: We have $p_t(\nu) = 1 - \mathbb{P}_{\nu}(A)$ and $p_t(\nu') = \mathbb{P}_{\nu'}(A)$ (since $A$ is wrong for $\nu'$).
 But since algorithm $\mathcal{A}$ is consistent for both $\nu$ and $\nu'$, we know that there should exist some number of samples such that the probability of event $A$ is bigger in setting $\nu$ (where it is the correct decision) than in setting $\nu'$ (where this would be a wrong decision and failure).
@@
 \begin{align*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1' || \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2' || \nu_2) & \geq \der(\epsilon,1-p_t(\nu))) \\
+\mathbb{E}_{\nu'}[T_1(t)]\KL(\nu_1' || \nu_1) + \mathbb{E}_{\nu'}[T_2(t)]\KL(\nu_2' || \nu_2) & \geq \der(\epsilon,1-p_t(\nu))) \\
 & = \epsilon \log \frac{\epsilon}{1-p_t(\nu)} + (1-\epsilon) \log \frac{1-\epsilon}{p_t(\nu)} \\
@@
 \begin{align*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1' || \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2' || \nu_2)
+\mathbb{E}_{\nu'}[T_1(t)]\KL(\nu_1' || \nu_1) + \mathbb{E}_{\nu'}[T_2(t)]\KL(\nu_2' || \nu_2)
 & \geq \log \frac{1}{p_t(\nu)} = -\log p_t(\nu).
@@
 \limsup_{t \to \infty} - \frac{1}{t} \log p_t(\nu)
-& \leq \limsup_{t \to 0} \frac{1}{t} \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)] \KL(\nu_a' || \nu_a) \\
-& \leq \max_{a=1,2} \KL(\nu_a' || \nu_a),
+& \leq \limsup_{t \to 0} \frac{1}{t} \sum_{i=1}^2 \mathbb{E}_{\nu'}[T_i(t)] \KL(\nu_i' || \nu_i) \\
+& \leq \max_{i=1,2} \KL(\nu_i' || \nu_i),
 \end{align*}
 
-where the last line follows from the fact that the $\frac{1}{t} \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)]$ part creates a weighted average of the two divergences $\KL(\nu_a', \nu_a)$.
+where the last line follows from the fact that the $\frac{1}{t} \sum_{i=1}^2 \mathbb{E}_{\nu'}[T_i(t)]$ part creates a weighted average of the two divergences $\KL(\nu_i', \nu_i)$.
 As noted in Kaufmann et al.
@@
 (2016), the advantage of this lower bound is that it makes the complexity in the fixed confidence and the fixed budget setting directly comparable.
-The disadvantage of course being that the result only holds for two-armed models.
-While the authors are not able to derive directly comparable lower bounds for the top-$m$ case, they derive a first lower bound in the Gaussian case with equal variances, which we describe shortly in the appendix in \autoref{sec:KaufmannLBTopMGaussian}.
-
-Before we discuss algorithms given in Kaufmann et al. (2016) that match the lower bounds, we show how lower bounds can be derived very similarly for the fixed budget thresholding problem.
+The disadvantage being that the result only holds for two-armed models.
+While the authors are not able to derive directly comparable lower bounds for the top-$m$ case, they derive a first lower bound in the Gaussian case with equal variances.
+
+Before we discuss algorithms given in Kaufmann et al.
+(2016) that match the lower bounds, we show how based on the proof of Theorem 12 in Kaufmann et al.
+(2016) very similar lower bounds can be derived for the fixed budget thresholding problem.
 
@@
 In order to derive a bound for the fixed budget problem, Kaufmann et al.
-(2016) have focused on the setting with two arms which is the most simple version of the top-$m$ problem.
-Less than two arms do not make sense, since the single arm is by definition the best arm.
+(2016) focus on the setting with two arms which is the most simple version of the top-$m$ problem.
+Less than two arms does not make sense, since the single arm is by definition the best arm.
 In the case of the thresholding bandit, however, a single-armed problem makes still at least limited sense in that we still have to classify this arm correctly with respect to the threshold.
@@
 \begin{corollary}
+Consider the setting in \autoref{sec:Setup}.
 Let $\nu = \nu_1$ be a one-armed thresholding bandit model where $\tau$ is the threshold fixed upfront.
-Let $\nu$ be from the univariate exponential family of distributions such that $\nu_1$ can be parameterized by its mean, $\mu_1$, and the Kullback-Leibler divergence between distributions $\nu_1$ and $\nu_1'$ can be written as $\KL(\nu_1', \nu_1) = \KL(\mu_1', \mu_1)$.
-In the fixed budget setting, any consistent algorithm ($p_t(\nu) \rightarrow 0$ as $t \rightarrow \infty$) satisfies:
-
-$$
-- \frac{1}{t} \log p_t(\nu) \leq \KL(\tau || \mu_1)
+Let $\nu$ be from the one-parameter exponential family of distributions such that $\nu_1$ can be parameterized by its mean, $\mu_1$, and the Kullback-Leibler divergence between distributions $\nu_1$ and $\nu_1'$ can be written as $\KL(\nu_1', \nu_1) = \KL(\mu_1', \mu_1)$.
+In the fixed budget setting, any consistent algorithm ($p_t(\nu) \rightarrow 0$ as $t \rightarrow \infty$) satisfies for $\mu_1' \rightarrow \tau$:
+
+$$
+- \frac{1}{t} \log p_t(\nu) \leq \KL(\mu_1' || \mu_1)
 $$
@@
 
-This is basically the Chernoff-Stein Lemma for the hypothesis test of two alternatives (compare chapter 11 in Cover and Thomas, 2006, or \autoref{theorem:ChernoffStein}).
+This is basically the Chernoff-Stein Lemma for the hypothesis test of two alternatives (compare chapter 11 in Cover and Thomas, 2006, or \autoref{theorem:ChernoffStein}), in which the optimal error exponent is based on the Kullback-Leibler divergence.
 We arrive at this result as the one-armed bandit does not require sequential sampling: The single arm receives all samples.
 $\mathbb{E}_{\nu'}[N_1(t)]$ is not a random variable but equals $T$.
+The single-armed bandit is a simple hypothesis test.
 
@@
 \begin{corollary}
+Consider the setting in \autoref{sec:Setup}.
 Let $\nu = (\nu_1, ..., \nu_K)$ be a $K$-armed thresholding bandit problem in which $\tau$ is the threshold fixed upfront.
-For $i \in \{1,...,K\}$, let $\nu_i$ be from the univariate exponential family of distributions such that $\nu_i$ can be parameterized by its mean, $\mu_i$, and the Kullback-Leibler divergence between distributions $\nu_i$ and $\nu_i'$ can be written as $\KL(\nu_i, \nu_i') = \KL(\mu_i, \mu_i')$.
-In the fixed budget setting, any consistent algorithm satisfies:
-
-$$
-\limsup_{t \rightarrow \infty} -\frac{1}{t} \log p_t(\nu) \leq \max_{a \in \{1,...,K\}} \KL(\tau || \mu_a)
+For $i \in \{1,...,K\}$, let $\nu_i$ be from the one-parameter exponential family of distributions such that $\nu_i$ can be parameterized by its mean, $\mu_i$, and the Kullback-Leibler divergence between distributions $\nu_i$ and $\nu_i'$ can be written as $\KL(\nu_i, \nu_i') = \KL(\mu_i, \mu_i')$.
+In the fixed budget setting, any consistent algorithm satisfies for $\mu_i' \rightarrow \tau$:
+
+$$
+\limsup_{t \rightarrow \infty} -\frac{1}{t} \log p_t(\nu) \leq \max_{i \in \{1,...,K\}} \KL(\mu_i' || \mu_i)
 $$
@@
 $$
-\kappa_{TBP}(\nu) = \inf_{A \text{ consistent}} \Big(\limsup_{t \rightarrow \infty} - \frac{1}{t} \log p_t(\nu)\Big)^{-1} \geq K \Big(\sum_{i=1}^{K} \KL(\tau||\mu_i)\Big)^{-1}
+\kappa_{TBP}(\nu) = \inf_{S \text{ consistent}} \Big(\limsup_{t \rightarrow \infty} - \frac{1}{t} \log p_t(\nu)\Big)^{-1} \geq K \Big(\sum_{i=1}^{K} \KL(\mu_i'||\mu_i)\Big)^{-1}
 $$
@@
 \begin{equation*}
-\sum_{a \in S^*_m} \frac{1}{\KL(\theta_a || \theta_{[m+1]})} + \sum_{a \notin S^*_m} \frac{1}{\KL(\theta_a || \theta_{[m]})} \leq \kappa_C(\nu) \leq 24 \min_{\theta \in [\theta_{[m+1]},\theta_{[m]}]} \sum_{a=1}^{K} \frac{1}{\KL^*(\theta_a || \theta)},
+\sum_{i \in S^*_m} \frac{1}{\KL(\mu_i || \mu_{[m+1]})} + \sum_{i \notin S^*_m} \frac{1}{\KL(\mu_i || \mu_{[m]})} \leq \kappa_C(\nu) \leq 24 \min_{\mu \in [\mu_{[m+1]},\mu_{[m]}]} \sum_{i=1}^{K} \frac{1}{\KL^*(\mu_i || \mu)},
 \end{equation*}
 
-where again we write with slight abuse of notation $\KL(\theta || \theta') = \KL(\nu_{\theta}|| \nu_{\theta'})$ for $(\theta, \theta') \in \Theta^2$ as the shorthand for the KL-divergence of two distributions from the exponential family parameterized by $\theta$ and $\theta'$ respectively.
-$\KL^*(\theta || \theta') = \KL(\theta^* || \theta)$ is the Chernoff information between the two distributions, where $\theta^*$ is chosen so that $\KL(\theta^* || \theta) = \KL(\theta^* || \theta')$.
+where again we write with slight abuse of notation $\KL(\nu_{\mu}|| \nu_{\mu'}) = \KL(\mu || \mu')$ as the shorthand for the KL-divergence of two distributions from the exponential family parameterized by $\mu$ and $\mu'$ respectively.
+$\KL^*(\mu || \mu') = \KL(\mu^* || \mu)$ is the Chernoff information between the two distributions, where $\mu^*$ is chosen so that $\KL(\mu^* || \mu) = \KL(\mu^* || \mu')$.
 
@@
 Instead of discussing the KL-LUCB algorithm for the fixed confidence top-$m$ problem, we shift our focus onto the fixed confidence best arm identification problem, as discussed in Garivier and Kaufmann (2016).
-The authors also derive a lower bound on the sample complexity using the Lemma \autoref{theorem:KaufmannEtAlLemma1}.
+The authors also derive a lower bound on the sample complexity using Lemma \autoref{theorem:KaufmannEtAlLemma1}.
 Furthermore, they propose a matching strategy for $K \geq 2$ arms.
@@
 (2016).
-In particular, Garivier and Kaufmann (2016) focus on distributions $\nu_{\theta}$ from the univariate canonical exponential family of distributions, which can be parameterized by their mean $\mu$, and thus can be written as $\nu_{\mu}$; as before, we simplify the notation of the KL-divergence for these distributions to $\KL(\nu || \nu') = \KL(\mu || \mu')$.
+In particular, Garivier and Kaufmann (2016) focus on distributions $\nu_{\theta}$ from the one-parameter canonical exponential family of distributions, which can be parameterized by their mean $\mu$, and thus can be written as $\nu_{\mu}$; as before, we simplify the notation of the KL-divergence for these distributions to $\KL(\nu || \nu') = \KL(\mu || \mu')$.
 
 Furthermore, if we let $\mathcal{S}$ to be a set of bandit models with $K$ distributions each, then each model is fully defined by a vector $\bm{\mu} = (\mu_1, \dots, \mu_K)$.
-Assume that every $\bm{\mu} \in \mathcal{S}$ has a unique maximum given by $a^*(\bm{\mu})$ such that $\mu_{a^*} > \max_{a \neq a^*(\bm{\mu})} \mu_a$.
+Assume that every $\bm{\mu} \in \mathcal{S}$ has a unique maximum given by $i^*(\bm{\mu})$ such that $\mu_{i^*} > \max_{i \neq i^*(\bm{\mu})} \mu_i$.
 In order to fix the confidence $1-\delta$, we specify the risk $\delta$.
-Similar to the top-$m$ case considered before, strategies corresponding to this risk are called $\delta$-PAC if for every $\bm{\mu} \in \mathcal{S}$, the strategy ends surely after a finite number of samples, $\mathbb{P}_{\bm{\mu}}(T_{\delta} < \infty) = 1$, and the error probability is at least as small as the fixed risk level, $\mathbb{P}_{\bm{\mu}}(\hat{a}_{T_{\delta}} \neq a^*) \leq \delta$.
+Similar to the top-$m$ case considered before, strategies corresponding to this risk are called $\delta$-PAC if for every $\bm{\mu} \in \mathcal{S}$, the strategy ends surely after a finite number of samples, $\mathbb{P}_{\bm{\mu}}(T_{\delta} < \infty) = 1$, and the error probability is at least as small as the fixed risk level, $\mathbb{P}_{\bm{\mu}}(\hat{i}_{T_{\delta}} \neq i^*) \leq \delta$.
 In order to derive the lower bound on the expected number of samples $\mathbb{E}[T]$ through a change in distributions, we introduce the set of alternative problems for which the optimal arm is different from $\bm{\mu}$:
@@
 \begin{equation*}
-\text{Alt}(\bm{\mu}) := \{\bm{\lambda} \in \mathcal{S}: a^*(\bm{\lambda}) \neq a^*(\bm{\mu})\},
+\text{Alt}(\bm{\mu}) := \{\bm{\lambda} \in \mathcal{S}: i^*(\bm{\lambda}) \neq i^*(\bm{\mu})\},
 \end{equation*}
@@
 Lastly, we have the set of probability distributions on the arms $\{1,...,K\}$: $\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}$.
-Each $w_i$ corresponds to the fraction of overall samples that arm $i$ receives.
+Each $w_i$ corresponds to the fraction of overall samples that arm $i$ receives (which are random variables similar to $T_i$ in \autoref{sec:UpperBoundProof}).
 We now state the lower bound:
@@
 \begin{equation*}
-\mathbb{E}_{\bm{\mu}} [T_{\delta}] \geq T^*(\bm{\mu}) \text{\em{d}}(\delta,1-\delta),
+\mathbb{E}_{\bm{\mu}} [T_{\delta}] \geq T^*(\bm{\mu}) d(\delta,1-\delta),
 \end{equation*}
@@
 \begin{equation} \label{eq:GarivierKaufmann_Theorem1_Game}
-T^*(\bm{\mu})^{-1} := \sup_{w \in \Sigma_K} \inf_{\bm{\lambda} \in \text{\em{Alt}}(\bm{\mu})} \left( \sum_{a=1}^K w_a \text{\em{KL}}(\mu_a|| \lambda_a)\right).
+T^*(\bm{\mu})^{-1} := \sup_{w \in \Sigma_K} \inf_{\bm{\lambda} \in \text{\em{Alt}}(\bm{\mu})} \left( \sum_{i=1}^K w_i \text{\em{KL}}(\mu_i|| \lambda_i)\right).
 \end{equation}
@@
 To proof Theorem \ref{theorem:GarivierKaufmannTheorem1}, we let $\delta \in (0,1)$, $\bm{\mu} \in \mathcal{S}$, and only consider $\delta$-PAC strategies.
-As before, $N_a(t)$ describes the random number of pulls of arm $a$ until time $t$, for all $t\geq 1$.
+As before, $T_i(t)$ describes the random number of pulls of arm $i$ until time $t$, for all $t\geq 1$.
 Again, Lemma \ref{theorem:KaufmannEtAlLemma1} states how the risk $\delta$ relates to the expected number of draws of each arm given two models which differ in their optimal arm.
@@
 \begin{equation*}
-\forall \lambda \in \mathcal{S}: a^*(\lambda) \neq a^*(\mu), \sum_{a=1}^K \KL(\mu_a,\lambda_a)\mathbb{E}_{\bm{\mu}}[N_a(T_{\delta})] \geq \d(\delta, 1- \delta).
+\forall \lambda \in \mathcal{S}: i^*(\lambda) \neq i^*(\mu), \sum_{i=1}^K \KL(\mu_i,\lambda_i)\mathbb{E}_{\bm{\mu}}[T_i(T_{\delta})] \geq d(\delta, 1- \delta).
 \end{equation*}
 
-As mentioned, we now do not consider a specific alternative for each arm, but instead look at the infimum over all the possible alternatives, and use the fact that $\mathbb{E}_{\bm{\mu}}[T_{\delta}] = \sum_{a=1}^K \mathbb{E}_{\bm{\mu}}[N_a(T_{\delta})]$:
+As mentioned, we now do not consider a specific alternative for each arm, but instead look at the infimum over all the possible alternatives, and use the fact that $\mathbb{E}_{\bm{\mu}}[T_{\delta}] = \sum_{i=1}^K \mathbb{E}_{\bm{\mu}}[T_i(T_{\delta})]$:
 
 \begin{align*}
-\der(\delta, 1-\delta) & \leq \inf_{\lambda \in \text{Alt}(\bm{\mu})} \mathbb{E}_{\bm{\mu}}[T_{\delta}] \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[T_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
-& = \mathbb{E}_{\bm{\mu}}[T_{\delta}] \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[T_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
-& \leq \mathbb{E}_{\bm{\mu}}[T_{\delta}] \sup_{w \in \Sigma_K} \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K w_a \KL(\mu_a, \lambda_a)\Big).
+\der(\delta, 1-\delta) & \leq \inf_{\lambda \in \text{Alt}(\bm{\mu})} \mathbb{E}_{\bm{\mu}}[T_{\delta}] \Big(\sum_{i=1}^K \frac{\mathbb{E}_{\bm{\mu}}[T_i]}{\mathbb{E}_{\mu}[T_{\delta}]} \KL(\mu_i, \lambda_i)\Big) \\
+& = \mathbb{E}_{\bm{\mu}}[T_{\delta}] \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{i=1}^K \frac{\mathbb{E}_{\bm{\mu}}[T_i]}{\mathbb{E}_{\mu}[T_{\delta}]} \KL(\mu_i, \lambda_i)\Big) \\
+& \leq \mathbb{E}_{\bm{\mu}}[T_{\delta}] \sup_{w \in \Sigma_K} \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{i=1}^K w_i \KL(\mu_i, \lambda_i)\Big).
 \end{align*}
 
-As stated in Garivier and Kaufmann (2016), the term $\frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[T_{\delta}]}$ gives the fraction of draws each arm receives.
+As stated in Garivier and Kaufmann (2016), the term $\frac{\mathbb{E}_{\bm{\mu}}[T_i]}{\mathbb{E}_{\mu}[T_{\delta}]}$ gives the fraction of draws each arm receives.
 This value, however, depends on the used algorithm.
-To make it hold for any $\delta$-PAC algorithm, it is replaced by the supremum over $\Sigma_K$, which is the distribution over these fractions for any $\mathcal{A}$, that is, for any $\delta$-PAC strategy.
-
-This lower bound can be interpreted as a minimax game^[See the presentation by Aurélien Garivier at COLT 2016: <https://youtu.be/eLyrrYqJlkE>], where the experimenter has to choose the share of samples he attributes to each arm in a way that is optimal given that nature will respond and choose the most difficult alternative model given his weights.
+To make it hold for any $\delta$-PAC algorithm, it is replaced by the supremum over $\Sigma_K$, which is the distribution over these fractions for any $\delta$-PAC strategy.
+
+This lower bound can be interpreted as a minimax game^[See the presentation by Aurélien Garivier at COLT 2016: <https://youtu.be/eLyrrYqJlkE>], where the experimenter has to choose the share of samples she attributes to each arm in a way that is optimal given that nature will respond and choose the most difficult alternative model given her weights.
 Thus, to make the lower bound practical, it is a matter of finding the optimal weights $w^*(\bm{\mu})$.
@@
 
-This is what happens when we look for proportions $w \in \Sigma_K$ that minimize the cost from a change in distributions, that is, the term $F(\bm{\mu}, \bm{w}) = \inf_{\bm{\lambda} \in \text{Alt}(\bm{\mu})} \Big(\sum_{a= 1}^K w_a \KL(\mu_a, \lambda_a)\Big)$.
-In the proof of Lemma 3 of Garivier and Kaufmann, it is shown that nature, selecting the alternative model $\bm{\lambda}$, will always pick an alternative model in which only a single arm $a$ is changed such that $\lambda_a > \lambda_1$ since
+This is what happens when we look for proportions $w \in \Sigma_K$ that minimize the cost from a change in distributions, that is, the term $F(\bm{\mu}, \bm{w}) = \inf_{\bm{\lambda} \in \text{Alt}(\bm{\mu})} \Big(\sum_{i= 1}^K w_i \KL(\mu_i, \lambda_i)\Big)$.
+In the proof of Lemma 3 of Garivier and Kaufmann, it is shown that nature, selecting the alternative model $\bm{\lambda}$, will always pick an alternative model in which only a single arm $i$ is changed such that $\lambda_i > \lambda_1$ since
 
 \begin{align*}
-T^*(\bm{\mu})^{-1} & = \sup_{w \in \Sigma_K} \min_{a \neq 1} \inf_{\bm{\lambda} \in \mathcal{S}: \lambda_a > \lambda_1} \sum_{a=1}^K w_a \KL(\mu_a, \lambda_a)  \\
-& = \sup_{w \in \Sigma_K} \min_{a \neq 1} \inf_{\bm{\lambda}: \lambda_a \geq \lambda_1} [w_1 \KL(\mu_1, \lambda_1)+w_a \KL(\mu_a, \lambda_a)]. \Alignyesnumber\label{eqn:ComplexityTrackStopStrategy}
+T^*(\bm{\mu})^{-1} & = \sup_{w \in \Sigma_K} \min_{i \neq 1} \inf_{\bm{\lambda} \in \mathcal{S}: \lambda_i > \lambda_1} \sum_{i=1}^K w_i \KL(\mu_i, \lambda_i)  \\
+& = \sup_{w \in \Sigma_K} \min_{i \neq 1} \inf_{\bm{\lambda}: \lambda_i \geq \lambda_1} [w_1 \KL(\mu_1, \lambda_1)+w_i \KL(\mu_i, \lambda_i)]. \Alignyesnumber\label{eqn:ComplexityTrackStopStrategy}
 \end{align*}
 
-Consequently, $w$ will be chosen so as to minimize $T^*(\bm{\mu})$ no matter which arm $a$ was picked.
-It is a minimax game, so the ideal solution is to keep for each arm $a \neq 1$ the term $w_1 \KL(\mu_1, \lambda_1) + w_a \KL(\mu_a, \lambda_a)$ at the same level.
+Consequently, $w$ will be chosen so as to minimize $T^*(\bm{\mu})$ no matter which arm $i$ is picked.
+It is a minimax game, so the ideal solution is to keep for each arm $i \neq 1$ the term $w_1 \KL(\mu_1, \lambda_1) + w_i \KL(\mu_i, \lambda_i)$ at the same level.
 Garivier and Kaufmann show that this can be written in terms of the Jenson-Shannon divergence, defined for every $\alpha \in [0,1]$ as
@@
 \begin{equation*}
-w^*(\bm{\mu}) = \arg \max_{w \in \Sigma_K} \min_{a \neq 1} (w_1 + w_a) I_{\frac{w_1}{w_1+w_a}}(\mu_1, \mu_a)
+w^*(\bm{\mu}) = \arg \max_{w \in \Sigma_K} \min_{i \neq 1} (w_1 + w_i) I_{\frac{w_1}{w_1+w_i}}(\mu_1, \mu_i)
 \end{equation*}
 
-which let's us furthermore conclude that these quantities are equal for all $a,b \in \{2,\dots, K\}$ with
+which let's us furthermore conclude that these quantities are equal for all $i,j \in \{2,\dots, K\}$ with
 \begin{equation*}
-(w_1^* + w_a^*) I_{\frac{w_1^*}{w_1^*+w_a^*}}(\mu_1, \mu_a) = (w_1^* + w_b^*) I_{\frac{w_1^*}{w_1^*+w_b^*}}(\mu_1, \mu_b),
+(w_1^* + w_i^*) I_{\frac{w_1^*}{w_1^*+w_i^*}}(\mu_1, \mu_i) = (w_1^* + w_j^*) I_{\frac{w_1^*}{w_1^*+w_j^*}}(\mu_1, \mu_j),
 \end{equation*}
@@
 
-And so by assuring the reader that there are ways to compute $w_a^*$ and $T^*$ given $\bm{\mu}$ (see chapter 2.2 in Garivier and Kaufmann (2016)), we can now introduce the *Track-and-Stop* strategy given in Garivier and Kaufmann (2016) that is able to match the lower bound.
-The main idea of the *Track-and-Stop* algorithm is now to keep track of the optimal shares for each arm by equalizing the error probabilies for each arm.
+And so by assuring the reader that there are ways to compute $w_i^*$ and $T^*$ given $\bm{\mu}$ (see chapter 2.2 in Garivier and Kaufmann (2016)), we can now introduce the *Track-and-Stop* strategy given in Garivier and Kaufmann (2016) that is able to match the lower bound.
+The main idea of the *Track-and-Stop* algorithm is to keep track of the optimal shares for each arm by equalizing the error probabilies for each arm.
 
@@
 And so wrong estimates, which naturally occur most easily in the beginning when not many samples have been pulled, are prone to lead to wrong weights.
-Thus, if a wrong estimate $\hat{\mu}_a$ for arm $a$ leads to a small weight $w_a$, then after a few more rounds neither the estimate nor the weight will be correct.
+Thus, if a wrong estimate $\hat{\mu}_i$ for arm $i$ leads to a small weight $w_i$, then after a few more rounds neither the estimate nor the weight will be correct.
 Thus, Kaufmann and Garivier conclude that "a naive plug-in sampling rule sometimes fails".
@@
 A very intuitive solution to this problem is proposed in Lemma 8 of Garivier and Kaufmann (2016) with the $D-Tracking$ rule.
-Whenever some arm has received a very small number of pulls $N_a(t)$ given the number of iterations $t$ so far, and the number of arms $K$ that have to share the samples, pull the arm that has received the smallest amount of samples so far.
-Else, pull the arm whose number of pulls so far $N_a(t)$ is the farthest away from what its optimal share $t\cdot w^*_a(\hat{\bm{\mu}}(t))$ would be.
+Whenever some arm has received a very small number of pulls $T_i(t)$ given the number of iterations $t$ so far, and the number of arms $K$ that have to share the samples, pull the arm that has received the smallest amount of samples so far.
+Else, pull the arm whose number of pulls so far $T_i(t)$ is the farthest away from what its optimal share $t\cdot w^*_i(\hat{\bm{\mu}}(t))$ would be.
 Given this sampling rule, the authors can show in their Proposition 9 that the empirical proportion of draws converges in probability to the optimal weights given the true means.
@@
 Given that the sampling rule is independent of this stopping rule, the rule boils down to a statistical test at every iteration and thus is a sequential test based on the current estimate of $\hat{\bm{\mu}}$.
-Chernoff's Stopping Rule proposed in Garivier and Kaufmann (2016) calculates for each arm $a\in \{1,...K\}$ the Generalized Likelihood Ratio statistic with every arm $b \in \mathcal{A}^{\setminus a}$, which for $\hat{\mu}_a(t) \geq \hat{\mu}_b(t)$ can be written as
+Chernoff's Stopping Rule proposed in Garivier and Kaufmann (2016) calculates for each arm $i\in \mathbb{A} = \{1,...K\}$ the Generalized Likelihood Ratio statistic with every arm $j \in \mathbb{A}^{\setminus i}$, which for $\hat{\mu}_i(t) \geq \hat{\mu}_j(t)$ can be written as
 
 \begin{equation*}
-Z_{a,b}(t) = - Z_{b,a} = N_a(t) \KL(\hat{\mu}_a(t) || \hat{\mu}_{a,b}(t)) + N_b(t) \KL(\hat{\mu}_{b}(t) || \hat{\mu}_{a,b}(t)),
+Z_{i,j}(t) = - Z_{j,i} = T_i(t) \KL(\hat{\mu}_i(t) || \hat{\mu}_{i,j}(t)) + T_j(t) \KL(\hat{\mu}_{j}(t) || \hat{\mu}_{i,j}(t)),
 \end{equation*}
@@
 \begin{equation*}
-\hat{\mu}_{a,b}(t) := \frac{N_a(t)}{N_a(t) + N_b(t)}\hat{\mu}_a(t) + \frac{N_b(t)}{N_a(t) + N_b(t)}\hat{\mu}_b(t).
+\hat{\mu}_{i,j}(t) := \frac{T_i(t)}{T_i(t) + T_j(t)}\hat{\mu}_i(t) + \frac{T_j(t)}{T_i(t) + T_j(t)}\hat{\mu}_j(t).
 \end{equation*}
 
-Consequently, a sensible idea for a stopping rule would be that there has to be an arm $a \in \{1,...,K\}$ for which $Z_{a,b} \geq 0 \text{ for all }  b \in \{1,...,K\}^{\setminus a}$ (which is always fulfilled if there is a uniquely best arm), and we demand that for this arm the smallest of the $(K-1)$ test statistics has to be larger than an exploration threshold $\beta(t, \delta)$.
+Consequently, a sensible idea for a stopping rule would be that there has to be an arm $i \in \{1,...,K\}$ for which $Z_{i,j} \geq 0 \text{ for all }  j \in \{1,...,K\}^{\setminus i}$ (which is always fulfilled if there is a uniquely best arm), and we demand that for this arm the smallest of the $(K-1)$ test statistics has to be larger than an exploration threshold $\beta(t, \delta)$.
 The final sampling round $T_{\delta}$ of the algorithm is given by:
@@
 \begin{equation*}
-T_{\delta} = \inf \{t \in \mathbb{N}: \exists a \in \mathcal{A}, \forall b\in \mathcal{A}^{\setminus a}, Z_{a,b}(t) > \beta(t, \delta)\}
+T_{\delta} = \inf \{t \in \mathbb{T}: \exists i \in \mathbb{A}, \forall j\in \mathbb{A}^{\setminus i}, Z_{i,j}(t) > \beta(t, \delta)\}
 \end{equation*}
@@
 Lemma \ref{theorem:KaufmannEtAlLemma1} is able to measure the "transportation cost" (see Garivier and Kaufmann, 2016) of moving from one distribution to another one in terms of Kullback-Leibler divergence.
-It is a bound on the expected likelihood ratio term that appears when changes in distribution are applied.
-
-In the case of the fixed budget top-$m$ arm identification problem, we have seen that the derivation of a lower bound on the complexity term is mostly limited by the difficulty of defining an alternative problem $\nu'$ to $\nu$ that fits into the Lemma \ref{theorem:KaufmannEtAlLemma1}.
+It is the bound on the expected likelihood ratio term that appears when changes in distribution are applied.
+
+In the case of the fixed budget top-$m$ arm identification problem, we see that the derivation of a lower bound on the complexity term is mostly limited by the difficulty of defining an alternative problem $\nu'$ to $\nu$ that fits the Lemma \ref{theorem:KaufmannEtAlLemma1}.
 But given the intuition that in top-$m$ problems the $m$-th best arm and the $(m+1)$-th best arm define an implied threshold between the two groups of arms, we were able to apply the ideas of Kaufmann et al.
@@
 This is not the case for the Track-and-Stop strategy introduced in Garivier and Kaufmann, and neither for our Simple Likelihood Ratio strategy introduced in \autoref{sec:1DSLR}.
-In \autoref{sec:Simulation2}, we show empirically that the performance of the Simple Likelihood Ratio strategy can be further improved by naively adding the D-Tracking rule to it.
+In \autoref{sec:Simulation2}, we show empirically that the performance of the Simple Likelihood Ratio strategy can be further improved by adding the D-Tracking rule.
+
+\newpage
 
@@
 
-In \autoref{chap:ThresholdingBanditProblem} we have introduced the thresholding bandit problem as proposed in Locatelli et al.
+In \autoref{chap:ThresholdingBanditProblem} we introduced the thresholding bandit problem as proposed in Locatelli et al.
 (2016) alongside the APT algorithm.
-We have seen that the upper bound on the APT algorithm matches the lower bound for the thresholding bandit problem given in Locatelli et al.
+We saw that the upper bound for the APT algorithm matches the lower bound for the thresholding bandit problem given in Locatelli et al.
 (2016).
-The algorithm also exhibits favorable characteristics such that its upper bound holds at any stopping time, and that it does not require any parameter to be known upfront.
-However, we have seen that the index and the complexity term $H$ employed by the APT algorithm are the most effective for $R$-sub-Gaussian distributions.
+The algorithm also exhibits favorable characteristics such as its upper bound holding at any stopping time, and that it does not require any parameter to be tuned upfront.
+However, we have seen that the index $B^{APT}$ and the complexity term $H$ employed by the APT algorithm are the most effective for $R$-sub-Gaussian distributions.
 Both are related to the KL-divergence between two Gaussian distributions of equal variance.
-Given that this sub-Gaussian approximation can be poor in certain cases, we motivated the use of information theoretic measures in an algorithm's index (compare \autoref{sec:DiscussionLocatelli}).
-
-Another goal can be to compare the distributions with the threshold based not only on the empirical mean -- as done by the APT algorithm.
-A logical extension is for example the empirical variance.
-After all arms do not necessarily have the same variance, even if they are sub-Gaussian.
+Given that this sub-Gaussian approximation can be poor in certain cases, we motivated information theoretic measures in an algorithm's index (compare \autoref{sec:DiscussionLocatelli}).
+
+Information theoretic measures are one way of taking not only the sample mean into account to estimate differences between distributions -- as done by the APT algorithm.
+Another logical extension is to consider higher moments of a distribution, like its variance.
+After all, arms do not necessarily have the same variance, even if they are sub-Gaussian (two arms might be $R_1$-sub-Gaussian and $R_2$-sub-Gaussian).
 And given two arms for which we estimate the same mean, we would prefer to draw more samples from the arm with the larger variance.
-
-In the case of Gaussian distributions with varying variances, for example, it makes sense to take the variance into account; after all, given two Gaussians with equal mean, intuitively we would prefer to get a sample from the distribution of larger variance.
+The simplest example of this are two Normal distributions with different variances.
 
@@
 (2017).
-We then introduce a new algorithm based on the concept of likelihood ratios in \autoref{sec:LikelihoodRatioForExponentialFamily}.
+We then go back to the information theoretic ideas and introduce a new algorithm based on the concept of likelihood ratios in \autoref{sec:LikelihoodRatioForExponentialFamily}.
 Finally, we compare the performance of different algorithms based on simulations and real world data sets in \autoref{chap:Experiments}.
@@
 (2017) propose the Augmented-UCB (AugUCB) algorithm based on variance estimates for the thresholding bandit problem.
-The setting they consider is thus very similar to the setting in Locatelli et al.
+The setting they consider is very similar to the setting in Locatelli et al.
 (2016).
@@
 (2016) assume $R$-sub-Gaussian reward distributions, Mukherjee et al.
-(2017) assume rewards to be bounded in $[0,1]$, which makes the AugUCB applicable to less distributions.
+(2017) assume rewards to be bounded in $[0,1]$, which makes the AugUCB applicable to fewer distributions.
 The AugUCB algorithm itself differs significantly from the APT algorithm.
-The two main ideas it employs are first, upper confidence bounds based on the Bernstein inequality and empirical variance estimates to compute the index based on which an arm is chosen at every round.
-Second, if an arm estimate is "far enough away" from the threshold as measured by the confidence bounds, it will be "eliminated", and no longer be pulled until the end of the budget.
-Both ideas are based not only on the empirical mean estimate $\mu_i(t)$, but also on a term $s_i$ that is increasing linearly in the estimated standard deviation.
-While the APT algorithm plays the arm minimizing the quantity $B_i^{APT}(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t) = \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau| + \epsilon)$, AugUCB plays the arm minimizing the quantity $\hat{\Delta}_i(t) - 2s_i$, where $s_i$ is based on the variance estimate $\hat{v}_i$, and an exploration $\psi_m$ term linear in $T$, as well as an elimination parameter $\rho$ (compare Algorithm 1 in Mukherjee et al., 2017):
+The two main ideas it employs are, first, upper confidence bounds based on the Bernstein inequality and empirical variance estimates to compute the index based on which an arm is chosen at every round.
+Second, if an arm estimate is "far enough" away from the threshold as measured by the confidence bounds, it will be eliminated, that is, no longer be pulled until the end of the budget.
+Both ideas are based not only on the empirical mean estimate $\hat{\mu}_i(t)$, but also on a term $s_i$ that is increasing linearly in the estimated standard deviation.
+While the APT algorithm plays the arm minimizing the quantity $\sqrt{T_i(t)} \hat{\Delta}_i(t)$, AugUCB plays the arm minimizing the quantity $\hat{\Delta}_i(t) - 2s_i$, where $s_i$ is based on the variance estimate $\hat{v}_i$, and an exploration term $\psi_m$ linear in $T$, as well as an elimination parameter $\rho$ (compare Algorithm 1 in Mukherjee et al., 2017):
 
@@
 (2016).
-Essentially, every arm's complexity contribution is additionally scaled by a term increasing in the arm's variance (see also the graph comparing the complexity terms of APT, AugUCB, and EVT algorithms below).
+Essentially, every arm's complexity contribution is additionally scaled by a term increasing in the arm's variance (see also Figure 3 below).
 
@@
 This exploration is regulated by the combination of the variance estimate $\hat{v}_i$ and the exploration factor $\psi_m$ in the case of the AugUCB algorithm.
-The terms ensure that certain arms are no longer pulled when the algorithm is sufficiently confident in the location of true mean.
-Indeed, the AugUCB algorithm goes a little further than the APT algorithm in that it eliminates arms (no longer considers them in sampling) when a separation condition is estimated to hold.
-The same separation condition of estimated mean away from the threshold is used in the authors' upper bound proof and is reminiscient of the separation condition used in Locatelli et al.'s (2016) upper bound proof.
+The terms ensure that certain arms are no longer pulled when the algorithm is sufficiently confident in the location of the true mean.
+Indeed, the AugUCB algorithm goes a little further than the APT algorithm in that it stops to sample arms when a separation condition (mean separated from threshold) is estimated to hold.
+The same separation condition is used in the authors' upper bound proof and is reminiscient of the separation condition used in the proof of the upper bound in Locatelli et al.'s (2016) (compare \autoref{sec:CheckSeparationCondition}).
 
 Therefore, when using a very similar favorable event in the proof of their upper bound, Mukherjee et al.
-(2017) have to bound the probability that an an arm is not removed from the active set after the a certain number of rounds -- even though the arm is above (respectively below) the threshold.
-If this probability is low, then the algorithm is able to be certain about an arm's true mean by employing variance estimates.
-In comparison, Locatelli et al (2016) used bounds on on how often arms are drawn ($T_i$) to give a bound on the probability of the favorable event.
+(2017) have to bound the probability that an arm is not removed from the active set after a certain number of rounds -- even though the arm is above (respectively below) the threshold.
+If this probability is small, then the algorithm is able to be confident in an arm's true mean by employing variance estimates.
 In order to derive the bound, Mukherjee et al.
@@
 (2017) have to assume that the distributions have rewards bounded in $[0,1]$ in order to derive the bound on the probability that an arm has not been eliminated correctly in round $T_i$.
-Else it would not be possible to upper bound the $s_i$ term by $\Delta_i/4$ as Mukherjee et al.
-do in their proof.
 Thus, the distributions for which their upper bound holds are a subset of the $R$-sub-Gaussian distributions considered in Locatelli et al.
 (2016).
-However, while the authors demand in their setting that the rewards are bounded in $[0,1]$, it seems that the upper bound only requires the arms' variances to be bounded in $[0,1]$ such that $\hat{v}_i \in [0,1]$.
-Thus, the upper bound should hold in particular for Gaussian distributions with variance $\sigma^2 \in [0,1]$.
-Consequently, the simulations by Mukherjee et al.
-are performed on Gaussian arms with variance smaller than one.
+It would otherwise not be possible to upper bound the $s_i$ term by $\Delta_i/4$ as Mukherjee et al.
+do in their proof: With bounded rewards, the arms' variances are also bounded in $[0,1]$ such that $\hat{v}_i \in [0,1]$.
+Yet, the simulations by Mukherjee et al.
+are performed on Gaussian arms with variance smaller than one, which at least makes empirical variances smaller 1 likely.
 
@@
 (2017) for the notation.
-Then it becomes clear that the left part of the RHS gives the probability that the mean estimate is out of wack, while the right term gives the probability that the variance is overestimated.
+Then it becomes clear that the left part of the RHS gives the probability that the mean estimate is poor, while the right term gives the probability that the variance is overestimated.
 The first term is bounded by the Bernstein inequality.
@@
 There, the expected number of pulls of a suboptimal arm is bounded.
-Compare for example chapter 3.1 in Kaufmann, Korda and Munos (2012), in which the authors decompose the expected number of draws of an suboptimal arm into the probability that the optimal arm's mean is underestimated, and the probability that the upper confidence bound of the suboptimal arm is still very large.
+Compare for example chapter 3.1 in Kaufmann et al.
+(2012b), in which the expected number of draws of an suboptimal arm is decomposed into the probability that the optimal arm's mean is underestimated, and the probability that the upper confidence bound of the suboptimal arm is still very large.
 To give bounds for UCB algorithms, certain convergence rates are shown for these two probabilities.
@@
 
-Another algorithm for the thresholding bandit problem employing empirical variance estimates is introduced in Zhong et al.
+A second algorithm for the thresholding bandit problem employing empirical variance estimates is introduced in Zhong et al.
 (2017).
-Indeed, the authors discuss several variations of their algorithm which extend their central idea to applications in which several samples need to be pulled in a parallel and asynchronous fashion.
-An standard example known from the multi-armed bandit literature (see for example Li et al.
-(2010)) is a website for which different versions are served to visitors and each version is an arm in the bandit setting.
-If the feedback that is observed by the algorithm is whether or not a user makes a purchase, then it is likely that a new user arrives before the feedback for the previous user has been observed.
-The algorithm has to pull the next arm before the feedback of the previous arm has been observed.
-With their variants the authors approach this problem of having to take asynchronous and parallel actions.
-But their algorithm can also be reduced to a simpler version that can be compared directly with the problem described in Locatelli et al.
-(2016) where the feedback lag is assumed to be zero.
-
-This simpler version is the parameter-free version of their Empirical Variance Guided Algorithm (EVT$_{pf}$).
+While they propose different algorithms for different setting of the thresholding bandit problem, we focus here on their strategy that can be compared directly with the problem described in Locatelli et al.
+(2016).
+
+This strategy is the parameter-free version of their Empirical Variance Guided Algorithm (EVT$_{pf}$).
 The EVT$_{pf}$ algorithm is an extension of the APT algorithm that takes the empirical variance of the arms into account and deduces an upper bound through empirical Bernstein bounds in a proof following the model of the one described in Locatelli et al.
-(2016).
-
-In order to describe their algorithm, we adapt a formulation used in Zhong et al.
-(2017) to describe the index used by the algorithms in a more general fashion.
-Write the index $B_i(t+1)$ of arm $i$ at round $t$ as previously as
+(2016) (compare \autoref{sec:UpperBoundProof}).
+
+In order to describe $EVT_{pf}$, we adapt a formulation used in Zhong et al.
+(2017) to describe the index used by the algorithms in a more generally.
+Write the index $B_i(t+1)$ of arm $i$ at round $t$ as
 
@@
 
-where $D_i(t)$ is some measure of the distance between the mean $\mu_i$ or the distribution $\nu_i$ of arm $i$ from the threshold $\tau$, while $S_i(t)$ is some confidence value measuring how confident we can be in $.
+where $D_i(t)$ is some measure of the distance between the mean $\mu_i$ or the distribution $\nu_i$ of arm $i$ from the threshold $\tau$, while $S_i(t)$ is some confidence value measuring how confident we can be in $D_i(t)$.
 Thus, for the APT algorithm, if we let $\epsilon = 0$ as in Zhong et al.
@@
 $$
-D_i^{APT}(t) = \hat{\Delta}_i(t) = |\hat{\mu}_i(t) - \tau| \quad \text{and} \quad S_i^{APT}(t) = \sqrt{T_i(t)}
-$$
-
-We see that $D_i(t)$ is the probably most straightforward distance between the sample mean and the threshold, while $S_i(t)$ increases over time, as we become more confident in our sample mean, and thus ensures that we do not continue pulling the same arm forever.
-
+D_i^{APT}(t) = \hat{\Delta}_i(t) = |\hat{\mu}_i(t) - \tau| \quad \text{and} \quad S_i^{APT}(t) = \sqrt{T_i(t)}.
+$$
+
+We see that $D_i(t)$ is the probably most straightforward distance between the sample mean and the threshold, while $S_i(t)$ increases over time, as we become more confident in our sample mean, and thus ensures that we do not pull the same arm forever.
 Based on this, we can now easily compare APT to EVT$_{pf}$ for which the index can be written as:
@@
 We see that both algorithms employ the same confidence term.
-The empirical variance describes the shape of the distribution and thus is a measure of how far the distribution (in contrast to just the mean) is away from the threshold.
+The empirical variance describes the shape of the distribution and thus is a measure of how far the distribution is away from the threshold.
 It consequently makes sense to have it appear in $D_i^{EVT}$.
-And in contrast to the APT algorithm, the EVT$_{pf}$ algorithm consequently takes more information about the arms into account than just their mean.
-As mentioned previously, this should especially be valuable whenever arms have indeed different variances.
-Similar (very roughly) to how the Kullback-Leibler divergence measures distances between distributions, the $D_i^{EVT}$ including the empirical variance serves as a crude measure of distance between threshold and distribution.
-We note that for a Bernoulli distributed random variable, $D_i^{EVT}$ is always decreasing as the mean approaches the threshold (compare the figure 2).
+And in contrast to the APT algorithm, the EVT$_{pf}$ algorithm takes more information about the arms into account than just their mean.
+As mentioned previously, this should especially be valuable whenever arms have different variances.
+Roughly similar to how the Kullback-Leibler divergence measures distances between distributions, $D_i^{EVT}$ including the empirical variance serves as a crude measure of distance between threshold and distribution.
+We note that for a Bernoulli distributed random variable, $D_i^{EVT}$ is always decreasing as the mean approaches the threshold (compare figure 2).
 Similar should hold in general for bounded variables as the variance and the mean are linked by the distance of the mean to the bound of the support (in contrast to, for example, a normal distributed random variable where a change in the mean does not correspond to a change in the variance).
 This is important as the bounds of the EVT$_{pf}$ algorithm only hold for random variables bounded in $[0,1]$.
-In contrast to the AugUCB, this restriction is not just on the variance of the arm but explicitly on the reward itself in the current version that builds on empirical Bernstein bounds as shown in Maurer and Pontil (2009).
+Thus, it is limited to the same set of distributions as the AugUCB algorithm.
 
@@
   geom_line() +
-  labs(title = "Comparison of Distance Measures by Algorithm",
+  labs(#title = "Comparison of Distance Measures by Algorithm",
        subtitle = "For Bernoulli arms and a threshold at 0.1.",
@@
 
-Then one can state the following theorem.
+Then one can state the following theorem with notation as in \autoref{sec:Setup}.
 
@@
 \begin{equation*}
-\mathbb{E}[L] \leq TK \exp\Big(-C\frac{T}{H^{\text{EVT}_{pf}}}\Big),
+\mathbb{E}[\mathcal{L}[T]] \leq TK \exp\Big(-C\frac{T}{H^{\text{EVT}_{pf}}}\Big),
 \end{equation*}
@@
 
-The authors approach the proof very similarly as Locatelli et al.
+The authors approach the proof very similar as Locatelli et al.
 (2016) in the proof of their lower bound.
 They define favorable events that hold with large probability, and ensure that the same separation condition as in Locatelli et al.
-holds for them given that each arm is pulled sufficiently often.
+holds given that each arm is pulled sufficiently often.
 Additionally to a favorable event that bounds the deviation between sample mean and population mean, they define a second event on which the sample standard deviation is close to the population standard deviation.
@@
 
-Given a lower bound adapted to the new complexity $H^{\text{EVT}_{pf}}$, the Zhong et al.
+Given a lower bound adapted to the new complexity $H^{\text{EVT}_{pf}}$, Zhong et al.
 (2017) show that the EVT$_{pf}$ algorithm is optimal in that its upper bound matches the lower bound.
@@
 Each experiment compares 100 arms with variances picked at random from a range of possible variances.
-Over three experiments, the range of variances is varied from small to large, where the authors expect their algorithm to show the largest advantage compared to APT on the problem with small variances.
-Interestingly, they report the largest advantage of their variance based algorithms in comparison to APT when the variances are very small; given they only consider problems bounded on a support of $[0,1]$, $\sigma_i \ll 1$.
+Over three experiments, the range of variances is varied from small to large.
+They report the largest advantage of their variance based algorithms in comparison to APT when the variances are very small; given they only consider problems bounded on a support of $[0,1]$, $\sigma_i \ll 1$.
 In this case the problem complexity $H^{\text{EVT}_{pf}}$ can be much smaller than $H^{APT}$ -- the EVT$_{pf}$ algorithm profits more from distributions that are simple to estimate in terms of their variance than the APT algorithm does.
 
-When comparing the two complexities for example for Bernoulli random variables against some fixed threshold, we see that the smaller complexity of the EVT$_{pf}$ algorithm implies in particular that EVT$_{pf}$ could be able to cope with distributions of parameter $\mu$ close to $\tau$ much better than APT (compare figure 3).
+When comparing the two complexities for Bernoulli random variables against a threshold, we see that the smaller complexity of the EVT$_{pf}$ algorithm implies in particular that EVT$_{pf}$ could be able to cope with distributions of parameter $\mu$ close to $\tau$ much better than APT (compare Figure 3).
 
@@
 We now present a new sequential sampling algorithm for the fixed budget thresholding bandit problem that builds on the idea of the likelihood ratio statistic for hypothesis tests.
-We first shortly describe the general idea of likelihood ratio based tests, to then introduce this new algorithm for the thresholding bandit problem, which we call Simple Likelihood Ratio (SLR) algorithm.
+We first describe the general idea of likelihood ratio based tests shortly, to then introduce the new algorithm for the thresholding bandit problem, which we call Simple Likelihood Ratio (SLR) algorithm.
 
@@
 
-In a standard parametric testing problem, we have drawn an iid sample $x = (x_1, ..., x_T)$, where each $x_i$ is a realization from the random variable $X_i$.
-We assume that $X_i$ follows some probability distribution $Q(\theta)$ paramaterized by a vector $\theta$.
+In a standard parametric testing problem, we have an i.i.d.
+sample $\bm{x} = (x_1, ..., x_T)$, where each $x_s$ is a realization from the random variable $X$.
+We assume that $X$ follows some probability distribution $Q(\theta)$ paramaterized by a vector $\theta$.
 Let $q(x;\theta)$ be the density function corresponding to the distribution.
@@
 
-In order to assess whether the $H_0$ hypothesis can be rejected, one computes the likelihood $L(x|\theta)$ of the observed sample under both parameterizations: $L_{H_0} = L(x|\theta = \theta_{H_0}) = \prod_{i=1}^T q(x_i|\theta_{H_0})$ and $L_{H_1} = L(x|\theta = \theta_{H_1}) = \prod_{s=1}^T q(x_s|\theta_{H_1})$.
+In order to assess whether the $H_0$ hypothesis can be rejected, we compute the likelihood $L(x|\theta)$ of the observed sample under both parameterizations: $L_{H_0} = L(x|\theta = \theta_{H_0}) = \prod_{s=1}^T q(x_s|\theta_{H_0})$ and $L_{H_1} = L(x|\theta = \theta_{H_1}) = \prod_{s=1}^T q(x_s|\theta_{H_1})$.
 The likelihood ratio test statistic is then given as
@@
 
-The intuition behind the test of course being that, if the true parameterization is $H_1$ and not $H_0$, then the likelihood $L_{T,H_1}$ should be larger than $L_{T,H_0}$.
-A small enough likelihood ratio would thus lead us to a rejection of the null hypothesis, while a large likelihood ratio is evidence in favor of the null hypothesis.
+The intuition behind the test is that, if the true parameterization is $H_1$ and not $H_0$, then the likelihood $L_{T,H_1}$ should be larger than $L_{T,H_0}$.
+A small enough likelihood ratio would thus lead us to a rejection of the null hypothesis, while a large likelihood ratio is evidence in favor of it.
 
@@
 
-where $\hat{\theta}$ is the maximum likelihood estimate of the parameter $\theta$ given the sample $x$.
-If we hold the $H_0$ hypothesis fixed and set $\theta_{H_1} = \hat{\theta}$ as often done in praxis, then with $\KL(Q(\hat{\theta})||Q(\hat{\theta})) = 0$:
-
-$$
--\log(LR_T(\theta_{H_0}|| \theta_{H_1})) = -\log(LR_T(\theta_{H_0}|| \hat{\theta})) = \KL(Q(\hat{\theta}||Q(\theta_{H_0}))
-$$
-
-Furthermore, we have for any distributions $Q_{H_0}$ and $Q_{H_1}$ for a sample $x$ sampled from the $H_0$ distribution, that
-
-$$
-\frac{1}{n} \log(LR_T(\theta_{H_0}||\theta_{H_1})) \rightarrow \KL(Q(\theta_{H_0})||Q(\theta_{H_1})) \quad \text{in probability},
+where $\hat{\theta}$ is the maximum likelihood estimate of the parameter $\theta$ given the sample $\bm{x}$.
+If we hold the $H_0$ hypothesis fixed and set $\theta_{H_1} = \hat{\theta}$, then with $\KL(Q(\hat{\theta})||Q(\hat{\theta})) = 0$:
+
+$$
+-\log(LR_T(\theta_{H_0}|| \theta_{H_1})) = -\log(LR_T(\theta_{H_0}|| \hat{\theta})) = T\KL(Q(\hat{\theta}||Q(\theta_{H_0}))
+$$
+
+Furthermore, we have for any distributions $Q_{H_0}$ and $Q_{H_1}$ for a sample $\bm{x}$ sampled from the $H_0$ distribution, that
+
+$$
+\frac{1}{T} \log(LR_T(\theta_{H_0}||\theta_{H_1})) \rightarrow \KL(Q(\theta_{H_0})||Q(\theta_{H_1})) \quad \text{in probability},
 $$
@@
 
+Indeed, our Corollary \autoref{corollary:LB1TBP} for the one-armed thresholding bandit problem corresponds directly to this result, and shows that the thresholding bandit can be viewed as a sequential testing of separate hypotheses.
+
 ### Likelihood Ratio as Index in Sequential Sampling
 
-We now employ the concept of the likelihood-ratio test for a new sequential sampling strategy for the thresholding bandit problem.
+We now employ the concept of the likelihood-ratio test to a new sequential sampling strategy for the thresholding bandit problem.
 In contrast to the cumulative regret problem or the best arm identification problem, the thresholding bandit problem offers a natural $H_0$ hypothesis for the arms' distributions: the threshold $\tau$.
@@
 The likelihood ratio then quantifies how "significant" of a difference there is between the threshold $\tau$ and the current sample mean $\hat{\mu}_i(t)$ of an arm, assuming distributions for which the maximum likelihood estimate of the mean is given by the empirical mean.
-In these cases, the likelihood ratio will be smaller than 1 and decrease in sample size even if the threshold and sample mean are constant.
-
-Due to these characteristics, the likelihood ratio can serve as a natural index for sampling strategies.
-Consider the setting described in \autoref{sec:Setup} and \autoref{sec:TheAPTAlgorithm} though without assuming $R$-sub-Gaussian distributions.
-Consider $B_i^{APT}$ and compare it to
+The likelihood ratio will be smaller than 1 and decrease in sample size even if the threshold and sample mean are constant.
+
+These characteristics make the likelihood ratio a natural index for adaptive sampling strategies (compare also Chernoff, 1958; Garivier and Kaufmann, 2016).
+Consider the setting described in \autoref{sec:Setup} and \autoref{sec:TheAPTAlgorithm}, and write as index:
 
@@
 
-We have $B_i(t) \leq 1$, $t \uparrow \rightarrow B_i(t) \downarrow$, and $|\hat{\mu}_i(t) - \tau| \uparrow \rightarrow B_i(t) \downarrow$.
-Consequently, by choosing the arm that maximizes $B_i(t)$, we choose an arm for which we either have not collected many samples, or for which the sample mean is close to the threshold $\tau$.
+We have $B_i^{LR}(t) \leq 1$, $t \uparrow \rightarrow B_i^{LR}(t) \downarrow$, and $|\hat{\mu}_i(t) - \tau| \uparrow \rightarrow B_i^{LR}(t) \downarrow$.
+Consequently, by choosing the arm that maximizes $B_i^{LR}(t)$, we choose an arm for which we either have not collected many samples, or for which the sample mean is close to the threshold $\tau$.
 In this sense, a strategy based on the likelihood ratio is reminiscient of the index employed by the APT algorithm.
-Indeed, assuming the samples are normally distributed with the same variance for the distribution $\nu_i$ under both $H_0$ and $H_1$, then $-\log(LR(\tau||\hat{\mu}_i(t)))$ equals the index in APT.
-Why then would one use the likelihood based strategy?
-
-Given that the APT index and the likelihood-ratio based index are only equivalent for normally distributed random variables with fixed standard deviation, the new strategy promises efficiency improvements whenever the true distribution is known and different from the normal distribution.
-The most important example are Bernoulli arms with small means as motivated.
+Indeed, assuming the samples are normally distributed with equal variance for all arms under both $H_0$ and $H_1$, $-\log(B_i^{LR}(t))$ equals the index in APT.
+Why then would we prefer the likelihood based strategy?
+
+Given that the APT index and the likelihood-ratio based index are only equivalent for normally distributed arms with equal variances, the new strategy promises efficiency improvements whenever the true distribution is known and different from the normal distribution.
+The most important example are Bernoulli arms with small means as motivated above.
 While the likelihood ratio can in theory be used for any distributions, and arms could even have different classes of distributions, the class of distribution has to be known upfront for every arm.
-Given the role of the threshold $\tau$ and the goal of classification of the mean against $\tau$, the likelihood ratio strategy is arguably most naturally employed on distributions parameterized by their mean.
-In the following descriptions, we thus focus on univariate distributions of the exponential family.
+Given the role of the threshold $\tau$ and the goal of classification of the mean against $\tau$, the likelihood ratio strategy is most naturally employed on distributions parameterized by their mean.
+In the following descriptions, we thus focus on one-parameter distributions of the exponential family.
 Additionally, we also propose a version for the Normal distribution with unknown mean.
-Before we describe the algorithm, we show that the likelihood ratio has a very convenient form for this family of distributions.
-
-### Likelihood Ratio for Univariate Exponential Family of Distributions \label{sec:LRforUnivariateExponentialFamily}
+Before we describe the algorithm, we show that the likelihood ratio has a convenient form for this distribution family.
+
+### Likelihood Ratio for One-Parameter Exponential Family of Distributions \label{sec:LRforUnivariateExponentialFamily}
 
@@
 Given that $b'(x)$ is strictly convex, we have a one-to-one relation between $b'(\theta)$ and $\mathbb{E}(\nu_{\theta})$ through the continuous inverse $b'^{-1}(\theta)$.
-Consequently, one can just as well parameterize the distribution its mean $\mu = \mathbb{\nu_{\theta}}$ and write $\nu_{b'^{-1}(\mu)}$ with the probability density function (compare Cappé et al., 2013)
-
-$$
-q(x|b'^{-1}(\mu)) = h(x) \exp(T(x) b'^{-1}(\mu) - b(b'^{-1}(\mu))).
+Consequently, one can just as well parameterize the distribution by its mean $\mu = \mathbb{\nu_{\theta}}$ and write $\nu_{b'^{-1}(\mu)}$ with the probability density function (compare Cappé et al., 2013)
+
+$$
+q(x|b'^{-1}(\mu)) = h(x) \exp(S(x) b'^{-1}(\mu) - b(b'^{-1}(\mu))).
 $$
@@
 $$
-LR(b'^{-1}(\mu_0)||b'^{-1}(\mu_1)) = \prod_{i=1}^n \frac{\exp(T(x_i) b'^{-1}(\mu_0) - b(b'^{-1}(\mu_0)))}{\exp(T(x_i) b'^{-1}(\mu_1) - b(b'^{-1}(\mu_1)))}
+LR_T(b'^{-1}(\mu_0)||b'^{-1}(\mu_1)) = \prod_{s=1}^T \frac{\exp(S(x_s) b'^{-1}(\mu_0) - b(b'^{-1}(\mu_0)))}{\exp(S(x_s) b'^{-1}(\mu_1) - b(b'^{-1}(\mu_1)))}
 $$
@@
 $$
--\log(LR) = n\Big(b\big(b'^{-1}(\mu_0)) - b(b'^{-1}(\mu_1)\big)\Big) - \Big(b'^{-1}(\mu_0)-b'^{-1}(\mu_1)\Big)\sum_{i=1}^nT(x_i)
-$$
-
-As we will see now, this statistic takes a very convenient closed form for many common distributions.
+-\log(LR_T) = T\Big(b\big(b'^{-1}(\mu_0)) - b(b'^{-1}(\mu_1)\big)\Big) - \Big(b'^{-1}(\mu_0)-b'^{-1}(\mu_1)\Big)\sum_{i=1}^nS(x_i)
+$$
+
+As we will see now, the last equation takes a convenient form for many common distributions.
 
@@
 
-We have $T(x_i) = x_i$, $\theta = \log(\mu/(1-\mu))$, $\Theta = (0,1)$, $b(\theta) = \log(1+\exp(\theta))$, and $\mu \in (0,1)$. Then $b'(\theta) = \mu$, and we can write
+We have $S(x_s) = x_s$, $\theta = \log(\mu/(1-\mu))$, $\Theta = (0,1)$, $b(\theta) = \log(1+\exp(\theta))$, and $\mu \in (0,1)$. Then $b'(\theta) = \mu$, and we can write
 
 \begin{align*}
--\log(LR(\mu_0||\mu_1)) & = n(\log\Big(\frac{1-\mu_0}{1-\mu_1}\Big)) - \Big(\log(\frac{\mu_0}{1-\mu_0}) - \log(\frac{\mu_1}{1-\mu_1})\Big)\sum_{i=1}^{n}x_i \\
+-\log(LR_T(\mu_0||\mu_1)) & = T(\log\Big(\frac{1-\mu_0}{1-\mu_1}\Big)) - \Big(\log(\frac{\mu_0}{1-\mu_0}) - \log(\frac{\mu_1}{1-\mu_1})\Big)\sum_{s=1}^{T}x_i \\
 & = n \Big( (1-\hat{\mu})\log\Big(\frac{1-\mu_1}{1-\mu_0}\Big) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}) \Big)
@@
 $$
--\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n \Big(\hat{\mu}\log\big(\frac{\hat{\mu}}{\tau}\big) + (1-\hat{\mu})\log\big(\frac{1-\hat{\mu}}{1-\tau}\big)\Big)
+-\log(LR_T(\tau||\hat{\mu})) = T\KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) =  = T \KL(\hat{\mu}||\tau) = n \Big(\hat{\mu}\log\big(\frac{\hat{\mu}}{\tau}\big) + (1-\hat{\mu})\log\big(\frac{1-\hat{\mu}}{1-\tau}\big)\Big)
 $$
@@
 
-We have $T(x_i) = x_i$, $\theta = \log(\mu)$, $\Theta = \mathbb{R}$, $b(\theta) = \exp(\theta)$, and $\mu \in (0, +\infty)$. Then $b'(\theta) = \mu$, and we can write:
-
-$$
--\log(LR(\mu_0||\mu_1)) = n(\mu_0 - \mu_1) - (\log(\mu_0) - \log(\mu_1))\sum_{i=1}^n x_i = n\Big((\mu_0 - \mu_1) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}\Big)\Big)
+We have $S(x_s) = x_s$, $\theta = \log(\mu)$, $\Theta = \mathbb{R}$, $b(\theta) = \exp(\theta)$, and $\mu \in (0, +\infty)$. Then $b'(\theta) = \mu$, and we can write:
+
+$$
+-\log(LR_T(\mu_0||\mu_1)) = T(\mu_0 - \mu_1) - (\log(\mu_0) - \log(\mu_1))\sum_{s=1}^T x_s = T\Big((\mu_0 - \mu_1) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}\Big)\Big)
 $$
@@
 $$
--\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n\Big((\tau - \hat{\mu}) + \hat{\mu}\log\Big(\frac{\hat{\mu}}{\tau}\Big)\Big)
+-\log(LR_T(\tau||\hat{\mu})) = T \KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = T \KL(\hat{\mu}||\tau) = T\Big((\tau - \hat{\mu}) + \hat{\mu}\log\Big(\frac{\hat{\mu}}{\tau}\Big)\Big)
 $$
@@
 
-We have $T(x_i) = x_i$, $\theta = \mu/\sigma^2$, $\Theta = \mathbb{R}$, $b(\theta) = \sigma^2\theta^2/2$, $\mu \in \mathbb{R}$. Then $b'(\theta) = \mu$, and we can write
-
-$$
--\log(LR(\mu_0||\mu_1)) = n (\frac{\mu_0^2}{2\sigma^2} - \frac{\mu_1^2}{2\sigma^2}) - (\frac{\mu_0}{\sigma^2} - \frac{\mu_1}{\sigma^2})\sum_{i=1}^nx_i = n\frac{1}{2\sigma^2}\Big(\mu_0^2-\mu_1^2 - 2\mu_0\hat{\mu} + 2\mu_1\hat{\mu}\Big)
+We have $S(x_s) = x_s$, $\theta = \mu/\sigma^2$, $\Theta = \mathbb{R}$, $b(\theta) = \sigma^2\theta^2/2$, $\mu \in \mathbb{R}$. Then $b'(\theta) = \mu$, and we can write
+
+$$
+-\log(LR_T(\mu_0||\mu_1)) = T (\frac{\mu_0^2}{2\sigma^2} - \frac{\mu_1^2}{2\sigma^2}) - (\frac{\mu_0}{\sigma^2} - \frac{\mu_1}{\sigma^2})\sum_{s=1}^Tx_s = T\frac{1}{2\sigma^2}\Big(\mu_0^2-\mu_1^2 - 2\mu_0\hat{\mu} + 2\mu_1\hat{\mu}\Big)
 $$
@@
 $$
--\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n\frac{(\hat{\mu} - \tau)^2}{2\sigma^2}.
+-\log(LR_T(\tau||\hat{\mu})) = T\KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = T \KL(\hat{\mu}||\tau) = T\frac{(\hat{\mu} - \tau)^2}{2\sigma^2}.
 $$
@@
 
-We have $T(x_i) = x_i$, $\theta = -\alpha/\mu$, $\Theta = (-\infty, 0)$, $b(\theta) = -\alpha \log(-\theta)$, $\mu \in (0,+\infty)$. Then $b'(\theta) = -\mu$, and we can write
-
-$$
--\log(LR(\mu_0||\mu_1)) = n\alpha(-\log(\frac{\alpha}{\mu_0}) - \log(\frac{\mu_1}{\alpha})) - (-\frac{\alpha}{\mu_0} + \frac{\alpha}{\mu_1})\sum_{i=1}^{n}x_i = n\alpha \Big(\log\big(\frac{\mu_0}{\mu_1}\big) - \frac{\hat{\mu}}{\mu_1} + \frac{\hat{\mu}}{\mu_0}\Big).
+We have $S(x_s) = x_s$, $\theta = -\alpha/\mu$, $\Theta = (-\infty, 0)$, $b(\theta) = -\alpha \log(-\theta)$, $\mu \in (0,+\infty)$. Then $b'(\theta) = -\mu$, and we can write
+
+$$
+-\log(LR_T(\mu_0||\mu_1)) = T\alpha(-\log(\frac{\alpha}{\mu_0}) - \log(\frac{\mu_1}{\alpha})) - (-\frac{\alpha}{\mu_0} + \frac{\alpha}{\mu_1})\sum_{s=1}^{T}x_s = T\alpha \Big(\log\big(\frac{\mu_0}{\mu_1}\big) - \frac{\hat{\mu}}{\mu_1} + \frac{\hat{\mu}}{\mu_0}\Big).
 $$
@@
 $$
--\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n\alpha \Big(\frac{\hat{\mu}}{\tau} - 1 - \log\big(\frac{\hat{\mu}}{\tau}\big)\Big).
+-\log(LR_T(\tau||\hat{\mu})) = T \KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = T \KL(\hat{\mu}||\tau) = T\alpha \Big(\frac{\hat{\mu}}{\tau} - 1 - \log\big(\frac{\hat{\mu}}{\tau}\big)\Big).
 $$
@@
 
+We now define the Simple Likelihood Ratio Algorithm for the one-parameter exponential family of distributions (1D-SLR).
 Consider again the setting in \autoref{sec:Setup} though without the assumption of $R$-sub-Gaussian distributions.
-Instead, assume that the class of distributions that the arms $i \in \mathbb{A}$ follow is known upfront.
-For the 1D-SLR algorithm, we restrict the potential classes to the univariate exponential family of distributions and write the class generally as $\nu(\mu, \theta)$.
-Here, $\theta$ describes additional parameters known upfront, as for example $\sigma_1, ..., \sigma_K$ for Normal distributions, or $\alpha_1, ..., \alpha_K$ for Gamma distributions.
-Additionally to $\nu(\mu)$, the 1D-SLR algorithm receives as input the definition of the problem $(\tau, \epsilon)$ (compare Locatelli et al., 2016).
+Instead, assume that the distributions $\nu_i$ of arms $i \in \mathbb{A}$ are all the same distribution from the one-parameter exponential family of distributions.
+We write this class of distributions as $\nu(\mu, \theta)$.
+While $\mu$ is the unknown mean parameter, $\theta$ describes potentially *known* parameters, as for example $\sigma_1, ..., \sigma_K$ for Normal distributions, or $\alpha_1, ..., \alpha_K$ for Gamma distributions.
+Additionally to $\nu(\mu, \theta)$, the 1D-SLR algorithm receives as input the definition of the problem $(\tau, \epsilon)$.
 As initialization, the algorithm pulls each arm once.
@@
 As in Locatelli et al.
-(2016), the $X_{i,s}$ is the sample received when pulling arm $i$ for the $s$-th time.
+(2016), $X_{i,s}$ is the sample received when pulling arm $i$ for the $s$-th time.
 Depending on the distribution, the algorithm then computes the index
@@
 \begin{align*}
-B_i^{SLR}(t+1) & = \mathbb{I}(\hat{\mu}\geq \tau)(-\log\big(LR(\tau-\epsilon||\hat{\mu}_i(t))\big) \\
-& \quad +\: \mathbb{I}(\hat{\mu} <\tau)(-\log\big(LR(\tau+\epsilon||\hat{\mu}_i(t))\big) \\
-& = T_i(t) \Big( \mathbb{I}(\hat{\mu}\geq \tau)\cdot KL(\nu_{b'^{-1}(\hat{\mu}(t))}||\nu_{b'^{-1}(\tau-\epsilon)}) \\
-& \quad \quad +\: \mathbb{I}(\hat{\mu} < \tau)\cdot KL(\nu_{b'^{-1}(\hat{\mu}(t))}||\nu_{b'^{-1}(\tau+\epsilon)}) \Big) \Alignyesnumber\label{eqn:SLRIndex}.
+B_i^{SLR}(t+1) & = \mathbb{I}(\hat{\mu}_i(t)\geq \tau) \Big(-\log \big(LR_{T_i(t)}(\tau-\epsilon||\hat{\mu}_i(t))\big)\Big) \\
+& \quad +\: \mathbb{I}(\hat{\mu}_i(t) <\tau) \Big(-\log\big(LR_{T_i(t)}(\tau+\epsilon||\hat{\mu}_i(t))\big)\Big) \\
+& = T_i(t) \Big( \mathbb{I}(\hat{\mu}_i(t) \geq \tau)\cdot \KL(\hat{\mu}_i(t)||\tau+\epsilon) \\
+& \quad \quad \quad +\: \mathbb{I}(\hat{\mu}_i(t) < \tau)\cdot \KL(\hat{\mu}_i(t)||\tau+\epsilon) \Big) \Alignyesnumber\label{eqn:SLRIndex}.
 \end{align*}
@@
 }
-\caption{SLR algorithm for univariate exponential family of distributions}\label{algo_slr_1d}
+\caption{SLR algorithm for one-parameter exponential family of distributions.}\label{algo_slr_1d}
 \end{algorithm}\DecMargin{1em}
@@
 
-As soon as we move away from univariate distributions parameterized by their mean, it becomes less clear how the likelihood ratio for $H_0: \mu = \tau$ and $H_1: \mu = \hat{\mu}$ should be calculated.
-In the case of Normal distributions with unknown mean and unknown variance, given that the variance and mean estimate are linked, we can use $H_0: \mu = \tau \land \sigma^2 = \sigma^2_{\tau} = \frac{1}{n}\sum_{i=1}^{n}(x_i-\tau)^2$ and the alternative hypothesis based on the maximum likelihood estimates $H_1: \mu = \hat{\mu} \land \sigma^2 = \hat{\sigma}^2 = \frac{1}{n}\sum_{i=1}^{n}(x_i-\hat{\mu})^2$.
+As soon as we move away from one-parameter distributions parameterized by their mean, it becomes less clear how the likelihood ratio for $H_0: \mu = \tau$ and $H_1: \mu = \hat{\mu}$ should be calculated.
+In the case of Normal distributions with unknown mean and unknown variance, given that the variance and mean estimate are linked, we can use
+$$
+H_0: \mu_0 = \tau \land \sigma_0^2 = \sigma^2_{\tau} = \frac{1}{n}\sum_{i=1}^{n}(x_i-\tau)^2 \quad \text{vs.} \quad H_1: \mu_1 = \hat{\mu} \land \sigma_1^2 = \hat{\sigma}^2 = \frac{1}{n}\sum_{i=1}^{n}(x_i-\hat{\mu})^2
+$$
+
 In the following, we assume $\epsilon = 0$ for simplicity.
-
 At each round $t$, the algorithm computes $T_i(t)$ and $\hat{\mu}_i(t)$ as before, and additionally the empirical variances $\sigma_{\tau,i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\tau)^2$ and $\hat{\sigma}_{i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\hat{\mu})^2$, where $\hat{\sigma}_{i}^2(t) < \sigma_{\tau,i}^2(t)$ if $\hat{\mu} \neq \tau$ since $\hat{\mu}$ is the maximum likelihood estimate.
@@
 \begin{align*}
-B_i^{SLR_{2D}}(t+1) & = -\log\big(LR(\tau, \sigma_{\tau,i}^2(t)||\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t))\big) \\
+B_i^{2DSLR}(t+1) & = -\log\big(LR_T(\tau, \sigma_{\tau,i}^2(t)||\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t))\big) \\
 & = T_i(t) \log\Big(\frac{\sigma_{\tau,i}^2(t)}{\hat{\sigma}_i^2(t)}\Big) \\
@@
 
-Then, as for the univariate case, the next arm to be pulled is the minimizer of the index $B_i^{SLR_{2D}}(t+1)$, $I_{t+1} = \arg \min_{i \leq K} B_i(t+1)$.
+The next arm to be pulled is the minimizer of the index $B_i^{2DSLR}(t+1)$, $I_{t+1} = \arg \min_{i \leq K} B_i(t+1)$.
 At the end of the horizon $T$, the algorithm outputs the set of arms $\hat{S}_\tau = \{i \in \mathbb{A}, \hat{\mu}_i(T) \geq \tau\}$.
@@
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
-\Input{\emph{$\tau$, $\epsilon$, $\nu(\mu, \theta) = N(\mu,\sigma^2) \, \forall i \in \mathbb{A}$, where $\mu$ and $\sigma^2$ are unknown}}
+\Input{\emph{$\tau$, $\epsilon$, $\nu(\mu, \theta) = \mathcal{N}(\mu,\sigma^2) \, \forall i \in \mathbb{A}$, where $\mu$ and $\sigma^2$ are unknown}}
 \Output{$\hat{S}_\tau = \{i \in \mathbb{A},  \hat{\mu}_i(T) \geq \tau\}$}
@@
 }
-\caption{2D-SLR algorithm for Normal distributions with unknown mean and unknown variance}\label{algo_slr_2d}
+\caption{2D-SLR algorithm for Normal distributions with unknown mean and variance.}\label{algo_slr_2d}
 \end{algorithm}\DecMargin{1em}
@@
 At the beginning of this thesis, we set out to find an algorithm that improves upon the Anytime Parameter Free algorithm introduced in Locatelli et al.
-(2016) for the thresholding bandit problem in two points.
-First, we wanted to make the algorithm perform better in problems with arms that are not well approximated as sub-Gaussian; in particular a problem with Bernoulli arms of small means, and with a threshold close to 0.
-We thus tried to find a strategy that takes more information about the arms into account than purely the sample mean.
+(2016) for the thresholding bandit problem.
+We aimed to make the algorithm perform better in problems with arms that are not well approximated as sub-Gaussian; in particular a problem with Bernoulli arms of small means, and with a threshold close to 0.
+We thus tried to find a strategy that takes more information about the arms into account than only the sample mean.
 With the Simple Likelihood Ratio strategy, we propose an algorithm that fulfills this goal at the cost of being distribution specific.
@@
 While this is likely to be a negligiable problem in the case of $\{0,1\}$ observations whose mean can be modeled reasonably by Bernoulli distributions, it can be more difficult to know the true class of distributions upfront when $\nu_i$ are continuous distributions.
-We have shown however, that the SLR strategy can be adapted to all univariate distributions in the exponential family of distributions.
+We have shown however, that the SLR strategy can be adapted to all one-parameter distributions in the exponential family of distributions.
 The algorithm even offers a natural adaptation to the problem of normal distributions with unknown mean and unknown variance.
 
-Furthermore, the SLR strategy reduces to the APT strategy in the case where arms are normally distributed with equal variance that is known upfront.
-In that case we have as index (compare example 3 above):
+Furthermore, the SLR strategy reduces to the APT strategy in the case where arms are normally distributed with known, equal variances. In this case we have as index (compare example 3 above): 
 $$
@@
 
+Thus, SLR achieves the same upper bound as APT on this problem.
 Given that in all other cases the SLR is able to take more information about the distributions into account through the Kullback-Leibler divergence (in the case of the exponential family of distributions), the algorithm is expected to improve upon the APT strategy.
-Just consider a situation of known, but different variances for Normal distributions.
-Then we had in \autoref{eqn:SLRWithKnownVar} $\sigma_i^2$ and $\sigma_j^2$ instead of $\sigma^2$, which should lead to more pulls of the arm with larger variance.
-This is not taken into account by APT.
 
 As mentioned before, this improvement comes only at the cost of knowing the correct distribution upfront.
-In particular, as for the APT algorithm, there are no parameters which need to be tuned upfront as is usually the case for upper-confidence bound based algorithms (see for example UCB-E in Audibert et al., 2010).
+In particular, as for the APT algorithm, there are no parameters which need to be tuned upfront as is often the case for upper-confidence bound based algorithms (see for example UCB-E in Audibert et al., 2010).
 
@@
 $$
-B_i(t) = S_i(t) D_i(t),
-$$
-where $S_i(t)$ is a confidence term of the estimate of the arm $i$ at time $t$, and $D_i(t)$ is a measure of distance between the distribution of arm $i$ and the threshold $\tau$.
-The index of the Simple Likelihood Ratio strategy for univariate exponential family distributions can then be written with
-$$
-S_i(t) = T_i(t) \quad \text{and} \quad
-D_i(t) = \KL(\hat{\mu}_i(t)||\tau),
+B_i^{SLR}(t) = S_i^{SLR}(t) D_i^{SLR}(t),
+$$
+where $S_i^{SLR}(t)$ is the confidence term and $D_i^{SLR}(t)$ is the measure of distance between the distribution of arm $i$ and the threshold $\tau$.
+The index of the Simple Likelihood Ratio strategy for one-parameter exponential family distributions can then be written with
+$$
+S_i^{SLR}(t) = T_i(t) \quad \text{and} \quad
+D_i^{SLR}(t) = \KL(\hat{\mu}_i(t)||\tau),
 $$
@@
 As we see in the experiments that follow, the SLR strategy is able to improve significantly upon the APT strategy in many cases.
+
+\newpage
 
@@
 ```
+
+\newpage
 
@@
 
-```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Budget allocation across arms for APT and SLR algorithms in simulation 2."}
+```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '70%', fig.cap = "Budget allocation across arms for APT and SLR algorithms in simulation 2."}
 load(file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/loc6nt_ma.Rda")
@@
 
+J.-Y. Audibert, S. Bubeck, and R. Munos. Best Arm Identification in Multi-Armed Bandits. In *Proceedings of the 23rd Conference on Learning Theory*, 2010.\par
+
+E.
+Brochu, V.M.
+Cora, and N.
+de Freitas.
+A Tutorial on Bayesian Optimization of Expensive Cost Functions, with Application to Active User Modeling and Hierarchical Reinforcement Learning, *arXiv preprint arXiv:1012.2599*, 2010.
+\par
+
+S. Bubeck and N. Cesa-Bianchi. Regret analysis of stochastic and nonstochastic multi-armed bandit problems. *Foundations and Trends in Machine Learning*, 5:1–122, 2012.\par
+
+S. Bubeck, N. Cesa-Bianchi, and G. Lugosi. Bandits with heavy tail. *Information Theory, IEEE Transactions on*, 59(11):7711-7717, 2013.\par
+
+A.N. Burnetas and M.N. Katehakis. Optimal adaptive policies for sequential allocation problems. *Advances in Applied Mathematics*, 17:122–142, 1996.\par
+
+O. Capp´e, A. Garivier, O-A. Maillard, R. Munos, and G. Stoltz. Kullback-Leibler upper confidence bounds for optimal sequential allocation. *Annals of Statistics*, 41(3):1516–1541, 2013a.\par
+
+O. Capp´e, A. Garivier, O.-A. Maillard, R. Munos, G. and Stoltz. Supple-
+ment to “Kullback–Leibler upper confidence bounds for optimal sequential allocation.”, *Annals of Statistics*, <DOI:10.1214/13-AOS1119SUPP>, 2013b. \par
+
+H. Chernoff. Sequential Design of Experiments. *The Annals of Mathematical Statistics*, 30(3):755-770, 1959. \par
+
+J.C. Gittins. Bandit processes and dynamic allocation indices. *Journal of the Royal Statistical Society*. 41(2):148–177, 1979.\par
+
+A. Garivier and E. Kaufmann. Optimal Best Arm Identification with Fixed Confidence. In *JMLR Workshop and Conference Proceedings (Conference on Learning Theory)*, 49:1-30, 2016.\par
+
+E. Kaufmann and S. Kalyanakrishnan. Information Complexity in Bandit Subset Selection. In *JMLR Workshop and Conference Proceedings (Conference on Learning Theory)*, 30:228–251, 2013.\par
+
+E.
+Kaufmann, O.
+Capp´e, and A.
+Garivier.
+On Bayesian Upper Confidence Bounds for Bandit Problems.
+In *Proceedings of the 15th International Conference on Artificial Intelligence and Statistics (AISTATS)*, 2012.\par
+
+E. Kaufmann, O. Capp´e, A. Garivier. On the Complexity of Best Arm Identification in Multi-Armed Bandit Models. Journal of Machine Learning Research, 17:1-42, 2016.\par
+
+T.L. Lai and H. Robbins. Asymptotically efficient adaptive allocation rules. *Advances in Applied Mathematics*, 6:4–22, 1985.\par
+
+A.
+Locatelli, M.
+Gutzeit, and A.
+Carpentier.
+An optimal algorithm for the Thresholding Bandit Problem.
+In *Proceedings of the 33rd International Conference on Machine Learning*, JMLR: W&CP 48, 2016.\par
+
+S. Mukherjee, K.P. Naveen, N. Sudarsanam, and B. Ravindran. Thresholding Bandits with Augmented UCB. 2017. *arXiv preprint arXiv:1704.02281*, 2015.\par
+
+H. Robbins. Some aspects of the sequential design of experiments. *Bulletin of the American Mathematical Society*, 58:527-535, 1952.\par
+
+D. Russo. Simple Bayesian Algorithms for Best Arm Identification. In *JMLR Workshop and Conference Proceedings (Conference on Learning Theory)*, 2016.\par
+
+W.R. Thompson. On the likelihood that one unknown probability exceeds another in view of the evidence of two samples. *Biometrika*, 25:285–294, 1933.\par
+
+W.R. Thompson. On the Theory of Apportionment. *American Journal of Mathematics*, 57:450–456, 1933.\par
+
+J. Zhong, Y. Huang, and J. Liu. Asynchronous Parallel Empirical Variance Guided Algorithms for the Thresholding Bandit Problem. *arXiv preprint arXiv:1704.04567*, 2017.\par
+
 \newpage
@@
 However, the alternative model needs more motivation than in the case of a single arm.
-But first, consider again that we are in the thresholding bandit problem with $K$ arms of univariate canonical exponential family distributions that are parameterized by their means $\mu_1, ..., \mu_K$ for the original problem $\nu = (\nu_1, ..., \nu_K)$.
+But first, consider again that we are in the thresholding bandit problem with $K$ arms of one-parameter canonical exponential family distributions that are parameterized by their means $\mu_1, ..., \mu_K$ for the original problem $\nu = (\nu_1, ..., \nu_K)$.
 W.l.o.g, assume that all arms are above the threshold, that is, $\mu_1 \geq \tau, ..., \mu_K \geq \tau$.

### 2017-09-10 Thesis/Draft.tex
Add References

@@
 \hypersetup{unicode=true,
-            pdftitle={Draft},
+            pdftitle={On Pure Exploration, Thresholding Bandits, and Kullback-Leibler Divergence},
             colorlinks=true,
@@
 \setlength{\droptitle}{-2em}
-  \title{Draft}
+  \title{On Pure Exploration, Thresholding Bandits, and Kullback-Leibler
+Divergence}
   \pretitle{\vspace{\droptitle}\centering\huge}
@@
 
+\vspace*{10\baselineskip}
+
 ``In general, we look for a new law by the following process: First we
@@
 
-\section{Abbreviations}\label{abbreviations}
-
-Kullback-Leibler divergence between distributions \(\nu_i\) and
-\(\nu_j\): \(\KL(\nu_i||\nu_j)\).
-
-Binary relative entropy:
-\(d(x,y) := x \log(x/y) + (1-x) \log((1-x)/(1-y))\), where
-\(d(0,0) = d(1,1) = 0\).
-
-Kullback-Leibler divergence for two Bernoulli distributions
-parameterized by their means \(\mu_i\) and \(\mu_j\):
-\(KL_{Ber}(\nu_i||\nu_j) = d(\mu_i, \mu_j)\).
-
-Define exponential family of distributions
-
-Define KL Divergence for this family
-
-\newpage
-
 \section{\texorpdfstring{Introduction
@@
 This makes sequential sampling especially relevant in situations where
-there is an inherent cost to obtaining samples. The classical example is
-that of clinical trials in which a researcher tests two drugs on
-patients to observe which one performs better. Not only is it difficult
-to gather enough patients, but one would also like to adapt the sampling
-such that as soon as possible more patients receive the better drug and
-are cured. As noted in Cappé et al. (2013), this example dates back to
-Thompson (1933, 1935). Such problems are known as multi-armed bandit
-problems in which the sampling is adapted so as to minimize the
-cumulative regret: In the case of the drug tests, one would like to
-sample the two drugs in a way to find the best drug as soon as possible
-and then to test this drug more and more often and more often than the
-worse drug. This would lead to cumulatively more healthy patients than
-testing both drugs uniformly; it would minimize the regret from treating
-patients with an ineffective drug.
+there is an inherent cost to obtaining samples, or where only a limited
+amount of samples can be collected. The classical example is that of
+clinical trials in which a researcher tests two drugs on patients to
+observe which one performs better. Not only is it difficult to gather
+enough patients, but one would also like to adapt the sampling such that
+as soon as possible more patients receive the better drug and are cured.
+As noted in Cappé et al. (2013), this example dates back to Thompson
+(1933, 1935). Such problems are known as multi-armed bandit problems in
+which the sampling is adapted so as to minimize the cumulative regret:
+In the case of the drug tests, one would like to sample the two drugs in
+a way to find the best drug as soon as possible and then to test this
+drug more and more often and more often than the worse drug. This would
+lead to cumulatively more healthy patients than testing both drugs
+uniformly; it would minimize the regret from treating patients with an
+ineffective drug.
 
@@
 
-In this thesis, we consider the thresholding bandit problem. Instead of
-identifying the best \(m\) out of \(K\) arms, we aim to find all
-distributions out of \(K\) that have a mean at least as large as a
-threshold fixed upfront. In the form described in Locatelli et al.
-(2016), algorithms in the thresholding bandit problem are evaluated
-against a binary loss function penalizing whenever an arm has not been
-classified correctly as being above or below the threshold, and thus
-focus on exploration similar to algorithms employed for best arm
-identification. Indeed, Locatelli et al. (2016) show how their
+In this thesis, we consider the thresholding bandit problem. While the
+name is reminiscient of the cumulative regret multi-armed bandit, the
+problem is more similar to the top-\(m\) problem. But instead of
+identifying the best \(m\) out of \(K\) arms, one aims to find all
+distributions out of \(K\) that have a mean at least as large as a fixed
+threshold. Given that an implicit threshold arises in the top-\(m\)
+problem between the \(m\)-th best and the \((m+1)\)-th best arm
+(Kaufmann et al., 2016), the two problems share many characteristics. We
+discuss this in more detail in
+\autoref{chap:KullbackLeiblerPureExploration}. In the form described in
+Locatelli et al. (2016), algorithms in the thresholding bandit problem
+are evaluated against a binary loss function penalizing whenever an arm
+has not been classified correctly as being above or below the threshold,
+and thus focus on exploration similar to algorithms employed for best
+arm identification. Indeed, Locatelli et al. (2016) show how their
 thresholding algorithm can be used for best arm identification when the
@@
 
-To introduce the thresholding bandit problem, consider a game in which
-the learner is tasked to find the slot machines within a row of \(K\)
-slot machines in a casino that give a mean payoff larger than a fixed
-threshold \(\tau\), for example \(\tau = 0\). The learner cannot pull
-all slot machines at the same time. Instead, he acquires samples
-sequentially from one slot machine at a time to learn about their payoff
-structure. The learner has a budget of \(T>K\) slot machine pulls. After
-\(t-1\) samples, the learner has observed \(T_i(t-1)\) samples from slot
-machine \(i\). The payoffs \(X_{i,1}, ..., X_{i,T_i(t-1)}\) are drawn
-from the payoff distribution \(\nu_i\) underlying the slot machine
-\(i\). At time \(t\), the learner considers the payoffs he observed so
-far in order to choose the next slot machine he would like to pull. Her
-decision is lead by the goal to classify the slot machines with
-distribution \(\nu_i\) and mean payoff
-\(\mu_i = \mathbb{E}_{X \sim \nu_i}[X]\) after \(T\) samples as being
-above or below the threshold with error probability as small as
-possible.
-
-The thresholding bandit problem can thus be framed in the literature on
-sequential sampling strategies. Even though its name is reminiscient of
-the multi-armed bandit setting, the thresholding bandit problem is more
-akin to best arm identification and top-\(m\) identification problems
-due to its focus on exploration: While the classical multi-armed bandit
-problems are concerned with cumulative regret which increases
-\emph{during} sampling, best arm identification and thresholding bandits
-collect loss only once \emph{after} the sampling procedure (compare
-Garivier and Kaufmann, 2016; Kaufmann et al., 2016; Kaufmann and
-Kalyanakrishnan, 2013). As we will see in
-\autoref{chap:KullbackLeiblerPureExploration} there arises an implicit
-threshold between the means of the \(m\)-th best arm and the \(m+1\)-th
-best arm in the top-\(m\) identification problem (Kaufmann et al., 2016;
-Kaufmann and Kalyanakrishnan, 2013). Because of this, the two settings
-are very related.
-
-\subsection{\texorpdfstring{Setup
-\label{sec:Setup}}{Setup }}\label{setup}
+\subsection{An Example}\label{an-example}
+
+To introduce the thresholding bandit problem, consider a common
+situation among internet-based companies. These companies often collect
+user feedback to offer reviews and ratings on websites or in apps, or
+collect it to improve their services. Netflix lets users rate movies
+with ``Thumbs up'' and ``Thumbs down'', apps like Clue ask users a
+question per day to learn to predict the user's health and mood. An
+online shop might give customers a one-question survey after they make a
+purchase. Finally, Foursquare and Yelp ask users to rate coffee shops,
+bars, and restaurants.
+
+Consider the problem the latter companies face. Whenever a user reports
+that she visited a restaurant, the app would like to ask questions about
+her experience. To give a simple example, assume users are not willing
+to answer more than one question per restaurant visit, and the app would
+like to find out two things: Does the restaurant have good service? Is
+the restaurant trendy?
+
+If the feedback that users can give is restricted to binary ``Yes'' or
+``No'' answers, then we can model the feedback as Bernoulli random
+variables
+
+\[
+X_{\text{service}} \sim \text{Ber}(\mu_{\text{service}}) \quad \text{and} \quad X_{\text{trendy}} \sim \text{Ber}(\mu_{\text{trendy}}).
+\]
+
+The app will then display a ``Good service'' or ``This place is trendy''
+description for the restaurant if \(\mu_{\text{service}}\) and
+\(\mu_{\text{trendy}}\) are estimated to be above a certain threshold,
+for example \(\tau = 0.5\). That is, more than half of the people would
+describe the place as having good service, or as trendy.
+
+To make the app as useful as possible to other users, this information
+should be shown as quickly as possible. But even though the app has
+thousands of users, not that many people visit a specific restaurant,
+and even less people report this back to the app. Thus the company only
+has a limited budget of \(T\) potential users from which to collect
+samples \(X_{\text{service}}\) and \(X_{\text{trendy}}\) from. How can
+the company ask these \(T\) questions to be as confident as possible in
+its classification, that is, in the information it displays?
+
+A straightforward way of sampling users would be to ask the two
+questions in a round-robin fashion: Ask for ``Service'', then for
+``Trendy'', then for ``Service'', \ldots{} Given 100 users, 50 users
+give feedback on the service level, 50 users report on the trendiness
+level. This however is unlikely to be optimal with respect to the
+confidence after 100 samples. Given that the company asks the users
+sequentially, there is the option to adapt the sampling strategy over
+time: If the first ten users report
+\(\sum_{s=1}^{10}X_{\text{service},s}=10\), while
+\(\sum_{s=1}^{10}X_{\text{trendy},s}=5\), then the company might already
+be quite confident that \(\mu_{\text{service}} \geq \tau = 0.5\), while
+this is less clear for \(\mu_{\text{trendy}}\). Instead of continuously
+sampling both questions, it might be more useful to collect more
+feedback on the trendiness level so as to figure out its position
+relative to the threshold. After all, the company would like to use the
+100 samples to maximize its confidence in both displayed tips.
+
+Finding the optimal sequential sampling strategy to classify
+distributions against a threshold with as much confidence as possible
+after a limited budget of samples is the problem described above, and
+the problem described by the thresholding bandit problem which we
+discuss for the remainder of this thesis. In the following section, we
+define the general setting of the thresholding bandit problem.
+
+\subsection{\texorpdfstring{General Setting
+\label{sec:Setup}}{General Setting }}\label{general-setting}
 
@@
 by sequentially drawing observations \(X_{i,1}, X_{i,2}, ...\) from the
-different arms. However, at time \(t\) the learner cannot observe a
-reward from every distribution but must select a single arm \(I_t\) from
-which she would like to observe the reward \(X_{I_t,t}\). Often,
-adaptive sampling strategies makes the decision of which arm to pull by
-computing an index \(B_i(t)\) for each arm. If \(T_i(t)\) is the number
-of samples observed until time \(t\) for arm \(i\), then is \(B_i(t)\) a
-function of the past rewards \(X_{i,1}, ..., X_{i,T_i(t)}\) observed for
-arm \(i\), and w.l.o.g. \(I_t = \arg \min_{i = 1,...K} B_i(t)\). The set
-of indexes can be called strategy (Kaufmann et al., 2012) which makes it
-clear that the strategy is adapted as more observations are collected.
-Strategies of this kind are also called index policies.
+different arms, where \(X_{i} \sim \nu_i\). However, at time \(t\) the
+learner cannot observe a reward from every distribution but must select
+a single arm \(I_t\) from which she would like to observe the reward
+\(X_{I_t,t}\). Often, adaptive sampling strategies makes the decision of
+which arm to pull by computing an index \(B_i(t)\) for each arm. If
+\(T_i(t)\) is the number of samples observed until time \(t\) for arm
+\(i\), then is \(B_i(t)\) a function of the past rewards
+\(X_{i,1}, ..., X_{i,T_i(t)}\) observed for arm \(i\), and w.l.o.g.
+\(I_t = \arg \min_{i = 1,...K} B_i(t)\). The set of indexes can be
+called strategy (Kaufmann et al., 2012) which makes it clear that the
+strategy is adapted as more observations are collected. Strategies of
+this kind are also called index policies.
 
@@
 \subsubsection{\texorpdfstring{Proof of Theorem
-\ref{theorem:LocatelliTheorem4}}{Proof of Theorem }}\label{proof-of-theorem}
+\ref{theorem:LocatelliTheorem4}
+\label{sec:UpperBoundProof}}{Proof of Theorem  }}\label{proof-of-theorem}
 
@@
 can now show that there exists an arm that has been pulled at least as
-often as the share of his complexity contribution.
+often as the share of its complexity contribution.
 
@@
 
-\subsubsection{Check Separation
-Condition}\label{check-separation-condition}
+\subsubsection{\texorpdfstring{Check Separation Condition
+\label{sec:CheckSeparationCondition}}{Check Separation Condition }}\label{check-separation-condition}
 
@@
 the \((\log(T)+1)K\) term which is negligiable in comparison with the
-exponent for large \(T\) as shown in Locatelli et al. (2016), which
-makes the APT algorithm order optimal.
+exponent for large \(T\) as shown in Locatelli et al. (2016). This makes
+the APT algorithm order optimal.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Mention Optimality (Upper Bound matches lower bound)
-\item
-  Anytime
-\end{itemize}
-
 One of the APT algorithm's main features is its simplicity. The sampling
-rule is very straightforward, and, as highlighted in Locatelli et al.
-(2016), it does not require any knowledge about the type of
-sub-Gaussianity \(R\), or the complexity \(H\) upfront. This makes the
-algorithm immediately applicable in practice while it still enjoys its
-upper bound on the expected regret. This is in particular worth
-highlighting when comparing APT to algorithms used in the best arm
-identification or Top-\(m\) setting. As alluded to in
-\autoref{sec:TheAPTAlgorithm}, many algorithms that fix the sampling
-budget upfront (i.e., fixed budget algorithms as UCB-E or KL-LUCB-E)
-require knowledge about the corresponding complexity upfront (Audibert
-et al., 2010; Kaufmann and Kalyanakrishnan, 2013). The problem however
-being, that to know the complexity, the experimenter has to know all
-means up to a permutation of the arms. This, of course, is not given in
-practice. Thus alternative algorithms try to estimate the complexity
-online which can be difficult as especially in the beginning plug-in
-estimates based on the estimated means may lead to wrong estimates of
-the complexity, which in turn leads to poor budget allocation based on
-mistaken beliefs (compare Garivier and Kaufmann, 2016). On the other
-hand, the sequential sampling strategy has to rely on some estimate.
-While the APT algorithm does not explicitly estimate the complexity, the
-gaps that serve as index are essentially the same. Faced not with
-sub-Gaussian but more heavy-tailed distributions, these estimates might
-well lead to poor performance.
-
-Here, the APT algorithm shows room for improvement, as also mentioned in
-Locatelli et al. (2016). The problem is that the assumptions for the
-bounds no longer hold as arms are less sub-Gaussian; of course the
+rule is straightforward, and, as highlighted in Locatelli et al. (2016),
+it does not require any knowledge about the type of sub-Gaussianity
+\(R\), or the complexity \(H\) upfront. This makes the algorithm
+immediately applicable in practice while it still enjoys its upper bound
+on the expected regret. This is in particular worth highlighting when
+comparing APT to algorithms used in the best arm identification or
+top-\(m\) setting. As alluded to in \autoref{sec:TheAPTAlgorithm}, many
+algorithms that fix the sampling budget upfront (i.e., fixed budget
+algorithms as UCB-E or KL-LUCB-E) require knowledge about the complexity
+upfront (Audibert et al., 2010; Kaufmann and Kalyanakrishnan, 2013). The
+problem however being that to know the complexity, the experimenter has
+to know all means up to a permutation of the arms. This, of course, is
+not given in practice. Thus alternative algorithms try to estimate the
+complexity online which can be difficult as especially in the beginning
+plug-in estimates based on the estimated means may lead to wrong
+estimates of the complexity, which in turn leads to poor budget
+allocation based on mistaken beliefs (compare Garivier and Kaufmann,
+2016). On the other hand, the sequential sampling strategy has to rely
+on some estimate. While the APT algorithm does not explicitly estimate
+the complexity, the gaps that serve as index are essentially the same.
+Empirically, we see in \autoref{chap:Experiments} that the problem
+described by Garivier and Kaufmann (2016) does also occur for the APT
+strategy. Faced not with sub-Gaussian but with more heavy-tailed
+distributions, this sensitivity is likely to increase.
+
+Furthermore, as mentioned in Locatelli et al. (2016), the assumptions
+for the bounds no longer hold as arms become less sub-Gaussian; the
 complexity \(H\) and the term \(\hat{\Delta}_i(t)\) in the algorithm's
-index are motivated by sub-Gaussian distributions. The more one moves
-away from those, the less appropriate these quantities become. In
-particular, the empirical mean will be less (or not at all) concentrated
-around the true mean and more impacted by outliers which are more likely
-under non sub-Gaussian distributions. Locatelli et al. (2016) thus
-refers to Bubeck et al. (2013a) which considers solutions for
+index are both motivated by sub-Gaussian distributions. The more a
+problem deviates from those, the less appropriate the quantities become.
+In particular, the empirical mean will be less (or not at all)
+concentrated around the true mean and more impacted by outliers which
+are more likely under non sub-Gaussian distributions. Locatelli et al.
+(2016) thus refers to Bubeck et al. (2013a) which consider solutions for
 multi-armed bandits that are based on heavy-tail distributions. By using
@@
 al. (2016). We will continue to discuss their results in
-\autoref{chap:VarianceBasedAlgorithms}.
+\autoref{sec:VarianceBasedAlgorithms}.
 
@@
 \[
-\KL_{N}(\nu_i || \nu_j) = 2(\mu_i - \mu_j)^2.
+\KL_{\mathcal{N}}(\nu_i || \nu_j) = 2(\mu_i - \mu_j)^2.
 \]
@@
 \[
-\KL_{Ber}(\nu_i||\nu_j) = \mu_i \log(\frac{\mu_i}{\tau}) + (1-\mu_i) \log(\frac{1-\mu_i}{1-\tau})
+\KL_{\text{Ber}}(\nu_i||\nu_j) = \mu_i \log(\frac{\mu_i}{\tau}) + (1-\mu_i) \log(\frac{1-\mu_i}{1-\tau})
 \]
@@
 \[
-\KL_{Ber}(\nu_i||\nu_j) \geq 2(\mu_i - \tau)^2.
-\]
-
-This is of course equal to the Gaussian KL-divergence described before.
-This approximation, however, suffers for heavily for very small values
-of \(\mu_i\) and \(\tau\). In particular, the Bernoulli KL-divergence
-becomes asymmetric in its first argument as \(\tau \neq 0.5\). Thus, in
-contrast to the complexity measure \(H\) based on the Gaussian
+\KL_{\text{Ber}}(\nu_i||\nu_j) \geq 2(\mu_i - \tau)^2.
+\]
+
+This is equal to the Gaussian KL-divergence described before. The
+approximation, however, suffers heavily for very small values of
+\(\mu_i\) and \(\tau\). In particular, the Bernoulli KL-divergence
+becomes asymmetric in its first argument when \(\tau \neq 0.5\). Thus,
+in contrast to the complexity measure \(H\) based on the Gaussian
 KL-divergence, a complexity measure based on the Bernoulli KL-divergence
@@
 Thus similarly to how UCB algorithms in the cumulative regret setting
-have been extended to KL-UCB algorithms (compare Cappé et al., 2013),
-also the APT algorithm offers room for improvement. As a more explicit
-example of such adaptation, consider the case of Top-\(m\)
-identification described in Kaufmann et al. (2016). The authors develop
-a lower bound based on KL-divergence, and note that ``This
-information-theoretic lower bound permits to interpret the quantity
-\(H(\nu)\) {[}\ldots{}{]} as a subgaussian approximation''. Given that
-Bernoulli distributions with very small parameter values arise naturally
-in many applications, an improvement in this regard would be valuable.
+have been extended to KL-UCB algorithms (Cappé et al., 2013), the APT
+algorithm offers room for improvement, too. As a more explicit example
+of such adaptation, consider the case of top-\(m\) identification
+described in Kaufmann et al. (2016). The authors develop a lower bound
+based on KL-divergence, and note that ``This information-theoretic lower
+bound permits to interpret the quantity \(H(\nu)\) {[}\ldots{}{]} as a
+subgaussian approximation''. Given that Bernoulli distributions with
+very small or very large parameter values arise naturally in many
+applications, an improvement in this regard would be valuable.
 
@@
 \autoref{chap:KullbackLeiblerPureExploration} how information theoretic
-quantities are employed in the best arm identification and Top-\(m\)
+quantities are employed in the best arm identification and top-\(m\)
 problem as detailed in Kaufmann and Garivier (2016) and Kaufmann et al.
@@
 
+\newpage
+
 \section{\texorpdfstring{Information Theoretic Approaches to Pure
@@
 The previous chapter introduces the thresholding bandit problem as
-described in Locatelli et al. (2016), and with the APT strategy a first
+described in Locatelli et al. (2016), and the APT strategy as a first
 algorithm that is simple, yet order-optimal for large budgets. However,
-we end with the conclusion that a distance measure between the
-distributions and the threshold based on the Kullback-Leibler divergence
-might be more useful than the simple gap
-\(\Delta^2_i = (\mu_i - \tau_i)^2\) employed so far. Indeed, citing
-Kaufmann et al. (2016), we note that the complexity \(H\) used so far
-can be considered a sub-Gaussian approximation of a better complexity
-measure based on information theoretic measures like the
-Kullback-Leibler divergence.
-
-In order to give more intuition to why that is the case, and in what
+we end with the conclusion that a KL-divergence based measure of the
+distance between the distributions and the threshold might be more
+useful than the simple gap \(\Delta^2_i = (\mu_i - \tau_i)^2\) employed
+so far. Indeed, citing Kaufmann et al. (2016), we note that the
+complexity \(H\) -- and thus the gaps -- used so far can be considered a
+sub-Gaussian approximation of a better complexity measure based on
+information theoretic measures like the Kullback-Leibler divergence.
+
+In order to give more intuition to why that is the case, and in which
 ways information theoretic measures can be introduced to measure the
@@
 while the first derives complexity measures based on the divergence.
-Ideally, their work offers methods that can inform our work of extending
-the thresholding bandit problem. In what follows, we adopt the notation
-of Kaufmann et al. (2016) to ease a comparison with their arguments.
+Their work offers methods that can inform our goal of extending the
+thresholding bandit problem. In what follows, we adopt the notation of
+Kaufmann et al. (2016) to ease a comparison with their arguments.
 
@@
 consider the problem of identifying the best \(m\) out of \(K\) arms,
-that is, the top-\(m\) problem. They describe their bandit model \(\nu\)
-by \(K\) arms characterized by probability distributions \(\nu_a\),
-\(a \in \{1,...,K\}\), with mean \(\mu_a\). A learner picks at any time
-step \(t=1,2,...,\) an arm \(A_t \in \{1,...,K\}\) for which he observes
-the independent reward \(Z_{t} \sim \nu_{A_t}\). The learner aims to
-find the \(m\) out of \(K\) arms with the largest expected reward. This
-set of arm indexes is denoted by \(\mathcal{S}_m^*\). Kaufmann et al.
-write the means \((\mu_{1}, ..., \mu_{K})\) sorted in decreasing order
-as the K-tuple \((\mu_{[1]}, ..., \mu_{[K]})\). Based on this, they
-require that \(\mu_{[m]} > \mu_{[m+1]}\) such that the solution
-\(\mathcal{S}_m^*\) is unique. The class of bandit problems \(\nu\) for
-which the latter condition holds is called \(\mathcal{M}_m\) by Kaufmann
-et al. At the end of the sampling procedure, after \(T\) samples
-(denoted by \(\tau\) in Kaufmann et al.) the learner is required to
-return a classification \(\hat{\mathcal{S}}_m\). This classification is
-then evaluated by the loss function
+that is, the top-\(m\) problem. They describe their bandit model
+\(\nu = (\nu_1,...,\nu_K)\) by \(K\) arms characterized by probability
+distributions \(\nu_i\), \(i \in \mathbb{A} = \{1,...,K\}\), with mean
+\(\mu_i\). A learner picks at any time step \(t=1,2,...,\) an arm
+\(I_t \in \{1,...,K\}\) for which she observes the independent reward
+\(X_{t} \sim \nu_{I_t}\). The learner aims to find the \(m\) out of
+\(K\) arms with the largest expected reward. This set of arm indexes is
+denoted by \(\mathcal{S}_m^*\). Kaufmann et al. write the means
+\((\mu_{1}, ..., \mu_{K})\) sorted in decreasing order as the K-tuple
+\((\mu_{[1]}, ..., \mu_{[K]})\). Based on this, they require that
+\(\mu_{[m]} > \mu_{[m+1]}\) such that the solution \(\mathcal{S}_m^*\)
+is unique. The class of bandit problems \(\nu\) for which the latter
+condition holds is called \(\mathcal{M}_m\) by Kaufmann et al. At the
+end of the sampling procedure, after \(T\) samples, the learner is
+required to return a classification \(\hat{\mathcal{S}}_m\). This
+classification is then evaluated by the loss function
 \(\mathcal{L}(T) = \mathbb{I}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m)\).
@@
 can now define a strategy of the learner as
-\(\mathcal{A} = ((A_t), T, \hat{\mathcal{S}}_m)\): The strategy defines
+\(\mathcal{S} = ((I_t), T, \hat{\mathcal{S}}_m)\): The strategy defines
 how an arm is chosen, how many samples are observed, and how the arms
@@
 When introducing the thresholding bandit setting, we did not mention the
-fact that the budget \(T\) does not need to be fixed upfront. Indeed,
-the setting in which the budget is \emph{not} fixed upfront might be
-more popular among the best arm identification and top-\(m\) literature.
-This setting is called \emph{fixed confidence}, while the setting we
-considered so far is called \emph{fixed budget}. In the fixed budget
-setting, we run algorithms for \(T\) samples and then compare them based
-on their expected loss,
+fact that there exists an alternative setting in which the budget \(T\)
+is not fixed upfront. This setting is called \emph{fixed confidence},
+while the case we considered so far is called \emph{fixed budget}. In
+the fixed budget setting, we run algorithms for \(T\) samples and then
+compare them based on their expected loss,
 \(\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m) =: p_t(\nu)\)
 as we have seen in \(\autoref{sec:Setup}\). Alternatively, consider a
-\(\delta\)-PAC strategy \(\mathcal{A}(\delta)\)for which it holds for
+\(\delta\)-PAC strategy \(\mathcal{S}(\delta)\)for which it holds for
 every problem \(\nu \in \mathcal{M}_m\) that the classification holds at
@@
 before it is allowed to stop sampling. This is the fixed confidence
-case, in which the budget \(T\) is no longer fixed upfront, but turns
-into a random variable. Algorithms are then compared by their expected
-number of draws \(\mathbb{E}_{\nu}[T_{\delta}]\) and we prefer those
-which achieve the confidence level \(1-\delta\) with a smaller expected
-budget.
+case, in which the budget \(T=T_{\delta}\) is no longer fixed upfront,
+but becomes a random variable. Algorithms are then compared by their
+expected number of draws \(\mathbb{E}_{\nu}[T_{\delta}]\) and we prefer
+those which achieve the confidence level \(1-\delta\) with a smaller
+expected budget.
 
 In the fixed confidence setting, a family of strategies
-\(A = (\mathcal{A}(\delta))_{\delta \in (0,1)}\) is called PAC if for
-every \(\delta\), \(\mathcal{A}(\delta)\) is \(\delta\)-PAC. On the
+\(S = (\mathcal{S}(\delta))_{\delta \in (0,1)}\) is called PAC if for
+every \(\delta\), \(\mathcal{S}(\delta)\) is \(\delta\)-PAC. On the
 other hand, in the fixed budget setting, a family of strategies
-\(A = (\mathcal{A}(t))_{t \in \mathbb{N}}\) is called consistent if
+\(S = (\mathcal{S}(t))_{t \in \mathbb{N}}\) is called consistent if
 \(p_t(\nu) \rightarrow 0\) as \(t \rightarrow \infty\) for every problem
@@
 complexity, it makes sense to first follow their arguments to a general
-lower bound on the sample complexity \(\mathbb{E}_{\nu}[\tau]\) which is
-given in their Theorem 4:
+lower bound on the sample complexity \(\mathbb{E}_{\nu}[T]\) which is
+given in their Theorem 4. Here, \(\mathcal{P}\) refers to a set of
+probability measures for which Kaufmann et al. (2016) assume certain
+continuity conditions in their Assumption 3, and
+\(\nu_i \in \mathcal{P}\). In the following,
+\(d(x,1-x) = x\log(\frac{x}{1-x}) + (1-x) \log(\frac{1-x}{x})\) is the
+binary KL-divergence.
 
@@
 
-To prove this statement for a given \(\delta\)-PAC algorithm
-\(\mathcal{A}\), we assume certain continuity conditions (compare
+To prove this statement for a given \(\delta\)-PAC strategy
+\(\mathcal{S}\), we assume certain continuity conditions (compare
 Kaufmann et al. (2016)) under which there exists for every arm
-\(a \in \{1, \dots, K\}\) an alternative model
-\(\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)\).
+\(i \in \{1, \dots, K\}\) an alternative model
+\(\nu' = (\nu_1, \dots, \nu_{i-1}, \nu_i', \nu_{i+1}, \dots, \nu_K)\).
 In this alternative model, in accordance with the continuity conditions,
-only arm \(a\) is modified. After the modification, the arm
-\(\nu_{m+1}\) is now closer to \(\nu_a\) as measured by the
-Kullback-Leibler divergence than \(\nu_a'\) is to \(\nu_a\), if
-\(\mu_a > \mu_{m+1}\) (consequently, \(\mu_a' < \mu_{m+1}\)). On the
+only arm \(i\) is modified. After the modification, the arm
+\(\nu_{m+1}\) is now closer to \(\nu_i\) as measured by the
+Kullback-Leibler divergence than \(\nu_i'\) is to \(\nu_i\), if
+\(\mu_i > \mu_{m+1}\) (consequently, \(\mu_i' < \mu_{m+1}\)). On the
 other hand, if \(\mu_a < \mu_{m}\), then \(\nu_a'\) will be moved away
-from \(\nu_a\) just enough so that \(\nu_a\) is closer to \(\nu_m\) than
-to \(\nu_a'\) (consequently, \(\mu_a' > \mu_m\)). These changes in
+from \(\nu_i\) just enough so that \(\nu_i\) is closer to \(\nu_m\) than
+to \(\nu_i'\) (consequently, \(\mu_i' > \mu_m\)). These changes in
 distribution make the original set of optimal arms, \(\{1,\dots,m\}\),
@@
 \(\tau \in (\mu_{m+1},\mu_m)\). Then, by creating an alternative problem
-as described here, we flip arm \(a\) around the implied threshold
+as described here, we flip arm \(i\) around the implied threshold
 \(\tau\) (compare the lower bound proof in \autoref{sec:AppendixAPTLB}).
@@
 We apply this Lemma directly on the expected number of draws for each
-arm, \(\mathbb{E}_{\nu}[N_a]\). For each arm \(a\), we thus have
-\(\KL(\nu_a, \nu_a') \mathbb{E}_{\nu}[N_a] \geq d(1-\delta, \delta)\).
+arm, \(\mathbb{E}_{\nu}[N_i]\). For each arm \(a\), we thus have
+\(\KL(\nu_i, \nu_i') \mathbb{E}_{\nu}[N_i] \geq d(1-\delta, \delta)\).
 Using the definition of the alternative model above, we get for every
-small but fixed \(\alpha > 0\), every arm \(a \in \{1, \dots, K\}\) and
-\(b \in \{m+1, \dots, K\}\):
+small but fixed \(\alpha > 0\), every arm \(i \in \{1, \dots, K\}\) and
+\(j \in \{m+1, \dots, K\}\):
 
 \begin{equation*}
-\mathbb{E}_{\nu}[N_a] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_a || \nu_{m+1}) + \alpha} \quad \text{and} \quad \mathbb{E}_{\nu}[N_b] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_b || \nu_{m}) + \alpha}.
+\mathbb{E}_{\nu}[T_i] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_i || \nu_{m+1}) + \alpha} \quad \text{and} \quad \mathbb{E}_{\nu}[T_j] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_j || \nu_{m}) + \alpha}.
 \end{equation*}
@@
 implied threshold between the \(m\)-th best arm and the \((m+1)\)-th
-best arm. The latter gives a lower bound on the effort (in terms of
-expected number of samples) required to achieve a certain confidence
+best arm. The last equation gives a lower bound on the effort (in terms
+of expected number of samples) required to achieve a certain confidence
 level, where a problem that requires a larger effort is described as
@@
 et al. (2016) describe problems as having a larger \emph{sampling
-complexity}.
-
-Following Kaufmann et al. (2016), we define the complexity
+complexity}. Following Kaufmann et al. (2016), we define the complexity
 \(\kappa_C(\nu)\) in the fixed confidence setting as
@@
 \begin{equation}
-\kappa_C(\nu) = \inf_{A \, \text{PAC}} \limsup_{\delta \to 0} \frac{\mathbb{E}_{\nu}[T_{\delta}]}{\log \frac{1}{\delta}}. \label{eq:KappaC}
+\kappa_C(\nu) = \inf_{S \, \text{PAC}} \limsup_{\delta \to 0} \frac{\mathbb{E}_{\nu}[T_{\delta}]}{\log \frac{1}{\delta}}. \label{eq:KappaC}
 \end{equation}
@@
 
-Consider a consistent fixed budget strategy \(\mathcal{A}\)
+Consider a consistent fixed budget strategy \(\mathcal{S}\)
 (\(p_t(\nu)\) tends to zero as \(t \rightarrow \infty\)), and define the
@@
 the lower bound on \(p_t(\nu)\). The resulting lower bound given in
-Theorem 12 of Kaufmann et al. (2016):
+Theorem 12 of Kaufmann et al. (2016). We see that the best exponent with
+which the error \(p_t(\nu)\) decreases as \(t \rightarrow \infty\) is
+based on Kullback-Leibler divergences:
 
@@
 For a proof, consider first the two different bandit models, \(\nu\) and
-\(\nu'\), where we fix w.l.o.g. \(a^* = 1\) as the best arm in \(\nu\),
-while \(a^* = 2\) in \(\nu'\). We require the algorithm \(\mathcal{A}\)
+\(\nu'\), where we fix w.l.o.g. \(i^* = 1\) as the best arm in \(\nu\),
+while \(i^* = 2\) in \(\nu'\). We require the algorithm \(\mathcal{S}\)
 to be consistent for both problems. Since we are in the fixed budget
@@
 \begin{equation*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1'|| \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2'|| \nu_2) \geq \der(\mathbb{P}_{\nu'}(A),\mathbb{P}_{\nu}(A)))
+\mathbb{E}_{\nu'}[T_1(t)]\KL(\nu_1'|| \nu_1) + \mathbb{E}_{\nu'}[T_2(t)]\KL(\nu_2'|| \nu_2) \geq \der(\mathbb{P}_{\nu'}(A),\mathbb{P}_{\nu}(A)))
 \end{equation*}
@@
 for the following: We have \(p_t(\nu) = 1 - \mathbb{P}_{\nu}(A)\) and
-\(p_t(\nu') = \mathbb{P}_{\nu'}(A)\) (since \(A\) is wrong in \(\nu'\)).
-But since algorithm \(\mathcal{A}\) is consistent for both \(\nu\) and
-\(\nu'\), we know that there should exist some number of samples such
-that the probability of event \(A\) is bigger in setting \(\nu\) (where
-it is the correct decision) than in setting \(\nu'\) (where this would
-be a wrong decision and failure). Thus, for every \(\epsilon > 0\),
-there exists \(t_0(\epsilon)\) such that for all
+\(p_t(\nu') = \mathbb{P}_{\nu'}(A)\) (since \(A\) is wrong for
+\(\nu'\)). But since algorithm \(\mathcal{A}\) is consistent for both
+\(\nu\) and \(\nu'\), we know that there should exist some number of
+samples such that the probability of event \(A\) is bigger in setting
+\(\nu\) (where it is the correct decision) than in setting \(\nu'\)
+(where this would be a wrong decision and failure). Thus, for every
+\(\epsilon > 0\), there exists \(t_0(\epsilon)\) such that for all
 \(t \geq t_0(\epsilon)\),
@@
 \limsup_{t \to \infty} - \frac{1}{t} \log p_t(\nu)
-& \leq \limsup_{t \to 0} \frac{1}{t} \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)] \KL(\nu_a' || \nu_a) \\
-& \leq \max_{a=1,2} \KL(\nu_a' || \nu_a),
+& \leq \limsup_{t \to 0} \frac{1}{t} \sum_{i=1}^2 \mathbb{E}_{\nu'}[T_i(t)] \KL(\nu_i' || \nu_i) \\
+& \leq \max_{i=1,2} \KL(\nu_i' || \nu_i),
 \end{align*}
@@
 where the last line follows from the fact that the
-\(\frac{1}{t} \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)]\) part creates a
-weighted average of the two divergences \(\KL(\nu_a', \nu_a)\). As noted
+\(\frac{1}{t} \sum_{i=1}^2 \mathbb{E}_{\nu'}[T_i(t)]\) part creates a
+weighted average of the two divergences \(\KL(\nu_i', \nu_i)\). As noted
 in Kaufmann et al. (2016), one arrives at the final result by choosing
@@
 that it makes the complexity in the fixed confidence and the fixed
-budget setting directly comparable. The disadvantage of course being
-that the result only holds for two-armed models. While the authors are
-not able to derive directly comparable lower bounds for the top-\(m\)
-case, they derive a first lower bound in the Gaussian case with equal
-variances, which we describe shortly in the appendix in
-\autoref{sec:KaufmannLBTopMGaussian}.
+budget setting directly comparable. The disadvantage being that the
+result only holds for two-armed models. While the authors are not able
+to derive directly comparable lower bounds for the top-\(m\) case, they
+derive a first lower bound in the Gaussian case with equal variances.
 
 Before we discuss algorithms given in Kaufmann et al. (2016) that match
-the lower bounds, we show how lower bounds can be derived very similarly
-for the fixed budget thresholding problem.
+the lower bounds, we show how based on the proof of Theorem 12 in
+Kaufmann et al. (2016) very similar lower bounds can be derived for the
+fixed budget thresholding problem.
 
@@
 In order to derive a bound for the fixed budget problem, Kaufmann et al.
-(2016) have focused on the setting with two arms which is the most
-simple version of the top-\(m\) problem. Less than two arms do not make
+(2016) focus on the setting with two arms which is the most simple
+version of the top-\(m\) problem. Less than two arms does not make
 sense, since the single arm is by definition the best arm. In the case
@@
 \begin{corollary}
+Consider the setting in \autoref{sec:Setup}.
 Let $\nu = \nu_1$ be a one-armed thresholding bandit model where $\tau$ is the threshold fixed upfront.
-Let $\nu$ be from the univariate exponential family of distributions such that $\nu_1$ can be parameterized by its mean, $\mu_1$, and the Kullback-Leibler divergence between distributions $\nu_1$ and $\nu_1'$ can be written as $\KL(\nu_1', \nu_1) = \KL(\mu_1', \mu_1)$.
-In the fixed budget setting, any consistent algorithm ($p_t(\nu) \rightarrow 0$ as $t \rightarrow \infty$) satisfies:
+Let $\nu$ be from the one-parameter exponential family of distributions such that $\nu_1$ can be parameterized by its mean, $\mu_1$, and the Kullback-Leibler divergence between distributions $\nu_1$ and $\nu_1'$ can be written as $\KL(\nu_1', \nu_1) = \KL(\mu_1', \mu_1)$.
+In the fixed budget setting, any consistent algorithm ($p_t(\nu) \rightarrow 0$ as $t \rightarrow \infty$) satisfies for $\mu_1' \rightarrow \tau$:
 
 $$
-- \frac{1}{t} \log p_t(\nu) \leq \KL(\tau || \mu_1)
+- \frac{1}{t} \log p_t(\nu) \leq \KL(\mu_1' || \mu_1)
 $$
@@
 two alternatives (compare chapter 11 in Cover and Thomas, 2006, or
-\autoref{theorem:ChernoffStein}). We arrive at this result as the
-one-armed bandit does not require sequential sampling: The single arm
-receives all samples. \(\mathbb{E}_{\nu'}[N_1(t)]\) is not a random
-variable but equals \(T\).
+\autoref{theorem:ChernoffStein}), in which the optimal error exponent is
+based on the Kullback-Leibler divergence. We arrive at this result as
+the one-armed bandit does not require sequential sampling: The single
+arm receives all samples. \(\mathbb{E}_{\nu'}[N_1(t)]\) is not a random
+variable but equals \(T\). The single-armed bandit is a simple
+hypothesis test.
 
@@
 \begin{corollary}
+Consider the setting in \autoref{sec:Setup}.
 Let $\nu = (\nu_1, ..., \nu_K)$ be a $K$-armed thresholding bandit problem in which $\tau$ is the threshold fixed upfront.
-For $i \in \{1,...,K\}$, let $\nu_i$ be from the univariate exponential family of distributions such that $\nu_i$ can be parameterized by its mean, $\mu_i$, and the Kullback-Leibler divergence between distributions $\nu_i$ and $\nu_i'$ can be written as $\KL(\nu_i, \nu_i') = \KL(\mu_i, \mu_i')$.
-In the fixed budget setting, any consistent algorithm satisfies:
+For $i \in \{1,...,K\}$, let $\nu_i$ be from the one-parameter exponential family of distributions such that $\nu_i$ can be parameterized by its mean, $\mu_i$, and the Kullback-Leibler divergence between distributions $\nu_i$ and $\nu_i'$ can be written as $\KL(\nu_i, \nu_i') = \KL(\mu_i, \mu_i')$.
+In the fixed budget setting, any consistent algorithm satisfies for $\mu_i' \rightarrow \tau$:
 
 $$
-\limsup_{t \rightarrow \infty} -\frac{1}{t} \log p_t(\nu) \leq \max_{a \in \{1,...,K\}} \KL(\tau || \mu_a)
+\limsup_{t \rightarrow \infty} -\frac{1}{t} \log p_t(\nu) \leq \max_{i \in \{1,...,K\}} \KL(\mu_i' || \mu_i)
 $$
@@
 \[
-\kappa_{TBP}(\nu) = \inf_{A \text{ consistent}} \Big(\limsup_{t \rightarrow \infty} - \frac{1}{t} \log p_t(\nu)\Big)^{-1} \geq K \Big(\sum_{i=1}^{K} \KL(\tau||\mu_i)\Big)^{-1}
+\kappa_{TBP}(\nu) = \inf_{S \text{ consistent}} \Big(\limsup_{t \rightarrow \infty} - \frac{1}{t} \log p_t(\nu)\Big)^{-1} \geq K \Big(\sum_{i=1}^{K} \KL(\mu_i'||\mu_i)\Big)^{-1}
 \]
@@
 \begin{equation*}
-\sum_{a \in S^*_m} \frac{1}{\KL(\theta_a || \theta_{[m+1]})} + \sum_{a \notin S^*_m} \frac{1}{\KL(\theta_a || \theta_{[m]})} \leq \kappa_C(\nu) \leq 24 \min_{\theta \in [\theta_{[m+1]},\theta_{[m]}]} \sum_{a=1}^{K} \frac{1}{\KL^*(\theta_a || \theta)},
+\sum_{i \in S^*_m} \frac{1}{\KL(\mu_i || \mu_{[m+1]})} + \sum_{i \notin S^*_m} \frac{1}{\KL(\mu_i || \mu_{[m]})} \leq \kappa_C(\nu) \leq 24 \min_{\mu \in [\mu_{[m+1]},\mu_{[m]}]} \sum_{i=1}^{K} \frac{1}{\KL^*(\mu_i || \mu)},
 \end{equation*}
@@
 where again we write with slight abuse of notation
-\(\KL(\theta || \theta') = \KL(\nu_{\theta}|| \nu_{\theta'})\) for
-\((\theta, \theta') \in \Theta^2\) as the shorthand for the
-KL-divergence of two distributions from the exponential family
-parameterized by \(\theta\) and \(\theta'\) respectively.
-\(\KL^*(\theta || \theta') = \KL(\theta^* || \theta)\) is the Chernoff
-information between the two distributions, where \(\theta^*\) is chosen
-so that \(\KL(\theta^* || \theta) = \KL(\theta^* || \theta')\).
+\(\KL(\nu_{\mu}|| \nu_{\mu'}) = \KL(\mu || \mu')\) as the shorthand for
+the KL-divergence of two distributions from the exponential family
+parameterized by \(\mu\) and \(\mu'\) respectively.
+\(\KL^*(\mu || \mu') = \KL(\mu^* || \mu)\) is the Chernoff information
+between the two distributions, where \(\mu^*\) is chosen so that
+\(\KL(\mu^* || \mu) = \KL(\mu^* || \mu')\).
 
@@
 identification problem, as discussed in Garivier and Kaufmann (2016).
-The authors also derive a lower bound on the sample complexity using the
+The authors also derive a lower bound on the sample complexity using
 Lemma \autoref{theorem:KaufmannEtAlLemma1}. Furthermore, they propose a
@@
 al. (2016). In particular, Garivier and Kaufmann (2016) focus on
-distributions \(\nu_{\theta}\) from the univariate canonical exponential
-family of distributions, which can be parameterized by their mean
-\(\mu\), and thus can be written as \(\nu_{\mu}\); as before, we
+distributions \(\nu_{\theta}\) from the one-parameter canonical
+exponential family of distributions, which can be parameterized by their
+mean \(\mu\), and thus can be written as \(\nu_{\mu}\); as before, we
 simplify the notation of the KL-divergence for these distributions to
@@
 \(\bm{\mu} \in \mathcal{S}\) has a unique maximum given by
-\(a^*(\bm{\mu})\) such that
-\(\mu_{a^*} > \max_{a \neq a^*(\bm{\mu})} \mu_a\). In order to fix the
+\(i^*(\bm{\mu})\) such that
+\(\mu_{i^*} > \max_{i \neq i^*(\bm{\mu})} \mu_i\). In order to fix the
 confidence \(1-\delta\), we specify the risk \(\delta\). Similar to the
@@
 probability is at least as small as the fixed risk level,
-\(\mathbb{P}_{\bm{\mu}}(\hat{a}_{T_{\delta}} \neq a^*) \leq \delta\). In
+\(\mathbb{P}_{\bm{\mu}}(\hat{i}_{T_{\delta}} \neq i^*) \leq \delta\). In
 order to derive the lower bound on the expected number of samples
@@
 \(w_i\) corresponds to the fraction of overall samples that arm \(i\)
-receives. We now state the lower bound:
+receives (which are random variables similar to \(T_i\) in
+\autoref{sec:UpperBoundProof}). We now state the lower bound:
 
@@
 \(\delta \in (0,1)\), \(\bm{\mu} \in \mathcal{S}\), and only consider
-\(\delta\)-PAC strategies. As before, \(N_a(t)\) describes the random
-number of pulls of arm \(a\) until time \(t\), for all \(t\geq 1\).
+\(\delta\)-PAC strategies. As before, \(T_i(t)\) describes the random
+number of pulls of arm \(i\) until time \(t\), for all \(t\geq 1\).
 Again, Lemma \ref{theorem:KaufmannEtAlLemma1} states how the risk
@@
 \begin{equation*}
-\forall \lambda \in \mathcal{S}: a^*(\lambda) \neq a^*(\mu), \sum_{a=1}^K \KL(\mu_a,\lambda_a)\mathbb{E}_{\bm{\mu}}[N_a(T_{\delta})] \geq \d(\delta, 1- \delta).
+\forall \lambda \in \mathcal{S}: i^*(\lambda) \neq i^*(\mu), \sum_{i=1}^K \KL(\mu_i,\lambda_i)\mathbb{E}_{\bm{\mu}}[T_i(T_{\delta})] \geq d(\delta, 1- \delta).
 \end{equation*}
@@
 and use the fact that
-\(\mathbb{E}_{\bm{\mu}}[T_{\delta}] = \sum_{a=1}^K \mathbb{E}_{\bm{\mu}}[N_a(T_{\delta})]\):
+\(\mathbb{E}_{\bm{\mu}}[T_{\delta}] = \sum_{i=1}^K \mathbb{E}_{\bm{\mu}}[T_i(T_{\delta})]\):
 
 \begin{align*}
-\der(\delta, 1-\delta) & \leq \inf_{\lambda \in \text{Alt}(\bm{\mu})} \mathbb{E}_{\bm{\mu}}[T_{\delta}] \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[T_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
-& = \mathbb{E}_{\bm{\mu}}[T_{\delta}] \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[T_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
-& \leq \mathbb{E}_{\bm{\mu}}[T_{\delta}] \sup_{w \in \Sigma_K} \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K w_a \KL(\mu_a, \lambda_a)\Big).
+\der(\delta, 1-\delta) & \leq \inf_{\lambda \in \text{Alt}(\bm{\mu})} \mathbb{E}_{\bm{\mu}}[T_{\delta}] \Big(\sum_{i=1}^K \frac{\mathbb{E}_{\bm{\mu}}[T_i]}{\mathbb{E}_{\mu}[T_{\delta}]} \KL(\mu_i, \lambda_i)\Big) \\
+& = \mathbb{E}_{\bm{\mu}}[T_{\delta}] \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{i=1}^K \frac{\mathbb{E}_{\bm{\mu}}[T_i]}{\mathbb{E}_{\mu}[T_{\delta}]} \KL(\mu_i, \lambda_i)\Big) \\
+& \leq \mathbb{E}_{\bm{\mu}}[T_{\delta}] \sup_{w \in \Sigma_K} \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{i=1}^K w_i \KL(\mu_i, \lambda_i)\Big).
 \end{align*}
@@
 As stated in Garivier and Kaufmann (2016), the term
-\(\frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[T_{\delta}]}\)
+\(\frac{\mathbb{E}_{\bm{\mu}}[T_i]}{\mathbb{E}_{\mu}[T_{\delta}]}\)
 gives the fraction of draws each arm receives. This value, however,
@@
 algorithm, it is replaced by the supremum over \(\Sigma_K\), which is
-the distribution over these fractions for any \(\mathcal{A}\), that is,
-for any \(\delta\)-PAC strategy.
+the distribution over these fractions for any \(\delta\)-PAC strategy.
 
@@
   \url{https://youtu.be/eLyrrYqJlkE}}, where the experimenter has to
-choose the share of samples he attributes to each arm in a way that is
+choose the share of samples she attributes to each arm in a way that is
 optimal given that nature will respond and choose the most difficult
-alternative model given his weights. Thus, to make the lower bound
+alternative model given her weights. Thus, to make the lower bound
 practical, it is a matter of finding the optimal weights
@@
 that minimize the cost from a change in distributions, that is, the term
-\(F(\bm{\mu}, \bm{w}) = \inf_{\bm{\lambda} \in \text{Alt}(\bm{\mu})} \Big(\sum_{a= 1}^K w_a \KL(\mu_a, \lambda_a)\Big)\).
+\(F(\bm{\mu}, \bm{w}) = \inf_{\bm{\lambda} \in \text{Alt}(\bm{\mu})} \Big(\sum_{i= 1}^K w_i \KL(\mu_i, \lambda_i)\Big)\).
 In the proof of Lemma 3 of Garivier and Kaufmann, it is shown that
 nature, selecting the alternative model \(\bm{\lambda}\), will always
-pick an alternative model in which only a single arm \(a\) is changed
-such that \(\lambda_a > \lambda_1\) since
+pick an alternative model in which only a single arm \(i\) is changed
+such that \(\lambda_i > \lambda_1\) since
 
 \begin{align*}
-T^*(\bm{\mu})^{-1} & = \sup_{w \in \Sigma_K} \min_{a \neq 1} \inf_{\bm{\lambda} \in \mathcal{S}: \lambda_a > \lambda_1} \sum_{a=1}^K w_a \KL(\mu_a, \lambda_a)  \\
-& = \sup_{w \in \Sigma_K} \min_{a \neq 1} \inf_{\bm{\lambda}: \lambda_a \geq \lambda_1} [w_1 \KL(\mu_1, \lambda_1)+w_a \KL(\mu_a, \lambda_a)]. \Alignyesnumber\label{eqn:ComplexityTrackStopStrategy}
+T^*(\bm{\mu})^{-1} & = \sup_{w \in \Sigma_K} \min_{i \neq 1} \inf_{\bm{\lambda} \in \mathcal{S}: \lambda_i > \lambda_1} \sum_{i=1}^K w_i \KL(\mu_i, \lambda_i)  \\
+& = \sup_{w \in \Sigma_K} \min_{i \neq 1} \inf_{\bm{\lambda}: \lambda_i \geq \lambda_1} [w_1 \KL(\mu_1, \lambda_1)+w_i \KL(\mu_i, \lambda_i)]. \Alignyesnumber\label{eqn:ComplexityTrackStopStrategy}
 \end{align*}
@@
 Consequently, \(w\) will be chosen so as to minimize \(T^*(\bm{\mu})\)
-no matter which arm \(a\) was picked. It is a minimax game, so the ideal
-solution is to keep for each arm \(a \neq 1\) the term
-\(w_1 \KL(\mu_1, \lambda_1) + w_a \KL(\mu_a, \lambda_a)\) at the same
+no matter which arm \(i\) is picked. It is a minimax game, so the ideal
+solution is to keep for each arm \(i \neq 1\) the term
+\(w_1 \KL(\mu_1, \lambda_1) + w_i \KL(\mu_i, \lambda_i)\) at the same
 level. Garivier and Kaufmann show that this can be written in terms of
@@
 \begin{equation*}
-w^*(\bm{\mu}) = \arg \max_{w \in \Sigma_K} \min_{a \neq 1} (w_1 + w_a) I_{\frac{w_1}{w_1+w_a}}(\mu_1, \mu_a)
+w^*(\bm{\mu}) = \arg \max_{w \in \Sigma_K} \min_{i \neq 1} (w_1 + w_i) I_{\frac{w_1}{w_1+w_i}}(\mu_1, \mu_i)
 \end{equation*}
@@
 which let's us furthermore conclude that these quantities are equal for
-all \(a,b \in \{2,\dots, K\}\) with
+all \(i,j \in \{2,\dots, K\}\) with
 
 \begin{equation*}
-(w_1^* + w_a^*) I_{\frac{w_1^*}{w_1^*+w_a^*}}(\mu_1, \mu_a) = (w_1^* + w_b^*) I_{\frac{w_1^*}{w_1^*+w_b^*}}(\mu_1, \mu_b),
+(w_1^* + w_i^*) I_{\frac{w_1^*}{w_1^*+w_i^*}}(\mu_1, \mu_i) = (w_1^* + w_j^*) I_{\frac{w_1^*}{w_1^*+w_j^*}}(\mu_1, \mu_j),
 \end{equation*}
@@
 
-And so by assuring the reader that there are ways to compute \(w_a^*\)
+And so by assuring the reader that there are ways to compute \(w_i^*\)
 and \(T^*\) given \(\bm{\mu}\) (see chapter 2.2 in Garivier and Kaufmann
@@
 in Garivier and Kaufmann (2016) that is able to match the lower bound.
-The main idea of the \emph{Track-and-Stop} algorithm is now to keep
-track of the optimal shares for each arm by equalizing the error
-probabilies for each arm.
+The main idea of the \emph{Track-and-Stop} algorithm is to keep track of
+the optimal shares for each arm by equalizing the error probabilies for
+each arm.
 
@@
 been pulled, are prone to lead to wrong weights. Thus, if a wrong
-estimate \(\hat{\mu}_a\) for arm \(a\) leads to a small weight \(w_a\),
+estimate \(\hat{\mu}_i\) for arm \(i\) leads to a small weight \(w_i\),
 then after a few more rounds neither the estimate nor the weight will be
@@
 Garivier and Kaufmann (2016) with the \(D-Tracking\) rule. Whenever some
-arm has received a very small number of pulls \(N_a(t)\) given the
+arm has received a very small number of pulls \(T_i(t)\) given the
 number of iterations \(t\) so far, and the number of arms \(K\) that
@@
 amount of samples so far. Else, pull the arm whose number of pulls so
-far \(N_a(t)\) is the farthest away from what its optimal share
-\(t\cdot w^*_a(\hat{\bm{\mu}}(t))\) would be. Given this sampling rule,
+far \(T_i(t)\) is the farthest away from what its optimal share
+\(t\cdot w^*_i(\hat{\bm{\mu}}(t))\) would be. Given this sampling rule,
 the authors can show in their Proposition 9 that the empirical
@@
 Stopping Rule proposed in Garivier and Kaufmann (2016) calculates for
-each arm \(a\in \{1,...K\}\) the Generalized Likelihood Ratio statistic
-with every arm \(b \in \mathcal{A}^{\setminus a}\), which for
-\(\hat{\mu}_a(t) \geq \hat{\mu}_b(t)\) can be written as
+each arm \(i\in \mathbb{A} = \{1,...K\}\) the Generalized Likelihood
+Ratio statistic with every arm \(j \in \mathbb{A}^{\setminus i}\), which
+for \(\hat{\mu}_i(t) \geq \hat{\mu}_j(t)\) can be written as
 
 \begin{equation*}
-Z_{a,b}(t) = - Z_{b,a} = N_a(t) \KL(\hat{\mu}_a(t) || \hat{\mu}_{a,b}(t)) + N_b(t) \KL(\hat{\mu}_{b}(t) || \hat{\mu}_{a,b}(t)),
+Z_{i,j}(t) = - Z_{j,i} = T_i(t) \KL(\hat{\mu}_i(t) || \hat{\mu}_{i,j}(t)) + T_j(t) \KL(\hat{\mu}_{j}(t) || \hat{\mu}_{i,j}(t)),
 \end{equation*}
@@
 \begin{equation*}
-\hat{\mu}_{a,b}(t) := \frac{N_a(t)}{N_a(t) + N_b(t)}\hat{\mu}_a(t) + \frac{N_b(t)}{N_a(t) + N_b(t)}\hat{\mu}_b(t).
+\hat{\mu}_{i,j}(t) := \frac{T_i(t)}{T_i(t) + T_j(t)}\hat{\mu}_i(t) + \frac{T_j(t)}{T_i(t) + T_j(t)}\hat{\mu}_j(t).
 \end{equation*}
@@
 Consequently, a sensible idea for a stopping rule would be that there
-has to be an arm \(a \in \{1,...,K\}\) for which
-\(Z_{a,b} \geq 0 \text{ for all } b \in \{1,...,K\}^{\setminus a}\)
+has to be an arm \(i \in \{1,...,K\}\) for which
+\(Z_{i,j} \geq 0 \text{ for all } j \in \{1,...,K\}^{\setminus i}\)
 (which is always fulfilled if there is a uniquely best arm), and we
@@
 Kaufmann, 2016) of moving from one distribution to another one in terms
-of Kullback-Leibler divergence. It is a bound on the expected likelihood
-ratio term that appears when changes in distribution are applied.
+of Kullback-Leibler divergence. It is the bound on the expected
+likelihood ratio term that appears when changes in distribution are
+applied.
 
 In the case of the fixed budget top-\(m\) arm identification problem, we
-have seen that the derivation of a lower bound on the complexity term is
+see that the derivation of a lower bound on the complexity term is
 mostly limited by the difficulty of defining an alternative problem
-\(\nu'\) to \(\nu\) that fits into the Lemma
+\(\nu'\) to \(\nu\) that fits the Lemma
 \ref{theorem:KaufmannEtAlLemma1}. But given the intuition that in
@@
 \autoref{sec:Simulation2}, we show empirically that the performance of
-the Simple Likelihood Ratio strategy can be further improved by naively
-adding the D-Tracking rule to it.
+the Simple Likelihood Ratio strategy can be further improved by adding
+the D-Tracking rule.
+
+\newpage
 
@@
 
-In \autoref{chap:ThresholdingBanditProblem} we have introduced the
+In \autoref{chap:ThresholdingBanditProblem} we introduced the
 thresholding bandit problem as proposed in Locatelli et al. (2016)
-alongside the APT algorithm. We have seen that the upper bound on the
-APT algorithm matches the lower bound for the thresholding bandit
-problem given in Locatelli et al. (2016). The algorithm also exhibits
-favorable characteristics such that its upper bound holds at any
-stopping time, and that it does not require any parameter to be known
-upfront. However, we have seen that the index and the complexity term
-\(H\) employed by the APT algorithm are the most effective for
+alongside the APT algorithm. We saw that the upper bound for the APT
+algorithm matches the lower bound for the thresholding bandit problem
+given in Locatelli et al. (2016). The algorithm also exhibits favorable
+characteristics such as its upper bound holding at any stopping time,
+and that it does not require any parameter to be tuned upfront. However,
+we have seen that the index \(B^{APT}\) and the complexity term \(H\)
+employed by the APT algorithm are the most effective for
 \(R\)-sub-Gaussian distributions. Both are related to the KL-divergence
@@
 sub-Gaussian approximation can be poor in certain cases, we motivated
-the use of information theoretic measures in an algorithm's index
-(compare \autoref{sec:DiscussionLocatelli}).
-
-Another goal can be to compare the distributions with the threshold
-based not only on the empirical mean -- as done by the APT algorithm. A
-logical extension is for example the empirical variance. After all arms
-do not necessarily have the same variance, even if they are
-sub-Gaussian. And given two arms for which we estimate the same mean, we
-would prefer to draw more samples from the arm with the larger variance.
-
-In the case of Gaussian distributions with varying variances, for
-example, it makes sense to take the variance into account; after all,
-given two Gaussians with equal mean, intuitively we would prefer to get
-a sample from the distribution of larger variance.
+information theoretic measures in an algorithm's index (compare
+\autoref{sec:DiscussionLocatelli}).
+
+Information theoretic measures are one way of taking not only the sample
+mean into account to estimate differences between distributions -- as
+done by the APT algorithm. Another logical extension is to consider
+higher moments of a distribution, like its variance. After all, arms do
+not necessarily have the same variance, even if they are sub-Gaussian
+(two arms might be \(R_1\)-sub-Gaussian and \(R_2\)-sub-Gaussian). And
+given two arms for which we estimate the same mean, we would prefer to
+draw more samples from the arm with the larger variance. The simplest
+example of this are two Normal distributions with different variances.
 
@@
 empirical variances as described in Mukherjee et al. (2017) and Zhong et
-al. (2017). We then introduce a new algorithm based on the concept of
-likelihood ratios in \autoref{sec:LikelihoodRatioForExponentialFamily}.
-Finally, we compare the performance of different algorithms based on
-simulations and real world data sets in \autoref{chap:Experiments}.
+al. (2017). We then go back to the information theoretic ideas and
+introduce a new algorithm based on the concept of likelihood ratios in
+\autoref{sec:LikelihoodRatioForExponentialFamily}. Finally, we compare
+the performance of different algorithms based on simulations and real
+world data sets in \autoref{chap:Experiments}.
 
@@
 estimates for the thresholding bandit problem. The setting they consider
-is thus very similar to the setting in Locatelli et al. (2016). The main
+is very similar to the setting in Locatelli et al. (2016). The main
 difference being that, while Locatelli et al. (2016) assume
@@
 rewards to be bounded in \([0,1]\), which makes the AugUCB applicable to
-less distributions. The AugUCB algorithm itself differs significantly
-from the APT algorithm. The two main ideas it employs are first, upper
+fewer distributions. The AugUCB algorithm itself differs significantly
+from the APT algorithm. The two main ideas it employs are, first, upper
 confidence bounds based on the Bernstein inequality and empirical
 variance estimates to compute the index based on which an arm is chosen
-at every round. Second, if an arm estimate is ``far enough away'' from
+at every round. Second, if an arm estimate is ``far enough'' away from
 the threshold as measured by the confidence bounds, it will be
-``eliminated'', and no longer be pulled until the end of the budget.
+eliminated, that is, no longer be pulled until the end of the budget.
 Both ideas are based not only on the empirical mean estimate
-\(\mu_i(t)\), but also on a term \(s_i\) that is increasing linearly in
-the estimated standard deviation. While the APT algorithm plays the arm
-minimizing the quantity
-\(B_i^{APT}(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t) = \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau| + \epsilon)\),
-AugUCB plays the arm minimizing the quantity
-\(\hat{\Delta}_i(t) - 2s_i\), where \(s_i\) is based on the variance
-estimate \(\hat{v}_i\), and an exploration \(\psi_m\) term linear in
-\(T\), as well as an elimination parameter \(\rho\) (compare Algorithm 1
-in Mukherjee et al., 2017):
+\(\hat{\mu}_i(t)\), but also on a term \(s_i\) that is increasing
+linearly in the estimated standard deviation. While the APT algorithm
+plays the arm minimizing the quantity
+\(\sqrt{T_i(t)} \hat{\Delta}_i(t)\), AugUCB plays the arm minimizing the
+quantity \(\hat{\Delta}_i(t) - 2s_i\), where \(s_i\) is based on the
+variance estimate \(\hat{v}_i\), and an exploration term \(\psi_m\)
+linear in \(T\), as well as an elimination parameter \(\rho\) (compare
+Algorithm 1 in Mukherjee et al., 2017):
 
@@
 contribution is additionally scaled by a term increasing in the arm's
-variance (see also the graph comparing the complexity terms of APT,
-AugUCB, and EVT algorithms below).
+variance (see also Figure 3 below).
 
@@
 The terms ensure that certain arms are no longer pulled when the
-algorithm is sufficiently confident in the location of true mean.
+algorithm is sufficiently confident in the location of the true mean.
 Indeed, the AugUCB algorithm goes a little further than the APT
-algorithm in that it eliminates arms (no longer considers them in
-sampling) when a separation condition is estimated to hold. The same
-separation condition of estimated mean away from the threshold is used
-in the authors' upper bound proof and is reminiscient of the separation
-condition used in Locatelli et al.'s (2016) upper bound proof.
+algorithm in that it stops to sample arms when a separation condition
+(mean separated from threshold) is estimated to hold. The same
+separation condition is used in the authors' upper bound proof and is
+reminiscient of the separation condition used in the proof of the upper
+bound in Locatelli et al.'s (2016) (compare
+\autoref{sec:CheckSeparationCondition}).
 
@@
 their upper bound, Mukherjee et al. (2017) have to bound the probability
-that an an arm is not removed from the active set after the a certain
-number of rounds -- even though the arm is above (respectively below)
-the threshold. If this probability is low, then the algorithm is able to
-be certain about an arm's true mean by employing variance estimates. In
-comparison, Locatelli et al (2016) used bounds on on how often arms are
-drawn (\(T_i\)) to give a bound on the probability of the favorable
-event. In order to derive the bound, Mukherjee et al. (2017) use the
-Bernstein inequality.
+that an arm is not removed from the active set after a certain number of
+rounds -- even though the arm is above (respectively below) the
+threshold. If this probability is small, then the algorithm is able to
+be confident in an arm's true mean by employing variance estimates. In
+order to derive the bound, Mukherjee et al. (2017) use the Bernstein
+inequality.
 
@@
 bound on the probability that an arm has not been eliminated correctly
-in round \(T_i\). Else it would not be possible to upper bound the
-\(s_i\) term by \(\Delta_i/4\) as Mukherjee et al. do in their proof.
-Thus, the distributions for which their upper bound holds are a subset
-of the \(R\)-sub-Gaussian distributions considered in Locatelli et al.
-(2016). However, while the authors demand in their setting that the
-rewards are bounded in \([0,1]\), it seems that the upper bound only
-requires the arms' variances to be bounded in \([0,1]\) such that
-\(\hat{v}_i \in [0,1]\). Thus, the upper bound should hold in particular
-for Gaussian distributions with variance \(\sigma^2 \in [0,1]\).
-Consequently, the simulations by Mukherjee et al. are performed on
-Gaussian arms with variance smaller than one.
+in round \(T_i\). Thus, the distributions for which their upper bound
+holds are a subset of the \(R\)-sub-Gaussian distributions considered in
+Locatelli et al. (2016). It would otherwise not be possible to upper
+bound the \(s_i\) term by \(\Delta_i/4\) as Mukherjee et al. do in their
+proof: With bounded rewards, the arms' variances are also bounded in
+\([0,1]\) such that \(\hat{v}_i \in [0,1]\). Yet, the simulations by
+Mukherjee et al. are performed on Gaussian arms with variance smaller
+than one, which at least makes empirical variances smaller 1 likely.
 
@@
 that the left part of the RHS gives the probability that the mean
-estimate is out of wack, while the right term gives the probability that
-the variance is overestimated. The first term is bounded by the
-Bernstein inequality. In the cumulative regret setting, there exists a
-similar decomposition for algorithms based on upper confidence bounds.
-There, the expected number of pulls of a suboptimal arm is bounded.
-Compare for example chapter 3.1 in Kaufmann, Korda and Munos (2012), in
-which the authors decompose the expected number of draws of an
-suboptimal arm into the probability that the optimal arm's mean is
-underestimated, and the probability that the upper confidence bound of
-the suboptimal arm is still very large. To give bounds for UCB
-algorithms, certain convergence rates are shown for these two
-probabilities. Mukherjee et al. do similarly for their upper confidence
-algorithm in the thresholding setting.
+estimate is poor, while the right term gives the probability that the
+variance is overestimated. The first term is bounded by the Bernstein
+inequality. In the cumulative regret setting, there exists a similar
+decomposition for algorithms based on upper confidence bounds. There,
+the expected number of pulls of a suboptimal arm is bounded. Compare for
+example chapter 3.1 in Kaufmann et al. (2012b), in which the expected
+number of draws of an suboptimal arm is decomposed into the probability
+that the optimal arm's mean is underestimated, and the probability that
+the upper confidence bound of the suboptimal arm is still very large. To
+give bounds for UCB algorithms, certain convergence rates are shown for
+these two probabilities. Mukherjee et al. do similarly for their upper
+confidence algorithm in the thresholding setting.
 
@@
 
-Another algorithm for the thresholding bandit problem employing
-empirical variance estimates is introduced in Zhong et al. (2017).
-Indeed, the authors discuss several variations of their algorithm which
-extend their central idea to applications in which several samples need
-to be pulled in a parallel and asynchronous fashion. An standard example
-known from the multi-armed bandit literature (see for example Li et al.
-(2010)) is a website for which different versions are served to visitors
-and each version is an arm in the bandit setting. If the feedback that
-is observed by the algorithm is whether or not a user makes a purchase,
-then it is likely that a new user arrives before the feedback for the
-previous user has been observed. The algorithm has to pull the next arm
-before the feedback of the previous arm has been observed. With their
-variants the authors approach this problem of having to take
-asynchronous and parallel actions. But their algorithm can also be
-reduced to a simpler version that can be compared directly with the
-problem described in Locatelli et al. (2016) where the feedback lag is
-assumed to be zero.
-
-This simpler version is the parameter-free version of their Empirical
-Variance Guided Algorithm (EVT\(_{pf}\)). The EVT\(_{pf}\) algorithm is
-an extension of the APT algorithm that takes the empirical variance of
-the arms into account and deduces an upper bound through empirical
-Bernstein bounds in a proof following the model of the one described in
-Locatelli et al. (2016).
-
-In order to describe their algorithm, we adapt a formulation used in
-Zhong et al. (2017) to describe the index used by the algorithms in a
-more general fashion. Write the index \(B_i(t+1)\) of arm \(i\) at round
-\(t\) as previously as
+A second algorithm for the thresholding bandit problem employing
+empirical variance estimates is introduced in Zhong et al. (2017). While
+they propose different algorithms for different setting of the
+thresholding bandit problem, we focus here on their strategy that can be
+compared directly with the problem described in Locatelli et al. (2016).
+
+This strategy is the parameter-free version of their Empirical Variance
+Guided Algorithm (EVT\(_{pf}\)). The EVT\(_{pf}\) algorithm is an
+extension of the APT algorithm that takes the empirical variance of the
+arms into account and deduces an upper bound through empirical Bernstein
+bounds in a proof following the model of the one described in Locatelli
+et al. (2016) (compare \autoref{sec:UpperBoundProof}).
+
+In order to describe \(EVT_{pf}\), we adapt a formulation used in Zhong
+et al. (2017) to describe the index used by the algorithms in a more
+generally. Write the index \(B_i(t+1)\) of arm \(i\) at round \(t\) as
 
@@
 \(\tau\), while \(S_i(t)\) is some confidence value measuring how
-confident we can be in \$. Thus, for the APT algorithm, if we let
-\(\epsilon = 0\) as in Zhong et al. (2016), we have
-
-\[
-D_i^{APT}(t) = \hat{\Delta}_i(t) = |\hat{\mu}_i(t) - \tau| \quad \text{and} \quad S_i^{APT}(t) = \sqrt{T_i(t)}
+confident we can be in \(D_i(t)\). Thus, for the APT algorithm, if we
+let \(\epsilon = 0\) as in Zhong et al. (2016), we have
+
+\[
+D_i^{APT}(t) = \hat{\Delta}_i(t) = |\hat{\mu}_i(t) - \tau| \quad \text{and} \quad S_i^{APT}(t) = \sqrt{T_i(t)}.
 \]
@@
 over time, as we become more confident in our sample mean, and thus
-ensures that we do not continue pulling the same arm forever.
-
-Based on this, we can now easily compare APT to EVT\(_{pf}\) for which
-the index can be written as:
+ensures that we do not pull the same arm forever. Based on this, we can
+now easily compare APT to EVT\(_{pf}\) for which the index can be
+written as:
 
@@
 empirical variance describes the shape of the distribution and thus is a
-measure of how far the distribution (in contrast to just the mean) is
-away from the threshold. It consequently makes sense to have it appear
-in \(D_i^{EVT}\). And in contrast to the APT algorithm, the EVT\(_{pf}\)
-algorithm consequently takes more information about the arms into
-account than just their mean. As mentioned previously, this should
-especially be valuable whenever arms have indeed different variances.
-Similar (very roughly) to how the Kullback-Leibler divergence measures
-distances between distributions, the \(D_i^{EVT}\) including the
-empirical variance serves as a crude measure of distance between
-threshold and distribution. We note that for a Bernoulli distributed
-random variable, \(D_i^{EVT}\) is always decreasing as the mean
-approaches the threshold (compare the figure 2). Similar should hold in
+measure of how far the distribution is away from the threshold. It
+consequently makes sense to have it appear in \(D_i^{EVT}\). And in
+contrast to the APT algorithm, the EVT\(_{pf}\) algorithm takes more
+information about the arms into account than just their mean. As
+mentioned previously, this should especially be valuable whenever arms
+have different variances. Roughly similar to how the Kullback-Leibler
+divergence measures distances between distributions, \(D_i^{EVT}\)
+including the empirical variance serves as a crude measure of distance
+between threshold and distribution. We note that for a Bernoulli
+distributed random variable, \(D_i^{EVT}\) is always decreasing as the
+mean approaches the threshold (compare figure 2). Similar should hold in
 general for bounded variables as the variance and the mean are linked by
@@
 as the bounds of the EVT\(_{pf}\) algorithm only hold for random
-variables bounded in \([0,1]\). In contrast to the AugUCB, this
-restriction is not just on the variance of the arm but explicitly on the
-reward itself in the current version that builds on empirical Bernstein
-bounds as shown in Maurer and Pontil (2009).
+variables bounded in \([0,1]\). Thus, it is limited to the same set of
+distributions as the AugUCB algorithm.
 
@@
 
-Then one can state the following theorem.
+Then one can state the following theorem with notation as in
+\autoref{sec:Setup}.
 
@@
 
-The authors approach the proof very similarly as Locatelli et al. (2016)
+The authors approach the proof very similar as Locatelli et al. (2016)
 in the proof of their lower bound. They define favorable events that
 hold with large probability, and ensure that the same separation
-condition as in Locatelli et al. holds for them given that each arm is
-pulled sufficiently often. Additionally to a favorable event that bounds
-the deviation between sample mean and population mean, they define a
-second event on which the sample standard deviation is close to the
-population standard deviation. This is bounded in large probability by
-an empirical Bernstein inequality (Maurer and Pontil, 2009). The union
-of the two events then serves as the favorable event in the remainder of
-their proof.
+condition as in Locatelli et al. holds given that each arm is pulled
+sufficiently often. Additionally to a favorable event that bounds the
+deviation between sample mean and population mean, they define a second
+event on which the sample standard deviation is close to the population
+standard deviation. This is bounded in large probability by an empirical
+Bernstein inequality (Maurer and Pontil, 2009). The union of the two
+events then serves as the favorable event in the remainder of their
+proof.
 
 Given a lower bound adapted to the new complexity
-\(H^{\text{EVT}_{pf}}\), the Zhong et al. (2017) show that the
-EVT\(_{pf}\) algorithm is optimal in that its upper bound matches the
-lower bound. Furthermore, they compare their algorithm in experiments
-against the APT algorithm. The experiments use data generated from
-uniform distributions. Each experiment compares 100 arms with variances
-picked at random from a range of possible variances. Over three
-experiments, the range of variances is varied from small to large, where
-the authors expect their algorithm to show the largest advantage
-compared to APT on the problem with small variances. Interestingly, they
-report the largest advantage of their variance based algorithms in
-comparison to APT when the variances are very small; given they only
-consider problems bounded on a support of \([0,1]\), \(\sigma_i \ll 1\).
-In this case the problem complexity \(H^{\text{EVT}_{pf}}\) can be much
-smaller than \(H^{APT}\) -- the EVT\(_{pf}\) algorithm profits more from
+\(H^{\text{EVT}_{pf}}\), Zhong et al. (2017) show that the EVT\(_{pf}\)
+algorithm is optimal in that its upper bound matches the lower bound.
+Furthermore, they compare their algorithm in experiments against the APT
+algorithm. The experiments use data generated from uniform
+distributions. Each experiment compares 100 arms with variances picked
+at random from a range of possible variances. Over three experiments,
+the range of variances is varied from small to large. They report the
+largest advantage of their variance based algorithms in comparison to
+APT when the variances are very small; given they only consider problems
+bounded on a support of \([0,1]\), \(\sigma_i \ll 1\). In this case the
+problem complexity \(H^{\text{EVT}_{pf}}\) can be much smaller than
+\(H^{APT}\) -- the EVT\(_{pf}\) algorithm profits more from
 distributions that are simple to estimate in terms of their variance
@@
 
-When comparing the two complexities for example for Bernoulli random
-variables against some fixed threshold, we see that the smaller
-complexity of the EVT\(_{pf}\) algorithm implies in particular that
-EVT\(_{pf}\) could be able to cope with distributions of parameter
-\(\mu\) close to \(\tau\) much better than APT (compare figure 3).
+When comparing the two complexities for Bernoulli random variables
+against a threshold, we see that the smaller complexity of the
+EVT\(_{pf}\) algorithm implies in particular that EVT\(_{pf}\) could be
+able to cope with distributions of parameter \(\mu\) close to \(\tau\)
+much better than APT (compare Figure 3).
 
@@
 thresholding bandit problem that builds on the idea of the likelihood
-ratio statistic for hypothesis tests. We first shortly describe the
-general idea of likelihood ratio based tests, to then introduce this new
+ratio statistic for hypothesis tests. We first describe the general idea
+of likelihood ratio based tests shortly, to then introduce the new
 algorithm for the thresholding bandit problem, which we call Simple
@@
 
-In a standard parametric testing problem, we have drawn an iid sample
-\(x = (x_1, ..., x_T)\), where each \(x_i\) is a realization from the
-random variable \(X_i\). We assume that \(X_i\) follows some probability
+In a standard parametric testing problem, we have an i.i.d. sample
+\(\bm{x} = (x_1, ..., x_T)\), where each \(x_s\) is a realization from
+the random variable \(X\). We assume that \(X\) follows some probability
 distribution \(Q(\theta)\) paramaterized by a vector \(\theta\). Let
@@
 
-In order to assess whether the \(H_0\) hypothesis can be rejected, one
-computes the likelihood \(L(x|\theta)\) of the observed sample under
-both parameterizations:
-\(L_{H_0} = L(x|\theta = \theta_{H_0}) = \prod_{i=1}^T q(x_i|\theta_{H_0})\)
+In order to assess whether the \(H_0\) hypothesis can be rejected, we
+compute the likelihood \(L(x|\theta)\) of the observed sample under both
+parameterizations:
+\(L_{H_0} = L(x|\theta = \theta_{H_0}) = \prod_{s=1}^T q(x_s|\theta_{H_0})\)
 and
@@
 
-The intuition behind the test of course being that, if the true
-parameterization is \(H_1\) and not \(H_0\), then the likelihood
-\(L_{T,H_1}\) should be larger than \(L_{T,H_0}\). A small enough
-likelihood ratio would thus lead us to a rejection of the null
-hypothesis, while a large likelihood ratio is evidence in favor of the
-null hypothesis.
+The intuition behind the test is that, if the true parameterization is
+\(H_1\) and not \(H_0\), then the likelihood \(L_{T,H_1}\) should be
+larger than \(L_{T,H_0}\). A small enough likelihood ratio would thus
+lead us to a rejection of the null hypothesis, while a large likelihood
+ratio is evidence in favor of it.
 
@@
 where \(\hat{\theta}\) is the maximum likelihood estimate of the
-parameter \(\theta\) given the sample \(x\). If we hold the \(H_0\)
-hypothesis fixed and set \(\theta_{H_1} = \hat{\theta}\) as often done
-in praxis, then with \(\KL(Q(\hat{\theta})||Q(\hat{\theta})) = 0\):
-
-\[
--\log(LR_T(\theta_{H_0}|| \theta_{H_1})) = -\log(LR_T(\theta_{H_0}|| \hat{\theta})) = \KL(Q(\hat{\theta}||Q(\theta_{H_0}))
+parameter \(\theta\) given the sample \(\bm{x}\). If we hold the \(H_0\)
+hypothesis fixed and set \(\theta_{H_1} = \hat{\theta}\), then with
+\(\KL(Q(\hat{\theta})||Q(\hat{\theta})) = 0\):
+
+\[
+-\log(LR_T(\theta_{H_0}|| \theta_{H_1})) = -\log(LR_T(\theta_{H_0}|| \hat{\theta})) = T\KL(Q(\hat{\theta}||Q(\theta_{H_0}))
 \]
@@
 Furthermore, we have for any distributions \(Q_{H_0}\) and \(Q_{H_1}\)
-for a sample \(x\) sampled from the \(H_0\) distribution, that
-
-\[
-\frac{1}{n} \log(LR_T(\theta_{H_0}||\theta_{H_1})) \rightarrow \KL(Q(\theta_{H_0})||Q(\theta_{H_1})) \quad \text{in probability},
+for a sample \(\bm{x}\) sampled from the \(H_0\) distribution, that
+
+\[
+\frac{1}{T} \log(LR_T(\theta_{H_0}||\theta_{H_1})) \rightarrow \KL(Q(\theta_{H_0})||Q(\theta_{H_1})) \quad \text{in probability},
 \]
@@
 
+Indeed, our Corollary \autoref{corollary:LB1TBP} for the one-armed
+thresholding bandit problem corresponds directly to this result, and
+shows that the thresholding bandit can be viewed as a sequential testing
+of separate hypotheses.
+
 \subsubsection{Likelihood Ratio as Index in Sequential
@@
 
-We now employ the concept of the likelihood-ratio test for a new
+We now employ the concept of the likelihood-ratio test to a new
 sequential sampling strategy for the thresholding bandit problem. In
@@
 arm, assuming distributions for which the maximum likelihood estimate of
-the mean is given by the empirical mean. In these cases, the likelihood
-ratio will be smaller than 1 and decrease in sample size even if the
-threshold and sample mean are constant.
-
-Due to these characteristics, the likelihood ratio can serve as a
-natural index for sampling strategies. Consider the setting described in
-\autoref{sec:Setup} and \autoref{sec:TheAPTAlgorithm} though without
-assuming \(R\)-sub-Gaussian distributions. Consider \(B_i^{APT}\) and
-compare it to
+the mean is given by the empirical mean. The likelihood ratio will be
+smaller than 1 and decrease in sample size even if the threshold and
+sample mean are constant.
+
+These characteristics make the likelihood ratio a natural index for
+adaptive sampling strategies (compare also Chernoff, 1958; Garivier and
+Kaufmann, 2016). Consider the setting described in \autoref{sec:Setup}
+and \autoref{sec:TheAPTAlgorithm}, and write as index:
 
@@
 
-We have \(B_i(t) \leq 1\), \(t \uparrow \rightarrow B_i(t) \downarrow\),
-and \(|\hat{\mu}_i(t) - \tau| \uparrow \rightarrow B_i(t) \downarrow\).
-Consequently, by choosing the arm that maximizes \(B_i(t)\), we choose
-an arm for which we either have not collected many samples, or for which
-the sample mean is close to the threshold \(\tau\). In this sense, a
-strategy based on the likelihood ratio is reminiscient of the index
-employed by the APT algorithm. Indeed, assuming the samples are normally
-distributed with the same variance for the distribution \(\nu_i\) under
-both \(H_0\) and \(H_1\), then \(-\log(LR(\tau||\hat{\mu}_i(t)))\)
-equals the index in APT. Why then would one use the likelihood based
-strategy?
+We have \(B_i^{LR}(t) \leq 1\),
+\(t \uparrow \rightarrow B_i^{LR}(t) \downarrow\), and
+\(|\hat{\mu}_i(t) - \tau| \uparrow \rightarrow B_i^{LR}(t) \downarrow\).
+Consequently, by choosing the arm that maximizes \(B_i^{LR}(t)\), we
+choose an arm for which we either have not collected many samples, or
+for which the sample mean is close to the threshold \(\tau\). In this
+sense, a strategy based on the likelihood ratio is reminiscient of the
+index employed by the APT algorithm. Indeed, assuming the samples are
+normally distributed with equal variance for all arms under both \(H_0\)
+and \(H_1\), \(-\log(B_i^{LR}(t))\) equals the index in APT. Why then
+would we prefer the likelihood based strategy?
 
 Given that the APT index and the likelihood-ratio based index are only
-equivalent for normally distributed random variables with fixed standard
-deviation, the new strategy promises efficiency improvements whenever
-the true distribution is known and different from the normal
-distribution. The most important example are Bernoulli arms with small
-means as motivated. While the likelihood ratio can in theory be used for
-any distributions, and arms could even have different classes of
-distributions, the class of distribution has to be known upfront for
-every arm. Given the role of the threshold \(\tau\) and the goal of
-classification of the mean against \(\tau\), the likelihood ratio
-strategy is arguably most naturally employed on distributions
-parameterized by their mean. In the following descriptions, we thus
-focus on univariate distributions of the exponential family.
-Additionally, we also propose a version for the Normal distribution with
-unknown mean. Before we describe the algorithm, we show that the
-likelihood ratio has a very convenient form for this family of
-distributions.
-
-\subsubsection{\texorpdfstring{Likelihood Ratio for Univariate
+equivalent for normally distributed arms with equal variances, the new
+strategy promises efficiency improvements whenever the true distribution
+is known and different from the normal distribution. The most important
+example are Bernoulli arms with small means as motivated above. While
+the likelihood ratio can in theory be used for any distributions, and
+arms could even have different classes of distributions, the class of
+distribution has to be known upfront for every arm. Given the role of
+the threshold \(\tau\) and the goal of classification of the mean
+against \(\tau\), the likelihood ratio strategy is most naturally
+employed on distributions parameterized by their mean. In the following
+descriptions, we thus focus on one-parameter distributions of the
+exponential family. Additionally, we also propose a version for the
+Normal distribution with unknown mean. Before we describe the algorithm,
+we show that the likelihood ratio has a convenient form for this
+distribution family.
+
+\subsubsection{\texorpdfstring{Likelihood Ratio for One-Parameter
 Exponential Family of Distributions
-\label{sec:LRforUnivariateExponentialFamily}}{Likelihood Ratio for Univariate Exponential Family of Distributions }}\label{likelihood-ratio-for-univariate-exponential-family-of-distributions}
+\label{sec:LRforUnivariateExponentialFamily}}{Likelihood Ratio for One-Parameter Exponential Family of Distributions }}\label{likelihood-ratio-for-one-parameter-exponential-family-of-distributions}
 
@@
 \(b'^{-1}(\theta)\). Consequently, one can just as well parameterize the
-distribution its mean \(\mu = \mathbb{\nu_{\theta}}\) and write
+distribution by its mean \(\mu = \mathbb{\nu_{\theta}}\) and write
 \(\nu_{b'^{-1}(\mu)}\) with the probability density function (compare
@@
 \[
-q(x|b'^{-1}(\mu)) = h(x) \exp(T(x) b'^{-1}(\mu) - b(b'^{-1}(\mu))).
+q(x|b'^{-1}(\mu)) = h(x) \exp(S(x) b'^{-1}(\mu) - b(b'^{-1}(\mu))).
 \]
@@
 \[
-LR(b'^{-1}(\mu_0)||b'^{-1}(\mu_1)) = \prod_{i=1}^n \frac{\exp(T(x_i) b'^{-1}(\mu_0) - b(b'^{-1}(\mu_0)))}{\exp(T(x_i) b'^{-1}(\mu_1) - b(b'^{-1}(\mu_1)))}
+LR_T(b'^{-1}(\mu_0)||b'^{-1}(\mu_1)) = \prod_{s=1}^T \frac{\exp(S(x_s) b'^{-1}(\mu_0) - b(b'^{-1}(\mu_0)))}{\exp(S(x_s) b'^{-1}(\mu_1) - b(b'^{-1}(\mu_1)))}
 \]
@@
 \[
--\log(LR) = n\Big(b\big(b'^{-1}(\mu_0)) - b(b'^{-1}(\mu_1)\big)\Big) - \Big(b'^{-1}(\mu_0)-b'^{-1}(\mu_1)\Big)\sum_{i=1}^nT(x_i)
-\]
-
-As we will see now, this statistic takes a very convenient closed form
-for many common distributions.
+-\log(LR_T) = T\Big(b\big(b'^{-1}(\mu_0)) - b(b'^{-1}(\mu_1)\big)\Big) - \Big(b'^{-1}(\mu_0)-b'^{-1}(\mu_1)\Big)\sum_{i=1}^nS(x_i)
+\]
+
+As we will see now, the last equation takes a convenient form for many
+common distributions.
 
@@
 
-We have \(T(x_i) = x_i\), \(\theta = \log(\mu/(1-\mu))\),
+We have \(S(x_s) = x_s\), \(\theta = \log(\mu/(1-\mu))\),
 \(\Theta = (0,1)\), \(b(\theta) = \log(1+\exp(\theta))\), and
@@
 \begin{align*}
--\log(LR(\mu_0||\mu_1)) & = n(\log\Big(\frac{1-\mu_0}{1-\mu_1}\Big)) - \Big(\log(\frac{\mu_0}{1-\mu_0}) - \log(\frac{\mu_1}{1-\mu_1})\Big)\sum_{i=1}^{n}x_i \\
+-\log(LR_T(\mu_0||\mu_1)) & = T(\log\Big(\frac{1-\mu_0}{1-\mu_1}\Big)) - \Big(\log(\frac{\mu_0}{1-\mu_0}) - \log(\frac{\mu_1}{1-\mu_1})\Big)\sum_{s=1}^{T}x_i \\
 & = n \Big( (1-\hat{\mu})\log\Big(\frac{1-\mu_1}{1-\mu_0}\Big) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}) \Big)
@@
 \[
--\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n \Big(\hat{\mu}\log\big(\frac{\hat{\mu}}{\tau}\big) + (1-\hat{\mu})\log\big(\frac{1-\hat{\mu}}{1-\tau}\big)\Big)
+-\log(LR_T(\tau||\hat{\mu})) = T\KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) =  = T \KL(\hat{\mu}||\tau) = n \Big(\hat{\mu}\log\big(\frac{\hat{\mu}}{\tau}\big) + (1-\hat{\mu})\log\big(\frac{1-\hat{\mu}}{1-\tau}\big)\Big)
 \]
@@
 
-We have \(T(x_i) = x_i\), \(\theta = \log(\mu)\),
+We have \(S(x_s) = x_s\), \(\theta = \log(\mu)\),
 \(\Theta = \mathbb{R}\), \(b(\theta) = \exp(\theta)\), and
@@
 \[
--\log(LR(\mu_0||\mu_1)) = n(\mu_0 - \mu_1) - (\log(\mu_0) - \log(\mu_1))\sum_{i=1}^n x_i = n\Big((\mu_0 - \mu_1) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}\Big)\Big)
+-\log(LR_T(\mu_0||\mu_1)) = T(\mu_0 - \mu_1) - (\log(\mu_0) - \log(\mu_1))\sum_{s=1}^T x_s = T\Big((\mu_0 - \mu_1) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}\Big)\Big)
 \]
@@
 \[
--\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n\Big((\tau - \hat{\mu}) + \hat{\mu}\log\Big(\frac{\hat{\mu}}{\tau}\Big)\Big)
+-\log(LR_T(\tau||\hat{\mu})) = T \KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = T \KL(\hat{\mu}||\tau) = T\Big((\tau - \hat{\mu}) + \hat{\mu}\log\Big(\frac{\hat{\mu}}{\tau}\Big)\Big)
 \]
@@
 
-We have \(T(x_i) = x_i\), \(\theta = \mu/\sigma^2\),
+We have \(S(x_s) = x_s\), \(\theta = \mu/\sigma^2\),
 \(\Theta = \mathbb{R}\), \(b(\theta) = \sigma^2\theta^2/2\),
@@
 \[
--\log(LR(\mu_0||\mu_1)) = n (\frac{\mu_0^2}{2\sigma^2} - \frac{\mu_1^2}{2\sigma^2}) - (\frac{\mu_0}{\sigma^2} - \frac{\mu_1}{\sigma^2})\sum_{i=1}^nx_i = n\frac{1}{2\sigma^2}\Big(\mu_0^2-\mu_1^2 - 2\mu_0\hat{\mu} + 2\mu_1\hat{\mu}\Big)
+-\log(LR_T(\mu_0||\mu_1)) = T (\frac{\mu_0^2}{2\sigma^2} - \frac{\mu_1^2}{2\sigma^2}) - (\frac{\mu_0}{\sigma^2} - \frac{\mu_1}{\sigma^2})\sum_{s=1}^Tx_s = T\frac{1}{2\sigma^2}\Big(\mu_0^2-\mu_1^2 - 2\mu_0\hat{\mu} + 2\mu_1\hat{\mu}\Big)
 \]
@@
 \[
--\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n\frac{(\hat{\mu} - \tau)^2}{2\sigma^2}.
+-\log(LR_T(\tau||\hat{\mu})) = T\KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = T \KL(\hat{\mu}||\tau) = T\frac{(\hat{\mu} - \tau)^2}{2\sigma^2}.
 \]
@@
 
-We have \(T(x_i) = x_i\), \(\theta = -\alpha/\mu\),
+We have \(S(x_s) = x_s\), \(\theta = -\alpha/\mu\),
 \(\Theta = (-\infty, 0)\), \(b(\theta) = -\alpha \log(-\theta)\),
@@
 \[
--\log(LR(\mu_0||\mu_1)) = n\alpha(-\log(\frac{\alpha}{\mu_0}) - \log(\frac{\mu_1}{\alpha})) - (-\frac{\alpha}{\mu_0} + \frac{\alpha}{\mu_1})\sum_{i=1}^{n}x_i = n\alpha \Big(\log\big(\frac{\mu_0}{\mu_1}\big) - \frac{\hat{\mu}}{\mu_1} + \frac{\hat{\mu}}{\mu_0}\Big).
+-\log(LR_T(\mu_0||\mu_1)) = T\alpha(-\log(\frac{\alpha}{\mu_0}) - \log(\frac{\mu_1}{\alpha})) - (-\frac{\alpha}{\mu_0} + \frac{\alpha}{\mu_1})\sum_{s=1}^{T}x_s = T\alpha \Big(\log\big(\frac{\mu_0}{\mu_1}\big) - \frac{\hat{\mu}}{\mu_1} + \frac{\hat{\mu}}{\mu_0}\Big).
 \]
@@
 \[
--\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n\alpha \Big(\frac{\hat{\mu}}{\tau} - 1 - \log\big(\frac{\hat{\mu}}{\tau}\big)\Big).
+-\log(LR_T(\tau||\hat{\mu})) = T \KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = T \KL(\hat{\mu}||\tau) = T\alpha \Big(\frac{\hat{\mu}}{\tau} - 1 - \log\big(\frac{\hat{\mu}}{\tau}\big)\Big).
 \]
@@
 
-Consider again the setting in \autoref{sec:Setup} though without the
-assumption of \(R\)-sub-Gaussian distributions. Instead, assume that the
-class of distributions that the arms \(i \in \mathbb{A}\) follow is
-known upfront. For the 1D-SLR algorithm, we restrict the potential
-classes to the univariate exponential family of distributions and write
-the class generally as \(\nu(\mu, \theta)\). Here, \(\theta\) describes
-additional parameters known upfront, as for example
-\(\sigma_1, ..., \sigma_K\) for Normal distributions, or
-\(\alpha_1, ..., \alpha_K\) for Gamma distributions. Additionally to
-\(\nu(\mu)\), the 1D-SLR algorithm receives as input the definition of
-the problem \((\tau, \epsilon)\) (compare Locatelli et al., 2016). As
-initialization, the algorithm pulls each arm once. At time \(t>K\), the
-algorithm updates the number of pulls for arm \(i\) at time \(t\),
-\(T_i(t)\), for each arm, as well as the empirical mean
-\(\hat{\mu}_i(t)\) of arm \(i\) after \(T_i(t)\) pulls. The empirical
-mean is calculated for each arm \(k\in \{1,...,K\}\) as
+We now define the Simple Likelihood Ratio Algorithm for the
+one-parameter exponential family of distributions (1D-SLR). Consider
+again the setting in \autoref{sec:Setup} though without the assumption
+of \(R\)-sub-Gaussian distributions. Instead, assume that the
+distributions \(\nu_i\) of arms \(i \in \mathbb{A}\) are all the same
+distribution from the one-parameter exponential family of distributions.
+We write this class of distributions as \(\nu(\mu, \theta)\). While
+\(\mu\) is the unknown mean parameter, \(\theta\) describes potentially
+\emph{known} parameters, as for example \(\sigma_1, ..., \sigma_K\) for
+Normal distributions, or \(\alpha_1, ..., \alpha_K\) for Gamma
+distributions. Additionally to \(\nu(\mu, \theta)\), the 1D-SLR
+algorithm receives as input the definition of the problem
+\((\tau, \epsilon)\). As initialization, the algorithm pulls each arm
+once. At time \(t>K\), the algorithm updates the number of pulls for arm
+\(i\) at time \(t\), \(T_i(t)\), for each arm, as well as the empirical
+mean \(\hat{\mu}_i(t)\) of arm \(i\) after \(T_i(t)\) pulls. The
+empirical mean is calculated for each arm \(k\in \{1,...,K\}\) as
 \(\hat{\mu}_i(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)} x_{i,s}\), with
@@
 likelihood estimate of the arm's mean. As in Locatelli et al. (2016),
-the \(X_{i,s}\) is the sample received when pulling arm \(i\) for the
+\(X_{i,s}\) is the sample received when pulling arm \(i\) for the
 \(s\)-th time. Depending on the distribution, the algorithm then
@@
 }
-\caption{SLR algorithm for univariate exponential family of distributions}\label{algo_slr_1d}
+\caption{SLR algorithm for one-parameter exponential family of distributions.}\label{algo_slr_1d}
 \end{algorithm}
@@
 
-As soon as we move away from univariate distributions parameterized by
-their mean, it becomes less clear how the likelihood ratio for
+As soon as we move away from one-parameter distributions parameterized
+by their mean, it becomes less clear how the likelihood ratio for
 \(H_0: \mu = \tau\) and \(H_1: \mu = \hat{\mu}\) should be calculated.
@@
 variance, given that the variance and mean estimate are linked, we can
-use
-\(H_0: \mu = \tau \land \sigma^2 = \sigma^2_{\tau} = \frac{1}{n}\sum_{i=1}^{n}(x_i-\tau)^2\)
-and the alternative hypothesis based on the maximum likelihood estimates
-\(H_1: \mu = \hat{\mu} \land \sigma^2 = \hat{\sigma}^2 = \frac{1}{n}\sum_{i=1}^{n}(x_i-\hat{\mu})^2\).
-In the following, we assume \(\epsilon = 0\) for simplicity.
-
-At each round \(t\), the algorithm computes \(T_i(t)\) and
-\(\hat{\mu}_i(t)\) as before, and additionally the empirical variances
+use \[
+H_0: \mu_0 = \tau \land \sigma_0^2 = \sigma^2_{\tau} = \frac{1}{n}\sum_{i=1}^{n}(x_i-\tau)^2 \quad \text{vs.} \quad H_1: \mu_1 = \hat{\mu} \land \sigma_1^2 = \hat{\sigma}^2 = \frac{1}{n}\sum_{i=1}^{n}(x_i-\hat{\mu})^2
+\]
+
+In the following, we assume \(\epsilon = 0\) for simplicity. At each
+round \(t\), the algorithm computes \(T_i(t)\) and \(\hat{\mu}_i(t)\) as
+before, and additionally the empirical variances
 \(\sigma_{\tau,i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\tau)^2\)
@@
 
-Then, as for the univariate case, the next arm to be pulled is the
-minimizer of the index \(B_i^{SLR_{2D}}(t+1)\),
-\(I_{t+1} = \arg \min_{i \leq K} B_i(t+1)\). At the end of the horizon
-\(T\), the algorithm outputs the set of arms
+The next arm to be pulled is the minimizer of the index
+\(B_i^{2DSLR}(t+1)\), \(I_{t+1} = \arg \min_{i \leq K} B_i(t+1)\). At
+the end of the horizon \(T\), the algorithm outputs the set of arms
 \(\hat{S}_\tau = \{i \in \mathbb{A}, \hat{\mu}_i(T) \geq \tau\}\).
@@
 }
-\caption{2D-SLR algorithm for Normal distributions with unknown mean and unknown variance}\label{algo_slr_2d}
+\caption{2D-SLR algorithm for Normal distributions with unknown mean and variance.}\label{algo_slr_2d}
 \end{algorithm}
@@
 improves upon the Anytime Parameter Free algorithm introduced in
-Locatelli et al. (2016) for the thresholding bandit problem in two
-points. First, we wanted to make the algorithm perform better in
-problems with arms that are not well approximated as sub-Gaussian; in
-particular a problem with Bernoulli arms of small means, and with a
-threshold close to 0. We thus tried to find a strategy that takes more
-information about the arms into account than purely the sample mean.
-With the Simple Likelihood Ratio strategy, we propose an algorithm that
-fulfills this goal at the cost of being distribution specific.
+Locatelli et al. (2016) for the thresholding bandit problem. We aimed to
+make the algorithm perform better in problems with arms that are not
+well approximated as sub-Gaussian; in particular a problem with
+Bernoulli arms of small means, and with a threshold close to 0. We thus
+tried to find a strategy that takes more information about the arms into
+account than only the sample mean. With the Simple Likelihood Ratio
+strategy, we propose an algorithm that fulfills this goal at the cost of
+being distribution specific.
 
@@
 have shown however, that the SLR strategy can be adapted to all
-univariate distributions in the exponential family of distributions. The
-algorithm even offers a natural adaptation to the problem of normal
+one-parameter distributions in the exponential family of distributions.
+The algorithm even offers a natural adaptation to the problem of normal
 distributions with unknown mean and unknown variance.
@@
 Furthermore, the SLR strategy reduces to the APT strategy in the case
-where arms are normally distributed with equal variance that is known
-upfront. In that case we have as index (compare example 3 above): \[
+where arms are normally distributed with known, equal variances. In this
+case we have as index (compare example 3 above): \[
 B_i^{SLR}(t) = T_i(t)\frac{(\hat{\mu}_i(t) - \tau)^2}{2\sigma^2}.
@@
 
-Given that in all other cases the SLR is able to take more information
-about the distributions into account through the Kullback-Leibler
-divergence (in the case of the exponential family of distributions), the
-algorithm is expected to improve upon the APT strategy. Just consider a
-situation of known, but different variances for Normal distributions.
-Then we had in \autoref{eqn:SLRWithKnownVar} \(\sigma_i^2\) and
-\(\sigma_j^2\) instead of \(\sigma^2\), which should lead to more pulls
-of the arm with larger variance. This is not taken into account by APT.
+Thus, SLR achieves the same upper bound as APT on this problem. Given
+that in all other cases the SLR is able to take more information about
+the distributions into account through the Kullback-Leibler divergence
+(in the case of the exponential family of distributions), the algorithm
+is expected to improve upon the APT strategy.
 
@@
 algorithm, there are no parameters which need to be tuned upfront as is
-usually the case for upper-confidence bound based algorithms (see for
+often the case for upper-confidence bound based algorithms (see for
 example UCB-E in Audibert et al., 2010).
@@
 again as \[
-B_i(t) = S_i(t) D_i(t),
-\] where \(S_i(t)\) is a confidence term of the estimate of the arm
-\(i\) at time \(t\), and \(D_i(t)\) is a measure of distance between the
-distribution of arm \(i\) and the threshold \(\tau\). The index of the
-Simple Likelihood Ratio strategy for univariate exponential family
-distributions can then be written with \[
-S_i(t) = T_i(t) \quad \text{and} \quad
-D_i(t) = \KL(\hat{\mu}_i(t)||\tau),
+B_i^{SLR}(t) = S_i^{SLR}(t) D_i^{SLR}(t),
+\] where \(S_i^{SLR}(t)\) is the confidence term and \(D_i^{SLR}(t)\) is
+the measure of distance between the distribution of arm \(i\) and the
+threshold \(\tau\). The index of the Simple Likelihood Ratio strategy
+for one-parameter exponential family distributions can then be written
+with \[
+S_i^{SLR}(t) = T_i(t) \quad \text{and} \quad
+D_i^{SLR}(t) = \KL(\hat{\mu}_i(t)||\tau),
 \] where we employ the number of pulls so far for a given arm as the
@@
 improve significantly upon the APT strategy in many cases.
+
+\newpage
 
@@
 \end{figure}
+
+\newpage
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-1-1}
+{\centering \includegraphics[width=0.7\linewidth]{Draft_files/figure-latex/unnamed-chunk-1-1}
 
@@
 
+J.-Y. Audibert, S. Bubeck, and R. Munos. Best Arm Identification in
+Multi-Armed Bandits. In \emph{Proceedings of the 23rd Conference on
+Learning Theory}, 2010.\par
+
+E. Brochu, V.M. Cora, and N. de Freitas. A Tutorial on Bayesian
+Optimization of Expensive Cost Functions, with Application to Active
+User Modeling and Hierarchical Reinforcement Learning, \emph{arXiv
+preprint arXiv:1012.2599}, 2010. \par
+
+S. Bubeck and N. Cesa-Bianchi. Regret analysis of stochastic and
+nonstochastic multi-armed bandit problems. \emph{Foundations and Trends
+in Machine Learning}, 5:1--122, 2012.\par
+
+S. Bubeck, N. Cesa-Bianchi, and G. Lugosi. Bandits with heavy tail.
+\emph{Information Theory, IEEE Transactions on}, 59(11):7711-7717,
+2013.\par
+
+A.N. Burnetas and M.N. Katehakis. Optimal adaptive policies for
+sequential allocation problems. \emph{Advances in Applied Mathematics},
+17:122--142, 1996.\par
+
+O. Capp´e, A. Garivier, O-A. Maillard, R. Munos, and G. Stoltz.
+Kullback-Leibler upper confidence bounds for optimal sequential
+allocation. \emph{Annals of Statistics}, 41(3):1516--1541, 2013a.\par
+
+O. Capp´e, A. Garivier, O.-A. Maillard, R. Munos, G. and Stoltz. Supple-
+ment to ``Kullback--Leibler upper confidence bounds for optimal
+sequential allocation.'', \emph{Annals of Statistics},
+\url{DOI:10.1214/13-AOS1119SUPP}, 2013b. \par
+
+H. Chernoff. Sequential Design of Experiments. \emph{The Annals of
+Mathematical Statistics}, 30(3):755-770, 1959. \par
+
+J.C. Gittins. Bandit processes and dynamic allocation indices.
+\emph{Journal of the Royal Statistical Society}. 41(2):148--177,
+1979.\par
+
+A. Garivier and E. Kaufmann. Optimal Best Arm Identification with Fixed
+Confidence. In \emph{JMLR Workshop and Conference Proceedings
+(Conference on Learning Theory)}, 49:1-30, 2016.\par
+
+E. Kaufmann and S. Kalyanakrishnan. Information Complexity in Bandit
+Subset Selection. In \emph{JMLR Workshop and Conference Proceedings
+(Conference on Learning Theory)}, 30:228--251, 2013.\par
+
+E. Kaufmann, O. Capp´e, and A. Garivier. On Bayesian Upper Confidence
+Bounds for Bandit Problems. In \emph{Proceedings of the 15th
+International Conference on Artificial Intelligence and Statistics
+(AISTATS)}, 2012.\par
+
+E. Kaufmann, O. Capp´e, A. Garivier. On the Complexity of Best Arm
+Identification in Multi-Armed Bandit Models. Journal of Machine Learning
+Research, 17:1-42, 2016.\par
+
+T.L. Lai and H. Robbins. Asymptotically efficient adaptive allocation
+rules. \emph{Advances in Applied Mathematics}, 6:4--22, 1985.\par
+
+A. Locatelli, M. Gutzeit, and A. Carpentier. An optimal algorithm for
+the Thresholding Bandit Problem. In \emph{Proceedings of the 33rd
+International Conference on Machine Learning}, JMLR: W\&CP 48, 2016.\par
+
+S. Mukherjee, K.P. Naveen, N. Sudarsanam, and B. Ravindran. Thresholding
+Bandits with Augmented UCB. 2017. \emph{arXiv preprint
+arXiv:1704.02281}, 2015.\par
+
+H. Robbins. Some aspects of the sequential design of experiments.
+\emph{Bulletin of the American Mathematical Society}, 58:527-535,
+1952.\par
+
+D. Russo. Simple Bayesian Algorithms for Best Arm Identification. In
+\emph{JMLR Workshop and Conference Proceedings (Conference on Learning
+Theory)}, 2016.\par
+
+W.R. Thompson. On the likelihood that one unknown probability exceeds
+another in view of the evidence of two samples. \emph{Biometrika},
+25:285--294, 1933.\par
+
+W.R. Thompson. On the Theory of Apportionment. \emph{American Journal of
+Mathematics}, 57:450--456, 1933.\par
+
+J. Zhong, Y. Huang, and J. Liu. Asynchronous Parallel Empirical Variance
+Guided Algorithms for the Thresholding Bandit Problem. \emph{arXiv
+preprint arXiv:1704.04567}, 2017.\par
+
 \newpage
@@
 in the case of a single arm. But first, consider again that we are in
-the thresholding bandit problem with \(K\) arms of univariate canonical
-exponential family distributions that are parameterized by their means
-\(\mu_1, ..., \mu_K\) for the original problem
+the thresholding bandit problem with \(K\) arms of one-parameter
+canonical exponential family distributions that are parameterized by
+their means \(\mu_1, ..., \mu_K\) for the original problem
 \(\nu = (\nu_1, ..., \nu_K)\). W.l.o.g, assume that all arms are above

### 2017-09-10 real_experiments/real_exp_1week_2_onearmless.R

@@ -1,0 +1,288 @@
+####################################################################
+
+# This script loads real data for 10 products out of 197 products.
+# We look at 10080 rounds per iteration so as to cover a whole week.
+# This is useful to account for seasonality effects in the data (if
+# looking at uniformly sampled data).
+
+####################################################################
+
+sessions_threshold <- 0
+set.seed(357458)
+selected_products <- sample(1:197, 10)
+niter <- 5000
+nrounds <- 10080 # These two values give the maximum size data 
+nahead <- 10080  # possible given the data set size we have
+source("/Users/timradtke/Desktop/thesis_data/get_dataset.R")
+
+dim(pv_list[[1]])
+pv_list[[1]]
+
+pv_list[[1]]
+pv_list[[5000]]
+tail(pv_list[[5000]])
+round(pv_next_means[[5000]],4)
+round(pv_next_means[[1]],4)
+
+####################################################################
+
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/AugUCB/"
+source(paste0(current_path, "run_from_data.R"))
+source(paste0(current_path, "run_parallelized_from_data.R"))
+current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/"
+
+####################################################################
+
+data_amo4 <- pv_list
+data_amo4_wide <- pv_products_wide
+data_amo4_own_means <- pv_own_means
+data_amo4_next_means <- pv_next_means
+data_amo4_mean_secondhalf <- colMeans(data_amo4_wide[15081:25160,])
+data_amo4_mean_middlehalf <- colMeans(data_amo4_wide[10081:20160,])
+data_amo4_mean_firsthalf <- colMeans(data_amo4_wide[1:15080,])
+save(data_amo4, file = paste0(current_path, "data_amo4.Rda"))
+save(data_amo4_wide, file = paste0(current_path, "data_amo4_wide.Rda"))
+save(data_amo4_own_means, file = paste0(current_path, "data_amo4_own_means.Rda"))
+save(data_amo4_next_means, file = paste0(current_path, "data_amo4_next_means.Rda"))
+save(data_amo4_mean_firsthalf, file = paste0(current_path, "data_amo4_mean_firsthalf.Rda"))
+save(data_amo4_mean_secondhalf, file = paste0(current_path, "data_amo4_mean_secondhalf.Rda"))
+rm(pv_list, pv_own_means, pv_next_means, pv_products_wide)
+gc()
+
[…]

### 2017-09-10 synthetic_experiments/poisson/exp_pois_2.R

@@ -44,6 +44,7 @@ lines(log(pois2_comp_UNIFORM), col = "black")
 lines(log(pois2_comp_APT), col = "darkgreen")
 lines(log(pois2_comp_LR), col = "blue")
 lines(log(pois2_comp_EVT), col = "red")
+lines(log(pois2_comp_AugUCB), col = "red")
 
 ########################################################################
 # Poisson Likelihood Ratio

### 2017-09-18 Thesis/20170916_Draft.Rmd
Printed version

--- 2017-09-10 Thesis/Draft.Rmd
@@
 Is the restaurant trendy?
+See \autoref{sec:Foursquare} for what this information looks like in the Foursquare app.
 
@@
 $\mathbb{E}_{\nu'}[N_1(t)]$ is not a random variable but equals $T$.
-The single-armed bandit is a simple hypothesis test.
+The single-armed bandit is a simple hypothesis test on a sample of size $T$.
+In a way, it is a degenerate case of a multi-armed bandit problem.
+
+We present the proofs of \autoref{sec:LBTBP} in the appendix in \autoref{sec:corollaryLBTBPproof}.
+While we were hoping to also prove a lower bound for the $K$-armed bandit problem, we were not able to do so as this entails the expectation under the alternative problem of the number of times the changed arm $a$ is pulled.
+Compare to the proof for the two-armed pure exploration bandit in Kaufmann et al.
+(2016).
 
@@
 $$
-\end{corollary}\label{corollary:LBKTBP}
-
-We present the proofs of \autoref{sec:LBTBP} in the appendix in \autoref{sec:corollaryLBTBPproof}.
-Corresponding to the complexity measures defined in equation $(1)$ of Kaufmann et al.
+\end{corollary} Corresponding to the complexity measures defined in equation $(1)$ of Kaufmann et al.
 (2016), we can define the complexity $\kappa_{TBP}(\nu)$ in the thresholding bandit problem and lower bound it:
@@
 index <- c(rep(10:2000, times = 4), 10:4000, 20:2000)
-alg_res <- log(c(loc2_comp_UNIFORM_2000, loc2_comp_APT_2000, 
+alg_res <- (c(loc2_comp_UNIFORM_2000, loc2_comp_APT_2000, 
                  loc2_comp_AugUCB_2000, loc2_comp_LR_2000,
@@
   geom_line(aes(group = names, color = names)) +
-  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
-  labs(subtitle = "Dashed Line indicates Error = 0.1.",
-       y = "log(Error)", x = "Round Index") + 
+  #geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
+  labs(#subtitle = "Dashed Line indicates Error = 0.1.",
+       y = "Error (log10 scale)", x = "Round Index") + 
   coord_cartesian(xlim = c(0,2000)) +
   scale_color_discrete(name = "Algorithm") + 
-  theme_bw() #+
+  theme_bw() +
+  scale_y_log10() #+
   #theme(legend.position = "bottom")
@@
 index <- c(rep(10:7000, times = 6), 20:7000)
-alg_res <- log(c(loc6nt_comp_UNIFORM_7000, loc6nt_comp_APT_7000,
+alg_res <- (c(loc6nt_comp_UNIFORM_7000, loc6nt_comp_APT_7000,
                  loc6nt_comp_AugUCB_7000, loc6nt_comp_LR_7000,
@@
 index <- c(rep(11:10000, times = 6), 22:10000)
-alg_res <- log(c(loc7nt_comp_UNIFORM_10000, loc7nt_comp_APT_10000,
+alg_res <- (c(loc7nt_comp_UNIFORM_10000, loc7nt_comp_APT_10000,
                  loc7nt_comp_AugUCB_10000, loc7nt_comp_LR_10000,
@@
   geom_line(aes(group = Algorithm, color = Algorithm)) +
-  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
+  #geom_hline(aes(yintercept = (0.1)), linetype = 2) +
   facet_grid(.~Simulation, scales = "free") +
-  labs(subtitle = "Dashed Line indicates Error = 0.1.",
-       y = "log(Error)", x = "Round Index") +
+  labs(#subtitle = "Dashed Line indicates Error = 0.1.",
+       y = "Error (log10 scale)", x = "Round Index") +
   scale_color_discrete(name = "Algorithm") +
   theme_bw() + 
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom") +
+  scale_y_log10()
 ```
 
-```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '70%', fig.cap = "Budget allocation across arms for APT and SLR algorithms in simulation 2."}
+```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Budget allocation across arms for APT and SLR algorithms in simulation 2."}
 load(file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/loc6nt_ma.Rda")
@@
 index <- c(rep(20:4000, times = 4), 40:4000)
-alg_res <- log(c(exp2_comp_UNIFORM, exp2_comp_APT, exp2_comp_LR,
+alg_res <- (c(exp2_comp_UNIFORM, exp2_comp_APT, exp2_comp_LR,
                  exp2_comp_AugUCB, exp2_comp_EVT))
@@
   geom_line(aes(group = Algorithm, color = Algorithm)) +
-  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
-  labs(subtitle = "Dashed Line indicates Error = 0.1.",
+  #geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
+  labs(#subtitle = "Dashed Line indicates Error = 0.1.",
        y = "log(Error)", x = "Round Index") +
-  theme_bw()# +
+  theme_bw() +
+  scale_y_log10()# +
   #theme(legend.position = "bottom")
@@
 index <- c(rep(20:10000, times = 4), 40:10000)
-alg_res <- log(c(pois2_comp_UNIFORM, pois2_comp_APT, 
+alg_res <- (c(pois2_comp_UNIFORM, pois2_comp_APT, 
                  pois2_comp_LR, pois2_comp_AugUCB, pois2_comp_EVT))
@@
   geom_line(aes(group = Algorithm, color = Algorithm)) +
-  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
+  #geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
   facet_grid(.~Distribution, scales = "free") +
   labs(#title = "Results of Experiment 5", 
-       subtitle = "Dashed line at Error = 0.1.", 
-       y = "log(Error)", x = "Round Index") +
+       #subtitle = "Dashed line at Error = 0.1.", 
+       y = "Error (log10 scale)", x = "Round Index") +
   theme_bw() +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom") +
+  scale_y_log10()
 ```
@@
 samples.
-Every company of course tries to run their algorithms under settings as ideal as possible, but there will always be problems.
+Every experimenter of course tries to run their algorithms under settings as ideal as possible, but there will always be problems.
 Thus our experiments serve as a first robustness check on the algorithms introduced before.
@@
 The data set we use here has been collected during the entire month of November 2016.
-It can be considered time series data collected at minutely frequency.
-Thus the data contain 43200 observations per product, and overall 8510400 observations.
-
-Since we want to run an offline comparison of bandit algorithms, it is important to have at each time point an observation for each arm.
+It can be considered time series data sampled at minutely frequency.
+Thus the data contain 43200 observations per product, and in total 8510400 observations.
+
+Since we would like to run an offline comparison of bandit algorithms, it is important to have at each time point an observation for each arm.
 Given that, it is easy to evaluate the perfomance of algorithms that make different decisions at different point in times and thus do not observe the same samples.
@@
 
-The choice of using what is basically multiple time series data as the sample offers a simple way of running the algorithms just as often on the data as for simulated data.
+The choice of using what is essentially multivariate time series data as the sample offers a simple way of running the algorithms just as often on the real data as on simulated data.
 The goal is to perform 5000 runs over the sample to confidently assess the performance.
@@
 Instead we perform time series cross validation.
-To preserve the autocorrelation, one can create different samples of $X$ observations by sliding a window of size $X$ over the time series.
-Moving the window one period (in our case one minute) at a time, one ensures that no sample shares start and end observation with another sample.
+To preserve the autocorrelation, one can create different samples of $n$ observations by sliding a window of size $n$ over the time series.
+Moving the window one period (in our case one minute) at a time, one ensures that no sample shares start and end observation with another sample (see Figure 8)^[The graphic is adapted from a graphic by Rob J.
+Hyndman available at <https://gist.github.com/robjhyndman/9fa152c585442bb076eb42a30a020091>].
 In particular, this means for a given bandit strategy and two samples that the observations that the algorithm collects as feedback during the initialization phases differ from sample to sample and are never the same.
@@
 
-```{r, echo = FALSE}
-load("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/arms_example_binary.Rda")
-
-knitr::kable(arms_example_binary, caption = "Example of the binary time series data for five products.")
+```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "We use time series crossvalidation, to create many samples from one data set."}
+plot(0,0,xlim=c(0,28),ylim=c(0,1),
+     xaxt="n",yaxt="n",bty="n",xlab="",ylab="",type="n")
+i <- 1
+for(j in 1:20)
+{
+  test <- (6+j):26
+  train <- 1:(5+j)
+  pre_train <- 1:(j-1)
+  arrows(0,1-j/20,27,1-j/20,0.05)
+  points(train,rep(1-j/20,length(train)),pch=19,col="blue")
+  if(j > 1)
+    points(pre_train, rep(1-j/20,length(pre_train)),pch=19,col="gray")
+  if(length(test) >= i)
+    points(test[i], 1-j/20, pch=19, col="red")
+  if(length(test) >= i)
+    points(test[-i], rep(1-j/20,length(test)-1), pch=19, col="gray")
+  else
+    points(test, rep(1-j/20,length(test)), pch=19, col="gray")
+}
+text(28,.95,"time")
 ```
@@
 Thus we have a binary time series of length $60\cdot 24 \cdot 30 = 43200$ for each of the 197 products.
-Given that the number of visitors that reach a given PDP is likely to vary by time of day and by day, and in general over time, we expect the mean of the time series to not be stable over time.
+Given that the number of visitors that reach a given PDP is likely to vary by time of day, by day, and in general over time, we expect the mean of the time series to not be stable over time.
 For example, less visitors visit during night than during the evening.
@@
 For this reason, the experiments we present below are run on $60 \cdot 24 \cdot 7 = 10080$ observations for each arm, so as to have a sample for one full week.
+
+```{r, echo = FALSE}
+load("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/arms_example_binary.Rda")
+
+knitr::kable(arms_example_binary, caption = "Example of the binary time series data for five products.")
+```
 
@@
 index <- c(rep(10:10080, times = 5), 20:10080)
-alg_res <- log(c(amo3_comp_UNIFORM, amo3_comp_APT, amo3_comp_AugUCB, amo3_comp_LR, amo3_comp_BUCB, amo3_comp_EVT))
+alg_res <- (c(amo3_comp_UNIFORM, amo3_comp_APT, amo3_comp_AugUCB, amo3_comp_LR, amo3_comp_BUCB, amo3_comp_EVT))
 loc3_comp_res <- data.frame(index = index, Algorithm = alg_names, 
@@
   geom_line(aes(group = Algorithm, color = Algorithm)) +
-  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
+  geom_hline(aes(yintercept = (0.1)), linetype = 2, color = "lightgrey") +
   labs(#title = "Results of Real Data Experiment 1", 
-       subtitle = paste0("Dashed Line indicates Error = 0.1."), 
-       y = "log(Error)", x = "Round Index") +
-  theme_bw()
+       #subtitle = paste0("Dashed Line indicates Error = 0.1."), 
+       y = "Error (log10 scale)", x = "Round Index") +
+  theme_bw() +
+  scale_y_log10()
 ```
@@
 index <- c(rep(10:10080, times = 5), 20:10080)
-alg_res <- log(c(amo4_comp_UNIFORM, amo4_comp_APT, amo4_comp_AugUCB, amo4_comp_LR, amo4_comp_BUCB, amo4_comp_EVT))
+alg_res <- (c(amo4_comp_UNIFORM, amo4_comp_APT, amo4_comp_AugUCB, amo4_comp_LR, amo4_comp_BUCB, amo4_comp_EVT))
 source_name <- rep("Real", 60416)
@@
 index <- c(rep(10:10080, times = 5), 20:10080)
-alg_res <- log(c(amo4sim_comp_UNIFORM, amo4sim_comp_APT, amo4sim_comp_AugUCB,
+alg_res <- (c(amo4sim_comp_UNIFORM, amo4sim_comp_APT, 
+                 amo4sim_comp_AugUCB,
                  amo4sim_comp_LR, amo4sim_comp_BUCB, amo4sim_comp_EVT))
@@
   facet_grid(.~source) +
-  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
+  #geom_hline(aes(yintercept = (0.1)), linetype = 2) +
   labs(#title = "Results of Real Data Experiment 2", 
-       subtitle = paste0("Dashed line indicates Error = 0.1."), 
-       y = "log(Error)", x = "Round Index") +
+       #subtitle = paste0("Dashed line indicates Error = 0.1."), 
+       y = "Error (log10 scale)", x = "Round Index") +
   theme_bw() +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom") +
+  scale_y_log10()
 ```
@@
 
+In the thesis at hand, we have introduced the general thresholding bandit problem introduced by Locatelli et al.
+(2016), as well as their Anytime Parameter-Free Thresholding algorithm that tries to solve the problem optimally.
+Given a few limitations of the APT algorithm, we explored the literature on top-$m$ multi-armed bandit problems to see how the Kullback-Leibler divergence can be used to improve algorithms and performance bounds.
+Based on this we exhibit the similarity between the thresholding bandit problem and simple hypothesis testing.
+We derive a lower bound on the complexity of a one-armed thresholding bandit that corresponds to the Chernoff-Stein Lemma.
+Continuing with the intuition from hypothesis testing, we propose the new Simple Likelihood Ratio algorithm for the multi-armed thresholding bandit for one-parameter exponential family of distributions.
+We show in extensive simulations that the the empirical performance of the SLR algorithm improves significantly upon the APT algorithm.
+We show that adding the D-Tracking Rule originally proposed by Garivier and Kaufmann (2016) can eradicate some of the remaining weaknesses.
+We propose a new method of testing thresholding bandit algorithms on real data by treating it as in time series cross validation.
+We show that the adaptive sampling strategies are not robust to the time dependency in the data set.
+
+Problems for future work are the derivation of lower and upper bounds on the error probability of the SLR algorithm.
+Furthermore, one might be able to adapt the lower bound on the complexity of the one-armed thresholding bandit to the multi-armed version.
+Lastly, the surprisingly very good performance of the Bayes-UCB algorithm in our simulations, as well as its better sample allocation to individual arms in terms of concentration compared to APT and SLR, justify more research effort, and a theoretical analysis of its performance.
+
 # Acknowledgements
@@
 # Appendix
+
+## Example of User Feedback in Foursquare App \label{sec:Foursquare}
+
+![The right screenshot shows aggregated user feedback in the Foursquare app.
+One could use thresholding bandit algorithms as presented in this thesis to ask different questions so as to optimize the confidence with which the results are displayed for a restaurant in the app.](figures/Foursquare_Screenshot.png)
 
@@
 
-## Empirical Analysis of the Bayes-UCB Algorithm in Simulation 2
+### Empirical Analysis of the Bayes-UCB Algorithm in Simulation 2
 
@@
 
-## Empirical Comparison of APT, SLR, and Bayes-UCB in Simulation 2
+### Empirical Comparison of APT, SLR, and Bayes-UCB in Simulation 2
 

### 2017-09-18 Thesis/Draft.tex
Printed version

@@
 \hypersetup{unicode=true,
-            pdftitle={On Pure Exploration, Thresholding Bandits, and Kullback-Leibler Divergence},
             colorlinks=true,
-            linkcolor=Maroon,
+            linkcolor=black,
             citecolor=Blue,
-            urlcolor=blue,
+            urlcolor=black,
             breaklinks=true}
@@
 \setlength{\droptitle}{-2em}
-  \title{On Pure Exploration, Thresholding Bandits, and Kullback-Leibler
-Divergence}
-  \pretitle{\vspace{\droptitle}\centering\huge}
-  \posttitle{\par}
+  \title{}
+  \pretitle{\vspace{\droptitle}}
+  \posttitle{}
   \author{}
@@
 \begin{document}
-\maketitle
-
-{
-\hypersetup{linkcolor=black}
-\setcounter{tocdepth}{2}
-\tableofcontents
-}
+
+\pagenumbering{gobble}
+
+\begin{centering}
+
+\vspace{5cm}
+
+    {\Large Humboldt-Universit\"at zu Berlin \\
+    School of Business and Economics \\
+    Institute for Statistics and Econometrics\\}
+
+    \vspace{4cm}
+
+{\huge{\bf On Pure Exploration, Thresholding Bandits, \\
+and Kullback-Leibler Divergence\\}}
+
+\vspace{2cm}
+
+{\large Master's Thesis submitted\\\vspace{0.5cm}
+    to}
+    \\\vspace{0.5cm}
+    {\large{\bf Prof. Dr. Marius Kloft \\}}
+    {\large{\bf Prof. Alexandra Carpentier, PhD \\}}
+    \vspace{0.5cm}
+
+    {\large by \\\vspace{0.5cm}
+    {\bf Tim Radtke\\}
+    (572481)\\
+    born on 11.01.1992 in Viersen \\\vspace{1cm}}
+
+    {\large in partial fulfillment of the requirements \\
+    for the degree of \\
+    {\bf Master of Science (M. Sc.)\\} \vspace{3cm}
+    Berlin, September 18, 2017\\}
+
+\end{centering}
+
 \newpage
@@
 experiment, it's wrong. That's all there is to it.''
-
-\begin{itemize}
-\tightlist
-\item
+\vspace*{1.5\baselineskip}
+
 Richard Feynman in \emph{Richard Feynman Messenger Lectures at Cornell
-  University: The Character of Physical Law. Chapter 7, Seeking New
-  Laws}.
-\end{itemize}
+University: The Character of Physical Law. Chapter 7, Seeking New Laws}.
 
 \newpage
+
+\vspace*{10\baselineskip}
+
+\Large{\bf Abstract\\}
+
+\vspace*{1\baselineskip}
+
+\normalsize
+In this thesis we present a new sequential sampling strategy for the
+fixed-budget thresholding bandit problem described in Locatelli et al.
+(2016). We draw from the literature on pure exploration bandit problems
+to show the similarity of the thresholding bandit to (sequential)
+hypothesis testing. In particular, we derive a lower bound on how fast
+the error probability in a one-armed thresholding bandit problem can
+decrease at best, and show that this corresponds to the Chernoff-Stein
+Lemma. This motivates the use of the Kullback-Leibler divergence in the
+index of our new algorithm. In simulations, our strategy is shown to
+outperform existing strategies. Using website analytics data from an
+online shop, we use time series cross-validation to create data sets for
+offline testing of adaptive sampling strategies; time dependency in the
+data is thus preserved. Our experiments show that the adaptive sampling
+strategies are disrupted by the dependency structure in the samples.
+
+\newpage
+
+\setcounter{tocdepth}{2} \tableofcontents
+
+\newpage
+
+\pagenumbering{arabic}
 
@@
 enough patients, but one would also like to adapt the sampling such that
-as soon as possible more patients receive the better drug and are cured.
-As noted in Cappé et al. (2013), this example dates back to Thompson
-(1933, 1935). Such problems are known as multi-armed bandit problems in
-which the sampling is adapted so as to minimize the cumulative regret:
-In the case of the drug tests, one would like to sample the two drugs in
-a way to find the best drug as soon as possible and then to test this
-drug more and more often and more often than the worse drug. This would
-lead to cumulatively more healthy patients than testing both drugs
-uniformly; it would minimize the regret from treating patients with an
-ineffective drug.
+more patients receive the better drug as soon as possible, and are
+cured. As noted in Cappé et al. (2013), this example dates back to
+Thompson (1933, 1935). Such problems are known as multi-armed bandit
+problems in which the sampling is adapted so as to minimize the
+cumulative regret: In the case of the drug tests, one would like to
+sample the two drugs in a way that quickly finds the best drug and then
+tests this drug more and more often, and more often than the worse drug.
+This would lead to cumulatively more healthy patients than testing both
+drugs uniformly; it would minimize the regret from treating patients
+with an ineffective drug.
 
@@
 order to estimate their means. To minimize the cumulative regret
-measure, one would like to play the distribution with the highest mean
-as much as possible (\emph{Exploitation}). At the same time, however,
-one has to sample all arms at least a little, so as to initially find
-the best arm (\emph{Exploration}). Any algorithm thus has to handle a
-trade-off between exploration and exploitation to minimize the regret.
-How can we organize the sampling in order to achieve this task?
+measure, one would like to sample from the distribution with the highest
+mean as often as possible (\emph{Exploitation}). At the same time,
+however, one has to sample all arms at least a little, so as to
+initially find the best arm (\emph{Exploration}). Any algorithm thus has
+to handle a trade-off between exploration and exploitation to minimize
+the regret. How can we organize the sampling in order to achieve this
+task?
 
@@
 Kullback-Leibler divergence upper confidence intervals (Cappé et al.,
-2013) or the Bayes-UCB algorithm (Kaufmann et al., 2012) have followed
+2013) or the Bayes-UCB algorithm (Kaufmann et al., 2012a) have followed
 and been shown to be optimal as they reach the lower bound introduced in
@@
 lower mean, but when drawing any sample is costly. Thus one needs to
-explore the distributions as efficiently as possible. Exploitation is
-not necessary, and the setting is thus referred to as \emph{Pure
-Exploration}. The need for strategies other than uniform sampling
-arises: One does not want to continue to sample distributions that one
-is confident in. This setting is related to the problem faced in
-Bayesian Optimization: Training large neural networks is costly in terms
-of time and computation, and so the parameter space needs to be explored
-with as few samples as possible. (Zhang et al., 2017; Brochu et al.,
-2010). The problem of best arm identification is also very related to
-statistical hypothesis testing as noted by Chernoff (1958) since one has
-to make a decision about how the means of distributions relate to each
-other. The main difference being that the bandit setting includes the
-testing procedure in the sampling process.
+explore the distributions as efficiently as possible. Given that the
+loss function only evaluates the classifiation once at the end of the
+sampling process, exploitation is \emph{not} necessary, and the setting
+is thus referred to as \emph{Pure Exploration}. The need for strategies
+different from uniform sampling arises still: One does not want to
+continue to sample distributions that one is already confident in. This
+setting is related to the problem faced in Bayesian Optimization:
+Training of, for example, deep neural network architectures is costly in
+terms of time and computation, and so the parameter space needs to be
+explored with as few samples as possible. (Zhang et al., 2017; Brochu et
+al., 2010). The problem of best arm identification is also very related
+to sequential statistical hypothesis testing as noted by Chernoff
+(1958), and picked up by Garivier and Kaufmann (2016) and Russo (2016),
+since the experimenter has to make a decision about how the means of
+distributions relate to each other.
 
@@
 These binary measures correspond to the probability of the identified
-arm being the best, and thus inherently related to hypothesis testing.
-The problem of best arm identification can readily be extended to the so
-called Top-\(m\) problem of identifying the best \(m\) of \(K\) arms
-(Kaufmann and Kalyanakrishnan, 2013; Kaufmann et al. 2016).
+arm being the best, and thus are inherently related to hypothesis
+testing. The problem of best arm identification can readily be extended
+to the so called Top-\(m\) problem of identifying the best \(m\) of
+\(K\) arms (Kaufmann and Kalyanakrishnan, 2013; Kaufmann et al. 2016).
 
@@
 distributions out of \(K\) that have a mean at least as large as a fixed
-threshold. Given that an implicit threshold arises in the top-\(m\)
+threshold (it is not known upfront how many distributions fulfill this
+condition). Given that an implicit threshold arises in the top-\(m\)
 problem between the \(m\)-th best and the \((m+1)\)-th best arm
@@
 discuss this in more detail in
-\autoref{chap:KullbackLeiblerPureExploration}. In the form described in
-Locatelli et al. (2016), algorithms in the thresholding bandit problem
-are evaluated against a binary loss function penalizing whenever an arm
-has not been classified correctly as being above or below the threshold,
-and thus focus on exploration similar to algorithms employed for best
-arm identification. Indeed, Locatelli et al. (2016) show how their
-thresholding algorithm can be used for best arm identification when the
-mean of the best arm is known upfront.
+\autoref{chap:KullbackLeiblerPureExploration}. In the setting described
+in Locatelli et al. (2016), algorithms in the thresholding bandit
+problem are evaluated against a binary loss function penalizing once
+after the sampling process if an arm has not been classified correctly
+as being above or below the threshold. This setting thus focuses on
+exploration similar to algorithms employed for best arm identification.
+Indeed, Locatelli et al. (2016) show how their thresholding algorithm
+can be used for best arm identification when the mean of the best arm is
+known upfront.
 
@@
 like to find out two things: Does the restaurant have good service? Is
-the restaurant trendy?
+the restaurant trendy? See \autoref{app:Foursquare} for how this
+information is then displayed in the Foursquare app.
 
@@
 
-The app will then display a ``Good service'' or ``This place is trendy''
+The app will display a ``Good service'' or ``This place is trendy''
 description for the restaurant if \(\mu_{\text{service}}\) and
 \(\mu_{\text{trendy}}\) are estimated to be above a certain threshold,
-for example \(\tau = 0.5\). That is, more than half of the people would
-describe the place as having good service, or as trendy.
+for example \(\tau = 0.5\). That is, more than half of the user base
+would describe the place as having good service, or as trendy.
 
@@
 thousands of users, not that many people visit a specific restaurant,
-and even less people report this back to the app. Thus the company only
-has a limited budget of \(T\) potential users from which to collect
-samples \(X_{\text{service}}\) and \(X_{\text{trendy}}\) from. How can
-the company ask these \(T\) questions to be as confident as possible in
-its classification, that is, in the information it displays?
+and even less people report this back to the app. Thus the company has
+only a limited budget of \(T\) potential users from which to collect
+samples \(X_{\text{service}}\) and \(X_{\text{trendy}}\). How can the
+company ask these \(T\) questions to be as confident as possible in its
+classification of the restaurant's features, that is, in the information
+it displays?
 
@@
 give feedback on the service level, 50 users report on the trendiness
-level. This however is unlikely to be optimal with respect to the
+level. This, however, is unlikely to be optimal with respect to the
 confidence after 100 samples. Given that the company asks the users
@@
 time: If the first ten users report
-\(\sum_{s=1}^{10}X_{\text{service},s}=10\), while
-\(\sum_{s=1}^{10}X_{\text{trendy},s}=5\), then the company might already
+\(\sum_{s=1}^{5}X_{\text{service},s}=5\), while
+\(\sum_{s=1}^{5}X_{\text{trendy},s}=3\), then the company might already
 be quite confident that \(\mu_{\text{service}} \geq \tau = 0.5\), while
@@
 sampling both questions, it might be more useful to collect more
-feedback on the trendiness level so as to figure out its position
-relative to the threshold. After all, the company would like to use the
-100 samples to maximize its confidence in both displayed tips.
+feedback on the trendiness level so as to ensure its position relative
+to the threshold. After all, the company would like to use the 100
+samples to maximize its confidence in \emph{both} displayed tips.
 
@@
 distributions against a threshold with as much confidence as possible
-after a limited budget of samples is the problem described above, and
-the problem described by the thresholding bandit problem which we
-discuss for the remainder of this thesis. In the following section, we
-define the general setting of the thresholding bandit problem.
+after a limited budget of samples is the problem described above. It is
+a setting described by the thresholding bandit problem, which we discuss
+for the remainder of this thesis. In the following section, we define
+setting of the thresholding bandit problem more generally.
 
@@
 
-Consider a setting with a set of \(\mathbb{A}=\{1, ..., K\}\) unknown
-probability distributions \(\nu_i, i \in \mathbb{A}\). To stick with the
-idea of multi-armed bandits, we call the distributions arms, and
-observations from the arms rewards (Bubeck and Cesa-Bianchi, 2012). The
-learner is interested in learning about the structure of the arms; in
-particular, she would like to estimate the means \(\mu_1, ..., \mu_K\)
-by sequentially drawing observations \(X_{i,1}, X_{i,2}, ...\) from the
-different arms, where \(X_{i} \sim \nu_i\). However, at time \(t\) the
-learner cannot observe a reward from every distribution but must select
-a single arm \(I_t\) from which she would like to observe the reward
-\(X_{I_t,t}\). Often, adaptive sampling strategies makes the decision of
-which arm to pull by computing an index \(B_i(t)\) for each arm. If
-\(T_i(t)\) is the number of samples observed until time \(t\) for arm
-\(i\), then is \(B_i(t)\) a function of the past rewards
-\(X_{i,1}, ..., X_{i,T_i(t)}\) observed for arm \(i\), and w.l.o.g.
-\(I_t = \arg \min_{i = 1,...K} B_i(t)\). The set of indexes can be
-called strategy (Kaufmann et al., 2012) which makes it clear that the
-strategy is adapted as more observations are collected. Strategies of
-this kind are also called index policies.
+Consider a setting with unknown probability distributions \(\nu_i\)
+indexed by \(i \in \mathbb{A}=\{1, ..., K\}\). To stick with the idea of
+multi-armed bandits, we call the distributions arms, and observations
+from the arms rewards (Bubeck and Cesa-Bianchi, 2012). The learner is
+interested in learning about the structure of the arms; in particular,
+it would like to estimate the means \(\mu_1, ..., \mu_K\) of each
+distribution \(\nu_i\) by sequentially drawing observations
+\(X_{i,1}, X_{i,2}, ...\) from the different arms, where
+\(X_{i} \sim \nu_i\). However, at time \(t\) the learner cannot observe
+a reward from every distribution but must select a single arm \(I_t\)
+from which it would like to observe the reward \(X_{I_t,t}\). The
+decision of which arm to pull next is often made by computing an index
+\(B_i(t)\) for each arm. If \(T_i(t)\) is the number of samples observed
+until time \(t\) for arm \(i\), then \(B_i(t)\) is a function of the
+past rewards \(X_{i,1}, ..., X_{i,T_i(t)}\) observed for arm \(i\), and
+w.l.o.g. \(I_t = \arg \min_{i = 1,...K} B_i(t)\). The set of indexes can
+be called strategy (Kaufmann et al., 2012a) which makes it clear that
+the strategy is adapted as more observations are collected. Strategies
+of this kind are also called index policies.
 
@@
 overall \(T\) samples (or rounds) to explore the different arms. After
-this exploration phase, the learner returns a set of arms that she
+this exploration phase, the learner returns a set of arms that it
 believes to be over the threshold. When evaluating the classification of
 the learner, arms with mean inside of the epsilon interval
-\(\tau \pm \epsilon\) will not be considered. The learner only has to
+\(\tau \pm \epsilon\) are not considered. The learner only has to
 correctly distinguish the means from the threshold up to the precision
@@
 The learner's classification is returned as the set
-\(\hat{\mathcal{S}}_{\tau} := \hat{\mathcal{S}}_{\tau}(T) \subset \mathbb{A}\)
+\(\hat{\mathcal{S}}_{\tau} := \hat{\mathcal{S}}_{\tau}(T) \subseteq \mathbb{A}\)
 after \(T\) rounds; that is, the set of arms estimated to be over the
-threshold. The classification is evaluated against the loss given as
-(Locatelli et al., 2016):
+threshold. The classification is evaluated against the binary loss given
+by (Locatelli et al., 2016):
 
@@
 expected loss. Let \(\mathbb{E}\) be the expectation with regard to the
-samples \(X_{i,1}, ..., X_{i,T}\) collected by the algorithm. The
-expected loss is then given as
+samples \(X_{i,1}, ..., X_{i,T}\) collected by the algorithm. Then
 
@@
 
-which corresponds to the probability of making at least one wrong
+is the expected loss, or the probability of making at least one wrong
 classification. Both the probability of not identifying an arm that is
@@
 Under this assumption, the authors are able to prove a lower bound on
-the largest probability of error of the best algorithm in the setting we
-have just introduced, as well as an upper bound on the performance of
-their APT algorithm which we will introduce in the following chapter. As
-in their paper, we define \(R\)-sub-Gaussian and assume it in the
-description of the their algorithm and bounds:
+the largest probability of error of the best algorithm in the setting
+just introduced, as well as an upper bound on the performance of their
+APT algorithm which we will show in the following chapter. As in their
+paper, we define \(R\)-sub-Gaussian as follows:
 
@@
 mean, which makes it possible to deduce the bounds presented by the
-authors and repeated below. The family of \(R\)-sub-Gaussian
-distributions encompasses Gaussian distributions of variance \(R^2\) for
-\(R \in \mathbb{R}\), as well as all bounded distributions, with the
-important case of Bernoulli distributions.
+authors and repeated below. Among other distributions, the family of
+\(R\)-sub-Gaussian distributions encompasses Gaussian distributions of
+variance \(R^2\) for \(R \in \mathbb{R}\), as well as all bounded
+distributions, with the important case of Bernoulli distributions.
 
 Having described the thresholding bandit setting as well as the
-assumption of \(R\)-sub-Gaussianity, we can now proceed to describe the
+assumption of \(R\)-sub-Gaussianity, we now proceed to describe the
 \emph{Anytime Parameter-free Thresholding} (APT) algorithm proposed in
@@
 \For{$t = K+1$ \KwTo $T$}{
-  \emph{Pull arm $I_t = \arg \min_{i \in A} B_i^{APT}(t) = \arg \min_{i \in A} \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau|+\epsilon)$}\;
+  \emph{Pull arm $I_t = \arg \min_{i \in A} B_i^{APT}(t) = \arg \min_{i \in A} \sqrt{T_i(t-1)} \cdot(|\hat{\mu}_i(t-1) - \tau|+\epsilon)$}\;
   \emph{Observe reward $X_t \sim \nu_{I_t}$}\;
@@
 observed until time \(t\). Given the arm with the smallest index is
-pulled at round \(t+1\), we observe that arms that are estimated to be
-further away from the threshold \(\tau\) as measured by the absolute
-distance to their empirical mean \(\hat{\mu}_i\), \(\hat{\Delta}_i(t)\),
-are pulled less often. Intuitively, it is easier to classify arms as
-below or above \(\tau\) when their mean is far away from the threshold.
-In contrast to the uniform sampling strategy, APT will gather more
-evidence for arms which appear to be inherently more difficult to
-classify. Likewise, APT tends to less often pull arms which it already
-pulled considerably often as measured by \(T_i(t)\). If arm \(i\) has
-been pulled more often than arm \(j\), then we should in general be more
-confident in its estimated mean and the corresponding distance to the
-threshold. If we are confident in \(i\), then it is better to explore
-other arms by drawing an observation from arm \(j\). By adapting its
-sampling strategy in this way during the sequential sampling process,
-the APT algorithm minimizes the probability of error
-\(\mathbb{E}[\mathcal{L}(T)]\) after \(T\) samples have been observed.
+pulled at round \(t+1\), we observe that arms estimated to be further
+away from the threshold \(\tau\) as measured by the absolute distance
+\(\hat{\Delta}_i(t)\) to their empirical mean \(\hat{\mu}_i\) are pulled
+less often. Intuitively, it is easier to classify arms as below or above
+\(\tau\) when their mean is far away from the threshold. In contrast to
+the uniform sampling strategy, APT will gather more evidence for arms
+which appear to be inherently more difficult to classify. Likewise, APT
+tends to less often pull arms which it already pulled considerably often
+as measured by \(T_i(t)\). If arm \(i\) has been pulled more often than
+arm \(j\), then we should in general be more confident in its estimated
+mean and the corresponding distance to the threshold. If we are
+confident in \(i\), then it is better to explore other arms by drawing
+an observation from arm \(j\). By adapting its sampling strategy in this
+way during the sequential sampling process, the APT algorithm minimizes
+the probability of error \(\mathbb{E}[\mathcal{L}(T)]\) after \(T\)
+samples have been observed.
 
@@
 larger. Or the empirical mean has to be better concentrated around the
-true mean. Otherwise it is easier to make a mistake on this arm. To gain
+true mean. Otherwise it is easy to make a mistake on this arm. To gain
 this confidence, the arm requires more samples, and thus a larger share
@@
 While the APT algorithm does not require the complexity to be known
-upfront (which would be problematic as it is not known upfront), it is
-necessary to define the complexity to deduce the upper bound on its
-probability of error. Similar to the distance measure used in the
+upfront (which would be problematic as it is \emph{not} known upfront),
+it is necessary to define the complexity to deduce the upper bound on
+its probability of error. Similar to the distance measure used in the
 algorithm's index, we define the gap \(\Delta_i^{\tau,\epsilon}\)
@@
 Consequently, when we require less precision, that is, we increase
-\(\epsilon\), the hardness decreases. Furthermore, we see that each arm
-contributes its individual complexity,
+\(\epsilon\), the hardness decreases. Indeed, by using \(\epsilon > 0\),
+we upper bound the complexity of a problem. Consider a problem with
+\(K\) arms. Then even in the worst case of \(\mu_i = \tau\) for all
+\(i \in \mathbb{A}\), \(H \geq \frac{K}{\epsilon^2}\). Furthermore, we
+see that each arm contributes its individual complexity,
 \(h_i^{\tau,\epsilon} = \frac{1}{(\Delta_i^{\tau,\epsilon})^2}\)
@@
 has which mean, we could allocate the ``optimal'' share of the budget,
-\(T \cdot h_i /H\) to arm \(i\). However, since we do not know neither
+\(T \cdot h_i /H\) to arm \(i\). However, since we know neither
 \(\mu_i\) nor \(H\) upfront, the best we can do is to adapt our
@@
 algorithm. In \autoref{sec:LowerBoundLocatelli} we then show the lower
-bound presented in Locatelli et al. (2016) and that the APT algorithm is
-optimal in that it matches the lower bound. We discuss the results and
-the APT algorithm further in \autoref{sec:DiscussionLocatelli}.
-
-\subsection{\texorpdfstring{Upper Bound for the APT Algorithm
-\label{sec:UpperBoundLocatelli}}{Upper Bound for the APT Algorithm }}\label{upper-bound-for-the-apt-algorithm}
+bound presented in Locatelli et al. (2016), and that the APT algorithm
+is optimal in that it matches the lower bound. We discuss the results
+and the APT algorithm further in \autoref{sec:DiscussionLocatelli}.
+
+\subsection{\texorpdfstring{Upper Bound for the Anytime Parameter-free
+Thresholding Algorithm
+\label{sec:UpperBoundLocatelli}}{Upper Bound for the Anytime Parameter-free Thresholding Algorithm }}\label{upper-bound-for-the-anytime-parameter-free-thresholding-algorithm}
 
@@
 classify arms at the final round is the following. For every arm
-\(i \in \{1, ..., K\}\) after the final round \(T\), require \[
-\hat{\mu}_{i}(T) \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
-\] or \[
-\hat{\mu}_{i}(T) \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
-\] Or simply in terms of the gap between the arm and the threshold as
-used in the index by the APT algorithm: \[
+\(i \in \{1, ..., K\}\) after the final round \(T\), require: \[
 | \hat{\mu}_{i}(T) - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
@@
 \(\mu_i < \tau\) and \(\epsilon = 0\), an incorrect classification would
-require \(\mu_i < \tau \leq \hat{\mu_i}\). But then
+require \(\mu_i < \tau \leq \hat{\mu}_i\). But then
 \(| \hat{\mu}_{i}(T) - \mu_i | \geq |\mu_i - \tau|\), which violates the
-separation condition.
-
-Thus, we need to show that this condition holds for every arm
-\(i \in \{1,...,K\}\) with large probability after the final round
-\(T\). In different words, we need to derive an upper bound on the
-probability with which this condition does not hold.
+separation condition. Thus, we need to show that this condition holds
+for every arm \(i \in \{1,...,K\}\) with large probability after the
+final round \(T\). Put differently, we need to derive an upper bound on
+the probability with which this condition does not hold.
 
@@
 
-The separation condition describes what event needs to hold in order for
-the APT algorithm to make a correct classification: The smaller the
+The separation condition describes which event needs to hold in order
+for the APT algorithm to make a correct classification: The smaller the
 deviation of the empirical mean from the population mean, the more
@@
 classification to be likely. To bound the absolute deviation of the
-empirical mean from the true mean, we define the favorable event \(\xi\)
-as
+empirical mean from the true mean for every potential number of pulls
+\(s\) that an arm \(i\) might have received at the end of the budget
+\(T\), we define the favorable event \(\xi\) as
 
@@
 
-We know that \(X_i\) are \(R\)-sub-Gaussian by assumption. That is, we
-have
+We know that \(X_i\) are \(R\)-sub-Gaussian random variables by
+assumption. That is, we have
 
@@
 
-\begin{lemma}[Höffding's Inequality (Kloft Lecture Notes)] \label{lemma:HoeffdingsInequality}
+\begin{lemma}[Höffding's Inequality (As in lecture notes of Professor Dr. Kloft)] \label{lemma:HoeffdingsInequality}
 Let $X_1, ..., X_s$ be independent, identically distributed random variables with mean $\mathbb{E}[X_t] = \mu$ and $\mathbb{P}(a_t \leq X_t - \mathbb{E}[X] \leq b_t) = 1$.
@@
 \(\xi_i = \{|\bar{X}_s - \mu| \leq \sqrt{\frac{T\delta^2}{Hs}}\}\) of an
-individual arm \(i\), for each \(i \in \mathbb{A}\) and each
-\(s \in \{1, ..., T\}\):
-
-\[
-\mathbb{P}(\xi_i) = \mathbb{P}\Big(|\bar{X}_{i,s} - \mu_i| \leq \sqrt{\frac{T\delta^2}{Hs}}\Big) \geq 1 - 2\exp (-\frac{T\delta^2}{2R^2H}),
+individual arm \(i \in \mathbb{A}\) and a given \(s \in \{1, ..., T\}\):
+
+\[
+\mathbb{P}(\xi_i) = \mathbb{P}\Big(|\bar{X}_{i,s} - \mu_i| \leq \sqrt{\frac{T\delta^2}{Hs}}\Big) \geq 1 - 2\exp \Big(-\frac{T\delta^2}{2R^2H}\Big),
 \] where \(T\) is again the total budget of samples, and \(H\) the
@@
 
-Locatelli et al. (2016) use instead of Höffding's inequality a
+Instead of Höffding's inequality, Locatelli et al. (2016) use a
 Sub-Gaussian martingale inequality including a peeling argument in order
@@
 
-This bound is non-trivial for much smaller values of \(T\), and we will
+This bound is non-trivial at much smaller values of \(T\), and we will
 use it in the following.
@@
 \subsubsection{\texorpdfstring{Need to Bound
-\(T_i\)}{Need to Bound T\_i}}\label{need-to-bound-t_i}
+\(T_i(T)\)}{Need to Bound T\_i(T)}}\label{need-to-bound-t_it}
 
 We now have that with large probability the favorable event holds. On
-the favorable event, we have for every arm \(i\):
-
-\[
-| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}
+\(\xi\), we have for every arm \(i\):
+
+\[
+|\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}}
 \]
@@
 The deviation of arm \(i\) at time \(t\) depends on how large \(H\),
-\(T\), and \(T_i(t)\) are. While \(t\), \(H\), \(T\) are deterministic,
-the number of times arm \(i\) has been pulled at round \(t\),
-\(T_i(t)\), is a random variable. In order to know how large the
-probability of the favorable event is (and thus the error probability),
-we need to know the value of \(T_i(t)\), or at least bound a range of
-potential values. Put differently: To ensure a deviation smaller than
-\(\sqrt{\frac{T\delta^2}{HT_i(t)}}\) for arm \(i\), we need to ensure
-that arm \(i\) has been pulled at least \(T_i(t)\) times. As usual in
-multi-armed bandits, and different from uniform sampling, the number of
-pulls is a random variable that also depends on how often other arms are
-pulled. In general, we do not want each arm to be pulled an equal
-amount, but each arm should be pulled some times, and not too many
-times.
+\(T\), and \(s = T_i(T)\) are. While \(\delta\), \(H\), \(T\) are
+deterministic, the number of times arm \(i\) has been pulled, \(s\), is
+a random variable. In order to know how large the probability of the
+favorable event is--and thus the error probability--at the end of the
+sampling period, we need to know the value of \(T_i(T)\), or at least
+bound a range of potential values. Put differently: To ensure a
+deviation smaller than \(\sqrt{\frac{T\delta^2}{HT_i(t)}}\) for arm
+\(i\), we need to ensure that arm \(i\) has been pulled at least
+\(T_i(t)\) times by the algorithm. As usual in multi-armed bandits, and
+different from uniform sampling, the number of pulls is a random
+variable that also depends on how often other arms are pulled. In
+general, we do not want each arm to be pulled an equal amount, but each
+arm should be pulled at least a few times, and no arm too many times.
 
@@
 
-which can be now be reduced to a form that is not specific to \(k\):
+which can be now be reduced to a form that is not specific to
+characteristics of arm \(k\):
 
@@
 We thus have derived a lower bound on the amount of pulls for any arm.
-That means that we can show that no arm is pulled an insufficient amount
+This means that we can show that no arm is pulled an insufficient amount
 of times with large probability, and that consequently the favorable
-event hold and the estimated mean is sufficienctly separated from the
+event holds and the estimated mean is sufficienctly separated from the
 threshold.
@@
 \(T_i(T) \geq (1-2\sqrt{2}\delta)^2 \frac{T}{2H\Delta_i^2}\), do we have
-\(|\hat{\mu}_i(T) - \mu | \leq \frac{\Delta}{2}\) on the favorable event
+\(|\hat{\mu}_i(T) - \mu | \leq \frac{\Delta_i}{2}\) on the favorable
+event
 \(\xi = \Big\{|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}}\Big\}\)?
@@
 
-We now present the lower bound given in Locatelli et al. (2016) for the
-thresholding bandit problem. In order to derive the bound, a problem is
-specified to show that the error of the lower bound is attained even in
-this specific problem. In particular, for a set of problems with
-Gaussian distributions of variance \(1\), the largest probability of
-error on these problems that the best algorithm exhibits is still at
-least as large as the lower bound.
-
 \subsection{\texorpdfstring{Lower Bound for the Thresholding Bandit
@@
 A proof of the lower bound is given in the Appendix in
-\autoref{sec:AppendixAPTLB}.
+\autoref{app:AppendixAPTLB}.
 
@@
 index are both motivated by sub-Gaussian distributions. The more a
-problem deviates from those, the less appropriate the quantities become.
-In particular, the empirical mean will be less (or not at all)
-concentrated around the true mean and more impacted by outliers which
-are more likely under non sub-Gaussian distributions. Locatelli et al.
-(2016) thus refers to Bubeck et al. (2013a) which consider solutions for
-multi-armed bandits that are based on heavy-tail distributions. By using
-more robust estimators of the mean, one could equip the APT algorithm to
-deal with such distributions.
+problem deviates from these, the less appropriate the quantities become.
+In particular, the empirical mean will be less concentrated around the
+true mean and impacted by outliers which are more likely under
+non-sub-Gaussian distributions. Locatelli et al. (2016) thus refers to
+Bubeck et al. (2013a) which consider solutions for multi-armed bandits
+that are based on heavy-tail distributions. By using more robust
+estimators of the mean, one could equip the APT algorithm to deal with
+such distributions.
 
@@
 described in Locatelli et al. (2016), and the APT strategy as a first
-algorithm that is simple, yet order-optimal for large budgets. However,
-we end with the conclusion that a KL-divergence based measure of the
-distance between the distributions and the threshold might be more
-useful than the simple gap \(\Delta^2_i = (\mu_i - \tau_i)^2\) employed
-so far. Indeed, citing Kaufmann et al. (2016), we note that the
-complexity \(H\) -- and thus the gaps -- used so far can be considered a
-sub-Gaussian approximation of a better complexity measure based on
-information theoretic measures like the Kullback-Leibler divergence.
+algorithm that is simple, yet order-optimal for large enough budgets.
+However, we end with the conclusion that a KL-divergence based measure
+of the distance between the distributions and the threshold might be
+more useful than the squared gaps \(\Delta^2_i\) employed so far.
+Indeed, citing Kaufmann et al. (2016), we note that the complexity
+\(H\)--and thus the gaps--can be considered a sub-Gaussian approximation
+of a better complexity measure based on information theoretic measures
+like the Kullback-Leibler divergence.
 
@@
 Their work offers methods that can inform our goal of extending the
-thresholding bandit problem. In what follows, we adopt the notation of
-Kaufmann et al. (2016) to ease a comparison with their arguments.
+thresholding bandit problem. In what follows, we adapt their notation to
+the one used by Locatelli et al. (2016).
 
@@
 \(\mu_i\). A learner picks at any time step \(t=1,2,...,\) an arm
-\(I_t \in \{1,...,K\}\) for which she observes the independent reward
+\(I_t \in \{1,...,K\}\) for which it observes the independent reward
 \(X_{t} \sim \nu_{I_t}\). The learner aims to find the \(m\) out of
@@
 as we have seen in \(\autoref{sec:Setup}\). Alternatively, consider a
-\(\delta\)-PAC strategy \(\mathcal{S}(\delta)\)for which it holds for
+\(\delta\)-PAC strategy \(\mathcal{S}(\delta)\) for which it holds for
 every problem \(\nu \in \mathcal{M}_m\) that the classification holds at
@@
 \(\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta\). The
-strategy has to achieve this level of confidence in its prediction
+strategy has to achieve this level of confidence in its classification
 before it is allowed to stop sampling. This is the fixed confidence
@@
 
-Given this setup, we can now follow the arguments of Kaufmann et al.
-(2016) to derive complexity measures for the top-\(m\) problem. As
-alluded to earlier, these complexity measures will rely on the
-KL-divergence in contrast to the complexity \(H\) used by Locatelli et
-al. (2016). When discussing \(H\), its motivation is that it represents
-the difficulty of the problem by measuring the distance between arms and
-the threshold. Instead, Kaufmann et al. approach complexity by how many
+Given this setup, we follow the arguments of Kaufmann et al. (2016) to
+derive complexity measures for the top-\(m\) problem. As alluded to
+earlier, the complexity measures will rely on the KL-divergence in
+contrast to the complexity \(H\) used by Locatelli et al. (2016). When
+discussing \(H\), the motivation has been that it represents the
+difficulty of the problem by measuring the distance between arms and the
+threshold. Instead, Kaufmann et al. approach complexity by how many
 samples (what error probability) one will need in the fixed confidence
@@
 To prove this statement for a given \(\delta\)-PAC strategy
-\(\mathcal{S}\), we assume certain continuity conditions (compare
-Kaufmann et al. (2016)) under which there exists for every arm
-\(i \in \{1, \dots, K\}\) an alternative model
+\(\mathcal{S}\), we assume certain continuity conditions which are
+fulfilled by the one-parameter exponential family of distributions, for
+example (compare Kaufmann et al. (2016)). Under those, there exists for
+every arm \(i \in \{1, \dots, K\}\) an alternative model
 \(\nu' = (\nu_1, \dots, \nu_{i-1}, \nu_i', \nu_{i+1}, \dots, \nu_K)\).
@@
 as described here, we flip arm \(i\) around the implied threshold
-\(\tau\) (compare the lower bound proof in \autoref{sec:AppendixAPTLB}).
+\(\tau\) (compare the lower bound proof in \autoref{app:AppendixAPTLB}).
 
@@
 the lower bounds, we show how based on the proof of Theorem 12 in
-Kaufmann et al. (2016) very similar lower bounds can be derived for the
+Kaufmann et al. (2016) a similar lower bound can be derived for the
 fixed budget thresholding problem.
@@
 corollary which gives a bound on the complexity of the single-armed
-thresholding bandit.
+thresholding bandit. That is, we bound how quickly the error probability
+decreases at best as the sample size increases.
 
@@
 variable but equals \(T\). The single-armed bandit is a simple
-hypothesis test.
-
-But as we see in the following corollary, we can extend the lower bound
-to the \(K\)-armed fixed budget thresholding bandit problem, which
-stands in contrast to the fact that for the top-\(m\) problem, it is
-only possible to show the lower bound for two arms. The result is based
-on an alternative setting \(\nu'\) in which all arms have means
-\(\mu' = \tau\) such that their expected number of pulls corresponds to
-uniform sampling, \(\mathbb{E}_{\nu'}[N_i(t)] = T/K\).
-
-\begin{corollary}
-Consider the setting in \autoref{sec:Setup}.
-Let $\nu = (\nu_1, ..., \nu_K)$ be a $K$-armed thresholding bandit problem in which $\tau$ is the threshold fixed upfront.
-For $i \in \{1,...,K\}$, let $\nu_i$ be from the one-parameter exponential family of distributions such that $\nu_i$ can be parameterized by its mean, $\mu_i$, and the Kullback-Leibler divergence between distributions $\nu_i$ and $\nu_i'$ can be written as $\KL(\nu_i, \nu_i') = \KL(\mu_i, \mu_i')$.
-In the fixed budget setting, any consistent algorithm satisfies for $\mu_i' \rightarrow \tau$:
-
-$$
-\limsup_{t \rightarrow \infty} -\frac{1}{t} \log p_t(\nu) \leq \max_{i \in \{1,...,K\}} \KL(\mu_i' || \mu_i)
-$$
-
-or
-
-$$
-- \frac{1}{t} \log p_t(\nu) \leq \frac{1}{K}\sum_{i=1}^{K} \KL(\tau || \mu_i),
-$$
-\end{corollary}
-
-\label{corollary:LBKTBP}
-
-We present the proofs of \autoref{sec:LBTBP} in the appendix in
-\autoref{sec:corollaryLBTBPproof}. Corresponding to the complexity
-measures defined in equation \((1)\) of Kaufmann et al. (2016), we can
-define the complexity \(\kappa_{TBP}(\nu)\) in the thresholding bandit
-problem and lower bound it:
-
-\[
-\kappa_{TBP}(\nu) = \inf_{S \text{ consistent}} \Big(\limsup_{t \rightarrow \infty} - \frac{1}{t} \log p_t(\nu)\Big)^{-1} \geq K \Big(\sum_{i=1}^{K} \KL(\mu_i'||\mu_i)\Big)^{-1}
-\]
+hypothesis test on a sample of size \(T\). In a way, it is a degenerate
+case of a multi-armed bandit problem.
+
+We present the proof of \autoref{sec:LBTBP} in
+\autoref{app:corollaryLBTBPproof}. While we were hoping to also prove a
+lower bound for the \(K\)-armed bandit problem, we were not able to do
+so as this entails the expectation under the alternative problem of the
+number of times the changed arm \(a\) is pulled. In any case, the result
+for the one-armed thresholding bandit stresses the similarity to
+hypothesis testing, and will give further motivation for the use of the
+likelihood ratio test statistic as index in the new Simple Likelihood
+Ratio algorithm in \autoref{sec:LRasIndex}.
 
@@
 
-Kaufmann et al. (2016) do not present algorithms matching the lower
-bound of Theorem \ref{theorem:KaufmannEtAlTheorem17}. They do consider
-algorithms that connect to Theorem \ref{theorem:KaufmannEtAlTheorem4}
-and Theorem \ref{theorem:KaufmannEtAlTheorem12}. Given that we aim to
-extend the fixed budget thresholding bandit problem, we are most
-interested in the matching strategies for Theorem
-\ref{theorem:KaufmannEtAlTheorem12}. However, given that this lower
-bound applies only to two-armed bandits, the algorithms proposed by
-Kaufmann et al. (2016) are of limited practical interest. Furthermore,
-the proposed strategies require knowledge that is in general not
-available upfront: For Gaussian distributions, the knowledge of the
-(potentially different) variance is assumed which enables a strategy
-that pulls each arm proportional to its variance.
+Kaufmann et al. (2016) present algorithms that connect to Theorem
+\ref{theorem:KaufmannEtAlTheorem4} and Theorem
+\ref{theorem:KaufmannEtAlTheorem12}. Given that we aim to extend the
+fixed budget thresholding bandit problem, we are most interested in the
+matching strategies for Theorem \ref{theorem:KaufmannEtAlTheorem12}.
+However, given that this lower bound applies only to two-armed bandits,
+the algorithms proposed by Kaufmann et al. (2016) are of limited
+practical interest. Furthermore, the proposed strategies require
+knowledge that is in general not available upfront: For Gaussian
+distributions, the knowledge of the (potentially different) variance is
+assumed which enables a strategy that pulls each arm proportional to its
+variance.
 
@@
 
-Thus, Kaufmann et al. (2016) joins other papers like Audibert et al.
-(2010) and Kaufmann and Kalyanakrishnan (2013) which struggle to find
-matching strategies in the fixed budget setting that do not rely on
+Consequently, Kaufmann et al. (2016) joins other papers like Audibert et
+al. (2010) and Kaufmann and Kalyanakrishnan (2013) which struggle to
+find matching strategies in the fixed budget setting that do not rely on
 knowledge of parameters or the complexity of the problem.
@@
 optimal given that nature will respond and choose the most difficult
-alternative model given her weights. Thus, to make the lower bound
-practical, it is a matter of finding the optimal weights
-\(w^*(\bm{\mu})\). This step did not occur in the lower bound for the
-top-\(m\) problem since the alternative models were specified by
-changing the distribution of one arm with respect to the ``border''
-between the two groups of arms.
+alternative model given her weights. Thus, making the lower bound
+practical is a matter of finding the optimal weights \(w^*(\bm{\mu})\).
+This step did not occur in the lower bound for the top-\(m\) problem
+since the alternative models were specified by changing the distribution
+of one arm with respect to the ``border'' between the two groups of
+arms.
 
@@
 likelihood ratio term that appears when changes in distribution are
-applied.
+applied (compare Garivier and Kaufmann, 2016).
 
@@
 mostly limited by the difficulty of defining an alternative problem
-\(\nu'\) to \(\nu\) that fits the Lemma
-\ref{theorem:KaufmannEtAlLemma1}. But given the intuition that in
-top-\(m\) problems the \(m\)-th best arm and the \((m+1)\)-th best arm
-define an implied threshold between the two groups of arms, we were able
-to apply the ideas of Kaufmann et al. (2016) to our fixed budget
-thresholding bandit problem. In contrast to their problem, arms are
-classified against the known threshold \(\tau\), which makes it possible
-to define an alternative problem \(\nu'\) in which we do not have to
-change arms with respect to each other, but only with respect to
-\(\tau\). This has lead us to the simple lower bound on the problem
-complexity for the thresholding bandit problem with exponential family
-distributions given in Corollary \ref{corollary:LBKTBP}.
+\(\nu'\) to \(\nu\) that fits Lemma \ref{theorem:KaufmannEtAlLemma1}.
+But given the intuition that in top-\(m\) problems the \(m\)-th best arm
+and the \((m+1)\)-th best arm define an implied threshold between the
+two groups of arms, we were able to apply the ideas of Kaufmann et al.
+(2016) to our fixed budget thresholding bandit problem. In contrast to
+their problem, arms are classified against the known threshold \(\tau\),
+which makes it possible to define an alternative problem \(\nu'\) in
+which we do not have to change arms with respect to each other, but only
+with respect to \(\tau\). This has lead us to the simple lower bound on
+the problem complexity for the one-armed thresholding bandit problem
+with exponential family distributions given in Corollary
+\ref{corollary:LB1TBP}.
 
@@
 we would compare each arm to the threshold \(\tau\). Intuitively, one
-can frame this problem for each arm individually as an hypothesis test
+can frame this problem for each arm individually as a hypothesis test
 between the maximum likelihood estimate of the mean and the threshold
@@
 protects them against poor estimates in the beginning of the sampling.
-Such rule should be mostly unnecessary, for example, the cumulative
-regret setting, as algorithms there rely on upper confidence bound
-estimates. This is not the case for the Track-and-Stop strategy
-introduced in Garivier and Kaufmann, and neither for our Simple
-Likelihood Ratio strategy introduced in \autoref{sec:1DSLR}. In
-\autoref{sec:Simulation2}, we show empirically that the performance of
-the Simple Likelihood Ratio strategy can be further improved by adding
-the D-Tracking rule.
+Such rule should be mostly unnecessary in the cumulative regret setting,
+as algorithms there rely on upper confidence bound estimates. This is
+not the case for the Track-and-Stop strategy introduced in Garivier and
+Kaufmann, and neither for our Simple Likelihood Ratio strategy
+introduced in \autoref{sec:1DSLR}. In \autoref{sec:Simulation2}, we show
+empirically that the performance of the Simple Likelihood Ratio strategy
+can be further improved by adding the D-Tracking rule.
 
@@
 and that it does not require any parameter to be tuned upfront. However,
-we have seen that the index \(B^{APT}\) and the complexity term \(H\)
-employed by the APT algorithm are the most effective for
-\(R\)-sub-Gaussian distributions. Both are related to the KL-divergence
-between two Gaussian distributions of equal variance. Given that this
-sub-Gaussian approximation can be poor in certain cases, we motivated
-information theoretic measures in an algorithm's index (compare
+we saw that the index \(B^{APT}\) and the complexity term \(H\) employed
+by the APT algorithm are the most effective for \(R\)-sub-Gaussian
+distributions. Both are related to the KL-divergence between two
+Gaussian distributions of equal variance. Given that this sub-Gaussian
+approximation can be poor in certain cases, we motivated information
+theoretic measures in an algorithm's index (compare
 \autoref{sec:DiscussionLocatelli}).
@@
 done by the APT algorithm. Another logical extension is to consider
-higher moments of a distribution, like its variance. After all, arms do
-not necessarily have the same variance, even if they are sub-Gaussian
-(two arms might be \(R_1\)-sub-Gaussian and \(R_2\)-sub-Gaussian). And
-given two arms for which we estimate the same mean, we would prefer to
-draw more samples from the arm with the larger variance. The simplest
-example of this are two Normal distributions with different variances.
+higher order moments like the sample variance. After all, arms do not
+necessarily have the same variance, even if they are sub-Gaussian (two
+arms might be \(R_1\)-sub-Gaussian and \(R_2\)-sub-Gaussian). And given
+two arms for which we estimate the same mean, we would prefer to draw
+more samples from the arm with the larger variance. The simplest example
+of this are two Normal distributions with different variances.
 
@@
 empirical variances as described in Mukherjee et al. (2017) and Zhong et
-al. (2017). We then go back to the information theoretic ideas and
+al. (2017). We then return to the information theoretic ideas and
 introduce a new algorithm based on the concept of likelihood ratios in
@@
 
-In the case of the APT algorithm the number of times a specific arm has
+In the case of the APT algorithm, the number of times a specific arm has
 been drawn \(T_i\) measures how concentrated the estimated mean is
@@
 reminiscient of the separation condition used in the proof of the upper
-bound in Locatelli et al.'s (2016) (compare
+bound in Locatelli et al. (2016) (compare
 \autoref{sec:CheckSeparationCondition}).
@@
 
-\subsubsection{\texorpdfstring{Anytime Parameter-free Empirical Variance
-Guided Algorithm
-\label{sec:EVTAlgorithm}}{Anytime Parameter-free Empirical Variance Guided Algorithm }}\label{anytime-parameter-free-empirical-variance-guided-algorithm}
+\subsubsection{\texorpdfstring{Empirical Variance Guided Thresholding
+Algorithm
+\label{sec:EVTAlgorithm}}{Empirical Variance Guided Thresholding Algorithm }}\label{empirical-variance-guided-thresholding-algorithm}
 
@@
 distributed random variable, \(D_i^{EVT}\) is always decreasing as the
-mean approaches the threshold (compare figure 2). Similar should hold in
+mean approaches the threshold (compare Figure 2). Similar should hold in
 general for bounded variables as the variance and the mean are linked by
@@
 \label{theorem:ZhongEtAl2017Theorem5}
-Let $K > 0$, $T > 2K$, and consider a thresholding bandit problem. Assume that all arms of the problem are bounded in $[0,1]$. Then the probability of an error is bounded as
+Let $K > 0$, $T > 2K$, and consider a thresholding bandit problem.
+Assume that all arms of the problem are bounded in $[0,1]$.
+Let $C$ be some positive constant.
+Then the probability of an error is bounded as
 
@@
 \end{equation*}
-
-where $C$ is some positive constant.
 \end{theorem}
@@
 
-\subsubsection{Likelihood Ratio as Index in Sequential
-Sampling}\label{likelihood-ratio-as-index-in-sequential-sampling}
-
-We now employ the concept of the likelihood-ratio test to a new
+\subsubsection{\texorpdfstring{Likelihood Ratio as Index in Sequential
+Sampling
+\label{sec:LRasIndex}}{Likelihood Ratio as Index in Sequential Sampling }}\label{likelihood-ratio-as-index-in-sequential-sampling}
+
+We now employ the concept of the likelihood ratio test to a new
 sequential sampling strategy for the thresholding bandit problem. In
@@
 choose an arm for which we either have not collected many samples, or
-for which the sample mean is close to the threshold \(\tau\). In this
-sense, a strategy based on the likelihood ratio is reminiscient of the
-index employed by the APT algorithm. Indeed, assuming the samples are
-normally distributed with equal variance for all arms under both \(H_0\)
-and \(H_1\), \(-\log(B_i^{LR}(t))\) equals the index in APT. Why then
-would we prefer the likelihood based strategy?
+for which the evidence collected so far suggests that the sample mean is
+not significantly separated from the threshold \(\tau\).
 
@@
 distributed according to \(\nu_{\theta_1}, ..., \nu_{\theta_K}\), which
-are all from the same canonical exponential family of distributions with
+are from the same canonical exponential family of distributions with
 scalar parameter \(\theta_i \in \Theta\). The probability density
@@
 
-\subsection{2D-SLR Algorithm for Normal
-Distributions}\label{d-slr-algorithm-for-normal-distributions}
+\subsection{2D-Simple Likelihood Ratio Algorithm for Normal
+Distributions}\label{d-simple-likelihood-ratio-algorithm-for-normal-distributions}
 
@@
 by their mean, it becomes less clear how the likelihood ratio for
-\(H_0: \mu = \tau\) and \(H_1: \mu = \hat{\mu}\) should be calculated.
-In the case of Normal distributions with unknown mean and unknown
-variance, given that the variance and mean estimate are linked, we can
-use \[
-H_0: \mu_0 = \tau \land \sigma_0^2 = \sigma^2_{\tau} = \frac{1}{n}\sum_{i=1}^{n}(x_i-\tau)^2 \quad \text{vs.} \quad H_1: \mu_1 = \hat{\mu} \land \sigma_1^2 = \hat{\sigma}^2 = \frac{1}{n}\sum_{i=1}^{n}(x_i-\hat{\mu})^2
-\]
+\(H_0: \mu = \tau\) and \(H_1: \mu \neq \tau\) should be calculated. In
+the case of Normal distributions with unknown mean and unknown variance,
+given that the variance and mean estimate are linked, we can use \[
+H_0: \mu_0 = \tau \land \sigma_0^2 = \sigma^2_{\tau} = \frac{1}{n}\sum_{i=1}^{n}(x_i-\tau)^2  
+\] and use the maximum likelihood estimates \(\mu_1 = \hat{\mu}\),
+\(\sigma_1^2 = \hat{\sigma}^2 = \frac{1}{n}\sum_{i=1}^{n}(x_i-\hat{\mu})^2\)
+in the likelihood ratio statistic.
 
@@
 At the beginning of this thesis, we set out to find an algorithm that
-improves upon the Anytime Parameter Free algorithm introduced in
-Locatelli et al. (2016) for the thresholding bandit problem. We aimed to
-make the algorithm perform better in problems with arms that are not
-well approximated as sub-Gaussian; in particular a problem with
-Bernoulli arms of small means, and with a threshold close to 0. We thus
-tried to find a strategy that takes more information about the arms into
-account than only the sample mean. With the Simple Likelihood Ratio
-strategy, we propose an algorithm that fulfills this goal at the cost of
-being distribution specific.
+improves upon the Anytime Parameter Free Thresholding algorithm
+introduced in Locatelli et al. (2016) for the thresholding bandit
+problem. We aimed to make the algorithm perform better in problems with
+arms that are not well approximated as sub-Gaussian; in particular a
+problem with Bernoulli arms of small means, and with a threshold close
+to 0. We thus tried to find a strategy that takes more information about
+the arms into account than only the sample mean. With the Simple
+Likelihood Ratio strategy, we propose an algorithm that fulfills this
+goal at the cost of being distribution specific.
 
@@
 As we see in the experiments that follow, the SLR strategy is able to
-improve significantly upon the APT strategy in many cases.
+improve significantly upon the APT strategy in many problems.
 
@@
 sampling strategy is included. Additionally, we include the Bayes-UCB
-algorithm introduced in Kaufmann et al. (2012) for the cumulative regret
-setting. See \autoref{sec:AppendixBUCB} in the appendix for how we adapt
-the Bayes-UCB algorithm to the thresholding bandit problem.
-
-\subsection{\texorpdfstring{Synthetic Data
-\label{sec:SyntheticData}}{Synthetic Data }}\label{synthetic-data}
+algorithm introduced in Kaufmann et al. (2012a) for the cumulative
+regret setting. See \autoref{app:AppendixBUCB} for how we adapt the
+Bayes-UCB algorithm to the thresholding bandit problem.
+
+\subsection{\texorpdfstring{Simulations with Synthetic Data
+\label{sec:SyntheticData}}{Simulations with Synthetic Data }}\label{simulations-with-synthetic-data}
 
@@
 
-As the next figure shows, essentially all methods converge rapidly to an
-error rate of very close to zero, where the error rate is the share of
-the 5000 simulations on which the classification of the algorithm is
-wrong. Only the uniform strategy that clearly lacks behind. We also
-observe that the variance based algorithms (AugUCB and EVT) lag behind
-at first. AugUCB is able to adjust its sampling scheme only after 1000
-iterations but then rapdily improves to the level of APT. EVT takes
-about 250 samples more to start a quick descend to the performance of
-the other algorithms. All of this, however, happens after the algorithms
-are below an error rate of 0.01. While the SLR algorithm improves upon
-APT, the improvement is a slight one, and not very large in terms of
-budget difference. This underlines that the scenario at hand is ideal
-for the APT algorithm.
+As Figure 4 shows, essentially all methods converge rapidly to an error
+rate of very close to zero, where the error rate is the share of the
+5000 simulations on which the classification of the algorithm is wrong.
+Only the uniform strategy that clearly lacks behind. We also observe
+that the variance based algorithms (AugUCB and EVT) lag behind at first.
+AugUCB is able to adjust its sampling scheme only after 1000 iterations
+but then rapdily improves to the level of APT. EVT takes about 250
+samples more to start a quick descend to the performance of the other
+algorithms. All of this, however, happens after the algorithms are below
+an error rate of 0.01. While the SLR algorithm improves upon APT, the
+improvement is a slight one, and not very large in terms of budget
+difference. This underlines that the scenario at hand is ideal for the
+APT algorithm.
 
@@
 
-The figure below shows the performance of all algorithms. The results
-underline that this problem is much harder in general
+Figure 5 shows the performance of all algorithms. The results underline
+that this problem is much harder in general
 (\(H_2^{APT} \approx 24703\)). The performance of the variance based
@@
 with Bernoulli arms, is the superior performance of the Bayes-UCB
-algorithm adapted from Kaufmann et al. (2012) which was originally
+algorithm adapted from Kaufmann et al. (2012a) which was originally
 designed for cumulative regret problems. Nonetheless, the algorithm
 proves again and again to be the best performing. Compare with
-\autoref{sec:AppendixBUCB} for more analysis on the behavior of the
+\autoref{app:AppendixBUCB} for more analysis on the behavior of the
 Bayes-UCB algorithm in simulation 2. In particular, consider Figures 17
@@
 
-{\centering \includegraphics[width=0.7\linewidth]{Draft_files/figure-latex/unnamed-chunk-1-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-2-1}
 
@@
 
-\caption{Budget allocation across arms for APT and SLR algorithms in simulation 2.}\label{fig:unnamed-chunk-1}
+\caption{Budget allocation across arms for APT and SLR algorithms in simulation 2.}\label{fig:unnamed-chunk-2}
 \end{figure}
@@
 
+\newpage
+
 \subsubsection{Simulations 4 and 5: Exponential and Poisson
@@
 how algorithms perform in presence of, for example, not perfectly i.i.d.
-samples. Every company of course tries to run their algorithms under
-settings as ideal as possible, but there will always be problems. Thus
-our experiments serve as a first robustness check on the algorithms
+samples. Every experimenter of course tries to run their algorithms
+under settings as ideal as possible, but there will always be problems.
+Thus our experiments serve as a first robustness check on the algorithms
 introduced before.
@@
 data set we use here has been collected during the entire month of
-November 2016. It can be considered time series data collected at
-minutely frequency. Thus the data contain 43200 observations per
-product, and overall 8510400 observations.
-
-Since we want to run an offline comparison of bandit algorithms, it is
-important to have at each time point an observation for each arm. Given
-that, it is easy to evaluate the perfomance of algorithms that make
-different decisions at different point in times and thus do not observe
-the same samples. By having an observation for each arm at any given
-time point, each algorithm had at least the opportunity to observe a
-certain sample. Other papers (for example, Li et al., 2011) have solved
-this problem by using a sample drawn uniformly during, for example, an
-A/B test. Then, if the next observation in the sample is not from the
-same arm that the algorithm would like to draw from, observations are
-discarded until the next observation from the selected arm.
-
-The choice of using what is basically multiple time series data as the
-sample offers a simple way of running the algorithms just as often on
-the data as for simulated data. The goal is to perform 5000 runs over
-the sample to confidently assess the performance. Since we would like to
-preserve potential time dependencies in the data, a simple resampling of
-the data is not an option to create the needed 5000 variations of the
-sample. Instead we perform time series cross validation. To preserve the
-autocorrelation, one can create different samples of \(X\) observations
-by sliding a window of size \(X\) over the time series. Moving the
-window one period (in our case one minute) at a time, one ensures that
-no sample shares start and end observation with another sample. In
-particular, this means for a given bandit strategy and two samples that
-the observations that the algorithm collects as feedback during the
+November 2016. It can be considered time series data sampled at minutely
+frequency. Thus the data contain 43200 observations per product, and in
+total 8510400 observations.
+
+Since we would like to run an offline comparison of bandit algorithms,
+it is important to have at each time point an observation for each arm.
+Given that, it is easy to evaluate the perfomance of algorithms that
+make different decisions at different point in times and thus do not
+observe the same samples. By having an observation for each arm at any
+given time point, each algorithm had at least the opportunity to observe
+a certain sample. Other papers (for example, Li et al., 2011) have
+solved this problem by using a sample drawn uniformly during, for
+example, an A/B test. Then, if the next observation in the sample is not
+from the same arm that the algorithm would like to draw from,
+observations are discarded until the next observation from the selected
+arm.
+
+The choice of using what is essentially multivariate time series data as
+the sample offers a simple way of running the algorithms just as often
+on the real data as on simulated data. The goal is to perform 5000 runs
+over the sample to confidently assess the performance. Since we would
+like to preserve potential time dependencies in the data, a simple
+resampling of the data is not an option to create the needed 5000
+variations of the sample. Instead we perform time series cross
+validation. To preserve the autocorrelation, one can create different
+samples of \(n\) observations by sliding a window of size \(n\) over the
+time series. Moving the window one period (in our case one minute) at a
+time, one ensures that no sample shares start and end observation with
+another sample (see Figure 8)\footnote{The graphic is adapted from a
+  graphic by Rob J. Hyndman available at
+  \url{https://gist.github.com/robjhyndman/9fa152c585442bb076eb42a30a020091}}.
+In particular, this means for a given bandit strategy and two samples
+that the observations that the algorithm collects as feedback during the
 initialization phases differ from sample to sample and are never the
@@
 \(1, ..., K\) (or \(1,...,2K\) for EVT) once in this order.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-3-1}
+
+}
+
+\caption{We use time series crossvalidation to create many samples from one data set.}\label{fig:unnamed-chunk-3}
+\end{figure}
+
+While the data set consists of count data (the number of visits to a PDP
+during a given minute), we binarize the data by applying a certain
+threshold. If the count is above this threshold, the new observation is
+\(1\), else \(0\). Thus we have a binary time series of length
+\(60\cdot 24 \cdot 30 = 43200\) for each of the 197 products. Given that
+the number of visitors that reach a given PDP is likely to vary by time
+of day, by day, and in general over time, we expect the mean of the time
+series to not be stable over time. For example, less visitors visit
+during night than during the evening. This leads to a decrease in the
+average number of visits, and creates a daily seasonality. On the other
+hand, more users may visit the site during a weekend, thus leading to a
+spike on Saturdays and Sundays. Because of the latter time dependency,
+it is best practice to run online A/B tests for at least a
+week\footnote{See for example the ``A/B Testing in the Wild''
+  presentation by Emily Robinson, \url{https://youtu.be/SF-ryGgLOgQ}},
+or an integer multiple of weeks, so as to take into account the weekly
+seasonality in the time series. For this reason, the experiments we
+present below are run on \(60 \cdot 24 \cdot 7 = 10080\) observations
+for each arm, so as to have a sample for one full week.
 
@@
 
-While the data set consists of count data (the number of visits to a PDP
-during a given minute), we binarize the data by applying a certain
-threshold. If the count is above this threshold, the new observation is
-\(1\), else \(0\). Thus we have a binary time series of length
-\(60\cdot 24 \cdot 30 = 43200\) for each of the 197 products. Given that
-the number of visitors that reach a given PDP is likely to vary by time
-of day and by day, and in general over time, we expect the mean of the
-time series to not be stable over time. For example, less visitors visit
-during night than during the evening. This leads to a decrease in the
-average number of visits, and creates a daily seasonality. On the other
-hand, more users may visit the site during a weekend, thus leading to a
-spike on Saturdays and Sundays. Because of the latter time dependency,
-it is best practice to run online A/B tests for at least a
-week\footnote{See for example the ``A/B Testing in the Wild''
-  presentation by Emily Robinson, \url{https://youtu.be/SF-ryGgLOgQ}},
-or an integer multiple of weeks, so as to take into account the weekly
-seasonality in the time series. For this reason, the experiments we
-present below are run on \(60 \cdot 24 \cdot 7 = 10080\) observations
-for each arm, so as to have a sample for one full week.
+\newpage
 
@@
 
-\caption{Moving average for the arms used in experiment 1.}\label{fig:unnamed-chunk-4}
+\caption{Moving average for the arms used in experiment 1.}\label{fig:unnamed-chunk-6}
 \end{figure}
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-5-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-7-1}
 
@@
 
-\caption{Performance comparison of algorithms for experiment 1.}\label{fig:unnamed-chunk-5}
+\caption{Performance comparison of algorithms for experiment 1.}\label{fig:unnamed-chunk-7}
 \end{figure}
@@
 arms over time. Indeed, roughly comparing the error curves to the moving
-averages in the previous figure, the increase in errors after round
-\(5000\) and the decreasing error after round \(7500\) seems to line up
-with the fluctuations observed in the data. Given that we evaluate the
-models against a sample mean of all observations, it is not surprising
-that the uniform sampling strategy has a certain advantage when it comes
-to ``factoring out'' the seasonalities. In contrast, the adaptive
-sampling schemes try to adapt more or less quickly to the changes in the
-means--a feature that would be valuable in a cumulative regret
-multi-armed bandit setting. Here, however, it leads to wrong estimates
-of the overall sample mean.
+averages in the Figure 9, the increase in errors after round \(5000\)
+and the decreasing error after round \(7500\) seems to line up with the
+fluctuations observed in the data. Given that we evaluate the models
+against a sample mean of all observations, it is not surprising that the
+uniform sampling strategy has a certain advantage when it comes to
+``factoring out'' the seasonalities. In contrast, the adaptive sampling
+schemes try to adapt more or less quickly to the changes in the means--a
+feature that would be valuable in a cumulative regret multi-armed bandit
+setting. Here, however, it leads to wrong estimates of the overall
+sample mean.
 
@@
 means. Given those and the previous experiment, the performance results
-of Experiment 2 shown in Figure 13 are not surprising. We recognize the
+of Experiment 2 shown in Figure 12 are not surprising. We recognize the
 same structure as previously. The uniform sampling strategy performs the
@@
 
-On the right hand side of figure 13, the performance of the algorithms
+On the right hand side of Figure 12, the performance of the algorithms
 on synthetic data from Bernoulli distributions is depicted. These
-synthetic samples were sampled from distributions with mean equal to the
+synthetic samples are sampled from distributions with mean equal to the
 sample means of the real data. We thereby create similar samples that
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-6-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-8-1}
 
@@
 
-\caption{Moving average of arms used in experiment 2. Dashed line indicates the threshold.}\label{fig:unnamed-chunk-6}
+\caption{Moving average of arms used in experiment 2. Dashed line indicates the threshold.}\label{fig:unnamed-chunk-8}
 \end{figure}
@@
 
-\caption{Performance results of algorithms in experiment 2.}\label{fig:unnamed-chunk-10}
+\caption{Performance results of algorithms in experiment 2.}\label{fig:unnamed-chunk-12}
 \end{figure}
@@
 Using a plot of the pulls at each round across the 5000 simulations in
-Figure 14, as we did for simulation 2, we can try to understand why some
+Figure 13, as we did for simulation 2, we can try to understand why some
 strategies perform well on synthetic data, but poorly on the time series
@@
 
-\caption{Budget allocation of algorithms across arms on real and synthetic data in experiment 2.}\label{fig:unnamed-chunk-11}
+\caption{Budget allocation of algorithms across arms on real and synthetic data in experiment 2.}\label{fig:unnamed-chunk-13}
 \end{figure}
@@
 
+In the thesis at hand, we presented the general thresholding bandit
+problem introduced by Locatelli et al. (2016), as well as their Anytime
+Parameter-Free Thresholding algorithm. Given a few limitations of the
+APT algorithm, we explored the literature on pure exploration
+multi-armed bandit problems to show how the Kullback-Leibler divergence
+can be used to improve algorithms and performance bounds. Based on this
+work, we exhibit the similarity between the thresholding bandit problem
+and hypothesis testing. We derive a lower bound on the complexity of a
+one-armed thresholding bandit that corresponds to the Chernoff-Stein
+Lemma. Continuing with the intuition from hypothesis testing, we propose
+the Simple Likelihood Ratio algorithm for the multi-armed thresholding
+bandit for one-parameter exponential family of distributions. The SLR
+algorithm is shown to repeatedly outperform existing algorithms in
+simulations on Bernoulli, Poisson, and Exponential distributions. We
+show that adding the D-Tracking Rule originally proposed by Garivier and
+Kaufmann (2016) can eradicate some of the remaining weaknesses.
+Additionally to simulations, we performed offline evaluation of adaptive
+sampling strategies using website analytics data. A new time series
+cross validation procedure helped to preserve the time dependency
+structure in the data and allowed for robustness tests of the adaptive
+sampling strategies.
+
+Problems for future work are the derivation of lower and upper bounds on
+the error probability of the SLR algorithm. Furthermore, one might be
+able to adapt the lower bound on the complexity of the one-armed
+thresholding bandit to the multi-armed problem. The surprisingly very
+good performance of the Bayes-UCB algorithm in our simulations, as well
+as its superior concentration of the number of times each arm is pulled,
+justify a theoretical analysis of its performance. Lastly, including
+features as in contextual bandits could improve robustness of strategies
+when data does not fulfill i.i.d. assumptions.
+
 \section{Acknowledgements}\label{acknowledgements}
@@
 the first place. Sonoma Internet GmbH (Amorelie) supported this work by
-giving the authors access to the discussed data set.
+giving the author access to the discussed data set.
+
+The website analytics data used in experiments is available upon
+request. The code for simulations and experiments is available on
+Github: \url{https://github.com/timradtke/master-thesis}
 
@@
 
-O. Capp´e, A. Garivier, O-A. Maillard, R. Munos, and G. Stoltz.
+O. Cappé, A. Garivier, O-A. Maillard, R. Munos, and G. Stoltz.
 Kullback-Leibler upper confidence bounds for optimal sequential
@@
 
-O. Capp´e, A. Garivier, O.-A. Maillard, R. Munos, G. and Stoltz. Supple-
-ment to ``Kullback--Leibler upper confidence bounds for optimal
+O. Cappé, A. Garivier, O.-A. Maillard, R. Munos, G. and Stoltz.
+Supplement to ``Kullback--Leibler upper confidence bounds for optimal
 sequential allocation.'', \emph{Annals of Statistics},
@@
 
-E. Kaufmann, O. Capp´e, and A. Garivier. On Bayesian Upper Confidence
+E. Kaufmann, O. Cappé, and A. Garivier. On Bayesian Upper Confidence
 Bounds for Bandit Problems. In \emph{Proceedings of the 15th
 International Conference on Artificial Intelligence and Statistics
-(AISTATS)}, 2012.\par
-
-E. Kaufmann, O. Capp´e, A. Garivier. On the Complexity of Best Arm
+(AISTATS)}, 2012a.\par
+
+E. Kaufmann, N. Korda, and R. Munos. Thompson Sampling: An
+Asymptotically Optimal Finite Time Analysis. In \emph{Proceedings of the
+23rd International ALT Conference}, Algorithmic Learning Theory,
+199-213, 2012b.
+
+E. Kaufmann, O. Cappé, A. Garivier. On the Complexity of Best Arm
 Identification in Multi-Armed Bandit Models. Journal of Machine Learning
@@
 
-\section{Appendix}\label{appendix}
-
-\subsection{\texorpdfstring{Proof of Thresholding Bandit Lower Bound
-\label{sec:AppendixAPTLB}}{Proof of Thresholding Bandit Lower Bound }}\label{proof-of-thresholding-bandit-lower-bound}
+\appendix
+
+\section{Example of User Feedback in Foursquare App} \label{app:Foursquare}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{figures/Foursquare_Screenshot.png}
+\caption{The right screenshot shows aggregated user feedback in the
+Foursquare app. One could use thresholding bandit algorithms as
+presented in this thesis to ask different questions so as to optimize
+the confidence with which the results are displayed for a restaurant in
+the app.}
+\end{figure}
+
+\section{Proof of Theorem 2} \label{app:AppendixAPTLB}
 
@@
 
-\emph{Proof of Theorem \ref{theorem:Locatelli2016Theorem1}}: Locatelli
-et al. (2016) derive a lower bound for the thresholding bandit problem.
-We restate the proof here. The idea is as follows. The problem
-formulation considered in the paper describes bandit problems for
-\(R\)-sub-Gaussian distributions. To show a lower bound, we show that
-every algorithm is expected to make a certain error even if we consider
-a very restricted scenario. Even then, the best algorithm will have a
-maximum error probability with which it cannot distinguish between the
-actual setting and slightly changed settings (under which the answer for
-the true setting leads to a misclassification).
+Locatelli et al. (2016) derive a lower bound for the thresholding bandit
+problem. The idea is as follows. The problem formulation considered in
+the paper describes bandit problems for \(R\)-sub-Gaussian
+distributions. To show a lower bound, we show that every algorithm is
+expected to make a certain error even if we consider a very restricted
+scenario. Even then, the best algorithm will have a maximum error
+probability with which it cannot distinguish between the actual setting
+and slightly changed settings (under which the answer for the true
+setting leads to a misclassification).
 
@@
 distributions \(\nu_i\) with mean \(\mu_i\) and variance
-\(\sigma^2 = 1\). ``in which w''e set \(\tau = 0\) and \(\epsilon = 0\)
-w.l.o.g. Consequently, for each arm \(i\) the distance from the
-threshold is given by \(\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i\).
-Thus, we have for every arm the distribution
+\(\sigma^2 = 1\). We set \(\tau = 0\) and \(\epsilon = 0\) w.l.o.g.
+Consequently, for each arm \(i\) the distance from the threshold is
+given by \(\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i\). Thus, we have
+for every arm the distribution
 \(\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)\). Furthermore,
@@
 At this point, we have defined a finite set of problems of Gaussian
-distributions with fixed variance 1 for a given set of set of gaps
-between the means of the distributions and the threshold,
-\((\Delta_k)_k\). We now proof a lower bound on the worst case regret of
-any algorithm; that is, the maximum error probability that even the best
+distributions with fixed variance 1 for a given set of gaps
+\((\Delta_k)_k\) between the means of the distributions and the
+threshold. We now prove a lower bound on the worst case regret of any
+algorithm; that is, the maximum error probability that even the best
 algorithm makes on this problem.
 
-\subsubsection{Statistical Decision}\label{statistical-decision}
+\textbf{Statistical Decision}
 
@@
 and \(H_1\). Then an overall error probability can be seperated into
-\(P_{H_0}(g=1) + P_{H_1}(g = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)\).
+\(\mathbb{P}_{H_0}(g=1) + \mathbb{P}_{H_1}(g = 0) = \mathbb{P}_{H_0}(\Omega^C) + \mathbb{P}_{H_1}(\Omega)\).
 
@@
 \begin{align}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big) \\
-& = \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \Big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \Big) \\
+& = \max \Big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \Big) \label{LocatelliTheorem1ExpRegret}
 \end{align}
 
-\subsubsection{Empirical Kullback-Leibler
-Divergence}\label{empirical-kullback-leibler-divergence}
+\textbf{Empirical Kullback-Leibler Divergence}
 
@@
 probability can be written as the expected change in the likelihood of
-observed data when moving from distribution \(P_{\mathcal{B}_0}\) to
-\(P_{\mathcal{B}_i}\), times the probability under the original state.
+observed data when moving from distribution \(P_{\mathcal{B}^0}\) to
+\(P_{\mathcal{B}^i}\), times the probability under the original state.
 In other words, the probability of event \(\mathcal{A}_i\) under state
@@
 
-\subsubsection{Change of Distribution}\label{change-of-distribution}
+\textbf{Change of Distribution}
 
@@
 
-\subsubsection{Concentration of the Empirical Kullback-Leibler
-Divergence}\label{concentration-of-the-empirical-kullback-leibler-divergence}
+\textbf{Concentration of the Empirical Kullback-Leibler Divergence}
 
@@
 
-Two things are left to do: With \(T_i\), we still have one random
-variable left which we cannot leave in our bound. Second, we are
-actually not interested in \(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)
-but in
+Two things are missing: With \(T_i\), there still is one random variable
+left which we need to bound to make the overall bound useful. Second, we
+are actually not interested in
+\(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\) but in
 \(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\).
 
-\subsubsection{\texorpdfstring{Bounding \(T_i\) for
-\(\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)}{Bounding T\_i for \textbackslash{}max\_\{i \textbackslash{}in \textbackslash{}\{1,\textbackslash{}dots,K\textbackslash{}\}\}\textbackslash{}mathbb\{P\}\_\{\textbackslash{}mathcal\{B\}\^{}i\}(\textbackslash{}mathcal\{A\}\_i)}}\label{bounding-t_i-for-max_i-in-1dotskmathbbp_mathcalbimathcala_i}
-
-We are actually interested in bounding
-\(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\).
+\textbf{Bounding \(T_i\) for
+\(\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)}
+
 In general it holds that
@@
 \(b = 4\sqrt{\log((4\log(T)+1)K)}\). Then use \(ab \leq a^2 + b^2\) to
-write \(ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)\). And so:
+write \(ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)\). Then:
 
@@
 
-\subsubsection{Bringing everything
-together}\label{bringing-everything-together}
+\textbf{Bringing everything together}
 
@@
 
-\subsection{\texorpdfstring{Lower Bound for Thresholding Bandit Problem
-with KL-divergence
-\label{sec:corollaryLBTBPproof}}{Lower Bound for Thresholding Bandit Problem with KL-divergence }}\label{lower-bound-for-thresholding-bandit-problem-with-kl-divergence}
-
-\subsubsection{\texorpdfstring{Lower Bound for One-Armed Thresholding
-Bandit
-\label{sec:corollaryLB1TBPproof}}{Lower Bound for One-Armed Thresholding Bandit }}\label{lower-bound-for-one-armed-thresholding-bandit}
-
-\textbf{Proof}: The proof follows closely the proof of Theorem 12 in
-Kaufmann et al. (2016) and is again an application of their
-transportation Lemma, Lemma 2.
-
-Consider the one-armed bandit problem, \(K = 1\) with the canonical
-exponential family of distributions distribution \(\nu_1\) parameterized
-by its mean \(\mu_1\). Furthermore, given we are in the thresholding
-bandit problem, we have a threshold \(\tau\) against which the arm is
-classified. Assume w.l.o.g. that for \(\nu_1\), \(\mu_1 \geq \tau\).
-Thus, \(\mathcal{S}_{\tau}^* = \{1\}\). After \(T\) rounds, a consistent
+\section{Proof of Corollary 1} \label{app:corollaryLBTBPproof}
+
+The proof follows closely the proof of Theorem 12 in Kaufmann et al.
+(2016) and is again an application of their Lemma 1. Consider the
+one-armed bandit problem, \(K = 1\) with the canonical exponential
+family of distributions distribution \(\nu_1\) parameterized by its mean
+\(\mu_1\). Furthermore, given we are in the thresholding bandit problem,
+we have a threshold \(\tau\) against which the arm is classified. Assume
+w.l.o.g. that for \(\nu_1\), \(\mu_1 \geq \tau\). Thus,
+\(\mathcal{S}_{\tau}^* = \{1\}\). After \(T\) rounds, a consistent
 algorithm returns with error probability \(p_T(\nu)\) the guess
@@
 \(\nu'\) with mean \(\mu_1' < \tau\) such that the correct
-classification from \(\nu\) is now wrong:
-\(\mathcal{S}_{\tau}^* {'} = (\mathcal{S}_{\tau}^*)^C = \{\emptyset\}\).
+classification of \(\nu\) is now wrong:
+\(\mathcal{S}_{\tau}^* {'} = (\mathcal{S}_{\tau}^*)^C = \emptyset\).
 Consequently, since the algorithm is still consistent on this problem,
@@
 problem \(\nu\) is larger than the error probability in problem
-\(\nu'\), that is: for every \(\epsilon > 0\), there exists
-\(t_0(\epsilon)\) such that for all \(t \geq t_0(\epsilon)\) we have
-
-\begin{equation*}
-\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_{\nu}(A). \label{eq:BoundForCorollary}
-\end{equation*}
+\(\nu'\), that is: for every \(\delta > 0\), there exists
+\(t_0(\delta)\) such that for all \(t \geq t_0(\delta)\) we have
+
+\begin{equation}
+\mathbb{P}_{\nu'}(A) \leq \delta \leq \mathbb{P}_{\nu}(A). \label{eq:BoundForCorollary}
+\end{equation}
 
@@
 & \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)) \\
-& \geq d(\epsilon, 1- p_t(\nu)) \\
-& = \epsilon \log\Big(\frac{\epsilon}{1-p_t(\nu)}\Big) + (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) \\
-& \geq (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) + \epsilon \log(\epsilon) \\
+& \geq d(\delta, 1- p_t(\nu)) \\
+& = \delta \log\Big(\frac{\delta}{1-p_t(\nu)}\Big) + (1-\delta) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) \\
+& \geq (1-\delta) \log \Big(\frac{1-\delta}{p_t(\nu)}\Big) + \delta \log(\delta) \\
 \end{align*}
 
-Letting \(\epsilon \rightarrow 0\), we get
+Letting \(\delta \rightarrow 0\), we get
 
@@
 \(\tau\) since else the classification of \(\nu_1\) is again correct).
-By pluggin in, we get the result:
-
-\[
-t \KL(\tau, \mu_1) \geq -\log p_t(\nu) \quad \text{for} \; \mu_1' \rightarrow \tau.
-\]
-
-\subsubsection{\texorpdfstring{Lower Bound for \(K\)-Armed Thresholding
-Bandit
-\label{sec:corollaryLBKTBPproof}}{Lower Bound for K-Armed Thresholding Bandit }}\label{lower-bound-for-k-armed-thresholding-bandit}
-
-\textbf{Proof}: The proof is very similar to the proof of the corollary
-for \(K=1\). However, the alternative model needs more motivation than
-in the case of a single arm. But first, consider again that we are in
-the thresholding bandit problem with \(K\) arms of one-parameter
-canonical exponential family distributions that are parameterized by
-their means \(\mu_1, ..., \mu_K\) for the original problem
-\(\nu = (\nu_1, ..., \nu_K)\). W.l.o.g, assume that all arms are above
-the threshold, that is, \(\mu_1 \geq \tau, ..., \mu_K \geq \tau\). Then
-\(\mathcal{S}_{\tau}^* = \{1, ... , K\}\). The correct classification
-returned after \(t\) rounds is thus the event
-\(A = (\hat{\mathcal{S}}_{\tau} = \{1, ..., K\})\). We can now consider
-Lemma 2. The RHS is maximized when the alternative model is chosen such
-that \(d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A))\) is maximized.
-Given the event \(A\) as defined before, this is the case when
-\(\mathbb{P}_{\nu'}(A)\) is as small as possible. For consistent
-algorithms, this is the case when \(\nu'\) is chosen such that all
-\(\mu_1' < \tau, ..., \mu_K' < \tau\). Then even classifying a single
-arm correctly under \(\nu\) would lead to a mistake in \(\nu'\).
-Consequently, \(A\) is the most unlikely classification for a consistent
-algorithm for the problem \(\nu'\). We thus expect for any consistent
-algorithm that \(\mathbb{P}_{\nu}(A)\) becomes large and
-\(\mathbb{P}_{\nu'}(A)\) becomes small as the number of observations
-\(t\) increases. Again, for every \(\epsilon > 0\), there exists
-\(t_0(\epsilon)\) such that for all \(t \geq t_0(\epsilon)\) we have
-\(\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)\). This
-allows us to now use Lemma 1 as previously:
-
-\begin{align*}
-\sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\nu_i', \nu_i) & \geq \sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\tau, \mu_i) \\
-& \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)) \\
-& \geq d(\epsilon, 1-p_t(\nu)) \\
-& = \epsilon \log \Big(\frac{\epsilon}{1-p_t(\nu)}\Big) + (1-\epsilon) \log \Big( \frac{1-\epsilon}{p_t(\nu)}\Big) \\
-& \geq (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) + \epsilon \log(\epsilon)
-\end{align*}
-
-We let \(\epsilon \rightarrow 0\), divide by \(t\) and take the limsup
-on both sides as in Kaufmann et al. (2016):
-
-\begin{align*}
-\lim_{t \rightarrow \infty} \sup - \frac{1}{t} \log p_t(\nu) & \leq \lim_{t \rightarrow \infty} \sup \frac{1}{t} \sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\tau, \mu_i) \\
-& \leq \max_{i \in \{1,...,K\}} \KL(\tau, \mu_i)
-\end{align*}
-
-Though, since for the alternative problem \(\nu'\) we have for every
-\(i \in \{1,...,K\}\) that \(\mu_i = \tau\), it should hold for any
-consistent algorithm that \(\mathbb{E}_{\nu'}[N_i(t)] = \frac{t}{K}\),
-that is, every arm receives an equal amount of the budget. In that case,
-the above equation simplifies to
-
-\[
-- \frac{1}{t} \log p_t(\nu) \leq \frac{1}{t} \sum_{i=1}^K \frac{t}{K}\KL(\tau, \mu_i) = \frac{1}{K} \sum_{i=1}^{K} \KL(\tau, \mu_i),
-\]
-
-that is, the complexity is given by the simple average of the
-Kullback-Leibler distances of the threshold with regard to the
-respective distributions. This relates well to the lower bound that
-Kaufmann et al. (2016) describe in their Theorem 12 for consistent
-algorithms using \emph{uniform} sampling strategies; in our case,
-however, it is explained by the fact that under the alternative model,
-every consistent algorithm should adapt to a uniform sampling strategy.
-Thus our bound holds for any consistent strategy.
-
-\subsection{\texorpdfstring{Bayes-UCB Algorithm for the Thresholding
-Bandit Problem
-\label{sec:AppendixBUCB}}{Bayes-UCB Algorithm for the Thresholding Bandit Problem }}\label{bayes-ucb-algorithm-for-the-thresholding-bandit-problem}
-
-We show how the Bayes-UCB algorithm (Algorithm 1, Kaufmann et al., 2012)
-is adapted to the thresholding bandit problem to be used in the
-experiments in chapter \autoref{chap:Experiments}. The adapted version
-of their Algorithm 1 is given in Algorithm 4 below. In particular,
-notice that we not only calculate upper quantiles \(q_i^u(t)\), but also
-lower quantiles \(q_i^l(t)\), as we have to be able to compare against
+
+\section{Bayes-UCB Algorithm for the Thresholding Bandit Problem} \label{app:AppendixBUCB}
+
+We show how the Bayes-UCB algorithm (Algorithm 1, Kaufmann et al.,
+2012a) is adapted to the thresholding bandit problem to be used in the
+experiments in \autoref{chap:Experiments}. The adapted version of their
+Algorithm 1 is given in Algorithm 4 below. In particular, notice that we
+not only calculate upper quantiles \(q_i^u(t)\), but also lower
+quantiles \(q_i^l(t)\), as we have to be able to compare against
 \(\tau\) from both sides. These quantiles rely on the posterior
@@
 distributions in simulations 1 to 3 and initialize them with parameters
-\(\alpha_0\) and \(\beta_0\). See the setup in Kaufmann et al. (2012),
+\(\alpha_0\) and \(\beta_0\). See the setup in Kaufmann et al. (2012a),
 especially equation (3), to see how the posterior distribution is
@@
 }
-\caption{Bayes-UCB algorithm from Kaufmann et al. (2012) adapted to the thresholding bandit problem.}\label{bayesucb_tbp}
+\caption{Bayes-UCB algorithm from Kaufmann et al. (2012a) adapted to the thresholding bandit problem.}\label{bayesucb_tbp}
 \end{algorithm}
@@
 which comes at a surprise given that is is designed for the cumulative
-regret setting and thus should tend to explore the arms to less, we run
-the Bayes-UCB algorithm for simulation 2 with three different choices of
-the parameter. In Figure 13, we see the performance results of the three
-versions, whereas Figure 14 shows how the algorithm allocates its budget
-across the arms over time. The three versions differ in the quantile
-parameter \(c\) (compare \autoref{sec:AppendixBUCB}) for which we choose
-\(c \in \{1/5, 1, 5\}\) to explore more or less. In Kaufmann et al.
-(2012), the cumulative regret upper bound for the Bayes-UCB is shown for
-\(c\geq 5\), though they report that the choice of \(c=0\) worked much
-better in their experiments. In our problem, it makes also sense that
-the versions with smaller quantiles (smaller \(c\)) tend to perform
-better, as these correspond to more exploration of the arms. In this
-particular simulation, the choices of \(c=1/5\) and \(c=1\) perform very
-similar. We see that the worse performance of \(c=5\) can be attributed
-to a initial phase of sampling primarily the arms with mean below the
-threshold. This comes from the fact that the Bernoulli and Beta
-distributions are bounded between \(0\) and \(1\), with \(\tau\) very
-close to \(0\). Thus, the index \(B_i^{BUCB}(t)\) cannot be larger than
-\(\tau\) for arms with \(\hat{\mu}_i(t) \geq \tau\). For arms with
-\(\hat{\mu}_i(t) < \tau\), however, the index can be as large as
-\(B_i^{BUCB}(t) = 0.95\). This leads to the effect seen in Figure 14:
+regret setting and thus should tend to explore the arms less, we run the
+Bayes-UCB algorithm for simulation 2 with three different choices of the
+parameter \(c\). In Figure 15, we see the performance results of the
+three versions, whereas Figure 16 shows how the algorithm allocates its
+budget across the arms over time. The three versions differ in the
+quantile parameter \(c\) (compare \autoref{app:AppendixBUCB}) for which
+we choose \(c \in \{1/5, 1, 5\}\) to explore more or less. In Kaufmann
+et al. (2012a), the cumulative regret upper bound for the Bayes-UCB is
+shown for \(c\geq 5\), though they report that the choice of \(c=0\)
+worked much better in their experiments. In our problem, it also makes
+sense that the versions with smaller quantiles (smaller \(c\)) tend to
+perform better, as these correspond to more exploration of the arms. In
+this particular simulation, the choices of \(c=1/5\) and \(c=1\) perform
+very similar. We see that the worse performance of \(c=5\) can be
+attributed to a long initial phase of sampling primarily the arms with
+mean below the threshold. This comes from the fact that the Bernoulli
+and Beta distributions are bounded between \(0\) and \(1\), with
+\(\tau\) very close to \(0\). Thus, the index \(B_i^{BUCB}(t)\) cannot
+be larger than \(\tau\) for arms with \(\hat{\mu}_i(t) \geq \tau\). For
+arms with \(\hat{\mu}_i(t) < \tau\), however, the index can be as large
+as \(B_i^{BUCB}(t) = 0.95\). This leads to the effect seen in Figure 14:
 Due to \(c=5\), the indexes are based on very large quantiles even in
@@
 
-\caption{Budget allocation across arms for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter.}\label{fig:unnamed-chunk-12}
+\caption{Budget allocation across arms for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter.}\label{fig:unnamed-chunk-14}
 \end{figure}
@@
 would sample an arm for the optimal share of the budget, in every
-simulation. This is of course not the case, since the number of pulls of
-a given arm at the end of the budget, \(T_i(T)\), is a random variable
-for adaptive sampling strategies. Given the 5000 iterations conducted in
-simulation 2, we can plot the empirical distribution of this random
-variable for different arms.
-
-In Figure 15, we show the distribution of \(T_6(T)\) for algorithms APT,
+simulation. This, of course, is not the case since the number of pulls
+of a given arm at the end of the budget, \(T_i(T)\), is a random
+variable for adaptive sampling strategies. Given the 5000 iterations
+conducted in simulation 2, we can plot the empirical distribution of
+this random variable for different arms.
+
+In Figure 17, we show the distribution of \(T_6(T)\) for algorithms APT,
 Bayes-UCB, and SLR. We see that the distribution of the Bayes-UCB
@@
 across a very large interval. Both algorithms have several iterations in
-which they draw arm 6, the most difficult arm only a single time (during
-initialization). This happens for APT more than 5\% of the iterations,
-and leads to the spike on the very left of the graph. In order to cope
-at least a little bit with this problem, we have also run the SLR
-algorithm with the D-Tracking rule as introduced in Garivier and
-Kaufmann (2016). The effect is nearly not noticeable in Figure 15, but
-the minimum number of observations is not clearly bounded away from 0.
-The effect on the performance was described before and is very
-noticeable in comparison to SLR without D-Tracking. However, even with
-D-Tracking the performance of Bayes-UCB is not reached. We describe SLR
-with D-Tracking in Algorithm 5.
+which they draw arm 6--the most difficult arm--only a single time
+(during initialization). This happens for APT in more than 5\% of the
+iterations, and leads to the spike on the very left of the graph. In
+order to cope at least a little bit with this problem, we have also run
+the SLR algorithm with the D-Tracking rule as introduced in Garivier and
+Kaufmann (2016). The effect is barely noticeable in Figure 17, but the
+minimum number of observations is now clearly bounded away from 0. The
+effect on the performance was described before and is very noticeable in
+comparison to SLR without D-Tracking. However, even with D-Tracking the
+performance of Bayes-UCB is not reached. We describe SLR with D-Tracking
+in Algorithm 5.
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-13-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-15-1}
 
@@
 
-\caption{Empirical distribution of pulls of arm 6 in simulation 2 by different algorithms.}\label{fig:unnamed-chunk-13}
+\caption{Empirical distribution of pulls of arm 6 in simulation 2 by different algorithms.}\label{fig:unnamed-chunk-15}
 \end{figure}
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-14-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-16-1}
 
@@
 
-\caption{Empirical distribution of pulls of arms 1 and 10 in simulation 2 by different algorithms.}\label{fig:unnamed-chunk-14}
+\caption{Empirical distribution of pulls of arms 1 and 10 in simulation 2 by different algorithms.}\label{fig:unnamed-chunk-16}
 \end{figure}
 
-\subsection{SLR Algorithm with D-Tracking
-Rule}\label{slr-algorithm-with-d-tracking-rule}
+\newpage
+
+\section{Simple Likelihood Ratio Algorithm with D-Tracking Rule} \label{app:SLRD}
 
@@
 
-\subsection{Means in Simulations 4 and
-5}\label{means-in-simulations-4-and-5}
+\newpage
+
+\section{Means in Simulations 4 and 5} \label{app:MeansSim45}
 
@@
 
+\newpage
+
+\pagenumbering{gobble}
+
+\Large{\bf Selbstständigkeitserklärung\\}
+
+\vspace*{1.5\baselineskip}
+
+\large Ich erkläre hiermit, dass ich die vorliegende Arbeit
+selbstständig und nur unter Verwendung der angegebenen Quellen und
+Hilfsmittel angefertigt habe und noch nicht für andere Prüfungen
+eingereicht habe. Sämtliche Quellen einschließlich Internetquellen, die
+unverändert oder abgewandelt wiedergegeben werden, insbesondere Quellen
+für Texte, Grafiken, Tabellen und Bilder, sind als solche kenntlich
+gemacht. Mir ist bekannt, dass bei Verstößen gegen diese Grundsätze ein
+Verfahren wegen Täuschungsversuchs bzw. Täuschung eingeleitet wird.
+
+\vspace*{3\baselineskip}
+
+Berlin, den 18. September 2017
+
 \end{document}

### 2017-09-18 Thesis/Draft_for_Markus.Rmd
Printed version

--- 2017-09-18 Thesis/20170916_Draft.Rmd
@@
 
-\vspace*{10\baselineskip}
-
-"In general, we look for a new law by the following process: First we guess it.
-Then we – now don't laugh, that's really true.
-Then we compute the consequences of the guess to see what, if this is right, if this law that we guessed is right, to see what it would imply.
-And then we compare the computation results to nature, or we say compare to experiment or experience, compare it directly with observations to see if it works.
-If it disagrees with experiment, it's wrong.
-In that simple statement is the key to science.
-It doesn't make any difference how beautiful your guess is, it doesn't make any difference how smart you are, who made the guess, or what his name is.
-If it disagrees with experiment, it's wrong.
-That's all there is to it."
-
-- Richard Feynman in *Richard Feynman Messenger Lectures at Cornell University: The Character of Physical Law. Chapter 7, Seeking New Laws*.
-
-\newpage
-
-# Introduction \label{chap:Introduction}
-
-The thesis at hand joins a large literature concerned with the problem of sequential sampling.
-One is familiar with the idea of "batch sampling", where the entire sample is gathered first and analyzed only after the last sample has become available.
-However, as noted in Chernoff (1958), many situations arise in which one would like to gather feedback from samples as they are drawn, so as to influence the choice of the next sample.
-The two fundamental characteristics of the latter sampling process are that it is sequential and adaptive.
-Since observations are drawn in sequence, one has a chance to analyze past observations in order to adapt the decision of what sample one would like to observe next.
-
-This makes sequential sampling especially relevant in situations where there is an inherent cost to obtaining samples, or where only a limited amount of samples can be collected.
-The classical example is that of clinical trials in which a researcher tests two drugs on patients to observe which one performs better.
-Not only is it difficult to gather enough patients, but one would also like to adapt the sampling such that as soon as possible more patients receive the better drug and are cured.
-As noted in Cappé et al.
-(2013), this example dates back to Thompson (1933, 1935).
-Such problems are known as multi-armed bandit problems in which the sampling is adapted so as to minimize the cumulative regret: In the case of the drug tests, one would like to sample the two drugs in a way to find the best drug as soon as possible and then to test this drug more and more often and more often than the worse drug.
-This would lead to cumulatively more healthy patients than testing both drugs uniformly; it would minimize the regret from treating patients with an ineffective drug.
-
-Instead of drugs, one can consider two or more unknown distributions (which we call arms in the multi-armed bandit problem in analogy with the one-armed bandit slot machine).
-These distributions have different means, and one can draw samples sequentially from the distributions in order to estimate their means.
-To minimize the cumulative regret measure, one would like to play the distribution with the highest mean as much as possible (*Exploitation*).
-At the same time, however, one has to sample all arms at least a little, so as to initially find the best arm (*Exploration*).
-Any algorithm thus has to handle a trade-off between exploration and exploitation to minimize the regret.
-How can we organize the sampling in order to achieve this task?
-
-While Gittins (1979) presents an Bayesian-optimal solution to the cumulative regret problem, the Upper-Confidence Bound (UCB) algorithms pioneered by Agrawal (1995) and Auer, Cesa-Bianchi and Fischer (2002) have lead to a blooming literature on multi-armed bandit problems that has been picked up to solve modern problems in website and advertising optimization, where advertisers try to allocate their advertising optimally so as to reduce regret from showing poorly converting advertisements.
-Several algorithms like the KL-UCB algorithm based on Kullback-Leibler divergence upper confidence intervals (Cappé et al., 2013) or the Bayes-UCB algorithm (Kaufmann et al., 2012)  have followed and been shown to be optimal as they reach the lower bound introduced in Lai and Robbins (1985) and Burnetas and Katehakis (1996).
-
-These algorithms have in common that they compute after every new sample an index for each of the unknown distributions.
-This index is based solely on the past (observed) data, and then used to pick the distribution from which the next sample should be drawn.
-Using these indexes, algorithms can sample sequentially and adapt their strategies to observations as they are collected.
-
-Similar algorithms based on indexes can be used on related problems.
-Instead of minimizing cumulative regret, it can be of interest to find the best arm, that is, the distribution with the largest mean -- with as few samples as possible and with confidence as large as possible.
-This is particularly useful when there is not a cost from testing arms with lower mean, but when drawing any sample is costly.
-Thus one needs to explore the distributions as efficiently as possible.
-Exploitation is not necessary, and the setting is thus referred to as *Pure Exploration*.
-The need for strategies other than uniform sampling arises: One does not want to continue to sample distributions that one is confident in.
-This setting is related to the problem faced in Bayesian Optimization: Training large neural networks is costly in terms of time and computation, and so the parameter space needs to be explored with as few samples as possible.
-(Zhang et al., 2017; Brochu et al., 2010).
-The problem of best arm identification is also very related to statistical hypothesis testing as noted by Chernoff (1958) since one has to make a decision about how the means of distributions relate to each other.
-The main difference being that the bandit setting includes the testing procedure in the sampling process.
-
-Given the focus on exploration, the pure exploration problem is usually described with a loss function different from the one in the cumulative regret settings.
-Audibert et al.
-(2010) introduce a soft measure called *simple regret* based on which they describe UCB policies.
-Other authors investigate binary measures that are equal to 1 when the best arm has not been identified (Russo, 2016; Garivier and Kaufmann, 2016).
-These binary measures correspond to the probability of the identified arm being the best, and thus inherently related to hypothesis testing.
-The problem of best arm identification can readily be extended to the so called Top-$m$ problem of identifying the best $m$ of $K$ arms (Kaufmann and Kalyanakrishnan, 2013; Kaufmann et al.
-2016).
-
-In this thesis, we consider the thresholding bandit problem.
-While the name is reminiscient of the cumulative regret multi-armed bandit, the problem is more similar to the top-$m$ problem.
-But instead of identifying the best $m$ out of $K$ arms, one aims to find all distributions out of $K$ that have a mean at least as large as a fixed threshold.
-Given that an implicit threshold arises in the top-$m$ problem between the $m$-th best and the $(m+1)$-th best arm (Kaufmann et al., 2016), the two problems share many characteristics.
-We discuss this in more detail in \autoref{chap:KullbackLeiblerPureExploration}.
-In the form described in Locatelli et al.
-(2016), algorithms in the thresholding bandit problem are evaluated against a binary loss function penalizing whenever an arm has not been classified correctly as being above or below the threshold, and thus focus on exploration similar to algorithms employed for best arm identification.
-Indeed, Locatelli et al.
-(2016) show how their thresholding algorithm can be used for best arm identification when the mean of the best arm is known upfront.
-
-In the following, we first present the thresholding bandit problem in detail in \autoref{chap:ThresholdingBanditProblem}.
-To then extend upon the algorithm proposed by Locatelli et al.
-(2016) and discussed in \autoref{sec:TheAPTAlgorithm}, we first explore in \autoref{chap:KullbackLeiblerPureExploration} how the Kullback-Leibler divergence has been employed in the best arm identification literature by Garivier and Kaufmann (2016) and Kaufmann et al.
-(2016) as this will lead us to our own extension.
-We shortly describe in \autoref{sec:VarianceBasedAlgorithms} two variance-based algorithms for the thresholding bandit problem introduced in Mukherjee et al.
-(2017) and Zhang et al.
-(2017), before introducing the new Simple Likelihood Ratio algorithm in \autoref{sec:LRforUnivariateExponentialFamily}.
-We end in \autoref{chap:Experiments} with experiments to examine the performance of different algorithms.
-
-\newpage
-
-# The Thresholding Bandit Problem \label{chap:ThresholdingBanditProblem}
-
-## An Example
-
-To introduce the thresholding bandit problem, consider a common situation among internet-based companies.
-These companies often collect user feedback to offer reviews and ratings on websites or in apps, or collect it to improve their services.
-Netflix lets users rate movies with "Thumbs up" and "Thumbs down", apps like Clue ask users a question per day to learn to predict the user's health and mood.
-An online shop might give customers a one-question survey after they make a purchase.
-Finally, Foursquare and Yelp ask users to rate coffee shops, bars, and restaurants.
-
-Consider the problem the latter companies face.
-Whenever a user reports that she visited a restaurant, the app would like to ask questions about her experience.
-To give a simple example, assume users are not willing to answer more than one question per restaurant visit, and the app would like to find out two things: Does the restaurant have good service?
-Is the restaurant trendy?
-See \autoref{sec:Foursquare} for what this information looks like in the Foursquare app.
-
-If the feedback that users can give is restricted to binary "Yes" or "No" answers, then we can model the feedback as Bernoulli random variables
-
-$$
-X_{\text{service}} \sim \text{Ber}(\mu_{\text{service}}) \quad \text{and} \quad X_{\text{trendy}} \sim \text{Ber}(\mu_{\text{trendy}}).
-$$
-
-The app will then display a "Good service" or "This place is trendy" description for the restaurant if $\mu_{\text{service}}$ and $\mu_{\text{trendy}}$ are estimated to be above a certain threshold, for example $\tau = 0.5$.
-That is, more than half of the people would describe the place as having good service, or as trendy.
-
-To make the app as useful as possible to other users, this information should be shown as quickly as possible.
-But even though the app has thousands of users, not that many people visit a specific restaurant, and even less people report this back to the app.
-Thus the company only has a limited budget of $T$ potential users from which to collect samples $X_{\text{service}}$ and $X_{\text{trendy}}$ from.
-How can the company ask these $T$ questions to be as confident as possible in its classification, that is, in the information it displays?
-
-A straightforward way of sampling users would be to ask the two questions in a round-robin fashion: Ask for "Service", then for "Trendy", then for "Service", ...
-Given 100 users, 50 users give feedback on the service level, 50 users report on the trendiness level.
-This however is unlikely to be optimal with respect to the confidence after 100 samples.
-Given that the company asks the users sequentially, there is the option to adapt the sampling strategy over time: If the first ten users report $\sum_{s=1}^{10}X_{\text{service},s}=10$, while $\sum_{s=1}^{10}X_{\text{trendy},s}=5$, then the company might already be quite confident that $\mu_{\text{service}} \geq \tau = 0.5$, while this is less clear for $\mu_{\text{trendy}}$.
-Instead of continuously sampling both questions, it might be more useful to collect more feedback on the trendiness level so as to figure out its position relative to the threshold.
-After all, the company would like to use the 100 samples to maximize its confidence in both displayed tips.
-
-Finding the optimal sequential sampling strategy to classify distributions against a threshold with as much confidence as possible after a limited budget of samples is the problem described above, and the problem described by the thresholding bandit problem which we discuss for the remainder of this thesis.
-In the following section, we define the general setting of the thresholding bandit problem.
-
-## General Setting \label{sec:Setup}
-
-Consider a setting with a set of $\mathbb{A}=\{1, ..., K\}$ unknown probability distributions $\nu_i, i \in \mathbb{A}$.
-To stick with the idea of multi-armed bandits, we call the distributions arms, and observations from the arms rewards (Bubeck and Cesa-Bianchi, 2012).
-The learner is interested in learning about the structure of the arms; in particular, she would like to estimate the means $\mu_1, ..., \mu_K$ by sequentially drawing observations $X_{i,1}, X_{i,2}, ...$ from the different arms, where $X_{i} \sim \nu_i$.
-However, at time $t$ the learner cannot observe a reward from every distribution but must select a single arm $I_t$ from which she would like to observe the reward $X_{I_t,t}$.
-Often, adaptive sampling strategies makes the decision of which arm to pull by computing an index $B_i(t)$ for each arm.
-If $T_i(t)$ is the number of samples observed until time $t$ for arm $i$, then is $B_i(t)$ a function of the past rewards $X_{i,1}, ..., X_{i,T_i(t)}$ observed for arm $i$, and w.l.o.g.
-$I_t = \arg \min_{i = 1,...K} B_i(t)$.
-The set of indexes can be called strategy (Kaufmann et al., 2012) which makes it clear that the strategy is adapted as more observations are collected.
-Strategies of this kind are also called index policies.
-
-Which index proves to be useful is determined by the loss function with which the decisions of the algorithm are evaluated.
-Many problems are concerned with finding the arm with the largest mean $\mu_i^*$ while collecting loss either cumulatively during (Auer and Cesa-Bianchi, 2012) or once at the end of the sampling (Kaufmann et al., 2016).
-The thresholding bandit problem considers a slightly different loss function.
-Consider a fixed threshold value $\tau \in \mathbb{R}$ and an epsilon interval $\tau \pm \epsilon$ around the threshold for $\epsilon \geq 0$.
-As mentioned in the introduction, the learner is tasked with classifying arms as having a mean $\mu_i$ larger or smaller than $\tau$.
-As in Locatelli et al.
-(2016), whenever we say that "an arm is over the threshold", we say that the mean of the arm is over the threshold.
-To describe which arms are over the threshold, we also introduce the following set notation: Let $\mathcal{S}_{u}$ be the set of distributions in $\mathbb{A}$ with mean larger than some $u \in \mathbb{R}$: $\mathcal{S}_{u} := \{i \in \mathbb{A}, \mu_i \geq u\}$.
-Consequently, the complement is given by the arms with mean below $u$, $\mathcal{S}^C_{u} := \{i \in \mathbb{A}, \mu_i < u\}$.
-
-The thresholding problem for the learner is now to use a budget of overall $T$ samples (or rounds) to explore the different arms.
-After this exploration phase, the learner returns a set of arms that she believes to be over the threshold.
-When evaluating the classification of the learner, arms with mean inside of the epsilon interval $\tau \pm \epsilon$ will not be considered.
-The learner only has to correctly distinguish the means from the threshold up to the precision given by $\epsilon$.
-Thus, the algorithm is not evaluated against $\mathcal{S}_{\tau}$ and $\mathcal{S}^C_{\tau}$, but needs to distinguish $\mathcal{S}_{\tau+\epsilon}$ from $\mathcal{S}^C_{\tau-\epsilon}$.
-
-The learner's classification is returned as the set $\hat{\mathcal{S}}_{\tau} := \hat{\mathcal{S}}_{\tau}(T) \subset \mathbb{A}$ after $T$ rounds; that is, the set of arms estimated to be over the threshold.
-The classification is evaluated against the loss given as (Locatelli et al., 2016):
-
-$$
-\mathcal{L}(T) = \mathbbm{1}{\big((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \lor (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset)\big)}
-$$
-
-In order to perform well, a learner has to identify all arms that are over the threshold as such, and to not claim arms as being over the threshold if they actually are below the threshold.
-Due to the precision $\epsilon$, the loss is not influenced by arms which are very close to the threshold $\tau$ as measured by $\epsilon$, that is, arms inside of the $\tau \pm \epsilon$ interval.
-If either $\hat{\mathcal{S}}_{\tau}$ contains an arm below $(\tau - \epsilon)$, or $\hat{\mathcal{S}}^C_{\tau}$ contains an arm above $(\tau + \epsilon)$, a loss of $1$ is accrued.
-Else, all arms outside the epsilon interval are classified correctly and the loss is equal to $0$.
-In the case of $\epsilon = 0$, all arms need to be classified correctly to not collect any loss.
-
-Algorithms for this thresholding problem can be compared based on their expected loss.
-Let $\mathbb{E}$ be the expectation with regard to the samples $X_{i,1}, ..., X_{i,T}$ collected by the algorithm.
-The expected loss is then given as
-
-$$
-\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}\big((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \lor(\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset)\big),
-$$
-
-which corresponds to the probability of making at least one wrong classification.
-Both the probability of not identifying an arm that is actually over the threshold, as well as the probability of accepting an arm as over the threshold when it is not, are evaluated.
-The oracle strategy would evaluate all arms correctly with an error probability of $0$ (Locatelli et al., 2016).
-
-At this point, we have introduced the general thresholding bandit problem setting which we will use throughout the thesis.
-The setting can be extended by different assumptions to make certain algorithms or bounds feasible.
-For that reason, Locatelli et al.
-(2016) assume that the distributions $\nu_i, i \in \mathbb{A}$ are $R$-sub-Gaussian.
-Under this assumption, the authors are able to prove a lower bound on the largest probability of error of the best algorithm in the setting we have just introduced, as well as an upper bound on the performance of their APT algorithm which we will introduce in the following chapter.
-As in their paper, we define $R$-sub-Gaussian and assume it in the description of the their algorithm and bounds:
-
-\begin{definition}[$R$-sub-Gaussian distribution] 
-\label{definition:rsubgaussian}
-Let $R > 0$. A distribution $\nu$ is $R$-sub-Gaussian if for all $t \in \mathbb{R}$ we have
-\begin{equation*}
-\mathbb{E}_{X \sim \nu}[\exp(tX - t\mathbb{E}[X])] \leq \exp(R^2t^2/2).
-\end{equation*}
-\end{definition}
-
-As noted by Locatelli et al.
-(2016), this ensures that the mean $\mu_i$ of the distributions $\nu_i$ considered in our problem are finite.
-$R$-sub-Gaussian distributions offer concentration inequalities for the concentration of the empirical mean around the true mean, which makes it possible to deduce the bounds presented by the authors and repeated below.
-The family of $R$-sub-Gaussian distributions encompasses Gaussian distributions of variance $R^2$ for $R \in \mathbb{R}$, as well as all bounded distributions, with the important case of Bernoulli distributions.
-
-Having described the thresholding bandit setting as well as the assumption of $R$-sub-Gaussianity, we can now proceed to describe the *Anytime Parameter-free Thresholding* (APT) algorithm proposed in Locatelli et al.
-(2016) for the thresholding bandit problem.
-
-## The Anytime Parameter-free Thresholding Algorithm \label{sec:TheAPTAlgorithm}
-
-In the following we describe the *Anytime Parameter-free Thresholding* (APT) algorithm proposed in Locatelli et al.
-(2016), which is a simple yet effective algorithm and displays some very favorable characteristics when compared to alternative algorithms.
-
-We fix the threshold $\tau$ and epsilon interval around the threshold given by $\epsilon$ upfront, and supply them as arguments to the algorithm: $(\tau, \epsilon)$.
-Based on the general thresholding problem, we demand that the algorithm draws samples $X_{i,t}$ for $T$ rounds from the distributions $\nu_i, i\in \mathbb{A}$.
-For a given arm $i$ and a given time $t$, we let $T_i(t)$ represent the number of samples drawn from arm $i$ until time $t$ (including).
-Consequently, the empirical mean of arm $i$ at time $t$ is given by $\hat{\mu}_i(t) = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}$ where $X_{i,s}$ is the feedback sampled from distribution $\nu_i$ when the arm is pulled for the $s$-th time.
-In the case of the APT algorithm, the decision $\hat{\mathcal{S}}_{\tau}$ is based on the empirical means $\hat{\mu}_i(T)$ estimated from the samples drawn up to time $T$: $\hat{\mathcal{S}}_{\tau} := \hat{\mathcal{S}}_{\tau}(T) = \{i \in \mathbb{A}, \hat{\mu}_i(T) \geq \tau\}$.
-
-As we see in algorithm \ref{alg:APT}, the APT algorithm initiates by pulling each arm once.
-Then, for each $t > K$, it calculates for every arm the values $T_i(t)$ and $\hat{\mu}_i(t)$.
-Based on the empirical mean, the algorithm computes the estimated gap between the mean and the threshold as $\hat{\Delta}_i(t) = \hat{\Delta}_i^{\tau, \epsilon}(t) = |\mu_i(t) - \tau| + \epsilon$.
-The decision of which arm is sampled next is then based on the value $B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t)$: the algorithm pulls arm $I_{t+1} = \arg \min_{i\leq K} B_i(t+1)$ minimizing this decision quantity.
-After overall $T$ pulls, the algorithm returns the sets described in the general setup, $\hat{\mathcal{S}}_{\tau}$ and $\hat{\mathcal{S}}^C_{\tau}$.
-
-\IncMargin{1em}
-\begin{algorithm}
-\SetKwData{Left}{left}\SetKwData{This}{this}\SetKwData{Up}{up}
-\SetKwFunction{Union}{Union}\SetKwFunction{FindCompress}{FindCompress}
-\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
-\Input{$\tau$, $\epsilon$}
-\Output{$\hat{S}_{\tau} = \{i \in \{1,...,K\}, \hat{\mu}_i(T) \geq \tau\}$}
-\BlankLine
-\emph{Pull each arm once}\;
-\For{$t = K+1$ \KwTo $T$}{
-  \emph{Pull arm $I_t = \arg \min_{i \in A} B_i^{APT}(t) = \arg \min_{i \in A} \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau|+\epsilon)$}\;
-  \emph{Observe reward $X_t \sim \nu_{I_t}$}\;
-}
-\caption{Anytime Parameter-free Thresholding Algorithm (Locatelli et al., 2016)}\label{alg:APT}
-\end{algorithm}
-\DecMargin{1em}
-
-Just like the general index policies mentioned in \autoref{sec:Setup}, we see that the APT algorithm adapts its strategy using an index $B_i(t+1)$ for each arm that is based entirely on the observations observed until time $t$.
-Given the arm with the smallest index is pulled at round $t+1$, we observe that arms that are estimated to be further away from the threshold $\tau$ as measured by the absolute distance to their empirical mean $\hat{\mu}_i$, $\hat{\Delta}_i(t)$, are pulled less often.
-Intuitively, it is easier to classify arms as below or above $\tau$ when their mean is far away from the threshold.
-In contrast to the uniform sampling strategy, APT will gather more evidence for arms which appear to be inherently more difficult to classify.
-Likewise, APT tends to less often pull arms which it already pulled considerably often as measured by $T_i(t)$.
-If arm $i$ has been pulled more often than arm $j$, then we should in general be more confident in its estimated mean and the corresponding distance to the threshold.
-If we are confident in $i$, then it is better to explore other arms by drawing an observation from arm $j$.
-By adapting its sampling strategy in this way during the sequential sampling process, the APT algorithm minimizes the probability of error $\mathbb{E}[\mathcal{L}(T)]$ after $T$ samples have been observed.
-
-The previous paragraph describes how arms close to the threshold are intuitively more difficult to classify.
-In the index employed by the APT algorithm, the distance between an arm and the threshold is measured by the absolute distance $\hat{\Delta}_i(t)$ between the (estimated) mean of the arm and the threshold $\tau$ (and the epsilon interval).
-When the APT algorithm realizes that an arm has a mean close to the threshold, then this arm requires more attention than an arm far away from the threshold; the confidence in the empirical mean has to be larger.
-Or the empirical mean has to be better concentrated around the true mean.
-Otherwise it is easier to make a mistake on this arm.
-To gain this confidence, the arm requires more samples, and thus a larger share of the overall $T$ samples available.
-With this intuition, it makes sense to measure the complexity of a thresholding problem: If we knew upfront how complex a given set of arms is, we would know whether to expect a small or large probability of error given our budget $T$.
-Also, for example in the best arm identification problem, there exist algorithms which take the complexity of a problem as input.
-Based on the complexity they then adapt their sampling strategy.
-See for example the UCB-E algorithm in Audibert et al.
-(2010) for the best arm identification problem, or the KL-LUCB-E algorithm in Kaufmann and Kalyanakrishnan (2013) as extension to the top-$m$ problem.
-
-While the APT algorithm does not require the complexity to be known upfront (which would be problematic as it is not known upfront), it is necessary to define the complexity to deduce the upper bound on its probability of error.
-Similar to the distance measure used in the algorithm's index, we define the gap $\Delta_i^{\tau,\epsilon}$ between arm $i$ and the threshold $\tau \pm \epsilon$ as
-
-$$
-\Delta_i := \Delta_i^{\tau,\epsilon} = |\mu_i - \tau| + \epsilon
-$$
-
-Given this gap, Locatelli et al. (2016) define the complexity $H_{\tau, \epsilon}$ for the thresholding bandit problem naturally as
-
-$$
-H := H_{\tau, \epsilon} = \sum_{i=1}^K \frac{1}{(\Delta_i^{\tau,\epsilon})^2}.
-$$
-
-Note that the complexity of the problem increases in the number of arms $K$ and decreases in the gap $\Delta_i^{\tau,\epsilon}$.
-Consequently, when we require less precision, that is, we increase $\epsilon$, the hardness decreases.
-Furthermore, we see that each arm contributes its individual complexity, $h_i^{\tau,\epsilon} = \frac{1}{(\Delta_i^{\tau,\epsilon})^2}$ linearly into the problem.
-Thus, if the complexity $H$ is a good measure of the actual problem complexity, and we knew upfront which arm has which mean, we could allocate the "optimal" share of the budget, $T \cdot h_i /H$ to arm $i$.
-However, since we do not know neither $\mu_i$ nor $H$ upfront, the best we can do is to adapt our allocation of samples more and more towards this optimum as we observe samples.
-
-At this point, one can question whether the measure of complexity $H$ proposed in Locatelli et al.
-(2016) is a good measure of the "true" problem complexity.
-In the following \autoref{sec:UpperBoundLocatelli}, we will show the upper bound on the probability of error for the APT algorithm and see how the complexity $H$ arises naturally for the APT algorithm.
-In \autoref{sec:LowerBoundLocatelli} we then show the lower bound presented in Locatelli et al.
-(2016) and that the APT algorithm is optimal in that it matches the lower bound.
-We discuss the results and the APT algorithm further in \autoref{sec:DiscussionLocatelli}.
-
-## Upper Bound for the APT Algorithm \label{sec:UpperBoundLocatelli}
-
-In this chapter we present the upper bound on the probability of error that the APT algorithm incurs, as proven in Locatelli et al.
-(2016).
-The upper bound is on the probability of error that the algorithm has after $T$ rounds of sampling for a problem with arms that are assumed to be $R$-sub-Gaussian.
-The bound depends also on the complexity of the problem, and we show in the proof that given the index of the APT algorithm as defined in \autoref{sec:TheAPTAlgorithm}, the complexity $H$ is an appropriate measure.
-
-We now state the theorem as in Locatelli et al. (2016) and present a proof.
-
-\begin{theorem}[Theorem 2, Locatelli et al., 2016] \label{theorem:LocatelliTheorem4}
-Let $K \geq 0$, $T \geq 2K$, and consider a problem $\mathcal{B}$.
-Assume that all arms $\nu_i$ of the problem are R-sub-Gaussian with means $\mu_i$.
-Let $\tau \in \mathbb{R}, \epsilon \geq 0$.
-Algorithm APT's expected loss is upper bounded on this problem as
-\begin{equation*} \mathbb{E}(\mathcal{L}(T)) \leq \exp
-\Big(-\frac{1}{64R^2}\frac{T}{H} + 2 \log((\log(T) + 1)K)\Big) \end{equation*}
-
-where we remind that $H = \sum_i (|\mu_i - \tau | + \epsilon)^{-2}$ and where
-$\mathbb{E}$ is the expectation according to the samples of the problem.
-\end{theorem}
-
-### Proof of Theorem \ref{theorem:LocatelliTheorem4} \label{sec:UpperBoundProof}
-
-In order to upper bound the expected loss of the APT algorithm, we want to define an event on which the algorithm correctly seperates arms from the threshold, that is, a separation condition holds on this event.
-We then want to show that this *favorable* event does indeed hold with large probability.
-Consequently, APT's probability of error will correspond to the probability that the favorable event does not hold, as this leads to a failure of the seperation condition, and consequently to an incorrect classification of at least one arm by the algorithm.
-We start by defining the separation condition.
-
-### Separation Condition
-
-As noted in Zhong et al. (2017), a simple requirement to correctly classify arms at the final round is the following. For every arm $i \in \{1, ..., K\}$ after the final round $T$, require
-$$
-\hat{\mu}_{i}(T) \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
-$$
-or
-$$
-\hat{\mu}_{i}(T) \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
-$$
-Or simply in terms of the gap between the arm and the threshold as used in the index by the APT algorithm:
-$$
-| \hat{\mu}_{i}(T) - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
-$$
-
-Intuitively, this condition makes sense as it ensures that the current mean estimate is closer to the true mean than to the threshold.
-Consequently, there is no arrangement possible in which the arm is classified wrong while the separation condition holds.
-Assuming $\mu_i < \tau$ and $\epsilon = 0$, an incorrect classification would require $\mu_i < \tau \leq \hat{\mu_i}$.
-But then  $| \hat{\mu}_{i}(T) - \mu_i | \geq |\mu_i - \tau|$, which violates the separation condition.
-
-Thus, we need to show that this condition holds for every arm $i \in \{1,...,K\}$ with large probability after the final round $T$.
-In different words, we need to derive an upper bound on the probability with which this condition does not hold.
-
-### The Favorable Event
-
-The separation condition describes what event needs to hold in order for the APT algorithm to make a correct classification: The smaller the deviation of the empirical mean from the population mean, the more difficult it is for the classification to be wrong.
-Moreover, if the mean and empirical mean are identical, then the classification is correct independent of the threshold.
-Also, the closer the mean to the threshold, the better the estimate has to be for a correct classification to be likely.
-To bound the absolute deviation of the empirical mean from the true mean, we define the favorable event $\xi$ as
-
-$$
-\xi = \Big\{\forall i \in \mathbb{A}, \forall s \in \{1,...,T\} : |\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}} \Big\}.
-$$
-
-The probability that this favorable event occurs should be large, or equivalently, the probability that the deviation is small should be large.
-Then it follows that the separation condition holds with large probability.
-
-We know that $X_i$ are $R$-sub-Gaussian by assumption. That is, we have
-
-$$
-\mathbb{E}[\exp (tX_{i,s}-t\mathbb{E}[X_{i,s}])] = \mathbb{E}[\exp (t(X_{i,s}-\mathbb{E}[X_{i,s}]))] \leq \exp (R^2t^2/2)
-$$
-
-where the RHS is the moment-generating function of the random variable $X_{i,s}-\mathbb{E}[X_{i,s}]$.
-While Höffding's Lemma and Höffding's Inequality are commonly applied to bounded random variables $Z$ with $\mathbb{P}(a\leq Z \leq b) = 1$ and $\mathbb{E}[Z] = 0$, we see that $Z$ are $R$-sub-Gaussian with $R^2 = \frac{(a-b)^2}{4}$.
-Using this last equality, we can easily apply Höffding's Inequality to our case.
-
-\begin{lemma}[Höffding's Inequality (Kloft Lecture Notes)] \label{lemma:HoeffdingsInequality}
-Let $X_1, ..., X_s$ be independent, identically distributed random variables with mean $\mathbb{E}[X_t] = \mu$ and $\mathbb{P}(a_t \leq X_t - \mathbb{E}[X] \leq b_t) = 1$.
-Denote their empirical mean by $\bar{X}_s=\frac{1}{s}\sum_{t=1}^{s}X_t$.
-Then, for any $\gamma > 0$, we have the following concentration inequality:
-
-\begin{equation*}
-\mathbb{P}(|\bar{X}_s - \mu| \geq \gamma) \leq 2\exp (-2s^2\gamma^2/\sum_{t=1}^s(b_t - a_t)^2).
-\end{equation*}
-\end{lemma}
-
-If we replace $\sum_{t=1}^s(b_t - a_t)^2$ by $4sR^2$, we have the concentration inequality for our $R$-sub-Gaussian random variables:
-
-$$
-\mathbb{P}(|\bar{X}_s - \mu| \geq \gamma) \leq 2\exp (-\frac{s\gamma^2}{2R^2}).
-$$
-
-Writing $\gamma = \sqrt{\frac{T\delta^2}{Hs}}$, we get for the favorable event $\xi_i = \{|\bar{X}_s - \mu| \leq \sqrt{\frac{T\delta^2}{Hs}}\}$ of an individual arm $i$, for each $i \in \mathbb{A}$ and each $s \in \{1, ..., T\}$:
-
-$$
-\mathbb{P}(\xi_i) = \mathbb{P}\Big(|\bar{X}_{i,s} - \mu_i| \leq \sqrt{\frac{T\delta^2}{Hs}}\Big) \geq 1 - 2\exp (-\frac{T\delta^2}{2R^2H}),
-$$
-where $T$ is again the total budget of samples, and $H$ the complexity. Now let
-
-$$
-\tilde{\xi} = \Big\{\forall i \in \mathbb{A}: |\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}} \Big\}.
-$$
-
-To derive the probability of event $\tilde{\xi}$, we apply a union bound on $\mathbb{P}(\cup_{i=1}^K \xi_i^C)$:
-
-\begin{align*}
-\mathbb{P}(\tilde{\xi}) & = 1-\mathbb{P}(\xi^C) \\
-& = 1-\mathbb{P}(\cup_{i=1}^K \xi_i^C) \\
-& \geq 1 - \sum_{i=1}^K \mathbb{P}(\xi_i^C) \\
-& \geq 1 - 2K\exp (-\frac{T\delta^2}{2R^2H})
-\end{align*}
-
-We could use the same union bound a second time to bound over all $s \in \{1, ..., T\}$ and derive for the favorable event $\xi$:
-
-$$
-\mathbb{P}(\xi) \geq 1 - 2TK \exp(-\frac{T\delta^2}{2R^2H})
-$$
-
-Locatelli et al. (2016) use instead of Höffding's inequality a Sub-Gaussian martingale inequality including a peeling argument in order to derive a better bound of
-
-$$
-\mathbb{P}(\xi) \geq 1 - 2(\log(T) +1)K \exp(-\frac{T\delta^2}{2R^2H})
-$$
-
-This bound is non-trivial for much smaller values of $T$, and we will use it in the following.
-
-### Need to Bound $T_i$
-
-We now have that with large probability the favorable event holds. On the favorable event, we have for every arm $i$:
-
-$$
-| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}
-$$
-
-The deviation of arm $i$ at time $t$ depends on how large $H$, $T$, and $T_i(t)$ are.
-While $t$, $H$, $T$ are deterministic, the number of times arm $i$ has been pulled at round $t$, $T_i(t)$, is a random variable.
-In order to know how large the probability of the favorable event is (and thus the error probability), we need to know the value of $T_i(t)$, or at least bound a range of potential values.
-Put differently: To ensure a deviation smaller than $\sqrt{\frac{T\delta^2}{HT_i(t)}}$ for arm $i$, we need to ensure that arm $i$ has been pulled at least $T_i(t)$ times.
-As usual in multi-armed bandits, and different from uniform sampling, the number of pulls is a random variable that also depends on how often other arms are pulled.
-In general, we do not want each arm to be pulled an equal amount, but each arm should be pulled some times, and not too many times.
-
-Thus, in order to check that the deviation of arm $i$ really is small enough for the separation condition to hold on the favorable event, we need to bound the number of pulls of every arm from below.
-
-### Characteristics of a Frequently Pulled Arm (Lower Bound on $T_k(T)$)
-
-Given that we do not follow a uniform sampling strategy, we know that at time $T$, some arms will have been pulled more frequently than others.
-In particular, some arms will have been pulled more than $T/K$ times.
-How often an arm is pulled can be related to the individual arm's contribution to the overall complexity measure.
-Let $h_i$ be a measure of arm $i$'s individual problem complexity and write for the overall problem complexity $H = \sum_{i = 1}^{K} h_i$.
-Then arm $i$ contributes a share of $h_i/H$ to the overall problem complexity.
-We can now show that there exists an arm that has been pulled at least as often as the share of its complexity contribution.
-
-Given the initialization of the APT algorithm, every arm is pulled once initially.
-Consequently, there is a budget of $T-K$ rounds left after the initialization.
-As shown in Locatelli et al.
-(2016), there exists an arm $k$ that has been pulled after the initialization ($\geq 2$ pulls) and for which at the final round $T$ it holds: $T_k(T) - 1 \geq \frac{(T-K)h_k}{H}$.
-This can be shown by a contradiction.
-Assume that the opposite holds, that is
-
-$$
-\forall i \in \{1,...,K\}: T_i(T) - 1 < \frac{(T-K)h_i}{H}
-$$
-
-Consequently, at time $T$, we would have pulled across all arms $\sum_{i=1}^KT_i(T)-1$ times. If the previous assumption holds, we would not have used the entire budget:
-
-$$
-\sum_{i=1}^K T_i(T)-1 < \sum_{i=1}^K \frac{(T-K)h_i}{H} = (T-K)\sum_{i=1}^K \frac{h_i}{H} = T-K
-$$
-
-This is a contradiction, since as an requirement to the algorithm we have that $\sum_{i=1}^K T_i(T)-1 = (T-K)$, that is, we use the entire budget of samples.
-
-Furthermore, we have assumed $T>2K$ in the statement of Theorem \ref{theorem:LocatelliTheorem4}. Plugging this in gives 
-$$
-T_k(T) - 1 \geq \frac{(T-K)h_k}{H} \geq \frac{(T-1/2T)h_k}{H} = \frac{Th_k}{2H}
-$$
-
-Now we know how often the arm has been pulled at the very end.
-That does not mean that $k$ has been pulled at time $T$.
-Thus we consider the time $t \leq T$ at which arm $k$ is pulled for the last time.
-We get
-
-$$
-T_k(t) \geq T_k(T) - 1 \geq \frac{Th_k}{2H}.
-$$
-
-This gives us a lower bound on how often arms are pulled that are pulled frequently relative to their contribution to the problem complexity.
-Now we need a lower bound on $T_i(T)$ for every other arm $i$.
-
-### Lower Bound on $T_i(T)$
-
-Consider again as before the round $t$ at which arm $k$ is pulled for the very last time.
-Since the APT algorithm minimizes at every round $s \geq K+1$ the index $B_j(s)$, and pulls the arm with the smallest index, we know that arm $k$ must have had the smallest index at round $t$.
-We have:
-
-$$
-B_k(t) \leq B_i(t) \Leftrightarrow \sqrt{T_k(t)}\hat{\Delta}_k(t) \leq \sqrt{T_i(t)} \hat{\Delta}_i(t)
-$$
-
-One can already expect that this can be used to derive a lower bound on $T_i(t)$ on the RHS, and this is exactly what we do.
-On the LHS, we plug in the lower bound for $T_k(t)$ derived before.
-Additionally bounding $\Delta_k(t)$ from below, and $\hat{\Delta}_i(t)$ from above using the favorable event will give the desired lower bound.
-
-Thus assume we are on the favorable event $\xi$ with large probability. we consequently have
-
-$$
-| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}.
-$$
-
-As shown in Locatelli et al. (2016), one can use the reverse triangle inequality to get:
-
-\begin{align*}
-|\hat{\mu}_i(t) - \mu_i| & = |(\hat{\mu}_i(t) - \tau) - (\mu_i - \tau)| \\
-& \geq || \hat{\mu}_i(t) - \tau | - |\mu_i - \tau|| \\
-& \geq |(|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i - \tau| + \epsilon)| \\
-& \geq |\hat{\Delta}_i(t) - \Delta_i|
-\end{align*}
-
-If we combine this with the favorable event, we get
-
-$$
-\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}} \leq \hat{\Delta}_k(t) \leq \Delta_k + \sqrt{\frac{T\delta^2}{HT_k(t)}}
-$$
-
-and similar for $\hat{\Delta}_i$. We can now lower bound the LHS of the indexes as
-
-\begin{align*}
-B_k(t) & \geq \Big(\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}}\Big) \sqrt{T_k(t)} \\
-& \geq \Big(\Delta_k - \sqrt{\frac{2}{h_k}}\delta \Big)
-\end{align*}
-
-At this point, it is useful to have a well chosen complexity measure. If we set $h_i = \frac{1}{\Delta_i^2}$ as in Locatelli et al. (2016), we get
-
-$$
-\Big(\Delta_k - \sqrt{2}\delta \Delta \Big) \sqrt{\frac{T}{2H\Delta_k^2}} \leq B_k(t)
-$$
-
-which can be now be reduced to a form that is not specific to $k$:
-
-$$
-\Big( \frac{1}{\sqrt{2}} - \delta \Big) \sqrt{\frac{T}{H}} \leq B_k(t).
-$$
-
-Now we need to remove $\hat{\Delta}_i$ in order to bound $T_i(t)$. Thus, we bound the RHS again using the favorable event much as we did for the LHS:
-
-$$
-B_i(t) = \hat{\Delta}_i \sqrt{T_i(t)} \leq \Big(\Delta_i + \sqrt{\frac{T\delta^2}{HT_i(t)}}\Big) \sqrt{T_i(t)} \leq \Delta_i \sqrt{T_i(t)} + \delta \sqrt{\frac{T}{H}}
-$$
-
-As in Locatelli et al. (2016) we use the fact that by definition $\Delta$ and $\hat{\Delta}$ are positive in order to square both sides and write
-
-$$
-(1 - 2\sqrt{2}\delta)^2 \frac{T}{2H\Delta^2_i} \leq T_i(t) \leq T_i(T)
-$$
-
-We thus have derived a lower bound on the amount of pulls for any arm.
-That means that we can show that no arm is pulled an insufficient amount of times with large probability, and that consequently the favorable event hold and the estimated mean is sufficienctly separated from the threshold.
-
-### Check Separation Condition \label{sec:CheckSeparationCondition}
-
-As the last step, we need to check whether the lower bound on the pulls of any arm suffices to ensure that the separation condition holds on the favorable event.
-That means, given $T_i(T) \geq (1-2\sqrt{2}\delta)^2 \frac{T}{2H\Delta_i^2}$, do we have $|\hat{\mu}_i(T) - \mu | \leq \frac{\Delta}{2}$ on the favorable event $\xi = \Big\{|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}}\Big\}$?
-To check, we plug the lower bound into the favorable event and get
-
-$$
-|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}} \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}
-$$
-Using $\delta = (4\sqrt{2})^-1$ as in Locatelli et al. (2016), we have that the separation condition holds exactly:
-
-$$
-|\hat{\mu}_i - \mu | \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta} \leq \frac{1}{2}\Delta_i.
-$$
-
-### Upper Bound on Error Probability
-
-We have seen that on the favorable event $\xi$, which holds with large probability $\mathbb{P}(\xi)$, the separation condition holds as all arms have been pulled a sufficient number of times, such that their estimated mean is close to the true mean.
-All arms are classified correctly, and the algorithm does not suffer a loss.
-On the other hand, we make an error whenever the favorable event does not hold after all; that is, the deviation bound for the mean does not hold.
-At least one arm is misclassified and the arm suffers a loss.
-This occurs with probability $1-\mathbb{P}(\xi)$.
-Consequently, the expected loss is upper bounded by
-
-$$
-\mathbb{E}[\mathcal{L}(T)] = 1 - \mathbb{P}(\xi) \leq 2(\log(T)+1)K \exp(-\frac{1}{64R^2}\frac{T}{H}).
-$$
-
-We now present the lower bound given in Locatelli et al.
-(2016) for the thresholding bandit problem.
-In order to derive the bound, a problem is specified to show that the error of the lower bound is attained even in this specific problem.
-In particular, for a set of problems with Gaussian distributions of variance $1$, the largest probability of error on these problems that the best algorithm exhibits is still at least as large as the lower bound.
-
-## Lower Bound for the Thresholding Bandit Problem \label{sec:LowerBoundLocatelli}
-
-Locatelli et al.
-(2016) also provide a general lower bound on the probability of error in the thresholding bandit problem.
-The bound is derived for a specified set of problems through a change in distribution as common in the multi-armed bandit literature (compare for example Audibert et al., 2010, or Kaufmann et al., 2016).
-For any of these problems, the largest probability of error that the best algorithm incurs is still lower bounded by the bound given below.
-
-\begin{theorem}[Theorem 1, Locatelli et al., 2016] 
-\label{theorem:Locatelli2016Theorem1}
-For any sequence of gaps $(d_k)_k$, define a finite set of problems with Gaussian distributions with means corresponding to the gaps, and with variance 1.
-Lower bound the largest probability of error among these problems for the best possible algorithm as follows.
-Let $K,T \geq 0$.
-Let for any $i \leq K$, $d_i \geq 0$.
-Let $\tau \in \mathbb{R}, \epsilon > 0$.
-
-For $0 \leq i \leq K$, we write $\mathcal{B}^i$ for the problem where the distribution of arm $j \in \{1, \dots, K\}$ is $\mathcal{N}(\tau+d_i+\epsilon, 1)$ if $i \neq j$ and $\mathcal{N}(\tau-d_i-\epsilon, 1)$ otherwise.
-For all these problems, $H := H_{\tau, \epsilon} = \sum_i (d_i+2\epsilon)^{-2}$ is the same by definition.
-
-It holds that for any bandit algorithm,
-
-\begin{equation*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) \geq \exp(-3T/H-4 \log(12(\log(T)+1)K)),
-\end{equation*}
-
-where $\mathbb{E}_{\mathcal{B}^i}$ is the expectation according to the samples of problem $\mathcal{B}^i$.
-\end{theorem}
-
-A proof of the lower bound is given in the Appendix in \autoref{sec:AppendixAPTLB}.
-
-If we write the lower bound as $LB = 12(\log(T)+1)K)\exp(-3T/H)\exp(-4) = C_{LB}(\log(T)+1)K\exp(-T/H)$ and the upper bound as
-$UB = (\log(T)+1)K \exp(2) \exp(-\frac{1}{64R^2}\frac{T}{H}) = C_{UB}(\log(T)+1)K\exp(-T/H)$, we see that $LB$ and $UB$ match up to multiplicative constants and the $(\log(T)+1)K$ term which is negligiable in comparison with the exponent for large $T$ as shown in Locatelli et al.
-(2016).
-This makes the APT algorithm order optimal.
-
-## Discussion \label{sec:DiscussionLocatelli}
-
-One of the APT algorithm's main features is its simplicity.
-The sampling rule is straightforward, and, as highlighted in Locatelli et al.
-(2016), it does not require any knowledge about the type of sub-Gaussianity $R$, or the complexity $H$ upfront.
-This makes the algorithm immediately applicable in practice while it still enjoys its upper bound on the expected regret.
-This is in particular worth highlighting when comparing APT to algorithms used in the best arm identification or top-$m$ setting.
-As alluded to in \autoref{sec:TheAPTAlgorithm}, many algorithms that fix the sampling budget upfront (i.e., fixed budget algorithms as UCB-E or KL-LUCB-E) require knowledge about the complexity upfront (Audibert et al., 2010; Kaufmann and Kalyanakrishnan, 2013).
-The problem however being that to know the complexity, the experimenter has to know all means up to a permutation of the arms.
-This, of course, is not given in practice.
-Thus alternative algorithms try to estimate the complexity online which can be difficult as especially in the beginning plug-in estimates based on the estimated means may lead to wrong estimates of the complexity, which in turn leads to poor budget allocation based on mistaken beliefs (compare Garivier and Kaufmann, 2016).
-On the other hand, the sequential sampling strategy has to rely on some estimate.
-While the APT algorithm does not explicitly estimate the complexity, the gaps that serve as index are essentially the same.
-Empirically, we see in \autoref{chap:Experiments} that the problem described by Garivier and Kaufmann (2016) does also occur for the APT strategy.
-Faced not with sub-Gaussian but with more heavy-tailed distributions, this sensitivity is likely to increase.
-
-Furthermore, as mentioned in Locatelli et al.
-(2016), the assumptions for the bounds no longer hold as arms become less sub-Gaussian; the complexity $H$ and the term $\hat{\Delta}_i(t)$ in the algorithm's index are both motivated by sub-Gaussian distributions.
-The more a problem deviates from those, the less appropriate the quantities become.
-In particular, the empirical mean will be less (or not at all) concentrated around the true mean and more impacted by outliers which are more likely under non sub-Gaussian distributions.
-Locatelli et al.
-(2016) thus refers to Bubeck et al.
-(2013a) which consider solutions for multi-armed bandits that are based on heavy-tail distributions.
-By using more robust estimators of the mean, one could equip the APT algorithm to deal with such distributions.
-
-Both Mukherjee et al.
-(2017) as well as Zhong et al.
-(2017) use estimates of the variance of the arms for their algorithms for the thresholding bandit problem and try to thereby improve upon the performance of the APT algorithm.
-While their simulations show promising results, their bounds rely on the assumption of bounded reward distributions.
-Thus their algorithms are not necessarily able to improve upon the assumption of sub-Gaussian distributions made by Locatelli et al.
-(2016).
-We will continue to discuss their results in \autoref{sec:VarianceBasedAlgorithms}.
-
-Yet another idea, again mentioned in Locatelli et al.
-(2016) is to show bounds based on the Kullback-Leibler divergence of the specific distribution directly.
-While the approximation through the Gaussian Kullback-Leibler divergence in the lower bound proof is convenient and leads to the simple APT algorithm, it might not stay appropriate for distributions whose Kullback-Leibler divergence tends to differ from the Gaussian.
-This, for example, is the case for Bernoulli distributions at very small parameters $\mu$.
-We have for the Kullback-Leibler divergence of two Gaussian distributions $\nu_i$ and $\nu_j$ of mean $\mu_i$ and $\mu_j$ with equal variance:
-
-$$
-\KL_{\mathcal{N}}(\nu_i || \nu_j) = 2(\mu_i - \mu_j)^2.
-$$
-
-Writing $\mu_j = \tau$ and $\epsilon = 0$, we see that the APT algorithm essentially measures the KL-divergence between two Normal distributions.
-For two Bernoulli distributions $\nu_i$ and $\nu_j$, parameterized by $\mu_i$ and $\mu_j=\tau$, we write
-
-$$
-\KL_{\text{Ber}}(\nu_i||\nu_j) = \mu_i \log(\frac{\mu_i}{\tau}) + (1-\mu_i) \log(\frac{1-\mu_i}{1-\tau})
-$$
-
-In the case of $\tau = 0.5$, the latter KL-divergence is symmetric in its first argument, and thus can be relatively well approximated by Pinsker's inequality:
-
-$$
-\KL_{\text{Ber}}(\nu_i||\nu_j) \geq 2(\mu_i - \tau)^2.
-$$
-
-This is equal to the Gaussian KL-divergence described before.
-The approximation, however, suffers heavily for very small values of $\mu_i$ and $\tau$.
-In particular, the Bernoulli KL-divergence becomes asymmetric in its first argument when $\tau \neq 0.5$.
-Thus, in contrast to the complexity measure $H$ based on the Gaussian KL-divergence, a complexity measure based on the Bernoulli KL-divergence would evaluate two arms as differently difficult if their absolute distance to the threshold is the same, but they lie on different sides of the threshold.
-
-Thus similarly to how UCB algorithms in the cumulative regret setting have been extended to KL-UCB algorithms (Cappé et al., 2013), the APT algorithm offers room for improvement, too.
-As a more explicit example of such adaptation, consider the case of top-$m$ identification described in Kaufmann et al.
-(2016).
-The authors develop a lower bound based on KL-divergence, and note that "This information-theoretic lower bound permits to interpret the quantity $H(\nu)$ [...] as a subgaussian approximation".
-Given that Bernoulli distributions with very small or very large parameter values arise naturally in many applications, an improvement in this regard would be valuable.
-
-In what follows, we first examine in \autoref{chap:KullbackLeiblerPureExploration} how information theoretic quantities are employed in the best arm identification and top-$m$ problem as detailed in Kaufmann and Garivier (2016) and Kaufmann et al.
-(2016).
-Before introducing a new algorithm for the thresholding bandit problem based on Kullback-Leibler divergences in \autoref{sec:LikelihoodRatioForExponentialFamily}, we first describe the variance-based approaches in \autoref{sec:VarianceBasedAlgorithms}.
-
-```{r KLApproximationComparison, echo = FALSE, message = FALSE, out.width = '80%', fig.align = "center", fig.cap= "The approximation of the Bernoulli KL-divergence by the Gaussian KL-divergence works well if the second argument is equal to 0.5.
-Else we observe poor approximation in both value and symmetry.
-This becomes more obvious as the arguments move away from 0.5."}
-library(dplyr)
-library(tidyr)
-library(ggplot2)
-KL_ber <- function(p,q) p*log(p/q) + (1-p)*log((1-p)/(1-q))
-KL_gauss <- function(p,q) 2*(p-q)^2
-
-kldf <- data.frame(mu = rep(seq(0.00001, 0.99999, 
-                                length.out = 10000), 2),
-                   tau = c(rep(0.5, 10000), rep(0.05, 10000)))
-
-kldf_long <- kldf %>% mutate(Gaussian = KL_gauss(mu, tau),
-                             Bernoulli = KL_ber(mu, tau)) %>%
-  gather(key = KL_Type, value = KL, -mu, -tau) %>%
-  mutate(tau = as.character(tau))
-
-kldf2 <- data.frame(mu = rep(seq(0.00001, 0.09999, 
-                                length.out = 10000), 1),
-                   tau = c(rep(0.05, 10000)))
-
-kldf2_long <- kldf2 %>% mutate(Gaussian = KL_gauss(mu, tau),
-                              Bernoulli = KL_ber(mu, tau)) %>%
-  gather(key = KL_Type, value = KL, -mu, -tau) %>%
-  mutate(tau = as.character(tau))
-
-kldf_total <- cbind.data.frame(level = c(rep("Global", 40000),
-                                         rep("Local", 20000)),
-                               rbind.data.frame(kldf_long, kldf2_long))
-
-ggplot(kldf_total, aes(x = mu, y = KL, 
-                      group = interaction(KL_Type, tau))) +
-  facet_grid(level~., scales = "free") +
-  geom_line(aes(color = tau, linetype = KL_Type)) +
-  labs(x = "First argument of KL-divergence",
-       y = "KL-divergence"#,
-       #title = "Comparison of Bernoulli KL-divergence and Gaussian Approximation"
-       )  +
-  theme_bw() +
-  #theme(legend.position = "bottom") +
-  scale_color_discrete(name = "Second argument \nof KL-divergence") +
-  scale_linetype_discrete(name = "Type of \nKL-divergence") +
-  guides(color = guide_legend(title.position = "top"),
-         linetype = guide_legend(title.position = "top"))
-```
-
-\newpage
-
-# Information Theoretic Approaches to Pure Exploration Bandits \label{chap:KullbackLeiblerPureExploration}
-
-The previous chapter introduces the thresholding bandit problem as described in Locatelli et al.
-(2016), and the APT strategy as a first algorithm that is simple, yet order-optimal for large budgets.
-However, we end with the conclusion that a KL-divergence based measure of the distance between the distributions and the threshold might be more useful than the simple gap $\Delta^2_i = (\mu_i - \tau_i)^2$ employed so far.
-Indeed, citing Kaufmann et al.
-(2016), we note that the complexity $H$ -- and thus the gaps -- used so far can be considered a sub-Gaussian approximation of a better complexity measure based on information theoretic measures like the Kullback-Leibler divergence.
-
-In order to give more intuition to why that is the case, and in which ways information theoretic measures can be introduced to measure the complexity of bandit problems, we now turn to Kaufmann et al.
-(2016) and Garivier and Kaufmann (2016).
-The latter describes a strategy based on Kullback-Leibler divergences for the best-arm identification problem, while the first derives complexity measures based on the divergence.
-Their work offers methods that can inform our goal of extending the thresholding bandit problem.
-In what follows, we adopt the notation of Kaufmann et al.
-(2016) to ease a comparison with their arguments.
-
-## Information Theoretic Complexity Measures in Top-$m$ Problems \label{sec:KaufmannEtAl2016}
-
-Instead of the thresholding bandit problem, Kaufmann et al.
-(2016) consider the problem of identifying the best $m$ out of $K$ arms, that is, the top-$m$ problem.
-They describe their bandit model $\nu = (\nu_1,...,\nu_K)$ by $K$ arms characterized by probability distributions $\nu_i$, $i \in \mathbb{A} = \{1,...,K\}$, with mean $\mu_i$.
-A learner picks at any time step $t=1,2,...,$ an arm $I_t \in \{1,...,K\}$ for which she observes the independent reward $X_{t} \sim \nu_{I_t}$.
-The learner aims to find the $m$ out of $K$ arms with the largest expected reward.
-This set of arm indexes is denoted by $\mathcal{S}_m^*$.
-Kaufmann et al.
-write the means $(\mu_{1}, ..., \mu_{K})$ sorted in decreasing order as the K-tuple $(\mu_{[1]}, ..., \mu_{[K]})$.
-Based on this, they require that $\mu_{[m]} > \mu_{[m+1]}$ such that the solution $\mathcal{S}_m^*$ is unique.
-The class of bandit problems $\nu$ for which the latter condition holds is called $\mathcal{M}_m$ by Kaufmann et al.
-At the end of the sampling procedure, after $T$ samples, the learner is required to return a classification $\hat{\mathcal{S}}_m$.
-This classification is then evaluated by the loss function $\mathcal{L}(T) = \mathbb{I}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m)$.
-This binary loss is similar to the loss in the thresholding bandit.
-We can now define a strategy of the learner as $\mathcal{S} = ((I_t), T, \hat{\mathcal{S}}_m)$: The strategy defines how an arm is chosen, how many samples are observed, and how the arms are eventually classified.
-
-When introducing the thresholding bandit setting, we did not mention the fact that there exists an alternative setting in which the budget $T$ is not fixed upfront.
-This setting is called *fixed confidence*, while the case we considered so far is called *fixed budget*.
-In the fixed budget setting, we run algorithms for $T$ samples and then compare them based on their expected loss, $\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m) =: p_t(\nu)$ as we have seen in $\autoref{sec:Setup}$.
-Alternatively, consider a $\delta$-PAC strategy $\mathcal{S}(\delta)$for which it holds for every problem $\nu \in \mathcal{M}_m$ that the classification holds at least with confidence level $1-\delta$, that is, $\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta$.
-The strategy has to achieve this level of confidence in its prediction before it is allowed to stop sampling.
-This is the fixed confidence case, in which the budget $T=T_{\delta}$ is no longer fixed upfront, but becomes a random variable.
-Algorithms are then compared by their expected number of draws $\mathbb{E}_{\nu}[T_{\delta}]$ and we prefer those which achieve the confidence level $1-\delta$ with a smaller expected budget.
-
-In the fixed confidence setting, a family of strategies $S = (\mathcal{S}(\delta))_{\delta \in (0,1)}$ is called PAC if for every $\delta$, $\mathcal{S}(\delta)$ is $\delta$-PAC.
-On the other hand, in the fixed budget setting, a family of strategies $S = (\mathcal{S}(t))_{t \in \mathbb{N}}$ is called consistent if $p_t(\nu) \rightarrow 0$ as $t \rightarrow \infty$ for every problem $\nu \in \mathcal{M}_m$.
-
-Given this setup, we can now follow the arguments of Kaufmann et al.
-(2016) to derive complexity measures for the top-$m$ problem.
-As alluded to earlier, these complexity measures will rely on the KL-divergence in contrast to the complexity $H$ used by Locatelli et al.
-(2016).
-When discussing $H$, its motivation is that it represents the difficulty of the problem by measuring the distance between arms and the threshold.
-Instead, Kaufmann et al.
-approach complexity by how many samples (what error probability) one will need in the fixed confidence (fixed budget) setting.
-In order to arrive at their new measure of complexity, it makes sense to first follow their arguments to a general lower bound on the sample complexity $\mathbb{E}_{\nu}[T]$ which is given in their Theorem 4.
-Here, $\mathcal{P}$ refers to a set of probability measures for which Kaufmann et al.
-(2016) assume certain continuity conditions in their Assumption 3, and $\nu_i \in \mathcal{P}$.
-In the following, $d(x,1-x) = x\log(\frac{x}{1-x}) + (1-x) \log(\frac{1-x}{x})$ is the binary KL-divergence.
-
-\begin{theorem}[Theorem 4, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem4}
-Let $\nu \in \mathcal{M}_m$, where $\mathcal{M}_m$ is the set of uniquely identifiable bandit models described above.
-Assume that $\mathcal{P}$ satisfies the continuity conditions in Assumption 3.
-Any $\delta$-PAC algorithm on $\mathcal{M}_m$ satisfies, for $\delta \leq 0.15$:
-
-\begin{equation*}
-\mathbb{E}_{\nu}[\tau] \geq \Big[ \sum_{a \in \mathcal{S}^*_m} \frac{1}{\KL(\nu_a || \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}^*_m} \frac{1}{\KL(\nu_a || \nu_{[m]})} \Big] \der(1-\delta, \delta),
-\end{equation*}
-\end{theorem}
-
-To prove this statement for a given $\delta$-PAC strategy $\mathcal{S}$, we assume certain continuity conditions (compare Kaufmann et al.
-(2016)) under which there exists for every arm $i \in \{1, \dots, K\}$ an alternative model $\nu' = (\nu_1, \dots, \nu_{i-1}, \nu_i', \nu_{i+1}, \dots, \nu_K)$.
-In this alternative model, in accordance with the continuity conditions, only arm $i$ is modified.
-After the modification, the arm $\nu_{m+1}$ is now closer to $\nu_i$ as measured by the Kullback-Leibler divergence than $\nu_i'$ is to $\nu_i$, if $\mu_i > \mu_{m+1}$ (consequently, $\mu_i' < \mu_{m+1}$).
-On the other hand, if $\mu_a < \mu_{m}$, then $\nu_a'$ will be moved away from $\nu_i$ just enough so that $\nu_i$ is closer to $\nu_m$ than to $\nu_i'$ (consequently, $\mu_i' > \mu_m$).
-These changes in distribution make the original set of optimal arms, $\{1,\dots,m\}$, no longer optimal under the alternative model $\nu'$.
-To compare this to the thresholding bandit problem, assume that arms $\nu_{m}$ and $\nu_{m+1}$ indirectly define a threshold $\tau \in (\mu_{m+1},\mu_m)$.
-Then, by creating an alternative problem as described here, we flip arm $i$ around the implied threshold $\tau$ (compare the lower bound proof in \autoref{sec:AppendixAPTLB}).
-
-Given the strategy returns $\hat{S}_m$, we know that for the event $\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})$ (which is element of the $\sigma$-Algebra $\mathcal{F}_{T}$ induced by the stopping time $T$), that $\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta$ and $\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta$ (because fixed confidence $\delta$!).
-To give the lower bound on the expected number of samples, $\mathbb{E}_{\nu}[\tau]$, we employ the general Lemma given by the authors for such changes in distribution in bandit models.
-
-\begin{lemma}[Lemma 1, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma1}
-Let $\nu$ and $\nu'$ be two bandit models with $K$ arms such that for all $i$, the distributions $\nu_i$ and $\nu_i'$ are mutually absolutely continuous.
-For any almost-surely finite stopping time $\sigma$ with respect to $(\mathcal{F}_t)$,
-
-\begin{equation*}
-\sum_{i=1}^{K} \mathbb{E}_{\nu} [N_i(\sigma)] \KL(\nu_i|| \nu_i') \geq \sup_{\mathcal{E} \in \mathcal{F}_{\sigma}} d(\mathbb{P}_{\nu}(\mathcal{E}), \mathbb{P}_{\nu'}(\mathcal{E})).
-\end{equation*}
-\end{lemma}
-
-We apply this Lemma directly on the expected number of draws for each arm, $\mathbb{E}_{\nu}[N_i]$.
-For each arm $a$, we thus have $\KL(\nu_i, \nu_i') \mathbb{E}_{\nu}[N_i] \geq d(1-\delta, \delta)$.
-Using the definition of the alternative model above, we get for every small but fixed $\alpha > 0$, every arm $i \in \{1, \dots, K\}$ and $j \in \{m+1, \dots, K\}$:
-
-\begin{equation*}
-\mathbb{E}_{\nu}[T_i] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_i || \nu_{m+1}) + \alpha} \quad \text{and} \quad \mathbb{E}_{\nu}[T_j] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_j || \nu_{m}) + \alpha}.
-\end{equation*}
-
-Let $\alpha \to 0$, sum the individual arms' bounds to get the bound on the overall number of draws:
-
-\begin{equation*}
-\mathbb{E}_{\nu}[T] = \sum_{i=1}^K \mathbb{E}_{\nu}[T_i] \geq \Big( \sum_{i \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_i|| \nu_{[m+1]})} + \sum_{i \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_i|| \nu_{[m]})} \Big) d(1-\delta, \delta)
-\end{equation*}
-
-Given that we will be naturally interested in either very high or very low confidence of our algorithm, that is, $P_\nu(\mathcal{E})$ is either close to 0 or 1, it is possible to use the following approximation to the binary relative entropy given in Kaufmann et al.
-(2016):
-
-\begin{equation}\label{bre_approx}
-\forall x \in [0,1], \quad d(x,1-x) = d(1-x,x) \geq \log \frac{1}{2.4x}.
-\end{equation}
-
-This allows us to write the lower bound on the expected stopping time as:
-
-\begin{equation*}
-\mathbb{E}_{\nu}[T] \geq \Big( \sum_{i \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_i|| \nu_{[m+1]})} + \sum_{i \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_i|| \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
-\end{equation*}
-
-Given this lower bound, it is clear that the complexity of the top-$m$ problem can be lower bounded by the KL-divergence between arms and the implied threshold between the $m$-th best arm and the $(m+1)$-th best arm.
-The last equation gives a lower bound on the effort (in terms of expected number of samples) required to achieve a certain confidence level, where a problem that requires a larger effort is described as more complex.
-Indeed, in the case of fixed confidence problems, Kaufmann et al.
-(2016) describe problems as having a larger *sampling complexity*.
-Following Kaufmann et al.
-(2016), we define the complexity $\kappa_C(\nu)$ in the fixed confidence setting as
-
-\begin{equation}
-\kappa_C(\nu) = \inf_{S \, \text{PAC}} \limsup_{\delta \to 0} \frac{\mathbb{E}_{\nu}[T_{\delta}]}{\log \frac{1}{\delta}}. \label{eq:KappaC}
-\end{equation}
-
-This definition makes sense if we consider the fact that the confidence level $\delta$ is experimenter chosen and thus not relevant in describing the complexity.
-Thus, by including $\log(1/\delta)$ explicitly in \eqref{eq:KappaC}, we get rid of the confidence term in the lower bound on $\mathbb{E}_{\nu}[T]$ after plugging it into \eqref{eq:KappaC}.
-We arrive at the lower bound on the complexity measure given in Kaufmann et al.
-(2016):
-
-\begin{equation*}
-\kappa_C(\nu) \geq \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a || \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a || \nu_{[m]})}
-\end{equation*}
-
-Given this description, we would expect that a complexity measure in a fixed confidence thresholding bandit probem might involve replacing $\mu_{[m]}$ and $\mu_{[m+1]}$ by the actual threshold $\tau$ that divides the group above the threshold from the group below the threshold.
-But given the setting in Locatelli et al.
-(2016), we are mainly interested in complexity measures and algorithms for the fixed budget problem.
-The results of Kaufmann et al.
-(2016) are more limited for this case.
-While the authors are able to provide a bound on their complexity measure in the fixed budget case, it only applies to the case of *two-armed* bandit models.
-
-Consider a consistent fixed budget strategy $\mathcal{S}$ ($p_t(\nu)$ tends to zero as $t \rightarrow \infty$), and define the complexity in the fixed budget setting as follows:
-
-\begin{equation}
-\kappa_B(\nu) = \inf_{A \, \text{consistent}} \Big(\limsup_{t \to \infty} - \frac{1}{t} \log p_t(\nu)\Big)^{-1}.
-\end{equation}
-
-While we included the experimenter-fixed $\delta$ in the definition of $\kappa_C$, we now include the fixed $T$ in the definition of $\kappa_B$ to disregard it in the complexity measure after plugging in the lower bound on $p_t(\nu)$.
-The resulting lower bound given in Theorem 12 of Kaufmann et al.
-(2016).
-We see that the best exponent with which the error $p_t(\nu)$ decreases as $t \rightarrow \infty$ is based on Kullback-Leibler divergences:
-
-\begin{theorem}[Theorem 12, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem12}
-Let $\nu = (\nu_1, \nu_2)$ be a two-armed bandit model such that $\mu_1 > \mu_2$. In the fixed budget setting, any consistent algorithm satisfies:
-
-\begin{equation*}
-\limsup_{t \to \infty} - \frac{1}{t} \log p_t(\nu) \leq \inf_{(\nu_1', \nu_2') \in \mathcal{M}: \mu_1' < \mu_2'} \max \big\{\KL(\nu_1' || \nu_1), \KL(\nu_2' || \nu_2)\big\}
-\end{equation*}
-\end{theorem}
-
-For a proof, consider first the two different bandit models, $\nu$ and $\nu'$, where we fix w.l.o.g.
-$i^* = 1$ as the best arm in $\nu$, while $i^* = 2$ in $\nu'$.
-We require the algorithm $\mathcal{S}$ to be consistent for both problems.
-Since we are in the fixed budget setting, the stopping time is fixed at $T = t$.
-The correct decision differs between the two problems, and we focus on the event $A = (\hat{S}_1 = 1)$.
-Now, we can apply Lemma 1 from Kaufmann et al.
-(2016) as before, as it gives a measure of how different two bandit models are (it bounds the change in distribution).
-Here, we want to know how different $\nu$ is from $\nu'$, and, given we have only two arms,
-
-\begin{equation*}
-\mathbb{E}_{\nu'}[T_1(t)]\KL(\nu_1'|| \nu_1) + \mathbb{E}_{\nu'}[T_2(t)]\KL(\nu_2'|| \nu_2) \geq \der(\mathbb{P}_{\nu'}(A),\mathbb{P}_{\nu}(A)))
-\end{equation*}
-
-The expectations were chosen with respect to $\nu'$ in order to allow for the following: We have $p_t(\nu) = 1 - \mathbb{P}_{\nu}(A)$ and $p_t(\nu') = \mathbb{P}_{\nu'}(A)$ (since $A$ is wrong for $\nu'$).
-But since algorithm $\mathcal{A}$ is consistent for both $\nu$ and $\nu'$, we know that there should exist some number of samples such that the probability of event $A$ is bigger in setting $\nu$ (where it is the correct decision) than in setting $\nu'$ (where this would be a wrong decision and failure).
-Thus, for every $\epsilon > 0$, there exists $t_0(\epsilon)$ such that for all $t \geq t_0(\epsilon)$, $\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)$.
-Consequently, if we plug in the bound of $\epsilon$ for $\mathbb{P}_{\nu'}(A)$, then
-
-\begin{align*}
-\mathbb{E}_{\nu'}[T_1(t)]\KL(\nu_1' || \nu_1) + \mathbb{E}_{\nu'}[T_2(t)]\KL(\nu_2' || \nu_2) & \geq \der(\epsilon,1-p_t(\nu))) \\
-& = \epsilon \log \frac{\epsilon}{1-p_t(\nu)} + (1-\epsilon) \log \frac{1-\epsilon}{p_t(\nu)} \\
-& \geq (1-\epsilon) \log \frac{1-\epsilon}{p_t(\nu)} + \epsilon \log \epsilon.
-\end{align*}
-
-Let $\epsilon$ go to zero so that
-
-\begin{align*}
-\mathbb{E}_{\nu'}[T_1(t)]\KL(\nu_1' || \nu_1) + \mathbb{E}_{\nu'}[T_2(t)]\KL(\nu_2' || \nu_2)
-& \geq \log \frac{1}{p_t(\nu)} = -\log p_t(\nu).
-\end{align*}
-
-Dividing both sides by $t$ and taking the limsup, we arrive at
-
-\begin{align*}
-\limsup_{t \to \infty} - \frac{1}{t} \log p_t(\nu)
-& \leq \limsup_{t \to 0} \frac{1}{t} \sum_{i=1}^2 \mathbb{E}_{\nu'}[T_i(t)] \KL(\nu_i' || \nu_i) \\
-& \leq \max_{i=1,2} \KL(\nu_i' || \nu_i),
-\end{align*}
-
-where the last line follows from the fact that the $\frac{1}{t} \sum_{i=1}^2 \mathbb{E}_{\nu'}[T_i(t)]$ part creates a weighted average of the two divergences $\KL(\nu_i', \nu_i)$.
-As noted in Kaufmann et al.
-(2016), one arrives at the final result by choosing $\mu_1'$, $\mu_2'$ so that $| \KL(\nu_1', \nu_1) - \KL(\nu_2', \nu_2) |$ is as small as possible.
-
-As noted by Kaufmann et al.
-(2016), the advantage of this lower bound is that it makes the complexity in the fixed confidence and the fixed budget setting directly comparable.
-The disadvantage being that the result only holds for two-armed models.
-While the authors are not able to derive directly comparable lower bounds for the top-$m$ case, they derive a first lower bound in the Gaussian case with equal variances.
-
-Before we discuss algorithms given in Kaufmann et al.
-(2016) that match the lower bounds, we show how based on the proof of Theorem 12 in Kaufmann et al.
-(2016) very similar lower bounds can be derived for the fixed budget thresholding problem.
-
-### Lower Bound for Fixed Budget Thresholding Problem \label{sec:LBTBP}
-
-In order to derive a bound for the fixed budget problem, Kaufmann et al.
-(2016) focus on the setting with two arms which is the most simple version of the top-$m$ problem.
-Less than two arms does not make sense, since the single arm is by definition the best arm.
-In the case of the thresholding bandit, however, a single-armed problem makes still at least limited sense in that we still have to classify this arm correctly with respect to the threshold.
-Thus, we can show the following corollary which gives a bound on the complexity of the single-armed thresholding bandit.
-
-\begin{corollary}
-Consider the setting in \autoref{sec:Setup}.
-Let $\nu = \nu_1$ be a one-armed thresholding bandit model where $\tau$ is the threshold fixed upfront.
-Let $\nu$ be from the one-parameter exponential family of distributions such that $\nu_1$ can be parameterized by its mean, $\mu_1$, and the Kullback-Leibler divergence between distributions $\nu_1$ and $\nu_1'$ can be written as $\KL(\nu_1', \nu_1) = \KL(\mu_1', \mu_1)$.
-In the fixed budget setting, any consistent algorithm ($p_t(\nu) \rightarrow 0$ as $t \rightarrow \infty$) satisfies for $\mu_1' \rightarrow \tau$:
-
-$$
-- \frac{1}{t} \log p_t(\nu) \leq \KL(\mu_1' || \mu_1)
-$$
-\end{corollary}\label{corollary:LB1TBP}
-
-This is basically the Chernoff-Stein Lemma for the hypothesis test of two alternatives (compare chapter 11 in Cover and Thomas, 2006, or \autoref{theorem:ChernoffStein}), in which the optimal error exponent is based on the Kullback-Leibler divergence.
-We arrive at this result as the one-armed bandit does not require sequential sampling: The single arm receives all samples.
-$\mathbb{E}_{\nu'}[N_1(t)]$ is not a random variable but equals $T$.
-The single-armed bandit is a simple hypothesis test on a sample of size $T$.
-In a way, it is a degenerate case of a multi-armed bandit problem.
-
-We present the proofs of \autoref{sec:LBTBP} in the appendix in \autoref{sec:corollaryLBTBPproof}.
-While we were hoping to also prove a lower bound for the $K$-armed bandit problem, we were not able to do so as this entails the expectation under the alternative problem of the number of times the changed arm $a$ is pulled.
-Compare to the proof for the two-armed pure exploration bandit in Kaufmann et al.
-(2016).
-
-But as we see in the following corollary, we can extend the lower bound to the $K$-armed fixed budget thresholding bandit problem, which stands in contrast to the fact that for the top-$m$ problem, it is only possible to show the lower bound for two arms.
-The result is based on an alternative setting $\nu'$ in which all arms have means $\mu' = \tau$ such that their expected number of pulls corresponds to uniform sampling, $\mathbb{E}_{\nu'}[N_i(t)] = T/K$.
-
-\begin{corollary}
-Consider the setting in \autoref{sec:Setup}.
-Let $\nu = (\nu_1, ..., \nu_K)$ be a $K$-armed thresholding bandit problem in which $\tau$ is the threshold fixed upfront.
-For $i \in \{1,...,K\}$, let $\nu_i$ be from the one-parameter exponential family of distributions such that $\nu_i$ can be parameterized by its mean, $\mu_i$, and the Kullback-Leibler divergence between distributions $\nu_i$ and $\nu_i'$ can be written as $\KL(\nu_i, \nu_i') = \KL(\mu_i, \mu_i')$.
-In the fixed budget setting, any consistent algorithm satisfies for $\mu_i' \rightarrow \tau$:
-
-$$
-\limsup_{t \rightarrow \infty} -\frac{1}{t} \log p_t(\nu) \leq \max_{i \in \{1,...,K\}} \KL(\mu_i' || \mu_i)
-$$
-
-or
-
-$$
-- \frac{1}{t} \log p_t(\nu) \leq \frac{1}{K}\sum_{i=1}^{K} \KL(\tau || \mu_i),
-$$
-\end{corollary} Corresponding to the complexity measures defined in equation $(1)$ of Kaufmann et al.
-(2016), we can define the complexity $\kappa_{TBP}(\nu)$ in the thresholding bandit problem and lower bound it:
-
-$$
-\kappa_{TBP}(\nu) = \inf_{S \text{ consistent}} \Big(\limsup_{t \rightarrow \infty} - \frac{1}{t} \log p_t(\nu)\Big)^{-1} \geq K \Big(\sum_{i=1}^{K} \KL(\mu_i'||\mu_i)\Big)^{-1}
-$$
-
-### Strategies Matching the Top-$m$ Lower Bound
-
-Kaufmann et al.
-(2016) do not present algorithms matching the lower bound of Theorem \ref{theorem:KaufmannEtAlTheorem17}.
-They do consider algorithms that connect to Theorem \ref{theorem:KaufmannEtAlTheorem4} and Theorem \ref{theorem:KaufmannEtAlTheorem12}.
-Given that we aim to extend the fixed budget thresholding bandit problem, we are most interested in the matching strategies for Theorem \ref{theorem:KaufmannEtAlTheorem12}.
-However, given that this lower bound applies only to two-armed bandits, the algorithms proposed by Kaufmann et al.
-(2016) are of limited practical interest.
-Furthermore, the proposed strategies require knowledge that is in general not available upfront: For Gaussian distributions, the knowledge of the (potentially different) variance is assumed which enables a strategy that pulls each arm proportional to its variance.
-
-Even more difficult are the assumptions in the case of Bernoulli two-armed bandit models: The proposed algorithm requires knowledge about the true parameters of the distributions.
-That this limits the practical interest is also noted by the authors of Kaufmann et al.
-(2016).
-Thus, they suggest to use uniform sampling strategies in the case of two-armed Bernoulli bandits, and show that there is not much to be lost by doing so.
-
-Thus, Kaufmann et al.
-(2016) joins other papers like Audibert et al.
-(2010) and Kaufmann and Kalyanakrishnan (2013) which struggle to find matching strategies in the fixed budget setting that do not rely on knowledge of parameters or the complexity of the problem.
-
-In contrast, Kaufmann et al.
-(2016) are able to show that their complexity measure derived for the fixed confidence setting, $\kappa_C(\nu)$, can be upper-bounded using the bound given for the KL-LUCB algorithm in Kaufmann and Kalyanakrishnan (2013).
-In the case of exponential family bandits, the complexity $\kappa_C(\nu)$ is bounded as given in equation (6) in Kaufmann et al.
-(2016):
-
-\begin{equation*}
-\sum_{i \in S^*_m} \frac{1}{\KL(\mu_i || \mu_{[m+1]})} + \sum_{i \notin S^*_m} \frac{1}{\KL(\mu_i || \mu_{[m]})} \leq \kappa_C(\nu) \leq 24 \min_{\mu \in [\mu_{[m+1]},\mu_{[m]}]} \sum_{i=1}^{K} \frac{1}{\KL^*(\mu_i || \mu)},
-\end{equation*}
-
-where again we write with slight abuse of notation $\KL(\nu_{\mu}|| \nu_{\mu'}) = \KL(\mu || \mu')$ as the shorthand for the KL-divergence of two distributions from the exponential family parameterized by $\mu$ and $\mu'$ respectively.
-$\KL^*(\mu || \mu') = \KL(\mu^* || \mu)$ is the Chernoff information between the two distributions, where $\mu^*$ is chosen so that $\KL(\mu^* || \mu) = \KL(\mu^* || \mu')$.
-
-## Information Theoretic Approach to Best Arm Identification \label{sec:OptimalBestArmIdentification}
-
-Instead of discussing the KL-LUCB algorithm for the fixed confidence top-$m$ problem, we shift our focus onto the fixed confidence best arm identification problem, as discussed in Garivier and Kaufmann (2016).
-The authors also derive a lower bound on the sample complexity using Lemma \autoref{theorem:KaufmannEtAlLemma1}.
-Furthermore, they propose a matching strategy for $K \geq 2$ arms.
-
-The setting differs slightly from the setting considered in Kaufmann et al.
-(2016).
-In particular, Garivier and Kaufmann (2016) focus on distributions $\nu_{\theta}$ from the one-parameter canonical exponential family of distributions, which can be parameterized by their mean $\mu$, and thus can be written as $\nu_{\mu}$; as before, we simplify the notation of the KL-divergence for these distributions to $\KL(\nu || \nu') = \KL(\mu || \mu')$.
-
-Furthermore, if we let $\mathcal{S}$ to be a set of bandit models with $K$ distributions each, then each model is fully defined by a vector $\bm{\mu} = (\mu_1, \dots, \mu_K)$.
-Assume that every $\bm{\mu} \in \mathcal{S}$ has a unique maximum given by $i^*(\bm{\mu})$ such that $\mu_{i^*} > \max_{i \neq i^*(\bm{\mu})} \mu_i$.
-In order to fix the confidence $1-\delta$, we specify the risk $\delta$.
-Similar to the top-$m$ case considered before, strategies corresponding to this risk are called $\delta$-PAC if for every $\bm{\mu} \in \mathcal{S}$, the strategy ends surely after a finite number of samples, $\mathbb{P}_{\bm{\mu}}(T_{\delta} < \infty) = 1$, and the error probability is at least as small as the fixed risk level, $\mathbb{P}_{\bm{\mu}}(\hat{i}_{T_{\delta}} \neq i^*) \leq \delta$.
-In order to derive the lower bound on the expected number of samples $\mathbb{E}[T]$ through a change in distributions, we introduce the set of alternative problems for which the optimal arm is different from $\bm{\mu}$:
-
-\begin{equation*}
-\text{Alt}(\bm{\mu}) := \{\bm{\lambda} \in \mathcal{S}: i^*(\bm{\lambda}) \neq i^*(\bm{\mu})\},
-\end{equation*}
-
-where $\bm{\lambda}$ is the vector of means defining the distributions of the alternative problem.
-Lastly, we have the set of probability distributions on the arms $\{1,...,K\}$: $\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}$.
-Each $w_i$ corresponds to the fraction of overall samples that arm $i$ receives (which are random variables similar to $T_i$ in \autoref{sec:UpperBoundProof}).
-We now state the lower bound:
-
-\begin{theorem}[Theorem 1, Garivier and Kaufmann, 2016] \label{theorem:GarivierKaufmannTheorem1}
-Let $\delta \in (0,1)$. For any $\delta$-PAC strategy and any bandit model $\bm{\mu} \in \mathcal{S}$,
-
-\begin{equation*}
-\mathbb{E}_{\bm{\mu}} [T_{\delta}] \geq T^*(\bm{\mu}) d(\delta,1-\delta),
-\end{equation*}
-
-where
-
-\begin{equation} \label{eq:GarivierKaufmann_Theorem1_Game}
-T^*(\bm{\mu})^{-1} := \sup_{w \in \Sigma_K} \inf_{\bm{\lambda} \in \text{\em{Alt}}(\bm{\mu})} \left( \sum_{i=1}^K w_i \text{\em{KL}}(\mu_i|| \lambda_i)\right).
-\end{equation}
-\end{theorem}
-
-We see that the two bounds given in Theorem \ref{theorem:KaufmannEtAlTheorem4} and Theorem \ref{theorem:GarivierKaufmannTheorem1} on the sample complexity differ only in the way in which they sum the Kullback-Leibler divergences over the $K$ arms.
-In contrast to Theorem \ref{theorem:KaufmannEtAlTheorem4}, here the contribution of each arm through its KL-divergence is weighted.
-The difference is that while we were able to clearly describe the change of distribution in the top-$m$ case for each arm -- we specified an alternative model for each arm that yields a new set of $m$ optimal arms -- we now consider all alternative models that yield a different best arm than the model $\bm{\mu}$.
-In the previous theorem, we sum over the complexity of each individual arm, since the change in distribution only affects one arm at a time, thus leading to a KL-divergence of 0 for the other arms while still changing the optimal set.
-Now, we consider all instances of alternative models $\bm{\lambda}$, and thus also those in which several arms are modified (and thus have a KL-divergence unequal 0 in the result of Lemma 1).
-
-To proof Theorem \ref{theorem:GarivierKaufmannTheorem1}, we let $\delta \in (0,1)$, $\bm{\mu} \in \mathcal{S}$, and only consider $\delta$-PAC strategies.
-As before, $T_i(t)$ describes the random number of pulls of arm $i$ until time $t$, for all $t\geq 1$.
-Again, Lemma \ref{theorem:KaufmannEtAlLemma1} states how the risk $\delta$ relates to the expected number of draws of each arm given two models which differ in their optimal arm.
-How much the two models differ is evaluated based on the KL-divergence for each pair of arms:
-
-\begin{equation*}
-\forall \lambda \in \mathcal{S}: i^*(\lambda) \neq i^*(\mu), \sum_{i=1}^K \KL(\mu_i,\lambda_i)\mathbb{E}_{\bm{\mu}}[T_i(T_{\delta})] \geq d(\delta, 1- \delta).
-\end{equation*}
-
-As mentioned, we now do not consider a specific alternative for each arm, but instead look at the infimum over all the possible alternatives, and use the fact that $\mathbb{E}_{\bm{\mu}}[T_{\delta}] = \sum_{i=1}^K \mathbb{E}_{\bm{\mu}}[T_i(T_{\delta})]$:
-
-\begin{align*}
-\der(\delta, 1-\delta) & \leq \inf_{\lambda \in \text{Alt}(\bm{\mu})} \mathbb{E}_{\bm{\mu}}[T_{\delta}] \Big(\sum_{i=1}^K \frac{\mathbb{E}_{\bm{\mu}}[T_i]}{\mathbb{E}_{\mu}[T_{\delta}]} \KL(\mu_i, \lambda_i)\Big) \\
-& = \mathbb{E}_{\bm{\mu}}[T_{\delta}] \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{i=1}^K \frac{\mathbb{E}_{\bm{\mu}}[T_i]}{\mathbb{E}_{\mu}[T_{\delta}]} \KL(\mu_i, \lambda_i)\Big) \\
-& \leq \mathbb{E}_{\bm{\mu}}[T_{\delta}] \sup_{w \in \Sigma_K} \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{i=1}^K w_i \KL(\mu_i, \lambda_i)\Big).
-\end{align*}
-
-As stated in Garivier and Kaufmann (2016), the term $\frac{\mathbb{E}_{\bm{\mu}}[T_i]}{\mathbb{E}_{\mu}[T_{\delta}]}$ gives the fraction of draws each arm receives.
-This value, however, depends on the used algorithm.
-To make it hold for any $\delta$-PAC algorithm, it is replaced by the supremum over $\Sigma_K$, which is the distribution over these fractions for any $\delta$-PAC strategy.
-
-This lower bound can be interpreted as a minimax game^[See the presentation by Aurélien Garivier at COLT 2016: <https://youtu.be/eLyrrYqJlkE>], where the experimenter has to choose the share of samples she attributes to each arm in a way that is optimal given that nature will respond and choose the most difficult alternative model given her weights.
-Thus, to make the lower bound practical, it is a matter of finding the optimal weights $w^*(\bm{\mu})$.
-This step did not occur in the lower bound for the top-$m$ problem since the alternative models were specified by changing the distribution of one arm with respect to the "border" between the two groups of arms.
-
-The existence of the optimal weights suggests an algorithm that keeps track of the share of samples that is attributed to each arm and makes sure that it stays close to the optimum until some decision rule assures that the $\delta$-PAC condition is fulfilled.
-
-Indeed, the optimal weights will lead to a sampling structure in which arms are drawn such that their individual probabilities of error stay at the same level.
-An arm more distant from the optimal arm in terms of Kullback-Leibler divergence should receive a smaller share of the samples to achieve the same error probability as an arm closer to the optimal arm.
-
-This is what happens when we look for proportions $w \in \Sigma_K$ that minimize the cost from a change in distributions, that is, the term $F(\bm{\mu}, \bm{w}) = \inf_{\bm{\lambda} \in \text{Alt}(\bm{\mu})} \Big(\sum_{i= 1}^K w_i \KL(\mu_i, \lambda_i)\Big)$.
-In the proof of Lemma 3 of Garivier and Kaufmann, it is shown that nature, selecting the alternative model $\bm{\lambda}$, will always pick an alternative model in which only a single arm $i$ is changed such that $\lambda_i > \lambda_1$ since
-
-\begin{align*}
-T^*(\bm{\mu})^{-1} & = \sup_{w \in \Sigma_K} \min_{i \neq 1} \inf_{\bm{\lambda} \in \mathcal{S}: \lambda_i > \lambda_1} \sum_{i=1}^K w_i \KL(\mu_i, \lambda_i)  \\
-& = \sup_{w \in \Sigma_K} \min_{i \neq 1} \inf_{\bm{\lambda}: \lambda_i \geq \lambda_1} [w_1 \KL(\mu_1, \lambda_1)+w_i \KL(\mu_i, \lambda_i)]. \Alignyesnumber\label{eqn:ComplexityTrackStopStrategy}
-\end{align*}
-
-Consequently, $w$ will be chosen so as to minimize $T^*(\bm{\mu})$ no matter which arm $i$ is picked.
-It is a minimax game, so the ideal solution is to keep for each arm $i \neq 1$ the term $w_1 \KL(\mu_1, \lambda_1) + w_i \KL(\mu_i, \lambda_i)$ at the same level.
-Garivier and Kaufmann show that this can be written in terms of the Jenson-Shannon divergence, defined for every $\alpha \in [0,1]$ as
-
-\begin{equation*}
-I_{\alpha}(\mu_1, \mu_2) := \alpha \KL(\mu_1 || \alpha \mu_1 + (1-\alpha) \mu_2) + (1-\alpha) \KL(\mu_2 || \alpha \mu_1 + (1-\alpha) \mu_2).
-\end{equation*}
-
-Using this notation, the optimal proportions can be written as 
-\begin{equation*}
-w^*(\bm{\mu}) = \arg \max_{w \in \Sigma_K} \min_{i \neq 1} (w_1 + w_i) I_{\frac{w_1}{w_1+w_i}}(\mu_1, \mu_i)
-\end{equation*}
-
-which let's us furthermore conclude that these quantities are equal for all $i,j \in \{2,\dots, K\}$ with
-\begin{equation*}
-(w_1^* + w_i^*) I_{\frac{w_1^*}{w_1^*+w_i^*}}(\mu_1, \mu_i) = (w_1^* + w_j^*) I_{\frac{w_1^*}{w_1^*+w_j^*}}(\mu_1, \mu_j),
-\end{equation*}
-
-which is simply the statement in Lemma 4 of Garivier and Kaufmann (2016).
-
-And so by assuring the reader that there are ways to compute $w_i^*$ and $T^*$ given $\bm{\mu}$ (see chapter 2.2 in Garivier and Kaufmann (2016)), we can now introduce the *Track-and-Stop* strategy given in Garivier and Kaufmann (2016) that is able to match the lower bound.
-The main idea of the *Track-and-Stop* algorithm is to keep track of the optimal shares for each arm by equalizing the error probabilies for each arm.
-
-When going from theory to algorithm, the obvious problem is that we no longer know the true parameters $\bm{\mu}$ and cannot calculate the optimal weights.
-Instead, we have to estimate the maximum likelihood estimates $\hat{\mu}(t) = (\hat{\mu}_1(t), \dots, \hat{\mu}_K(t))$ of the true mean at the current round $t$ and need to base our sample weights on them.
-It is however problematic to rely on the sample means as we are inherently unsure about them.
-And so wrong estimates, which naturally occur most easily in the beginning when not many samples have been pulled, are prone to lead to wrong weights.
-Thus, if a wrong estimate $\hat{\mu}_i$ for arm $i$ leads to a small weight $w_i$, then after a few more rounds neither the estimate nor the weight will be correct.
-Thus, Kaufmann and Garivier conclude that "a naive plug-in sampling rule sometimes fails".
-They propose to enforce a certain minimum level of exploration to ensure that arms that erroneously received a very small weight will be further explored regardless.
-
-A very intuitive solution to this problem is proposed in Lemma 8 of Garivier and Kaufmann (2016) with the $D-Tracking$ rule.
-Whenever some arm has received a very small number of pulls $T_i(t)$ given the number of iterations $t$ so far, and the number of arms $K$ that have to share the samples, pull the arm that has received the smallest amount of samples so far.
-Else, pull the arm whose number of pulls so far $T_i(t)$ is the farthest away from what its optimal share $t\cdot w^*_i(\hat{\bm{\mu}}(t))$ would be.
-Given this sampling rule, the authors can show in their Proposition 9 that the empirical proportion of draws converges in probability to the optimal weights given the true means.
-
-When combining this sampling rule with an appropriate stopping rule, the authors are able to prove in Theorem 14 an upper bound on the expected sampling complexity $\mathbb{E}_{\mu}[T_{\delta}]$.
-The stopping rule ensures that the algorithm explores sufficiently to promise a risk smaller than $\delta$, while stopping as soon as possible.
-Given that the sampling rule is independent of this stopping rule, the rule boils down to a statistical test at every iteration and thus is a sequential test based on the current estimate of $\hat{\bm{\mu}}$.
-Chernoff's Stopping Rule proposed in Garivier and Kaufmann (2016) calculates for each arm $i\in \mathbb{A} = \{1,...K\}$ the Generalized Likelihood Ratio statistic with every arm $j \in \mathbb{A}^{\setminus i}$, which for $\hat{\mu}_i(t) \geq \hat{\mu}_j(t)$ can be written as
-
-\begin{equation*}
-Z_{i,j}(t) = - Z_{j,i} = T_i(t) \KL(\hat{\mu}_i(t) || \hat{\mu}_{i,j}(t)) + T_j(t) \KL(\hat{\mu}_{j}(t) || \hat{\mu}_{i,j}(t)),
-\end{equation*}
-
-where
-
-\begin{equation*}
-\hat{\mu}_{i,j}(t) := \frac{T_i(t)}{T_i(t) + T_j(t)}\hat{\mu}_i(t) + \frac{T_j(t)}{T_i(t) + T_j(t)}\hat{\mu}_j(t).
-\end{equation*}
-
-Consequently, a sensible idea for a stopping rule would be that there has to be an arm $i \in \{1,...,K\}$ for which $Z_{i,j} \geq 0 \text{ for all }  j \in \{1,...,K\}^{\setminus i}$ (which is always fulfilled if there is a uniquely best arm), and we demand that for this arm the smallest of the $(K-1)$ test statistics has to be larger than an exploration threshold $\beta(t, \delta)$.
-The final sampling round $T_{\delta}$ of the algorithm is given by:
-
-\begin{equation*}
-T_{\delta} = \inf \{t \in \mathbb{T}: \exists i \in \mathbb{A}, \forall j\in \mathbb{A}^{\setminus i}, Z_{i,j}(t) > \beta(t, \delta)\}
-\end{equation*}
-
-Demanding that the optimal exploration threshold increases in rounds $t$ (if we have more samples, require more certainty; punish for failing previous tests) and decreases in risk $\delta$ at a diminishing rate, the optimal exploration rate for Bernoulli arms derived in Theorem 10 of Garivier and Kaufmann (2016) is intuitive:
-
-\begin{equation*}
-\beta(t, \delta) = \log \Big(\frac{2t(K-1)}{\delta}\Big).
-\end{equation*}
-
-With this, we can state the final theorem of the chapter, which gives the upper bound matching the lower bound in Theorem \ref{theorem:GarivierKaufmannTheorem1} for small risk values $\delta$ using the D-Tracking rule and Chernoff's stopping rule with the exploration term given in the previous equation:
-
-\begin{theorem}[Theorem 14, Garivier and Kaufmann, 2016] \label{theorem:GarivierAndKaufmannTheorem14}
-Let $\bm{\mu}$ be an exponential family bandit model.
-Let $\alpha \in [1, e/2]$ and $r(t) = O(t^{\alpha})$.
-Using Chernoff's stopping rule with $\beta(t,\delta) = \log(r(t)/\delta)$ and the sampling rule D-Tracking,
-
-\begin{equation*}
-\limsup_{\delta \to 0} \frac{\mathbb{E}_{\bm{\mu}}[T_{\delta}]}{\log(1/\delta)} \leq \alpha T^*(\mu), \quad \text{with } T^*(\mu) \text{ as defined in equation \ref{eqn:ComplexityTrackStopStrategy}}.
-\end{equation*}
-\end{theorem}
-
-## Conclusion
-
-Overall, the two papers presented in this chapter make significant contributions to identifying the top-$1$ or the top-$m$ arms in a multi-armed bandit setting.
-Their contribution is primarily based on including the Kullback-Leibler divergence and Chernoff information as information theoretic measures in the derivation of bounds and the matching algorithms.
-Thereby, they go beyond a sum of squared gaps which is most relevant only in the case of Gaussian distributions.
-While the contribution in the fixed budget setting is limited to the two-armed bandit case, the authors derive general lower bounds in the fixed confidence setting.
-All bounds presented are primarily based on Lemma \ref{theorem:KaufmannEtAlLemma1}.
-Lemma \ref{theorem:KaufmannEtAlLemma1} is able to measure the "transportation cost" (see Garivier and Kaufmann, 2016) of moving from one distribution to another one in terms of Kullback-Leibler divergence.
-It is the bound on the expected likelihood ratio term that appears when changes in distribution are applied.
-
-In the case of the fixed budget top-$m$ arm identification problem, we see that the derivation of a lower bound on the complexity term is mostly limited by the difficulty of defining an alternative problem $\nu'$ to $\nu$ that fits the Lemma \ref{theorem:KaufmannEtAlLemma1}.
-But given the intuition that in top-$m$ problems the $m$-th best arm and the $(m+1)$-th best arm define an implied threshold between the two groups of arms, we were able to apply the ideas of Kaufmann et al.
-(2016) to our fixed budget thresholding bandit problem.
-In contrast to their problem, arms are classified against the known threshold $\tau$, which makes it possible to define an alternative problem $\nu'$ in which we do not have to change arms with respect to each other, but only with respect to $\tau$.
-This has lead us to the simple lower bound on the problem complexity for the thresholding bandit problem with exponential family distributions given in Corollary \ref{corollary:LBKTBP}.
-
-In the best arm identification problem discussed by Garivier and Kaufmann (2016), we were introduced to the idea of comparing each arm to the best arm, and evaluating the difference between the best arm and the other arms based on the Generalized Likelihood Ratio test.
-This idea seems transferrable to the thresholding bandit problem.
-Indeed, it might even be easier as the best arm does not have to be estimated; instead, we would compare each arm to the threshold $\tau$.
-Intuitively, one can frame this problem for each arm individually as an hypothesis test between the maximum likelihood estimate of the mean and the threshold $\tau$.
-We will come back to this idea in \autoref{sec:LikelihoodRatioForExponentialFamily}.
-
-Lastly, we observe that Garivier and Kaufmann (2016) support their algorithm's main strategy by an additional D-Tracking rule which protects them against poor estimates in the beginning of the sampling.
-Such rule should be mostly unnecessary, for example, the cumulative regret setting, as algorithms there rely on upper confidence bound estimates.
-This is not the case for the Track-and-Stop strategy introduced in Garivier and Kaufmann, and neither for our Simple Likelihood Ratio strategy introduced in \autoref{sec:1DSLR}.
-In \autoref{sec:Simulation2}, we show empirically that the performance of the Simple Likelihood Ratio strategy can be further improved by adding the D-Tracking rule.
-
-\newpage
-
-# Extensions to the Thresholding Bandit Problem \label{chap:Extensions}
-
-## Introduction \label{sec:ExtensionsIntroduction}
-
-In \autoref{chap:ThresholdingBanditProblem} we introduced the thresholding bandit problem as proposed in Locatelli et al.
-(2016) alongside the APT algorithm.
-We saw that the upper bound for the APT algorithm matches the lower bound for the thresholding bandit problem given in Locatelli et al.
-(2016).
-The algorithm also exhibits favorable characteristics such as its upper bound holding at any stopping time, and that it does not require any parameter to be tuned upfront.
-However, we have seen that the index $B^{APT}$ and the complexity term $H$ employed by the APT algorithm are the most effective for $R$-sub-Gaussian distributions.
-Both are related to the KL-divergence between two Gaussian distributions of equal variance.
-Given that this sub-Gaussian approximation can be poor in certain cases, we motivated information theoretic measures in an algorithm's index (compare \autoref{sec:DiscussionLocatelli}).
-
-Information theoretic measures are one way of taking not only the sample mean into account to estimate differences between distributions -- as done by the APT algorithm.
-Another logical extension is to consider higher moments of a distribution, like its variance.
-After all, arms do not necessarily have the same variance, even if they are sub-Gaussian (two arms might be $R_1$-sub-Gaussian and $R_2$-sub-Gaussian).
-And given two arms for which we estimate the same mean, we would prefer to draw more samples from the arm with the larger variance.
-The simplest example of this are two Normal distributions with different variances.
-
-For these reasons, in the following, we first present in \autoref{sec:VarianceBasedAlgorithms} two algorithms which incorporate empirical variances as described in Mukherjee et al.
-(2017) and Zhong et al.
-(2017).
-We then go back to the information theoretic ideas and introduce a new algorithm based on the concept of likelihood ratios in \autoref{sec:LikelihoodRatioForExponentialFamily}.
-Finally, we compare the performance of different algorithms based on simulations and real world data sets in \autoref{chap:Experiments}.
-
-## Variance Based Algorithms for the Thresholding Bandit \label{sec:VarianceBasedAlgorithms}
-
-### Augmented-UCB Algorithm \label{sec:AugUCBAlgorithm}
-
-Combining learnings from the APT and other algorithms, Mukherjee et al.
-(2017) propose the Augmented-UCB (AugUCB) algorithm based on variance estimates for the thresholding bandit problem.
-The setting they consider is very similar to the setting in Locatelli et al.
-(2016).
-The main difference being that, while Locatelli et al.
-(2016) assume $R$-sub-Gaussian reward distributions, Mukherjee et al.
-(2017) assume rewards to be bounded in $[0,1]$, which makes the AugUCB applicable to fewer distributions.
-The AugUCB algorithm itself differs significantly from the APT algorithm.
-The two main ideas it employs are, first, upper confidence bounds based on the Bernstein inequality and empirical variance estimates to compute the index based on which an arm is chosen at every round.
-Second, if an arm estimate is "far enough" away from the threshold as measured by the confidence bounds, it will be eliminated, that is, no longer be pulled until the end of the budget.
-Both ideas are based not only on the empirical mean estimate $\hat{\mu}_i(t)$, but also on a term $s_i$ that is increasing linearly in the estimated standard deviation.
-While the APT algorithm plays the arm minimizing the quantity $\sqrt{T_i(t)} \hat{\Delta}_i(t)$, AugUCB plays the arm minimizing the quantity $\hat{\Delta}_i(t) - 2s_i$, where $s_i$ is based on the variance estimate $\hat{v}_i$, and an exploration term $\psi_m$ linear in $T$, as well as an elimination parameter $\rho$ (compare Algorithm 1 in Mukherjee et al., 2017):
-
-\begin{equation*}
-s_i = \sqrt{\frac{\rho \psi_m (\hat{v}_i + 1) \log(T \epsilon_m)}{4n_i}}.
-\end{equation*}
-
-Consequently, the authors also introduce complexity measures which take the variance into account.
-From Gabillon et al.
-(2011) they use $H_{\sigma, 1}= \sum_{i=1}^K \frac{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}{\Delta_i^2}$.
-Furthermore, with $\stackrel{\sim}{\Delta}_i^2 = \frac{\Delta_i^2}{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}$, where $\stackrel{\sim}{\Delta}_{(i)}$ is an increasing ordering of $\stackrel{\sim}{\Delta}_i$, the authors define a complexity corresponding to $H_{CSAR,2}$ in Chen et al.
-(2014):
-
-\begin{equation*}
-H_{\sigma,2} = \max_{i \in \mathcal{A}} \frac{i}{\stackrel{\sim}{\Delta}_{(i)}^2}.
-\end{equation*}
-
-While the latter complexity appears in the provided upper bound on the AugUCB algorithm's expected loss, it could be replaced by $H_{\sigma, 1}$ since $H_{\sigma, 2} \leq H_{\sigma,1}$.
-$H_{\sigma,1}$ is more easily compared to the complexity $H$ defined in Locatelli et al.
-(2016).
-Essentially, every arm's complexity contribution is additionally scaled by a term increasing in the arm's variance (see also Figure 3 below).
-
-In the case of the APT algorithm the number of times a specific arm has been drawn $T_i$ measures how concentrated the estimated mean is around the true mean (and thus for large $T_i$ an arm is no longer drawn even if $\hat{\mu}$ is close to $\tau$).
-This exploration is regulated by the combination of the variance estimate $\hat{v}_i$ and the exploration factor $\psi_m$ in the case of the AugUCB algorithm.
-The terms ensure that certain arms are no longer pulled when the algorithm is sufficiently confident in the location of the true mean.
-Indeed, the AugUCB algorithm goes a little further than the APT algorithm in that it stops to sample arms when a separation condition (mean separated from threshold) is estimated to hold.
-The same separation condition is used in the authors' upper bound proof and is reminiscient of the separation condition used in the proof of the upper bound in Locatelli et al.'s (2016) (compare \autoref{sec:CheckSeparationCondition}).
-
-Therefore, when using a very similar favorable event in the proof of their upper bound, Mukherjee et al.
-(2017) have to bound the probability that an arm is not removed from the active set after a certain number of rounds -- even though the arm is above (respectively below) the threshold.
-If this probability is small, then the algorithm is able to be confident in an arm's true mean by employing variance estimates.
-In order to derive the bound, Mukherjee et al.
-(2017) use the Bernstein inequality.
-
-It has to be noted that Mukherjee et al.
-(2017) have to assume that the distributions have rewards bounded in $[0,1]$ in order to derive the bound on the probability that an arm has not been eliminated correctly in round $T_i$.
-Thus, the distributions for which their upper bound holds are a subset of the $R$-sub-Gaussian distributions considered in Locatelli et al.
-(2016).
-It would otherwise not be possible to upper bound the $s_i$ term by $\Delta_i/4$ as Mukherjee et al.
-do in their proof: With bounded rewards, the arms' variances are also bounded in $[0,1]$ such that $\hat{v}_i \in [0,1]$.
-Yet, the simulations by Mukherjee et al.
-are performed on Gaussian arms with variance smaller than one, which at least makes empirical variances smaller 1 likely.
-
-Based on this assumption, the authors show that the probability that an arm has not been eliminated after $m_i$ rounds is given by (compare equation (2) in Mukherjee et al., 2017):
-
-\begin{equation} \label{Mukherjee2017Equation2}
-\mathbb{P}(\hat{\mu}_i > \mu_i + 2s_i) \leq \mathbb{P} (\hat{\mu}_i > \mu_i + 2\bar{s}_i) + \mathbb{P}(\hat{v}_i \geq \sigma^2_i + \sqrt{\rho \epsilon_{T_i}})
-\end{equation}
-
-Compare Mukherjee et al.
-(2017) for the notation.
-Then it becomes clear that the left part of the RHS gives the probability that the mean estimate is poor, while the right term gives the probability that the variance is overestimated.
-The first term is bounded by the Bernstein inequality.
-In the cumulative regret setting, there exists a similar decomposition for algorithms based on upper confidence bounds.
-There, the expected number of pulls of a suboptimal arm is bounded.
-Compare for example chapter 3.1 in Kaufmann et al.
-(2012b), in which the expected number of draws of an suboptimal arm is decomposed into the probability that the optimal arm's mean is underestimated, and the probability that the upper confidence bound of the suboptimal arm is still very large.
-To give bounds for UCB algorithms, certain convergence rates are shown for these two probabilities.
-Mukherjee et al.
-do similarly for their upper confidence algorithm in the thresholding setting.
-
-### Anytime Parameter-free Empirical Variance Guided Algorithm \label{sec:EVTAlgorithm}
-
-A second algorithm for the thresholding bandit problem employing empirical variance estimates is introduced in Zhong et al.
-(2017).
-While they propose different algorithms for different setting of the thresholding bandit problem, we focus here on their strategy that can be compared directly with the problem described in Locatelli et al.
-(2016).
-
-This strategy is the parameter-free version of their Empirical Variance Guided Algorithm (EVT$_{pf}$).
-The EVT$_{pf}$ algorithm is an extension of the APT algorithm that takes the empirical variance of the arms into account and deduces an upper bound through empirical Bernstein bounds in a proof following the model of the one described in Locatelli et al.
-(2016) (compare \autoref{sec:UpperBoundProof}).
-
-In order to describe $EVT_{pf}$, we adapt a formulation used in Zhong et al.
-(2017) to describe the index used by the algorithms in a more generally.
-Write the index $B_i(t+1)$ of arm $i$ at round $t$ as
-
-$$
-B_i(t+1) = S_i(t) D_i(t),
-$$
-
-where $D_i(t)$ is some measure of the distance between the mean $\mu_i$ or the distribution $\nu_i$ of arm $i$ from the threshold $\tau$, while $S_i(t)$ is some confidence value measuring how confident we can be in $D_i(t)$.
-Thus, for the APT algorithm, if we let $\epsilon = 0$ as in Zhong et al.
-(2016), we have
-
-$$
-D_i^{APT}(t) = \hat{\Delta}_i(t) = |\hat{\mu}_i(t) - \tau| \quad \text{and} \quad S_i^{APT}(t) = \sqrt{T_i(t)}.
-$$
-
-We see that $D_i(t)$ is the probably most straightforward distance between the sample mean and the threshold, while $S_i(t)$ increases over time, as we become more confident in our sample mean, and thus ensures that we do not pull the same arm forever.
-Based on this, we can now easily compare APT to EVT$_{pf}$ for which the index can be written as:
-
-$$
-D_i^{EVT_{pf}}(t) = \sqrt{\hat{\sigma}^2_{i}(t) + \hat{\Delta}_i(t)} - \hat{\sigma}_i(t) \quad \text{and} \quad S_i^{EVT_{pf}} = \sqrt{T_i(t)}
-$$
-
-We see that both algorithms employ the same confidence term.
-The empirical variance describes the shape of the distribution and thus is a measure of how far the distribution is away from the threshold.
-It consequently makes sense to have it appear in $D_i^{EVT}$.
-And in contrast to the APT algorithm, the EVT$_{pf}$ algorithm takes more information about the arms into account than just their mean.
-As mentioned previously, this should especially be valuable whenever arms have different variances.
-Roughly similar to how the Kullback-Leibler divergence measures distances between distributions, $D_i^{EVT}$ including the empirical variance serves as a crude measure of distance between threshold and distribution.
-We note that for a Bernoulli distributed random variable, $D_i^{EVT}$ is always decreasing as the mean approaches the threshold (compare figure 2).
-Similar should hold in general for bounded variables as the variance and the mean are linked by the distance of the mean to the bound of the support (in contrast to, for example, a normal distributed random variable where a change in the mean does not correspond to a change in the variance).
-This is important as the bounds of the EVT$_{pf}$ algorithm only hold for random variables bounded in $[0,1]$.
-Thus, it is limited to the same set of distributions as the AugUCB algorithm.
-
-```{r EVT_Index_Bernoulli, echo = FALSE, message = FALSE, warning = FALSE, fig.align = "center", out.width='80%', fig.cap = "This graph displays the distance part of the index of the APT, SLR, and EVT algorithms.
-While EVT's distance is based on both the empirical mean and empirical variance, the empirical mean determines the variance in the case of Bernoullis.
-We see that the distance of both EVT and SLR has an asymmetric behavior."}
-bfun <- function(mu, tau) sqrt((mu*(1-mu))^2 + abs(tau-mu)) - mu*(1-mu)
-KL_ber <- function(p,q) p*log(p/q) + (1-p)*log((1-p)/(1-q))
-KL_gauss <- function(p,q) 2*(p-q)^2
-
-evtdf <- data.frame(mu = seq(0.0000001,0.5,length.out = 10000),
-                    tau = rep(0.1, 10000)) %>%
-  mutate(APT = KL_gauss(mu, tau),
-         SLR = KL_ber(mu, tau),
-         EVT = bfun(mu, tau)) %>%
-  gather(key = Algorithm, value = Distance, -mu, -tau) %>%
-  mutate(tau = as.character(tau))
-
-ggplot(evtdf, aes(x = mu, y = Distance, 
-                  group = Algorithm, color = Algorithm,
-                  linetype = Algorithm)) +
-  geom_line() +
-  labs(#title = "Comparison of Distance Measures by Algorithm",
-       subtitle = "For Bernoulli arms and a threshold at 0.1.",
-       x = "Empirical Mean Estimate") +
-  theme_bw() +
-  theme(legend.position = "bottom")
-```
-
-By defining a new complexity measure $H^{\text{EVT}_{pf}}$ for the EVT$_{pf}$ algorithm, Zhong et al.
-(2017) are able to derive an upper bound on the expected loss of the algorithm.
-Let the complexity increase in the variance and decrease in the distance of the mean from the threshold such that
-
-$$
-H^{\text{EVT}_{pf}} = \sum_{i=1}^K h_i^{\text{EVT}_{pf}} = \sum_{i=1}^K (\sigma_i^2\Delta_i^{-2} + \Delta_i^{-1}).
-$$
-
-Then one can state the following theorem with notation as in \autoref{sec:Setup}.
-
-\begin{theorem}[Theorem 5, Zhong et al., 2017] 
-\label{theorem:ZhongEtAl2017Theorem5}
-Let $K > 0$, $T > 2K$, and consider a thresholding bandit problem. Assume that all arms of the problem are bounded in $[0,1]$. Then the probability of an error is bounded as
-
-\begin{equation*}
-\mathbb{E}[\mathcal{L}[T]] \leq TK \exp\Big(-C\frac{T}{H^{\text{EVT}_{pf}}}\Big),
-\end{equation*}
-
-where $C$ is some positive constant.
-\end{theorem}
-
-The authors approach the proof very similar as Locatelli et al.
-(2016) in the proof of their lower bound.
-They define favorable events that hold with large probability, and ensure that the same separation condition as in Locatelli et al.
-holds given that each arm is pulled sufficiently often.
-Additionally to a favorable event that bounds the deviation between sample mean and population mean, they define a second event on which the sample standard deviation is close to the population standard deviation.
-This is bounded in large probability by an empirical Bernstein inequality (Maurer and Pontil, 2009).
-The union of the two events then serves as the favorable event in the remainder of their proof.
-
-Given a lower bound adapted to the new complexity $H^{\text{EVT}_{pf}}$, Zhong et al.
-(2017) show that the EVT$_{pf}$ algorithm is optimal in that its upper bound matches the lower bound.
-Furthermore, they compare their algorithm in experiments against the APT algorithm.
-The experiments use data generated from uniform distributions.
-Each experiment compares 100 arms with variances picked at random from a range of possible variances.
-Over three experiments, the range of variances is varied from small to large.
-They report the largest advantage of their variance based algorithms in comparison to APT when the variances are very small; given they only consider problems bounded on a support of $[0,1]$, $\sigma_i \ll 1$.
-In this case the problem complexity $H^{\text{EVT}_{pf}}$ can be much smaller than $H^{APT}$ -- the EVT$_{pf}$ algorithm profits more from distributions that are simple to estimate in terms of their variance than the APT algorithm does.
-
-When comparing the two complexities for Bernoulli random variables against a threshold, we see that the smaller complexity of the EVT$_{pf}$ algorithm implies in particular that EVT$_{pf}$ could be able to cope with distributions of parameter $\mu$ close to $\tau$ much better than APT (compare Figure 3).
-
-```{r Hevt_Hapt_Comparison, echo = FALSE, message = FALSE, fig.align="center", out.width = '70%', fig.cap = "Comparing the complexity terms used in the APT, AugUCB, and EVT algorithms, we observe that the problem complexity of the EVT algorithm increases much less rapidly than for the other algorithms.
-Thus, the EVT should be able to cope with arms close to the threshold better than the APT algorithm.
-The complexity displayed for the AugUCB is an upper bound on the complexity used in the upper bound of Mukherjee et al.
-(2017)."}
-hevt <- function(mu, tau) {
-  (mu*(1-mu))^2 * (abs(mu-tau))^{-2} + abs(mu-tau)^{-1}
-}
-
-hapt <- function(mu, tau) {
-  abs(mu-tau)^{-2}
-}
-
-haugucb <- function(mu, tau) {
-  vars <- mu*(1-mu)
-  (sqrt(vars) + sqrt(vars + (16/3)*(abs(mu-tau))))/(abs(mu-tau)^2)
-}
-
-hcompdf <- data.frame(mu = seq(0.1,0.9,length.out = 10000),
-                      tau = rep(0.5, 10000)) %>%
-  mutate(APT = hapt(mu, tau),
-         EVT = hevt(mu, tau),
-         AugUCB = haugucb(mu, tau)) %>%
-  gather(key = Algorithm, value = Complexity, -mu, -tau)
-
-ggplot(hcompdf, aes(x = mu, y = Complexity, group = Algorithm,
-                    color = Algorithm, linetype = Algorithm)) +
-  geom_line() +
-  geom_vline(aes(xintercept = 0.5), linetype = 2) +
-  ylim(c(0,400)) +
-  theme_bw() +
-  theme(legend.position = "bottom") +
-  labs(x = "Mean", title = "Comparison of Complexity Terms",
-       subtitle = "Complexity of single Bernoulli arm for APT and EVT and a threshold at 0.5.")
-```
-
-## Likelihood Ratio for Sequential Sampling \label{sec:LikelihoodRatioForExponentialFamily}
-
-We now present a new sequential sampling algorithm for the fixed budget thresholding bandit problem that builds on the idea of the likelihood ratio statistic for hypothesis tests.
-We first describe the general idea of likelihood ratio based tests shortly, to then introduce the new algorithm for the thresholding bandit problem, which we call Simple Likelihood Ratio (SLR) algorithm.
-
-### Likelihood Ratio-based Hypothesis Tests \label{sec:LRTests}
-
-In a standard parametric testing problem, we have an i.i.d.
-sample $\bm{x} = (x_1, ..., x_T)$, where each $x_s$ is a realization from the random variable $X$.
-We assume that $X$ follows some probability distribution $Q(\theta)$ paramaterized by a vector $\theta$.
-Let $q(x;\theta)$ be the density function corresponding to the distribution.
-We would like to test whether an alternative parameterization is more likely than the parameterization given by the null hypothesis.
-That is, we test
-
-$$
-H_0: \quad \theta = \theta_{H_0} \qquad \text{vs.} \qquad H_1: \quad \theta = \theta_{H_1}
-$$
-
-In order to assess whether the $H_0$ hypothesis can be rejected, we compute the likelihood $L(x|\theta)$ of the observed sample under both parameterizations: $L_{H_0} = L(x|\theta = \theta_{H_0}) = \prod_{s=1}^T q(x_s|\theta_{H_0})$ and $L_{H_1} = L(x|\theta = \theta_{H_1}) = \prod_{s=1}^T q(x_s|\theta_{H_1})$.
-The likelihood ratio test statistic is then given as
-
-$$
-LR_T(\theta_{H_0}|| \theta_{H_1}) = \frac{L_{H_0}}{L_{H_1}} = \prod_{s=1}^T\frac{q(x_s|\theta_{H_0})}{ q(x_s|\theta_{H_1})}.
-$$
-
-and is used in the optimal test of two hypotheses as shown by the Neyman-Pearson lemma (see chapter 11, Theorem 11.7.1 in Cover and Thomas, 2006).
-
-The intuition behind the test is that, if the true parameterization is $H_1$ and not $H_0$, then the likelihood $L_{T,H_1}$ should be larger than $L_{T,H_0}$.
-A small enough likelihood ratio would thus lead us to a rejection of the null hypothesis, while a large likelihood ratio is evidence in favor of it.
-
-Furthermore, the likelihood ratio is inherently linked to information theoretic quantities and divergence measures.
-Assuming that $Q$ is a discrete distribution with support $\chi$, one can write the negative log-likelihood ratio as (compare Cover and Thomas, 2006)
-
-\begin{align*}
--\log(LR_T(\theta_{H_0}|| \theta_{H_1}) & = \sum_{i=1}^T \log(\frac{q(x_s|\theta_{H_0})}{ q(x_s|\theta_{H_1})}) \\
-& = \sum_{a \in \chi} T q(a|\hat{\theta}) \log(\frac{q(a|\theta_{H_0})}{ q(a|\theta_{H_1})}) \\
-& = \sum_{a \in \chi} T q(a|\hat{\theta}) \log(\frac{q(a|\theta_{H_0})}{ q(a|\theta_{H_1})}\frac{q(a|\hat{\theta})}{ q(a|\hat{\theta})}) \\
-& = T \KL(q(\hat{\theta})||q(\theta_{H_0})) - T \KL(q(\hat{\theta})||q(\theta_{H_1})),
-\end{align*}
-
-where $\hat{\theta}$ is the maximum likelihood estimate of the parameter $\theta$ given the sample $\bm{x}$.
-If we hold the $H_0$ hypothesis fixed and set $\theta_{H_1} = \hat{\theta}$, then with $\KL(Q(\hat{\theta})||Q(\hat{\theta})) = 0$:
-
-$$
--\log(LR_T(\theta_{H_0}|| \theta_{H_1})) = -\log(LR_T(\theta_{H_0}|| \hat{\theta})) = T\KL(Q(\hat{\theta}||Q(\theta_{H_0}))
-$$
-
-Furthermore, we have for any distributions $Q_{H_0}$ and $Q_{H_1}$ for a sample $\bm{x}$ sampled from the $H_0$ distribution, that
-
-$$
-\frac{1}{T} \log(LR_T(\theta_{H_0}||\theta_{H_1})) \rightarrow \KL(Q(\theta_{H_0})||Q(\theta_{H_1})) \quad \text{in probability},
-$$
-
-by the law of large numbers (or asymptotic equipartition property) for the Kullback-Leibler divergence as in Theorem 11.8.1 in Cover and Thomas (2006).
-Lastly, based on the characteristics shown before, for frequentist tests the Kullback-Leibler divergence between $Q(\theta_{H_0})$ and $Q(\theta_{H_1})$ gives the best possible exponent for the error of the second type given a fixed error of the first type.
-This is the result of the Chernoff-Stein Lemma (Theorem 11.8.3, Cover and Thomas, 2006), which is reminiscient of the complexity $\kappa_B$ derived by Kaufmann et al.
-(2016) and as described in \autoref{chap:KullbackLeiblerPureExploration}:
-
-\begin{theorem}[Chernoff-Stein Lemma] \label{theorem:ChernoffStein}
-Let $X_1, X_2, ..., X_n$ be i.i.d.
-distributed according to $Q$.
-Consider the hypothesis test between two alternatives, $Q=P_1$ and $Q=P_2$, where $\KL(P_1||P_2) < \infty$.
-Let $A_n \subseteq \chi^n$ be an acceptance region for hypothesis $H_1$.
-Let the probabilities of error be $\alpha_n = P_1^n(A_n^C)$, and $\beta_n = P_2^n(A_n)$, and for $0< \epsilon <1/2$, define $\beta_n^{\epsilon} = \min_{A_n \subseteq \chi^n, \alpha_n < \epsilon} \beta_n$.
-Then
-
-$$
-\text{lim}_{n\rightarrow \infty} \frac{1}{n} \log \beta_n^{\epsilon} = - \KL(P_1||P_2)
-$$
-\end{theorem}
-
-Indeed, our Corollary \autoref{corollary:LB1TBP} for the one-armed thresholding bandit problem corresponds directly to this result, and shows that the thresholding bandit can be viewed as a sequential testing of separate hypotheses.
-
-### Likelihood Ratio as Index in Sequential Sampling
-
-We now employ the concept of the likelihood-ratio test to a new sequential sampling strategy for the thresholding bandit problem.
-In contrast to the cumulative regret problem or the best arm identification problem, the thresholding bandit problem offers a natural $H_0$ hypothesis for the arms' distributions: the threshold $\tau$.
-Given that we want to classify the arms against the threshold, and given that $\tau$ is known and fixed, we can set a null hypothesis that is a function of $\tau$.
-In the simplest case, the distributions are parameterized by their mean $\theta_i = \mu_i$, and we set $\theta_{i,H_0} = \tau$ for all arms.
-The likelihood ratio then quantifies how "significant" of a difference there is between the threshold $\tau$ and the current sample mean $\hat{\mu}_i(t)$ of an arm, assuming distributions for which the maximum likelihood estimate of the mean is given by the empirical mean.
-The likelihood ratio will be smaller than 1 and decrease in sample size even if the threshold and sample mean are constant.
-
-These characteristics make the likelihood ratio a natural index for adaptive sampling strategies (compare also Chernoff, 1958; Garivier and Kaufmann, 2016).
-Consider the setting described in \autoref{sec:Setup} and \autoref{sec:TheAPTAlgorithm}, and write as index:
-
-$$
-B_i^{LR}(t+1) = LR(\tau|| \hat{\mu}_i(t)) = \prod_{i=1}^T\frac{q(x_i|\tau)}{ q(x_i|\hat{\mu}_i(t))}.
-$$
-
-We have $B_i^{LR}(t) \leq 1$, $t \uparrow \rightarrow B_i^{LR}(t) \downarrow$, and $|\hat{\mu}_i(t) - \tau| \uparrow \rightarrow B_i^{LR}(t) \downarrow$.
-Consequently, by choosing the arm that maximizes $B_i^{LR}(t)$, we choose an arm for which we either have not collected many samples, or for which the sample mean is close to the threshold $\tau$.
-In this sense, a strategy based on the likelihood ratio is reminiscient of the index employed by the APT algorithm.
-Indeed, assuming the samples are normally distributed with equal variance for all arms under both $H_0$ and $H_1$, $-\log(B_i^{LR}(t))$ equals the index in APT.
-Why then would we prefer the likelihood based strategy?
-
-Given that the APT index and the likelihood-ratio based index are only equivalent for normally distributed arms with equal variances, the new strategy promises efficiency improvements whenever the true distribution is known and different from the normal distribution.
-The most important example are Bernoulli arms with small means as motivated above.
-While the likelihood ratio can in theory be used for any distributions, and arms could even have different classes of distributions, the class of distribution has to be known upfront for every arm.
-Given the role of the threshold $\tau$ and the goal of classification of the mean against $\tau$, the likelihood ratio strategy is most naturally employed on distributions parameterized by their mean.
-In the following descriptions, we thus focus on one-parameter distributions of the exponential family.
-Additionally, we also propose a version for the Normal distribution with unknown mean.
-Before we describe the algorithm, we show that the likelihood ratio has a convenient form for this distribution family.
-
-### Likelihood Ratio for One-Parameter Exponential Family of Distributions \label{sec:LRforUnivariateExponentialFamily}
-
-We now focus on a thresholding bandit problem where the arms are distributed according to $\nu_{\theta_1}, ..., \nu_{\theta_K}$, which are all from the same canonical exponential family of distributions with scalar parameter $\theta_i \in \Theta$.
-The probability density function of the absolutely continuous distribution $\nu_{\theta_i}$ with regard to a dominating measure $\rho$ on $\mathbb{R}$ is given by $q(x|\theta) = h(x) \exp(T(x)\theta - b(\theta))$.
-As described in Cappé et al.
-(2013), citing Lehmann and Casella (1998), the derivative $b'(\theta)$ of $b(\theta)$ is an increasing continuous function such that the expected value $\mathbb{E}(\nu_{\theta}) = b'(\theta)$ for all $\theta \in \Theta$.
-Given that $b'(x)$ is strictly convex, we have a one-to-one relation between $b'(\theta)$ and $\mathbb{E}(\nu_{\theta})$ through the continuous inverse $b'^{-1}(\theta)$.
-Consequently, one can just as well parameterize the distribution by its mean $\mu = \mathbb{\nu_{\theta}}$ and write $\nu_{b'^{-1}(\mu)}$ with the probability density function (compare Cappé et al., 2013)
-
-$$
-q(x|b'^{-1}(\mu)) = h(x) \exp(S(x) b'^{-1}(\mu) - b(b'^{-1}(\mu))).
-$$
-
-This lets us write the likelihood ratio for the exponential family distributions as
-
-$$
-LR_T(b'^{-1}(\mu_0)||b'^{-1}(\mu_1)) = \prod_{s=1}^T \frac{\exp(S(x_s) b'^{-1}(\mu_0) - b(b'^{-1}(\mu_0)))}{\exp(S(x_s) b'^{-1}(\mu_1) - b(b'^{-1}(\mu_1)))}
-$$
-
-or if we write it as negative log-likelihood ratio:
-
-$$
--\log(LR_T) = T\Big(b\big(b'^{-1}(\mu_0)) - b(b'^{-1}(\mu_1)\big)\Big) - \Big(b'^{-1}(\mu_0)-b'^{-1}(\mu_1)\Big)\sum_{i=1}^nS(x_i)
-$$
-
-As we will see now, the last equation takes a convenient form for many common distributions.
-
-**Example 1: Bernoulli Distribution**
-
-We have $S(x_s) = x_s$, $\theta = \log(\mu/(1-\mu))$, $\Theta = (0,1)$, $b(\theta) = \log(1+\exp(\theta))$, and $\mu \in (0,1)$. Then $b'(\theta) = \mu$, and we can write
-
-\begin{align*}
--\log(LR_T(\mu_0||\mu_1)) & = T(\log\Big(\frac{1-\mu_0}{1-\mu_1}\Big)) - \Big(\log(\frac{\mu_0}{1-\mu_0}) - \log(\frac{\mu_1}{1-\mu_1})\Big)\sum_{s=1}^{T}x_i \\
-& = n \Big( (1-\hat{\mu})\log\Big(\frac{1-\mu_1}{1-\mu_0}\Big) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}) \Big)
-\end{align*}
-
-We observe that, if we let $\mu_0 = \tau$ and $\mu_1 = \hat{\mu}$ (compare \autoref{sec:LRTests}), then
-
-$$
--\log(LR_T(\tau||\hat{\mu})) = T\KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) =  = T \KL(\hat{\mu}||\tau) = n \Big(\hat{\mu}\log\big(\frac{\hat{\mu}}{\tau}\big) + (1-\hat{\mu})\log\big(\frac{1-\hat{\mu}}{1-\tau}\big)\Big)
-$$
-
-**Example 2: Poisson Distribution**
-
-We have $S(x_s) = x_s$, $\theta = \log(\mu)$, $\Theta = \mathbb{R}$, $b(\theta) = \exp(\theta)$, and $\mu \in (0, +\infty)$. Then $b'(\theta) = \mu$, and we can write:
-
-$$
--\log(LR_T(\mu_0||\mu_1)) = T(\mu_0 - \mu_1) - (\log(\mu_0) - \log(\mu_1))\sum_{s=1}^T x_s = T\Big((\mu_0 - \mu_1) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}\Big)\Big)
-$$
-
-We observe that, if we let $\mu_0 = \tau$ and $\mu_1 = \hat{\mu}$ (compare \autoref{sec:LRTests}), then
-
-$$
--\log(LR_T(\tau||\hat{\mu})) = T \KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = T \KL(\hat{\mu}||\tau) = T\Big((\tau - \hat{\mu}) + \hat{\mu}\log\Big(\frac{\hat{\mu}}{\tau}\Big)\Big)
-$$
-
-**Example 3: Normal distributions with known variance $\sigma^2$**
-
-We have $S(x_s) = x_s$, $\theta = \mu/\sigma^2$, $\Theta = \mathbb{R}$, $b(\theta) = \sigma^2\theta^2/2$, $\mu \in \mathbb{R}$. Then $b'(\theta) = \mu$, and we can write
-
-$$
--\log(LR_T(\mu_0||\mu_1)) = T (\frac{\mu_0^2}{2\sigma^2} - \frac{\mu_1^2}{2\sigma^2}) - (\frac{\mu_0}{\sigma^2} - \frac{\mu_1}{\sigma^2})\sum_{s=1}^Tx_s = T\frac{1}{2\sigma^2}\Big(\mu_0^2-\mu_1^2 - 2\mu_0\hat{\mu} + 2\mu_1\hat{\mu}\Big)
-$$
-
-And again, even though the distribution is continuous (compare \autoref{sec:LRTests}), if we let $\mu_1 = \hat{\mu}$ and $\mu_0 = \tau$, then
-
-$$
--\log(LR_T(\tau||\hat{\mu})) = T\KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = T \KL(\hat{\mu}||\tau) = T\frac{(\hat{\mu} - \tau)^2}{2\sigma^2}.
-$$
-
-**Example 4: Gamma distributions with known shape parameter $\alpha$**
-
-We have $S(x_s) = x_s$, $\theta = -\alpha/\mu$, $\Theta = (-\infty, 0)$, $b(\theta) = -\alpha \log(-\theta)$, $\mu \in (0,+\infty)$. Then $b'(\theta) = -\mu$, and we can write
-
-$$
--\log(LR_T(\mu_0||\mu_1)) = T\alpha(-\log(\frac{\alpha}{\mu_0}) - \log(\frac{\mu_1}{\alpha})) - (-\frac{\alpha}{\mu_0} + \frac{\alpha}{\mu_1})\sum_{s=1}^{T}x_s = T\alpha \Big(\log\big(\frac{\mu_0}{\mu_1}\big) - \frac{\hat{\mu}}{\mu_1} + \frac{\hat{\mu}}{\mu_0}\Big).
-$$
-
-And again, even though the distribution is continuous (compare \autoref{sec:LRTests}), if we let $\mu_1 = \hat{\mu}$ and $\mu_0 = \tau$, then
-
-$$
--\log(LR_T(\tau||\hat{\mu})) = T \KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = T \KL(\hat{\mu}||\tau) = T\alpha \Big(\frac{\hat{\mu}}{\tau} - 1 - \log\big(\frac{\hat{\mu}}{\tau}\big)\Big).
-$$
-
-For $\alpha = 1$, the Gamma distribution is equal to the Exponential distribution.
-
-Given these results for the exponential family of distributions, we can now define the Simple Likelihood Ratio algorithm.
-
-## 1D-Simple Likelihood Ratio Algorithm \label{sec:1DSLR}
-
-We now define the Simple Likelihood Ratio Algorithm for the one-parameter exponential family of distributions (1D-SLR).
-Consider again the setting in \autoref{sec:Setup} though without the assumption of $R$-sub-Gaussian distributions.
-Instead, assume that the distributions $\nu_i$ of arms $i \in \mathbb{A}$ are all the same distribution from the one-parameter exponential family of distributions.
-We write this class of distributions as $\nu(\mu, \theta)$.
-While $\mu$ is the unknown mean parameter, $\theta$ describes potentially *known* parameters, as for example $\sigma_1, ..., \sigma_K$ for Normal distributions, or $\alpha_1, ..., \alpha_K$ for Gamma distributions.
-Additionally to $\nu(\mu, \theta)$, the 1D-SLR algorithm receives as input the definition of the problem $(\tau, \epsilon)$.
-As initialization, the algorithm pulls each arm once.
-At time $t>K$, the algorithm updates the number of pulls for arm $i$ at time $t$, $T_i(t)$, for each arm, as well as the empirical mean $\hat{\mu}_i(t)$ of arm $i$ after $T_i(t)$ pulls.
-The empirical mean is calculated for each arm $k\in \{1,...,K\}$ as $\hat{\mu}_i(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)} x_{i,s}$, with $T_i(t) = \sum_{s=1}^{t}\mathbb{I}(I_s = i)$.
-It serves as maximum likelihood estimate of the arm's mean.
-As in Locatelli et al.
-(2016), $X_{i,s}$ is the sample received when pulling arm $i$ for the $s$-th time.
-Depending on the distribution, the algorithm then computes the index
-
-\begin{align*}
-B_i^{SLR}(t+1) & = \mathbb{I}(\hat{\mu}_i(t)\geq \tau) \Big(-\log \big(LR_{T_i(t)}(\tau-\epsilon||\hat{\mu}_i(t))\big)\Big) \\
-& \quad +\: \mathbb{I}(\hat{\mu}_i(t) <\tau) \Big(-\log\big(LR_{T_i(t)}(\tau+\epsilon||\hat{\mu}_i(t))\big)\Big) \\
-& = T_i(t) \Big( \mathbb{I}(\hat{\mu}_i(t) \geq \tau)\cdot \KL(\hat{\mu}_i(t)||\tau+\epsilon) \\
-& \quad \quad \quad +\: \mathbb{I}(\hat{\mu}_i(t) < \tau)\cdot \KL(\hat{\mu}_i(t)||\tau+\epsilon) \Big) \Alignyesnumber\label{eqn:SLRIndex}.
-\end{align*}
-
-The next arm to be pulled is the minimizer of the index $B_i^{SLR}(t+1)$, $I_{t+1} = \arg \min_{i\leq K} B_i(t+1)$.
-At the end of the horizon $T$, the algorithm outputs the set of arms $\hat{S}_\tau = \{i \in \mathbb{A},  \hat{\mu}_i(T) \geq \tau\}$.
-
-\IncMargin{1em}
-\begin{algorithm}
-\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
-\Input{$\tau$, $\epsilon$, class of distributions $\nu(\mu, \theta)$, $\theta_i \: \forall i \in \mathbb{A}$}
-\Output{$\hat{S}_\tau = \{i \in \mathbb{A},  \hat{\mu}_i(T) \geq \tau\}$}
-\BlankLine
-\emph{Pull each arm once}\;
-\For{$t = K+1$ \KwTo $T$}{
-  \emph{Pull arm $I_t = \arg \min_{i\leq K} B_i^{SLR}(t)$ as in \autoref{eqn:SLRIndex}}\;
-  \emph{Observe reward $X_t \sim \nu_{I_t}$}\;
-}
-\caption{SLR algorithm for one-parameter exponential family of distributions.}\label{algo_slr_1d}
-\end{algorithm}\DecMargin{1em}
-
-## 2D-SLR Algorithm for Normal Distributions
-
-As soon as we move away from one-parameter distributions parameterized by their mean, it becomes less clear how the likelihood ratio for $H_0: \mu = \tau$ and $H_1: \mu = \hat{\mu}$ should be calculated.
-In the case of Normal distributions with unknown mean and unknown variance, given that the variance and mean estimate are linked, we can use
-$$
-H_0: \mu_0 = \tau \land \sigma_0^2 = \sigma^2_{\tau} = \frac{1}{n}\sum_{i=1}^{n}(x_i-\tau)^2 \quad \text{vs.} \quad H_1: \mu_1 = \hat{\mu} \land \sigma_1^2 = \hat{\sigma}^2 = \frac{1}{n}\sum_{i=1}^{n}(x_i-\hat{\mu})^2
-$$
-
-In the following, we assume $\epsilon = 0$ for simplicity.
-At each round $t$, the algorithm computes $T_i(t)$ and $\hat{\mu}_i(t)$ as before, and additionally the empirical variances $\sigma_{\tau,i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\tau)^2$ and $\hat{\sigma}_{i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\hat{\mu})^2$, where $\hat{\sigma}_{i}^2(t) < \sigma_{\tau,i}^2(t)$ if $\hat{\mu} \neq \tau$ since $\hat{\mu}$ is the maximum likelihood estimate.
-The index is then
-
-\begin{align*}
-B_i^{2DSLR}(t+1) & = -\log\big(LR_T(\tau, \sigma_{\tau,i}^2(t)||\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t))\big) \\
-& = T_i(t) \log\Big(\frac{\sigma_{\tau,i}^2(t)}{\hat{\sigma}_i^2(t)}\Big) \\
-& = T_i(t) \KL\big(N(\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t))||N(\tau, \sigma_{\tau,i}^2(t))\big) \Alignyesnumber\label{eqn:SLR2DIndex}
-\end{align*}
-
-The next arm to be pulled is the minimizer of the index $B_i^{2DSLR}(t+1)$, $I_{t+1} = \arg \min_{i \leq K} B_i(t+1)$.
-At the end of the horizon $T$, the algorithm outputs the set of arms $\hat{S}_\tau = \{i \in \mathbb{A}, \hat{\mu}_i(T) \geq \tau\}$.
-
-\IncMargin{1em}
-\begin{algorithm}
-\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
-\Input{\emph{$\tau$, $\epsilon$, $\nu(\mu, \theta) = \mathcal{N}(\mu,\sigma^2) \, \forall i \in \mathbb{A}$, where $\mu$ and $\sigma^2$ are unknown}}
-\Output{$\hat{S}_\tau = \{i \in \mathbb{A},  \hat{\mu}_i(T) \geq \tau\}$}
-\BlankLine
-\emph{Pull each arm twice}\;
-\For{$t = 2K+1$ \KwTo $T$}{
-\For{$i = 1$ \KwTo $K$}{
-  \emph{Compute $\hat{\sigma}^2_{i}(t)$}\;
-  \If{$\hat{\sigma}^2_{i}(t) = 0$}{\emph{Set $\hat{\sigma}^2_{i}(t) = 1/T$}}
-}
-  \emph{Pull arm $I_t = \arg \min_{i\leq K} B_i^{SLR_{2D}}(t)$ as in \autoref{eqn:SLR2DIndex}}\;
-  \emph{Observe reward $X_t \sim \nu_{I_t}$}\;
-}
-\caption{2D-SLR algorithm for Normal distributions with unknown mean and variance.}\label{algo_slr_2d}
-\end{algorithm}\DecMargin{1em}
-
-## Discussion
-
-At the beginning of this thesis, we set out to find an algorithm that improves upon the Anytime Parameter Free algorithm introduced in Locatelli et al.
-(2016) for the thresholding bandit problem.
-We aimed to make the algorithm perform better in problems with arms that are not well approximated as sub-Gaussian; in particular a problem with Bernoulli arms of small means, and with a threshold close to 0.
-We thus tried to find a strategy that takes more information about the arms into account than only the sample mean.
-With the Simple Likelihood Ratio strategy, we propose an algorithm that fulfills this goal at the cost of being distribution specific.
-
-The SLR strategy requires the knowledge of the class of distribution upfront, just as other algorithms require parameters.
-While this is likely to be a negligiable problem in the case of $\{0,1\}$ observations whose mean can be modeled reasonably by Bernoulli distributions, it can be more difficult to know the true class of distributions upfront when $\nu_i$ are continuous distributions.
-We have shown however, that the SLR strategy can be adapted to all one-parameter distributions in the exponential family of distributions.
-The algorithm even offers a natural adaptation to the problem of normal distributions with unknown mean and unknown variance.
-
-Furthermore, the SLR strategy reduces to the APT strategy in the case where arms are normally distributed with known, equal variances. In this case we have as index (compare example 3 above): 
-$$
-B_i^{SLR}(t) = T_i(t)\frac{(\hat{\mu}_i(t) - \tau)^2}{2\sigma^2}.
-$$
-In order to decide at time $t$ which arm to draw next, we necessarily compare the indexes of arm $i$ and arm $j$. Assume w.l.o.g. that $B_i^{SLR}(t) < B_j^{SLR}(t)$. Then:
-
-\begin{align*}
-B_i^{SLR}(t) < B_j^{SLR}(t) & \Leftrightarrow 
-T_i(t)\frac{(\hat{\mu}_i(t) - \tau)^2}{2\sigma^2} < T_j(t)\frac{(\hat{\mu}_j(t) - \tau)^2}{2\sigma^2} \Alignyesnumber\label{eqn:SLRWithKnownVar}\\
-& \Leftrightarrow 
-\sqrt{T_i(t)}\sqrt{(\hat{\mu}_i(t) - \tau)^2} < \sqrt{T_j(t)}\sqrt{(\hat{\mu}_j(t) - \tau)^2} \\
-& \Leftrightarrow 
-B_i^{APT}(t) < B_j^{APT}(t)
-\end{align*}
-
-Thus, SLR achieves the same upper bound as APT on this problem.
-Given that in all other cases the SLR is able to take more information about the distributions into account through the Kullback-Leibler divergence (in the case of the exponential family of distributions), the algorithm is expected to improve upon the APT strategy.
-
-As mentioned before, this improvement comes only at the cost of knowing the correct distribution upfront.
-In particular, as for the APT algorithm, there are no parameters which need to be tuned upfront as is often the case for upper-confidence bound based algorithms (see for example UCB-E in Audibert et al., 2010).
-
-Additionally, the index used in the SLR algorithm offers the same interpretation considered in \autoref{sec:EVTAlgorithm}. Write the index again as
-$$
-B_i^{SLR}(t) = S_i^{SLR}(t) D_i^{SLR}(t),
-$$
-where $S_i^{SLR}(t)$ is the confidence term and $D_i^{SLR}(t)$ is the measure of distance between the distribution of arm $i$ and the threshold $\tau$.
-The index of the Simple Likelihood Ratio strategy for one-parameter exponential family distributions can then be written with
-$$
-S_i^{SLR}(t) = T_i(t) \quad \text{and} \quad
-D_i^{SLR}(t) = \KL(\hat{\mu}_i(t)||\tau),
-$$
-where we employ the number of pulls so far for a given arm as the confidence measure, while the Kullback-Leibler divergence fulfills its role as distance measure between distributions (see also Figure 2).
-The larger the Kullback-Leibler divergence, the less inclined we are to draw the arm; the same holds, if we have pulled an arm many times.
-Since the KL-divergence reduces to the squared distance between means for Normal distributions of known variance, the SLR and APT algorithms are identical in this case.
-
-As we see in the experiments that follow, the SLR strategy is able to improve significantly upon the APT strategy in many cases.
-
-\newpage
-
 # Experiments \label{chap:Experiments}
@@
 See \autoref{sec:AppendixBUCB} in the appendix for how we adapt the Bayes-UCB algorithm to the thresholding bandit problem.
-
-## Synthetic Data \label{sec:SyntheticData}
-
-Each of the following five simulations is repeated for 5000 iterations.
-Depending on the simulation, the observations are generated randomly by a given exponential family of distributions.
-As we are primarily concerned with improving upon APT with respect to non-sub-Gaussian distributions, the first three simulations focus on Bernoulli distributions, especially those with small means.
-We then go on to show with experiments on data from the Exponential distribution and Poisson distribution that the SLR strategy can be adapted to other distributions as well.
-
-### Simulation 1: Bernoulli Arms and $\tau = 0.5$
-
-The first experiment is equal to experiment 3 in Locatelli et al.
-(2016) to achieve a baseline comparison.
-We compare ten Bernoulli arms that move away from the threshold at $\tau = 0.5$ geometrically with $\mu_{1:4} = 0.4-0.2^{1:4}$, $\mu_5 = 0.45$, $\mu_6 = 0.55$, and $\mu_{7:10} = 0.6 + 0.2^{5-1:4}$.
-We run the standard APT algorithm as well as the SLR algorithm with $\epsilon = 0.1$.
-We compare them to the AugUCB algorithm with the parameter choice of $\rho = 1/3$ as used by its authors in Mukherjee et al.
-(2017).
-We run the parameter-free EVT$_{pf}$ algorithm without feedback delay, thus making it directly comparable to the other algorithms.
-The Bayes-UCB algorithm is run with $c=1$ and takes as prior a Beta distribution with parameters $\alpha_0 = \tau$ and $\beta_0 = 1 - \tau$, thus leading to a mean of the prior distribution at $\frac{\alpha_0}{\alpha_0+\beta_0}=\tau$ while keeping the prior as weak as possible.
-Lastly, we run the uniform sampling strategy as a benchmark.
-
-```{r loc2_data_summary, echo = FALSE, message = FALSE}
-get_apt_complexity <- function(x, tau, epsilon) {
-  gaps <- abs(x-tau)+epsilon
-  sum(1/gaps^2)
-}
-
-mean_loc2 <- c(0.4-0.2^(1:4),
-               0.45, 0.55,
-               0.6+0.2^(5-(1:4)))
-
-H_loc2 <- get_apt_complexity(mean_loc2, 0.5, 0.1)
-
-knitr::kable(t(mean_loc2), digits = 3, col.names = paste0("V", 1:10), caption = "Mean of arms in simulation 1.")
-```
-
-This first experiment is a problem in which all algorithms should be able to perform well.
-The problem is not very difficult with $H_1^{APT} \approx$ `r round(H_loc2)`, and due to $\tau = 0.5$, the Bernoulli distribution can be well approximated by a Gaussian.
-This is the perfect environment for the APT algorithm.
-
-As the next figure shows, essentially all methods converge rapidly to an error rate of very close to zero, where the error rate is the share of the 5000 simulations on which the classification of the algorithm is wrong.
-Only the uniform strategy that clearly lacks behind.
-We also observe that the variance based algorithms (AugUCB and EVT) lag behind at first.
-AugUCB is able to adjust its sampling scheme only after 1000 iterations but then rapdily improves to the level of APT.
-EVT takes about 250 samples more to start a quick descend to the performance of the other algorithms.
-All of this, however, happens after the algorithms are below an error rate of 0.01.
-While the SLR algorithm improves upon APT, the improvement is a slight one, and not very large in terms of budget difference.
-This underlines that the scenario at hand is ideal for the APT algorithm.
-
-```{r simulation1_results, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for simulation 1."}
-library(ggplot2)
-current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
-
-load(paste0(current_path, "loc2_comp_BUCB_horizon_4000.Rda"))
-load(paste0(current_path, "loc2_comp_APT_2000.Rda"))
-load(paste0(current_path, "loc2_comp_LR_2000.Rda"))
-load(paste0(current_path, "loc2_comp_AugUCB_2000.Rda"))
-load(paste0(current_path, "loc2_comp_UNIFORM_2000.Rda"))
-load(paste0(current_path, "loc2_comp_EVT.Rda"))
-
-alg_names <- c(rep(c("Uniform", "APT", "AugUCB","SLR"), 
-                   each = 1991), rep("B-UCB", 3991), rep("EVT", 1981))
-index <- c(rep(10:2000, times = 4), 10:4000, 20:2000)
-alg_res <- (c(loc2_comp_UNIFORM_2000, loc2_comp_APT_2000, 
-                 loc2_comp_AugUCB_2000, loc2_comp_LR_2000,
-                 loc2_comp_BUCB_horizon_4000, loc2_comp_EVT))
-loc2_comp_res <- data.frame(index = index, names = alg_names, 
-                            results = alg_res)
-ggplot(loc2_comp_res, aes(x = index, y = results)) + 
-  geom_line(aes(group = names, color = names)) +
-  #geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
-  labs(#subtitle = "Dashed Line indicates Error = 0.1.",
-       y = "Error (log10 scale)", x = "Round Index") + 
-  coord_cartesian(xlim = c(0,2000)) +
-  scale_color_discrete(name = "Algorithm") + 
-  theme_bw() +
-  scale_y_log10() #+
-  #theme(legend.position = "bottom")
-
-```
-
-\newpage
-
-### Simulation 2: Bernoulli Arms and $\tau = 0.05$ \label{sec:Simulation2}
-
-```{r loc6nt_data_summary, echo = FALSE, message = FALSE}
-mean_loc6nt <- c(0.001, 0.005, 0.01, 0.015,
-                 0.04, 0.06,
-                 0.085, 0.09, 0.095, 0.099)
-
-H_loc6 <- get_apt_complexity(mean_loc6nt, 0.05, 0)
-
-knitr::kable(t(mean_loc6nt), digits = 3, col.names = paste0("V", 1:10), caption = "Mean of arms in simulation 2 classified against threshold of 0.05.")
-```
-
-In the second experiment, we compare the same algorithms as in the first experiment.
-Again, we classify 10 arms, but this time against a threshold of $\tau = 0.05$ and without an epsilon interval, $\epsilon = 0$ (which generally rewards algorithms for pulling arms close to the threshold).
-We choose the means of the arms to be much smaller too, and arrange them symmetrically around the threshold.
-While the distributions are bounded and thus still sub-Gaussian, the Normal approximation should be poor in comparison to the previous case.
-We expect an improvement for SLR compared to APT as SLR takes the Bernoulli characteristics into account.
-In particular, even though the arms are symmetrically distributed around the threshold in terms of absolute distance, they are not symmetrically around the threshold in terms of their Kullback-Leibler divergence (compare Figure 2).
-Thus we expect the SLR algorithm to not pull them symmetrically.
-Furthermore, we expect an improvement for the variance-based algorithms, as the variances are now smaller than in the first simulation, which should benefit the EVT algorithm given its theoretical analysis in Zhong et al.
-(2017).
-
-The figure below shows the performance of all algorithms.
-The results underline that this problem is much harder in general ($H_2^{APT} \approx 24703$).
-The performance of the variance based algorithms is surprisingly poor; EVT performs even worse than uniform sampling until close to the horizon, while Augmented UCB takes a long time to adjust away from uniform sampling.
-Both algorithms perform worse than APT after 7000 samples.
-
-The Simple Likelihood Ratio strategy improves considerably upon the alternative strategies.
-SLR reaches the average empirical error of 0.1 within the budget, and it improves at an exponential rate within the entire budget; in contrast to APT which appears to improve linearly in the observations.
-At the end of the budget, the difference in the empirical error is nearly 10% between the two strategies.
-
-In order to assess how the SLR strategy improves upon the APT algorithm, it is useful to look at how the algorithms allocate their sampling budget across arms.
-Given that we run the simulation 5000 times, we can compare across simulations how often an algorithm pulls each arm at a given round.
-During the 5000 iterations, the algorithm should pull at any given iteration the arm most often that it thinks is the most difficult to classify.
-In Figure 6, we plot the resulting curves where the y-axis shows a 10-round moving average of the pulls to remove some variation.
-
-The graph shows that both APT and SLR correctly single out the two arms closest to the threshold, and allocate most of the budget to them.
-However, while SLR keeps the two arms constant at two different levels (about 1900 for arm 5 and about 2500 for arm 6), APT at first pulls arm 5 more often than arm 6.
-Then, for *both* arms, the budget appears to converge to about 2000.
-Given that the two arms are symmetric around the threshold, it makes sense that APT would allocate the same exploration effort to them.
-And given that the variation of arm 5 away from the threshold is limited from below by zero, it is much easier for arm 6 to have an empirical mean larger than its true mean, and thus to have a larger index than arm 5 in the beginning.
-Consequently, APT would prefer to sample arm 5.
-This, however, is wrong in terms of Kullback-Leibler divergence.
-Measured by the divergence, arm 6 is closer to the threshold than arm 5, thus harder to classify, and consequently preferred by the SLR algorithm.
-Furthermore, the SLR algorithm appears to quickly find the correct share that it has to allocate to the two arms.
-This is in contrast to APT which continues to adjust the shares across the entire budget.
-
-Additionally, we can observe that the SLR strategy starts to drop arms much quicker than APT, and it drops arm 1 to 3 first, which again underlines the effect of the asymmetric Kullback-Leibler divergence.
-If we consider arm 3 and arm 8, we have $d_3(0.01||0.05) \approx 0.025$ while $d_8(0.09||0.05) = 0.014$.
-The divergence is much smaller for arm 8.
-The asymmetry is even more dramatic for arm 1 and arm 10 with $d_1(0.001||0.05) \approx 0.046$ and $d_{10}(0.099||0.05) \approx 0.020$: In terms of the divergence, the distance between arm 1 and the threshold is twice as far as between arm 10 and the threshold.
-APT considers them to be equally distant from the threshold.
-
-One interesting observation, that we will observe in all simulations with Bernoulli arms, is the superior performance of the Bayes-UCB algorithm adapted from Kaufmann et al.
-(2012) which was originally designed for cumulative regret problems.
-Nonetheless, the algorithm proves again and again to be the best performing.
-Compare with \autoref{sec:AppendixBUCB} for more analysis on the behavior of the Bayes-UCB algorithm in simulation 2.
-In particular, consider Figures 17 and 18 which show for individual arms the distribution of pulls for that arm across simulations.
-The distributions highlight that both the APT and SLR fail in many iterations of the simulations to pull arms frequently enough to estimate their correct mean.
-The APT algorithm pulls the most difficult arm (Arm 6) in more than 5% of the simulations only once (during initialization).
-Consider arm 6 returns $X_{6,1} = 1$ as its first observation.
-Then $B_6(t+1) = 1 \cdot |1-0.05| = 0.95$.
-It will then not be pulled for a long time because its index is very large.
-Indeed, consider some arm that has been pulled 4000 times with $\mu_i(4000) = 0.03$.
-Then $B_i(t+1) = \sqrt{2000} \cdot |0.05-0.03| \approx 0.89$.
-Even though we have basically no evidence for the performance of arm $6$, we would continue to pull arm $i$.
-Similar holds for the SLR algorithm.
-For both, the distribution of pulls for arm 6 is very flat across the interval of $[1,6000]$ pulls.
-In contrast, the distribution of pulls appears normally distributed for the Bayes-UCB algorithm with the mode between 2100 and 2300 pulls.
-The numerical problem that arises for the APT and SLR algorithms might be weakened for the Bayes-UCB algorithm by the combination of a (weak) prior that shrinks the mean estimates, and the way in which quantiles are based on the posterior.
-Also, the fact alone that it is based on confidence bounds of the empirical mean, instead of the empirical mean itself.
-We show in the appendix that the problem does not only occur for arm 6.
-
-Empirically, part of this problem can be alleviated by including the D-Tracking rule proposed by Garivier and Kaufmann (2016) and discussed in \autoref{sec:OptimalBestArmIdentification} into the SLR algorithm, as it ensures that no arm is ``left behind'' in terms of samples.
-Figure 5 shows a significant improvement for the SLR-D algorithm in comparison to the SLR algorithm without D-Tracking.
-However, the algorithm still does not reach the performance of Bayes-UCB.
-
-Lastly, we remark on the shape of the error curve of the uniform strategy.
-Even though the uniform strategy samples arms at random from the set of arms with the least observations at any round, we observe a sawtooth pattern for simulation 2 and 3.
-This is an artifact of the comparison against the threshold of $0.05$ and $0.01$ respectively, combined with the discrete $0$ and $1$ observations.
-Take for example an arm with a true mean of $\mu = 0.06$ compared against $\tau = 0.05$.
-Let's say the arm observes the first 1 after 15 samples, $X_{15} = 1$, such that $\hat{\mu}(15) = 1/15 \approx 0.067$.
-At this point, it is correctly classified as above the arm.
-Even if the next samples are zeroes, it will continue to be correctly classified until observation 20.
-At that point, $\hat{\mu}(20)$ = 1/20 = 0.05.
-By observing one more observation, the arm will be classified as below the threshold, since then $\hat{\mu}(21) = 1/21 < 0.05 = \tau$.
-The classification is suddenly wrong for no particular reason, and a sudden spike in the error curve occurs.
-In the graph of simulation 3 it is obvious that the spike occurs with a period length of about 100 samples, which corresponds to $\tau = 0.01=1/100$.
-This explains why we do not observe such a pattern in the first simulation with $\tau = 0.5$, or for the continuous Exponential distribution in simulation 4.
-
-```{r simulation2_results, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for simulations 2 and 3. Note the different x-axes."}
-library(ggplot2)
-current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
-
-load(paste0(current_path, "loc6nt_comp_BUCB_horizon_7000.Rda"))
-load(paste0(current_path, "loc6nt_comp_AugUCB_7000.Rda"))
-load(paste0(current_path, "loc6nt_comp_UNIFORM_7000.Rda"))
-load(paste0(current_path, "loc6nt_comp_APT_7000.Rda"))
-load(paste0(current_path, "loc6nt_comp_LR_7000.Rda"))
-load(paste0(current_path, "loc6nt_comp_LRD.Rda"))
-load(paste0(current_path, "loc6nt_comp_EVT.Rda"))
-
-alg_names <- c(rep(c("Uniform", "APT", "AugUCB",
-                     "SLR", "SLR-D", "B-UCB"), 
-                   each = 6991), rep("EVT", 6981))
-index <- c(rep(10:7000, times = 6), 20:7000)
-alg_res <- (c(loc6nt_comp_UNIFORM_7000, loc6nt_comp_APT_7000,
-                 loc6nt_comp_AugUCB_7000, loc6nt_comp_LR_7000,
-                 loc6nt_comp_LRD,
-                 loc6nt_comp_BUCB_horizon_7000, loc6nt_comp_EVT))
-loc6nt_comp_res <- data.frame(index = index, Algorithm = alg_names, 
-                            results = alg_res)
-
-current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
-
-load(file = paste0(current_path, "loc7nt_comp_UNIFORM_10000.Rda"))
-load(file = paste0(current_path, "loc7nt_comp_APT_10000.Rda"))
-load(file = paste0(current_path, "loc7nt_comp_LR_10000.Rda"))
-load(file = paste0(current_path, "loc7nt_comp_LRD_10000.Rda"))
-load(file = paste0(current_path, "loc7nt_comp_BUCB_horizon_10000.Rda"))
-load(file = paste0(current_path, "loc7nt_comp_AugUCB_10000.Rda"))
-load(file = paste0(current_path, "loc7nt_comp_EVT.Rda"))
-
-alg_names <- c(rep(c("Uniform", "APT", "AugUCB", 
-                     "SLR", "SLR-D", "B-UCB"), 
-                   each = 9990), rep("EVT", times = 9979))
-index <- c(rep(11:10000, times = 6), 22:10000)
-alg_res <- (c(loc7nt_comp_UNIFORM_10000, loc7nt_comp_APT_10000,
-                 loc7nt_comp_AugUCB_10000, loc7nt_comp_LR_10000,
-                 loc7nt_comp_LRD_10000,
-                 loc7nt_comp_BUCB_horizon_10000, loc7nt_comp_EVT))
-loc7nt_comp_res <- data.frame(index = index, Algorithm = alg_names, 
-                            results = alg_res)
-
-sim23_res <- rbind.data.frame(loc6nt_comp_res, loc7nt_comp_res)
-sim23_res$Simulation <- c(rep("Simulation 2", 48927), rep("Simulation 3", 69919))
-
-ggplot(sim23_res, aes(x = index, y = results)) + 
-  geom_line(aes(group = Algorithm, color = Algorithm)) +
-  #geom_hline(aes(yintercept = (0.1)), linetype = 2) +
-  facet_grid(.~Simulation, scales = "free") +
-  labs(#subtitle = "Dashed Line indicates Error = 0.1.",
-       y = "Error (log10 scale)", x = "Round Index") +
-  scale_color_discrete(name = "Algorithm") +
-  theme_bw() + 
-  theme(legend.position = "bottom") +
-  scale_y_log10()
-```
-
-```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Budget allocation across arms for APT and SLR algorithms in simulation 2."}
-load(file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/loc6nt_ma.Rda")
-library(dplyr)
-
-rbind(loc6nt_APT_ma, loc6nt_LR_ma) %>%
-  rename(Arm = arm) %>%
-  ggplot(aes(x = index, y = mean, group = Arm, color = Arm)) +
-  geom_line(size = 0.3) +
-  facet_grid(.~algorithm) +
-  labs(x = "Index", y = "10 Rounds Moving Average"#,
-       #title = "Average Number of Pulls Allocated to Each Arm per Round",
-       #subtitle = "5000 iterations; a value of 1000 means that in 20% of 
-#the iterations the arm was pulled in that round."
-) +
-  theme_bw() +
-  theme(legend.position = "bottom")
-```
-
-\newpage
-
-### Simulation 3: Bernoulli Arms and $\tau = 0.01$
-
-In the third experiment, we lower the threshold further to $\tau = 0.01$ and arrange now $K=11$ arms on a $\log_{10}$ scale around it.
-Again, we set $\epsilon = 0$.
-We compare the same algorithms as previously with the settings adapted to $\tau$ and $\epsilon$ accordingly.
-Notice that the experiment horizon is now $T=10000$ rounds instead of $T=7000$ rounds in the previous experiment.
-
-```{r loc7nt_data_summary, echo = FALSE, message = FALSE}
-mean_loc7nt <- c(10^-4, 10^-3.5, 10^-3.25, 10^-3, 
-                 10^-2.75, 10^-2.5, 10^-2.25, 10^-1.85, 10^-1.75,
-                 10^-1.5, 10^-1)
-
-mean_loc7nt_char <- c("10^-4", "10^-3.5", "10^-3.25", "10^-3", "10^-2.75", "10^-2.5", "10^-2.25", "10^-1.85", "10^-1.75", "10^-1.5", "10^-1")
-
-#get_apt_complexity(mean_loc7nt, 0.01, 0)
-
-knitr::kable(t(mean_loc7nt), digits = 4, col.names = paste0("V", 1:11), caption = "Mean of arms in simulation 3.")
-```
-
-Looking at the performance after 7000 rounds, we see that the problem appears to be slightly more difficult compared to the previous one ($H_3^{APT} \approx 210359$).
-We see that up until this point the variance-based strategies cannot improve upon APT.
-Also, SLR has not yet crossed the 10% empirical error.
-We observe that in the following rounds EVT decreases at an exponential rate and thus crosses the error of APT and continues to improve.
-At the end of the budget, the improvement of SLR compared to the other algorithms is again large, and likely to increase.
-However, Bayes-UCB is again the best performing algorithm and is improving at a faster rate than SLR.
-As in the previous experiment, Bayes-UCB and SLR show significant improvements on this Bernoulli problem with very small means and threshold compared to APT in particular.
-Furthermore, the observation that the SLR algorithm with D-Tracking rule performs better than without is replicated.
-
-```{r simulation3_results, echo = FALSE, include = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for simulation 3."}
-library(ggplot2)
-current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
-
-load(file = paste0(current_path, "loc7nt_comp_UNIFORM_10000.Rda"))
-load(file = paste0(current_path, "loc7nt_comp_APT_10000.Rda"))
-load(file = paste0(current_path, "loc7nt_comp_LR_10000.Rda"))
-load(file = paste0(current_path, "loc7nt_comp_LRD_10000.Rda"))
-load(file = paste0(current_path, "loc7nt_comp_BUCB_horizon_10000.Rda"))
-load(file = paste0(current_path, "loc7nt_comp_AugUCB_10000.Rda"))
-load(file = paste0(current_path, "loc7nt_comp_EVT.Rda"))
-
-alg_names <- c(rep(c("Uniform", "APT", "AugUCB", "SLR", "SLR-D", "B-UCB"), 
-                   each = 9990), rep("EVT", times = 9979))
-index <- c(rep(11:10000, times = 6), 22:10000)
-alg_res <- log(c(loc7nt_comp_UNIFORM_10000, loc7nt_comp_APT_10000,
-                 loc7nt_comp_AugUCB_10000, loc7nt_comp_LR_10000,
-                 loc7nt_comp_LRD_10000,
-                 loc7nt_comp_BUCB_horizon_10000, loc7nt_comp_EVT))
-loc7nt_comp_res <- data.frame(index = index, Algorithm = alg_names, 
-                            results = alg_res)
-ggplot(loc7nt_comp_res, aes(x = index, y = results)) + 
-  geom_line(aes(group = Algorithm, color = Algorithm)) +
-  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
-  labs(subtitle = "Dashed Line indicates Error = 0.1.", 
-       y = "log(Error)", x = "Round Index") +
-  theme_bw() #+
-  #theme(legend.position = "bottom")
-```
-
-### Simulations 4 and 5: Exponential and Poisson Distributions
-
-In \autoref{sec:LRforUnivariateExponentialFamily}, we show that the likelihood ratio has a very useful form for the one-parameter exponential family of distributions, which allows us to use the SLR algorithm not only on Bernoulli arms, but also on Exponential or Poisson distributions, for example.
-In simulation 4, we consider Exponential distributions, in simulation 5, we test the algorithms on Poisson distributions.
-
-We run the same algorithms as before except for Bayes-UCB (even though it should certainly be possible to adapt it to these case based on a Gamma prior).
-In the case of the Exponential arms, we classify against $\tau = 1$ and have sampled the arms' mean parameters from an Exponential distribution with rate $\theta = 1$.
-The Poisson arms are classified against a threshold of $\tau = 0.4$, with the mean parameters being sampled from an Exponential distribution with mean $\mu = 0.7$.
-In both cases, we classify 20 arms.
-
-For the Exponential arms, APT crosses the 10% error mark first, followed by the AugUCB algorithm.
-All algorithms perform better than uniform sampling.
-After more than half of the budget, the SLR algorithm jumps in performance and performs better than APT and AugUCB.
-Indeed, the AugUCB basically stops improving after half of the budget.
-This is a consequence of it eliminating arms it believes to know very well.
-This happens at an error rate of less than $0.01$.
-On average, the AugUCB samples only for 2564 rounds of the budget of 4000 rounds across the 5000 simulations.
-
-The early elimination (when compared to the Bernoulli experiments) might be caused by the fact that the AugUCB assumes the variance of the arms to be in $[0,1]$, which does not hold for half of the arms in the experiment.
-Similar goes for the EVT algorithm which is only able to catch up at the very end of the budget.
-
-```{r simulation4_results, include = FALSE, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for simulation 4."}
-library(ggplot2)
-current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/exponential/"
-
-load(paste0(current_path, "exp2_comp_LR.Rda"))
-load(paste0(current_path, "exp2_comp_APT.Rda"))
-load(paste0(current_path, "exp2_comp_EVT.Rda"))
-load(paste0(current_path, "exp2_comp_UNIFORM.Rda"))
-load(paste0(current_path, "exp2_comp_AugUCB.Rda"))
-
-alg_names <- c(rep(c("Uniform", "APT","SLR", "AugUCB"), 
-                   each = 3981), rep("EVT", 3961))
-index <- c(rep(20:4000, times = 4), 40:4000)
-alg_res <- (c(exp2_comp_UNIFORM, exp2_comp_APT, exp2_comp_LR,
-                 exp2_comp_AugUCB, exp2_comp_EVT))
-exp2_comp_res <- data.frame(index = index, Algorithm = alg_names, 
-                            results = alg_res)
-ggplot(exp2_comp_res, aes(x = index, y = results)) + 
-  geom_line(aes(group = Algorithm, color = Algorithm)) +
-  #geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
-  labs(#subtitle = "Dashed Line indicates Error = 0.1.",
-       y = "log(Error)", x = "Round Index") +
-  theme_bw() +
-  scale_y_log10()# +
-  #theme(legend.position = "bottom")
-```
-
-In the case of Poisson arms, the performance of the arms is more clear cut.
-As expected, SLR improves upon APT.
-APT outperforms the EVT algorithm, which occurs even though the variance of all arms considered in this experiment is in $[0,1]$.
-After about 1000 observations, APT and EVT appear to improve at about the same rate, but APT has a much better initial exploration phase.
-Given the previous simulations, it is surprising to see the Augmented-UCB algorithm to come ahead after $T=10000$ observations.
-After about half the budget, the same pattern as before occurs where there is a drastic change in sampling behavior.
-This suffices to outpace both APT and SLR.
-
-```{r simulation5_results, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for simulations 4 and 5. Note the different x-axes."}
-library(ggplot2)
-current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/exponential/"
-
-load(paste0(current_path, "exp2_comp_LR.Rda"))
-load(paste0(current_path, "exp2_comp_APT.Rda"))
-load(paste0(current_path, "exp2_comp_EVT.Rda"))
-load(paste0(current_path, "exp2_comp_UNIFORM.Rda"))
-load(paste0(current_path, "exp2_comp_AugUCB.Rda"))
-
-alg_names <- c(rep(c("Uniform", "APT","SLR", "AugUCB"), 
-                   each = 3981), rep("EVT", 3961))
-index <- c(rep(20:4000, times = 4), 40:4000)
-alg_res <- (c(exp2_comp_UNIFORM, exp2_comp_APT, exp2_comp_LR,
-                 exp2_comp_AugUCB, exp2_comp_EVT))
-exp2_comp_res <- data.frame(index = index, Algorithm = alg_names, 
-                            results = alg_res)
-
-current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/poisson/"
-
-load(paste0(current_path, "pois2_comp_LR.Rda"))
-load(paste0(current_path, "pois2_comp_APT.Rda"))
-load(paste0(current_path, "pois2_comp_EVT.Rda"))
-load(paste0(current_path, "pois2_comp_UNIFORM.Rda"))
-load(paste0(current_path, "pois2_comp_AugUCB.Rda"))
-
-alg_names <- c(rep(c("Uniform", "APT", "SLR", "AugUCB"), each = 9981), 
-               rep("EVT", 9961))
-index <- c(rep(20:10000, times = 4), 40:10000)
-alg_res <- (c(pois2_comp_UNIFORM, pois2_comp_APT, 
-                 pois2_comp_LR, pois2_comp_AugUCB, pois2_comp_EVT))
-pois2_comp_res <- data.frame(index = index, Algorithm = alg_names, 
-                            results = alg_res)
-
-exp45_res <- rbind.data.frame(exp2_comp_res, pois2_comp_res)
-exp45_res$Distribution <- c(rep("Exponential", 19885), rep("Poisson", 49885))
-
-ggplot(exp45_res, aes(x = index, y = results)) + 
-  geom_line(aes(group = Algorithm, color = Algorithm)) +
-  #geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
-  facet_grid(.~Distribution, scales = "free") +
-  labs(#title = "Results of Experiment 5", 
-       #subtitle = "Dashed line at Error = 0.1.", 
-       y = "Error (log10 scale)", x = "Round Index") +
-  theme_bw() +
-  theme(legend.position = "bottom") +
-  scale_y_log10()
-```
 
@@
 
-In the thesis at hand, we have introduced the general thresholding bandit problem introduced by Locatelli et al.
-(2016), as well as their Anytime Parameter-Free Thresholding algorithm that tries to solve the problem optimally.
-Given a few limitations of the APT algorithm, we explored the literature on top-$m$ multi-armed bandit problems to see how the Kullback-Leibler divergence can be used to improve algorithms and performance bounds.
-Based on this we exhibit the similarity between the thresholding bandit problem and simple hypothesis testing.
-We derive a lower bound on the complexity of a one-armed thresholding bandit that corresponds to the Chernoff-Stein Lemma.
-Continuing with the intuition from hypothesis testing, we propose the new Simple Likelihood Ratio algorithm for the multi-armed thresholding bandit for one-parameter exponential family of distributions.
-We show in extensive simulations that the the empirical performance of the SLR algorithm improves significantly upon the APT algorithm.
-We show that adding the D-Tracking Rule originally proposed by Garivier and Kaufmann (2016) can eradicate some of the remaining weaknesses.
-We propose a new method of testing thresholding bandit algorithms on real data by treating it as in time series cross validation.
-We show that the adaptive sampling strategies are not robust to the time dependency in the data set.
-
-Problems for future work are the derivation of lower and upper bounds on the error probability of the SLR algorithm.
-Furthermore, one might be able to adapt the lower bound on the complexity of the one-armed thresholding bandit to the multi-armed version.
-Lastly, the surprisingly very good performance of the Bayes-UCB algorithm in our simulations, as well as its better sample allocation to individual arms in terms of concentration compared to APT and SLR, justify more research effort, and a theoretical analysis of its performance.
-
 # Acknowledgements
@@
 We thank Carlo Alberto Dall'Amico for bringing our attention to multi-armed bandits in the first place.
-Sonoma Internet GmbH (Amorelie) supported this work by giving the authors access to the discussed data set.
-
-\newpage
-
-# References
-
-J.-Y. Audibert, S. Bubeck, and R. Munos. Best Arm Identification in Multi-Armed Bandits. In *Proceedings of the 23rd Conference on Learning Theory*, 2010.\par
-
-E.
-Brochu, V.M.
-Cora, and N.
-de Freitas.
-A Tutorial on Bayesian Optimization of Expensive Cost Functions, with Application to Active User Modeling and Hierarchical Reinforcement Learning, *arXiv preprint arXiv:1012.2599*, 2010.
-\par
-
-S. Bubeck and N. Cesa-Bianchi. Regret analysis of stochastic and nonstochastic multi-armed bandit problems. *Foundations and Trends in Machine Learning*, 5:1–122, 2012.\par
-
-S. Bubeck, N. Cesa-Bianchi, and G. Lugosi. Bandits with heavy tail. *Information Theory, IEEE Transactions on*, 59(11):7711-7717, 2013.\par
-
-A.N. Burnetas and M.N. Katehakis. Optimal adaptive policies for sequential allocation problems. *Advances in Applied Mathematics*, 17:122–142, 1996.\par
-
-O. Capp´e, A. Garivier, O-A. Maillard, R. Munos, and G. Stoltz. Kullback-Leibler upper confidence bounds for optimal sequential allocation. *Annals of Statistics*, 41(3):1516–1541, 2013a.\par
-
-O. Capp´e, A. Garivier, O.-A. Maillard, R. Munos, G. and Stoltz. Supple-
-ment to “Kullback–Leibler upper confidence bounds for optimal sequential allocation.”, *Annals of Statistics*, <DOI:10.1214/13-AOS1119SUPP>, 2013b. \par
-
-H. Chernoff. Sequential Design of Experiments. *The Annals of Mathematical Statistics*, 30(3):755-770, 1959. \par
-
-J.C. Gittins. Bandit processes and dynamic allocation indices. *Journal of the Royal Statistical Society*. 41(2):148–177, 1979.\par
-
-A. Garivier and E. Kaufmann. Optimal Best Arm Identification with Fixed Confidence. In *JMLR Workshop and Conference Proceedings (Conference on Learning Theory)*, 49:1-30, 2016.\par
-
-E. Kaufmann and S. Kalyanakrishnan. Information Complexity in Bandit Subset Selection. In *JMLR Workshop and Conference Proceedings (Conference on Learning Theory)*, 30:228–251, 2013.\par
-
-E.
-Kaufmann, O.
-Capp´e, and A.
-Garivier.
-On Bayesian Upper Confidence Bounds for Bandit Problems.
-In *Proceedings of the 15th International Conference on Artificial Intelligence and Statistics (AISTATS)*, 2012.\par
-
-E. Kaufmann, O. Capp´e, A. Garivier. On the Complexity of Best Arm Identification in Multi-Armed Bandit Models. Journal of Machine Learning Research, 17:1-42, 2016.\par
-
-T.L. Lai and H. Robbins. Asymptotically efficient adaptive allocation rules. *Advances in Applied Mathematics*, 6:4–22, 1985.\par
-
-A.
-Locatelli, M.
-Gutzeit, and A.
-Carpentier.
-An optimal algorithm for the Thresholding Bandit Problem.
-In *Proceedings of the 33rd International Conference on Machine Learning*, JMLR: W&CP 48, 2016.\par
-
-S. Mukherjee, K.P. Naveen, N. Sudarsanam, and B. Ravindran. Thresholding Bandits with Augmented UCB. 2017. *arXiv preprint arXiv:1704.02281*, 2015.\par
-
-H. Robbins. Some aspects of the sequential design of experiments. *Bulletin of the American Mathematical Society*, 58:527-535, 1952.\par
-
-D. Russo. Simple Bayesian Algorithms for Best Arm Identification. In *JMLR Workshop and Conference Proceedings (Conference on Learning Theory)*, 2016.\par
-
-W.R. Thompson. On the likelihood that one unknown probability exceeds another in view of the evidence of two samples. *Biometrika*, 25:285–294, 1933.\par
-
-W.R. Thompson. On the Theory of Apportionment. *American Journal of Mathematics*, 57:450–456, 1933.\par
-
-J. Zhong, Y. Huang, and J. Liu. Asynchronous Parallel Empirical Variance Guided Algorithms for the Thresholding Bandit Problem. *arXiv preprint arXiv:1704.04567*, 2017.\par
-
-\newpage
-
-# Appendix
-
-## Example of User Feedback in Foursquare App \label{sec:Foursquare}
-
-![The right screenshot shows aggregated user feedback in the Foursquare app.
-One could use thresholding bandit algorithms as presented in this thesis to ask different questions so as to optimize the confidence with which the results are displayed for a restaurant in the app.](figures/Foursquare_Screenshot.png)
-
-## Proof of Thresholding Bandit Lower Bound \label{sec:AppendixAPTLB}
-
-We now give a proof for the lower bound for the thresholding bandit problem stated in \autoref{theorem:Locatelli2016Theorem1}.
-
-*Proof of Theorem \ref{theorem:Locatelli2016Theorem1}*: Locatelli et al.
-(2016) derive a lower bound for the thresholding bandit problem.
-We restate the proof here.
-The idea is as follows.
-The problem formulation considered in the paper describes bandit problems for $R$-sub-Gaussian distributions.
-To show a lower bound, we show that every algorithm is expected to make a certain error even if we consider a very restricted scenario.
-Even then, the best algorithm will have a maximum error probability with which it cannot distinguish between the actual setting and slightly changed settings (under which the answer for the true setting leads to a misclassification).
-
-Consider the thresholding bandit setting as in \autoref{sec:Setup}.
-More specifically, consider a problem in which all arms follow Normal distributions $\nu_i$ with mean $\mu_i$ and variance $\sigma^2 = 1$.
-"in which w"e set $\tau = 0$ and $\epsilon = 0$ w.l.o.g.
-Consequently, for each arm $i$ the distance from the threshold is given by $\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i$.
-Thus, we have for every arm the distribution $\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)$.
-Furthermore, define for each arm $i \in \{1, \dots, K\}$ the alternative distribution $\nu_i' = \mathcal{N}(-\Delta_i,1)$.
-It is easy to see that this is equivalent to a "flip around the threshold".
-Arms that originally have a mean larger than the threshold have a mean smaller than the threshold after the flip.
-
-The intuition now is that every arm $i \in \{1,\dots,K\}$ generates a sample for every time point $t\in \{1, \dots, T\}$ from its distribution $\nu_i$ before the algorithm starts to choose arms.
-Thus, we have a $T \times K$ table of realized observations from the product distribution given by $\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K$.
-This is a product distribution where the $K$ different means are all above the threshold.
-We would hope that an algorithm classifies the means accordingly.
-However, we will show in what follows that any algorithm makes a certain error by not being able to distinguish $\mathcal{B}^0$ from at least one of $K$ alternative product distributions $\mathcal{B}^i, i \in \{1, \dots, K\}$, of which each differs only slightly in one arm from the original distribution, and has the same overall complexity (as defined by $H = \sum_{i=1}^K (\Delta_i)^{-2}$).
-We require $K$ different distributions so that an algorithm sampling arm $i$ very often for some reason will not have a smaller lower bound by chance.
-
-For each of the $K$ arms, we introduce an alternative model of the following kind.
-Before the start of the algorithm, we introduce a slight variation in the setup.
-The idea is similar to how one can switch arms in the pure exploration setup for multi-armed bandits (compare Audibert et al., 2010; Garivier & Kaufmann, 2016) to "confuse" any algorithm without introducing additional complexity to the specified problem.
-However, since we do not compare arms directly with each other in the thresholding bandit problem (switching arms would still keep all means above the threshold), we instead need to flip an arm $i$ with respect to the threshold in order to get the alternative model $\mathcal{B}_i$.
-Since the threshold is $\tau = 0$, we have for the flipped arm the new distribution $\nu_i'$ as defined above.
-Indeed, define the new product distribution $B^i = \nu_1^i \otimes \dots \otimes \nu_K^i$ where for $k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}$.
-This arm flip corresponds to multiplying all $X_{i,t}$ of arm $i$ by $-1$.
-
-As in Locatelli et al.
-(2016), let for $i \leq K$, $\mathbb{P}_{\mathcal{B}^i}$ be the probability distribution describing all samples that a bandit strategy can potentially collect up to horizon $T$, i.e.
-according to the samples $(X_{k,s})_{k\leq K, s \leq T} \sim (\mathcal{B}^i)^{\otimes T}$.
-$(T_k)_{k\leq K}$ denotes the number of samples collected on arm $k$ until time $T$.
-
-At this point, we have defined a finite set of problems of Gaussian distributions with fixed variance 1 for a given set of set of gaps between the means of the distributions and the threshold, $(\Delta_k)_k$.
-We now proof a lower bound on the worst case regret of any algorithm; that is, the maximum error probability that even the best algorithm makes on this problem.
-
-### Statistical Decision
-
-The expected loss in our thresholding bandit setting, $\mathbb{E}[\mathcal{L}(T)]$, corresponds directly to the probability of making a wrong classification of any of the $K$ means.
-In general, given a binary decision function $g$, define events $\Omega = \{g = 0\}$ and $\Omega^C = \{g = 1\}$.
-Assume that the decision $g$ distinguishes between two states of the world, $H_0$ and $H_1$.
-Then an overall error probability can be seperated into $P_{H_0}(g=1) + P_{H_1}(g = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)$.
-
-In our case, $H_0$ may correspond to the state in which we have $\mathcal{B}^0$, and $H_1$ corresponds to the case where any arm has been flipped, $\mathcal{B}^i$.
-Furthermore, we consider the events in which the algorithm classifies arm $i$ as being above the threshold: $\mathcal{A}_i = \{i \in \hat{S}_\tau\}$.
-The event on which all arms are being classified as above the threshold is consequently given by $\mathcal{A} = \bigcap_{i=1}^K \mathcal{A}_i$.
-We could thus separate the error probability $\mathbb{E}[\mathcal{L}(T)]$ into $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$ and $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C)$.
-However, Theorem 1 does not bound the overall regret, but the maximum error probability on the $K+1$ different models.
-We can write this now as
-
-\begin{align}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big) \\
-& = \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
-\end{align}
-
-### Empirical Kullback-Leibler Divergence
-
-In order to give a bound on the previous equation, we start by considering $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$.
-This probability can be written as the expected change in the likelihood of observed data when moving from distribution $P_{\mathcal{B}_0}$ to $P_{\mathcal{B}_i}$, times the probability under the original state.
-In other words, the probability of event $\mathcal{A}_i$ under state $\mathcal{B}^i$ is given as the probability of $\mathcal{A}_i$ under the (original) state $\mathcal{B}^0$ multiplied by a factor.
-This factor describes whether the new distribution increases or decreases the probability of the event, and is given by the change in the data likelihoods due to moving from $\mathcal{B}^0$ to $\mathcal{B}^i$, expressed as the expected likelihood ratio under $\mathcal{B}^0$.
-By definition, the latter is equal to the empirical Kullback-Leibler divergence of the two distributions.
-
-We will define the change of distribution in terms of the empirical log-likelihood for our case.
-Then, we will show how to replace the log-likelihood by the empirical Kullback-Leibler divergence.
-Let us first introduce the empirical Kullback-Leibler divergence.
-
-Let every $\nu_i, \nu_i'$ be dominated by the Lebesgue measure $\lambda$.
-Then their density functions are given by $f_i = \frac{\der \nu_i}{\der \lambda}$ and $f_i' = \frac{\der \nu_i'}{\der \lambda}$ respectively.
-For $T \geq t \geq 0$, define the empirical Kullback-Leibler divergence for an i.i.d.
-sample $X_{k,1}, \dots,X_{k,t}$ as
-
-\begin{align*}
-\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log(\frac{\der \nu_k'}{\der \nu_k}(X_{k,s})) \\
-& = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
-& = \frac{1}{t} \log \big( \prod_{s=1}^{t} \frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
-& \stackrel{\text{iid}}{=} \frac{1}{t} \log \big( \frac{f_k'(X_{k,1}, \dots,X_{k,t})}{f_k(X_{k,1}, \dots,X_{k,t})} \big) \\
-& = \frac{1}{t} \log \big( \text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k) \big),
-\end{align*}
-
-where $\text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k)$ is the likelihood ratio for the sample.
-
-Since we consider Gaussian distributions with variance $\sigma^2 = 1$, we have density functions $f_i(x) \propto \exp \big(-\frac{1}{2} (x-\Delta_i)^2\big)$ and $f_i'(x) \propto \exp \big(-\frac{1}{2} (x+\Delta_i)^2\big)$.
-Plugging this into the above definition of the empirical Kullback-Leibler divergence, we easily see
-
-\begin{align*}
-\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log \Big(\frac{\exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2\big)}{\exp \big(-\frac{1}{2} (X_{k,s}-\Delta_k)^2\big)} \Big) \\
-& = \frac{1}{t} \sum_{s=1}^{t} \log \Big( \exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2 + \frac{1}{2} (X_{k,s}-\Delta_k)^2 \big) \Big) \\
-& = - \frac{1}{t} \sum_{s=1}^{t} 2 X_{k,s} \Delta_k
-\end{align*}
-
-### Change of Distribution
-
-We are now ready to state the change of distribution.
-As alluded to above, we consider how the probability changes for the event $\mathcal{A}_i$ when we move from $\mathcal{B}^0$ to $\mathcal{B}^i$.
-When flipping arm $i$, we only change the samples of this arm, that is, the first $T_i$ observations that the algorithm draws from arm $i$.
-The change of distribution is then defined as:
-
-\begin{align*}
-\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \text{LR}((X_{i,1}, \dots,X_{i,T_i}), \nu_i', \nu_i) ] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ]
-\end{align*}
-
-Obviously, $\hat{\KL}_{i,T_i}$ depends on the realized samples $X_{i,1}, \dots,X_{i,T_i}$.
-Consequently, we need to find a bound on $\hat{\KL}_{i,T_i}$ itself to incorporate the uncertainty involved in this metric.
-
-### Concentration of the Empirical Kullback-Leibler Divergence
-
-For our problem, the Kullback-Leibler divergence of $\nu_k'$ from $\nu_k$ is given by $\KL_k := \KL(\nu_k', \nu_k) = 2\Delta_k^2$, and consequently
-
-\begin{equation*}
-|\hat{\KL}_{k,t} - \KL_{k,t}| = |-\frac{2}{t} \Delta_k \sum_{s=1}^{t}(X_{k,s} - \Delta_k)|
-\end{equation*}
-
-itself is a normally distributed random variable with mean zero and a variance decreasing in $t$.
-Thus, one can show as in Locatelli et al.
-(2016) that $\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4$ for the event
-
-\begin{equation}
-\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}}\}. \label{LocatelliTheorem1EventXi}
-\end{equation}
-
-Thus, in order to bound the empirical Kullback-Leibler divergence in our change of measure, we can consider the intersection of $\mathcal{A}_i$ and $\xi$ as follows and plug in the bound on event $\xi$:
-
-\begin{align*}
-\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
-\end{align*}
-
-Two things are left to do: With $T_i$, we still have one random variable left which we cannot leave in our bound.
-Second, we are actually not interested in $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$ but in $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$.
-
-### Bounding $T_i$ for $\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$
-
-We are actually interested in bounding $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$.
-In general it holds that $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K}\sum_{i=1}^K X_i$.
-Thus we can write:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
-& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
-& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
-\end{align*}
-
-where the second line is again the intersection of $\mathcal{A}_i$ and $\xi$ as before, such that we can apply the change of distribution in the third line.
-
-What is left to show is a bound on $T_i$.
-Given that we want to show that even the best algorithm makes an error on at least one of the problems (one of the arms), it makes sense to show that $T_i$ is upper bounded.
-This implies that no arm can be infinitely sampled; we cannot reach full confidence in any arm, and a residual error probability should remain.
-
-First, let $a = \Delta_i \sqrt{T_i}$ and $b = 4\sqrt{\log((4\log(T)+1)K)}$. Then use $ab \leq a^2 + b^2$ to write $ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)$. And so:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) ]
-\end{align*}
-
-Furthermore, we know that the sum of the individual arm pulls has to be equal to the overall number of pulls (equal to the budget in the fixed budget sense), $\sum_i T_i = T$, and furthermore we know that $T_i>0$.
-The latter holds since any reasonable algorithm has to check each arm at least once in our setup.
-Thus it is easy to show that $\exists i: T_i \leq \frac{T}{H \Delta_i^2} = \frac{T}{(\sum_{i=1}^{K} \Delta_i^{-2}) \Delta_i^2}$.
-To see this, assume the opposite: $\forall i: T_i > T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2}$.
-This implies however $\sum_{i=1}^K T_i > \sum_{i=1}^K T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2} = T \cdot 1 = T$ which is a contradiction.
-
-So we can write $(\Delta_i \sqrt{T_i})^2 \leq \frac{T}{H}$. We use $\mathcal{A} = \cap_{i=1}^K \mathcal{A}_i$ to write:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big]
-\end{align*}
-
-We write $\frac{1}{K} \sum_{i=1}^K \exp(-3T_i \Delta_i^2) \geq \frac{1}{K} \sum_{i=1}^K \exp(-3 T/H) = \exp(-3 T/H)$. Thus:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \Big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i) \exp \big(-16 \log(4(\log(T)+1)K)\big) \Big] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \Big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp \big(- 3 \frac{T}{H}\big) \exp \big(-16 \log(4(\log(T)+1)K)\big) \Big] \\
-& = \mathbb{E}_{\mathcal{B}^0} \Big[\mathbbm{1}_{\mathcal{A} \cap \xi} \exp \big(- 3 \frac{T}{H}\big) \exp \big(-16 \log(4(\log(T)+1)K)\big) \Big] \\
-& = \mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp \Big(- 3 \frac{T}{H} -16 \log \big(4(\log(T)+1)K\big)\Big)
-\end{align*}
-
-### Bringing everything together
-
-Consider again the risk which we need to bound from equation \eqref{LocatelliTheorem1ExpRegret}.
-We bound the maximum expected loss over all $\mathcal{B}_i$.
-By using again the fact that in general $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K} \sum_{i = 1}^K X_i$, we plug into our previous calculations:
-
-\begin{align}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp \Big(- 3 \frac{T}{H} -16 \log \big(4(\log(T)+1)K\big)\Big) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \label{LocatelliTheorem1DefinitionOfRisk}
-\end{align}
-
-From \eqref{LocatelliTheorem1EventXi} we know that for any $i \in \{0, \dots, K\}$, $\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4$.
-Following the argument in Locatelli et al.
-(2016), we now consider two cases: $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2$ and $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2$.
-In the former case, we can plug in the two probabilities into \eqref{LocatelliTheorem1DefinitionOfRisk}.
-If $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2$ and $\mathbb{P}_{\mathcal{B}^0}(\xi) \geq 3/4$, then $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \geq 1/4$.
-Thus:
-
-\begin{align*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \\
-& \geq \frac{1}{8} \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
-\end{align*}
-
-where we drop the second summand of the second line so that the inequality holds.
-
-On the other hand, when $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2$, then we know that $\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \leq 1/2$ for any $\mathbb{P}_{\mathcal{B}^0}(\xi)$.
-At the same time $1-\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \geq 1/2$.
-Consequently, $1/4 \leq \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \leq 1/2$, while
-$\frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) \geq 0$.
-And so the stronger lower bound in that case is, as noticed by Locatelli et al.
-(2016), given simply by
-
-\begin{align*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \\
-& \geq \frac{1}{2}
-\end{align*}
-
-## Lower Bound for Thresholding Bandit Problem with KL-divergence \label{sec:corollaryLBTBPproof}
-
-### Lower Bound for One-Armed Thresholding Bandit \label{sec:corollaryLB1TBPproof}
-
-**Proof**: The proof follows closely the proof of Theorem 12 in Kaufmann et al. (2016) and is again an application of their transportation Lemma, Lemma 2.
-
-Consider the one-armed bandit problem, $K = 1$ with the canonical exponential family of distributions distribution $\nu_1$ parameterized by its mean $\mu_1$.
-Furthermore, given we are in the thresholding bandit problem, we have a threshold $\tau$ against which the arm is classified.
-Assume w.l.o.g.
-that for $\nu_1$, $\mu_1 \geq \tau$.
-Thus, $\mathcal{S}_{\tau}^* = \{1\}$.
-After $T$ rounds, a consistent algorithm returns with error probability $p_T(\nu)$ the guess $\hat{\mathcal{S}}_{\tau}$.
-Thus, we have for the event $A = (\hat{\mathcal{S}}_\tau = \{1\})$ the probability $\mathbb{P}_{\nu}(A)$.
-On the other hand, define the alternative model $\nu'$ with mean $\mu_1' < \tau$ such that the correct classification from $\nu$ is now wrong: $\mathcal{S}_{\tau}^* {'} = (\mathcal{S}_{\tau}^*)^C = \{\emptyset\}$.
-Consequently, since the algorithm is still consistent on this problem, we have that $\mathbb{P}_{\nu'}(A) = p_t(\nu')$.
-Thus, we expect that as we let $t$ increase, $\mathbb{P}_{\nu'}(A)$ will decrease while $\mathbb{P}_{\nu}(A)$ will increase.
-
-Indeed, given we consider only consistent algorithms, there should exist a number of samples for which the probability of the correct decision in problem $\nu$ is larger than the error probability in problem $\nu'$, that is: for every $\epsilon > 0$, there exists $t_0(\epsilon)$ such that for all $t \geq t_0(\epsilon)$ we have
-
-\begin{equation*}
-\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_{\nu}(A). \label{eq:BoundForCorollary}
-\end{equation*}
-
-Now, consider again Lemma 2 in Kaufmann et al. (2016). If we let the algorithm be such that $T = t$, we can apply the Lemma to the stopping time $\sigma = t$ a.s. and the event $A$ to get
-
-$$
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)).
-$$
-
-We can lower bound the RHS by using the bound on $\mathbb{P}_{\nu'}(A)$ given in \eqref{eq:BoundForCorollary} and the monotonicity of the binary relative entropy. We get:
-
-\begin{align*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) & = t \KL(\nu_1', \nu_1) \\
-& \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)) \\
-& \geq d(\epsilon, 1- p_t(\nu)) \\
-& = \epsilon \log\Big(\frac{\epsilon}{1-p_t(\nu)}\Big) + (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) \\
-& \geq (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) + \epsilon \log(\epsilon) \\
-\end{align*}
-
-Letting $\epsilon \rightarrow 0$, we get
-
-$$
-t \KL(\nu_1', \nu_1) \geq \log \Big(\frac{1}{p_t(\nu)}\Big) = -\log p_t(\nu).
-$$
-
-To make the bound as tight as possible, we choose the alternative model that minimizes $\KL(\nu_1', \nu_1)$ while still ensuring that $\mathcal{S}_{\tau}^* {'} = \{\emptyset\}$.
-In our case of the thresholding bandit with one-parameter exponential family distributions, this is given by choosing $\mu_1' \rightarrow \tau$ (not equal to $\tau$ since else the classification of $\nu_1$ is again correct).
-By pluggin in, we get the result:
-
-$$
-t \KL(\tau, \mu_1) \geq -\log p_t(\nu) \quad \text{for} \; \mu_1' \rightarrow \tau.
-$$
-
-### Lower Bound for $K$-Armed Thresholding Bandit \label{sec:corollaryLBKTBPproof}
-
-**Proof**: The proof is very similar to the proof of the corollary for $K=1$.
-However, the alternative model needs more motivation than in the case of a single arm.
-But first, consider again that we are in the thresholding bandit problem with $K$ arms of one-parameter canonical exponential family distributions that are parameterized by their means $\mu_1, ..., \mu_K$ for the original problem $\nu = (\nu_1, ..., \nu_K)$.
-W.l.o.g, assume that all arms are above the threshold, that is, $\mu_1 \geq \tau, ..., \mu_K \geq \tau$.
-Then $\mathcal{S}_{\tau}^* = \{1, ...
-, K\}$.
-The correct classification returned after $t$ rounds is thus the event $A = (\hat{\mathcal{S}}_{\tau} = \{1, ..., K\})$.
-We can now consider Lemma 2.
-The RHS is maximized when the alternative model is chosen such that $d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A))$ is maximized.
-Given the event $A$ as defined before, this is the case when $\mathbb{P}_{\nu'}(A)$ is as small as possible.
-For consistent algorithms, this is the case when $\nu'$ is chosen such that all $\mu_1' < \tau, ..., \mu_K' < \tau$.
-Then even classifying a single arm correctly under $\nu$ would lead to a mistake in $\nu'$.
-Consequently, $A$ is the most unlikely classification for a consistent algorithm for the problem $\nu'$.
-We thus expect for any consistent algorithm that $\mathbb{P}_{\nu}(A)$ becomes large and $\mathbb{P}_{\nu'}(A)$ becomes small as the number of observations $t$ increases.
-Again, for every $\epsilon > 0$, there exists $t_0(\epsilon)$ such that for all $t \geq t_0(\epsilon)$ we have $\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)$.
-This allows us to now use Lemma 1 as previously:
-
-\begin{align*}
-\sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\nu_i', \nu_i) & \geq \sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\tau, \mu_i) \\
-& \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)) \\
-& \geq d(\epsilon, 1-p_t(\nu)) \\
-& = \epsilon \log \Big(\frac{\epsilon}{1-p_t(\nu)}\Big) + (1-\epsilon) \log \Big( \frac{1-\epsilon}{p_t(\nu)}\Big) \\
-& \geq (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) + \epsilon \log(\epsilon)
-\end{align*}
-
-We let $\epsilon \rightarrow 0$, divide by $t$ and take the limsup on both sides as in Kaufmann et al. (2016):
-
-\begin{align*}
-\lim_{t \rightarrow \infty} \sup - \frac{1}{t} \log p_t(\nu) & \leq \lim_{t \rightarrow \infty} \sup \frac{1}{t} \sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\tau, \mu_i) \\
-& \leq \max_{i \in \{1,...,K\}} \KL(\tau, \mu_i)
-\end{align*}
-
-Though, since for the alternative problem $\nu'$ we have for every $i \in \{1,...,K\}$ that $\mu_i = \tau$, it should hold for any consistent algorithm that $\mathbb{E}_{\nu'}[N_i(t)] = \frac{t}{K}$, that is, every arm receives an equal amount of the budget.
-In that case, the above equation simplifies to
-
-$$
-- \frac{1}{t} \log p_t(\nu) \leq \frac{1}{t} \sum_{i=1}^K \frac{t}{K}\KL(\tau, \mu_i) = \frac{1}{K} \sum_{i=1}^{K} \KL(\tau, \mu_i),
-$$
-
-that is, the complexity is given by the simple average of the Kullback-Leibler distances of the threshold with regard to the respective distributions.
-This relates well to the lower bound that Kaufmann et al.
-(2016) describe in their Theorem 12 for consistent algorithms using *uniform* sampling strategies; in our case, however, it is explained by the fact that under the alternative model, every consistent algorithm should adapt to a uniform sampling strategy.
-Thus our bound holds for any consistent strategy.
-
-## Bayes-UCB Algorithm for the Thresholding Bandit Problem \label{sec:AppendixBUCB}
-
-We show how the Bayes-UCB algorithm (Algorithm 1, Kaufmann et al., 2012) is adapted to the thresholding bandit problem to be used in the experiments in chapter \autoref{chap:Experiments}.
-The adapted version of their Algorithm 1 is given in Algorithm 4 below.
-In particular, notice that we not only calculate upper quantiles $q_i^u(t)$, but also lower quantiles $q_i^l(t)$, as we have to be able to compare against $\tau$ from both sides.
-These quantiles rely on the posterior distributions $\lambda_i^t$ for each mean $\mu_i$.
-In our case, we employ Beta prior distributions as conjugate prior for the Bernoulli distributions in simulations 1 to 3 and initialize them with parameters $\alpha_0$ and $\beta_0$.
-See the setup in Kaufmann et al.
-(2012), especially equation (3), to see how the posterior distribution is updated in every round.
-
-\IncMargin{1em}
-\begin{algorithm}
-\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
-\Input{\emph{$\tau$, $\epsilon$, $T$, $\Pi^0$ (initial prior on $\mu$), $c$ (parameters of the quantile)}}
-\Output{$\hat{S}_\tau = \{i \in \mathbb{A},  \hat{\mu}_i(T) \geq \tau\}$}
-\BlankLine
-\emph{Pull each arm once}\;
-\For{$t = K+1$ \KwTo $T$}{
-\For{$i = 1$ \KwTo $K$}{
-  \emph{Compute $q_i^u(t) = Q\Big(1-\frac{1}{t(\log T)^c}, \lambda_i^{t-1}\Big)$ and $q_i^l(t) = Q\Big(\frac{1}{t(\log T)^c}, \lambda_i^{t-1}\Big)$}\;
-  \emph{Compute $B_i^{BUCB}(t) = (\tau - q_i^l(t))\cdot\mathbb{I}(\hat{\mu}_i(t) \geq \tau) + (q_i^u(t) - \tau)\cdot\mathbb{I}(\hat{\mu}_i(t) < \tau)$}\;
-}
-  \emph{Pull arm $I_t = \arg \max_{i\leq K} B_i^{BUCB}(t)$}\;
-  \emph{Observe reward $X \sim \nu_{I_t}$ and update $\Pi^t$}\;
-}
-\caption{Bayes-UCB algorithm from Kaufmann et al. (2012) adapted to the thresholding bandit problem.}\label{bayesucb_tbp}
-\end{algorithm}\DecMargin{1em}
-
-### Empirical Analysis of the Bayes-UCB Algorithm in Simulation 2
-
-In order to assess the excellent performance of the Bayes-UCB algorithm, which comes at a surprise given that is is designed for the cumulative regret setting and thus should tend to explore the arms to less, we run the Bayes-UCB algorithm for simulation 2 with three different choices of the parameter.
-In Figure 13, we see the performance results of the three versions, whereas Figure 14 shows how the algorithm allocates its budget across the arms over time.
-The three versions differ in the quantile parameter $c$ (compare \autoref{sec:AppendixBUCB}) for which we choose $c \in \{1/5, 1, 5\}$ to explore more or less.
-In Kaufmann et al.
-(2012), the cumulative regret upper bound for the Bayes-UCB is shown for $c\geq 5$, though they report that the choice of $c=0$ worked much better in their experiments.
-In our problem, it makes also sense that the versions with smaller quantiles (smaller $c$) tend to perform better, as these correspond to more exploration of the arms.
-In this particular simulation, the choices of $c=1/5$ and $c=1$ perform very similar.
-We see that the worse performance of $c=5$ can be attributed to a initial phase of sampling primarily the arms with mean below the threshold.
-This comes from the fact that the Bernoulli and Beta distributions are bounded between $0$ and $1$, with $\tau$ very close to $0$.
-Thus, the index $B_i^{BUCB}(t)$ cannot be larger than $\tau$ for arms with $\hat{\mu}_i(t) \geq \tau$.
-For arms with $\hat{\mu}_i(t) < \tau$, however, the index can be as large as $B_i^{BUCB}(t) = 0.95$.
-This leads to the effect seen in Figure 14: Due to $c=5$, the indexes are based on very large quantiles even in the beginning, which leads to large indexes for the arms with small means.
-This however is not the ideal sampling behavior.
-The other two variants adapt much better due to their smaller quantiles (and more exploration).
-
-```{r simulation2_results_bucb, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for simulation 2."}
-library(ggplot2)
-current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
-
-load(paste0(current_path, "loc6nt_comp_BUCB_horizon_7000.Rda"))
-load(paste0(current_path, "loc6nt_comp_BUCB_horizon_c5_7000.Rda"))
-load(paste0(current_path, "loc6nt_comp_BUCB_horizon_c15_7000.Rda"))
-#load(paste0(current_path, "loc6nt_comp_BUCB_horizon_7000.Rda"))
-
-alg_names <- c(rep(c("BUCB_C0.25", "BUCB_C1", "BUCB_C5"), 
-                   each = 6991))
-index <- c(rep(10:7000, times = 3))
-alg_res <- log(c(loc6nt_comp_BUCB_horizon_c15_7000,
-                 loc6nt_comp_BUCB_horizon_7000,
-                 loc6nt_comp_BUCB_horizon_c5_7000))
-loc6nt_comp_res <- data.frame(index = index, names = alg_names, 
-                            results = alg_res)
-ggplot(loc6nt_comp_res, aes(x = index, y = results)) + 
-  geom_line(aes(group = names, color = names)) +
-  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
-  labs(#title = "Results of Synthetic Experiment 2", 
-       subtitle = "Dashed line at Error = 0.1.", 
-       y = "log(Error)", x = "Round Index") +
-  scale_color_discrete(name = "Algorithm") +
-  theme_bw() 
-```
-
-```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Budget allocation across arms for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter."}
-rbind(loc6nt_BUCB_c15_ma, loc6nt_BUCB_ma, loc6nt_BUCB_c5_ma) %>%
-  rename(Arm = arm) %>%
-  ggplot(aes(x = index, y = mean, group = Arm, color = Arm)) +
-  geom_line(size = 0.3) +
-  facet_grid(.~algorithm) +
-  labs(x = "Index", y = "10 Rounds Moving Average"#,
-       #title = "Average Number of Pulls Allocated to Each Arm per Round",
-       #subtitle = "5000 iterations; a value of 1000 means that in 20% of 
-       #the iterations the arm was pulled in that round."
-       ) +
-  theme_bw() +
-  theme(legend.position = "bottom")
-```
-
-### Empirical Comparison of APT, SLR, and Bayes-UCB in Simulation 2
-
-We can compare the different algorithms used in Simulation 2 based on the overall number of pulls of each arm.
-In the best case, an algorithm would sample an arm for the optimal share of the budget, in every simulation.
-This is of course not the case, since the number of pulls of a given arm at the end of the budget, $T_i(T)$, is a random variable for adaptive sampling strategies.
-Given the 5000 iterations conducted in simulation 2, we can plot the empirical distribution of this random variable for different arms.
-
-In Figure 15, we show the distribution of $T_6(T)$ for algorithms APT, Bayes-UCB, and SLR.
-We see that the distribution of the Bayes-UCB algorithm is much better concentrated around the optimal share of the budget, and has a bell curve shape.
-In contrast, the distributions of APT and SLR are much less concentrated but flat and wide, and spread across a very large interval.
-Both algorithms have several iterations in which they draw arm 6, the most difficult arm only a single time (during initialization).
-This happens for APT more than 5% of the iterations, and leads to the spike on the very left of the graph.
-In order to cope at least a little bit with this problem, we have also run the SLR algorithm with the D-Tracking rule as introduced in Garivier and Kaufmann (2016).
-The effect is nearly not noticeable in Figure 15, but the minimum number of observations is not clearly bounded away from 0.
-The effect on the performance was described before and is very noticeable in comparison to SLR without D-Tracking.
-However, even with D-Tracking the performance of Bayes-UCB is not reached.
-We describe SLR with D-Tracking in Algorithm 5.
-
-```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Empirical distribution of pulls of arm 6 in simulation 2 by different algorithms."}
-current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"
-
-load(paste0(current_path, "loc6nt_pulls_of_arms_vis.Rda"))
-
-pulls_arm_6_long %>%
-  ggplot(aes(x = Pulls)) +
-  geom_histogram(binwidth = 100) +
-  facet_grid(.~Algorithm, scales = "free_y") +
-  geom_vline(aes(xintercept = 7000/10), linetype = 2) +
-  labs(x = "Pulls", y = "Count"#, 
-       #title = "Distribution of Pulls of Arm 6 Across Simulations",
-       #subtitle = "Binwidth = 100. Budget = 7000. 5000 Simulations.
-#Vertical line indicates pulls by uniform sampling given 10 arms in experiment."
-) +
-  theme_bw()
-```
-
-```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Empirical distribution of pulls of arms 1 and 10 in simulation 2 by different algorithms."}
-
-cbind.data.frame(
-  Arm = rep(c("01", "10"), each = 20000),
-  rbind.data.frame(pulls_arm_1_long, pulls_arm_10_long),
-  stringsAsFactors = FALSE
-) %>% 
-  ggplot(aes(x = Pulls, group = Arm)) +
-  geom_histogram(binwidth = 50) +
-  facet_grid(Arm~Algorithm, scales = "free_y")+
-  geom_vline(aes(xintercept = 7000/10), linetype = 2) +
-  labs(x = "Pulls", y = "Count"#, 
-       #title = "Distribution of Pulls of Arms 1 and 10 Across Simulations",
-       #subtitle = "Binwidth = 50. Budget = 7000. 5000 Simulations.
-#Vertical line indicates pulls by uniform sampling given 10 arms in experiment."
-) +
-  theme_bw()
-```
-
-## SLR Algorithm with D-Tracking Rule
-
-\IncMargin{1em}
-\begin{algorithm}
-\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
-\Input{$\tau$, $\epsilon$, class of distributions $\nu(\mu, \theta)$, $\theta_i \: \forall i \in \mathbb{A}$}
-\Output{$\hat{S}_\tau = \{i \in \mathbb{A},  \hat{\mu}_i(T) \geq \tau\}$}
-\BlankLine
-\emph{Pull each arm once}\;
-\For{$t = K+1$ \KwTo $T$}{
-  \emph{Calculate $U_t = \{i \in \mathbb{A}, T_i(t) < \sqrt{t} - K/2\}$}\;
-  \emph{Set $I_t = \arg \min_{i \in \mathbb{A}} B_i^{SLR}(t)$ as in \autoref{eqn:SLRIndex}}\;
-  \If{$U_t \neq \emptyset$}{Set $I_t = \arg \min_{i \in \mathbb{A}} T_i(t)$}
-  \emph{Pull arm $I_t$}\;
-  \emph{Observe reward $X_t \sim \nu_{I_t}$}\;
-}
-\caption{SLR algorithm with D-Tracking Rule (Garivier and Kaufmann, 2016)} \label{algo_slr_1d_dTracking}
-\end{algorithm}
-\DecMargin{1em}
-
-## Means in Simulations 4 and 5
-
-We give here the means of the distributions used in simulations 4 and 5 for completeness.
-
-```{r, echo = FALSE, fig.align = "center", out.width = '80%'}
-library(ggplot2)
-
-set.seed(93468734)
-tau_exp2 <- 1
-epsilon_exp2 <- 0
-mu_exp2 <- rexp(20, 1)
-
-knitr::kable(t(sort(mu_exp2)[1:10]), digits = 4, col.names = paste0("V", 1:10), caption = "Mean of Exponential arms 1 to 10 in simulation 4.")
-
-knitr::kable(t(sort(mu_exp2)[11:20]), digits = 4, col.names = paste0("V", 11:20), caption = "Mean of Exponential arms 11 to 20 in simulation 4.")
-
-set.seed(3795969)
-tau_pois2 <- 0.4
-epsilon_pois2 <- 0
-mu_pois2 <- rexp(20, 1/0.7)
-
-knitr::kable(t(sort(mu_pois2)[1:10]), digits = 4, col.names = paste0("V", 1:10), caption = "Mean of Poisson arms 1 to 10 in simulation 5.")
-
-knitr::kable(t(sort(mu_pois2)[11:20]), digits = 4, col.names = paste0("V", 11:20), caption = "Mean of Poisson arms 11 to 20 in simulation 10.")
-```
+Sonoma Internet GmbH (Amorelie) supported this work by giving the author access to the discussed data set.

### 2017-09-18 Thesis/Draft_for_Markus.tex
Printed version

--- 2017-09-08 Thesis/Draft.tex
@@
 
-``In general, we look for a new law by the following process: First we
-guess it. Then we -- now don't laugh, that's really true. Then we
-compute the consequences of the guess to see what, if this is right, if
-this law that we guessed is right, to see what it would imply. And then
-we compare the computation results to nature, or we say compare to
-experiment or experience, compare it directly with observations to see
-if it works. If it disagrees with experiment, it's wrong. In that simple
-statement is the key to science. It doesn't make any difference how
-beautiful your guess is, it doesn't make any difference how smart you
-are, who made the guess, or what his name is. If it disagrees with
-experiment, it's wrong. That's all there is to it.''
-
-\begin{itemize}
-\tightlist
-\item
-  Richard Feynman in \emph{Richard Feynman Messenger Lectures at Cornell
-  University: The Character of Physical Law. Chapter 7, Seeking New
-  Laws}.
-\end{itemize}
-
-\newpage
-
-\section{Abbreviations}\label{abbreviations}
-
-Kullback-Leibler divergence between distributions \(\nu_i\) and
-\(\nu_j\): \(\KL(\nu_i||\nu_j)\).
-
-Binary relative entropy:
-\(d(x,y) := x \log(x/y) + (1-x) \log((1-x)/(1-y))\), where
-\(d(0,0) = d(1,1) = 0\).
-
-Kullback-Leibler divergence for two Bernoulli distributions
-parameterized by their means \(\mu_i\) and \(\mu_j\):
-\(KL_{Ber}(\nu_i||\nu_j) = d(\mu_i, \mu_j)\).
-
-Define exponential family of distributions
-
-Define KL Divergence for this family
-
-\newpage
-
-\section{\texorpdfstring{Introduction
-\label{chap:Introduction}}{Introduction }}\label{introduction}
-
-The thesis at hand joins a large literature concerned with the problem
-of sequential sampling. One is familiar with the idea of ``batch
-sampling'', where the entire sample is gathered first and analyzed only
-after the last sample has become available. However, as noted in
-Chernoff (1958), many situations arise in which one would like to gather
-feedback from samples as they are drawn, so as to influence the choice
-of the next sample. The two fundamental characteristics of the latter
-sampling process are that it is sequential and adaptive. Since
-observations are drawn in sequence, one has a chance to analyze past
-observations in order to adapt the decision of what sample one would
-like to observe next.
-
-This makes sequential sampling especially relevant in situations where
-there is an inherent cost to obtaining samples. The classical example is
-that of clinical trials in which a researcher tests two drugs on
-patients to observe which one performs better. Not only is it difficult
-to gather enough patients, but one would also like to adapt the sampling
-such that as soon as possible more patients receive the better drug and
-are cured. As noted in Cappé et al. (2013), this example dates back to
-Thompson (1933, 1935). Such problems are known as multi-armed bandit
-problems in which the sampling is adapted so as to minimize the
-cumulative regret: In the case of the drug tests, one would like to
-sample the two drugs in a way to find the best drug as soon as possible
-and then to test this drug more and more often and more often than the
-worse drug. This would lead to cumulatively more healthy patients than
-testing both drugs uniformly; it would minimize the regret from treating
-patients with an ineffective drug.
-
-Instead of drugs, one can consider two or more unknown distributions
-(which we call arms in the multi-armed bandit problem in analogy with
-the one-armed bandit slot machine). These distributions have different
-means, and one can draw samples sequentially from the distributions in
-order to estimate their means. To minimize the cumulative regret
-measure, one would like to play the distribution with the highest mean
-as much as possible (\emph{Exploitation}). At the same time, however,
-one has to sample all arms at least a little, so as to initially find
-the best arm (\emph{Exploration}). Any algorithm thus has to handle a
-trade-off between exploration and exploitation to minimize the regret.
-How can we organize the sampling in order to achieve this task?
-
-While Gittins (1979) presents an Bayesian-optimal solution to the
-cumulative regret problem, the Upper-Confidence Bound (UCB) algorithms
-pioneered by Agrawal (1995) and Auer, Cesa-Bianchi and Fischer (2002)
-have lead to a blooming literature on multi-armed bandit problems that
-has been picked up to solve modern problems in website and advertising
-optimization, where advertisers try to allocate their advertising
-optimally so as to reduce regret from showing poorly converting
-advertisements. Several algorithms like the KL-UCB algorithm based on
-Kullback-Leibler divergence upper confidence intervals (Cappé et al.,
-2013) or the Bayes-UCB algorithm (Kaufmann et al., 2012) have followed
-and been shown to be optimal as they reach the lower bound introduced in
-Lai and Robbins (1985) and Burnetas and Katehakis (1996).
-
-These algorithms have in common that they compute after every new sample
-an index for each of the unknown distributions. This index is based
-solely on the past (observed) data, and then used to pick the
-distribution from which the next sample should be drawn. Using these
-indexes, algorithms can sample sequentially and adapt their strategies
-to observations as they are collected.
-
-Similar algorithms based on indexes can be used on related problems.
-Instead of minimizing cumulative regret, it can be of interest to find
-the best arm, that is, the distribution with the largest mean -- with as
-few samples as possible and with confidence as large as possible. This
-is particularly useful when there is not a cost from testing arms with
-lower mean, but when drawing any sample is costly. Thus one needs to
-explore the distributions as efficiently as possible. Exploitation is
-not necessary, and the setting is thus referred to as \emph{Pure
-Exploration}. The need for strategies other than uniform sampling
-arises: One does not want to continue to sample distributions that one
-is confident in. This setting is related to the problem faced in
-Bayesian Optimization: Training large neural networks is costly in terms
-of time and computation, and so the parameter space needs to be explored
-with as few samples as possible. (Zhang et al., 2017; Brochu et al.,
-2010). The problem of best arm identification is also very related to
-statistical hypothesis testing as noted by Chernoff (1958) since one has
-to make a decision about how the means of distributions relate to each
-other. The main difference being that the bandit setting includes the
-testing procedure in the sampling process.
-
-Given the focus on exploration, the pure exploration problem is usually
-described with a loss function different from the one in the cumulative
-regret settings. Audibert et al. (2010) introduce a soft measure called
-\emph{simple regret} based on which they describe UCB policies. Other
-authors investigate binary measures that are equal to 1 when the best
-arm has not been identified (Russo, 2016; Garivier and Kaufmann, 2016).
-These binary measures correspond to the probability of the identified
-arm being the best, and thus inherently related to hypothesis testing.
-The problem of best arm identification can readily be extended to the so
-called Top-\(m\) problem of identifying the best \(m\) of \(K\) arms
-(Kaufmann and Kalyanakrishnan, 2013; Kaufmann et al. 2016).
-
-In this thesis, we consider the thresholding bandit problem. Instead of
-identifying the best \(m\) out of \(K\) arms, we aim to find all
-distributions out of \(K\) that have a mean at least as large as a
-threshold fixed upfront. In the form described in Locatelli et al.
-(2016), algorithms in the thresholding bandit problem are evaluated
-against a binary loss function penalizing whenever an arm has not been
-classified correctly as being above or below the threshold, and thus
-focus on exploration similar to algorithms employed for best arm
-identification. Indeed, Locatelli et al. (2016) show how their
-thresholding algorithm can be used for best arm identification when the
-mean of the best arm is known upfront.
-
-In the following, we first present the thresholding bandit problem in
-detail in \autoref{chap:ThresholdingBanditProblem}. To then extend upon
-the algorithm proposed by Locatelli et al. (2016) and discussed in
-\autoref{sec:TheAPTAlgorithm}, we first explore in
-\autoref{chap:KullbackLeiblerPureExploration} how the Kullback-Leibler
-divergence has been employed in the best arm identification literature
-by Garivier and Kaufmann (2016) and Kaufmann et al. (2016) as this will
-lead us to our own extension. We shortly describe in
-\autoref{sec:VarianceBasedAlgorithms} two variance-based algorithms for
-the thresholding bandit problem introduced in Mukherjee et al. (2017)
-and Zhang et al. (2017), before introducing the new Simple Likelihood
-Ratio algorithm in \autoref{sec:LRforUnivariateExponentialFamily}. We
-end in \autoref{chap:Experiments} with experiments to examine the
-performance of different algorithms.
-
-\newpage
-
-\section{\texorpdfstring{The Thresholding Bandit Problem
-\label{chap:ThresholdingBanditProblem}}{The Thresholding Bandit Problem }}\label{the-thresholding-bandit-problem}
-
-To introduce the thresholding bandit problem, consider a game in which
-the learner is tasked to find the slot machines within a row of \(K\)
-slot machines in a casino that give a mean payoff larger than a fixed
-threshold \(\tau\), for example \(\tau = 0\). The learner cannot pull
-all slot machines at the same time. Instead, he acquires samples
-sequentially from one slot machine at a time to learn about their payoff
-structure. The learner has a budget of \(T>K\) slot machine pulls. After
-\(t-1\) samples, the learner has observed \(T_i(t-1)\) samples from slot
-machine \(i\). The payoffs \(X_{i,1}, ..., X_{i,T_i(t-1)}\) are drawn
-from the payoff distribution \(\nu_i\) underlying the slot machine
-\(i\). At time \(t\), the learner considers the payoffs he observed so
-far in order to choose the next slot machine he would like to pull. Her
-decision is lead by the goal to classify the slot machines with
-distribution \(\nu_i\) and mean payoff
-\(\mu_i = \mathbb{E}_{X \sim \nu_i}[X]\) after \(T\) samples as being
-above or below the threshold with error probability as small as
-possible.
-
-The thresholding bandit problem can thus be framed in the literature on
-sequential sampling strategies. Even though its name is reminiscient of
-the multi-armed bandit setting, the thresholding bandit problem is more
-akin to best arm identification and top-\(m\) identification problems
-due to its focus on exploration: While the classical multi-armed bandit
-problems are concerned with cumulative regret which increases
-\emph{during} sampling, best arm identification and thresholding bandits
-collect loss only once \emph{after} the sampling procedure (compare
-Garivier and Kaufmann, 2016; Kaufmann et al., 2016; Kaufmann and
-Kalyanakrishnan, 2013). As we will see in
-\autoref{chap:KullbackLeiblerPureExploration} there arises an implicit
-threshold between the means of the \(m\)-th best arm and the \(m+1\)-th
-best arm in the top-\(m\) identification problem (Kaufmann et al., 2016;
-Kaufmann and Kalyanakrishnan, 2013). Because of this, the two settings
-are very related.
-
-\subsection{\texorpdfstring{Setup
-\label{sec:Setup}}{Setup }}\label{setup}
-
-Consider a setting with a set of \(\mathbb{A}=\{1, ..., K\}\) unknown
-probability distributions \(\nu_i, i \in \mathbb{A}\). To stick with the
-idea of multi-armed bandits, we call the distributions arms, and
-observations from the arms rewards (Bubeck and Cesa-Bianchi, 2012). The
-learner is interested in learning about the structure of the arms; in
-particular, she would like to estimate the means \(\mu_1, ..., \mu_K\)
-by sequentially drawing observations \(X_{i,1}, X_{i,2}, ...\) from the
-different arms. However, at time \(t\) the learner cannot observe a
-reward from every distribution but must select a single arm \(I_t\) from
-which she would like to observe the reward \(X_{I_t,t}\). Often,
-adaptive sampling strategies makes the decision of which arm to pull by
-computing an index \(B_i(t)\) for each arm. If \(T_i(t)\) is the number
-of samples observed until time \(t\) for arm \(i\), then is \(B_i(t)\) a
-function of the past rewards \(X_{i,1}, ..., X_{i,T_i(t)}\) observed for
-arm \(i\), and w.l.o.g. \(I_t = \arg \min_{i = 1,...K} B_i(t)\). The set
-of indexes can be called strategy (Kaufmann et al., 2012) which makes it
-clear that the strategy is adapted as more observations are collected.
-Strategies of this kind are also called index policies.
-
-Which index proves to be useful is determined by the loss function with
-which the decisions of the algorithm are evaluated. Many problems are
-concerned with finding the arm with the largest mean \(\mu_i^*\) while
-collecting loss either cumulatively during (Auer and Cesa-Bianchi, 2012)
-or once at the end of the sampling (Kaufmann et al., 2016). The
-thresholding bandit problem considers a slightly different loss
-function. Consider a fixed threshold value \(\tau \in \mathbb{R}\) and
-an epsilon interval \(\tau \pm \epsilon\) around the threshold for
-\(\epsilon \geq 0\). As mentioned in the introduction, the learner is
-tasked with classifying arms as having a mean \(\mu_i\) larger or
-smaller than \(\tau\). As in Locatelli et al. (2016), whenever we say
-that ``an arm is over the threshold'', we say that the mean of the arm
-is over the threshold. To describe which arms are over the threshold, we
-also introduce the following set notation: Let \(\mathcal{S}_{u}\) be
-the set of distributions in \(\mathbb{A}\) with mean larger than some
-\(u \in \mathbb{R}\):
-\(\mathcal{S}_{u} := \{i \in \mathbb{A}, \mu_i \geq u\}\). Consequently,
-the complement is given by the arms with mean below \(u\),
-\(\mathcal{S}^C_{u} := \{i \in \mathbb{A}, \mu_i < u\}\).
-
-The thresholding problem for the learner is now to use a budget of
-overall \(T\) samples (or rounds) to explore the different arms. After
-this exploration phase, the learner returns a set of arms that she
-believes to be over the threshold. When evaluating the classification of
-the learner, arms with mean inside of the epsilon interval
-\(\tau \pm \epsilon\) will not be considered. The learner only has to
-correctly distinguish the means from the threshold up to the precision
-given by \(\epsilon\). Thus, the algorithm is not evaluated against
-\(\mathcal{S}_{\tau}\) and \(\mathcal{S}^C_{\tau}\), but needs to
-distinguish \(\mathcal{S}_{\tau+\epsilon}\) from
-\(\mathcal{S}^C_{\tau-\epsilon}\).
-
-The learner's classification is returned as the set
-\(\hat{\mathcal{S}}_{\tau} := \hat{\mathcal{S}}_{\tau}(T) \subset \mathbb{A}\)
-after \(T\) rounds; that is, the set of arms estimated to be over the
-threshold. The classification is evaluated against the loss given as
-(Locatelli et al., 2016):
-
-\[
-\mathcal{L}(T) = \mathbbm{1}{\big((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \lor (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset)\big)}
-\]
-
-In order to perform well, a learner has to identify all arms that are
-over the threshold as such, and to not claim arms as being over the
-threshold if they actually are below the threshold. Due to the precision
-\(\epsilon\), the loss is not influenced by arms which are very close to
-the threshold \(\tau\) as measured by \(\epsilon\), that is, arms inside
-of the \(\tau \pm \epsilon\) interval. If either
-\(\hat{\mathcal{S}}_{\tau}\) contains an arm below
-\((\tau - \epsilon)\), or \(\hat{\mathcal{S}}^C_{\tau}\) contains an arm
-above \((\tau + \epsilon)\), a loss of \(1\) is accrued. Else, all arms
-outside the epsilon interval are classified correctly and the loss is
-equal to \(0\). In the case of \(\epsilon = 0\), all arms need to be
-classified correctly to not collect any loss.
-
-Algorithms for this thresholding problem can be compared based on their
-expected loss. Let \(\mathbb{E}\) be the expectation with regard to the
-samples \(X_{i,1}, ..., X_{i,T}\) collected by the algorithm. The
-expected loss is then given as
-
-\[
-\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}\big((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \lor(\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset)\big),
-\]
-
-which corresponds to the probability of making at least one wrong
-classification. Both the probability of not identifying an arm that is
-actually over the threshold, as well as the probability of accepting an
-arm as over the threshold when it is not, are evaluated. The oracle
-strategy would evaluate all arms correctly with an error probability of
-\(0\) (Locatelli et al., 2016).
-
-At this point, we have introduced the general thresholding bandit
-problem setting which we will use throughout the thesis. The setting can
-be extended by different assumptions to make certain algorithms or
-bounds feasible. For that reason, Locatelli et al. (2016) assume that
-the distributions \(\nu_i, i \in \mathbb{A}\) are \(R\)-sub-Gaussian.
-Under this assumption, the authors are able to prove a lower bound on
-the largest probability of error of the best algorithm in the setting we
-have just introduced, as well as an upper bound on the performance of
-their APT algorithm which we will introduce in the following chapter. As
-in their paper, we define \(R\)-sub-Gaussian and assume it in the
-description of the their algorithm and bounds:
-
-\begin{definition}[$R$-sub-Gaussian distribution] 
-\label{definition:rsubgaussian}
-Let $R > 0$. A distribution $\nu$ is $R$-sub-Gaussian if for all $t \in \mathbb{R}$ we have
-\begin{equation*}
-\mathbb{E}_{X \sim \nu}[\exp(tX - t\mathbb{E}[X])] \leq \exp(R^2t^2/2).
-\end{equation*}
-\end{definition}
-
-As noted by Locatelli et al. (2016), this ensures that the mean
-\(\mu_i\) of the distributions \(\nu_i\) considered in our problem are
-finite. \(R\)-sub-Gaussian distributions offer concentration
-inequalities for the concentration of the empirical mean around the true
-mean, which makes it possible to deduce the bounds presented by the
-authors and repeated below. The family of \(R\)-sub-Gaussian
-distributions encompasses Gaussian distributions of variance \(R^2\) for
-\(R \in \mathbb{R}\), as well as all bounded distributions, with the
-important case of Bernoulli distributions.
-
-Having described the thresholding bandit setting as well as the
-assumption of \(R\)-sub-Gaussianity, we can now proceed to describe the
-\emph{Anytime Parameter-free Thresholding} (APT) algorithm proposed in
-Locatelli et al. (2016) for the thresholding bandit problem.
-
-\subsection{\texorpdfstring{The Anytime Parameter-free Thresholding
-Algorithm
-\label{sec:TheAPTAlgorithm}}{The Anytime Parameter-free Thresholding Algorithm }}\label{the-anytime-parameter-free-thresholding-algorithm}
-
-In the following we describe the \emph{Anytime Parameter-free
-Thresholding} (APT) algorithm proposed in Locatelli et al. (2016), which
-is a simple yet effective algorithm and displays some very favorable
-characteristics when compared to alternative algorithms.
-
-We fix the threshold \(\tau\) and epsilon interval around the threshold
-given by \(\epsilon\) upfront, and supply them as arguments to the
-algorithm: \((\tau, \epsilon)\). Based on the general thresholding
-problem, we demand that the algorithm draws samples \(X_{i,t}\) for
-\(T\) rounds from the distributions \(\nu_i, i\in \mathbb{A}\). For a
-given arm \(i\) and a given time \(t\), we let \(T_i(t)\) represent the
-number of samples drawn from arm \(i\) until time \(t\) (including).
-Consequently, the empirical mean of arm \(i\) at time \(t\) is given by
-\(\hat{\mu}_i(t) = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}\) where
-\(X_{i,s}\) is the feedback sampled from distribution \(\nu_i\) when the
-arm is pulled for the \(s\)-th time. In the case of the APT algorithm,
-the decision \(\hat{\mathcal{S}}_{\tau}\) is based on the empirical
-means \(\hat{\mu}_i(T)\) estimated from the samples drawn up to time
-\(T\):
-\(\hat{\mathcal{S}}_{\tau} := \hat{\mathcal{S}}_{\tau}(T) = \{i \in \mathbb{A}, \hat{\mu}_i(T) \geq \tau\}\).
-
-As we see in algorithm \ref{alg:APT}, the APT algorithm initiates by
-pulling each arm once. Then, for each \(t > K\), it calculates for every
-arm the values \(T_i(t)\) and \(\hat{\mu}_i(t)\). Based on the empirical
-mean, the algorithm computes the estimated gap between the mean and the
-threshold as
-\(\hat{\Delta}_i(t) = \hat{\Delta}_i^{\tau, \epsilon}(t) = |\mu_i(t) - \tau| + \epsilon\).
-The decision of which arm is sampled next is then based on the value
-\(B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t)\): the algorithm pulls arm
-\(I_{t+1} = \arg \min_{i\leq K} B_i(t+1)\) minimizing this decision
-quantity. After overall \(T\) pulls, the algorithm returns the sets
-described in the general setup, \(\hat{\mathcal{S}}_{\tau}\) and
-\(\hat{\mathcal{S}}^C_{\tau}\).
-
-\IncMargin{1em}
-
-\begin{algorithm}
-\SetKwData{Left}{left}\SetKwData{This}{this}\SetKwData{Up}{up}
-\SetKwFunction{Union}{Union}\SetKwFunction{FindCompress}{FindCompress}
-\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
-\Input{$\tau$, $\epsilon$}
-\Output{$\hat{S}_{\tau} = \{i \in \{1,...,K\}, \hat{\mu}_i(T) \geq \tau\}$}
-\BlankLine
-\emph{Pull each arm once}\;
-\For{$t = K+1$ \KwTo $T$}{
-  \emph{Pull arm $I_t = \arg \min_{i \in A} B_i^{APT}(t) = \arg \min_{i \in A} \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau|+\epsilon)$}\;
-  \emph{Observe reward $X_t \sim \nu_{I_t}$}\;
-}
-\caption{Anytime Parameter-free Thresholding Algorithm (Locatelli et al., 2016)}\label{alg:APT}
-\end{algorithm}
-
-\DecMargin{1em}
-
-Just like the general index policies mentioned in \autoref{sec:Setup},
-we see that the APT algorithm adapts its strategy using an index
-\(B_i(t+1)\) for each arm that is based entirely on the observations
-observed until time \(t\). Given the arm with the smallest index is
-pulled at round \(t+1\), we observe that arms that are estimated to be
-further away from the threshold \(\tau\) as measured by the absolute
-distance to their empirical mean \(\hat{\mu}_i\), \(\hat{\Delta}_i(t)\),
-are pulled less often. Intuitively, it is easier to classify arms as
-below or above \(\tau\) when their mean is far away from the threshold.
-In contrast to the uniform sampling strategy, APT will gather more
-evidence for arms which appear to be inherently more difficult to
-classify. Likewise, APT tends to less often pull arms which it already
-pulled considerably often as measured by \(T_i(t)\). If arm \(i\) has
-been pulled more often than arm \(j\), then we should in general be more
-confident in its estimated mean and the corresponding distance to the
-threshold. If we are confident in \(i\), then it is better to explore
-other arms by drawing an observation from arm \(j\). By adapting its
-sampling strategy in this way during the sequential sampling process,
-the APT algorithm minimizes the probability of error
-\(\mathbb{E}[\mathcal{L}(T)]\) after \(T\) samples have been observed.
-
-The previous paragraph describes how arms close to the threshold are
-intuitively more difficult to classify. In the index employed by the APT
-algorithm, the distance between an arm and the threshold is measured by
-the absolute distance \(\hat{\Delta}_i(t)\) between the (estimated) mean
-of the arm and the threshold \(\tau\) (and the epsilon interval). When
-the APT algorithm realizes that an arm has a mean close to the
-threshold, then this arm requires more attention than an arm far away
-from the threshold; the confidence in the empirical mean has to be
-larger. Or the empirical mean has to be better concentrated around the
-true mean. Otherwise it is easier to make a mistake on this arm. To gain
-this confidence, the arm requires more samples, and thus a larger share
-of the overall \(T\) samples available. With this intuition, it makes
-sense to measure the complexity of a thresholding problem: If we knew
-upfront how complex a given set of arms is, we would know whether to
-expect a small or large probability of error given our budget \(T\).
-Also, for example in the best arm identification problem, there exist
-algorithms which take the complexity of a problem as input. Based on the
-complexity they then adapt their sampling strategy. See for example the
-UCB-E algorithm in Audibert et al. (2010) for the best arm
-identification problem, or the KL-LUCB-E algorithm in Kaufmann and
-Kalyanakrishnan (2013) as extension to the top-\(m\) problem.
-
-While the APT algorithm does not require the complexity to be known
-upfront (which would be problematic as it is not known upfront), it is
-necessary to define the complexity to deduce the upper bound on its
-probability of error. Similar to the distance measure used in the
-algorithm's index, we define the gap \(\Delta_i^{\tau,\epsilon}\)
-between arm \(i\) and the threshold \(\tau \pm \epsilon\) as
-
-\[
-\Delta_i := \Delta_i^{\tau,\epsilon} = |\mu_i - \tau| + \epsilon
-\]
-
-Given this gap, Locatelli et al. (2016) define the complexity
-\(H_{\tau, \epsilon}\) for the thresholding bandit problem naturally as
-
-\[
-H := H_{\tau, \epsilon} = \sum_{i=1}^K \frac{1}{(\Delta_i^{\tau,\epsilon})^2}.
-\]
-
-Note that the complexity of the problem increases in the number of arms
-\(K\) and decreases in the gap \(\Delta_i^{\tau,\epsilon}\).
-Consequently, when we require less precision, that is, we increase
-\(\epsilon\), the hardness decreases. Furthermore, we see that each arm
-contributes its individual complexity,
-\(h_i^{\tau,\epsilon} = \frac{1}{(\Delta_i^{\tau,\epsilon})^2}\)
-linearly into the problem. Thus, if the complexity \(H\) is a good
-measure of the actual problem complexity, and we knew upfront which arm
-has which mean, we could allocate the ``optimal'' share of the budget,
-\(T \cdot h_i /H\) to arm \(i\). However, since we do not know neither
-\(\mu_i\) nor \(H\) upfront, the best we can do is to adapt our
-allocation of samples more and more towards this optimum as we observe
-samples.
-
-At this point, one can question whether the measure of complexity \(H\)
-proposed in Locatelli et al. (2016) is a good measure of the ``true''
-problem complexity. In the following \autoref{sec:UpperBoundLocatelli},
-we will show the upper bound on the probability of error for the APT
-algorithm and see how the complexity \(H\) arises naturally for the APT
-algorithm. In \autoref{sec:LowerBoundLocatelli} we then show the lower
-bound presented in Locatelli et al. (2016) and that the APT algorithm is
-optimal in that it matches the lower bound. We discuss the results and
-the APT algorithm further in \autoref{sec:DiscussionLocatelli}.
-
-\subsection{\texorpdfstring{Upper Bound for the APT Algorithm
-\label{sec:UpperBoundLocatelli}}{Upper Bound for the APT Algorithm }}\label{upper-bound-for-the-apt-algorithm}
-
-In this chapter we present the upper bound on the probability of error
-that the APT algorithm incurs, as proven in Locatelli et al. (2016). The
-upper bound is on the probability of error that the algorithm has after
-\(T\) rounds of sampling for a problem with arms that are assumed to be
-\(R\)-sub-Gaussian. The bound depends also on the complexity of the
-problem, and we show in the proof that given the index of the APT
-algorithm as defined in \autoref{sec:TheAPTAlgorithm}, the complexity
-\(H\) is an appropriate measure.
-
-We now state the theorem as in Locatelli et al. (2016) and present a
-proof.
-
-\begin{theorem}[Theorem 2, Locatelli et al., 2016] \label{theorem:LocatelliTheorem4}
-Let $K \geq 0$, $T \geq 2K$, and consider a problem $\mathcal{B}$.
-Assume that all arms $\nu_i$ of the problem are R-sub-Gaussian with means $\mu_i$.
-Let $\tau \in \mathbb{R}, \epsilon \geq 0$.
-Algorithm APT's expected loss is upper bounded on this problem as
-\begin{equation*} \mathbb{E}(\mathcal{L}(T)) \leq \exp
-\Big(-\frac{1}{64R^2}\frac{T}{H} + 2 \log((\log(T) + 1)K)\Big) \end{equation*}
-
-where we remind that $H = \sum_i (|\mu_i - \tau | + \epsilon)^{-2}$ and where
-$\mathbb{E}$ is the expectation according to the samples of the problem.
-\end{theorem}
-
-\subsubsection{\texorpdfstring{Proof of Theorem
-\ref{theorem:LocatelliTheorem4}}{Proof of Theorem }}\label{proof-of-theorem}
-
-In order to upper bound the expected loss of the APT algorithm, we want
-to define an event on which the algorithm correctly seperates arms from
-the threshold, that is, a separation condition holds on this event. We
-then want to show that this \emph{favorable} event does indeed hold with
-large probability. Consequently, APT's probability of error will
-correspond to the probability that the favorable event does not hold, as
-this leads to a failure of the seperation condition, and consequently to
-an incorrect classification of at least one arm by the algorithm. We
-start by defining the separation condition.
-
-\subsubsection{Separation Condition}\label{separation-condition}
-
-As noted in Zhong et al. (2017), a simple requirement to correctly
-classify arms at the final round is the following. For every arm
-\(i \in \{1, ..., K\}\) after the final round \(T\), require \[
-\hat{\mu}_{i}(T) \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
-\] or \[
-\hat{\mu}_{i}(T) \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
-\] Or simply in terms of the gap between the arm and the threshold as
-used in the index by the APT algorithm: \[
-| \hat{\mu}_{i}(T) - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
-\]
-
-Intuitively, this condition makes sense as it ensures that the current
-mean estimate is closer to the true mean than to the threshold.
-Consequently, there is no arrangement possible in which the arm is
-classified wrong while the separation condition holds. Assuming
-\(\mu_i < \tau\) and \(\epsilon = 0\), an incorrect classification would
-require \(\mu_i < \tau \leq \hat{\mu_i}\). But then
-\(| \hat{\mu}_{i}(T) - \mu_i | \geq |\mu_i - \tau|\), which violates the
-separation condition.
-
-Thus, we need to show that this condition holds for every arm
-\(i \in \{1,...,K\}\) with large probability after the final round
-\(T\). In different words, we need to derive an upper bound on the
-probability with which this condition does not hold.
-
-\subsubsection{The Favorable Event}\label{the-favorable-event}
-
-The separation condition describes what event needs to hold in order for
-the APT algorithm to make a correct classification: The smaller the
-deviation of the empirical mean from the population mean, the more
-difficult it is for the classification to be wrong. Moreover, if the
-mean and empirical mean are identical, then the classification is
-correct independent of the threshold. Also, the closer the mean to the
-threshold, the better the estimate has to be for a correct
-classification to be likely. To bound the absolute deviation of the
-empirical mean from the true mean, we define the favorable event \(\xi\)
-as
-
-\[
-\xi = \Big\{\forall i \in \mathbb{A}, \forall s \in \{1,...,T\} : |\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}} \Big\}.
-\]
-
-The probability that this favorable event occurs should be large, or
-equivalently, the probability that the deviation is small should be
-large. Then it follows that the separation condition holds with large
-probability.
-
-We know that \(X_i\) are \(R\)-sub-Gaussian by assumption. That is, we
-have
-
-\[
-\mathbb{E}[\exp (tX_{i,s}-t\mathbb{E}[X_{i,s}])] = \mathbb{E}[\exp (t(X_{i,s}-\mathbb{E}[X_{i,s}]))] \leq \exp (R^2t^2/2)
-\]
-
-where the RHS is the moment-generating function of the random variable
-\(X_{i,s}-\mathbb{E}[X_{i,s}]\). While Höffding's Lemma and Höffding's
-Inequality are commonly applied to bounded random variables \(Z\) with
-\(\mathbb{P}(a\leq Z \leq b) = 1\) and \(\mathbb{E}[Z] = 0\), we see
-that \(Z\) are \(R\)-sub-Gaussian with \(R^2 = \frac{(a-b)^2}{4}\).
-Using this last equality, we can easily apply Höffding's Inequality to
-our case.
-
-\begin{lemma}[Höffding's Inequality (Kloft Lecture Notes)] \label{lemma:HoeffdingsInequality}
-Let $X_1, ..., X_s$ be independent, identically distributed random variables with mean $\mathbb{E}[X_t] = \mu$ and $\mathbb{P}(a_t \leq X_t - \mathbb{E}[X] \leq b_t) = 1$.
-Denote their empirical mean by $\bar{X}_s=\frac{1}{s}\sum_{t=1}^{s}X_t$.
-Then, for any $\gamma > 0$, we have the following concentration inequality:
-
-\begin{equation*}
-\mathbb{P}(|\bar{X}_s - \mu| \geq \gamma) \leq 2\exp (-2s^2\gamma^2/\sum_{t=1}^s(b_t - a_t)^2).
-\end{equation*}
-\end{lemma}
-
-If we replace \(\sum_{t=1}^s(b_t - a_t)^2\) by \(4sR^2\), we have the
-concentration inequality for our \(R\)-sub-Gaussian random variables:
-
-\[
-\mathbb{P}(|\bar{X}_s - \mu| \geq \gamma) \leq 2\exp (-\frac{s\gamma^2}{2R^2}).
-\]
-
-Writing \(\gamma = \sqrt{\frac{T\delta^2}{Hs}}\), we get for the
-favorable event
-\(\xi_i = \{|\bar{X}_s - \mu| \leq \sqrt{\frac{T\delta^2}{Hs}}\}\) of an
-individual arm \(i\), for each \(i \in \mathbb{A}\) and each
-\(s \in \{1, ..., T\}\):
-
-\[
-\mathbb{P}(\xi_i) = \mathbb{P}\Big(|\bar{X}_{i,s} - \mu_i| \leq \sqrt{\frac{T\delta^2}{Hs}}\Big) \geq 1 - 2\exp (-\frac{T\delta^2}{2R^2H}),
-\] where \(T\) is again the total budget of samples, and \(H\) the
-complexity. Now let
-
-\[
-\tilde{\xi} = \Big\{\forall i \in \mathbb{A}: |\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}} \Big\}.
-\]
-
-To derive the probability of event \(\tilde{\xi}\), we apply a union
-bound on \(\mathbb{P}(\cup_{i=1}^K \xi_i^C)\):
-
-\begin{align*}
-\mathbb{P}(\tilde{\xi}) & = 1-\mathbb{P}(\xi^C) \\
-& = 1-\mathbb{P}(\cup_{i=1}^K \xi_i^C) \\
-& \geq 1 - \sum_{i=1}^K \mathbb{P}(\xi_i^C) \\
-& \geq 1 - 2K\exp (-\frac{T\delta^2}{2R^2H})
-\end{align*}
-
-We could use the same union bound a second time to bound over all
-\(s \in \{1, ..., T\}\) and derive for the favorable event \(\xi\):
-
-\[
-\mathbb{P}(\xi) \geq 1 - 2TK \exp(-\frac{T\delta^2}{2R^2H})
-\]
-
-Locatelli et al. (2016) use instead of Höffding's inequality a
-Sub-Gaussian martingale inequality including a peeling argument in order
-to derive a better bound of
-
-\[
-\mathbb{P}(\xi) \geq 1 - 2(\log(T) +1)K \exp(-\frac{T\delta^2}{2R^2H})
-\]
-
-This bound is non-trivial for much smaller values of \(T\), and we will
-use it in the following.
-
-\subsubsection{\texorpdfstring{Need to Bound
-\(T_i\)}{Need to Bound T\_i}}\label{need-to-bound-t_i}
-
-We now have that with large probability the favorable event holds. On
-the favorable event, we have for every arm \(i\):
-
-\[
-| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}
-\]
-
-The deviation of arm \(i\) at time \(t\) depends on how large \(H\),
-\(T\), and \(T_i(t)\) are. While \(t\), \(H\), \(T\) are deterministic,
-the number of times arm \(i\) has been pulled at round \(t\),
-\(T_i(t)\), is a random variable. In order to know how large the
-probability of the favorable event is (and thus the error probability),
-we need to know the value of \(T_i(t)\), or at least bound a range of
-potential values. Put differently: To ensure a deviation smaller than
-\(\sqrt{\frac{T\delta^2}{HT_i(t)}}\) for arm \(i\), we need to ensure
-that arm \(i\) has been pulled at least \(T_i(t)\) times. As usual in
-multi-armed bandits, and different from uniform sampling, the number of
-pulls is a random variable that also depends on how often other arms are
-pulled. In general, we do not want each arm to be pulled an equal
-amount, but each arm should be pulled some times, and not too many
-times.
-
-Thus, in order to check that the deviation of arm \(i\) really is small
-enough for the separation condition to hold on the favorable event, we
-need to bound the number of pulls of every arm from below.
-
-\subsubsection{\texorpdfstring{Characteristics of a Frequently Pulled
-Arm (Lower Bound on
-\(T_k(T)\))}{Characteristics of a Frequently Pulled Arm (Lower Bound on T\_k(T))}}\label{characteristics-of-a-frequently-pulled-arm-lower-bound-on-t_kt}
-
-Given that we do not follow a uniform sampling strategy, we know that at
-time \(T\), some arms will have been pulled more frequently than others.
-In particular, some arms will have been pulled more than \(T/K\) times.
-How often an arm is pulled can be related to the individual arm's
-contribution to the overall complexity measure. Let \(h_i\) be a measure
-of arm \(i\)'s individual problem complexity and write for the overall
-problem complexity \(H = \sum_{i = 1}^{K} h_i\). Then arm \(i\)
-contributes a share of \(h_i/H\) to the overall problem complexity. We
-can now show that there exists an arm that has been pulled at least as
-often as the share of his complexity contribution.
-
-Given the initialization of the APT algorithm, every arm is pulled once
-initially. Consequently, there is a budget of \(T-K\) rounds left after
-the initialization. As shown in Locatelli et al. (2016), there exists an
-arm \(k\) that has been pulled after the initialization (\(\geq 2\)
-pulls) and for which at the final round \(T\) it holds:
-\(T_k(T) - 1 \geq \frac{(T-K)h_k}{H}\). This can be shown by a
-contradiction. Assume that the opposite holds, that is
-
-\[
-\forall i \in \{1,...,K\}: T_i(T) - 1 < \frac{(T-K)h_i}{H}
-\]
-
-Consequently, at time \(T\), we would have pulled across all arms
-\(\sum_{i=1}^KT_i(T)-1\) times. If the previous assumption holds, we
-would not have used the entire budget:
-
-\[
-\sum_{i=1}^K T_i(T)-1 < \sum_{i=1}^K \frac{(T-K)h_i}{H} = (T-K)\sum_{i=1}^K \frac{h_i}{H} = T-K
-\]
-
-This is a contradiction, since as an requirement to the algorithm we
-have that \(\sum_{i=1}^K T_i(T)-1 = (T-K)\), that is, we use the entire
-budget of samples.
-
-Furthermore, we have assumed \(T>2K\) in the statement of Theorem
-\ref{theorem:LocatelliTheorem4}. Plugging this in gives \[
-T_k(T) - 1 \geq \frac{(T-K)h_k}{H} \geq \frac{(T-1/2T)h_k}{H} = \frac{Th_k}{2H}
-\]
-
-Now we know how often the arm has been pulled at the very end. That does
-not mean that \(k\) has been pulled at time \(T\). Thus we consider the
-time \(t \leq T\) at which arm \(k\) is pulled for the last time. We get
-
-\[
-T_k(t) \geq T_k(T) - 1 \geq \frac{Th_k}{2H}.
-\]
-
-This gives us a lower bound on how often arms are pulled that are pulled
-frequently relative to their contribution to the problem complexity. Now
-we need a lower bound on \(T_i(T)\) for every other arm \(i\).
-
-\subsubsection{\texorpdfstring{Lower Bound on
-\(T_i(T)\)}{Lower Bound on T\_i(T)}}\label{lower-bound-on-t_it}
-
-Consider again as before the round \(t\) at which arm \(k\) is pulled
-for the very last time. Since the APT algorithm minimizes at every round
-\(s \geq K+1\) the index \(B_j(s)\), and pulls the arm with the smallest
-index, we know that arm \(k\) must have had the smallest index at round
-\(t\). We have:
-
-\[
-B_k(t) \leq B_i(t) \Leftrightarrow \sqrt{T_k(t)}\hat{\Delta}_k(t) \leq \sqrt{T_i(t)} \hat{\Delta}_i(t)
-\]
-
-One can already expect that this can be used to derive a lower bound on
-\(T_i(t)\) on the RHS, and this is exactly what we do. On the LHS, we
-plug in the lower bound for \(T_k(t)\) derived before. Additionally
-bounding \(\Delta_k(t)\) from below, and \(\hat{\Delta}_i(t)\) from
-above using the favorable event will give the desired lower bound.
-
-Thus assume we are on the favorable event \(\xi\) with large
-probability. we consequently have
-
-\[
-| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}.
-\]
-
-As shown in Locatelli et al. (2016), one can use the reverse triangle
-inequality to get:
-
-\begin{align*}
-|\hat{\mu}_i(t) - \mu_i| & = |(\hat{\mu}_i(t) - \tau) - (\mu_i - \tau)| \\
-& \geq || \hat{\mu}_i(t) - \tau | - |\mu_i - \tau|| \\
-& \geq |(|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i - \tau| + \epsilon)| \\
-& \geq |\hat{\Delta}_i(t) - \Delta_i|
-\end{align*}
-
-If we combine this with the favorable event, we get
-
-\[
-\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}} \leq \hat{\Delta}_k(t) \leq \Delta_k + \sqrt{\frac{T\delta^2}{HT_k(t)}}
-\]
-
-and similar for \(\hat{\Delta}_i\). We can now lower bound the LHS of
-the indexes as
-
-\begin{align*}
-B_k(t) & \geq \Big(\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}}\Big) \sqrt{T_k(t)} \\
-& \geq \Big(\Delta_k - \sqrt{\frac{2}{h_k}}\delta \Big)
-\end{align*}
-
-At this point, it is useful to have a well chosen complexity measure. If
-we set \(h_i = \frac{1}{\Delta_i^2}\) as in Locatelli et al. (2016), we
-get
-
-\[
-\Big(\Delta_k - \sqrt{2}\delta \Delta \Big) \sqrt{\frac{T}{2H\Delta_k^2}} \leq B_k(t)
-\]
-
-which can be now be reduced to a form that is not specific to \(k\):
-
-\[
-\Big( \frac{1}{\sqrt{2}} - \delta \Big) \sqrt{\frac{T}{H}} \leq B_k(t).
-\]
-
-Now we need to remove \(\hat{\Delta}_i\) in order to bound \(T_i(t)\).
-Thus, we bound the RHS again using the favorable event much as we did
-for the LHS:
-
-\[
-B_i(t) = \hat{\Delta}_i \sqrt{T_i(t)} \leq \Big(\Delta_i + \sqrt{\frac{T\delta^2}{HT_i(t)}}\Big) \sqrt{T_i(t)} \leq \Delta_i \sqrt{T_i(t)} + \delta \sqrt{\frac{T}{H}}
-\]
-
-As in Locatelli et al. (2016) we use the fact that by definition
-\(\Delta\) and \(\hat{\Delta}\) are positive in order to square both
-sides and write
-
-\[
-(1 - 2\sqrt{2}\delta)^2 \frac{T}{2H\Delta^2_i} \leq T_i(t) \leq T_i(T)
-\]
-
-We thus have derived a lower bound on the amount of pulls for any arm.
-That means that we can show that no arm is pulled an insufficient amount
-of times with large probability, and that consequently the favorable
-event hold and the estimated mean is sufficienctly separated from the
-threshold.
-
-\subsubsection{Check Separation
-Condition}\label{check-separation-condition}
-
-As the last step, we need to check whether the lower bound on the pulls
-of any arm suffices to ensure that the separation condition holds on the
-favorable event. That means, given
-\(T_i(T) \geq (1-2\sqrt{2}\delta)^2 \frac{T}{2H\Delta_i^2}\), do we have
-\(|\hat{\mu}_i(T) - \mu | \leq \frac{\Delta}{2}\) on the favorable event
-\(\xi = \Big\{|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}}\Big\}\)?
-To check, we plug the lower bound into the favorable event and get
-
-\[
-|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}} \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}
-\] Using \(\delta = (4\sqrt{2})^-1\) as in Locatelli et al. (2016), we
-have that the separation condition holds exactly:
-
-\[
-|\hat{\mu}_i - \mu | \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta} \leq \frac{1}{2}\Delta_i.
-\]
-
-\subsubsection{Upper Bound on Error
-Probability}\label{upper-bound-on-error-probability}
-
-We have seen that on the favorable event \(\xi\), which holds with large
-probability \(\mathbb{P}(\xi)\), the separation condition holds as all
-arms have been pulled a sufficient number of times, such that their
-estimated mean is close to the true mean. All arms are classified
-correctly, and the algorithm does not suffer a loss. On the other hand,
-we make an error whenever the favorable event does not hold after all;
-that is, the deviation bound for the mean does not hold. At least one
-arm is misclassified and the arm suffers a loss. This occurs with
-probability \(1-\mathbb{P}(\xi)\). Consequently, the expected loss is
-upper bounded by
-
-\[
-\mathbb{E}[\mathcal{L}(T)] = 1 - \mathbb{P}(\xi) \leq 2(\log(T)+1)K \exp(-\frac{1}{64R^2}\frac{T}{H}).
-\]
-
-We now present the lower bound given in Locatelli et al. (2016) for the
-thresholding bandit problem. In order to derive the bound, a problem is
-specified to show that the error of the lower bound is attained even in
-this specific problem. In particular, for a set of problems with
-Gaussian distributions of variance \(1\), the largest probability of
-error on these problems that the best algorithm exhibits is still at
-least as large as the lower bound.
-
-\subsection{\texorpdfstring{Lower Bound for the Thresholding Bandit
-Problem
-\label{sec:LowerBoundLocatelli}}{Lower Bound for the Thresholding Bandit Problem }}\label{lower-bound-for-the-thresholding-bandit-problem}
-
-Locatelli et al. (2016) also provide a general lower bound on the
-probability of error in the thresholding bandit problem. The bound is
-derived for a specified set of problems through a change in distribution
-as common in the multi-armed bandit literature (compare for example
-Audibert et al., 2010, or Kaufmann et al., 2016). For any of these
-problems, the largest probability of error that the best algorithm
-incurs is still lower bounded by the bound given below.
-
-\begin{theorem}[Theorem 1, Locatelli et al., 2016] 
-\label{theorem:Locatelli2016Theorem1}
-For any sequence of gaps $(d_k)_k$, define a finite set of problems with Gaussian distributions with means corresponding to the gaps, and with variance 1.
-Lower bound the largest probability of error among these problems for the best possible algorithm as follows.
-Let $K,T \geq 0$.
-Let for any $i \leq K$, $d_i \geq 0$.
-Let $\tau \in \mathbb{R}, \epsilon > 0$.
-
-For $0 \leq i \leq K$, we write $\mathcal{B}^i$ for the problem where the distribution of arm $j \in \{1, \dots, K\}$ is $\mathcal{N}(\tau+d_i+\epsilon, 1)$ if $i \neq j$ and $\mathcal{N}(\tau-d_i-\epsilon, 1)$ otherwise.
-For all these problems, $H := H_{\tau, \epsilon} = \sum_i (d_i+2\epsilon)^{-2}$ is the same by definition.
-
-It holds that for any bandit algorithm,
-
-\begin{equation*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) \geq \exp(-3T/H-4 \log(12(\log(T)+1)K)),
-\end{equation*}
-
-where $\mathbb{E}_{\mathcal{B}^i}$ is the expectation according to the samples of problem $\mathcal{B}^i$.
-\end{theorem}
-
-A proof of the lower bound is given in the Appendix in
-\autoref{sec:AppendixAPTLB}.
-
-If we write the lower bound as
-\(LB = 12(\log(T)+1)K)\exp(-3T/H)\exp(-4) = C_{LB}(\log(T)+1)K\exp(-T/H)\)
-and the upper bound as
-\(UB = (\log(T)+1)K \exp(2) \exp(-\frac{1}{64R^2}\frac{T}{H}) = C_{UB}(\log(T)+1)K\exp(-T/H)\),
-we see that \(LB\) and \(UB\) match up to multiplicative constants and
-the \((\log(T)+1)K\) term which is negligiable in comparison with the
-exponent for large \(T\) as shown in Locatelli et al. (2016), which
-makes the APT algorithm order optimal.
-
-\subsection{\texorpdfstring{Discussion
-\label{sec:DiscussionLocatelli}}{Discussion }}\label{discussion}
-
-\begin{itemize}
-\tightlist
-\item
-  Mention Optimality (Upper Bound matches lower bound)
-\item
-  Anytime
-\end{itemize}
-
-One of the APT algorithm's main features is its simplicity. The sampling
-rule is very straightforward, and, as highlighted in Locatelli et al.
-(2016), it does not require any knowledge about the type of
-sub-Gaussianity \(R\), or the complexity \(H\) upfront. This makes the
-algorithm immediately applicable in practice while it still enjoys its
-upper bound on the expected regret. This is in particular worth
-highlighting when comparing APT to algorithms used in the best arm
-identification or Top-\(m\) setting. As alluded to in
-\autoref{sec:TheAPTAlgorithm}, many algorithms that fix the sampling
-budget upfront (i.e., fixed budget algorithms as UCB-E or KL-LUCB-E)
-require knowledge about the corresponding complexity upfront (Audibert
-et al., 2010; Kaufmann and Kalyanakrishnan, 2013). The problem however
-being, that to know the complexity, the experimenter has to know all
-means up to a permutation of the arms. This, of course, is not given in
-practice. Thus alternative algorithms try to estimate the complexity
-online which can be difficult as especially in the beginning plug-in
-estimates based on the estimated means may lead to wrong estimates of
-the complexity, which in turn leads to poor budget allocation based on
-mistaken beliefs (compare Garivier and Kaufmann, 2016). On the other
-hand, the sequential sampling strategy has to rely on some estimate.
-While the APT algorithm does not explicitly estimate the complexity, the
-gaps that serve as index are essentially the same. Faced not with
-sub-Gaussian but more heavy-tailed distributions, these estimates might
-well lead to poor performance.
-
-Here, the APT algorithm shows room for improvement, as also mentioned in
-Locatelli et al. (2016). The problem is that the assumptions for the
-bounds no longer hold as arms are less sub-Gaussian; of course the
-complexity \(H\) and the term \(\hat{\Delta}_i(t)\) in the algorithm's
-index are motivated by sub-Gaussian distributions. The more one moves
-away from those, the less appropriate these quantities become. In
-particular, the empirical mean will be less (or not at all) concentrated
-around the true mean and more impacted by outliers which are more likely
-under non sub-Gaussian distributions. Locatelli et al. (2016) thus
-refers to Bubeck et al. (2013a) which considers solutions for
-multi-armed bandits that are based on heavy-tail distributions. By using
-more robust estimators of the mean, one could equip the APT algorithm to
-deal with such distributions.
-
-Both Mukherjee et al. (2017) as well as Zhong et al. (2017) use
-estimates of the variance of the arms for their algorithms for the
-thresholding bandit problem and try to thereby improve upon the
-performance of the APT algorithm. While their simulations show promising
-results, their bounds rely on the assumption of bounded reward
-distributions. Thus their algorithms are not necessarily able to improve
-upon the assumption of sub-Gaussian distributions made by Locatelli et
-al. (2016). We will continue to discuss their results in
-\autoref{chap:VarianceBasedAlgorithms}.
-
-Yet another idea, again mentioned in Locatelli et al. (2016) is to show
-bounds based on the Kullback-Leibler divergence of the specific
-distribution directly. While the approximation through the Gaussian
-Kullback-Leibler divergence in the lower bound proof is convenient and
-leads to the simple APT algorithm, it might not stay appropriate for
-distributions whose Kullback-Leibler divergence tends to differ from the
-Gaussian. This, for example, is the case for Bernoulli distributions at
-very small parameters \(\mu\). We have for the Kullback-Leibler
-divergence of two Gaussian distributions \(\nu_i\) and \(\nu_j\) of mean
-\(\mu_i\) and \(\mu_j\) with equal variance:
-
-\[
-\KL_{N}(\nu_i || \nu_j) = 2(\mu_i - \mu_j)^2.
-\]
-
-Writing \(\mu_j = \tau\) and \(\epsilon = 0\), we see that the APT
-algorithm essentially measures the KL-divergence between two Normal
-distributions. For two Bernoulli distributions \(\nu_i\) and \(\nu_j\),
-parameterized by \(\mu_i\) and \(\mu_j=\tau\), we write
-
-\[
-\KL_{Ber}(\nu_i||\nu_j) = \mu_i \log(\frac{\mu_i}{\tau}) + (1-\mu_i) \log(\frac{1-\mu_i}{1-\tau})
-\]
-
-In the case of \(\tau = 0.5\), the latter KL-divergence is symmetric in
-its first argument, and thus can be relatively well approximated by
-Pinsker's inequality:
-
-\[
-\KL_{Ber}(\nu_i||\nu_j) \geq 2(\mu_i - \tau)^2.
-\]
-
-This is of course equal to the Gaussian KL-divergence described before.
-This approximation, however, suffers for heavily for very small values
-of \(\mu_i\) and \(\tau\). In particular, the Bernoulli KL-divergence
-becomes asymmetric in its first argument as \(\tau \neq 0.5\). Thus, in
-contrast to the complexity measure \(H\) based on the Gaussian
-KL-divergence, a complexity measure based on the Bernoulli KL-divergence
-would evaluate two arms as differently difficult if their absolute
-distance to the threshold is the same, but they lie on different sides
-of the threshold.
-
-Thus similarly to how UCB algorithms in the cumulative regret setting
-have been extended to KL-UCB algorithms (compare Cappé et al., 2013),
-also the APT algorithm offers room for improvement. As a more explicit
-example of such adaptation, consider the case of Top-\(m\)
-identification described in Kaufmann et al. (2016). The authors develop
-a lower bound based on KL-divergence, and note that ``This
-information-theoretic lower bound permits to interpret the quantity
-\(H(\nu)\) {[}\ldots{}{]} as a subgaussian approximation''. Given that
-Bernoulli distributions with very small parameter values arise naturally
-in many applications, an improvement in this regard would be valuable.
-
-In what follows, we first examine in
-\autoref{chap:KullbackLeiblerPureExploration} how information theoretic
-quantities are employed in the best arm identification and Top-\(m\)
-problem as detailed in Kaufmann and Garivier (2016) and Kaufmann et al.
-(2016). Before introducing a new algorithm for the thresholding bandit
-problem based on Kullback-Leibler divergences in
-\autoref{sec:LikelihoodRatioForExponentialFamily}, we first describe the
-variance-based approaches in \autoref{sec:VarianceBasedAlgorithms}.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/KLApproximationComparison-1}
-
-}
-
-\caption{The approximation of the Bernoulli KL-divergence by the Gaussian KL-divergence works well if the second argument is equal to 0.5.
-Else we observe poor approximation in both value and symmetry.
-This becomes more obvious as the arguments move away from 0.5.}\label{fig:KLApproximationComparison}
-\end{figure}
-
-\section{\texorpdfstring{Information Theoretic Approaches to Pure
-Exploration Bandits
-\label{chap:KullbackLeiblerPureExploration}}{Information Theoretic Approaches to Pure Exploration Bandits }}\label{information-theoretic-approaches-to-pure-exploration-bandits}
-
-The previous chapter introduces the thresholding bandit problem as
-described in Locatelli et al. (2016), and with the APT strategy a first
-algorithm that is simple, yet order-optimal for large budgets. However,
-we end with the conclusion that a distance measure between the
-distributions and the threshold based on the Kullback-Leibler divergence
-might be more useful than the simple gap
-\(\Delta^2_i = (\mu_i - \tau_i)^2\) employed so far. Indeed, citing
-Kaufmann et al. (2016), we note that the complexity \(H\) used so far
-can be considered a sub-Gaussian approximation of a better complexity
-measure based on information theoretic measures like the
-Kullback-Leibler divergence.
-
-In order to give more intuition to why that is the case, and in what
-ways information theoretic measures can be introduced to measure the
-complexity of bandit problems, we now turn to Kaufmann et al. (2016) and
-Garivier and Kaufmann (2016). The latter describes a strategy based on
-Kullback-Leibler divergences for the best-arm identification problem,
-while the first derives complexity measures based on the divergence.
-Ideally, their work offers methods that can inform our work of extending
-the thresholding bandit problem. In what follows, we adopt the notation
-of Kaufmann et al. (2016) to ease a comparison with their arguments.
-
-\subsection{\texorpdfstring{Information Theoretic Complexity Measures in
-Top-\(m\) Problems
-\label{sec:KaufmannEtAl2016}}{Information Theoretic Complexity Measures in Top-m Problems }}\label{information-theoretic-complexity-measures-in-top-m-problems}
-
-Instead of the thresholding bandit problem, Kaufmann et al. (2016)
-consider the problem of identifying the best \(m\) out of \(K\) arms,
-that is, the top-\(m\) problem. They describe their bandit model \(\nu\)
-by \(K\) arms characterized by probability distributions \(\nu_a\),
-\(a \in \{1,...,K\}\), with mean \(\mu_a\). A learner picks at any time
-step \(t=1,2,...,\) an arm \(A_t \in \{1,...,K\}\) for which he observes
-the independent reward \(Z_{t} \sim \nu_{A_t}\). The learner aims to
-find the \(m\) out of \(K\) arms with the largest expected reward. This
-set of arm indexes is denoted by \(\mathcal{S}_m^*\). Kaufmann et al.
-write the means \((\mu_{1}, ..., \mu_{K})\) sorted in decreasing order
-as the K-tuple \((\mu_{[1]}, ..., \mu_{[K]})\). Based on this, they
-require that \(\mu_{[m]} > \mu_{[m+1]}\) such that the solution
-\(\mathcal{S}_m^*\) is unique. The class of bandit problems \(\nu\) for
-which the latter condition holds is called \(\mathcal{M}_m\) by Kaufmann
-et al. At the end of the sampling procedure, after \(T\) samples
-(denoted by \(\tau\) in Kaufmann et al.) the learner is required to
-return a classification \(\hat{\mathcal{S}}_m\). This classification is
-then evaluated by the loss function
-\(\mathcal{L}(T) = \mathbb{I}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m)\).
-This binary loss is similar to the loss in the thresholding bandit. We
-can now define a strategy of the learner as
-\(\mathcal{A} = ((A_t), T, \hat{\mathcal{S}}_m)\): The strategy defines
-how an arm is chosen, how many samples are observed, and how the arms
-are eventually classified.
-
-When introducing the thresholding bandit setting, we did not mention the
-fact that the budget \(T\) does not need to be fixed upfront. Indeed,
-the setting in which the budget is \emph{not} fixed upfront might be
-more popular among the best arm identification and top-\(m\) literature.
-This setting is called \emph{fixed confidence}, while the setting we
-considered so far is called \emph{fixed budget}. In the fixed budget
-setting, we run algorithms for \(T\) samples and then compare them based
-on their expected loss,
-\(\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m) =: p_t(\nu)\)
-as we have seen in \(\autoref{sec:Setup}\). Alternatively, consider a
-\(\delta\)-PAC strategy \(\mathcal{A}(\delta)\)for which it holds for
-every problem \(\nu \in \mathcal{M}_m\) that the classification holds at
-least with confidence level \(1-\delta\), that is,
-\(\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta\). The
-strategy has to achieve this level of confidence in its prediction
-before it is allowed to stop sampling. This is the fixed confidence
-case, in which the budget \(T\) is no longer fixed upfront, but turns
-into a random variable. Algorithms are then compared by their expected
-number of draws \(\mathbb{E}_{\nu}[T_{\delta}]\) and we prefer those
-which achieve the confidence level \(1-\delta\) with a smaller expected
-budget.
-
-In the fixed confidence setting, a family of strategies
-\(A = (\mathcal{A}(\delta))_{\delta \in (0,1)}\) is called PAC if for
-every \(\delta\), \(\mathcal{A}(\delta)\) is \(\delta\)-PAC. On the
-other hand, in the fixed budget setting, a family of strategies
-\(A = (\mathcal{A}(t))_{t \in \mathbb{N}}\) is called consistent if
-\(p_t(\nu) \rightarrow 0\) as \(t \rightarrow \infty\) for every problem
-\(\nu \in \mathcal{M}_m\).
-
-Given this setup, we can now follow the arguments of Kaufmann et al.
-(2016) to derive complexity measures for the top-\(m\) problem. As
-alluded to earlier, these complexity measures will rely on the
-KL-divergence in contrast to the complexity \(H\) used by Locatelli et
-al. (2016). When discussing \(H\), its motivation is that it represents
-the difficulty of the problem by measuring the distance between arms and
-the threshold. Instead, Kaufmann et al. approach complexity by how many
-samples (what error probability) one will need in the fixed confidence
-(fixed budget) setting. In order to arrive at their new measure of
-complexity, it makes sense to first follow their arguments to a general
-lower bound on the sample complexity \(\mathbb{E}_{\nu}[\tau]\) which is
-given in their Theorem 4:
-
-\begin{theorem}[Theorem 4, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem4}
-Let $\nu \in \mathcal{M}_m$, where $\mathcal{M}_m$ is the set of uniquely identifiable bandit models described above.
-Assume that $\mathcal{P}$ satisfies the continuity conditions in Assumption 3.
-Any $\delta$-PAC algorithm on $\mathcal{M}_m$ satisfies, for $\delta \leq 0.15$:
-
-\begin{equation*}
-\mathbb{E}_{\nu}[\tau] \geq \Big[ \sum_{a \in \mathcal{S}^*_m} \frac{1}{\KL(\nu_a || \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}^*_m} \frac{1}{\KL(\nu_a || \nu_{[m]})} \Big] \der(1-\delta, \delta),
-\end{equation*}
-\end{theorem}
-
-To prove this statement for a given \(\delta\)-PAC algorithm
-\(\mathcal{A}\), we assume certain continuity conditions (compare
-Kaufmann et al. (2016)) under which there exists for every arm
-\(a \in \{1, \dots, K\}\) an alternative model
-\(\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)\).
-In this alternative model, in accordance with the continuity conditions,
-only arm \(a\) is modified. After the modification, the arm
-\(\nu_{m+1}\) is now closer to \(\nu_a\) as measured by the
-Kullback-Leibler divergence than \(\nu_a'\) is to \(\nu_a\), if
-\(\mu_a > \mu_{m+1}\) (consequently, \(\mu_a' < \mu_{m+1}\)). On the
-other hand, if \(\mu_a < \mu_{m}\), then \(\nu_a'\) will be moved away
-from \(\nu_a\) just enough so that \(\nu_a\) is closer to \(\nu_m\) than
-to \(\nu_a'\) (consequently, \(\mu_a' > \mu_m\)). These changes in
-distribution make the original set of optimal arms, \(\{1,\dots,m\}\),
-no longer optimal under the alternative model \(\nu'\). To compare this
-to the thresholding bandit problem, assume that arms \(\nu_{m}\) and
-\(\nu_{m+1}\) indirectly define a threshold
-\(\tau \in (\mu_{m+1},\mu_m)\). Then, by creating an alternative problem
-as described here, we flip arm \(a\) around the implied threshold
-\(\tau\) (compare the lower bound proof in \autoref{sec:AppendixAPTLB}).
-
-Given the strategy returns \(\hat{S}_m\), we know that for the event
-\(\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})\) (which is element of the
-\(\sigma\)-Algebra \(\mathcal{F}_{T}\) induced by the stopping time
-\(T\)), that \(\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta\) and
-\(\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta\) (because fixed confidence
-\(\delta\)!). To give the lower bound on the expected number of samples,
-\(\mathbb{E}_{\nu}[\tau]\), we employ the general Lemma given by the
-authors for such changes in distribution in bandit models.
-
-\begin{lemma}[Lemma 1, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma1}
-Let $\nu$ and $\nu'$ be two bandit models with $K$ arms such that for all $a$, the distributions $\nu_a$ and $\nu_a'$ are mutually absolutely continuous.
-For any almost-surely finite stopping time $\sigma$ with respect to $(\mathcal{F}_t)$,
-
-\begin{equation*}
-\sum_{a=1}^{K} \mathbb{E}_{\nu} [N_a(\sigma)] \KL(\nu_a|| \nu_a') \geq \sup_{\mathcal{E} \in \mathcal{F}_{\sigma}} \der (\mathbb{P}_{\nu}(\mathcal{E}), \mathbb{P}_{\nu'}(\mathcal{E})).
-\end{equation*}
-\end{lemma}
-
-We apply this Lemma directly on the expected number of draws for each
-arm, \(\mathbb{E}_{\nu}[N_a]\). For each arm \(a\), we thus have
-\(\KL(\nu_a, \nu_a') \mathbb{E}_{\nu}[N_a] \geq d(1-\delta, \delta)\).
-Using the definition of the alternative model above, we get for every
-small but fixed \(\alpha > 0\), every arm \(a \in \{1, \dots, K\}\) and
-\(b \in \{m+1, \dots, K\}\):
-
-\begin{equation*}
-\mathbb{E}_{\nu}[N_a] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_a || \nu_{m+1}) + \alpha} \quad \text{and} \quad \mathbb{E}_{\nu}[N_b] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_b || \nu_{m}) + \alpha}.
-\end{equation*}
-
-Let \(\alpha \to 0\), sum the individual arms' bounds to get the bound
-on the overall number of draws:
-
-\begin{equation*}
-\mathbb{E}_{\nu}[T] = \sum_{a=1}^K \mathbb{E}_{\nu}[N_a] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m]})} \Big) \der(1-\delta, \delta)
-\end{equation*}
-
-Given that we will be naturally interested in either very high or very
-low confidence of our algorithm, that is, \(P_\nu(\mathcal{E})\) is
-either close to 0 or 1, it is possible to use the following
-approximation to the binary relative entropy given in Kaufmann et al.
-(2016):
-
-\begin{equation}\label{bre_approx}
-\forall x \in [0,1], \quad \der(x,1-x) = \der(1-x,x) \geq \log \frac{1}{2.4x}.
-\end{equation}
-
-This allows us to write the lower bound on the expected stopping time
-as:
-
-\begin{equation*}
-\mathbb{E}_{\nu}[T] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
-\end{equation*}
-
-Given this lower bound, it is clear that the complexity of the top-\(m\)
-problem can be lower bounded by the KL-divergence between arms and the
-implied threshold between the \(m\)-th best arm and the \((m+1)\)-th
-best arm. The latter gives a lower bound on the effort (in terms of
-expected number of samples) required to achieve a certain confidence
-level, where a problem that requires a larger effort is described as
-more complex. Indeed, in the case of fixed confidence problems, Kaufmann
-et al. (2016) describe problems as having a larger \emph{sampling
-complexity}.
-
-Following Kaufmann et al. (2016), we define the complexity
-\(\kappa_C(\nu)\) in the fixed confidence setting as
-
-\begin{equation}
-\kappa_C(\nu) = \inf_{A \, \text{PAC}} \limsup_{\delta \to 0} \frac{\mathbb{E}_{\nu}[T_{\delta}]}{\log \frac{1}{\delta}}. \label{eq:KappaC}
-\end{equation}
-
-This definition makes sense if we consider the fact that the confidence
-level \(\delta\) is experimenter chosen and thus not relevant in
-describing the complexity. Thus, by including \(\log(1/\delta)\)
-explicitly in \eqref{eq:KappaC}, we get rid of the confidence term in
-the lower bound on \(\mathbb{E}_{\nu}[T]\) after plugging it into
-\eqref{eq:KappaC}. We arrive at the lower bound on the complexity
-measure given in Kaufmann et al. (2016):
-
-\begin{equation*}
-\kappa_C(\nu) \geq \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a || \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a || \nu_{[m]})}
-\end{equation*}
-
-Given this description, we would expect that a complexity measure in a
-fixed confidence thresholding bandit probem might involve replacing
-\(\mu_{[m]}\) and \(\mu_{[m+1]}\) by the actual threshold \(\tau\) that
-divides the group above the threshold from the group below the
-threshold. But given the setting in Locatelli et al. (2016), we are
-mainly interested in complexity measures and algorithms for the fixed
-budget problem. The results of Kaufmann et al. (2016) are more limited
-for this case. While the authors are able to provide a bound on their
-complexity measure in the fixed budget case, it only applies to the case
-of \emph{two-armed} bandit models.
-
-Consider a consistent fixed budget strategy \(\mathcal{A}\)
-(\(p_t(\nu)\) tends to zero as \(t \rightarrow \infty\)), and define the
-complexity in the fixed budget setting as follows:
-
-\begin{equation}
-\kappa_B(\nu) = \inf_{A \, \text{consistent}} \Big(\limsup_{t \to \infty} - \frac{1}{t} \log p_t(\nu)\Big)^{-1}.
-\end{equation}
-
-While we included the experimenter-fixed \(\delta\) in the definition of
-\(\kappa_C\), we now include the fixed \(T\) in the definition of
-\(\kappa_B\) to disregard it in the complexity measure after plugging in
-the lower bound on \(p_t(\nu)\). The resulting lower bound given in
-Theorem 12 of Kaufmann et al. (2016):
-
-\begin{theorem}[Theorem 12, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem12}
-Let $\nu = (\nu_1, \nu_2)$ be a two-armed bandit model such that $\mu_1 > \mu_2$. In the fixed budget setting, any consistent algorithm satisfies:
-
-\begin{equation*}
-\limsup_{t \to \infty} - \frac{1}{t} \log p_t(\nu) \leq \inf_{(\nu_1', \nu_2') \in \mathcal{M}: \mu_1' < \mu_2'} \max \big\{\KL(\nu_1' || \nu_1), \KL(\nu_2' || \nu_2)\big\}
-\end{equation*}
-\end{theorem}
-
-For a proof, consider first the two different bandit models, \(\nu\) and
-\(\nu'\), where we fix w.l.o.g. \(a^* = 1\) as the best arm in \(\nu\),
-while \(a^* = 2\) in \(\nu'\). We require the algorithm \(\mathcal{A}\)
-to be consistent for both problems. Since we are in the fixed budget
-setting, the stopping time is fixed at \(T = t\). The correct decision
-differs between the two problems, and we focus on the event
-\(A = (\hat{S}_1 = 1)\). Now, we can apply Lemma 1 from Kaufmann et al.
-(2016) as before, as it gives a measure of how different two bandit
-models are (it bounds the change in distribution). Here, we want to know
-how different \(\nu\) is from \(\nu'\), and, given we have only two
-arms,
-
-\begin{equation*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1'|| \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2'|| \nu_2) \geq \der(\mathbb{P}_{\nu'}(A),\mathbb{P}_{\nu}(A)))
-\end{equation*}
-
-The expectations were chosen with respect to \(\nu'\) in order to allow
-for the following: We have \(p_t(\nu) = 1 - \mathbb{P}_{\nu}(A)\) and
-\(p_t(\nu') = \mathbb{P}_{\nu'}(A)\) (since \(A\) is wrong in \(\nu'\)).
-But since algorithm \(\mathcal{A}\) is consistent for both \(\nu\) and
-\(\nu'\), we know that there should exist some number of samples such
-that the probability of event \(A\) is bigger in setting \(\nu\) (where
-it is the correct decision) than in setting \(\nu'\) (where this would
-be a wrong decision and failure). Thus, for every \(\epsilon > 0\),
-there exists \(t_0(\epsilon)\) such that for all
-\(t \geq t_0(\epsilon)\),
-\(\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)\).
-Consequently, if we plug in the bound of \(\epsilon\) for
-\(\mathbb{P}_{\nu'}(A)\), then
-
-\begin{align*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1' || \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2' || \nu_2) & \geq \der(\epsilon,1-p_t(\nu))) \\
-& = \epsilon \log \frac{\epsilon}{1-p_t(\nu)} + (1-\epsilon) \log \frac{1-\epsilon}{p_t(\nu)} \\
-& \geq (1-\epsilon) \log \frac{1-\epsilon}{p_t(\nu)} + \epsilon \log \epsilon.
-\end{align*}
-
-Let \(\epsilon\) go to zero so that
-
-\begin{align*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1' || \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2' || \nu_2)
-& \geq \log \frac{1}{p_t(\nu)} = -\log p_t(\nu).
-\end{align*}
-
-Dividing both sides by \(t\) and taking the limsup, we arrive at
-
-\begin{align*}
-\limsup_{t \to \infty} - \frac{1}{t} \log p_t(\nu)
-& \leq \limsup_{t \to 0} \frac{1}{t} \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)] \KL(\nu_a' || \nu_a) \\
-& \leq \max_{a=1,2} \KL(\nu_a' || \nu_a),
-\end{align*}
-
-where the last line follows from the fact that the
-\(\frac{1}{t} \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)]\) part creates a
-weighted average of the two divergences \(\KL(\nu_a', \nu_a)\). As noted
-in Kaufmann et al. (2016), one arrives at the final result by choosing
-\(\mu_1'\), \(\mu_2'\) so that
-\(| \KL(\nu_1', \nu_1) - \KL(\nu_2', \nu_2) |\) is as small as possible.
-
-As noted by Kaufmann et al. (2016), the advantage of this lower bound is
-that it makes the complexity in the fixed confidence and the fixed
-budget setting directly comparable. The disadvantage of course being
-that the result only holds for two-armed models. While the authors are
-not able to derive directly comparable lower bounds for the top-\(m\)
-case, they derive a first lower bound in the Gaussian case with equal
-variances, which we describe shortly in the appendix in
-\autoref{sec:KaufmannLBTopMGaussian}.
-
-Before we discuss algorithms given in Kaufmann et al. (2016) that match
-the lower bounds, we show how lower bounds can be derived very similarly
-for the fixed budget thresholding problem.
-
-\subsubsection{\texorpdfstring{Lower Bound for Fixed Budget Thresholding
-Problem
-\label{sec:LBTBP}}{Lower Bound for Fixed Budget Thresholding Problem }}\label{lower-bound-for-fixed-budget-thresholding-problem}
-
-In order to derive a bound for the fixed budget problem, Kaufmann et al.
-(2016) have focused on the setting with two arms which is the most
-simple version of the top-\(m\) problem. Less than two arms do not make
-sense, since the single arm is by definition the best arm. In the case
-of the thresholding bandit, however, a single-armed problem makes still
-at least limited sense in that we still have to classify this arm
-correctly with respect to the threshold. Thus, we can show the following
-corollary which gives a bound on the complexity of the single-armed
-thresholding bandit.
-
-\begin{corollary}
-Let $\nu = \nu_1$ be a one-armed thresholding bandit model where $\tau$ is the threshold fixed upfront.
-Let $\nu$ be from the univariate exponential family of distributions such that $\nu_1$ can be parameterized by its mean, $\mu_1$, and the Kullback-Leibler divergence between distributions $\nu_1$ and $\nu_1'$ can be written as $\KL(\nu_1', \nu_1) = \KL(\mu_1', \mu_1)$.
-In the fixed budget setting, any consistent algorithm ($p_t(\nu) \rightarrow 0$ as $t \rightarrow \infty$) satisfies:
-
-$$
-- \frac{1}{t} \log p_t(\nu) \leq \KL(\tau || \mu_1)
-$$
-\end{corollary}
-
-\label{corollary:LB1TBP}
-
-This is basically the Chernoff-Stein Lemma for the hypothesis test of
-two alternatives (compare chapter 11 in Cover and Thomas, 2006, or
-\autoref{theorem:ChernoffStein}). We arrive at this result as the
-one-armed bandit does not require sequential sampling: The single arm
-receives all samples. \(\mathbb{E}_{\nu'}[N_1(t)]\) is not a random
-variable but equals \(T\).
-
-But as we see in the following corollary, we can extend the lower bound
-to the \(K\)-armed fixed budget thresholding bandit problem, which
-stands in contrast to the fact that for the top-\(m\) problem, it is
-only possible to show the lower bound for two arms. The result is based
-on an alternative setting \(\nu'\) in which all arms have means
-\(\mu' = \tau\) such that their expected number of pulls corresponds to
-uniform sampling, \(\mathbb{E}_{\nu'}[N_i(t)] = T/K\).
-
-\begin{corollary}
-Let $\nu = (\nu_1, ..., \nu_K)$ be a $K$-armed thresholding bandit problem in which $\tau$ is the threshold fixed upfront.
-For $i \in \{1,...,K\}$, let $\nu_i$ be from the univariate exponential family of distributions such that $\nu_i$ can be parameterized by its mean, $\mu_i$, and the Kullback-Leibler divergence between distributions $\nu_i$ and $\nu_i'$ can be written as $\KL(\nu_i, \nu_i') = \KL(\mu_i, \mu_i')$.
-In the fixed budget setting, any consistent algorithm satisfies:
-
-$$
-\limsup_{t \rightarrow \infty} -\frac{1}{t} \log p_t(\nu) \leq \max_{a \in \{1,...,K\}} \KL(\tau || \mu_a)
-$$
-
-or
-
-$$
-- \frac{1}{t} \log p_t(\nu) \leq \frac{1}{K}\sum_{i=1}^{K} \KL(\tau || \mu_i),
-$$
-\end{corollary}
-
-\label{corollary:LBKTBP}
-
-We present the proofs of \autoref{sec:LBTBP} in the appendix in
-\autoref{sec:corollaryLBTBPproof}. Corresponding to the complexity
-measures defined in equation \((1)\) of Kaufmann et al. (2016), we can
-define the complexity \(\kappa_{TBP}(\nu)\) in the thresholding bandit
-problem and lower bound it:
-
-\[
-\kappa_{TBP}(\nu) = \inf_{A \text{ consistent}} \Big(\limsup_{t \rightarrow \infty} - \frac{1}{t} \log p_t(\nu)\Big)^{-1} \geq K \Big(\sum_{i=1}^{K} \KL(\tau||\mu_i)\Big)^{-1}
-\]
-
-\subsubsection{\texorpdfstring{Strategies Matching the Top-\(m\) Lower
-Bound}{Strategies Matching the Top-m Lower Bound}}\label{strategies-matching-the-top-m-lower-bound}
-
-Kaufmann et al. (2016) do not present algorithms matching the lower
-bound of Theorem \ref{theorem:KaufmannEtAlTheorem17}. They do consider
-algorithms that connect to Theorem \ref{theorem:KaufmannEtAlTheorem4}
-and Theorem \ref{theorem:KaufmannEtAlTheorem12}. Given that we aim to
-extend the fixed budget thresholding bandit problem, we are most
-interested in the matching strategies for Theorem
-\ref{theorem:KaufmannEtAlTheorem12}. However, given that this lower
-bound applies only to two-armed bandits, the algorithms proposed by
-Kaufmann et al. (2016) are of limited practical interest. Furthermore,
-the proposed strategies require knowledge that is in general not
-available upfront: For Gaussian distributions, the knowledge of the
-(potentially different) variance is assumed which enables a strategy
-that pulls each arm proportional to its variance.
-
-Even more difficult are the assumptions in the case of Bernoulli
-two-armed bandit models: The proposed algorithm requires knowledge about
-the true parameters of the distributions. That this limits the practical
-interest is also noted by the authors of Kaufmann et al. (2016). Thus,
-they suggest to use uniform sampling strategies in the case of two-armed
-Bernoulli bandits, and show that there is not much to be lost by doing
-so.
-
-Thus, Kaufmann et al. (2016) joins other papers like Audibert et al.
-(2010) and Kaufmann and Kalyanakrishnan (2013) which struggle to find
-matching strategies in the fixed budget setting that do not rely on
-knowledge of parameters or the complexity of the problem.
-
-In contrast, Kaufmann et al. (2016) are able to show that their
-complexity measure derived for the fixed confidence setting,
-\(\kappa_C(\nu)\), can be upper-bounded using the bound given for the
-KL-LUCB algorithm in Kaufmann and Kalyanakrishnan (2013). In the case of
-exponential family bandits, the complexity \(\kappa_C(\nu)\) is bounded
-as given in equation (6) in Kaufmann et al. (2016):
-
-\begin{equation*}
-\sum_{a \in S^*_m} \frac{1}{\KL(\theta_a || \theta_{[m+1]})} + \sum_{a \notin S^*_m} \frac{1}{\KL(\theta_a || \theta_{[m]})} \leq \kappa_C(\nu) \leq 24 \min_{\theta \in [\theta_{[m+1]},\theta_{[m]}]} \sum_{a=1}^{K} \frac{1}{\KL^*(\theta_a || \theta)},
-\end{equation*}
-
-where again we write with slight abuse of notation
-\(\KL(\theta || \theta') = \KL(\nu_{\theta}|| \nu_{\theta'})\) for
-\((\theta, \theta') \in \Theta^2\) as the shorthand for the
-KL-divergence of two distributions from the exponential family
-parameterized by \(\theta\) and \(\theta'\) respectively.
-\(\KL^*(\theta || \theta') = \KL(\theta^* || \theta)\) is the Chernoff
-information between the two distributions, where \(\theta^*\) is chosen
-so that \(\KL(\theta^* || \theta) = \KL(\theta^* || \theta')\).
-
-\subsection{\texorpdfstring{Information Theoretic Approach to Best Arm
-Identification
-\label{sec:OptimalBestArmIdentification}}{Information Theoretic Approach to Best Arm Identification }}\label{information-theoretic-approach-to-best-arm-identification}
-
-Instead of discussing the KL-LUCB algorithm for the fixed confidence
-top-\(m\) problem, we shift our focus onto the fixed confidence best arm
-identification problem, as discussed in Garivier and Kaufmann (2016).
-The authors also derive a lower bound on the sample complexity using the
-Lemma \autoref{theorem:KaufmannEtAlLemma1}. Furthermore, they propose a
-matching strategy for \(K \geq 2\) arms.
-
-The setting differs slightly from the setting considered in Kaufmann et
-al. (2016). In particular, Garivier and Kaufmann (2016) focus on
-distributions \(\nu_{\theta}\) from the univariate canonical exponential
-family of distributions, which can be parameterized by their mean
-\(\mu\), and thus can be written as \(\nu_{\mu}\); as before, we
-simplify the notation of the KL-divergence for these distributions to
-\(\KL(\nu || \nu') = \KL(\mu || \mu')\).
-
-Furthermore, if we let \(\mathcal{S}\) to be a set of bandit models with
-\(K\) distributions each, then each model is fully defined by a vector
-\(\bm{\mu} = (\mu_1, \dots, \mu_K)\). Assume that every
-\(\bm{\mu} \in \mathcal{S}\) has a unique maximum given by
-\(a^*(\bm{\mu})\) such that
-\(\mu_{a^*} > \max_{a \neq a^*(\bm{\mu})} \mu_a\). In order to fix the
-confidence \(1-\delta\), we specify the risk \(\delta\). Similar to the
-top-\(m\) case considered before, strategies corresponding to this risk
-are called \(\delta\)-PAC if for every \(\bm{\mu} \in \mathcal{S}\), the
-strategy ends surely after a finite number of samples,
-\(\mathbb{P}_{\bm{\mu}}(T_{\delta} < \infty) = 1\), and the error
-probability is at least as small as the fixed risk level,
-\(\mathbb{P}_{\bm{\mu}}(\hat{a}_{T_{\delta}} \neq a^*) \leq \delta\). In
-order to derive the lower bound on the expected number of samples
-\(\mathbb{E}[T]\) through a change in distributions, we introduce the
-set of alternative problems for which the optimal arm is different from
-\(\bm{\mu}\):
-
-\begin{equation*}
-\text{Alt}(\bm{\mu}) := \{\bm{\lambda} \in \mathcal{S}: a^*(\bm{\lambda}) \neq a^*(\bm{\mu})\},
-\end{equation*}
-
-where \(\bm{\lambda}\) is the vector of means defining the distributions
-of the alternative problem. Lastly, we have the set of probability
-distributions on the arms \(\{1,...,K\}\):
-\(\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}\). Each
-\(w_i\) corresponds to the fraction of overall samples that arm \(i\)
-receives. We now state the lower bound:
-
-\begin{theorem}[Theorem 1, Garivier and Kaufmann, 2016] \label{theorem:GarivierKaufmannTheorem1}
-Let $\delta \in (0,1)$. For any $\delta$-PAC strategy and any bandit model $\bm{\mu} \in \mathcal{S}$,
-
-\begin{equation*}
-\mathbb{E}_{\bm{\mu}} [T_{\delta}] \geq T^*(\bm{\mu}) \text{\em{d}}(\delta,1-\delta),
-\end{equation*}
-
-where
-
-\begin{equation} \label{eq:GarivierKaufmann_Theorem1_Game}
-T^*(\bm{\mu})^{-1} := \sup_{w \in \Sigma_K} \inf_{\bm{\lambda} \in \text{\em{Alt}}(\bm{\mu})} \left( \sum_{a=1}^K w_a \text{\em{KL}}(\mu_a|| \lambda_a)\right).
-\end{equation}
-\end{theorem}
-
-We see that the two bounds given in Theorem
-\ref{theorem:KaufmannEtAlTheorem4} and Theorem
-\ref{theorem:GarivierKaufmannTheorem1} on the sample complexity differ
-only in the way in which they sum the Kullback-Leibler divergences over
-the \(K\) arms. In contrast to Theorem
-\ref{theorem:KaufmannEtAlTheorem4}, here the contribution of each arm
-through its KL-divergence is weighted. The difference is that while we
-were able to clearly describe the change of distribution in the
-top-\(m\) case for each arm -- we specified an alternative model for
-each arm that yields a new set of \(m\) optimal arms -- we now consider
-all alternative models that yield a different best arm than the model
-\(\bm{\mu}\). In the previous theorem, we sum over the complexity of
-each individual arm, since the change in distribution only affects one
-arm at a time, thus leading to a KL-divergence of 0 for the other arms
-while still changing the optimal set. Now, we consider all instances of
-alternative models \(\bm{\lambda}\), and thus also those in which
-several arms are modified (and thus have a KL-divergence unequal 0 in
-the result of Lemma 1).
-
-To proof Theorem \ref{theorem:GarivierKaufmannTheorem1}, we let
-\(\delta \in (0,1)\), \(\bm{\mu} \in \mathcal{S}\), and only consider
-\(\delta\)-PAC strategies. As before, \(N_a(t)\) describes the random
-number of pulls of arm \(a\) until time \(t\), for all \(t\geq 1\).
-Again, Lemma \ref{theorem:KaufmannEtAlLemma1} states how the risk
-\(\delta\) relates to the expected number of draws of each arm given two
-models which differ in their optimal arm. How much the two models differ
-is evaluated based on the KL-divergence for each pair of arms:
-
-\begin{equation*}
-\forall \lambda \in \mathcal{S}: a^*(\lambda) \neq a^*(\mu), \sum_{a=1}^K \KL(\mu_a,\lambda_a)\mathbb{E}_{\bm{\mu}}[N_a(T_{\delta})] \geq \d(\delta, 1- \delta).
-\end{equation*}
-
-As mentioned, we now do not consider a specific alternative for each
-arm, but instead look at the infimum over all the possible alternatives,
-and use the fact that
-\(\mathbb{E}_{\bm{\mu}}[T_{\delta}] = \sum_{a=1}^K \mathbb{E}_{\bm{\mu}}[N_a(T_{\delta})]\):
-
-\begin{align*}
-\der(\delta, 1-\delta) & \leq \inf_{\lambda \in \text{Alt}(\bm{\mu})} \mathbb{E}_{\bm{\mu}}[T_{\delta}] \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[T_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
-& = \mathbb{E}_{\bm{\mu}}[T_{\delta}] \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[T_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
-& \leq \mathbb{E}_{\bm{\mu}}[T_{\delta}] \sup_{w \in \Sigma_K} \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K w_a \KL(\mu_a, \lambda_a)\Big).
-\end{align*}
-
-As stated in Garivier and Kaufmann (2016), the term
-\(\frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[T_{\delta}]}\)
-gives the fraction of draws each arm receives. This value, however,
-depends on the used algorithm. To make it hold for any \(\delta\)-PAC
-algorithm, it is replaced by the supremum over \(\Sigma_K\), which is
-the distribution over these fractions for any \(\mathcal{A}\), that is,
-for any \(\delta\)-PAC strategy.
-
-This lower bound can be interpreted as a minimax game\footnote{See the
-  presentation by Aurélien Garivier at COLT 2016:
-  \url{https://youtu.be/eLyrrYqJlkE}}, where the experimenter has to
-choose the share of samples he attributes to each arm in a way that is
-optimal given that nature will respond and choose the most difficult
-alternative model given his weights. Thus, to make the lower bound
-practical, it is a matter of finding the optimal weights
-\(w^*(\bm{\mu})\). This step did not occur in the lower bound for the
-top-\(m\) problem since the alternative models were specified by
-changing the distribution of one arm with respect to the ``border''
-between the two groups of arms.
-
-The existence of the optimal weights suggests an algorithm that keeps
-track of the share of samples that is attributed to each arm and makes
-sure that it stays close to the optimum until some decision rule assures
-that the \(\delta\)-PAC condition is fulfilled.
-
-Indeed, the optimal weights will lead to a sampling structure in which
-arms are drawn such that their individual probabilities of error stay at
-the same level. An arm more distant from the optimal arm in terms of
-Kullback-Leibler divergence should receive a smaller share of the
-samples to achieve the same error probability as an arm closer to the
-optimal arm.
-
-This is what happens when we look for proportions \(w \in \Sigma_K\)
-that minimize the cost from a change in distributions, that is, the term
-\(F(\bm{\mu}, \bm{w}) = \inf_{\bm{\lambda} \in \text{Alt}(\bm{\mu})} \Big(\sum_{a= 1}^K w_a \KL(\mu_a, \lambda_a)\Big)\).
-In the proof of Lemma 3 of Garivier and Kaufmann, it is shown that
-nature, selecting the alternative model \(\bm{\lambda}\), will always
-pick an alternative model in which only a single arm \(a\) is changed
-such that \(\lambda_a > \lambda_1\) since
-
-\begin{align*}
-T^*(\bm{\mu})^{-1} & = \sup_{w \in \Sigma_K} \min_{a \neq 1} \inf_{\bm{\lambda} \in \mathcal{S}: \lambda_a > \lambda_1} \sum_{a=1}^K w_a \KL(\mu_a, \lambda_a)  \\
-& = \sup_{w \in \Sigma_K} \min_{a \neq 1} \inf_{\bm{\lambda}: \lambda_a \geq \lambda_1} [w_1 \KL(\mu_1, \lambda_1)+w_a \KL(\mu_a, \lambda_a)]. \Alignyesnumber\label{eqn:ComplexityTrackStopStrategy}
-\end{align*}
-
-Consequently, \(w\) will be chosen so as to minimize \(T^*(\bm{\mu})\)
-no matter which arm \(a\) was picked. It is a minimax game, so the ideal
-solution is to keep for each arm \(a \neq 1\) the term
-\(w_1 \KL(\mu_1, \lambda_1) + w_a \KL(\mu_a, \lambda_a)\) at the same
-level. Garivier and Kaufmann show that this can be written in terms of
-the Jenson-Shannon divergence, defined for every \(\alpha \in [0,1]\) as
-
-\begin{equation*}
-I_{\alpha}(\mu_1, \mu_2) := \alpha \KL(\mu_1 || \alpha \mu_1 + (1-\alpha) \mu_2) + (1-\alpha) \KL(\mu_2 || \alpha \mu_1 + (1-\alpha) \mu_2).
-\end{equation*}
-
-Using this notation, the optimal proportions can be written as
-
-\begin{equation*}
-w^*(\bm{\mu}) = \arg \max_{w \in \Sigma_K} \min_{a \neq 1} (w_1 + w_a) I_{\frac{w_1}{w_1+w_a}}(\mu_1, \mu_a)
-\end{equation*}
-
-which let's us furthermore conclude that these quantities are equal for
-all \(a,b \in \{2,\dots, K\}\) with
-
-\begin{equation*}
-(w_1^* + w_a^*) I_{\frac{w_1^*}{w_1^*+w_a^*}}(\mu_1, \mu_a) = (w_1^* + w_b^*) I_{\frac{w_1^*}{w_1^*+w_b^*}}(\mu_1, \mu_b),
-\end{equation*}
-
-which is simply the statement in Lemma 4 of Garivier and Kaufmann
-(2016).
-
-And so by assuring the reader that there are ways to compute \(w_a^*\)
-and \(T^*\) given \(\bm{\mu}\) (see chapter 2.2 in Garivier and Kaufmann
-(2016)), we can now introduce the \emph{Track-and-Stop} strategy given
-in Garivier and Kaufmann (2016) that is able to match the lower bound.
-The main idea of the \emph{Track-and-Stop} algorithm is now to keep
-track of the optimal shares for each arm by equalizing the error
-probabilies for each arm.
-
-When going from theory to algorithm, the obvious problem is that we no
-longer know the true parameters \(\bm{\mu}\) and cannot calculate the
-optimal weights. Instead, we have to estimate the maximum likelihood
-estimates \(\hat{\mu}(t) = (\hat{\mu}_1(t), \dots, \hat{\mu}_K(t))\) of
-the true mean at the current round \(t\) and need to base our sample
-weights on them. It is however problematic to rely on the sample means
-as we are inherently unsure about them. And so wrong estimates, which
-naturally occur most easily in the beginning when not many samples have
-been pulled, are prone to lead to wrong weights. Thus, if a wrong
-estimate \(\hat{\mu}_a\) for arm \(a\) leads to a small weight \(w_a\),
-then after a few more rounds neither the estimate nor the weight will be
-correct. Thus, Kaufmann and Garivier conclude that ``a naive plug-in
-sampling rule sometimes fails''. They propose to enforce a certain
-minimum level of exploration to ensure that arms that erroneously
-received a very small weight will be further explored regardless.
-
-A very intuitive solution to this problem is proposed in Lemma 8 of
-Garivier and Kaufmann (2016) with the \(D-Tracking\) rule. Whenever some
-arm has received a very small number of pulls \(N_a(t)\) given the
-number of iterations \(t\) so far, and the number of arms \(K\) that
-have to share the samples, pull the arm that has received the smallest
-amount of samples so far. Else, pull the arm whose number of pulls so
-far \(N_a(t)\) is the farthest away from what its optimal share
-\(t\cdot w^*_a(\hat{\bm{\mu}}(t))\) would be. Given this sampling rule,
-the authors can show in their Proposition 9 that the empirical
-proportion of draws converges in probability to the optimal weights
-given the true means.
-
-When combining this sampling rule with an appropriate stopping rule, the
-authors are able to prove in Theorem 14 an upper bound on the expected
-sampling complexity \(\mathbb{E}_{\mu}[T_{\delta}]\). The stopping rule
-ensures that the algorithm explores sufficiently to promise a risk
-smaller than \(\delta\), while stopping as soon as possible. Given that
-the sampling rule is independent of this stopping rule, the rule boils
-down to a statistical test at every iteration and thus is a sequential
-test based on the current estimate of \(\hat{\bm{\mu}}\). Chernoff's
-Stopping Rule proposed in Garivier and Kaufmann (2016) calculates for
-each arm \(a\in \{1,...K\}\) the Generalized Likelihood Ratio statistic
-with every arm \(b \in \mathcal{A}^{\setminus a}\), which for
-\(\hat{\mu}_a(t) \geq \hat{\mu}_b(t)\) can be written as
-
-\begin{equation*}
-Z_{a,b}(t) = - Z_{b,a} = N_a(t) \KL(\hat{\mu}_a(t) || \hat{\mu}_{a,b}(t)) + N_b(t) \KL(\hat{\mu}_{b}(t) || \hat{\mu}_{a,b}(t)),
-\end{equation*}
-
-where
-
-\begin{equation*}
-\hat{\mu}_{a,b}(t) := \frac{N_a(t)}{N_a(t) + N_b(t)}\hat{\mu}_a(t) + \frac{N_b(t)}{N_a(t) + N_b(t)}\hat{\mu}_b(t).
-\end{equation*}
-
-Consequently, a sensible idea for a stopping rule would be that there
-has to be an arm \(a \in \{1,...,K\}\) for which
-\(Z_{a,b} \geq 0 \text{ for all } b \in \{1,...,K\}^{\setminus a}\)
-(which is always fulfilled if there is a uniquely best arm), and we
-demand that for this arm the smallest of the \((K-1)\) test statistics
-has to be larger than an exploration threshold \(\beta(t, \delta)\). The
-final sampling round \(T_{\delta}\) of the algorithm is given by:
-
-\begin{equation*}
-T_{\delta} = \inf \{t \in \mathbb{N}: \exists a \in \mathcal{A}, \forall b\in \mathcal{A}^{\setminus a}, Z_{a,b}(t) > \beta(t, \delta)\}
-\end{equation*}
-
-Demanding that the optimal exploration threshold increases in rounds
-\(t\) (if we have more samples, require more certainty; punish for
-failing previous tests) and decreases in risk \(\delta\) at a
-diminishing rate, the optimal exploration rate for Bernoulli arms
-derived in Theorem 10 of Garivier and Kaufmann (2016) is intuitive:
-
-\begin{equation*}
-\beta(t, \delta) = \log \Big(\frac{2t(K-1)}{\delta}\Big).
-\end{equation*}
-
-With this, we can state the final theorem of the chapter, which gives
-the upper bound matching the lower bound in Theorem
-\ref{theorem:GarivierKaufmannTheorem1} for small risk values \(\delta\)
-using the D-Tracking rule and Chernoff's stopping rule with the
-exploration term given in the previous equation:
-
-\begin{theorem}[Theorem 14, Garivier and Kaufmann, 2016] \label{theorem:GarivierAndKaufmannTheorem14}
-Let $\bm{\mu}$ be an exponential family bandit model.
-Let $\alpha \in [1, e/2]$ and $r(t) = O(t^{\alpha})$.
-Using Chernoff's stopping rule with $\beta(t,\delta) = \log(r(t)/\delta)$ and the sampling rule D-Tracking,
-
-\begin{equation*}
-\limsup_{\delta \to 0} \frac{\mathbb{E}_{\bm{\mu}}[T_{\delta}]}{\log(1/\delta)} \leq \alpha T^*(\mu), \quad \text{with } T^*(\mu) \text{ as defined in equation \ref{eqn:ComplexityTrackStopStrategy}}.
-\end{equation*}
-\end{theorem}
-
-\subsection{Conclusion}\label{conclusion}
-
-Overall, the two papers presented in this chapter make significant
-contributions to identifying the top-\(1\) or the top-\(m\) arms in a
-multi-armed bandit setting. Their contribution is primarily based on
-including the Kullback-Leibler divergence and Chernoff information as
-information theoretic measures in the derivation of bounds and the
-matching algorithms. Thereby, they go beyond a sum of squared gaps which
-is most relevant only in the case of Gaussian distributions. While the
-contribution in the fixed budget setting is limited to the two-armed
-bandit case, the authors derive general lower bounds in the fixed
-confidence setting. All bounds presented are primarily based on Lemma
-\ref{theorem:KaufmannEtAlLemma1}. Lemma \ref{theorem:KaufmannEtAlLemma1}
-is able to measure the ``transportation cost'' (see Garivier and
-Kaufmann, 2016) of moving from one distribution to another one in terms
-of Kullback-Leibler divergence. It is a bound on the expected likelihood
-ratio term that appears when changes in distribution are applied.
-
-In the case of the fixed budget top-\(m\) arm identification problem, we
-have seen that the derivation of a lower bound on the complexity term is
-mostly limited by the difficulty of defining an alternative problem
-\(\nu'\) to \(\nu\) that fits into the Lemma
-\ref{theorem:KaufmannEtAlLemma1}. But given the intuition that in
-top-\(m\) problems the \(m\)-th best arm and the \((m+1)\)-th best arm
-define an implied threshold between the two groups of arms, we were able
-to apply the ideas of Kaufmann et al. (2016) to our fixed budget
-thresholding bandit problem. In contrast to their problem, arms are
-classified against the known threshold \(\tau\), which makes it possible
-to define an alternative problem \(\nu'\) in which we do not have to
-change arms with respect to each other, but only with respect to
-\(\tau\). This has lead us to the simple lower bound on the problem
-complexity for the thresholding bandit problem with exponential family
-distributions given in Corollary \ref{corollary:LBKTBP}.
-
-In the best arm identification problem discussed by Garivier and
-Kaufmann (2016), we were introduced to the idea of comparing each arm to
-the best arm, and evaluating the difference between the best arm and the
-other arms based on the Generalized Likelihood Ratio test. This idea
-seems transferrable to the thresholding bandit problem. Indeed, it might
-even be easier as the best arm does not have to be estimated; instead,
-we would compare each arm to the threshold \(\tau\). Intuitively, one
-can frame this problem for each arm individually as an hypothesis test
-between the maximum likelihood estimate of the mean and the threshold
-\(\tau\). We will come back to this idea in
-\autoref{sec:LikelihoodRatioForExponentialFamily}.
-
-Lastly, we observe that Garivier and Kaufmann (2016) support their
-algorithm's main strategy by an additional D-Tracking rule which
-protects them against poor estimates in the beginning of the sampling.
-Such rule should be mostly unnecessary, for example, the cumulative
-regret setting, as algorithms there rely on upper confidence bound
-estimates. This is not the case for the Track-and-Stop strategy
-introduced in Garivier and Kaufmann, and neither for our Simple
-Likelihood Ratio strategy introduced in \autoref{sec:1DSLR}. In
-\autoref{sec:Simulation2}, we show empirically that the performance of
-the Simple Likelihood Ratio strategy can be further improved by naively
-adding the D-Tracking rule to it.
-
-\section{\texorpdfstring{Extensions to the Thresholding Bandit Problem
-\label{chap:Extensions}}{Extensions to the Thresholding Bandit Problem }}\label{extensions-to-the-thresholding-bandit-problem}
-
-\subsection{\texorpdfstring{Introduction
-\label{sec:ExtensionsIntroduction}}{Introduction }}\label{introduction-1}
-
-In \autoref{chap:ThresholdingBanditProblem} we have introduced the
-thresholding bandit problem as proposed in Locatelli et al. (2016)
-alongside the APT algorithm. We have seen that the upper bound on the
-APT algorithm matches the lower bound for the thresholding bandit
-problem given in Locatelli et al. (2016). The algorithm also exhibits
-favorable characteristics such that its upper bound holds at any
-stopping time, and that it does not require any parameter to be known
-upfront. However, we have seen that the index and the complexity term
-\(H\) employed by the APT algorithm are the most effective for
-\(R\)-sub-Gaussian distributions. Both are related to the KL-divergence
-between two Gaussian distributions of equal variance. Given that this
-sub-Gaussian approximation can be poor in certain cases, we motivated
-the use of information theoretic measures in an algorithm's index
-(compare \autoref{sec:DiscussionLocatelli}).
-
-Another goal can be to compare the distributions with the threshold
-based not only on the empirical mean -- as done by the APT algorithm. A
-logical extension is for example the empirical variance. After all arms
-do not necessarily have the same variance, even if they are
-sub-Gaussian. And given two arms for which we estimate the same mean, we
-would prefer to draw more samples from the arm with the larger variance.
-
-In the case of Gaussian distributions with varying variances, for
-example, it makes sense to take the variance into account; after all,
-given two Gaussians with equal mean, intuitively we would prefer to get
-a sample from the distribution of larger variance.
-
-For these reasons, in the following, we first present in
-\autoref{sec:VarianceBasedAlgorithms} two algorithms which incorporate
-empirical variances as described in Mukherjee et al. (2017) and Zhong et
-al. (2017). We then introduce a new algorithm based on the concept of
-likelihood ratios in \autoref{sec:LikelihoodRatioForExponentialFamily}.
-Finally, we compare the performance of different algorithms based on
-simulations and real world data sets in \autoref{chap:Experiments}.
-
-\subsection{\texorpdfstring{Variance Based Algorithms for the
-Thresholding Bandit
-\label{sec:VarianceBasedAlgorithms}}{Variance Based Algorithms for the Thresholding Bandit }}\label{variance-based-algorithms-for-the-thresholding-bandit}
-
-\subsubsection{\texorpdfstring{Augmented-UCB Algorithm
-\label{sec:AugUCBAlgorithm}}{Augmented-UCB Algorithm }}\label{augmented-ucb-algorithm}
-
-Combining learnings from the APT and other algorithms, Mukherjee et al.
-(2017) propose the Augmented-UCB (AugUCB) algorithm based on variance
-estimates for the thresholding bandit problem. The setting they consider
-is thus very similar to the setting in Locatelli et al. (2016). The main
-difference being that, while Locatelli et al. (2016) assume
-\(R\)-sub-Gaussian reward distributions, Mukherjee et al. (2017) assume
-rewards to be bounded in \([0,1]\), which makes the AugUCB applicable to
-less distributions. The AugUCB algorithm itself differs significantly
-from the APT algorithm. The two main ideas it employs are first, upper
-confidence bounds based on the Bernstein inequality and empirical
-variance estimates to compute the index based on which an arm is chosen
-at every round. Second, if an arm estimate is ``far enough away'' from
-the threshold as measured by the confidence bounds, it will be
-``eliminated'', and no longer be pulled until the end of the budget.
-Both ideas are based not only on the empirical mean estimate
-\(\mu_i(t)\), but also on a term \(s_i\) that is increasing linearly in
-the estimated standard deviation. While the APT algorithm plays the arm
-minimizing the quantity
-\(B_i^{APT}(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t) = \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau| + \epsilon)\),
-AugUCB plays the arm minimizing the quantity
-\(\hat{\Delta}_i(t) - 2s_i\), where \(s_i\) is based on the variance
-estimate \(\hat{v}_i\), and an exploration \(\psi_m\) term linear in
-\(T\), as well as an elimination parameter \(\rho\) (compare Algorithm 1
-in Mukherjee et al., 2017):
-
-\begin{equation*}
-s_i = \sqrt{\frac{\rho \psi_m (\hat{v}_i + 1) \log(T \epsilon_m)}{4n_i}}.
-\end{equation*}
-
-Consequently, the authors also introduce complexity measures which take
-the variance into account. From Gabillon et al. (2011) they use
-\(H_{\sigma, 1}= \sum_{i=1}^K \frac{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}{\Delta_i^2}\).
-Furthermore, with
-\(\stackrel{\sim}{\Delta}_i^2 = \frac{\Delta_i^2}{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}\),
-where \(\stackrel{\sim}{\Delta}_{(i)}\) is an increasing ordering of
-\(\stackrel{\sim}{\Delta}_i\), the authors define a complexity
-corresponding to \(H_{CSAR,2}\) in Chen et al. (2014):
-
-\begin{equation*}
-H_{\sigma,2} = \max_{i \in \mathcal{A}} \frac{i}{\stackrel{\sim}{\Delta}_{(i)}^2}.
-\end{equation*}
-
-While the latter complexity appears in the provided upper bound on the
-AugUCB algorithm's expected loss, it could be replaced by
-\(H_{\sigma, 1}\) since \(H_{\sigma, 2} \leq H_{\sigma,1}\).
-\(H_{\sigma,1}\) is more easily compared to the complexity \(H\) defined
-in Locatelli et al. (2016). Essentially, every arm's complexity
-contribution is additionally scaled by a term increasing in the arm's
-variance (see also the graph comparing the complexity terms of APT,
-AugUCB, and EVT algorithms below).
-
-In the case of the APT algorithm the number of times a specific arm has
-been drawn \(T_i\) measures how concentrated the estimated mean is
-around the true mean (and thus for large \(T_i\) an arm is no longer
-drawn even if \(\hat{\mu}\) is close to \(\tau\)). This exploration is
-regulated by the combination of the variance estimate \(\hat{v}_i\) and
-the exploration factor \(\psi_m\) in the case of the AugUCB algorithm.
-The terms ensure that certain arms are no longer pulled when the
-algorithm is sufficiently confident in the location of true mean.
-Indeed, the AugUCB algorithm goes a little further than the APT
-algorithm in that it eliminates arms (no longer considers them in
-sampling) when a separation condition is estimated to hold. The same
-separation condition of estimated mean away from the threshold is used
-in the authors' upper bound proof and is reminiscient of the separation
-condition used in Locatelli et al.'s (2016) upper bound proof.
-
-Therefore, when using a very similar favorable event in the proof of
-their upper bound, Mukherjee et al. (2017) have to bound the probability
-that an an arm is not removed from the active set after the a certain
-number of rounds -- even though the arm is above (respectively below)
-the threshold. If this probability is low, then the algorithm is able to
-be certain about an arm's true mean by employing variance estimates. In
-comparison, Locatelli et al (2016) used bounds on on how often arms are
-drawn (\(T_i\)) to give a bound on the probability of the favorable
-event. In order to derive the bound, Mukherjee et al. (2017) use the
-Bernstein inequality.
-
-It has to be noted that Mukherjee et al. (2017) have to assume that the
-distributions have rewards bounded in \([0,1]\) in order to derive the
-bound on the probability that an arm has not been eliminated correctly
-in round \(T_i\). Else it would not be possible to upper bound the
-\(s_i\) term by \(\Delta_i/4\) as Mukherjee et al. do in their proof.
-Thus, the distributions for which their upper bound holds are a subset
-of the \(R\)-sub-Gaussian distributions considered in Locatelli et al.
-(2016). However, while the authors demand in their setting that the
-rewards are bounded in \([0,1]\), it seems that the upper bound only
-requires the arms' variances to be bounded in \([0,1]\) such that
-\(\hat{v}_i \in [0,1]\). Thus, the upper bound should hold in particular
-for Gaussian distributions with variance \(\sigma^2 \in [0,1]\).
-Consequently, the simulations by Mukherjee et al. are performed on
-Gaussian arms with variance smaller than one.
-
-Based on this assumption, the authors show that the probability that an
-arm has not been eliminated after \(m_i\) rounds is given by (compare
-equation (2) in Mukherjee et al., 2017):
-
-\begin{equation} \label{Mukherjee2017Equation2}
-\mathbb{P}(\hat{\mu}_i > \mu_i + 2s_i) \leq \mathbb{P} (\hat{\mu}_i > \mu_i + 2\bar{s}_i) + \mathbb{P}(\hat{v}_i \geq \sigma^2_i + \sqrt{\rho \epsilon_{T_i}})
-\end{equation}
-
-Compare Mukherjee et al. (2017) for the notation. Then it becomes clear
-that the left part of the RHS gives the probability that the mean
-estimate is out of wack, while the right term gives the probability that
-the variance is overestimated. The first term is bounded by the
-Bernstein inequality. In the cumulative regret setting, there exists a
-similar decomposition for algorithms based on upper confidence bounds.
-There, the expected number of pulls of a suboptimal arm is bounded.
-Compare for example chapter 3.1 in Kaufmann, Korda and Munos (2012), in
-which the authors decompose the expected number of draws of an
-suboptimal arm into the probability that the optimal arm's mean is
-underestimated, and the probability that the upper confidence bound of
-the suboptimal arm is still very large. To give bounds for UCB
-algorithms, certain convergence rates are shown for these two
-probabilities. Mukherjee et al. do similarly for their upper confidence
-algorithm in the thresholding setting.
-
-\subsubsection{\texorpdfstring{Anytime Parameter-free Empirical Variance
-Guided Algorithm
-\label{sec:EVTAlgorithm}}{Anytime Parameter-free Empirical Variance Guided Algorithm }}\label{anytime-parameter-free-empirical-variance-guided-algorithm}
-
-Another algorithm for the thresholding bandit problem employing
-empirical variance estimates is introduced in Zhong et al. (2017).
-Indeed, the authors discuss several variations of their algorithm which
-extend their central idea to applications in which several samples need
-to be pulled in a parallel and asynchronous fashion. An standard example
-known from the multi-armed bandit literature (see for example Li et al.
-(2010)) is a website for which different versions are served to visitors
-and each version is an arm in the bandit setting. If the feedback that
-is observed by the algorithm is whether or not a user makes a purchase,
-then it is likely that a new user arrives before the feedback for the
-previous user has been observed. The algorithm has to pull the next arm
-before the feedback of the previous arm has been observed. With their
-variants the authors approach this problem of having to take
-asynchronous and parallel actions. But their algorithm can also be
-reduced to a simpler version that can be compared directly with the
-problem described in Locatelli et al. (2016) where the feedback lag is
-assumed to be zero.
-
-This simpler version is the parameter-free version of their Empirical
-Variance Guided Algorithm (EVT\(_{pf}\)). The EVT\(_{pf}\) algorithm is
-an extension of the APT algorithm that takes the empirical variance of
-the arms into account and deduces an upper bound through empirical
-Bernstein bounds in a proof following the model of the one described in
-Locatelli et al. (2016).
-
-In order to describe their algorithm, we adapt a formulation used in
-Zhong et al. (2017) to describe the index used by the algorithms in a
-more general fashion. Write the index \(B_i(t+1)\) of arm \(i\) at round
-\(t\) as previously as
-
-\[
-B_i(t+1) = S_i(t) D_i(t),
-\]
-
-where \(D_i(t)\) is some measure of the distance between the mean
-\(\mu_i\) or the distribution \(\nu_i\) of arm \(i\) from the threshold
-\(\tau\), while \(S_i(t)\) is some confidence value measuring how
-confident we can be in \$. Thus, for the APT algorithm, if we let
-\(\epsilon = 0\) as in Zhong et al. (2016), we have
-
-\[
-D_i^{APT}(t) = \hat{\Delta}_i(t) = |\hat{\mu}_i(t) - \tau| \quad \text{and} \quad S_i^{APT}(t) = \sqrt{T_i(t)}
-\]
-
-We see that \(D_i(t)\) is the probably most straightforward distance
-between the sample mean and the threshold, while \(S_i(t)\) increases
-over time, as we become more confident in our sample mean, and thus
-ensures that we do not continue pulling the same arm forever.
-
-Based on this, we can now easily compare APT to EVT\(_{pf}\) for which
-the index can be written as:
-
-\[
-D_i^{EVT_{pf}}(t) = \sqrt{\hat{\sigma}^2_{i}(t) + \hat{\Delta}_i(t)} - \hat{\sigma}_i(t) \quad \text{and} \quad S_i^{EVT_{pf}} = \sqrt{T_i(t)}
-\]
-
-We see that both algorithms employ the same confidence term. The
-empirical variance describes the shape of the distribution and thus is a
-measure of how far the distribution (in contrast to just the mean) is
-away from the threshold. It consequently makes sense to have it appear
-in \(D_i^{EVT}\). And in contrast to the APT algorithm, the EVT\(_{pf}\)
-algorithm consequently takes more information about the arms into
-account than just their mean. As mentioned previously, this should
-especially be valuable whenever arms have indeed different variances.
-Similar (very roughly) to how the Kullback-Leibler divergence measures
-distances between distributions, the \(D_i^{EVT}\) including the
-empirical variance serves as a crude measure of distance between
-threshold and distribution. We note that for a Bernoulli distributed
-random variable, \(D_i^{EVT}\) is always decreasing as the mean
-approaches the threshold (compare the figure 2). Similar should hold in
-general for bounded variables as the variance and the mean are linked by
-the distance of the mean to the bound of the support (in contrast to,
-for example, a normal distributed random variable where a change in the
-mean does not correspond to a change in the variance). This is important
-as the bounds of the EVT\(_{pf}\) algorithm only hold for random
-variables bounded in \([0,1]\). In contrast to the AugUCB, this
-restriction is not just on the variance of the arm but explicitly on the
-reward itself in the current version that builds on empirical Bernstein
-bounds as shown in Maurer and Pontil (2009).
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/EVT_Index_Bernoulli-1}
-
-}
-
-\caption{This graph displays the distance part of the index of the APT, SLR, and EVT algorithms.
-While EVT's distance is based on both the empirical mean and empirical variance, the empirical mean determines the variance in the case of Bernoullis.
-We see that the distance of both EVT and SLR has an asymmetric behavior.}\label{fig:EVT_Index_Bernoulli}
-\end{figure}
-
-By defining a new complexity measure \(H^{\text{EVT}_{pf}}\) for the
-EVT\(_{pf}\) algorithm, Zhong et al. (2017) are able to derive an upper
-bound on the expected loss of the algorithm. Let the complexity increase
-in the variance and decrease in the distance of the mean from the
-threshold such that
-
-\[
-H^{\text{EVT}_{pf}} = \sum_{i=1}^K h_i^{\text{EVT}_{pf}} = \sum_{i=1}^K (\sigma_i^2\Delta_i^{-2} + \Delta_i^{-1}).
-\]
-
-Then one can state the following theorem.
-
-\begin{theorem}[Theorem 5, Zhong et al., 2017] 
-\label{theorem:ZhongEtAl2017Theorem5}
-Let $K > 0$, $T > 2K$, and consider a thresholding bandit problem. Assume that all arms of the problem are bounded in $[0,1]$. Then the probability of an error is bounded as
-
-\begin{equation*}
-\mathbb{E}[L] \leq TK \exp\Big(-C\frac{T}{H^{\text{EVT}_{pf}}}\Big),
-\end{equation*}
-
-where $C$ is some positive constant.
-\end{theorem}
-
-The authors approach the proof very similarly as Locatelli et al. (2016)
-in the proof of their lower bound. They define favorable events that
-hold with large probability, and ensure that the same separation
-condition as in Locatelli et al. holds for them given that each arm is
-pulled sufficiently often. Additionally to a favorable event that bounds
-the deviation between sample mean and population mean, they define a
-second event on which the sample standard deviation is close to the
-population standard deviation. This is bounded in large probability by
-an empirical Bernstein inequality (Maurer and Pontil, 2009). The union
-of the two events then serves as the favorable event in the remainder of
-their proof.
-
-Given a lower bound adapted to the new complexity
-\(H^{\text{EVT}_{pf}}\), the Zhong et al. (2017) show that the
-EVT\(_{pf}\) algorithm is optimal in that its upper bound matches the
-lower bound. Furthermore, they compare their algorithm in experiments
-against the APT algorithm. The experiments use data generated from
-uniform distributions. Each experiment compares 100 arms with variances
-picked at random from a range of possible variances. Over three
-experiments, the range of variances is varied from small to large, where
-the authors expect their algorithm to show the largest advantage
-compared to APT on the problem with small variances. Interestingly, they
-report the largest advantage of their variance based algorithms in
-comparison to APT when the variances are very small; given they only
-consider problems bounded on a support of \([0,1]\), \(\sigma_i \ll 1\).
-In this case the problem complexity \(H^{\text{EVT}_{pf}}\) can be much
-smaller than \(H^{APT}\) -- the EVT\(_{pf}\) algorithm profits more from
-distributions that are simple to estimate in terms of their variance
-than the APT algorithm does.
-
-When comparing the two complexities for example for Bernoulli random
-variables against some fixed threshold, we see that the smaller
-complexity of the EVT\(_{pf}\) algorithm implies in particular that
-EVT\(_{pf}\) could be able to cope with distributions of parameter
-\(\mu\) close to \(\tau\) much better than APT (compare figure 3).
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.7\linewidth]{Draft_files/figure-latex/Hevt_Hapt_Comparison-1}
-
-}
-
-\caption{Comparing the complexity terms used in the APT, AugUCB, and EVT algorithms, we observe that the problem complexity of the EVT algorithm increases much less rapidly than for the other algorithms.
-Thus, the EVT should be able to cope with arms close to the threshold better than the APT algorithm.
-The complexity displayed for the AugUCB is an upper bound on the complexity used in the upper bound of Mukherjee et al.
-(2017).}\label{fig:Hevt_Hapt_Comparison}
-\end{figure}
-
-\subsection{\texorpdfstring{Likelihood Ratio for Sequential Sampling
-\label{sec:LikelihoodRatioForExponentialFamily}}{Likelihood Ratio for Sequential Sampling }}\label{likelihood-ratio-for-sequential-sampling}
-
-We now present a new sequential sampling algorithm for the fixed budget
-thresholding bandit problem that builds on the idea of the likelihood
-ratio statistic for hypothesis tests. We first shortly describe the
-general idea of likelihood ratio based tests, to then introduce this new
-algorithm for the thresholding bandit problem, which we call Simple
-Likelihood Ratio (SLR) algorithm.
-
-\subsubsection{\texorpdfstring{Likelihood Ratio-based Hypothesis Tests
-\label{sec:LRTests}}{Likelihood Ratio-based Hypothesis Tests }}\label{likelihood-ratio-based-hypothesis-tests}
-
-In a standard parametric testing problem, we have drawn an iid sample
-\(x = (x_1, ..., x_T)\), where each \(x_i\) is a realization from the
-random variable \(X_i\). We assume that \(X_i\) follows some probability
-distribution \(Q(\theta)\) paramaterized by a vector \(\theta\). Let
-\(q(x;\theta)\) be the density function corresponding to the
-distribution. We would like to test whether an alternative
-parameterization is more likely than the parameterization given by the
-null hypothesis. That is, we test
-
-\[
-H_0: \quad \theta = \theta_{H_0} \qquad \text{vs.} \qquad H_1: \quad \theta = \theta_{H_1}
-\]
-
-In order to assess whether the \(H_0\) hypothesis can be rejected, one
-computes the likelihood \(L(x|\theta)\) of the observed sample under
-both parameterizations:
-\(L_{H_0} = L(x|\theta = \theta_{H_0}) = \prod_{i=1}^T q(x_i|\theta_{H_0})\)
-and
-\(L_{H_1} = L(x|\theta = \theta_{H_1}) = \prod_{s=1}^T q(x_s|\theta_{H_1})\).
-The likelihood ratio test statistic is then given as
-
-\[
-LR_T(\theta_{H_0}|| \theta_{H_1}) = \frac{L_{H_0}}{L_{H_1}} = \prod_{s=1}^T\frac{q(x_s|\theta_{H_0})}{ q(x_s|\theta_{H_1})}.
-\]
-
-and is used in the optimal test of two hypotheses as shown by the
-Neyman-Pearson lemma (see chapter 11, Theorem 11.7.1 in Cover and
-Thomas, 2006).
-
-The intuition behind the test of course being that, if the true
-parameterization is \(H_1\) and not \(H_0\), then the likelihood
-\(L_{T,H_1}\) should be larger than \(L_{T,H_0}\). A small enough
-likelihood ratio would thus lead us to a rejection of the null
-hypothesis, while a large likelihood ratio is evidence in favor of the
-null hypothesis.
-
-Furthermore, the likelihood ratio is inherently linked to information
-theoretic quantities and divergence measures. Assuming that \(Q\) is a
-discrete distribution with support \(\chi\), one can write the negative
-log-likelihood ratio as (compare Cover and Thomas, 2006)
-
-\begin{align*}
--\log(LR_T(\theta_{H_0}|| \theta_{H_1}) & = \sum_{i=1}^T \log(\frac{q(x_s|\theta_{H_0})}{ q(x_s|\theta_{H_1})}) \\
-& = \sum_{a \in \chi} T q(a|\hat{\theta}) \log(\frac{q(a|\theta_{H_0})}{ q(a|\theta_{H_1})}) \\
-& = \sum_{a \in \chi} T q(a|\hat{\theta}) \log(\frac{q(a|\theta_{H_0})}{ q(a|\theta_{H_1})}\frac{q(a|\hat{\theta})}{ q(a|\hat{\theta})}) \\
-& = T \KL(q(\hat{\theta})||q(\theta_{H_0})) - T \KL(q(\hat{\theta})||q(\theta_{H_1})),
-\end{align*}
-
-where \(\hat{\theta}\) is the maximum likelihood estimate of the
-parameter \(\theta\) given the sample \(x\). If we hold the \(H_0\)
-hypothesis fixed and set \(\theta_{H_1} = \hat{\theta}\) as often done
-in praxis, then with \(\KL(Q(\hat{\theta})||Q(\hat{\theta})) = 0\):
-
-\[
--\log(LR_T(\theta_{H_0}|| \theta_{H_1})) = -\log(LR_T(\theta_{H_0}|| \hat{\theta})) = \KL(Q(\hat{\theta}||Q(\theta_{H_0}))
-\]
-
-Furthermore, we have for any distributions \(Q_{H_0}\) and \(Q_{H_1}\)
-for a sample \(x\) sampled from the \(H_0\) distribution, that
-
-\[
-\frac{1}{n} \log(LR_T(\theta_{H_0}||\theta_{H_1})) \rightarrow \KL(Q(\theta_{H_0})||Q(\theta_{H_1})) \quad \text{in probability},
-\]
-
-by the law of large numbers (or asymptotic equipartition property) for
-the Kullback-Leibler divergence as in Theorem 11.8.1 in Cover and Thomas
-(2006). Lastly, based on the characteristics shown before, for
-frequentist tests the Kullback-Leibler divergence between
-\(Q(\theta_{H_0})\) and \(Q(\theta_{H_1})\) gives the best possible
-exponent for the error of the second type given a fixed error of the
-first type. This is the result of the Chernoff-Stein Lemma (Theorem
-11.8.3, Cover and Thomas, 2006), which is reminiscient of the complexity
-\(\kappa_B\) derived by Kaufmann et al. (2016) and as described in
-\autoref{chap:KullbackLeiblerPureExploration}:
-
-\begin{theorem}[Chernoff-Stein Lemma] \label{theorem:ChernoffStein}
-Let $X_1, X_2, ..., X_n$ be i.i.d.
-distributed according to $Q$.
-Consider the hypothesis test between two alternatives, $Q=P_1$ and $Q=P_2$, where $\KL(P_1||P_2) < \infty$.
-Let $A_n \subseteq \chi^n$ be an acceptance region for hypothesis $H_1$.
-Let the probabilities of error be $\alpha_n = P_1^n(A_n^C)$, and $\beta_n = P_2^n(A_n)$, and for $0< \epsilon <1/2$, define $\beta_n^{\epsilon} = \min_{A_n \subseteq \chi^n, \alpha_n < \epsilon} \beta_n$.
-Then
-
-$$
-\text{lim}_{n\rightarrow \infty} \frac{1}{n} \log \beta_n^{\epsilon} = - \KL(P_1||P_2)
-$$
-\end{theorem}
-
-\subsubsection{Likelihood Ratio as Index in Sequential
-Sampling}\label{likelihood-ratio-as-index-in-sequential-sampling}
-
-We now employ the concept of the likelihood-ratio test for a new
-sequential sampling strategy for the thresholding bandit problem. In
-contrast to the cumulative regret problem or the best arm identification
-problem, the thresholding bandit problem offers a natural \(H_0\)
-hypothesis for the arms' distributions: the threshold \(\tau\). Given
-that we want to classify the arms against the threshold, and given that
-\(\tau\) is known and fixed, we can set a null hypothesis that is a
-function of \(\tau\). In the simplest case, the distributions are
-parameterized by their mean \(\theta_i = \mu_i\), and we set
-\(\theta_{i,H_0} = \tau\) for all arms. The likelihood ratio then
-quantifies how ``significant'' of a difference there is between the
-threshold \(\tau\) and the current sample mean \(\hat{\mu}_i(t)\) of an
-arm, assuming distributions for which the maximum likelihood estimate of
-the mean is given by the empirical mean. In these cases, the likelihood
-ratio will be smaller than 1 and decrease in sample size even if the
-threshold and sample mean are constant.
-
-Due to these characteristics, the likelihood ratio can serve as a
-natural index for sampling strategies. Consider the setting described in
-\autoref{sec:Setup} and \autoref{sec:TheAPTAlgorithm} though without
-assuming \(R\)-sub-Gaussian distributions. Consider \(B_i^{APT}\) and
-compare it to
-
-\[
-B_i^{LR}(t+1) = LR(\tau|| \hat{\mu}_i(t)) = \prod_{i=1}^T\frac{q(x_i|\tau)}{ q(x_i|\hat{\mu}_i(t))}.
-\]
-
-We have \(B_i(t) \leq 1\), \(t \uparrow \rightarrow B_i(t) \downarrow\),
-and \(|\hat{\mu}_i(t) - \tau| \uparrow \rightarrow B_i(t) \downarrow\).
-Consequently, by choosing the arm that maximizes \(B_i(t)\), we choose
-an arm for which we either have not collected many samples, or for which
-the sample mean is close to the threshold \(\tau\). In this sense, a
-strategy based on the likelihood ratio is reminiscient of the index
-employed by the APT algorithm. Indeed, assuming the samples are normally
-distributed with the same variance for the distribution \(\nu_i\) under
-both \(H_0\) and \(H_1\), then \(-\log(LR(\tau||\hat{\mu}_i(t)))\)
-equals the index in APT. Why then would one use the likelihood based
-strategy?
-
-Given that the APT index and the likelihood-ratio based index are only
-equivalent for normally distributed random variables with fixed standard
-deviation, the new strategy promises efficiency improvements whenever
-the true distribution is known and different from the normal
-distribution. The most important example are Bernoulli arms with small
-means as motivated. While the likelihood ratio can in theory be used for
-any distributions, and arms could even have different classes of
-distributions, the class of distribution has to be known upfront for
-every arm. Given the role of the threshold \(\tau\) and the goal of
-classification of the mean against \(\tau\), the likelihood ratio
-strategy is arguably most naturally employed on distributions
-parameterized by their mean. In the following descriptions, we thus
-focus on univariate distributions of the exponential family.
-Additionally, we also propose a version for the Normal distribution with
-unknown mean. Before we describe the algorithm, we show that the
-likelihood ratio has a very convenient form for this family of
-distributions.
-
-\subsubsection{\texorpdfstring{Likelihood Ratio for Univariate
-Exponential Family of Distributions
-\label{sec:LRforUnivariateExponentialFamily}}{Likelihood Ratio for Univariate Exponential Family of Distributions }}\label{likelihood-ratio-for-univariate-exponential-family-of-distributions}
-
-We now focus on a thresholding bandit problem where the arms are
-distributed according to \(\nu_{\theta_1}, ..., \nu_{\theta_K}\), which
-are all from the same canonical exponential family of distributions with
-scalar parameter \(\theta_i \in \Theta\). The probability density
-function of the absolutely continuous distribution \(\nu_{\theta_i}\)
-with regard to a dominating measure \(\rho\) on \(\mathbb{R}\) is given
-by \(q(x|\theta) = h(x) \exp(T(x)\theta - b(\theta))\). As described in
-Cappé et al. (2013), citing Lehmann and Casella (1998), the derivative
-\(b'(\theta)\) of \(b(\theta)\) is an increasing continuous function
-such that the expected value \(\mathbb{E}(\nu_{\theta}) = b'(\theta)\)
-for all \(\theta \in \Theta\). Given that \(b'(x)\) is strictly convex,
-we have a one-to-one relation between \(b'(\theta)\) and
-\(\mathbb{E}(\nu_{\theta})\) through the continuous inverse
-\(b'^{-1}(\theta)\). Consequently, one can just as well parameterize the
-distribution its mean \(\mu = \mathbb{\nu_{\theta}}\) and write
-\(\nu_{b'^{-1}(\mu)}\) with the probability density function (compare
-Cappé et al., 2013)
-
-\[
-q(x|b'^{-1}(\mu)) = h(x) \exp(T(x) b'^{-1}(\mu) - b(b'^{-1}(\mu))).
-\]
-
-This lets us write the likelihood ratio for the exponential family
-distributions as
-
-\[
-LR(b'^{-1}(\mu_0)||b'^{-1}(\mu_1)) = \prod_{i=1}^n \frac{\exp(T(x_i) b'^{-1}(\mu_0) - b(b'^{-1}(\mu_0)))}{\exp(T(x_i) b'^{-1}(\mu_1) - b(b'^{-1}(\mu_1)))}
-\]
-
-or if we write it as negative log-likelihood ratio:
-
-\[
--\log(LR) = n\Big(b\big(b'^{-1}(\mu_0)) - b(b'^{-1}(\mu_1)\big)\Big) - \Big(b'^{-1}(\mu_0)-b'^{-1}(\mu_1)\Big)\sum_{i=1}^nT(x_i)
-\]
-
-As we will see now, this statistic takes a very convenient closed form
-for many common distributions.
-
-\textbf{Example 1: Bernoulli Distribution}
-
-We have \(T(x_i) = x_i\), \(\theta = \log(\mu/(1-\mu))\),
-\(\Theta = (0,1)\), \(b(\theta) = \log(1+\exp(\theta))\), and
-\(\mu \in (0,1)\). Then \(b'(\theta) = \mu\), and we can write
-
-\begin{align*}
--\log(LR(\mu_0||\mu_1)) & = n(\log\Big(\frac{1-\mu_0}{1-\mu_1}\Big)) - \Big(\log(\frac{\mu_0}{1-\mu_0}) - \log(\frac{\mu_1}{1-\mu_1})\Big)\sum_{i=1}^{n}x_i \\
-& = n \Big( (1-\hat{\mu})\log\Big(\frac{1-\mu_1}{1-\mu_0}\Big) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}) \Big)
-\end{align*}
-
-We observe that, if we let \(\mu_0 = \tau\) and \(\mu_1 = \hat{\mu}\)
-(compare \autoref{sec:LRTests}), then
-
-\[
--\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n \Big(\hat{\mu}\log\big(\frac{\hat{\mu}}{\tau}\big) + (1-\hat{\mu})\log\big(\frac{1-\hat{\mu}}{1-\tau}\big)\Big)
-\]
-
-\textbf{Example 2: Poisson Distribution}
-
-We have \(T(x_i) = x_i\), \(\theta = \log(\mu)\),
-\(\Theta = \mathbb{R}\), \(b(\theta) = \exp(\theta)\), and
-\(\mu \in (0, +\infty)\). Then \(b'(\theta) = \mu\), and we can write:
-
-\[
--\log(LR(\mu_0||\mu_1)) = n(\mu_0 - \mu_1) - (\log(\mu_0) - \log(\mu_1))\sum_{i=1}^n x_i = n\Big((\mu_0 - \mu_1) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}\Big)\Big)
-\]
-
-We observe that, if we let \(\mu_0 = \tau\) and \(\mu_1 = \hat{\mu}\)
-(compare \autoref{sec:LRTests}), then
-
-\[
--\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n\Big((\tau - \hat{\mu}) + \hat{\mu}\log\Big(\frac{\hat{\mu}}{\tau}\Big)\Big)
-\]
-
-\textbf{Example 3: Normal distributions with known variance
-\(\sigma^2\)}
-
-We have \(T(x_i) = x_i\), \(\theta = \mu/\sigma^2\),
-\(\Theta = \mathbb{R}\), \(b(\theta) = \sigma^2\theta^2/2\),
-\(\mu \in \mathbb{R}\). Then \(b'(\theta) = \mu\), and we can write
-
-\[
--\log(LR(\mu_0||\mu_1)) = n (\frac{\mu_0^2}{2\sigma^2} - \frac{\mu_1^2}{2\sigma^2}) - (\frac{\mu_0}{\sigma^2} - \frac{\mu_1}{\sigma^2})\sum_{i=1}^nx_i = n\frac{1}{2\sigma^2}\Big(\mu_0^2-\mu_1^2 - 2\mu_0\hat{\mu} + 2\mu_1\hat{\mu}\Big)
-\]
-
-And again, even though the distribution is continuous (compare
-\autoref{sec:LRTests}), if we let \(\mu_1 = \hat{\mu}\) and
-\(\mu_0 = \tau\), then
-
-\[
--\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n\frac{(\hat{\mu} - \tau)^2}{2\sigma^2}.
-\]
-
-\textbf{Example 4: Gamma distributions with known shape parameter
-\(\alpha\)}
-
-We have \(T(x_i) = x_i\), \(\theta = -\alpha/\mu\),
-\(\Theta = (-\infty, 0)\), \(b(\theta) = -\alpha \log(-\theta)\),
-\(\mu \in (0,+\infty)\). Then \(b'(\theta) = -\mu\), and we can write
-
-\[
--\log(LR(\mu_0||\mu_1)) = n\alpha(-\log(\frac{\alpha}{\mu_0}) - \log(\frac{\mu_1}{\alpha})) - (-\frac{\alpha}{\mu_0} + \frac{\alpha}{\mu_1})\sum_{i=1}^{n}x_i = n\alpha \Big(\log\big(\frac{\mu_0}{\mu_1}\big) - \frac{\hat{\mu}}{\mu_1} + \frac{\hat{\mu}}{\mu_0}\Big).
-\]
-
-And again, even though the distribution is continuous (compare
-\autoref{sec:LRTests}), if we let \(\mu_1 = \hat{\mu}\) and
-\(\mu_0 = \tau\), then
-
-\[
--\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n\alpha \Big(\frac{\hat{\mu}}{\tau} - 1 - \log\big(\frac{\hat{\mu}}{\tau}\big)\Big).
-\]
-
-For \(\alpha = 1\), the Gamma distribution is equal to the Exponential
-distribution.
-
-Given these results for the exponential family of distributions, we can
-now define the Simple Likelihood Ratio algorithm.
-
-\subsection{\texorpdfstring{1D-Simple Likelihood Ratio Algorithm
-\label{sec:1DSLR}}{1D-Simple Likelihood Ratio Algorithm }}\label{d-simple-likelihood-ratio-algorithm}
-
-Consider again the setting in \autoref{sec:Setup} though without the
-assumption of \(R\)-sub-Gaussian distributions. Instead, assume that the
-class of distributions that the arms \(i \in \mathbb{A}\) follow is
-known upfront. For the 1D-SLR algorithm, we restrict the potential
-classes to the univariate exponential family of distributions and write
-the class generally as \(\nu(\mu, \theta)\). Here, \(\theta\) describes
-additional parameters known upfront, as for example
-\(\sigma_1, ..., \sigma_K\) for Normal distributions, or
-\(\alpha_1, ..., \alpha_K\) for Gamma distributions. Additionally to
-\(\nu(\mu)\), the 1D-SLR algorithm receives as input the definition of
-the problem \((\tau, \epsilon)\) (compare Locatelli et al., 2016). As
-initialization, the algorithm pulls each arm once. At time \(t>K\), the
-algorithm updates the number of pulls for arm \(i\) at time \(t\),
-\(T_i(t)\), for each arm, as well as the empirical mean
-\(\hat{\mu}_i(t)\) of arm \(i\) after \(T_i(t)\) pulls. The empirical
-mean is calculated for each arm \(k\in \{1,...,K\}\) as
-\(\hat{\mu}_i(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)} x_{i,s}\), with
-\(T_i(t) = \sum_{s=1}^{t}\mathbb{I}(I_s = i)\). It serves as maximum
-likelihood estimate of the arm's mean. As in Locatelli et al. (2016),
-the \(X_{i,s}\) is the sample received when pulling arm \(i\) for the
-\(s\)-th time. Depending on the distribution, the algorithm then
-computes the index
-
-\begin{align*}
-B_i^{SLR}(t+1) & = \mathbb{I}(\hat{\mu}\geq \tau)(-\log\big(LR(\tau-\epsilon||\hat{\mu}_i(t))\big) \\
-& \quad +\: \mathbb{I}(\hat{\mu} <\tau)(-\log\big(LR(\tau+\epsilon||\hat{\mu}_i(t))\big) \\
-& = T_i(t) \Big( \mathbb{I}(\hat{\mu}\geq \tau)\cdot KL(\nu_{b'^{-1}(\hat{\mu}(t))}||\nu_{b'^{-1}(\tau-\epsilon)}) \\
-& \quad \quad +\: \mathbb{I}(\hat{\mu} < \tau)\cdot KL(\nu_{b'^{-1}(\hat{\mu}(t))}||\nu_{b'^{-1}(\tau+\epsilon)}) \Big) \Alignyesnumber\label{eqn:SLRIndex}.
-\end{align*}
-
-The next arm to be pulled is the minimizer of the index
-\(B_i^{SLR}(t+1)\), \(I_{t+1} = \arg \min_{i\leq K} B_i(t+1)\). At the
-end of the horizon \(T\), the algorithm outputs the set of arms
-\(\hat{S}_\tau = \{i \in \mathbb{A}, \hat{\mu}_i(T) \geq \tau\}\).
-
-\IncMargin{1em}
-
-\begin{algorithm}
-\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
-\Input{$\tau$, $\epsilon$, class of distributions $\nu(\mu, \theta)$, $\theta_i \: \forall i \in \mathbb{A}$}
-\Output{$\hat{S}_\tau = \{i \in \mathbb{A},  \hat{\mu}_i(T) \geq \tau\}$}
-\BlankLine
-\emph{Pull each arm once}\;
-\For{$t = K+1$ \KwTo $T$}{
-  \emph{Pull arm $I_t = \arg \min_{i\leq K} B_i^{SLR}(t)$ as in \autoref{eqn:SLRIndex}}\;
-  \emph{Observe reward $X_t \sim \nu_{I_t}$}\;
-}
-\caption{SLR algorithm for univariate exponential family of distributions}\label{algo_slr_1d}
-\end{algorithm}
-
-\DecMargin{1em}
-
-\subsection{2D-SLR Algorithm for Normal
-Distributions}\label{d-slr-algorithm-for-normal-distributions}
-
-As soon as we move away from univariate distributions parameterized by
-their mean, it becomes less clear how the likelihood ratio for
-\(H_0: \mu = \tau\) and \(H_1: \mu = \hat{\mu}\) should be calculated.
-In the case of Normal distributions with unknown mean and unknown
-variance, given that the variance and mean estimate are linked, we can
-use
-\(H_0: \mu = \tau \land \sigma^2 = \sigma^2_{\tau} = \frac{1}{n}\sum_{i=1}^{n}(x_i-\tau)^2\)
-and the alternative hypothesis based on the maximum likelihood estimates
-\(H_1: \mu = \hat{\mu} \land \sigma^2 = \hat{\sigma}^2 = \frac{1}{n}\sum_{i=1}^{n}(x_i-\hat{\mu})^2\).
-In the following, we assume \(\epsilon = 0\) for simplicity.
-
-At each round \(t\), the algorithm computes \(T_i(t)\) and
-\(\hat{\mu}_i(t)\) as before, and additionally the empirical variances
-\(\sigma_{\tau,i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\tau)^2\)
-and
-\(\hat{\sigma}_{i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\hat{\mu})^2\),
-where \(\hat{\sigma}_{i}^2(t) < \sigma_{\tau,i}^2(t)\) if
-\(\hat{\mu} \neq \tau\) since \(\hat{\mu}\) is the maximum likelihood
-estimate. The index is then
-
-\begin{align*}
-B_i^{SLR_{2D}}(t+1) & = -\log\big(LR(\tau, \sigma_{\tau,i}^2(t)||\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t))\big) \\
-& = T_i(t) \log\Big(\frac{\sigma_{\tau,i}^2(t)}{\hat{\sigma}_i^2(t)}\Big) \\
-& = T_i(t) \KL\big(N(\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t))||N(\tau, \sigma_{\tau,i}^2(t))\big) \Alignyesnumber\label{eqn:SLR2DIndex}
-\end{align*}
-
-Then, as for the univariate case, the next arm to be pulled is the
-minimizer of the index \(B_i^{SLR_{2D}}(t+1)\),
-\(I_{t+1} = \arg \min_{i \leq K} B_i(t+1)\). At the end of the horizon
-\(T\), the algorithm outputs the set of arms
-\(\hat{S}_\tau = \{i \in \mathbb{A}, \hat{\mu}_i(T) \geq \tau\}\).
-
-\IncMargin{1em}
-
-\begin{algorithm}
-\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
-\Input{\emph{$\tau$, $\epsilon$, $\nu(\mu, \theta) = N(\mu,\sigma^2) \, \forall i \in \mathbb{A}$, where $\mu$ and $\sigma^2$ are unknown}}
-\Output{$\hat{S}_\tau = \{i \in \mathbb{A},  \hat{\mu}_i(T) \geq \tau\}$}
-\BlankLine
-\emph{Pull each arm twice}\;
-\For{$t = 2K+1$ \KwTo $T$}{
-\For{$i = 1$ \KwTo $K$}{
-  \emph{Compute $\hat{\sigma}^2_{i}(t)$}\;
-  \If{$\hat{\sigma}^2_{i}(t) = 0$}{\emph{Set $\hat{\sigma}^2_{i}(t) = 1/T$}}
-}
-  \emph{Pull arm $I_t = \arg \min_{i\leq K} B_i^{SLR_{2D}}(t)$ as in \autoref{eqn:SLR2DIndex}}\;
-  \emph{Observe reward $X_t \sim \nu_{I_t}$}\;
-}
-\caption{2D-SLR algorithm for Normal distributions with unknown mean and unknown variance}\label{algo_slr_2d}
-\end{algorithm}
-
-\DecMargin{1em}
-
-\subsection{Discussion}\label{discussion-1}
-
-At the beginning of this thesis, we set out to find an algorithm that
-improves upon the Anytime Parameter Free algorithm introduced in
-Locatelli et al. (2016) for the thresholding bandit problem in two
-points. First, we wanted to make the algorithm perform better in
-problems with arms that are not well approximated as sub-Gaussian; in
-particular a problem with Bernoulli arms of small means, and with a
-threshold close to 0. We thus tried to find a strategy that takes more
-information about the arms into account than purely the sample mean.
-With the Simple Likelihood Ratio strategy, we propose an algorithm that
-fulfills this goal at the cost of being distribution specific.
-
-The SLR strategy requires the knowledge of the class of distribution
-upfront, just as other algorithms require parameters. While this is
-likely to be a negligiable problem in the case of \(\{0,1\}\)
-observations whose mean can be modeled reasonably by Bernoulli
-distributions, it can be more difficult to know the true class of
-distributions upfront when \(\nu_i\) are continuous distributions. We
-have shown however, that the SLR strategy can be adapted to all
-univariate distributions in the exponential family of distributions. The
-algorithm even offers a natural adaptation to the problem of normal
-distributions with unknown mean and unknown variance.
-
-Furthermore, the SLR strategy reduces to the APT strategy in the case
-where arms are normally distributed with equal variance that is known
-upfront. In that case we have as index (compare example 3 above): \[
-B_i^{SLR}(t) = T_i(t)\frac{(\hat{\mu}_i(t) - \tau)^2}{2\sigma^2}.
-\] In order to decide at time \(t\) which arm to draw next, we
-necessarily compare the indexes of arm \(i\) and arm \(j\). Assume
-w.l.o.g. that \(B_i^{SLR}(t) < B_j^{SLR}(t)\). Then:
-
-\begin{align*}
-B_i^{SLR}(t) < B_j^{SLR}(t) & \Leftrightarrow 
-T_i(t)\frac{(\hat{\mu}_i(t) - \tau)^2}{2\sigma^2} < T_j(t)\frac{(\hat{\mu}_j(t) - \tau)^2}{2\sigma^2} \Alignyesnumber\label{eqn:SLRWithKnownVar}\\
-& \Leftrightarrow 
-\sqrt{T_i(t)}\sqrt{(\hat{\mu}_i(t) - \tau)^2} < \sqrt{T_j(t)}\sqrt{(\hat{\mu}_j(t) - \tau)^2} \\
-& \Leftrightarrow 
-B_i^{APT}(t) < B_j^{APT}(t)
-\end{align*}
-
-Given that in all other cases the SLR is able to take more information
-about the distributions into account through the Kullback-Leibler
-divergence (in the case of the exponential family of distributions), the
-algorithm is expected to improve upon the APT strategy. Just consider a
-situation of known, but different variances for Normal distributions.
-Then we had in \autoref{eqn:SLRWithKnownVar} \(\sigma_i^2\) and
-\(\sigma_j^2\) instead of \(\sigma^2\), which should lead to more pulls
-of the arm with larger variance. This is not taken into account by APT.
-
-As mentioned before, this improvement comes only at the cost of knowing
-the correct distribution upfront. In particular, as for the APT
-algorithm, there are no parameters which need to be tuned upfront as is
-usually the case for upper-confidence bound based algorithms (see for
-example UCB-E in Audibert et al., 2010).
-
-Additionally, the index used in the SLR algorithm offers the same
-interpretation considered in \autoref{sec:EVTAlgorithm}. Write the index
-again as \[
-B_i(t) = S_i(t) D_i(t),
-\] where \(S_i(t)\) is a confidence term of the estimate of the arm
-\(i\) at time \(t\), and \(D_i(t)\) is a measure of distance between the
-distribution of arm \(i\) and the threshold \(\tau\). The index of the
-Simple Likelihood Ratio strategy for univariate exponential family
-distributions can then be written with \[
-S_i(t) = T_i(t) \quad \text{and} \quad
-D_i(t) = \KL(\hat{\mu}_i(t)||\tau),
-\] where we employ the number of pulls so far for a given arm as the
-confidence measure, while the Kullback-Leibler divergence fulfills its
-role as distance measure between distributions (see also Figure 2). The
-larger the Kullback-Leibler divergence, the less inclined we are to draw
-the arm; the same holds, if we have pulled an arm many times. Since the
-KL-divergence reduces to the squared distance between means for Normal
-distributions of known variance, the SLR and APT algorithms are
-identical in this case.
-
-As we see in the experiments that follow, the SLR strategy is able to
-improve significantly upon the APT strategy in many cases.
-
 \section{\texorpdfstring{Experiments
@@
 
-\subsection{\texorpdfstring{Synthetic Data
-\label{sec:SyntheticData}}{Synthetic Data }}\label{synthetic-data}
-
-Each of the following five simulations is repeated for 5000 iterations.
-Depending on the simulation, the observations are generated randomly by
-a given exponential family of distributions. As we are primarily
-concerned with improving upon APT with respect to non-sub-Gaussian
-distributions, the first three simulations focus on Bernoulli
-distributions, especially those with small means. We then go on to show
-with experiments on data from the Exponential distribution and Poisson
-distribution that the SLR strategy can be adapted to other distributions
-as well.
-
-\subsubsection{\texorpdfstring{Simulation 1: Bernoulli Arms and
-\(\tau = 0.5\)}{Simulation 1: Bernoulli Arms and \textbackslash{}tau = 0.5}}\label{simulation-1-bernoulli-arms-and-tau-0.5}
-
-The first experiment is equal to experiment 3 in Locatelli et al. (2016)
-to achieve a baseline comparison. We compare ten Bernoulli arms that
-move away from the threshold at \(\tau = 0.5\) geometrically with
-\(\mu_{1:4} = 0.4-0.2^{1:4}\), \(\mu_5 = 0.45\), \(\mu_6 = 0.55\), and
-\(\mu_{7:10} = 0.6 + 0.2^{5-1:4}\). We run the standard APT algorithm as
-well as the SLR algorithm with \(\epsilon = 0.1\). We compare them to
-the AugUCB algorithm with the parameter choice of \(\rho = 1/3\) as used
-by its authors in Mukherjee et al. (2017). We run the parameter-free
-EVT\(_{pf}\) algorithm without feedback delay, thus making it directly
-comparable to the other algorithms. The Bayes-UCB algorithm is run with
-\(c=1\) and takes as prior a Beta distribution with parameters
-\(\alpha_0 = \tau\) and \(\beta_0 = 1 - \tau\), thus leading to a mean
-of the prior distribution at \(\frac{\alpha_0}{\alpha_0+\beta_0}=\tau\)
-while keeping the prior as weak as possible. Lastly, we run the uniform
-sampling strategy as a benchmark.
-
-\begin{longtable}[]{@{}rrrrrrrrrr@{}}
-\caption{Mean of arms in simulation 1.}\tabularnewline
-\toprule
-V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
-\midrule
-\endhead
-0.2 & 0.36 & 0.392 & 0.398 & 0.45 & 0.55 & 0.602 & 0.608 & 0.64 &
-0.8\tabularnewline
-\bottomrule
-\end{longtable}
-
-This first experiment is a problem in which all algorithms should be
-able to perform well. The problem is not very difficult with
-\(H_1^{APT} \approx\) 232, and due to \(\tau = 0.5\), the Bernoulli
-distribution can be well approximated by a Gaussian. This is the perfect
-environment for the APT algorithm.
-
-As the next figure shows, essentially all methods converge rapidly to an
-error rate of very close to zero, where the error rate is the share of
-the 5000 simulations on which the classification of the algorithm is
-wrong. Only the uniform strategy that clearly lacks behind. We also
-observe that the variance based algorithms (AugUCB and EVT) lag behind
-at first. AugUCB is able to adjust its sampling scheme only after 1000
-iterations but then rapdily improves to the level of APT. EVT takes
-about 250 samples more to start a quick descend to the performance of
-the other algorithms. All of this, however, happens after the algorithms
-are below an error rate of 0.01. While the SLR algorithm improves upon
-APT, the improvement is a slight one, and not very large in terms of
-budget difference. This underlines that the scenario at hand is ideal
-for the APT algorithm.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation1_results-1}
-
-}
-
-\caption{Performance comparison of algorithms for simulation 1.}\label{fig:simulation1_results}
-\end{figure}
-
-\subsubsection{\texorpdfstring{Simulation 2: Bernoulli Arms and
-\(\tau = 0.05\)
-\label{sec:Simulation2}}{Simulation 2: Bernoulli Arms and \textbackslash{}tau = 0.05 }}\label{simulation-2-bernoulli-arms-and-tau-0.05}
-
-\begin{longtable}[]{@{}rrrrrrrrrr@{}}
-\caption{Mean of arms in simulation 2 classified against threshold of
-0.05.}\tabularnewline
-\toprule
-V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
-\midrule
-\endhead
-0.001 & 0.005 & 0.01 & 0.015 & 0.04 & 0.06 & 0.085 & 0.09 & 0.095 &
-0.099\tabularnewline
-\bottomrule
-\end{longtable}
-
-In the second experiment, we compare the same algorithms as in the first
-experiment. Again, we classify 10 arms, but this time against a
-threshold of \(\tau = 0.05\) and without an epsilon interval,
-\(\epsilon = 0\) (which generally rewards algorithms for pulling arms
-close to the threshold). We choose the means of the arms to be much
-smaller too, and arrange them symmetrically around the threshold. While
-the distributions are bounded and thus still sub-Gaussian, the Normal
-approximation should be poor in comparison to the previous case. We
-expect an improvement for SLR compared to APT as SLR takes the Bernoulli
-characteristics into account. In particular, even though the arms are
-symmetrically distributed around the threshold in terms of absolute
-distance, they are not symmetrically around the threshold in terms of
-their Kullback-Leibler divergence (compare Figure 2). Thus we expect the
-SLR algorithm to not pull them symmetrically. Furthermore, we expect an
-improvement for the variance-based algorithms, as the variances are now
-smaller than in the first simulation, which should benefit the EVT
-algorithm given its theoretical analysis in Zhong et al. (2017).
-
-The figure below shows the performance of all algorithms. The results
-underline that this problem is much harder in general
-(\(H_2^{APT} \approx 24703\)). The performance of the variance based
-algorithms is surprisingly poor; EVT performs even worse than uniform
-sampling until close to the horizon, while Augmented UCB takes a long
-time to adjust away from uniform sampling. Both algorithms perform worse
-than APT after 7000 samples.
-
-The Simple Likelihood Ratio strategy improves considerably upon the
-alternative strategies. SLR reaches the average empirical error of 0.1
-within the budget, and it improves at an exponential rate within the
-entire budget; in contrast to APT which appears to improve linearly in
-the observations. At the end of the budget, the difference in the
-empirical error is nearly 10\% between the two strategies.
-
-In order to assess how the SLR strategy improves upon the APT algorithm,
-it is useful to look at how the algorithms allocate their sampling
-budget across arms. Given that we run the simulation 5000 times, we can
-compare across simulations how often an algorithm pulls each arm at a
-given round. During the 5000 iterations, the algorithm should pull at
-any given iteration the arm most often that it thinks is the most
-difficult to classify. In Figure 6, we plot the resulting curves where
-the y-axis shows a 10-round moving average of the pulls to remove some
-variation.
-
-The graph shows that both APT and SLR correctly single out the two arms
-closest to the threshold, and allocate most of the budget to them.
-However, while SLR keeps the two arms constant at two different levels
-(about 1900 for arm 5 and about 2500 for arm 6), APT at first pulls arm
-5 more often than arm 6. Then, for \emph{both} arms, the budget appears
-to converge to about 2000. Given that the two arms are symmetric around
-the threshold, it makes sense that APT would allocate the same
-exploration effort to them. And given that the variation of arm 5 away
-from the threshold is limited from below by zero, it is much easier for
-arm 6 to have an empirical mean larger than its true mean, and thus to
-have a larger index than arm 5 in the beginning. Consequently, APT would
-prefer to sample arm 5. This, however, is wrong in terms of
-Kullback-Leibler divergence. Measured by the divergence, arm 6 is closer
-to the threshold than arm 5, thus harder to classify, and consequently
-preferred by the SLR algorithm. Furthermore, the SLR algorithm appears
-to quickly find the correct share that it has to allocate to the two
-arms. This is in contrast to APT which continues to adjust the shares
-across the entire budget.
-
-Additionally, we can observe that the SLR strategy starts to drop arms
-much quicker than APT, and it drops arm 1 to 3 first, which again
-underlines the effect of the asymmetric Kullback-Leibler divergence. If
-we consider arm 3 and arm 8, we have \(d_3(0.01||0.05) \approx 0.025\)
-while \(d_8(0.09||0.05) = 0.014\). The divergence is much smaller for
-arm 8. The asymmetry is even more dramatic for arm 1 and arm 10 with
-\(d_1(0.001||0.05) \approx 0.046\) and
-\(d_{10}(0.099||0.05) \approx 0.020\): In terms of the divergence, the
-distance between arm 1 and the threshold is twice as far as between arm
-10 and the threshold. APT considers them to be equally distant from the
-threshold.
-
-One interesting observation, that we will observe in all simulations
-with Bernoulli arms, is the superior performance of the Bayes-UCB
-algorithm adapted from Kaufmann et al. (2012) which was originally
-designed for cumulative regret problems. Nonetheless, the algorithm
-proves again and again to be the best performing. Compare with
-\autoref{sec:AppendixBUCB} for more analysis on the behavior of the
-Bayes-UCB algorithm in simulation 2. In particular, consider Figures 17
-and 18 which show for individual arms the distribution of pulls for that
-arm across simulations. The distributions highlight that both the APT
-and SLR fail in many iterations of the simulations to pull arms
-frequently enough to estimate their correct mean. The APT algorithm
-pulls the most difficult arm (Arm 6) in more than 5\% of the simulations
-only once (during initialization). Consider arm 6 returns
-\(X_{6,1} = 1\) as its first observation. Then
-\(B_6(t+1) = 1 \cdot |1-0.05| = 0.95\). It will then not be pulled for a
-long time because its index is very large. Indeed, consider some arm
-that has been pulled 4000 times with \(\mu_i(4000) = 0.03\). Then
-\(B_i(t+1) = \sqrt{2000} \cdot |0.05-0.03| \approx 0.89\). Even though
-we have basically no evidence for the performance of arm \(6\), we would
-continue to pull arm \(i\). Similar holds for the SLR algorithm. For
-both, the distribution of pulls for arm 6 is very flat across the
-interval of \([1,6000]\) pulls. In contrast, the distribution of pulls
-appears normally distributed for the Bayes-UCB algorithm with the mode
-between 2100 and 2300 pulls. The numerical problem that arises for the
-APT and SLR algorithms might be weakened for the Bayes-UCB algorithm by
-the combination of a (weak) prior that shrinks the mean estimates, and
-the way in which quantiles are based on the posterior. Also, the fact
-alone that it is based on confidence bounds of the empirical mean,
-instead of the empirical mean itself. We show in the appendix that the
-problem does not only occur for arm 6.
-
-Empirically, part of this problem can be alleviated by including the
-D-Tracking rule proposed by Garivier and Kaufmann (2016) and discussed
-in \autoref{sec:OptimalBestArmIdentification} into the SLR algorithm, as
-it ensures that no arm is ``left behind'' in terms of samples. Figure 5
-shows a significant improvement for the SLR-D algorithm in comparison to
-the SLR algorithm without D-Tracking. However, the algorithm still does
-not reach the performance of Bayes-UCB.
-
-Lastly, we remark on the shape of the error curve of the uniform
-strategy. Even though the uniform strategy samples arms at random from
-the set of arms with the least observations at any round, we observe a
-sawtooth pattern for simulation 2 and 3. This is an artifact of the
-comparison against the threshold of \(0.05\) and \(0.01\) respectively,
-combined with the discrete \(0\) and \(1\) observations. Take for
-example an arm with a true mean of \(\mu = 0.06\) compared against
-\(\tau = 0.05\). Let's say the arm observes the first 1 after 15
-samples, \(X_{15} = 1\), such that
-\(\hat{\mu}(15) = 1/15 \approx 0.067\). At this point, it is correctly
-classified as above the arm. Even if the next samples are zeroes, it
-will continue to be correctly classified until observation 20. At that
-point, \(\hat{\mu}(20)\) = 1/20 = 0.05. By observing one more
-observation, the arm will be classified as below the threshold, since
-then \(\hat{\mu}(21) = 1/21 < 0.05 = \tau\). The classification is
-suddenly wrong for no particular reason, and a sudden spike in the error
-curve occurs. In the graph of simulation 3 it is obvious that the spike
-occurs with a period length of about 100 samples, which corresponds to
-\(\tau = 0.01=1/100\). This explains why we do not observe such a
-pattern in the first simulation with \(\tau = 0.5\), or for the
-continuous Exponential distribution in simulation 4.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation2_results-1}
-
-}
-
-\caption{Performance comparison of algorithms for simulations 2 and 3. Note the different x-axes.}\label{fig:simulation2_results}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-1-1}
-
-}
-
-\caption{Budget allocation across arms for APT and SLR algorithms in simulation 2.}\label{fig:unnamed-chunk-1}
-\end{figure}
-
-\subsubsection{\texorpdfstring{Simulation 3: Bernoulli Arms and
-\(\tau = 0.01\)}{Simulation 3: Bernoulli Arms and \textbackslash{}tau = 0.01}}\label{simulation-3-bernoulli-arms-and-tau-0.01}
-
-In the third experiment, we lower the threshold further to
-\(\tau = 0.01\) and arrange now \(K=11\) arms on a \(\log_{10}\) scale
-around it. Again, we set \(\epsilon = 0\). We compare the same
-algorithms as previously with the settings adapted to \(\tau\) and
-\(\epsilon\) accordingly. Notice that the experiment horizon is now
-\(T=10000\) rounds instead of \(T=7000\) rounds in the previous
-experiment.
-
-\begin{longtable}[]{@{}rrrrrrrrrrr@{}}
-\caption{Mean of arms in simulation 3.}\tabularnewline
-\toprule
-V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10 & V11\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10 & V11\tabularnewline
-\midrule
-\endhead
-1e-04 & 3e-04 & 6e-04 & 0.001 & 0.0018 & 0.0032 & 0.0056 & 0.0141 &
-0.0178 & 0.0316 & 0.1\tabularnewline
-\bottomrule
-\end{longtable}
-
-Looking at the performance after 7000 rounds, we see that the problem
-appears to be slightly more difficult compared to the previous one
-(\(H_3^{APT} \approx 210359\)). We see that up until this point the
-variance-based strategies cannot improve upon APT. Also, SLR has not yet
-crossed the 10\% empirical error. We observe that in the following
-rounds EVT decreases at an exponential rate and thus crosses the error
-of APT and continues to improve. At the end of the budget, the
-improvement of SLR compared to the other algorithms is again large, and
-likely to increase. However, Bayes-UCB is again the best performing
-algorithm and is improving at a faster rate than SLR. As in the previous
-experiment, Bayes-UCB and SLR show significant improvements on this
-Bernoulli problem with very small means and threshold compared to APT in
-particular. Furthermore, the observation that the SLR algorithm with
-D-Tracking rule performs better than without is replicated.
-
-\subsubsection{Simulations 4 and 5: Exponential and Poisson
-Distributions}\label{simulations-4-and-5-exponential-and-poisson-distributions}
-
-In \autoref{sec:LRforUnivariateExponentialFamily}, we show that the
-likelihood ratio has a very useful form for the one-parameter
-exponential family of distributions, which allows us to use the SLR
-algorithm not only on Bernoulli arms, but also on Exponential or Poisson
-distributions, for example. In simulation 4, we consider Exponential
-distributions, in simulation 5, we test the algorithms on Poisson
-distributions.
-
-We run the same algorithms as before except for Bayes-UCB (even though
-it should certainly be possible to adapt it to these case based on a
-Gamma prior). In the case of the Exponential arms, we classify against
-\(\tau = 1\) and have sampled the arms' mean parameters from an
-Exponential distribution with rate \(\theta = 1\). The Poisson arms are
-classified against a threshold of \(\tau = 0.4\), with the mean
-parameters being sampled from an Exponential distribution with mean
-\(\mu = 0.7\). In both cases, we classify 20 arms.
-
-For the Exponential arms, APT crosses the 10\% error mark first,
-followed by the AugUCB algorithm. All algorithms perform better than
-uniform sampling. After more than half of the budget, the SLR algorithm
-jumps in performance and performs better than APT and AugUCB. Indeed,
-the AugUCB basically stops improving after half of the budget. This is a
-consequence of it eliminating arms it believes to know very well. This
-happens at an error rate of less than \(0.01\). On average, the AugUCB
-samples only for 2564 rounds of the budget of 4000 rounds across the
-5000 simulations.
-
-The early elimination (when compared to the Bernoulli experiments) might
-be caused by the fact that the AugUCB assumes the variance of the arms
-to be in \([0,1]\), which does not hold for half of the arms in the
-experiment. Similar goes for the EVT algorithm which is only able to
-catch up at the very end of the budget.
-
-In the case of Poisson arms, the performance of the arms is more clear
-cut. As expected, SLR improves upon APT. APT outperforms the EVT
-algorithm, which occurs even though the variance of all arms considered
-in this experiment is in \([0,1]\). After about 1000 observations, APT
-and EVT appear to improve at about the same rate, but APT has a much
-better initial exploration phase. Given the previous simulations, it is
-surprising to see the Augmented-UCB algorithm to come ahead after
-\(T=10000\) observations. After about half the budget, the same pattern
-as before occurs where there is a drastic change in sampling behavior.
-This suffices to outpace both APT and SLR.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation5_results-1}
-
-}
-
-\caption{Performance comparison of algorithms for simulations 4 and 5. Note the different x-axes.}\label{fig:simulation5_results}
-\end{figure}
-
 \subsection{\texorpdfstring{Experiments on Web Analytics Data
@@
 
-\begin{longtable}[]{@{}llrrrrr@{}}
-\caption{Example of the binary time series data for five
-products.}\tabularnewline
-\toprule
-& SessionDateTime & V104 & V110 & V150 & V112 & V154\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-& SessionDateTime & V104 & V110 & V150 & V112 & V154\tabularnewline
-\midrule
-\endhead
-1000 & 2016-11-01 16:39:00 & 0 & 0 & 0 & 0 & 0\tabularnewline
-1001 & 2016-11-01 16:40:00 & 0 & 0 & 0 & 0 & 1\tabularnewline
-1002 & 2016-11-01 16:41:00 & 0 & 0 & 0 & 0 & 1\tabularnewline
-1003 & 2016-11-01 16:42:00 & 0 & 0 & 0 & 0 & 0\tabularnewline
-1004 & 2016-11-01 16:43:00 & 0 & 0 & 1 & 0 & 1\tabularnewline
-1005 & 2016-11-01 16:44:00 & 0 & 0 & 0 & 0 & 0\tabularnewline
-\bottomrule
-\end{longtable}
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{Draft_for_Markus_files/figure-latex/unnamed-chunk-1-1}
+
+}
+
+\caption{We use time series crossvalidation, to create many samples from one data set.}\label{fig:unnamed-chunk-1}
+\end{figure}
 
@@
 the number of visitors that reach a given PDP is likely to vary by time
-of day and by day, and in general over time, we expect the mean of the
-time series to not be stable over time. For example, less visitors visit
+of day, by day, and in general over time, we expect the mean of the time
+series to not be stable over time. For example, less visitors visit
 during night than during the evening. This leads to a decrease in the
@@
 for each arm, so as to have a sample for one full week.
+
+\begin{longtable}[]{@{}llrrrrr@{}}
+\caption{Example of the binary time series data for five
+products.}\tabularnewline
+\toprule
+& SessionDateTime & V104 & V110 & V150 & V112 & V154\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+& SessionDateTime & V104 & V110 & V150 & V112 & V154\tabularnewline
+\midrule
+\endhead
+1000 & 2016-11-01 16:39:00 & 0 & 0 & 0 & 0 & 0\tabularnewline
+1001 & 2016-11-01 16:40:00 & 0 & 0 & 0 & 0 & 1\tabularnewline
+1002 & 2016-11-01 16:41:00 & 0 & 0 & 0 & 0 & 1\tabularnewline
+1003 & 2016-11-01 16:42:00 & 0 & 0 & 0 & 0 & 0\tabularnewline
+1004 & 2016-11-01 16:43:00 & 0 & 0 & 1 & 0 & 1\tabularnewline
+1005 & 2016-11-01 16:44:00 & 0 & 0 & 0 & 0 & 0\tabularnewline
+\bottomrule
+\end{longtable}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-4-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_for_Markus_files/figure-latex/unnamed-chunk-4-1}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-5-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_for_Markus_files/figure-latex/unnamed-chunk-5-1}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-6-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_for_Markus_files/figure-latex/unnamed-chunk-6-1}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-10-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_for_Markus_files/figure-latex/unnamed-chunk-10-1}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-11-1}
+{\centering \includegraphics[width=0.8\linewidth]{Draft_for_Markus_files/figure-latex/unnamed-chunk-11-1}
 
@@
 
-\section{Conclusion}\label{conclusion-1}
+\section{Conclusion}\label{conclusion}
 
@@
 the first place. Sonoma Internet GmbH (Amorelie) supported this work by
-giving the authors access to the discussed data set.
-
-\newpage
-
-\section{References}\label{references}
-
-\newpage
-
-\section{Appendix}\label{appendix}
-
-\subsection{\texorpdfstring{Proof of Thresholding Bandit Lower Bound
-\label{sec:AppendixAPTLB}}{Proof of Thresholding Bandit Lower Bound }}\label{proof-of-thresholding-bandit-lower-bound}
-
-We now give a proof for the lower bound for the thresholding bandit
-problem stated in \autoref{theorem:Locatelli2016Theorem1}.
-
-\emph{Proof of Theorem \ref{theorem:Locatelli2016Theorem1}}: Locatelli
-et al. (2016) derive a lower bound for the thresholding bandit problem.
-We restate the proof here. The idea is as follows. The problem
-formulation considered in the paper describes bandit problems for
-\(R\)-sub-Gaussian distributions. To show a lower bound, we show that
-every algorithm is expected to make a certain error even if we consider
-a very restricted scenario. Even then, the best algorithm will have a
-maximum error probability with which it cannot distinguish between the
-actual setting and slightly changed settings (under which the answer for
-the true setting leads to a misclassification).
-
-Consider the thresholding bandit setting as in \autoref{sec:Setup}. More
-specifically, consider a problem in which all arms follow Normal
-distributions \(\nu_i\) with mean \(\mu_i\) and variance
-\(\sigma^2 = 1\). ``in which w''e set \(\tau = 0\) and \(\epsilon = 0\)
-w.l.o.g. Consequently, for each arm \(i\) the distance from the
-threshold is given by \(\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i\).
-Thus, we have for every arm the distribution
-\(\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)\). Furthermore,
-define for each arm \(i \in \{1, \dots, K\}\) the alternative
-distribution \(\nu_i' = \mathcal{N}(-\Delta_i,1)\). It is easy to see
-that this is equivalent to a ``flip around the threshold''. Arms that
-originally have a mean larger than the threshold have a mean smaller
-than the threshold after the flip.
-
-The intuition now is that every arm \(i \in \{1,\dots,K\}\) generates a
-sample for every time point \(t\in \{1, \dots, T\}\) from its
-distribution \(\nu_i\) before the algorithm starts to choose arms. Thus,
-we have a \(T \times K\) table of realized observations from the product
-distribution given by
-\(\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K\).
-This is a product distribution where the \(K\) different means are all
-above the threshold. We would hope that an algorithm classifies the
-means accordingly. However, we will show in what follows that any
-algorithm makes a certain error by not being able to distinguish
-\(\mathcal{B}^0\) from at least one of \(K\) alternative product
-distributions \(\mathcal{B}^i, i \in \{1, \dots, K\}\), of which each
-differs only slightly in one arm from the original distribution, and has
-the same overall complexity (as defined by
-\(H = \sum_{i=1}^K (\Delta_i)^{-2}\)). We require \(K\) different
-distributions so that an algorithm sampling arm \(i\) very often for
-some reason will not have a smaller lower bound by chance.
-
-For each of the \(K\) arms, we introduce an alternative model of the
-following kind. Before the start of the algorithm, we introduce a slight
-variation in the setup. The idea is similar to how one can switch arms
-in the pure exploration setup for multi-armed bandits (compare Audibert
-et al., 2010; Garivier \& Kaufmann, 2016) to ``confuse'' any algorithm
-without introducing additional complexity to the specified problem.
-However, since we do not compare arms directly with each other in the
-thresholding bandit problem (switching arms would still keep all means
-above the threshold), we instead need to flip an arm \(i\) with respect
-to the threshold in order to get the alternative model
-\(\mathcal{B}_i\). Since the threshold is \(\tau = 0\), we have for the
-flipped arm the new distribution \(\nu_i'\) as defined above. Indeed,
-define the new product distribution
-\(B^i = \nu_1^i \otimes \dots \otimes \nu_K^i\) where for
-\(k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}\).
-This arm flip corresponds to multiplying all \(X_{i,t}\) of arm \(i\) by
-\(-1\).
-
-As in Locatelli et al. (2016), let for \(i \leq K\),
-\(\mathbb{P}_{\mathcal{B}^i}\) be the probability distribution
-describing all samples that a bandit strategy can potentially collect up
-to horizon \(T\), i.e.~according to the samples
-\((X_{k,s})_{k\leq K, s \leq T} \sim (\mathcal{B}^i)^{\otimes T}\).
-\((T_k)_{k\leq K}\) denotes the number of samples collected on arm \(k\)
-until time \(T\).
-
-At this point, we have defined a finite set of problems of Gaussian
-distributions with fixed variance 1 for a given set of set of gaps
-between the means of the distributions and the threshold,
-\((\Delta_k)_k\). We now proof a lower bound on the worst case regret of
-any algorithm; that is, the maximum error probability that even the best
-algorithm makes on this problem.
-
-\subsubsection{Statistical Decision}\label{statistical-decision}
-
-The expected loss in our thresholding bandit setting,
-\(\mathbb{E}[\mathcal{L}(T)]\), corresponds directly to the probability
-of making a wrong classification of any of the \(K\) means. In general,
-given a binary decision function \(g\), define events
-\(\Omega = \{g = 0\}\) and \(\Omega^C = \{g = 1\}\). Assume that the
-decision \(g\) distinguishes between two states of the world, \(H_0\)
-and \(H_1\). Then an overall error probability can be seperated into
-\(P_{H_0}(g=1) + P_{H_1}(g = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)\).
-
-In our case, \(H_0\) may correspond to the state in which we have
-\(\mathcal{B}^0\), and \(H_1\) corresponds to the case where any arm has
-been flipped, \(\mathcal{B}^i\). Furthermore, we consider the events in
-which the algorithm classifies arm \(i\) as being above the threshold:
-\(\mathcal{A}_i = \{i \in \hat{S}_\tau\}\). The event on which all arms
-are being classified as above the threshold is consequently given by
-\(\mathcal{A} = \bigcap_{i=1}^K \mathcal{A}_i\). We could thus separate
-the error probability \(\mathbb{E}[\mathcal{L}(T)]\) into
-\(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\) and
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C)\). However, Theorem 1 does
-not bound the overall regret, but the maximum error probability on the
-\(K+1\) different models. We can write this now as
-
-\begin{align}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big) \\
-& = \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
-\end{align}
-
-\subsubsection{Empirical Kullback-Leibler
-Divergence}\label{empirical-kullback-leibler-divergence}
-
-In order to give a bound on the previous equation, we start by
-considering \(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\). This
-probability can be written as the expected change in the likelihood of
-observed data when moving from distribution \(P_{\mathcal{B}_0}\) to
-\(P_{\mathcal{B}_i}\), times the probability under the original state.
-In other words, the probability of event \(\mathcal{A}_i\) under state
-\(\mathcal{B}^i\) is given as the probability of \(\mathcal{A}_i\) under
-the (original) state \(\mathcal{B}^0\) multiplied by a factor. This
-factor describes whether the new distribution increases or decreases the
-probability of the event, and is given by the change in the data
-likelihoods due to moving from \(\mathcal{B}^0\) to \(\mathcal{B}^i\),
-expressed as the expected likelihood ratio under \(\mathcal{B}^0\). By
-definition, the latter is equal to the empirical Kullback-Leibler
-divergence of the two distributions.
-
-We will define the change of distribution in terms of the empirical
-log-likelihood for our case. Then, we will show how to replace the
-log-likelihood by the empirical Kullback-Leibler divergence. Let us
-first introduce the empirical Kullback-Leibler divergence.
-
-Let every \(\nu_i, \nu_i'\) be dominated by the Lebesgue measure
-\(\lambda\). Then their density functions are given by
-\(f_i = \frac{\der \nu_i}{\der \lambda}\) and
-\(f_i' = \frac{\der \nu_i'}{\der \lambda}\) respectively. For
-\(T \geq t \geq 0\), define the empirical Kullback-Leibler divergence
-for an i.i.d. sample \(X_{k,1}, \dots,X_{k,t}\) as
-
-\begin{align*}
-\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log(\frac{\der \nu_k'}{\der \nu_k}(X_{k,s})) \\
-& = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
-& = \frac{1}{t} \log \big( \prod_{s=1}^{t} \frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
-& \stackrel{\text{iid}}{=} \frac{1}{t} \log \big( \frac{f_k'(X_{k,1}, \dots,X_{k,t})}{f_k(X_{k,1}, \dots,X_{k,t})} \big) \\
-& = \frac{1}{t} \log \big( \text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k) \big),
-\end{align*}
-
-where \(\text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k)\) is the
-likelihood ratio for the sample.
-
-Since we consider Gaussian distributions with variance \(\sigma^2 = 1\),
-we have density functions
-\(f_i(x) \propto \exp \big(-\frac{1}{2} (x-\Delta_i)^2\big)\) and
-\(f_i'(x) \propto \exp \big(-\frac{1}{2} (x+\Delta_i)^2\big)\). Plugging
-this into the above definition of the empirical Kullback-Leibler
-divergence, we easily see
-
-\begin{align*}
-\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log \Big(\frac{\exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2\big)}{\exp \big(-\frac{1}{2} (X_{k,s}-\Delta_k)^2\big)} \Big) \\
-& = \frac{1}{t} \sum_{s=1}^{t} \log \Big( \exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2 + \frac{1}{2} (X_{k,s}-\Delta_k)^2 \big) \Big) \\
-& = - \frac{1}{t} \sum_{s=1}^{t} 2 X_{k,s} \Delta_k
-\end{align*}
-
-\subsubsection{Change of Distribution}\label{change-of-distribution}
-
-We are now ready to state the change of distribution. As alluded to
-above, we consider how the probability changes for the event
-\(\mathcal{A}_i\) when we move from \(\mathcal{B}^0\) to
-\(\mathcal{B}^i\). When flipping arm \(i\), we only change the samples
-of this arm, that is, the first \(T_i\) observations that the algorithm
-draws from arm \(i\). The change of distribution is then defined as:
-
-\begin{align*}
-\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \text{LR}((X_{i,1}, \dots,X_{i,T_i}), \nu_i', \nu_i) ] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ]
-\end{align*}
-
-Obviously, \(\hat{\KL}_{i,T_i}\) depends on the realized samples
-\(X_{i,1}, \dots,X_{i,T_i}\). Consequently, we need to find a bound on
-\(\hat{\KL}_{i,T_i}\) itself to incorporate the uncertainty involved in
-this metric.
-
-\subsubsection{Concentration of the Empirical Kullback-Leibler
-Divergence}\label{concentration-of-the-empirical-kullback-leibler-divergence}
-
-For our problem, the Kullback-Leibler divergence of \(\nu_k'\) from
-\(\nu_k\) is given by \(\KL_k := \KL(\nu_k', \nu_k) = 2\Delta_k^2\), and
-consequently
-
-\begin{equation*}
-|\hat{\KL}_{k,t} - \KL_{k,t}| = |-\frac{2}{t} \Delta_k \sum_{s=1}^{t}(X_{k,s} - \Delta_k)|
-\end{equation*}
-
-itself is a normally distributed random variable with mean zero and a
-variance decreasing in \(t\). Thus, one can show as in Locatelli et al.
-(2016) that \(\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4\) for the event
-
-\begin{equation}
-\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}}\}. \label{LocatelliTheorem1EventXi}
-\end{equation}
-
-Thus, in order to bound the empirical Kullback-Leibler divergence in our
-change of measure, we can consider the intersection of \(\mathcal{A}_i\)
-and \(\xi\) as follows and plug in the bound on event \(\xi\):
-
-\begin{align*}
-\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
-\end{align*}
-
-Two things are left to do: With \(T_i\), we still have one random
-variable left which we cannot leave in our bound. Second, we are
-actually not interested in \(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)
-but in
-\(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\).
-
-\subsubsection{\texorpdfstring{Bounding \(T_i\) for
-\(\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)}{Bounding T\_i for \textbackslash{}max\_\{i \textbackslash{}in \textbackslash{}\{1,\textbackslash{}dots,K\textbackslash{}\}\}\textbackslash{}mathbb\{P\}\_\{\textbackslash{}mathcal\{B\}\^{}i\}(\textbackslash{}mathcal\{A\}\_i)}}\label{bounding-t_i-for-max_i-in-1dotskmathbbp_mathcalbimathcala_i}
-
-We are actually interested in bounding
-\(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\).
-In general it holds that
-\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K}\sum_{i=1}^K X_i\).
-Thus we can write:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
-& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
-& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
-\end{align*}
-
-where the second line is again the intersection of \(\mathcal{A}_i\) and
-\(\xi\) as before, such that we can apply the change of distribution in
-the third line.
-
-What is left to show is a bound on \(T_i\). Given that we want to show
-that even the best algorithm makes an error on at least one of the
-problems (one of the arms), it makes sense to show that \(T_i\) is upper
-bounded. This implies that no arm can be infinitely sampled; we cannot
-reach full confidence in any arm, and a residual error probability
-should remain.
-
-First, let \(a = \Delta_i \sqrt{T_i}\) and
-\(b = 4\sqrt{\log((4\log(T)+1)K)}\). Then use \(ab \leq a^2 + b^2\) to
-write \(ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)\). And so:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) ]
-\end{align*}
-
-Furthermore, we know that the sum of the individual arm pulls has to be
-equal to the overall number of pulls (equal to the budget in the fixed
-budget sense), \(\sum_i T_i = T\), and furthermore we know that
-\(T_i>0\). The latter holds since any reasonable algorithm has to check
-each arm at least once in our setup. Thus it is easy to show that
-\(\exists i: T_i \leq \frac{T}{H \Delta_i^2} = \frac{T}{(\sum_{i=1}^{K} \Delta_i^{-2}) \Delta_i^2}\).
-To see this, assume the opposite:
-\(\forall i: T_i > T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2}\). This
-implies however
-\(\sum_{i=1}^K T_i > \sum_{i=1}^K T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2} = T \cdot 1 = T\)
-which is a contradiction.
-
-So we can write \((\Delta_i \sqrt{T_i})^2 \leq \frac{T}{H}\). We use
-\(\mathcal{A} = \cap_{i=1}^K \mathcal{A}_i\) to write:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big]
-\end{align*}
-
-We write
-\(\frac{1}{K} \sum_{i=1}^K \exp(-3T_i \Delta_i^2) \geq \frac{1}{K} \sum_{i=1}^K \exp(-3 T/H) = \exp(-3 T/H)\).
-Thus:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \Big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i) \exp \big(-16 \log(4(\log(T)+1)K)\big) \Big] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \Big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp \big(- 3 \frac{T}{H}\big) \exp \big(-16 \log(4(\log(T)+1)K)\big) \Big] \\
-& = \mathbb{E}_{\mathcal{B}^0} \Big[\mathbbm{1}_{\mathcal{A} \cap \xi} \exp \big(- 3 \frac{T}{H}\big) \exp \big(-16 \log(4(\log(T)+1)K)\big) \Big] \\
-& = \mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp \Big(- 3 \frac{T}{H} -16 \log \big(4(\log(T)+1)K\big)\Big)
-\end{align*}
-
-\subsubsection{Bringing everything
-together}\label{bringing-everything-together}
-
-Consider again the risk which we need to bound from equation
-\eqref{LocatelliTheorem1ExpRegret}. We bound the maximum expected loss
-over all \(\mathcal{B}_i\). By using again the fact that in general
-\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K} \sum_{i = 1}^K X_i\),
-we plug into our previous calculations:
-
-\begin{align}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp \Big(- 3 \frac{T}{H} -16 \log \big(4(\log(T)+1)K\big)\Big) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \label{LocatelliTheorem1DefinitionOfRisk}
-\end{align}
-
-From \eqref{LocatelliTheorem1EventXi} we know that for any
-\(i \in \{0, \dots, K\}\), \(\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4\).
-Following the argument in Locatelli et al. (2016), we now consider two
-cases: \(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2\) and
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2\). In the former
-case, we can plug in the two probabilities into
-\eqref{LocatelliTheorem1DefinitionOfRisk}. If
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2\) and
-\(\mathbb{P}_{\mathcal{B}^0}(\xi) \geq 3/4\), then
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \geq 1/4\). Thus:
-
-\begin{align*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \\
-& \geq \frac{1}{8} \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
-\end{align*}
-
-where we drop the second summand of the second line so that the
-inequality holds.
-
-On the other hand, when
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2\), then we know that
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \leq 1/2\) for any
-\(\mathbb{P}_{\mathcal{B}^0}(\xi)\). At the same time
-\(1-\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \geq 1/2\).
-Consequently,
-\(1/4 \leq \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \leq 1/2\),
-while
-\(\frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) \geq 0\).
-And so the stronger lower bound in that case is, as noticed by Locatelli
-et al. (2016), given simply by
-
-\begin{align*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \\
-& \geq \frac{1}{2}
-\end{align*}
-
-\subsection{\texorpdfstring{Lower Bound for Thresholding Bandit Problem
-with KL-divergence
-\label{sec:corollaryLBTBPproof}}{Lower Bound for Thresholding Bandit Problem with KL-divergence }}\label{lower-bound-for-thresholding-bandit-problem-with-kl-divergence}
-
-\subsubsection{\texorpdfstring{Lower Bound for One-Armed Thresholding
-Bandit
-\label{sec:corollaryLB1TBPproof}}{Lower Bound for One-Armed Thresholding Bandit }}\label{lower-bound-for-one-armed-thresholding-bandit}
-
-\textbf{Proof}: The proof follows closely the proof of Theorem 12 in
-Kaufmann et al. (2016) and is again an application of their
-transportation Lemma, Lemma 2.
-
-Consider the one-armed bandit problem, \(K = 1\) with the canonical
-exponential family of distributions distribution \(\nu_1\) parameterized
-by its mean \(\mu_1\). Furthermore, given we are in the thresholding
-bandit problem, we have a threshold \(\tau\) against which the arm is
-classified. Assume w.l.o.g. that for \(\nu_1\), \(\mu_1 \geq \tau\).
-Thus, \(\mathcal{S}_{\tau}^* = \{1\}\). After \(T\) rounds, a consistent
-algorithm returns with error probability \(p_T(\nu)\) the guess
-\(\hat{\mathcal{S}}_{\tau}\). Thus, we have for the event
-\(A = (\hat{\mathcal{S}}_\tau = \{1\})\) the probability
-\(\mathbb{P}_{\nu}(A)\). On the other hand, define the alternative model
-\(\nu'\) with mean \(\mu_1' < \tau\) such that the correct
-classification from \(\nu\) is now wrong:
-\(\mathcal{S}_{\tau}^* {'} = (\mathcal{S}_{\tau}^*)^C = \{\emptyset\}\).
-Consequently, since the algorithm is still consistent on this problem,
-we have that \(\mathbb{P}_{\nu'}(A) = p_t(\nu')\). Thus, we expect that
-as we let \(t\) increase, \(\mathbb{P}_{\nu'}(A)\) will decrease while
-\(\mathbb{P}_{\nu}(A)\) will increase.
-
-Indeed, given we consider only consistent algorithms, there should exist
-a number of samples for which the probability of the correct decision in
-problem \(\nu\) is larger than the error probability in problem
-\(\nu'\), that is: for every \(\epsilon > 0\), there exists
-\(t_0(\epsilon)\) such that for all \(t \geq t_0(\epsilon)\) we have
-
-\begin{equation*}
-\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_{\nu}(A). \label{eq:BoundForCorollary}
-\end{equation*}
-
-Now, consider again Lemma 2 in Kaufmann et al. (2016). If we let the
-algorithm be such that \(T = t\), we can apply the Lemma to the stopping
-time \(\sigma = t\) a.s. and the event \(A\) to get
-
-\[
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)).
-\]
-
-We can lower bound the RHS by using the bound on
-\(\mathbb{P}_{\nu'}(A)\) given in \eqref{eq:BoundForCorollary} and the
-monotonicity of the binary relative entropy. We get:
-
-\begin{align*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) & = t \KL(\nu_1', \nu_1) \\
-& \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)) \\
-& \geq d(\epsilon, 1- p_t(\nu)) \\
-& = \epsilon \log\Big(\frac{\epsilon}{1-p_t(\nu)}\Big) + (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) \\
-& \geq (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) + \epsilon \log(\epsilon) \\
-\end{align*}
-
-Letting \(\epsilon \rightarrow 0\), we get
-
-\[
-t \KL(\nu_1', \nu_1) \geq \log \Big(\frac{1}{p_t(\nu)}\Big) = -\log p_t(\nu).
-\]
-
-To make the bound as tight as possible, we choose the alternative model
-that minimizes \(\KL(\nu_1', \nu_1)\) while still ensuring that
-\(\mathcal{S}_{\tau}^* {'} = \{\emptyset\}\). In our case of the
-thresholding bandit with one-parameter exponential family distributions,
-this is given by choosing \(\mu_1' \rightarrow \tau\) (not equal to
-\(\tau\) since else the classification of \(\nu_1\) is again correct).
-By pluggin in, we get the result:
-
-\[
-t \KL(\tau, \mu_1) \geq -\log p_t(\nu) \quad \text{for} \; \mu_1' \rightarrow \tau.
-\]
-
-\subsubsection{\texorpdfstring{Lower Bound for \(K\)-Armed Thresholding
-Bandit
-\label{sec:corollaryLBKTBPproof}}{Lower Bound for K-Armed Thresholding Bandit }}\label{lower-bound-for-k-armed-thresholding-bandit}
-
-\textbf{Proof}: The proof is very similar to the proof of the corollary
-for \(K=1\). However, the alternative model needs more motivation than
-in the case of a single arm. But first, consider again that we are in
-the thresholding bandit problem with \(K\) arms of univariate canonical
-exponential family distributions that are parameterized by their means
-\(\mu_1, ..., \mu_K\) for the original problem
-\(\nu = (\nu_1, ..., \nu_K)\). W.l.o.g, assume that all arms are above
-the threshold, that is, \(\mu_1 \geq \tau, ..., \mu_K \geq \tau\). Then
-\(\mathcal{S}_{\tau}^* = \{1, ... , K\}\). The correct classification
-returned after \(t\) rounds is thus the event
-\(A = (\hat{\mathcal{S}}_{\tau} = \{1, ..., K\})\). We can now consider
-Lemma 2. The RHS is maximized when the alternative model is chosen such
-that \(d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A))\) is maximized.
-Given the event \(A\) as defined before, this is the case when
-\(\mathbb{P}_{\nu'}(A)\) is as small as possible. For consistent
-algorithms, this is the case when \(\nu'\) is chosen such that all
-\(\mu_1' < \tau, ..., \mu_K' < \tau\). Then even classifying a single
-arm correctly under \(\nu\) would lead to a mistake in \(\nu'\).
-Consequently, \(A\) is the most unlikely classification for a consistent
-algorithm for the problem \(\nu'\). We thus expect for any consistent
-algorithm that \(\mathbb{P}_{\nu}(A)\) becomes large and
-\(\mathbb{P}_{\nu'}(A)\) becomes small as the number of observations
-\(t\) increases. Again, for every \(\epsilon > 0\), there exists
-\(t_0(\epsilon)\) such that for all \(t \geq t_0(\epsilon)\) we have
-\(\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)\). This
-allows us to now use Lemma 1 as previously:
-
-\begin{align*}
-\sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\nu_i', \nu_i) & \geq \sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\tau, \mu_i) \\
-& \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)) \\
-& \geq d(\epsilon, 1-p_t(\nu)) \\
-& = \epsilon \log \Big(\frac{\epsilon}{1-p_t(\nu)}\Big) + (1-\epsilon) \log \Big( \frac{1-\epsilon}{p_t(\nu)}\Big) \\
-& \geq (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) + \epsilon \log(\epsilon)
-\end{align*}
-
-We let \(\epsilon \rightarrow 0\), divide by \(t\) and take the limsup
-on both sides as in Kaufmann et al. (2016):
-
-\begin{align*}
-\lim_{t \rightarrow \infty} \sup - \frac{1}{t} \log p_t(\nu) & \leq \lim_{t \rightarrow \infty} \sup \frac{1}{t} \sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\tau, \mu_i) \\
-& \leq \max_{i \in \{1,...,K\}} \KL(\tau, \mu_i)
-\end{align*}
-
-Though, since for the alternative problem \(\nu'\) we have for every
-\(i \in \{1,...,K\}\) that \(\mu_i = \tau\), it should hold for any
-consistent algorithm that \(\mathbb{E}_{\nu'}[N_i(t)] = \frac{t}{K}\),
-that is, every arm receives an equal amount of the budget. In that case,
-the above equation simplifies to
-
-\[
-- \frac{1}{t} \log p_t(\nu) \leq \frac{1}{t} \sum_{i=1}^K \frac{t}{K}\KL(\tau, \mu_i) = \frac{1}{K} \sum_{i=1}^{K} \KL(\tau, \mu_i),
-\]
-
-that is, the complexity is given by the simple average of the
-Kullback-Leibler distances of the threshold with regard to the
-respective distributions. This relates well to the lower bound that
-Kaufmann et al. (2016) describe in their Theorem 12 for consistent
-algorithms using \emph{uniform} sampling strategies; in our case,
-however, it is explained by the fact that under the alternative model,
-every consistent algorithm should adapt to a uniform sampling strategy.
-Thus our bound holds for any consistent strategy.
-
-\subsection{\texorpdfstring{Bayes-UCB Algorithm for the Thresholding
-Bandit Problem
-\label{sec:AppendixBUCB}}{Bayes-UCB Algorithm for the Thresholding Bandit Problem }}\label{bayes-ucb-algorithm-for-the-thresholding-bandit-problem}
-
-We show how the Bayes-UCB algorithm (Algorithm 1, Kaufmann et al., 2012)
-is adapted to the thresholding bandit problem to be used in the
-experiments in chapter \autoref{chap:Experiments}. The adapted version
-of their Algorithm 1 is given in Algorithm 4 below. In particular,
-notice that we not only calculate upper quantiles \(q_i^u(t)\), but also
-lower quantiles \(q_i^l(t)\), as we have to be able to compare against
-\(\tau\) from both sides. These quantiles rely on the posterior
-distributions \(\lambda_i^t\) for each mean \(\mu_i\). In our case, we
-employ Beta prior distributions as conjugate prior for the Bernoulli
-distributions in simulations 1 to 3 and initialize them with parameters
-\(\alpha_0\) and \(\beta_0\). See the setup in Kaufmann et al. (2012),
-especially equation (3), to see how the posterior distribution is
-updated in every round.
-
-\IncMargin{1em}
-
-\begin{algorithm}
-\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
-\Input{\emph{$\tau$, $\epsilon$, $T$, $\Pi^0$ (initial prior on $\mu$), $c$ (parameters of the quantile)}}
-\Output{$\hat{S}_\tau = \{i \in \mathbb{A},  \hat{\mu}_i(T) \geq \tau\}$}
-\BlankLine
-\emph{Pull each arm once}\;
-\For{$t = K+1$ \KwTo $T$}{
-\For{$i = 1$ \KwTo $K$}{
-  \emph{Compute $q_i^u(t) = Q\Big(1-\frac{1}{t(\log T)^c}, \lambda_i^{t-1}\Big)$ and $q_i^l(t) = Q\Big(\frac{1}{t(\log T)^c}, \lambda_i^{t-1}\Big)$}\;
-  \emph{Compute $B_i^{BUCB}(t) = (\tau - q_i^l(t))\cdot\mathbb{I}(\hat{\mu}_i(t) \geq \tau) + (q_i^u(t) - \tau)\cdot\mathbb{I}(\hat{\mu}_i(t) < \tau)$}\;
-}
-  \emph{Pull arm $I_t = \arg \max_{i\leq K} B_i^{BUCB}(t)$}\;
-  \emph{Observe reward $X \sim \nu_{I_t}$ and update $\Pi^t$}\;
-}
-\caption{Bayes-UCB algorithm from Kaufmann et al. (2012) adapted to the thresholding bandit problem.}\label{bayesucb_tbp}
-\end{algorithm}
-
-\DecMargin{1em}
-
-\subsection{Empirical Analysis of the Bayes-UCB Algorithm in Simulation
-2}\label{empirical-analysis-of-the-bayes-ucb-algorithm-in-simulation-2}
-
-In order to assess the excellent performance of the Bayes-UCB algorithm,
-which comes at a surprise given that is is designed for the cumulative
-regret setting and thus should tend to explore the arms to less, we run
-the Bayes-UCB algorithm for simulation 2 with three different choices of
-the parameter. In Figure 13, we see the performance results of the three
-versions, whereas Figure 14 shows how the algorithm allocates its budget
-across the arms over time. The three versions differ in the quantile
-parameter \(c\) (compare \autoref{sec:AppendixBUCB}) for which we choose
-\(c \in \{1/5, 1, 5\}\) to explore more or less. In Kaufmann et al.
-(2012), the cumulative regret upper bound for the Bayes-UCB is shown for
-\(c\geq 5\), though they report that the choice of \(c=0\) worked much
-better in their experiments. In our problem, it makes also sense that
-the versions with smaller quantiles (smaller \(c\)) tend to perform
-better, as these correspond to more exploration of the arms. In this
-particular simulation, the choices of \(c=1/5\) and \(c=1\) perform very
-similar. We see that the worse performance of \(c=5\) can be attributed
-to a initial phase of sampling primarily the arms with mean below the
-threshold. This comes from the fact that the Bernoulli and Beta
-distributions are bounded between \(0\) and \(1\), with \(\tau\) very
-close to \(0\). Thus, the index \(B_i^{BUCB}(t)\) cannot be larger than
-\(\tau\) for arms with \(\hat{\mu}_i(t) \geq \tau\). For arms with
-\(\hat{\mu}_i(t) < \tau\), however, the index can be as large as
-\(B_i^{BUCB}(t) = 0.95\). This leads to the effect seen in Figure 14:
-Due to \(c=5\), the indexes are based on very large quantiles even in
-the beginning, which leads to large indexes for the arms with small
-means. This however is not the ideal sampling behavior. The other two
-variants adapt much better due to their smaller quantiles (and more
-exploration).
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation2_results_bucb-1}
-
-}
-
-\caption{Performance comparison of algorithms for simulation 2.}\label{fig:simulation2_results_bucb}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-12-1}
-
-}
-
-\caption{Budget allocation across arms for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter.}\label{fig:unnamed-chunk-12}
-\end{figure}
-
-\subsection{Empirical Comparison of APT, SLR, and Bayes-UCB in
-Simulation
-2}\label{empirical-comparison-of-apt-slr-and-bayes-ucb-in-simulation-2}
-
-We can compare the different algorithms used in Simulation 2 based on
-the overall number of pulls of each arm. In the best case, an algorithm
-would sample an arm for the optimal share of the budget, in every
-simulation. This is of course not the case, since the number of pulls of
-a given arm at the end of the budget, \(T_i(T)\), is a random variable
-for adaptive sampling strategies. Given the 5000 iterations conducted in
-simulation 2, we can plot the empirical distribution of this random
-variable for different arms.
-
-In Figure 15, we show the distribution of \(T_6(T)\) for algorithms APT,
-Bayes-UCB, and SLR. We see that the distribution of the Bayes-UCB
-algorithm is much better concentrated around the optimal share of the
-budget, and has a bell curve shape. In contrast, the distributions of
-APT and SLR are much less concentrated but flat and wide, and spread
-across a very large interval. Both algorithms have several iterations in
-which they draw arm 6, the most difficult arm only a single time (during
-initialization). This happens for APT more than 5\% of the iterations,
-and leads to the spike on the very left of the graph. In order to cope
-at least a little bit with this problem, we have also run the SLR
-algorithm with the D-Tracking rule as introduced in Garivier and
-Kaufmann (2016). The effect is nearly not noticeable in Figure 15, but
-the minimum number of observations is not clearly bounded away from 0.
-The effect on the performance was described before and is very
-noticeable in comparison to SLR without D-Tracking. However, even with
-D-Tracking the performance of Bayes-UCB is not reached. We describe SLR
-with D-Tracking in Algorithm 5.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-13-1}
-
-}
-
-\caption{Empirical distribution of pulls of arm 6 in simulation 2 by different algorithms.}\label{fig:unnamed-chunk-13}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-14-1}
-
-}
-
-\caption{Empirical distribution of pulls of arms 1 and 10 in simulation 2 by different algorithms.}\label{fig:unnamed-chunk-14}
-\end{figure}
-
-\subsection{SLR Algorithm with D-Tracking
-Rule}\label{slr-algorithm-with-d-tracking-rule}
-
-\IncMargin{1em}
-
-\begin{algorithm}
-\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
-\Input{$\tau$, $\epsilon$, class of distributions $\nu(\mu, \theta)$, $\theta_i \: \forall i \in \mathbb{A}$}
-\Output{$\hat{S}_\tau = \{i \in \mathbb{A},  \hat{\mu}_i(T) \geq \tau\}$}
-\BlankLine
-\emph{Pull each arm once}\;
-\For{$t = K+1$ \KwTo $T$}{
-  \emph{Calculate $U_t = \{i \in \mathbb{A}, T_i(t) < \sqrt{t} - K/2\}$}\;
-  \emph{Set $I_t = \arg \min_{i \in \mathbb{A}} B_i^{SLR}(t)$ as in \autoref{eqn:SLRIndex}}\;
-  \If{$U_t \neq \emptyset$}{Set $I_t = \arg \min_{i \in \mathbb{A}} T_i(t)$}
-  \emph{Pull arm $I_t$}\;
-  \emph{Observe reward $X_t \sim \nu_{I_t}$}\;
-}
-\caption{SLR algorithm with D-Tracking Rule (Garivier and Kaufmann, 2016)} \label{algo_slr_1d_dTracking}
-\end{algorithm}
-
-\DecMargin{1em}
-
-\subsection{Means in Simulations 4 and
-5}\label{means-in-simulations-4-and-5}
-
-We give here the means of the distributions used in simulations 4 and 5
-for completeness.
-
-\begin{longtable}[]{@{}rrrrrrrrrr@{}}
-\caption{Mean of Exponential arms 1 to 10 in simulation
-4.}\tabularnewline
-\toprule
-V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
-\midrule
-\endhead
-0.176 & 0.2233 & 0.2407 & 0.3026 & 0.3359 & 0.35 & 0.3705 & 0.5497 &
-0.7374 & 0.8758\tabularnewline
-\bottomrule
-\end{longtable}
-
-\begin{longtable}[]{@{}rrrrrrrrrr@{}}
-\caption{Mean of Exponential arms 11 to 20 in simulation
-4.}\tabularnewline
-\toprule
-V11 & V12 & V13 & V14 & V15 & V16 & V17 & V18 & V19 & V20\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-V11 & V12 & V13 & V14 & V15 & V16 & V17 & V18 & V19 & V20\tabularnewline
-\midrule
-\endhead
-1.1419 & 1.2168 & 1.4021 & 1.6445 & 1.6868 & 1.9661 & 1.9716 & 3.2218 &
-3.2907 & 4.055\tabularnewline
-\bottomrule
-\end{longtable}
-
-\begin{longtable}[]{@{}rrrrrrrrrr@{}}
-\caption{Mean of Poisson arms 1 to 10 in simulation 5.}\tabularnewline
-\toprule
-V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
-\midrule
-\endhead
-0.0072 & 0.0576 & 0.0613 & 0.0925 & 0.1452 & 0.1559 & 0.1869 & 0.1958 &
-0.2235 & 0.2467\tabularnewline
-\bottomrule
-\end{longtable}
-
-\begin{longtable}[]{@{}rrrrrrrrrr@{}}
-\caption{Mean of Poisson arms 11 to 20 in simulation 10.}\tabularnewline
-\toprule
-V11 & V12 & V13 & V14 & V15 & V16 & V17 & V18 & V19 & V20\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-V11 & V12 & V13 & V14 & V15 & V16 & V17 & V18 & V19 & V20\tabularnewline
-\midrule
-\endhead
-0.2664 & 0.3008 & 0.4295 & 0.4948 & 0.5857 & 0.6904 & 0.7609 & 0.785 &
-0.8878 & 1.7114\tabularnewline
-\bottomrule
-\end{longtable}
+giving the author access to the discussed data set.
 

### 2017-09-18 Thesis/eigenstatement.Rmd
Printed version

--- 2017-09-08 Thesis/Draft.tex
@@
-\documentclass[11pt,]{article}
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
-  \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage{microtype}
-\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\usepackage[margin=1in]{geometry}
-\usepackage{hyperref}
-\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
-\hypersetup{unicode=true,
-            pdftitle={Draft},
-            colorlinks=true,
-            linkcolor=Maroon,
-            citecolor=Blue,
-            urlcolor=blue,
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-\usepackage{longtable,booktabs}
-\usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
+---
+output: pdf_document
+header-includes:
+   #- \documentclass[a4paper,twoside,english]{article}
+   - \usepackage{setspace}
+---
 
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
+\pagenumbering{gobble}
+\normalsize Copyright © 2017 Tim Radtke \newline
+tim@timradtke.net \newline
 
-%%% Change title format to be more compact
-\usepackage{titling}
+\vspace*{0.5\baselineskip}
 
-% Create subtitle command for use in maketitle
-\newcommand{\subtitle}[1]{
-  \posttitle{
-    \begin{center}\large#1\end{center}
-    }
-}
+\normalsize Humboldt-Universität zu Berlin \newline
+Unter den Linden 6 \newline
+10099 Berlin \newline
+Germany \newline
 
-\setlength{\droptitle}{-2em}
-  \title{Draft}
-  \pretitle{\vspace{\droptitle}\centering\huge}
-  \posttitle{\par}
-  \author{}
-  \preauthor{}\postauthor{}
-  \date{}
-  \predate{}\postdate{}
+\vspace*{3\baselineskip}
 
-\usepackage[retainorgcmds]{IEEEtrantools}
-\usepackage{bm}
-\usepackage{amsmath}
-\usepackage{bbm}
-\usepackage{hyperref}
-\usepackage[lined,boxed]{algorithm2e}
-\newtheorem{theorem}{Theorem}
-\newtheorem{definition}{Definition}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-\newcommand{\KL}{\,\text{KL}}
-\newcommand{\der}{\,\text{d}}
-\newcommand*{\Alignyesnumber}{\refstepcounter{equation}\tag{\theequation}}%
+\Large{\bf Selbstständigkeitserklärung\\}
 
-\begin{document}
-\maketitle
+\vspace*{1.5\baselineskip}
 
-{
-\hypersetup{linkcolor=black}
-\setcounter{tocdepth}{2}
-\tableofcontents
-}
-\newpage
+\large Ich erkläre hiermit, dass ich die vorliegende Arbeit selbstständig und nur unter Verwendung der angegebenen Quellen und Hilfsmittel angefertigt habe und noch nicht für andere Prüfungen eingereicht habe.
+Sämtliche Quellen einschließlich Internetquellen, die unverändert oder abgewandelt wiedergegeben werden, insbesondere Quellen für Texte, Grafiken, Tabellen und Bilder, sind als solche kenntlich gemacht.
+Mir ist bekannt, dass bei Verstößen gegen diese Grundsätze ein Verfahren wegen Täuschungsversuchs bzw.
+Täuschung eingeleitet wird.
 
-``In general, we look for a new law by the following process: First we
-guess it. Then we -- now don't laugh, that's really true. Then we
-compute the consequences of the guess to see what, if this is right, if
-this law that we guessed is right, to see what it would imply. And then
-we compare the computation results to nature, or we say compare to
-experiment or experience, compare it directly with observations to see
-if it works. If it disagrees with experiment, it's wrong. In that simple
-statement is the key to science. It doesn't make any difference how
-beautiful your guess is, it doesn't make any difference how smart you
-are, who made the guess, or what his name is. If it disagrees with
-experiment, it's wrong. That's all there is to it.''
+\vspace*{3\baselineskip}
 
-\begin{itemize}
-\tightlist
-\item
-  Richard Feynman in \emph{Richard Feynman Messenger Lectures at Cornell
-  University: The Character of Physical Law. Chapter 7, Seeking New
-  Laws}.
-\end{itemize}
-
-\newpage
-
-\section{Abbreviations}\label{abbreviations}
-
-Kullback-Leibler divergence between distributions \(\nu_i\) and
-\(\nu_j\): \(\KL(\nu_i||\nu_j)\).
-
-Binary relative entropy:
-\(d(x,y) := x \log(x/y) + (1-x) \log((1-x)/(1-y))\), where
-\(d(0,0) = d(1,1) = 0\).
-
-Kullback-Leibler divergence for two Bernoulli distributions
-parameterized by their means \(\mu_i\) and \(\mu_j\):
-\(KL_{Ber}(\nu_i||\nu_j) = d(\mu_i, \mu_j)\).
-
-Define exponential family of distributions
-
-Define KL Divergence for this family
-
-\newpage
-
-\section{\texorpdfstring{Introduction
-\label{chap:Introduction}}{Introduction }}\label{introduction}
-
-The thesis at hand joins a large literature concerned with the problem
-of sequential sampling. One is familiar with the idea of ``batch
-sampling'', where the entire sample is gathered first and analyzed only
-after the last sample has become available. However, as noted in
-Chernoff (1958), many situations arise in which one would like to gather
-feedback from samples as they are drawn, so as to influence the choice
-of the next sample. The two fundamental characteristics of the latter
-sampling process are that it is sequential and adaptive. Since
-observations are drawn in sequence, one has a chance to analyze past
-observations in order to adapt the decision of what sample one would
-like to observe next.
-
-This makes sequential sampling especially relevant in situations where
-there is an inherent cost to obtaining samples. The classical example is
-that of clinical trials in which a researcher tests two drugs on
-patients to observe which one performs better. Not only is it difficult
-to gather enough patients, but one would also like to adapt the sampling
-such that as soon as possible more patients receive the better drug and
-are cured. As noted in Cappé et al. (2013), this example dates back to
-Thompson (1933, 1935). Such problems are known as multi-armed bandit
-problems in which the sampling is adapted so as to minimize the
-cumulative regret: In the case of the drug tests, one would like to
-sample the two drugs in a way to find the best drug as soon as possible
-and then to test this drug more and more often and more often than the
-worse drug. This would lead to cumulatively more healthy patients than
-testing both drugs uniformly; it would minimize the regret from treating
-patients with an ineffective drug.
-
-Instead of drugs, one can consider two or more unknown distributions
-(which we call arms in the multi-armed bandit problem in analogy with
-the one-armed bandit slot machine). These distributions have different
-means, and one can draw samples sequentially from the distributions in
-order to estimate their means. To minimize the cumulative regret
-measure, one would like to play the distribution with the highest mean
-as much as possible (\emph{Exploitation}). At the same time, however,
-one has to sample all arms at least a little, so as to initially find
-the best arm (\emph{Exploration}). Any algorithm thus has to handle a
-trade-off between exploration and exploitation to minimize the regret.
-How can we organize the sampling in order to achieve this task?
-
-While Gittins (1979) presents an Bayesian-optimal solution to the
-cumulative regret problem, the Upper-Confidence Bound (UCB) algorithms
-pioneered by Agrawal (1995) and Auer, Cesa-Bianchi and Fischer (2002)
-have lead to a blooming literature on multi-armed bandit problems that
-has been picked up to solve modern problems in website and advertising
-optimization, where advertisers try to allocate their advertising
-optimally so as to reduce regret from showing poorly converting
-advertisements. Several algorithms like the KL-UCB algorithm based on
-Kullback-Leibler divergence upper confidence intervals (Cappé et al.,
-2013) or the Bayes-UCB algorithm (Kaufmann et al., 2012) have followed
-and been shown to be optimal as they reach the lower bound introduced in
-Lai and Robbins (1985) and Burnetas and Katehakis (1996).
-
-These algorithms have in common that they compute after every new sample
-an index for each of the unknown distributions. This index is based
-solely on the past (observed) data, and then used to pick the
-distribution from which the next sample should be drawn. Using these
-indexes, algorithms can sample sequentially and adapt their strategies
-to observations as they are collected.
-
-Similar algorithms based on indexes can be used on related problems.
-Instead of minimizing cumulative regret, it can be of interest to find
-the best arm, that is, the distribution with the largest mean -- with as
-few samples as possible and with confidence as large as possible. This
-is particularly useful when there is not a cost from testing arms with
-lower mean, but when drawing any sample is costly. Thus one needs to
-explore the distributions as efficiently as possible. Exploitation is
-not necessary, and the setting is thus referred to as \emph{Pure
-Exploration}. The need for strategies other than uniform sampling
-arises: One does not want to continue to sample distributions that one
-is confident in. This setting is related to the problem faced in
-Bayesian Optimization: Training large neural networks is costly in terms
-of time and computation, and so the parameter space needs to be explored
-with as few samples as possible. (Zhang et al., 2017; Brochu et al.,
-2010). The problem of best arm identification is also very related to
-statistical hypothesis testing as noted by Chernoff (1958) since one has
-to make a decision about how the means of distributions relate to each
-other. The main difference being that the bandit setting includes the
-testing procedure in the sampling process.
-
-Given the focus on exploration, the pure exploration problem is usually
-described with a loss function different from the one in the cumulative
-regret settings. Audibert et al. (2010) introduce a soft measure called
-\emph{simple regret} based on which they describe UCB policies. Other
-authors investigate binary measures that are equal to 1 when the best
-arm has not been identified (Russo, 2016; Garivier and Kaufmann, 2016).
-These binary measures correspond to the probability of the identified
-arm being the best, and thus inherently related to hypothesis testing.
-The problem of best arm identification can readily be extended to the so
-called Top-\(m\) problem of identifying the best \(m\) of \(K\) arms
-(Kaufmann and Kalyanakrishnan, 2013; Kaufmann et al. 2016).
-
-In this thesis, we consider the thresholding bandit problem. Instead of
-identifying the best \(m\) out of \(K\) arms, we aim to find all
-distributions out of \(K\) that have a mean at least as large as a
-threshold fixed upfront. In the form described in Locatelli et al.
-(2016), algorithms in the thresholding bandit problem are evaluated
-against a binary loss function penalizing whenever an arm has not been
-classified correctly as being above or below the threshold, and thus
-focus on exploration similar to algorithms employed for best arm
-identification. Indeed, Locatelli et al. (2016) show how their
-thresholding algorithm can be used for best arm identification when the
-mean of the best arm is known upfront.
-
-In the following, we first present the thresholding bandit problem in
-detail in \autoref{chap:ThresholdingBanditProblem}. To then extend upon
-the algorithm proposed by Locatelli et al. (2016) and discussed in
-\autoref{sec:TheAPTAlgorithm}, we first explore in
-\autoref{chap:KullbackLeiblerPureExploration} how the Kullback-Leibler
-divergence has been employed in the best arm identification literature
-by Garivier and Kaufmann (2016) and Kaufmann et al. (2016) as this will
-lead us to our own extension. We shortly describe in
-\autoref{sec:VarianceBasedAlgorithms} two variance-based algorithms for
-the thresholding bandit problem introduced in Mukherjee et al. (2017)
-and Zhang et al. (2017), before introducing the new Simple Likelihood
-Ratio algorithm in \autoref{sec:LRforUnivariateExponentialFamily}. We
-end in \autoref{chap:Experiments} with experiments to examine the
-performance of different algorithms.
-
-\newpage
-
-\section{\texorpdfstring{The Thresholding Bandit Problem
-\label{chap:ThresholdingBanditProblem}}{The Thresholding Bandit Problem }}\label{the-thresholding-bandit-problem}
-
-To introduce the thresholding bandit problem, consider a game in which
-the learner is tasked to find the slot machines within a row of \(K\)
-slot machines in a casino that give a mean payoff larger than a fixed
-threshold \(\tau\), for example \(\tau = 0\). The learner cannot pull
-all slot machines at the same time. Instead, he acquires samples
-sequentially from one slot machine at a time to learn about their payoff
-structure. The learner has a budget of \(T>K\) slot machine pulls. After
-\(t-1\) samples, the learner has observed \(T_i(t-1)\) samples from slot
-machine \(i\). The payoffs \(X_{i,1}, ..., X_{i,T_i(t-1)}\) are drawn
-from the payoff distribution \(\nu_i\) underlying the slot machine
-\(i\). At time \(t\), the learner considers the payoffs he observed so
-far in order to choose the next slot machine he would like to pull. Her
-decision is lead by the goal to classify the slot machines with
-distribution \(\nu_i\) and mean payoff
-\(\mu_i = \mathbb{E}_{X \sim \nu_i}[X]\) after \(T\) samples as being
-above or below the threshold with error probability as small as
-possible.
-
-The thresholding bandit problem can thus be framed in the literature on
-sequential sampling strategies. Even though its name is reminiscient of
-the multi-armed bandit setting, the thresholding bandit problem is more
-akin to best arm identification and top-\(m\) identification problems
-due to its focus on exploration: While the classical multi-armed bandit
-problems are concerned with cumulative regret which increases
-\emph{during} sampling, best arm identification and thresholding bandits
-collect loss only once \emph{after} the sampling procedure (compare
-Garivier and Kaufmann, 2016; Kaufmann et al., 2016; Kaufmann and
-Kalyanakrishnan, 2013). As we will see in
-\autoref{chap:KullbackLeiblerPureExploration} there arises an implicit
-threshold between the means of the \(m\)-th best arm and the \(m+1\)-th
-best arm in the top-\(m\) identification problem (Kaufmann et al., 2016;
-Kaufmann and Kalyanakrishnan, 2013). Because of this, the two settings
-are very related.
-
-\subsection{\texorpdfstring{Setup
-\label{sec:Setup}}{Setup }}\label{setup}
-
-Consider a setting with a set of \(\mathbb{A}=\{1, ..., K\}\) unknown
-probability distributions \(\nu_i, i \in \mathbb{A}\). To stick with the
-idea of multi-armed bandits, we call the distributions arms, and
-observations from the arms rewards (Bubeck and Cesa-Bianchi, 2012). The
-learner is interested in learning about the structure of the arms; in
-particular, she would like to estimate the means \(\mu_1, ..., \mu_K\)
-by sequentially drawing observations \(X_{i,1}, X_{i,2}, ...\) from the
-different arms. However, at time \(t\) the learner cannot observe a
-reward from every distribution but must select a single arm \(I_t\) from
-which she would like to observe the reward \(X_{I_t,t}\). Often,
-adaptive sampling strategies makes the decision of which arm to pull by
-computing an index \(B_i(t)\) for each arm. If \(T_i(t)\) is the number
-of samples observed until time \(t\) for arm \(i\), then is \(B_i(t)\) a
-function of the past rewards \(X_{i,1}, ..., X_{i,T_i(t)}\) observed for
-arm \(i\), and w.l.o.g. \(I_t = \arg \min_{i = 1,...K} B_i(t)\). The set
-of indexes can be called strategy (Kaufmann et al., 2012) which makes it
-clear that the strategy is adapted as more observations are collected.
-Strategies of this kind are also called index policies.
-
-Which index proves to be useful is determined by the loss function with
-which the decisions of the algorithm are evaluated. Many problems are
-concerned with finding the arm with the largest mean \(\mu_i^*\) while
-collecting loss either cumulatively during (Auer and Cesa-Bianchi, 2012)
-or once at the end of the sampling (Kaufmann et al., 2016). The
-thresholding bandit problem considers a slightly different loss
-function. Consider a fixed threshold value \(\tau \in \mathbb{R}\) and
-an epsilon interval \(\tau \pm \epsilon\) around the threshold for
-\(\epsilon \geq 0\). As mentioned in the introduction, the learner is
-tasked with classifying arms as having a mean \(\mu_i\) larger or
-smaller than \(\tau\). As in Locatelli et al. (2016), whenever we say
-that ``an arm is over the threshold'', we say that the mean of the arm
-is over the threshold. To describe which arms are over the threshold, we
-also introduce the following set notation: Let \(\mathcal{S}_{u}\) be
-the set of distributions in \(\mathbb{A}\) with mean larger than some
-\(u \in \mathbb{R}\):
-\(\mathcal{S}_{u} := \{i \in \mathbb{A}, \mu_i \geq u\}\). Consequently,
-the complement is given by the arms with mean below \(u\),
-\(\mathcal{S}^C_{u} := \{i \in \mathbb{A}, \mu_i < u\}\).
-
-The thresholding problem for the learner is now to use a budget of
-overall \(T\) samples (or rounds) to explore the different arms. After
-this exploration phase, the learner returns a set of arms that she
-believes to be over the threshold. When evaluating the classification of
-the learner, arms with mean inside of the epsilon interval
-\(\tau \pm \epsilon\) will not be considered. The learner only has to
-correctly distinguish the means from the threshold up to the precision
-given by \(\epsilon\). Thus, the algorithm is not evaluated against
-\(\mathcal{S}_{\tau}\) and \(\mathcal{S}^C_{\tau}\), but needs to
-distinguish \(\mathcal{S}_{\tau+\epsilon}\) from
-\(\mathcal{S}^C_{\tau-\epsilon}\).
-
-The learner's classification is returned as the set
-\(\hat{\mathcal{S}}_{\tau} := \hat{\mathcal{S}}_{\tau}(T) \subset \mathbb{A}\)
-after \(T\) rounds; that is, the set of arms estimated to be over the
-threshold. The classification is evaluated against the loss given as
-(Locatelli et al., 2016):
-
-\[
-\mathcal{L}(T) = \mathbbm{1}{\big((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \lor (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset)\big)}
-\]
-
-In order to perform well, a learner has to identify all arms that are
-over the threshold as such, and to not claim arms as being over the
-threshold if they actually are below the threshold. Due to the precision
-\(\epsilon\), the loss is not influenced by arms which are very close to
-the threshold \(\tau\) as measured by \(\epsilon\), that is, arms inside
-of the \(\tau \pm \epsilon\) interval. If either
-\(\hat{\mathcal{S}}_{\tau}\) contains an arm below
-\((\tau - \epsilon)\), or \(\hat{\mathcal{S}}^C_{\tau}\) contains an arm
-above \((\tau + \epsilon)\), a loss of \(1\) is accrued. Else, all arms
-outside the epsilon interval are classified correctly and the loss is
-equal to \(0\). In the case of \(\epsilon = 0\), all arms need to be
-classified correctly to not collect any loss.
-
-Algorithms for this thresholding problem can be compared based on their
-expected loss. Let \(\mathbb{E}\) be the expectation with regard to the
-samples \(X_{i,1}, ..., X_{i,T}\) collected by the algorithm. The
-expected loss is then given as
-
-\[
-\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}\big((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \lor(\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset)\big),
-\]
-
-which corresponds to the probability of making at least one wrong
-classification. Both the probability of not identifying an arm that is
-actually over the threshold, as well as the probability of accepting an
-arm as over the threshold when it is not, are evaluated. The oracle
-strategy would evaluate all arms correctly with an error probability of
-\(0\) (Locatelli et al., 2016).
-
-At this point, we have introduced the general thresholding bandit
-problem setting which we will use throughout the thesis. The setting can
-be extended by different assumptions to make certain algorithms or
-bounds feasible. For that reason, Locatelli et al. (2016) assume that
-the distributions \(\nu_i, i \in \mathbb{A}\) are \(R\)-sub-Gaussian.
-Under this assumption, the authors are able to prove a lower bound on
-the largest probability of error of the best algorithm in the setting we
-have just introduced, as well as an upper bound on the performance of
-their APT algorithm which we will introduce in the following chapter. As
-in their paper, we define \(R\)-sub-Gaussian and assume it in the
-description of the their algorithm and bounds:
-
-\begin{definition}[$R$-sub-Gaussian distribution] 
-\label{definition:rsubgaussian}
-Let $R > 0$. A distribution $\nu$ is $R$-sub-Gaussian if for all $t \in \mathbb{R}$ we have
-\begin{equation*}
-\mathbb{E}_{X \sim \nu}[\exp(tX - t\mathbb{E}[X])] \leq \exp(R^2t^2/2).
-\end{equation*}
-\end{definition}
-
-As noted by Locatelli et al. (2016), this ensures that the mean
-\(\mu_i\) of the distributions \(\nu_i\) considered in our problem are
-finite. \(R\)-sub-Gaussian distributions offer concentration
-inequalities for the concentration of the empirical mean around the true
-mean, which makes it possible to deduce the bounds presented by the
-authors and repeated below. The family of \(R\)-sub-Gaussian
-distributions encompasses Gaussian distributions of variance \(R^2\) for
-\(R \in \mathbb{R}\), as well as all bounded distributions, with the
-important case of Bernoulli distributions.
-
-Having described the thresholding bandit setting as well as the
-assumption of \(R\)-sub-Gaussianity, we can now proceed to describe the
-\emph{Anytime Parameter-free Thresholding} (APT) algorithm proposed in
-Locatelli et al. (2016) for the thresholding bandit problem.
-
-\subsection{\texorpdfstring{The Anytime Parameter-free Thresholding
-Algorithm
-\label{sec:TheAPTAlgorithm}}{The Anytime Parameter-free Thresholding Algorithm }}\label{the-anytime-parameter-free-thresholding-algorithm}
-
-In the following we describe the \emph{Anytime Parameter-free
-Thresholding} (APT) algorithm proposed in Locatelli et al. (2016), which
-is a simple yet effective algorithm and displays some very favorable
-characteristics when compared to alternative algorithms.
-
-We fix the threshold \(\tau\) and epsilon interval around the threshold
-given by \(\epsilon\) upfront, and supply them as arguments to the
-algorithm: \((\tau, \epsilon)\). Based on the general thresholding
-problem, we demand that the algorithm draws samples \(X_{i,t}\) for
-\(T\) rounds from the distributions \(\nu_i, i\in \mathbb{A}\). For a
-given arm \(i\) and a given time \(t\), we let \(T_i(t)\) represent the
-number of samples drawn from arm \(i\) until time \(t\) (including).
-Consequently, the empirical mean of arm \(i\) at time \(t\) is given by
-\(\hat{\mu}_i(t) = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}\) where
-\(X_{i,s}\) is the feedback sampled from distribution \(\nu_i\) when the
-arm is pulled for the \(s\)-th time. In the case of the APT algorithm,
-the decision \(\hat{\mathcal{S}}_{\tau}\) is based on the empirical
-means \(\hat{\mu}_i(T)\) estimated from the samples drawn up to time
-\(T\):
-\(\hat{\mathcal{S}}_{\tau} := \hat{\mathcal{S}}_{\tau}(T) = \{i \in \mathbb{A}, \hat{\mu}_i(T) \geq \tau\}\).
-
-As we see in algorithm \ref{alg:APT}, the APT algorithm initiates by
-pulling each arm once. Then, for each \(t > K\), it calculates for every
-arm the values \(T_i(t)\) and \(\hat{\mu}_i(t)\). Based on the empirical
-mean, the algorithm computes the estimated gap between the mean and the
-threshold as
-\(\hat{\Delta}_i(t) = \hat{\Delta}_i^{\tau, \epsilon}(t) = |\mu_i(t) - \tau| + \epsilon\).
-The decision of which arm is sampled next is then based on the value
-\(B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t)\): the algorithm pulls arm
-\(I_{t+1} = \arg \min_{i\leq K} B_i(t+1)\) minimizing this decision
-quantity. After overall \(T\) pulls, the algorithm returns the sets
-described in the general setup, \(\hat{\mathcal{S}}_{\tau}\) and
-\(\hat{\mathcal{S}}^C_{\tau}\).
-
-\IncMargin{1em}
-
-\begin{algorithm}
-\SetKwData{Left}{left}\SetKwData{This}{this}\SetKwData{Up}{up}
-\SetKwFunction{Union}{Union}\SetKwFunction{FindCompress}{FindCompress}
-\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
-\Input{$\tau$, $\epsilon$}
-\Output{$\hat{S}_{\tau} = \{i \in \{1,...,K\}, \hat{\mu}_i(T) \geq \tau\}$}
-\BlankLine
-\emph{Pull each arm once}\;
-\For{$t = K+1$ \KwTo $T$}{
-  \emph{Pull arm $I_t = \arg \min_{i \in A} B_i^{APT}(t) = \arg \min_{i \in A} \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau|+\epsilon)$}\;
-  \emph{Observe reward $X_t \sim \nu_{I_t}$}\;
-}
-\caption{Anytime Parameter-free Thresholding Algorithm (Locatelli et al., 2016)}\label{alg:APT}
-\end{algorithm}
-
-\DecMargin{1em}
-
-Just like the general index policies mentioned in \autoref{sec:Setup},
-we see that the APT algorithm adapts its strategy using an index
-\(B_i(t+1)\) for each arm that is based entirely on the observations
-observed until time \(t\). Given the arm with the smallest index is
-pulled at round \(t+1\), we observe that arms that are estimated to be
-further away from the threshold \(\tau\) as measured by the absolute
-distance to their empirical mean \(\hat{\mu}_i\), \(\hat{\Delta}_i(t)\),
-are pulled less often. Intuitively, it is easier to classify arms as
-below or above \(\tau\) when their mean is far away from the threshold.
-In contrast to the uniform sampling strategy, APT will gather more
-evidence for arms which appear to be inherently more difficult to
-classify. Likewise, APT tends to less often pull arms which it already
-pulled considerably often as measured by \(T_i(t)\). If arm \(i\) has
-been pulled more often than arm \(j\), then we should in general be more
-confident in its estimated mean and the corresponding distance to the
-threshold. If we are confident in \(i\), then it is better to explore
-other arms by drawing an observation from arm \(j\). By adapting its
-sampling strategy in this way during the sequential sampling process,
-the APT algorithm minimizes the probability of error
-\(\mathbb{E}[\mathcal{L}(T)]\) after \(T\) samples have been observed.
-
-The previous paragraph describes how arms close to the threshold are
-intuitively more difficult to classify. In the index employed by the APT
-algorithm, the distance between an arm and the threshold is measured by
-the absolute distance \(\hat{\Delta}_i(t)\) between the (estimated) mean
-of the arm and the threshold \(\tau\) (and the epsilon interval). When
-the APT algorithm realizes that an arm has a mean close to the
-threshold, then this arm requires more attention than an arm far away
-from the threshold; the confidence in the empirical mean has to be
-larger. Or the empirical mean has to be better concentrated around the
-true mean. Otherwise it is easier to make a mistake on this arm. To gain
-this confidence, the arm requires more samples, and thus a larger share
-of the overall \(T\) samples available. With this intuition, it makes
-sense to measure the complexity of a thresholding problem: If we knew
-upfront how complex a given set of arms is, we would know whether to
-expect a small or large probability of error given our budget \(T\).
-Also, for example in the best arm identification problem, there exist
-algorithms which take the complexity of a problem as input. Based on the
-complexity they then adapt their sampling strategy. See for example the
-UCB-E algorithm in Audibert et al. (2010) for the best arm
-identification problem, or the KL-LUCB-E algorithm in Kaufmann and
-Kalyanakrishnan (2013) as extension to the top-\(m\) problem.
-
-While the APT algorithm does not require the complexity to be known
-upfront (which would be problematic as it is not known upfront), it is
-necessary to define the complexity to deduce the upper bound on its
-probability of error. Similar to the distance measure used in the
-algorithm's index, we define the gap \(\Delta_i^{\tau,\epsilon}\)
-between arm \(i\) and the threshold \(\tau \pm \epsilon\) as
-
-\[
-\Delta_i := \Delta_i^{\tau,\epsilon} = |\mu_i - \tau| + \epsilon
-\]
-
-Given this gap, Locatelli et al. (2016) define the complexity
-\(H_{\tau, \epsilon}\) for the thresholding bandit problem naturally as
-
-\[
-H := H_{\tau, \epsilon} = \sum_{i=1}^K \frac{1}{(\Delta_i^{\tau,\epsilon})^2}.
-\]
-
-Note that the complexity of the problem increases in the number of arms
-\(K\) and decreases in the gap \(\Delta_i^{\tau,\epsilon}\).
-Consequently, when we require less precision, that is, we increase
-\(\epsilon\), the hardness decreases. Furthermore, we see that each arm
-contributes its individual complexity,
-\(h_i^{\tau,\epsilon} = \frac{1}{(\Delta_i^{\tau,\epsilon})^2}\)
-linearly into the problem. Thus, if the complexity \(H\) is a good
-measure of the actual problem complexity, and we knew upfront which arm
-has which mean, we could allocate the ``optimal'' share of the budget,
-\(T \cdot h_i /H\) to arm \(i\). However, since we do not know neither
-\(\mu_i\) nor \(H\) upfront, the best we can do is to adapt our
-allocation of samples more and more towards this optimum as we observe
-samples.
-
-At this point, one can question whether the measure of complexity \(H\)
-proposed in Locatelli et al. (2016) is a good measure of the ``true''
-problem complexity. In the following \autoref{sec:UpperBoundLocatelli},
-we will show the upper bound on the probability of error for the APT
-algorithm and see how the complexity \(H\) arises naturally for the APT
-algorithm. In \autoref{sec:LowerBoundLocatelli} we then show the lower
-bound presented in Locatelli et al. (2016) and that the APT algorithm is
-optimal in that it matches the lower bound. We discuss the results and
-the APT algorithm further in \autoref{sec:DiscussionLocatelli}.
-
-\subsection{\texorpdfstring{Upper Bound for the APT Algorithm
-\label{sec:UpperBoundLocatelli}}{Upper Bound for the APT Algorithm }}\label{upper-bound-for-the-apt-algorithm}
-
-In this chapter we present the upper bound on the probability of error
-that the APT algorithm incurs, as proven in Locatelli et al. (2016). The
-upper bound is on the probability of error that the algorithm has after
-\(T\) rounds of sampling for a problem with arms that are assumed to be
-\(R\)-sub-Gaussian. The bound depends also on the complexity of the
-problem, and we show in the proof that given the index of the APT
-algorithm as defined in \autoref{sec:TheAPTAlgorithm}, the complexity
-\(H\) is an appropriate measure.
-
-We now state the theorem as in Locatelli et al. (2016) and present a
-proof.
-
-\begin{theorem}[Theorem 2, Locatelli et al., 2016] \label{theorem:LocatelliTheorem4}
-Let $K \geq 0$, $T \geq 2K$, and consider a problem $\mathcal{B}$.
-Assume that all arms $\nu_i$ of the problem are R-sub-Gaussian with means $\mu_i$.
-Let $\tau \in \mathbb{R}, \epsilon \geq 0$.
-Algorithm APT's expected loss is upper bounded on this problem as
-\begin{equation*} \mathbb{E}(\mathcal{L}(T)) \leq \exp
-\Big(-\frac{1}{64R^2}\frac{T}{H} + 2 \log((\log(T) + 1)K)\Big) \end{equation*}
-
-where we remind that $H = \sum_i (|\mu_i - \tau | + \epsilon)^{-2}$ and where
-$\mathbb{E}$ is the expectation according to the samples of the problem.
-\end{theorem}
-
-\subsubsection{\texorpdfstring{Proof of Theorem
-\ref{theorem:LocatelliTheorem4}}{Proof of Theorem }}\label{proof-of-theorem}
-
-In order to upper bound the expected loss of the APT algorithm, we want
-to define an event on which the algorithm correctly seperates arms from
-the threshold, that is, a separation condition holds on this event. We
-then want to show that this \emph{favorable} event does indeed hold with
-large probability. Consequently, APT's probability of error will
-correspond to the probability that the favorable event does not hold, as
-this leads to a failure of the seperation condition, and consequently to
-an incorrect classification of at least one arm by the algorithm. We
-start by defining the separation condition.
-
-\subsubsection{Separation Condition}\label{separation-condition}
-
-As noted in Zhong et al. (2017), a simple requirement to correctly
-classify arms at the final round is the following. For every arm
-\(i \in \{1, ..., K\}\) after the final round \(T\), require \[
-\hat{\mu}_{i}(T) \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
-\] or \[
-\hat{\mu}_{i}(T) \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
-\] Or simply in terms of the gap between the arm and the threshold as
-used in the index by the APT algorithm: \[
-| \hat{\mu}_{i}(T) - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
-\]
-
-Intuitively, this condition makes sense as it ensures that the current
-mean estimate is closer to the true mean than to the threshold.
-Consequently, there is no arrangement possible in which the arm is
-classified wrong while the separation condition holds. Assuming
-\(\mu_i < \tau\) and \(\epsilon = 0\), an incorrect classification would
-require \(\mu_i < \tau \leq \hat{\mu_i}\). But then
-\(| \hat{\mu}_{i}(T) - \mu_i | \geq |\mu_i - \tau|\), which violates the
-separation condition.
-
-Thus, we need to show that this condition holds for every arm
-\(i \in \{1,...,K\}\) with large probability after the final round
-\(T\). In different words, we need to derive an upper bound on the
-probability with which this condition does not hold.
-
-\subsubsection{The Favorable Event}\label{the-favorable-event}
-
-The separation condition describes what event needs to hold in order for
-the APT algorithm to make a correct classification: The smaller the
-deviation of the empirical mean from the population mean, the more
-difficult it is for the classification to be wrong. Moreover, if the
-mean and empirical mean are identical, then the classification is
-correct independent of the threshold. Also, the closer the mean to the
-threshold, the better the estimate has to be for a correct
-classification to be likely. To bound the absolute deviation of the
-empirical mean from the true mean, we define the favorable event \(\xi\)
-as
-
-\[
-\xi = \Big\{\forall i \in \mathbb{A}, \forall s \in \{1,...,T\} : |\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}} \Big\}.
-\]
-
-The probability that this favorable event occurs should be large, or
-equivalently, the probability that the deviation is small should be
-large. Then it follows that the separation condition holds with large
-probability.
-
-We know that \(X_i\) are \(R\)-sub-Gaussian by assumption. That is, we
-have
-
-\[
-\mathbb{E}[\exp (tX_{i,s}-t\mathbb{E}[X_{i,s}])] = \mathbb{E}[\exp (t(X_{i,s}-\mathbb{E}[X_{i,s}]))] \leq \exp (R^2t^2/2)
-\]
-
-where the RHS is the moment-generating function of the random variable
-\(X_{i,s}-\mathbb{E}[X_{i,s}]\). While Höffding's Lemma and Höffding's
-Inequality are commonly applied to bounded random variables \(Z\) with
-\(\mathbb{P}(a\leq Z \leq b) = 1\) and \(\mathbb{E}[Z] = 0\), we see
-that \(Z\) are \(R\)-sub-Gaussian with \(R^2 = \frac{(a-b)^2}{4}\).
-Using this last equality, we can easily apply Höffding's Inequality to
-our case.
-
-\begin{lemma}[Höffding's Inequality (Kloft Lecture Notes)] \label{lemma:HoeffdingsInequality}
-Let $X_1, ..., X_s$ be independent, identically distributed random variables with mean $\mathbb{E}[X_t] = \mu$ and $\mathbb{P}(a_t \leq X_t - \mathbb{E}[X] \leq b_t) = 1$.
-Denote their empirical mean by $\bar{X}_s=\frac{1}{s}\sum_{t=1}^{s}X_t$.
-Then, for any $\gamma > 0$, we have the following concentration inequality:
-
-\begin{equation*}
-\mathbb{P}(|\bar{X}_s - \mu| \geq \gamma) \leq 2\exp (-2s^2\gamma^2/\sum_{t=1}^s(b_t - a_t)^2).
-\end{equation*}
-\end{lemma}
-
-If we replace \(\sum_{t=1}^s(b_t - a_t)^2\) by \(4sR^2\), we have the
-concentration inequality for our \(R\)-sub-Gaussian random variables:
-
-\[
-\mathbb{P}(|\bar{X}_s - \mu| \geq \gamma) \leq 2\exp (-\frac{s\gamma^2}{2R^2}).
-\]
-
-Writing \(\gamma = \sqrt{\frac{T\delta^2}{Hs}}\), we get for the
-favorable event
-\(\xi_i = \{|\bar{X}_s - \mu| \leq \sqrt{\frac{T\delta^2}{Hs}}\}\) of an
-individual arm \(i\), for each \(i \in \mathbb{A}\) and each
-\(s \in \{1, ..., T\}\):
-
-\[
-\mathbb{P}(\xi_i) = \mathbb{P}\Big(|\bar{X}_{i,s} - \mu_i| \leq \sqrt{\frac{T\delta^2}{Hs}}\Big) \geq 1 - 2\exp (-\frac{T\delta^2}{2R^2H}),
-\] where \(T\) is again the total budget of samples, and \(H\) the
-complexity. Now let
-
-\[
-\tilde{\xi} = \Big\{\forall i \in \mathbb{A}: |\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}} \Big\}.
-\]
-
-To derive the probability of event \(\tilde{\xi}\), we apply a union
-bound on \(\mathbb{P}(\cup_{i=1}^K \xi_i^C)\):
-
-\begin{align*}
-\mathbb{P}(\tilde{\xi}) & = 1-\mathbb{P}(\xi^C) \\
-& = 1-\mathbb{P}(\cup_{i=1}^K \xi_i^C) \\
-& \geq 1 - \sum_{i=1}^K \mathbb{P}(\xi_i^C) \\
-& \geq 1 - 2K\exp (-\frac{T\delta^2}{2R^2H})
-\end{align*}
-
-We could use the same union bound a second time to bound over all
-\(s \in \{1, ..., T\}\) and derive for the favorable event \(\xi\):
-
-\[
-\mathbb{P}(\xi) \geq 1 - 2TK \exp(-\frac{T\delta^2}{2R^2H})
-\]
-
-Locatelli et al. (2016) use instead of Höffding's inequality a
-Sub-Gaussian martingale inequality including a peeling argument in order
-to derive a better bound of
-
-\[
-\mathbb{P}(\xi) \geq 1 - 2(\log(T) +1)K \exp(-\frac{T\delta^2}{2R^2H})
-\]
-
-This bound is non-trivial for much smaller values of \(T\), and we will
-use it in the following.
-
-\subsubsection{\texorpdfstring{Need to Bound
-\(T_i\)}{Need to Bound T\_i}}\label{need-to-bound-t_i}
-
-We now have that with large probability the favorable event holds. On
-the favorable event, we have for every arm \(i\):
-
-\[
-| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}
-\]
-
-The deviation of arm \(i\) at time \(t\) depends on how large \(H\),
-\(T\), and \(T_i(t)\) are. While \(t\), \(H\), \(T\) are deterministic,
-the number of times arm \(i\) has been pulled at round \(t\),
-\(T_i(t)\), is a random variable. In order to know how large the
-probability of the favorable event is (and thus the error probability),
-we need to know the value of \(T_i(t)\), or at least bound a range of
-potential values. Put differently: To ensure a deviation smaller than
-\(\sqrt{\frac{T\delta^2}{HT_i(t)}}\) for arm \(i\), we need to ensure
-that arm \(i\) has been pulled at least \(T_i(t)\) times. As usual in
-multi-armed bandits, and different from uniform sampling, the number of
-pulls is a random variable that also depends on how often other arms are
-pulled. In general, we do not want each arm to be pulled an equal
-amount, but each arm should be pulled some times, and not too many
-times.
-
-Thus, in order to check that the deviation of arm \(i\) really is small
-enough for the separation condition to hold on the favorable event, we
-need to bound the number of pulls of every arm from below.
-
-\subsubsection{\texorpdfstring{Characteristics of a Frequently Pulled
-Arm (Lower Bound on
-\(T_k(T)\))}{Characteristics of a Frequently Pulled Arm (Lower Bound on T\_k(T))}}\label{characteristics-of-a-frequently-pulled-arm-lower-bound-on-t_kt}
-
-Given that we do not follow a uniform sampling strategy, we know that at
-time \(T\), some arms will have been pulled more frequently than others.
-In particular, some arms will have been pulled more than \(T/K\) times.
-How often an arm is pulled can be related to the individual arm's
-contribution to the overall complexity measure. Let \(h_i\) be a measure
-of arm \(i\)'s individual problem complexity and write for the overall
-problem complexity \(H = \sum_{i = 1}^{K} h_i\). Then arm \(i\)
-contributes a share of \(h_i/H\) to the overall problem complexity. We
-can now show that there exists an arm that has been pulled at least as
-often as the share of his complexity contribution.
-
-Given the initialization of the APT algorithm, every arm is pulled once
-initially. Consequently, there is a budget of \(T-K\) rounds left after
-the initialization. As shown in Locatelli et al. (2016), there exists an
-arm \(k\) that has been pulled after the initialization (\(\geq 2\)
-pulls) and for which at the final round \(T\) it holds:
-\(T_k(T) - 1 \geq \frac{(T-K)h_k}{H}\). This can be shown by a
-contradiction. Assume that the opposite holds, that is
-
-\[
-\forall i \in \{1,...,K\}: T_i(T) - 1 < \frac{(T-K)h_i}{H}
-\]
-
-Consequently, at time \(T\), we would have pulled across all arms
-\(\sum_{i=1}^KT_i(T)-1\) times. If the previous assumption holds, we
-would not have used the entire budget:
-
-\[
-\sum_{i=1}^K T_i(T)-1 < \sum_{i=1}^K \frac{(T-K)h_i}{H} = (T-K)\sum_{i=1}^K \frac{h_i}{H} = T-K
-\]
-
-This is a contradiction, since as an requirement to the algorithm we
-have that \(\sum_{i=1}^K T_i(T)-1 = (T-K)\), that is, we use the entire
-budget of samples.
-
-Furthermore, we have assumed \(T>2K\) in the statement of Theorem
-\ref{theorem:LocatelliTheorem4}. Plugging this in gives \[
-T_k(T) - 1 \geq \frac{(T-K)h_k}{H} \geq \frac{(T-1/2T)h_k}{H} = \frac{Th_k}{2H}
-\]
-
-Now we know how often the arm has been pulled at the very end. That does
-not mean that \(k\) has been pulled at time \(T\). Thus we consider the
-time \(t \leq T\) at which arm \(k\) is pulled for the last time. We get
-
-\[
-T_k(t) \geq T_k(T) - 1 \geq \frac{Th_k}{2H}.
-\]
-
-This gives us a lower bound on how often arms are pulled that are pulled
-frequently relative to their contribution to the problem complexity. Now
-we need a lower bound on \(T_i(T)\) for every other arm \(i\).
-
-\subsubsection{\texorpdfstring{Lower Bound on
-\(T_i(T)\)}{Lower Bound on T\_i(T)}}\label{lower-bound-on-t_it}
-
-Consider again as before the round \(t\) at which arm \(k\) is pulled
-for the very last time. Since the APT algorithm minimizes at every round
-\(s \geq K+1\) the index \(B_j(s)\), and pulls the arm with the smallest
-index, we know that arm \(k\) must have had the smallest index at round
-\(t\). We have:
-
-\[
-B_k(t) \leq B_i(t) \Leftrightarrow \sqrt{T_k(t)}\hat{\Delta}_k(t) \leq \sqrt{T_i(t)} \hat{\Delta}_i(t)
-\]
-
-One can already expect that this can be used to derive a lower bound on
-\(T_i(t)\) on the RHS, and this is exactly what we do. On the LHS, we
-plug in the lower bound for \(T_k(t)\) derived before. Additionally
-bounding \(\Delta_k(t)\) from below, and \(\hat{\Delta}_i(t)\) from
-above using the favorable event will give the desired lower bound.
-
-Thus assume we are on the favorable event \(\xi\) with large
-probability. we consequently have
-
-\[
-| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}.
-\]
-
-As shown in Locatelli et al. (2016), one can use the reverse triangle
-inequality to get:
-
-\begin{align*}
-|\hat{\mu}_i(t) - \mu_i| & = |(\hat{\mu}_i(t) - \tau) - (\mu_i - \tau)| \\
-& \geq || \hat{\mu}_i(t) - \tau | - |\mu_i - \tau|| \\
-& \geq |(|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i - \tau| + \epsilon)| \\
-& \geq |\hat{\Delta}_i(t) - \Delta_i|
-\end{align*}
-
-If we combine this with the favorable event, we get
-
-\[
-\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}} \leq \hat{\Delta}_k(t) \leq \Delta_k + \sqrt{\frac{T\delta^2}{HT_k(t)}}
-\]
-
-and similar for \(\hat{\Delta}_i\). We can now lower bound the LHS of
-the indexes as
-
-\begin{align*}
-B_k(t) & \geq \Big(\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}}\Big) \sqrt{T_k(t)} \\
-& \geq \Big(\Delta_k - \sqrt{\frac{2}{h_k}}\delta \Big)
-\end{align*}
-
-At this point, it is useful to have a well chosen complexity measure. If
-we set \(h_i = \frac{1}{\Delta_i^2}\) as in Locatelli et al. (2016), we
-get
-
-\[
-\Big(\Delta_k - \sqrt{2}\delta \Delta \Big) \sqrt{\frac{T}{2H\Delta_k^2}} \leq B_k(t)
-\]
-
-which can be now be reduced to a form that is not specific to \(k\):
-
-\[
-\Big( \frac{1}{\sqrt{2}} - \delta \Big) \sqrt{\frac{T}{H}} \leq B_k(t).
-\]
-
-Now we need to remove \(\hat{\Delta}_i\) in order to bound \(T_i(t)\).
-Thus, we bound the RHS again using the favorable event much as we did
-for the LHS:
-
-\[
-B_i(t) = \hat{\Delta}_i \sqrt{T_i(t)} \leq \Big(\Delta_i + \sqrt{\frac{T\delta^2}{HT_i(t)}}\Big) \sqrt{T_i(t)} \leq \Delta_i \sqrt{T_i(t)} + \delta \sqrt{\frac{T}{H}}
-\]
-
-As in Locatelli et al. (2016) we use the fact that by definition
-\(\Delta\) and \(\hat{\Delta}\) are positive in order to square both
-sides and write
-
-\[
-(1 - 2\sqrt{2}\delta)^2 \frac{T}{2H\Delta^2_i} \leq T_i(t) \leq T_i(T)
-\]
-
-We thus have derived a lower bound on the amount of pulls for any arm.
-That means that we can show that no arm is pulled an insufficient amount
-of times with large probability, and that consequently the favorable
-event hold and the estimated mean is sufficienctly separated from the
-threshold.
-
-\subsubsection{Check Separation
-Condition}\label{check-separation-condition}
-
-As the last step, we need to check whether the lower bound on the pulls
-of any arm suffices to ensure that the separation condition holds on the
-favorable event. That means, given
-\(T_i(T) \geq (1-2\sqrt{2}\delta)^2 \frac{T}{2H\Delta_i^2}\), do we have
-\(|\hat{\mu}_i(T) - \mu | \leq \frac{\Delta}{2}\) on the favorable event
-\(\xi = \Big\{|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}}\Big\}\)?
-To check, we plug the lower bound into the favorable event and get
-
-\[
-|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}} \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta}
-\] Using \(\delta = (4\sqrt{2})^-1\) as in Locatelli et al. (2016), we
-have that the separation condition holds exactly:
-
-\[
-|\hat{\mu}_i - \mu | \leq \Delta_i \frac{\sqrt{2}\delta}{1-2\sqrt{2}\delta} \leq \frac{1}{2}\Delta_i.
-\]
-
-\subsubsection{Upper Bound on Error
-Probability}\label{upper-bound-on-error-probability}
-
-We have seen that on the favorable event \(\xi\), which holds with large
-probability \(\mathbb{P}(\xi)\), the separation condition holds as all
-arms have been pulled a sufficient number of times, such that their
-estimated mean is close to the true mean. All arms are classified
-correctly, and the algorithm does not suffer a loss. On the other hand,
-we make an error whenever the favorable event does not hold after all;
-that is, the deviation bound for the mean does not hold. At least one
-arm is misclassified and the arm suffers a loss. This occurs with
-probability \(1-\mathbb{P}(\xi)\). Consequently, the expected loss is
-upper bounded by
-
-\[
-\mathbb{E}[\mathcal{L}(T)] = 1 - \mathbb{P}(\xi) \leq 2(\log(T)+1)K \exp(-\frac{1}{64R^2}\frac{T}{H}).
-\]
-
-We now present the lower bound given in Locatelli et al. (2016) for the
-thresholding bandit problem. In order to derive the bound, a problem is
-specified to show that the error of the lower bound is attained even in
-this specific problem. In particular, for a set of problems with
-Gaussian distributions of variance \(1\), the largest probability of
-error on these problems that the best algorithm exhibits is still at
-least as large as the lower bound.
-
-\subsection{\texorpdfstring{Lower Bound for the Thresholding Bandit
-Problem
-\label{sec:LowerBoundLocatelli}}{Lower Bound for the Thresholding Bandit Problem }}\label{lower-bound-for-the-thresholding-bandit-problem}
-
-Locatelli et al. (2016) also provide a general lower bound on the
-probability of error in the thresholding bandit problem. The bound is
-derived for a specified set of problems through a change in distribution
-as common in the multi-armed bandit literature (compare for example
-Audibert et al., 2010, or Kaufmann et al., 2016). For any of these
-problems, the largest probability of error that the best algorithm
-incurs is still lower bounded by the bound given below.
-
-\begin{theorem}[Theorem 1, Locatelli et al., 2016] 
-\label{theorem:Locatelli2016Theorem1}
-For any sequence of gaps $(d_k)_k$, define a finite set of problems with Gaussian distributions with means corresponding to the gaps, and with variance 1.
-Lower bound the largest probability of error among these problems for the best possible algorithm as follows.
-Let $K,T \geq 0$.
-Let for any $i \leq K$, $d_i \geq 0$.
-Let $\tau \in \mathbb{R}, \epsilon > 0$.
-
-For $0 \leq i \leq K$, we write $\mathcal{B}^i$ for the problem where the distribution of arm $j \in \{1, \dots, K\}$ is $\mathcal{N}(\tau+d_i+\epsilon, 1)$ if $i \neq j$ and $\mathcal{N}(\tau-d_i-\epsilon, 1)$ otherwise.
-For all these problems, $H := H_{\tau, \epsilon} = \sum_i (d_i+2\epsilon)^{-2}$ is the same by definition.
-
-It holds that for any bandit algorithm,
-
-\begin{equation*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) \geq \exp(-3T/H-4 \log(12(\log(T)+1)K)),
-\end{equation*}
-
-where $\mathbb{E}_{\mathcal{B}^i}$ is the expectation according to the samples of problem $\mathcal{B}^i$.
-\end{theorem}
-
-A proof of the lower bound is given in the Appendix in
-\autoref{sec:AppendixAPTLB}.
-
-If we write the lower bound as
-\(LB = 12(\log(T)+1)K)\exp(-3T/H)\exp(-4) = C_{LB}(\log(T)+1)K\exp(-T/H)\)
-and the upper bound as
-\(UB = (\log(T)+1)K \exp(2) \exp(-\frac{1}{64R^2}\frac{T}{H}) = C_{UB}(\log(T)+1)K\exp(-T/H)\),
-we see that \(LB\) and \(UB\) match up to multiplicative constants and
-the \((\log(T)+1)K\) term which is negligiable in comparison with the
-exponent for large \(T\) as shown in Locatelli et al. (2016), which
-makes the APT algorithm order optimal.
-
-\subsection{\texorpdfstring{Discussion
-\label{sec:DiscussionLocatelli}}{Discussion }}\label{discussion}
-
-\begin{itemize}
-\tightlist
-\item
-  Mention Optimality (Upper Bound matches lower bound)
-\item
-  Anytime
-\end{itemize}
-
-One of the APT algorithm's main features is its simplicity. The sampling
-rule is very straightforward, and, as highlighted in Locatelli et al.
-(2016), it does not require any knowledge about the type of
-sub-Gaussianity \(R\), or the complexity \(H\) upfront. This makes the
-algorithm immediately applicable in practice while it still enjoys its
-upper bound on the expected regret. This is in particular worth
-highlighting when comparing APT to algorithms used in the best arm
-identification or Top-\(m\) setting. As alluded to in
-\autoref{sec:TheAPTAlgorithm}, many algorithms that fix the sampling
-budget upfront (i.e., fixed budget algorithms as UCB-E or KL-LUCB-E)
-require knowledge about the corresponding complexity upfront (Audibert
-et al., 2010; Kaufmann and Kalyanakrishnan, 2013). The problem however
-being, that to know the complexity, the experimenter has to know all
-means up to a permutation of the arms. This, of course, is not given in
-practice. Thus alternative algorithms try to estimate the complexity
-online which can be difficult as especially in the beginning plug-in
-estimates based on the estimated means may lead to wrong estimates of
-the complexity, which in turn leads to poor budget allocation based on
-mistaken beliefs (compare Garivier and Kaufmann, 2016). On the other
-hand, the sequential sampling strategy has to rely on some estimate.
-While the APT algorithm does not explicitly estimate the complexity, the
-gaps that serve as index are essentially the same. Faced not with
-sub-Gaussian but more heavy-tailed distributions, these estimates might
-well lead to poor performance.
-
-Here, the APT algorithm shows room for improvement, as also mentioned in
-Locatelli et al. (2016). The problem is that the assumptions for the
-bounds no longer hold as arms are less sub-Gaussian; of course the
-complexity \(H\) and the term \(\hat{\Delta}_i(t)\) in the algorithm's
-index are motivated by sub-Gaussian distributions. The more one moves
-away from those, the less appropriate these quantities become. In
-particular, the empirical mean will be less (or not at all) concentrated
-around the true mean and more impacted by outliers which are more likely
-under non sub-Gaussian distributions. Locatelli et al. (2016) thus
-refers to Bubeck et al. (2013a) which considers solutions for
-multi-armed bandits that are based on heavy-tail distributions. By using
-more robust estimators of the mean, one could equip the APT algorithm to
-deal with such distributions.
-
-Both Mukherjee et al. (2017) as well as Zhong et al. (2017) use
-estimates of the variance of the arms for their algorithms for the
-thresholding bandit problem and try to thereby improve upon the
-performance of the APT algorithm. While their simulations show promising
-results, their bounds rely on the assumption of bounded reward
-distributions. Thus their algorithms are not necessarily able to improve
-upon the assumption of sub-Gaussian distributions made by Locatelli et
-al. (2016). We will continue to discuss their results in
-\autoref{chap:VarianceBasedAlgorithms}.
-
-Yet another idea, again mentioned in Locatelli et al. (2016) is to show
-bounds based on the Kullback-Leibler divergence of the specific
-distribution directly. While the approximation through the Gaussian
-Kullback-Leibler divergence in the lower bound proof is convenient and
-leads to the simple APT algorithm, it might not stay appropriate for
-distributions whose Kullback-Leibler divergence tends to differ from the
-Gaussian. This, for example, is the case for Bernoulli distributions at
-very small parameters \(\mu\). We have for the Kullback-Leibler
-divergence of two Gaussian distributions \(\nu_i\) and \(\nu_j\) of mean
-\(\mu_i\) and \(\mu_j\) with equal variance:
-
-\[
-\KL_{N}(\nu_i || \nu_j) = 2(\mu_i - \mu_j)^2.
-\]
-
-Writing \(\mu_j = \tau\) and \(\epsilon = 0\), we see that the APT
-algorithm essentially measures the KL-divergence between two Normal
-distributions. For two Bernoulli distributions \(\nu_i\) and \(\nu_j\),
-parameterized by \(\mu_i\) and \(\mu_j=\tau\), we write
-
-\[
-\KL_{Ber}(\nu_i||\nu_j) = \mu_i \log(\frac{\mu_i}{\tau}) + (1-\mu_i) \log(\frac{1-\mu_i}{1-\tau})
-\]
-
-In the case of \(\tau = 0.5\), the latter KL-divergence is symmetric in
-its first argument, and thus can be relatively well approximated by
-Pinsker's inequality:
-
-\[
-\KL_{Ber}(\nu_i||\nu_j) \geq 2(\mu_i - \tau)^2.
-\]
-
-This is of course equal to the Gaussian KL-divergence described before.
-This approximation, however, suffers for heavily for very small values
-of \(\mu_i\) and \(\tau\). In particular, the Bernoulli KL-divergence
-becomes asymmetric in its first argument as \(\tau \neq 0.5\). Thus, in
-contrast to the complexity measure \(H\) based on the Gaussian
-KL-divergence, a complexity measure based on the Bernoulli KL-divergence
-would evaluate two arms as differently difficult if their absolute
-distance to the threshold is the same, but they lie on different sides
-of the threshold.
-
-Thus similarly to how UCB algorithms in the cumulative regret setting
-have been extended to KL-UCB algorithms (compare Cappé et al., 2013),
-also the APT algorithm offers room for improvement. As a more explicit
-example of such adaptation, consider the case of Top-\(m\)
-identification described in Kaufmann et al. (2016). The authors develop
-a lower bound based on KL-divergence, and note that ``This
-information-theoretic lower bound permits to interpret the quantity
-\(H(\nu)\) {[}\ldots{}{]} as a subgaussian approximation''. Given that
-Bernoulli distributions with very small parameter values arise naturally
-in many applications, an improvement in this regard would be valuable.
-
-In what follows, we first examine in
-\autoref{chap:KullbackLeiblerPureExploration} how information theoretic
-quantities are employed in the best arm identification and Top-\(m\)
-problem as detailed in Kaufmann and Garivier (2016) and Kaufmann et al.
-(2016). Before introducing a new algorithm for the thresholding bandit
-problem based on Kullback-Leibler divergences in
-\autoref{sec:LikelihoodRatioForExponentialFamily}, we first describe the
-variance-based approaches in \autoref{sec:VarianceBasedAlgorithms}.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/KLApproximationComparison-1}
-
-}
-
-\caption{The approximation of the Bernoulli KL-divergence by the Gaussian KL-divergence works well if the second argument is equal to 0.5.
-Else we observe poor approximation in both value and symmetry.
-This becomes more obvious as the arguments move away from 0.5.}\label{fig:KLApproximationComparison}
-\end{figure}
-
-\section{\texorpdfstring{Information Theoretic Approaches to Pure
-Exploration Bandits
-\label{chap:KullbackLeiblerPureExploration}}{Information Theoretic Approaches to Pure Exploration Bandits }}\label{information-theoretic-approaches-to-pure-exploration-bandits}
-
-The previous chapter introduces the thresholding bandit problem as
-described in Locatelli et al. (2016), and with the APT strategy a first
-algorithm that is simple, yet order-optimal for large budgets. However,
-we end with the conclusion that a distance measure between the
-distributions and the threshold based on the Kullback-Leibler divergence
-might be more useful than the simple gap
-\(\Delta^2_i = (\mu_i - \tau_i)^2\) employed so far. Indeed, citing
-Kaufmann et al. (2016), we note that the complexity \(H\) used so far
-can be considered a sub-Gaussian approximation of a better complexity
-measure based on information theoretic measures like the
-Kullback-Leibler divergence.
-
-In order to give more intuition to why that is the case, and in what
-ways information theoretic measures can be introduced to measure the
-complexity of bandit problems, we now turn to Kaufmann et al. (2016) and
-Garivier and Kaufmann (2016). The latter describes a strategy based on
-Kullback-Leibler divergences for the best-arm identification problem,
-while the first derives complexity measures based on the divergence.
-Ideally, their work offers methods that can inform our work of extending
-the thresholding bandit problem. In what follows, we adopt the notation
-of Kaufmann et al. (2016) to ease a comparison with their arguments.
-
-\subsection{\texorpdfstring{Information Theoretic Complexity Measures in
-Top-\(m\) Problems
-\label{sec:KaufmannEtAl2016}}{Information Theoretic Complexity Measures in Top-m Problems }}\label{information-theoretic-complexity-measures-in-top-m-problems}
-
-Instead of the thresholding bandit problem, Kaufmann et al. (2016)
-consider the problem of identifying the best \(m\) out of \(K\) arms,
-that is, the top-\(m\) problem. They describe their bandit model \(\nu\)
-by \(K\) arms characterized by probability distributions \(\nu_a\),
-\(a \in \{1,...,K\}\), with mean \(\mu_a\). A learner picks at any time
-step \(t=1,2,...,\) an arm \(A_t \in \{1,...,K\}\) for which he observes
-the independent reward \(Z_{t} \sim \nu_{A_t}\). The learner aims to
-find the \(m\) out of \(K\) arms with the largest expected reward. This
-set of arm indexes is denoted by \(\mathcal{S}_m^*\). Kaufmann et al.
-write the means \((\mu_{1}, ..., \mu_{K})\) sorted in decreasing order
-as the K-tuple \((\mu_{[1]}, ..., \mu_{[K]})\). Based on this, they
-require that \(\mu_{[m]} > \mu_{[m+1]}\) such that the solution
-\(\mathcal{S}_m^*\) is unique. The class of bandit problems \(\nu\) for
-which the latter condition holds is called \(\mathcal{M}_m\) by Kaufmann
-et al. At the end of the sampling procedure, after \(T\) samples
-(denoted by \(\tau\) in Kaufmann et al.) the learner is required to
-return a classification \(\hat{\mathcal{S}}_m\). This classification is
-then evaluated by the loss function
-\(\mathcal{L}(T) = \mathbb{I}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m)\).
-This binary loss is similar to the loss in the thresholding bandit. We
-can now define a strategy of the learner as
-\(\mathcal{A} = ((A_t), T, \hat{\mathcal{S}}_m)\): The strategy defines
-how an arm is chosen, how many samples are observed, and how the arms
-are eventually classified.
-
-When introducing the thresholding bandit setting, we did not mention the
-fact that the budget \(T\) does not need to be fixed upfront. Indeed,
-the setting in which the budget is \emph{not} fixed upfront might be
-more popular among the best arm identification and top-\(m\) literature.
-This setting is called \emph{fixed confidence}, while the setting we
-considered so far is called \emph{fixed budget}. In the fixed budget
-setting, we run algorithms for \(T\) samples and then compare them based
-on their expected loss,
-\(\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m) =: p_t(\nu)\)
-as we have seen in \(\autoref{sec:Setup}\). Alternatively, consider a
-\(\delta\)-PAC strategy \(\mathcal{A}(\delta)\)for which it holds for
-every problem \(\nu \in \mathcal{M}_m\) that the classification holds at
-least with confidence level \(1-\delta\), that is,
-\(\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta\). The
-strategy has to achieve this level of confidence in its prediction
-before it is allowed to stop sampling. This is the fixed confidence
-case, in which the budget \(T\) is no longer fixed upfront, but turns
-into a random variable. Algorithms are then compared by their expected
-number of draws \(\mathbb{E}_{\nu}[T_{\delta}]\) and we prefer those
-which achieve the confidence level \(1-\delta\) with a smaller expected
-budget.
-
-In the fixed confidence setting, a family of strategies
-\(A = (\mathcal{A}(\delta))_{\delta \in (0,1)}\) is called PAC if for
-every \(\delta\), \(\mathcal{A}(\delta)\) is \(\delta\)-PAC. On the
-other hand, in the fixed budget setting, a family of strategies
-\(A = (\mathcal{A}(t))_{t \in \mathbb{N}}\) is called consistent if
-\(p_t(\nu) \rightarrow 0\) as \(t \rightarrow \infty\) for every problem
-\(\nu \in \mathcal{M}_m\).
-
-Given this setup, we can now follow the arguments of Kaufmann et al.
-(2016) to derive complexity measures for the top-\(m\) problem. As
-alluded to earlier, these complexity measures will rely on the
-KL-divergence in contrast to the complexity \(H\) used by Locatelli et
-al. (2016). When discussing \(H\), its motivation is that it represents
-the difficulty of the problem by measuring the distance between arms and
-the threshold. Instead, Kaufmann et al. approach complexity by how many
-samples (what error probability) one will need in the fixed confidence
-(fixed budget) setting. In order to arrive at their new measure of
-complexity, it makes sense to first follow their arguments to a general
-lower bound on the sample complexity \(\mathbb{E}_{\nu}[\tau]\) which is
-given in their Theorem 4:
-
-\begin{theorem}[Theorem 4, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem4}
-Let $\nu \in \mathcal{M}_m$, where $\mathcal{M}_m$ is the set of uniquely identifiable bandit models described above.
-Assume that $\mathcal{P}$ satisfies the continuity conditions in Assumption 3.
-Any $\delta$-PAC algorithm on $\mathcal{M}_m$ satisfies, for $\delta \leq 0.15$:
-
-\begin{equation*}
-\mathbb{E}_{\nu}[\tau] \geq \Big[ \sum_{a \in \mathcal{S}^*_m} \frac{1}{\KL(\nu_a || \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}^*_m} \frac{1}{\KL(\nu_a || \nu_{[m]})} \Big] \der(1-\delta, \delta),
-\end{equation*}
-\end{theorem}
-
-To prove this statement for a given \(\delta\)-PAC algorithm
-\(\mathcal{A}\), we assume certain continuity conditions (compare
-Kaufmann et al. (2016)) under which there exists for every arm
-\(a \in \{1, \dots, K\}\) an alternative model
-\(\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)\).
-In this alternative model, in accordance with the continuity conditions,
-only arm \(a\) is modified. After the modification, the arm
-\(\nu_{m+1}\) is now closer to \(\nu_a\) as measured by the
-Kullback-Leibler divergence than \(\nu_a'\) is to \(\nu_a\), if
-\(\mu_a > \mu_{m+1}\) (consequently, \(\mu_a' < \mu_{m+1}\)). On the
-other hand, if \(\mu_a < \mu_{m}\), then \(\nu_a'\) will be moved away
-from \(\nu_a\) just enough so that \(\nu_a\) is closer to \(\nu_m\) than
-to \(\nu_a'\) (consequently, \(\mu_a' > \mu_m\)). These changes in
-distribution make the original set of optimal arms, \(\{1,\dots,m\}\),
-no longer optimal under the alternative model \(\nu'\). To compare this
-to the thresholding bandit problem, assume that arms \(\nu_{m}\) and
-\(\nu_{m+1}\) indirectly define a threshold
-\(\tau \in (\mu_{m+1},\mu_m)\). Then, by creating an alternative problem
-as described here, we flip arm \(a\) around the implied threshold
-\(\tau\) (compare the lower bound proof in \autoref{sec:AppendixAPTLB}).
-
-Given the strategy returns \(\hat{S}_m\), we know that for the event
-\(\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})\) (which is element of the
-\(\sigma\)-Algebra \(\mathcal{F}_{T}\) induced by the stopping time
-\(T\)), that \(\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta\) and
-\(\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta\) (because fixed confidence
-\(\delta\)!). To give the lower bound on the expected number of samples,
-\(\mathbb{E}_{\nu}[\tau]\), we employ the general Lemma given by the
-authors for such changes in distribution in bandit models.
-
-\begin{lemma}[Lemma 1, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma1}
-Let $\nu$ and $\nu'$ be two bandit models with $K$ arms such that for all $a$, the distributions $\nu_a$ and $\nu_a'$ are mutually absolutely continuous.
-For any almost-surely finite stopping time $\sigma$ with respect to $(\mathcal{F}_t)$,
-
-\begin{equation*}
-\sum_{a=1}^{K} \mathbb{E}_{\nu} [N_a(\sigma)] \KL(\nu_a|| \nu_a') \geq \sup_{\mathcal{E} \in \mathcal{F}_{\sigma}} \der (\mathbb{P}_{\nu}(\mathcal{E}), \mathbb{P}_{\nu'}(\mathcal{E})).
-\end{equation*}
-\end{lemma}
-
-We apply this Lemma directly on the expected number of draws for each
-arm, \(\mathbb{E}_{\nu}[N_a]\). For each arm \(a\), we thus have
-\(\KL(\nu_a, \nu_a') \mathbb{E}_{\nu}[N_a] \geq d(1-\delta, \delta)\).
-Using the definition of the alternative model above, we get for every
-small but fixed \(\alpha > 0\), every arm \(a \in \{1, \dots, K\}\) and
-\(b \in \{m+1, \dots, K\}\):
-
-\begin{equation*}
-\mathbb{E}_{\nu}[N_a] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_a || \nu_{m+1}) + \alpha} \quad \text{and} \quad \mathbb{E}_{\nu}[N_b] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_b || \nu_{m}) + \alpha}.
-\end{equation*}
-
-Let \(\alpha \to 0\), sum the individual arms' bounds to get the bound
-on the overall number of draws:
-
-\begin{equation*}
-\mathbb{E}_{\nu}[T] = \sum_{a=1}^K \mathbb{E}_{\nu}[N_a] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m]})} \Big) \der(1-\delta, \delta)
-\end{equation*}
-
-Given that we will be naturally interested in either very high or very
-low confidence of our algorithm, that is, \(P_\nu(\mathcal{E})\) is
-either close to 0 or 1, it is possible to use the following
-approximation to the binary relative entropy given in Kaufmann et al.
-(2016):
-
-\begin{equation}\label{bre_approx}
-\forall x \in [0,1], \quad \der(x,1-x) = \der(1-x,x) \geq \log \frac{1}{2.4x}.
-\end{equation}
-
-This allows us to write the lower bound on the expected stopping time
-as:
-
-\begin{equation*}
-\mathbb{E}_{\nu}[T] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
-\end{equation*}
-
-Given this lower bound, it is clear that the complexity of the top-\(m\)
-problem can be lower bounded by the KL-divergence between arms and the
-implied threshold between the \(m\)-th best arm and the \((m+1)\)-th
-best arm. The latter gives a lower bound on the effort (in terms of
-expected number of samples) required to achieve a certain confidence
-level, where a problem that requires a larger effort is described as
-more complex. Indeed, in the case of fixed confidence problems, Kaufmann
-et al. (2016) describe problems as having a larger \emph{sampling
-complexity}.
-
-Following Kaufmann et al. (2016), we define the complexity
-\(\kappa_C(\nu)\) in the fixed confidence setting as
-
-\begin{equation}
-\kappa_C(\nu) = \inf_{A \, \text{PAC}} \limsup_{\delta \to 0} \frac{\mathbb{E}_{\nu}[T_{\delta}]}{\log \frac{1}{\delta}}. \label{eq:KappaC}
-\end{equation}
-
-This definition makes sense if we consider the fact that the confidence
-level \(\delta\) is experimenter chosen and thus not relevant in
-describing the complexity. Thus, by including \(\log(1/\delta)\)
-explicitly in \eqref{eq:KappaC}, we get rid of the confidence term in
-the lower bound on \(\mathbb{E}_{\nu}[T]\) after plugging it into
-\eqref{eq:KappaC}. We arrive at the lower bound on the complexity
-measure given in Kaufmann et al. (2016):
-
-\begin{equation*}
-\kappa_C(\nu) \geq \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a || \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a || \nu_{[m]})}
-\end{equation*}
-
-Given this description, we would expect that a complexity measure in a
-fixed confidence thresholding bandit probem might involve replacing
-\(\mu_{[m]}\) and \(\mu_{[m+1]}\) by the actual threshold \(\tau\) that
-divides the group above the threshold from the group below the
-threshold. But given the setting in Locatelli et al. (2016), we are
-mainly interested in complexity measures and algorithms for the fixed
-budget problem. The results of Kaufmann et al. (2016) are more limited
-for this case. While the authors are able to provide a bound on their
-complexity measure in the fixed budget case, it only applies to the case
-of \emph{two-armed} bandit models.
-
-Consider a consistent fixed budget strategy \(\mathcal{A}\)
-(\(p_t(\nu)\) tends to zero as \(t \rightarrow \infty\)), and define the
-complexity in the fixed budget setting as follows:
-
-\begin{equation}
-\kappa_B(\nu) = \inf_{A \, \text{consistent}} \Big(\limsup_{t \to \infty} - \frac{1}{t} \log p_t(\nu)\Big)^{-1}.
-\end{equation}
-
-While we included the experimenter-fixed \(\delta\) in the definition of
-\(\kappa_C\), we now include the fixed \(T\) in the definition of
-\(\kappa_B\) to disregard it in the complexity measure after plugging in
-the lower bound on \(p_t(\nu)\). The resulting lower bound given in
-Theorem 12 of Kaufmann et al. (2016):
-
-\begin{theorem}[Theorem 12, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem12}
-Let $\nu = (\nu_1, \nu_2)$ be a two-armed bandit model such that $\mu_1 > \mu_2$. In the fixed budget setting, any consistent algorithm satisfies:
-
-\begin{equation*}
-\limsup_{t \to \infty} - \frac{1}{t} \log p_t(\nu) \leq \inf_{(\nu_1', \nu_2') \in \mathcal{M}: \mu_1' < \mu_2'} \max \big\{\KL(\nu_1' || \nu_1), \KL(\nu_2' || \nu_2)\big\}
-\end{equation*}
-\end{theorem}
-
-For a proof, consider first the two different bandit models, \(\nu\) and
-\(\nu'\), where we fix w.l.o.g. \(a^* = 1\) as the best arm in \(\nu\),
-while \(a^* = 2\) in \(\nu'\). We require the algorithm \(\mathcal{A}\)
-to be consistent for both problems. Since we are in the fixed budget
-setting, the stopping time is fixed at \(T = t\). The correct decision
-differs between the two problems, and we focus on the event
-\(A = (\hat{S}_1 = 1)\). Now, we can apply Lemma 1 from Kaufmann et al.
-(2016) as before, as it gives a measure of how different two bandit
-models are (it bounds the change in distribution). Here, we want to know
-how different \(\nu\) is from \(\nu'\), and, given we have only two
-arms,
-
-\begin{equation*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1'|| \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2'|| \nu_2) \geq \der(\mathbb{P}_{\nu'}(A),\mathbb{P}_{\nu}(A)))
-\end{equation*}
-
-The expectations were chosen with respect to \(\nu'\) in order to allow
-for the following: We have \(p_t(\nu) = 1 - \mathbb{P}_{\nu}(A)\) and
-\(p_t(\nu') = \mathbb{P}_{\nu'}(A)\) (since \(A\) is wrong in \(\nu'\)).
-But since algorithm \(\mathcal{A}\) is consistent for both \(\nu\) and
-\(\nu'\), we know that there should exist some number of samples such
-that the probability of event \(A\) is bigger in setting \(\nu\) (where
-it is the correct decision) than in setting \(\nu'\) (where this would
-be a wrong decision and failure). Thus, for every \(\epsilon > 0\),
-there exists \(t_0(\epsilon)\) such that for all
-\(t \geq t_0(\epsilon)\),
-\(\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)\).
-Consequently, if we plug in the bound of \(\epsilon\) for
-\(\mathbb{P}_{\nu'}(A)\), then
-
-\begin{align*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1' || \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2' || \nu_2) & \geq \der(\epsilon,1-p_t(\nu))) \\
-& = \epsilon \log \frac{\epsilon}{1-p_t(\nu)} + (1-\epsilon) \log \frac{1-\epsilon}{p_t(\nu)} \\
-& \geq (1-\epsilon) \log \frac{1-\epsilon}{p_t(\nu)} + \epsilon \log \epsilon.
-\end{align*}
-
-Let \(\epsilon\) go to zero so that
-
-\begin{align*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1' || \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2' || \nu_2)
-& \geq \log \frac{1}{p_t(\nu)} = -\log p_t(\nu).
-\end{align*}
-
-Dividing both sides by \(t\) and taking the limsup, we arrive at
-
-\begin{align*}
-\limsup_{t \to \infty} - \frac{1}{t} \log p_t(\nu)
-& \leq \limsup_{t \to 0} \frac{1}{t} \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)] \KL(\nu_a' || \nu_a) \\
-& \leq \max_{a=1,2} \KL(\nu_a' || \nu_a),
-\end{align*}
-
-where the last line follows from the fact that the
-\(\frac{1}{t} \sum_{a=1}^2 \mathbb{E}_{\nu'}[N_a(t)]\) part creates a
-weighted average of the two divergences \(\KL(\nu_a', \nu_a)\). As noted
-in Kaufmann et al. (2016), one arrives at the final result by choosing
-\(\mu_1'\), \(\mu_2'\) so that
-\(| \KL(\nu_1', \nu_1) - \KL(\nu_2', \nu_2) |\) is as small as possible.
-
-As noted by Kaufmann et al. (2016), the advantage of this lower bound is
-that it makes the complexity in the fixed confidence and the fixed
-budget setting directly comparable. The disadvantage of course being
-that the result only holds for two-armed models. While the authors are
-not able to derive directly comparable lower bounds for the top-\(m\)
-case, they derive a first lower bound in the Gaussian case with equal
-variances, which we describe shortly in the appendix in
-\autoref{sec:KaufmannLBTopMGaussian}.
-
-Before we discuss algorithms given in Kaufmann et al. (2016) that match
-the lower bounds, we show how lower bounds can be derived very similarly
-for the fixed budget thresholding problem.
-
-\subsubsection{\texorpdfstring{Lower Bound for Fixed Budget Thresholding
-Problem
-\label{sec:LBTBP}}{Lower Bound for Fixed Budget Thresholding Problem }}\label{lower-bound-for-fixed-budget-thresholding-problem}
-
-In order to derive a bound for the fixed budget problem, Kaufmann et al.
-(2016) have focused on the setting with two arms which is the most
-simple version of the top-\(m\) problem. Less than two arms do not make
-sense, since the single arm is by definition the best arm. In the case
-of the thresholding bandit, however, a single-armed problem makes still
-at least limited sense in that we still have to classify this arm
-correctly with respect to the threshold. Thus, we can show the following
-corollary which gives a bound on the complexity of the single-armed
-thresholding bandit.
-
-\begin{corollary}
-Let $\nu = \nu_1$ be a one-armed thresholding bandit model where $\tau$ is the threshold fixed upfront.
-Let $\nu$ be from the univariate exponential family of distributions such that $\nu_1$ can be parameterized by its mean, $\mu_1$, and the Kullback-Leibler divergence between distributions $\nu_1$ and $\nu_1'$ can be written as $\KL(\nu_1', \nu_1) = \KL(\mu_1', \mu_1)$.
-In the fixed budget setting, any consistent algorithm ($p_t(\nu) \rightarrow 0$ as $t \rightarrow \infty$) satisfies:
-
-$$
-- \frac{1}{t} \log p_t(\nu) \leq \KL(\tau || \mu_1)
-$$
-\end{corollary}
-
-\label{corollary:LB1TBP}
-
-This is basically the Chernoff-Stein Lemma for the hypothesis test of
-two alternatives (compare chapter 11 in Cover and Thomas, 2006, or
-\autoref{theorem:ChernoffStein}). We arrive at this result as the
-one-armed bandit does not require sequential sampling: The single arm
-receives all samples. \(\mathbb{E}_{\nu'}[N_1(t)]\) is not a random
-variable but equals \(T\).
-
-But as we see in the following corollary, we can extend the lower bound
-to the \(K\)-armed fixed budget thresholding bandit problem, which
-stands in contrast to the fact that for the top-\(m\) problem, it is
-only possible to show the lower bound for two arms. The result is based
-on an alternative setting \(\nu'\) in which all arms have means
-\(\mu' = \tau\) such that their expected number of pulls corresponds to
-uniform sampling, \(\mathbb{E}_{\nu'}[N_i(t)] = T/K\).
-
-\begin{corollary}
-Let $\nu = (\nu_1, ..., \nu_K)$ be a $K$-armed thresholding bandit problem in which $\tau$ is the threshold fixed upfront.
-For $i \in \{1,...,K\}$, let $\nu_i$ be from the univariate exponential family of distributions such that $\nu_i$ can be parameterized by its mean, $\mu_i$, and the Kullback-Leibler divergence between distributions $\nu_i$ and $\nu_i'$ can be written as $\KL(\nu_i, \nu_i') = \KL(\mu_i, \mu_i')$.
-In the fixed budget setting, any consistent algorithm satisfies:
-
-$$
-\limsup_{t \rightarrow \infty} -\frac{1}{t} \log p_t(\nu) \leq \max_{a \in \{1,...,K\}} \KL(\tau || \mu_a)
-$$
-
-or
-
-$$
-- \frac{1}{t} \log p_t(\nu) \leq \frac{1}{K}\sum_{i=1}^{K} \KL(\tau || \mu_i),
-$$
-\end{corollary}
-
-\label{corollary:LBKTBP}
-
-We present the proofs of \autoref{sec:LBTBP} in the appendix in
-\autoref{sec:corollaryLBTBPproof}. Corresponding to the complexity
-measures defined in equation \((1)\) of Kaufmann et al. (2016), we can
-define the complexity \(\kappa_{TBP}(\nu)\) in the thresholding bandit
-problem and lower bound it:
-
-\[
-\kappa_{TBP}(\nu) = \inf_{A \text{ consistent}} \Big(\limsup_{t \rightarrow \infty} - \frac{1}{t} \log p_t(\nu)\Big)^{-1} \geq K \Big(\sum_{i=1}^{K} \KL(\tau||\mu_i)\Big)^{-1}
-\]
-
-\subsubsection{\texorpdfstring{Strategies Matching the Top-\(m\) Lower
-Bound}{Strategies Matching the Top-m Lower Bound}}\label{strategies-matching-the-top-m-lower-bound}
-
-Kaufmann et al. (2016) do not present algorithms matching the lower
-bound of Theorem \ref{theorem:KaufmannEtAlTheorem17}. They do consider
-algorithms that connect to Theorem \ref{theorem:KaufmannEtAlTheorem4}
-and Theorem \ref{theorem:KaufmannEtAlTheorem12}. Given that we aim to
-extend the fixed budget thresholding bandit problem, we are most
-interested in the matching strategies for Theorem
-\ref{theorem:KaufmannEtAlTheorem12}. However, given that this lower
-bound applies only to two-armed bandits, the algorithms proposed by
-Kaufmann et al. (2016) are of limited practical interest. Furthermore,
-the proposed strategies require knowledge that is in general not
-available upfront: For Gaussian distributions, the knowledge of the
-(potentially different) variance is assumed which enables a strategy
-that pulls each arm proportional to its variance.
-
-Even more difficult are the assumptions in the case of Bernoulli
-two-armed bandit models: The proposed algorithm requires knowledge about
-the true parameters of the distributions. That this limits the practical
-interest is also noted by the authors of Kaufmann et al. (2016). Thus,
-they suggest to use uniform sampling strategies in the case of two-armed
-Bernoulli bandits, and show that there is not much to be lost by doing
-so.
-
-Thus, Kaufmann et al. (2016) joins other papers like Audibert et al.
-(2010) and Kaufmann and Kalyanakrishnan (2013) which struggle to find
-matching strategies in the fixed budget setting that do not rely on
-knowledge of parameters or the complexity of the problem.
-
-In contrast, Kaufmann et al. (2016) are able to show that their
-complexity measure derived for the fixed confidence setting,
-\(\kappa_C(\nu)\), can be upper-bounded using the bound given for the
-KL-LUCB algorithm in Kaufmann and Kalyanakrishnan (2013). In the case of
-exponential family bandits, the complexity \(\kappa_C(\nu)\) is bounded
-as given in equation (6) in Kaufmann et al. (2016):
-
-\begin{equation*}
-\sum_{a \in S^*_m} \frac{1}{\KL(\theta_a || \theta_{[m+1]})} + \sum_{a \notin S^*_m} \frac{1}{\KL(\theta_a || \theta_{[m]})} \leq \kappa_C(\nu) \leq 24 \min_{\theta \in [\theta_{[m+1]},\theta_{[m]}]} \sum_{a=1}^{K} \frac{1}{\KL^*(\theta_a || \theta)},
-\end{equation*}
-
-where again we write with slight abuse of notation
-\(\KL(\theta || \theta') = \KL(\nu_{\theta}|| \nu_{\theta'})\) for
-\((\theta, \theta') \in \Theta^2\) as the shorthand for the
-KL-divergence of two distributions from the exponential family
-parameterized by \(\theta\) and \(\theta'\) respectively.
-\(\KL^*(\theta || \theta') = \KL(\theta^* || \theta)\) is the Chernoff
-information between the two distributions, where \(\theta^*\) is chosen
-so that \(\KL(\theta^* || \theta) = \KL(\theta^* || \theta')\).
-
-\subsection{\texorpdfstring{Information Theoretic Approach to Best Arm
-Identification
-\label{sec:OptimalBestArmIdentification}}{Information Theoretic Approach to Best Arm Identification }}\label{information-theoretic-approach-to-best-arm-identification}
-
-Instead of discussing the KL-LUCB algorithm for the fixed confidence
-top-\(m\) problem, we shift our focus onto the fixed confidence best arm
-identification problem, as discussed in Garivier and Kaufmann (2016).
-The authors also derive a lower bound on the sample complexity using the
-Lemma \autoref{theorem:KaufmannEtAlLemma1}. Furthermore, they propose a
-matching strategy for \(K \geq 2\) arms.
-
-The setting differs slightly from the setting considered in Kaufmann et
-al. (2016). In particular, Garivier and Kaufmann (2016) focus on
-distributions \(\nu_{\theta}\) from the univariate canonical exponential
-family of distributions, which can be parameterized by their mean
-\(\mu\), and thus can be written as \(\nu_{\mu}\); as before, we
-simplify the notation of the KL-divergence for these distributions to
-\(\KL(\nu || \nu') = \KL(\mu || \mu')\).
-
-Furthermore, if we let \(\mathcal{S}\) to be a set of bandit models with
-\(K\) distributions each, then each model is fully defined by a vector
-\(\bm{\mu} = (\mu_1, \dots, \mu_K)\). Assume that every
-\(\bm{\mu} \in \mathcal{S}\) has a unique maximum given by
-\(a^*(\bm{\mu})\) such that
-\(\mu_{a^*} > \max_{a \neq a^*(\bm{\mu})} \mu_a\). In order to fix the
-confidence \(1-\delta\), we specify the risk \(\delta\). Similar to the
-top-\(m\) case considered before, strategies corresponding to this risk
-are called \(\delta\)-PAC if for every \(\bm{\mu} \in \mathcal{S}\), the
-strategy ends surely after a finite number of samples,
-\(\mathbb{P}_{\bm{\mu}}(T_{\delta} < \infty) = 1\), and the error
-probability is at least as small as the fixed risk level,
-\(\mathbb{P}_{\bm{\mu}}(\hat{a}_{T_{\delta}} \neq a^*) \leq \delta\). In
-order to derive the lower bound on the expected number of samples
-\(\mathbb{E}[T]\) through a change in distributions, we introduce the
-set of alternative problems for which the optimal arm is different from
-\(\bm{\mu}\):
-
-\begin{equation*}
-\text{Alt}(\bm{\mu}) := \{\bm{\lambda} \in \mathcal{S}: a^*(\bm{\lambda}) \neq a^*(\bm{\mu})\},
-\end{equation*}
-
-where \(\bm{\lambda}\) is the vector of means defining the distributions
-of the alternative problem. Lastly, we have the set of probability
-distributions on the arms \(\{1,...,K\}\):
-\(\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}\). Each
-\(w_i\) corresponds to the fraction of overall samples that arm \(i\)
-receives. We now state the lower bound:
-
-\begin{theorem}[Theorem 1, Garivier and Kaufmann, 2016] \label{theorem:GarivierKaufmannTheorem1}
-Let $\delta \in (0,1)$. For any $\delta$-PAC strategy and any bandit model $\bm{\mu} \in \mathcal{S}$,
-
-\begin{equation*}
-\mathbb{E}_{\bm{\mu}} [T_{\delta}] \geq T^*(\bm{\mu}) \text{\em{d}}(\delta,1-\delta),
-\end{equation*}
-
-where
-
-\begin{equation} \label{eq:GarivierKaufmann_Theorem1_Game}
-T^*(\bm{\mu})^{-1} := \sup_{w \in \Sigma_K} \inf_{\bm{\lambda} \in \text{\em{Alt}}(\bm{\mu})} \left( \sum_{a=1}^K w_a \text{\em{KL}}(\mu_a|| \lambda_a)\right).
-\end{equation}
-\end{theorem}
-
-We see that the two bounds given in Theorem
-\ref{theorem:KaufmannEtAlTheorem4} and Theorem
-\ref{theorem:GarivierKaufmannTheorem1} on the sample complexity differ
-only in the way in which they sum the Kullback-Leibler divergences over
-the \(K\) arms. In contrast to Theorem
-\ref{theorem:KaufmannEtAlTheorem4}, here the contribution of each arm
-through its KL-divergence is weighted. The difference is that while we
-were able to clearly describe the change of distribution in the
-top-\(m\) case for each arm -- we specified an alternative model for
-each arm that yields a new set of \(m\) optimal arms -- we now consider
-all alternative models that yield a different best arm than the model
-\(\bm{\mu}\). In the previous theorem, we sum over the complexity of
-each individual arm, since the change in distribution only affects one
-arm at a time, thus leading to a KL-divergence of 0 for the other arms
-while still changing the optimal set. Now, we consider all instances of
-alternative models \(\bm{\lambda}\), and thus also those in which
-several arms are modified (and thus have a KL-divergence unequal 0 in
-the result of Lemma 1).
-
-To proof Theorem \ref{theorem:GarivierKaufmannTheorem1}, we let
-\(\delta \in (0,1)\), \(\bm{\mu} \in \mathcal{S}\), and only consider
-\(\delta\)-PAC strategies. As before, \(N_a(t)\) describes the random
-number of pulls of arm \(a\) until time \(t\), for all \(t\geq 1\).
-Again, Lemma \ref{theorem:KaufmannEtAlLemma1} states how the risk
-\(\delta\) relates to the expected number of draws of each arm given two
-models which differ in their optimal arm. How much the two models differ
-is evaluated based on the KL-divergence for each pair of arms:
-
-\begin{equation*}
-\forall \lambda \in \mathcal{S}: a^*(\lambda) \neq a^*(\mu), \sum_{a=1}^K \KL(\mu_a,\lambda_a)\mathbb{E}_{\bm{\mu}}[N_a(T_{\delta})] \geq \d(\delta, 1- \delta).
-\end{equation*}
-
-As mentioned, we now do not consider a specific alternative for each
-arm, but instead look at the infimum over all the possible alternatives,
-and use the fact that
-\(\mathbb{E}_{\bm{\mu}}[T_{\delta}] = \sum_{a=1}^K \mathbb{E}_{\bm{\mu}}[N_a(T_{\delta})]\):
-
-\begin{align*}
-\der(\delta, 1-\delta) & \leq \inf_{\lambda \in \text{Alt}(\bm{\mu})} \mathbb{E}_{\bm{\mu}}[T_{\delta}] \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[T_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
-& = \mathbb{E}_{\bm{\mu}}[T_{\delta}] \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K \frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[T_{\delta}]} \KL(\mu_a, \lambda_a)\Big) \\
-& \leq \mathbb{E}_{\bm{\mu}}[T_{\delta}] \sup_{w \in \Sigma_K} \inf_{\lambda \in \text{Alt}(\bm{\mu})} \Big(\sum_{a=1}^K w_a \KL(\mu_a, \lambda_a)\Big).
-\end{align*}
-
-As stated in Garivier and Kaufmann (2016), the term
-\(\frac{\mathbb{E}_{\bm{\mu}}[N_a]}{\mathbb{E}_{\mu}[T_{\delta}]}\)
-gives the fraction of draws each arm receives. This value, however,
-depends on the used algorithm. To make it hold for any \(\delta\)-PAC
-algorithm, it is replaced by the supremum over \(\Sigma_K\), which is
-the distribution over these fractions for any \(\mathcal{A}\), that is,
-for any \(\delta\)-PAC strategy.
-
-This lower bound can be interpreted as a minimax game\footnote{See the
-  presentation by Aurélien Garivier at COLT 2016:
-  \url{https://youtu.be/eLyrrYqJlkE}}, where the experimenter has to
-choose the share of samples he attributes to each arm in a way that is
-optimal given that nature will respond and choose the most difficult
-alternative model given his weights. Thus, to make the lower bound
-practical, it is a matter of finding the optimal weights
-\(w^*(\bm{\mu})\). This step did not occur in the lower bound for the
-top-\(m\) problem since the alternative models were specified by
-changing the distribution of one arm with respect to the ``border''
-between the two groups of arms.
-
-The existence of the optimal weights suggests an algorithm that keeps
-track of the share of samples that is attributed to each arm and makes
-sure that it stays close to the optimum until some decision rule assures
-that the \(\delta\)-PAC condition is fulfilled.
-
-Indeed, the optimal weights will lead to a sampling structure in which
-arms are drawn such that their individual probabilities of error stay at
-the same level. An arm more distant from the optimal arm in terms of
-Kullback-Leibler divergence should receive a smaller share of the
-samples to achieve the same error probability as an arm closer to the
-optimal arm.
-
-This is what happens when we look for proportions \(w \in \Sigma_K\)
-that minimize the cost from a change in distributions, that is, the term
-\(F(\bm{\mu}, \bm{w}) = \inf_{\bm{\lambda} \in \text{Alt}(\bm{\mu})} \Big(\sum_{a= 1}^K w_a \KL(\mu_a, \lambda_a)\Big)\).
-In the proof of Lemma 3 of Garivier and Kaufmann, it is shown that
-nature, selecting the alternative model \(\bm{\lambda}\), will always
-pick an alternative model in which only a single arm \(a\) is changed
-such that \(\lambda_a > \lambda_1\) since
-
-\begin{align*}
-T^*(\bm{\mu})^{-1} & = \sup_{w \in \Sigma_K} \min_{a \neq 1} \inf_{\bm{\lambda} \in \mathcal{S}: \lambda_a > \lambda_1} \sum_{a=1}^K w_a \KL(\mu_a, \lambda_a)  \\
-& = \sup_{w \in \Sigma_K} \min_{a \neq 1} \inf_{\bm{\lambda}: \lambda_a \geq \lambda_1} [w_1 \KL(\mu_1, \lambda_1)+w_a \KL(\mu_a, \lambda_a)]. \Alignyesnumber\label{eqn:ComplexityTrackStopStrategy}
-\end{align*}
-
-Consequently, \(w\) will be chosen so as to minimize \(T^*(\bm{\mu})\)
-no matter which arm \(a\) was picked. It is a minimax game, so the ideal
-solution is to keep for each arm \(a \neq 1\) the term
-\(w_1 \KL(\mu_1, \lambda_1) + w_a \KL(\mu_a, \lambda_a)\) at the same
-level. Garivier and Kaufmann show that this can be written in terms of
-the Jenson-Shannon divergence, defined for every \(\alpha \in [0,1]\) as
-
-\begin{equation*}
-I_{\alpha}(\mu_1, \mu_2) := \alpha \KL(\mu_1 || \alpha \mu_1 + (1-\alpha) \mu_2) + (1-\alpha) \KL(\mu_2 || \alpha \mu_1 + (1-\alpha) \mu_2).
-\end{equation*}
-
-Using this notation, the optimal proportions can be written as
-
-\begin{equation*}
-w^*(\bm{\mu}) = \arg \max_{w \in \Sigma_K} \min_{a \neq 1} (w_1 + w_a) I_{\frac{w_1}{w_1+w_a}}(\mu_1, \mu_a)
-\end{equation*}
-
-which let's us furthermore conclude that these quantities are equal for
-all \(a,b \in \{2,\dots, K\}\) with
-
-\begin{equation*}
-(w_1^* + w_a^*) I_{\frac{w_1^*}{w_1^*+w_a^*}}(\mu_1, \mu_a) = (w_1^* + w_b^*) I_{\frac{w_1^*}{w_1^*+w_b^*}}(\mu_1, \mu_b),
-\end{equation*}
-
-which is simply the statement in Lemma 4 of Garivier and Kaufmann
-(2016).
-
-And so by assuring the reader that there are ways to compute \(w_a^*\)
-and \(T^*\) given \(\bm{\mu}\) (see chapter 2.2 in Garivier and Kaufmann
-(2016)), we can now introduce the \emph{Track-and-Stop} strategy given
-in Garivier and Kaufmann (2016) that is able to match the lower bound.
-The main idea of the \emph{Track-and-Stop} algorithm is now to keep
-track of the optimal shares for each arm by equalizing the error
-probabilies for each arm.
-
-When going from theory to algorithm, the obvious problem is that we no
-longer know the true parameters \(\bm{\mu}\) and cannot calculate the
-optimal weights. Instead, we have to estimate the maximum likelihood
-estimates \(\hat{\mu}(t) = (\hat{\mu}_1(t), \dots, \hat{\mu}_K(t))\) of
-the true mean at the current round \(t\) and need to base our sample
-weights on them. It is however problematic to rely on the sample means
-as we are inherently unsure about them. And so wrong estimates, which
-naturally occur most easily in the beginning when not many samples have
-been pulled, are prone to lead to wrong weights. Thus, if a wrong
-estimate \(\hat{\mu}_a\) for arm \(a\) leads to a small weight \(w_a\),
-then after a few more rounds neither the estimate nor the weight will be
-correct. Thus, Kaufmann and Garivier conclude that ``a naive plug-in
-sampling rule sometimes fails''. They propose to enforce a certain
-minimum level of exploration to ensure that arms that erroneously
-received a very small weight will be further explored regardless.
-
-A very intuitive solution to this problem is proposed in Lemma 8 of
-Garivier and Kaufmann (2016) with the \(D-Tracking\) rule. Whenever some
-arm has received a very small number of pulls \(N_a(t)\) given the
-number of iterations \(t\) so far, and the number of arms \(K\) that
-have to share the samples, pull the arm that has received the smallest
-amount of samples so far. Else, pull the arm whose number of pulls so
-far \(N_a(t)\) is the farthest away from what its optimal share
-\(t\cdot w^*_a(\hat{\bm{\mu}}(t))\) would be. Given this sampling rule,
-the authors can show in their Proposition 9 that the empirical
-proportion of draws converges in probability to the optimal weights
-given the true means.
-
-When combining this sampling rule with an appropriate stopping rule, the
-authors are able to prove in Theorem 14 an upper bound on the expected
-sampling complexity \(\mathbb{E}_{\mu}[T_{\delta}]\). The stopping rule
-ensures that the algorithm explores sufficiently to promise a risk
-smaller than \(\delta\), while stopping as soon as possible. Given that
-the sampling rule is independent of this stopping rule, the rule boils
-down to a statistical test at every iteration and thus is a sequential
-test based on the current estimate of \(\hat{\bm{\mu}}\). Chernoff's
-Stopping Rule proposed in Garivier and Kaufmann (2016) calculates for
-each arm \(a\in \{1,...K\}\) the Generalized Likelihood Ratio statistic
-with every arm \(b \in \mathcal{A}^{\setminus a}\), which for
-\(\hat{\mu}_a(t) \geq \hat{\mu}_b(t)\) can be written as
-
-\begin{equation*}
-Z_{a,b}(t) = - Z_{b,a} = N_a(t) \KL(\hat{\mu}_a(t) || \hat{\mu}_{a,b}(t)) + N_b(t) \KL(\hat{\mu}_{b}(t) || \hat{\mu}_{a,b}(t)),
-\end{equation*}
-
-where
-
-\begin{equation*}
-\hat{\mu}_{a,b}(t) := \frac{N_a(t)}{N_a(t) + N_b(t)}\hat{\mu}_a(t) + \frac{N_b(t)}{N_a(t) + N_b(t)}\hat{\mu}_b(t).
-\end{equation*}
-
-Consequently, a sensible idea for a stopping rule would be that there
-has to be an arm \(a \in \{1,...,K\}\) for which
-\(Z_{a,b} \geq 0 \text{ for all } b \in \{1,...,K\}^{\setminus a}\)
-(which is always fulfilled if there is a uniquely best arm), and we
-demand that for this arm the smallest of the \((K-1)\) test statistics
-has to be larger than an exploration threshold \(\beta(t, \delta)\). The
-final sampling round \(T_{\delta}\) of the algorithm is given by:
-
-\begin{equation*}
-T_{\delta} = \inf \{t \in \mathbb{N}: \exists a \in \mathcal{A}, \forall b\in \mathcal{A}^{\setminus a}, Z_{a,b}(t) > \beta(t, \delta)\}
-\end{equation*}
-
-Demanding that the optimal exploration threshold increases in rounds
-\(t\) (if we have more samples, require more certainty; punish for
-failing previous tests) and decreases in risk \(\delta\) at a
-diminishing rate, the optimal exploration rate for Bernoulli arms
-derived in Theorem 10 of Garivier and Kaufmann (2016) is intuitive:
-
-\begin{equation*}
-\beta(t, \delta) = \log \Big(\frac{2t(K-1)}{\delta}\Big).
-\end{equation*}
-
-With this, we can state the final theorem of the chapter, which gives
-the upper bound matching the lower bound in Theorem
-\ref{theorem:GarivierKaufmannTheorem1} for small risk values \(\delta\)
-using the D-Tracking rule and Chernoff's stopping rule with the
-exploration term given in the previous equation:
-
-\begin{theorem}[Theorem 14, Garivier and Kaufmann, 2016] \label{theorem:GarivierAndKaufmannTheorem14}
-Let $\bm{\mu}$ be an exponential family bandit model.
-Let $\alpha \in [1, e/2]$ and $r(t) = O(t^{\alpha})$.
-Using Chernoff's stopping rule with $\beta(t,\delta) = \log(r(t)/\delta)$ and the sampling rule D-Tracking,
-
-\begin{equation*}
-\limsup_{\delta \to 0} \frac{\mathbb{E}_{\bm{\mu}}[T_{\delta}]}{\log(1/\delta)} \leq \alpha T^*(\mu), \quad \text{with } T^*(\mu) \text{ as defined in equation \ref{eqn:ComplexityTrackStopStrategy}}.
-\end{equation*}
-\end{theorem}
-
-\subsection{Conclusion}\label{conclusion}
-
-Overall, the two papers presented in this chapter make significant
-contributions to identifying the top-\(1\) or the top-\(m\) arms in a
-multi-armed bandit setting. Their contribution is primarily based on
-including the Kullback-Leibler divergence and Chernoff information as
-information theoretic measures in the derivation of bounds and the
-matching algorithms. Thereby, they go beyond a sum of squared gaps which
-is most relevant only in the case of Gaussian distributions. While the
-contribution in the fixed budget setting is limited to the two-armed
-bandit case, the authors derive general lower bounds in the fixed
-confidence setting. All bounds presented are primarily based on Lemma
-\ref{theorem:KaufmannEtAlLemma1}. Lemma \ref{theorem:KaufmannEtAlLemma1}
-is able to measure the ``transportation cost'' (see Garivier and
-Kaufmann, 2016) of moving from one distribution to another one in terms
-of Kullback-Leibler divergence. It is a bound on the expected likelihood
-ratio term that appears when changes in distribution are applied.
-
-In the case of the fixed budget top-\(m\) arm identification problem, we
-have seen that the derivation of a lower bound on the complexity term is
-mostly limited by the difficulty of defining an alternative problem
-\(\nu'\) to \(\nu\) that fits into the Lemma
-\ref{theorem:KaufmannEtAlLemma1}. But given the intuition that in
-top-\(m\) problems the \(m\)-th best arm and the \((m+1)\)-th best arm
-define an implied threshold between the two groups of arms, we were able
-to apply the ideas of Kaufmann et al. (2016) to our fixed budget
-thresholding bandit problem. In contrast to their problem, arms are
-classified against the known threshold \(\tau\), which makes it possible
-to define an alternative problem \(\nu'\) in which we do not have to
-change arms with respect to each other, but only with respect to
-\(\tau\). This has lead us to the simple lower bound on the problem
-complexity for the thresholding bandit problem with exponential family
-distributions given in Corollary \ref{corollary:LBKTBP}.
-
-In the best arm identification problem discussed by Garivier and
-Kaufmann (2016), we were introduced to the idea of comparing each arm to
-the best arm, and evaluating the difference between the best arm and the
-other arms based on the Generalized Likelihood Ratio test. This idea
-seems transferrable to the thresholding bandit problem. Indeed, it might
-even be easier as the best arm does not have to be estimated; instead,
-we would compare each arm to the threshold \(\tau\). Intuitively, one
-can frame this problem for each arm individually as an hypothesis test
-between the maximum likelihood estimate of the mean and the threshold
-\(\tau\). We will come back to this idea in
-\autoref{sec:LikelihoodRatioForExponentialFamily}.
-
-Lastly, we observe that Garivier and Kaufmann (2016) support their
-algorithm's main strategy by an additional D-Tracking rule which
-protects them against poor estimates in the beginning of the sampling.
-Such rule should be mostly unnecessary, for example, the cumulative
-regret setting, as algorithms there rely on upper confidence bound
-estimates. This is not the case for the Track-and-Stop strategy
-introduced in Garivier and Kaufmann, and neither for our Simple
-Likelihood Ratio strategy introduced in \autoref{sec:1DSLR}. In
-\autoref{sec:Simulation2}, we show empirically that the performance of
-the Simple Likelihood Ratio strategy can be further improved by naively
-adding the D-Tracking rule to it.
-
-\section{\texorpdfstring{Extensions to the Thresholding Bandit Problem
-\label{chap:Extensions}}{Extensions to the Thresholding Bandit Problem }}\label{extensions-to-the-thresholding-bandit-problem}
-
-\subsection{\texorpdfstring{Introduction
-\label{sec:ExtensionsIntroduction}}{Introduction }}\label{introduction-1}
-
-In \autoref{chap:ThresholdingBanditProblem} we have introduced the
-thresholding bandit problem as proposed in Locatelli et al. (2016)
-alongside the APT algorithm. We have seen that the upper bound on the
-APT algorithm matches the lower bound for the thresholding bandit
-problem given in Locatelli et al. (2016). The algorithm also exhibits
-favorable characteristics such that its upper bound holds at any
-stopping time, and that it does not require any parameter to be known
-upfront. However, we have seen that the index and the complexity term
-\(H\) employed by the APT algorithm are the most effective for
-\(R\)-sub-Gaussian distributions. Both are related to the KL-divergence
-between two Gaussian distributions of equal variance. Given that this
-sub-Gaussian approximation can be poor in certain cases, we motivated
-the use of information theoretic measures in an algorithm's index
-(compare \autoref{sec:DiscussionLocatelli}).
-
-Another goal can be to compare the distributions with the threshold
-based not only on the empirical mean -- as done by the APT algorithm. A
-logical extension is for example the empirical variance. After all arms
-do not necessarily have the same variance, even if they are
-sub-Gaussian. And given two arms for which we estimate the same mean, we
-would prefer to draw more samples from the arm with the larger variance.
-
-In the case of Gaussian distributions with varying variances, for
-example, it makes sense to take the variance into account; after all,
-given two Gaussians with equal mean, intuitively we would prefer to get
-a sample from the distribution of larger variance.
-
-For these reasons, in the following, we first present in
-\autoref{sec:VarianceBasedAlgorithms} two algorithms which incorporate
-empirical variances as described in Mukherjee et al. (2017) and Zhong et
-al. (2017). We then introduce a new algorithm based on the concept of
-likelihood ratios in \autoref{sec:LikelihoodRatioForExponentialFamily}.
-Finally, we compare the performance of different algorithms based on
-simulations and real world data sets in \autoref{chap:Experiments}.
-
-\subsection{\texorpdfstring{Variance Based Algorithms for the
-Thresholding Bandit
-\label{sec:VarianceBasedAlgorithms}}{Variance Based Algorithms for the Thresholding Bandit }}\label{variance-based-algorithms-for-the-thresholding-bandit}
-
-\subsubsection{\texorpdfstring{Augmented-UCB Algorithm
-\label{sec:AugUCBAlgorithm}}{Augmented-UCB Algorithm }}\label{augmented-ucb-algorithm}
-
-Combining learnings from the APT and other algorithms, Mukherjee et al.
-(2017) propose the Augmented-UCB (AugUCB) algorithm based on variance
-estimates for the thresholding bandit problem. The setting they consider
-is thus very similar to the setting in Locatelli et al. (2016). The main
-difference being that, while Locatelli et al. (2016) assume
-\(R\)-sub-Gaussian reward distributions, Mukherjee et al. (2017) assume
-rewards to be bounded in \([0,1]\), which makes the AugUCB applicable to
-less distributions. The AugUCB algorithm itself differs significantly
-from the APT algorithm. The two main ideas it employs are first, upper
-confidence bounds based on the Bernstein inequality and empirical
-variance estimates to compute the index based on which an arm is chosen
-at every round. Second, if an arm estimate is ``far enough away'' from
-the threshold as measured by the confidence bounds, it will be
-``eliminated'', and no longer be pulled until the end of the budget.
-Both ideas are based not only on the empirical mean estimate
-\(\mu_i(t)\), but also on a term \(s_i\) that is increasing linearly in
-the estimated standard deviation. While the APT algorithm plays the arm
-minimizing the quantity
-\(B_i^{APT}(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t) = \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau| + \epsilon)\),
-AugUCB plays the arm minimizing the quantity
-\(\hat{\Delta}_i(t) - 2s_i\), where \(s_i\) is based on the variance
-estimate \(\hat{v}_i\), and an exploration \(\psi_m\) term linear in
-\(T\), as well as an elimination parameter \(\rho\) (compare Algorithm 1
-in Mukherjee et al., 2017):
-
-\begin{equation*}
-s_i = \sqrt{\frac{\rho \psi_m (\hat{v}_i + 1) \log(T \epsilon_m)}{4n_i}}.
-\end{equation*}
-
-Consequently, the authors also introduce complexity measures which take
-the variance into account. From Gabillon et al. (2011) they use
-\(H_{\sigma, 1}= \sum_{i=1}^K \frac{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}{\Delta_i^2}\).
-Furthermore, with
-\(\stackrel{\sim}{\Delta}_i^2 = \frac{\Delta_i^2}{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}\),
-where \(\stackrel{\sim}{\Delta}_{(i)}\) is an increasing ordering of
-\(\stackrel{\sim}{\Delta}_i\), the authors define a complexity
-corresponding to \(H_{CSAR,2}\) in Chen et al. (2014):
-
-\begin{equation*}
-H_{\sigma,2} = \max_{i \in \mathcal{A}} \frac{i}{\stackrel{\sim}{\Delta}_{(i)}^2}.
-\end{equation*}
-
-While the latter complexity appears in the provided upper bound on the
-AugUCB algorithm's expected loss, it could be replaced by
-\(H_{\sigma, 1}\) since \(H_{\sigma, 2} \leq H_{\sigma,1}\).
-\(H_{\sigma,1}\) is more easily compared to the complexity \(H\) defined
-in Locatelli et al. (2016). Essentially, every arm's complexity
-contribution is additionally scaled by a term increasing in the arm's
-variance (see also the graph comparing the complexity terms of APT,
-AugUCB, and EVT algorithms below).
-
-In the case of the APT algorithm the number of times a specific arm has
-been drawn \(T_i\) measures how concentrated the estimated mean is
-around the true mean (and thus for large \(T_i\) an arm is no longer
-drawn even if \(\hat{\mu}\) is close to \(\tau\)). This exploration is
-regulated by the combination of the variance estimate \(\hat{v}_i\) and
-the exploration factor \(\psi_m\) in the case of the AugUCB algorithm.
-The terms ensure that certain arms are no longer pulled when the
-algorithm is sufficiently confident in the location of true mean.
-Indeed, the AugUCB algorithm goes a little further than the APT
-algorithm in that it eliminates arms (no longer considers them in
-sampling) when a separation condition is estimated to hold. The same
-separation condition of estimated mean away from the threshold is used
-in the authors' upper bound proof and is reminiscient of the separation
-condition used in Locatelli et al.'s (2016) upper bound proof.
-
-Therefore, when using a very similar favorable event in the proof of
-their upper bound, Mukherjee et al. (2017) have to bound the probability
-that an an arm is not removed from the active set after the a certain
-number of rounds -- even though the arm is above (respectively below)
-the threshold. If this probability is low, then the algorithm is able to
-be certain about an arm's true mean by employing variance estimates. In
-comparison, Locatelli et al (2016) used bounds on on how often arms are
-drawn (\(T_i\)) to give a bound on the probability of the favorable
-event. In order to derive the bound, Mukherjee et al. (2017) use the
-Bernstein inequality.
-
-It has to be noted that Mukherjee et al. (2017) have to assume that the
-distributions have rewards bounded in \([0,1]\) in order to derive the
-bound on the probability that an arm has not been eliminated correctly
-in round \(T_i\). Else it would not be possible to upper bound the
-\(s_i\) term by \(\Delta_i/4\) as Mukherjee et al. do in their proof.
-Thus, the distributions for which their upper bound holds are a subset
-of the \(R\)-sub-Gaussian distributions considered in Locatelli et al.
-(2016). However, while the authors demand in their setting that the
-rewards are bounded in \([0,1]\), it seems that the upper bound only
-requires the arms' variances to be bounded in \([0,1]\) such that
-\(\hat{v}_i \in [0,1]\). Thus, the upper bound should hold in particular
-for Gaussian distributions with variance \(\sigma^2 \in [0,1]\).
-Consequently, the simulations by Mukherjee et al. are performed on
-Gaussian arms with variance smaller than one.
-
-Based on this assumption, the authors show that the probability that an
-arm has not been eliminated after \(m_i\) rounds is given by (compare
-equation (2) in Mukherjee et al., 2017):
-
-\begin{equation} \label{Mukherjee2017Equation2}
-\mathbb{P}(\hat{\mu}_i > \mu_i + 2s_i) \leq \mathbb{P} (\hat{\mu}_i > \mu_i + 2\bar{s}_i) + \mathbb{P}(\hat{v}_i \geq \sigma^2_i + \sqrt{\rho \epsilon_{T_i}})
-\end{equation}
-
-Compare Mukherjee et al. (2017) for the notation. Then it becomes clear
-that the left part of the RHS gives the probability that the mean
-estimate is out of wack, while the right term gives the probability that
-the variance is overestimated. The first term is bounded by the
-Bernstein inequality. In the cumulative regret setting, there exists a
-similar decomposition for algorithms based on upper confidence bounds.
-There, the expected number of pulls of a suboptimal arm is bounded.
-Compare for example chapter 3.1 in Kaufmann, Korda and Munos (2012), in
-which the authors decompose the expected number of draws of an
-suboptimal arm into the probability that the optimal arm's mean is
-underestimated, and the probability that the upper confidence bound of
-the suboptimal arm is still very large. To give bounds for UCB
-algorithms, certain convergence rates are shown for these two
-probabilities. Mukherjee et al. do similarly for their upper confidence
-algorithm in the thresholding setting.
-
-\subsubsection{\texorpdfstring{Anytime Parameter-free Empirical Variance
-Guided Algorithm
-\label{sec:EVTAlgorithm}}{Anytime Parameter-free Empirical Variance Guided Algorithm }}\label{anytime-parameter-free-empirical-variance-guided-algorithm}
-
-Another algorithm for the thresholding bandit problem employing
-empirical variance estimates is introduced in Zhong et al. (2017).
-Indeed, the authors discuss several variations of their algorithm which
-extend their central idea to applications in which several samples need
-to be pulled in a parallel and asynchronous fashion. An standard example
-known from the multi-armed bandit literature (see for example Li et al.
-(2010)) is a website for which different versions are served to visitors
-and each version is an arm in the bandit setting. If the feedback that
-is observed by the algorithm is whether or not a user makes a purchase,
-then it is likely that a new user arrives before the feedback for the
-previous user has been observed. The algorithm has to pull the next arm
-before the feedback of the previous arm has been observed. With their
-variants the authors approach this problem of having to take
-asynchronous and parallel actions. But their algorithm can also be
-reduced to a simpler version that can be compared directly with the
-problem described in Locatelli et al. (2016) where the feedback lag is
-assumed to be zero.
-
-This simpler version is the parameter-free version of their Empirical
-Variance Guided Algorithm (EVT\(_{pf}\)). The EVT\(_{pf}\) algorithm is
-an extension of the APT algorithm that takes the empirical variance of
-the arms into account and deduces an upper bound through empirical
-Bernstein bounds in a proof following the model of the one described in
-Locatelli et al. (2016).
-
-In order to describe their algorithm, we adapt a formulation used in
-Zhong et al. (2017) to describe the index used by the algorithms in a
-more general fashion. Write the index \(B_i(t+1)\) of arm \(i\) at round
-\(t\) as previously as
-
-\[
-B_i(t+1) = S_i(t) D_i(t),
-\]
-
-where \(D_i(t)\) is some measure of the distance between the mean
-\(\mu_i\) or the distribution \(\nu_i\) of arm \(i\) from the threshold
-\(\tau\), while \(S_i(t)\) is some confidence value measuring how
-confident we can be in \$. Thus, for the APT algorithm, if we let
-\(\epsilon = 0\) as in Zhong et al. (2016), we have
-
-\[
-D_i^{APT}(t) = \hat{\Delta}_i(t) = |\hat{\mu}_i(t) - \tau| \quad \text{and} \quad S_i^{APT}(t) = \sqrt{T_i(t)}
-\]
-
-We see that \(D_i(t)\) is the probably most straightforward distance
-between the sample mean and the threshold, while \(S_i(t)\) increases
-over time, as we become more confident in our sample mean, and thus
-ensures that we do not continue pulling the same arm forever.
-
-Based on this, we can now easily compare APT to EVT\(_{pf}\) for which
-the index can be written as:
-
-\[
-D_i^{EVT_{pf}}(t) = \sqrt{\hat{\sigma}^2_{i}(t) + \hat{\Delta}_i(t)} - \hat{\sigma}_i(t) \quad \text{and} \quad S_i^{EVT_{pf}} = \sqrt{T_i(t)}
-\]
-
-We see that both algorithms employ the same confidence term. The
-empirical variance describes the shape of the distribution and thus is a
-measure of how far the distribution (in contrast to just the mean) is
-away from the threshold. It consequently makes sense to have it appear
-in \(D_i^{EVT}\). And in contrast to the APT algorithm, the EVT\(_{pf}\)
-algorithm consequently takes more information about the arms into
-account than just their mean. As mentioned previously, this should
-especially be valuable whenever arms have indeed different variances.
-Similar (very roughly) to how the Kullback-Leibler divergence measures
-distances between distributions, the \(D_i^{EVT}\) including the
-empirical variance serves as a crude measure of distance between
-threshold and distribution. We note that for a Bernoulli distributed
-random variable, \(D_i^{EVT}\) is always decreasing as the mean
-approaches the threshold (compare the figure 2). Similar should hold in
-general for bounded variables as the variance and the mean are linked by
-the distance of the mean to the bound of the support (in contrast to,
-for example, a normal distributed random variable where a change in the
-mean does not correspond to a change in the variance). This is important
-as the bounds of the EVT\(_{pf}\) algorithm only hold for random
-variables bounded in \([0,1]\). In contrast to the AugUCB, this
-restriction is not just on the variance of the arm but explicitly on the
-reward itself in the current version that builds on empirical Bernstein
-bounds as shown in Maurer and Pontil (2009).
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/EVT_Index_Bernoulli-1}
-
-}
-
-\caption{This graph displays the distance part of the index of the APT, SLR, and EVT algorithms.
-While EVT's distance is based on both the empirical mean and empirical variance, the empirical mean determines the variance in the case of Bernoullis.
-We see that the distance of both EVT and SLR has an asymmetric behavior.}\label{fig:EVT_Index_Bernoulli}
-\end{figure}
-
-By defining a new complexity measure \(H^{\text{EVT}_{pf}}\) for the
-EVT\(_{pf}\) algorithm, Zhong et al. (2017) are able to derive an upper
-bound on the expected loss of the algorithm. Let the complexity increase
-in the variance and decrease in the distance of the mean from the
-threshold such that
-
-\[
-H^{\text{EVT}_{pf}} = \sum_{i=1}^K h_i^{\text{EVT}_{pf}} = \sum_{i=1}^K (\sigma_i^2\Delta_i^{-2} + \Delta_i^{-1}).
-\]
-
-Then one can state the following theorem.
-
-\begin{theorem}[Theorem 5, Zhong et al., 2017] 
-\label{theorem:ZhongEtAl2017Theorem5}
-Let $K > 0$, $T > 2K$, and consider a thresholding bandit problem. Assume that all arms of the problem are bounded in $[0,1]$. Then the probability of an error is bounded as
-
-\begin{equation*}
-\mathbb{E}[L] \leq TK \exp\Big(-C\frac{T}{H^{\text{EVT}_{pf}}}\Big),
-\end{equation*}
-
-where $C$ is some positive constant.
-\end{theorem}
-
-The authors approach the proof very similarly as Locatelli et al. (2016)
-in the proof of their lower bound. They define favorable events that
-hold with large probability, and ensure that the same separation
-condition as in Locatelli et al. holds for them given that each arm is
-pulled sufficiently often. Additionally to a favorable event that bounds
-the deviation between sample mean and population mean, they define a
-second event on which the sample standard deviation is close to the
-population standard deviation. This is bounded in large probability by
-an empirical Bernstein inequality (Maurer and Pontil, 2009). The union
-of the two events then serves as the favorable event in the remainder of
-their proof.
-
-Given a lower bound adapted to the new complexity
-\(H^{\text{EVT}_{pf}}\), the Zhong et al. (2017) show that the
-EVT\(_{pf}\) algorithm is optimal in that its upper bound matches the
-lower bound. Furthermore, they compare their algorithm in experiments
-against the APT algorithm. The experiments use data generated from
-uniform distributions. Each experiment compares 100 arms with variances
-picked at random from a range of possible variances. Over three
-experiments, the range of variances is varied from small to large, where
-the authors expect their algorithm to show the largest advantage
-compared to APT on the problem with small variances. Interestingly, they
-report the largest advantage of their variance based algorithms in
-comparison to APT when the variances are very small; given they only
-consider problems bounded on a support of \([0,1]\), \(\sigma_i \ll 1\).
-In this case the problem complexity \(H^{\text{EVT}_{pf}}\) can be much
-smaller than \(H^{APT}\) -- the EVT\(_{pf}\) algorithm profits more from
-distributions that are simple to estimate in terms of their variance
-than the APT algorithm does.
-
-When comparing the two complexities for example for Bernoulli random
-variables against some fixed threshold, we see that the smaller
-complexity of the EVT\(_{pf}\) algorithm implies in particular that
-EVT\(_{pf}\) could be able to cope with distributions of parameter
-\(\mu\) close to \(\tau\) much better than APT (compare figure 3).
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.7\linewidth]{Draft_files/figure-latex/Hevt_Hapt_Comparison-1}
-
-}
-
-\caption{Comparing the complexity terms used in the APT, AugUCB, and EVT algorithms, we observe that the problem complexity of the EVT algorithm increases much less rapidly than for the other algorithms.
-Thus, the EVT should be able to cope with arms close to the threshold better than the APT algorithm.
-The complexity displayed for the AugUCB is an upper bound on the complexity used in the upper bound of Mukherjee et al.
-(2017).}\label{fig:Hevt_Hapt_Comparison}
-\end{figure}
-
-\subsection{\texorpdfstring{Likelihood Ratio for Sequential Sampling
-\label{sec:LikelihoodRatioForExponentialFamily}}{Likelihood Ratio for Sequential Sampling }}\label{likelihood-ratio-for-sequential-sampling}
-
-We now present a new sequential sampling algorithm for the fixed budget
-thresholding bandit problem that builds on the idea of the likelihood
-ratio statistic for hypothesis tests. We first shortly describe the
-general idea of likelihood ratio based tests, to then introduce this new
-algorithm for the thresholding bandit problem, which we call Simple
-Likelihood Ratio (SLR) algorithm.
-
-\subsubsection{\texorpdfstring{Likelihood Ratio-based Hypothesis Tests
-\label{sec:LRTests}}{Likelihood Ratio-based Hypothesis Tests }}\label{likelihood-ratio-based-hypothesis-tests}
-
-In a standard parametric testing problem, we have drawn an iid sample
-\(x = (x_1, ..., x_T)\), where each \(x_i\) is a realization from the
-random variable \(X_i\). We assume that \(X_i\) follows some probability
-distribution \(Q(\theta)\) paramaterized by a vector \(\theta\). Let
-\(q(x;\theta)\) be the density function corresponding to the
-distribution. We would like to test whether an alternative
-parameterization is more likely than the parameterization given by the
-null hypothesis. That is, we test
-
-\[
-H_0: \quad \theta = \theta_{H_0} \qquad \text{vs.} \qquad H_1: \quad \theta = \theta_{H_1}
-\]
-
-In order to assess whether the \(H_0\) hypothesis can be rejected, one
-computes the likelihood \(L(x|\theta)\) of the observed sample under
-both parameterizations:
-\(L_{H_0} = L(x|\theta = \theta_{H_0}) = \prod_{i=1}^T q(x_i|\theta_{H_0})\)
-and
-\(L_{H_1} = L(x|\theta = \theta_{H_1}) = \prod_{s=1}^T q(x_s|\theta_{H_1})\).
-The likelihood ratio test statistic is then given as
-
-\[
-LR_T(\theta_{H_0}|| \theta_{H_1}) = \frac{L_{H_0}}{L_{H_1}} = \prod_{s=1}^T\frac{q(x_s|\theta_{H_0})}{ q(x_s|\theta_{H_1})}.
-\]
-
-and is used in the optimal test of two hypotheses as shown by the
-Neyman-Pearson lemma (see chapter 11, Theorem 11.7.1 in Cover and
-Thomas, 2006).
-
-The intuition behind the test of course being that, if the true
-parameterization is \(H_1\) and not \(H_0\), then the likelihood
-\(L_{T,H_1}\) should be larger than \(L_{T,H_0}\). A small enough
-likelihood ratio would thus lead us to a rejection of the null
-hypothesis, while a large likelihood ratio is evidence in favor of the
-null hypothesis.
-
-Furthermore, the likelihood ratio is inherently linked to information
-theoretic quantities and divergence measures. Assuming that \(Q\) is a
-discrete distribution with support \(\chi\), one can write the negative
-log-likelihood ratio as (compare Cover and Thomas, 2006)
-
-\begin{align*}
--\log(LR_T(\theta_{H_0}|| \theta_{H_1}) & = \sum_{i=1}^T \log(\frac{q(x_s|\theta_{H_0})}{ q(x_s|\theta_{H_1})}) \\
-& = \sum_{a \in \chi} T q(a|\hat{\theta}) \log(\frac{q(a|\theta_{H_0})}{ q(a|\theta_{H_1})}) \\
-& = \sum_{a \in \chi} T q(a|\hat{\theta}) \log(\frac{q(a|\theta_{H_0})}{ q(a|\theta_{H_1})}\frac{q(a|\hat{\theta})}{ q(a|\hat{\theta})}) \\
-& = T \KL(q(\hat{\theta})||q(\theta_{H_0})) - T \KL(q(\hat{\theta})||q(\theta_{H_1})),
-\end{align*}
-
-where \(\hat{\theta}\) is the maximum likelihood estimate of the
-parameter \(\theta\) given the sample \(x\). If we hold the \(H_0\)
-hypothesis fixed and set \(\theta_{H_1} = \hat{\theta}\) as often done
-in praxis, then with \(\KL(Q(\hat{\theta})||Q(\hat{\theta})) = 0\):
-
-\[
--\log(LR_T(\theta_{H_0}|| \theta_{H_1})) = -\log(LR_T(\theta_{H_0}|| \hat{\theta})) = \KL(Q(\hat{\theta}||Q(\theta_{H_0}))
-\]
-
-Furthermore, we have for any distributions \(Q_{H_0}\) and \(Q_{H_1}\)
-for a sample \(x\) sampled from the \(H_0\) distribution, that
-
-\[
-\frac{1}{n} \log(LR_T(\theta_{H_0}||\theta_{H_1})) \rightarrow \KL(Q(\theta_{H_0})||Q(\theta_{H_1})) \quad \text{in probability},
-\]
-
-by the law of large numbers (or asymptotic equipartition property) for
-the Kullback-Leibler divergence as in Theorem 11.8.1 in Cover and Thomas
-(2006). Lastly, based on the characteristics shown before, for
-frequentist tests the Kullback-Leibler divergence between
-\(Q(\theta_{H_0})\) and \(Q(\theta_{H_1})\) gives the best possible
-exponent for the error of the second type given a fixed error of the
-first type. This is the result of the Chernoff-Stein Lemma (Theorem
-11.8.3, Cover and Thomas, 2006), which is reminiscient of the complexity
-\(\kappa_B\) derived by Kaufmann et al. (2016) and as described in
-\autoref{chap:KullbackLeiblerPureExploration}:
-
-\begin{theorem}[Chernoff-Stein Lemma] \label{theorem:ChernoffStein}
-Let $X_1, X_2, ..., X_n$ be i.i.d.
-distributed according to $Q$.
-Consider the hypothesis test between two alternatives, $Q=P_1$ and $Q=P_2$, where $\KL(P_1||P_2) < \infty$.
-Let $A_n \subseteq \chi^n$ be an acceptance region for hypothesis $H_1$.
-Let the probabilities of error be $\alpha_n = P_1^n(A_n^C)$, and $\beta_n = P_2^n(A_n)$, and for $0< \epsilon <1/2$, define $\beta_n^{\epsilon} = \min_{A_n \subseteq \chi^n, \alpha_n < \epsilon} \beta_n$.
-Then
-
-$$
-\text{lim}_{n\rightarrow \infty} \frac{1}{n} \log \beta_n^{\epsilon} = - \KL(P_1||P_2)
-$$
-\end{theorem}
-
-\subsubsection{Likelihood Ratio as Index in Sequential
-Sampling}\label{likelihood-ratio-as-index-in-sequential-sampling}
-
-We now employ the concept of the likelihood-ratio test for a new
-sequential sampling strategy for the thresholding bandit problem. In
-contrast to the cumulative regret problem or the best arm identification
-problem, the thresholding bandit problem offers a natural \(H_0\)
-hypothesis for the arms' distributions: the threshold \(\tau\). Given
-that we want to classify the arms against the threshold, and given that
-\(\tau\) is known and fixed, we can set a null hypothesis that is a
-function of \(\tau\). In the simplest case, the distributions are
-parameterized by their mean \(\theta_i = \mu_i\), and we set
-\(\theta_{i,H_0} = \tau\) for all arms. The likelihood ratio then
-quantifies how ``significant'' of a difference there is between the
-threshold \(\tau\) and the current sample mean \(\hat{\mu}_i(t)\) of an
-arm, assuming distributions for which the maximum likelihood estimate of
-the mean is given by the empirical mean. In these cases, the likelihood
-ratio will be smaller than 1 and decrease in sample size even if the
-threshold and sample mean are constant.
-
-Due to these characteristics, the likelihood ratio can serve as a
-natural index for sampling strategies. Consider the setting described in
-\autoref{sec:Setup} and \autoref{sec:TheAPTAlgorithm} though without
-assuming \(R\)-sub-Gaussian distributions. Consider \(B_i^{APT}\) and
-compare it to
-
-\[
-B_i^{LR}(t+1) = LR(\tau|| \hat{\mu}_i(t)) = \prod_{i=1}^T\frac{q(x_i|\tau)}{ q(x_i|\hat{\mu}_i(t))}.
-\]
-
-We have \(B_i(t) \leq 1\), \(t \uparrow \rightarrow B_i(t) \downarrow\),
-and \(|\hat{\mu}_i(t) - \tau| \uparrow \rightarrow B_i(t) \downarrow\).
-Consequently, by choosing the arm that maximizes \(B_i(t)\), we choose
-an arm for which we either have not collected many samples, or for which
-the sample mean is close to the threshold \(\tau\). In this sense, a
-strategy based on the likelihood ratio is reminiscient of the index
-employed by the APT algorithm. Indeed, assuming the samples are normally
-distributed with the same variance for the distribution \(\nu_i\) under
-both \(H_0\) and \(H_1\), then \(-\log(LR(\tau||\hat{\mu}_i(t)))\)
-equals the index in APT. Why then would one use the likelihood based
-strategy?
-
-Given that the APT index and the likelihood-ratio based index are only
-equivalent for normally distributed random variables with fixed standard
-deviation, the new strategy promises efficiency improvements whenever
-the true distribution is known and different from the normal
-distribution. The most important example are Bernoulli arms with small
-means as motivated. While the likelihood ratio can in theory be used for
-any distributions, and arms could even have different classes of
-distributions, the class of distribution has to be known upfront for
-every arm. Given the role of the threshold \(\tau\) and the goal of
-classification of the mean against \(\tau\), the likelihood ratio
-strategy is arguably most naturally employed on distributions
-parameterized by their mean. In the following descriptions, we thus
-focus on univariate distributions of the exponential family.
-Additionally, we also propose a version for the Normal distribution with
-unknown mean. Before we describe the algorithm, we show that the
-likelihood ratio has a very convenient form for this family of
-distributions.
-
-\subsubsection{\texorpdfstring{Likelihood Ratio for Univariate
-Exponential Family of Distributions
-\label{sec:LRforUnivariateExponentialFamily}}{Likelihood Ratio for Univariate Exponential Family of Distributions }}\label{likelihood-ratio-for-univariate-exponential-family-of-distributions}
-
-We now focus on a thresholding bandit problem where the arms are
-distributed according to \(\nu_{\theta_1}, ..., \nu_{\theta_K}\), which
-are all from the same canonical exponential family of distributions with
-scalar parameter \(\theta_i \in \Theta\). The probability density
-function of the absolutely continuous distribution \(\nu_{\theta_i}\)
-with regard to a dominating measure \(\rho\) on \(\mathbb{R}\) is given
-by \(q(x|\theta) = h(x) \exp(T(x)\theta - b(\theta))\). As described in
-Cappé et al. (2013), citing Lehmann and Casella (1998), the derivative
-\(b'(\theta)\) of \(b(\theta)\) is an increasing continuous function
-such that the expected value \(\mathbb{E}(\nu_{\theta}) = b'(\theta)\)
-for all \(\theta \in \Theta\). Given that \(b'(x)\) is strictly convex,
-we have a one-to-one relation between \(b'(\theta)\) and
-\(\mathbb{E}(\nu_{\theta})\) through the continuous inverse
-\(b'^{-1}(\theta)\). Consequently, one can just as well parameterize the
-distribution its mean \(\mu = \mathbb{\nu_{\theta}}\) and write
-\(\nu_{b'^{-1}(\mu)}\) with the probability density function (compare
-Cappé et al., 2013)
-
-\[
-q(x|b'^{-1}(\mu)) = h(x) \exp(T(x) b'^{-1}(\mu) - b(b'^{-1}(\mu))).
-\]
-
-This lets us write the likelihood ratio for the exponential family
-distributions as
-
-\[
-LR(b'^{-1}(\mu_0)||b'^{-1}(\mu_1)) = \prod_{i=1}^n \frac{\exp(T(x_i) b'^{-1}(\mu_0) - b(b'^{-1}(\mu_0)))}{\exp(T(x_i) b'^{-1}(\mu_1) - b(b'^{-1}(\mu_1)))}
-\]
-
-or if we write it as negative log-likelihood ratio:
-
-\[
--\log(LR) = n\Big(b\big(b'^{-1}(\mu_0)) - b(b'^{-1}(\mu_1)\big)\Big) - \Big(b'^{-1}(\mu_0)-b'^{-1}(\mu_1)\Big)\sum_{i=1}^nT(x_i)
-\]
-
-As we will see now, this statistic takes a very convenient closed form
-for many common distributions.
-
-\textbf{Example 1: Bernoulli Distribution}
-
-We have \(T(x_i) = x_i\), \(\theta = \log(\mu/(1-\mu))\),
-\(\Theta = (0,1)\), \(b(\theta) = \log(1+\exp(\theta))\), and
-\(\mu \in (0,1)\). Then \(b'(\theta) = \mu\), and we can write
-
-\begin{align*}
--\log(LR(\mu_0||\mu_1)) & = n(\log\Big(\frac{1-\mu_0}{1-\mu_1}\Big)) - \Big(\log(\frac{\mu_0}{1-\mu_0}) - \log(\frac{\mu_1}{1-\mu_1})\Big)\sum_{i=1}^{n}x_i \\
-& = n \Big( (1-\hat{\mu})\log\Big(\frac{1-\mu_1}{1-\mu_0}\Big) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}) \Big)
-\end{align*}
-
-We observe that, if we let \(\mu_0 = \tau\) and \(\mu_1 = \hat{\mu}\)
-(compare \autoref{sec:LRTests}), then
-
-\[
--\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n \Big(\hat{\mu}\log\big(\frac{\hat{\mu}}{\tau}\big) + (1-\hat{\mu})\log\big(\frac{1-\hat{\mu}}{1-\tau}\big)\Big)
-\]
-
-\textbf{Example 2: Poisson Distribution}
-
-We have \(T(x_i) = x_i\), \(\theta = \log(\mu)\),
-\(\Theta = \mathbb{R}\), \(b(\theta) = \exp(\theta)\), and
-\(\mu \in (0, +\infty)\). Then \(b'(\theta) = \mu\), and we can write:
-
-\[
--\log(LR(\mu_0||\mu_1)) = n(\mu_0 - \mu_1) - (\log(\mu_0) - \log(\mu_1))\sum_{i=1}^n x_i = n\Big((\mu_0 - \mu_1) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}\Big)\Big)
-\]
-
-We observe that, if we let \(\mu_0 = \tau\) and \(\mu_1 = \hat{\mu}\)
-(compare \autoref{sec:LRTests}), then
-
-\[
--\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n\Big((\tau - \hat{\mu}) + \hat{\mu}\log\Big(\frac{\hat{\mu}}{\tau}\Big)\Big)
-\]
-
-\textbf{Example 3: Normal distributions with known variance
-\(\sigma^2\)}
-
-We have \(T(x_i) = x_i\), \(\theta = \mu/\sigma^2\),
-\(\Theta = \mathbb{R}\), \(b(\theta) = \sigma^2\theta^2/2\),
-\(\mu \in \mathbb{R}\). Then \(b'(\theta) = \mu\), and we can write
-
-\[
--\log(LR(\mu_0||\mu_1)) = n (\frac{\mu_0^2}{2\sigma^2} - \frac{\mu_1^2}{2\sigma^2}) - (\frac{\mu_0}{\sigma^2} - \frac{\mu_1}{\sigma^2})\sum_{i=1}^nx_i = n\frac{1}{2\sigma^2}\Big(\mu_0^2-\mu_1^2 - 2\mu_0\hat{\mu} + 2\mu_1\hat{\mu}\Big)
-\]
-
-And again, even though the distribution is continuous (compare
-\autoref{sec:LRTests}), if we let \(\mu_1 = \hat{\mu}\) and
-\(\mu_0 = \tau\), then
-
-\[
--\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n\frac{(\hat{\mu} - \tau)^2}{2\sigma^2}.
-\]
-
-\textbf{Example 4: Gamma distributions with known shape parameter
-\(\alpha\)}
-
-We have \(T(x_i) = x_i\), \(\theta = -\alpha/\mu\),
-\(\Theta = (-\infty, 0)\), \(b(\theta) = -\alpha \log(-\theta)\),
-\(\mu \in (0,+\infty)\). Then \(b'(\theta) = -\mu\), and we can write
-
-\[
--\log(LR(\mu_0||\mu_1)) = n\alpha(-\log(\frac{\alpha}{\mu_0}) - \log(\frac{\mu_1}{\alpha})) - (-\frac{\alpha}{\mu_0} + \frac{\alpha}{\mu_1})\sum_{i=1}^{n}x_i = n\alpha \Big(\log\big(\frac{\mu_0}{\mu_1}\big) - \frac{\hat{\mu}}{\mu_1} + \frac{\hat{\mu}}{\mu_0}\Big).
-\]
-
-And again, even though the distribution is continuous (compare
-\autoref{sec:LRTests}), if we let \(\mu_1 = \hat{\mu}\) and
-\(\mu_0 = \tau\), then
-
-\[
--\log(LR(\tau||\hat{\mu})) = nKL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = nd(\hat{\mu},\tau) = n\alpha \Big(\frac{\hat{\mu}}{\tau} - 1 - \log\big(\frac{\hat{\mu}}{\tau}\big)\Big).
-\]
-
-For \(\alpha = 1\), the Gamma distribution is equal to the Exponential
-distribution.
-
-Given these results for the exponential family of distributions, we can
-now define the Simple Likelihood Ratio algorithm.
-
-\subsection{\texorpdfstring{1D-Simple Likelihood Ratio Algorithm
-\label{sec:1DSLR}}{1D-Simple Likelihood Ratio Algorithm }}\label{d-simple-likelihood-ratio-algorithm}
-
-Consider again the setting in \autoref{sec:Setup} though without the
-assumption of \(R\)-sub-Gaussian distributions. Instead, assume that the
-class of distributions that the arms \(i \in \mathbb{A}\) follow is
-known upfront. For the 1D-SLR algorithm, we restrict the potential
-classes to the univariate exponential family of distributions and write
-the class generally as \(\nu(\mu, \theta)\). Here, \(\theta\) describes
-additional parameters known upfront, as for example
-\(\sigma_1, ..., \sigma_K\) for Normal distributions, or
-\(\alpha_1, ..., \alpha_K\) for Gamma distributions. Additionally to
-\(\nu(\mu)\), the 1D-SLR algorithm receives as input the definition of
-the problem \((\tau, \epsilon)\) (compare Locatelli et al., 2016). As
-initialization, the algorithm pulls each arm once. At time \(t>K\), the
-algorithm updates the number of pulls for arm \(i\) at time \(t\),
-\(T_i(t)\), for each arm, as well as the empirical mean
-\(\hat{\mu}_i(t)\) of arm \(i\) after \(T_i(t)\) pulls. The empirical
-mean is calculated for each arm \(k\in \{1,...,K\}\) as
-\(\hat{\mu}_i(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)} x_{i,s}\), with
-\(T_i(t) = \sum_{s=1}^{t}\mathbb{I}(I_s = i)\). It serves as maximum
-likelihood estimate of the arm's mean. As in Locatelli et al. (2016),
-the \(X_{i,s}\) is the sample received when pulling arm \(i\) for the
-\(s\)-th time. Depending on the distribution, the algorithm then
-computes the index
-
-\begin{align*}
-B_i^{SLR}(t+1) & = \mathbb{I}(\hat{\mu}\geq \tau)(-\log\big(LR(\tau-\epsilon||\hat{\mu}_i(t))\big) \\
-& \quad +\: \mathbb{I}(\hat{\mu} <\tau)(-\log\big(LR(\tau+\epsilon||\hat{\mu}_i(t))\big) \\
-& = T_i(t) \Big( \mathbb{I}(\hat{\mu}\geq \tau)\cdot KL(\nu_{b'^{-1}(\hat{\mu}(t))}||\nu_{b'^{-1}(\tau-\epsilon)}) \\
-& \quad \quad +\: \mathbb{I}(\hat{\mu} < \tau)\cdot KL(\nu_{b'^{-1}(\hat{\mu}(t))}||\nu_{b'^{-1}(\tau+\epsilon)}) \Big) \Alignyesnumber\label{eqn:SLRIndex}.
-\end{align*}
-
-The next arm to be pulled is the minimizer of the index
-\(B_i^{SLR}(t+1)\), \(I_{t+1} = \arg \min_{i\leq K} B_i(t+1)\). At the
-end of the horizon \(T\), the algorithm outputs the set of arms
-\(\hat{S}_\tau = \{i \in \mathbb{A}, \hat{\mu}_i(T) \geq \tau\}\).
-
-\IncMargin{1em}
-
-\begin{algorithm}
-\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
-\Input{$\tau$, $\epsilon$, class of distributions $\nu(\mu, \theta)$, $\theta_i \: \forall i \in \mathbb{A}$}
-\Output{$\hat{S}_\tau = \{i \in \mathbb{A},  \hat{\mu}_i(T) \geq \tau\}$}
-\BlankLine
-\emph{Pull each arm once}\;
-\For{$t = K+1$ \KwTo $T$}{
-  \emph{Pull arm $I_t = \arg \min_{i\leq K} B_i^{SLR}(t)$ as in \autoref{eqn:SLRIndex}}\;
-  \emph{Observe reward $X_t \sim \nu_{I_t}$}\;
-}
-\caption{SLR algorithm for univariate exponential family of distributions}\label{algo_slr_1d}
-\end{algorithm}
-
-\DecMargin{1em}
-
-\subsection{2D-SLR Algorithm for Normal
-Distributions}\label{d-slr-algorithm-for-normal-distributions}
-
-As soon as we move away from univariate distributions parameterized by
-their mean, it becomes less clear how the likelihood ratio for
-\(H_0: \mu = \tau\) and \(H_1: \mu = \hat{\mu}\) should be calculated.
-In the case of Normal distributions with unknown mean and unknown
-variance, given that the variance and mean estimate are linked, we can
-use
-\(H_0: \mu = \tau \land \sigma^2 = \sigma^2_{\tau} = \frac{1}{n}\sum_{i=1}^{n}(x_i-\tau)^2\)
-and the alternative hypothesis based on the maximum likelihood estimates
-\(H_1: \mu = \hat{\mu} \land \sigma^2 = \hat{\sigma}^2 = \frac{1}{n}\sum_{i=1}^{n}(x_i-\hat{\mu})^2\).
-In the following, we assume \(\epsilon = 0\) for simplicity.
-
-At each round \(t\), the algorithm computes \(T_i(t)\) and
-\(\hat{\mu}_i(t)\) as before, and additionally the empirical variances
-\(\sigma_{\tau,i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\tau)^2\)
-and
-\(\hat{\sigma}_{i}^2(t) = \frac{1}{T_i(t)}\sum_{s=1}^{T_i(t)}(x_{i,s}-\hat{\mu})^2\),
-where \(\hat{\sigma}_{i}^2(t) < \sigma_{\tau,i}^2(t)\) if
-\(\hat{\mu} \neq \tau\) since \(\hat{\mu}\) is the maximum likelihood
-estimate. The index is then
-
-\begin{align*}
-B_i^{SLR_{2D}}(t+1) & = -\log\big(LR(\tau, \sigma_{\tau,i}^2(t)||\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t))\big) \\
-& = T_i(t) \log\Big(\frac{\sigma_{\tau,i}^2(t)}{\hat{\sigma}_i^2(t)}\Big) \\
-& = T_i(t) \KL\big(N(\hat{\mu}_i(t),\hat{\sigma}^2_{i}(t))||N(\tau, \sigma_{\tau,i}^2(t))\big) \Alignyesnumber\label{eqn:SLR2DIndex}
-\end{align*}
-
-Then, as for the univariate case, the next arm to be pulled is the
-minimizer of the index \(B_i^{SLR_{2D}}(t+1)\),
-\(I_{t+1} = \arg \min_{i \leq K} B_i(t+1)\). At the end of the horizon
-\(T\), the algorithm outputs the set of arms
-\(\hat{S}_\tau = \{i \in \mathbb{A}, \hat{\mu}_i(T) \geq \tau\}\).
-
-\IncMargin{1em}
-
-\begin{algorithm}
-\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
-\Input{\emph{$\tau$, $\epsilon$, $\nu(\mu, \theta) = N(\mu,\sigma^2) \, \forall i \in \mathbb{A}$, where $\mu$ and $\sigma^2$ are unknown}}
-\Output{$\hat{S}_\tau = \{i \in \mathbb{A},  \hat{\mu}_i(T) \geq \tau\}$}
-\BlankLine
-\emph{Pull each arm twice}\;
-\For{$t = 2K+1$ \KwTo $T$}{
-\For{$i = 1$ \KwTo $K$}{
-  \emph{Compute $\hat{\sigma}^2_{i}(t)$}\;
-  \If{$\hat{\sigma}^2_{i}(t) = 0$}{\emph{Set $\hat{\sigma}^2_{i}(t) = 1/T$}}
-}
-  \emph{Pull arm $I_t = \arg \min_{i\leq K} B_i^{SLR_{2D}}(t)$ as in \autoref{eqn:SLR2DIndex}}\;
-  \emph{Observe reward $X_t \sim \nu_{I_t}$}\;
-}
-\caption{2D-SLR algorithm for Normal distributions with unknown mean and unknown variance}\label{algo_slr_2d}
-\end{algorithm}
-
-\DecMargin{1em}
-
-\subsection{Discussion}\label{discussion-1}
-
-At the beginning of this thesis, we set out to find an algorithm that
-improves upon the Anytime Parameter Free algorithm introduced in
-Locatelli et al. (2016) for the thresholding bandit problem in two
-points. First, we wanted to make the algorithm perform better in
-problems with arms that are not well approximated as sub-Gaussian; in
-particular a problem with Bernoulli arms of small means, and with a
-threshold close to 0. We thus tried to find a strategy that takes more
-information about the arms into account than purely the sample mean.
-With the Simple Likelihood Ratio strategy, we propose an algorithm that
-fulfills this goal at the cost of being distribution specific.
-
-The SLR strategy requires the knowledge of the class of distribution
-upfront, just as other algorithms require parameters. While this is
-likely to be a negligiable problem in the case of \(\{0,1\}\)
-observations whose mean can be modeled reasonably by Bernoulli
-distributions, it can be more difficult to know the true class of
-distributions upfront when \(\nu_i\) are continuous distributions. We
-have shown however, that the SLR strategy can be adapted to all
-univariate distributions in the exponential family of distributions. The
-algorithm even offers a natural adaptation to the problem of normal
-distributions with unknown mean and unknown variance.
-
-Furthermore, the SLR strategy reduces to the APT strategy in the case
-where arms are normally distributed with equal variance that is known
-upfront. In that case we have as index (compare example 3 above): \[
-B_i^{SLR}(t) = T_i(t)\frac{(\hat{\mu}_i(t) - \tau)^2}{2\sigma^2}.
-\] In order to decide at time \(t\) which arm to draw next, we
-necessarily compare the indexes of arm \(i\) and arm \(j\). Assume
-w.l.o.g. that \(B_i^{SLR}(t) < B_j^{SLR}(t)\). Then:
-
-\begin{align*}
-B_i^{SLR}(t) < B_j^{SLR}(t) & \Leftrightarrow 
-T_i(t)\frac{(\hat{\mu}_i(t) - \tau)^2}{2\sigma^2} < T_j(t)\frac{(\hat{\mu}_j(t) - \tau)^2}{2\sigma^2} \Alignyesnumber\label{eqn:SLRWithKnownVar}\\
-& \Leftrightarrow 
-\sqrt{T_i(t)}\sqrt{(\hat{\mu}_i(t) - \tau)^2} < \sqrt{T_j(t)}\sqrt{(\hat{\mu}_j(t) - \tau)^2} \\
-& \Leftrightarrow 
-B_i^{APT}(t) < B_j^{APT}(t)
-\end{align*}
-
-Given that in all other cases the SLR is able to take more information
-about the distributions into account through the Kullback-Leibler
-divergence (in the case of the exponential family of distributions), the
-algorithm is expected to improve upon the APT strategy. Just consider a
-situation of known, but different variances for Normal distributions.
-Then we had in \autoref{eqn:SLRWithKnownVar} \(\sigma_i^2\) and
-\(\sigma_j^2\) instead of \(\sigma^2\), which should lead to more pulls
-of the arm with larger variance. This is not taken into account by APT.
-
-As mentioned before, this improvement comes only at the cost of knowing
-the correct distribution upfront. In particular, as for the APT
-algorithm, there are no parameters which need to be tuned upfront as is
-usually the case for upper-confidence bound based algorithms (see for
-example UCB-E in Audibert et al., 2010).
-
-Additionally, the index used in the SLR algorithm offers the same
-interpretation considered in \autoref{sec:EVTAlgorithm}. Write the index
-again as \[
-B_i(t) = S_i(t) D_i(t),
-\] where \(S_i(t)\) is a confidence term of the estimate of the arm
-\(i\) at time \(t\), and \(D_i(t)\) is a measure of distance between the
-distribution of arm \(i\) and the threshold \(\tau\). The index of the
-Simple Likelihood Ratio strategy for univariate exponential family
-distributions can then be written with \[
-S_i(t) = T_i(t) \quad \text{and} \quad
-D_i(t) = \KL(\hat{\mu}_i(t)||\tau),
-\] where we employ the number of pulls so far for a given arm as the
-confidence measure, while the Kullback-Leibler divergence fulfills its
-role as distance measure between distributions (see also Figure 2). The
-larger the Kullback-Leibler divergence, the less inclined we are to draw
-the arm; the same holds, if we have pulled an arm many times. Since the
-KL-divergence reduces to the squared distance between means for Normal
-distributions of known variance, the SLR and APT algorithms are
-identical in this case.
-
-As we see in the experiments that follow, the SLR strategy is able to
-improve significantly upon the APT strategy in many cases.
-
-\section{\texorpdfstring{Experiments
-\label{chap:Experiments}}{Experiments }}\label{experiments}
-
-We now compare the algorithms introduced in the previous chapters in
-simulations and experiments against each other to evaluate their
-performance. We first perform experiments on synthetic data in
-\autoref{sec:SyntheticData}. We then use Bernoulli time series data
-collected by the online shop Amorelie to evaluate the algorithms on real
-world data in \autoref{sec:RealData}.
-
-We compare the empirical performance of the SLR algorithm not only
-against the APT algorithm, but also against the variance-based
-algorithms. Thus we also compare the variance-based algorithms for the
-first time directly against each other. As benchmark, the uniform
-sampling strategy is included. Additionally, we include the Bayes-UCB
-algorithm introduced in Kaufmann et al. (2012) for the cumulative regret
-setting. See \autoref{sec:AppendixBUCB} in the appendix for how we adapt
-the Bayes-UCB algorithm to the thresholding bandit problem.
-
-\subsection{\texorpdfstring{Synthetic Data
-\label{sec:SyntheticData}}{Synthetic Data }}\label{synthetic-data}
-
-Each of the following five simulations is repeated for 5000 iterations.
-Depending on the simulation, the observations are generated randomly by
-a given exponential family of distributions. As we are primarily
-concerned with improving upon APT with respect to non-sub-Gaussian
-distributions, the first three simulations focus on Bernoulli
-distributions, especially those with small means. We then go on to show
-with experiments on data from the Exponential distribution and Poisson
-distribution that the SLR strategy can be adapted to other distributions
-as well.
-
-\subsubsection{\texorpdfstring{Simulation 1: Bernoulli Arms and
-\(\tau = 0.5\)}{Simulation 1: Bernoulli Arms and \textbackslash{}tau = 0.5}}\label{simulation-1-bernoulli-arms-and-tau-0.5}
-
-The first experiment is equal to experiment 3 in Locatelli et al. (2016)
-to achieve a baseline comparison. We compare ten Bernoulli arms that
-move away from the threshold at \(\tau = 0.5\) geometrically with
-\(\mu_{1:4} = 0.4-0.2^{1:4}\), \(\mu_5 = 0.45\), \(\mu_6 = 0.55\), and
-\(\mu_{7:10} = 0.6 + 0.2^{5-1:4}\). We run the standard APT algorithm as
-well as the SLR algorithm with \(\epsilon = 0.1\). We compare them to
-the AugUCB algorithm with the parameter choice of \(\rho = 1/3\) as used
-by its authors in Mukherjee et al. (2017). We run the parameter-free
-EVT\(_{pf}\) algorithm without feedback delay, thus making it directly
-comparable to the other algorithms. The Bayes-UCB algorithm is run with
-\(c=1\) and takes as prior a Beta distribution with parameters
-\(\alpha_0 = \tau\) and \(\beta_0 = 1 - \tau\), thus leading to a mean
-of the prior distribution at \(\frac{\alpha_0}{\alpha_0+\beta_0}=\tau\)
-while keeping the prior as weak as possible. Lastly, we run the uniform
-sampling strategy as a benchmark.
-
-\begin{longtable}[]{@{}rrrrrrrrrr@{}}
-\caption{Mean of arms in simulation 1.}\tabularnewline
-\toprule
-V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
-\midrule
-\endhead
-0.2 & 0.36 & 0.392 & 0.398 & 0.45 & 0.55 & 0.602 & 0.608 & 0.64 &
-0.8\tabularnewline
-\bottomrule
-\end{longtable}
-
-This first experiment is a problem in which all algorithms should be
-able to perform well. The problem is not very difficult with
-\(H_1^{APT} \approx\) 232, and due to \(\tau = 0.5\), the Bernoulli
-distribution can be well approximated by a Gaussian. This is the perfect
-environment for the APT algorithm.
-
-As the next figure shows, essentially all methods converge rapidly to an
-error rate of very close to zero, where the error rate is the share of
-the 5000 simulations on which the classification of the algorithm is
-wrong. Only the uniform strategy that clearly lacks behind. We also
-observe that the variance based algorithms (AugUCB and EVT) lag behind
-at first. AugUCB is able to adjust its sampling scheme only after 1000
-iterations but then rapdily improves to the level of APT. EVT takes
-about 250 samples more to start a quick descend to the performance of
-the other algorithms. All of this, however, happens after the algorithms
-are below an error rate of 0.01. While the SLR algorithm improves upon
-APT, the improvement is a slight one, and not very large in terms of
-budget difference. This underlines that the scenario at hand is ideal
-for the APT algorithm.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation1_results-1}
-
-}
-
-\caption{Performance comparison of algorithms for simulation 1.}\label{fig:simulation1_results}
-\end{figure}
-
-\subsubsection{\texorpdfstring{Simulation 2: Bernoulli Arms and
-\(\tau = 0.05\)
-\label{sec:Simulation2}}{Simulation 2: Bernoulli Arms and \textbackslash{}tau = 0.05 }}\label{simulation-2-bernoulli-arms-and-tau-0.05}
-
-\begin{longtable}[]{@{}rrrrrrrrrr@{}}
-\caption{Mean of arms in simulation 2 classified against threshold of
-0.05.}\tabularnewline
-\toprule
-V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
-\midrule
-\endhead
-0.001 & 0.005 & 0.01 & 0.015 & 0.04 & 0.06 & 0.085 & 0.09 & 0.095 &
-0.099\tabularnewline
-\bottomrule
-\end{longtable}
-
-In the second experiment, we compare the same algorithms as in the first
-experiment. Again, we classify 10 arms, but this time against a
-threshold of \(\tau = 0.05\) and without an epsilon interval,
-\(\epsilon = 0\) (which generally rewards algorithms for pulling arms
-close to the threshold). We choose the means of the arms to be much
-smaller too, and arrange them symmetrically around the threshold. While
-the distributions are bounded and thus still sub-Gaussian, the Normal
-approximation should be poor in comparison to the previous case. We
-expect an improvement for SLR compared to APT as SLR takes the Bernoulli
-characteristics into account. In particular, even though the arms are
-symmetrically distributed around the threshold in terms of absolute
-distance, they are not symmetrically around the threshold in terms of
-their Kullback-Leibler divergence (compare Figure 2). Thus we expect the
-SLR algorithm to not pull them symmetrically. Furthermore, we expect an
-improvement for the variance-based algorithms, as the variances are now
-smaller than in the first simulation, which should benefit the EVT
-algorithm given its theoretical analysis in Zhong et al. (2017).
-
-The figure below shows the performance of all algorithms. The results
-underline that this problem is much harder in general
-(\(H_2^{APT} \approx 24703\)). The performance of the variance based
-algorithms is surprisingly poor; EVT performs even worse than uniform
-sampling until close to the horizon, while Augmented UCB takes a long
-time to adjust away from uniform sampling. Both algorithms perform worse
-than APT after 7000 samples.
-
-The Simple Likelihood Ratio strategy improves considerably upon the
-alternative strategies. SLR reaches the average empirical error of 0.1
-within the budget, and it improves at an exponential rate within the
-entire budget; in contrast to APT which appears to improve linearly in
-the observations. At the end of the budget, the difference in the
-empirical error is nearly 10\% between the two strategies.
-
-In order to assess how the SLR strategy improves upon the APT algorithm,
-it is useful to look at how the algorithms allocate their sampling
-budget across arms. Given that we run the simulation 5000 times, we can
-compare across simulations how often an algorithm pulls each arm at a
-given round. During the 5000 iterations, the algorithm should pull at
-any given iteration the arm most often that it thinks is the most
-difficult to classify. In Figure 6, we plot the resulting curves where
-the y-axis shows a 10-round moving average of the pulls to remove some
-variation.
-
-The graph shows that both APT and SLR correctly single out the two arms
-closest to the threshold, and allocate most of the budget to them.
-However, while SLR keeps the two arms constant at two different levels
-(about 1900 for arm 5 and about 2500 for arm 6), APT at first pulls arm
-5 more often than arm 6. Then, for \emph{both} arms, the budget appears
-to converge to about 2000. Given that the two arms are symmetric around
-the threshold, it makes sense that APT would allocate the same
-exploration effort to them. And given that the variation of arm 5 away
-from the threshold is limited from below by zero, it is much easier for
-arm 6 to have an empirical mean larger than its true mean, and thus to
-have a larger index than arm 5 in the beginning. Consequently, APT would
-prefer to sample arm 5. This, however, is wrong in terms of
-Kullback-Leibler divergence. Measured by the divergence, arm 6 is closer
-to the threshold than arm 5, thus harder to classify, and consequently
-preferred by the SLR algorithm. Furthermore, the SLR algorithm appears
-to quickly find the correct share that it has to allocate to the two
-arms. This is in contrast to APT which continues to adjust the shares
-across the entire budget.
-
-Additionally, we can observe that the SLR strategy starts to drop arms
-much quicker than APT, and it drops arm 1 to 3 first, which again
-underlines the effect of the asymmetric Kullback-Leibler divergence. If
-we consider arm 3 and arm 8, we have \(d_3(0.01||0.05) \approx 0.025\)
-while \(d_8(0.09||0.05) = 0.014\). The divergence is much smaller for
-arm 8. The asymmetry is even more dramatic for arm 1 and arm 10 with
-\(d_1(0.001||0.05) \approx 0.046\) and
-\(d_{10}(0.099||0.05) \approx 0.020\): In terms of the divergence, the
-distance between arm 1 and the threshold is twice as far as between arm
-10 and the threshold. APT considers them to be equally distant from the
-threshold.
-
-One interesting observation, that we will observe in all simulations
-with Bernoulli arms, is the superior performance of the Bayes-UCB
-algorithm adapted from Kaufmann et al. (2012) which was originally
-designed for cumulative regret problems. Nonetheless, the algorithm
-proves again and again to be the best performing. Compare with
-\autoref{sec:AppendixBUCB} for more analysis on the behavior of the
-Bayes-UCB algorithm in simulation 2. In particular, consider Figures 17
-and 18 which show for individual arms the distribution of pulls for that
-arm across simulations. The distributions highlight that both the APT
-and SLR fail in many iterations of the simulations to pull arms
-frequently enough to estimate their correct mean. The APT algorithm
-pulls the most difficult arm (Arm 6) in more than 5\% of the simulations
-only once (during initialization). Consider arm 6 returns
-\(X_{6,1} = 1\) as its first observation. Then
-\(B_6(t+1) = 1 \cdot |1-0.05| = 0.95\). It will then not be pulled for a
-long time because its index is very large. Indeed, consider some arm
-that has been pulled 4000 times with \(\mu_i(4000) = 0.03\). Then
-\(B_i(t+1) = \sqrt{2000} \cdot |0.05-0.03| \approx 0.89\). Even though
-we have basically no evidence for the performance of arm \(6\), we would
-continue to pull arm \(i\). Similar holds for the SLR algorithm. For
-both, the distribution of pulls for arm 6 is very flat across the
-interval of \([1,6000]\) pulls. In contrast, the distribution of pulls
-appears normally distributed for the Bayes-UCB algorithm with the mode
-between 2100 and 2300 pulls. The numerical problem that arises for the
-APT and SLR algorithms might be weakened for the Bayes-UCB algorithm by
-the combination of a (weak) prior that shrinks the mean estimates, and
-the way in which quantiles are based on the posterior. Also, the fact
-alone that it is based on confidence bounds of the empirical mean,
-instead of the empirical mean itself. We show in the appendix that the
-problem does not only occur for arm 6.
-
-Empirically, part of this problem can be alleviated by including the
-D-Tracking rule proposed by Garivier and Kaufmann (2016) and discussed
-in \autoref{sec:OptimalBestArmIdentification} into the SLR algorithm, as
-it ensures that no arm is ``left behind'' in terms of samples. Figure 5
-shows a significant improvement for the SLR-D algorithm in comparison to
-the SLR algorithm without D-Tracking. However, the algorithm still does
-not reach the performance of Bayes-UCB.
-
-Lastly, we remark on the shape of the error curve of the uniform
-strategy. Even though the uniform strategy samples arms at random from
-the set of arms with the least observations at any round, we observe a
-sawtooth pattern for simulation 2 and 3. This is an artifact of the
-comparison against the threshold of \(0.05\) and \(0.01\) respectively,
-combined with the discrete \(0\) and \(1\) observations. Take for
-example an arm with a true mean of \(\mu = 0.06\) compared against
-\(\tau = 0.05\). Let's say the arm observes the first 1 after 15
-samples, \(X_{15} = 1\), such that
-\(\hat{\mu}(15) = 1/15 \approx 0.067\). At this point, it is correctly
-classified as above the arm. Even if the next samples are zeroes, it
-will continue to be correctly classified until observation 20. At that
-point, \(\hat{\mu}(20)\) = 1/20 = 0.05. By observing one more
-observation, the arm will be classified as below the threshold, since
-then \(\hat{\mu}(21) = 1/21 < 0.05 = \tau\). The classification is
-suddenly wrong for no particular reason, and a sudden spike in the error
-curve occurs. In the graph of simulation 3 it is obvious that the spike
-occurs with a period length of about 100 samples, which corresponds to
-\(\tau = 0.01=1/100\). This explains why we do not observe such a
-pattern in the first simulation with \(\tau = 0.5\), or for the
-continuous Exponential distribution in simulation 4.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation2_results-1}
-
-}
-
-\caption{Performance comparison of algorithms for simulations 2 and 3. Note the different x-axes.}\label{fig:simulation2_results}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-1-1}
-
-}
-
-\caption{Budget allocation across arms for APT and SLR algorithms in simulation 2.}\label{fig:unnamed-chunk-1}
-\end{figure}
-
-\subsubsection{\texorpdfstring{Simulation 3: Bernoulli Arms and
-\(\tau = 0.01\)}{Simulation 3: Bernoulli Arms and \textbackslash{}tau = 0.01}}\label{simulation-3-bernoulli-arms-and-tau-0.01}
-
-In the third experiment, we lower the threshold further to
-\(\tau = 0.01\) and arrange now \(K=11\) arms on a \(\log_{10}\) scale
-around it. Again, we set \(\epsilon = 0\). We compare the same
-algorithms as previously with the settings adapted to \(\tau\) and
-\(\epsilon\) accordingly. Notice that the experiment horizon is now
-\(T=10000\) rounds instead of \(T=7000\) rounds in the previous
-experiment.
-
-\begin{longtable}[]{@{}rrrrrrrrrrr@{}}
-\caption{Mean of arms in simulation 3.}\tabularnewline
-\toprule
-V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10 & V11\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10 & V11\tabularnewline
-\midrule
-\endhead
-1e-04 & 3e-04 & 6e-04 & 0.001 & 0.0018 & 0.0032 & 0.0056 & 0.0141 &
-0.0178 & 0.0316 & 0.1\tabularnewline
-\bottomrule
-\end{longtable}
-
-Looking at the performance after 7000 rounds, we see that the problem
-appears to be slightly more difficult compared to the previous one
-(\(H_3^{APT} \approx 210359\)). We see that up until this point the
-variance-based strategies cannot improve upon APT. Also, SLR has not yet
-crossed the 10\% empirical error. We observe that in the following
-rounds EVT decreases at an exponential rate and thus crosses the error
-of APT and continues to improve. At the end of the budget, the
-improvement of SLR compared to the other algorithms is again large, and
-likely to increase. However, Bayes-UCB is again the best performing
-algorithm and is improving at a faster rate than SLR. As in the previous
-experiment, Bayes-UCB and SLR show significant improvements on this
-Bernoulli problem with very small means and threshold compared to APT in
-particular. Furthermore, the observation that the SLR algorithm with
-D-Tracking rule performs better than without is replicated.
-
-\subsubsection{Simulations 4 and 5: Exponential and Poisson
-Distributions}\label{simulations-4-and-5-exponential-and-poisson-distributions}
-
-In \autoref{sec:LRforUnivariateExponentialFamily}, we show that the
-likelihood ratio has a very useful form for the one-parameter
-exponential family of distributions, which allows us to use the SLR
-algorithm not only on Bernoulli arms, but also on Exponential or Poisson
-distributions, for example. In simulation 4, we consider Exponential
-distributions, in simulation 5, we test the algorithms on Poisson
-distributions.
-
-We run the same algorithms as before except for Bayes-UCB (even though
-it should certainly be possible to adapt it to these case based on a
-Gamma prior). In the case of the Exponential arms, we classify against
-\(\tau = 1\) and have sampled the arms' mean parameters from an
-Exponential distribution with rate \(\theta = 1\). The Poisson arms are
-classified against a threshold of \(\tau = 0.4\), with the mean
-parameters being sampled from an Exponential distribution with mean
-\(\mu = 0.7\). In both cases, we classify 20 arms.
-
-For the Exponential arms, APT crosses the 10\% error mark first,
-followed by the AugUCB algorithm. All algorithms perform better than
-uniform sampling. After more than half of the budget, the SLR algorithm
-jumps in performance and performs better than APT and AugUCB. Indeed,
-the AugUCB basically stops improving after half of the budget. This is a
-consequence of it eliminating arms it believes to know very well. This
-happens at an error rate of less than \(0.01\). On average, the AugUCB
-samples only for 2564 rounds of the budget of 4000 rounds across the
-5000 simulations.
-
-The early elimination (when compared to the Bernoulli experiments) might
-be caused by the fact that the AugUCB assumes the variance of the arms
-to be in \([0,1]\), which does not hold for half of the arms in the
-experiment. Similar goes for the EVT algorithm which is only able to
-catch up at the very end of the budget.
-
-In the case of Poisson arms, the performance of the arms is more clear
-cut. As expected, SLR improves upon APT. APT outperforms the EVT
-algorithm, which occurs even though the variance of all arms considered
-in this experiment is in \([0,1]\). After about 1000 observations, APT
-and EVT appear to improve at about the same rate, but APT has a much
-better initial exploration phase. Given the previous simulations, it is
-surprising to see the Augmented-UCB algorithm to come ahead after
-\(T=10000\) observations. After about half the budget, the same pattern
-as before occurs where there is a drastic change in sampling behavior.
-This suffices to outpace both APT and SLR.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation5_results-1}
-
-}
-
-\caption{Performance comparison of algorithms for simulations 4 and 5. Note the different x-axes.}\label{fig:simulation5_results}
-\end{figure}
-
-\subsection{\texorpdfstring{Experiments on Web Analytics Data
-\label{sec:RealData}}{Experiments on Web Analytics Data }}\label{experiments-on-web-analytics-data}
-
-In the following, we present the results of two experiments performed on
-a real world data set. While most multi-armed bandit algorithms are
-assessed on synthetic data, as we have done in
-\autoref{sec:SyntheticData}, a real world data set is useful to observe
-how algorithms perform in presence of, for example, not perfectly i.i.d.
-samples. Every company of course tries to run their algorithms under
-settings as ideal as possible, but there will always be problems. Thus
-our experiments serve as a first robustness check on the algorithms
-introduced before.
-
-\subsubsection{The Data Set}\label{the-data-set}
-
-Data have been collected by the German online shop
-\href{https://amorelie.de}{Amorelie} as part of standard website
-analytics. For 197 selected products, we observe the number of users
-visiting each product's detail page (PDP) during a given minute. The
-data set we use here has been collected during the entire month of
-November 2016. It can be considered time series data collected at
-minutely frequency. Thus the data contain 43200 observations per
-product, and overall 8510400 observations.
-
-Since we want to run an offline comparison of bandit algorithms, it is
-important to have at each time point an observation for each arm. Given
-that, it is easy to evaluate the perfomance of algorithms that make
-different decisions at different point in times and thus do not observe
-the same samples. By having an observation for each arm at any given
-time point, each algorithm had at least the opportunity to observe a
-certain sample. Other papers (for example, Li et al., 2011) have solved
-this problem by using a sample drawn uniformly during, for example, an
-A/B test. Then, if the next observation in the sample is not from the
-same arm that the algorithm would like to draw from, observations are
-discarded until the next observation from the selected arm.
-
-The choice of using what is basically multiple time series data as the
-sample offers a simple way of running the algorithms just as often on
-the data as for simulated data. The goal is to perform 5000 runs over
-the sample to confidently assess the performance. Since we would like to
-preserve potential time dependencies in the data, a simple resampling of
-the data is not an option to create the needed 5000 variations of the
-sample. Instead we perform time series cross validation. To preserve the
-autocorrelation, one can create different samples of \(X\) observations
-by sliding a window of size \(X\) over the time series. Moving the
-window one period (in our case one minute) at a time, one ensures that
-no sample shares start and end observation with another sample. In
-particular, this means for a given bandit strategy and two samples that
-the observations that the algorithm collects as feedback during the
-initialization phases differ from sample to sample and are never the
-same. This is because during initialization every strategy pulls arms
-\(1, ..., K\) (or \(1,...,2K\) for EVT) once in this order.
-
-\begin{longtable}[]{@{}llrrrrr@{}}
-\caption{Example of the binary time series data for five
-products.}\tabularnewline
-\toprule
-& SessionDateTime & V104 & V110 & V150 & V112 & V154\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-& SessionDateTime & V104 & V110 & V150 & V112 & V154\tabularnewline
-\midrule
-\endhead
-1000 & 2016-11-01 16:39:00 & 0 & 0 & 0 & 0 & 0\tabularnewline
-1001 & 2016-11-01 16:40:00 & 0 & 0 & 0 & 0 & 1\tabularnewline
-1002 & 2016-11-01 16:41:00 & 0 & 0 & 0 & 0 & 1\tabularnewline
-1003 & 2016-11-01 16:42:00 & 0 & 0 & 0 & 0 & 0\tabularnewline
-1004 & 2016-11-01 16:43:00 & 0 & 0 & 1 & 0 & 1\tabularnewline
-1005 & 2016-11-01 16:44:00 & 0 & 0 & 0 & 0 & 0\tabularnewline
-\bottomrule
-\end{longtable}
-
-While the data set consists of count data (the number of visits to a PDP
-during a given minute), we binarize the data by applying a certain
-threshold. If the count is above this threshold, the new observation is
-\(1\), else \(0\). Thus we have a binary time series of length
-\(60\cdot 24 \cdot 30 = 43200\) for each of the 197 products. Given that
-the number of visitors that reach a given PDP is likely to vary by time
-of day and by day, and in general over time, we expect the mean of the
-time series to not be stable over time. For example, less visitors visit
-during night than during the evening. This leads to a decrease in the
-average number of visits, and creates a daily seasonality. On the other
-hand, more users may visit the site during a weekend, thus leading to a
-spike on Saturdays and Sundays. Because of the latter time dependency,
-it is best practice to run online A/B tests for at least a
-week\footnote{See for example the ``A/B Testing in the Wild''
-  presentation by Emily Robinson, \url{https://youtu.be/SF-ryGgLOgQ}},
-or an integer multiple of weeks, so as to take into account the weekly
-seasonality in the time series. For this reason, the experiments we
-present below are run on \(60 \cdot 24 \cdot 7 = 10080\) observations
-for each arm, so as to have a sample for one full week.
-
-We can look at summary statistics for the sample means of the 197
-products over the month of November to get a first impression of the
-binary data we are dealing with. We see that most products have a small
-mean, which is very common also for actual conversion rate or
-click-through rate data that can be tested with A/B tests or multi-armed
-bandits. Yet the sample of products contains a few outliers with very
-large view rates, with a maximum rate of 78\%. If we used a threshold
-\(\gamma\) to binarize the count data, then this means that on average
-every fourth minute the count of visitors was below \(\gamma\) for this
-product. On the other hand, we conclude that using thresholding bandit
-strategies to test the products against a threshold of for example
-\(\tau = \frac{2}{60} = 0.0333\) or \(\tau = \frac{5}{60} = 0.083\) is
-likely to create more complex problems than a threshold of, say,
-\(\tau = \frac{15}{60} = 0.25\) would.
-
-\begin{longtable}[]{@{}rrrrrr@{}}
-\caption{Summary Statistics for View Rates of 197
-Products}\tabularnewline
-\toprule
-Mean & Minimum & 25\% Quantile & Median & 75\% Quantile &
-Maximum\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-Mean & Minimum & 25\% Quantile & Median & 75\% Quantile &
-Maximum\tabularnewline
-\midrule
-\endhead
-0.12 & 0 & 0.036 & 0.074 & 0.136 & 0.778\tabularnewline
-\bottomrule
-\end{longtable}
-
-\subsubsection{Experiment 1}\label{experiment-1}
-
-In the first experiment, we pick ten arms randomly from the set of 197
-arms. The experiment is run with a budget of \(T=10080\) samples for
-each of the \(5000\) iterations for which we repeat the experiment.
-Given the time series cross-validation idea described above, this means
-that in total, \(15080\) observations of the \(43200\) available
-observations per arm are used in training. In the thresholding bandit
-problem, we classify arms as below or above a threshold. Thus we can
-evaluate the strategies also based on whether their classifications are
-correct in a holdout sample (the time period after training). As this
-holdout sample, we can use the 10080 observations in our data set that
-follow the first 15080 observations used in training. In the table
-below, we present the count rates of the ten products for both training
-and test samples.
-
-\begin{longtable}[]{@{}lrrrrrrrrrr@{}}
-\caption{Training and test sample means for experiment
-1.}\tabularnewline
-\toprule
-& V1 & V159 & V64 & V139 & V189 & V70 & V114 & V148 & V118 &
-V119\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-& V1 & V159 & V64 & V139 & V189 & V70 & V114 & V148 & V118 &
-V119\tabularnewline
-\midrule
-\endhead
-Training & 0.001 & 0.013 & 0.027 & 0.053 & 0.059 & 0.071 & 0.071 & 0.102
-& 0.156 & 0.158\tabularnewline
-Test & 0.000 & 0.011 & 0.022 & 0.055 & 0.058 & 0.064 & 0.060 & 0.115 &
-0.150 & 0.130\tabularnewline
-\bottomrule
-\end{longtable}
-
-We see that while the rates do vary across training and test samples,
-they are relatively stable which is likely due to the fact that the
-samples come from an entire week's worth of observations. In particular,
-since we test against a threshold of \(\tau = \frac{2}{60} = 0.0333\) in
-this experiment, the true classifications of arms do not differ across
-training and test data. A correct classification after training will be
-correct in the test set. For the rest of the analysis, we thus evaluate
-the performance using the training rates.
-
-In order to visualize the time dependency that we expect for our
-samples, we plot a moving average of the mean of the time series for the
-first week of data. To remove daily seasonality, we select a sliding
-window of \(60\cdot24 = 1440\) observations. To make the time dependency
-even more obvious, we contrast the actual data against synthetic data
-generated using the sample means of the actual data.
-
-The graph again underlines that arm \(V64\) is likely to be very
-difficult to classify given that its moving average crosses the
-threshold twice. The same is true for arm \(V139\), which is not visible
-when looking at the overall mean alone. Furthermore, arms \(V159\) and
-\(V189\) come very close to the threshold at times.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-4-1}
-
-}
-
-\caption{Moving average for the arms used in experiment 1.}\label{fig:unnamed-chunk-4}
-\end{figure}
-
-These difficulties seem to have a large impact on the performance of all
-algorithms. Given that the data are binary observations, we can compare
-all algorithms in a setting in which one expects all assumptions to hold
-before having observed the data: The distributions are sub-Gaussian for
-the APT algorithm, bounded between \(0\) and \(1\) for the
-variance-based algorithms, and assumed to be Bernoulli for the SLR
-algorithm. Additionally, we use the Bayes-UCB algorithm as it performed
-best on the synthetic data. We set \(\epsilon = 0\), and
-\(\tau = 2/60\). For the AugUCB algorithm we use the parameters as in
-Mukherjee et al. (2017), that is, \(\rho = 1/3\). For Bayes-UCB we set
-the prior to \(\alpha_0 = \tau\) and \(\beta_0 = 1-\tau\), and pick
-\(c=1\).
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-5-1}
-
-}
-
-\caption{Performance comparison of algorithms for experiment 1.}\label{fig:unnamed-chunk-5}
-\end{figure}
-
-Compared to the previous simulations with synthetic data, the results
-are dramatically poor. First of all, we see that all strategies perform
-poorly. All of them end above the 10\% error rate mark after 1 week of
-data. Second, the uniform sampling strategy fares best when evaluated
-against the sample mean of all observations used during training. This
-of course is the opposite of what we would like to see, and the opposite
-of what we saw on the synthetic data, where we were able to improve upon
-the naive strategy. Third, again in contrast to the results on synthetic
-data, we observe non-monotonicity in the error curves. Given that the
-highs and lows for the different models run mostly parallel, it stands
-to reason that this effect is caused by the variation in means of the
-arms over time. Indeed, roughly comparing the error curves to the moving
-averages in the previous figure, the increase in errors after round
-\(5000\) and the decreasing error after round \(7500\) seems to line up
-with the fluctuations observed in the data. Given that we evaluate the
-models against a sample mean of all observations, it is not surprising
-that the uniform sampling strategy has a certain advantage when it comes
-to ``factoring out'' the seasonalities. In contrast, the adaptive
-sampling schemes try to adapt more or less quickly to the changes in the
-means--a feature that would be valuable in a cumulative regret
-multi-armed bandit setting. Here, however, it leads to wrong estimates
-of the overall sample mean.
-
-If we focus on a comparison of adaptive sampling strategies and less on
-their globally bad performance, we see that the variance based
-strategies perform worse than APT and SLR. Very dramatic is the behavior
-of the Augmented-UCB algorithm, which first seems to perform well; this,
-however, is a result of it pulling arms mostly uniformly, until it
-starts to adapt its sampling and discarding arms after nearly 5000
-rounds. The result is a dramatic increase in error which leads to the
-worst performance at the budget horizon. The differences between APT,
-SLR, and EVT are small, and their performance fluctuates in sync. None
-of them is really able to converge due to the changes in the underlying
-means. Advantageous only seems to be the fact that their behavior is
-less erratic than that of the AugUCB strategy given that they do not
-discard arms.
-
-\subsubsection{Experiment 2}\label{experiment-2}
-
-In order to underline the results of the previous experiment, we perform
-a second experiment using the data collected by Amorelie. We increase
-the threshold to \(\tau = \frac{5}{60} = 0.833\) to make the problem in
-general slightly easier, and again pick 10 arms at random from the data
-set of 197 arms. We again use a sliding window of \(10080\) observations
-to create \(5000\) iterations and look at the training and test sample
-means as in the previous experiment.
-
-Some arms, in particular \(V110\) and \(V150\), but also \(V103\),
-\(V149\), \(V104\), and \(V112\) are quite close to the threshold. Two
-arms, \(V129\) and \(V32\) appear to have basically no positive
-observation in the training set. On the other hand, arm \(V154\) is
-larger than the threshold by a fair amount and should be easier to
-classify.
-
-\begin{longtable}[]{@{}lrrrrrrrrrr@{}}
-\caption{Training and test sample means for experiment
-2.}\tabularnewline
-\toprule
-& V112 & V129 & V104 & V76 & V103 & V110 & V150 & V149 & V32 &
-V154\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-& V112 & V129 & V104 & V76 & V103 & V110 & V150 & V149 & V32 &
-V154\tabularnewline
-\midrule
-\endhead
-Training & 0.000 & 0 & 0.012 & 0.044 & 0.049 & 0.053 & 0.055 & 0.095 &
-0.123 & 0.199\tabularnewline
-Test & 0.013 & 0 & 0.011 & 0.040 & 0.049 & 0.063 & 0.060 & 0.114 & 0.137
-& 0.202\tabularnewline
-\bottomrule
-\end{longtable}
-
-As in the previous experiment, we can also take a look at the one day
-moving averages of the arms to quickly assess the time dependency of the
-means. Given those and the previous experiment, the performance results
-of Experiment 2 shown in Figure 13 are not surprising. We recognize the
-same structure as previously. The uniform sampling strategy performs the
-best. The adaptive sampling strategies perform bad, do not converge, and
-end above the 10\% error rate mark. This time, AugUCB is not (yet) the
-worst performing strategy, but equally erratic after it eventually
-adapts its sampling. This time around, it even has two spikes in its
-adaptive phase. Again, APT, SLR, and EVT perform in sync and more or
-less equally bad, with EVT slightly better than APT and SLR this time
-around. Interestingly, Bayes-UCB performs clearly worst of all
-strategies. Its performance changes at the same time as AugUCB starts to
-adapt its sampling strategy. This last fact is of particular interest,
-as Bayes-UCB is dramatically better than the other strategies in
-experiments on synthetic data.
-
-On the right hand side of figure 13, the performance of the algorithms
-on synthetic data from Bernoulli distributions is depicted. These
-synthetic samples were sampled from distributions with mean equal to the
-sample means of the real data. We thereby create similar samples that
-are perfectly i.i.d. On this data, Bayes-UCB performs very well, ending
-at an average error rate of about 0.1\%. This mirrors its performance
-observed in the previous simulations with synthetic data. Also all other
-adaptive strategies perform clearly better now, and their error rates
-are strictly decreasing. Interestingly, the uniform sampling scheme is
-now clearly worse than in the experiment on real data; it does no longer
-have the advantage of sampling the different mean phases at a
-representative rate. Excluding Bayes-UCB, we see that the SLR algorithm
-performs the best, followed by the variance-based algorithms. APT comes
-in at the same error rate as uniform sampling. While the difference
-between SLR and EVT is less than 2\% (1.2\% vs 3\%), the difference to
-uniform sampling (10\%) is relevant. The error rate of 10\% is achieved
-by SLR about 1000 observations earlier than by EVT.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-6-1}
-
-}
-
-\caption{Moving average of arms used in experiment 2. Dashed line indicates the threshold.}\label{fig:unnamed-chunk-6}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-10-1}
-
-}
-
-\caption{Performance results of algorithms in experiment 2.}\label{fig:unnamed-chunk-10}
-\end{figure}
-
-Using a plot of the pulls at each round across the 5000 simulations in
-Figure 14, as we did for simulation 2, we can try to understand why some
-strategies perform well on synthetic data, but poorly on the time series
-data.
-
-We observe that the patterns across algorithms are quite similar, while
-the patterns are very different across data sets. On the synthetic data,
-given that arm \(V149\) is clearly the most difficult arm to classify
-due to its closeness to the threshold \(\tau\), all algorithms focus a
-major share of their budget on this arm. The speed at which they start
-to do so, however, differs. Perhaps surprisingly, the best performing
-Bayes-UCB algorithm increases its focus on arm \(V149\) the slowest,
-while in many iterations spending budget on exploring other arms. This
-is surprising as the Bayes-UCB algorithm's exploration factor was
-originally conceived for the cumulative regret problem. Thus one would
-expect it to explore \emph{less} than other algorithms. But its
-performance does not seem to be easily explained by the lessened focus
-on the most difficult arm; else we would expect the APT algorithm to
-perform second best. However, both SLR and EVT perform better than APT
-while converging more quickly to a higher share of samples allocated to
-the most difficult arm.
-
-Something that might be hidden by this aggregated view of all 5000
-iterations are a share of iterations in which the EVT completely fails
-by exploring wrong arms for long periods. This effect might even be more
-drastic for the APT algorithm. Even though it seems as if its behavior
-is very similar to SLR and EVT, the overall performance is not better
-than the performance of uniform sampling. Taking this reasoning into
-account, one can hypothesize that the Bayes-UCB algorithm finds the most
-difficult arm uniformly across most iterations as the rounds increase,
-while other algorithms either find the most difficult arm right away or
-never and thus have many iterations that end with a misclassification.
-
-For the real data, the difference between Bayes-UCB and the other
-algorithms is just as apparent. As is the effect of the time varying
-means of the arms on the rate at which they are sampled. APT, SLR, and
-EVT all focus quickly in many iterations on the still most difficult arm
-\(V149\). However, in the case of the real data this behavior is not
-rewarded in the end, as this leads to biased samples and thus wrong
-estimation of the overall sample mean against which the algorithms are
-evaluated. We see in the curves of arms \(V32\) and arm \(V154\) that
-the EVT algorithm is less impacted by daily seasonalities, while APT
-clearly is.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-11-1}
-
-}
-
-\caption{Budget allocation of algorithms across arms on real and synthetic data in experiment 2.}\label{fig:unnamed-chunk-11}
-\end{figure}
-
-\subsubsection{Experiments Conclusion}\label{experiments-conclusion}
-
-In the two previous experiments, we observe that the real time series
-data poses a major hurdle for the adaptive sampling algorithms. It seems
-that the poor performance can be mostly explained by the seasonality and
-sudden changes in the samples over time. The observations clearly do not
-correspond to i.i.d. Bernoulli samples, but have large time
-dependencies. However, the effect might be overly stark due to the fact
-that we use minutely time series data, which leads to observations even
-in minutes when there are few or no users on the website (during night).
-In contrast, the daily seasonality might be less represented in an
-actual online experiment observations are only drawn when there is an
-actual visitor on the site (and a proper conversion rate would fluctuate
-less than the count of visitors on a given product page).
-
-Furthermore, some of the problems in dealing with the fluctuating
-distributions might be specific to the thresholding bandit problem as
-opposed to the cumulative regret or best-arm identification problems. In
-the experiments above, we observe that the order of the arms is mostly
-unaffected by the seasonalities and fluctuations, which implies that the
-best arm could still be identified. In contrast, given that all arms are
-individually classified against the \emph{fixed} threshold, a weekly
-seasonality can declare a correct classification on the first half of
-the sample null and void on the second half of the sample.
-
-\section{Conclusion}\label{conclusion-1}
-
-\section{Acknowledgements}\label{acknowledgements}
-
-We thank Alexandra Carpentier, Andrea Locatelli, Urun Dogan, and Marius
-Kloft for many hours of fruitful discussions and ideas. We thank Carlo
-Alberto Dall'Amico for bringing our attention to multi-armed bandits in
-the first place. Sonoma Internet GmbH (Amorelie) supported this work by
-giving the authors access to the discussed data set.
-
-\newpage
-
-\section{References}\label{references}
-
-\newpage
-
-\section{Appendix}\label{appendix}
-
-\subsection{\texorpdfstring{Proof of Thresholding Bandit Lower Bound
-\label{sec:AppendixAPTLB}}{Proof of Thresholding Bandit Lower Bound }}\label{proof-of-thresholding-bandit-lower-bound}
-
-We now give a proof for the lower bound for the thresholding bandit
-problem stated in \autoref{theorem:Locatelli2016Theorem1}.
-
-\emph{Proof of Theorem \ref{theorem:Locatelli2016Theorem1}}: Locatelli
-et al. (2016) derive a lower bound for the thresholding bandit problem.
-We restate the proof here. The idea is as follows. The problem
-formulation considered in the paper describes bandit problems for
-\(R\)-sub-Gaussian distributions. To show a lower bound, we show that
-every algorithm is expected to make a certain error even if we consider
-a very restricted scenario. Even then, the best algorithm will have a
-maximum error probability with which it cannot distinguish between the
-actual setting and slightly changed settings (under which the answer for
-the true setting leads to a misclassification).
-
-Consider the thresholding bandit setting as in \autoref{sec:Setup}. More
-specifically, consider a problem in which all arms follow Normal
-distributions \(\nu_i\) with mean \(\mu_i\) and variance
-\(\sigma^2 = 1\). ``in which w''e set \(\tau = 0\) and \(\epsilon = 0\)
-w.l.o.g. Consequently, for each arm \(i\) the distance from the
-threshold is given by \(\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i\).
-Thus, we have for every arm the distribution
-\(\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)\). Furthermore,
-define for each arm \(i \in \{1, \dots, K\}\) the alternative
-distribution \(\nu_i' = \mathcal{N}(-\Delta_i,1)\). It is easy to see
-that this is equivalent to a ``flip around the threshold''. Arms that
-originally have a mean larger than the threshold have a mean smaller
-than the threshold after the flip.
-
-The intuition now is that every arm \(i \in \{1,\dots,K\}\) generates a
-sample for every time point \(t\in \{1, \dots, T\}\) from its
-distribution \(\nu_i\) before the algorithm starts to choose arms. Thus,
-we have a \(T \times K\) table of realized observations from the product
-distribution given by
-\(\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K\).
-This is a product distribution where the \(K\) different means are all
-above the threshold. We would hope that an algorithm classifies the
-means accordingly. However, we will show in what follows that any
-algorithm makes a certain error by not being able to distinguish
-\(\mathcal{B}^0\) from at least one of \(K\) alternative product
-distributions \(\mathcal{B}^i, i \in \{1, \dots, K\}\), of which each
-differs only slightly in one arm from the original distribution, and has
-the same overall complexity (as defined by
-\(H = \sum_{i=1}^K (\Delta_i)^{-2}\)). We require \(K\) different
-distributions so that an algorithm sampling arm \(i\) very often for
-some reason will not have a smaller lower bound by chance.
-
-For each of the \(K\) arms, we introduce an alternative model of the
-following kind. Before the start of the algorithm, we introduce a slight
-variation in the setup. The idea is similar to how one can switch arms
-in the pure exploration setup for multi-armed bandits (compare Audibert
-et al., 2010; Garivier \& Kaufmann, 2016) to ``confuse'' any algorithm
-without introducing additional complexity to the specified problem.
-However, since we do not compare arms directly with each other in the
-thresholding bandit problem (switching arms would still keep all means
-above the threshold), we instead need to flip an arm \(i\) with respect
-to the threshold in order to get the alternative model
-\(\mathcal{B}_i\). Since the threshold is \(\tau = 0\), we have for the
-flipped arm the new distribution \(\nu_i'\) as defined above. Indeed,
-define the new product distribution
-\(B^i = \nu_1^i \otimes \dots \otimes \nu_K^i\) where for
-\(k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}\).
-This arm flip corresponds to multiplying all \(X_{i,t}\) of arm \(i\) by
-\(-1\).
-
-As in Locatelli et al. (2016), let for \(i \leq K\),
-\(\mathbb{P}_{\mathcal{B}^i}\) be the probability distribution
-describing all samples that a bandit strategy can potentially collect up
-to horizon \(T\), i.e.~according to the samples
-\((X_{k,s})_{k\leq K, s \leq T} \sim (\mathcal{B}^i)^{\otimes T}\).
-\((T_k)_{k\leq K}\) denotes the number of samples collected on arm \(k\)
-until time \(T\).
-
-At this point, we have defined a finite set of problems of Gaussian
-distributions with fixed variance 1 for a given set of set of gaps
-between the means of the distributions and the threshold,
-\((\Delta_k)_k\). We now proof a lower bound on the worst case regret of
-any algorithm; that is, the maximum error probability that even the best
-algorithm makes on this problem.
-
-\subsubsection{Statistical Decision}\label{statistical-decision}
-
-The expected loss in our thresholding bandit setting,
-\(\mathbb{E}[\mathcal{L}(T)]\), corresponds directly to the probability
-of making a wrong classification of any of the \(K\) means. In general,
-given a binary decision function \(g\), define events
-\(\Omega = \{g = 0\}\) and \(\Omega^C = \{g = 1\}\). Assume that the
-decision \(g\) distinguishes between two states of the world, \(H_0\)
-and \(H_1\). Then an overall error probability can be seperated into
-\(P_{H_0}(g=1) + P_{H_1}(g = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)\).
-
-In our case, \(H_0\) may correspond to the state in which we have
-\(\mathcal{B}^0\), and \(H_1\) corresponds to the case where any arm has
-been flipped, \(\mathcal{B}^i\). Furthermore, we consider the events in
-which the algorithm classifies arm \(i\) as being above the threshold:
-\(\mathcal{A}_i = \{i \in \hat{S}_\tau\}\). The event on which all arms
-are being classified as above the threshold is consequently given by
-\(\mathcal{A} = \bigcap_{i=1}^K \mathcal{A}_i\). We could thus separate
-the error probability \(\mathbb{E}[\mathcal{L}(T)]\) into
-\(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\) and
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C)\). However, Theorem 1 does
-not bound the overall regret, but the maximum error probability on the
-\(K+1\) different models. We can write this now as
-
-\begin{align}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big) \\
-& = \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
-\end{align}
-
-\subsubsection{Empirical Kullback-Leibler
-Divergence}\label{empirical-kullback-leibler-divergence}
-
-In order to give a bound on the previous equation, we start by
-considering \(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\). This
-probability can be written as the expected change in the likelihood of
-observed data when moving from distribution \(P_{\mathcal{B}_0}\) to
-\(P_{\mathcal{B}_i}\), times the probability under the original state.
-In other words, the probability of event \(\mathcal{A}_i\) under state
-\(\mathcal{B}^i\) is given as the probability of \(\mathcal{A}_i\) under
-the (original) state \(\mathcal{B}^0\) multiplied by a factor. This
-factor describes whether the new distribution increases or decreases the
-probability of the event, and is given by the change in the data
-likelihoods due to moving from \(\mathcal{B}^0\) to \(\mathcal{B}^i\),
-expressed as the expected likelihood ratio under \(\mathcal{B}^0\). By
-definition, the latter is equal to the empirical Kullback-Leibler
-divergence of the two distributions.
-
-We will define the change of distribution in terms of the empirical
-log-likelihood for our case. Then, we will show how to replace the
-log-likelihood by the empirical Kullback-Leibler divergence. Let us
-first introduce the empirical Kullback-Leibler divergence.
-
-Let every \(\nu_i, \nu_i'\) be dominated by the Lebesgue measure
-\(\lambda\). Then their density functions are given by
-\(f_i = \frac{\der \nu_i}{\der \lambda}\) and
-\(f_i' = \frac{\der \nu_i'}{\der \lambda}\) respectively. For
-\(T \geq t \geq 0\), define the empirical Kullback-Leibler divergence
-for an i.i.d. sample \(X_{k,1}, \dots,X_{k,t}\) as
-
-\begin{align*}
-\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log(\frac{\der \nu_k'}{\der \nu_k}(X_{k,s})) \\
-& = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
-& = \frac{1}{t} \log \big( \prod_{s=1}^{t} \frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
-& \stackrel{\text{iid}}{=} \frac{1}{t} \log \big( \frac{f_k'(X_{k,1}, \dots,X_{k,t})}{f_k(X_{k,1}, \dots,X_{k,t})} \big) \\
-& = \frac{1}{t} \log \big( \text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k) \big),
-\end{align*}
-
-where \(\text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k)\) is the
-likelihood ratio for the sample.
-
-Since we consider Gaussian distributions with variance \(\sigma^2 = 1\),
-we have density functions
-\(f_i(x) \propto \exp \big(-\frac{1}{2} (x-\Delta_i)^2\big)\) and
-\(f_i'(x) \propto \exp \big(-\frac{1}{2} (x+\Delta_i)^2\big)\). Plugging
-this into the above definition of the empirical Kullback-Leibler
-divergence, we easily see
-
-\begin{align*}
-\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log \Big(\frac{\exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2\big)}{\exp \big(-\frac{1}{2} (X_{k,s}-\Delta_k)^2\big)} \Big) \\
-& = \frac{1}{t} \sum_{s=1}^{t} \log \Big( \exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2 + \frac{1}{2} (X_{k,s}-\Delta_k)^2 \big) \Big) \\
-& = - \frac{1}{t} \sum_{s=1}^{t} 2 X_{k,s} \Delta_k
-\end{align*}
-
-\subsubsection{Change of Distribution}\label{change-of-distribution}
-
-We are now ready to state the change of distribution. As alluded to
-above, we consider how the probability changes for the event
-\(\mathcal{A}_i\) when we move from \(\mathcal{B}^0\) to
-\(\mathcal{B}^i\). When flipping arm \(i\), we only change the samples
-of this arm, that is, the first \(T_i\) observations that the algorithm
-draws from arm \(i\). The change of distribution is then defined as:
-
-\begin{align*}
-\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \text{LR}((X_{i,1}, \dots,X_{i,T_i}), \nu_i', \nu_i) ] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ]
-\end{align*}
-
-Obviously, \(\hat{\KL}_{i,T_i}\) depends on the realized samples
-\(X_{i,1}, \dots,X_{i,T_i}\). Consequently, we need to find a bound on
-\(\hat{\KL}_{i,T_i}\) itself to incorporate the uncertainty involved in
-this metric.
-
-\subsubsection{Concentration of the Empirical Kullback-Leibler
-Divergence}\label{concentration-of-the-empirical-kullback-leibler-divergence}
-
-For our problem, the Kullback-Leibler divergence of \(\nu_k'\) from
-\(\nu_k\) is given by \(\KL_k := \KL(\nu_k', \nu_k) = 2\Delta_k^2\), and
-consequently
-
-\begin{equation*}
-|\hat{\KL}_{k,t} - \KL_{k,t}| = |-\frac{2}{t} \Delta_k \sum_{s=1}^{t}(X_{k,s} - \Delta_k)|
-\end{equation*}
-
-itself is a normally distributed random variable with mean zero and a
-variance decreasing in \(t\). Thus, one can show as in Locatelli et al.
-(2016) that \(\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4\) for the event
-
-\begin{equation}
-\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}}\}. \label{LocatelliTheorem1EventXi}
-\end{equation}
-
-Thus, in order to bound the empirical Kullback-Leibler divergence in our
-change of measure, we can consider the intersection of \(\mathcal{A}_i\)
-and \(\xi\) as follows and plug in the bound on event \(\xi\):
-
-\begin{align*}
-\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
-\end{align*}
-
-Two things are left to do: With \(T_i\), we still have one random
-variable left which we cannot leave in our bound. Second, we are
-actually not interested in \(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)
-but in
-\(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\).
-
-\subsubsection{\texorpdfstring{Bounding \(T_i\) for
-\(\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)}{Bounding T\_i for \textbackslash{}max\_\{i \textbackslash{}in \textbackslash{}\{1,\textbackslash{}dots,K\textbackslash{}\}\}\textbackslash{}mathbb\{P\}\_\{\textbackslash{}mathcal\{B\}\^{}i\}(\textbackslash{}mathcal\{A\}\_i)}}\label{bounding-t_i-for-max_i-in-1dotskmathbbp_mathcalbimathcala_i}
-
-We are actually interested in bounding
-\(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\).
-In general it holds that
-\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K}\sum_{i=1}^K X_i\).
-Thus we can write:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
-& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
-& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
-\end{align*}
-
-where the second line is again the intersection of \(\mathcal{A}_i\) and
-\(\xi\) as before, such that we can apply the change of distribution in
-the third line.
-
-What is left to show is a bound on \(T_i\). Given that we want to show
-that even the best algorithm makes an error on at least one of the
-problems (one of the arms), it makes sense to show that \(T_i\) is upper
-bounded. This implies that no arm can be infinitely sampled; we cannot
-reach full confidence in any arm, and a residual error probability
-should remain.
-
-First, let \(a = \Delta_i \sqrt{T_i}\) and
-\(b = 4\sqrt{\log((4\log(T)+1)K)}\). Then use \(ab \leq a^2 + b^2\) to
-write \(ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)\). And so:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) ]
-\end{align*}
-
-Furthermore, we know that the sum of the individual arm pulls has to be
-equal to the overall number of pulls (equal to the budget in the fixed
-budget sense), \(\sum_i T_i = T\), and furthermore we know that
-\(T_i>0\). The latter holds since any reasonable algorithm has to check
-each arm at least once in our setup. Thus it is easy to show that
-\(\exists i: T_i \leq \frac{T}{H \Delta_i^2} = \frac{T}{(\sum_{i=1}^{K} \Delta_i^{-2}) \Delta_i^2}\).
-To see this, assume the opposite:
-\(\forall i: T_i > T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2}\). This
-implies however
-\(\sum_{i=1}^K T_i > \sum_{i=1}^K T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2} = T \cdot 1 = T\)
-which is a contradiction.
-
-So we can write \((\Delta_i \sqrt{T_i})^2 \leq \frac{T}{H}\). We use
-\(\mathcal{A} = \cap_{i=1}^K \mathcal{A}_i\) to write:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big] \\
-& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big]
-\end{align*}
-
-We write
-\(\frac{1}{K} \sum_{i=1}^K \exp(-3T_i \Delta_i^2) \geq \frac{1}{K} \sum_{i=1}^K \exp(-3 T/H) = \exp(-3 T/H)\).
-Thus:
-
-\begin{align*}
-\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \Big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i) \exp \big(-16 \log(4(\log(T)+1)K)\big) \Big] \\
-& \geq \mathbb{E}_{\mathcal{B}^0} \Big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp \big(- 3 \frac{T}{H}\big) \exp \big(-16 \log(4(\log(T)+1)K)\big) \Big] \\
-& = \mathbb{E}_{\mathcal{B}^0} \Big[\mathbbm{1}_{\mathcal{A} \cap \xi} \exp \big(- 3 \frac{T}{H}\big) \exp \big(-16 \log(4(\log(T)+1)K)\big) \Big] \\
-& = \mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp \Big(- 3 \frac{T}{H} -16 \log \big(4(\log(T)+1)K\big)\Big)
-\end{align*}
-
-\subsubsection{Bringing everything
-together}\label{bringing-everything-together}
-
-Consider again the risk which we need to bound from equation
-\eqref{LocatelliTheorem1ExpRegret}. We bound the maximum expected loss
-over all \(\mathcal{B}_i\). By using again the fact that in general
-\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K} \sum_{i = 1}^K X_i\),
-we plug into our previous calculations:
-
-\begin{align}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp \Big(- 3 \frac{T}{H} -16 \log \big(4(\log(T)+1)K\big)\Big) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \label{LocatelliTheorem1DefinitionOfRisk}
-\end{align}
-
-From \eqref{LocatelliTheorem1EventXi} we know that for any
-\(i \in \{0, \dots, K\}\), \(\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4\).
-Following the argument in Locatelli et al. (2016), we now consider two
-cases: \(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2\) and
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2\). In the former
-case, we can plug in the two probabilities into
-\eqref{LocatelliTheorem1DefinitionOfRisk}. If
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2\) and
-\(\mathbb{P}_{\mathcal{B}^0}(\xi) \geq 3/4\), then
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \geq 1/4\). Thus:
-
-\begin{align*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \\
-& \geq \frac{1}{8} \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
-\end{align*}
-
-where we drop the second summand of the second line so that the
-inequality holds.
-
-On the other hand, when
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2\), then we know that
-\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \leq 1/2\) for any
-\(\mathbb{P}_{\mathcal{B}^0}(\xi)\). At the same time
-\(1-\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \geq 1/2\).
-Consequently,
-\(1/4 \leq \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \leq 1/2\),
-while
-\(\frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) \geq 0\).
-And so the stronger lower bound in that case is, as noticed by Locatelli
-et al. (2016), given simply by
-
-\begin{align*}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
-& \geq 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \\
-& \geq \frac{1}{2}
-\end{align*}
-
-\subsection{\texorpdfstring{Lower Bound for Thresholding Bandit Problem
-with KL-divergence
-\label{sec:corollaryLBTBPproof}}{Lower Bound for Thresholding Bandit Problem with KL-divergence }}\label{lower-bound-for-thresholding-bandit-problem-with-kl-divergence}
-
-\subsubsection{\texorpdfstring{Lower Bound for One-Armed Thresholding
-Bandit
-\label{sec:corollaryLB1TBPproof}}{Lower Bound for One-Armed Thresholding Bandit }}\label{lower-bound-for-one-armed-thresholding-bandit}
-
-\textbf{Proof}: The proof follows closely the proof of Theorem 12 in
-Kaufmann et al. (2016) and is again an application of their
-transportation Lemma, Lemma 2.
-
-Consider the one-armed bandit problem, \(K = 1\) with the canonical
-exponential family of distributions distribution \(\nu_1\) parameterized
-by its mean \(\mu_1\). Furthermore, given we are in the thresholding
-bandit problem, we have a threshold \(\tau\) against which the arm is
-classified. Assume w.l.o.g. that for \(\nu_1\), \(\mu_1 \geq \tau\).
-Thus, \(\mathcal{S}_{\tau}^* = \{1\}\). After \(T\) rounds, a consistent
-algorithm returns with error probability \(p_T(\nu)\) the guess
-\(\hat{\mathcal{S}}_{\tau}\). Thus, we have for the event
-\(A = (\hat{\mathcal{S}}_\tau = \{1\})\) the probability
-\(\mathbb{P}_{\nu}(A)\). On the other hand, define the alternative model
-\(\nu'\) with mean \(\mu_1' < \tau\) such that the correct
-classification from \(\nu\) is now wrong:
-\(\mathcal{S}_{\tau}^* {'} = (\mathcal{S}_{\tau}^*)^C = \{\emptyset\}\).
-Consequently, since the algorithm is still consistent on this problem,
-we have that \(\mathbb{P}_{\nu'}(A) = p_t(\nu')\). Thus, we expect that
-as we let \(t\) increase, \(\mathbb{P}_{\nu'}(A)\) will decrease while
-\(\mathbb{P}_{\nu}(A)\) will increase.
-
-Indeed, given we consider only consistent algorithms, there should exist
-a number of samples for which the probability of the correct decision in
-problem \(\nu\) is larger than the error probability in problem
-\(\nu'\), that is: for every \(\epsilon > 0\), there exists
-\(t_0(\epsilon)\) such that for all \(t \geq t_0(\epsilon)\) we have
-
-\begin{equation*}
-\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_{\nu}(A). \label{eq:BoundForCorollary}
-\end{equation*}
-
-Now, consider again Lemma 2 in Kaufmann et al. (2016). If we let the
-algorithm be such that \(T = t\), we can apply the Lemma to the stopping
-time \(\sigma = t\) a.s. and the event \(A\) to get
-
-\[
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)).
-\]
-
-We can lower bound the RHS by using the bound on
-\(\mathbb{P}_{\nu'}(A)\) given in \eqref{eq:BoundForCorollary} and the
-monotonicity of the binary relative entropy. We get:
-
-\begin{align*}
-\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) & = t \KL(\nu_1', \nu_1) \\
-& \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)) \\
-& \geq d(\epsilon, 1- p_t(\nu)) \\
-& = \epsilon \log\Big(\frac{\epsilon}{1-p_t(\nu)}\Big) + (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) \\
-& \geq (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) + \epsilon \log(\epsilon) \\
-\end{align*}
-
-Letting \(\epsilon \rightarrow 0\), we get
-
-\[
-t \KL(\nu_1', \nu_1) \geq \log \Big(\frac{1}{p_t(\nu)}\Big) = -\log p_t(\nu).
-\]
-
-To make the bound as tight as possible, we choose the alternative model
-that minimizes \(\KL(\nu_1', \nu_1)\) while still ensuring that
-\(\mathcal{S}_{\tau}^* {'} = \{\emptyset\}\). In our case of the
-thresholding bandit with one-parameter exponential family distributions,
-this is given by choosing \(\mu_1' \rightarrow \tau\) (not equal to
-\(\tau\) since else the classification of \(\nu_1\) is again correct).
-By pluggin in, we get the result:
-
-\[
-t \KL(\tau, \mu_1) \geq -\log p_t(\nu) \quad \text{for} \; \mu_1' \rightarrow \tau.
-\]
-
-\subsubsection{\texorpdfstring{Lower Bound for \(K\)-Armed Thresholding
-Bandit
-\label{sec:corollaryLBKTBPproof}}{Lower Bound for K-Armed Thresholding Bandit }}\label{lower-bound-for-k-armed-thresholding-bandit}
-
-\textbf{Proof}: The proof is very similar to the proof of the corollary
-for \(K=1\). However, the alternative model needs more motivation than
-in the case of a single arm. But first, consider again that we are in
-the thresholding bandit problem with \(K\) arms of univariate canonical
-exponential family distributions that are parameterized by their means
-\(\mu_1, ..., \mu_K\) for the original problem
-\(\nu = (\nu_1, ..., \nu_K)\). W.l.o.g, assume that all arms are above
-the threshold, that is, \(\mu_1 \geq \tau, ..., \mu_K \geq \tau\). Then
-\(\mathcal{S}_{\tau}^* = \{1, ... , K\}\). The correct classification
-returned after \(t\) rounds is thus the event
-\(A = (\hat{\mathcal{S}}_{\tau} = \{1, ..., K\})\). We can now consider
-Lemma 2. The RHS is maximized when the alternative model is chosen such
-that \(d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A))\) is maximized.
-Given the event \(A\) as defined before, this is the case when
-\(\mathbb{P}_{\nu'}(A)\) is as small as possible. For consistent
-algorithms, this is the case when \(\nu'\) is chosen such that all
-\(\mu_1' < \tau, ..., \mu_K' < \tau\). Then even classifying a single
-arm correctly under \(\nu\) would lead to a mistake in \(\nu'\).
-Consequently, \(A\) is the most unlikely classification for a consistent
-algorithm for the problem \(\nu'\). We thus expect for any consistent
-algorithm that \(\mathbb{P}_{\nu}(A)\) becomes large and
-\(\mathbb{P}_{\nu'}(A)\) becomes small as the number of observations
-\(t\) increases. Again, for every \(\epsilon > 0\), there exists
-\(t_0(\epsilon)\) such that for all \(t \geq t_0(\epsilon)\) we have
-\(\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)\). This
-allows us to now use Lemma 1 as previously:
-
-\begin{align*}
-\sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\nu_i', \nu_i) & \geq \sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\tau, \mu_i) \\
-& \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)) \\
-& \geq d(\epsilon, 1-p_t(\nu)) \\
-& = \epsilon \log \Big(\frac{\epsilon}{1-p_t(\nu)}\Big) + (1-\epsilon) \log \Big( \frac{1-\epsilon}{p_t(\nu)}\Big) \\
-& \geq (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) + \epsilon \log(\epsilon)
-\end{align*}
-
-We let \(\epsilon \rightarrow 0\), divide by \(t\) and take the limsup
-on both sides as in Kaufmann et al. (2016):
-
-\begin{align*}
-\lim_{t \rightarrow \infty} \sup - \frac{1}{t} \log p_t(\nu) & \leq \lim_{t \rightarrow \infty} \sup \frac{1}{t} \sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\tau, \mu_i) \\
-& \leq \max_{i \in \{1,...,K\}} \KL(\tau, \mu_i)
-\end{align*}
-
-Though, since for the alternative problem \(\nu'\) we have for every
-\(i \in \{1,...,K\}\) that \(\mu_i = \tau\), it should hold for any
-consistent algorithm that \(\mathbb{E}_{\nu'}[N_i(t)] = \frac{t}{K}\),
-that is, every arm receives an equal amount of the budget. In that case,
-the above equation simplifies to
-
-\[
-- \frac{1}{t} \log p_t(\nu) \leq \frac{1}{t} \sum_{i=1}^K \frac{t}{K}\KL(\tau, \mu_i) = \frac{1}{K} \sum_{i=1}^{K} \KL(\tau, \mu_i),
-\]
-
-that is, the complexity is given by the simple average of the
-Kullback-Leibler distances of the threshold with regard to the
-respective distributions. This relates well to the lower bound that
-Kaufmann et al. (2016) describe in their Theorem 12 for consistent
-algorithms using \emph{uniform} sampling strategies; in our case,
-however, it is explained by the fact that under the alternative model,
-every consistent algorithm should adapt to a uniform sampling strategy.
-Thus our bound holds for any consistent strategy.
-
-\subsection{\texorpdfstring{Bayes-UCB Algorithm for the Thresholding
-Bandit Problem
-\label{sec:AppendixBUCB}}{Bayes-UCB Algorithm for the Thresholding Bandit Problem }}\label{bayes-ucb-algorithm-for-the-thresholding-bandit-problem}
-
-We show how the Bayes-UCB algorithm (Algorithm 1, Kaufmann et al., 2012)
-is adapted to the thresholding bandit problem to be used in the
-experiments in chapter \autoref{chap:Experiments}. The adapted version
-of their Algorithm 1 is given in Algorithm 4 below. In particular,
-notice that we not only calculate upper quantiles \(q_i^u(t)\), but also
-lower quantiles \(q_i^l(t)\), as we have to be able to compare against
-\(\tau\) from both sides. These quantiles rely on the posterior
-distributions \(\lambda_i^t\) for each mean \(\mu_i\). In our case, we
-employ Beta prior distributions as conjugate prior for the Bernoulli
-distributions in simulations 1 to 3 and initialize them with parameters
-\(\alpha_0\) and \(\beta_0\). See the setup in Kaufmann et al. (2012),
-especially equation (3), to see how the posterior distribution is
-updated in every round.
-
-\IncMargin{1em}
-
-\begin{algorithm}
-\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
-\Input{\emph{$\tau$, $\epsilon$, $T$, $\Pi^0$ (initial prior on $\mu$), $c$ (parameters of the quantile)}}
-\Output{$\hat{S}_\tau = \{i \in \mathbb{A},  \hat{\mu}_i(T) \geq \tau\}$}
-\BlankLine
-\emph{Pull each arm once}\;
-\For{$t = K+1$ \KwTo $T$}{
-\For{$i = 1$ \KwTo $K$}{
-  \emph{Compute $q_i^u(t) = Q\Big(1-\frac{1}{t(\log T)^c}, \lambda_i^{t-1}\Big)$ and $q_i^l(t) = Q\Big(\frac{1}{t(\log T)^c}, \lambda_i^{t-1}\Big)$}\;
-  \emph{Compute $B_i^{BUCB}(t) = (\tau - q_i^l(t))\cdot\mathbb{I}(\hat{\mu}_i(t) \geq \tau) + (q_i^u(t) - \tau)\cdot\mathbb{I}(\hat{\mu}_i(t) < \tau)$}\;
-}
-  \emph{Pull arm $I_t = \arg \max_{i\leq K} B_i^{BUCB}(t)$}\;
-  \emph{Observe reward $X \sim \nu_{I_t}$ and update $\Pi^t$}\;
-}
-\caption{Bayes-UCB algorithm from Kaufmann et al. (2012) adapted to the thresholding bandit problem.}\label{bayesucb_tbp}
-\end{algorithm}
-
-\DecMargin{1em}
-
-\subsection{Empirical Analysis of the Bayes-UCB Algorithm in Simulation
-2}\label{empirical-analysis-of-the-bayes-ucb-algorithm-in-simulation-2}
-
-In order to assess the excellent performance of the Bayes-UCB algorithm,
-which comes at a surprise given that is is designed for the cumulative
-regret setting and thus should tend to explore the arms to less, we run
-the Bayes-UCB algorithm for simulation 2 with three different choices of
-the parameter. In Figure 13, we see the performance results of the three
-versions, whereas Figure 14 shows how the algorithm allocates its budget
-across the arms over time. The three versions differ in the quantile
-parameter \(c\) (compare \autoref{sec:AppendixBUCB}) for which we choose
-\(c \in \{1/5, 1, 5\}\) to explore more or less. In Kaufmann et al.
-(2012), the cumulative regret upper bound for the Bayes-UCB is shown for
-\(c\geq 5\), though they report that the choice of \(c=0\) worked much
-better in their experiments. In our problem, it makes also sense that
-the versions with smaller quantiles (smaller \(c\)) tend to perform
-better, as these correspond to more exploration of the arms. In this
-particular simulation, the choices of \(c=1/5\) and \(c=1\) perform very
-similar. We see that the worse performance of \(c=5\) can be attributed
-to a initial phase of sampling primarily the arms with mean below the
-threshold. This comes from the fact that the Bernoulli and Beta
-distributions are bounded between \(0\) and \(1\), with \(\tau\) very
-close to \(0\). Thus, the index \(B_i^{BUCB}(t)\) cannot be larger than
-\(\tau\) for arms with \(\hat{\mu}_i(t) \geq \tau\). For arms with
-\(\hat{\mu}_i(t) < \tau\), however, the index can be as large as
-\(B_i^{BUCB}(t) = 0.95\). This leads to the effect seen in Figure 14:
-Due to \(c=5\), the indexes are based on very large quantiles even in
-the beginning, which leads to large indexes for the arms with small
-means. This however is not the ideal sampling behavior. The other two
-variants adapt much better due to their smaller quantiles (and more
-exploration).
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation2_results_bucb-1}
-
-}
-
-\caption{Performance comparison of algorithms for simulation 2.}\label{fig:simulation2_results_bucb}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-12-1}
-
-}
-
-\caption{Budget allocation across arms for the Bayes-UCB algorithm in simulation 2 at three different values for the quantile parameter.}\label{fig:unnamed-chunk-12}
-\end{figure}
-
-\subsection{Empirical Comparison of APT, SLR, and Bayes-UCB in
-Simulation
-2}\label{empirical-comparison-of-apt-slr-and-bayes-ucb-in-simulation-2}
-
-We can compare the different algorithms used in Simulation 2 based on
-the overall number of pulls of each arm. In the best case, an algorithm
-would sample an arm for the optimal share of the budget, in every
-simulation. This is of course not the case, since the number of pulls of
-a given arm at the end of the budget, \(T_i(T)\), is a random variable
-for adaptive sampling strategies. Given the 5000 iterations conducted in
-simulation 2, we can plot the empirical distribution of this random
-variable for different arms.
-
-In Figure 15, we show the distribution of \(T_6(T)\) for algorithms APT,
-Bayes-UCB, and SLR. We see that the distribution of the Bayes-UCB
-algorithm is much better concentrated around the optimal share of the
-budget, and has a bell curve shape. In contrast, the distributions of
-APT and SLR are much less concentrated but flat and wide, and spread
-across a very large interval. Both algorithms have several iterations in
-which they draw arm 6, the most difficult arm only a single time (during
-initialization). This happens for APT more than 5\% of the iterations,
-and leads to the spike on the very left of the graph. In order to cope
-at least a little bit with this problem, we have also run the SLR
-algorithm with the D-Tracking rule as introduced in Garivier and
-Kaufmann (2016). The effect is nearly not noticeable in Figure 15, but
-the minimum number of observations is not clearly bounded away from 0.
-The effect on the performance was described before and is very
-noticeable in comparison to SLR without D-Tracking. However, even with
-D-Tracking the performance of Bayes-UCB is not reached. We describe SLR
-with D-Tracking in Algorithm 5.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-13-1}
-
-}
-
-\caption{Empirical distribution of pulls of arm 6 in simulation 2 by different algorithms.}\label{fig:unnamed-chunk-13}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-14-1}
-
-}
-
-\caption{Empirical distribution of pulls of arms 1 and 10 in simulation 2 by different algorithms.}\label{fig:unnamed-chunk-14}
-\end{figure}
-
-\subsection{SLR Algorithm with D-Tracking
-Rule}\label{slr-algorithm-with-d-tracking-rule}
-
-\IncMargin{1em}
-
-\begin{algorithm}
-\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
-\Input{$\tau$, $\epsilon$, class of distributions $\nu(\mu, \theta)$, $\theta_i \: \forall i \in \mathbb{A}$}
-\Output{$\hat{S}_\tau = \{i \in \mathbb{A},  \hat{\mu}_i(T) \geq \tau\}$}
-\BlankLine
-\emph{Pull each arm once}\;
-\For{$t = K+1$ \KwTo $T$}{
-  \emph{Calculate $U_t = \{i \in \mathbb{A}, T_i(t) < \sqrt{t} - K/2\}$}\;
-  \emph{Set $I_t = \arg \min_{i \in \mathbb{A}} B_i^{SLR}(t)$ as in \autoref{eqn:SLRIndex}}\;
-  \If{$U_t \neq \emptyset$}{Set $I_t = \arg \min_{i \in \mathbb{A}} T_i(t)$}
-  \emph{Pull arm $I_t$}\;
-  \emph{Observe reward $X_t \sim \nu_{I_t}$}\;
-}
-\caption{SLR algorithm with D-Tracking Rule (Garivier and Kaufmann, 2016)} \label{algo_slr_1d_dTracking}
-\end{algorithm}
-
-\DecMargin{1em}
-
-\subsection{Means in Simulations 4 and
-5}\label{means-in-simulations-4-and-5}
-
-We give here the means of the distributions used in simulations 4 and 5
-for completeness.
-
-\begin{longtable}[]{@{}rrrrrrrrrr@{}}
-\caption{Mean of Exponential arms 1 to 10 in simulation
-4.}\tabularnewline
-\toprule
-V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
-\midrule
-\endhead
-0.176 & 0.2233 & 0.2407 & 0.3026 & 0.3359 & 0.35 & 0.3705 & 0.5497 &
-0.7374 & 0.8758\tabularnewline
-\bottomrule
-\end{longtable}
-
-\begin{longtable}[]{@{}rrrrrrrrrr@{}}
-\caption{Mean of Exponential arms 11 to 20 in simulation
-4.}\tabularnewline
-\toprule
-V11 & V12 & V13 & V14 & V15 & V16 & V17 & V18 & V19 & V20\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-V11 & V12 & V13 & V14 & V15 & V16 & V17 & V18 & V19 & V20\tabularnewline
-\midrule
-\endhead
-1.1419 & 1.2168 & 1.4021 & 1.6445 & 1.6868 & 1.9661 & 1.9716 & 3.2218 &
-3.2907 & 4.055\tabularnewline
-\bottomrule
-\end{longtable}
-
-\begin{longtable}[]{@{}rrrrrrrrrr@{}}
-\caption{Mean of Poisson arms 1 to 10 in simulation 5.}\tabularnewline
-\toprule
-V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-V1 & V2 & V3 & V4 & V5 & V6 & V7 & V8 & V9 & V10\tabularnewline
-\midrule
-\endhead
-0.0072 & 0.0576 & 0.0613 & 0.0925 & 0.1452 & 0.1559 & 0.1869 & 0.1958 &
-0.2235 & 0.2467\tabularnewline
-\bottomrule
-\end{longtable}
-
-\begin{longtable}[]{@{}rrrrrrrrrr@{}}
-\caption{Mean of Poisson arms 11 to 20 in simulation 10.}\tabularnewline
-\toprule
-V11 & V12 & V13 & V14 & V15 & V16 & V17 & V18 & V19 & V20\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-V11 & V12 & V13 & V14 & V15 & V16 & V17 & V18 & V19 & V20\tabularnewline
-\midrule
-\endhead
-0.2664 & 0.3008 & 0.4295 & 0.4948 & 0.5857 & 0.6904 & 0.7609 & 0.785 &
-0.8878 & 1.7114\tabularnewline
-\bottomrule
-\end{longtable}
-
-\end{document}
+Berlin, den 18. September 2017

### 2017-09-18 real_experiments/real_exp_1week_2_onearmless.R

@@ -33,22 +33,6 @@ current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis
 
 ####################################################################
 
-data_amo4 <- pv_list
-data_amo4_wide <- pv_products_wide
-data_amo4_own_means <- pv_own_means
-data_amo4_next_means <- pv_next_means
-data_amo4_mean_secondhalf <- colMeans(data_amo4_wide[15081:25160,])
-data_amo4_mean_middlehalf <- colMeans(data_amo4_wide[10081:20160,])
-data_amo4_mean_firsthalf <- colMeans(data_amo4_wide[1:15080,])
-save(data_amo4, file = paste0(current_path, "data_amo4.Rda"))
-save(data_amo4_wide, file = paste0(current_path, "data_amo4_wide.Rda"))
-save(data_amo4_own_means, file = paste0(current_path, "data_amo4_own_means.Rda"))
-save(data_amo4_next_means, file = paste0(current_path, "data_amo4_next_means.Rda"))
-save(data_amo4_mean_firsthalf, file = paste0(current_path, "data_amo4_mean_firsthalf.Rda"))
-save(data_amo4_mean_secondhalf, file = paste0(current_path, "data_amo4_mean_secondhalf.Rda"))
-rm(pv_list, pv_own_means, pv_next_means, pv_products_wide)
-gc()
-
 load(paste0(current_path, "data_amo4_mean_firsthalf.Rda"))
 load(paste0(current_path, "data_amo4_mean_secondhalf.Rda"))
 load(paste0(current_path, "data_amo4_own_means.Rda"))
@@ -56,34 +40,27 @@ load(paste0(current_path, "data_amo4.Rda"))
 tau_amo4 <- 5/60
 epsilon_amo4 <- 0
 
+data_amo5 <- data_amo4
+for(i in 1:length(data_amo5)) {
+  data_amo5[[i]]$V149 <- NULL
+}
+
+data_amo5_mean_firsthalf <- data_amo4_mean_firsthalf[-5]
+data_amo4_own_means <- data_amo4_own_means[-5]
+
 ########################################################################
 # Standard Likelihood Ratio
-system.time(amo4_LR <- para_bandit_sim_LR(data = data_amo4, 
+system.time(amo5_LR <- para_bandit_sim_LR(data = data_amo5, 
                                           rounds = 10080, 
                                           tau = tau_amo4, 
                                           epsilon = epsilon_amo4))
 
[…]

### 2017-09-18 Thesis/Draft.Rmd
final

@@
 ---
-title: "On Pure Exploration, Thresholding Bandits, and Kullback-Leibler Divergence"
 header-includes:
-   #- \documentclass[a4paper,twoside,english]{article}
+   #- \documentclass[a4paper,oneside,english]{article}
    - \usepackage[retainorgcmds]{IEEEtrantools}
@@
     keep_tex: true
-    toc: true
+    #toc: true
     toc_depth: 2
+    fig_caption: yes
     #latex_engine: xelatex
+#documentclass: article
+#classoption: oneside
+#geometry: left=2.5cm, right=2cm
 fontsize: 11pt
-urlcolor: blue
+urlcolor: black
+linkcolor: black
 ---
+
+\pagenumbering{gobble}
+
+```{r child = 'titlepage.Rmd'}
+```
 
@@
 If it disagrees with experiment, it's wrong.
-That's all there is to it."
-
-- Richard Feynman in *Richard Feynman Messenger Lectures at Cornell University: The Character of Physical Law. Chapter 7, Seeking New Laws*.
+That's all there is to it." \vspace*{1.5\baselineskip}
+
+Richard Feynman in *Richard Feynman Messenger Lectures at Cornell University: The Character of Physical Law. Chapter 7, Seeking New Laws*.
 
 \newpage
+
+\vspace*{10\baselineskip}
+
+\Large{\bf Abstract\\}
+
+\vspace*{1\baselineskip}
+
+\normalsize
+In this thesis we present a new sequential sampling strategy for the fixed-budget thresholding bandit problem described in Locatelli et al.
+(2016).
+We draw from the literature on pure exploration bandit problems to show the similarity of the thresholding bandit to (sequential) hypothesis testing.
+In particular, we derive a lower bound on how fast the error probability in a one-armed thresholding bandit problem can decrease at best, and show that this corresponds to the Chernoff-Stein Lemma.
+This motivates the use of the Kullback-Leibler divergence in the index of our new algorithm.
+In simulations, our strategy is shown to outperform existing strategies.
+Using website analytics data from an online shop, we use time series cross-validation to create data sets for offline testing of adaptive sampling strategies; time dependency in the data is thus preserved.
+Our experiments show that the adaptive sampling strategies are disrupted by the dependency structure in the samples.
+
+\newpage
+
+\setcounter{tocdepth}{2}
+\tableofcontents
+
+\newpage
+\pagenumbering{arabic}
 
@@
 The classical example is that of clinical trials in which a researcher tests two drugs on patients to observe which one performs better.
-Not only is it difficult to gather enough patients, but one would also like to adapt the sampling such that as soon as possible more patients receive the better drug and are cured.
+Not only is it difficult to gather enough patients, but one would also like to adapt the sampling such that more patients receive the better drug as soon as possible, and are cured.
 As noted in Cappé et al.
 (2013), this example dates back to Thompson (1933, 1935).
-Such problems are known as multi-armed bandit problems in which the sampling is adapted so as to minimize the cumulative regret: In the case of the drug tests, one would like to sample the two drugs in a way to find the best drug as soon as possible and then to test this drug more and more often and more often than the worse drug.
+Such problems are known as multi-armed bandit problems in which the sampling is adapted so as to minimize the cumulative regret: In the case of the drug tests, one would like to sample the two drugs in a way that quickly finds the best drug and then tests this drug more and more often, and more often than the worse drug.
 This would lead to cumulatively more healthy patients than testing both drugs uniformly; it would minimize the regret from treating patients with an ineffective drug.
@@
 These distributions have different means, and one can draw samples sequentially from the distributions in order to estimate their means.
-To minimize the cumulative regret measure, one would like to play the distribution with the highest mean as much as possible (*Exploitation*).
+To minimize the cumulative regret measure, one would like to sample from the distribution with the highest mean as often as possible (*Exploitation*).
 At the same time, however, one has to sample all arms at least a little, so as to initially find the best arm (*Exploration*).
@@
 While Gittins (1979) presents an Bayesian-optimal solution to the cumulative regret problem, the Upper-Confidence Bound (UCB) algorithms pioneered by Agrawal (1995) and Auer, Cesa-Bianchi and Fischer (2002) have lead to a blooming literature on multi-armed bandit problems that has been picked up to solve modern problems in website and advertising optimization, where advertisers try to allocate their advertising optimally so as to reduce regret from showing poorly converting advertisements.
-Several algorithms like the KL-UCB algorithm based on Kullback-Leibler divergence upper confidence intervals (Cappé et al., 2013) or the Bayes-UCB algorithm (Kaufmann et al., 2012)  have followed and been shown to be optimal as they reach the lower bound introduced in Lai and Robbins (1985) and Burnetas and Katehakis (1996).
+Several algorithms like the KL-UCB algorithm based on Kullback-Leibler divergence upper confidence intervals (Cappé et al., 2013) or the Bayes-UCB algorithm (Kaufmann et al., 2012a)  have followed and been shown to be optimal as they reach the lower bound introduced in Lai and Robbins (1985) and Burnetas and Katehakis (1996).
 
@@
 Thus one needs to explore the distributions as efficiently as possible.
-Exploitation is not necessary, and the setting is thus referred to as *Pure Exploration*.
-The need for strategies other than uniform sampling arises: One does not want to continue to sample distributions that one is confident in.
-This setting is related to the problem faced in Bayesian Optimization: Training large neural networks is costly in terms of time and computation, and so the parameter space needs to be explored with as few samples as possible.
+Given that the loss function only evaluates the classifiation once at the end of the sampling process, exploitation is *not* necessary, and the setting is thus referred to as *Pure Exploration*.
+The need for strategies different from uniform sampling arises still: One does not want to continue to sample distributions that one is already confident in.
+This setting is related to the problem faced in Bayesian Optimization: Training of, for example, deep neural network architectures is costly in terms of time and computation, and so the parameter space needs to be explored with as few samples as possible.
 (Zhang et al., 2017; Brochu et al., 2010).
-The problem of best arm identification is also very related to statistical hypothesis testing as noted by Chernoff (1958) since one has to make a decision about how the means of distributions relate to each other.
-The main difference being that the bandit setting includes the testing procedure in the sampling process.
+The problem of best arm identification is also very related to sequential statistical hypothesis testing as noted by Chernoff (1958), and picked up by Garivier and Kaufmann (2016) and Russo (2016), since the experimenter has to make a decision about how the means of distributions relate to each other.
 
@@
 Other authors investigate binary measures that are equal to 1 when the best arm has not been identified (Russo, 2016; Garivier and Kaufmann, 2016).
-These binary measures correspond to the probability of the identified arm being the best, and thus inherently related to hypothesis testing.
+These binary measures correspond to the probability of the identified arm being the best, and thus are inherently related to hypothesis testing.
 The problem of best arm identification can readily be extended to the so called Top-$m$ problem of identifying the best $m$ of $K$ arms (Kaufmann and Kalyanakrishnan, 2013; Kaufmann et al.
@@
 While the name is reminiscient of the cumulative regret multi-armed bandit, the problem is more similar to the top-$m$ problem.
-But instead of identifying the best $m$ out of $K$ arms, one aims to find all distributions out of $K$ that have a mean at least as large as a fixed threshold.
+But instead of identifying the best $m$ out of $K$ arms, one aims to find all distributions out of $K$ that have a mean at least as large as a fixed threshold (it is not known upfront how many distributions fulfill this condition).
 Given that an implicit threshold arises in the top-$m$ problem between the $m$-th best and the $(m+1)$-th best arm (Kaufmann et al., 2016), the two problems share many characteristics.
 We discuss this in more detail in \autoref{chap:KullbackLeiblerPureExploration}.
-In the form described in Locatelli et al.
-(2016), algorithms in the thresholding bandit problem are evaluated against a binary loss function penalizing whenever an arm has not been classified correctly as being above or below the threshold, and thus focus on exploration similar to algorithms employed for best arm identification.
+In the setting described in Locatelli et al.
+(2016), algorithms in the thresholding bandit problem are evaluated against a binary loss function penalizing once after the sampling process if an arm has not been classified correctly as being above or below the threshold.
+This setting thus focuses on exploration similar to algorithms employed for best arm identification.
 Indeed, Locatelli et al.
@@
 
-The app will then display a "Good service" or "This place is trendy" description for the restaurant if $\mu_{\text{service}}$ and $\mu_{\text{trendy}}$ are estimated to be above a certain threshold, for example $\tau = 0.5$.
-That is, more than half of the people would describe the place as having good service, or as trendy.
+The app will display a "Good service" or "This place is trendy" description for the restaurant if $\mu_{\text{service}}$ and $\mu_{\text{trendy}}$ are estimated to be above a certain threshold, for example $\tau = 0.5$.
+That is, more than half of the user base would describe the place as having good service, or as trendy.
 
@@
 But even though the app has thousands of users, not that many people visit a specific restaurant, and even less people report this back to the app.
-Thus the company only has a limited budget of $T$ potential users from which to collect samples $X_{\text{service}}$ and $X_{\text{trendy}}$ from.
-How can the company ask these $T$ questions to be as confident as possible in its classification, that is, in the information it displays?
+Thus the company has only a limited budget of $T$ potential users from which to collect samples $X_{\text{service}}$ and $X_{\text{trendy}}$.
+How can the company ask these $T$ questions to be as confident as possible in its classification of the restaurant's features, that is, in the information it displays?
 
@@
 Given 100 users, 50 users give feedback on the service level, 50 users report on the trendiness level.
-This however is unlikely to be optimal with respect to the confidence after 100 samples.
-Given that the company asks the users sequentially, there is the option to adapt the sampling strategy over time: If the first ten users report $\sum_{s=1}^{10}X_{\text{service},s}=10$, while $\sum_{s=1}^{10}X_{\text{trendy},s}=5$, then the company might already be quite confident that $\mu_{\text{service}} \geq \tau = 0.5$, while this is less clear for $\mu_{\text{trendy}}$.
-Instead of continuously sampling both questions, it might be more useful to collect more feedback on the trendiness level so as to figure out its position relative to the threshold.
-After all, the company would like to use the 100 samples to maximize its confidence in both displayed tips.
-
-Finding the optimal sequential sampling strategy to classify distributions against a threshold with as much confidence as possible after a limited budget of samples is the problem described above, and the problem described by the thresholding bandit problem which we discuss for the remainder of this thesis.
-In the following section, we define the general setting of the thresholding bandit problem.
+This, however, is unlikely to be optimal with respect to the confidence after 100 samples.
+Given that the company asks the users sequentially, there is the option to adapt the sampling strategy over time: If the first ten users report $\sum_{s=1}^{5}X_{\text{service},s}=5$, while $\sum_{s=1}^{5}X_{\text{trendy},s}=3$, then the company might already be quite confident that $\mu_{\text{service}} \geq \tau = 0.5$, while this is less clear for $\mu_{\text{trendy}}$.
+Instead of continuously sampling both questions, it might be more useful to collect more feedback on the trendiness level so as to ensure its position relative to the threshold.
+After all, the company would like to use the 100 samples to maximize its confidence in *both* displayed tips.
+
+Finding the optimal sequential sampling strategy to classify distributions against a threshold with as much confidence as possible after a limited budget of samples is the problem described above.
+It is a setting described by the thresholding bandit problem, which we discuss for the remainder of this thesis.
+In the following section, we define setting of the thresholding bandit problem more generally.
 
@@
 
-Consider a setting with a set of $\mathbb{A}=\{1, ..., K\}$ unknown probability distributions $\nu_i, i \in \mathbb{A}$.
+Consider a setting with unknown probability distributions $\nu_i$ indexed by $i \in \mathbb{A}=\{1, ..., K\}$.
 To stick with the idea of multi-armed bandits, we call the distributions arms, and observations from the arms rewards (Bubeck and Cesa-Bianchi, 2012).
-The learner is interested in learning about the structure of the arms; in particular, she would like to estimate the means $\mu_1, ..., \mu_K$ by sequentially drawing observations $X_{i,1}, X_{i,2}, ...$ from the different arms, where $X_{i} \sim \nu_i$.
-However, at time $t$ the learner cannot observe a reward from every distribution but must select a single arm $I_t$ from which she would like to observe the reward $X_{I_t,t}$.
-Often, adaptive sampling strategies makes the decision of which arm to pull by computing an index $B_i(t)$ for each arm.
-If $T_i(t)$ is the number of samples observed until time $t$ for arm $i$, then is $B_i(t)$ a function of the past rewards $X_{i,1}, ..., X_{i,T_i(t)}$ observed for arm $i$, and w.l.o.g.
+The learner is interested in learning about the structure of the arms; in particular, it would like to estimate the means $\mu_1, ..., \mu_K$ of each distribution $\nu_i$ by sequentially drawing observations $X_{i,1}, X_{i,2}, ...$ from the different arms, where $X_{i} \sim \nu_i$.
+However, at time $t$ the learner cannot observe a reward from every distribution but must select a single arm $I_t$ from which it would like to observe the reward $X_{I_t,t}$.
+The decision of which arm to pull next is often made by computing an index $B_i(t)$ for each arm.
+If $T_i(t)$ is the number of samples observed until time $t$ for arm $i$, then $B_i(t)$ is a function of the past rewards $X_{i,1}, ..., X_{i,T_i(t)}$ observed for arm $i$, and w.l.o.g.
 $I_t = \arg \min_{i = 1,...K} B_i(t)$.
-The set of indexes can be called strategy (Kaufmann et al., 2012) which makes it clear that the strategy is adapted as more observations are collected.
+The set of indexes can be called strategy (Kaufmann et al., 2012a) which makes it clear that the strategy is adapted as more observations are collected.
 Strategies of this kind are also called index policies.
@@
 The thresholding problem for the learner is now to use a budget of overall $T$ samples (or rounds) to explore the different arms.
-After this exploration phase, the learner returns a set of arms that she believes to be over the threshold.
-When evaluating the classification of the learner, arms with mean inside of the epsilon interval $\tau \pm \epsilon$ will not be considered.
+After this exploration phase, the learner returns a set of arms that it believes to be over the threshold.
+When evaluating the classification of the learner, arms with mean inside of the epsilon interval $\tau \pm \epsilon$ are not considered.
 The learner only has to correctly distinguish the means from the threshold up to the precision given by $\epsilon$.
@@
 
-The learner's classification is returned as the set $\hat{\mathcal{S}}_{\tau} := \hat{\mathcal{S}}_{\tau}(T) \subset \mathbb{A}$ after $T$ rounds; that is, the set of arms estimated to be over the threshold.
-The classification is evaluated against the loss given as (Locatelli et al., 2016):
+The learner's classification is returned as the set $\hat{\mathcal{S}}_{\tau} := \hat{\mathcal{S}}_{\tau}(T) \subseteq \mathbb{A}$ after $T$ rounds; that is, the set of arms estimated to be over the threshold.
+The classification is evaluated against the binary loss given by (Locatelli et al., 2016):
 
@@
 Let $\mathbb{E}$ be the expectation with regard to the samples $X_{i,1}, ..., X_{i,T}$ collected by the algorithm.
-The expected loss is then given as
+Then
 
@@
 
-which corresponds to the probability of making at least one wrong classification.
+is the expected loss, or the probability of making at least one wrong classification.
 Both the probability of not identifying an arm that is actually over the threshold, as well as the probability of accepting an arm as over the threshold when it is not, are evaluated.
@@
 (2016) assume that the distributions $\nu_i, i \in \mathbb{A}$ are $R$-sub-Gaussian.
-Under this assumption, the authors are able to prove a lower bound on the largest probability of error of the best algorithm in the setting we have just introduced, as well as an upper bound on the performance of their APT algorithm which we will introduce in the following chapter.
-As in their paper, we define $R$-sub-Gaussian and assume it in the description of the their algorithm and bounds:
+Under this assumption, the authors are able to prove a lower bound on the largest probability of error of the best algorithm in the setting just introduced, as well as an upper bound on the performance of their APT algorithm which we will show in the following chapter.
+As in their paper, we define $R$-sub-Gaussian as follows:
 
@@
 $R$-sub-Gaussian distributions offer concentration inequalities for the concentration of the empirical mean around the true mean, which makes it possible to deduce the bounds presented by the authors and repeated below.
-The family of $R$-sub-Gaussian distributions encompasses Gaussian distributions of variance $R^2$ for $R \in \mathbb{R}$, as well as all bounded distributions, with the important case of Bernoulli distributions.
-
-Having described the thresholding bandit setting as well as the assumption of $R$-sub-Gaussianity, we can now proceed to describe the *Anytime Parameter-free Thresholding* (APT) algorithm proposed in Locatelli et al.
+Among other distributions, the family of $R$-sub-Gaussian distributions encompasses Gaussian distributions of variance $R^2$ for $R \in \mathbb{R}$, as well as all bounded distributions, with the important case of Bernoulli distributions.
+
+Having described the thresholding bandit setting as well as the assumption of $R$-sub-Gaussianity, we now proceed to describe the *Anytime Parameter-free Thresholding* (APT) algorithm proposed in Locatelli et al.
 (2016) for the thresholding bandit problem.
@@
 Just like the general index policies mentioned in \autoref{sec:Setup}, we see that the APT algorithm adapts its strategy using an index $B_i(t+1)$ for each arm that is based entirely on the observations observed until time $t$.
-Given the arm with the smallest index is pulled at round $t+1$, we observe that arms that are estimated to be further away from the threshold $\tau$ as measured by the absolute distance to their empirical mean $\hat{\mu}_i$, $\hat{\Delta}_i(t)$, are pulled less often.
+Given the arm with the smallest index is pulled at round $t+1$, we observe that arms estimated to be further away from the threshold $\tau$ as measured by the absolute distance $\hat{\Delta}_i(t)$ to their empirical mean $\hat{\mu}_i$ are pulled less often.
 Intuitively, it is easier to classify arms as below or above $\tau$ when their mean is far away from the threshold.
@@
 Or the empirical mean has to be better concentrated around the true mean.
-Otherwise it is easier to make a mistake on this arm.
+Otherwise it is easy to make a mistake on this arm.
 To gain this confidence, the arm requires more samples, and thus a larger share of the overall $T$ samples available.
@@
 
-While the APT algorithm does not require the complexity to be known upfront (which would be problematic as it is not known upfront), it is necessary to define the complexity to deduce the upper bound on its probability of error.
+While the APT algorithm does not require the complexity to be known upfront (which would be problematic as it is *not* known upfront), it is necessary to define the complexity to deduce the upper bound on its probability of error.
 Similar to the distance measure used in the algorithm's index, we define the gap $\Delta_i^{\tau,\epsilon}$ between arm $i$ and the threshold $\tau \pm \epsilon$ as
@@
 Consequently, when we require less precision, that is, we increase $\epsilon$, the hardness decreases.
+Indeed, by using $\epsilon > 0$, we upper bound the complexity of a problem.
+Consider a problem with $K$ arms.
+Then even in the worst case of $\mu_i = \tau$ for all $i \in \mathbb{A}$, $H \geq \frac{K}{\epsilon^2}$.
 Furthermore, we see that each arm contributes its individual complexity, $h_i^{\tau,\epsilon} = \frac{1}{(\Delta_i^{\tau,\epsilon})^2}$ linearly into the problem.
 Thus, if the complexity $H$ is a good measure of the actual problem complexity, and we knew upfront which arm has which mean, we could allocate the "optimal" share of the budget, $T \cdot h_i /H$ to arm $i$.
-However, since we do not know neither $\mu_i$ nor $H$ upfront, the best we can do is to adapt our allocation of samples more and more towards this optimum as we observe samples.
+However, since we know neither $\mu_i$ nor $H$ upfront, the best we can do is to adapt our allocation of samples more and more towards this optimum as we observe samples.
 
@@
 In \autoref{sec:LowerBoundLocatelli} we then show the lower bound presented in Locatelli et al.
-(2016) and that the APT algorithm is optimal in that it matches the lower bound.
+(2016), and that the APT algorithm is optimal in that it matches the lower bound.
 We discuss the results and the APT algorithm further in \autoref{sec:DiscussionLocatelli}.
 
-## Upper Bound for the APT Algorithm \label{sec:UpperBoundLocatelli}
+## Upper Bound for the Anytime Parameter-free Thresholding Algorithm \label{sec:UpperBoundLocatelli}
 
@@
 
-As noted in Zhong et al. (2017), a simple requirement to correctly classify arms at the final round is the following. For every arm $i \in \{1, ..., K\}$ after the final round $T$, require
-$$
-\hat{\mu}_{i}(T) \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
-$$
-or
-$$
-\hat{\mu}_{i}(T) \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
-$$
-Or simply in terms of the gap between the arm and the threshold as used in the index by the APT algorithm:
+As noted in Zhong et al. (2017), a simple requirement to correctly classify arms at the final round is the following. For every arm $i \in \{1, ..., K\}$ after the final round $T$, require:
 $$
@@
 Consequently, there is no arrangement possible in which the arm is classified wrong while the separation condition holds.
-Assuming $\mu_i < \tau$ and $\epsilon = 0$, an incorrect classification would require $\mu_i < \tau \leq \hat{\mu_i}$.
+Assuming $\mu_i < \tau$ and $\epsilon = 0$, an incorrect classification would require $\mu_i < \tau \leq \hat{\mu}_i$.
 But then  $| \hat{\mu}_{i}(T) - \mu_i | \geq |\mu_i - \tau|$, which violates the separation condition.
-
 Thus, we need to show that this condition holds for every arm $i \in \{1,...,K\}$ with large probability after the final round $T$.
-In different words, we need to derive an upper bound on the probability with which this condition does not hold.
+Put differently, we need to derive an upper bound on the probability with which this condition does not hold.
 
@@
 
-The separation condition describes what event needs to hold in order for the APT algorithm to make a correct classification: The smaller the deviation of the empirical mean from the population mean, the more difficult it is for the classification to be wrong.
+The separation condition describes which event needs to hold in order for the APT algorithm to make a correct classification: The smaller the deviation of the empirical mean from the population mean, the more difficult it is for the classification to be wrong.
 Moreover, if the mean and empirical mean are identical, then the classification is correct independent of the threshold.
 Also, the closer the mean to the threshold, the better the estimate has to be for a correct classification to be likely.
-To bound the absolute deviation of the empirical mean from the true mean, we define the favorable event $\xi$ as
+To bound the absolute deviation of the empirical mean from the true mean for every potential number of pulls $s$ that an arm $i$ might have received at the end of the budget $T$, we define the favorable event $\xi$ as
 
@@
 
-We know that $X_i$ are $R$-sub-Gaussian by assumption. That is, we have
+We know that $X_i$ are $R$-sub-Gaussian random variables by assumption. That is, we have
 
@@
 
-Writing $\gamma = \sqrt{\frac{T\delta^2}{Hs}}$, we get for the favorable event $\xi_i = \{|\bar{X}_s - \mu| \leq \sqrt{\frac{T\delta^2}{Hs}}\}$ of an individual arm $i$, for each $i \in \mathbb{A}$ and each $s \in \{1, ..., T\}$:
-
-$$
-\mathbb{P}(\xi_i) = \mathbb{P}\Big(|\bar{X}_{i,s} - \mu_i| \leq \sqrt{\frac{T\delta^2}{Hs}}\Big) \geq 1 - 2\exp (-\frac{T\delta^2}{2R^2H}),
+Writing $\gamma = \sqrt{\frac{T\delta^2}{Hs}}$, we get for the favorable event $\xi_i = \{|\bar{X}_s - \mu| \leq \sqrt{\frac{T\delta^2}{Hs}}\}$ of an individual arm $i \in \mathbb{A}$ and a given $s \in \{1, ..., T\}$:
+
+$$
+\mathbb{P}(\xi_i) = \mathbb{P}\Big(|\bar{X}_{i,s} - \mu_i| \leq \sqrt{\frac{T\delta^2}{Hs}}\Big) \geq 1 - 2\exp \Big(-\frac{T\delta^2}{2R^2H}\Big),
 $$
@@
 
-Locatelli et al. (2016) use instead of Höffding's inequality a Sub-Gaussian martingale inequality including a peeling argument in order to derive a better bound of
+Instead of Höffding's inequality, Locatelli et al. (2016) use a Sub-Gaussian martingale inequality including a peeling argument in order to derive a better bound of
 
@@
 
-This bound is non-trivial for much smaller values of $T$, and we will use it in the following.
-
-### Need to Bound $T_i$
-
-We now have that with large probability the favorable event holds. On the favorable event, we have for every arm $i$:
-
-$$
-| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}
-$$
-
-The deviation of arm $i$ at time $t$ depends on how large $H$, $T$, and $T_i(t)$ are.
-While $t$, $H$, $T$ are deterministic, the number of times arm $i$ has been pulled at round $t$, $T_i(t)$, is a random variable.
-In order to know how large the probability of the favorable event is (and thus the error probability), we need to know the value of $T_i(t)$, or at least bound a range of potential values.
-Put differently: To ensure a deviation smaller than $\sqrt{\frac{T\delta^2}{HT_i(t)}}$ for arm $i$, we need to ensure that arm $i$ has been pulled at least $T_i(t)$ times.
+This bound is non-trivial at much smaller values of $T$, and we will use it in the following.
+
+### Need to Bound $T_i(T)$
+
+We now have that with large probability the favorable event holds. On $\xi$, we have for every arm $i$:
+
+$$
+|\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}}
+$$
+
+The deviation of arm $i$ at time $t$ depends on how large $H$, $T$, and $s = T_i(T)$ are.
+While $\delta$, $H$, $T$ are deterministic, the number of times arm $i$ has been pulled, $s$, is a random variable.
+In order to know how large the probability of the favorable event is--and thus the error probability--at the end of the sampling period, we need to know the value of $T_i(T)$, or at least bound a range of potential values.
+Put differently: To ensure a deviation smaller than $\sqrt{\frac{T\delta^2}{HT_i(t)}}$ for arm $i$, we need to ensure that arm $i$ has been pulled at least $T_i(t)$ times by the algorithm.
 As usual in multi-armed bandits, and different from uniform sampling, the number of pulls is a random variable that also depends on how often other arms are pulled.
-In general, we do not want each arm to be pulled an equal amount, but each arm should be pulled some times, and not too many times.
+In general, we do not want each arm to be pulled an equal amount, but each arm should be pulled at least a few times, and no arm too many times.
 
@@
 
-which can be now be reduced to a form that is not specific to $k$:
+which can be now be reduced to a form that is not specific to characteristics of arm $k$:
 
@@
 We thus have derived a lower bound on the amount of pulls for any arm.
-That means that we can show that no arm is pulled an insufficient amount of times with large probability, and that consequently the favorable event hold and the estimated mean is sufficienctly separated from the threshold.
+This means that we can show that no arm is pulled an insufficient amount of times with large probability, and that consequently the favorable event holds and the estimated mean is sufficienctly separated from the threshold.
 
@@
 As the last step, we need to check whether the lower bound on the pulls of any arm suffices to ensure that the separation condition holds on the favorable event.
-That means, given $T_i(T) \geq (1-2\sqrt{2}\delta)^2 \frac{T}{2H\Delta_i^2}$, do we have $|\hat{\mu}_i(T) - \mu | \leq \frac{\Delta}{2}$ on the favorable event $\xi = \Big\{|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}}\Big\}$?
+That means, given $T_i(T) \geq (1-2\sqrt{2}\delta)^2 \frac{T}{2H\Delta_i^2}$, do we have $|\hat{\mu}_i(T) - \mu | \leq \frac{\Delta_i}{2}$ on the favorable event $\xi = \Big\{|\hat{\mu}_i - \mu | \leq \sqrt{\frac{T\delta^2}{H T_i(T)}}\Big\}$?
 To check, we plug the lower bound into the favorable event and get
@@
 $$
-
-We now present the lower bound given in Locatelli et al.
-(2016) for the thresholding bandit problem.
-In order to derive the bound, a problem is specified to show that the error of the lower bound is attained even in this specific problem.
-In particular, for a set of problems with Gaussian distributions of variance $1$, the largest probability of error on these problems that the best algorithm exhibits is still at least as large as the lower bound.
 
@@
 
-A proof of the lower bound is given in the Appendix in \autoref{sec:AppendixAPTLB}.
+A proof of the lower bound is given in the Appendix in \autoref{app:AppendixAPTLB}.
 
@@
 (2016), the assumptions for the bounds no longer hold as arms become less sub-Gaussian; the complexity $H$ and the term $\hat{\Delta}_i(t)$ in the algorithm's index are both motivated by sub-Gaussian distributions.
-The more a problem deviates from those, the less appropriate the quantities become.
-In particular, the empirical mean will be less (or not at all) concentrated around the true mean and more impacted by outliers which are more likely under non sub-Gaussian distributions.
+The more a problem deviates from these, the less appropriate the quantities become.
+In particular, the empirical mean will be less concentrated around the true mean and impacted by outliers which are more likely under non-sub-Gaussian distributions.
 Locatelli et al.
@@
 The previous chapter introduces the thresholding bandit problem as described in Locatelli et al.
-(2016), and the APT strategy as a first algorithm that is simple, yet order-optimal for large budgets.
-However, we end with the conclusion that a KL-divergence based measure of the distance between the distributions and the threshold might be more useful than the simple gap $\Delta^2_i = (\mu_i - \tau_i)^2$ employed so far.
+(2016), and the APT strategy as a first algorithm that is simple, yet order-optimal for large enough budgets.
+However, we end with the conclusion that a KL-divergence based measure of the distance between the distributions and the threshold might be more useful than the squared gaps $\Delta^2_i$ employed so far.
 Indeed, citing Kaufmann et al.
-(2016), we note that the complexity $H$ -- and thus the gaps -- used so far can be considered a sub-Gaussian approximation of a better complexity measure based on information theoretic measures like the Kullback-Leibler divergence.
+(2016), we note that the complexity $H$--and thus the gaps--can be considered a sub-Gaussian approximation of a better complexity measure based on information theoretic measures like the Kullback-Leibler divergence.
 
@@
 Their work offers methods that can inform our goal of extending the thresholding bandit problem.
-In what follows, we adopt the notation of Kaufmann et al.
-(2016) to ease a comparison with their arguments.
+In what follows, we adapt their notation to the one used by Locatelli et al.
+(2016).
 
@@
 They describe their bandit model $\nu = (\nu_1,...,\nu_K)$ by $K$ arms characterized by probability distributions $\nu_i$, $i \in \mathbb{A} = \{1,...,K\}$, with mean $\mu_i$.
-A learner picks at any time step $t=1,2,...,$ an arm $I_t \in \{1,...,K\}$ for which she observes the independent reward $X_{t} \sim \nu_{I_t}$.
+A learner picks at any time step $t=1,2,...,$ an arm $I_t \in \{1,...,K\}$ for which it observes the independent reward $X_{t} \sim \nu_{I_t}$.
 The learner aims to find the $m$ out of $K$ arms with the largest expected reward.
@@
 In the fixed budget setting, we run algorithms for $T$ samples and then compare them based on their expected loss, $\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m) =: p_t(\nu)$ as we have seen in $\autoref{sec:Setup}$.
-Alternatively, consider a $\delta$-PAC strategy $\mathcal{S}(\delta)$for which it holds for every problem $\nu \in \mathcal{M}_m$ that the classification holds at least with confidence level $1-\delta$, that is, $\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta$.
-The strategy has to achieve this level of confidence in its prediction before it is allowed to stop sampling.
+Alternatively, consider a $\delta$-PAC strategy $\mathcal{S}(\delta)$ for which it holds for every problem $\nu \in \mathcal{M}_m$ that the classification holds at least with confidence level $1-\delta$, that is, $\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta$.
+The strategy has to achieve this level of confidence in its classification before it is allowed to stop sampling.
 This is the fixed confidence case, in which the budget $T=T_{\delta}$ is no longer fixed upfront, but becomes a random variable.
@@
 
-Given this setup, we can now follow the arguments of Kaufmann et al.
+Given this setup, we follow the arguments of Kaufmann et al.
 (2016) to derive complexity measures for the top-$m$ problem.
-As alluded to earlier, these complexity measures will rely on the KL-divergence in contrast to the complexity $H$ used by Locatelli et al.
+As alluded to earlier, the complexity measures will rely on the KL-divergence in contrast to the complexity $H$ used by Locatelli et al.
 (2016).
-When discussing $H$, its motivation is that it represents the difficulty of the problem by measuring the distance between arms and the threshold.
+When discussing $H$, the motivation has been that it represents the difficulty of the problem by measuring the distance between arms and the threshold.
 Instead, Kaufmann et al.
@@
 
-To prove this statement for a given $\delta$-PAC strategy $\mathcal{S}$, we assume certain continuity conditions (compare Kaufmann et al.
-(2016)) under which there exists for every arm $i \in \{1, \dots, K\}$ an alternative model $\nu' = (\nu_1, \dots, \nu_{i-1}, \nu_i', \nu_{i+1}, \dots, \nu_K)$.
+To prove this statement for a given $\delta$-PAC strategy $\mathcal{S}$, we assume certain continuity conditions which are fulfilled by the one-parameter exponential family of distributions, for example (compare Kaufmann et al.
+(2016)).
+Under those, there exists for every arm $i \in \{1, \dots, K\}$ an alternative model $\nu' = (\nu_1, \dots, \nu_{i-1}, \nu_i', \nu_{i+1}, \dots, \nu_K)$.
 In this alternative model, in accordance with the continuity conditions, only arm $i$ is modified.
@@
 To compare this to the thresholding bandit problem, assume that arms $\nu_{m}$ and $\nu_{m+1}$ indirectly define a threshold $\tau \in (\mu_{m+1},\mu_m)$.
-Then, by creating an alternative problem as described here, we flip arm $i$ around the implied threshold $\tau$ (compare the lower bound proof in \autoref{sec:AppendixAPTLB}).
+Then, by creating an alternative problem as described here, we flip arm $i$ around the implied threshold $\tau$ (compare the lower bound proof in \autoref{app:AppendixAPTLB}).
 
@@
 (2016) that match the lower bounds, we show how based on the proof of Theorem 12 in Kaufmann et al.
-(2016) very similar lower bounds can be derived for the fixed budget thresholding problem.
+(2016) a similar lower bound can be derived for the fixed budget thresholding problem.
 
@@
 Thus, we can show the following corollary which gives a bound on the complexity of the single-armed thresholding bandit.
+That is, we bound how quickly the error probability decreases at best as the sample size increases.
 
@@
 $\mathbb{E}_{\nu'}[N_1(t)]$ is not a random variable but equals $T$.
-The single-armed bandit is a simple hypothesis test.
-
-But as we see in the following corollary, we can extend the lower bound to the $K$-armed fixed budget thresholding bandit problem, which stands in contrast to the fact that for the top-$m$ problem, it is only possible to show the lower bound for two arms.
-The result is based on an alternative setting $\nu'$ in which all arms have means $\mu' = \tau$ such that their expected number of pulls corresponds to uniform sampling, $\mathbb{E}_{\nu'}[N_i(t)] = T/K$.
-
-\begin{corollary}
-Consider the setting in \autoref{sec:Setup}.
-Let $\nu = (\nu_1, ..., \nu_K)$ be a $K$-armed thresholding bandit problem in which $\tau$ is the threshold fixed upfront.
-For $i \in \{1,...,K\}$, let $\nu_i$ be from the one-parameter exponential family of distributions such that $\nu_i$ can be parameterized by its mean, $\mu_i$, and the Kullback-Leibler divergence between distributions $\nu_i$ and $\nu_i'$ can be written as $\KL(\nu_i, \nu_i') = \KL(\mu_i, \mu_i')$.
-In the fixed budget setting, any consistent algorithm satisfies for $\mu_i' \rightarrow \tau$:
-
-$$
-\limsup_{t \rightarrow \infty} -\frac{1}{t} \log p_t(\nu) \leq \max_{i \in \{1,...,K\}} \KL(\mu_i' || \mu_i)
-$$
-
-or
-
-$$
-- \frac{1}{t} \log p_t(\nu) \leq \frac{1}{K}\sum_{i=1}^{K} \KL(\tau || \mu_i),
-$$
-\end{corollary}\label{corollary:LBKTBP}
-
-We present the proofs of \autoref{sec:LBTBP} in the appendix in \autoref{sec:corollaryLBTBPproof}.
-Corresponding to the complexity measures defined in equation $(1)$ of Kaufmann et al.
-(2016), we can define the complexity $\kappa_{TBP}(\nu)$ in the thresholding bandit problem and lower bound it:
-
-$$
-\kappa_{TBP}(\nu) = \inf_{S \text{ consistent}} \Big(\limsup_{t \rightarrow \infty} - \frac{1}{t} \log p_t(\nu)\Big)^{-1} \geq K \Big(\sum_{i=1}^{K} \KL(\mu_i'||\mu_i)\Big)^{-1}
-$$
+The single-armed bandit is a simple hypothesis test on a sample of size $T$.
+In a way, it is a degenerate case of a multi-armed bandit problem.
+
+We present the proof of \autoref{sec:LBTBP} in \autoref{app:corollaryLBTBPproof}.
+While we were hoping to also prove a lower bound for the $K$-armed bandit problem, we were not able to do so as this entails the expectation under the alternative problem of the number of times the changed arm $a$ is pulled.
+In any case, the result for the one-armed thresholding bandit stresses the similarity to hypothesis testing, and will give further motivation for the use of the likelihood ratio test statistic as index in the new Simple Likelihood Ratio algorithm in \autoref{sec:LRasIndex}.
 
@@
 Kaufmann et al.
-(2016) do not present algorithms matching the lower bound of Theorem \ref{theorem:KaufmannEtAlTheorem17}.
-They do consider algorithms that connect to Theorem \ref{theorem:KaufmannEtAlTheorem4} and Theorem \ref{theorem:KaufmannEtAlTheorem12}.
+(2016) present algorithms that connect to Theorem \ref{theorem:KaufmannEtAlTheorem4} and Theorem \ref{theorem:KaufmannEtAlTheorem12}.
 Given that we aim to extend the fixed budget thresholding bandit problem, we are most interested in the matching strategies for Theorem \ref{theorem:KaufmannEtAlTheorem12}.
@@
 
-Thus, Kaufmann et al.
+Consequently, Kaufmann et al.
 (2016) joins other papers like Audibert et al.
@@
 This lower bound can be interpreted as a minimax game^[See the presentation by Aurélien Garivier at COLT 2016: <https://youtu.be/eLyrrYqJlkE>], where the experimenter has to choose the share of samples she attributes to each arm in a way that is optimal given that nature will respond and choose the most difficult alternative model given her weights.
-Thus, to make the lower bound practical, it is a matter of finding the optimal weights $w^*(\bm{\mu})$.
+Thus, making the lower bound practical is a matter of finding the optimal weights $w^*(\bm{\mu})$.
 This step did not occur in the lower bound for the top-$m$ problem since the alternative models were specified by changing the distribution of one arm with respect to the "border" between the two groups of arms.
@@
 Lemma \ref{theorem:KaufmannEtAlLemma1} is able to measure the "transportation cost" (see Garivier and Kaufmann, 2016) of moving from one distribution to another one in terms of Kullback-Leibler divergence.
-It is the bound on the expected likelihood ratio term that appears when changes in distribution are applied.
-
-In the case of the fixed budget top-$m$ arm identification problem, we see that the derivation of a lower bound on the complexity term is mostly limited by the difficulty of defining an alternative problem $\nu'$ to $\nu$ that fits the Lemma \ref{theorem:KaufmannEtAlLemma1}.
+It is the bound on the expected likelihood ratio term that appears when changes in distribution are applied (compare Garivier and Kaufmann, 2016).
+
+In the case of the fixed budget top-$m$ arm identification problem, we see that the derivation of a lower bound on the complexity term is mostly limited by the difficulty of defining an alternative problem $\nu'$ to $\nu$ that fits Lemma \ref{theorem:KaufmannEtAlLemma1}.
 But given the intuition that in top-$m$ problems the $m$-th best arm and the $(m+1)$-th best arm define an implied threshold between the two groups of arms, we were able to apply the ideas of Kaufmann et al.
@@
 In contrast to their problem, arms are classified against the known threshold $\tau$, which makes it possible to define an alternative problem $\nu'$ in which we do not have to change arms with respect to each other, but only with respect to $\tau$.
-This has lead us to the simple lower bound on the problem complexity for the thresholding bandit problem with exponential family distributions given in Corollary \ref{corollary:LBKTBP}.
+This has lead us to the simple lower bound on the problem complexity for the one-armed thresholding bandit problem with exponential family distributions given in Corollary \ref{corollary:LB1TBP}.
 
@@
 Indeed, it might even be easier as the best arm does not have to be estimated; instead, we would compare each arm to the threshold $\tau$.
-Intuitively, one can frame this problem for each arm individually as an hypothesis test between the maximum likelihood estimate of the mean and the threshold $\tau$.
+Intuitively, one can frame this problem for each arm individually as a hypothesis test between the maximum likelihood estimate of the mean and the threshold $\tau$.
 We will come back to this idea in \autoref{sec:LikelihoodRatioForExponentialFamily}.
@@
 Lastly, we observe that Garivier and Kaufmann (2016) support their algorithm's main strategy by an additional D-Tracking rule which protects them against poor estimates in the beginning of the sampling.
-Such rule should be mostly unnecessary, for example, the cumulative regret setting, as algorithms there rely on upper confidence bound estimates.
+Such rule should be mostly unnecessary in the cumulative regret setting, as algorithms there rely on upper confidence bound estimates.
 This is not the case for the Track-and-Stop strategy introduced in Garivier and Kaufmann, and neither for our Simple Likelihood Ratio strategy introduced in \autoref{sec:1DSLR}.
@@
 The algorithm also exhibits favorable characteristics such as its upper bound holding at any stopping time, and that it does not require any parameter to be tuned upfront.
-However, we have seen that the index $B^{APT}$ and the complexity term $H$ employed by the APT algorithm are the most effective for $R$-sub-Gaussian distributions.
+However, we saw that the index $B^{APT}$ and the complexity term $H$ employed by the APT algorithm are the most effective for $R$-sub-Gaussian distributions.
 Both are related to the KL-divergence between two Gaussian distributions of equal variance.
@@
 Information theoretic measures are one way of taking not only the sample mean into account to estimate differences between distributions -- as done by the APT algorithm.
-Another logical extension is to consider higher moments of a distribution, like its variance.
+Another logical extension is to consider higher order moments like the sample variance.
 After all, arms do not necessarily have the same variance, even if they are sub-Gaussian (two arms might be $R_1$-sub-Gaussian and $R_2$-sub-Gaussian).
@@
 (2017).
-We then go back to the information theoretic ideas and introduce a new algorithm based on the concept of likelihood ratios in \autoref{sec:LikelihoodRatioForExponentialFamily}.
+We then return to the information theoretic ideas and introduce a new algorithm based on the concept of likelihood ratios in \autoref{sec:LikelihoodRatioForExponentialFamily}.
 Finally, we compare the performance of different algorithms based on simulations and real world data sets in \autoref{chap:Experiments}.
@@
 
-In the case of the APT algorithm the number of times a specific arm has been drawn $T_i$ measures how concentrated the estimated mean is around the true mean (and thus for large $T_i$ an arm is no longer drawn even if $\hat{\mu}$ is close to $\tau$).
+In the case of the APT algorithm, the number of times a specific arm has been drawn $T_i$ measures how concentrated the estimated mean is around the true mean (and thus for large $T_i$ an arm is no longer drawn even if $\hat{\mu}$ is close to $\tau$).
 This exploration is regulated by the combination of the variance estimate $\hat{v}_i$ and the exploration factor $\psi_m$ in the case of the AugUCB algorithm.
@@
 Indeed, the AugUCB algorithm goes a little further than the APT algorithm in that it stops to sample arms when a separation condition (mean separated from threshold) is estimated to hold.
-The same separation condition is used in the authors' upper bound proof and is reminiscient of the separation condition used in the proof of the upper bound in Locatelli et al.'s (2016) (compare \autoref{sec:CheckSeparationCondition}).
+The same separation condition is used in the authors' upper bound proof and is reminiscient of the separation condition used in the proof of the upper bound in Locatelli et al.
+(2016) (compare \autoref{sec:CheckSeparationCondition}).
 
@@
 
-### Anytime Parameter-free Empirical Variance Guided Algorithm \label{sec:EVTAlgorithm}
+### Empirical Variance Guided Thresholding Algorithm \label{sec:EVTAlgorithm}
 
@@
 Roughly similar to how the Kullback-Leibler divergence measures distances between distributions, $D_i^{EVT}$ including the empirical variance serves as a crude measure of distance between threshold and distribution.
-We note that for a Bernoulli distributed random variable, $D_i^{EVT}$ is always decreasing as the mean approaches the threshold (compare figure 2).
+We note that for a Bernoulli distributed random variable, $D_i^{EVT}$ is always decreasing as the mean approaches the threshold (compare Figure 2).
 Similar should hold in general for bounded variables as the variance and the mean are linked by the distance of the mean to the bound of the support (in contrast to, for example, a normal distributed random variable where a change in the mean does not correspond to a change in the variance).
@@
 
+point_index <- seq(1, dim(evtdf)[1], by = 3000)
+
 ggplot(evtdf, aes(x = mu, y = Distance, 
@@
   geom_line() +
+  geom_point(aes(x = mu, y = Distance, group = Algorithm,
+                    color = Algorithm, linetype = Algorithm, 
+                 shape = Algorithm), data = evtdf[point_index,],
+             size = 2) +
   labs(#title = "Comparison of Distance Measures by Algorithm",
@@
 
-```{r Hevt_Hapt_Comparison, echo = FALSE, message = FALSE, fig.align="center", out.width = '70%', fig.cap = "Comparing the complexity terms used in the APT, AugUCB, and EVT algorithms, we observe that the problem complexity of the EVT algorithm increases much less rapidly than for the other algorithms.
+```{r Hevt_Hapt_Comparison, echo = FALSE, warning = FALSE, message = FALSE, fig.align="center", out.width = '70%', fig.cap = "Comparing the complexity terms used in the APT, AugUCB, and EVT algorithms, we observe that the problem complexity of the EVT algorithm increases much less rapidly than for the other algorithms.
 Thus, the EVT should be able to cope with arms close to the threshold better than the APT algorithm.
@@
 
+point_index <- seq(1, dim(hcompdf)[1], by = 3000)
+
 ggplot(hcompdf, aes(x = mu, y = Complexity, group = Algorithm,
@@
   geom_line() +
+  geom_point(aes(x = mu, y = Complexity, group = Algorithm,
+                    color = Algorithm, 
+                 shape = Algorithm), data = hcompdf[point_index,],
+             size = 2) +
   geom_vline(aes(xintercept = 0.5), linetype = 2) +
@@
 
-### Likelihood Ratio as Index in Sequential Sampling
-
-We now employ the concept of the likelihood-ratio test to a new sequential sampling strategy for the thresholding bandit problem.
+### Likelihood Ratio as Index in Sequential Sampling \label{sec:LRasIndex}
+
+We now employ the concept of the likelihood ratio test to a new sequential sampling strategy for the thresholding bandit problem.
 In contrast to the cumulative regret problem or the best arm identification problem, the thresholding bandit problem offers a natural $H_0$ hypothesis for the arms' distributions: the threshold $\tau$.
@@
 We have $B_i^{LR}(t) \leq 1$, $t \uparrow \rightarrow B_i^{LR}(t) \downarrow$, and $|\hat{\mu}_i(t) - \tau| \uparrow \rightarrow B_i^{LR}(t) \downarrow$.
-Consequently, by choosing the arm that maximizes $B_i^{LR}(t)$, we choose an arm for which we either have not collected many samples, or for which the sample mean is close to the threshold $\tau$.
-In this sense, a strategy based on the likelihood ratio is reminiscient of the index employed by the APT algorithm.
-Indeed, assuming the samples are normally distributed with equal variance for all arms under both $H_0$ and $H_1$, $-\log(B_i^{LR}(t))$ equals the index in APT.
-Why then would we prefer the likelihood based strategy?
+Consequently, by choosing the arm that maximizes $B_i^{LR}(t)$, we choose an arm for which we either have not collected many samples, or for which the evidence collected so far suggests that the sample mean is not significantly separated from the threshold $\tau$.
 
@@
 
-We now focus on a thresholding bandit problem where the arms are distributed according to $\nu_{\theta_1}, ..., \nu_{\theta_K}$, which are all from the same canonical exponential family of distributions with scalar parameter $\theta_i \in \Theta$.
+We now focus on a thresholding bandit problem where the arms are distributed according to $\nu_{\theta_1}, ..., \nu_{\theta_K}$, which are from the same canonical exponential family of distributions with scalar parameter $\theta_i \in \Theta$.
 The probability density function of the absolutely continuous distribution $\nu_{\theta_i}$ with regard to a dominating measure $\rho$ on $\mathbb{R}$ is given by $q(x|\theta) = h(x) \exp(T(x)\theta - b(\theta))$.
@@
 
-## 2D-SLR Algorithm for Normal Distributions
-
-As soon as we move away from one-parameter distributions parameterized by their mean, it becomes less clear how the likelihood ratio for $H_0: \mu = \tau$ and $H_1: \mu = \hat{\mu}$ should be calculated.
+## 2D-Simple Likelihood Ratio Algorithm for Normal Distributions
+
+As soon as we move away from one-parameter distributions parameterized by their mean, it becomes less clear how the likelihood ratio for $H_0: \mu = \tau$ and $H_1: \mu \neq \tau$ should be calculated.
 In the case of Normal distributions with unknown mean and unknown variance, given that the variance and mean estimate are linked, we can use
 $$
-H_0: \mu_0 = \tau \land \sigma_0^2 = \sigma^2_{\tau} = \frac{1}{n}\sum_{i=1}^{n}(x_i-\tau)^2 \quad \text{vs.} \quad H_1: \mu_1 = \hat{\mu} \land \sigma_1^2 = \hat{\sigma}^2 = \frac{1}{n}\sum_{i=1}^{n}(x_i-\hat{\mu})^2
-$$
+H_0: \mu_0 = \tau \land \sigma_0^2 = \sigma^2_{\tau} = \frac{1}{n}\sum_{i=1}^{n}(x_i-\tau)^2  
+$$
+and use the maximum likelihood estimates $\mu_1 = \hat{\mu}$,  $\sigma_1^2 = \hat{\sigma}^2 = \frac{1}{n}\sum_{i=1}^{n}(x_i-\hat{\mu})^2$ in the likelihood ratio statistic.
 
@@
 
-At the beginning of this thesis, we set out to find an algorithm that improves upon the Anytime Parameter Free algorithm introduced in Locatelli et al.
+At the beginning of this thesis, we set out to find an algorithm that improves upon the Anytime Parameter Free Thresholding algorithm introduced in Locatelli et al.
 (2016) for the thresholding bandit problem.
@@
 
-As we see in the experiments that follow, the SLR strategy is able to improve significantly upon the APT strategy in many cases.
+As we see in the experiments that follow, the SLR strategy is able to improve significantly upon the APT strategy in many problems.
 
@@
 Additionally, we include the Bayes-UCB algorithm introduced in Kaufmann et al.
-(2012) for the cumulative regret setting.
-See \autoref{sec:AppendixBUCB} in the appendix for how we adapt the Bayes-UCB algorithm to the thresholding bandit problem.
-
-## Synthetic Data \label{sec:SyntheticData}
+(2012a) for the cumulative regret setting.
+See \autoref{app:AppendixBUCB} for how we adapt the Bayes-UCB algorithm to the thresholding bandit problem.
+
+## Simulations with Synthetic Data \label{sec:SyntheticData}
 
@@
 
-As the next figure shows, essentially all methods converge rapidly to an error rate of very close to zero, where the error rate is the share of the 5000 simulations on which the classification of the algorithm is wrong.
+As Figure 4 shows, essentially all methods converge rapidly to an error rate of very close to zero, where the error rate is the share of the 5000 simulations on which the classification of the algorithm is wrong.
 Only the uniform strategy that clearly lacks behind.
@@
 
-```{r simulation1_results, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for simulation 1."}
+```{r simulation1_results, warning = FALSE, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for simulation 1."}
 library(ggplot2)
@@
                             results = alg_res)
-ggplot(loc2_comp_res, aes(x = index, y = results)) + 
-  geom_line(aes(group = names, color = names)) +
-  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
-  labs(subtitle = "Dashed Line indicates Error = 0.1.",
-       y = "log(Error)", x = "Round Index") + 
+point_index <- seq(1, dim(loc2_comp_res)[1], by = 900)
+
+ggplot(loc2_comp_res, aes(x = index, y = results,
+                          group = names, color = names)) + 
+  geom_line() +
+  geom_point(aes(x = index, y = results,
+                group = names, color = names,
+                shape = names),
+             data = loc2_comp_res[point_index,], size = 2.5) +
+  #geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
+  labs(#subtitle = "Dashed Line indicates Error = 0.1.",
+       y = "Error (log10 scale)", x = "Round Index") + 
   coord_cartesian(xlim = c(0,2000)) +
   scale_color_discrete(name = "Algorithm") + 
-  theme_bw() #+
+  scale_shape_discrete(name = "Algorithm") + 
+  theme_bw() +
+  scale_y_log10() #+
   #theme(legend.position = "bottom")
@@
 
-The figure below shows the performance of all algorithms.
+Figure 5 shows the performance of all algorithms.
 The results underline that this problem is much harder in general ($H_2^{APT} \approx 24703$).
@@
 One interesting observation, that we will observe in all simulations with Bernoulli arms, is the superior performance of the Bayes-UCB algorithm adapted from Kaufmann et al.
-(2012) which was originally designed for cumulative regret problems.
+(2012a) which was originally designed for cumulative regret problems.
 Nonetheless, the algorithm proves again and again to be the best performing.
-Compare with \autoref{sec:AppendixBUCB} for more analysis on the behavior of the Bayes-UCB algorithm in simulation 2.
+Compare with \autoref{app:AppendixBUCB} for more analysis on the behavior of the Bayes-UCB algorithm in simulation 2.
 In particular, consider Figures 17 and 18 which show for individual arms the distribution of pulls for that arm across simulations.
@@
 
-```{r simulation2_results, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for simulations 2 and 3. Note the different x-axes."}
+```{r simulation2_results, echo = FALSE, warning = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for simulations 2 and 3. Note the different x-axes."}
 library(ggplot2)
@@
 
-ggplot(sim23_res, aes(x = index, y = results)) + 
-  geom_line(aes(group = Algorithm, color = Algorithm)) +
-  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
+point_index <- seq(1, dim(sim23_res)[1], by = 1800)
+
+ggplot(sim23_res, aes(x = index, y = results,
+                      group = Algorithm, color = Algorithm)) + 
+  geom_line() +
+  geom_point(aes(x = index, y = results,
+                group = Algorithm, color = Algorithm,
+                shape = Algorithm),
+             data = sim23_res[point_index,], size = 2) +
+  #geom_hline(aes(yintercept = (0.1)), linetype = 2) +
   facet_grid(.~Simulation, scales = "free") +
-  labs(subtitle = "Dashed Line indicates Error = 0.1.",
-       y = "log(Error)", x = "Round Index") +
+  labs(#subtitle = "Dashed Line indicates Error = 0.1.",
+       y = "Error (log10 scale)", x = "Round Index") +
   scale_color_discrete(name = "Algorithm") +
   theme_bw() + 
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom") +
+  scale_y_log10()
 ```
 
-```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '70%', fig.cap = "Budget allocation across arms for APT and SLR algorithms in simulation 2."}
+```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Budget allocation across arms for APT and SLR algorithms in simulation 2."}
 load(file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/loc6nt_ma.Rda")
@@
 
+\newpage
+
 ### Simulations 4 and 5: Exponential and Poisson Distributions
@@
 exp45_res$Distribution <- c(rep("Exponential", 19885), rep("Poisson", 49885))
-
-ggplot(exp45_res, aes(x = index, y = results)) + 
-  geom_line(aes(group = Algorithm, color = Algorithm)) +
-  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
+point_index <- seq(1, dim(exp45_res)[1], by = 1200)
+
+ggplot(exp45_res, aes(x = index, y = results, 
+                      group = Algorithm, color = Algorithm)) + 
+  geom_line() +
+  geom_point(aes(x = index, y = results,
+                group = Algorithm, color = Algorithm,
+                shape = Algorithm),
+             data = exp45_res[point_index,], size = 2) +
+  #geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
   facet_grid(.~Distribution, scales = "free") +
   labs(#title = "Results of Experiment 5", 
-       subtitle = "Dashed line at Error = 0.1.", 
-       y = "log(Error)", x = "Round Index") +
+       #subtitle = "Dashed line at Error = 0.1.", 
+       y = "Error (log10 scale)", x = "Round Index") +
   theme_bw() +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom") +
+  scale_y_log10()
 ```
@@
 
-```{r, echo = FALSE}
-load("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/arms_example_binary.Rda")
-
-knitr::kable(arms_example_binary, caption = "Example of the binary time series data for five products.")
+```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%', fig.cap = "We use time series crossvalidation to create many samples from one data set."}
+plot(0,0,xlim=c(0,28),ylim=c(0,1),
+     xaxt="n",yaxt="n",bty="n",xlab="",ylab="",type="n")
+i <- 1
+for(j in 1:20)
+{
+  test <- (6+j):26
+  train <- 1:(5+j)
+  pre_train <- 1:(j-1)
+  arrows(0,1-j/20,27,1-j/20,0.05)
+  points(train,rep(1-j/20,length(train)),pch=19,col="blue")
+  if(j > 1)
+    points(pre_train, rep(1-j/20,length(pre_train)),pch=19,col="gray")
+  if(length(test) >= i)
+    points(test[i], 1-j/20, pch=19, col="red")
+  if(length(test) >= i)
+    points(test[-i], rep(1-j/20,length(test)-1), pch=19, col="gray")
+  else
+    points(test, rep(1-j/20,length(test)), pch=19, col="gray")
+}
+text(28,.95,"time")
 ```
@@
 For this reason, the experiments we present below are run on $60 \cdot 24 \cdot 7 = 10080$ observations for each arm, so as to have a sample for one full week.
+
+```{r, echo = FALSE}
+load("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/arms_example_binary.Rda")
+
+knitr::kable(arms_example_binary, caption = "Example of the binary time series data for five products.")
+```
+
+\newpage
 
@@
 
-```{r, echo = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for experiment 1."}
+```{r, echo = FALSE, warning = FALSE, fig.align = "center", out.width = '80%', fig.cap = "Performance comparison of algorithms for experiment 1."}
 library(ggplot2)
@@
 index <- c(rep(10:10080, times = 5), 20:10080)
-alg_res <- log(c(amo3_comp_UNIFORM, amo3_comp_APT, amo3_comp_AugUCB, amo3_comp_LR, amo3_comp_BUCB, amo3_comp_EVT))
+alg_res <- (c(amo3_comp_UNIFORM, amo3_comp_APT, amo3_comp_AugUCB, amo3_comp_LR, amo3_comp_BUCB, amo3_comp_EVT))
 loc3_comp_res <- data.frame(index = index, Algorithm = alg_names, 
                             results = alg_res)
-ggplot(loc3_comp_res, aes(x = index, y = results)) + 
-  geom_line(aes(group = Algorithm, color = Algorithm)) +
-  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
+point_index <- seq(1, dim(loc3_comp_res)[1], by = 900)
+
+ggplot(loc3_comp_res, aes(x = index, y = results,
+                          group = Algorithm, color = Algorithm,
+                          shape = Algorithm)) + 
+  geom_line() +
+  geom_point(aes(x = index, y = results,
+                group = Algorithm, color = Algorithm,
+                shape = Algorithm),
+             data = loc3_comp_res[point_index,], size = 2) +
+  #geom_hline(aes(yintercept = (0.1)), linetype = 2, color = "lightgrey") +
   labs(#title = "Results of Real Data Experiment 1", 
-       subtitle = paste0("Dashed Line indicates Error = 0.1."), 
-       y = "log(Error)", x = "Round Index") +
-  theme_bw()
+       #subtitle = paste0("Dashed Line indicates Error = 0.1."), 
+       y = "Error Rate", x = "Round Index") +
+  theme_bw() +
+  ylim(c(0,1))
 ```
@@
 Given that the highs and lows for the different models run mostly parallel, it stands to reason that this effect is caused by the variation in means of the arms over time.
-Indeed, roughly comparing the error curves to the moving averages in the previous figure, the increase in errors after round $5000$ and the decreasing error after round $7500$ seems to line up with the fluctuations observed in the data.
+Indeed, roughly comparing the error curves to the moving averages in the Figure 9, the increase in errors after round $5000$ and the decreasing error after round $7500$ seems to line up with the fluctuations observed in the data.
 Given that we evaluate the models against a sample mean of all observations, it is not surprising that the uniform sampling strategy has a certain advantage when it comes to "factoring out" the seasonalities.
@@
 As in the previous experiment, we can also take a look at the one day moving averages of the arms to quickly assess the time dependency of the means.
-Given those and the previous experiment, the performance results of Experiment 2 shown in Figure 13 are not surprising.
+Given those and the previous experiment, the performance results of Experiment 2 shown in Figure 12 are not surprising.
 We recognize the same structure as previously.
@@
 
-On the right hand side of figure 13, the performance of the algorithms on synthetic data from Bernoulli distributions is depicted.
-These synthetic samples were sampled from distributions with mean equal to the sample means of the real data.
+On the right hand side of Figure 12, the performance of the algorithms on synthetic data from Bernoulli distributions is depicted.
+These synthetic samples are sampled from distributions with mean equal to the sample means of the real data.
 We thereby create similar samples that are perfectly i.i.d.
@@
 
-rbind(real_daily, syn_daily) %>%
-  rename(Arm = arm) %>%
-  ggplot(aes(x = index, y = mean, group = Arm, color = Arm)) +
+total_daily <- rbind(real_daily, syn_daily) %>% rename(Arm = arm)
+
+total_daily %>%
+  ggplot(aes(x = index, y = mean, 
+             group = Arm, color = Arm)) +
   geom_line(size = 0.4) +
@@
   rename(Algorithm = names)
+point_index <- seq(1,dim(loc4total)[1], by = 1800)
 
 ggplot(loc4total, aes(x = index, y = results, 
-                      group = Algorithm, color = Algorithm)) + 
+                      group = Algorithm, color = Algorithm, 
+                      shape = Algorithm)) + 
   geom_line() +
+  geom_point(aes(x = index, y = results, 
+                      group = Algorithm, color = Algorithm, 
+                      shape = Algorithm),
+             data = loc4total[point_index,], size = 2) +
   facet_grid(.~source) +
-  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
+  #geom_hline(aes(yintercept = (0.1)), linetype = 2) +
   labs(#title = "Results of Real Data Experiment 2", 
-       subtitle = paste0("Dashed line indicates Error = 0.1."), 
-       y = "log(Error)", x = "Round Index") +
+       #subtitle = paste0("Dashed line indicates Error = 0.1."), 
+       y = "Error (log10 scale)", x = "Round Index") +
   theme_bw() +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom") +
+  scale_y_log10()
 ```
 
-Using a plot of the pulls at each round across the 5000 simulations in Figure 14, as we did for simulation 2, we can try to understand why some strategies perform well on synthetic data, but poorly on the time series data.
+Using a plot of the pulls at each round across the 5000 simulations in Figure 13, as we did for simulation 2, we can try to understand why some strategies perform well on synthetic data, but poorly on the time series data.
 
@@
 
+In the thesis at hand, we presented the general thresholding bandit problem introduced by Locatelli et al.
+(2016), as well as their Anytime Parameter-Free Thresholding algorithm.
+Given a few limitations of the APT algorithm, we explored the literature on pure exploration multi-armed bandit problems to show how the Kullback-Leibler divergence can be used to improve algorithms and performance bounds.
+Based on this work, we exhibit the similarity between the thresholding bandit problem and hypothesis testing.
+We derive a lower bound on the complexity of a one-armed thresholding bandit that corresponds to the Chernoff-Stein Lemma.
+Continuing with the intuition from hypothesis testing, we propose the Simple Likelihood Ratio algorithm for the multi-armed thresholding bandit for one-parameter exponential family of distributions.
+The SLR algorithm is shown to repeatedly outperform existing algorithms in simulations on Bernoulli, Poisson, and Exponential distributions.
+We show that adding the D-Tracking Rule originally proposed by Garivier and Kaufmann (2016) can eradicate some of the remaining weaknesses.
+Additionally to simulations, we performed offline evaluation of adaptive sampling strategies using website analytics data.
+A new time series cross validation procedure helped to preserve the time dependency structure in the data and allowed for robustness tests of the adaptive sampling strategies.
+
+Problems for future work are the derivation of lower and upper bounds on the error probability of the SLR algorithm.
+Furthermore, one might be able to adapt the lower bound on the complexity of the one-armed thresholding bandit to the multi-armed problem.
+The surprisingly very good performance of the Bayes-UCB algorithm in our simulations, as well as its superior concentration of the number of times each arm is pulled, justify a theoretical analysis of its performance.
+Lastly, including features as in contextual bandits could improve robustness of strategies when data does not fulfill i.i.d.
+assumptions.
+
 # Acknowledgements
@@
 We thank Carlo Alberto Dall'Amico for bringing our attention to multi-armed bandits in the first place.
-Sonoma Internet GmbH (Amorelie) supported this work by giving the authors access to the discussed data set.
+Sonoma Internet GmbH (Amorelie) supported this work by giving the author access to the discussed data set.
+
+The website analytics data used in experiments is available upon request. The code for simulations and experiments is available on Github: <https://github.com/timradtke/master-thesis>
 
@@
 
-O. Capp´e, A. Garivier, O-A. Maillard, R. Munos, and G. Stoltz. Kullback-Leibler upper confidence bounds for optimal sequential allocation. *Annals of Statistics*, 41(3):1516–1541, 2013a.\par
-
-O. Capp´e, A. Garivier, O.-A. Maillard, R. Munos, G. and Stoltz. Supple-
-ment to “Kullback–Leibler upper confidence bounds for optimal sequential allocation.”, *Annals of Statistics*, <DOI:10.1214/13-AOS1119SUPP>, 2013b. \par
+O. Cappé, A. Garivier, O-A. Maillard, R. Munos, and G. Stoltz. Kullback-Leibler upper confidence bounds for optimal sequential allocation. *Annals of Statistics*, 41(3):1516–1541, 2013a.\par
+
+O.
+Cappé, A.
+Garivier, O.-A.
+Maillard, R.
+Munos, G.
+and Stoltz.
+Supplement to “Kullback–Leibler upper confidence bounds for optimal sequential allocation.”, *Annals of Statistics*, <DOI:10.1214/13-AOS1119SUPP>, 2013b.
+\par
 
@@
 Kaufmann, O.
-Capp´e, and A.
+Cappé, and A.
 Garivier.
 On Bayesian Upper Confidence Bounds for Bandit Problems.
-In *Proceedings of the 15th International Conference on Artificial Intelligence and Statistics (AISTATS)*, 2012.\par
-
-E. Kaufmann, O. Capp´e, A. Garivier. On the Complexity of Best Arm Identification in Multi-Armed Bandit Models. Journal of Machine Learning Research, 17:1-42, 2016.\par
+In *Proceedings of the 15th International Conference on Artificial Intelligence and Statistics (AISTATS)*, 2012a.\par
+
+E.
+Kaufmann, N.
+Korda, and R.
+Munos.
+Thompson Sampling: An Asymptotically Optimal Finite Time Analysis.
+In *Proceedings of the 23rd International ALT Conference*, Algorithmic Learning Theory, 199-213, 2012b.
+
+E. Kaufmann, O. Cappé, A. Garivier. On the Complexity of Best Arm Identification in Multi-Armed Bandit Models. Journal of Machine Learning Research, 17:1-42, 2016.\par
 
@@
 
-# Appendix
-
-## Proof of Thresholding Bandit Lower Bound \label{sec:AppendixAPTLB}
+\appendix
+
+\section{Proof of Theorem 2} \label{app:AppendixAPTLB}
 
@@
 
-*Proof of Theorem \ref{theorem:Locatelli2016Theorem1}*: Locatelli et al.
+Locatelli et al.
 (2016) derive a lower bound for the thresholding bandit problem.
-We restate the proof here.
 The idea is as follows.
@@
 More specifically, consider a problem in which all arms follow Normal distributions $\nu_i$ with mean $\mu_i$ and variance $\sigma^2 = 1$.
-"in which w"e set $\tau = 0$ and $\epsilon = 0$ w.l.o.g.
+We set $\tau = 0$ and $\epsilon = 0$ w.l.o.g.
 Consequently, for each arm $i$ the distance from the threshold is given by $\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i$.
@@
 
-At this point, we have defined a finite set of problems of Gaussian distributions with fixed variance 1 for a given set of set of gaps between the means of the distributions and the threshold, $(\Delta_k)_k$.
-We now proof a lower bound on the worst case regret of any algorithm; that is, the maximum error probability that even the best algorithm makes on this problem.
-
-### Statistical Decision
+At this point, we have defined a finite set of problems of Gaussian distributions with fixed variance 1 for a given set of gaps $(\Delta_k)_k$ between the means of the distributions and the threshold.
+We now prove a lower bound on the worst case regret of any algorithm; that is, the maximum error probability that even the best algorithm makes on this problem.
+
+\newpage
+
+**Statistical Decision**
 
@@
 Assume that the decision $g$ distinguishes between two states of the world, $H_0$ and $H_1$.
-Then an overall error probability can be seperated into $P_{H_0}(g=1) + P_{H_1}(g = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)$.
+Then an overall error probability can be seperated into $\mathbb{P}_{H_0}(g=1) + \mathbb{P}_{H_1}(g = 0) = \mathbb{P}_{H_0}(\Omega^C) + \mathbb{P}_{H_1}(\Omega)$.
 
@@
 \begin{align}
-\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big) \\
-& = \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
+\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \Big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \Big) \\
+& = \max \Big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \Big) \label{LocatelliTheorem1ExpRegret}
 \end{align}
 
-### Empirical Kullback-Leibler Divergence
+**Empirical Kullback-Leibler Divergence**
 
 In order to give a bound on the previous equation, we start by considering $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$.
-This probability can be written as the expected change in the likelihood of observed data when moving from distribution $P_{\mathcal{B}_0}$ to $P_{\mathcal{B}_i}$, times the probability under the original state.
+This probability can be written as the expected change in the likelihood of observed data when moving from distribution $P_{\mathcal{B}^0}$ to $P_{\mathcal{B}^i}$, times the probability under the original state.
 In other words, the probability of event $\mathcal{A}_i$ under state $\mathcal{B}^i$ is given as the probability of $\mathcal{A}_i$ under the (original) state $\mathcal{B}^0$ multiplied by a factor.
@@
 
-### Change of Distribution
+**Change of Distribution**
 
@@
 
-### Concentration of the Empirical Kullback-Leibler Divergence
+**Concentration of the Empirical Kullback-Leibler Divergence**
 
@@
 
-Two things are left to do: With $T_i$, we still have one random variable left which we cannot leave in our bound.
+Two things are missing: With $T_i$, there still is one random variable left which we need to bound to make the overall bound useful.
 Second, we are actually not interested in $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$ but in $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$.
 
-### Bounding $T_i$ for $\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$
-
-We are actually interested in bounding $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$.
-In general it holds that $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K}\sum_{i=1}^K X_i$.
-Thus we can write:
+**Bounding $T_i$ for $\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$**
+
+In general it holds that $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K}\sum_{i=1}^K X_i$. Thus we can write:
 
@@
 
-First, let $a = \Delta_i \sqrt{T_i}$ and $b = 4\sqrt{\log((4\log(T)+1)K)}$. Then use $ab \leq a^2 + b^2$ to write $ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)$. And so:
+First, let $a = \Delta_i \sqrt{T_i}$ and $b = 4\sqrt{\log((4\log(T)+1)K)}$. Then use $ab \leq a^2 + b^2$ to write $ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)$. Then:
 
@@
 
-### Bringing everything together
+**Bringing everything together**
 
@@
 
-## Lower Bound for Thresholding Bandit Problem with KL-divergence \label{sec:corollaryLBTBPproof}
-
-### Lower Bound for One-Armed Thresholding Bandit \label{sec:corollaryLB1TBPproof}
-
-**Proof**: The proof follows closely the proof of Theorem 12 in Kaufmann et al. (2016) and is again an application of their transportation Lemma, Lemma 2.
-
+\section{Proof of Corollary 1} \label{app:corollaryLBTBPproof}
+
+The proof follows closely the proof of Theorem 12 in Kaufmann et al. (2016) and is again an application of their Lemma 1. 
 Consider the one-armed bandit problem, $K = 1$ with the canonical exponential family of distributions distribution $\nu_1$ parameterized by its mean $\mu_1$.
@@
 Thus, we have for the event $A = (\hat{\mathcal{S}}_\tau = \{1\})$ the probability $\mathbb{P}_{\nu}(A)$.
-On the other hand, define the alternative model $\nu'$ with mean $\mu_1' < \tau$ such that the correct classification from $\nu$ is now wrong: $\mathcal{S}_{\tau}^* {'} = (\mathcal{S}_{\tau}^*)^C = \{\emptyset\}$.
+On the other hand, define the alternative model $\nu'$ with mean $\mu_1' < \tau$ such that the correct classification of $\nu$ is now wrong: $\mathcal{S}_{\tau}^* {'} = (\mathcal{S}_{\tau}^*)^C = \emptyset$.
 Consequently, since the algorithm is still consistent on this problem, we have that $\mathbb{P}_{\nu'}(A) = p_t(\nu')$.
@@
 
-Indeed, given we consider only consistent algorithms, there should exist a number of samples for which the probability of the correct decision in problem $\nu$ is larger than the error probability in problem $\nu'$, that is: for every $\epsilon > 0$, there exists $t_0(\epsilon)$ such that for all $t \geq t_0(\epsilon)$ we have
-
-\begin{equation*}
-\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_{\nu}(A). \label{eq:BoundForCorollary}
-\end{equation*}
+Indeed, given we consider only consistent algorithms, there should exist a number of samples for which the probability of the correct decision in problem $\nu$ is larger than the error probability in problem $\nu'$, that is: for every $\delta > 0$, there exists $t_0(\delta)$ such that for all $t \geq t_0(\delta)$ we have
+
+\begin{equation}
+\mathbb{P}_{\nu'}(A) \leq \delta \leq \mathbb{P}_{\nu}(A). \label{eq:BoundForCorollary}
+\end{equation}
 
@@
 & \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)) \\
-& \geq d(\epsilon, 1- p_t(\nu)) \\
-& = \epsilon \log\Big(\frac{\epsilon}{1-p_t(\nu)}\Big) + (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) \\
-& \geq (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) + \epsilon \log(\epsilon) \\
+& \geq d(\delta, 1- p_t(\nu)) \\
+& = \delta \log\Big(\frac{\delta}{1-p_t(\nu)}\Big) + (1-\delta) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) \\
+& \geq (1-\delta) \log \Big(\frac{1-\delta}{p_t(\nu)}\Big) + \delta \log(\delta) \\
 \end{align*}
 
-Letting $\epsilon \rightarrow 0$, we get
+Letting $\delta \rightarrow 0$, we get
 
@@
 In our case of the thresholding bandit with one-parameter exponential family distributions, this is given by choosing $\mu_1' \rightarrow \tau$ (not equal to $\tau$ since else the classification of $\nu_1$ is again correct).
-By pluggin in, we get the result:
-
-$$
-t \KL(\tau, \mu_1) \geq -\log p_t(\nu) \quad \text{for} \; \mu_1' \rightarrow \tau.
-$$
-
-### Lower Bound for $K$-Armed Thresholding Bandit \label{sec:corollaryLBKTBPproof}
-
-**Proof**: The proof is very similar to the proof of the corollary for $K=1$.
-However, the alternative model needs more motivation than in the case of a single arm.
-But first, consider again that we are in the thresholding bandit problem with $K$ arms of one-parameter canonical exponential family distributions that are parameterized by their means $\mu_1, ..., \mu_K$ for the original problem $\nu = (\nu_1, ..., \nu_K)$.
-W.l.o.g, assume that all arms are above the threshold, that is, $\mu_1 \geq \tau, ..., \mu_K \geq \tau$.
-Then $\mathcal{S}_{\tau}^* = \{1, ...
-, K\}$.
-The correct classification returned after $t$ rounds is thus the event $A = (\hat{\mathcal{S}}_{\tau} = \{1, ..., K\})$.
-We can now consider Lemma 2.
-The RHS is maximized when the alternative model is chosen such that $d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A))$ is maximized.
-Given the event $A$ as defined before, this is the case when $\mathbb{P}_{\nu'}(A)$ is as small as possible.
-For consistent algorithms, this is the case when $\nu'$ is chosen such that all $\mu_1' < \tau, ..., \mu_K' < \tau$.
-Then even classifying a single arm correctly under $\nu$ would lead to a mistake in $\nu'$.
-Consequently, $A$ is the most unlikely classification for a consistent algorithm for the problem $\nu'$.
-We thus expect for any consistent algorithm that $\mathbb{P}_{\nu}(A)$ becomes large and $\mathbb{P}_{\nu'}(A)$ becomes small as the number of observations $t$ increases.
-Again, for every $\epsilon > 0$, there exists $t_0(\epsilon)$ such that for all $t \geq t_0(\epsilon)$ we have $\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)$.
-This allows us to now use Lemma 1 as previously:
-
-\begin{align*}
-\sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\nu_i', \nu_i) & \geq \sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\tau, \mu_i) \\
-& \geq d(\mathbb{P}_{\nu'}(A), \mathbb{P}_{\nu}(A)) \\
-& \geq d(\epsilon, 1-p_t(\nu)) \\
-& = \epsilon \log \Big(\frac{\epsilon}{1-p_t(\nu)}\Big) + (1-\epsilon) \log \Big( \frac{1-\epsilon}{p_t(\nu)}\Big) \\
-& \geq (1-\epsilon) \log \Big(\frac{1-\epsilon}{p_t(\nu)}\Big) + \epsilon \log(\epsilon)
-\end{align*}
-
-We let $\epsilon \rightarrow 0$, divide by $t$ and take the limsup on both sides as in Kaufmann et al. (2016):
-
-\begin{align*}
-\lim_{t \rightarrow \infty} \sup - \frac{1}{t} \log p_t(\nu) & \leq \lim_{t \rightarrow \infty} \sup \frac{1}{t} \sum_{i=1}^K \mathbb{E}_{\nu'}[N_i(t)]\KL(\tau, \mu_i) \\
-& \leq \max_{i \in \{1,...,K\}} \KL(\tau, \mu_i)
-\end{align*}
-
-Though, since for the alternative problem $\nu'$ we have for every $i \in \{1,...,K\}$ that $\mu_i = \tau$, it should hold for any consistent algorithm that $\mathbb{E}_{\nu'}[N_i(t)] = \frac{t}{K}$, that is, every arm receives an equal amount of the budget.
-In that case, the above equation simplifies to
-
-$$
-- \frac{1}{t} \log p_t(\nu) \leq \frac{1}{t} \sum_{i=1}^K \frac{t}{K}\KL(\tau, \mu_i) = \frac{1}{K} \sum_{i=1}^{K} \KL(\tau, \mu_i),
-$$
-
-that is, the complexity is given by the simple average of the Kullback-Leibler distances of the threshold with regard to the respective distributions.
-This relates well to the lower bound that Kaufmann et al.
-(2016) describe in their Theorem 12 for consistent algorithms using *uniform* sampling strategies; in our case, however, it is explained by the fact that under the alternative model, every consistent algorithm should adapt to a uniform sampling strategy.
-Thus our bound holds for any consistent strategy.
-
-## Bayes-UCB Algorithm for the Thresholding Bandit Problem \label{sec:AppendixBUCB}
-
-We show how the Bayes-UCB algorithm (Algorithm 1, Kaufmann et al., 2012) is adapted to the thresholding bandit problem to be used in the experiments in chapter \autoref{chap:Experiments}.
+
+\section{Bayes-UCB Algorithm for the Thresholding Bandit Problem} \label{app:AppendixBUCB}
+
+We show how the Bayes-UCB algorithm (Algorithm 1, Kaufmann et al., 2012a) is adapted to the thresholding bandit problem to be used in the experiments in \autoref{chap:Experiments}.
 The adapted version of their Algorithm 1 is given in Algorithm 4 below.
@@
 See the setup in Kaufmann et al.
-(2012), especially equation (3), to see how the posterior distribution is updated in every round.
+(2012a), especially equation (3), to see how the posterior distribution is updated in every round.
 
@@
 }
-\caption{Bayes-UCB algorithm from Kaufmann et al. (2012) adapted to the thresholding bandit problem.}\label{bayesucb_tbp}
+\caption{Bayes-UCB algorithm from Kaufmann et al. (2012a) adapted to the thresholding bandit problem.}\label{bayesucb_tbp}
 \end{algorithm}\DecMargin{1em}
@@
 
-In order to assess the excellent performance of the Bayes-UCB algorithm, which comes at a surprise given that is is designed for the cumulative regret setting and thus should tend to explore the arms to less, we run the Bayes-UCB algorithm for simulation 2 with three different choices of the parameter.
-In Figure 13, we see the performance results of the three versions, whereas Figure 14 shows how the algorithm allocates its budget across the arms over time.
-The three versions differ in the quantile parameter $c$ (compare \autoref{sec:AppendixBUCB}) for which we choose $c \in \{1/5, 1, 5\}$ to explore more or less.
+In order to assess the excellent performance of the Bayes-UCB algorithm, which comes at a surprise given that is is designed for the cumulative regret setting and thus should tend to explore the arms less, we run the Bayes-UCB algorithm for simulation 2 with three different choices of the parameter $c$.
+In Figure 14, we see the performance results of the three versions, whereas Figure 15 shows how the algorithm allocates its budget across the arms over time.
+The three versions differ in the quantile parameter $c$ (compare \autoref{app:AppendixBUCB}) for which we choose $c \in \{1/5, 1, 5\}$ to explore more or less.
 In Kaufmann et al.
-(2012), the cumulative regret upper bound for the Bayes-UCB is shown for $c\geq 5$, though they report that the choice of $c=0$ worked much better in their experiments.
-In our problem, it makes also sense that the versions with smaller quantiles (smaller $c$) tend to perform better, as these correspond to more exploration of the arms.
+(2012a), the cumulative regret upper bound for the Bayes-UCB is shown for $c\geq 5$, though they report that the choice of $c=0$ worked much better in their experiments.
+In our problem, it also makes sense that the versions with smaller quantiles (smaller $c$) tend to perform better, as these correspond to more exploration of the arms.
 In this particular simulation, the choices of $c=1/5$ and $c=1$ perform very similar.
-We see that the worse performance of $c=5$ can be attributed to a initial phase of sampling primarily the arms with mean below the threshold.
+We see that the worse performance of $c=5$ can be attributed to a long initial phase of sampling primarily the arms with mean below the threshold.
 This comes from the fact that the Bernoulli and Beta distributions are bounded between $0$ and $1$, with $\tau$ very close to $0$.
@@
 For arms with $\hat{\mu}_i(t) < \tau$, however, the index can be as large as $B_i^{BUCB}(t) = 0.95$.
-This leads to the effect seen in Figure 14: Due to $c=5$, the indexes are based on very large quantiles even in the beginning, which leads to large indexes for the arms with small means.
+This leads to the effect seen in Figure 13: Due to $c=5$, the indexes are based on very large quantiles even in the beginning, which leads to large indexes for the arms with small means.
 This however is not the ideal sampling behavior.
@@
                             results = alg_res)
-ggplot(loc6nt_comp_res, aes(x = index, y = results)) + 
-  geom_line(aes(group = names, color = names)) +
+point_index <- seq(1,3*6991,by=1000)
+ggplot(loc6nt_comp_res, aes(x = index, y = results, 
+                            group = names, color = names, 
+                            shape = names)) +
+  geom_line() +
+  geom_point(aes(x = index, y = results, 
+                 group = names, shape = names),
+             loc6nt_comp_res[point_index,], size = 2.5) +
   geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
@@
   scale_color_discrete(name = "Algorithm") +
+  scale_shape_discrete(name = "Algorithm") +
   theme_bw() 
@@
 In the best case, an algorithm would sample an arm for the optimal share of the budget, in every simulation.
-This is of course not the case, since the number of pulls of a given arm at the end of the budget, $T_i(T)$, is a random variable for adaptive sampling strategies.
+This, of course, is not the case since the number of pulls of a given arm at the end of the budget, $T_i(T)$, is a random variable for adaptive sampling strategies.
 Given the 5000 iterations conducted in simulation 2, we can plot the empirical distribution of this random variable for different arms.
 
-In Figure 15, we show the distribution of $T_6(T)$ for algorithms APT, Bayes-UCB, and SLR.
+In Figure 16, we show the distribution of $T_6(T)$ for algorithms APT, Bayes-UCB, and SLR.
 We see that the distribution of the Bayes-UCB algorithm is much better concentrated around the optimal share of the budget, and has a bell curve shape.
 In contrast, the distributions of APT and SLR are much less concentrated but flat and wide, and spread across a very large interval.
-Both algorithms have several iterations in which they draw arm 6, the most difficult arm only a single time (during initialization).
-This happens for APT more than 5% of the iterations, and leads to the spike on the very left of the graph.
+Both algorithms have several iterations in which they draw arm 6--the most difficult arm--only a single time (during initialization).
+This happens for APT in more than 5% of the iterations, and leads to the spike on the very left of the graph.
 In order to cope at least a little bit with this problem, we have also run the SLR algorithm with the D-Tracking rule as introduced in Garivier and Kaufmann (2016).
-The effect is nearly not noticeable in Figure 15, but the minimum number of observations is not clearly bounded away from 0.
+The effect is barely noticeable in Figure 16, but the minimum number of observations is now clearly bounded away from 0.
 The effect on the performance was described before and is very noticeable in comparison to SLR without D-Tracking.
@@
 
-## SLR Algorithm with D-Tracking Rule
+\newpage
+
+\section{Simple Likelihood Ratio Algorithm with D-Tracking Rule} \label{app:SLRD}
 
@@
 
-## Means in Simulations 4 and 5
+\newpage
+
+\section{Means in Simulations 4 and 5} \label{app:MeansSim45}
 
@@
 ```
+
+\newpage
+
+\pagenumbering{gobble}
+
+\Large{\bf Selbstständigkeitserklärung\\}
+
+\vspace*{1.5\baselineskip}
+
+\large Ich erkläre hiermit, dass ich die vorliegende Arbeit selbstständig und nur unter Verwendung der angegebenen Quellen und Hilfsmittel angefertigt habe und noch nicht für andere Prüfungen eingereicht habe.
+Sämtliche Quellen einschließlich Internetquellen, die unverändert oder abgewandelt wiedergegeben werden, insbesondere Quellen für Texte, Grafiken, Tabellen und Bilder, sind als solche kenntlich gemacht.
+Mir ist bekannt, dass bei Verstößen gegen diese Grundsätze ein Verfahren wegen Täuschungsversuchs bzw.
+Täuschung eingeleitet wird.
+
+\vspace*{3\baselineskip}
+
+Berlin, den 18. September 2017

### 2017-09-18 Thesis/Draft.tex
final

@@
     {\large{\bf Prof. Dr. Marius Kloft \\}}
-    {\large{\bf Prof. Alexandra Carpentier, PhD \\}}
+    {\large{\bf Dr. Alexandra Carpentier \\}}
     \vspace{0.5cm}
@@
     for the degree of \\
-    {\bf Master of Science (M. Sc.)\\} \vspace{3cm}
+    {\bf Master of Science (M. Sc.) in Statistics\\} \vspace{3cm}
     Berlin, September 18, 2017\\}
@@
 like to find out two things: Does the restaurant have good service? Is
-the restaurant trendy? See \autoref{app:Foursquare} for how this
-information is then displayed in the Foursquare app.
+the restaurant trendy?
 
@@
 
-\section{Example of User Feedback in Foursquare App} \label{app:Foursquare}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{figures/Foursquare_Screenshot.png}
-\caption{The right screenshot shows aggregated user feedback in the
-Foursquare app. One could use thresholding bandit algorithms as
-presented in this thesis to ask different questions so as to optimize
-the confidence with which the results are displayed for a restaurant in
-the app.}
-\end{figure}
-
 \section{Proof of Theorem 2} \label{app:AppendixAPTLB}
@@
 algorithm makes on this problem.
+
+\newpage
 
@@
 Bayes-UCB algorithm for simulation 2 with three different choices of the
-parameter \(c\). In Figure 15, we see the performance results of the
-three versions, whereas Figure 16 shows how the algorithm allocates its
+parameter \(c\). In Figure 14, we see the performance results of the
+three versions, whereas Figure 15 shows how the algorithm allocates its
 budget across the arms over time. The three versions differ in the
@@
 arms with \(\hat{\mu}_i(t) < \tau\), however, the index can be as large
-as \(B_i^{BUCB}(t) = 0.95\). This leads to the effect seen in Figure 14:
+as \(B_i^{BUCB}(t) = 0.95\). This leads to the effect seen in Figure 13:
 Due to \(c=5\), the indexes are based on very large quantiles even in
@@
 
-In Figure 17, we show the distribution of \(T_6(T)\) for algorithms APT,
+In Figure 16, we show the distribution of \(T_6(T)\) for algorithms APT,
 Bayes-UCB, and SLR. We see that the distribution of the Bayes-UCB
@@
 the SLR algorithm with the D-Tracking rule as introduced in Garivier and
-Kaufmann (2016). The effect is barely noticeable in Figure 17, but the
+Kaufmann (2016). The effect is barely noticeable in Figure 16, but the
 minimum number of observations is now clearly bounded away from 0. The
